### 2015-03-03 inst/examples/summary.Rmd
ok

---
title: "Summary"
author: "Niko Ilomäki"
date: "Tuesday, March 3, 2015"
output: html_document
---

# Summary of the preprocessed Fennica data

## Annotated documents

Fraction of documents with entries for each annotation field.

```{r, annotations, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=10, fig.height=15}

library(stringr)

load(file="../../dfs.RData")

df <- df.summary

library(dplyr)
library(ggplot2)
missing <- 100*apply(df, 2, function (x) {mean(is.na(x))})
df3 <- data.frame(list(missing = missing, field = names(missing)))
df3$field <- factor(df3$field, levels = df3$field[rev(order(df3$missing))])
theme_set(theme_bw(15))
p <- ggplot(df3, aes(x = field, y = 100 - missing))
p <- p + geom_bar(stat = "identity")
p <- p + coord_flip()
p <- p + ylab("")
p <- p + xlab("")
p <- p + ggtitle("Documents with data (%)")
print(p)
```

## Topics

```{r, topics, echo=FALSE, message=FALSE, warning=FALSE}

load(file="../../dff.RData")

df <- df.full

# List all topics
spl <- strsplit(na.omit(as.character(df$term_tpc)), ";")

# Topics per document
# hist(sapply(spl, length))

# Documents per topic
tab <- sort(table(unlist(spl)))
tab <- tab[!names(tab) == "NA"]
tab <- rev(sort(tab)) 
```

```{r, topics2, echo=FALSE, message=FALSE, warning=FALSE}
# Write to file
f <- "output.tables/subjecttopics.tab"
print(paste("Complete subject topic counts in file:", f))
write.table(cbind(Topic = sort(names(tab))), file = f, sep = "\t", quote = F, row.names = F)
ntop <- 50
```

Top-`r ntop` topics and number of documents for each. In total, there are `r length(unique(df$term_tpc))` unique topics and `r sum(!is.na(df$term_tpc))` documents assigned to one or more topics (`r round(100*mean(!is.na(df$term_tpc)))`).

```{r, topics22, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=10}
par(mar = c(5, 10, 3, 1)); barplot(rev(rev(sort(table(df$term_tpc)))[1:ntop]), horiz = T, las = 1, cex.names = 0.8, xlab = "Documents", main = "Most common topics")
```

## Authors

Top-`r ntop` uniquely identified authors and number of documents for each (duplicate docs not checked yet).

```{r, authors, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=10}
ntop <- 50
a <- rev(rev(sort(table(df$author_nam)))[1:ntop])
par(mar = c(5, 10, 3, 1)); barplot(a, horiz = T, las = 1, cex.names = 0.8, xlab = "Documents", main = "Top authors")
```

## Subject geographical places

```{r, geo, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=10}
tab <- rev(sort(table(unlist(strsplit(as.character(df$term_geo), ";")))))
```

Top-`r ntop` geographical places are shown together with the number of documents assigned to that region. Geography information is available for `r sum(!is.na(df$term_geo))` documents (`r round(100*mean(!is.na(df$term_geo)))`%). There are `r length(tab)` unique geographical places.

```{r, geo2, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=10}
ntop <- 50
par(mar = c(5, 10, 3, 1)); barplot(log10(rev(tab[1:ntop])), horiz = T, las = 1, cex.names = 0.8, xlab = "Documents (log10)", main = "Most common geographic places")
```

```{r, geo3, echo=FALSE, message=FALSE, warning=FALSE}
f <- "output.tables/geoplaces.csv"
print(paste("Complete counts in file:", f))
write.table(cbind(Geography = names(tab), Documents = tab), file = f, sep = "|", quote = F, row.names = F)
```

## Publication

### Publication places

Top-`r ntop` publication places are shown together with the number of documents. This info is available for `r sum(!is.na(df$publication_plc))` documents (`r round(100*mean(!is.na(df$publication_plc)))`%). There are `r length(unique(str_trim(unlist(strsplit(as.character(df$publication_plc), ";")))))` unique publication places.

```{r, place, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=10}
tab <- rev(sort(table(str_trim(unlist(strsplit(as.character(df$publication_plc), ";"))))))
ntop <- 50
par(mar = c(5, 10, 3, 1)); barplot(log10(rev(tab[1:ntop])), horiz = T, las = 1, cex.names = 0.8, xlab = "Documents (log10)", main = "Most common publication places")
```

```{r, place2, echo=FALSE, message=FALSE, warning=FALSE}
f <- "output.tables/publicationplaces.csv"
print(paste("Complete counts in file:", f))
write.table(cbind(Place = names(tab), Documents = tab), file = f, sep = "|", quote = F, row.names = F)
```

### 2015-03-03 R/correct_misspellings.R

@@ -1,118 +1,0 @@
-correct_misspellings <- function(v) {
-	v[v %in% city$almena] <- "Almena WI"
-	v[v %in% city$altdorf] <- "Altdorf"
-	v[v %in% city$ashtabula] <- "Ashtabula OH"
-	v[v %in% city$astoria] <- "Astoria OR"
-	v[v %in% city$berliini] <- "Berliini"
-	v[v %in% city$boston] <- "Boston MA"
-	v[v %in% city$bridgeport] <- "Bridgeport CT"
-	v[v %in% city$bronx] <- "Bronx NY"
-	v[v %in% city$brooklyn] <- "Brooklyn NY"
-	v[v %in% city$calumet] <- "Calumet MI"
-	v[v %in% city$chicago] <- "Chicago IL"
-	v[v %in% city$chisholm] <- "Chisholm MN"
-	v[v %in% city$cincinnati] <- "Cincinnati OH"
-	v[v %in% city$cleveland] <- "Cleveland OH"
-	v[v %in% city$duluth] <- "Duluth MN"
-	v[v %in% city$espoo] <- "Espoo"
-	v[v %in% city$fitchburg] <- "Fitchburg MA"
-	v[v %in% city$giessen] <- "Giessen"
-	v[v %in% city$goteborg] <- "Göteborg"
-	v[v %in% city$gottingen] <- "Göttingen"
-	v[v %in% city$greifswald] <- "Greifswald"
-	v[v %in% city$haaparanta] <- "Haaparanta"
-	v[v %in% city$hamina] <- "Hamina"
-	v[v %in% city$hampuri] <- "Hampuri"
-	v[v %in% city$hancock] <- "Hancock MI"
-	v[v %in% city$hanko] <- "Hanko"
-	v[v %in% city$helsinki] <- "Helsinki"
-	v[v %in% city$hameenlinna] <- "Hämeenlinna"
-	v[v %in% city$ironwood] <- "Ironwood MI"
-	v[v %in% city$ishpeming] <- "Ishpeming MI"
-	v[v %in% city$jena] <- "Jena"
-	v[v %in% city$jyvaskyla] <- "Jyväskylä"
-	v[v %in% city$kaleva] <- "Kaleva MI"
-	v[v %in% city$kaliningrad] <- "Kaliningrad"
-	v[v %in% city$karjaa] <- "Karjaa"
-	v[v %in% city$kaskinen] <- "Kaskinen"
[…]

### 2015-03-03 inst/examples/city.R

@@ -1,124 +1,246 @@
-city <- new.env()
+source("R/placenames.R", encoding="UTF-8")
 
-city$almena <- collect_misspellings(df$publication@place,c("Almena","Almena WI","Almena Wis","Almena Wisconsin"))
-city$altdorf <- collect_misspellings(df$publication@place,c("Altdorf"))
-city$ashtabula <- collect_misspellings(df$publication@place,c("Ashtabula","Ashtabula OH","Ashtabula Ohio"))
-city$astoria <- collect_misspellings(df$publication@place,c("Astoria","Astoria OR","Astoria Ore","Astoria Oregon"))
-city$berliini <- collect_misspellings(df$publication@place,c("Berliini","Berlin"))
-city$boston <- collect_misspellings(df$publication@place,c("Boston","Boston MA","Boston Mass","Boston Massachusetts"))
-city$bridgeport <- collect_misspellings(df$publication@place,c("Bridgeport","Bridgeport CT","Bridgeport Conn","Bridgeport Connecticut"))
-city$bronx <- collect_misspellings(df$publication@place,c("Bronx","Bronx NY","Bronx New York"))
-city$brooklyn <- collect_misspellings(df$publication@place,c("Brooklyn","Brooklyn NY","Brooklyn New York"))
-city$calumet <- collect_misspellings(df$publication@place,c("Calumet","Calumet MI","Calumet Mich","Calumet Michigan"))
-city$chicago <- collect_misspellings(df$publication@place,c("Chicago","Chicago IL","Chicago Ill","Chicago Illinois"))
-city$chisholm <- collect_misspellings(df$publication@place,c("Chisholm","Chisholm MN","Chisholm Minn","Chisholm Minnesota"))
-city$cincinnati <- collect_misspellings(df$publication@place,c("Cincinnati","Cincinnati OH","Cincinnati Ohio"))
-city$cleveland <- collect_misspellings(df$publication@place,c("Cleveland","Cleveland OH","Cleveland Ohio"))
-city$duluth <- collect_misspellings(df$publication@place,c("Duluth","Duluth MN","Duluth Minn","Duluth Minnesota"))
-city$espoo <- collect_misspellings(df$publication@place,c("Espoo","Esbo"))
-city$fitchburg <- collect_misspellings(df$publication@place,c("Fitchburg","Fitchburg MA","Fitchburg Mass","Fitchburg Massachusetts"))
[…]

### 2015-03-03 inst/examples/phase2.R

@@ -1,0 +1,28 @@
+library(dplyr)
+
+source("R/AllClasses.R", encoding="UTF-8")
+source("R/editing.R", encoding = "UTF-8")
+
+print("Start collecting variables to a polished data frame")
+
+df <- data.frame(list(row.index = 1:size_global))
+
+df$language <- new("Lingua", embellish(combine(df.orig[["041a"]],df.orig[["041h"]])))
+df$author <- new("Auctor", embellish(combine(df.orig[["100a"]],df.orig[["100d"]])),
+	name=embellish(df.orig[["100a"]]), date=embellish(df.orig[["100d"]]))
+df$title <- new("Titulus", embellish(combine(df.orig[["240a"]],df.orig[["245a"]],df.orig[["245b"]])),
+	uniform=embellish(df.orig[["240a"]]), proper=embellish(df.orig[["245a"]]), remainder=embellish(df.orig[["245b"]]))
+df$publication <- new("Publicus", embellish(combine(df.orig[["260a"]],df.orig[["260b"]],df.orig[["260c"]],df.orig[["310a"]],df.orig[["362a"]])),
+	place=embellish(df.orig[["260a"]]), publisher=embellish(df.orig[["260b"]]), time=embellish(df.orig[["260c"]]), frequency=embellish(df.orig[["310a"]]),
+	interval=embellish(df.orig[["362a"]]))
+df$physical <- new("Physica", embellish(combine(df.orig[["300a"]],df.orig[["300b"]],df.orig[["300c"]],df.orig[["300e"]])),
+	extent=embellish(df.orig[["300a"]]), details=embellish(df.orig[["300b"]]), dimension=embellish(df.orig[["300c"]]), accomppanied=embellish(df.orig[["300e"]]))
+df$note <- new("Nota", embellish(combine(df.orig[["500a"]],df.orig[["502a"]],df.orig[["502c"]],df.orig[["502d"]],df.orig[["510a"]],df.orig[["510c"]])),
+	general=embellish(df.orig[["500a"]]), dissertation=embellish(df.orig[["502a"]]), granter=embellish(df.orig[["502c"]]), year=embellish(df.orig[["502d"]]),
+	source=embellish(df.orig[["510a"]]), location=embellish(df.orig[["510c"]]))
+df$term <- new("Terminus", embellish(combine(df.orig[["650a"]],df.orig[["651a"]])),
[…]

### 2015-03-22 inst/examples/Vaasa.Rmd
Vaasa

---
title: "Julkaisutoiminta Vaasassa 1764-1917"
author: "Niko Ilomäki"
date: "`r Sys.Date()`"
output: markdown_document
---

```{r, echo=FALSE, message=FALSE}
library(dplyr)
```

```{r, echo=FALSE}
# data ei välttämättä lopullinen
df <- readRDS("df.Rdata")
vaasa <- df %>% filter(city == "Vaasa") %>% group_by(published_in) %>% tally() %>% arrange(published_in)
```

```{r, echo=FALSE, fig.width=20, fig.height=10}
plot(vaasa$published_in,vaasa$n,pch="_",cex.main=2,main="Julkaisutoiminta Vaasassa 1764-1917",cex.lab=1.5,xlab="vuosi",ylab="dokumenttia",axes=FALSE)
axis(side = 1, at = c(1764,1809,1863,1917))
axis(side = 2, at = c(0,25,50,75,100,125,150,175,194))
```

### 2015-03-22 inst/examples/Vaasa.Rmd
Vaasa, osa 2

@@
 
-```{r, echo=FALSE}
+```{r, echo=FALSE, message=FALSE}
 # data ei välttämättä lopullinen
 df <- readRDS("df.Rdata")
-vaasa <- df %>% filter(city == "Vaasa") %>% group_by(published_in) %>% tally() %>% arrange(published_in)
+df <- df %>% filter(!is.na(published_in))
+vaasa1 <- df %>% filter(city == "Vaasa") %>% group_by(published_in) %>% tally() %>% arrange(published_in)
+vaasa1$decade <- as.numeric(paste0(substr(vaasa1$published_in,1,3),"0"))
+vaasa2 <- vaasa1 %>% group_by(decade) %>% summarise(m = sum(n)/10)
+vaasa <- inner_join(vaasa1,vaasa2)
 ```
@@
 ```{r, echo=FALSE, fig.width=20, fig.height=10}
-plot(vaasa$published_in,vaasa$n,pch="_",cex.main=2,main="Julkaisutoiminta Vaasassa 1764-1917",cex.lab=1.5,xlab="vuosi",ylab="dokumenttia",axes=FALSE)
+par(las=1)
+par(mar=c(8,8,5,3))
+plot(vaasa$published_in,vaasa$n,pch="_",cex.main=3,main="Julkaisutoiminta Vaasassa 1764-1917",cex.lab=2.5,xlab="vuosi",ylab="dokumenttia",cex.axis=2,axes=FALSE,col="black")
+lines(vaasa$published_in,vaasa$m,type="l",lty=3,col="grey",lwd=2.5)
 axis(side = 1, at = c(1764,1809,1863,1917))

### 2015-03-22 R/placenames.R

@@ -12,7 +12,7 @@ collect_misspellings <- function (city, variations, all) {
 			}
 		}
 	}
-	write.csv2(variations, file=paste0("inst/examples/output.tables/city_",city,".csv"), fileEncoding="UTF-8")
+	write.csv2(variations, file=paste0("output.tables/city_",city,".csv"), fileEncoding="UTF-8")
 	for (x in variations){
 		all <- all[which(all!=get("x"))]
 	}
@@ -138,7 +138,7 @@ preprocess_placenames <- function(df.orig, df) {
 }
 
 correct_misspellings <- function(v,filename,correct) {
-	synonyms <- read.csv2(paste0("inst/examples/output.tables/city_",filename,".csv"),header=FALSE,encoding="UTF-8")
+	synonyms <- read.csv2(paste0("output.tables/city_",filename,".csv"),header=FALSE,encoding="UTF-8")
 	synonyms <- unlist(synonyms[[2]])
 	v[v %in% synonyms] <- correct
 

### 2015-03-22 R/plots.R

@@ -2,11 +2,11 @@ counts_total <- function(ldf) {
   f <- ldf %>% group_by(publication_tia) %>% tally() %>% arrange(publication_tia)
   f$cumul <- cumsum(f$n)
   
-  png("inst/examples/figure/total_noncumul.png")
+  png("figure/total_noncumul.png")
   plot(f$publication_tia,f$n)
   dev.off()
   
-  png("inst/examples/figure/total_cumul.png")
+  png("figure/total_cumul.png")
   plot(f$publication_tia,f$cumul)
   dev.off()
   
@@ -16,11 +16,11 @@ counts_by_town <- function(ldf, str, file) {
   f <- ldf %>% filter(publication_plc == str) %>% group_by(publication_tia) %>% tally() %>% arrange(publication_tia)
   f$cumul <- cumsum(f$n)
   
-  png(paste0("inst/examples/figure/",file,"_noncumul.png"))
+  png(paste0("figure/",file,"_noncumul.png"))
   plot(f$publication_tia,f$n)
   dev.off()
   
-  png(paste0("inst/examples/figure/",file,"_cumul.png"))
+  png(paste0("figure/",file,"_cumul.png"))
   plot(f$publication_tia,f$cumul)
   dev.off()
 }
@@ -29,11 +29,11 @@ counts_by_language <- function(ldf, str, file) {
   f <- ldf %>% filter(ldf[,get("str")] == 1) %>% group_by(publication_tia) %>% tally() %>% arrange(publication_tia)
   f$cumul <- cumsum(f$n)
   
-  png(paste0("inst/examples/figure/",file,"_noncumul.png"))
+  png(paste0("figure/",file,"_noncumul.png"))
   plot(f$publication_tia,f$n)
   dev.off()
   
-  png(paste0("inst/examples/figure/",file,"_cumul.png"))
+  png(paste0("figure/",file,"_cumul.png"))
   plot(f$publication_tia,f$cumul)
   dev.off()
 }

### 2015-03-22 inst/examples/city.R

@@ -1,4 +1,4 @@
-source("R/placenames.R", encoding="UTF-8")
+source("../../R/placenames.R", encoding="UTF-8")
 
 unique_cities <- unique(df$city)
 
@@ -107,7 +107,7 @@ unique_cities <- collect_misspellings("vasteros",c("Västerås","Arosia","Arosie
 unique_cities <- collect_misspellings("wittenberg",c("Wittenberg","Wittenbergae"),unique_cities)
 unique_cities <- collect_misspellings("worcester",c("Worcester","Worcester MA","Worcester Mass","Worcester Massachusetts"),unique_cities)
 
-write(unique_cities, file="inst/examples/output.tables/city_others.csv")
+write(unique_cities, file="output.tables/city_others.csv")
 
 # -------------------------------------------------------------------------------------------------------------------------------------------------------------
 

### 2015-03-22 inst/examples/phase1.R

@@ -5,13 +5,13 @@
 # Load R package
 # library(fennica)
 
-fennica.data.file <- "inst/examples/data/fennica.csv.gz"
-output.folder <- "inst/examples/output.tables/"
+fennica.data.file <- "data/fennica.csv.gz"
+output.folder <- "output.tables/"
 
 # Create the output directory if not yet exists
 dir.create(output.folder)
 
-source("R/data.R")
+source("../../R/data.R")
 print("Read raw data")
 df.raw <- read_fennica_data(fennica.data.file)
 data_size <- nrow(df.raw)

### 2015-03-22 inst/examples/phase3.R

@@ -4,13 +4,13 @@ df <- tbl_df(data.frame(list(row.index = 1:data_size)))
 # ---------------------------------------------
 
 print("Languages")
-source("R/languages.R", encoding = "UTF-8")
+source("../../R/languages.R", encoding = "UTF-8")
 df <- mark_languages(df.orig, df)
 
 # ---------------------------------------------
 
 print("Author data")
-source("R/author.R", encoding="UTF-8")
+source("../../R/author.R", encoding="UTF-8")
 df <- fix_family(df.orig, df)
 df <- fix_first(df.orig, df)
 df <- fix_other(df.orig, df)
@@ -27,13 +27,13 @@ df$title_remainder <- df.orig$title_remainder
 # ---------------------------------------------
 
 print("Publication data")
-source("R/placenames.R", encoding = "UTF-8")
+source("../../R/placenames.R", encoding = "UTF-8")
 df <- preprocess_placenames(df.orig, df)
-source("inst/examples/city.R", encoding = "UTF-8") # later account for multiple places
+source("city.R", encoding = "UTF-8") # later account for multiple places
 df <- deduce_country(df)
-source("R/house.R", encoding = "UTF-8")
+source("../../R/house.R", encoding = "UTF-8")
 df <- fix_pubhouses(df.orig, df)
-source("R/time.R", encoding = "UTF-8")
+source("../../R/time.R", encoding = "UTF-8")
 df <- fix_pubwhen(df.orig, df)
 df <- fix_pubfrom(df.orig, df)
 df <- fix_pubtill(df.orig, df)
@@ -51,7 +51,7 @@ df$physical_accomppanied <- df.orig$physical_accomppanied
 # ---------------------------------------------
 
 print("Notes")
-source("R/notes.R", encoding = "UTF-8")
+source("../../R/notes.R", encoding = "UTF-8")
 df$note_general <- df.orig$note_general
 df <- fix_note_diss(df.orig, df)
 df <- fix_university(df.orig, df)

### 2015-03-22 inst/examples/Vaasa.Rmd
Vaasa, osa 3

@@
 par(mar=c(8,8,5,3))
-plot(vaasa$published_in,vaasa$n,pch="_",cex.main=3,main="Julkaisutoiminta Vaasassa 1764-1917",cex.lab=2.5,xlab="vuosi",ylab="dokumenttia",cex.axis=2,axes=FALSE,col="black")
-lines(vaasa$published_in,vaasa$m,type="l",lty=3,col="grey",lwd=2.5)
-axis(side = 1, at = c(1764,1809,1863,1917))
-axis(side = 2, at = c(0,25,50,75,100,125,150,175,194))
+plot(vaasa$published_in,vaasa$n,pch="_",cex.main=3,main="Julkaisutoiminta Vaasassa 1764-1917",cex.lab=2,xlab="",ylab="Dokumenttia / vuosi",axes=FALSE,col="black")
+lines(vaasa$published_in,vaasa$m,type="l",lty=3,col="darkgrey",lwd=2.5)
+axis(side = 1, at = c(1764,1809,1863,1917),cex.axis=1.5)
+axis(side = 2, at = c(0,20,40,60,80,100,120,140,160,180,194),cex.axis=1.2)
 ```
+
+```{r, echo=FALSE, fig.width=20, fig.height=10}
+par(las=1)
+par(mar=c(8,8,5,3))
+plot(vaasa$published_in,vaasa$n,pch="_",cex.main=3,main="Julkaisutoiminta Vaasassa 1764-1917",cex.lab=2,xlab="",ylab="Dokumenttia / vuosi",axes=FALSE,col="black")
+lines(vaasa$published_in,vaasa$m,type="l",lty=3,col="darkgrey",lwd=2.5)
+axis(side = 1, at = c(1764,1780,1800,1820,1840,1860,1880,1900,1917),cex.axis=1.5)
+axis(side = 2, at = c(0,20,40,60,80,100,120,140,160,180,194),cex.axis=1.2)
+```

### 2015-03-22 inst/examples/Vaasa.Rmd
Vaasa, osa 4

--- 2015-03-22 inst/examples/Vaasa.Rmd
@@
 par(las=1)
+par(mgp=c(6,2,0))
 par(mar=c(8,8,5,3))
-plot(vaasa$published_in,vaasa$n,pch="_",cex.main=3,main="Julkaisutoiminta Vaasassa 1764-1917",cex.lab=2.5,xlab="vuosi",ylab="dokumenttia",cex.axis=2,axes=FALSE,col="black")
-lines(vaasa$published_in,vaasa$m,type="l",lty=3,col="grey",lwd=2.5)
-axis(side = 1, at = c(1764,1809,1863,1917))
-axis(side = 2, at = c(0,25,50,75,100,125,150,175,194))
+plot(vaasa$published_in,vaasa$n,pch="_",cex.main=3.2,main="Julkaisutoiminta Vaasassa 1764-1917",cex.lab=2.4,xlab="",ylab="Dokumenttia / vuosi",axes=FALSE,col="black")
+lines(vaasa$published_in,vaasa$m,type="l",lty=3,col="darkgrey",lwd=4)
+axis(side = 1, at = c(1764,1809,1863,1917),cex.axis=3.2)
+axis(side = 2, at = c(0,20,40,60,80,100,120,140,160,180,194),cex.axis=2.4)
 ```
+
+```{r, echo=FALSE, fig.width=20, fig.height=10}
+par(las=1)
+par(mgp=c(6,2,0))
+par(mar=c(8,8,5,3))
+plot(vaasa$published_in,vaasa$n,pch="_",cex.main=3.2,main="Julkaisutoiminta Vaasassa 1764-1917",cex.lab=2.4,xlab="",ylab="Dokumenttia / vuosi",axes=FALSE,col="black")
+lines(vaasa$published_in,vaasa$m,type="l",lty=3,col="darkgrey",lwd=4)
+axis(side = 1, at = c(1764,1780,1800,1820,1840,1860,1880,1900,1917),cex.axis=3.2)
+axis(side = 2, at = c(0,20,40,60,80,100,120,140,160,180,194),cex.axis=2.4)
+```

### 2015-03-22 inst/examples/Vaasa.Rmd
Vaasa, osa 5

--- 2015-03-22 inst/examples/Vaasa.Rmd
@@
 par(las=1)
-par(mar=c(8,8,5,3))
-plot(vaasa$published_in,vaasa$n,pch="_",cex.main=3,main="Julkaisutoiminta Vaasassa 1764-1917",cex.lab=2.5,xlab="vuosi",ylab="dokumenttia",cex.axis=2,axes=FALSE,col="black")
-lines(vaasa$published_in,vaasa$m,type="l",lty=3,col="grey",lwd=2.5)
-axis(side = 1, at = c(1764,1809,1863,1917))
-axis(side = 2, at = c(0,25,50,75,100,125,150,175,194))
+par(mgp=c(7,2,0))
+par(mar=c(8,13,5,3))
+plot(vaasa$published_in,vaasa$n,pch="|",cex.main=3.2,main="Julkaisutoiminta Vaasassa 1764-1917",cex.lab=3.2,xlab="",ylab="Dokumenttia / vuosi",axes=FALSE,col="black")
+lines(vaasa$published_in,vaasa$m,type="l",lty=3,col="black",lwd=4)
+axis(side = 1, at = c(1764,1809,1863,1917),cex.axis=3.2)
+axis(side = 2, at = c(0,40,80,120,160,194),cex.axis=3.2)
 ```
+
+```{r, echo=FALSE, fig.width=20, fig.height=10}
+par(las=1)
+par(mgp=c(7,2,0))
+par(mar=c(8,13,5,3))
+plot(vaasa$published_in,vaasa$n,pch="|",cex.main=3.2,main="Julkaisutoiminta Vaasassa 1764-1917",cex.lab=3.2,xlab="",ylab="Dokumenttia / vuosi",axes=FALSE,col="black")
+lines(vaasa$published_in,vaasa$m,type="l",lty=3,col="black",lwd=4)
+axis(side = 1, at = c(1764,1780,1800,1820,1840,1860,1880,1900,1917),cex.axis=3.2)
+axis(side = 2, at = c(0,40,80,120,160,194),cex.axis=3.2)
+```

### 2015-03-22 inst/examples/Vaasa.Rmd
Vaasa, osa 6

@@
 par(mar=c(8,13,5,3))
-plot(vaasa$published_in,vaasa$n,pch="|",cex.main=3.2,main="Julkaisutoiminta Vaasassa 1764-1917",cex.lab=3.2,xlab="",ylab="Dokumenttia / vuosi",axes=FALSE,col="black")
+plot(vaasa$published_in,vaasa$n,cex=1.8,pch="|",cex.main=3.2,main="Julkaisutoiminta Vaasassa 1764-1917",cex.lab=3.2,xlab="",ylab="Dokumenttia / vuosi",axes=FALSE,col="black")
 lines(vaasa$published_in,vaasa$m,type="l",lty=3,col="black",lwd=4)

### 2015-03-22 inst/examples/Vaasa.Rmd
Vaasa, osa 7

--- 2015-03-22 inst/examples/Vaasa.Rmd
@@
 par(las=1)
-par(mgp=c(7,2,0))
-par(mar=c(8,13,5,3))
-plot(vaasa$published_in,vaasa$n,pch="|",cex.main=3.2,main="Julkaisutoiminta Vaasassa 1764-1917",cex.lab=3.2,xlab="",ylab="Dokumenttia / vuosi",axes=FALSE,col="black")
+par(mgp=c(10,3,0))
+par(mar=c(7,17,6,4))
+plot(vaasa$published_in,vaasa$n,cex=1.8,pch="|",cex.main=5.0,main="Julkaisutoiminta Vaasassa 1764-1917",cex.lab=5.0,xlab="",ylab="Dokumenttia / vuosi",axes=FALSE,col="black")
 lines(vaasa$published_in,vaasa$m,type="l",lty=3,col="black",lwd=4)
@@
 par(las=1)
-par(mgp=c(7,2,0))
-par(mar=c(8,13,5,3))
-plot(vaasa$published_in,vaasa$n,pch="|",cex.main=3.2,main="Julkaisutoiminta Vaasassa 1764-1917",cex.lab=3.2,xlab="",ylab="Dokumenttia / vuosi",axes=FALSE,col="black")
+par(mgp=c(10,3,0))
+par(mar=c(7,17,6,4))
+plot(vaasa$published_in,vaasa$n,cex=1.8,pch="|",cex.main=5.0,main="Julkaisutoiminta Vaasassa 1764-1917",cex.lab=5.0,xlab="",ylab="Dokumenttia / vuosi",axes=FALSE,col="black")
 lines(vaasa$published_in,vaasa$m,type="l",lty=3,col="black",lwd=4)
-axis(side = 1, at = c(1764,1780,1800,1820,1840,1860,1880,1900,1917),cex.axis=3.2)
+axis(side = 1, at = c(1764,1800,1840,1880,1917),cex.axis=3.2)
 axis(side = 2, at = c(0,40,80,120,160,194),cex.axis=3.2)

### 2015-03-24 inst/examples/Helsinki.Rmd
More case studies

---
title: "Julkaisutoiminta Helsingissä 1746-1917"
author: "Niko Ilomäki"
date: "`r Sys.Date()`"
output: markdown_document
---

```{r, echo=FALSE, message=FALSE}
library(dplyr)
```

```{r, echo=FALSE, message=FALSE}
# data ei välttämättä lopullinen
df <- readRDS("df.Rdata")
df <- df %>% filter(!is.na(published_in))
tmp1 <- df %>% filter(city == "Helsinki") %>% group_by(published_in) %>% tally() %>% arrange(published_in)
tmp1$decade <- as.numeric(paste0(substr(tmp1$published_in,1,3),"0"))
tmp2 <- tmp1 %>% group_by(decade) %>% summarise(m = sum(n)/10)
final <- inner_join(tmp1,tmp2)
```

```{r Helsinki, echo=FALSE, fig.width=20, fig.height=10}
par(las=1)
par(mgp=c(10,3,0))
par(mar=c(7,17,6,4))
plot(final$published_in,final$n,cex=1.8,pch="|",cex.main=5.0,main="Julkaisutoiminta Helsingissä 1746-1917",cex.lab=5.0,xlab="",ylab="Dokumenttia / vuosi",axes=FALSE,col="black")
lines(final$published_in,final$m,type="l",lty=3,col="black",lwd=4)
axis(side = 1, at = c(1746,1809,1863,1917),cex.axis=3.2)
axis(side = 2, at = c(0,250,500,750,1000,1159),cex.axis=3.2)
```

```{r, echo=FALSE}
remove(tmp1,tmp2,final)
```

### 2015-03-24 inst/examples/Suomi.Rmd
More case studies

---
title: "Julkaisutoiminta Suomessa 1640-1917"
author: "Niko Ilomäki"
date: "`r Sys.Date()`"
output: markdown_document
---

```{r, echo=FALSE, message=FALSE}
library(dplyr)
```

```{r, echo=FALSE, message=FALSE}
# data ei välttämättä lopullinen
df <- readRDS("df.Rdata")
df <- df %>% filter(!is.na(published_in))
tmp1 <- df %>% filter(country == "Suomi") %>% group_by(published_in) %>% tally() %>% arrange(published_in)
tmp1$decade <- as.numeric(paste0(substr(tmp1$published_in,1,3),"0"))
tmp2 <- tmp1 %>% group_by(decade) %>% summarise(m = sum(n)/10)
final <- inner_join(tmp1,tmp2)
```

```{r Suomi, echo=FALSE, fig.width=20, fig.height=10}
par(las=1)
par(mgp=c(10,3,0))
par(mar=c(7,17,6,4))
plot(final$published_in,final$n,cex=1.8,pch="|",cex.main=5.0,main="Julkaisutoiminta Suomessa 1640-1917",cex.lab=5.0,xlab="",ylab="Dokumenttia / vuosi",axes=FALSE,col="black")
lines(final$published_in,final$m,type="l",lty=3,col="black",lwd=4)
axis(side = 1, at = c(1640,1809,1863,1917),cex.axis=3.2)
axis(side = 2, at = c(0,400,800,1200,1600,1874),cex.axis=3.2)
```

```{r, echo=FALSE}
remove(tmp1,tmp2,final)
```

### 2015-03-24 inst/examples/Turku.Rmd
More case studies

---
title: "Julkaisutoiminta Turussa 1640-1917"
author: "Niko Ilomäki"
date: "`r Sys.Date()`"
output: markdown_document
---

```{r, echo=FALSE, message=FALSE}
library(dplyr)
```

```{r, echo=FALSE, message=FALSE}
# data ei välttämättä lopullinen
df <- readRDS("df.Rdata")
df <- df %>% filter(!is.na(published_in))
tmp1 <- df %>% filter(city == "Turku") %>% group_by(published_in) %>% tally() %>% arrange(published_in)
tmp1$decade <- as.numeric(paste0(substr(tmp1$published_in,1,3),"0"))
tmp2 <- tmp1 %>% group_by(decade) %>% summarise(m = sum(n)/10)
final <- inner_join(tmp1,tmp2)
```

```{r Turku, echo=FALSE, fig.width=20, fig.height=10}
par(las=1)
par(mgp=c(10,3,0))
par(mar=c(7,17,6,4))
plot(final$published_in,final$n,cex=1.8,pch="|",cex.main=5.0,main="Julkaisutoiminta Turussa 1640-1917",cex.lab=5.0,xlab="",ylab="Dokumenttia / vuosi",axes=FALSE,col="black")
lines(final$published_in,final$m,type="l",lty=3,col="black",lwd=4)
axis(side = 1, at = c(1640,1809,1863,1917),cex.axis=3.2)
axis(side = 2, at = c(0,35,70,105,140,169),cex.axis=3.2)
```

```{r, echo=FALSE}
remove(tmp1,tmp2,final)
```

### 2015-03-24 inst/examples/knit_all.R

@@ -1,0 +1,4 @@
+knit2html("Helsinki.Rmd", encoding="UTF-8")
+knit2html("Suomi.Rmd", encoding="UTF-8")
+knit2html("Turku.Rmd", encoding="UTF-8")
+knit2html("Vaasa.Rmd", encoding="UTF-8")

### 2015-05-10 inst/examples/suvut.Rmd
suvut example

---
title: "Suvut"
author: "Niko Ilomäki"
date: "`r Sys.Date()`"
output: markdown_document
---

```{r, echo=FALSE, message=FALSE}
library(dplyr)
library(ggplot2)
library(stringr)
```

```{r, annotations, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=10, fig.height=15}
df <- readRDS("df.Rdata")
df <- df %>% filter(!is.na(family_name))
df2 <- df %>% group_by(family_name) %>% summarise(members = n_distinct(first_name))
df2 <- df2 %>% filter(members > 10) %>% arrange(desc(members))
theme_set(theme_bw(15))
df2$extra <- reorder(df2$family_name, df2$members)
p <- ggplot(df2, aes(x=family_name, y=members))
p <- p + geom_bar(aes(x=extra), data=df2, stat = "identity")
p <- p + coord_flip()
p <- p + ylab("")
p <- p + xlab("")
p <- p + ggtitle("Etunimiä per sukunimi")
print(p)
```

### 2015-05-10 inst/examples/summary.Rmd
pdf
fixed summary.Rmd

@@
 date: "Tuesday, March 3, 2015"
-output: html_document
+output: markdown_document
 ---
@@
 library(stringr)
-
-load(file="../../dfs.RData")
-
-df <- df.summary
-
 library(dplyr)
 library(ggplot2)
+
+df <- readRDS("df.RData")
+
 missing <- 100*apply(df, 2, function (x) {mean(is.na(x))})
-df3 <- data.frame(list(missing = missing, field = names(missing)))
-df3$field <- factor(df3$field, levels = df3$field[rev(order(df3$missing))])
+df2 <- data.frame(list(missing = missing, field = names(missing)))
+df2$field <- factor(df2$field, levels = df2$field[rev(order(df3$missing))])
 theme_set(theme_bw(15))
-p <- ggplot(df3, aes(x = field, y = 100 - missing))
+p <- ggplot(df2, aes(x = field, y = 100 - missing))
 p <- p + geom_bar(stat = "identity")
@@
 
-load(file="../../dff.RData")
-
-df <- df.full
-
 # List all topics
-spl <- strsplit(na.omit(as.character(df$term_tpc)), ";")
+spl <- strsplit(na.omit(as.character(df$term_topic)), ";")
 
@@
 Top-`r ntop` topics and number of documents for each.
-In total, there are `r length(unique(df$term_tpc))` unique topics and `r sum(!is.na(df$term_tpc))` documents assigned to one or more topics (`r round(100*mean(!is.na(df$term_tpc)))`).
+In total, there are `r length(unique(df$term_topic))` unique topics and `r sum(!is.na(df$term_topic))` documents assigned to one or more topics (`r round(100*mean(!is.na(df$term_topic)))`).
 
 ```{r, topics22, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=10}
-par(mar = c(5, 10, 3, 1)); barplot(rev(rev(sort(table(df$term_tpc)))[1:ntop]), horiz = T, las = 1, cex.names = 0.8, xlab = "Documents", main = "Most common topics")
+par(mar = c(5, 10, 3, 1)); barplot(rev(rev(sort(table(df$term_topic)))[1:ntop]), horiz = T, las = 1, cex.names = 0.8, xlab = "Documents", main = "Most common topics")
 ```
@@
 ntop <- 50
-a <- rev(rev(sort(table(df$author_nam)))[1:ntop])
+a <- rev(rev(sort(table(paste(df$author_family,df$author_first,sep=", "))))[1:ntop])
 par(mar = c(5, 10, 3, 1)); barplot(a, horiz = T, las = 1, cex.names = 0.8, xlab = "Documents", main = "Top authors")
@@
 ```{r, geo, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=10}
-tab <- rev(sort(table(unlist(strsplit(as.character(df$term_geo), ";")))))
+tab <- rev(sort(table(unlist(strsplit(as.character(df$term_geography), ";")))))
 ```
@@
 Top-`r ntop` geographical places are shown together with the number of documents assigned to that region.
-Geography information is available for `r sum(!is.na(df$term_geo))` documents (`r round(100*mean(!is.na(df$term_geo)))`%).
+Geography information is available for `r sum(!is.na(df$term_geography))` documents (`r round(100*mean(!is.na(df$term_geography)))`%).
 There are `r length(tab)` unique geographical places.
@@
 Top-`r ntop` publication places are shown together with the number of documents.
-This info is available for `r sum(!is.na(df$publication_plc))` documents (`r round(100*mean(!is.na(df$publication_plc)))`%).
-There are `r length(unique(str_trim(unlist(strsplit(as.character(df$publication_plc), ";")))))` unique publication places.
+This info is available for `r sum(!is.na(df$city))` documents (`r round(100*mean(!is.na(df$city)))`%).
+There are `r length(unique(str_trim(unlist(strsplit(as.character(df$city), ";")))))` unique publication places.
 
 ```{r, place, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=10}
-tab <- rev(sort(table(str_trim(unlist(strsplit(as.character(df$publication_plc), ";"))))))
+tab <- rev(sort(table(str_trim(unlist(strsplit(as.character(df$city), ";"))))))
 ntop <- 50

### 2015-05-10 inst/examples/do_all.R

@@ -1,0 +1,3 @@
+source("phase1.R",encoding="UTF-8")
+source("phase2.R",encoding="UTF-8")
+source("phase3.R",encoding="UTF-8")

### 2015-05-10 inst/examples/phase3.R

@@ -76,3 +76,5 @@ df$holder <- df.orig$holder
 # ---------------------------------------------
 
 df <- df[,-1]
+
+saveRDS(df, "df.RData")

### 2015-05-10 inst/examples/summary.Rmd
Rmd fixes

@@
 
-```{r, annotations, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=10, fig.height=15}
+```{r missing, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=10, fig.height=15}
 
@@
 df2 <- data.frame(list(missing = missing, field = names(missing)))
-df2$field <- factor(df2$field, levels = df2$field[rev(order(df3$missing))])
+df2$field <- factor(df2$field, levels = df2$field[rev(order(df2$missing))])
 theme_set(theme_bw(15))
@@
 
-```{r, topics, echo=FALSE, message=FALSE, warning=FALSE}
+```{r topics1, topics, echo=FALSE, message=FALSE, warning=FALSE}
 
@@
 
-```{r, topics2, echo=FALSE, message=FALSE, warning=FALSE}
+```{r topics2, echo=FALSE, message=FALSE, warning=FALSE}
 # Write to file
@@
 
-```{r, topics22, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=10}
+```{r topics3, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=10}
 par(mar = c(5, 10, 3, 1)); barplot(rev(rev(sort(table(df$term_topic)))[1:ntop]), horiz = T, las = 1, cex.names = 0.8, xlab = "Documents", main = "Most common topics")
@@
 
-```{r, authors, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=10}
+```{r authors, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=10}
 ntop <- 50
@@
 
-```{r, geo, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=10}
+```{r geo, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=10}
 tab <- rev(sort(table(unlist(strsplit(as.character(df$term_geography), ";")))))
@@
 
-```{r, geo2, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=10}
+```{r geo2, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=10}
 ntop <- 50
@@
 
-```{r, geo3, echo=FALSE, message=FALSE, warning=FALSE}
+```{r geo3, echo=FALSE, message=FALSE, warning=FALSE}
 f <- "output.tables/geoplaces.csv"
@@
 
-```{r, place, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=10}
+```{r city, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=10}
 tab <- rev(sort(table(str_trim(unlist(strsplit(as.character(df$city), ";"))))))
@@
 
-```{r, place2, echo=FALSE, message=FALSE, warning=FALSE}
+```{r city2, echo=FALSE, message=FALSE, warning=FALSE}
 f <- "output.tables/publicationplaces.csv"

### 2015-05-10 inst/examples/suvut.Rmd
Rmd fixes

@@
 
-```{r, annotations, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=10, fig.height=15}
+```{r suvut, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=10, fig.height=15}
 df <- readRDS("df.Rdata")

### 2015-05-10 inst/examples/summary.Rmd
limits fix (cheap)

@@
 ```{r authors, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=10}
+df$author <- paste(df$family_name,df$first_name,sep=", ")
 ntop <- 50
-a <- rev(rev(sort(table(paste(df$author_family,df$author_first,sep=", "))))[1:ntop])
+a <- rev(rev(sort(table(df$author)))[2:ntop+1])
 par(mar = c(5, 10, 3, 1)); barplot(a, horiz = T, las = 1, cex.names = 0.8, xlab = "Documents", main = "Top authors")

### 2015-10-14 inst/examples/summary.Rmd
more refactoring

@@
 Top-`r ntop` topics and number of documents for each.
-In total, there are `r length(unique(df$term_topic))` unique topics and `r sum(!is.na(df$term_topic))` documents assigned to one or more topics (`r round(100*mean(!is.na(df$term_topic)))`).
+In total, there are `r length(unique(df$subject_topic))` unique topics and `r sum(!is.na(df$subject_topic))` documents assigned to one or more topics (`r round(100*mean(!is.na(df$subject_topic)))`).
 
 ```{r topics3, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=10}
-par(mar = c(5, 10, 3, 1)); barplot(rev(rev(sort(table(df$term_topic)))[1:ntop]), horiz = T, las = 1, cex.names = 0.8, xlab = "Documents", main = "Most common topics")
+par(mar = c(5, 10, 3, 1)); barplot(rev(rev(sort(table(df$subject_topic)))[1:ntop]), horiz = T, las = 1, cex.names = 0.8, xlab = "Documents", main = "Most common topics")
 ```

### 2015-10-14 inst/examples/knit_all.R

@@ -1,6 +1,6 @@
-knit("summary.Rmd", encoding="UTF-8")
-knit("Helsinki.Rmd", encoding="UTF-8")
-knit("Suomi.Rmd", encoding="UTF-8")
-knit("Turku.Rmd", encoding="UTF-8")
-knit("Vaasa.Rmd", encoding="UTF-8")
-knit("suvut.Rmd", encoding="UTF-8")
+knitr::knit("summary.Rmd", encoding="UTF-8")
+knitr::knit("Helsinki.Rmd", encoding="UTF-8")
+knitr::knit("Suomi.Rmd", encoding="UTF-8")
+knitr::knit("Turku.Rmd", encoding="UTF-8")
+knitr::knit("Vaasa.Rmd", encoding="UTF-8")
+knitr::knit("suvut.Rmd", encoding="UTF-8")

### 2015-10-14 inst/examples/Vaasa.Rmd
more refactoring

@@
 # data ei välttämättä lopullinen
-df <- readRDS("df.Rdata")
+df <- readRDS("df.Rds")
 df <- df %>% filter(!is.na(published_in))
-vaasa1 <- df %>% filter(city == "Vaasa") %>% group_by(published_in) %>% tally() %>% arrange(published_in)
-vaasa1$decade <- as.numeric(paste0(substr(vaasa1$published_in,1,3),"0"))
-vaasa2 <- vaasa1 %>% group_by(decade) %>% summarise(m = sum(n)/10)
-vaasa <- inner_join(vaasa1,vaasa2)
+tmp1 <- df %>% filter(publication_place == "Vaasa") %>% group_by(published_in) %>% tally() %>% arrange(published_in)
+tmp1$decade <- as.numeric(paste0(substr(tmp1$published_in,1,3),"0"))
+tmp2 <- tmp1 %>% group_by(decade) %>% summarise(m = sum(n)/10)
+final <- inner_join(tmp1,tmp2)
 ```
 
-```{r, echo=FALSE, fig.width=20, fig.height=10}
+```{r Vaasa, echo=FALSE, fig.width=20, fig.height=10}
 par(las=1)
@@
 par(mar=c(7,17,6,4))
-plot(vaasa$published_in,vaasa$n,cex=1.8,pch="|",cex.main=5.0,main="Julkaisutoiminta Vaasassa 1764-1917",cex.lab=5.0,xlab="",ylab="Dokumenttia / vuosi",axes=FALSE,col="black")
-lines(vaasa$published_in,vaasa$m,type="l",lty=3,col="black",lwd=4)
+plot(final$published_in,final$n,cex=1.8,pch="|",cex.main=5.0,main="Julkaisutoiminta Vaasassa 1764-1917",cex.lab=5.0,xlab="",ylab="Dokumenttia / vuosi",axes=FALSE,col="black")
+lines(final$published_in,final$m,type="l",lty=3,col="black",lwd=4)
 axis(side = 1, at = c(1764,1809,1863,1917),cex.axis=3.2)
@@
 
-```{r, echo=FALSE, fig.width=20, fig.height=10}
-par(las=1)
-par(mgp=c(10,3,0))
-par(mar=c(7,17,6,4))
-plot(vaasa$published_in,vaasa$n,cex=1.8,pch="|",cex.main=5.0,main="Julkaisutoiminta Vaasassa 1764-1917",cex.lab=5.0,xlab="",ylab="Dokumenttia / vuosi",axes=FALSE,col="black")
-lines(vaasa$published_in,vaasa$m,type="l",lty=3,col="black",lwd=4)
-axis(side = 1, at = c(1764,1800,1840,1880,1917),cex.axis=3.2)
-axis(side = 2, at = c(0,40,80,120,160,194),cex.axis=3.2)
+```{r, echo=FALSE}
+remove(tmp1,tmp2,final)
 ```

### 2015-10-14 inst/examples/summary.Rmd
more refactoring

@@
 
-df <- readRDS("df.RData")
+df <- readRDS("df.Rds")
 
@@
 # List all topics
-spl <- strsplit(na.omit(as.character(df$term_topic)), ";")
+spl <- strsplit(na.omit(as.character(df$subject_topic)), ";")
 
@@
 ```{r geo, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=10}
-tab <- rev(sort(table(unlist(strsplit(as.character(df$term_geography), ";")))))
+tab <- rev(sort(table(unlist(strsplit(as.character(df$subject_geography), ";")))))
 ```
@@
 Top-`r ntop` geographical places are shown together with the number of documents assigned to that region.
-Geography information is available for `r sum(!is.na(df$term_geography))` documents (`r round(100*mean(!is.na(df$term_geography)))`%).
+Geography information is available for `r sum(!is.na(df$subject_geography))` documents (`r round(100*mean(!is.na(df$subject_geography)))`%).
 There are `r length(tab)` unique geographical places.
@@
 Top-`r ntop` publication places are shown together with the number of documents.
-This info is available for `r sum(!is.na(df$city))` documents (`r round(100*mean(!is.na(df$city)))`%).
-There are `r length(unique(str_trim(unlist(strsplit(as.character(df$city), ";")))))` unique publication places.
+This info is available for `r sum(!is.na(df$publication_place))` documents (`r round(100*mean(!is.na(df$publication_place)))`%).
+There are `r length(unique(str_trim(unlist(strsplit(as.character(df$publication_place), ";")))))` unique publication places.
 
-```{r city, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=10}
-tab <- rev(sort(table(str_trim(unlist(strsplit(as.character(df$city), ";"))))))
+```{r publication_place, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=10}
+tab <- rev(sort(table(str_trim(unlist(strsplit(as.character(df$publication_place), ";"))))))
 ntop <- 50
@@
 
-```{r city2, echo=FALSE, message=FALSE, warning=FALSE}
+```{r publication_place2, echo=FALSE, message=FALSE, warning=FALSE}
 f <- "output.tables/publicationplaces.csv"

### 2015-10-14 R/country.R

@@ -1,154 +1,151 @@
 #' @title deduce_country
 #' @description Add country field to data frame based on city field
 #'
-#' @param df Main dataframe
-#' @return Main dataframe
+#' @param city City vector
+#' @return Country vector
 #'
 #' @export
 #' 
 #' @author Niko Ilomaki \email{niko.ilomaki@@helsinki.fi}
 #' @references See citation("fennica")
 #' 
-#' @examples \dontrun{df <- deduce_country(df)}
+#' @examples \dontrun{country <- deduce_country(c("Helsinki","Tukholma"))}
 #' @keywords utilities
-deduce_country <- function(df) {
-	v <- df$city
-	w <- rep(NA, nrow(df))
-	w[v=="Almena WI"] <- "USA"
-	w[v=="Altdorf"] <- "Saksa"
-	w[v=="Amsterdam"] <- "Alankomaat"
-	w[v=="Ashtabula OH"] <- "USA"
-	w[v=="Astoria OR"] <- "USA"
-	w[v=="Barcelona"] <- "Espanja"
-	w[v=="Berliini"] <- "Saksa"
-	w[v=="Boston MA"] <- "USA"
-	w[v=="Braunschweig"] <- "Saksa"
-	w[v=="Bridgeport CT"] <- "USA"
-	w[v=="Bronx NY"] <- "USA"
-	w[v=="Brooklyn NY"] <- "USA"
-	w[v=="Calumet MI"] <- "USA"
-	w[v=="Chicago IL"] <- "USA"
-	w[v=="Chisholm MN"] <- "USA"
-	w[v=="Cincinnati OH"] <- "USA"
-	w[v=="Cleveland OH"] <- "USA"
-	w[v=="Budapest"] <- "Unkari"
-	w[v=="Dresden"] <- "Saksa"
-	w[v=="Duluth MN"] <- "USA"
-	w[v=="Espoo"] <- "Suomi"
-	w[v=="Eura"] <- "Suomi"
-	w[v=="Firenze"] <- "Italia"
-	w[v=="Fitchburg MA"] <- "USA"
-	w[v=="Forssa"] <- "Suomi"
-	w[v=="Frankfurt"] <- "Saksa"
-	w[v=="Giessen"] <- "Saksa"
-	w[v=="Göteborg"] <- "Ruotsi"
-	w[v=="Göttingen"] <- "Saksa"
[…]

### 2015-10-14 inst/examples/import.R

@@ -1,17 +1,12 @@
 # Update the pkg
-library(devtools)
 devtools::install_github("ropengov/bibliographica")
 devtools::install_github("ropengov/fennica")
 
-# Load R packages
+# Load dplyr
 library(dplyr)
-library(tau)
-library(fennica)
-library(bibliographica)
-
-output.folder <- "output.tables/"
 
 # Create the output directory if not yet exists
+output.folder <- "output.tables/"
 dir.create(output.folder)
 
 print("Read raw data")
@@ -73,8 +68,8 @@ print("Place names")
 df$publication_place <- bibliographica::polish_place(df$publication_place, remove.unknown = FALSE)
 
 source("city_examples.R", encoding = "UTF-8") # later account for multiple places
-df <- deduce_country(df)
+df$country <- fennica::deduce_country(df$publication_place)
 
-df <- tbl_df(df) # cbind overrides locality above
+df <- dplyr::tbl_df(df) # cbind overrides locality above
 
 saveRDS(df, "df.Rds")

### 2015-10-15 inst/examples/summary.Rmd
publication places ok

--- 2015-10-14 inst/examples/summary.Rmd
@@
 ```{r city2, echo=FALSE, message=FALSE, warning=FALSE}
-f <- "output.tables/publicationplaces.csv"
+f <- "output.tables/publication_place.csv"
 print(paste("Complete counts in file:", f))
-write.table(cbind(Place = names(tab), Documents = tab), file = f, sep = "|", quote = F, row.names = F)
+tmp <- write_xtable(df$publication_place, filename = f)
 ```

### 2015-10-15 inst/examples/summary.Rmd

--- 2015-10-14 inst/examples/summary.Rmd
@@
 
-```{r publication_place2, echo=FALSE, message=FALSE, warning=FALSE}
-f <- "output.tables/publicationplaces.csv"
+```{r city2, echo=FALSE, message=FALSE, warning=FALSE}
+f <- "output.tables/publication_place.csv"
 print(paste("Complete counts in file:", f))
-write.table(cbind(Place = names(tab), Documents = tab), file = f, sep = "|", quote = F, row.names = F)
+tmp <- write_xtable(df$publication_place, filename = f)
 ```

### 2015-10-23 inst/examples/summary.Rmd
Rmd update

@@
 title: "Summary"
-author: "Niko Ilomäki"
-date: "Tuesday, March 3, 2015"
+author: "Niko Ilomäki and Leo Lahti"
+date: "Tuesday, October 20, 2015"
 output: markdown_document
@@
 
-# Summary of the preprocessed Fennica data
+# Fennica summary
 
@@
 
+# Read the preprocessed data
 df <- readRDS("df.Rds")

### 2015-10-23 inst/examples/summary.Rmd
fixed some fields

@@
 
-missing <- 100*apply(df, 2, function (x) {mean(is.na(x))})
+# Need to use this trick to have NAs for all data types
+missing <- 100*apply(df, 2, function (x) {mean(is.na(gsub("^NA$", NA, as.character(x))))})
 df2 <- data.frame(list(missing = missing, field = names(missing)))
 df2$field <- factor(df2$field, levels = df2$field[rev(order(df2$missing))])
+
 theme_set(theme_bw(15))

### 2015-10-23 inst/examples/import.R

@@ -41,7 +41,7 @@ df <- dplyr::rename(df, author_birth = from)
 df <- dplyr::rename(df, author_death = till)
 
 print("Publishers")
-df$publisher_simplified <- bibliographica::polish_publisher(df$publisher)
+df$publisher_simplified <- bibliographica::polish_publisher(df$publisher)$name
 
 print("Years of publication")
 df <- cbind(
@@ -56,7 +56,7 @@ df <- cbind(
 )
 
 print("Universities")
-df$note_granter <- bibliographica::polish_university(df$note_granter)
+df$note_granter <- bibliographica::polish_university(df$note_granter)$name
 
 print("Place names")
 
@@ -85,7 +85,7 @@ print("Write unrecognized place names to file")
 tmp <- write_xtable(as.character(df.orig[which(is.na(df$publication_place)), ]$publication_place), paste(output.folder, "publication_place_discarded.csv", sep = ""))
 
 
-df$country <- get_country(df$publication_place)
+df$country <- get_country(df$publication_place)$country
 #df <- dplyr::tbl_df(df) # cbind overrides locality above
 
 

### 2015-10-24 inst/examples/summary.Rmd
ok

--- 2015-10-23 inst/examples/summary.Rmd
@@
 
-missing <- 100*apply(df, 2, function (x) {mean(is.na(x))})
+# Need to use this trick to have NAs for all data types
+missing <- 100*apply(df, 2, function (x) {mean(is.na(gsub("^NA$", NA, as.character(x))))})
 df2 <- data.frame(list(missing = missing, field = names(missing)))
 df2$field <- factor(df2$field, levels = df2$field[rev(order(df2$missing))])
+```
+
+Percentage of non-NA entries among all documents in the preprocessed data (note that in some cases a significant fraction of this information is missing already in the raw data)
+
+```{r missingb, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=10, fig.height=15}
 theme_set(theme_bw(15))
@@
 p <- p + ggtitle("Documents with data (%)")
+print(p)
+```
+
+Fields of special interest: success percentage compared to non-NA entries in the raw data:
+
+```{r missing2, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=10, fig.height=15}
+dfs <- df %>% select(publication_place, country, published_in, published_from, published_till, corporate, area, pagecount, gatherings, width, height, paper.consumption.km2)
+missing <- 100*apply(dfs, 2, function (x) {mean(is.na(gsub("^NA$", NA, as.character(x))))})
+df2 <- data.frame(list(missing = missing, field = names(missing)))
+df2$field <- factor(df2$field, levels = df2$field[rev(order(df2$missing))])
+
+theme_set(theme_bw(15))
+p <- ggplot(df2, aes(x = field, y = 100 - missing))
+p <- p + geom_bar(stat = "identity")
+p <- p + coord_flip()
+p <- p + ylab("")
+p <- p + xlab("")
+p <- p + ggtitle("Documents with data (%)")
+print(p)
+
+dfs <- df.orig %>% select(publication_place, note_year, corporate, physical_extent, physical_dimension)
+missing <- 100*apply(dfs, 2, function (x) {mean(is.na(gsub("^NA$", NA, as.character(x))))})
+df2 <- data.frame(list(missing = missing, field = names(missing)))
+df2$field <- factor(df2$field, levels = df2$field[rev(order(df2$missing))])
+
+theme_set(theme_bw(15))
+p <- ggplot(df2, aes(x = field, y = 100 - missing))
+p <- p + geom_bar(stat = "identity")
+p <- p + coord_flip()
+p <- p + ylab("")
+p <- p + xlab("")
+p <- p + ggtitle("Documents with raw data (%)")
 print(p)

### 2015-10-29 inst/examples/summary.Rmd
ok

--- 2015-10-23 inst/examples/summary.Rmd
@@
 library(ggplot2)
+ntop <- 20
 
@@
 print(p)
+```
+
+Fields of special interest: real success percentage (proportion of successful conversions compared to non-NA entries in the original data):
+
+```{r missing2, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=10, fig.height=15}
+dfs <- df %>% select(author, publication_place, country, publication_year, published_from, published_till, corporate, area, pagecount, gatherings, width, height, paper.consumption.km2, publisher)
+success <- as.data.frame(t(apply(dfs, 2, function (x) {sum(!is.na(gsub("^NA$", NA, as.character(x))))})))
+original.nonNA <- as.data.frame(t(apply(select(df.orig, publication_place, publication_time, corporate, physical_extent, physical_dimension), 2, function (x) {sum(!is.na(gsub("^NA$", NA, as.character(x))))})))
+
+# Compare the number of non-NA entries in preprocessed data to number
+# of non-NA entries in the original data:
+real.success <- c()
+real.success[["publication_place"]] <- success$publication_place/original.nonNA$publication_place
+real.success[["country"]] <- success$country/original.nonNA$publication_place
+real.success[["publication_year"]] <- success$publication_year/original.nonNA$publication_time
+real.success[["published_from"]] <- success$published_from/original.nonNA$publication_time
+real.success[["published_till"]] <- success$published_till/original.nonNA$publication_time
+real.success[["corporate"]] <- success$corporate/original.nonNA$corporate
+real.success[["publisher"]] <- success$publisher/original.nonNA$publisher
+real.success[["pagecount"]] <- success$pagecount/original.nonNA$physical_extent
+real.success[["area"]] <- success$area/original.nonNA$physical_dimension
+real.success[["gatherings"]] <- success$gatherings/original.nonNA$physical_dimension
+real.success[["author"]] <- success$author/original.nonNA$author
+real.success[["paper"]] <- success$paper.consumption.km2/sum(rowMeans(!is.na(df.orig[, c("physical_extent", "physical_dimension")])) == 1)
+par(mar = c(3, 8, 2, 1)); barplot(100*sort(real.success), horiz = T, main = "Real success rate (selected fields)", las = 1, xlim = c(0, 1), xlab = "Success rate (%)")
+```
+
+## Pagecounts
+
+[Discarded page count data](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/documentpages-accepted-discarded.csv)
+
+[Successfully converted page counts](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/documentpages-accepted.csv)
+
+Compare gatherings and cm2 sizes as a quality check. This includes all data; the area has been estimated from the gatherings when dimension information was not available.
+
+```{r summarysizecomp, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=7}
+dfs <- df %>% filter(!is.na(area) & !is.na(gatherings))
+dfs <- dfs[, c("gatherings", "area")]
+dfm <- melt(table(dfs))
+names(dfm) <- c("gatherings", "area", "documents")
+dfm$gatherings <- order_gatherings(dfm$gatherings)
+p <- ggplot(dfm, aes(x = gatherings, y = area)) 
+p <- p + scale_y_continuous(trans = "log2")
+p <- p + geom_point(aes(size = documents))
+p <- p + scale_size(trans="log10")
+p <- p + ggtitle("Document size distribution: gatherings vs. cm2")
+p <- p + xlab("Size (gatherings)")
+p <- p + ylab("Size (cm2)")
+p <- p + coord_flip()
+print(p)
+```
+
+Compare gatherings and page counts.
+
+```{r summarypagecomp, echo=FALSE, message=FALSE, warning=FALSE, fig.width=15, fig.height=7}
+dfs <- select(df, pagecount, gatherings) 
+dfs$pagecount <- as.numeric(gsub(" pages", "", dfs$pagecount))
+dfs <- dfs %>% filter(!is.na(pagecount) & !is.na(gatherings))
+dfg <- group_by(dfs, pagecount, gatherings) %>% tally()
+names(dfg) <- c("pages", "gatherings", "documents")
+dfg$gatherings <- order_gatherings(dfg$gatherings)
+ylims <- range(dfg$pages)
+p <- ggplot(dfg, aes(x = gatherings, y = pages)) 
+n <- nchar(max(na.omit(table(dfg$pages))))
+ylim <- ylim(ylims)
+p <- p + scale_y_log10(breaks=10^(0:n))
+p <- p + geom_point(aes(size = documents))
+p <- p + scale_size(trans="log10")
+p <- p + xlab("Size (gatherings)")
+p <- p + ylab("Pages (original and estimated)")
+p <- p + coord_flip()
+print(p)
+```
+
+## Publication time
+
+[Successfully converted publication times](publication-time-accepted.csv)
+
+[Discarded publication times](publication-time-discarded.csv)
+
+```{r publication_time, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=10}
+hist(df$publication_year, main = "Document frequencies over time")
+```
+
+## Publication places
+
+Top-`r ntop` publication places are shown together with the number of documents.
+This info is available for `r sum(!is.na(df$publication_place))` documents (`r round(100*mean(!is.na(df$publication_place)))`%).
+There are `r length(unique(str_trim(unlist(strsplit(as.character(df$publication_place), ";")))))` unique publication places.
+
+```{r publication_place, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=10}
+tab <- rev(sort(table(str_trim(unlist(strsplit(as.character(df$publication_place), ";"))))))
+ntop <- 50
+par(mar = c(5, 10, 3, 1)); barplot(log10(rev(tab[1:ntop])), horiz = T, las = 1, cex.names = 0.8, xlab = "Documents (log10)", main = "Most common publication places")
+```
+
+[Successfully converted publication places](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/publication_place.csv)
+
+[Discarded publication places](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/publication_place_discarded.csv)
+
+[Publication places missing country information](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/publication_place_missingcountry.csv)
+
+## Dimensions
+
+[Successfully converted dimension info](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/accepted_dimensions.csv)
+
+[Discarded dimension info](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/missing_dimensions.csv)
+
+[Discarded gatherings info](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/missing_gatherings.csv)
+
+## Publisher
+
+[Accepted publisher info](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/publisher_accepted.csv)
+
+[Discarded publisher info](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/publisher_discarded.csv)
+
+We also have corporate info available ?
+
+[Accepted corporate info](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/corporate_accepted.csv)
+
+## Authors
+
+[Accepted author info](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/author_accepted.csv)
+
+[Discarded author info](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/author_discarded.csv)
+
+Top-`r ntop` uniquely identified authors and number of documents for each (duplicate docs not checked yet).
+
+```{r authors, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=10}
+df$author <- paste(df$family_name,df$first_name,sep=", ")
+ntop <- 50
+a <- rev(rev(sort(table(df$author)))[2:ntop+1])
+par(mar = c(5, 10, 3, 1)); barplot(a, horiz = T, las = 1, cex.names = 0.8, xlab = "Documents", main = "Top authors")
 ```
@@
 
-## Authors
-
-Top-`r ntop` uniquely identified authors and number of documents for each (duplicate docs not checked yet).
-
-```{r authors, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=10}
-df$author <- paste(df$family_name,df$first_name,sep=", ")
-ntop <- 50
-a <- rev(rev(sort(table(df$author)))[2:ntop+1])
-par(mar = c(5, 10, 3, 1)); barplot(a, horiz = T, las = 1, cex.names = 0.8, xlab = "Documents", main = "Top authors")
-```
-
 ## Subject geographical places
@@
 ```
-
-## Publication
-
-### Publication places
-
-Top-`r ntop` publication places are shown together with the number of documents.
-This info is available for `r sum(!is.na(df$publication_place))` documents (`r round(100*mean(!is.na(df$publication_place)))`%).
-There are `r length(unique(str_trim(unlist(strsplit(as.character(df$publication_place), ";")))))` unique publication places.
-
-```{r publication_place, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=10}
-tab <- rev(sort(table(str_trim(unlist(strsplit(as.character(df$publication_place), ";"))))))
-ntop <- 50
-par(mar = c(5, 10, 3, 1)); barplot(log10(rev(tab[1:ntop])), horiz = T, las = 1, cex.names = 0.8, xlab = "Documents (log10)", main = "Most common publication places")
-```
-
-```{r city2, echo=FALSE, message=FALSE, warning=FALSE}
-f <- "output.tables/publication_place.csv"
-print(paste("Complete counts in file:", f))
-tmp <- write_xtable(df$publication_place, filename = f)
-```

### 2015-10-29 inst/examples/import.R

@@ -17,22 +17,13 @@ df <- bibliographica::read_bibliographic_metadata("data/fennica.csv.gz")
 df.orig <- df
 
 print("Languages")
-df$language <- paste0(df$language,";",df$language2)
-df$language <- gsub("NA","",df$language)
-df$language <- gsub("^;","",df$language)
-df$language <- gsub(";$","",df$language)
 df <- cbind(
 	df,
-	bibliographica::mark_languages(df$language)
+	bibliographica::mark_languages(df$language2)
 )
+	
 
-print("Names of authors")
-df <- cbind(
-	df,
-	bibliographica::polish_name_of_author(df$author_name)
-)
-
-print("Lifespans of authors")
+print("Author lifespans")
 df <- cbind(
 	df,
 	bibliographica::polish_years(df$author_date)
@@ -40,15 +31,34 @@ df <- cbind(
 df <- dplyr::rename(df, author_birth = from)
 df <- dplyr::rename(df, author_death = till)
 
+print("Author names")
+df <- cbind(
+	df,
+	bibliographica::polish_name_of_author(df$author_name)
+)
+
+print("Unique author IDs")
+# Unique author identifier by combining name, birth and death years
+df$author <- apply(df[, c("author_name", "author_birth", "author_death")], 1, function (x) {paste(x[[1]], " (", x[[2]], "-", x[[3]], ")", sep = "")})
+df$author <- gsub("NA \\(NA-NA\\)", NA, df$author)
+df$author <- gsub(" \\(NA-NA\\)", "", df$author)
+
+
 print("Publishers")
-df$publisher_simplified <- bibliographica::polish_publisher(df$publisher)$name
+df$publisher <- bibliographica::polish_publisher(df.orig$publisher)$name
+
+print("Take corporate field as such for now")
+df$corporate <- df.orig$corporate
 
 print("Years of publication")
 tmp <- bibliographica::polish_years(df$publication_time)
 df$published_from <- tmp$from
 df$published_till <- tmp$till
 # Now published from == published in for simplicity; perhaps separated later
-df$published_in <- tmp$from 
+df$publication_year <- tmp$from
+# Accepted and Discarded time entries
+tmp2 <- write_xtable(tmp, paste(output.folder, "publication-time-accepted.csv", sep = ""))
[…]

### 2015-10-29 inst/examples/summary.Rmd
ok

@@
 df <- readRDS("df.Rds")
+df.orig <- readRDS("df.orig.Rds")
 
@@
 success <- as.data.frame(t(apply(dfs, 2, function (x) {sum(!is.na(gsub("^NA$", NA, as.character(x))))})))
-original.nonNA <- as.data.frame(t(apply(select(df.orig, publication_place, publication_time, corporate, physical_extent, physical_dimension), 2, function (x) {sum(!is.na(gsub("^NA$", NA, as.character(x))))})))
+original.nonNA <- as.data.frame(t(apply(select(df.orig, publication_place, publication_time, corporate, physical_extent, physical_dimension, publisher, author_name), 2, function (x) {sum(!is.na(gsub("^NA$", NA, as.character(x))))})))
 
@@
 real.success[["paper"]] <- success$paper.consumption.km2/sum(rowMeans(!is.na(df.orig[, c("physical_extent", "physical_dimension")])) == 1)
-par(mar = c(3, 8, 2, 1)); barplot(100*sort(real.success), horiz = T, main = "Real success rate (selected fields)", las = 1, xlim = c(0, 1), xlab = "Success rate (%)")
+par(mar = c(3, 8, 2, 1)); barplot(100*sort(real.success), horiz = T, main = "Real success rate (selected fields)", las = 1, xlim = c(0, 100), xlab = "Success rate (%)")
 ```

### 2015-10-29 inst/examples/summary.Rmd
ok

@@
 library(dplyr)
+library(reshape2)
 library(ggplot2)
@@
 
-[Discarded page count data](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/documentpages-accepted-discarded.csv)
+[Discarded page count data](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/documentpages_discarded.csv)
 
-[Successfully converted page counts](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/documentpages-accepted.csv)
+[Successfully converted page counts](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/documentpages_accepted.csv)
 

### 2015-10-29 inst/examples/summary.Rmd
ok

@@
 
-[Discarded page count data](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/documentpages_discarded.csv)
+[Discarded page count data](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/pagecount_discarded.csv)
 
-[Successfully converted page counts](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/documentpages_accepted.csv)
+[Successfully converted page counts](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/pagecount_conversion.csv)
 
@@
 
-[Successfully converted publication places](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/publication_place.csv)
+[Successfully converted publication places](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/publication_place_accepted.csv)
 
@@
 
-[Accepted publisher info](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/publisher_accepted.csv)
+[Accepted publisher info](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/publisher_accepted.tab)
 
-[Discarded publisher info](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/publisher_discarded.csv)
+[Discarded publisher info](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/publisher_discarded.tab)
 
@@
 
-[Accepted corporate info](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/corporate_accepted.csv)
+[Accepted corporate info](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/corporate_accepted.tab)
 
@@
 
-[Accepted author info](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/author_accepted.csv)
+[Accepted author info](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/author_accepted.tab)
 
-[Discarded author info](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/author_discarded.csv)
+[Discarded author info](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/author_discarded.tab)
 
@@
 f <- "output.tables/subjecttopics.tab"
-print(paste("Complete subject topic counts in file:", f))
 write.table(cbind(Topic = sort(names(tab))), file = f, sep = "\t", quote = F, row.names = F)
@@
 ```
+
+[Complete subject topic counts](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/subjecttopics.tab)
 
@@
 ```
+
+[Complete geoplace listing](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/geoplaces.csv)

### 2015-10-29 inst/examples/summary.Rmd
separated functions into their own files and removed empty roxygen lines to avoid some warnings in official build check

@@
 
-[Successfully converted publication times](publication-time-accepted.csv)
+[Successfully converted publication times](output.tables/publication-time-accepted.csv)
 
-[Discarded publication times](publication-time-discarded.csv)
+[Discarded publication times](output.tables/publication-time-discarded.csv)
 
@@
 ```{r authors, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=10}
-df$author <- paste(df$family_name,df$first_name,sep=", ")
-ntop <- 50
 a <- rev(rev(sort(table(df$author)))[2:ntop+1])
@@
 ```{r topics1, topics, echo=FALSE, message=FALSE, warning=FALSE}
-
 # List all topics
@@
 f <- "output.tables/geoplaces.csv"
-print(paste("Complete counts in file:", f))
 write.table(cbind(Geography = names(tab), Documents = tab), file = f, sep = "|", quote = F, row.names = F)

### 2015-10-29 R/city.R

@@ -1,85 +1,16 @@
-#' @title sanitize_name
-#' @description Remove Nordic characters etc. from strings to use in filenames
-#'
-#' @param x String or vector of strings
-#' @return String or vector of strings
-#'
-#' @export
-#' @importFrom sorvi harmonize_names
-#' 
-#' @author Niko Ilomaki \email{niko.ilomaki@@helsinki.fi}
-#' @references See citation("fennica")
-#' 
-#' @examples name <- sanitize_name("Turku")
-#' @keywords utilities
-sanitize_name <- function(x) {
-
-  f <- system.file("extdata/specialchars.csv", package = "fennica")
-  sn <- read.csv(f, sep = "\t")
-
-  x <- harmonize_names(x, sn)$name
-  x <- gsub(" ","",x)
-
-  x
-}
-
-#' @title collect_misspellings
-#' @description Use Levenshtein distance iteratively to find plausible misspellings
-#'
-#' @param city Correct name (prechosen form)
-#' @param variations List of usual forms (possibly including usual misspellings)
-#' @param all List of all non-assigned city names in the data
-#' @return List of all non-assigned city names in the data
-#'
-#' @export
-#' 
-#' @author Niko Ilomaki \email{niko.ilomaki@@helsinki.fi}
-#' @references See citation("fennica")
-#' 
-#' @examples \dontrun{all <- collect_misspellings("Hämeenlinna",c("Hämeenlinna","Tavastehus"),
-#'					                        c("Hämeenlinnae","Tavasteehuus"))}
-#' @keywords utilities
-collect_misspellings <- function (city, variations, all) {
-	eff <- 1
-	while (eff > 0) {
-		eff <- 0
-		for (i in 1:length(all)) {
-			if(is.na(all[i])) {
-				next
-			}
-			if(min(adist(all[i],variations)) == 1){
-				variations <- c(variations,as.character(all[i]))
-				eff <- 1
-			}
-		}
-	}
-	write.csv(variations, file=paste0("output.tables/city_",sanitize_name(city),".csv"), fileEncoding="UTF-8")
-	for (x in variations){
-		all <- all[which(all!=get("x"))]
-	}
-	all
-}
-
-
-
 #' @title correct_misspellings
 #' @description Correct misspelled city names based on mapping constructed earlier
-#'
 #' @param v Vector of city names
[…]

### 2015-10-29 R/collect_misspellings.R

@@ -1,0 +1,34 @@
+#' @title collect_misspellings
+#' @description Use Levenshtein distance iteratively to find plausible misspellings
+#' @param city Correct name (prechosen form)
+#' @param variations List of usual forms (possibly including usual misspellings)
+#' @param all List of all non-assigned city names in the data
+#' @return List of all non-assigned city names in the data
+#' @export
+#' @author Niko Ilomaki \email{niko.ilomaki@@helsinki.fi}
+#' @references See citation("fennica")
+#' @examples \dontrun{all <- collect_misspellings("Turku",c("Turku","Turkue"), c("Turku","Aboensis"))}
+#' @keywords utilities
+collect_misspellings <- function (city, variations, all) {
+	eff <- 1
+	while (eff > 0) {
+		eff <- 0
+		for (i in 1:length(all)) {
+			if(is.na(all[i])) {
+				next
+			}
+			if(min(adist(all[i],variations)) == 1){
+				variations <- c(variations,as.character(all[i]))
+				eff <- 1
+			}
+		}
+	}
+	write.csv(variations, file=paste0("output.tables/city_",sanitize_name(city),".csv"), fileEncoding="UTF-8")
+	for (x in variations){
+		all <- all[which(all!=get("x"))]
+	}
+	all
+}
+
+
+

### 2015-10-29 inst/examples/import.R

@@ -49,6 +49,7 @@ df$publisher <- bibliographica::polish_publisher(df.orig$publisher)$name
 
 print("Take corporate field as such for now")
 df$corporate <- df.orig$corporate
+df$corporate <- gsub("S\\.n\\. \\(tuntematon kirjapaino\\)", NA, df$corporate)
 
 print("Years of publication")
 tmp <- bibliographica::polish_years(df$publication_time)
@@ -113,7 +114,7 @@ for (field in c("gatherings", "width", "height", "area", "obl")) {
   df[[field]] <- tmp[[field]]
 }
 
-tmp2 <- write_xtable(tmp, paste(output.folder, "accepted_dimensions.csv", sep = ""))
+tmp2 <- write_xtable(tmp[, c("original", "gatherings", "width", "height", "obl")], paste(output.folder, "accepted_dimensions.csv", sep = ""))
 
 tmp3 <- write_xtable(df.orig$physical_dimension[which(tmp$gatherings == "NA")], paste(output.folder, "missing_gatherings.csv", sep = ""))
 
@@ -136,13 +137,13 @@ for (varname in c("author", "corporate", "publisher", "language", "publication_p
 
   # Accepted fields
   x <- as.character(df[[varname]])
-  tmp1 <- write_xtable(x, paste(output.folder, paste(varname, "accepted.tab", sep = "_"), sep = ""))  
+  tmp1 <- write_xtable(x, paste(output.folder, paste(varname, "accepted.csv", sep = "_"), sep = ""))  
 
   # Discarded fields
   o <- as.character(df.orig[[varname]])
   disc <- as.vector(na.omit(o[which(is.na(x))]))
   if (is.null(disc)) {disc <- NA}
-  tmp2 <- write_xtable(disc, paste(output.folder, paste(varname, "discarded.tab", sep = "_"), sep = ""))
+  tmp2 <- write_xtable(disc, paste(output.folder, paste(varname, "discarded.csv", sep = "_"), sep = ""))
 
 }
 
@@ -171,5 +172,4 @@ for (nam in names(originals)) {
 }
 
 
-# -------------------------------------
 

### 2015-10-30 inst/examples/summary.Rmd
ok

@@
 
-[Accepted publisher info](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/publisher_accepted.tab)
+[Discarded publisher info](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/publisher_discarded.csv)
 
-[Discarded publisher info](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/publisher_discarded.tab)
+[Converted publishers](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/publisher_conversion.csv)
 
@@
 
-[Accepted author info](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/author_accepted.tab)
+[Accepted author info](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/author_accepted.csv)
 
-[Discarded author info](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/author_discarded.tab)
+[Discarded author info](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/author_discarded.csv)
 

### 2015-10-30 inst/examples/import.R

@@ -133,7 +133,7 @@ saveRDS(df.orig, "df.orig.Rds")
 # ---------------------------------------------------------------
 
 print("Summarize accepted and discarded entries")
-for (varname in c("author", "corporate", "publisher", "language", "publication_place")) {
+for (varname in c("author", "corporate", "language", "publication_place")) {
 
   # Accepted fields
   x <- as.character(df[[varname]])

### 2015-10-30 inst/examples/summary.Rmd
ok

@@
 
-[Discarded publisher info](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/publisher_discarded.csv)
+[Discarded publisher info](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/publisher_discarded.csv) (Check that ok to discard these)
 
-[Converted publishers](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/publisher_conversion.csv)
+[Converted publishers](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/publisher_accepted.csv) (Check for formatting and synonymes)
 

### 2015-11-20 inst/examples/summary.Rmd
ok

@@
 
-Fraction of documents with entries for each annotation field.
+Fraction of documents with entries for each annotation field. For a full list of summaries for field contents, see [here](https://github.com/rOpenGov/fennica/tree/master/inst/examples/output.tables).
 
@@
 
-[Accepted corporate info](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/corporate_accepted.tab)
+[Accepted corporate info](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/corporate_accepted.csv)
+
+[Discarded corporate info](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/corporate_discarded.csv)
 

### 2015-11-24 inst/examples/summary.Rmd
ok

@@
 real.success[["publisher"]] <- success$publisher/original.nonNA$publisher
+real.success[["self_published"]] <- success$self_published/original.nonNA$publisher
 real.success[["pagecount"]] <- success$pagecount/original.nonNA$physical_extent
@@
 
+[Self-published accepted](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/self_published_accepted.csv) (Check for formatting and synonymes)
+
+[Self-published raw fields](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/self_published_rawfields.csv) (Check that the self-publication is a correct classification for these docs)
+
 We also have corporate info available ?

### 2015-11-24 inst/examples/summary.Rmd
name validations

@@
 ```{r missing2, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=10, fig.height=15}
-dfs <- df %>% select(author, publication_place, country, publication_year, published_from, published_till, corporate, area, pagecount, gatherings, width, height, paper.consumption.km2, publisher)
+dfs <- df %>% select(author, publication_place, country, publication_year, published_from, published_till, corporate, area, pagecount, gatherings, width, height, paper.consumption.km2, publisher, self_published)
 success <- as.data.frame(t(apply(dfs, 2, function (x) {sum(!is.na(gsub("^NA$", NA, as.character(x))))})))
@@
 
-[Accepted author info](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/author_accepted.csv)
+[Accepted unique authors](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/author_accepted.csv)
 
-[Discarded author info](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/author_discarded.csv)
+[Discarded authors](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/author_discarded.csv)
 

### 2015-11-24 inst/examples/summarize.R

@@ -59,7 +59,7 @@ o2 <- as.character(df.original[["author_name"]])
 x <- df[["self_published"]]
 inds <- which(x) # List conversions for self-published docs
 tmp <- write_xtable(cbind(o1[inds], o2[inds]),
-  paste(output.folder, "self_published_rawfields.csv"))
+  paste(output.folder, "self_published_rawfields.csv", sep = ""))
 # Self published: summary of the final self-publisher names
 tmp <- write_xtable(df[inds, c("publisher")], paste(output.folder, "self_published_accepted.csv", sep = ""))
 

### 2015-12-07 inst/examples/Paper.Rmd
Some plots

---
title: "Paper Consumption in Finland, 1488-1828"
author: "Niko Ilomäki"
date: "December 7, 2015"
output: markdown_document
---

```{r summaryinit, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE}
library(stringr)
library(dplyr)
library(ggplot2)
library(bibliographica)
library(fennica)
library(sorvi)
df <- readRDS("df.Rds")
dfs <- df %>% filter(publication_year > 1400 & publication_year < 1829) %>%
  filter(!is.na(paper.consumption.km2) & paper.consumption.km2 > -0.01) %>%
  group_by(publication_year) %>%
  summarise(titles = n(), paper = sum(paper.consumption.km2))
authors <- df %>% filter(publication_year > 1400 & publication_year < 1829) %>%
  group_by(author_name) %>%
  summarise(titles=n()) %>% arrange(desc(titles))
top10 <- tail(head(authors,11),10)
dfs10 <- df %>% filter(publication_year > 1400 & publication_year < 1829) %>%
  filter(author_name %in% c(top10$author_name)) %>%
  filter(!is.na(paper.consumption.km2) & paper.consumption.km2 > -0.01) %>%
  group_by(publication_year) %>%
  summarise(titles = n(), paper = sum(paper.consumption.km2))
```

```{r titles, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=4, fig.width=8}
p1 <- ggplot(dfs, aes(y = titles, x = publication_year))
p1 <- p1 + geom_smooth(color = "black") + geom_point()
p1 <- p1 + xlab("Publication Year") + ylab("Title Count") 
p1 <- p1 + theme(axis.text.x = element_text(size = 20), axis.text.y = element_text(size = 20))
p1 <- p1 + theme(axis.title.x = element_text(size = 20), axis.title.y = element_text(size = 20))
p1 <- p1 + guides(fill = "none", alpha = "none")
p1 <- p1 + ggtitle("Finnish publications 1488-1828: title count (all authors)")
print(p1)
```

```{r paper, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=4, fig.width=8.2}
p2 <- ggplot(dfs, aes(y = paper, x = publication_year))
p2 <- p2 + geom_smooth(color = "black") + geom_point() +
       xlab("Publication Year") +
       ylab("Paper Consumption (km2)")

p2 <- p2 + theme(axis.text.x = element_text(size = 20), axis.text.y = element_text(size = 20))
p2 <- p2 + theme(axis.title.x = element_text(size = 20), axis.title.y = element_text(size = 20))
p2 <- p2 + guides(fill = "none", alpha = "none")
p2 <- p2 + ggtitle("Finnish publications 1488-1828: paper consumption (all authors)")
print(p2)
```

```{r titles10, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=4, fig.width=8}
p1b <- ggplot(dfs10, aes(y = titles, x = publication_year))
p1b <- p1b + geom_smooth(color = "black") + geom_point()
p1b <- p1b + xlab("Publication Year") + ylab("Title Count") 
p1b <- p1b + theme(axis.text.x = element_text(size = 20), axis.text.y = element_text(size = 20))
p1b <- p1b + theme(axis.title.x = element_text(size = 20), axis.title.y = element_text(size = 20))
p1b <- p1b + guides(fill = "none", alpha = "none")
p1b <- p1b + ggtitle("Finnish publications 1488-1828: title count (top 10 authors)")
print(p1b)
```

```{r paper10, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=4, fig.width=8.2}
p2b <- ggplot(dfs10, aes(y = paper, x = publication_year))
p2b <- p2b + geom_smooth(color = "black") + geom_point() +
       xlab("Publication Year") +
       ylab("Paper Consumption (km2)")

p2b <- p2b + theme(axis.text.x = element_text(size = 20), axis.text.y = element_text(size = 20))
p2b <- p2b + theme(axis.title.x = element_text(size = 20), axis.title.y = element_text(size = 20))
p2b <- p2b + guides(fill = "none", alpha = "none")
p2b <- p2b + ggtitle("Finnish publications 1488-1828: paper consumption (top 10 authors)")
print(p2b)
```

### 2015-12-08 inst/examples/20151209-HelsinkiDH.Rmd
20151209 created

---
title: "Paper Consumption in Finland, 1488-1828"
author: "Niko Ilomäki"
date: "December 7, 2015"
output: markdown_document
---

```{r 20150912-HDH-init, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE}
library(stringr)
library(dplyr)
library(ggplot2)
library(bibliographica)
library(fennica)
library(sorvi)

# Nice theme
theme_set(theme_bw(20))

# Read data
df <- readRDS("df.Rds")

# Let us focus on years 1400-1828
df <- df %>% filter(publication_year > 1400 & publication_year < 1829)

# Add publication decade
# TODO add already in the original preprocessed data matrix
df$publication_decade <- 10*floor(df$publication_year/10)
```

```{r 20150912-HDH-TurkuVSOthers, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=4, fig.width=8}

# Add indicator field: Turku or Not Turku
myplace <- "Turku"
df$myplace <- rep(NA, nrow(df))
df$myplace[df$publication_place == myplace] <- myplace
df$myplace[!df$publication_place == myplace & df$country == "Finland"] <- "Finland"
df$myplace[!df$publication_place == myplace & !df$country == "Finland"] <- "Foreign"
df$myplace <- factor(df$myplace, levels = rev(c("Other", "Finland", "Turku")))

# Keep entries with known publication place and paper consumption
# Group by year/decade and Turku/Other
dfs <- df %>%
  #filter(publication_year >= 1600) %>%
  filter(!is.na(publication_place) & !is.na(paper.consumption.km2) & paper.consumption.km2 > -0.01) %>%
  group_by(publication_decade, myplace) %>%
  summarise(titles = n(), paper = sum(paper.consumption.km2))

#p <- ggplot(dfs, aes(x = publication_decade, y = paper, color = myplace)) +
#     geom_point() + geom_smooth() +
#     ylim(0, max(dfs$paper)) +
#     ggtitle("Turku vs. other publication places")

p <- ggplot(dfs, aes(x = publication_decade, y = paper, fill = myplace, order = -as.numeric(myplace))) +
     geom_bar(position = "stack", stat = "identity") +
     ggtitle("Paper consumption") +
     scale_fill_manual(values = c("blue", "black", "darkgreen")) +
     xlab("Publication decade") + ylab("Paper (km2)")
print(p)

p <- ggplot(dfs, aes(x = publication_decade, y = titles, fill = myplace, order = -as.numeric(myplace))) +
     geom_bar(position = "stack", stat = "identity") +
     ggtitle("Title count") +
     scale_fill_manual(values = c("blue", "black", "darkgreen")) +
     xlab("Publication decade") + ylab("Title count (n)")
print(p)
```

### 2015-12-08 inst/examples/20151209-HelsinkiDH.Rmd
ok

@@
 df$myplace[!df$publication_place == myplace & df$country == "Finland"] <- "Finland"
-df$myplace[!df$publication_place == myplace & !df$country == "Finland"] <- "Foreign"
-df$myplace <- factor(df$myplace, levels = rev(c("Other", "Finland", "Turku")))
+df$myplace[!df$country == "Finland"] <- "Foreign"
+df$myplace <- factor(df$myplace, levels = rev(c("Foreign", "Finland", "Turku")))
 
@@
   summarise(titles = n(), paper = sum(paper.consumption.km2))
-
-#p <- ggplot(dfs, aes(x = publication_decade, y = paper, color = myplace)) +
-#     geom_point() + geom_smooth() +
-#     ylim(0, max(dfs$paper)) +
-#     ggtitle("Turku vs. other publication places")
 
@@
 print(p)
+
+#p + guides(fill = guide_legend(order = 1))
+
 ```

### 2015-12-08 inst/examples/20151209-HelsinkiDH.Rmd
top authors

@@
 ---
-title: "Paper Consumption in Finland, 1488-1828"
-author: "Niko Ilomäki"
-date: "December 7, 2015"
+title: "Digital History in Finland, 1488-1828"
+author: "Leo Lahti"
+date: "December 9, 2015"
 output: markdown_document
 ---
+
+This markdown document contains presentation material for [Digital History in Finland seminar (University of Helsinki, Dec 9, 2015)](http://blogs.helsinki.fi/mstolone/2015/09/21/call-for-papers-digital-history-in-finland-wednesday-9-12-2015/).
+The source code to reproduce the figures is in the [Rmarkdown document](https://github.com/rOpenGov/fennica/blob/master/inst/examples/20151209-HelsinkiDH.md).
 
@@
 # Read data
-df <- readRDS("df.Rds")
-
-# Let us focus on years 1400-1828
-df <- df %>% filter(publication_year > 1400 & publication_year < 1829)
+dfo <- readRDS("df.Rds")
 
@@
 # TODO add already in the original preprocessed data matrix
-df$publication_decade <- 10*floor(df$publication_year/10)
+dfo$publication_decade <- 10*floor(dfo$publication_year/10)
+
+# Remove very early and late years
+dfo <- dfo %>% filter(publication_year > 1400 & publication_year < 1911)
 ```
@@
 ```{r 20150912-HDH-TurkuVSOthers, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=4, fig.width=8}
+
+# Let us focus on years 1400-1828
+df <- dfo %>% filter(publication_year > 1400 & publication_year < 1829)
 
@@
 #p + guides(fill = guide_legend(order = 1))
+```
 
+```{r 20150912-HDH-Author, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=4, fig.width=8}
+p1 <- top_plot(dfo, "author", 10) + ggtitle(paste("Top authors (", min(na.omit(dfo$publication_year)), "-", max(na.omit(dfo$publication_year)), ")", sep = ""))
+
+p2 <- top_plot(df, "author", 10) + ggtitle(paste("Top authors (", min(na.omit(df$publication_year)), "-", max(na.omit(df$publication_year)), ")", sep = ""))
+
+library(gridExtra)
+grid.arrange(p1, p2, nrow = 1)
 ```

### 2015-12-08 inst/examples/20151209-HelsinkiDH.Rmd
ok

@@
 This markdown document contains presentation material for [Digital History in Finland seminar (University of Helsinki, Dec 9, 2015)](http://blogs.helsinki.fi/mstolone/2015/09/21/call-for-papers-digital-history-in-finland-wednesday-9-12-2015/).
-The source code to reproduce the figures is in the [Rmarkdown document](https://github.com/rOpenGov/fennica/blob/master/inst/examples/20151209-HelsinkiDH.md).
+The source code to reproduce the figures is in the [Rmarkdown document](https://github.com/rOpenGov/fennica/blob/master/inst/examples/20151209-HelsinkiDH.Rmd).
 
@@
 
-```{r 20150912-HDH-Author, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=4, fig.width=8}
+```{r 20150912-HDH-Author, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=4, fig.width=12}
 p1 <- top_plot(dfo, "author", 10) + ggtitle(paste("Top authors (", min(na.omit(dfo$publication_year)), "-", max(na.omit(dfo$publication_year)), ")", sep = ""))

### 2015-12-08 inst/examples/20151209-HelsinkiDH.Rmd
ok

@@
 ```{r 20150912-HDH-Author, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=4, fig.width=12}
-p1 <- top_plot(dfo, "author", 10) + ggtitle(paste("Top authors (", min(na.omit(dfo$publication_year)), "-", max(na.omit(dfo$publication_year)), ")", sep = ""))
+p1 <- top_plot(dfo, "author", 10) + ggtitle(paste("Top authors (", min(na.omit(dfo$publication_year)), "-", max(na.omit(dfo$publication_year)), ")", sep = "")) + ylab("Title count (n)")
 
-p2 <- top_plot(df, "author", 10) + ggtitle(paste("Top authors (", min(na.omit(df$publication_year)), "-", max(na.omit(df$publication_year)), ")", sep = ""))
+p2 <- top_plot(df, "author", 10) + ggtitle(paste("Top authors (", min(na.omit(df$publication_year)), "-", max(na.omit(df$publication_year)), ")", sep = "")) + ylab("Title count (n)")
 

### 2015-12-08 inst/examples/20151209-HelsinkiDH.Rmd
ok

--- 2015-12-08 inst/examples/20151209-HelsinkiDH.Rmd
@@
 ```{r 20150912-HDH-Author, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=4, fig.width=12}
-p1 <- top_plot(dfo, "author", 10) + ggtitle(paste("Top authors (", min(na.omit(dfo$publication_year)), "-", max(na.omit(dfo$publication_year)), ")", sep = ""))
+p1 <- top_plot(dfo, "author", 10) + ggtitle(paste("Top authors (", min(na.omit(dfo$publication_year)), "-", max(na.omit(dfo$publication_year)), ")", sep = "")) + xlab("Title count (n)")
 
-p2 <- top_plot(df, "author", 10) + ggtitle(paste("Top authors (", min(na.omit(df$publication_year)), "-", max(na.omit(df$publication_year)), ")", sep = ""))
+p2 <- top_plot(df, "author", 10) + ggtitle(paste("Top authors (", min(na.omit(df$publication_year)), "-", max(na.omit(df$publication_year)), ")", sep = "")) + xlab("Title count (n)")
 

### 2015-12-08 inst/examples/20151209-HelsinkiDH.Rmd
ok

--- 2015-12-08 inst/examples/20151209-HelsinkiDH.Rmd
@@
 ```{r 20150912-HDH-Author, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=4, fig.width=12}
-p1 <- top_plot(dfo, "author", 10) + ggtitle(paste("Top authors (", min(na.omit(dfo$publication_year)), "-", max(na.omit(dfo$publication_year)), ")", sep = ""))
+p1 <- top_plot(dfo, "author", 10) + ggtitle(paste("Top authors (", min(na.omit(dfo$publication_year)), "-", max(na.omit(dfo$publication_year)), ")", sep = "")) + ylab("Title count (n)")
+print(p1)
 
-p2 <- top_plot(df, "author", 10) + ggtitle(paste("Top authors (", min(na.omit(df$publication_year)), "-", max(na.omit(df$publication_year)), ")", sep = ""))
-
-library(gridExtra)
-grid.arrange(p1, p2, nrow = 1)
+p2 <- top_plot(df, "author", 10) + ggtitle(paste("Top authors (", min(na.omit(df$publication_year)), "-", max(na.omit(df$publication_year)), ")", sep = "")) + ylab("Title count (n)")
+print(p2)
 ```

### 2015-12-08 inst/examples/20151209-HelsinkiDH.Rmd
ok

@@
 
-```{r 20150912-HDH-Author, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=4, fig.width=12}
+```{r 20150912-HDH-Author, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=4, fig.width=6}
 p1 <- top_plot(dfo, "author", 10) + ggtitle(paste("Top authors (", min(na.omit(dfo$publication_year)), "-", max(na.omit(dfo$publication_year)), ")", sep = "")) + ylab("Title count (n)")

### 2015-12-08 inst/examples/20151209-HelsinkiDH.Rmd
20151209 pics

@@
 
-```{r 20150912-HDH-init, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE}
+```{r 20151209-HDH-init, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE}
 library(stringr)
@@
 
-```{r 20150912-HDH-TurkuVSOthers, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=4, fig.width=8}
+```{r 20151209-HDH-TurkuVSOthers, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=4, fig.width=8}
 
@@
 
-```{r 20150912-HDH-Author, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=4, fig.width=6}
+```{r 20151209-HDH-Author, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=4, fig.width=6}
 p1 <- top_plot(dfo, "author", 10) + ggtitle(paste("Top authors (", min(na.omit(dfo$publication_year)), "-", max(na.omit(dfo$publication_year)), ")", sep = "")) + ylab("Title count (n)")

### 2015-12-08 inst/examples/20151209-HelsinkiDH.Rmd
author plots

@@
 ```{r 20151209-HDH-TurkuVSOthers, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=4, fig.width=8}
-
 # Let us focus on years 1400-1828
-df <- dfo %>% filter(publication_year > 1400 & publication_year < 1829)
+df <- dfo %>% filter(publication_year > 1400 & publication_year < 1829) %>%
+      filter(!is.na(country)) %>%
+      filter(!is.na(publication_place) & !is.na(paper.consumption.km2) & paper.consumption.km2 > -0.01)
 
@@
 myplace <- "Turku"
+
 df$myplace <- rep(NA, nrow(df))
@@
 df$myplace[!df$publication_place == myplace & df$country == "Finland"] <- "Finland"
-df$myplace[!df$country == "Finland"] <- "Foreign"
+df$myplace[!df$country == "Finland" & !df$publication_place == myplace] <- "Foreign"
 df$myplace <- factor(df$myplace, levels = rev(c("Foreign", "Finland", "Turku")))
@@
 # Group by year/decade and Turku/Other
-dfs <- df %>%
-  #filter(publication_year >= 1600) %>%
-  filter(!is.na(publication_place) & !is.na(paper.consumption.km2) & paper.consumption.km2 > -0.01) %>%
-  group_by(publication_decade, myplace) %>%
-  summarise(titles = n(), paper = sum(paper.consumption.km2))
+dfs <- df %>% group_by(publication_decade, myplace) %>%
+  summarise(titles = n(), paper = sum(paper.consumption.km2, na.rm = TRUE))
 
@@
 print(p)
-
-#p + guides(fill = guide_legend(order = 1))
 ```
@@
 ```
+
+```{r 20151209-HDH-topauthor, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=4, fig.width=6}
+# Top author
+topa <- names(rev(sort(table(dfo$author))))[1:2]
+
+dfs <- dfo %>% filter(author %in% topa) %>% group_by(author, publication_decade) %>% summarize(paper = sum(paper.consumption.km2, na.rm = T), titles = n())
+
+p1 <- p2 <- ggplot(dfs, aes(x = publication_decade, y = titles, color = author)) + geom_point() + geom_line(size = 2) + scale_color_manual(values = c("blue", "red")) + ggtitle("Title count") + xlab("Publication decade") + ylab("Title count (n)")
+print(p1)
+
+p2 <- ggplot(dfs, aes(x = publication_decade, y = paper, color = author)) + geom_point() + geom_line(size = 2) + scale_color_manual(values = c("blue", "red")) + ggtitle("Paper consumption") + xlab("Publication decade") + ylab("Paper (km2)")
+print(p2)
+```

### 2015-12-08 inst/examples/20151209-HelsinkiDH.Rmd
ok

@@
 
-```{r 20151209-HDH-topauthor, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=4, fig.width=6}
+```{r 20151209-HDH-topauthor, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=4, fig.width=8}
 # Top author

### 2015-12-08 inst/examples/20151209-HelsinkiDH.Rmd
gatherings timeline

@@
 ```
+
+```{r 20151209-HDH-topplace, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=4, fig.width=6}
+top_plot(dfo, "publication_place", 10) + ylab("Title count (n)") + ggtitle("Top publication places")
+
+top_plot(dfo, "subject_topic", 10) + ylab("Title count (n)") + ggtitle("Top themes")
+```
+
+```{r 20151209-HDH-topg, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=4, fig.width=6}
+topg <- setdiff(names(rev(sort(table(dfo$gatherings))))[1:6], "NA")
+dfs <- dfo %>%
+    filter(gatherings %in% topg & publication_year > 1650) %>%
+    group_by(publication_decade, gatherings) %>% tally()
+dfs$gatherings <- order_gatherings(dfs$gatherings)    
+p <- ggplot(dfs, aes(x = publication_decade, y = n, color = gatherings)) + geom_point(size = 3) + geom_smooth(fill = "lightgray", size = 2, alpha = 0.2) + ggtitle("Top gatherings timeline") + ylim(c(0, max(dfs$n)))
+print(p)
+```

### 2015-12-08 inst/examples/20151209-HelsinkiDH.Rmd
author plots

--- 2015-12-08 inst/examples/20151209-HelsinkiDH.Rmd
@@
 ```
+
+```{r 20151209-HDH-topplace, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=4, fig.width=5}
+top_plot(dfo, "publication_place", 10) + ylab("Title count (n)") + ggtitle("Top publication places")
+```
+
+```{r 20151209-HDH-toptopic, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=4, fig.width=6}
+top_plot(dfo, "subject_topic", 10) + ylab("Title count (n)") + ggtitle("Top themes")
+```
+
+```{r 20151209-HDH-topg, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=6, fig.width=9}
+topg <- setdiff(names(rev(sort(table(dfo$gatherings))))[1:6], "NA")
+dfs <- dfo %>%
+    filter(gatherings %in% topg & publication_year > 1650) %>%
+    group_by(publication_decade, gatherings) %>% tally()
+dfs$gatherings <- order_gatherings(dfs$gatherings)    
+p <- ggplot(dfs, aes(x = publication_decade, y = n, color = gatherings)) + geom_point(size = 3) + geom_smooth(fill = "lightgray", size = 2, alpha = 0.2) + ggtitle("Top gatherings timeline") + ylim(c(0, max(dfs$n)))
+print(p)
+```

### 2015-12-08 inst/examples/20151209-HelsinkiDH.Rmd
ok

--- 2015-12-08 inst/examples/20151209-HelsinkiDH.Rmd
@@
 ```
+
+```{r 20151209-HDH-topplace, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=4, fig.width=5}
+top_plot(dfo, "publication_place", 10) + ylab("Title count (n)") + ggtitle("Top publication places")
+```
+
+```{r 20151209-HDH-toptopic, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=4, fig.width=6}
+top_plot(dfo, "subject_topic", 10) + ylab("Title count (n)") + ggtitle("Top themes")
+```
+
+```{r 20151209-HDH-topg, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=6, fig.width=10}
+topg <- setdiff(names(rev(sort(table(dfo$gatherings))))[1:6], "NA")
+dfs <- dfo %>%
+    filter(gatherings %in% topg & publication_year > 1650) %>%
+    group_by(publication_decade, gatherings) %>% tally()
+dfs$gatherings <- order_gatherings(dfs$gatherings)    
+p <- ggplot(dfs, aes(x = publication_decade, y = n, color = gatherings)) + geom_point(size = 3) + geom_smooth(fill = "lightgray", size = 2, alpha = 0.2) + ggtitle("Top gatherings timeline") + ylim(c(0, max(dfs$n))) + xlab("Publication decade") + ylab("Title count (n)")
+print(p)
+```

### 2015-12-08 inst/examples/20151209-HelsinkiDH.Rmd
ok

--- 2015-12-08 inst/examples/20151209-HelsinkiDH.Rmd
@@
 
-```{r 20151209-HDH-topg, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=6, fig.width=9}
+```{r 20151209-HDH-topg, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=5, fig.width=8}
 topg <- setdiff(names(rev(sort(table(dfo$gatherings))))[1:6], "NA")
@@
 dfs$gatherings <- order_gatherings(dfs$gatherings)    
-p <- ggplot(dfs, aes(x = publication_decade, y = n, color = gatherings)) + geom_point(size = 3) + geom_smooth(fill = "lightgray", size = 2, alpha = 0.2) + ggtitle("Top gatherings timeline") + ylim(c(0, max(dfs$n)))
+p <- ggplot(dfs, aes(x = publication_decade, y = n, color = gatherings)) + geom_point(size = 3) + geom_smooth(fill = "lightgray", size = 2, alpha = 0.2) + ggtitle("Top gatherings timeline") + ylim(c(0, max(dfs$n))) + xlab("Publication decade") + ylab("Title count (n)")
 print(p)

### 2015-12-08 inst/examples/20151209-HelsinkiDH.Rmd
ok

@@
 
-```{r 20151209-HDH-topplace, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=4, fig.width=5}
+```{r 20151209-HDH-topplace, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=4, fig.width=4}
 top_plot(dfo, "publication_place", 10) + ylab("Title count (n)") + ggtitle("Top publication places")

### 2015-12-08 inst/examples/20151209-HelsinkiDH.Rmd
ok

@@
 
-```{r 20151209-HDH-topg, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=5, fig.width=8}
+```{r 20151209-HDH-topg, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=5, fig.width=9}
 topg <- setdiff(names(rev(sort(table(dfo$gatherings))))[1:6], "NA")

### 2016-01-17 inst/examples/20151209-HelsinkiDH.Rmd

@@
 
-```{r 20151209-HDH-topplace, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=4, fig.width=4}
-top_plot(dfo, "publication_place", 10) + ylab("Title count (n)") + ggtitle("Top publication places")
+```{r 20151209-HDH-topplace, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=4, fig.width=6}
+p1 <- top_plot(dfo, "publication_place", 10) + ylab("Title count (n)") + ggtitle(paste("Top publication places (", min(na.omit(dfo$publication_year)), "-", max(na.omit(dfo$publication_year)), ")", sep = ""))
+print(p1)
+
+p2 <- top_plot(df, "publication_place", 10) + ylab("Title count (n)") + ggtitle(paste("Top publication places (", min(na.omit(df$publication_year)), "-", max(na.omit(df$publication_year)), ")", sep = ""))
+print(p2)
 ```
@@
 ```{r 20151209-HDH-toptopic, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=4, fig.width=6}
-top_plot(dfo, "subject_topic", 10) + ylab("Title count (n)") + ggtitle("Top themes")
+p1 <- top_plot(dfo, "subject_topic", 10) + ylab("Title count (n)") + ggtitle(paste("Top themes (", min(na.omit(dfo$publication_year)), "-", max(na.omit(dfo$publication_year)), ")", sep = ""))
+print(p1)
+
+p2 <- top_plot(df, "subject_topic", 10) + ylab("Title count (n)") + ggtitle(paste("Top themes (", min(na.omit(df$publication_year)), "-", max(na.omit(df$publication_year)), ")", sep = ""))
+print(p2)
 ```

### 2016-01-17 inst/examples/Paper.Rmd

@@
   summarise(titles=n()) %>% arrange(desc(titles))
-top10 <- tail(head(authors,11),10)
-dfs10 <- df %>% filter(publication_year > 1400 & publication_year < 1829) %>%
-  filter(author_name %in% c(top10$author_name)) %>%
+top10.authors <- tail(head(authors,11),10)
+df.authors <- df %>% filter(publication_year > 1400 & publication_year < 1829) %>%
+  filter(author_name %in% c(top10.authors$author_name)) %>%
+  filter(!is.na(paper.consumption.km2) & paper.consumption.km2 > -0.01) %>%
+  group_by(publication_year) %>%
+  summarise(titles = n(), paper = sum(paper.consumption.km2))
+df.Turku <- df %>% filter(publication_year > 1400 & publication_year < 1829) %>%
+  filter(publication_place == "Turku") %>%
+  filter(!is.na(paper.consumption.km2) & paper.consumption.km2 > -0.01) %>%
+  group_by(publication_year) %>%
+  summarise(titles = n(), paper = sum(paper.consumption.km2))
+df.Tukholma <- df %>% filter(publication_year > 1400 & publication_year < 1829) %>%
+  filter(publication_place == "Stockholm") %>%
+  filter(!is.na(paper.consumption.km2) & paper.consumption.km2 > -0.01) %>%
+  group_by(publication_year) %>%
+  summarise(titles = n(), paper = sum(paper.consumption.km2))
+df.Vaasa <- df %>% filter(publication_year > 1400 & publication_year < 1829) %>%
+  filter(publication_place == "Vaasa") %>%
+  filter(!is.na(paper.consumption.km2) & paper.consumption.km2 > -0.01) %>%
+  group_by(publication_year) %>%
+  summarise(titles = n(), paper = sum(paper.consumption.km2))
+df.Uppsala <- df %>% filter(publication_year > 1400 & publication_year < 1829) %>%
+  filter(publication_place == "Uppsala") %>%
   filter(!is.na(paper.consumption.km2) & paper.consumption.km2 > -0.01) %>%
@@
 ```{r titles10, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=4, fig.width=8}
-p1b <- ggplot(dfs10, aes(y = titles, x = publication_year))
+p1b <- ggplot(df.authors, aes(y = titles, x = publication_year))
 p1b <- p1b + geom_smooth(color = "black") + geom_point()
@@
 ```{r paper10, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=4, fig.width=8.2}
-p2b <- ggplot(dfs10, aes(y = paper, x = publication_year))
+p2b <- ggplot(df.authors, aes(y = paper, x = publication_year))
 p2b <- p2b + geom_smooth(color = "black") + geom_point() +
@@
 ```
+
+```{r titlesTurku, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=4, fig.width=8}
+p1.Turku <- ggplot(df.Turku, aes(y = titles, x = publication_year))
+p1.Turku <- p1.Turku + geom_smooth(color = "black") + geom_point()
+p1.Turku <- p1.Turku + xlab("Publication Year") + ylab("Title Count") 
+p1.Turku <- p1.Turku + theme(axis.text.x = element_text(size = 20), axis.text.y = element_text(size = 20))
+p1.Turku <- p1.Turku + theme(axis.title.x = element_text(size = 20), axis.title.y = element_text(size = 20))
+p1.Turku <- p1.Turku + guides(fill = "none", alpha = "none")
+p1.Turku <- p1.Turku + ggtitle("Finnish publications in Turku, 1488-1828: title count")
+print(p1.Turku)
+```
+
+```{r paperTurku, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=4, fig.width=8.2}
+p2.Turku <- ggplot(df.Turku, aes(y = paper, x = publication_year))
+p2.Turku <- p2.Turku + geom_smooth(color = "black") + geom_point() +
+       xlab("Publication Year") +
+       ylab("Paper Consumption (km2)")
+
+p2.Turku <- p2.Turku + theme(axis.text.x = element_text(size = 20), axis.text.y = element_text(size = 20))
+p2.Turku <- p2.Turku + theme(axis.title.x = element_text(size = 20), axis.title.y = element_text(size = 20))
+p2.Turku <- p2.Turku + guides(fill = "none", alpha = "none")
+p2.Turku <- p2.Turku + ggtitle("Finnish publications in Turku, 1488-1828: paper consumption")
+print(p2.Turku)
+```
+
+```{r titlesTukholma, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=4, fig.width=8}
+p1.Tukholma <- ggplot(df.Tukholma, aes(y = titles, x = publication_year))
+p1.Tukholma <- p1.Tukholma + geom_smooth(color = "black") + geom_point()
+p1.Tukholma <- p1.Tukholma + xlab("Publication Year") + ylab("Title Count") 
+p1.Tukholma <- p1.Tukholma + theme(axis.text.x = element_text(size = 20), axis.text.y = element_text(size = 20))
+p1.Tukholma <- p1.Tukholma + theme(axis.title.x = element_text(size = 20), axis.title.y = element_text(size = 20))
+p1.Tukholma <- p1.Tukholma + guides(fill = "none", alpha = "none")
+p1.Tukholma <- p1.Tukholma + ggtitle("Finnish publications in Stockholm, 1488-1828: title count")
+print(p1.Tukholma)
+```
+
+```{r paperTukholma, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=4, fig.width=8.2}
+p2.Tukholma <- ggplot(df.Tukholma, aes(y = paper, x = publication_year))
+p2.Tukholma <- p2.Tukholma + geom_smooth(color = "black") + geom_point() +
+       xlab("Publication Year") +
+       ylab("Paper Consumption (km2)")
+
+p2.Tukholma <- p2.Tukholma + theme(axis.text.x = element_text(size = 20), axis.text.y = element_text(size = 20))
+p2.Tukholma <- p2.Tukholma + theme(axis.title.x = element_text(size = 20), axis.title.y = element_text(size = 20))
+p2.Tukholma <- p2.Tukholma + guides(fill = "none", alpha = "none")
+p2.Tukholma <- p2.Tukholma + ggtitle("Finnish publications in Stockholm, 1488-1828: paper consumption")
+print(p2.Tukholma)
+```
+
+```{r titlesVaasa, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=4, fig.width=8}
+p1.Vaasa <- ggplot(df.Vaasa, aes(y = titles, x = publication_year))
+p1.Vaasa <- p1.Vaasa + geom_smooth(color = "black") + geom_point()
+p1.Vaasa <- p1.Vaasa + xlab("Publication Year") + ylab("Title Count") 
+p1.Vaasa <- p1.Vaasa + theme(axis.text.x = element_text(size = 20), axis.text.y = element_text(size = 20))
+p1.Vaasa <- p1.Vaasa + theme(axis.title.x = element_text(size = 20), axis.title.y = element_text(size = 20))
+p1.Vaasa <- p1.Vaasa + guides(fill = "none", alpha = "none")
+p1.Vaasa <- p1.Vaasa + ggtitle("Finnish publications in Vaasa, 1488-1828: title count")
+print(p1.Vaasa)
+```
+
+```{r paperVaasa, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=4, fig.width=8.2}
+p2.Vaasa <- ggplot(df.Vaasa, aes(y = paper, x = publication_year))
+p2.Vaasa <- p2.Vaasa + geom_smooth(color = "black") + geom_point() +
+       xlab("Publication Year") +
+       ylab("Paper Consumption (km2)")
+
+p2.Vaasa <- p2.Vaasa + theme(axis.text.x = element_text(size = 20), axis.text.y = element_text(size = 20))
+p2.Vaasa <- p2.Vaasa + theme(axis.title.x = element_text(size = 20), axis.title.y = element_text(size = 20))
+p2.Vaasa <- p2.Vaasa + guides(fill = "none", alpha = "none")
+p2.Vaasa <- p2.Vaasa + ggtitle("Finnish publications in Vaasa, 1488-1828: paper consumption")
+print(p2.Vaasa)
+```
+
+```{r titlesUppsala, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=4, fig.width=8}
+p1.Uppsala <- ggplot(df.Uppsala, aes(y = titles, x = publication_year))
+p1.Uppsala <- p1.Uppsala + geom_smooth(color = "black") + geom_point()
+p1.Uppsala <- p1.Uppsala + xlab("Publication Year") + ylab("Title Count") 
+p1.Uppsala <- p1.Uppsala + theme(axis.text.x = element_text(size = 20), axis.text.y = element_text(size = 20))
+p1.Uppsala <- p1.Uppsala + theme(axis.title.x = element_text(size = 20), axis.title.y = element_text(size = 20))
+p1.Uppsala <- p1.Uppsala + guides(fill = "none", alpha = "none")
+p1.Uppsala <- p1.Uppsala + ggtitle("Finnish publications in Uppsala, 1488-1828: title count")
+print(p1.Uppsala)
+```
+
+```{r paperUppsala, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=4, fig.width=8.2}
+p2.Uppsala <- ggplot(df.Uppsala, aes(y = paper, x = publication_year))
+p2.Uppsala <- p2.Uppsala + geom_smooth(color = "black") + geom_point() +
+       xlab("Publication Year") +
+       ylab("Paper Consumption (km2)")
+
+p2.Uppsala <- p2.Uppsala + theme(axis.text.x = element_text(size = 20), axis.text.y = element_text(size = 20))
+p2.Uppsala <- p2.Uppsala + theme(axis.title.x = element_text(size = 20), axis.title.y = element_text(size = 20))
+p2.Uppsala <- p2.Uppsala + guides(fill = "none", alpha = "none")
+p2.Uppsala <- p2.Uppsala + ggtitle("Finnish publications in Uppsala, 1488-1828: paper consumption")
+print(p2.Uppsala)
+```

### 2016-02-04 inst/examples/summary.Rmd
ok
fixed bugs with bibliographica updates

@@
 title: "Summary"
-author: "Niko Ilomäki and Leo Lahti"
-date: "Tuesday, October 20, 2015"
+author: "Leo Lahti and Niko Ilomäki"
+date: "Feb 3, 2016"
 output: markdown_document
@@
 ```{r missing2, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=10, fig.height=15}
-dfs <- df %>% select(author, publication_place, country, publication_year, published_from, published_till, corporate, area, pagecount, gatherings, width, height, paper.consumption.km2, publisher, self_published)
+dfs <- df %>% select(author, publication_place, country, publication_year, publication_year_from, publication_year_till, corporate, area, pagecount, gatherings, width, height, paper.consumption.km2, publisher, self_published)
 success <- as.data.frame(t(apply(dfs, 2, function (x) {sum(!is.na(gsub("^NA$", NA, as.character(x))))})))
@@
 real.success[["publication_year"]] <- success$publication_year/original.nonNA$publication_time
-real.success[["published_from"]] <- success$published_from/original.nonNA$publication_time
-real.success[["published_till"]] <- success$published_till/original.nonNA$publication_time
+real.success[["publication_year_from"]] <- success$published_from/original.nonNA$publication_time
+real.success[["publication_year_till"]] <- success$published_till/original.nonNA$publication_time
 real.success[["corporate"]] <- success$corporate/original.nonNA$corporate
@@
 
+[Discarded author first names](output.tables/author_name_discarded_first.csv)
+
+[Discarded author last names](output.tables/author_name_discarded_last.csv)
+
+[Authors missing life years](output.tables/authors_missing_lifeyears.csv)
+
 Top-`r ntop` uniquely identified authors and number of documents for each (duplicate docs not checked yet).

### 2016-02-04 inst/examples/enrich.R

@@ -1,32 +1,40 @@
-print("Unique author IDs")
-df$author <- author_unique(df, initialize.first = TRUE)
+print("Enrich author info")
+# Life years + author_unique field
+library(estc)
+#life.info <- read.csv("author_info.csv", sep = "\t", header = TRUE)
+ambiguous.authors <- ambiguous_authors_table()
+df.preprocessed <- augment_author(df.preprocessed, life_info = NULL, ambiguous.authors)
+
+# TODO improve: many names are missing gender now
+print("Estimate author genders")
+# Assumes that the author name is in the form "Last, First".
+df.preprocessed$author_gender <- get_gender(pick_firstname(df.preprocessed$author_name, format = "last, first"))
 
 print("Self-published docs where author is known but publisher not")
 # Note: also unknown authors are considered as self-publishers
 print("Add a separate self-published field")
-tmp <- self_published(df)
-df$self_published <- tmp$self_published
-df$publisher <- tmp$publisher
+tmp <- self_published(df.preprocessed)
+df.preprocessed$self_published <- tmp$self_published
+df.preprocessed$publisher <- tmp$publisher
 
 # Now published from == published in for simplicity; perhaps separated later
-df$publication_year <- df$publication_year_from
+df.preprocessed$publication_year <- df.preprocessed$publication_year_from
 
-# Add publication country
-df$country <- get_country(df$publication_place)$country
+print("Add publication country")
+df.preprocessed$country <- get_country(df.preprocessed$publication_place)$country
 
-# Estimate missing dimension info
-dim.orig <- df[, c("gatherings.original", "width.original", "height.original")]
+print("Estimate missing dimension info")
+dim.orig <- df.preprocessed[, c("gatherings.original", "width.original", "height.original")]
 names(dim.orig) <- gsub("\\.original$", "", names(dim.orig))
 dim.estimated <- augment_dimension_table(dim.orig)
-df <- cbind(df, dim.estimated)
-
+df.preprocessed <- cbind(df.preprocessed, dim.estimated)
 
 print("Add estimated paper consumption")
 # One m2 is 100 * 100 cm2 = 1e4 cm2
 # One km2 is 1000 * 1000 m2 = 1e6 m2 = 1e10 cm2
 # Estimated average print run per document: 1000
 printrun <- 1000
[…]

### 2016-02-04 inst/examples/summary.Rmd
ok

@@
 real.success[["publication_year"]] <- success$publication_year/original.nonNA$publication_time
-real.success[["publication_year_from"]] <- success$published_from/original.nonNA$publication_time
-real.success[["publication_year_till"]] <- success$published_till/original.nonNA$publication_time
+real.success[["publication_year_from"]] <- success$publication_year_from/original.nonNA$publication_time
+real.success[["publication_year_till"]] <- success$publication_year_till/original.nonNA$publication_time
 real.success[["corporate"]] <- success$corporate/original.nonNA$corporate

### 2016-02-05 inst/examples/summary.Rmd
ok

@@
 ```{r publication_time, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=10}
-hist(df$publication_year, main = "Document frequencies over time")
+#hist(df$publication_year, main = "Document frequencies over time")
+dfs <- df %>% group_by(publication_year) %>% tally()
+ggplot(dfs, aes(x = publication_year, y = n)) + geom_point() + ggtitle("Document frequencies over time") + ylab("Title count") + xlab("Publication year")
 ```

### 2016-02-05 inst/examples/summary.Rmd
ok

@@
 df.orig <- readRDS("df.orig.Rds")
-
-# Need to use this trick to have NAs for all data types
-missing <- 100*apply(df, 2, function (x) {mean(is.na(gsub("^NA$", NA, as.character(x))))})
-df2 <- data.frame(list(missing = missing, field = names(missing)))
-df2$field <- factor(df2$field, levels = df2$field[rev(order(df2$missing))])
 ```
@@
 ```{r missingb, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=10, fig.height=15}
+# Need to use this trick to have NAs for all data types
+missing <- 100*apply(df, 2, function (x) {mean(is.na(gsub("^NA$", NA, as.character(x))))})
+df2 <- data.frame(list(missing = missing, field = names(missing)))
+df2$field <- factor(df2$field, levels = df2$field[rev(order(df2$missing))])
+
 theme_set(theme_bw(15))

### 2016-02-05 inst/examples/import2.R

@@ -1,6 +1,5 @@
 print("Read raw data")
-df <- bibliographica::read_bibliographic_metadata("data/fennica.csv.gz")
-df.orig <- df
+df.orig <- bibliographica::read_bibliographic_metadata("data/fennica.csv.gz")
 
 print("Entry identifier to match back to the originals")
 df.preprocessed <- data.frame(original_row = df.orig$original_row)
@@ -50,7 +49,8 @@ for (field in update.fields) {
 
 }
 
-#saveRDS(df.preprocessed, "df.Rds")
+df.preprocessed0 <- df.preprocessed
+saveRDS(df.preprocessed0, "df0.Rds")
 saveRDS(df.orig, "df.orig.Rds")
 
 

### 2016-02-05 inst/examples/20151209-HelsinkiDH.Rmd
ok

@@
 ```{r 20151209-HDH-toptopic, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=4, fig.width=6}
-p1 <- top_plot(dfo, "subject_topic", 10) + ylab("Title count (n)") + ggtitle(paste("Top themes (", min(na.omit(dfo$publication_year)), "-", max(na.omit(dfo$publication_year)), ")", sep = ""))
+p1 <- top_plot(dfo, "topic", 10) + ylab("Title count (n)") + ggtitle(paste("Top themes (", min(na.omit(dfo$publication_year)), "-", max(na.omit(dfo$publication_year)), ")", sep = ""))
 print(p1)
 
-p2 <- top_plot(df, "subject_topic", 10) + ylab("Title count (n)") + ggtitle(paste("Top themes (", min(na.omit(df$publication_year)), "-", max(na.omit(df$publication_year)), ")", sep = ""))
+p2 <- top_plot(df, "topic", 10) + ylab("Title count (n)") + ggtitle(paste("Top themes (", min(na.omit(df$publication_year)), "-", max(na.omit(df$publication_year)), ")", sep = ""))
 print(p2)

### 2016-02-05 inst/examples/summary.Rmd
ok

@@
 ```{r missing, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=10, fig.height=15}
-
 library(stringr)
@@
 df.orig <- readRDS("df.orig.Rds")
+```
+
+Conversions from the original to preprocessed fields:
+
+```{r summary-conversions, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=10, fig.height=15}
+field.conversions <- cbind(harmonize_field_names(), preprocessed = unname(sapply(conversions, function (x) {paste(x, collapse = ";")})[as.character(harmonize_field_names()$name)]))
+names(field.conversions) <- c("marc_clearname", "marc_field", "preprocessed_fields")
+field.conversions <- field.conversions[, c(2, 1, 3)]
+kable(field.conversions)
 ```
@@
 # List all topics
-spl <- strsplit(na.omit(as.character(df$subject_topic)), ";")
+spl <- strsplit(na.omit(as.character(df$topic)), ";")
 
@@
 Top-`r ntop` topics and number of documents for each.
-In total, there are `r length(unique(df$subject_topic))` unique topics and `r sum(!is.na(df$subject_topic))` documents assigned to one or more topics (`r round(100*mean(!is.na(df$subject_topic)))`).
+In total, there are `r length(unique(df$topic))` unique topics and `r sum(!is.na(df$topic))` documents assigned to one or more topics (`r round(100*mean(!is.na(df$topic)))`).
 
 ```{r topics3, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=10}
-par(mar = c(5, 10, 3, 1)); barplot(rev(rev(sort(table(df$subject_topic)))[1:ntop]), horiz = T, las = 1, cex.names = 0.8, xlab = "Documents", main = "Most common topics")
+par(mar = c(5, 10, 3, 1)); barplot(rev(rev(sort(table(df$topic)))[1:ntop]), horiz = T, las = 1, cex.names = 0.8, xlab = "Documents", main = "Most common topics")
 ```

### 2016-02-05 inst/examples/import.R

@@ -1,6 +1,6 @@
 print("Read raw data")
-df <- bibliographica::read_bibliographic_metadata("data/fennica.csv.gz")
-df.orig <- df
+df.orig <- bibliographica::read_bibliographic_metadata("data/fennica.csv.gz")
+df <- df.orig
 
 print("Languages")
 df <- cbind(

### 2016-02-23 inst/examples/summary.Rmd
Finnish geoplaces added - still some places missing

@@
 author: "Leo Lahti and Niko Ilomäki"
-date: "Feb 3, 2016"
+date: "Feb 24, 2016"
 output: markdown_document
@@
 [Complete geoplace listing](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/geoplaces.csv)
+
+## Geocoordinates for publication places
+
+Altogether ```r 100 * mean(is.na(df.preprocessed$latitude) | is.na(df.preprocessed$longitude))``` places have missing geocoordinates:
+
+[Places with missing geocoordinates](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/missing_geocoordinates.csv)

### 2016-02-23 inst/examples/enrich.R

@@ -24,10 +24,115 @@ print("Add publication country")
 df.preprocessed$country <- get_country(df.preprocessed$publication_place)$country
 
 print("Enrich geo info: Geocoordinates")
+skip <- FALSE
+if (skip)  {
 load("geonames.RData")
 load("places.geonames.RData") # places.geonames
-geoc <- bibliographica::get_geocoordinates(df.preprocessed$publication_place, geonames, places.geonames)
+
+# harmonize some publication place names manually
+place <- df.preprocessed$publication_place
+place <- gsub("New York NY", "New York", place)
+place <- gsub("Philadelphia PA", "Philadelphia", place)
+
+# Translations
+place <- gsub("Billnäs", "Karjaa", place)
+
+# Missing geoc - TODO manual table to augment the data
+#Hancock MI            217
+#Fitchburg MA          140
+#Ashtabula OH           51
+#Kaleva MI              50
+#Duluth MN              42
+#Calumet MI             37
+#Port Arthur ON         28
+#Astoria OR             25
+#Superior WI            14
+#Ironwood MI            13
+#New York Mills MN      10
+#Worcester MA            8
+#Quincy MA               7
+#Ishpeming MI            7
+#Visingsborg             5
+#Jönnköping              5
+#Almena WI               5
+#Seattle WA              4
+#Sääksmäki               3
+#Kauvatsa                3
+#Haunia                  3
+#Cincinnati OH           3
+#Tyrvää                  2
+#Smithville MN           2
+#Red Jacket MI           2
+#New Haven MA            2
+#Minneapolis MN          2
+#Leibzig                 2
+#Houghton MI             2
+#Harbor OH               2
+#Freiburg im Breisgau    2
+#Ely MI                  2
+#Cleveland OH            2
+#Chisholm MN             2
+#Watton MI               1
+#Virginia MN             1
+#Vammala                 1
+#Turtle Lake WI          1
+#Tsingshi                1
+#Tervonsalmi             1
+#Sudbury ON              1
+#St Louis Kaunti MI      1
+#Sarvilahti              1
+#Sandstone MI            1
+#Portland OR             1
+#Pinjainen               1
+#Nanaimo BC              1
+#Milwaukee WI            1
+#Laihiala                1
+#Kivennapa               1
+#Kaukaa                  1
+#Kaprio                  1
[…]

### 2016-03-02 inst/examples/20160303-Krakow.Rmd
ok

---
title: "Digital History in Finland, 1488-1828"
author: "Leo Lahti"
date: "March 3, 2016"
output: markdown_document
---

```{r 20160303-init, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE}
library(stringr)
library(dplyr)
library(ggplot2)
library(bibliographica)
library(fennica)
library(sorvi)

# Nice theme
theme_set(theme_bw(26))

# Read data
dfo <- readRDS("df.Rds")

# Add publication decade
# TODO add already in the original preprocessed data matrix
dfo$publication_decade <- 10*floor(dfo$publication_year/10)

# Remove very early and late years
dfo <- dfo %>% filter(publication_year > 1400 & publication_year < 1911)
```

```{r 20160303-turkuvsother, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=4, fig.width=8}
# Let us focus on years 1400-1828
df <- dfo %>% filter(publication_year > 1400 & publication_year < 1829) %>%
      filter(!is.na(country)) %>%
      filter(!is.na(publication_place) & !is.na(paper.consumption.km2) & paper.consumption.km2 > -0.01)

# Add indicator field: Turku or Not Turku
myplace <- "Turku"

df$myplace <- rep(NA, nrow(df))
df$myplace[df$publication_place == myplace] <- myplace
df$myplace[!df$publication_place == myplace & df$country == "Finland"] <- "Finland"
df$myplace[!df$country == "Finland" & !df$publication_place == myplace] <- "Foreign"
df$myplace <- factor(df$myplace, levels = rev(c("Foreign", "Finland", "Turku")))

# Keep entries with known publication place and paper consumption
# Group by year/decade and Turku/Other
dfs <- df %>% group_by(publication_decade, myplace) %>%
  summarise(titles = n(), paper = sum(paper.consumption.km2, na.rm = TRUE))

p <- ggplot(dfs, aes(x = publication_decade, y = paper, fill = myplace, order = -as.numeric(myplace))) +
     geom_bar(position = "stack", stat = "identity", color = "black") +
     ggtitle("Paper consumption") +
     #scale_fill_manual(values = c("blue", "black", "darkgreen")) +
     scale_fill_grey() +
     guides(fill = guide_legend(reverse = TRUE, title = "")) + 
     xlab("Publication decade") + ylab("Paper (km2)")
print(p)

#jpeg("20160303-paper.jpeg", quality = 100, height = 300, width = 480)
pdf("20160303-paper.pdf", width = 12, height = 9)
print(p)
dev.off()

p <- ggplot(dfs, aes(x = publication_decade, y = titles, fill = myplace, order = -as.numeric(myplace))) +
     geom_bar(position = "stack", stat = "identity", color = "black") +
     ggtitle("Title count") +
     # scale_fill_manual(values = c("blue", "black", "darkgreen")) +
     scale_fill_grey() +
     guides(fill = guide_legend(reverse = TRUE)) +      
     xlab("Publication decade") + ylab("Title count (n)")
print(p)

pdf("20160303-titles.pdf", width = 12, height = 9)
print(p)
dev.off()

```

### 2016-03-26 inst/examples/summary.Rmd
ok

@@
 ---
-title: "Summary"
+title: "Preprocessing summary"
 author: "Leo Lahti and Niko Ilomäki"
-date: "Feb 24, 2016"
-output: markdown_document
+date: "March 2, 2016"
 ---
@@
 df.orig <- readRDS("df.orig.Rds")
+conversions <- readRDS("conversions.Rds")
 ```

### 2016-03-26 inst/examples/import2.R

@@ -1,19 +1,10 @@
 print("Read raw data")
-df.orig <- bibliographica::read_bibliographic_metadata("data/fennica.csv.gz")
-
-print("Entry identifier to match back to the originals")
-df.preprocessed <- data.frame(original_row = df.orig$original_row)
-
-print("List raw data fields to be preprocessed")
-# update.fields <- names(df.orig) # Update all
-
-#> setdiff(names(df.orig), update.fields)
-#skip.fields <- c("language2", "title_uniform", "title_remainder", "physical_details", "physical_accomppanied", "note_general", "note_year", "note_source", "note_510c", "uncontrolled", "successor", "holder") 
-
-update.fields <- c("language", "author_date", "physical_extent", "author_name", "publisher", "corporate", "publication_time", "note_dissertation", "note_granter", "publication_place", "physical_dimension",
-"title", "subject_topic", "subject_geography", "publication_frequency", "publication_interval")
+df.orig <- bibliographica::read_bibliographic_metadata(original.datafile)
+saveRDS(df.orig, "df.orig.Rds")
 
 # -----------------------------------------------------------------------
+
+# Modify the original data if needed
 
 # Finnish/Swedish specific fixes 
 # In Finnish texts s. is used instead of p.		
@@ -22,39 +13,25 @@ synonyms <- read.csv(f, sep = ";")
 df.orig$physical_dimension <- harmonize_names(df.orig$physical_dimension,
 					synonyms, mode = "recursive")
 
+
+# Remove unknown fields
+# TODO: modify polish_fields such that it can automatically ignore
+# unknown fields
+#df.orig$language2 <- NULL
+#df.orig$title_remainder <- NULL
+#df.orig$physical_details <- NULL
+#df.orig$physical_accomppanied <- NULL
+#df.orig$note_general <- NULL
+#df.orig$note_year <- NULL
+
 # -----------------------------------------------------------------------
 
-# List how raw data fields will be converted into
-# preprocessed data fields
-conversions <- list()
-
-# Preprocess the field only if it has to be updated
-for (field in update.fields) {
-
-  print(field)
-
-  # Polish the given field
-  df.tmp <- polish_field(df.orig, field, verbose = FALSE)
-
-  # List the output fields for this input field
-  conversions[[field]] <- names(df.tmp)
-
[…]

### 2016-03-26 inst/examples/main.R

@@ -2,6 +2,9 @@
 output.folder <- "output.tables/"
 dir.create(output.folder)
 
+# Parsed raw data
+original.datafile <- "data/fennica.csv.gz"
+
 # ----------------------------------------------
 
 source("init.R")
@@ -9,5 +12,6 @@ source("import2.R")    # Data preprocessing
 source("enrich.R")
 source("validation.R")
 saveRDS(df.preprocessed, "df.Rds")
+
 source("summarize.R") # Summary tables
 source("knit_all.R")  # Summary md docs

### 2016-04-02 inst/examples/summary.Rmd
ok

@@
 ```{r summary-conversions, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=10, fig.height=15}
-field.conversions <- cbind(harmonize_field_names(), preprocessed = unname(sapply(conversions, function (x) {paste(x, collapse = ";")})[as.character(harmonize_field_names()$name)]))
+a <- harmonize_field_names()
+b <- sapply(conversions, function (x) {paste(x, collapse = ";")})
+coms <- intersect(as.character(a$name), names(b))
+
+field.conversions <- cbind(a[match(coms, a$name), ], preprocessed = unname(b[coms]))
 names(field.conversions) <- c("marc_clearname", "marc_field", "preprocessed_fields")

### 2016-04-02 inst/examples/summary.Rmd
ok

--- 2016-03-26 inst/examples/summary.Rmd
@@
 
-Conversions from the original to preprocessed fields:
-
-```{r summary-conversions, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=10, fig.height=15}
-field.conversions <- cbind(harmonize_field_names(), preprocessed = unname(sapply(conversions, function (x) {paste(x, collapse = ";")})[as.character(harmonize_field_names()$name)]))
-names(field.conversions) <- c("marc_clearname", "marc_field", "preprocessed_fields")
-field.conversions <- field.conversions[, c(2, 1, 3)]
-kable(field.conversions)
-```
-
-Percentage of non-NA entries among all documents in the preprocessed data (note that in some cases a significant fraction of this information is missing already in the raw data)
-
-```{r missingb, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=10, fig.height=15}
-# Need to use this trick to have NAs for all data types
-missing <- 100*apply(df, 2, function (x) {mean(is.na(gsub("^NA$", NA, as.character(x))))})
-df2 <- data.frame(list(missing = missing, field = names(missing)))
-df2$field <- factor(df2$field, levels = df2$field[rev(order(df2$missing))])
-
-theme_set(theme_bw(15))
-p <- ggplot(df2, aes(x = field, y = 100 - missing))
-p <- p + geom_bar(stat = "identity")
-p <- p + coord_flip()
-p <- p + ylab("")
-p <- p + xlab("")
-p <- p + ggtitle("Documents with data (%)")
-print(p)
-```
-
-Fields of special interest: real success percentage (proportion of successful conversions compared to non-NA entries in the original data):
-
-```{r missing2, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=10, fig.height=15}
-dfs <- df %>% select(author, publication_place, country, publication_year, publication_year_from, publication_year_till, corporate, area, pagecount, gatherings, width, height, paper.consumption.km2, publisher, self_published)
-success <- as.data.frame(t(apply(dfs, 2, function (x) {sum(!is.na(gsub("^NA$", NA, as.character(x))))})))
-original.nonNA <- as.data.frame(t(apply(select(df.orig, publication_place, publication_time, corporate, physical_extent, physical_dimension, publisher, author_name), 2, function (x) {sum(!is.na(gsub("^NA$", NA, as.character(x))))})))
-
-# Compare the number of non-NA entries in preprocessed data to number
-# of non-NA entries in the original data:
-real.success <- c()
-real.success[["publication_place"]] <- success$publication_place/original.nonNA$publication_place
-real.success[["country"]] <- success$country/original.nonNA$publication_place
-real.success[["publication_year"]] <- success$publication_year/original.nonNA$publication_time
-real.success[["publication_year_from"]] <- success$publication_year_from/original.nonNA$publication_time
-real.success[["publication_year_till"]] <- success$publication_year_till/original.nonNA$publication_time
-real.success[["corporate"]] <- success$corporate/original.nonNA$corporate
-real.success[["publisher"]] <- success$publisher/original.nonNA$publisher
-real.success[["self_published"]] <- success$self_published/original.nonNA$publisher
-real.success[["pagecount"]] <- success$pagecount/original.nonNA$physical_extent
-real.success[["area"]] <- success$area/original.nonNA$physical_dimension
-real.success[["gatherings"]] <- success$gatherings/original.nonNA$physical_dimension
-real.success[["author"]] <- success$author/original.nonNA$author
-real.success[["paper"]] <- success$paper.consumption.km2/sum(rowMeans(!is.na(df.orig[, c("physical_extent", "physical_dimension")])) == 1)
-par(mar = c(3, 8, 2, 1)); barplot(100*sort(real.success), horiz = T, main = "Real success rate (selected fields)", las = 1, xlim = c(0, 100), xlab = "Success rate (%)")
-```
-
-## Pagecounts
-
-[Discarded page count data](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/pagecount_discarded.csv)
-
-[Successfully converted page counts](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/pagecount_conversion.csv)
-
-Compare gatherings and cm2 sizes as a quality check. This includes all data; the area has been estimated from the gatherings when dimension information was not available.
-
-```{r summarysizecomp, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=7}
-dfs <- df %>% filter(!is.na(area) & !is.na(gatherings))
-dfs <- dfs[, c("gatherings", "area")]
-dfm <- melt(table(dfs))
-names(dfm) <- c("gatherings", "area", "documents")
-dfm$gatherings <- order_gatherings(dfm$gatherings)
-p <- ggplot(dfm, aes(x = gatherings, y = area)) 
-p <- p + scale_y_continuous(trans = "log2")
-p <- p + geom_point(aes(size = documents))
-p <- p + scale_size(trans="log10")
-p <- p + ggtitle("Document size distribution: gatherings vs. cm2")
-p <- p + xlab("Size (gatherings)")
-p <- p + ylab("Size (cm2)")
-p <- p + coord_flip()
-print(p)
-```
-
-Compare gatherings and page counts.
-
-```{r summarypagecomp, echo=FALSE, message=FALSE, warning=FALSE, fig.width=15, fig.height=7}
-dfs <- select(df, pagecount, gatherings) 
-dfs$pagecount <- as.numeric(gsub(" pages", "", dfs$pagecount))
-dfs <- dfs %>% filter(!is.na(pagecount) & !is.na(gatherings))
-dfg <- group_by(dfs, pagecount, gatherings) %>% tally()
-names(dfg) <- c("pages", "gatherings", "documents")
-dfg$gatherings <- order_gatherings(dfg$gatherings)
-ylims <- range(dfg$pages)
-p <- ggplot(dfg, aes(x = gatherings, y = pages)) 
-n <- nchar(max(na.omit(table(dfg$pages))))
-ylim <- ylim(ylims)
-p <- p + scale_y_log10(breaks=10^(0:n))
-p <- p + geom_point(aes(size = documents))
-p <- p + scale_size(trans="log10")
-p <- p + xlab("Size (gatherings)")
-p <- p + ylab("Pages (original and estimated)")
-p <- p + coord_flip()
-print(p)
-```
-
-## Publication time
-
-[Successfully converted publication times](output.tables/publication-time-accepted.csv)
-
-[Discarded publication times](output.tables/publication-time-discarded.csv)
-
-```{r publication_time, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=10}
-#hist(df$publication_year, main = "Document frequencies over time")
-dfs <- df %>% group_by(publication_year) %>% tally()
-ggplot(dfs, aes(x = publication_year, y = n)) + geom_point() + ggtitle("Document frequencies over time") + ylab("Title count") + xlab("Publication year")
-```
-
-## Publication places
-
-Top-`r ntop` publication places are shown together with the number of documents.
-This info is available for `r sum(!is.na(df$publication_place))` documents (`r round(100*mean(!is.na(df$publication_place)))`%).
-There are `r length(unique(str_trim(unlist(strsplit(as.character(df$publication_place), ";")))))` unique publication places.
-
-```{r publication_place, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=10}
-tab <- rev(sort(table(str_trim(unlist(strsplit(as.character(df$publication_place), ";"))))))
-ntop <- 50
-par(mar = c(5, 10, 3, 1)); barplot(log10(rev(tab[1:ntop])), horiz = T, las = 1, cex.names = 0.8, xlab = "Documents (log10)", main = "Most common publication places")
-```
-
-[Successfully converted publication places](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/publication_place_accepted.csv)
-
-[Discarded publication places](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/publication_place_discarded.csv)
-
-[Publication places missing country information](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/publication_place_missingcountry.csv)
-
-## Dimensions
-
-[Successfully converted dimension info](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/accepted_dimensions.csv)
-
-[Discarded dimension info](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/missing_dimensions.csv)
-
-[Discarded gatherings info](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/missing_gatherings.csv)
-
 ## Publisher
-
-[Discarded publisher info](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/publisher_discarded.csv) (Check that ok to discard these)
-
-[Converted publishers](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/publisher_accepted.csv) (Check for formatting and synonymes)
 
@@
 [Discarded corporate info](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/corporate_discarded.csv)
-
-## Authors
-
-[Accepted unique authors](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/author_accepted.csv)
-
-[Discarded authors](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/author_discarded.csv)
-
-[Discarded author first names](output.tables/author_name_discarded_first.csv)
-
-[Discarded author last names](output.tables/author_name_discarded_last.csv)
-
-[Authors missing life years](output.tables/authors_missing_lifeyears.csv)
-
-Top-`r ntop` uniquely identified authors and number of documents for each (duplicate docs not checked yet).
-
-```{r authors, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=10}
-a <- rev(rev(sort(table(df$author)))[2:ntop+1])
-par(mar = c(5, 10, 3, 1)); barplot(a, horiz = T, las = 1, cex.names = 0.8, xlab = "Documents", main = "Top authors")
-```
-
-## Topics
-
-```{r topics1, topics, echo=FALSE, message=FALSE, warning=FALSE}
-# List all topics
-spl <- strsplit(na.omit(as.character(df$topic)), ";")
-
-# Topics per document
-# hist(sapply(spl, length))
-
-# Documents per topic
-tab <- sort(table(unlist(spl)))
-tab <- tab[!names(tab) == "NA"]
-tab <- rev(sort(tab)) 
-```
-
-```{r topics2, echo=FALSE, message=FALSE, warning=FALSE}
-# Write to file
-f <- "output.tables/subjecttopics.tab"
-write.table(cbind(Topic = sort(names(tab))), file = f, sep = "\t", quote = F, row.names = F)
-ntop <- 50
-```
-
-[Complete subject topic counts](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/subjecttopics.tab)
-
-Top-`r ntop` topics and number of documents for each.
-In total, there are `r length(unique(df$topic))` unique topics and `r sum(!is.na(df$topic))` documents assigned to one or more topics (`r round(100*mean(!is.na(df$topic)))`).
-
-```{r topics3, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=10}
-par(mar = c(5, 10, 3, 1)); barplot(rev(rev(sort(table(df$topic)))[1:ntop]), horiz = T, las = 1, cex.names = 0.8, xlab = "Documents", main = "Most common topics")
-```
 
@@
 [Complete geoplace listing](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/geoplaces.csv)
-
-## Geocoordinates for publication places
-
-Altogether ```r 100 * mean(is.na(df.preprocessed$latitude) | is.na(df.preprocessed$longitude))``` places have missing geocoordinates:
-
-[Places with missing geocoordinates](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/missing_geocoordinates.csv)

### 2016-04-02 inst/extras/misc.Rmd
ok

## Topics

```{r topics1, topics, echo=FALSE, message=FALSE, warning=FALSE}
# List all topics
spl <- strsplit(na.omit(as.character(df$topic)), ";")

# Topics per document
# hist(sapply(spl, length))

# Documents per topic
tab <- sort(table(unlist(spl)))
tab <- tab[!names(tab) == "NA"]
tab <- rev(sort(tab)) 
```

```{r topics2, echo=FALSE, message=FALSE, warning=FALSE}
# Write to file
f <- "output.tables/subjecttopics.tab"
write.table(cbind(Topic = sort(names(tab))), file = f, sep = "\t", quote = F, row.names = F)
ntop <- 50
```

[Complete subject topic counts](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/subjecttopics.tab)

Top-`r ntop` topics and number of documents for each. In total, there are `r length(unique(df$topic))` unique topics and `r sum(!is.na(df$topic))` documents assigned to one or more topics (`r round(100*mean(!is.na(df$topic)))`).

```{r topics3, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=10}
par(mar = c(5, 10, 3, 1)); barplot(rev(rev(sort(table(df$topic)))[1:ntop]), horiz = T, las = 1, cex.names = 0.8, xlab = "Documents", main = "Most common topics")
```

Conversions from the original to preprocessed fields:

```{r summary-conversions, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=10, fig.height=15}
a <- harmonize_field_names()
b <- sapply(conversions, function (x) {paste(x, collapse = ";")})
coms <- intersect(as.character(a$name), names(b))

field.conversions <- cbind(a[match(coms, a$name), ], preprocessed = unname(b[coms]))
names(field.conversions) <- c("marc_clearname", "marc_field", "preprocessed_fields")
field.conversions <- field.conversions[, c(2, 1, 3)]
kable(field.conversions)
```

Percentage of non-NA entries among all documents in the preprocessed data (note that in some cases a significant fraction of this information is missing already in the raw data)

```{r missingb, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=10, fig.height=15}
# Need to use this trick to have NAs for all data types
missing <- 100*apply(df, 2, function (x) {mean(is.na(gsub("^NA$", NA, as.character(x))))})
df2 <- data.frame(list(missing = missing, field = names(missing)))
df2$field <- factor(df2$field, levels = df2$field[rev(order(df2$missing))])

theme_set(theme_bw(15))
p <- ggplot(df2, aes(x = field, y = 100 - missing))
p <- p + geom_bar(stat = "identity")
p <- p + coord_flip()
p <- p + ylab("")
p <- p + xlab("")
p <- p + ggtitle("Documents with data (%)")
print(p)
```

## Publication time

[Successfully converted publication times](output.tables/publication-time-accepted.csv)

[Discarded publication times](output.tables/publication-time-discarded.csv)

```{r publication_time, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=10}
#hist(df$publication_year, main = "Document frequencies over time")
dfs <- df %>% group_by(publication_year) %>% tally()
ggplot(dfs, aes(x = publication_year, y = n)) + geom_point() + ggtitle("Document frequencies over time") + ylab("Title count") + xlab("Publication year")
```

## Publication places

Top-`r ntop` publication places are shown together with the number of documents. This info is available for `r sum(!is.na(df$publication_place))` documents (`r round(100*mean(!is.na(df$publication_place)))`%). There are `r length(unique(str_trim(unlist(strsplit(as.character(df$publication_place), ";")))))` unique publication places.

```{r publication_place, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=10}
tab <- rev(sort(table(str_trim(unlist(strsplit(as.character(df$publication_place), ";"))))))
ntop <- 50
par(mar = c(5, 10, 3, 1)); barplot(log10(rev(tab[1:ntop])), horiz = T, las = 1, cex.names = 0.8, xlab = "Documents (log10)", main = "Most common publication places")
```

[Successfully converted publication places](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/publication_place_accepted.csv)

[Discarded publication places](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/publication_place_discarded.csv)

[Publication places missing country information](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/publication_place_missingcountry.csv)

## Dimensions

[Successfully converted dimension info](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/accepted_dimensions.csv)

[Discarded dimension info](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/missing_dimensions.csv)

[Discarded gatherings info](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/missing_gatherings.csv)

## Authors

[Accepted unique authors](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/author_accepted.csv)

[Discarded authors](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/author_discarded.csv)

[Discarded author first names](output.tables/author_name_discarded_first.csv)

[Discarded author last names](output.tables/author_name_discarded_last.csv)

[Authors missing life years](output.tables/authors_missing_lifeyears.csv)

Top-`r ntop` uniquely identified authors and number of documents for each (duplicate docs not checked yet).

```{r authors, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=10}
a <- rev(rev(sort(table(df$author)))[2:ntop+1])
par(mar = c(5, 10, 3, 1)); barplot(a, horiz = T, las = 1, cex.names = 0.8, xlab = "Documents", main = "Top authors")
```

### 2016-04-02 inst/examples/summary.Rmd
ok

@@
 # Fennica summary
-
-## Annotated documents
-
-Fraction of documents with entries for each annotation field. For a full list of summaries for field contents, see [here](https://github.com/rOpenGov/fennica/tree/master/inst/examples/output.tables).
 
@@
 conversions <- readRDS("conversions.Rds")
+```
+
+Fields of special interest. Real success percentage (proportion of successful conversions compared to non-NA entries in the original data):
+
+```{r missing2, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=10, fig.height=15}
+dfs <- df %>% select(author, publication_place, country, publication_year, publication_year_from, publication_year_till, corporate, area, pagecount, gatherings, width, height, paper.consumption.km2, publisher, self_published)
+success <- as.data.frame(t(apply(dfs, 2, function (x) {sum(!is.na(gsub("^NA$", NA, as.character(x))))})))
+original.nonNA <- as.data.frame(t(apply(select(df.orig, publication_place, publication_time, corporate, physical_extent, physical_dimension, publisher, author_name), 2, function (x) {sum(!is.na(gsub("^NA$", NA, as.character(x))))})))
+
+# Compare the number of non-NA entries in preprocessed data to number
+# of non-NA entries in the original data:
+real.success <- c()
+real.success[["publication_place"]] <- success$publication_place/original.nonNA$publication_place
+real.success[["country"]] <- success$country/original.nonNA$publication_place
+real.success[["publication_year"]] <- success$publication_year/original.nonNA$publication_time
+real.success[["publication_year_from"]] <- success$publication_year_from/original.nonNA$publication_time
+real.success[["publication_year_till"]] <- success$publication_year_till/original.nonNA$publication_time
+real.success[["corporate"]] <- success$corporate/original.nonNA$corporate
+real.success[["publisher"]] <- success$publisher/original.nonNA$publisher
+real.success[["self_published"]] <- success$self_published/original.nonNA$publisher
+real.success[["pagecount"]] <- success$pagecount/original.nonNA$physical_extent
+real.success[["area"]] <- success$area/original.nonNA$physical_dimension
+real.success[["gatherings"]] <- success$gatherings/original.nonNA$physical_dimension
+real.success[["author"]] <- success$author/original.nonNA$author
+real.success[["paper"]] <- success$paper.consumption.km2/sum(rowMeans(!is.na(df.orig[, c("physical_extent", "physical_dimension")])) == 1)
+par(mar = c(3, 8, 2, 1)); barplot(100*sort(real.success), horiz = T, main = "Real success rate (selected fields)", las = 1, xlim = c(0, 100), xlab = "Success rate (%)")
 ```

### 2016-05-05 R/get_gender_fi.R
vignete added

@@ -13,11 +13,11 @@
 #' first names for living Finnish citizens that live in Finland and
 #' abroad. Only names with frequency n>10 are included.
 #'  Source: avoindata.fi service and Vaestorekisterikeskus (VRK).
-#'  URL: https://www.avoindata.fi/data/fi/dataset/none
+#'  \url{https://www.avoindata.fi/data/fi/dataset/none}
 #'  Version: 3/2016
 #'  Data license CC-BY 4.0
-#' The data was downloaded with this function as sorvi::get_gender_table_fi()
-#' and integrated in the sorvi package. The frequencies of male/female names
+#' The data was downloaded with this function as fennica::get_gender_fi()
+#' and integrated in the fennica package. The frequencies of male/female names
 #' are added after the download as some names occur for both genders.
 #' @references See cite("fennica")
 #' @keywords data

### 2016-06-13 inst/examples/20151209-HelsinkiDH.Rmd
ok

@@
 p <- ggplot(dfs, aes(x = publication_decade, y = paper, fill = myplace, order = -as.numeric(myplace))) +
-     geom_bar(position = "stack", stat = "identity") +
+     geom_bar(position = "stack", stat = "identity", color = "black") +
      ggtitle("Paper consumption") +
-     scale_fill_manual(values = c("blue", "black", "darkgreen")) +
+     #scale_fill_manual(values = c("blue", "black", "darkgreen")) +
+     scale_fill_grey() +
+     guides(fill = guide_legend(reverse = TRUE)) + 
      xlab("Publication decade") + ylab("Paper (km2)")
@@
 p <- ggplot(dfs, aes(x = publication_decade, y = titles, fill = myplace, order = -as.numeric(myplace))) +
-     geom_bar(position = "stack", stat = "identity") +
+     geom_bar(position = "stack", stat = "identity", color = "black") +
      ggtitle("Title count") +
-     scale_fill_manual(values = c("blue", "black", "darkgreen")) +
+     # scale_fill_manual(values = c("blue", "black", "darkgreen")) +
+     scale_fill_grey() +
+     guides(fill = guide_legend(reverse = TRUE)) +      
      xlab("Publication decade") + ylab("Title count (n)")

### 2016-06-14 inst/examples/20160303-Krakow.Rmd

@@
 
-#jpeg("20160303-paper.jpeg", quality = 100, height = 300, width = 480)
 pdf("20160303-paper.pdf", width = 12, height = 9)
+print(p)
+dev.off()
+
+jpeg("20160303-paper.jpg", quality = 100, height = 480, width = 600)
 print(p)
@@
      scale_fill_grey() +
-     guides(fill = guide_legend(reverse = TRUE)) +      
+     guides(fill = guide_legend(reverse = TRUE, title = "")) +      
      xlab("Publication decade") + ylab("Title count (n)")
@@
 
+jpeg("20160303-titles.jpg", quality = 100, height = 480, width = 600)
+print(p)
+dev.off()
 ```

### 2016-06-21 inst/examples/manuscript-krakow.Rmd
started manu

--- 2016-03-02 inst/examples/20160303-Krakow.Rmd
@@
 title: "Digital History in Finland, 1488-1828"
-author: "Leo Lahti"
-date: "March 3, 2016"
+author: "Mikko Tolonen, Jani Marjanen, Hege Roivainen, Leo Lahti"
+date: "June 22, 2016"
 output: markdown_document
@@
 
-```{r 20160303-init, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE}
+```{r 201606krakow-init, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE}
 library(stringr)
@@
 
+# Figure path
+opts_chunk$set(fig.path = "figure_201606_Krakow/")
+
+# Define time span
+min.year = 1470
+max.year = 1828
+
 # Read data
-dfo <- readRDS("df.Rds")
+fen <- readRDS("df.Rds")
+kun <- readRDS("../../../kungliga/antagomir/df.Rds")
 
-# Add publication decade
-# TODO add already in the original preprocessed data matrix
-dfo$publication_decade <- 10*floor(dfo$publication_year/10)
-
-# Remove very early and late years
-dfo <- dfo %>% filter(publication_year > 1400 & publication_year < 1911)
+fen <- fen %>% filter(publication_year >= min.year & publication_year <= max.year)
+kun <- kun %>% filter(publication_year >= min.year & publication_year <= max.year)
 ```
 
-```{r 20160303-turkuvsother, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=4, fig.width=8}
-# Let us focus on years 1400-1828
-df <- dfo %>% filter(publication_year > 1400 & publication_year < 1829) %>%
+```{r 201606krakow-turkuvsother, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=4, fig.width=8}
+df <- fen %>% 
       filter(!is.na(country)) %>%
@@
 
-#jpeg("20160303-paper.jpeg", quality = 100, height = 300, width = 480)
-pdf("20160303-paper.pdf", width = 12, height = 9)
-print(p)
-dev.off()
-
 p <- ggplot(dfs, aes(x = publication_decade, y = titles, fill = myplace, order = -as.numeric(myplace))) +
@@
      scale_fill_grey() +
-     guides(fill = guide_legend(reverse = TRUE)) +      
+     guides(fill = guide_legend(reverse = TRUE, title = "")) +      
      xlab("Publication decade") + ylab("Title count (n)")
 print(p)
-
-pdf("20160303-titles.pdf", width = 12, height = 9)
-print(p)
-dev.off()
-
 ```

### 2016-06-21 inst/examples/analysis.R

@@ -10,6 +10,7 @@ knitr::knit("Vaasa.Rmd", encoding="UTF-8")
 knitr::knit("suvut.Rmd", encoding="UTF-8")
 knitr::knit("20151209-HelsinkiDH.Rmd", encoding="UTF-8")
 knitr::knit("20160303-Krakow.Rmd", encoding="UTF-8")
+knitr::knit("manuscript-krakow.Rmd", encoding="UTF-8")
 
 # Push changes to github
 # https://github.com/ropensci/git2r

### 2016-06-21 inst/examples/manuscript-krakow.Rmd
Rmd update

@@
 ---
+
+Digital History in Finland, 1488-1828
+==============
+
+## Introduction
+
+Matti Klinge HYn historia; Jari Niemelä, Vain hyödynkö tähden
+(väitöskirja) käsittelee Turun yliopiston asemaa.
+
+## Results
+
+### General trends
+
+Relevant summaries can be moved here and polished. Which figures at least ?
+
+General trends (top authors etc):
+ * [Fennica overview](https://github.com/rOpenGov/fennica/blob/master/inst/examples/overview.md)
+ * [Kungliga overview](https://github.com/rOpenGov/kungliga/blob/master/antagomir/overview.md)
+
+[ESTC-analyses](https://github.com/rOpenGov/estc)
+([LIBER](https://github.com/rOpenGov/estc/blob/master/inst/examples/20151023-LIBER.md)
+in particular); toisto Fennica/Kungliga datoilla ? LL: Voidaan tehda
+mut kandee miettia ehka spesifimmin et mitka analyysit sielta
+kiinnostaa. Muuten menee aikaa hukkaan jos pitaa fiksata juttuja joita
+ei sitten kaytetakaan.
+
+### Fennica vs. Kungliga
+
+Alustavia vertailuja Kungligasta suhteessa Fennicaan.
+
+ * Fennica pois lukien Suomi ?
+ * Kungliga pois lukien Ruotsi ?
+ * Julkaisumäärien tilastointeja yleisesti ja paikkakunnittain
+
+Turku vertailut Upsalaan, Lundiin, Tukholmaan yms. Turussa
+julkaiseminen alkaa vasta 1640-luvulla, mutta ollaan kiinnostuttu
+ruotsalaisesta julkaisemisesta ennen sitä. Esim miten Turun yliopiston
+perustaminen vaikuttaa ruotsalaiseen julkaisukenttään 1600-luvun
+aikana.
+
+**Valtiopäivät**
+
+Miten Valtiopäivät vaikuttaa julkaisemiseen? Näkyykö Vapauden ajan
+valtiopäivät tässä 1719 eteenpäin? Voidaanko löytää julkaisupiikkejä
+sen mukaan milloin on valtiopäivät? Oletus on, että pitäisi näkyä
+selvästi. Myös, tuleeko uusia kustantajia kenttään?
+
+Erityisesti:
+
+Riksdag Stockholm 20 januari 1719 1 juni 1719
+
+Riksdag Stockholm 14 maj 1734 14 december 1734
+
+Riksdag Stockholm 21 februari 1765 21 oktober 1766
+
+Riksdag Norrköping & Stockholm 22 april 1769 5 februari 1770
+
+Riksdag Stockholm 19 juni 1771 12 september 1772
+
+Riksdag Gävle 26 januari 1792 24 februari 1792
+
+--> tapahtuuko Gävlessä selvää nousua julkaisemisessa.
+
+### Book as media: development over time
+
+Miten paperinkulutus suhtautuu dokumenttien määrään? Löydetäänkö
+ajankohtia jolloin on poikkeuksellista kasvua / laskua
+tms. Esim. top-10 julkaisupaikat.
+
+Kirjan kehitys mediana (paperinkulutus / dokumentti, miten yli 50
+sivuiset dokumentit yleistyvät ajassa / voidaanko tässä nähdä jotain
+paikallisia eroja?)
+
+Kirjakokojen kehityksiä pitää analysoida myöhemmin
+tarkkaan. mielenkiintoista Kungligan osalta erityisesti että foliot
+(1to ja 2to) puuttuvat melkein kokonaan joka on eri kuvio kuin ESTC,
+lisäksi sitten 4to ja 8vo voimakas nousu 1700-luvulla on
+mielenkiintoista.
+
+### Publisher analysis (HR)
+
+toiveissa että pystyttäisiin puhumaan julkaisijatoiminnan kehityksestä
+ikään kuin luonnollisena kehityksenä - eli yhteys luonnonilmiöiden
+kehitykseen säilyisi.
+
+Tärkein tehtävä tutkia pystytäänkö julkaisemiseen liittyvästä
+Fennica-datasta erottelemaan selkeitä trendejä suomalaisesta
+tiedontuotannosta 1640-1828, pääfokus julkaisijat.
+
+Miten uusia julkaisijoita tulee julkaisijakenttään Suomessa ja
+katoaa. Pääpaino erityisesti sillä kun julkaisijakartalle tulee uusia
+toimijoita! Toimijoita voisi myös yrittää luokitella suhteellisesti
+(“iso”, “keskikokoinen”, “pieni”) liittyen vuosittaiseen
+julkaisuvoluumiin jota mitataan niin julkaisujen määrän kuin myös
+paperinkulutusvoluumin suhteen. Vertailua suurimpien julkaisijoiden
+kesken.
+
+Analyysia voisi tästä tehdä sitten näiden luokkien kehityksen
+mukaan. “Siinä missä Londicer 1700-luvun Vaasassa näyttää aina
+julkaisseen asetukset jonkinlaisena kokoomapainoksena, mutta
+Frenckellin kirjapainosta ne tuli yksitellen. Siten Frenckellin
+julkaisemien niteiden määrä saattaa näyttää suurelta verrattuna
+Londiceriin, mutta itse asiassa sisältömäärä on sama”. → Tämä
+hypoteesi voidaan todentaa/tarkistaa/korjata kun mukana on
+paperinkulutus!
+
+Julkaisijoiden ilmentyminen kartalle paperinkulutusvoluumi huomioiden:
+julkaisutoiminnan leviäminen ja kasvu ajassa eri
+paikkakunnilla. Paperinkulutus voi osoittautua hyväksi työvälineeksi erityisesti kun
+tiedetään, että toiset isot julkaisijat julkaisivat esim. jotain
+asetuskokoelmia yksittäin ja toiset taas ryppäinä. Eli julkaisijoiden
+sisällä erottelua eri tyyppisten julkaisujen suhteen pitää tehdä.
+
+Lisäksi kiinnostaa mitä voidaan sanoa suomalaisesta kirjatuotannosta
+ylipäänsä sekä löydetäänkö sieltä mitään mielenkiintoisia
+kehityskulkuja ylipäänsä vai pelkästään toteamus, että suomalainen
+tiedontuotanto oli hyvin vähäistä tarkastellulla ajanjaksolla.
+
+Julkaisijoista tehtävä verkostoanalyysi on sitten toinen keskeinen
+tavoite. Löydetään keskeisimmät “nodet” siihen miten julkaisijakenttä
+muuttuu ajassa. Julkaisijoita voisi myös yrittää luokitella eniten
+käytettyjen asiasanojen mukaan. Näiden perusteella voidaan varmaankin
+erotella yliopistojulkaiseminen, asiakirja/asetusjulkaiseminen ja
+kirjajulkaiseminen. Tämän jälkeen auktorit, valtioasiakirjat,
+yliopistodokumentit, kirjat ja muut julkaisut kategoroina joiden
+ympärille verkostoanalyysi voisi syntyä (valtionasiakirjojen ja
+yliopisto-aineiston luokittelu voisi yhdistää myös asiasanojen ja
+otsikoiden analyysia).
+
+Turku vs. muu Suomi (sillä kytköksellä että kun Kungliga aineisto
+tulee mukaan analyysiin, niin Turku osana ruotsalaista
+yliopistojärjestelmää (ml. Tarto) muuttuu tärkeäksi). Eli Turun
+erityistapaus analysoidaan tarkkaan, kuinka paljon yliopistoon
+liittyvää julkaisutoimintaa, kuinka paljon julkaisijoita, miten
+julkaisijoiden verkosto muodostuu Turussa; miten eri julkaisijoita
+Turussa voitaisiin luokitella (julkaiseeko joku paperinkulutukseltaan
+vain pieniä dokumentteja, julkaiseeko joku painotalo huomattavasti
+enemmän kuin toiset), tarkoituksena yleisten historiallisten trendien
+löytäminen.
+
+### University analysis (HR)
+
+Tekee yliopistopuolta Fennica-Kungliga. Samalla voisi tehdä Fennicaa
+yleisesti. Eli keskittyä julkaisijoihin ja uusien julkaisijoiden
+analyysiin.
+
+- yliopistojulkaisuista mahd. pian yleiset tilastolliset näkymät ja
+  voidaan sitten arvioida onko joku mahdollisesti pahastikin vielä
+  pielessä esim. väitöskirjoiksi Kungligan osalta luokiteltavissa
+  aineistoissa.
+
+Subject topics: pientä analyysia. Ainakin yliopisto-väitöskirjoihin liittyen.
+
+keskittyy erityisesti kaikkiin väitöskirja-kategorian alla liikkuviin
+yliopistotuotoksiin. Tätä kautta päästään hyvin kiinni Turku, Upsala,
+Lund, Tarto yms. vertailuihin. Siitä sitten kuljetaan kohti Turun
+suhdetta muuhun Suomeen ja katso kääntyy erityisesti julkaisijoihin
+(samaten toki myös noiden yliopistokaupunkien osalla, jossa myös
+tehdään sitten vertailua akateeminen vs. hallinnollinen vs. muu
+julkaisutoiminta).
+
+analyysi mitä julkaisukentällä tapahtuu eri paikoissa kun uusia
+julkaisijoita tulee kartalle (meneekö esim. jossain toisessa
+yliopistossa tuotanto suhteessa alas kun matkan varrella tulee uusia
+yliopistoja vai ei) jne.
+
+Yleinen tilasto "väitöskirjaksi" merkityistä teoksista (aikajana,
+julkaisupaikka) olisi hyvä Kungligan osalta. Tämä toimii lähtökohtana
+että nähdään sisällöstä jotain: milloin niitä väitöskirja-luokiteltuja
+teoksia Kungligassa on merkitty julkaistuiksi sekä missä. Tämän
+vertaaminen Fennican pohjalta samaan eli "väitöskirjaksi" täggättyihin
+on tärkeää.
+
+Yliopistojen ilmestyminen ruotsinvaltakunnassahan on:
+
+Uppsala: 1477
+
+Tartu / Dorpat / Tarto (eikös paikkakunnittain synonyymit toimi jo?): 1633
+
+Turku: 1640
+
+Lund: 1666
+
+Greifwald: 1456 (Ruotsin systeemissä 1600-1815)
+
+Greifswald mukaan yliopistoanalyysiin. osana Ruotsin valtakuntaa.
+
+Lisäksi kieli, milloin alkaa erityisesti tulemaan ruotsinkielellä
+väitöksiä eri paikoissa on mielenkiintoinen kysymys. tuleeko jostain
+yliopistosta erityisesti ruotsinkielistä materiaalia 1700-luvulla.
+https://github.com/rOpenGov/fennica/blob/master/inst/examples/language.md
+Näissä pitää erityisesti analysoida niitä väitöskirjoja sekä niissä
+tapahtuvia muutoksia.
+
+- Turun akateemisen julkaisemisen vertautuminen muihin ruotsalaisen
+  yliopistojärjestelmän kaupunkeihin. Lukumäärävertailut aikajanalla
+  ja ne akateemisten julkaisujen blokkaaminenhan ei pitäisi olla
+  kovinkaan hankalaa. Tämä saattaisi hyvin riittää siitä Kungligan
+  käytöstä. Samalla vertailukohtia CERListä tai sitten ehkä ESTCstä
+  pitää ottaa Fennicalle että pystytään suhteuttamaan mistä puhutaan.
+
+Painovapaus, 1766, räjähtääkö / kasvaako julkaiseminen merkittävästi
+ja miten tämä näkyy Tukholma vs. muu valtakunta (ml. Turku)?
+Painovapaus on 1766-1772, miten tämä näkyy Kungligassa ja Fennicassa?
+
+### Other points
+
+Lets think these if there is time.
+
+[Topic](https://github.com/rOpenGov/kungliga/blob/master/antagomir/topic.md)
+saadaanko mitään irti (1470-1830 tai 1640-1830).
+
+Further todo points. Let us move in this manuscript only those points
+that there is time to do.
+
+ * [Fennica TODO](https://github.com/rOpenGov/fennica/blob/master/inst/examples/TODO.md)
+ * [Kungliga TODO](https://github.com/rOpenGov/kungliga/blob/master/antagomir/TODO.md)
 
@@
 ```
+
+## Conclusions
+
+## Materials and Methods
+
+ * Library catalogues (Fennica & Kungliga)
+ * Material also from the funding application
+ * Open data analytical ecosystem
+ * Github links
+ * Explanation
+
+### Acknowledgements
+
+Supported by Academy of Finland (grant 293316).
+
+## References

### 2016-06-21 inst/examples/manuscript-krakow.Rmd
Rmd update

@@
 
-Digital History in Finland, 1488-1828
+Printing in a Periphery: a Quantitative Study of Finnish Knowledge Production, 1640-1828
 ==============
@@
 (väitöskirja) käsittelee Turun yliopiston asemaa.
+
+Aatehistoria ja digitaalisten  aineistojen mahdollisuudet ([Tolonen & Lahti (2015)](http://www.ennenjanyt.net/2015/08/aatehistoria-ja-digitaalisten-aineistojen-mahdollisuudet/))
+
+We have prepared open data analytical ecosystem for in-depth analysis of such data collections ([Lahti, Ilomaki, Tolonen (2015)](http://doi.org/10.18352/lq.10112)).
 
@@
 
- * Library catalogues (Fennica & Kungliga)
- * Material also from the funding application
- * Open data analytical ecosystem
- * Github links
- * Explanation
+Library catalogues contain rich metadata on...
+
+Here we analyse Fennica & Kungliga..
+
+Further draft text in the funding application..?
+
+We have prepared open data analytical ecosystem for in-depth analysis of such data collections ([Lahti, Ilomaki, Tolonen (2015)](http://doi.org/10.18352/lq.10112)).
+
+In summary, the data analytical ecosystem does ..
+
+Reading, parsing, cleaning up, enriching, summarizing, analysis, visualization, figures and tables..
+
+Full source code to reproduce these analyses are available via Github ([Fennica](https://github.com/rOpenGov/fennica/); [Kungliga](https://github.com/rOpenGov/kungliga/)).
 

### 2016-06-21 inst/examples/manuscript-krakow.Rmd
ok

@@
 author: "Mikko Tolonen, Jani Marjanen, Hege Roivainen, Leo Lahti"
-date: "June 22, 2016"
-output: markdown_document
+date: "`r Sys.Date()`"
+bibliography: 
+- bibliography.bib
+- references.bib
+output: 
+  md_document:
+    variant: markdown_github
 ---
+<!--
+  %\VignetteEngine{knitr::rmarkdown}
+  %\VignetteIndexEntry{microbiome tutorial}
+  %\usepackage[utf8]{inputenc}
+-->
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+# Handle citations
+require(knitcitations)
+cleanbib()
+#options("citation_format" = "pandoc")
+bib <- read.bibtex("bibliography.bib")
+#opts_chunk$set(fig.width=4, fig.height=3, par=TRUE, out.width='2in', fig.pos='H')
+#knitr::opts_chunk$set(fig.path = "figure_201606_Krakow/", dev="CairoPNG")
+knitr::opts_chunk$set(fig.path = "figure_201606_Krakow/")
+```
+
+```{r 201606krakow-init, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE}
+library(stringr)
+library(dplyr)
+library(ggplot2)
+library(bibliographica)
+library(fennica)
+library(sorvi)
+
+# Nice theme
+theme_set(theme_bw(26))
+
+# Define time span
+min.year = 1470
+max.year = 1828
+
+# Read data
+fen <- readRDS("df.Rds")
+kun <- readRDS("../../../kungliga/antagomir/df.Rds")
+
+fen <- fen %>% filter(publication_year >= min.year & publication_year <= max.year)
+kun <- kun %>% filter(publication_year >= min.year & publication_year <= max.year)
+```
 
@@
 
-Aatehistoria ja digitaalisten  aineistojen mahdollisuudet ([Tolonen & Lahti (2015)](http://www.ennenjanyt.net/2015/08/aatehistoria-ja-digitaalisten-aineistojen-mahdollisuudet/))
+Aatehistoria ja digitaalisten  aineistojen mahdollisuudet ([Tolonen & Lahti (2015)](http://www.ennenjanyt.net/2015/08/aatehistoria-ja-digitaalisten-aineistojen-mahdollisuudet/)).
+Citing with URL `r citep("http://www.ennenjanyt.net/2015/08/aatehistoria-ja-digitaalisten-aineistojen-mahdollisuudet")`
 
 We have prepared open data analytical ecosystem for in-depth analysis of such data collections ([Lahti, Ilomaki, Tolonen (2015)](http://doi.org/10.18352/lq.10112)).
+Citing with DOI: `r citep("10.18352/lq.10112")`
 
@@
 
-```{r 201606krakow-init, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE}
-library(stringr)
-library(dplyr)
-library(ggplot2)
-library(bibliographica)
-library(fennica)
-library(sorvi)
-
-# Nice theme
-theme_set(theme_bw(26))
-
-# Figure path
-opts_chunk$set(fig.path = "figure_201606_Krakow/")
-
-# Define time span
-min.year = 1470
-max.year = 1828
-
-# Read data
-fen <- readRDS("df.Rds")
-kun <- readRDS("../../../kungliga/antagomir/df.Rds")
-
-fen <- fen %>% filter(publication_year >= min.year & publication_year <= max.year)
-kun <- kun %>% filter(publication_year >= min.year & publication_year <= max.year)
-```
-
 ```{r 201606krakow-turkuvsother, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=4, fig.width=8}
@@
 ## References
+
+### References
+
+```{r, echo=FALSE, message=FALSE}
+#Embed citations from bib files with `r citep(bib[["lahti14natcomm"]])`. Or with @lahti14natcomm
+#You can embed citations, for example: `r citep(bib[["lahti14natcomm"]])`
+#You can embed citations, for example2: @lahti14natcomm
+#Cite with DOI: `r citep("10.1890/11-0011.1")`
+#Cite URL `r citep("http://knowledgeblog.org/greycite")`
+#For automated markdown citations, check [this](http://rmarkdown.rstudio.com/authoring_bibliographies_and_citations.html), [this](https://github.com/cboettig/knitcitations), and [this](http://www.carlboettiger.info/2012/03/24/citations-in-markdown-using-knitr.html).
+#write.bibtex(file="references.bib")
+```
+
+```{r, echo=FALSE, message=FALSE, results='asis'}
+bibliography()
+```
+
+### Dependencies
+
+The package utilizes tools from a number of other R extensions,
+including dplyr `r citep(citation("dplyr"))`, ggplot2 `r citep(citation("ggplot2"))`, stats `r citep(citation("stats"))`, tidyr `r citep(citation("tidyr"))`.

### 2016-06-21 inst/examples/manuscript-krakow.Rmd
citations

@@
 #options("citation_format" = "pandoc")
+cite_options(hyperlink = TRUE, max.names = 3)
 bib <- read.bibtex("bibliography.bib")
@@
 Citing with URL `r citep("http://www.ennenjanyt.net/2015/08/aatehistoria-ja-digitaalisten-aineistojen-mahdollisuudet")`
+
+Embed citations from bib files with `r citep(bib[["lahti14natcomm"]])`.
 
@@
 ```{r, echo=FALSE, message=FALSE, results='asis'}
-bibliography()
+bibliography(sorting = 'ynt')
 ```

### 2016-06-21 inst/examples/manuscript-krakow.Rmd
ok

@@
 
-Aatehistoria ja digitaalisten  aineistojen mahdollisuudet ([Tolonen & Lahti (2015)](http://www.ennenjanyt.net/2015/08/aatehistoria-ja-digitaalisten-aineistojen-mahdollisuudet/)).
-Citing with URL `r citep("http://www.ennenjanyt.net/2015/08/aatehistoria-ja-digitaalisten-aineistojen-mahdollisuudet")`
+Aatehistoria ja digitaalisten aineistojen mahdollisuudet ([Tolonen &
+Lahti (2015) - add to
+bib](http://www.ennenjanyt.net/2015/08/aatehistoria-ja-digitaalisten-aineistojen-mahdollisuudet/)).
 
@@
 
-We have prepared open data analytical ecosystem for in-depth analysis of such data collections ([Lahti, Ilomaki, Tolonen (2015)](http://doi.org/10.18352/lq.10112)).
-Citing with DOI: `r citep("10.18352/lq.10112")`
+We have prepared open data analytical ecosystem for in-depth analysis
+of such data collections `r citep("10.18352/lq.10112")`.
 
@@
 
+The package utilizes tools from a number of other R extensions,
+including dplyr `r citep(citation("dplyr"))`, ggplot2 `r citep(citation("ggplot2"))`, stats `r citep(citation("stats"))`, tidyr `r citep(citation("tidyr"))`.
+
 ### Acknowledgements
@@
 ```
-
-### Dependencies
-
-The package utilizes tools from a number of other R extensions,
-including dplyr `r citep(citation("dplyr"))`, ggplot2 `r citep(citation("ggplot2"))`, stats `r citep(citation("stats"))`, tidyr `r citep(citation("tidyr"))`.

### 2016-06-22 inst/examples/manuscript-krakow.Rmd
Rmd update

@@
 
-## Introduction
+## Introduction (MT + JM voi jo kasata tähän hyvää läppää + viitteitä)
 
@@
 
-Embed citations from bib files with `r citep(bib[["lahti14natcomm"]])`.
-
 We have prepared open data analytical ecosystem for in-depth analysis
 of such data collections `r citep("10.18352/lq.10112")`.
+
+You can also add citations by adding new references to the [bib
+file](bibliography.bib) and then citing in this text with
+`r citep(bib[["lahti14natcomm"]])`. These will then be automatically
+numbered and collected in references section. Alternatively, you can cite with the DOI (the citation info will then be collected automatically): `r citep("10.18352/lq.10112")`.
 

### 2016-06-22 inst/examples/manuscript-krakow.Rmd
Rmd update

@@
 file](bibliography.bib) and then citing in this text with
-`r citep(bib[["lahti14natcomm"]])`. These will then be automatically
+`r citep(bib[["Lahti15LIBER"]])`. These will then be automatically
 numbered and collected in references section. Alternatively, you can cite with the DOI (the citation info will then be collected automatically): `r citep("10.18352/lq.10112")`.

### 2016-06-22 inst/examples/manuscript-krakow.Rmd
Rmd update

--- 2016-06-21 inst/examples/manuscript-krakow.Rmd
@@
 
-Aatehistoria ja digitaalisten aineistojen mahdollisuudet ([Tolonen &
-Lahti (2015) - add to
-bib](http://www.ennenjanyt.net/2015/08/aatehistoria-ja-digitaalisten-aineistojen-mahdollisuudet/)).
-
-Embed citations from bib files with `r citep(bib[["lahti14natcomm"]])`.
+Aatehistoria ja digitaalisten aineistojen mahdollisuudet `r citep(bib[["Tolonen15EnnenNyt"]])`
 
@@
 of such data collections `r citep("10.18352/lq.10112")`.
+
+You can cite with the DOI (the citation info will then be collected automatically): `r citep("10.18352/lq.10112")` or alternatively add new references to the [bib
+file](bibliography.bib) and then cite using the key with
+`r citep(bib[["Lahti15LIBER"]])`. Such citations will be automatically
+numbered and collected in references section.
 

### 2016-06-22 inst/examples/manuscript-krakow.Rmd
Rmd update

@@
 General trends (top authors etc):
+
   * [Fennica overview](https://github.com/rOpenGov/fennica/blob/master/inst/examples/overview.md)
@@
 
-Lisäksi kieli, milloin alkaa erityisesti tulemaan ruotsinkielellä
-väitöksiä eri paikoissa on mielenkiintoinen kysymys. tuleeko jostain
+Lisäksi kieli [Fennica](https://github.com/rOpenGov/fennica/blob/master/inst/examples/language.md) ja [Kungliga](https://github.com/rOpenGov/kungliga/blob/master/antagomir/language.md), milloin alkaa erityisesti tulemaan ruotsinkielellä väitöksiä eri paikoissa on mielenkiintoinen kysymys.
+tuleeko jostain
 yliopistosta erityisesti ruotsinkielistä materiaalia 1700-luvulla.
-https://github.com/rOpenGov/fennica/blob/master/inst/examples/language.md
 Näissä pitää erityisesti analysoida niitä väitöskirjoja sekä niissä
@@
 
-- Turun akateemisen julkaisemisen vertautuminen muihin ruotsalaisen
-  yliopistojärjestelmän kaupunkeihin. Lukumäärävertailut aikajanalla
-  ja ne akateemisten julkaisujen blokkaaminenhan ei pitäisi olla
-  kovinkaan hankalaa. Tämä saattaisi hyvin riittää siitä Kungligan
+Turun akateemisen julkaisemisen vertautuminen muihin ruotsalaisen
+yliopistojärjestelmän kaupunkeihin. Lukumäärävertailut aikajanalla ja
+ne akateemisten julkaisujen blokkaaminenhan ei pitäisi olla kovinkaan
+hankalaa. Tämä saattaisi hyvin riittää siitä Kungligan
 käytöstä. Samalla vertailukohtia CERListä tai sitten ehkä ESTCstä

### 2016-06-22 inst/examples/manuscript-krakow.Rmd
Update manuscript-krakow.Rmd

@@
 numbered and collected in references section.
+
+- Knowledge production has been approached largely through a national perspective, here we shift focus by combining materials from Sweden and Finland and by specifically looking at cities as sites for knowledge production.
+Cities are to this effect seen as partly supplementing, partly competing intellectual centres.
 

### 2016-06-22 inst/examples/LIBER.Rmd
ok

---
title: "LIBER Analyses with Fennica"
author: "Leo Lahti"
date: "23/06/2016"
output: markdown_document
---

## LIBER Analyses

```{r summaryinit, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE}
library(stringr)
library(bibliographica)
library(dplyr)
library(rmarkdown)
library(knitr)
library(ggplot2)
opts_chunk$set(cache=FALSE, fig.path = "figure_20151023_LIBER/")
library(ggthemes)

# Nice theme
theme_set(theme_bw(26))

# Define time span
min.year = 1470
max.year = 1828

# Read data
fen <- readRDS("df.Rds")
kun <- readRDS("../../../kungliga/antagomir/df.Rds")

# Select the subset to analyze
fen <- fen %>% filter(publication_year >= min.year & publication_year <= max.year)
kun <- kun %>% filter(publication_year >= min.year & publication_year <= max.year)

# Define the data to check
df = df.preprocessed = fen
```

This document repeats the ESTC analysis from [Lahti, Ilomaki, Tolonen (2015); Liber Quarterly 25(2), pp.87–116](http://doi.org/10.18352/lq.10112) for other data sets.

## Who wrote history ?

### The life spans of the top authors based on the title count

```{r LIBER-2, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=5, fig.width=7.5}
theme_set(theme_bw(20))
df = df.preprocessed
dfs = subset(df, author_name %in% names(top(df, "author_name", 20)))
dfa <- dfs[, c("author_name", "author", "author_birth", "author_death")]
dfa <- dfa[!duplicated(dfa), ]
dfa <- arrange(dfa, author_birth)
# Order authors by birth year
dfa$author_name <- factor(dfa$author_name, levels = unique(dfa$author_name))
dfa$index <- sample(factor(1:nrow(dfa)))
dfa$fill <- rep("black", nrow(dfa))

p <- ggplot(dfa)
p <- p + geom_segment(aes(y = author_name, yend = author_name, x = author_birth, xend = author_death, color = fill), size = 2) 
p <- p + theme(axis.text.y = element_text(size = 14))
p <- p + xlab("Author life span (year)") + ylab("")
p <- p + guides(color = FALSE)
p <- p + scale_color_manual(values = c("darkgray", "black"))
p <- p + ggtitle("Top author life span")
print(p)
```

### The most active known female authors based on the title count

The gender is inferred automatically from the first names

```{r LIBER-5, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=6, fig.width=10}
theme_set(theme_bw(20))
dfs <- df.preprocessed %>% filter(author_gender == "female")
p <- top_plot(dfs, "author", ntop = 20)
p <- p + scale_fill_manual(values = "black")
p <- p + guides(fill = "none")
p <- p + ylab("Title count")
p <- p + ggtitle("Top female authors")
p <- p + theme(axis.text.x = element_text(size = 16), axis.text.y = element_text(size = 16), axis.title.x = element_text(size = 25), axis.title.y = element_text(size = 22), title = element_text(size = 22))
print(p)	 
```

## Where was history published ?

### The top publication places ranked by the title count

```{r LIBER-topplace, echo=FALSE, message=FALSE, cache=FALSE, fig.height=6, fig.width=6}
theme_set(theme_bw(30))
dfs <- df.preprocessed
p <- top_plot(dfs, "publication_place", ntop = 20)
p <- p + scale_fill_manual(values = "black")
p <- p + guides(fill = "none")
p <- p + ylab("Title count (Log10 scale)")
p <- p + scale_y_log10()
p <- p + ggtitle("Top publication places")
print(p)	 
```

### Title count and overall paper consumption in the top publication locations

The current country of origin is indicated. Finland is highlighted.

```{r LIBER-8, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=6, fig.width=8}
df <- df.preprocessed
theme_set(theme_bw(20))
top <- names(rev(sort(table(df$publication_place))))[1:50]
dfs <- df %>% filter(publication_place %in% top) %>% group_by(publication_place) %>% summarize(titles = n(), paper = sum(paper.consumption.km2, na.rm = T))
dfs$country <- get_country(dfs$publication_place)
dfs$finland <- dfs$country == "Finland"
p <- ggplot(dfs, aes(x = titles, y = paper))
p <- p + geom_text(aes(label = publication_place, color = finland), size = 5)
p <- p + xlab("Title Count") + ylab("Paper consumption (km2)")
p <- p + scale_color_manual(values = c("darkgray", "black"))
p <- p + guides(color = "none")
p <- p + scale_x_log10() + scale_y_log10() 
p <- p + ggtitle("Title count versus paper (places)")
print(p)	 
```

### Title count and paper consumption in Finland and Sweden

```{r 20150611paris-places4, message=FALSE, fig.height=5, fig.width=10, echo=FALSE}
theme_set(theme_bw(20))
selected.countries = c("Finland", "Sweden")
df2 <- df.preprocessed %>%
    filter(!is.na(country)) %>%
    group_by(country) %>%
    summarize(paper = sum(paper.consumption.km2, na.rm = TRUE),
	      docs = n()) %>%
    arrange(desc(docs)) %>%
    filter(country %in% selected.countries)

p1 <- ggplot(df2, aes(x = country, y = docs)) + geom_bar(stat = "identity") + ggtitle("Title count") + theme(axis.text.x = element_text(angle = 45, hjust = 1)) + ylab("Documents") + xlab("")
p2 <- ggplot(df2, aes(x = country, y = paper)) + geom_bar(stat = "identity") + ggtitle("Paper consumption") + theme(axis.text.x = element_text(angle = 45, hjust = 1)) + ylab("Paper (km2)") + xlab("")
library(gridExtra)
grid.arrange(p1, p2, nrow = 1)
```

Estimated gatherings per country:

```{r LIBER-docsizecomp1, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
dfs <- df %>% select(gatherings, country) %>% group_by(gatherings, country) %>% tally() %>% filter(country %in% selected.countries)
p <- ggplot(dfs, aes(x = gatherings, y = country, size = n)) +
     geom_point()
print(p)
```

Estimated pagecounts per country:

```{r LIBER-docsizecomp2, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
dfs <- df %>% select(pagecount, country) %>% filter(country %in% selected.countries)
p <- ggplot(dfs, aes(x = pagecount)) +
     geom_histogram() + facet_grid(country ~ .) + scale_x_log10()
print(p)
```

Gatherings vs. pagecounts per country

```{r LIBER-docsizecomp3, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=10}
dfs <- df %>% select(pagecount, gatherings, country) %>% filter(country %in% selected.countries) %>% group_by(pagecount, gatherings, country) %>% tally()
p <- ggplot(dfs, aes(x = pagecount, y = gatherings, size = n)) +
     geom_point() + facet_grid(country ~ .) + scale_x_log10()
print(p)
```

## How does publishing change ?

### Average paper consumption per document

```{r LIBER-11, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=5, fig.width=9}
theme_set(theme_bw(25))
library(sorvi)
df = df.preprocessed
dfs <- df %>% group_by(publication_year) %>%
         summarize(paper.per.doc = mean(paper.consumption.km2, na.rm = T))
p <- ggplot(dfs, aes(y = paper.per.doc, x = publication_year)) +
       geom_line() + geom_point() +
       xlab("Publication Year") + ylab("Paper per document")
p <- p + ggtitle("Average paper consumption per document")
print(p)
```

### Paper consumption in books (balls) versus pamphlets (triangles)

Books are any documents with more than 32 pages. Pamphlets are anything less or equal than 32 pages.

```{r LIBER-12, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=6, fig.width=12}
df2 <- df
df2$document.type <- rep(NA, nrow(df2))
df2$document.type[df2$pagecount > 32] <- "book"
df2$document.type[df2$pagecount <= 32] <- "pamphlet"
df2 <- df2[which(!is.na(df2$document.type)),]
df2$document.type <- factor(df2$document.type)
df2 <- df2 %>% group_by(publication_decade, document.type) %>% summarize(paper.consumption.km2 = sum(paper.consumption.km2, na.rm = TRUE), n = n()) 
p <- ggplot(df2, aes(x = publication_decade, y = paper.consumption.km2, group = document.type))
p <- p + geom_point(aes(shape = document.type), size = 5)
p <- p + geom_smooth(method = "loess", color = "black")
p <- p + ggtitle("Paper consumption per document type")
p <- p + xlab("Year")
p <- p + ylab("Paper consumption (km2)")
p <- p + scale_color_manual(values=c("black", "darkgray"))
p <- p + guides(shape = "none")
p <- p + ggtitle("Books versus pamphlets: paper consumption")
print(p)
```

### Paper consumption for different document formats over time

Each point represents a decade. Loess smoothing.

```{r LIBER-13, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=11, fig.height=6}
df2 <- df %>% group_by(publication_decade, gatherings) %>% summarize(paper.consumption.km2 = sum(paper.consumption.km2, na.rm = TRUE), n = n()) 
df2 <- filter(df2, gatherings %in% setdiff(names(which(table(df2$gatherings) >= 15)), "NA"))
p <- ggplot(df2, aes(y = paper.consumption.km2, x = publication_decade, shape = gatherings, linetype = gatherings))
p <- p + geom_point(size = 4)
p <- p + geom_smooth(method = "loess", size = 1, color = "black")
p <- p + ggtitle("Paper consumption in time by gatherings")
p <- p + xlab("Year")
p <- p + ylab("Paper consumption (km2)")
p <- p + guides(linetype = guide_legend(keywidth = 5), shape = guide_legend(keywidth = 5))
p <- p + ggtitle("Paper consumption for different document formats")
print(p)
```

## Session info

This document was created with the following versions:

```{r sessioninfo, message=FALSE, warning=FALSE}
sessionInfo()
```

### 2016-06-22 inst/examples/manuscript-krakow.Rmd
ok
Rmd update

@@
 
-## Introduction (MT + JM voi jo kasata tähän hyvää läppää + viitteitä)
+## Introduction
 
@@
 aikana.
+
+The most active known female authors based on the title count:
+
+```{r 201606krakow-fennica-topfemale, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=6, fig.width=10}
+
+theme_set(theme_bw(20))
+dfs <- fen %>% filter(author_gender == "female")
+p <- top_plot(dfs, "author", ntop = 20)
+p <- p + scale_fill_manual(values = "black")
+p <- p + guides(fill = "none")
+p <- p + ylab("Title count")
+p <- p + ggtitle("Top female authors (Fennica)")
+p <- p + theme(axis.text.x = element_text(size = 16), axis.text.y = element_text(size = 16), axis.title.x = element_text(size = 25), axis.title.y = element_text(size = 22), title = element_text(size = 22))
+pf = p
+
+theme_set(theme_bw(20))
+dfs <- kun %>% filter(author_gender == "female")
+p <- top_plot(dfs, "author", ntop = 20)
+p <- p + scale_fill_manual(values = "black")
+p <- p + guides(fill = "none")
+p <- p + ylab("Title count")
+p <- p + ggtitle("Top female authors (Kungliga)")
+p <- p + theme(axis.text.x = element_text(size = 16), axis.text.y = element_text(size = 16), axis.title.x = element_text(size = 25), axis.title.y = element_text(size = 22), title = element_text(size = 22))
+pk = p
+
+library(gridExtra)
+grid.arrange(pf, pk, nrow = 1)
+```
+
+The top publication places ranked by the title count
+
+```{r LIBER-topplace, echo=FALSE, message=FALSE, cache=FALSE, fig.height=6, fig.width=6}
+theme_set(theme_bw(30))
+p <- top_plot(fen, "publication_place", ntop = 20)
+p <- p + scale_fill_manual(values = "black")
+p <- p + guides(fill = "none")
+p <- p + ylab("Title count (Log10 scale)")
+p <- p + scale_y_log10()
+p <- p + ggtitle("Top publication places (Fennica)")
+pf = p
+
+theme_set(theme_bw(30))
+p <- top_plot(kun, "publication_place", ntop = 20)
+p <- p + scale_fill_manual(values = "black")
+p <- p + guides(fill = "none")
+p <- p + ylab("Title count (Log10 scale)")
+p <- p + scale_y_log10()
+p <- p + ggtitle("Top publication places (Kungliga)")
+pk = p
+
+grid.arrange(pf, pk, nrow = 1)
+```
+
+Title count and overall paper consumption in the top publication locations (Fennica).
+The current country of origin is indicated.
+Finland is highlighted.
+Note that paper consumption estimates have still problems.
+
+```{r LIBER-8, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=6, fig.width=8}
+df <- fen
+theme_set(theme_bw(20))
+top <- names(rev(sort(table(df$publication_place))))[1:50]
+dfs <- df %>% filter(publication_place %in% top) %>% group_by(publication_place) %>% summarize(titles = n(), paper = sum(paper.consumption.km2, na.rm = T))
+dfs$country <- get_country(dfs$publication_place)
+dfs$finland <- dfs$country == "Finland"
+p <- ggplot(dfs, aes(x = titles, y = paper))
+p <- p + geom_text(aes(label = publication_place, color = finland), size = 5)
+p <- p + xlab("Title Count") + ylab("Paper consumption (km2)")
+p <- p + scale_color_manual(values = c("darkgray", "black"))
+p <- p + guides(color = "none")
+p <- p + scale_x_log10() + scale_y_log10() 
+p <- p + ggtitle("Title count versus paper (places)")
+print(p)	 
+```
+
+Gatherings vs. pagecounts per country (Fennica)
+
+```{r LIBER-docsizecomp3, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=10}
+dfs <- fen %>% select(pagecount, gatherings, country) %>% filter(country %in% selected.countries) %>% group_by(pagecount, gatherings, country) %>% tally()
+p <- ggplot(dfs, aes(x = pagecount, y = gatherings, size = n)) +
+     geom_point() + facet_grid(country ~ .) + scale_x_log10()
+print(p)
+```
+
+Average paper consumption per document
+
+```{r LIBER-11, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=5, fig.width=9}
+theme_set(theme_bw(25))
+library(sorvi)
+df = df.preprocessed
+dfs <- df %>% group_by(publication_year) %>%
+         summarize(paper.per.doc = mean(paper.consumption.km2, na.rm = T))
+p <- ggplot(dfs, aes(y = paper.per.doc, x = publication_year)) +
+       geom_line() + geom_point() +
+       xlab("Publication Year") + ylab("Paper per document")
+p <- p + ggtitle("Average paper consumption per document")
+print(p)
+```
+
+Paper consumption in books (balls) versus pamphlets (triangles). Books are any documents with more than 32 pages. Pamphlets are anything less or equal than 32 pages. Fennica data
+
+```{r LIBER-12, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=6, fig.width=12}
+df2 <- fen
+df2$document.type <- rep(NA, nrow(df2))
+df2$document.type[df2$pagecount > 32] <- "book"
+df2$document.type[df2$pagecount <= 32] <- "pamphlet"
+df2 <- df2[which(!is.na(df2$document.type)),]
+df2$document.type <- factor(df2$document.type)
+df2 <- df2 %>% group_by(publication_decade, document.type) %>% summarize(paper.consumption.km2 = sum(paper.consumption.km2, na.rm = TRUE), n = n()) 
+p <- ggplot(df2, aes(x = publication_decade, y = paper.consumption.km2, group = document.type))
+p <- p + geom_point(aes(shape = document.type), size = 5)
+p <- p + geom_smooth(method = "loess", color = "black")
+p <- p + ggtitle("Paper consumption per document type")
+p <- p + xlab("Year")
+p <- p + ylab("Paper consumption (km2)")
+p <- p + scale_color_manual(values=c("black", "darkgray"))
+p <- p + guides(shape = "none")
+p <- p + ggtitle("Books versus pamphlets: paper consumption")
+print(p)
+```
+
+Paper consumption for different document formats over time. Each point represents a decade. Loess smoothing. Fennica.
+
+```{r LIBER-13, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=11, fig.height=6}
+df2 <- df %>% group_by(publication_decade, gatherings) %>% summarize(paper.consumption.km2 = sum(paper.consumption.km2, na.rm = TRUE), n = n()) 
+df2 <- filter(df2, gatherings %in% setdiff(names(which(table(df2$gatherings) >= 15)), "NA"))
+p <- ggplot(df2, aes(y = paper.consumption.km2, x = publication_decade, shape = gatherings, linetype = gatherings))
+p <- p + geom_point(size = 4)
+p <- p + geom_smooth(method = "loess", size = 1, color = "black")
+p <- p + ggtitle("Paper consumption in time by gatherings")
+p <- p + xlab("Year")
+p <- p + ylab("Paper consumption (km2)")
+p <- p + guides(linetype = guide_legend(keywidth = 5), shape = guide_legend(keywidth = 5))
+p <- p + ggtitle("Paper consumption for different document formats")
+print(p)
+```
 
@@
 ```
+
+## Session info
+
+This document was created with the following versions:
+
+```{r sessioninfo, message=FALSE, warning=FALSE}
+sessionInfo()
+```

### 2016-06-22 inst/examples/manuscript-krakow.Rmd
Rmd update

@@
 kun <- kun %>% filter(publication_year >= min.year & publication_year <= max.year)
+df0 = bind_rows(fen, kun)
+df0$catalogue = factor(c(rep("Fennica", nrow(fen)), rep("Kungliga", nrow(kun))))
 ```
@@
 ```{r 201606krakow-fennica-topfemale, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=6, fig.width=10}
-
 theme_set(theme_bw(20))
@@
 grid.arrange(pf, pk, nrow = 1)
-```
-
-Title count and overall paper consumption in the top publication locations (Fennica).
-The current country of origin is indicated.
-Finland is highlighted.
-Note that paper consumption estimates have still problems.
-
-```{r LIBER-8, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=6, fig.width=8}
-df <- fen
-theme_set(theme_bw(20))
-top <- names(rev(sort(table(df$publication_place))))[1:50]
-dfs <- df %>% filter(publication_place %in% top) %>% group_by(publication_place) %>% summarize(titles = n(), paper = sum(paper.consumption.km2, na.rm = T))
-dfs$country <- get_country(dfs$publication_place)
-dfs$finland <- dfs$country == "Finland"
-p <- ggplot(dfs, aes(x = titles, y = paper))
-p <- p + geom_text(aes(label = publication_place, color = finland), size = 5)
-p <- p + xlab("Title Count") + ylab("Paper consumption (km2)")
-p <- p + scale_color_manual(values = c("darkgray", "black"))
-p <- p + guides(color = "none")
-p <- p + scale_x_log10() + scale_y_log10() 
-p <- p + ggtitle("Title count versus paper (places)")
-print(p)	 
-```
-
-Gatherings vs. pagecounts per country (Fennica)
-
-```{r LIBER-docsizecomp3, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=10}
-dfs <- fen %>% select(pagecount, gatherings, country) %>% filter(country %in% selected.countries) %>% group_by(pagecount, gatherings, country) %>% tally()
-p <- ggplot(dfs, aes(x = pagecount, y = gatherings, size = n)) +
-     geom_point() + facet_grid(country ~ .) + scale_x_log10()
-print(p)
-```
-
-Average paper consumption per document
-
-```{r LIBER-11, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=5, fig.width=9}
-theme_set(theme_bw(25))
-library(sorvi)
-df = df.preprocessed
-dfs <- df %>% group_by(publication_year) %>%
-         summarize(paper.per.doc = mean(paper.consumption.km2, na.rm = T))
-p <- ggplot(dfs, aes(y = paper.per.doc, x = publication_year)) +
-       geom_line() + geom_point() +
-       xlab("Publication Year") + ylab("Paper per document")
-p <- p + ggtitle("Average paper consumption per document")
-print(p)
-```
-
-Paper consumption in books (balls) versus pamphlets (triangles). Books are any documents with more than 32 pages. Pamphlets are anything less or equal than 32 pages. Fennica data
-
-```{r LIBER-12, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=6, fig.width=12}
-df2 <- fen
-df2$document.type <- rep(NA, nrow(df2))
-df2$document.type[df2$pagecount > 32] <- "book"
-df2$document.type[df2$pagecount <= 32] <- "pamphlet"
-df2 <- df2[which(!is.na(df2$document.type)),]
-df2$document.type <- factor(df2$document.type)
-df2 <- df2 %>% group_by(publication_decade, document.type) %>% summarize(paper.consumption.km2 = sum(paper.consumption.km2, na.rm = TRUE), n = n()) 
-p <- ggplot(df2, aes(x = publication_decade, y = paper.consumption.km2, group = document.type))
-p <- p + geom_point(aes(shape = document.type), size = 5)
-p <- p + geom_smooth(method = "loess", color = "black")
-p <- p + ggtitle("Paper consumption per document type")
-p <- p + xlab("Year")
-p <- p + ylab("Paper consumption (km2)")
-p <- p + scale_color_manual(values=c("black", "darkgray"))
-p <- p + guides(shape = "none")
-p <- p + ggtitle("Books versus pamphlets: paper consumption")
-print(p)
 ```
@@
 
+## Miscellaneous figures to consider
+
+Gatherings vs. pagecounts per country (Fennica)
+
+```{r LIBER-docsizecomp3, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=10}
+dfs <- fen %>% select(pagecount, gatherings, country) %>% filter(country %in% selected.countries) %>% group_by(pagecount, gatherings, country) %>% tally()
+p <- ggplot(dfs, aes(x = pagecount, y = gatherings, size = n)) +
+     geom_point() + facet_grid(country ~ .) + scale_x_log10()
+print(p)
+```
+
+Average paper consumption per document
+
+```{r LIBER-11, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=5, fig.width=9}
+theme_set(theme_bw(25))
+library(sorvi)
+df = df0
+dfs <- df %>% group_by(publication_year) %>%
+         summarize(paper.per.doc = mean(paper.consumption.km2, na.rm = T))
+p <- ggplot(dfs, aes(y = paper.per.doc, x = publication_year)) +
+       geom_line() + geom_point() +
+       xlab("Publication Year") + ylab("Paper per document")
+p <- p + ggtitle("Average paper consumption per document")
+print(p)
+```
+
+Title count and overall paper consumption in the top publication locations (Fennica).
+The current country of origin is indicated.
+Finland is highlighted.
+Note that paper consumption estimates have still problems.
+
+```{r LIBER-8, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=6, fig.width=8}
+df <- fen
+theme_set(theme_bw(20))
+top <- names(rev(sort(table(df$publication_place))))[1:50]
+dfs <- df %>% filter(publication_place %in% top) %>% group_by(publication_place) %>% summarize(titles = n(), paper = sum(paper.consumption.km2, na.rm = T))
+dfs$country <- get_country(dfs$publication_place)
+dfs$finland <- dfs$country == "Finland"
+p <- ggplot(dfs, aes(x = titles, y = paper))
+p <- p + geom_text(aes(label = publication_place, color = finland), size = 5)
+p <- p + xlab("Title Count") + ylab("Paper consumption (km2)")
+p <- p + scale_color_manual(values = c("darkgray", "black"))
+p <- p + guides(color = "none")
+p <- p + scale_x_log10() + scale_y_log10() 
+p <- p + ggtitle("Title count versus paper (places)")
+print(p)	 
+```
+
+Paper consumption in books (balls) versus pamphlets (triangles). Books are any documents with more than 32 pages. Pamphlets are anything less or equal than 32 pages. Fennica data
+
+```{r LIBER-12, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=6, fig.width=12}
+df2 <- fen
+df2$document.type <- rep(NA, nrow(df2))
+df2$document.type[df2$pagecount > 32] <- "book"
+df2$document.type[df2$pagecount <= 32] <- "pamphlet"
+df2 <- df2[which(!is.na(df2$document.type)),]
+df2$document.type <- factor(df2$document.type)
+df2 <- df2 %>% group_by(publication_decade, document.type) %>% summarize(paper.consumption.km2 = sum(paper.consumption.km2, na.rm = TRUE), n = n()) 
+p <- ggplot(df2, aes(x = publication_decade, y = paper.consumption.km2, group = document.type))
+p <- p + geom_point(aes(shape = document.type), size = 5)
+p <- p + geom_smooth(method = "loess", color = "black")
+p <- p + ggtitle("Paper consumption per document type")
+p <- p + xlab("Year")
+p <- p + ylab("Paper consumption (km2)")
+p <- p + scale_color_manual(values=c("black", "darkgray"))
+p <- p + guides(shape = "none")
+p <- p + ggtitle("Books versus pamphlets: paper consumption")
+print(p)
+```
+
 ## Session info

### 2016-06-22 inst/examples/manuscript-krakow.Rmd
Rmd update

@@
 
-[ESTC-analyses](https://github.com/rOpenGov/estc)
-([LIBER](https://github.com/rOpenGov/estc/blob/master/inst/examples/20151023-LIBER.md)
-in particular); toisto Fennica/Kungliga datoilla ? LL: Voidaan tehda
-mut kandee miettia ehka spesifimmin et mitka analyysit sielta
-kiinnostaa. Muuten menee aikaa hukkaan jos pitaa fiksata juttuja joita
-ei sitten kaytetakaan.
-
 ### Fennica vs. Kungliga
@@
 
-```{r 201606krakow-fennica-topfemale, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=6, fig.width=10}
-theme_set(theme_bw(20))
+```{r 201606krakow-fennica-topfemale, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=5, fig.width=15, out.width="850px"}
+theme_set(theme_bw(10))
 dfs <- fen %>% filter(author_gender == "female")
@@
 
-```{r LIBER-topplace, echo=FALSE, message=FALSE, cache=FALSE, fig.height=6, fig.width=6}
-theme_set(theme_bw(30))
-p <- top_plot(fen, "publication_place", ntop = 20)
+```{r LIBER-topplace, echo=FALSE, message=FALSE, cache=FALSE, fig.height=6, fig.width=12}
+theme_set(theme_bw(20))
+ntop = 10
+p <- top_plot(fen, "publication_place", ntop = ntop)
 p <- p + scale_fill_manual(values = "black")
@@
 p <- p + scale_y_log10()
-p <- p + ggtitle("Top publication places (Fennica)")
+p <- p + ggtitle("Top publication places\n(Fennica)")
 pf = p
@@
 theme_set(theme_bw(30))
-p <- top_plot(kun, "publication_place", ntop = 20)
+p <- top_plot(kun, "publication_place", ntop = ntop)
 p <- p + scale_fill_manual(values = "black")
@@
 p <- p + scale_y_log10()
-p <- p + ggtitle("Top publication places (Kungliga)")
+p <- p + ggtitle("Top publication places\n(Kungliga)")
 pk = p
@@
 
-Paper consumption for different document formats over time. Each point represents a decade. Loess smoothing. Fennica.
+Paper consumption for different document formats over time. Each point represents a decade. Loess smoothing.
 
-```{r LIBER-13, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=11, fig.height=6}
-df2 <- df %>% group_by(publication_decade, gatherings) %>% summarize(paper.consumption.km2 = sum(paper.consumption.km2, na.rm = TRUE), n = n()) 
+```{r LIBER-13, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=10, fig.height=8, fig.show="hold", out.width="430px"}
+for (catal in unique(df0$catalogue)) {
+  df2 <- subset(df0, catalogue == catal) %>% group_by(publication_decade, gatherings) %>% summarize(paper.consumption.km2 = sum(paper.consumption.km2, na.rm = TRUE), n = n()) 
   df2 <- filter(df2, gatherings %in% setdiff(names(which(table(df2$gatherings) >= 15)), "NA"))
@@
   p <- p + guides(linetype = guide_legend(keywidth = 5), shape = guide_legend(keywidth = 5))
-p <- p + ggtitle("Paper consumption for different document formats")
+  p <- p + ggtitle(paste("Paper consumption\n(", catal, ")", sep = ""))
   print(p)
+}
+
 ```
@@
 
-## Miscellaneous figures to consider
+## Miscellaneous ideas to consider
+
+[ESTC-analyses](https://github.com/rOpenGov/estc)
+([LIBER](https://github.com/rOpenGov/estc/blob/master/inst/examples/20151023-LIBER.md)
+in particular); toisto Fennica/Kungliga datoilla ? LL: lisäilin
+joitain analyyseja tahan mutta jos tahdotte lisaa niin pyytakaa
+erikseen.
 

### 2016-06-22 inst/examples/manuscript-krakow.Rmd
Rmd update

@@
 
-The most active known female authors based on the title count:
-
-```{r 201606krakow-fennica-topfemale, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=5, fig.width=15, out.width="850px"}
-theme_set(theme_bw(10))
-dfs <- fen %>% filter(author_gender == "female")
-p <- top_plot(dfs, "author", ntop = 20)
-p <- p + scale_fill_manual(values = "black")
-p <- p + guides(fill = "none")
-p <- p + ylab("Title count")
-p <- p + ggtitle("Top female authors (Fennica)")
-p <- p + theme(axis.text.x = element_text(size = 16), axis.text.y = element_text(size = 16), axis.title.x = element_text(size = 25), axis.title.y = element_text(size = 22), title = element_text(size = 22))
-pf = p
-
-theme_set(theme_bw(20))
-dfs <- kun %>% filter(author_gender == "female")
-p <- top_plot(dfs, "author", ntop = 20)
-p <- p + scale_fill_manual(values = "black")
-p <- p + guides(fill = "none")
-p <- p + ylab("Title count")
-p <- p + ggtitle("Top female authors (Kungliga)")
-p <- p + theme(axis.text.x = element_text(size = 16), axis.text.y = element_text(size = 16), axis.title.x = element_text(size = 25), axis.title.y = element_text(size = 22), title = element_text(size = 22))
-pk = p
-
-library(gridExtra)
-grid.arrange(pf, pk, nrow = 1)
-```
-
 The top publication places ranked by the title count
@@
 grid.arrange(pf, pk, nrow = 1)
-```
-
-Paper consumption for different document formats over time. Each point represents a decade. Loess smoothing.
-
-```{r LIBER-13, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=10, fig.height=8, fig.show="hold", out.width="430px"}
-for (catal in unique(df0$catalogue)) {
-  df2 <- subset(df0, catalogue == catal) %>% group_by(publication_decade, gatherings) %>% summarize(paper.consumption.km2 = sum(paper.consumption.km2, na.rm = TRUE), n = n()) 
-  df2 <- filter(df2, gatherings %in% setdiff(names(which(table(df2$gatherings) >= 15)), "NA"))
-  p <- ggplot(df2, aes(y = paper.consumption.km2, x = publication_decade, shape = gatherings, linetype = gatherings))
-  p <- p + geom_point(size = 4)
-  p <- p + geom_smooth(method = "loess", size = 1, color = "black")
-  p <- p + ggtitle("Paper consumption in time by gatherings")
-  p <- p + xlab("Year")
-  p <- p + ylab("Paper consumption (km2)")
-  p <- p + guides(linetype = guide_legend(keywidth = 5), shape = guide_legend(keywidth = 5))
-  p <- p + ggtitle(paste("Paper consumption\n(", catal, ")", sep = ""))
-  print(p)
-}
-
 ```
@@
 mielenkiintoista.
+
+Paper consumption for different document formats over time. Each point represents a decade. Loess smoothing.
+
+```{r LIBER-13, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=10, fig.height=8, fig.show="hold", out.width="430px"}
+for (catal in unique(df0$catalogue)) {
+  df2 <- subset(df0, catalogue == catal) %>% group_by(publication_decade, gatherings) %>% summarize(paper.consumption.km2 = sum(paper.consumption.km2, na.rm = TRUE), n = n()) 
+  df2 <- filter(df2, gatherings %in% setdiff(names(which(table(df2$gatherings) >= 15)), "NA"))
+  p <- ggplot(df2, aes(y = paper.consumption.km2, x = publication_decade, shape = gatherings, linetype = gatherings))
+  p <- p + geom_point(size = 4)
+  p <- p + geom_smooth(method = "loess", size = 1, color = "black")
+  p <- p + ggtitle("Paper consumption in time by gatherings")
+  p <- p + xlab("Year")
+  p <- p + ylab("Paper consumption (km2)")
+  p <- p + guides(linetype = guide_legend(keywidth = 5), shape = guide_legend(keywidth = 5))
+  p <- p + ggtitle(paste("Paper consumption\n(", catal, ")", sep = ""))
+  print(p)
+}
+
+```
 
@@
 
+The most active known female authors based on the title count:
+
+```{r 201606krakow-fennica-topfemale, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=5, fig.width=15, out.width="850px"}
+theme_set(theme_bw(10))
+dfs <- fen %>% filter(author_gender == "female")
+p <- top_plot(dfs, "author", ntop = 20)
+p <- p + scale_fill_manual(values = "black")
+p <- p + guides(fill = "none")
+p <- p + ylab("Title count")
+p <- p + ggtitle("Top female authors\n(Fennica)")
+p <- p + theme(axis.text.x = element_text(size = 16), axis.text.y = element_text(size = 16), axis.title.x = element_text(size = 25), axis.title.y = element_text(size = 22), title = element_text(size = 22))
+pf = p
+
+theme_set(theme_bw(20))
+dfs <- kun %>% filter(author_gender == "female")
+p <- top_plot(dfs, "author", ntop = 20)
+p <- p + scale_fill_manual(values = "black")
+p <- p + guides(fill = "none")
+p <- p + ylab("Title count")
+p <- p + ggtitle("Top female authors\n(Kungliga)")
+p <- p + theme(axis.text.x = element_text(size = 16), axis.text.y = element_text(size = 16), axis.title.x = element_text(size = 25), axis.title.y = element_text(size = 22), title = element_text(size = 22))
+pk = p
+
+library(gridExtra)
+grid.arrange(pf, pk, nrow = 1)
+```
+
 Gatherings vs. pagecounts per country (Fennica)

### 2016-06-22 inst/examples/manuscript-krakow.Rmd
Rmd update

@@
 df0 = bind_rows(fen, kun)
-df0$catalogue = factor(c(rep("Fennica", nrow(fen)), rep("Kungliga", nrow(kun))))
+df0$catalog = factor(c(rep("Fennica", nrow(fen)), rep("Kungliga", nrow(kun))))
 ```
@@
 
-### General trends
+### General trends: Fennica vs. Kungliga
 
-Relevant summaries can be moved here and polished. Which figures at least ?
-
-General trends (top authors etc):
+Relevant summaries can be moved here and polished. Which figures at least ? Just let me know and I will add.
 
@@
 
-### Fennica vs. Kungliga
+Alustavia vertailuja
 
-Alustavia vertailuja Kungligasta suhteessa Fennicaan.
-
+ * Julkaisumäärien tilastointeja yleisesti ja paikkakunnittain
  * Fennica pois lukien Suomi ?
  * Kungliga pois lukien Ruotsi ?
- * Julkaisumäärien tilastointeja yleisesti ja paikkakunnittain
 
@@
 aikana.
+
+Title count per decade:
+
+```{r publishingovertime, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
+df2 <- df0 %>% group_by(publication_decade, catalog) 
+p <- ggplot(df2, aes(publication_decade)) +
+     geom_bar() + scale_y_log10() + facet_grid(catalog ~ .) +
+     ggtitle("Title count timeline")
+print(p)
+```
 
@@
 
+```{r papercompbyformat, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=7, fig.show="hold", out.width="430px"}
+for (catal in unique(df0$catalog)) {
+  dfs <- df0 %>% filter(!gatherings == "NA" & catalog == catal)
+
+  res <- titlecount_timeline(dfs, "gatherings", nmin = 15, mode = "n") 
+  print(res$plot + ggtitle(paste(catal, " (n)", sep = "")))
+
+  res <- titlecount_timeline(dfs, "gatherings", nmin = 15, mode = "percentage") 
+  print(res$plot + ggtitle(paste(catal, " (%)", sep = "")))
+}
+```
+
 Paper consumption for different document formats over time. Each point represents a decade. Loess smoothing.
@@
 ```{r LIBER-13, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=10, fig.height=8, fig.show="hold", out.width="430px"}
-for (catal in unique(df0$catalogue)) {
-  df2 <- subset(df0, catalogue == catal) %>% group_by(publication_decade, gatherings) %>% summarize(paper.consumption.km2 = sum(paper.consumption.km2, na.rm = TRUE), n = n()) 
+for (catal in unique(df0$catalog)) {
+  df2 <- subset(df0, catalog == catal) %>% group_by(publication_decade, gatherings) %>% summarize(paper.consumption.km2 = sum(paper.consumption.km2, na.rm = TRUE), n = n()) 
   df2 <- filter(df2, gatherings %in% setdiff(names(which(table(df2$gatherings) >= 15)), "NA"))
@@
 
-Library catalogues contain rich metadata on...
+Library catalogs contain rich metadata on...
 

### 2016-06-22 inst/examples/manuscript-krakow.Rmd
lisäsin viitteen
Rmd update

@@
 (väitöskirja) käsittelee Turun yliopiston asemaa.
+
+Östholm, Hanna, Litteraturens uppodling : läsesällskap och litteraturkritik som politisk strategi vid sekelskiftet 1800; vertailee Turkua ja Uppsalaa lukuseurojen kautta.
 
@@
 ```{r LIBER-docsizecomp3, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=10}
+selected.countries = c("Finland", "Sweden")
 dfs <- fen %>% select(pagecount, gatherings, country) %>% filter(country %in% selected.countries) %>% group_by(pagecount, gatherings, country) %>% tally()

### 2016-06-22 inst/examples/manuscript-krakow.Rmd
Rmd update

@@
 
-Title count per decade:
+Paper consumption per decade:
 
 ```{r publishingovertime, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
-df2 <- df0 %>% group_by(publication_decade, catalog) 
-p <- ggplot(df2, aes(publication_decade)) +
-     geom_bar() + scale_y_log10() + facet_grid(catalog ~ .) +
-     ggtitle("Title count timeline")
+df2 <- df0 %>% group_by(publication_decade, catalog) %>% summarise(paper = sum(paper.consumption.km2, na.rm = TRUE))
+p <- ggplot(df2, aes(x = publication_decade, y = paper)) +
+     geom_bar(stat = "identity") + #scale_y_log10() +
+     facet_grid(catalog ~ .) +
+     ggtitle("Paper consumption timeline")
 print(p)

### 2016-06-22 inst/examples/manuscript-krakow.Rmd
Rmd update

@@
 --> tapahtuuko Gävlessä selvää nousua julkaisemisessa.
+
+The publishing of historical works in .. on a timeline highlighting the eras of the riksdagar (16..-16..)..
+
+```{r valtiopaivat, echo=FALSE, warning=FALSE, fig.width=11, fig.height=4}
+# Use timeinterval year intervals
+dfsel = df0
+#dfsel = subset(df0, publication_place == "Stockholm")
+#dfsel = subset(df0, publication_place == "Norrköping")
+#dfsel = subset(df0, publication_place == "Gävle")
+
+df <- subset(dfsel, publication_year >= 1700 & publication_year < 1800 )
+
+timeinterval <- 1
+df$timeunit <- round(df$publication_year/timeinterval)*timeinterval
+
+df$unity = rep(1, nrow(df))
+publications <- tapply(df$unity, list(df$timeunit), sum)
+
+publications[is.na(publications)] <- 0 # Set NAs to 0
+publications <- publications/timeinterval # Instead of decadal sum, use average annual output 
+dfm <- melt(publications) 
+names(dfm) <- c("Time", "Documents")
+dfm <- transform(dfm, date = as.numeric(as.character(Time)))
+ymin = min(dfm$Documents)
+ymax = max(dfm$Documents)
+
+rect_left <- c(min(na.omit(dfm$date)),
+               1719-.5, 1719+.5, # Stockholm 20 januari 1719 1 juni 1719
+               1734-.5, 1734+.5, # Stockholm 14 maj 1734 14 december 1734
+               1765-.5, 1766+.5, # Stockholm 21 februari 1765 21 oktober 1766
+               1769-.5, 1770+.5, # Norrköping & Stockholm 22 april 1769 5 februari 1770
+               1771-.5, 1772+.5, # Stockholm 19 juni 1771 12 september 1772
+               1792-.5, 1792+.5, # Gävle 26 januari 1792 24 februari 1792	       
+               max(na.omit(dfm$date)))
+  rectangles <- data.frame(
+    xmin = rect_left[-length(rect_left)],
+    xmax = rect_left[-1],
+    ymin = ymin,
+    ymax = ymax
+    )
+  rectangles$shade <- rep(c("White", "Highlight"), length = nrow(rectangles))
+  #rectangles$shade <- rep(c("White", "Highlight"), length = nrow(rectangles))
+
+ riksplace = c("Stockholm", "Stockholm", "Stockholm", "Norrköping", "Stockholm", "Gävle")
+ cols = c("gray", "lightblue", "yellow", "white")
+ rectangles$shade[rectangles$shade == "Highlight"] = riksplace
+ rectangles$shade = factor(rectangles$shade)
+
+# Draw Figure
+theme_set(theme_bw(20))
+p <- ggplot()
+p <- p + geom_rect(data = rectangles, 
+	   aes(xmin=xmin, xmax=xmax, ymin=ymin, ymax=ymax, fill=shade), alpha=0.8) + 
+         scale_fill_manual(values = cols) # + guides(fill = "none") 
+p <- p + geom_line(data = dfm, aes(x = date, y = Documents), col = "black")
+p <- p + geom_point(data = dfm, aes(x = date, y = Documents), col = "black")
+p <- p + scale_x_continuous(breaks=seq(min(dfm$date), max(dfm$date), 20))
+p <- p + ggtitle("Publishing activity")
+p <- p + ylab("Documents / Year")
+p <- p + xlab("Year")
+p <- p + ggtitle("Riksdagar - overall titlecount (Fen + Kun)")
+print(p)
+```
 

### 2016-06-22 inst/examples/manuscript-krakow.Rmd
Rmd update

@@
 
-```{r valtiopaivat, echo=FALSE, warning=FALSE, fig.width=11, fig.height=4}
+```{r valtiopaivat-total, echo=FALSE, warning=FALSE, fig.width=11, fig.height=4}
 # Use timeinterval year intervals
@@
 p <- p + ggtitle("Riksdagar - overall titlecount (Fen + Kun)")
+print(p)
+```
+
+```{r valtiopaivat-gavle, echo=FALSE, warning=FALSE, fig.width=11, fig.height=4}
+# Use timeinterval year intervals
+myplace = "Gävle" # Norrköping / Stockholm
+dfsel = subset(df0, publication_place == myplace)
+
+df <- subset(dfsel, publication_year >= 1700 & publication_year < 1800 )
+
+timeinterval <- 1
+df$timeunit <- round(df$publication_year/timeinterval)*timeinterval
+
+df$unity = rep(1, nrow(df))
+publications <- tapply(df$unity, list(df$timeunit), sum)
+
+publications[is.na(publications)] <- 0 # Set NAs to 0
+publications <- publications/timeinterval # Instead of decadal sum, use average annual output 
+dfm <- melt(publications) 
+names(dfm) <- c("Time", "Documents")
+dfm <- transform(dfm, date = as.numeric(as.character(Time)))
+ymin = min(dfm$Documents)
+ymax = max(dfm$Documents)
+
+rect_left <- c(min(na.omit(dfm$date)),
+               1719-.5, 1719+.5, # Stockholm 20 januari 1719 1 juni 1719
+               1734-.5, 1734+.5, # Stockholm 14 maj 1734 14 december 1734
+               1765-.5, 1766+.5, # Stockholm 21 februari 1765 21 oktober 1766
+               1769-.5, 1770+.5, # Norrköping & Stockholm 22 april 1769 5 februari 1770
+               1771-.5, 1772+.5, # Stockholm 19 juni 1771 12 september 1772
+               1792-.5, 1792+.5, # Gävle 26 januari 1792 24 februari 1792	       
+               max(na.omit(dfm$date)))
+  rectangles <- data.frame(
+    xmin = rect_left[-length(rect_left)],
+    xmax = rect_left[-1],
+    #xmin = min(dfsel$publication_year),
+    #xmax = max(dfsel$publication_year),    
+    ymin = ymin,
+    ymax = ymax
+    )
+  rectangles$shade <- rep(c("White", "Highlight"), length = nrow(rectangles))
+  #rectangles$shade <- rep(c("White", "Highlight"), length = nrow(rectangles))
+
+ riksplace = c("Stockholm", "Stockholm", "Stockholm", "Norrköping", "Stockholm", "Gävle")
+ cols = c("gray", "lightblue", "yellow", "white")
+ rectangles$shade[rectangles$shade == "Highlight"] = riksplace
+ rectangles$shade = factor(rectangles$shade)
+
+# Draw Figure
+theme_set(theme_bw(20))
+p <- ggplot()
+p <- p + geom_rect(data = rectangles, 
+	   aes(xmin=xmin, xmax=xmax, ymin=ymin, ymax=ymax, fill=shade), alpha=0.8) + 
+         scale_fill_manual(values = cols) # + guides(fill = "none") 
+p <- p + geom_line(data = dfm, aes(x = date, y = Documents), col = "black")
+p <- p + geom_point(data = dfm, aes(x = date, y = Documents), col = "black")
+p <- p + scale_x_continuous(breaks=seq(min(dfsel$publication_year), max(dfsel$publication_year), 20))
+p <- p + ggtitle("Publishing activity")
+p <- p + ylab("Documents / Year")
+p <- p + xlab("Year")
+p <- p + ggtitle(paste("Riksdagar - titlecount in", myplace, sep = ""))
 print(p)

### 2016-06-22 inst/examples/manuscript-krakow.Rmd
Rmd update

@@
 dfsel = subset(df0, publication_place == myplace)
+minyear = 1700
+maxyear = 1800
 
-df <- subset(dfsel, publication_year >= 1700 & publication_year < 1800 )
+df <- subset(dfsel, publication_year >= minyear & publication_year < maxyear)
 
@@
 p <- p + geom_point(data = dfm, aes(x = date, y = Documents), col = "black")
-p <- p + scale_x_continuous(breaks=seq(min(dfsel$publication_year), max(dfsel$publication_year), 20))
+p <- p + scale_x_continuous(breaks=seq(minyear, maxyear, 20))
 p <- p + ggtitle("Publishing activity")
@@
 print(p)
+
 ```

### 2016-06-22 inst/examples/manuscript-krakow.Rmd
ok

@@
 p <- p + xlab("Year")
-p <- p + ggtitle(paste("Riksdagar - titlecount in", myplace, sep = ""))
+p <- p + ggtitle(paste("Riksdagar - titlecount in ", myplace, sep = ""))
 print(p)

### 2016-06-22 inst/examples/manuscript-krakow.Rmd
Rmd update

@@
 
-Alustavia vertailuja
-
- * Julkaisumäärien tilastointeja yleisesti ja paikkakunnittain
- * Fennica pois lukien Suomi ?
- * Kungliga pois lukien Ruotsi ?
-
-Turku vertailut Upsalaan, Lundiin, Tukholmaan yms. Turussa
-julkaiseminen alkaa vasta 1640-luvulla, mutta ollaan kiinnostuttu
-ruotsalaisesta julkaisemisesta ennen sitä. Esim miten Turun yliopiston
-perustaminen vaikuttaa ruotsalaiseen julkaisukenttään 1600-luvun
-aikana.
-
-Paper consumption per decade:
+Julkaisumäärien tilastointeja yleisesti:
 
 ```{r publishingovertime, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
-df2 <- df0 %>% group_by(publication_decade, catalog) %>% summarise(paper = sum(paper.consumption.km2, na.rm = TRUE))
-p <- ggplot(df2, aes(x = publication_decade, y = paper)) +
-     geom_bar(stat = "identity") + #scale_y_log10() +
-     facet_grid(catalog ~ .) +
-     ggtitle("Paper consumption timeline")
+df2 <- df0 %>% group_by(publication_decade, catalog) %>% summarise(paper = sum(paper.consumption.km2, na.rm = TRUE), n = n())
+df2$catalog = factor(df2$catalog, levels = rev(c("Fennica", "Kungliga")))
+p <- ggplot(df2, aes(x = publication_decade, y = n)) +
+     #geom_bar(stat = "identity") + #scale_y_log10() +
+     geom_line(aes(linetype = catalog)) +
+     geom_point(aes(shape = catalog), size = 3) +     
+     #ylab("Paper consumption (km2)")
+     ylab("Title count (n)") + xlab("Publication year") +  
+     ggtitle("Publishing activity")
 print(p)
 ```
+
+Julkaisumäärien tilastointeja paikkakunnittain:
 
@@
 grid.arrange(pf, pk, nrow = 1)
+```
+
+Comparing printing activity in Turku, Uppsala, Lund, and
+Stockholm. Turussa julkaiseminen alkaa vasta 1640-luvulla, mutta
+ollaan kiinnostuttu ruotsalaisesta julkaisemisesta ennen sitä. Esim
+miten Turun yliopiston perustaminen vaikuttaa ruotsalaiseen
+julkaisukenttään 1600-luvun aikana.
+
+I can here provide percentages, barplots, selected time spans,
+selected places etc.. just let me know what is needed.
+
+```{r publishingactivitycomparisons, echo=FALSE, message=FALSE, cache=FALSE, fig.width=10, fig.height=7, fig.show="hold", out.width="430px"}
+selected.places = c("Turku", "Uppsala", "Lund", "Stockholm")
+df2 <- df0 %>% group_by(publication_decade, publication_place, catalog) %>%
+               summarise(n = n()) %>%
+               #summarise(paper = sum(paper.consumption.km2, na.rm = TRUE), n = n()) %>%	       
+	       filter(publication_place %in% selected.places) # %>%
+	       #filter(publication_decade >= 1600)
+df2$catalog = factor(df2$catalog, levels = rev(c("Fennica", "Kungliga")))
+df2$publication_place = droplevels(factor(df2$publication_place))
+df3 = spread(df2, publication_decade, n, fill = 0)
+df2 = melt(df3)
+colnames(df2) = c("publication_place", "catalog", "publication_decade", "n")
+df2$publication_decade = as.numeric(as.character(df2$publication_decade))
+df2$n = as.numeric(as.character(df2$n))
+for (catal in unique(df2$catalog)) {
+
+  p <- ggplot(subset(df2, catalog == catal), aes(x = publication_decade, y = n)) +
+     geom_line(aes(linetype = publication_place)) +
+     geom_point(aes(shape = publication_place), size = 3) +
+     #scale_y_log10() +
+     #facet_wrap(catalog ~ .) + 
+     ylab("Title count (n)") + xlab("Publication year") +  
+     ggtitle(catal)
+  print(p)
+
+}
 ```
@@
 
+ * Fennica pois lukien Suomi ?
+ * Kungliga pois lukien Ruotsi ?
+
 [Topic](https://github.com/rOpenGov/kungliga/blob/master/antagomir/topic.md)

### 2016-06-22 inst/examples/manuscript-krakow.Rmd
Rmd update

--- 2016-06-22 inst/examples/manuscript-krakow.Rmd
@@
 
-Alustavia vertailuja
+Overall development in publishing activity:
 
- * Julkaisumäärien tilastointeja yleisesti ja paikkakunnittain
- * Fennica pois lukien Suomi ?
- * Kungliga pois lukien Ruotsi ?
-
-Turku vertailut Upsalaan, Lundiin, Tukholmaan yms. Turussa
-julkaiseminen alkaa vasta 1640-luvulla, mutta ollaan kiinnostuttu
-ruotsalaisesta julkaisemisesta ennen sitä. Esim miten Turun yliopiston
-perustaminen vaikuttaa ruotsalaiseen julkaisukenttään 1600-luvun
-aikana.
-
-Paper consumption per decade:
-
-```{r publishingovertime, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
-df2 <- df0 %>% group_by(publication_decade, catalog) %>% summarise(paper = sum(paper.consumption.km2, na.rm = TRUE))
-p <- ggplot(df2, aes(x = publication_decade, y = paper)) +
-     geom_bar(stat = "identity") + #scale_y_log10() +
-     facet_grid(catalog ~ .) +
-     ggtitle("Paper consumption timeline")
+```{r publishingovertime, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10, out.width="430px"}
+df2 <- df0 %>% group_by(publication_decade, catalog) %>% summarise(paper = sum(paper.consumption.km2, na.rm = TRUE), n = n())
+df2$catalog = factor(df2$catalog, levels = rev(c("Fennica", "Kungliga")))
+p <- ggplot(df2, aes(x = publication_decade, y = n)) +
+     #geom_bar(stat = "identity") + #scale_y_log10() +
+     geom_line(aes(linetype = catalog)) +
+     geom_point(aes(shape = catalog), size = 3) +     
+     #ylab("Paper consumption (km2)")
+     ylab("Title count (n)") + xlab("Publication year") +  
+     ggtitle("Overall publishing activity")
 print(p)
@@
 grid.arrange(pf, pk, nrow = 1)
+```
+
+Comparison of printing activity in Turku, Uppsala, Lund, and
+Stockholm. Turussa julkaiseminen alkaa vasta 1640-luvulla, mutta
+ollaan kiinnostuttu ruotsalaisesta julkaisemisesta ennen sitä. Esim
+miten Turun yliopiston perustaminen vaikuttaa ruotsalaiseen
+julkaisukenttään 1600-luvun aikana. I can provide percentages instead
+of counts, or paper consumption estimates (not reliable yet, though),
+barplots, selected time spans, selected places etc.. just let me know
+what is needed.
+
+```{r publishingactivitycomparisons, echo=FALSE, message=FALSE, cache=FALSE, fig.width=8, fig.height=6, fig.show="hold", out.width="430px"}
+selected.places = c("Turku", "Uppsala", "Lund", "Stockholm")
+df2 <- df0 %>% group_by(publication_decade, publication_place, catalog) %>%
+               summarise(n = n()) %>%
+               #summarise(paper = sum(paper.consumption.km2, na.rm = TRUE), n = n()) %>%	       
+	       filter(publication_place %in% selected.places) # %>%
+	       #filter(publication_decade >= 1600)
+df2$catalog = factor(df2$catalog, levels = rev(c("Fennica", "Kungliga")))
+df2$publication_place = droplevels(factor(df2$publication_place))
+df3 = spread(df2, publication_decade, n, fill = 0)
+df2 = melt(df3)
+colnames(df2) = c("publication_place", "catalog", "publication_decade", "n")
+df2$publication_decade = as.numeric(as.character(df2$publication_decade))
+df2$n = as.numeric(as.character(df2$n))
+for (catal in unique(df2$catalog)) {
+
+  p <- ggplot(subset(df2, catalog == catal), aes(x = publication_decade, y = n)) +
+     geom_line(aes(linetype = publication_place)) +
+     geom_point(aes(shape = publication_place), size = 3) +
+     #scale_y_log10() +
+     #facet_wrap(catalog ~ .) + 
+     ylab("Title count (n)") + xlab("Publication year") +  
+     ggtitle(catal)
+  print(p)
+
+}
 ```
@@
 }
+```
 
+```{r 201606krakow-turkuvsother, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=4, fig.width=8}
+df <- fen %>% 
+      filter(!is.na(country)) %>%
+      filter(!is.na(publication_place) & !is.na(paper.consumption.km2) & paper.consumption.km2 > -0.01)
+
+# Add indicator field: Turku or Not Turku
+myplace <- "Turku"
+
+df$myplace <- rep(NA, nrow(df))
+df$myplace[df$publication_place == myplace] <- myplace
+df$myplace[!df$publication_place == myplace & df$country == "Finland"] <- "Finland"
+df$myplace[!df$country == "Finland" & !df$publication_place == myplace] <- "Foreign"
+df$myplace <- factor(df$myplace, levels = rev(c("Foreign", "Finland", "Turku")))
+
+# Keep entries with known publication place and paper consumption
+# Group by year/decade and Turku/Other
+dfs <- df %>% group_by(publication_decade, myplace) %>%
+  summarise(titles = n(), paper = sum(paper.consumption.km2, na.rm = TRUE))
+
+p <- ggplot(dfs, aes(x = publication_decade, y = paper, fill = myplace, order = -as.numeric(myplace))) +
+     geom_bar(position = "stack", stat = "identity", color = "black") +
+     ggtitle("Paper consumption") +
+     #scale_fill_manual(values = c("blue", "black", "darkgreen")) +
+     scale_fill_grey() +
+     guides(fill = guide_legend(reverse = TRUE, title = "")) + 
+     xlab("Publication decade") + ylab("Paper (km2)")
+print(p)
+
+p <- ggplot(dfs, aes(x = publication_decade, y = titles, fill = myplace, order = -as.numeric(myplace))) +
+     geom_bar(position = "stack", stat = "identity", color = "black") +
+     ggtitle("Title count") +
+     # scale_fill_manual(values = c("blue", "black", "darkgreen")) +
+     scale_fill_grey() +
+     guides(fill = guide_legend(reverse = TRUE, title = "")) +      
+     xlab("Publication decade") + ylab("Title count (n)")
+print(p)
 ```
@@
  * [Kungliga TODO](https://github.com/rOpenGov/kungliga/blob/master/antagomir/TODO.md)
-
-```{r 201606krakow-turkuvsother, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=4, fig.width=8}
-df <- fen %>% 
-      filter(!is.na(country)) %>%
-      filter(!is.na(publication_place) & !is.na(paper.consumption.km2) & paper.consumption.km2 > -0.01)
-
-# Add indicator field: Turku or Not Turku
-myplace <- "Turku"
-
-df$myplace <- rep(NA, nrow(df))
-df$myplace[df$publication_place == myplace] <- myplace
-df$myplace[!df$publication_place == myplace & df$country == "Finland"] <- "Finland"
-df$myplace[!df$country == "Finland" & !df$publication_place == myplace] <- "Foreign"
-df$myplace <- factor(df$myplace, levels = rev(c("Foreign", "Finland", "Turku")))
-
-# Keep entries with known publication place and paper consumption
-# Group by year/decade and Turku/Other
-dfs <- df %>% group_by(publication_decade, myplace) %>%
-  summarise(titles = n(), paper = sum(paper.consumption.km2, na.rm = TRUE))
-
-p <- ggplot(dfs, aes(x = publication_decade, y = paper, fill = myplace, order = -as.numeric(myplace))) +
-     geom_bar(position = "stack", stat = "identity", color = "black") +
-     ggtitle("Paper consumption") +
-     #scale_fill_manual(values = c("blue", "black", "darkgreen")) +
-     scale_fill_grey() +
-     guides(fill = guide_legend(reverse = TRUE, title = "")) + 
-     xlab("Publication decade") + ylab("Paper (km2)")
-print(p)
-
-p <- ggplot(dfs, aes(x = publication_decade, y = titles, fill = myplace, order = -as.numeric(myplace))) +
-     geom_bar(position = "stack", stat = "identity", color = "black") +
-     ggtitle("Title count") +
-     # scale_fill_manual(values = c("blue", "black", "darkgreen")) +
-     scale_fill_grey() +
-     guides(fill = guide_legend(reverse = TRUE, title = "")) +      
-     xlab("Publication decade") + ylab("Title count (n)")
-print(p)
-```
 

### 2016-06-22 inst/examples/manuscript-krakow.Rmd
Rmd update

@@
 
-Miten Valtiopäivät vaikuttaa julkaisemiseen? Näkyykö Vapauden ajan
-valtiopäivät tässä 1719 eteenpäin? Voidaanko löytää julkaisupiikkejä
-sen mukaan milloin on valtiopäivät? Oletus on, että pitäisi näkyä
-selvästi. Myös, tuleeko uusia kustantajia kenttään?
+Riksdagar are in some cases associated with publishing peaks (see
+Figure ...). See "Vapauden ajan valtiopäivät" from 1719 onwards ?
 
@@
 
-Kirjan kehitys mediana (paperinkulutus / dokumentti, miten yli 50
-sivuiset dokumentit yleistyvät ajassa / voidaanko tässä nähdä jotain
-paikallisia eroja?)
+Kirjan kehitys mediana (miten yli 50 sivuiset dokumentit yleistyvät
+ajassa / voidaanko tässä nähdä jotain paikallisia eroja?)
 
-Kirjakokojen kehityksiä pitää analysoida myöhemmin
-tarkkaan. mielenkiintoista Kungligan osalta erityisesti että foliot
-(1to ja 2to) puuttuvat melkein kokonaan joka on eri kuvio kuin ESTC,
-lisäksi sitten 4to ja 8vo voimakas nousu 1700-luvulla on
-mielenkiintoista.
+Paper consumption in books (balls) versus pamphlets (triangles). Books are any documents with more than 50 pages. Pamphlets are anything less or equal than 50 pages. Fennica data
+
+```{r LIBER-12, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=6, fig.width=12}
+df2 <- fen
+pagelimit = 50
+df2$document.type <- rep(NA, nrow(df2))
+df2$document.type[df2$pagecount > pagelimit] <- "book"
+df2$document.type[df2$pagecount <= pagelimit] <- "pamphlet"
+df2 <- df2[which(!is.na(df2$document.type)),]
+df2$document.type <- factor(df2$document.type)
+df2 <- df2 %>% group_by(publication_decade, document.type) %>% summarize(paper.consumption.km2 = sum(paper.consumption.km2, na.rm = TRUE), n = n()) 
+p <- ggplot(df2, aes(x = publication_decade, y = paper.consumption.km2, group = document.type))
+p <- p + geom_point(aes(shape = document.type), size = 5)
+p <- p + geom_smooth(method = "loess", color = "black")
+p <- p + ggtitle("Paper consumption per document type")
+p <- p + xlab("Year")
+p <- p + ylab("Paper consumption (km2)")
+p <- p + scale_color_manual(values=c("black", "darkgray"))
+p <- p + guides(shape = "none")
+p <- p + ggtitle("Books versus pamphlets: paper consumption")
+print(p)
+```
+
+Average paper consumption per document over time:
+
+```{r LIBER-11, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=5, fig.width=9}
+theme_set(theme_bw(25))
+library(sorvi)
+df = df0
+dfs <- df %>% group_by(publication_year) %>%
+         summarize(paper.per.doc = mean(paper.consumption.km2, na.rm = T))
+p <- ggplot(dfs, aes(y = paper.per.doc, x = publication_year)) +
+       geom_line() + geom_point() +
+       xlab("Publication Year") + ylab("Paper per document")
+p <- p + ggtitle("Average paper consumption per document")
+print(p)
+```
+
+The development of book formats over time. Folios (1to ja 2to) are
+largely missing (in contrast to ESTC). Moreover, the quarto (4to) and
+octavo (8vo) increase rapidly in 1700s.
 
@@
 
-toiveissa että pystyttäisiin puhumaan julkaisijatoiminnan kehityksestä
-ikään kuin luonnollisena kehityksenä - eli yhteys luonnonilmiöiden
-kehitykseen säilyisi.
-
-Tärkein tehtävä tutkia pystytäänkö julkaisemiseen liittyvästä
-Fennica-datasta erottelemaan selkeitä trendejä suomalaisesta
-tiedontuotannosta 1640-1828, pääfokus julkaisijat.
+Pystytäänkö julkaisemiseen liittyvästä Fennica-datasta erottelemaan
+selkeitä trendejä suomalaisesta tiedontuotannosta 1640-1828, pääfokus
+julkaisijat.
 
@@
 löytäminen.
+
+Puhutaan julkaisijatoiminnan kehityksestä ikään kuin luonnollisena
+kehityksenä - eli yhteys luonnonilmiöiden kehitykseen säilyisi.
 
@@
 
-### Other points
+### Other points if the time allows
 
-Lets think these if there is time.
+TODO HR Ja tuleeko uusia kustantajia kenttään valtiopäivien myötä ?
 
@@
 
-Average paper consumption per document
-
-```{r LIBER-11, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=5, fig.width=9}
-theme_set(theme_bw(25))
-library(sorvi)
-df = df0
-dfs <- df %>% group_by(publication_year) %>%
-         summarize(paper.per.doc = mean(paper.consumption.km2, na.rm = T))
-p <- ggplot(dfs, aes(y = paper.per.doc, x = publication_year)) +
-       geom_line() + geom_point() +
-       xlab("Publication Year") + ylab("Paper per document")
-p <- p + ggtitle("Average paper consumption per document")
-print(p)
-```
-
 Title count and overall paper consumption in the top publication locations (Fennica).
@@
 
-Paper consumption in books (balls) versus pamphlets (triangles). Books are any documents with more than 32 pages. Pamphlets are anything less or equal than 32 pages. Fennica data
-
-```{r LIBER-12, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=6, fig.width=12}
-df2 <- fen
-df2$document.type <- rep(NA, nrow(df2))
-df2$document.type[df2$pagecount > 32] <- "book"
-df2$document.type[df2$pagecount <= 32] <- "pamphlet"
-df2 <- df2[which(!is.na(df2$document.type)),]
-df2$document.type <- factor(df2$document.type)
-df2 <- df2 %>% group_by(publication_decade, document.type) %>% summarize(paper.consumption.km2 = sum(paper.consumption.km2, na.rm = TRUE), n = n()) 
-p <- ggplot(df2, aes(x = publication_decade, y = paper.consumption.km2, group = document.type))
-p <- p + geom_point(aes(shape = document.type), size = 5)
-p <- p + geom_smooth(method = "loess", color = "black")
-p <- p + ggtitle("Paper consumption per document type")
-p <- p + xlab("Year")
-p <- p + ylab("Paper consumption (km2)")
-p <- p + scale_color_manual(values=c("black", "darkgray"))
-p <- p + guides(shape = "none")
-p <- p + ggtitle("Books versus pamphlets: paper consumption")
-print(p)
-```
-
 ## Session info

### 2016-06-22 inst/examples/manuscript-krakow.Rmd
Rmd update

@@
 
-Miten paperinkulutus suhtautuu dokumenttien määrään? Löydetäänkö
+TODO Miten paperinkulutus suhtautuu dokumenttien määrään? Löydetäänkö
 ajankohtia jolloin on poikkeuksellista kasvua / laskua
@@
 
-Kirjan kehitys mediana (miten yli 50 sivuiset dokumentit yleistyvät
-ajassa / voidaanko tässä nähdä jotain paikallisia eroja?)
+How over 50 page documents are spreading in time. Paper consumption in
+books (over 50 pages; balls) versus other documents (less or equal
+than 50 pages; triangles). TODO: voidaanko tässä nähdä paikallisia
+eroja ?
 
-Paper consumption in books (balls) versus pamphlets (triangles). Books are any documents with more than 50 pages. Pamphlets are anything less or equal than 50 pages. Fennica data
-
-```{r LIBER-12, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=6, fig.width=12}
-df2 <- fen
+```{r bookmedia1, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=7, fig.show="hold", out.width="430px"}
+for (catal in unique(df0$catalog)) {
+  df2 <- subset(df0, catalog = catal)
   pagelimit = 50
@@
   p <- p + scale_color_manual(values=c("black", "darkgray"))
-p <- p + guides(shape = "none")
-p <- p + ggtitle("Books versus pamphlets: paper consumption")
+  # p <- p + guides(shape = "none") 
+  p <- p + ggtitle(catal)
   print(p)
+}
 ```

### 2016-06-22 inst/examples/manuscript-krakow.Rmd
ok

@@
 
-TODO Miten paperinkulutus suhtautuu dokumenttien määrään? Löydetäänkö
-ajankohtia jolloin on poikkeuksellista kasvua / laskua
-tms. Esim. top-10 julkaisupaikat.
+Paper consumption per document in the top publication places. Note
+that paper consumption estimates have still problems so take this with
+reservations. Are there time periods with remarkable changes in paper
+consumption per document (meaning that small or large volumes suddenly
+become more frequent) ?
 
-How over 50 page documents are spreading in time. Paper consumption in
-books (over 50 pages; balls) versus other documents (less or equal
-than 50 pages; triangles). TODO: voidaanko tässä nähdä paikallisia
-eroja ?
+```{r bookmedia2, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=7, fig.show="hold", out.width="430px"}
+for (catal in unique(df0$catalog)) {
+  df <- subset(df0, catalog = catal)
+  theme_set(theme_bw(20))
+  top <- names(top(df, "publication_place", 10))
+
+  dfs <- df %>% filter(publication_place %in% top) %>% group_by(publication_decade, publication_place, country) %>% summarize(n = n(), paper = sum(paper.consumption.km2, na.rm = T))  %>% mutate(paper.per.document = paper/n)
+
+  p <- ggplot(dfs, aes(x = publication_decade, y = paper.per.document)) +
+       geom_point(aes(color = publication_place, shape = publication_place)) +
+       geom_line(aes(color = publication_place, linetype = publication_place)) +
+       xlab("Title Count") + 
+       ggtitle(paste("Paper consumption per document\n", catal)) +
+       scale_y_log10() 
+  #p <- p + geom_text(aes(label = publication_place), size = 5)
+  #p <- p + xlab("Title Count") + ylab("Paper consumption (km2)")
+  #p <- p + scale_color_manual(values = c("darkgray", "black"))
+  #p <- p + guides(color = "none")
+  print(p)	 
+}
+```
+
+Overview on how over 50 page documents spread in time. Paper
+consumption in books (over 50 pages; balls) versus other documents
+(less or equal than 50 pages; triangles). TODO: voidaanko tässä nähdä
+paikallisia eroja ?
 
@@
 
-Gatherings vs. pagecounts per country (Fennica)
-
-```{r LIBER-docsizecomp3, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=10}
-selected.countries = c("Finland", "Sweden")
-dfs <- fen %>% select(pagecount, gatherings, country) %>% filter(country %in% selected.countries) %>% group_by(pagecount, gatherings, country) %>% tally()
-p <- ggplot(dfs, aes(x = pagecount, y = gatherings, size = n)) +
-     geom_point() + facet_grid(country ~ .) + scale_x_log10()
-print(p)
-```
-
-Title count and overall paper consumption in the top publication locations (Fennica).
-The current country of origin is indicated.
-Finland is highlighted.
-Note that paper consumption estimates have still problems.
-
-```{r LIBER-8, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=6, fig.width=8}
-df <- fen
-theme_set(theme_bw(20))
-top <- names(rev(sort(table(df$publication_place))))[1:50]
-dfs <- df %>% filter(publication_place %in% top) %>% group_by(publication_place) %>% summarize(titles = n(), paper = sum(paper.consumption.km2, na.rm = T))
-dfs$country <- get_country(dfs$publication_place)
-dfs$finland <- dfs$country == "Finland"
-p <- ggplot(dfs, aes(x = titles, y = paper))
-p <- p + geom_text(aes(label = publication_place, color = finland), size = 5)
-p <- p + xlab("Title Count") + ylab("Paper consumption (km2)")
-p <- p + scale_color_manual(values = c("darkgray", "black"))
-p <- p + guides(color = "none")
-p <- p + scale_x_log10() + scale_y_log10() 
-p <- p + ggtitle("Title count versus paper (places)")
-print(p)	 
-```
-
 ## Session info

### 2016-06-22 inst/examples/manuscript-krakow.Rmd
Rmd update

@@
 ```{r bookmedia2, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=7, fig.show="hold", out.width="430px"}
-for (catal in unique(df0$catalog)) {
-  df <- subset(df0, catalog = catal)
+for (catal in as.character(unique(df0$catalog))) {
+  df <- subset(df0, catalog == catal)
   theme_set(theme_bw(20))
@@
 
-```{r 201606krakow-fennica-topfemale, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=5, fig.width=15, out.width="850px"}
+```{r 201606krakow-fennica-topfemale, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=5, fig.width=20, out.width="850px"}
 theme_set(theme_bw(10))

### 2016-06-22 inst/examples/manuscript-krakow.Rmd
Rmd update

@@
 for (catal in unique(df0$catalog)) {
-  df2 <- subset(df0, catalog = catal)
+  df2 <- subset(df0, catalog == catal)
   pagelimit = 50

### 2016-06-22 inst/examples/manuscript-krakow.Rmd
Rmd update

@@
 
-```{r LIBER-11, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=5, fig.width=9}
+```{r LIBER-11, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=5, fig.width=9, out.width="430px"}
 theme_set(theme_bw(25))
 library(sorvi)
-df = df0
-dfs <- df %>% group_by(publication_year) %>%
+dfs <- df0 %>% group_by(publication_decade) %>%
          summarize(paper.per.doc = mean(paper.consumption.km2, na.rm = T))
-p <- ggplot(dfs, aes(y = paper.per.doc, x = publication_year)) +
-       geom_line() + geom_point() +
-       xlab("Publication Year") + ylab("Paper per document")
-p <- p + ggtitle("Average paper consumption per document")
+p <- ggplot(dfs, aes(y = paper.per.doc, x = publication_decade)) +
+       geom_point() + geom_smooth(col = "black") +
+       xlab("Publication year") + ylab("Paper per document") +
+       ggtitle("Average paper consumption per document")
 print(p)

### 2016-06-22 inst/examples/manuscript-krakow.Rmd
Rmd update

--- 2016-06-22 inst/examples/manuscript-krakow.Rmd
@@
 
-```{r LIBER-11, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=5, fig.width=9}
+```{r LIBER-11, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=5, fig.width=8, out.width="600px"}
 theme_set(theme_bw(25))
 library(sorvi)
-df = df0
-dfs <- df %>% group_by(publication_year) %>%
+dfs <- df0 %>% group_by(publication_decade) %>%
          summarize(paper.per.doc = mean(paper.consumption.km2, na.rm = T))
-p <- ggplot(dfs, aes(y = paper.per.doc, x = publication_year)) +
-       geom_line() + geom_point() +
-       xlab("Publication Year") + ylab("Paper per document")
-p <- p + ggtitle("Average paper consumption per document")
+p <- ggplot(dfs, aes(y = paper.per.doc, x = publication_decade)) +
+       geom_point() + geom_smooth(col = "black") +
+       xlab("Publication year") + ylab("Paper per document") +
+       ggtitle("Average paper consumption per document")
 print(p)

### 2016-06-22 inst/examples/manuscript-krakow.Rmd
Rmd update

--- 2016-06-22 inst/examples/manuscript-krakow.Rmd
@@
 
-```{r LIBER-11, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=5, fig.width=9}
+```{r LIBER-11, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=5, fig.width=8, out.width="600px"}
 theme_set(theme_bw(25))
 library(sorvi)
-df = df0
-dfs <- df %>% group_by(publication_year) %>%
+dfs <- df0 %>% group_by(publication_decade) %>%
          summarize(paper.per.doc = mean(paper.consumption.km2, na.rm = T))
-p <- ggplot(dfs, aes(y = paper.per.doc, x = publication_year)) +
-       geom_line() + geom_point() +
-       xlab("Publication Year") + ylab("Paper per document")
-p <- p + ggtitle("Average paper consumption per document")
+p <- ggplot(dfs, aes(y = paper.per.doc, x = publication_decade)) +
+       geom_point() + geom_smooth(method = "loess", size = 1, color = "black") +
+       xlab("Publication year") + ylab("Paper per document") +
+       ggtitle("Average paper consumption per document")
 print(p)

### 2016-06-22 inst/examples/manuscript-krakow.Rmd
Rmd update

@@
 
-```{r 201606krakow-turkuvsother, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=4, fig.width=8}
+```{r 201606krakow-turkuvsother, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=7, fig.width=9, fig.show="hold", out.width="430px"}
 df <- fen %>% 

### 2016-06-22 inst/examples/manuscript-krakow.Rmd
Rmd update

--- 2016-06-22 inst/examples/manuscript-krakow.Rmd
@@
 
-```{r 201606krakow-turkuvsother, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=4, fig.width=8}
+```{r 201606krakow-turkuvsother, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=7, fig.width=10, fig.show="hold", out.width="430px"}
 df <- fen %>% 

### 2016-06-22 inst/examples/manuscript-krakow.Rmd
Rmd update

@@
 
+Paper consumption in selected places (Fennica):
+
 ```{r 201606krakow-turkuvsother, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=7, fig.width=10, fig.show="hold", out.width="430px"}
@@
 
-## Materials and Methods
+Library catalogues contain rich metadata on...
 
-Library catalogs contain rich metadata on...
-
-Here we analyse Fennica & Kungliga..
+Here we have analysed Fennica & Kungliga..
 
@@
 
+## Materials and Methods
+
+We obtained Fennica and Kungliga library catalogues from..
+
+After initial preprocessing, we had `r nrow(subset(df0, catalog == "Fennica"))` and `r nrow(subset(df0, catalog == "Kungliga"))` documents in Fennica and Kungliga, respectively between the years `r min(df0$publication_year)`-`r max(df0$publication_year)`.
+
 We have prepared open data analytical ecosystem for in-depth analysis of such data collections ([Lahti, Ilomaki, Tolonen (2015)](http://doi.org/10.18352/lq.10112)).
+In summary, the data analytical ecosystem does ..
+Reading, parsing, cleaning up, enriching, summarizing, analysis, visualization, figures and tables..
+[SUMMARY FIGURE OF THE PROCESS?].
+Full source code to reproduce these analyses are available via Github ([Fennica](https://github.com/rOpenGov/fennica/); [Kungliga](https://github.com/rOpenGov/kungliga/)).
 
-In summary, the data analytical ecosystem does ..
+A brief summary of the data processing steps:
 
-Reading, parsing, cleaning up, enriching, summarizing, analysis, visualization, figures and tables..
+**Author names**
 
-Full source code to reproduce these analyses are available via Github ([Fennica](https://github.com/rOpenGov/fennica/); [Kungliga](https://github.com/rOpenGov/kungliga/)).
+**Author life years**
+
+**Publication place**
+
+**Publishers**
+
+**Dissertations**
+
+**Duplicate removal** Combining the catalogs ..
+
+**Enriching** to add gender, country, geocoordinates ..
 

### 2016-06-22 inst/examples/manuscript-krakow.Rmd
Rmd update

@@
 kun <- readRDS("../../../kungliga/antagomir/df.Rds")
+
+fenraw <- readRDS("df.raw.Rds")
+kunraw <- readRDS("../../../kungliga/antagomir/df.raw.Rds")
 
@@
 
-After initial preprocessing, we had `r nrow(subset(df0, catalog == "Fennica"))` and `r nrow(subset(df0, catalog == "Kungliga"))` documents in Fennica and Kungliga, respectively between the years `r min(df0$publication_year)`-`r max(df0$publication_year)`.
+The raw data contains metadata `r nrow(fenraw)` and `r nrow(kunraw)` documents in Fennica and Kungliga, respectively.
+After initial preprocessing and limiting the analysis between the years `r min(df0$publication_year)`-`r max(df0$publication_year)`, we had `r nrow(subset(df0, catalog == "Fennica"))` and `r nrow(subset(df0, catalog == "Kungliga"))` documents for Fennica and Kungliga, respectively.
 

### 2016-06-22 inst/examples/manuscript-krakow.Rmd
Rmd update

@@
 The raw data contains metadata `r nrow(fenraw)` and `r nrow(kunraw)` documents in Fennica and Kungliga, respectively.
-After initial preprocessing and limiting the analysis between the years `r min(df0$publication_year)`-`r max(df0$publication_year)`, we had `r nrow(subset(df0, catalog == "Fennica"))` and `r nrow(subset(df0, catalog == "Kungliga"))` documents for Fennica and Kungliga, respectively.
+We limited the present analysis in the time interval `r min(df0$publication_year)`-`r max(df0$publication_year)`, yielding a subset of `r nrow(subset(df0, catalog == "Fennica"))` (`r round(100*nrow(subset(df0, catalog == "Fennica"))/nrow(fenraw), 1)`) and `r nrow(subset(df0, catalog == "Kungliga"))` (`r round(100*nrow(subset(df0, catalog == "Fennica"))/nrow(fenraw), 1)`) documents for Fennica and Kungliga, respectively.
 

### 2016-06-22 inst/examples/manuscript-krakow.Rmd
Rmd update

--- 2016-06-22 inst/examples/manuscript-krakow.Rmd
@@
 The raw data contains metadata `r nrow(fenraw)` and `r nrow(kunraw)` documents in Fennica and Kungliga, respectively.
-After initial preprocessing and limiting the analysis between the years `r min(df0$publication_year)`-`r max(df0$publication_year)`, we had `r nrow(subset(df0, catalog == "Fennica"))` and `r nrow(subset(df0, catalog == "Kungliga"))` documents for Fennica and Kungliga, respectively.
+We limited the present analysis in the time interval `r min(df0$publication_year)`-`r max(df0$publication_year)`, yielding a subset of `r nrow(subset(df0, catalog == "Fennica"))` (`r round(100*nrow(subset(df0, catalog == "Fennica"))/nrow(fenraw), 1)`%) and `r nrow(subset(df0, catalog == "Kungliga"))` (`r round(100*nrow(subset(df0, catalog == "Kunliga"))/nrow(kunraw), 1)`%) documents for Fennica and Kungliga, respectively.
 

### 2016-06-22 inst/examples/manuscript-krakow.Rmd
Rmd update

@@
 #opts_chunk$set(fig.width=4, fig.height=3, par=TRUE, out.width='2in', fig.pos='H')
-#knitr::opts_chunk$set(fig.path = "figure_201606_Krakow/", dev="CairoPNG")
-knitr::opts_chunk$set(fig.path = "figure_201606_Krakow/")
+knitr::opts_chunk$set(fig.path = "figure_201606_Krakow/", dev="CairoPNG")
+#knitr::opts_chunk$set(fig.path = "figure_201606_Krakow/")
 ```

### 2016-06-22 inst/examples/manuscript-krakow.Rmd
Rmd update

@@
 
-Erityisesti:
-
-Riksdag Stockholm 20 januari 1719 1 juni 1719
-
-Riksdag Stockholm 14 maj 1734 14 december 1734
-
-Riksdag Stockholm 21 februari 1765 21 oktober 1766
-
-Riksdag Norrköping & Stockholm 22 april 1769 5 februari 1770
-
-Riksdag Stockholm 19 juni 1771 12 september 1772
-
-Riksdag Gävle 26 januari 1792 24 februari 1792
-
---> tapahtuuko Gävlessä selvää nousua julkaisemisessa.
+In particular: Riksdag Stockholm 20 januari 1719 1 juni 1719; Stockholm 14 maj 1734 14 december 1734; Stockholm 21 februari 1765 21 oktober 1766; Norrköping & Stockholm 22 april 1769 5 februari 1770; Stockholm 19 juni 1771 12 september 1772; Gävle 26 januari 1792 24 februari 1792.
 
@@
 
-```{r valtiopaivat-total, echo=FALSE, warning=FALSE, fig.width=11, fig.height=4}
+```{r riksdar1, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=7, fig.show="hold", out.width="430px"}
+for (catal in as.character(unique(df0$catalog))) {
+
   # Use timeinterval year intervals
-dfsel = df0
+  dfsel = subset(df0, catalog == catal)
   #dfsel = subset(df0, publication_place == "Stockholm")
@@
   p <- p + xlab("Year")
-p <- p + ggtitle("Riksdagar - overall titlecount (Fen + Kun)")
+  p <- p + ggtitle(catal)
   print(p)
+}
 ```
 
-```{r valtiopaivat-gavle, echo=FALSE, warning=FALSE, fig.width=11, fig.height=4}
+Focus on Gävle (gray) during riksdagar. Gävle has `r sum("Gävle" %in% fen$publication_place)` occurrences in Fennica, hence not included here. The figure on Gävle is based on Kungliga.
+
+```{r riksdar2, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=7, out.width="430px"}
+
   # Use timeinterval year intervals
   myplace = "Gävle" # Norrköping / Stockholm
-dfsel = subset(df0, publication_place == myplace)
   minyear = 1700
   maxyear = 1800
+  catal = "Kungliga"
 
-df <- subset(dfsel, publication_year >= minyear & publication_year < maxyear)
+  df = subset(df0, publication_place == myplace & catalog == catal)
+  df <- subset(df, publication_year >= minyear & publication_year < maxyear)
 
@@
     xmax = rect_left[-1],
-    #xmin = min(dfsel$publication_year),
-    #xmax = max(dfsel$publication_year),    
     ymin = ymin,
@@
   rectangles$shade <- rep(c("White", "Highlight"), length = nrow(rectangles))
-  #rectangles$shade <- rep(c("White", "Highlight"), length = nrow(rectangles))
 
@@
   p <- p + geom_rect(data = rectangles, 
-	   aes(xmin=xmin, xmax=xmax, ymin=ymin, ymax=ymax, fill=shade), alpha=0.8) + 
+	   aes(xmin=xmin, xmax=xmax,
+	       ymin=ymin, ymax=ymax,
+	       fill=shade), alpha=0.8) + 
          scale_fill_manual(values = cols) # + guides(fill = "none") 
@@
   p <- p + geom_point(data = dfm, aes(x = date, y = Documents), col = "black")
-p <- p + scale_x_continuous(breaks=seq(minyear, maxyear, 20))
+  p <- p + scale_x_continuous(breaks = seq(minyear, maxyear, 20))
   p <- p + ggtitle("Publishing activity")
@@
   p <- p + xlab("Year")
-p <- p + ggtitle(paste("Riksdagar - titlecount in ", myplace, sep = ""))
+  p <- p + ggtitle(paste(myplace, " (", catal, ")", sep = ""))
   print(p)

### 2016-06-22 inst/examples/manuscript-krakow.Rmd
ok
Rmd update

@@
 
-```{r riksdar1, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=7, fig.show="hold", out.width="430px"}
+```{r riksdar1, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=6, fig.show="hold", out.width="430px"}
 for (catal in as.character(unique(df0$catalog))) {
@@
     )
-  rectangles$shade <- rep(c("White", "Highlight"), length = nrow(rectangles))
-  #rectangles$shade <- rep(c("White", "Highlight"), length = nrow(rectangles))
+  rectangles$shade <- rep(c("", "Highlight"), length = nrow(rectangles))
 

### 2016-06-22 inst/examples/manuscript-krakow.Rmd
Rmd update

@@
 
-**Valtiopäivät**
+### Effects of historical events
 
-Riksdagar are in some cases associated with publishing peaks (see
+**Riksdagar** are in some cases associated with publishing peaks (see
 Figure ...). See "Vapauden ajan valtiopäivät" from 1719 onwards ?
@@
 The publishing of historical works in .. on a timeline highlighting the eras of the riksdagar (16..-16..)..
+
+**Painovapaus**, 1766, räjähtääkö / kasvaako julkaiseminen merkittävästi
+ja miten tämä näkyy Tukholma vs. muu valtakunta (ml. Turku)?
+Painovapaus on 1766-1772, miten tämä näkyy ?
 
@@
 
+### Book printing in Finland
+
+mitä voidaan sanoa suomalaisesta kirjatuotannosta ylipäänsä sekä
+löydetäänkö sieltä mitään mielenkiintoisia kehityskulkuja ylipäänsä
+vai pelkästään toteamus, että suomalainen tiedontuotanto oli hyvin
+vähäistä tarkastellulla ajanjaksolla.
+
 ### Book as media: development over time
@@
 
-```{r LIBER-11, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=5, fig.width=8, out.width="600px"}
+```{r LIBER-11, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=8, fig.width=12, out.width="600px"}
 theme_set(theme_bw(25))
@@
 
-### Publisher analysis (HR)
+### Publisher analysis
+
+Puhutaan julkaisijatoiminnan kehityksestä ikään kuin luonnollisena
+kehityksenä - eli yhteys luonnonilmiöiden kehitykseen säilyisi.
 
@@
 selkeitä trendejä suomalaisesta tiedontuotannosta 1640-1828, pääfokus
-julkaisijat.
+julkaisijat: Miten uusia julkaisijoita tulee julkaisijakenttään
+Suomessa ja katoaa. Pääpaino erityisesti sillä kun julkaisijakartalle
+tulee uusia toimijoita! [TÄHÄN VOISI MIETTIÄ KARTTAKUVIEN SARJAA TAI
+STACKED BARPLOTTIA JONKA DIVERSITEETTI KASVAA]
 
-Miten uusia julkaisijoita tulee julkaisijakenttään Suomessa ja
-katoaa. Pääpaino erityisesti sillä kun julkaisijakartalle tulee uusia
-toimijoita! Toimijoita voisi myös yrittää luokitella suhteellisesti
-(“iso”, “keskikokoinen”, “pieni”) liittyen vuosittaiseen
-julkaisuvoluumiin jota mitataan niin julkaisujen määrän kuin myös
-paperinkulutusvoluumin suhteen. Vertailua suurimpien julkaisijoiden
-kesken.
+Toimijoita voisi myös yrittää luokitella suhteellisesti (“iso”,
+“keskikokoinen”, “pieni”) liittyen vuosittaiseen julkaisuvoluumiin
+jota mitataan niin julkaisujen määrän kuin myös paperinkulutusvoluumin
+suhteen. Vertailua suurimpien julkaisijoiden kesken.
 
@@
 julkaisutoiminnan leviäminen ja kasvu ajassa eri
-paikkakunnilla. Paperinkulutus voi osoittautua hyväksi työvälineeksi erityisesti kun
-tiedetään, että toiset isot julkaisijat julkaisivat esim. jotain
-asetuskokoelmia yksittäin ja toiset taas ryppäinä. Eli julkaisijoiden
-sisällä erottelua eri tyyppisten julkaisujen suhteen pitää tehdä.
+paikkakunnilla. Paperinkulutus voi osoittautua hyväksi työvälineeksi
+erityisesti kun tiedetään, että toiset isot julkaisijat julkaisivat
+esim. jotain asetuskokoelmia yksittäin ja toiset taas ryppäinä. Eli
+julkaisijoiden sisällä erottelua eri tyyppisten julkaisujen suhteen
+pitää tehdä.
 
-Lisäksi kiinnostaa mitä voidaan sanoa suomalaisesta kirjatuotannosta
-ylipäänsä sekä löydetäänkö sieltä mitään mielenkiintoisia
-kehityskulkuja ylipäänsä vai pelkästään toteamus, että suomalainen
-tiedontuotanto oli hyvin vähäistä tarkastellulla ajanjaksolla.
+Julkaisijoista tehtävä verkostoanalyysi. keskeisimmät “nodet” siihen
+miten julkaisijakenttä muuttuu ajassa. Julkaisijoita voisi myös
+yrittää luokitella eniten käytettyjen asiasanojen mukaan. Näiden
+perusteella voidaan varmaankin erotella yliopistojulkaiseminen,
+asiakirja/asetusjulkaiseminen ja kirjajulkaiseminen. Tämän jälkeen
+auktorit, valtioasiakirjat, yliopistodokumentit, kirjat ja muut
+julkaisut kategoroina joiden ympärille verkostoanalyysi voisi syntyä
+(valtionasiakirjojen ja yliopisto-aineiston luokittelu voisi yhdistää
+myös asiasanojen ja otsikoiden analyysia). [OK monenlaista voidaan
+tehdä, onko tämä asiasanajuttu nyt tärkeä vai vähemmän tärkeä
+prioriteetti?]
 
-Julkaisijoista tehtävä verkostoanalyysi on sitten toinen keskeinen
-tavoite. Löydetään keskeisimmät “nodet” siihen miten julkaisijakenttä
-muuttuu ajassa. Julkaisijoita voisi myös yrittää luokitella eniten
-käytettyjen asiasanojen mukaan. Näiden perusteella voidaan varmaankin
-erotella yliopistojulkaiseminen, asiakirja/asetusjulkaiseminen ja
-kirjajulkaiseminen. Tämän jälkeen auktorit, valtioasiakirjat,
-yliopistodokumentit, kirjat ja muut julkaisut kategoroina joiden
-ympärille verkostoanalyysi voisi syntyä (valtionasiakirjojen ja
-yliopisto-aineiston luokittelu voisi yhdistää myös asiasanojen ja
-otsikoiden analyysia).
+### University publishing
 
-Turku vs. muu Suomi (sillä kytköksellä että kun Kungliga aineisto
-tulee mukaan analyysiin, niin Turku osana ruotsalaista
-yliopistojärjestelmää (ml. Tarto) muuttuu tärkeäksi). Eli Turun
-erityistapaus analysoidaan tarkkaan, kuinka paljon yliopistoon
-liittyvää julkaisutoimintaa, kuinka paljon julkaisijoita, miten
-julkaisijoiden verkosto muodostuu Turussa; miten eri julkaisijoita
-Turussa voitaisiin luokitella (julkaiseeko joku paperinkulutukseltaan
-vain pieniä dokumentteja, julkaiseeko joku painotalo huomattavasti
-enemmän kuin toiset), tarkoituksena yleisten historiallisten trendien
-löytäminen.
-
-Puhutaan julkaisijatoiminnan kehityksestä ikään kuin luonnollisena
-kehityksenä - eli yhteys luonnonilmiöiden kehitykseen säilyisi.
-
-### University analysis (HR)
-
-Tekee yliopistopuolta Fennica-Kungliga. Samalla voisi tehdä Fennicaa
-yleisesti. Eli keskittyä julkaisijoihin ja uusien julkaisijoiden
-analyysiin.
-
-- yliopistojulkaisuista mahd. pian yleiset tilastolliset näkymät ja
+Yliopistojulkaisuista mahd. pian yleiset tilastolliset näkymät ja
 voidaan sitten arvioida onko joku mahdollisesti pahastikin vielä
@@
 aineistoissa.
-
-Subject topics: pientä analyysia. Ainakin yliopisto-väitöskirjoihin liittyen.
-
-keskittyy erityisesti kaikkiin väitöskirja-kategorian alla liikkuviin
-yliopistotuotoksiin. Tätä kautta päästään hyvin kiinni Turku, Upsala,
-Lund, Tarto yms. vertailuihin. Siitä sitten kuljetaan kohti Turun
-suhdetta muuhun Suomeen ja katso kääntyy erityisesti julkaisijoihin
-(samaten toki myös noiden yliopistokaupunkien osalla, jossa myös
-tehdään sitten vertailua akateeminen vs. hallinnollinen vs. muu
-julkaisutoiminta).
-
-analyysi mitä julkaisukentällä tapahtuu eri paikoissa kun uusia
-julkaisijoita tulee kartalle (meneekö esim. jossain toisessa
-yliopistossa tuotanto suhteessa alas kun matkan varrella tulee uusia
-yliopistoja vai ei) jne.
 
@@
 
-Yliopistojen ilmestyminen ruotsinvaltakunnassahan on:
+analyysi mitä julkaisukentällä tapahtuu eri paikoissa kun uusia
+julkaisijoita tulee kartalle (meneekö esim. jossain toisessa
+yliopistossa tuotanto suhteessa alas kun matkan varrella tulee uusia
+yliopistoja vai ei) jne.
+
+Yliopistojen ilmestyminen ruotsinvaltakunnassahan on (ks. aikajanat):
 
@@
 
-Lisäksi kieli [Fennica](https://github.com/rOpenGov/fennica/blob/master/inst/examples/language.md) ja [Kungliga](https://github.com/rOpenGov/kungliga/blob/master/antagomir/language.md), milloin alkaa erityisesti tulemaan ruotsinkielellä väitöksiä eri paikoissa on mielenkiintoinen kysymys.
-tuleeko jostain
-yliopistosta erityisesti ruotsinkielistä materiaalia 1700-luvulla.
-Näissä pitää erityisesti analysoida niitä väitöskirjoja sekä niissä
-tapahtuvia muutoksia.
+Tätä kautta päästään hyvin kiinni Turku, Upsala,
+Lund, Tarto yms. vertailuihin. Siitä sitten kuljetaan kohti Turun
+suhdetta muuhun Suomeen ja katso kääntyy erityisesti julkaisijoihin
+(samaten toki myös noiden yliopistokaupunkien osalla, jossa myös
+tehdään sitten vertailua akateeminen vs. hallinnollinen vs. muu
+julkaisutoiminta).
+
+**Dissertation language** milloin alkaa erityisesti tulemaan ruotsinkielellä väitöksiä eri paikoissa on mielenkiintoinen kysymys. tuleeko jostain yliopistosta
+erityisesti ruotsinkielistä materiaalia 1700-luvulla.  pitää
+erityisesti analysoida niitä väitöskirjoja sekä niissä tapahtuvia
+muutoksia. See [Fennica](https://github.com/rOpenGov/fennica/blob/master/inst/examples/language.md) and [Kungliga](https://github.com/rOpenGov/kungliga/blob/master/antagomir/language.md),
+
+### Case of Turku
 
 Turun akateemisen julkaisemisen vertautuminen muihin ruotsalaisen
-yliopistojärjestelmän kaupunkeihin. Lukumäärävertailut aikajanalla ja
-ne akateemisten julkaisujen blokkaaminenhan ei pitäisi olla kovinkaan
-hankalaa. Tämä saattaisi hyvin riittää siitä Kungligan
-käytöstä. Samalla vertailukohtia CERListä tai sitten ehkä ESTCstä
-pitää ottaa Fennicalle että pystytään suhteuttamaan mistä puhutaan.
+yliopistojärjestelmän kaupunkeihin: Lukumäärävertailut
+aikajanalla. Akateemisten julkaisujen blokkaaminenhan ei pitäisi olla
+kovinkaan hankalaa [väitöskirjat, mitä muuta tähän siis?].
 
-Painovapaus, 1766, räjähtääkö / kasvaako julkaiseminen merkittävästi
-ja miten tämä näkyy Tukholma vs. muu valtakunta (ml. Turku)?
-Painovapaus on 1766-1772, miten tämä näkyy Kungligassa ja Fennicassa?
+Turku vs. muu Suomi: Turku osana ruotsalaista yliopistojärjestelmää
+(ml. Tarto) muuttuu tärkeäksi).
+
+Kuinka paljon yliopistoon liittyvää julkaisutoimintaa
+
+Kuinka paljon julkaisijoita
+
+Miten julkaisijoiden verkosto muodostuu Turussa
+
+Miten eri julkaisijoita Turussa voitaisiin luokitella (julkaiseeko
+joku paperinkulutukseltaan vain pieniä dokumentteja, julkaiseeko joku
+painotalo huomattavasti enemmän kuin toiset).
 
@@
 
-TODO HR Ja tuleeko uusia kustantajia kenttään valtiopäivien myötä ?
+Vertailukohtia CERListä tai sitten ehkä ESTCstä pitää ottaa Fennicalle
+että pystytään suhteuttamaan mistä puhutaan [verratkaa vaikka aiempiin
+julkaisuihin, ei sotketa enempää katalogeja nyt tähän soppaan ?]
+
+Ks myös Subject topics ainakin yliopisto-väitöskirjoihin liittyen.
+
+tuleeko uusia kustantajia kenttään valtiopäivien myötä ?
 

### 2016-06-22 inst/examples/manuscript-krakow.Rmd
Rmd update

@@
     )
-  rectangles$shade <- rep(c("", "Highlight"), length = nrow(rectangles))
+  rectangles$shade <- rep(c("White", "Highlight"), length = nrow(rectangles))
 

### 2016-06-23 inst/examples/manuscript-krakow.Rmd
Rmd update
ok

@@
 Cities are to this effect seen as partly supplementing, partly competing intellectual centres.
+
+TODO: try to check duplicates. Clustering with identical place, identical year, near identical title and then print table with potential duplicates for manual checks.
+
+TODO: why Fennica has huge drop in 1700s
+
+TODO: yksittäiset kuvat eri kaupungeista julkaisumääristä auttaisivat paljon yleistä miettimistä ja nämä olisi varmaan helppo generoida.
+Eli onko mahdollista tehdä kuvat kaupungeittain (eli samalla tavalla kun on jo Gävle):
+
+Kungliga:
+
+Tartu, Skara, Växjö, Uppsala, Lund, Strängnäs, Linköping, Gothenburg, Västerås, Nyköping
+
+Ja lisäksi sitten muu kuin Suomi tai Ruotsi julkaisumaana.
 

### 2016-06-23 inst/examples/manuscript-krakow.Rmd
Rmd update

--- 2016-06-22 inst/examples/manuscript-krakow.Rmd
@@
 Cities are to this effect seen as partly supplementing, partly competing intellectual centres.
+
+TODO: try check duplicates. Clustering with identical place, identical year, near identical title and then print table with potential duplicates for manual checks.
+
+TODO: why Fennica has huge drop in 1700s
 
@@
   print(p)
+```
 
+TODO: yksittäiset kuvat eri kaupungeista julkaisumääristä auttaisivat yleistä miettimistä. onko mahdollista tehdä kuvat kaupungeittain (eli samalla tavalla kun on jo Gävle):
+
+Kungliga:
+
+Ja lisäksi sitten muu kuin Suomi tai Ruotsi julkaisumaana.
+
+```{r selectedplaces, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=8, out.width="280px"}
+selected.places = c("Tartu", "Skara", "Växjö", "Uppsala", "Lund", "Strängnäs", "Linköping", "Gothenburg", "Västerås", "Nyköping", "Norrköping", "Stockholm", "Turku")
+for (myplace in selected.places) {
+  # Use timeinterval year intervals
+  catal = "Kungliga"
+  #minyear = 1470
+  #maxyear = 1800
+  minyear = min(na.omit(df0$publication_year))
+  maxyear = max(na.omit(df0$publication_year))
+
+  df = subset(df0, publication_place == myplace & catalog == catal)
+  df <- subset(df, publication_year >= minyear & publication_year < maxyear)
+
+  timeinterval <- 5
+  df$timeunit <- round(df$publication_year/timeinterval)*timeinterval
+
+  df$unity = rep(1, nrow(df))
+  publications <- tapply(df$unity, list(df$timeunit), sum)
+
+  publications[is.na(publications)] <- 0 # Set NAs to 0
+  publications <- publications/timeinterval # Instead of decadal sum, use average annual output 
+  dfm <- melt(publications) 
+  names(dfm) <- c("Time", "Documents")
+  dfm <- transform(dfm, date = as.numeric(as.character(Time)))
+
+  # Draw Figure
+  theme_set(theme_bw(20))
+  p <- ggplot(data = dfm, aes(x = date, y = Documents))
+  p <- p + geom_line(col = "black")
+  p <- p + geom_smooth(col = "black")  
+  p <- p + geom_point(col = "black", size = 3)
+  p <- p + scale_x_continuous(breaks = seq(minyear, maxyear, 20), limits = c(minyear, maxyear))
+  p <- p + ggtitle("Publishing activity")
+  p <- p + ylab("Documents / Year")
+  p <- p + xlab("Year")
+  p <- p + ggtitle(paste(myplace, " (", catal, ")", sep = ""))
+  print(p)
+}
 ```

### 2016-06-23 inst/examples/manuscript-krakow.Rmd
Rmd update

@@
 
-TODO: yksittäiset kuvat eri kaupungeista julkaisumääristä auttaisivat yleistä miettimistä. onko mahdollista tehdä kuvat kaupungeittain (eli samalla tavalla kun on jo Gävle):
-
-Kungliga:
+Title counts in selected places.
 
@@
 
-```{r selectedplaces, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=8, out.width="280px"}
+```{r selectedplaces, echo=FALSE, message=FALSE, warning=FALSE, fig.width=9, fig.height=6, out.width="280px"}
 selected.places = c("Tartu", "Skara", "Växjö", "Uppsala", "Lund", "Strängnäs", "Linköping", "Gothenburg", "Västerås", "Nyköping", "Norrköping", "Stockholm", "Turku")
@@
   catal = "Kungliga"
-  #minyear = 1470
+  minyear = 1500
   #maxyear = 1800
-  minyear = min(na.omit(df0$publication_year))
-  maxyear = max(na.omit(df0$publication_year))
+  #minyear = min(na.omit(df0$publication_year))
+  #maxyear = max(na.omit(df0$publication_year))
 

### 2016-06-23 inst/examples/manuscript-krakow.Rmd
Rmd update

@@
 
-Title counts in selected places.
-
-Ja lisäksi sitten muu kuin Suomi tai Ruotsi julkaisumaana.
+Title counts in selected places in the Kungliga catalogue.
 
@@
 }
+```
+
+Kungliga publications outside Sweden and Finland.
+
+```{r selectedplaces2, echo=FALSE, message=FALSE, warning=FALSE, fig.width=9, fig.height=6, out.width="0px"}
+
+  # Use timeinterval year intervals
+  catal = "Kungliga"
+  minyear = 1500
+  #maxyear = 1800
+  #minyear = min(na.omit(df0$publication_year))
+  #maxyear = max(na.omit(df0$publication_year))
+
+  df = subset(df0, !country %in% c("Finland", "Sweden") & catalog == catal)
+  df <- subset(df, publication_year >= minyear & publication_year < maxyear)
+
+  timeinterval <- 5
+  df$timeunit <- round(df$publication_year/timeinterval)*timeinterval
+
+  df$unity = rep(1, nrow(df))
+  publications <- tapply(df$unity, list(df$timeunit), sum)
+
+  publications[is.na(publications)] <- 0 # Set NAs to 0
+  publications <- publications/timeinterval # Instead of decadal sum, use average annual output 
+  dfm <- melt(publications) 
+  names(dfm) <- c("Time", "Documents")
+  dfm <- transform(dfm, date = as.numeric(as.character(Time)))
+
+  # Draw Figure
+  theme_set(theme_bw(20))
+  p <- ggplot(data = dfm, aes(x = date, y = Documents))
+  p <- p + geom_line(col = "black")
+  p <- p + geom_smooth(col = "black")  
+  p <- p + geom_point(col = "black", size = 3)
+  p <- p + scale_x_continuous(breaks = seq(minyear, maxyear, 20), limits = c(minyear, maxyear))
+  p <- p + ggtitle("Publishing activity")
+  p <- p + ylab("Documents / Year")
+  p <- p + xlab("Year")
+  p <- p + ggtitle(paste("Outside of Sweden and Finland", " (", catal, ")", sep = ""))
+  print(p)
+
 ```

### 2016-06-23 inst/examples/manuscript-krakow.Rmd
Rmd update

@@
 
-TODO: why Fennica has huge drop in 1700s
+Why Fennica has huge drop in 1700s. Do some publisher disappear (TODO). Let us look at top publication places in Fennica:
+
+```{r drop1700, echo=FALSE, message=FALSE, warning=FALSE, fig.width=9, fig.height=6, out.width="280px"}
+selected.places = names(top(subset(df0, catalog == "Fennica"), "publication_place", 10))
+for (myplace in selected.places) {
+  # Use timeinterval year intervals
+  catal = "Fennica"
+  minyear = 1650
+  maxyear = 1750
+
+  df = subset(df0, publication_place == myplace & catalog == catal)
+  df <- subset(df, publication_year >= minyear & publication_year < maxyear)
+
+  timeinterval <- 1
+  df$timeunit <- round(df$publication_year/timeinterval)*timeinterval
+
+  df$unity = rep(1, nrow(df))
+  publications <- tapply(df$unity, list(df$timeunit), sum)
+
+  publications[is.na(publications)] <- 0 # Set NAs to 0
+  publications <- publications/timeinterval # Instead of decadal sum, use average annual output 
+  dfm <- melt(publications) 
+  names(dfm) <- c("Time", "Documents")
+  dfm <- transform(dfm, date = as.numeric(as.character(Time)))
+
+  # Draw Figure
+  theme_set(theme_bw(20))
+  p <- ggplot(data = dfm, aes(x = date, y = Documents))
+  p <- p + geom_line(col = "black")
+  #p <- p + geom_smooth(col = "black")  
+  p <- p + geom_point(col = "black", size = 3)
+  p <- p + scale_x_continuous(breaks = seq(minyear, maxyear, 20), limits = c(minyear, maxyear))
+  p <- p + ggtitle("Publishing activity")
+  p <- p + ylab("Documents / Year")
+  p <- p + xlab("Year")
+  p <- p + ggtitle(paste(myplace, " (", catal, ")", sep = ""))
+
+  print(p)
+}
+```
 
@@
 
-```{r selectedplaces2, echo=FALSE, message=FALSE, warning=FALSE, fig.width=9, fig.height=6, out.width="0px"}
+```{r selectedplaces2, echo=FALSE, message=FALSE, warning=FALSE, fig.width=9, fig.height=6, out.width="600px"}
 

### 2016-06-23 inst/examples/manuscript-krakow.Rmd
Rmd update

@@
 
-Why Fennica has huge drop in 1700s. Do some publisher disappear (TODO). Let us look at top publication places in Fennica:
+Why Fennica has huge drop in 1700s. Do some publisher disappear (TODO). Let us look at top publication places during the period 1650-1750 in Fennica:
 
 ```{r drop1700, echo=FALSE, message=FALSE, warning=FALSE, fig.width=9, fig.height=6, out.width="280px"}
-selected.places = names(top(subset(df0, catalog == "Fennica"), "publication_place", 10))
-for (myplace in selected.places) {
-  # Use timeinterval year intervals
+
   catal = "Fennica"
@@
   maxyear = 1750
+  df = subset(df0, catalog == catal)
+  df <- subset(df, publication_year >= minyear & publication_year < maxyear)
+  mydf = df
 
-  df = subset(df0, publication_place == myplace & catalog == catal)
-  df <- subset(df, publication_year >= minyear & publication_year < maxyear)
+selected.places = names(top(mydf, "publication_place", 6))
 
+for (myplace in selected.places) {
+
+  df = subset(mydf, publication_place == myplace)
+
+  # Use timeinterval year intervals
   timeinterval <- 1

### 2016-06-23 inst/examples/manuscript-krakow.Rmd
Rmd update

@@
 
-TODO: try check duplicates. Clustering with identical place, identical year, near identical title and then print table with potential duplicates for manual checks.
+## Results
 
@@
   # Use timeinterval year intervals
-  timeinterval <- 1
+  timeinterval <- 5
   df$timeunit <- round(df$publication_year/timeinterval)*timeinterval
@@
   p <- p + xlab("Year")
+  p = p + ylim(c(0, 80))
   p <- p + ggtitle(paste(myplace, " (", catal, ")", sep = ""))
@@
 
-## Results
+TODO: try check duplicates. Clustering with identical place, identical year, near identical title and then print table with potential duplicates for manual checks.
 

### 2016-06-23 inst/examples/manuscript-krakow.Rmd
Rmd update

@@
   p <- p + xlab("Year")
-  p = p + ylim(c(0, 80))
+  p = p + ylim(limits = c(0, 80))
   p <- p + ggtitle(paste(myplace, " (", catal, ")", sep = ""))

### 2016-06-23 inst/examples/manuscript-krakow.Rmd
Rmd update

--- 2016-06-23 inst/examples/manuscript-krakow.Rmd
@@
   p <- p + xlab("Year")
-  p = p + ylim(c(0, 80))
+  p <- p + scale_y_continuous(limits = c(0, 100))  
   p <- p + ggtitle(paste(myplace, " (", catal, ")", sep = ""))

### 2016-06-24 inst/examples/manuscript-krakow.Rmd
Update manuscript-krakow.Rmd

@@
 
+Grönroos, Henrik & Nyman, Ann-Charlotte, Boken i Finland, 1996.
+
+Suomen taloushistoria, Historiallinen tilasto 3, 1983.
+
+Vasenius, Valfrid, Suomalainen kirjallisuus, 1544-1877, 1878.
+
+Gardberg, Carl-Rudolf, Kirjapainotaito Suomessa I-III, 1949-1973.
+
+Heininen, Simo, Ulkomaisen kirjallisuuden tulo Suomeen 1531-1600. SKHSV, 1991.
+
+Häkli, Esko, Näin syntyi ja säilyi suomalainen kirja, 1989.
+
+Laine, Tuija, Vanhimman suomalaisen kirjallisuuden käsikirja, 1997.
+
+Vieraskielinen kirjallisuus Suomessa Ruotsin vallan aikana.
+
+Wittman, Reinhard, Was there a reading revolution at the end of the eighteenth century? A history of reading in the west. Cambridge, 2003.
+
 Aatehistoria ja digitaalisten aineistojen mahdollisuudet `r citep(bib[["Tolonen15EnnenNyt"]])`
@@
 TODO: try check duplicates. Clustering with identical place, identical year, near identical title and then print table with potential duplicates for manual checks.
+
+TODO (uusi, juhannustaika): Hartauskirjallisuuden kieli (suomi vai ruotsi) milloin alkaa yleistyä suomenkielinen ja miten tämän julkaiseminen suomeksi kasvaa?
+Muutenkin näitä suomi vs.
+ruotsinkieli kysymyksiä kannattaa yrittää toteuttaa.
+Mm.
+yleinen vertailu suomenkielisestä materiaalista ja ruotsinkielisestä materiaalista Fennicassa.
+Hartauskirjallisuuden osalta jos tämä näyttää järkevältä tarkastelukohdalta, niin sitten kannattaa tältä osin jatkaa analyysi myös 1828 eteenpäin suomenkielisen aineiston osalta niin pitkälle kuin Fennicassa riittää aineistoa.
 

### 2016-06-24 inst/examples/manuscript-krakow.Rmd
Update manuscript-krakow.Rmd

@@
 
-TODO (uusi, juhannustaika): Hartauskirjallisuuden kieli (suomi vai ruotsi) milloin alkaa yleistyä suomenkielinen ja miten tämän julkaiseminen suomeksi kasvaa?
-Muutenkin näitä suomi vs.
-ruotsinkieli kysymyksiä kannattaa yrittää toteuttaa.
-Mm.
-yleinen vertailu suomenkielisestä materiaalista ja ruotsinkielisestä materiaalista Fennicassa.
-Hartauskirjallisuuden osalta jos tämä näyttää järkevältä tarkastelukohdalta, niin sitten kannattaa tältä osin jatkaa analyysi myös 1828 eteenpäin suomenkielisen aineiston osalta niin pitkälle kuin Fennicassa riittää aineistoa.
+TODO: Fennica, Hartaus- yms.
+kirjallisuuden kieli (suomi vai ruotsi) milloin alkaa yleistyä suomenkielinen ja miten tämän julkaiseminen suomeksi kasvaa?
+Toteutus, valitaan kaikki teokset joihin liittyy joku seuraavista asiasanoista:
+
+virret	 
+arkkiveisut	 
+hartauskirjat	 
+katekismukset	 
+rukouspäivät	 
+saarnat	 
+aapiset	 
+rukoukset	  
+rukous	  
+hengelliset laulut	  
+hartauspuheet	  
+virsikirjat
+
+Tämän jälkeen tarkkaillaan aikajanalla näiden teosten esiintymistä, erottavana tekijänä kieli (suomi vs.
+ruotsi).
+ko.
+analyysi kannattaa jatkaa myös pidemmälle kuin 1828 Fennican osalta.
+Erilaisia tarkkailukulmia: 1) yleinen, 2) paikkakunta sekä 3) julkaisijakohtainen kehitys.
+
+Muutenkin, näitä suomi vs. ruotsinkieli kysymyksiä kannattaa yrittää toteuttaa. Mm. yleinen vertailu suomen-, ruotsin- ja muun kielisestä materiaalista Fennicassa aikajanalla.
 

### 2016-06-24 inst/examples/summarize.R
ok

@@ -1,7 +1,7 @@
 library(bibliographica)
 library(dplyr)
 df.preprocessed <- readRDS("df.Rds")
-df.orig <- readRDS("df.orig.Rds")
+df.orig <- readRDS("df.raw.Rds")
 output.folder <- "output.tables/"
 dir.create(output.folder)
 

### 2016-06-27 inst/examples/manuscript-krakow.Rmd
Update manuscript-krakow.Rmd

@@
 
-Why Fennica has huge drop in 1700s. Do some publisher disappear (TODO). Let us look at top publication places during the period 1650-1750 in Fennica:
+Why Fennica has huge drop in 1700s? Do some publisher disappear (TODO)? Let us look at top publication places during the period 1650-1750 in Fennica:
 
@@
 
+The drop in Fennica is explained largely by Great Nortern War (1700-1721).
+The war and difficult times seems to hit Turku particularly hard in early eighteenth century.
+What is telling also is that the curve of overall publishing activity in Kungliga is much steeper in eighteenth century compared to Fennica also in the second half of the century.
+This is the Enlightenment’s rising trend of knowledge production in most of Europe (for example ESTC has a similar development with Kungliga).
+Thus, development of publishing in Finland is much slower compared to larger European centers in the eighteenth century – this is an important context for the even further difficulties that follow after 1828.
+
 TODO: try check duplicates. Clustering with identical place, identical year, near identical title and then print table with potential duplicates for manual checks.
@@
 
-virret	 
-arkkiveisut	 
-hartauskirjat	 
-katekismukset	 
-rukouspäivät	 
-saarnat	 
-aapiset	 
-rukoukset	  
-rukous	  
-hengelliset laulut	  
-hartauspuheet	  
-virsikirjat
+virret;arkkiveisut;hartauskirjat;katekismukset;rukouspäivät;saarnat;aapiset;rukoukset;rukous;hengelliset laulut;hartauspuheet;virsikirjat
 

### 2016-06-27 inst/examples/manuscript-krakow.Rmd
Update manuscript-krakow.Rmd

@@
   * [Kungliga overview](https://github.com/rOpenGov/kungliga/blob/master/antagomir/overview.md)
+
+Voisiko nämä molemmat rajata tätä analyysia varten 1640-1828?
+Voisin sitten poimia sieltä sopivat summaryt tänne tuotaviksi.
+Mielessä on mm.
+https://github.com/rOpenGov/fennica/blob/master/inst/examples/author.md Niin että täältä ottaisi top-author timelinen molemmista Fennicasta ja Kungligasta vierekkäin.
+Tätä ennen pitää kuitenkin tehdä näiden top-auktoreiden osalta putsaus.
+Kun aineisto rajattu nyt tarkasteltaviin niin tiedetään sitten mitkä auktorit tätä varten putsataan.
 

### 2016-06-29 inst/examples/manuscript-krakow.Rmd
Update manuscript-krakow.Rmd

@@
 ==============
+
+TODO-järjestyksestä:
+
+Tärkein ASAP tehtävä on ##Publisher analysis
+
+Selvensin alle (##Publisher analysis kohtaan): PUBLISHER-TODO1 ja PUBLISHER-TODO2. Aloitetaan näiden työstäminen niin pian kuin mahdollista.
+
+Lisäksi tuolla on paljon näistä riippumattomia (kuin myös näistä riippuvia) analyysiajatuksia.
+
+Muiden osalta (eli sellaisista joita voi tehdä jo nyt ilman publisher kenttää), järjestys voisi olla:
+
+### Book printing in Finland - kohdasta BOOKINFINLAND-TODO1 ja BOOKINFINLAND-TODO2.
+
+Eli ehdottaisin että analyysivaihe johon nyt siirrytään, niin Leo jos ehdit, niin aloita noilla BOOKINFINLAND-TODOilla ja sitten kun julkaisijakenttä tsekattu varmasti loppuun, niin sitten heti Publisher analysis kohtaan ja PUBLISHER-TODOt.
+Samalla Marjanen ja minä siivotaan näitä muita analyysi-ideoita toteuttamiskelpoisiksi ohjeiksi.
+Jani voi tehdä tätä omatoimisesti myös.
 
@@
 TODO: try check duplicates. Clustering with identical place, identical year, near identical title and then print table with potential duplicates for manual checks.
-
-TODO: Fennica, Hartaus- yms.
-kirjallisuuden kieli (suomi vai ruotsi) milloin alkaa yleistyä suomenkielinen ja miten tämän julkaiseminen suomeksi kasvaa?
-Toteutus, valitaan kaikki teokset joihin liittyy joku seuraavista asiasanoista:
-
-virret;arkkiveisut;hartauskirjat;katekismukset;rukouspäivät;saarnat;aapiset;rukoukset;rukous;hengelliset laulut;hartauspuheet;virsikirjat
-
-Tämän jälkeen tarkkaillaan aikajanalla näiden teosten esiintymistä, erottavana tekijänä kieli (suomi vs.
-ruotsi).
-ko.
-analyysi kannattaa jatkaa myös pidemmälle kuin 1828 Fennican osalta.
-Erilaisia tarkkailukulmia: 1) yleinen, 2) paikkakunta sekä 3) julkaisijakohtainen kehitys.
-
-Muutenkin, näitä suomi vs. ruotsinkieli kysymyksiä kannattaa yrittää toteuttaa. Mm. yleinen vertailu suomen-, ruotsin- ja muun kielisestä materiaalista Fennicassa aikajanalla.
 
@@
 
+BOOKINFINLAND-TODO1: Kielikohtainen yleinen vertailu julkaisumääristä ja paperinkulutuksesta.
+Eli kaksi kuvaa (julkaisumäärät ja paperinkulutus kielittäin).
+Tarkkailtavia kielikategorioita on 5: suomi, ruotsi, latina, saksa sekä kategoria jossa kaikki muun kielisiset kuin edellä mainitut niputetaan yhteen.
+Tarkoituksena tarkkailla miten kielten kehitys suhtautuu toisiinsa (suomi kasvaa, latina laskee jne.).
+Tärkeää on vertailu, mutta myös että nähdään kielikohtainen kehitys.
+Täten esim.
+pienemmän saksankielen kohdalla kannattaa varmaan piirtää erillinen kuva.
+Analyysi voi tapahtua aikajanalla, mutta voisi myös ajatella suhteellista kehitystä tässä jollain muulla esitystavalla, olisiko se sitten jonkinlainen prosenttianalyysi?
+Tämä analyysi kannattaa jatkaa myös pidemmälle kuin 1828 Fennican osalta.
+
+BOOKINFINLAND-TODO2: Fennica, Hartaus- yms.
+kirjallisuuden kieli (suomi vai ruotsi) milloin alkaa yleistyä suomenkielinen ja miten tämän julkaiseminen suomeksi kasvaa?
+Toteutus, valitaan kaikki teokset joihin liittyy joku seuraavista asiasanoista:
+
+virret;arkkiveisut;hartauskirjat;katekismukset;rukouspäivät;saarnat;aapiset;rukoukset;rukous;hengelliset laulut;hartauspuheet;virsikirjat
+
+Tämän jälkeen tarkkaillaan aikajanalla näiden teosten esiintymistä, erottavana tekijänä kieli (samat 5 kategoriaa kuin edellisessä analyysissä).
+Erilaisia tarkkailukulmia: 1) yleinen, 2) paikkakunta sekä 3) julkaisijakohtainen kehitys (sitten kun mahdollista).
+
+Tämä analyysi kannattaa jatkaa myös pidemmälle kuin 1828 Fennican osalta.
+
+Hartauskirjallisuudesta ks. Osmo Tiililä, Rukoilevaisten kirjoja, 1961.
+
 ### Book as media: development over time
@@
 
-Pystytäänkö julkaisemiseen liittyvästä Fennica-datasta erottelemaan
-selkeitä trendejä suomalaisesta tiedontuotannosta 1640-1828, pääfokus
-julkaisijat: Miten uusia julkaisijoita tulee julkaisijakenttään
-Suomessa ja katoaa. Pääpaino erityisesti sillä kun julkaisijakartalle
-tulee uusia toimijoita! [TÄHÄN VOISI MIETTIÄ KARTTAKUVIEN SARJAA TAI
+PUBLISHER-TODO1: Fennica-datasta pyritään erottamaan selkeitä trendejä suomalaisesta tiedontuotannosta 1640-1828, pääfokus
+julkaisijat: 1) Miten uusia julkaisijoita tulee eri paikkakunnille
+Suomessa ja aikaisempia julkaisijoita katoaa? Pääpaino erityisesti sillä kun julkaisijakartalle
+tulee uusia toimijoita (eli uudet paikkakunnat).
+Ideana että julkaisijan nimi ei tässä ole tärkeää, vaan se että milloin uusia julkaisijoita tulee ja milloin aikaisempia häviää.
+Lisäksi suuremmat pudotukset tärkeitä (vrt.
+Turku julkaisumäärät yleensä 1700-luvun alku) [TÄHÄN VOISI MIETTIÄ KARTTAKUVIEN SARJAA TAI
 STACKED BARPLOTTIA JONKA DIVERSITEETTI KASVAA]
 
-Toimijoita voisi myös yrittää luokitella suhteellisesti (“iso”,
-“keskikokoinen”, “pieni”) liittyen vuosittaiseen julkaisuvoluumiin
-jota mitataan niin julkaisujen määrän kuin myös paperinkulutusvoluumin
-suhteen. Vertailua suurimpien julkaisijoiden kesken.
-
-Analyysia voisi tästä tehdä sitten näiden luokkien kehityksen
-mukaan. “Siinä missä Londicer 1700-luvun Vaasassa näyttää aina
+Ylläolevalla analyysillä pyritään vastaamaan myös tähän: “Siinä missä Londicer 1700-luvun Vaasassa näyttää aina
 julkaisseen asetukset jonkinlaisena kokoomapainoksena, mutta
@@
 julkaisemien niteiden määrä saattaa näyttää suurelta verrattuna
-Londiceriin, mutta itse asiassa sisältömäärä on sama”. → Tämä
-hypoteesi voidaan todentaa/tarkistaa/korjata kun mukana on
-paperinkulutus!
+Londiceriin, mutta itse asiassa sisältömäärä on sama”. 
+→ Tätä hypoteesia voidaan yrittää todentaa/tarkistaa/korjata kun mukana on
+paperinkulutus. Eli jos verrataan Londicer ja Frenckell paperinkulutusta vuositasolla ja julkaisujen määrää, niin tästä pitäisi pystyä sanomaan jotain.
 
-Julkaisijoiden ilmentyminen kartalle paperinkulutusvoluumi huomioiden:
+PUBLISHER-TODO2: Fennican suurimpien tarkasteltavan ajanjakson julkaisijoiden (top-5) julkaisuprofiilin ja siinä mahdollisesti tapahtuvan muutoksen tutkiminen.
+Ts.
+julkaisumäärät aikajanalla (on jo osittain), lisäksi paperinkulutusvertailu.
+Tärkeänä kysymyksenä on mitä eri julkaisijat julkaisee.
+Tähän liittyen top-5 julkaisijoista voisi tuottaa julkaisujen yhteiset, julkaisijakohtaiset asiasanalistat (mitä asiasanoja yhden julkaisijan kaikista töistä löytyy) jotka voitaisiin sitten käsin ryhmitellä isompiin kategorioihin (esim.
+yliopistojulkaisu, uskonnollinen teksti, säädökset, kaunokirjallinen ja muut (tai vast.)).
+Näin pystyttäisiin puhumaan siitä minkälainen julkaisija on kyseessä, muuttuuko profiili asiasanojen esiintymisen mukaan aikajanalla sekä nähdä onko julkaisijoiden kohdalla tässä mitään eroja.
+
+PUBLISHER-TODO(jos ehtii): Fennican julkaisijoita voisi myös laajemmin yrittää luokitella suhteellisesti (“iso”,
+“keskikokoinen”, “pieni”) liittyen vuosittaiseen julkaisuvoluumiin
+jota mitataan niin julkaisujen määrän kuin myös paperinkulutusvoluumin
+suhteen. Tällä tavalla olisi helpompi hahmottaa eri kaupungeissa tapahtuvaa kehitystä. Vertailua suurimpien julkaisijoiden kesken.
+
+AJATUKSIA: Julkaisijoiden ilmentyminen kartalle paperinkulutusvoluumi huomioiden:
 julkaisutoiminnan leviäminen ja kasvu ajassa eri
@@
 
-Julkaisijoista tehtävä verkostoanalyysi. keskeisimmät “nodet” siihen
+PUBLISHER-TODO (jos ehtii): Julkaisijoista tehtävä verkostoanalyysi. keskeisimmät “nodet” siihen
 miten julkaisijakenttä muuttuu ajassa. Julkaisijoita voisi myös

### 2016-06-29 inst/examples/manuscript-krakow.Rmd
Update manuscript-krakow.Rmd

@@
 
+BOOKINFINLAND-TODO3: Sama kuin edellä, mutta asiasanat tässä:
+
+hautajaiset;häät;juhlamenot
+
+BOOKINFINLAND-TODO4: edellisten yhdistäminen, eli täsmälleen samat analyysit, mutta asiasanoina kaikki (todo2 ja todo3), eli:
+
+virret;arkkiveisut;hartauskirjat;katekismukset;rukouspäivät;saarnat;aapiset;rukoukset;rukous;hengelliset laulut;hartauspuheet;virsikirjat;hautajaiset;häät;juhlamenot
+
 Hartauskirjallisuudesta ks. Osmo Tiililä, Rukoilevaisten kirjoja, 1961.

### 2016-06-29 inst/examples/manuscript-krakow.Rmd
Rmd update

@@
 fen <- readRDS("df.Rds")
-kun <- readRDS("../../../kungliga/antagomir/df.Rds")
+kun <- readRDS("../../../kungliga/df.Rds")
 
 fenraw <- readRDS("df.raw.Rds")
-kunraw <- readRDS("../../../kungliga/antagomir/df.raw.Rds")
+kunraw <- readRDS("../../../kungliga/df.raw.Rds")
 

### 2016-06-30 inst/examples/manuscript-krakow.Rmd

@@
 
-Voisiko nämä molemmat rajata tätä analyysia varten 1640-1828?
-Voisin sitten poimia sieltä sopivat summaryt tänne tuotaviksi.
-Mielessä on mm.
-https://github.com/rOpenGov/fennica/blob/master/inst/examples/author.md Niin että täältä ottaisi top-author timelinen molemmista Fennicasta ja Kungligasta vierekkäin.
-Tätä ennen pitää kuitenkin tehdä näiden top-auktoreiden osalta putsaus.
-Kun aineisto rajattu nyt tarkasteltaviin niin tiedetään sitten mitkä auktorit tätä varten putsataan.
+ https://github.com/rOpenGov/fennica/blob/master/inst/examples/author.md täältä top-author timelinen molemmista Fennicasta ja Kungligasta vierekkäin.
+Putsaus ok (näistä tsekattu, että ei löydy ainakaan isoa määrää laskuista puuttuvia nimivariantilla julkaistuja teoksia).
+Pointtina tässä on, että Kungligassa väitöskirjat näyttelevät huomattavasti pienempää osaa kuin Fennicassa.
+Näkyy näistä top-auktori kuvista.
+
+ Tämä kuva Fennica Summarysta on hyvä publisher analyysiin:
+
+https://raw.githubusercontent.com/rOpenGov/fennica/master/inst/examples/figure/summaryTop10pubtimeline-1.png
+
+Voisiko tästä julkaisijoiden title vs.
+paper countista laskea jonkun suhdeluvun per julkaisija?
+Idea että nähdään voidaanko sanoa onko joku selkeästi asetusten julkaisija ja toisella myös kirjoja (tai asetuskokoelmia).
+
+Tuolla Fennica yhteenvedoissa on myös ##EDITIONS kohta. Siellä ei kuitenkaan ole mitään kuvia. Olisiko ne mahdollista saada? On nimittäin mielenkiintoinen kysymys:
+
+https://github.com/rOpenGov/fennica/blob/master/inst/examples/publicationyear.md
 
@@
 ```
+Tässä on meille tärkeät kuvat.
+Erityisesti paper consumption (Kungliga) kertoo Valistuksen voittokulusta Euroopassa.
+Octavo kokoisten kirjojen paper consumption on merkki kirjojen merkityksen korostumisesta ja muutoksesta.
+Sama päti ESTCn.
+Suomi taas tulee tässä orastavasti perässä kirjatuotannon puolesta.
+Mitä me halutaan sanoa tästä suomalaisen sivistysvaltion myöhemmästä kehityksestä?
 

### 2016-07-01 inst/examples/manuscript-krakow.Rmd
Rmd update

@@
 # Define time span
-min.year = 1470
-max.year = 1828
+min.year <- 1488
+max.year <- 1828
 
@@
 
-Tärkein ASAP tehtävä on ##Publisher analysis
+Tärkein ASAP tehtävä on **Publisher analysis**
 
-Selvensin alle (##Publisher analysis kohtaan): PUBLISHER-TODO1 ja PUBLISHER-TODO2. Aloitetaan näiden työstäminen niin pian kuin mahdollista.
-
-Lisäksi tuolla on paljon näistä riippumattomia (kuin myös näistä riippuvia) analyysiajatuksia.
+Selvensin alle (Publisher analysis kohtaan): PUBLISHER-TODO1 ja PUBLISHER-TODO2.
+Aloitetaan näiden työstäminen niin pian kuin mahdollista.
+Lisäksi tuolla paljon näistä riippumattomia (kuin myös näistä riippuvia) analyysiajatuksia.
 

### 2016-07-01 inst/examples/manuscript-krakow.Rmd
ok

@@
 
-Muiden osalta (eli sellaisista joita voi tehdä jo nyt ilman publisher kenttää), järjestys voisi olla:
+Muiden osalta (eli sellaisista joita voi tehdä jo nyt ilman publisher kenttää), järjestys voisi olla: **Book printing in Finland** - kohdasta
+  * BOOKINFINLAND-TODO1 ja
+  * BOOKINFINLAND-TODO2.
 
-### Book printing in Finland - kohdasta BOOKINFINLAND-TODO1 ja BOOKINFINLAND-TODO2.
-
-Eli ehdottaisin että analyysivaihe johon nyt siirrytään, niin Leo jos ehdit, niin aloita noilla BOOKINFINLAND-TODOilla ja sitten kun julkaisijakenttä tsekattu varmasti loppuun, niin sitten heti Publisher analysis kohtaan ja PUBLISHER-TODOt.
+Eli ehdottaisin että analyysivaihe johon nyt siirrytään, niin Leo jos ehdit, niin aloita noilla BOOKINFINLAND-TODOilla ja kun julkaisijakenttä tsekattu varmasti loppuun, niin heti Publisher analysis kohtaan ja PUBLISHER-TODOt.
 Samalla Marjanen ja minä siivotaan näitä muita analyysi-ideoita toteuttamiskelpoisiksi ohjeiksi.
@@
 
-### Publisher analysis
+### Dynamics and evolution of publisher networks
 
-Puhutaan julkaisijatoiminnan kehityksestä ikään kuin luonnollisena
-kehityksenä - eli yhteys luonnonilmiöiden kehitykseen säilyisi.
+DONE1: Observed trends in Fennica regarding Finnish knowledge
+production 1640-1828, focusing on the appearance of new publishers on
+the publishing landscape.
 
-PUBLISHER-TODO1: Fennica-datasta pyritään erottamaan selkeitä trendejä suomalaisesta tiedontuotannosta 1640-1828, pääfokus
-julkaisijat: 1) Miten uusia julkaisijoita tulee eri paikkakunnille
-Suomessa ja aikaisempia julkaisijoita katoaa? Pääpaino erityisesti sillä kun julkaisijakartalle
-tulee uusia toimijoita (eli uudet paikkakunnat).
-Ideana että julkaisijan nimi ei tässä ole tärkeää, vaan se että milloin uusia julkaisijoita tulee ja milloin aikaisempia häviää.
-Lisäksi suuremmat pudotukset tärkeitä (vrt.
-Turku julkaisumäärät yleensä 1700-luvun alku) [TÄHÄN VOISI MIETTIÄ KARTTAKUVIEN SARJAA TAI
-STACKED BARPLOTTIA JONKA DIVERSITEETTI KASVAA]
+  1. Miten uusia julkaisijoita ilmestyy ja katoaa eri paikkakunnilla
+     Suomessa?  Pääpaino erityisesti kun julkaisijakartalle tulee
+     uusia toimijoita (uudet paikkakunnat). Julkaisijan nimi ei
+     tärkeää, vaan se milloin uusia tulee ja aikaisempia
+     häviää.
 
-Ylläolevalla analyysillä pyritään vastaamaan myös tähän: “Siinä missä Londicer 1700-luvun Vaasassa näyttää aina
-julkaisseen asetukset jonkinlaisena kokoomapainoksena, mutta
-Frenckellin kirjapainosta ne tuli yksitellen. Siten Frenckellin
-julkaisemien niteiden määrä saattaa näyttää suurelta verrattuna
-Londiceriin, mutta itse asiassa sisältömäärä on sama”. 
-→ Tätä hypoteesia voidaan yrittää todentaa/tarkistaa/korjata kun mukana on
-paperinkulutus. Eli jos verrataan Londicer ja Frenckell paperinkulutusta vuositasolla ja julkaisujen määrää, niin tästä pitäisi pystyä sanomaan jotain.
+  1. Suuremmat pudotukset tärkeitä (vrt. Turku julkaisumäärät
+     yleensä 1700-luvun alku) [TÄHÄN VOISI MIETTIÄ KARTTAKUVIEN SARJAA
+     TAI STACKED BARPLOTTIA JONKA DIVERSITEETTI KASVAA]
+
+  1. Pyritään vastaamaan myös tähän: “Siinä missä Londicer 1700-luvun
+     Vaasassa näyttää aina julkaisseen asetukset jonkinlaisena
+     kokoomapainoksena, mutta Frenckellin kirjapainosta ne tuli
+     yksitellen. Siten Frenckellin julkaisemien niteiden määrä saattaa
+     näyttää suurelta verrattuna Londiceriin, mutta itse asiassa
+     sisältömäärä on sama”.  → Tätä hypoteesia voidaan yrittää
+     todentaa/tarkistaa/korjata kun mukana on paperinkulutus. Eli jos
+     verrataan Londicer ja Frenckell paperinkulutusta vuositasolla ja
+     julkaisujen määrää, niin tästä pitäisi pystyä sanomaan jotain.
+
+Number of unique publishers per decade in Finland and elsewhere (based on the Fennica catalogue).
+
+```{r publishers-finland, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=7, fig.width=10, fig.show="hold", out.width="430px"}
+
+# Unique publishers
+df <- df0
+# Indicator Finland yes/no
+df$Finland <- (df$country == "Finland")
+
+df <- df %>%
+        filter(catalog == "Fennica" & !is.na(Finland)) %>%
+        filter(publication_year >= 1640 & publication_year < 1828) %>%	
+        select(publisher, publication_decade, Finland)
+npub <- unique(df) %>% group_by(publication_decade, Finland) %>% tally()
+theme_set(theme_bw(20))
+p <- ggplot(npub, aes(x = publication_decade, y = n, group = Finland)) +
+       geom_point(aes(shape = Finland), size = 5) +
+       geom_line(col = "black", aes(shape = Finland)) +       
+       geom_smooth(col = "black") + 
+       xlab("Publication year") +
+       ylab("Unique publishers (n)") +        
+       ggtitle("Unique publishers (Fennica)")
+print(p)
+
+# -----------------------------
+
+# Unique publication places
+df <- df0
+df <- df %>%
+        filter(catalog == "Fennica" & country == "Finland") %>%
+        filter(publication_year >= 1640 & publication_year < 1828) %>%	
+        select(publication_decade, publication_place)
+npub <- unique(df) %>% group_by(publication_decade) %>% tally()
+theme_set(theme_bw(20))
+p <- ggplot(npub, aes(x = publication_decade, y = n)) +
+       geom_point(size = 5) +
+       geom_line(col = "black") +       
+       geom_smooth(col = "black") + 
+       xlab("Publication year") +
+       ylab("Unique publication places (n)") +        
+       ggtitle("Unique publication places in Finland (Fennica)")
+print(p)
+```
 

### 2016-07-01 inst/examples/manuscript-krakow.Rmd
ok

@@
 ```{r publishers-finland, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=7, fig.width=10, fig.show="hold", out.width="430px"}
-
 # Unique publishers
@@
        ggtitle("Unique publication places in Finland (Fennica)")
+print(p)
+
+# Places in Fennica Finland 1770
+#unique(subset(df0, catalog == "Fennica" & publication_decade == 1770 & country == "Finland")$publication_place)
+```
+
+```{r publishers2-finland, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=7, fig.width=10, out.width="800px"}
+df <- df0
+df <- df %>%
+        filter(catalog == "Fennica" & country == "Finland") %>%
+        filter(publication_year >= 1640 & publication_year < 1828)
+
+# Top publication places
+ntop <- 10
+top <- names(top(df, "publication_place", ntop))
+
+df <- df %>%	
+        filter(publication_place %in% top) %>%	
+        select(publication_decade, publication_place, publisher)
+
+npub <- unique(df) %>% group_by(publication_decade, publication_place) %>% tally()
+npub$publication_place <- factor(npub$publication_place, levels = top)
+theme_set(theme_bw(20))
+
+p <- ggplot(npub, aes(x = publication_decade, y = n)) +
+       geom_bar(stat = "identity", position = "stack", aes(fill = publication_place)) + 
+       #geom_point(size = 5, aes(shape = publication_place)) +
+       #geom_line(col = "black", aes(shape = publication_place)) +       
+       # geom_smooth(col = "black", aes(shape = publication_place)) + 
+       xlab("Publication year") +
+       ylab("Unique publishers (n)") +        
+       ggtitle("Unique publishers in top publication places (Finland/Fennica)")
 print(p)

### 2016-07-01 inst/examples/manuscript-krakow.Rmd
ok

@@
 
-```{r publishers2-finland, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=7, fig.width=10, out.width="800px"}
+```{r publishers2-finland, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=5, fig.width=10}
 df <- df0
@@
 print(p)
+```
+
+```{r publishers3-finland, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=5, fig.width=10}
+# Title count
+catalogue <- "Fennica"
+place <- "Turku"
+
+df <- df0
+df <- df %>%
+        filter(catalog == catalogue & publication_place == place) %>%
+        filter(publication_year >= 1640 & publication_year < 1828)
+
+df <- df %>%	
+        select(publication_decade, publisher, paper.consumption.km2)
+
+# Group small publishers
+# Top publishers by title count
+ntop <- 10
+top <- names(top(df, "publisher", ntop))
+df$publisher[!df$publisher %in% top] <- "Other"
+df$publisher <- factor(df$publisher, c(top, "Other"))
+
+# Title count per decade & publisher	
+npub <- df %>% group_by(publication_decade, publisher) %>% tally()
+
+theme_set(theme_bw(20))
+p <- ggplot(npub, aes(x = publication_decade, y = n)) +
+       geom_bar(stat = "identity", position = "stack", aes(fill = publisher)) + 
+       #geom_point(size = 5, aes(shape = publication_place)) +
+       #geom_line(col = "black", aes(shape = publication_place)) +       
+       # geom_smooth(col = "black", aes(shape = publisher)) + 
+       xlab("Publication year") +
+       ylab("Title count (n)") +        
+       ggtitle(paste("Title count per publisher (", place, "/", catalogue, ")", sep = ""))
+print(p)
+
+catalogue <- "Fennica"
+place <- "Turku"
+
+df <- df0
+df <- df %>%
+        filter(catalog == catalogue & publication_place == place) %>%
+        filter(publication_year >= 1640 & publication_year < 1828)
+
+df <- df %>%	
+        select(publication_decade, publisher, paper.consumption.km2)
+
+# Group small publishers
+# Top publishers
+ntop <- 5
+top <- names(top(df, "publisher", ntop))
+df$publisher[!df$publisher %in% top] <- "Other"
+df$publisher <- factor(df$publisher, c(top, "Other"))
+
+# Publishing per decade & publisher	
+npub <- df %>%
+     	  group_by(publication_decade, publisher) %>%
+	  summarize(paper = sum(paper.consumption.km2, na.rm = TRUE), n = n()) %>%
+	  mutate(paper.per.title = paper/n)
+
+theme_set(theme_bw(20))
+p <- ggplot(npub, aes(x = publication_decade, y = n)) +
+       geom_bar(stat = "identity", position = "dodge", aes(fill = publisher)) + 
+       #geom_point(size = 5, aes(shape = publisher)) +
+       #geom_line(col = "black", aes(shape = publisher)) +       
+       # geom_smooth(col = "black", aes(shape = publisher)) + 
+       xlab("Publication year") +
+       ylab("Title count (n)") +        
+       ggtitle(paste("Title count (", place, "/", catalogue, ")", sep = ""))
+print(p)
+
+# Paper consumption
+catalogue <- "Fennica"
+place <- "Turku"
+
+df <- df0
+df <- df %>%
+        filter(catalog == catalogue & publication_place == place) %>%
+        filter(publication_year >= 1640 & publication_year < 1828)
+
+df <- df %>%	
+        select(publication_decade, publisher, paper.consumption.km2)
+
+# Group small publishers
+# Top publishers by title count
+ntop <- 10
+top <- names(top(df, "publisher", ntop))
+df$publisher[!df$publisher %in% top] <- "Other"
+df$publisher <- factor(df$publisher, c(top, "Other"))
+
+# Publishing per decade & publisher	
+npub <- df %>% group_by(publication_decade, publisher) %>% summarize(paper = sum(paper.consumption.km2, na.rm = TRUE))
+
+theme_set(theme_bw(20))
+p <- ggplot(npub, aes(x = publication_decade, y = paper)) +
+       geom_bar(stat = "identity", position = "stack", aes(fill = publisher)) + 
+       #geom_point(size = 5, aes(shape = publication_place)) +
+       #geom_line(col = "black", aes(shape = publication_place)) +       
+       # geom_smooth(col = "black", aes(shape = publisher)) + 
+       xlab("Publication year") +
+       ylab("Paper consumption") +        
+       ggtitle(paste("Paper consumption per publisher (", place, "/", catalogue, ")", sep = ""))
+print(p)
+
+catalogue <- "Fennica"
+place <- "Turku"
+
+df <- df0
+df <- df %>%
+        filter(catalog == catalogue & publication_place == place) %>%
+        filter(publication_year >= 1640 & publication_year < 1828)
+
+df <- df %>%	
+        select(publication_decade, publisher, paper.consumption.km2)
+
+# Group small publishers
+# Top publishers
+ntop <- 5
+top <- names(top(df, "publisher", ntop))
+df$publisher[!df$publisher %in% top] <- "Other"
+df$publisher <- factor(df$publisher, c(top, "Other"))
+
+# Publishing per decade & publisher	
+npub <- df %>%
+     	  group_by(publication_decade, publisher) %>%
+	  summarize(paper = sum(paper.consumption.km2, na.rm = TRUE), n = n()) %>%
+	  mutate(paper.per.title = paper/n)
+
+theme_set(theme_bw(20))
+p <- ggplot(npub, aes(x = publication_decade, y = paper)) +
+       geom_bar(stat = "identity", position = "dodge", aes(fill = publisher)) + 
+       #geom_point(size = 5, aes(shape = publisher)) +
+       #geom_line(col = "black", aes(shape = publisher)) +       
+       # geom_smooth(col = "black", aes(shape = publisher)) + 
+       xlab("Publication year") +
+       ylab("Paper") +        
+       ggtitle(paste("Paper (", place, "/", catalogue, ")", sep = ""))
+print(p)
+
 ```

### 2016-07-01 inst/examples/manuscript-krakow.Rmd
ok

@@
 
+Number of unique publishers in top publication places over time:
+
 ```{r publishers2-finland, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=5, fig.width=10}
@@
 
-```{r publishers3-finland, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=5, fig.width=10}
+Title count per top publisher (two alternative visualizations):
+
+```{r publishers3-finland, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=7, fig.width=15}
 # Title count
@@
 print(p)
+```
+
+Paper consumption per top publisher (two alternative visualizations):
+
+```{r publishers4-finland, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=7, fig.width=15}
 
@@
 print(p)
-
 ```

### 2016-07-01 inst/examples/manuscript-krakow.Rmd
ok

@@
 
-  1. Miten uusia julkaisijoita ilmestyy ja katoaa eri paikkakunnilla
-     Suomessa?  Pääpaino erityisesti kun julkaisijakartalle tulee
-     uusia toimijoita (uudet paikkakunnat). Julkaisijan nimi ei
-     tärkeää, vaan se milloin uusia tulee ja aikaisempia
-     häviää.
-
-  1. Suuremmat pudotukset tärkeitä (vrt. Turku julkaisumäärät
-     yleensä 1700-luvun alku) [TÄHÄN VOISI MIETTIÄ KARTTAKUVIEN SARJAA
-     TAI STACKED BARPLOTTIA JONKA DIVERSITEETTI KASVAA]
-
-  1. Pyritään vastaamaan myös tähän: “Siinä missä Londicer 1700-luvun
-     Vaasassa näyttää aina julkaisseen asetukset jonkinlaisena
-     kokoomapainoksena, mutta Frenckellin kirjapainosta ne tuli
-     yksitellen. Siten Frenckellin julkaisemien niteiden määrä saattaa
-     näyttää suurelta verrattuna Londiceriin, mutta itse asiassa
-     sisältömäärä on sama”.  → Tätä hypoteesia voidaan yrittää
-     todentaa/tarkistaa/korjata kun mukana on paperinkulutus. Eli jos
-     verrataan Londicer ja Frenckell paperinkulutusta vuositasolla ja
-     julkaisujen määrää, niin tästä pitäisi pystyä sanomaan jotain.
+How new publishers appear and disappear from the Finnish publishing
+landscape. We have analyzed the number of unique publication places
+and unique publishers in terms of title count and paper consumption
+over Finland in general, and more specifically within the top
+publication places over time.
 
@@
 
-```{r publishers2-finland, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=5, fig.width=10}
+```{r publishers2-finland, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=7, fig.width=15}
 df <- df0
@@
 ```{r publishers4-finland, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=7, fig.width=15}
-
 # Paper consumption
@@
        ggtitle(paste("Paper (", place, "/", catalogue, ")", sep = ""))
+print(p)
+```
+
+**Londicer versus Frencell** “Siinä missä Londicer 1700-luvun Vaasassa
+     näyttää aina julkaisseen asetukset jonkinlaisena
+     kokoomapainoksena, mutta Frenckellin kirjapainosta ne tuli
+     yksitellen. Siten Frenckellin julkaisemien niteiden määrä saattaa
+     näyttää suurelta verrattuna Londiceriin, mutta itse asiassa
+     sisältömäärä on sama”.  → Tätä hypoteesia voidaan yrittää
+     todentaa/tarkistaa/korjata kun mukana on paperinkulutus. Eli jos
+     verrataan Londicer ja Frenckell paperinkulutusta vuositasolla ja
+     julkaisujen määrää, niin tästä pitäisi pystyä sanomaan jotain.
+
+```{r publishers5-finland, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=7, fig.width=15}
+catalogue <- "Fennica"
+df <- df0
+df <- df %>%
+        filter(catalog == catalogue) %>%
+        filter(publication_year >= 1750 & publication_year < 1828)
+
+df <- df %>%	
+        select(publication_decade, publisher, paper.consumption.km2)
+
+# Selected ones
+top <- c("Frenckell, Johan Christopher I", "Londicer, Georg Wilhelm", "Frenckell, Johan Christopher II")
+df$publisher[!df$publisher %in% top] <- "Other"
+df$publisher <- factor(df$publisher, c(top, "Other"))
+
+# Publishing per decade & publisher	
+npub <- df %>%
+     	  group_by(publication_decade, publisher) %>%
+	  summarize(paper = sum(paper.consumption.km2, na.rm = TRUE), n = n()) %>%
+	  mutate(paper.per.title = paper/n)
+
+theme_set(theme_bw(20))
+p <- ggplot(npub, aes(x = publication_decade, y = n, group = publisher)) +
+       geom_bar(stat = "identity", position = "dodge", aes(fill = publisher)) + 
+       #geom_point(size = 5, aes(shape = publisher)) +
+       #geom_line(col = "black", aes(shape = publisher)) +       
+       # geom_smooth(col = "black", aes(shape = publisher)) + 
+       xlab("Publication year") +
+       ylab("Title count (n)") +        
+       ggtitle(paste("Title count (", catalogue, ")", sep = ""))
+print(p)
+
+theme_set(theme_bw(20))
+p <- ggplot(npub, aes(x = publication_decade, y = paper, group = publisher)) +
+       geom_bar(stat = "identity", position = "dodge", aes(fill = publisher)) + 
+       #geom_point(size = 5, aes(shape = publisher)) +
+       #geom_line(col = "black", aes(shape = publisher)) +       
+       # geom_smooth(col = "black", aes(shape = publisher)) + 
+       xlab("Publication year") +
+       ylab("Paper") +        
+       ggtitle(paste("Paper (", catalogue, ")", sep = ""))
 print(p)

### 2016-07-01 inst/examples/manuscript-krakow.Rmd
ok

@@
 
+**PUBLISHER-TODO2** (Done?) Analysis of the top publishers publishing
+  profile (title count and paper consumption) over time.
+
 Title count per top publisher (two alternative visualizations):
@@
 print(p)
+```
+
+Tärkeänä kysymyksenä on mitä eri julkaisijat julkaisee. Top-5
+julkaisijoista voisi tuottaa julkaisujen yhteiset, julkaisijakohtaiset
+asiasanalistat (mitä asiasanoja yhden julkaisijan kaikista töistä
+löytyy) jotka voitaisiin sitten käsin ryhmitellä isompiin
+kategorioihin (esim. yliopistojulkaisu, uskonnollinen teksti,
+säädökset, kaunokirjallinen ja muut (tai vast.)). Näin pystyttäisiin
+puhumaan siitä minkälainen julkaisija on kyseessä, muuttuuko profiili
+asiasanojen esiintymisen mukaan aikajanalla sekä nähdä onko
+julkaisijoiden kohdalla tässä mitään eroja.
+
+OK, see lists for
+  * [Frenckell Johan Christopher II](output.tables/subjecttopicsFrenckell,_Johan_Christopher_II.tab)
+  * [Frenckell Johan Christopher I](output.tables/Frenckell,_Johan_Christopher_I.tab)
+  * [Hansson Peter](output.tables/Hansson,_Peter.tab)
+  * [Londicer Georg Wilhelm](output.tables/Londicer,_Georg_Wilhelm.tab)
+  * [Wall Johan Larsson](output.tables/Wall,_Johan_Larsson.tab)
+
+```{r publishers-subtop, echo=FALSE, message=FALSE, warning=FALSE}
+#Top-5 julkaisijoista voisi julkaisujen yhteiset, julkaisijakohtaiset
+#asiasanalistat (mitä asiasanoja yhden julkaisijan kaikista töistä
+#löytyy)
+
+catalogue <- "Fennica"
+df <- df0
+df <- df %>%
+        filter(catalog == catalogue) %>%
+        filter(publication_year >= 1640 & publication_year < 1828)
+
+# Selected ones
+top <- names(top(df, "publisher", 5))
+df <- df %>% filter(publisher %in% top)
+
+spl <- split(df$subject_topic, df$publisher)
+x <- lapply(spl, function (x) {unlist(strsplit(x, ";"))})
+
+for (pn in names(x)) {
+  fnam <- gsub(" ", "_", pn)
+  write_xtable(x[[pn]], file = paste(output.folder, "subjecttopics", fnam, ".tab", sep = ""))
+}
 ```
@@
 ```
-
-PUBLISHER-TODO2: Fennican suurimpien tarkasteltavan ajanjakson julkaisijoiden (top-5) julkaisuprofiilin ja siinä mahdollisesti tapahtuvan muutoksen tutkiminen.
-Ts.
-julkaisumäärät aikajanalla (on jo osittain), lisäksi paperinkulutusvertailu.
-Tärkeänä kysymyksenä on mitä eri julkaisijat julkaisee.
-Tähän liittyen top-5 julkaisijoista voisi tuottaa julkaisujen yhteiset, julkaisijakohtaiset asiasanalistat (mitä asiasanoja yhden julkaisijan kaikista töistä löytyy) jotka voitaisiin sitten käsin ryhmitellä isompiin kategorioihin (esim.
-yliopistojulkaisu, uskonnollinen teksti, säädökset, kaunokirjallinen ja muut (tai vast.)).
-Näin pystyttäisiin puhumaan siitä minkälainen julkaisija on kyseessä, muuttuuko profiili asiasanojen esiintymisen mukaan aikajanalla sekä nähdä onko julkaisijoiden kohdalla tässä mitään eroja.
 

### 2016-07-01 inst/examples/manuscript-krakow.Rmd
ok

@@
 OK, see lists for
-  * [Frenckell Johan Christopher II](output.tables/subjecttopicsFrenckell,_Johan_Christopher_II.tab)
-  * [Frenckell Johan Christopher I](output.tables/Frenckell,_Johan_Christopher_I.tab)
-  * [Hansson Peter](output.tables/Hansson,_Peter.tab)
-  * [Londicer Georg Wilhelm](output.tables/Londicer,_Georg_Wilhelm.tab)
-  * [Wall Johan Larsson](output.tables/Wall,_Johan_Larsson.tab)
+
+  * [Frenckell Johan Christopher II](output.tables/subjecttopicsFrenckell_Johan_Christopher_II.tab)
+  * [Frenckell Johan Christopher I](output.tables/Frenckell_Johan_Christopher_I.tab)
+  * [Hansson Peter](output.tables/Hansson_Peter.tab)
+  * [Londicer Georg Wilhelm](output.tables/Londicer_Georg_Wilhelm.tab)
+  * [Wall Johan Larsson](output.tables/Wall_Johan_Larsson.tab)
 
@@
 for (pn in names(x)) {
-  fnam <- gsub(" ", "_", pn)
+  fnam <- gsub(",", "", gsub(" ", "_", pn))
   write_xtable(x[[pn]], file = paste(output.folder, "subjecttopics", fnam, ".tab", sep = ""))

### 2016-07-01 inst/examples/manuscript-krakow.Rmd
ok

@@
   * [Frenckell Johan Christopher II](output.tables/subjecttopicsFrenckell_Johan_Christopher_II.tab)
-  * [Frenckell Johan Christopher I](output.tables/Frenckell_Johan_Christopher_I.tab)
-  * [Hansson Peter](output.tables/Hansson_Peter.tab)
-  * [Londicer Georg Wilhelm](output.tables/Londicer_Georg_Wilhelm.tab)
-  * [Wall Johan Larsson](output.tables/Wall_Johan_Larsson.tab)
+  * [Frenckell Johan Christopher I](output.tables/subjecttopicsFrenckell_Johan_Christopher_I.tab)
+  * [Hansson Peter](output.tables/subjecttopicsHansson_Peter.tab)
+  * [Londicer Georg Wilhelm](output.tables/subjecttopicsLondicer_Georg_Wilhelm.tab)
+  * [Wall Johan Larsson](output.tables/subjecttopicsWall_Johan_Larsson.tab)
 

### 2016-07-01 inst/examples/manuscript-krakow.Rmd
Update manuscript-krakow.Rmd

@@
 Hartauskirjallisuudesta ks. Osmo Tiililä, Rukoilevaisten kirjoja, 1961.
+
+BOOKINFINLAND-TODO4
+
+Kielikohtainen vertailu myös lääketieteen osalta.
+Ajatuksena tässä on, että hartauskirjallisuutta on hyvä verrata tiedejulkaisemiseen.
+1800-luvun jukisuuteen kuuluu vahvasti tarina kansallisista tieteista (historia, suomen kieli, folkloristiikka jne), ja niissä suomenkielen nusu on aika hyvin selvitetty juttu.
+Sama koskee tiedejulkaisemista, mutta siinä argumentit olivat erilaiset.
+Tästä on Katja Huumon väitöskirja ”Perkeleen kieli”, jossa käydään laadullisen tutkimuksen kautta tieteen kielikiistoja 1800-luvulla.
+Ajattelen, että lääketieteen osalta asiasanat ovat ehkä kaikkein luotettavimmat, joten voisi tarkastella lääketiedettä ja verrata siihen hartauskirjallisuuteen.
+Hartauskirjallisuuden osaltahan pyrkimys suomeksi julkaisemiseen oli kovin vahva koska se tieto oli kansalle tärkeää.
+Lääketieteellinenkin tieto kansallistettiin, mutta myöhemmin.
+
+Eli: Fennicasta kaikki kirjallisuus, jossa asiasana lääketiede (muut lääkeaiheiset eivät välttämättä kuulu tähän, noita on muuten kummallisen vähän).
+Tätä pitää jatkaa mielellään vuoteen 1900 asti, tai ainakin yhtää pitkälle kuin hartauskirjojakin.
+
+Myös kaupungittain vertailu on kiinnostavaa, koska tuntuma on, että Turun ja Helsingin osalta ei latinan, ranskan ja saksankielista matskua pitäisi löytyä.
+Silloin vernakularisointi tapahtuu erityisesti muualla.
+
+Huumo, Katja. "Perkeleen kieli" : suomen kieli ja poliittisesti korrekti tiede 1800-luvulla, Helsinki : Suomen tiedeseura, 2005.
 

### 2016-07-02 inst/examples/manuscript-krakow.Rmd
Update manuscript-krakow.Rmd
Rmd update

@@
 
-Selvensin alle (Publisher analysis kohtaan): PUBLISHER-TODO1 ja PUBLISHER-TODO2.
-Aloitetaan näiden työstäminen niin pian kuin mahdollista.
-Lisäksi tuolla paljon näistä riippumattomia (kuin myös näistä riippuvia) analyysiajatuksia.
+Selvensin alle (Publisher analysis kohtaan): PUBLISHER-TODO1 ja PUBLISHER-TODO2. Lisäksi tuolla paljon näistä riippumattomia (kuin myös näistä riippuvia) analyysiajatuksia.
 
@@
 
-Eli ehdottaisin että analyysivaihe johon nyt siirrytään, niin Leo jos ehdit, niin aloita noilla BOOKINFINLAND-TODOilla ja kun julkaisijakenttä tsekattu varmasti loppuun, niin heti Publisher analysis kohtaan ja PUBLISHER-TODOt.
+Eli ehdottaisin että analyysivaihe johon nyt siirrytään, aloita BOOKINFINLAND-TODOilla ja kun julkaisijakenttä tsekattu varmasti loppuun, niin heti Publisher analysis kohtaan ja PUBLISHER-TODOt.
 Samalla Marjanen ja minä siivotaan näitä muita analyysi-ideoita toteuttamiskelpoisiksi ohjeiksi.
@@
 Thus, development of publishing in Finland is much slower compared to larger European centers in the eighteenth century – this is an important context for the even further difficulties that follow after 1828.
+
+```{r drop1700B, echo=FALSE, message=FALSE, warning=FALSE, fig.width=9, fig.height=6, out.width="280px"}
+
+```
 
@@
 
+PUBLISHER-TODO NEXT: julkaisioiden osalta  Kungligan aineiston osalta samat analyysit Tukholmasta, Lundista, Uppsalasta ja Gerifswaldista. Tämä mahdollistaa Turun sijoittamisen kontekstiin.
+
 PUBLISHER-TODO(jos ehtii): Fennican julkaisijoita voisi myös laajemmin yrittää luokitella suhteellisesti (“iso”,

### 2016-07-02 inst/examples/manuscript-krakow.Rmd
Rmd update

@@
 
+The following figure highlights publisher title count changes around 1700 drop in Turku, the most significant publishing place at the time:
+
 ```{r drop1700B, echo=FALSE, message=FALSE, warning=FALSE, fig.width=9, fig.height=6, out.width="280px"}
-
-```
-
-TODO: try check duplicates. Clustering with identical place, identical year, near identical title and then print table with potential duplicates for manual checks.
+catalogue <- "Fennica"
+place <- "Turku"
+
+df <- df0
+df <- df %>%
+        filter(catalog == catalogue & publication_place == place) %>%
+        filter(publication_year >= 1650 & publication_year < 1750)
+
+# Selected ones
+top <- names(top(df, "publisher", 5))
+df$publisher[!df$publisher %in% top] <- "Other"
+df$publisher <- factor(df$publisher, levels = c(top, "Other"))
+
+# Publishing per year & publisher	
+npub <- df %>%
+     	  group_by(publication_year, publisher) %>%
+	  summarize(paper = sum(paper.consumption.km2, na.rm = TRUE), n = n())
+
+theme_set(theme_bw(20))
+p <- ggplot(npub, aes(x = publication_year, y = n, group = publisher)) +
+       #geom_bar(stat = "identity", position = "dodge", aes(fill = publisher)) + 
+       geom_point(size = 5, aes(shape = publisher, color = publisher)) +
+       #geom_line(col = "black", aes(shape = publisher)) +       
+       geom_smooth(col = "black", aes(shape = publisher, fill = publisher, color = publisher)) + 
+       xlab("Publication year") +
+       ylab("Title count (n)") +
+       ylim(c(0, 1.1*max(npub$n))) +
+       ggtitle(paste("Title count (", place, "/", catalogue, ")", sep = ""))
+print(p)
+```
+
+Here the same for the complete Fennica:
+
+```{r summaryTop10pubtimeline, fig.height=10, fig.width=20, echo=FALSE}
+df <- filter(df0, catalog == "Fennica")
+theme_set(theme_bw(20))
+tops <- names(top(df, field = "publisher", n = 5))
+field <- "publisher"
+dfs <- df
+dfs$field <- dfs[[field]]
+dfs <- dfs %>% filter(field %in% tops) %>%
+     	 group_by(field, publication_decade) %>%
+     	 tally() %>%
+     	 arrange(publication_decade)
+p <- ggplot(dfs, aes(x = publication_decade, y = n, fill = field)) +
+       geom_bar(stat = "identity", position = "stack", color = "black") +
+       xlab("Publication Decade") +
+       ylab("Title Count") +
+       scale_fill_grey() +
+       guides(fill = guide_legend("field")) +
+       ggtitle("Title count timeline for the top publishers in Fennica")
+print(p)
+```
+
+TODO: try check duplicates.
+Clustering with identical place, identical year, near identical title and then print table with potential duplicates for manual checks.
+- LL: you mean something different from what HR already did ?
+Duplicates within Fennica, or duplicates between Fennica vs Kungliga ?
+To be removed from all analyses, or a specific figure ?
+
+Paper per title count ratio per publisher. [nähdään voidaanko sanoa onko joku selkeästi asetusten julkaisija ja toisella myös kirjoja (tai asetuskokoelmia).]
+
+```{r publisherpapertitle, echo=FALSE, message=FALSE, warning=FALSE, fig.width=9, fig.height=6, out.width="430px", fig.show="hold"}
+for (catalogue in c("Fennica", "Kungliga")) {
+
+df <- df0
+df <- df %>%
+        filter(catalog == catalogue) %>%
+	filter(publication_year >= 1640 & publication_year <= 1828)
+
+# Selected ones
+top <- names(top(df, "publisher", 5))
+df$publisher[!df$publisher %in% top] <- "Other"
+df$publisher <- factor(df$publisher, levels = c(top, "Other"))
+
+# Publishing per decade & publisher	
+npub <- df %>%
+     	  group_by(publication_decade, publisher) %>%
+	  summarize(paper = sum(paper.consumption.km2, na.rm = TRUE), n = n()) %>%
+	  mutate(paper.per.title = paper/n)
+
+theme_set(theme_bw(20))
+p <- ggplot(npub, aes(x = publication_decade, y = paper.per.title, group = publisher)) +
+       #geom_bar(stat = "identity", position = "dodge", aes(fill = publisher)) + 
+       geom_point(size = 5, aes(shape = publisher, color = publisher)) +
+       #geom_line(col = "black", aes(shape = publisher)) +       
+       geom_smooth(col = "black", aes(shape = publisher, fill = publisher, color = publisher)) + 
+       xlab("Publication year") +
+       ylab("Paper per title") +
+       ylim(c(0, 1.1*max(npub$paper.per.title))) +
+       ggtitle(paste("Paper per title ratio (", catalogue, ")", sep = ""))
+print(p)
+}
+```
 
 ### General trends: Fennica vs. Kungliga
-
-Relevant summaries can be moved here and polished. Which figures at least ? Just let me know and I will add.
 
@@
 
- https://github.com/rOpenGov/fennica/blob/master/inst/examples/author.md täältä top-author timelinen molemmista Fennicasta ja Kungligasta vierekkäin.
+Top-author timelines.
 Putsaus ok (näistä tsekattu, että ei löydy ainakaan isoa määrää laskuista puuttuvia nimivariantilla julkaistuja teoksia).
-Pointtina tässä on, että Kungligassa väitöskirjat näyttelevät huomattavasti pienempää osaa kuin Fennicassa.
+Kungligassa väitöskirjat näyttelevät huomattavasti pienempää osaa kuin Fennicassa.
 Näkyy näistä top-auktori kuvista.
 
- Tämä kuva Fennica Summarysta on hyvä publisher analyysiin:
-
-https://raw.githubusercontent.com/rOpenGov/fennica/master/inst/examples/figure/summaryTop10pubtimeline-1.png
-
-Voisiko tästä julkaisijoiden title vs.
-paper countista laskea jonkun suhdeluvun per julkaisija?
-Idea että nähdään voidaanko sanoa onko joku selkeästi asetusten julkaisija ja toisella myös kirjoja (tai asetuskokoelmia).
-
-Tuolla Fennica yhteenvedoissa on myös ##EDITIONS kohta. Siellä ei kuitenkaan ole mitään kuvia. Olisiko ne mahdollista saada? On nimittäin mielenkiintoinen kysymys:
-
-https://github.com/rOpenGov/fennica/blob/master/inst/examples/publicationyear.md
+```{r summaryTop10authorstimeline, fig.height=10, fig.width=20, echo=FALSE, fig.show="hold", out.width="430px"}
+theme_set(theme_bw(20))
+for (catalogue in c("Fennica", "Kungliga")) {
+  df <- filter(df0, catalog == catalogue)
+  top.authors <- names(top(df, field = "author", n = 3))
+  dfs <- df %>% filter(author %in% top.authors) %>%
+     	 group_by(author, publication_decade) %>%
+     	 tally() %>%
+     	 arrange(publication_decade)
+  p <- ggplot(dfs, aes(x = publication_decade, y = n, fill = author)) +
+       geom_bar(stat = "identity", position = "stack", color = "black") +
+       xlab("Publication Decade") +
+       ylab("Title Count") +
+       scale_fill_grey() +
+       guides(fill = guide_legend("Author")) +
+       ggtitle(paste("Title count top authors\n", catalogue)) +
+       xlim(range(df0$publication_year))
+  print(p)
+}
+```
+
+Fennica yhteenvedoissa on myös EDITIONS kohta.
+Siellä ei kuitenkaan ole mitään kuvia.
+Olisiko ne mahdollista saada?
+On nimittäin mielenkiintoinen kysymys.
+LL: ok lisasin tan sinne - voin elaboroida lisaa jos on ehdotuksia:
+
+```{r firsteditions, echo=FALSE, message=FALSE, warning=FALSE, fig.width=9, fig.height=6, out.width="430px", fig.show="hold"}
+for (catalogue in c("Fennica", "Kungliga")) {
+df <- df0
+df <- df %>%
+        filter(catalog == catalogue) %>%
+	filter(publication_year >= 1640 & publication_year <= 1828)
+
+df <- df %>% group_by(publication_decade) %>%
+             summarise(n = sum(first_edition, na.rm = TRUE))
+theme_set(theme_bw(20))
+p <- ggplot(df, aes(x = publication_decade, y = n)) +
+       geom_point(size = 5) +
+       geom_smooth(col = "black") + 
+       xlab("Publication year") +
+       ylab("Title count (n)") +
+       ggtitle(paste("First editions per decade (", catalogue, ")", sep = ""))
+print(p)
+}
+```
 
@@
 miten Turun yliopiston perustaminen vaikuttaa ruotsalaiseen
-julkaisukenttään 1600-luvun aikana. I can provide percentages instead
+julkaisukenttään 1600-luvun aikana.
+
+I can provide percentages instead
 of counts, or paper consumption estimates (not reliable yet, though),
@@
 
-mitä voidaan sanoa suomalaisesta kirjatuotannosta ylipäänsä sekä
+Mitä voidaan sanoa suomalaisesta kirjatuotannosta ylipäänsä sekä
 löydetäänkö sieltä mitään mielenkiintoisia kehityskulkuja ylipäänsä

### 2016-07-02 inst/examples/manuscript-krakow.Rmd
ok

@@
 
-```{r drop1700B, echo=FALSE, message=FALSE, warning=FALSE, fig.width=9, fig.height=6, out.width="280px"}
+```{r drop1700B, echo=FALSE, message=FALSE, warning=FALSE, fig.width=15, fig.height=7}
 catalogue <- "Fennica"
@@
 
-```{r publisherpapertitle, echo=FALSE, message=FALSE, warning=FALSE, fig.width=9, fig.height=6, out.width="430px", fig.show="hold"}
+```{r publisherpapertitle, echo=FALSE, message=FALSE, warning=FALSE, fig.width=14, fig.height=6, out.width="430px", fig.show="hold"}
 for (catalogue in c("Fennica", "Kungliga")) {
@@
 
-```{r summaryTop10authorstimeline, fig.height=10, fig.width=20, echo=FALSE, fig.show="hold", out.width="430px"}
+```{r summaryTop10authorstimeline, fig.height=6, fig.width=10, echo=FALSE, fig.show="hold", out.width="430px"}
 theme_set(theme_bw(20))

### 2016-07-02 inst/examples/manuscript-krakow.Rmd
Update manuscript-krakow.Rmd

@@
 
+PUBLISHER-TODO: julkaisijakuvat jotka edellä, samat kuin Fennica Kungligalle.
+
 Tärkeänä kysymyksenä on mitä eri julkaisijat julkaisee. Top-5
@@
 ```
+PUBLISHER-TODO: julkaisijakuvat jotka edellä, samat kuin Fennica Kungligalle.
 

### 2016-07-03 inst/examples/manuscript-krakow.Rmd
ok

@@
 # Read data
-fen <- readRDS("df.Rds")
-kun <- readRDS("../../../kungliga/df.Rds")
+fen0 <- readRDS("df.Rds")
+kun0 <- readRDS("../../../kungliga/df.Rds")
 
@@
 
-fen <- fen %>% filter(publication_year >= min.year & publication_year <= max.year)
-kun <- kun %>% filter(publication_year >= min.year & publication_year <= max.year)
+fen <- fen0 %>% filter(publication_year >= min.year & publication_year <= max.year)
+kun <- kun0 %>% filter(publication_year >= min.year & publication_year <= max.year)
+
+# Full time span
+df.full = bind_rows(fen0, kun0)
+df.full$catalog = factor(c(rep("Fennica", nrow(fen0)), rep("Kungliga", nrow(kun0))))
+
+# Selected time spam
 df0 = bind_rows(fen, kun)
@@
 
-Selvensin alle (Publisher analysis kohtaan): PUBLISHER-TODO1 ja PUBLISHER-TODO2. Lisäksi tuolla paljon näistä riippumattomia (kuin myös näistä riippuvia) analyysiajatuksia.
-
-Muiden osalta (eli sellaisista joita voi tehdä jo nyt ilman publisher kenttää), järjestys voisi olla: **Book printing in Finland** - kohdasta
+Selvensin alle (Publisher analysis kohtaan): PUBLISHER-TODO1 ja
+PUBLISHER-TODO2. Lisäksi löytyy muita ajatuksia.
+
+Muiden osalta (voi tehdä jo ilman publisher kenttää), järjestys: **Book printing in Finland** - kohdasta
   * BOOKINFINLAND-TODO1 ja
@@
 
-Eli ehdottaisin että analyysivaihe johon nyt siirrytään, aloita BOOKINFINLAND-TODOilla ja kun julkaisijakenttä tsekattu varmasti loppuun, niin heti Publisher analysis kohtaan ja PUBLISHER-TODOt.
+Eli aloita BOOKINFINLAND-TODOilla ja kun julkaisijakenttä tsekattu, niin heti Publisher analysis kohtaan ja PUBLISHER-TODOt.
 Samalla Marjanen ja minä siivotaan näitä muita analyysi-ideoita toteuttamiskelpoisiksi ohjeiksi.
@@
 
-Fennica yhteenvedoissa on myös EDITIONS kohta.
-Siellä ei kuitenkaan ole mitään kuvia.
-Olisiko ne mahdollista saada?
-On nimittäin mielenkiintoinen kysymys.
-LL: ok lisasin tan sinne - voin elaboroida lisaa jos on ehdotuksia:
+Fennica yhteenvedoissa on EDITIONS kohta. Kuvia mahdollista saada? On nimittäin mielenkiintoinen kysymys. LL: ok lisasin tan sinne - voin elaboroida lisaa jos on ehdotuksia:
 
@@
 
-BOOKINFINLAND-TODO1: Kielikohtainen yleinen vertailu julkaisumääristä ja paperinkulutuksesta.
+Kielikohtainen yleinen vertailu julkaisumääristä ja paperinkulutuksesta.
 Eli kaksi kuvaa (julkaisumäärät ja paperinkulutus kielittäin).
+Miten kielten kehitys suhtautuu toisiinsa (suomi kasvaa, latina laskee jne.)?
 Tarkkailtavia kielikategorioita on 5: suomi, ruotsi, latina, saksa sekä kategoria jossa kaikki muun kielisiset kuin edellä mainitut niputetaan yhteen.
-Tarkoituksena tarkkailla miten kielten kehitys suhtautuu toisiinsa (suomi kasvaa, latina laskee jne.).
-Tärkeää on vertailu, mutta myös että nähdään kielikohtainen kehitys.
-Täten esim.
-pienemmän saksankielen kohdalla kannattaa varmaan piirtää erillinen kuva.
+
+```{r language1, echo=FALSE, message=FALSE, warning=FALSE, fig.width=14, fig.height=6, out.width="430px"}
+# TITLE COUNT
+for (catalogue in c("Fennica", "Kungliga")) {
+
+  df <- df0
+  df <- df %>% filter(catalog == catalogue)
+
+langs <- c("Finnish", "Swedish", "Latin", "German", "Other")
+lang <- paste("language.", langs, sep = "")
+otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
+df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
+
+dfl <- NULL
+
+for (lan in lang) {
+
+  # Classify a document to the specifed language
+  # If document is assigned with languages, each case is considered
+  # so one doc may have multiple entries corresponding to different languages
+  # mean(rowSums(df[, lang]) == 1) # 93% Fennica docs have just 1 language
+  # Combine data frames for specified languages
+  dflsub <- filter(df, df[[lan]])
+  dflsub$language <- gsub("language.", "", lan)
+  dfl <- bind_rows(dfl, dflsub)
+
+}
+dfl$language <- factor(dfl$language, levels = langs)
+
+df <- dfl %>% group_by(publication_decade, language) %>%
+             summarise(n = n(),
+	               paper = sum(paper.consumption.km2, na.rm = TRUE))
+
+theme_set(theme_bw(20))
+p <- ggplot(df, aes(x = publication_decade, y = n, group = language)) +
+       #geom_bar(stat = "identity", position = "dodge", aes(fill = publisher)) + 
+       geom_point(aes(col = language, shape = language), size = 5) +
+       geom_line(aes(col = language, shape = language)) +       
+       # geom_smooth(aes(col = language)) + 
+       xlab("Publication year") +
+       ylab("Title count (n)") +
+       # ylim(c(0, 1.1*max(npub$paper.per.title))) +
+       ggtitle(paste("Languages (", catalogue, ")", sep = ""))
+print(p)
+
+# PAPER CONSUMPTION
+
+theme_set(theme_bw(20))
+p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
+       #geom_bar(stat = "identity", position = "dodge", aes(fill = publisher)) + 
+       geom_point(aes(col = language, shape = language), size = 5) +
+       geom_line(aes(col = language, shape = language)) +       
+       # geom_smooth(aes(col = language)) + 
+       xlab("Publication year") +
+       ylab("Paper consumption") +
+       # ylim(c(0, 1.1*max(npub$paper.per.title))) +
+       ggtitle(paste("Languages (", catalogue, ")", sep = ""))
+print(p)
+
+}
+```
+
 Analyysi voi tapahtua aikajanalla, mutta voisi myös ajatella suhteellista kehitystä tässä jollain muulla esitystavalla, olisiko se sitten jonkinlainen prosenttianalyysi?
 Tämä analyysi kannattaa jatkaa myös pidemmälle kuin 1828 Fennican osalta.
+
+```{r language-perc, echo=FALSE, message=FALSE, warning=FALSE, fig.width=14, fig.height=6, out.width="430px"}
+# TITLE COUNT
+for (catalogue in c("Fennica", "Kungliga")) {
+
+  if (catalogue == "Fennica") {
+    df <- df.full # full time span
+  } else if (catalogue == "Kungliga") {
+    df <- df0 # selected time span
+  }
+
+  df <- df %>% filter(catalog == catalogue)
+
+langs <- c("Finnish", "Swedish", "Latin", "German", "Other")
+lang <- paste("language.", langs, sep = "")
+otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
+df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
+
+dfl <- NULL
+
+for (lan in lang) {
+
+  # Classify a document to the specifed language
+  # If document is assigned with languages, each case is considered
+  # so one doc may have multiple entries corresponding to different languages
+  # mean(rowSums(df[, lang]) == 1) # 93% Fennica docs have just 1 language
+  # Combine data frames for specified languages
+  dflsub <- filter(df, df[[lan]])
+  dflsub$language <- gsub("language.", "", lan)
+  dfl <- bind_rows(dfl, dflsub)
+
+}
+dfl$language <- factor(dfl$language, levels = langs)
+
+df <- dfl %>% group_by(publication_decade, language) %>%
+     	     summarise(n = n())
+
+# Calculate percentages
+dff <- spread(df, language, n, fill = 0)
+dff[, -1] <- 100 * t(apply(dff[, -1], 1, function (x) {x/sum(x)}))
+dff <- gather(dff, publication_decade);
+colnames(dff) <- c("publication_decade", "language", "f")
+# Order languages by title count over the complete time span 
+# (same ordering used with both catalogs)
+dff$language <- factor(dff$language, levels = langs)
+
+theme_set(theme_bw(20))
+p <- ggplot(dff, aes(x = publication_decade, y = f)) +
+     geom_bar(position = "stack", stat = "identity", aes(fill = language)) + 
+     xlab("Publication year") +
+     ylab("Title count frequency (%)") +
+     ggtitle(paste("Languages (", catalogue, ")", sep = ""))
+print(p)
+
+}
+```
+
+Tärkeää on vertailu, mutta myös että nähdään kielikohtainen kehitys. Täten esim. pienemmän saksankielen kohdalla kannattaa varmaan piirtää erillinen kuva.
+
+```{r language-sel, echo=FALSE, message=FALSE, warning=FALSE, fig.width=14, fig.height=6, out.width="430px"}
+# TITLE COUNT
+for (catalogue in c("Fennica", "Kungliga")) {
+
+  df <- df0
+  df <- df %>% filter(catalog == catalogue)
+
+langs <- c("Finnish", "Swedish", "Latin", "German", "Other")
+lang <- paste("language.", langs, sep = "")
+otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
+df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
+
+dfl <- NULL
+
+for (lan in lang) {
+
+  # Classify a document to the specifed language
+  # If document is assigned with languages, each case is considered
+  # so one doc may have multiple entries corresponding to different languages
+  # mean(rowSums(df[, lang]) == 1) # 93% Fennica docs have just 1 language
+  # Combine data frames for specified languages
+  dflsub <- filter(df, df[[lan]])
+  dflsub$language <- gsub("language.", "", lan)
+  dfl <- bind_rows(dfl, dflsub)
+
+}
+dfl$language <- factor(dfl$language, levels = langs)
+
+df <- dfl %>% group_by(publication_decade, language) %>%
+             summarise(n = n(),
+	               paper = sum(paper.consumption.km2, na.rm = TRUE))
+
+for (sel.lan in "German") {
+
+dfs <- filter(df, language == sel.lan)
+
+theme_set(theme_bw(20))
+p <- ggplot(dfs, aes(x = publication_decade, y = n)) +
+       geom_point(size = 5) +
+       geom_line() +       
+       xlab("Publication year") +
+       ylab("Title count (n)") +
+       ggtitle(paste("Languages (", sel.lan, "/", catalogue, ")", sep = ""))       
+print(p)
+
+# PAPER CONSUMPTION
+
+theme_set(theme_bw(20))
+p <- ggplot(dfs, aes(x = publication_decade, y = paper)) +
+       geom_point(size = 5) +
+       geom_line() +       
+       xlab("Publication year") +
+       ylab("Paper consumption") +
+       ggtitle(paste("Languages (", sel.lan, "/", catalogue, ")", sep = ""))
+print(p)
+
+}
+}
+```
 

### 2016-07-03 inst/examples/manuscript-krakow.Rmd
ok

@@
 
-```{r publisherpapertitle, echo=FALSE, message=FALSE, warning=FALSE, fig.width=14, fig.height=6, out.width="430px", fig.show="hold"}
+```{r publisherpapertitle, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, out.width="430px", fig.show="hold"}
 for (catalogue in c("Fennica", "Kungliga")) {
@@
 
-```{r summaryTop10authorstimeline, fig.height=6, fig.width=10, echo=FALSE, fig.show="hold", out.width="430px"}
+```{r summaryTop10authorstimeline, fig.height=4, fig.width=10, echo=FALSE, fig.show="hold", out.width="430px"}
 theme_set(theme_bw(20))
@@
 
-```{r language1, echo=FALSE, message=FALSE, warning=FALSE, fig.width=14, fig.height=6, out.width="430px"}
+```{r language1, echo=FALSE, message=FALSE, warning=FALSE, fig.width=14, fig.height=6, out.width="430px", fig.show="hold"}
 # TITLE COUNT
@@
 
-```{r language-perc, echo=FALSE, message=FALSE, warning=FALSE, fig.width=14, fig.height=6, out.width="430px"}
+```{r language-perc, echo=FALSE, message=FALSE, warning=FALSE, fig.width=14, fig.height=6, out.width="430px", fig.show="hold"}
 # TITLE COUNT
@@
 
-```{r language-sel, echo=FALSE, message=FALSE, warning=FALSE, fig.width=14, fig.height=6, out.width="430px"}
+```{r language-sel, echo=FALSE, message=FALSE, warning=FALSE, fig.width=14, fig.height=6, out.width="430px", fig.show="hold"}
 # TITLE COUNT

### 2016-07-03 inst/examples/manuscript-krakow.Rmd
ok

@@
 
-```{r language1, echo=FALSE, message=FALSE, warning=FALSE, fig.width=14, fig.height=6, out.width="430px", fig.show="hold"}
+```{r language1, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, out.width="430px", fig.show="hold"}
 # TITLE COUNT
@@
 
-```{r language-perc, echo=FALSE, message=FALSE, warning=FALSE, fig.width=14, fig.height=6, out.width="430px", fig.show="hold"}
+```{r language-perc, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, out.width="430px", fig.show="hold"}
 # TITLE COUNT
@@
 
-df <- dfl %>% group_by(publication_decade, language) %>%
+df <- dfl %>% group_by(publication_year, language) %>%
              summarise(n = n(),
@@
 theme_set(theme_bw(20))
-p <- ggplot(dfs, aes(x = publication_decade, y = n)) +
-       geom_point(size = 5) +
-       geom_line() +       
+p <- ggplot(dfs, aes(x = publication_year, y = n)) +
+       geom_point(size = 2) +
+       #geom_line() +
+       geom_smooth(col = "black") +              
        xlab("Publication year") +
@@
 theme_set(theme_bw(20))
-p <- ggplot(dfs, aes(x = publication_decade, y = paper)) +
-       geom_point(size = 5) +
-       geom_line() +       
+p <- ggplot(dfs, aes(x = publication_year, y = paper)) +
+       geom_point(size = 2) +
+       #geom_line() +
+       geom_smooth(col = "black") +              
        xlab("Publication year") +

### 2016-07-03 inst/examples/manuscript-krakow.Rmd
ok

@@
 
-```{r language-sel, echo=FALSE, message=FALSE, warning=FALSE, fig.width=14, fig.height=6, out.width="430px", fig.show="hold"}
+```{r language-sel, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, out.width="430px", fig.show="hold"}
 # TITLE COUNT
@@
 kirjallisuuden kieli (suomi vai ruotsi) milloin alkaa yleistyä suomenkielinen ja miten tämän julkaiseminen suomeksi kasvaa?
-Toteutus, valitaan kaikki teokset joihin liittyy joku seuraavista asiasanoista:
-
-virret;arkkiveisut;hartauskirjat;katekismukset;rukouspäivät;saarnat;aapiset;rukoukset;rukous;hengelliset laulut;hartauspuheet;virsikirjat
-
+Toteutus, valitaan kaikki teokset joihin liittyy joku seuraavista asiasanoista: virret;arkkiveisut;hartauskirjat;katekismukset;rukouspäivät;saarnat;aapiset;rukoukset;rukous;hengelliset laulut;hartauspuheet;virsikirjat.
 Tämän jälkeen tarkkaillaan aikajanalla näiden teosten esiintymistä, erottavana tekijänä kieli (samat 5 kategoriaa kuin edellisessä analyysissä).
-Erilaisia tarkkailukulmia: 1) yleinen, 2) paikkakunta sekä 3) julkaisijakohtainen kehitys (sitten kun mahdollista).
-
+Erilaisia tarkkailukulmia.
 Tämä analyysi kannattaa jatkaa myös pidemmälle kuin 1828 Fennican osalta.
+
+NOTE: Kungliga is missing those subject topics hence skipped.
+
+1. General analysis with all documents combined:
+
+```{r topics, echo=FALSE, message=FALSE, warning=FALSE, fig.width=14, fig.height=6, out.width="430px", fig.show="hold"}
+# TITLE COUNT
+catalogue <- "Fennica"
+
+  if (catalogue == "Fennica") {
+    df <- df.full # full time span
+  } else if (catalogue == "Kungliga") {
+    df <- df0 # selected time span
+  }
+
+  df <- df %>% filter(catalog == catalogue & subject_topic %in% sel)
+
+langs <- c("Finnish", "Swedish", "Latin", "German", "Other")
+lang <- paste("language.", langs, sep = "")
+otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
+df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
+
+dfl <- NULL
+
+for (lan in lang) {
+
+  # Classify a document to the specifed language
+  # If document is assigned with languages, each case is considered
+  # so one doc may have multiple entries corresponding to different languages
+  # mean(rowSums(df[, lang]) == 1) # 93% Fennica docs have just 1 language
+  # Combine data frames for specified languages
+  dflsub <- filter(df, df[[lan]])
+  dflsub$language <- gsub("language.", "", lan)
+  dfl <- bind_rows(dfl, dflsub)
+
+}
+dfl$language <- factor(dfl$language, levels = langs)
+
+df <- dfl %>% group_by(publication_decade, language) %>%
+             summarise(n = n(),
+	               paper = sum(paper.consumption.km2, na.rm = TRUE))
+
+theme_set(theme_bw(20))
+p <- ggplot(df, aes(x = publication_decade, y = n, group = language)) +
+       #geom_bar(stat = "identity", position = "dodge", aes(fill = publisher)) + 
+       geom_point(aes(col = language, shape = language), size = 5) +
+       geom_line(aes(col = language, shape = language)) +       
+       # geom_smooth(aes(col = language)) + 
+       xlab("Publication year") +
+       ylab("Title count (n)") +
+       # ylim(c(0, 1.1*max(npub$paper.per.title))) +
+       ggtitle(paste("Languages (", catalogue, ")", sep = ""))
+print(p)
+
+# PAPER CONSUMPTION
+
+theme_set(theme_bw(20))
+p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
+       #geom_bar(stat = "identity", position = "dodge", aes(fill = publisher)) + 
+       geom_point(aes(col = language, shape = language), size = 5) +
+       geom_line(aes(col = language, shape = language)) +       
+       # geom_smooth(aes(col = language)) + 
+       xlab("Publication year") +
+       ylab("Paper consumption") +
+       # ylim(c(0, 1.1*max(npub$paper.per.title))) +
+       ggtitle(paste("Languages (", catalogue, ")", sep = ""))
+print(p)
+```
+
+2. Selected publication places
+
+```{r topics.per.place, echo=FALSE, message=FALSE, warning=FALSE, fig.width=14, fig.height=6, out.width="430px", fig.show="hold"}
+
+for (place in c("Turku", "Stockholm", "Vaasa")) {
+catalogue <- "Fennica"
+
+  if (catalogue == "Fennica") {
+    df <- df.full # full time span
+  } else if (catalogue == "Kungliga") {
+    df <- df0 # selected time span
+  }
+
+  sel <- c("virret","arkkiveisut","hartauskirjat","katekismukset","rukouspäivät","saarnat","aapiset","rukoukset","rukous","hengelliset laulut","hartauspuheet","virsikirjat")
+  df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)  
+  df <- df %>% filter(catalog == catalogue & hit & publication_place == place)
+
+langs <- c("Finnish", "Swedish", "Latin", "German", "Other")
+lang <- paste("language.", langs, sep = "")
+otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
+df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
+
+dfl <- NULL
+
+for (lan in lang) {
+
+  # Classify a document to the specifed language
+  # If document is assigned with languages, each case is considered
+  # so one doc may have multiple entries corresponding to different languages
+  # mean(rowSums(df[, lang]) == 1) # 93% Fennica docs have just 1 language
+  # Combine data frames for specified languages
+  dflsub <- filter(df, df[[lan]])
+  if (nrow(dflsub) > 0) {
+    dflsub$language <- gsub("language.", "", lan)
+    dfl <- bind_rows(dfl, dflsub)
+  }
+}
+dfl$language <- factor(dfl$language, levels = langs)
+
+df <- dfl %>% group_by(publication_decade, language) %>%
+             summarise(n = n(),
+	               paper = sum(paper.consumption.km2, na.rm = TRUE))
+
+df$language <- factor(df$language, levels = names(table(df$language)))
+
+# TITLE COUNT
+theme_set(theme_bw(20))
+p <- ggplot(df, aes(x = publication_decade, y = n, group = language)) +
+       #geom_bar(stat = "identity", position = "dodge", aes(fill = publisher)) + 
+       geom_point(aes(col = language, shape = language), size = 5) +
+       geom_line(aes(col = language, shape = language)) +       
+       # geom_smooth(aes(col = language)) + 
+       xlab("Publication year") +
+       ylab("Title count (n)") +
+       # ylim(c(0, 1.1*max(npub$paper.per.title))) +
+       ggtitle(paste("Languages (", catalogue, ")", sep = ""))
+print(p)
+
+# PAPER CONSUMPTION
+
+theme_set(theme_bw(20))
+p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
+       #geom_bar(stat = "identity", position = "dodge", aes(fill = publisher)) + 
+       geom_point(aes(col = language, shape = language), size = 5) +
+       geom_line(aes(col = language, shape = language)) +       
+       # geom_smooth(aes(col = language)) + 
+       xlab("Publication year") +
+       ylab("Paper consumption") +
+       # ylim(c(0, 1.1*max(npub$paper.per.title))) +
+       ggtitle(paste("Languages (", catalogue, ")", sep = ""))
+print(p)
+
+}
+```
+
+3. Top publishers
+
+```{r topics.per.publisher, echo=FALSE, message=FALSE, warning=FALSE, fig.width=14, fig.height=6, out.width="430px", fig.show="hold"}
+
+tops <-  names(top(fen, "publisher", 5))
+
+for (publ in tops) {
+catalogue <- "Fennica"
+
+  if (catalogue == "Fennica") {
+    df <- df.full # full time span
+  } else if (catalogue == "Kungliga") {
+    df <- df0 # selected time span
+  }
+
+  sel <- c("virret","arkkiveisut","hartauskirjat","katekismukset","rukouspäivät","saarnat","aapiset","rukoukset","rukous","hengelliset laulut","hartauspuheet","virsikirjat")
+
+  df <- df %>% filter(catalog == catalogue & publisher == publ)
+
+langs <- c("Finnish", "Swedish", "Latin", "German", "Other")
+lang <- paste("language.", langs, sep = "")
+otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
+df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
+
+dfl <- NULL
+
+for (lan in lang) {
+
+  # Classify a document to the specifed language
+  # If document is assigned with languages, each case is considered
+  # so one doc may have multiple entries corresponding to different languages
+  # mean(rowSums(df[, lang]) == 1) # 93% Fennica docs have just 1 language
+  # Combine data frames for specified languages
+  dflsub <- filter(df, df[[lan]])
+  if (nrow(dflsub) > 0) {
+    dflsub$language <- gsub("language.", "", lan)
+    dfl <- bind_rows(dfl, dflsub)
+  }
+}
+dfl$language <- factor(dfl$language, levels = langs)
+
+df <- dfl %>% group_by(publication_decade, language) %>%
+             summarise(n = n(),
+	               paper = sum(paper.consumption.km2, na.rm = TRUE))
+
+df$language <- factor(df$language, levels = names(table(df$language)))
+
+# TITLE COUNT
+theme_set(theme_bw(20))
+p <- ggplot(df, aes(x = publication_decade, y = n, group = language)) +
+       #geom_bar(stat = "identity", position = "dodge", aes(fill = publisher)) + 
+       geom_point(aes(col = language, shape = language), size = 5) +
+       geom_line(aes(col = language, shape = language)) +       
+       # geom_smooth(aes(col = language)) + 
+       xlab("Publication year") +
+       ylab("Title count (n)") +
+       # ylim(c(0, 1.1*max(npub$paper.per.title))) +
+       ggtitle(paste("Languages (", catalogue, ")", sep = ""))
+print(p)
+
+# PAPER CONSUMPTION
+
+theme_set(theme_bw(20))
+p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
+       #geom_bar(stat = "identity", position = "dodge", aes(fill = publisher)) + 
+       geom_point(aes(col = language, shape = language), size = 5) +
+       geom_line(aes(col = language, shape = language)) +       
+       # geom_smooth(aes(col = language)) + 
+       xlab("Publication year") +
+       ylab("Paper consumption") +
+       # ylim(c(0, 1.1*max(npub$paper.per.title))) +
+       ggtitle(paste("Languages (", catalogue, ")", sep = ""))
+print(p)
+
+}
+
+```
 

### 2016-07-03 inst/examples/manuscript-krakow.Rmd
ok

@@
 
-BOOKINFINLAND-TODO2: Fennica, Hartaus- yms.
+BOOKINFINLAND-DONE2: Fennica, Hartaus- yms.
 kirjallisuuden kieli (suomi vai ruotsi) milloin alkaa yleistyä suomenkielinen ja miten tämän julkaiseminen suomeksi kasvaa?
@@
 
-1. General analysis with all documents combined:
+General analysis with all documents combined:
 
 ```{r topics, echo=FALSE, message=FALSE, warning=FALSE, fig.width=14, fig.height=6, out.width="430px", fig.show="hold"}
-# TITLE COUNT
+sel <- c("virret","arkkiveisut","hartauskirjat","katekismukset","rukouspäivät","saarnat","aapiset","rukoukset","rukous","hengelliset laulut","hartauspuheet","virsikirjat")
 catalogue <- "Fennica"
-
   if (catalogue == "Fennica") {
@@
   }
-
-  df <- df %>% filter(catalog == catalogue & subject_topic %in% sel)
+  df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)
+
+# Selected catalogue with selected topics
+df <- df %>% filter(catalog == catalogue & hit)
 
@@
 df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
-
 dfl <- NULL
-
 for (lan in lang) {
-
   # Classify a document to the specifed language
@@
   dfl <- bind_rows(dfl, dflsub)
-
 }
 dfl$language <- factor(dfl$language, levels = langs)
+
+# -------------------------------------------
 
@@
 
+# TITLE COUNT
 theme_set(theme_bw(20))
@@
 
-2. Selected publication places
+Same with selected publication places:
 
@@
 for (place in c("Turku", "Stockholm", "Vaasa")) {
-catalogue <- "Fennica"
-
-  if (catalogue == "Fennica") {
-    df <- df.full # full time span
-  } else if (catalogue == "Kungliga") {
-    df <- df0 # selected time span
-  }
-
-  sel <- c("virret","arkkiveisut","hartauskirjat","katekismukset","rukouspäivät","saarnat","aapiset","rukoukset","rukous","hengelliset laulut","hartauspuheet","virsikirjat")
-  df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)  
-  df <- df %>% filter(catalog == catalogue & hit & publication_place == place)
-
-langs <- c("Finnish", "Swedish", "Latin", "German", "Other")
-lang <- paste("language.", langs, sep = "")
-otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
-df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
-
-dfl <- NULL
-
-for (lan in lang) {
-
-  # Classify a document to the specifed language
-  # If document is assigned with languages, each case is considered
-  # so one doc may have multiple entries corresponding to different languages
-  # mean(rowSums(df[, lang]) == 1) # 93% Fennica docs have just 1 language
-  # Combine data frames for specified languages
-  dflsub <- filter(df, df[[lan]])
-  if (nrow(dflsub) > 0) {
-    dflsub$language <- gsub("language.", "", lan)
-    dfl <- bind_rows(dfl, dflsub)
-  }
-}
-dfl$language <- factor(dfl$language, levels = langs)
-
-df <- dfl %>% group_by(publication_decade, language) %>%
+
+ df <- dfl %>% filter(publication_place == place)
+
+ df <- df %>% group_by(publication_decade, language) %>%
              summarise(n = n(),
@@
 
-3. Top publishers
+Same with top publishers
 
 ```{r topics.per.publisher, echo=FALSE, message=FALSE, warning=FALSE, fig.width=14, fig.height=6, out.width="430px", fig.show="hold"}
-
 tops <-  names(top(fen, "publisher", 5))
@@
 for (publ in tops) {
-catalogue <- "Fennica"
-
-  if (catalogue == "Fennica") {
-    df <- df.full # full time span
-  } else if (catalogue == "Kungliga") {
-    df <- df0 # selected time span
-  }
-
-  sel <- c("virret","arkkiveisut","hartauskirjat","katekismukset","rukouspäivät","saarnat","aapiset","rukoukset","rukous","hengelliset laulut","hartauspuheet","virsikirjat")
-
-  df <- df %>% filter(catalog == catalogue & publisher == publ)
-
-langs <- c("Finnish", "Swedish", "Latin", "German", "Other")
-lang <- paste("language.", langs, sep = "")
-otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
-df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
-
-dfl <- NULL
-
-for (lan in lang) {
-
-  # Classify a document to the specifed language
-  # If document is assigned with languages, each case is considered
-  # so one doc may have multiple entries corresponding to different languages
-  # mean(rowSums(df[, lang]) == 1) # 93% Fennica docs have just 1 language
-  # Combine data frames for specified languages
-  dflsub <- filter(df, df[[lan]])
-  if (nrow(dflsub) > 0) {
-    dflsub$language <- gsub("language.", "", lan)
-    dfl <- bind_rows(dfl, dflsub)
-  }
-}
-dfl$language <- factor(dfl$language, levels = langs)
-
-df <- dfl %>% group_by(publication_decade, language) %>%
-             summarise(n = n(),
-	               paper = sum(paper.consumption.km2, na.rm = TRUE))
+
+  df <- dfl %>% filter(publisher == publ)
+
+  df <- df %>% group_by(publication_decade, language) %>%
+             summarise(n = n(), paper = sum(paper.consumption.km2, na.rm = TRUE))
 
@@
 }
-
 ```

### 2016-07-03 inst/examples/manuscript-krakow.Rmd
ok

@@
 
-BOOKINFINLAND-DONE2: Fennica, Hartaus- yms.
+### BOOKINFINLAND-DONE2
+
+Fennica, Hartaus- yms.
 kirjallisuuden kieli (suomi vai ruotsi) milloin alkaa yleistyä suomenkielinen ja miten tämän julkaiseminen suomeksi kasvaa?
@@
 
-```{r topics, echo=FALSE, message=FALSE, warning=FALSE, fig.width=14, fig.height=6, out.width="430px", fig.show="hold"}
+```{r topics, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, out.width="430px", fig.show="hold"}
 sel <- c("virret","arkkiveisut","hartauskirjat","katekismukset","rukouspäivät","saarnat","aapiset","rukoukset","rukous","hengelliset laulut","hartauspuheet","virsikirjat")
@@
 
-```{r topics.per.place, echo=FALSE, message=FALSE, warning=FALSE, fig.width=14, fig.height=6, out.width="430px", fig.show="hold"}
+```{r topics.per.place, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, out.width="430px", fig.show="hold"}
 
@@
        # ylim(c(0, 1.1*max(npub$paper.per.title))) +
+       ggtitle(paste("Languages (", place, "/", catalogue, ")", sep = ""))
+print(p)
+
+# PAPER CONSUMPTION
+
+theme_set(theme_bw(20))
+p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
+       #geom_bar(stat = "identity", position = "dodge", aes(fill = publisher)) + 
+       geom_point(aes(col = language, shape = language), size = 5) +
+       geom_line(aes(col = language, shape = language)) +       
+       # geom_smooth(aes(col = language)) + 
+       xlab("Publication year") +
+       ylab("Paper consumption") +
+       # ylim(c(0, 1.1*max(npub$paper.per.title))) +
+       ggtitle(paste("Languages (", place, "/", catalogue, ")", sep = ""))
+print(p)
+
+}
+```
+
+Same with top publishers
+
+```{r topics.per.publisher, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, out.width="430px", fig.show="hold"}
+tops <-  names(top(fen, "publisher", 5))
+
+for (publ in tops) {
+
+  df <- dfl %>% filter(publisher == publ)
+
+  df <- df %>% group_by(publication_decade, language) %>%
+             summarise(n = n(), paper = sum(paper.consumption.km2, na.rm = TRUE))
+
+  df$language <- factor(df$language, levels = names(table(df$language)))
+
+# TITLE COUNT
+theme_set(theme_bw(20))
+p <- ggplot(df, aes(x = publication_decade, y = n, group = language)) +
+       #geom_bar(stat = "identity", position = "dodge", aes(fill = publisher)) + 
+       geom_point(aes(col = language, shape = language), size = 5) +
+       geom_line(aes(col = language, shape = language)) +       
+       # geom_smooth(aes(col = language)) + 
+       xlab("Publication year") +
+       ylab("Title count (n)") +
+       # ylim(c(0, 1.1*max(npub$paper.per.title))) +
+       ggtitle(paste("Languages (", publ, "/", catalogue, ")", sep = ""))
+print(p)
+
+# PAPER CONSUMPTION
+
+theme_set(theme_bw(20))
+p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
+       #geom_bar(stat = "identity", position = "dodge", aes(fill = publisher)) + 
+       geom_point(aes(col = language, shape = language), size = 5) +
+       geom_line(aes(col = language, shape = language)) +       
+       # geom_smooth(aes(col = language)) + 
+       xlab("Publication year") +
+       ylab("Paper consumption") +
+       # ylim(c(0, 1.1*max(npub$paper.per.title))) +
+       ggtitle(paste("Languages (", publ, "/", catalogue, ")", sep = ""))
+print(p)
+
+}
+```
+
+### BOOKINFINLAND-DONE3
+
+Sama kuin edellä, mutta asiasanat tässä: hautajaiset;häät;juhlamenot
+
+General analysis with all documents combined:
+
+```{r topics2, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, out.width="430px", fig.show="hold"}
+sel <- c("hautajaiset", "häät", "juhlamenot")
+
+catalogue <- "Fennica"
+  if (catalogue == "Fennica") {
+    df <- df.full # full time span
+  } else if (catalogue == "Kungliga") {
+    df <- df0 # selected time span
+  }
+  df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)
+
+# Selected catalogue with selected topics
+df <- df %>% filter(catalog == catalogue & hit)
+
+langs <- c("Finnish", "Swedish", "Latin", "German", "Other")
+lang <- paste("language.", langs, sep = "")
+otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
+df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
+dfl <- NULL
+for (lan in lang) {
+  # Classify a document to the specifed language
+  # If document is assigned with languages, each case is considered
+  # so one doc may have multiple entries corresponding to different languages
+  # mean(rowSums(df[, lang]) == 1) # 93% Fennica docs have just 1 language
+  # Combine data frames for specified languages
+  dflsub <- filter(df, df[[lan]])
+  dflsub$language <- gsub("language.", "", lan)
+  dfl <- bind_rows(dfl, dflsub)
+}
+dfl$language <- factor(dfl$language, levels = langs)
+
+# -------------------------------------------
+
+df <- dfl %>% group_by(publication_decade, language) %>%
+             summarise(n = n(),
+	               paper = sum(paper.consumption.km2, na.rm = TRUE))
+
+# TITLE COUNT
+theme_set(theme_bw(20))
+p <- ggplot(df, aes(x = publication_decade, y = n, group = language)) +
+       #geom_bar(stat = "identity", position = "dodge", aes(fill = publisher)) + 
+       geom_point(aes(col = language, shape = language), size = 5) +
+       geom_line(aes(col = language, shape = language)) +       
+       # geom_smooth(aes(col = language)) + 
+       xlab("Publication year") +
+       ylab("Title count (n)") +
+       # ylim(c(0, 1.1*max(npub$paper.per.title))) +
        ggtitle(paste("Languages (", catalogue, ")", sep = ""))
@@
 print(p)
+```
+
+Same with selected publication places:
+
+```{r topics2.per.place, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, out.width="430px", fig.show="hold"}
+
+for (place in c("Turku", "Stockholm", "Vaasa")) {
+
+ df <- dfl %>% filter(publication_place == place)
+
+ df <- df %>% group_by(publication_decade, language) %>%
+             summarise(n = n(),
+	               paper = sum(paper.consumption.km2, na.rm = TRUE))
+
+ df$language <- factor(df$language, levels = names(table(df$language)))
+
+# TITLE COUNT
+theme_set(theme_bw(20))
+p <- ggplot(df, aes(x = publication_decade, y = n, group = language)) +
+       #geom_bar(stat = "identity", position = "dodge", aes(fill = publisher)) + 
+       geom_point(aes(col = language, shape = language), size = 5) +
+       geom_line(aes(col = language, shape = language)) +       
+       # geom_smooth(aes(col = language)) + 
+       xlab("Publication year") +
+       ylab("Title count (n)") +
+       # ylim(c(0, 1.1*max(npub$paper.per.title))) +
+       ggtitle(paste("Languages (", place, "/", catalogue, ")", sep = ""))
+print(p)
+
+# PAPER CONSUMPTION
+
+theme_set(theme_bw(20))
+p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
+       #geom_bar(stat = "identity", position = "dodge", aes(fill = publisher)) + 
+       geom_point(aes(col = language, shape = language), size = 5) +
+       geom_line(aes(col = language, shape = language)) +       
+       # geom_smooth(aes(col = language)) + 
+       xlab("Publication year") +
+       ylab("Paper consumption") +
+       # ylim(c(0, 1.1*max(npub$paper.per.title))) +
+       ggtitle(paste("Languages (", place, "/", catalogue, ")", sep = ""))
+print(p)
 
@@
 
-```{r topics.per.publisher, echo=FALSE, message=FALSE, warning=FALSE, fig.width=14, fig.height=6, out.width="430px", fig.show="hold"}
+```{r topics2.per.publisher, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, out.width="430px", fig.show="hold"}
 tops <-  names(top(fen, "publisher", 5))
@@
   df$language <- factor(df$language, levels = names(table(df$language)))
+
+# TITLE COUNT
+theme_set(theme_bw(20))
+p <- ggplot(df, aes(x = publication_decade, y = n, group = language)) +
+       #geom_bar(stat = "identity", position = "dodge", aes(fill = publisher)) + 
+       geom_point(aes(col = language, shape = language), size = 5) +
+       geom_line(aes(col = language, shape = language)) +       
+       # geom_smooth(aes(col = language)) + 
+       xlab("Publication year") +
+       ylab("Title count (n)") +
+       # ylim(c(0, 1.1*max(npub$paper.per.title))) +
+       ggtitle(paste("Languages (", publ, "/", catalogue, ")", sep = ""))
+print(p)
+
+# PAPER CONSUMPTION
+
+theme_set(theme_bw(20))
+p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
+       #geom_bar(stat = "identity", position = "dodge", aes(fill = publisher)) + 
+       geom_point(aes(col = language, shape = language), size = 5) +
+       geom_line(aes(col = language, shape = language)) +       
+       # geom_smooth(aes(col = language)) + 
+       xlab("Publication year") +
+       ylab("Paper consumption") +
+       # ylim(c(0, 1.1*max(npub$paper.per.title))) +
+       ggtitle(paste("Languages (", publ, "/", catalogue, ")", sep = ""))
+print(p)
+
+}
+```
+
+### BOOKINFINLAND-DONE4
+
+edellisten yhdistäminen, eli täsmälleen samat analyysit, mutta asiasanoina kaikki (todo2 ja todo3), eli: virret;arkkiveisut;hartauskirjat;katekismukset;rukouspäivät;saarnat;aapiset;rukoukset;rukous;hengelliset laulut;hartauspuheet;virsikirjat;hautajaiset;häät;juhlamenot
+
+Hartauskirjallisuudesta ks. Osmo Tiililä, Rukoilevaisten kirjoja, 1961.
+
+General analysis with all documents combined:
+
+```{r topics3, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, out.width="430px", fig.show="hold"}
+sel <- c("virret","arkkiveisut","hartauskirjat","katekismukset","rukouspäivät","saarnat","aapiset","rukoukset","rukous","hengelliset laulut","hartauspuheet","virsikirjat","hautajaiset","häät","juhlamenot")
+catalogue <- "Fennica"
+  if (catalogue == "Fennica") {
+    df <- df.full # full time span
+  } else if (catalogue == "Kungliga") {
+    df <- df0 # selected time span
+  }
+  df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)
+
+# Selected catalogue with selected topics
+df <- df %>% filter(catalog == catalogue & hit)
+
+langs <- c("Finnish", "Swedish", "Latin", "German", "Other")
+lang <- paste("language.", langs, sep = "")
+otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
+df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
+dfl <- NULL
+for (lan in lang) {
+  # Classify a document to the specifed language
+  # If document is assigned with languages, each case is considered
+  # so one doc may have multiple entries corresponding to different languages
+  # mean(rowSums(df[, lang]) == 1) # 93% Fennica docs have just 1 language
+  # Combine data frames for specified languages
+  dflsub <- filter(df, df[[lan]])
+  dflsub$language <- gsub("language.", "", lan)
+  dfl <- bind_rows(dfl, dflsub)
+}
+dfl$language <- factor(dfl$language, levels = langs)
+
+# -------------------------------------------
+
+df <- dfl %>% group_by(publication_decade, language) %>%
+             summarise(n = n(),
+	               paper = sum(paper.consumption.km2, na.rm = TRUE))
 
@@
 print(p)
-
-}
-```
-
-BOOKINFINLAND-TODO3: Sama kuin edellä, mutta asiasanat tässä:
-
-hautajaiset;häät;juhlamenot
-
-BOOKINFINLAND-TODO4: edellisten yhdistäminen, eli täsmälleen samat analyysit, mutta asiasanoina kaikki (todo2 ja todo3), eli:
-
-virret;arkkiveisut;hartauskirjat;katekismukset;rukouspäivät;saarnat;aapiset;rukoukset;rukous;hengelliset laulut;hartauspuheet;virsikirjat;hautajaiset;häät;juhlamenot
-
-Hartauskirjallisuudesta ks. Osmo Tiililä, Rukoilevaisten kirjoja, 1961.
-
-BOOKINFINLAND-TODO4
+```
+
+Same with selected publication places:
+
+```{r topics3.per.place, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, out.width="430px", fig.show="hold"}
+
+for (place in c("Turku", "Stockholm", "Vaasa")) {
+
+ df <- dfl %>% filter(publication_place == place)
+
+ df <- df %>% group_by(publication_decade, language) %>%
+             summarise(n = n(),
+	               paper = sum(paper.consumption.km2, na.rm = TRUE))
+
+ df$language <- factor(df$language, levels = names(table(df$language)))
+
+# TITLE COUNT
+theme_set(theme_bw(20))
+p <- ggplot(df, aes(x = publication_decade, y = n, group = language)) +
+       #geom_bar(stat = "identity", position = "dodge", aes(fill = publisher)) + 
+       geom_point(aes(col = language, shape = language), size = 5) +
+       geom_line(aes(col = language, shape = language)) +       
+       # geom_smooth(aes(col = language)) + 
+       xlab("Publication year") +
+       ylab("Title count (n)") +
+       # ylim(c(0, 1.1*max(npub$paper.per.title))) +
+       ggtitle(paste("Languages (", place, "/", catalogue, ")", sep = ""))
+print(p)
+
+# PAPER CONSUMPTION
+
+theme_set(theme_bw(20))
+p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
+       #geom_bar(stat = "identity", position = "dodge", aes(fill = publisher)) + 
+       geom_point(aes(col = language, shape = language), size = 5) +
+       geom_line(aes(col = language, shape = language)) +       
+       # geom_smooth(aes(col = language)) + 
+       xlab("Publication year") +
+       ylab("Paper consumption") +
+       # ylim(c(0, 1.1*max(npub$paper.per.title))) +
+       ggtitle(paste("Languages (", place, "/", catalogue, ")", sep = ""))
+print(p)
+
+}
+```
+
+Same with top publishers
+
+```{r topics3.per.publisher, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, out.width="430px", fig.show="hold"}
+tops <-  names(top(fen, "publisher", 5))
+
+for (publ in tops) {
+
+  df <- dfl %>% filter(publisher == publ)
+
+  df <- df %>% group_by(publication_decade, language) %>%
+             summarise(n = n(), paper = sum(paper.consumption.km2, na.rm = TRUE))
+
+  df$language <- factor(df$language, levels = names(table(df$language)))
+
+# TITLE COUNT
+theme_set(theme_bw(20))
+p <- ggplot(df, aes(x = publication_decade, y = n, group = language)) +
+       #geom_bar(stat = "identity", position = "dodge", aes(fill = publisher)) + 
+       geom_point(aes(col = language, shape = language), size = 5) +
+       geom_line(aes(col = language, shape = language)) +       
+       # geom_smooth(aes(col = language)) + 
+       xlab("Publication year") +
+       ylab("Title count (n)") +
+       # ylim(c(0, 1.1*max(npub$paper.per.title))) +
+       ggtitle(paste("Languages (", publ, "/", catalogue, ")", sep = ""))
+print(p)
+
+# PAPER CONSUMPTION
+
+theme_set(theme_bw(20))
+p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
+       #geom_bar(stat = "identity", position = "dodge", aes(fill = publisher)) + 
+       geom_point(aes(col = language, shape = language), size = 5) +
+       geom_line(aes(col = language, shape = language)) +       
+       # geom_smooth(aes(col = language)) + 
+       xlab("Publication year") +
+       ylab("Paper consumption") +
+       # ylim(c(0, 1.1*max(npub$paper.per.title))) +
+       ggtitle(paste("Languages (", publ, "/", catalogue, ")", sep = ""))
+print(p)
+
+}
+```
+
+### BOOKINFINLAND-DONE4
 
@@
 
-Myös kaupungittain vertailu on kiinnostavaa, koska tuntuma on, että Turun ja Helsingin osalta ei latinan, ranskan ja saksankielista matskua pitäisi löytyä.
+Title count for different places. Fennica, no time limit.
+
+```{r medicne, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, out.width="430px", fig.show="hold"}
+dfs <-subset(df.full, catalog == "Fennica");
+print(sort(table(dfs[grep("lääketiede", dfs$subject_topic),"publication_place"])))
+```
+
+General analysis with all documents combined:
+
+```{r topics4, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, out.width="430px", fig.show="hold"}
+sel <- "lääketiede"
+catalogue <- "Fennica"
+  if (catalogue == "Fennica") {
+    df <- df.full # full time span
+  } else if (catalogue == "Kungliga") {
+    df <- df0 # selected time span
+  }
+  df$hit <- grepl(sel, tolower(df$subject_topic))
+
+# Selected catalogue with selected topics
+df <- df %>% filter(catalog == catalogue & hit)
+
+langs <- c("Finnish", "Swedish", "Latin", "German", "Other")
+lang <- paste("language.", langs, sep = "")
+otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
+df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
+dfl <- NULL
+for (lan in lang) {
+  # Classify a document to the specifed language
+  # If document is assigned with languages, each case is considered
+  # so one doc may have multiple entries corresponding to different languages
+  # mean(rowSums(df[, lang]) == 1) # 93% Fennica docs have just 1 language
+  # Combine data frames for specified languages
+  dflsub <- filter(df, df[[lan]])
+  if (nrow(dflsub) > 0) {
+    dflsub$language <- gsub("language.", "", lan)
+    dfl <- bind_rows(dfl, dflsub)
+  }
+}
+dfl$language <- factor(dfl$language, levels = names(table(dfl$language)))
+
+# -------------------------------------------
+
+df <- dfl %>% group_by(publication_decade, language) %>%
+             summarise(n = n(),
+	               paper = sum(paper.consumption.km2, na.rm = TRUE))
+
+# TITLE COUNT
+theme_set(theme_bw(20))
+p <- ggplot(df, aes(x = publication_decade, y = n, group = language)) +
+       #geom_bar(stat = "identity", position = "dodge", aes(fill = publisher)) + 
+       geom_point(aes(col = language, shape = language), size = 5) +
+       geom_line(aes(col = language, shape = language)) +       
+       # geom_smooth(aes(col = language)) + 
+       xlab("Publication year") +
+       ylab("Title count (n)") +
+       # ylim(c(0, 1.1*max(npub$paper.per.title))) +
+       ggtitle(paste("Languages (", catalogue, ")", sep = ""))
+print(p)
+
+# PAPER CONSUMPTION
+
+theme_set(theme_bw(20))
+p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
+       #geom_bar(stat = "identity", position = "dodge", aes(fill = publisher)) + 
+       geom_point(aes(col = language, shape = language), size = 5) +
+       geom_line(aes(col = language, shape = language)) +       
+       # geom_smooth(aes(col = language)) + 
+       xlab("Publication year") +
+       ylab("Paper consumption") +
+       # ylim(c(0, 1.1*max(npub$paper.per.title))) +
+       ggtitle(paste("Languages (", catalogue, ")", sep = ""))
+print(p)
+```
+
+Kaupungittain vertailu on kiinnostavaa, koska tuntuma on, että Turun ja Helsingin osalta ei latinan, ranskan ja saksankielista matskua pitäisi löytyä.
 Silloin vernakularisointi tapahtuu erityisesti muualla.
@@
 Huumo, Katja. "Perkeleen kieli" : suomen kieli ja poliittisesti korrekti tiede 1800-luvulla, Helsinki : Suomen tiedeseura, 2005.
+
+```{r topics4.per.place, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, out.width="430px", fig.show="hold"}
+
+for (place in c("Turku", "Uppsala")) {
+
+ df <- dfl %>% filter(publication_place == place)
+
+ df <- df %>% group_by(publication_decade, language) %>%
+             summarise(n = n(),
+	               paper = sum(paper.consumption.km2, na.rm = TRUE))
+
+ df$language <- factor(df$language, levels = names(table(df$language)))
+
+  # TITLE COUNT
+  theme_set(theme_bw(20))
+  p <- ggplot(df, aes(x = publication_decade, y = n, group = language)) +
+       geom_point(aes(col = language, shape = language), size = 5) +
+       geom_line(aes(col = language, shape = language)) +       
+       xlab("Publication year") +
+       ylab("Title count (n)") +
+       ggtitle(paste("Languages (", place, "/", catalogue, ")", sep = ""))
+  print(p)
+
+  # PAPER CONSUMPTION
+  theme_set(theme_bw(20))
+  p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
+       geom_point(aes(col = language, shape = language), size = 5) +
+       geom_line(aes(col = language, shape = language)) +       
+       xlab("Publication year") +
+       ylab("Paper consumption") +
+       ggtitle(paste("Languages (", place, "/", catalogue, ")", sep = ""))
+  print(p)
+
+}
+```
 
@@
 **PUBLISHER-TODO2** (Done?) Analysis of the top publishers publishing
-  profile (title count and paper consumption) over time.
+  profile (title count and paper consumption) over time. DONE: now also added for Kungliga.
 
@@
 
-```{r publishers3-finland, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=7, fig.width=15}
-# Title count
-catalogue <- "Fennica"
+```{r publishers3-finland, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=7, fig.width=15, fig.show="hold"}
+for (catalogue in c("Fennica", "Kungliga")) {
+
 place <- "Turku"
 
-df <- df0
+  if (catalogue == "Fennica") {
+    df <- df.full # full time span
+  } else if (catalogue == "Kungliga") {
+    df <- df0 # selected time span
+  }
+
 df <- df %>%
-        filter(catalog == catalogue & publication_place == place) %>%
-        filter(publication_year >= 1640 & publication_year < 1828)
+        filter(catalog == catalogue & publication_place == place)
 
@@
 
-catalogue <- "Fennica"
-place <- "Turku"
-
-df <- df0
+# -------------------------------------
+
+# PAPER CONSUMPTION
+  if (catalogue == "Fennica") {
+    df <- df.full # full time span
+  } else if (catalogue == "Kungliga") {
+    df <- df0 # selected time span
+  }
+
 df <- df %>%
-        filter(catalog == catalogue & publication_place == place) %>%
-        filter(publication_year >= 1640 & publication_year < 1828)
+        filter(catalog == catalogue & publication_place == place)
 
@@
 print(p)
+
+}
 ```
@@
 ```{r publishers4-finland, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=7, fig.width=15}
-# Paper consumption
-catalogue <- "Fennica"
-place <- "Turku"
-
-df <- df0
+for (catalogue in c("Fennica", "Kungliga")) {
+
+  if (catalogue == "Fennica") {
+    df <- df.full # full time span
+  } else if (catalogue == "Kungliga") {
+    df <- df0 # selected time span
+  }
+
 df <- df %>%
-        filter(catalog == catalogue & publication_place == place) %>%
-        filter(publication_year >= 1640 & publication_year < 1828)
+        filter(catalog == catalogue & publication_place == place)
 
@@
 
-catalogue <- "Fennica"
-place <- "Turku"
-
-df <- df0
+  if (catalogue == "Fennica") {
+    df <- df.full # full time span
+  } else if (catalogue == "Kungliga") {
+    df <- df0 # selected time span
+  }
+
 df <- df %>%
-        filter(catalog == catalogue & publication_place == place) %>%
-        filter(publication_year >= 1640 & publication_year < 1828)
+        filter(catalog == catalogue & publication_place == place)
 
@@
        geom_bar(stat = "identity", position = "dodge", aes(fill = publisher)) + 
-       #geom_point(size = 5, aes(shape = publisher)) +
-       #geom_line(col = "black", aes(shape = publisher)) +       
-       # geom_smooth(col = "black", aes(shape = publisher)) + 
        xlab("Publication year") +
@@
 print(p)
-```
-
-PUBLISHER-TODO: julkaisijakuvat jotka edellä, samat kuin Fennica Kungligalle.
+}
+```
 
@@
 #löytyy)
-
 catalogue <- "Fennica"
@@
 ```
+
 PUBLISHER-TODO: julkaisijakuvat jotka edellä, samat kuin Fennica Kungligalle.

### 2016-07-03 inst/examples/manuscript-krakow.Rmd
ok

@@
 Silloin vernakularisointi tapahtuu erityisesti muualla.
+HUOM: Helsingissä ei ole painettu mitään asiasanalla lääketiede.
 
@@
 ```
+
 Tässä on meille tärkeät kuvat.
@@
 
-DONE1: Observed trends in Fennica regarding Finnish knowledge
-production 1640-1828, focusing on the appearance of new publishers on
-the publishing landscape.
+Observed trends in Fennica regarding Finnish knowledge production
+1640-1828, focusing on the appearance of new publishers on the
+publishing landscape.
 
@@
         filter(catalog == "Fennica" & !is.na(Finland)) %>%
-        filter(publication_year >= 1640 & publication_year < 1828) %>%	
+        filter(publication_year >= 1640 & publication_year <= 1828) %>%	
         select(publisher, publication_decade, Finland)
@@
         filter(catalog == "Fennica" & country == "Finland") %>%
-        filter(publication_year >= 1640 & publication_year < 1828) %>%	
+        filter(publication_year >= 1640 & publication_year <= 1828) %>%	
         select(publication_decade, publication_place)
@@
 
-Number of unique publishers in top publication places over time:
+Number of unique publishers in top publication places over time (Fennica):
 
@@
         filter(catalog == "Fennica" & country == "Finland") %>%
-        filter(publication_year >= 1640 & publication_year < 1828)
+        filter(publication_year >= 1640 & publication_year <= 1828)
 
@@
 
+Number of unique publishers in selected publication places over time
+(Kungliga). [Julkaisijoiden osalta Kungligan aineiston osalta samat
+analyysit Tukholmasta, Lundista, Uppsalasta ja Greifswaldista. Tämä
+mahdollistaa Turun sijoittamisen kontekstiin.]
+
+```{r publishers2-kungliga, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=7, fig.width=15}
+df <- df0
+catalogue <- "Kungliga"
+df <- df %>%
+        filter(catalog == catalogue) %>%
+        filter(publication_year >= 1640 & publication_year <= 1828)
+
+# Selected publication places
+top <- c("Stockholm", "Lund", "Uppsala", "Greifswald")
+df <- df %>%	
+        filter(publication_place %in% top) %>%	
+        select(publication_decade, publication_place, publisher)
+
+npub <- unique(df) %>% group_by(publication_decade, publication_place) %>% tally()
+npub$publication_place <- factor(npub$publication_place, levels = top)
+theme_set(theme_bw(20))
+
+p <- ggplot(npub, aes(x = publication_decade, y = n)) +
+       geom_bar(stat = "identity", position = "stack", aes(fill = publication_place)) + 
+       xlab("Publication year") +
+       ylab("Unique publishers (n)") +        
+       ggtitle(paste("Unique publishers in selected publication places (", catalogue, ")"))
+print(p)
+```
+
 **PUBLISHER-TODO2** (Done?) Analysis of the top publishers publishing
-  profile (title count and paper consumption) over time. DONE: now also added for Kungliga.
+  profile (title count and paper consumption) over time. DONE: now
+  also added for Kungliga.
 
@@
         filter(catalog == catalogue) %>%
-        filter(publication_year >= 1640 & publication_year < 1828)
+        filter(publication_year >= 1640 & publication_year <= 1828)
 
@@
 ```
-
-PUBLISHER-TODO: julkaisijakuvat jotka edellä, samat kuin Fennica Kungligalle.
 
@@
      näyttää suurelta verrattuna Londiceriin, mutta itse asiassa
-     sisältömäärä on sama”.  → Tätä hypoteesia voidaan yrittää
+     sisältömäärä on sama”.  Tätä hypoteesia voidaan yrittää
      todentaa/tarkistaa/korjata kun mukana on paperinkulutus. Eli jos
@@
         filter(catalog == catalogue) %>%
-        filter(publication_year >= 1750 & publication_year < 1828)
+        filter(publication_year >= 1750 & publication_year <= 1828)
 
@@
 
-PUBLISHER-TODO NEXT: julkaisioiden osalta  Kungligan aineiston osalta samat analyysit Tukholmasta, Lundista, Uppsalasta ja Gerifswaldista. Tämä mahdollistaa Turun sijoittamisen kontekstiin.
-
-PUBLISHER-TODO(jos ehtii): Fennican julkaisijoita voisi myös laajemmin yrittää luokitella suhteellisesti (“iso”,
-“keskikokoinen”, “pieni”) liittyen vuosittaiseen julkaisuvoluumiin
-jota mitataan niin julkaisujen määrän kuin myös paperinkulutusvoluumin
-suhteen. Tällä tavalla olisi helpompi hahmottaa eri kaupungeissa tapahtuvaa kehitystä. Vertailua suurimpien julkaisijoiden kesken.
-
-AJATUKSIA: Julkaisijoiden ilmentyminen kartalle paperinkulutusvoluumi huomioiden:
-julkaisutoiminnan leviäminen ja kasvu ajassa eri
-paikkakunnilla. Paperinkulutus voi osoittautua hyväksi työvälineeksi
-erityisesti kun tiedetään, että toiset isot julkaisijat julkaisivat
-esim. jotain asetuskokoelmia yksittäin ja toiset taas ryppäinä. Eli
-julkaisijoiden sisällä erottelua eri tyyppisten julkaisujen suhteen
-pitää tehdä.
-
-PUBLISHER-TODO (jos ehtii): Julkaisijoista tehtävä verkostoanalyysi. keskeisimmät “nodet” siihen
-miten julkaisijakenttä muuttuu ajassa. Julkaisijoita voisi myös
-yrittää luokitella eniten käytettyjen asiasanojen mukaan. Näiden
-perusteella voidaan varmaankin erotella yliopistojulkaiseminen,
-asiakirja/asetusjulkaiseminen ja kirjajulkaiseminen. Tämän jälkeen
-auktorit, valtioasiakirjat, yliopistodokumentit, kirjat ja muut
-julkaisut kategoroina joiden ympärille verkostoanalyysi voisi syntyä
-(valtionasiakirjojen ja yliopisto-aineiston luokittelu voisi yhdistää
-myös asiasanojen ja otsikoiden analyysia). [OK monenlaista voidaan
-tehdä, onko tämä asiasanajuttu nyt tärkeä vai vähemmän tärkeä
-prioriteetti?]
+**PUBLISHER-TODO** (jos ehtii)
+
+  * Fennican julkaisijoita voisi myös laajemmin yrittää luokitella
+    suhteellisesti (“iso”, “keskikokoinen”, “pieni”) liittyen
+    vuosittaiseen julkaisuvoluumiin jota mitataan niin julkaisujen
+    määrän kuin myös paperinkulutusvoluumin suhteen. Tällä tavalla
+    olisi helpompi hahmottaa eri kaupungeissa tapahtuvaa
+    kehitystä. Vertailua suurimpien julkaisijoiden kesken.
+
+  * AJATUKSIA: Julkaisijoiden ilmentyminen kartalle
+    paperinkulutusvoluumi huomioiden: julkaisutoiminnan leviäminen ja
+    kasvu ajassa eri paikkakunnilla. Paperinkulutus voi osoittautua
+    hyväksi työvälineeksi erityisesti kun tiedetään, että toiset isot
+    julkaisijat julkaisivat esim. jotain asetuskokoelmia yksittäin ja
+    toiset taas ryppäinä. Eli julkaisijoiden sisällä erottelua eri
+    tyyppisten julkaisujen suhteen pitää tehdä.
+
+  * Julkaisijoista tehtävä verkostoanalyysi. keskeisimmät “nodet”
+    siihen miten julkaisijakenttä muuttuu ajassa. Julkaisijoita voisi
+    myös yrittää luokitella eniten käytettyjen asiasanojen
+    mukaan. Näiden perusteella voidaan varmaankin erotella
+    yliopistojulkaiseminen, asiakirja/asetusjulkaiseminen ja
+    kirjajulkaiseminen. Tämän jälkeen auktorit, valtioasiakirjat,
+    yliopistodokumentit, kirjat ja muut julkaisut kategoroina joiden
+    ympärille verkostoanalyysi voisi syntyä (valtionasiakirjojen ja
+    yliopisto-aineiston luokittelu voisi yhdistää myös asiasanojen ja
+    otsikoiden analyysia). [OK monenlaista voidaan tehdä, onko tämä
+    asiasanajuttu nyt tärkeä vai vähemmän tärkeä prioriteetti?]
 

### 2016-07-03 inst/examples/manuscript-krakow.Rmd
ok
Update manuscript-krakow.Rmd

@@
 ```
+
+### BOOKINFINLAND-5
+
+Samat analyysit kuin yllä, seuraavat asiasanaryppäät. Tarkoituksena analysoida yliopisto-opetuksen muutosta. Kokonaismäärät ja kielikohtaiset vaihtelut kiinnostavat.
+
+i) kirkkohistoria;raamatunhistoria;eksegetiikka;homiletiikka;dogmatiikka;teologia
+
+ii) oppihistoria;antiikki;historia
+
+iii) filosofia;luonnonfilosofia;metafysiikka;logiikka
+
+iv) luonnontieteet;matematiikka;fysiikka;kemia;tähtitiede;maantiede;geodesia;geofysiikka;meteorologia
+
+v) retoriikka;poetiikka;kielitiede;kielioppi
+
+vi) heprean kieli;kreikan kieli;latinan kieli
+
+vii) psykologia;yhteiskuntafilosofia;valtiofilosofia;talous;raha;moraali;velvollisuudet;kasvatus
+
+viii) luonnonhistoria;lääketiede;tartuntataudit;eläintiede;kasvitiede;kasvisto;eläimet;eläinsuojelu;eläimistö;eläintaudit;hevonen;maanviljely;maatalous;kalastus
+
+ix) naiset;naisen asema;naisasialiikkeet;naisasiajärjestöt
+
+x) etsintäkuulutukset;rikokset;oikeus;rangaistukset
+
+Näissä kiinnostaa myös julkaisijakohtaiset vaihtelut (tai oikeastaan kaikki kuvat joita esim. BOOKINFINLAND-4:ssa. Tämä vain jatkaa siitä mihin tuo edellinen jää.
 

### 2016-07-04 inst/examples/manuscript-krakow.Rmd
Update manuscript-krakow.Rmd

@@
 
-Fennica yhteenvedoissa on EDITIONS kohta. Kuvia mahdollista saada? On nimittäin mielenkiintoinen kysymys. LL: ok lisasin tan sinne - voin elaboroida lisaa jos on ehdotuksia:
+Fennica yhteenvedoissa on EDITIONS kohta.
+Kuvia mahdollista saada?
+On nimittäin mielenkiintoinen kysymys.
+LL: ok lisasin tan sinne - voin elaboroida lisaa jos on ehdotuksia: MT: otetaan tarkasteluun ainoastaan sellaiset julkaisut joista on enemmän kuin yksi editio.
+Eli editioita pitää olla kaksi tai useampi, että lasketaan mukaan.
+Näistä sitten tarkastellaan ainoastaan sen ensimmäisen edition ilmestymistä.
+Lisäksi voisi piirtää toisen kuvan jossa tarkastellaan muita kuin sen ensimmäisen edition ilmestymistä (eli toinen, kolmas jne.
+editiot).
 

### 2016-07-04 inst/examples/manuscript-krakow.Rmd
Update manuscript-krakow.Rmd

@@
 
+MT: We are in a session called "MAPS and SPACE", so I think we need to have some of the results presented on a map.
+Now, the question is what is possible to do within this time?
+But perhaps the publishing houses should be included in this?
+
 Why Fennica has huge drop in 1700s? Do some publisher disappear (TODO)? Let us look at top publication places during the period 1650-1750 in Fennica:
@@
 Tämä analyysi kannattaa jatkaa myös pidemmälle kuin 1828 Fennican osalta.
+MT: Korjataan tätä kommenttia.
+Tässä data ei riitä siihen että kannattaa analyysia jatkaa.
+Eli siis 1828 takalautana kaikissa kuvissa.
+Näin viilaamalla noista erittäin hyvistä kuvista tuossa alla (ja kohdassa BOOKINFINLAND-DONE4) tulee vielä parempia.
 

### 2016-07-04 inst/examples/manuscript-krakow.Rmd
Update manuscript-krakow.Rmd

@@
 ```
+MITEN ON MAHDOLLISTA, ETTÄ VYBORG EI NÄY TÄSSÄ? Tai jos syynä että merkattu Suomen ulkopuolelle, niin se pitäisi saada tähän poikkeuksena mukaan. Tuolla alkupäässä sen pitäisi näkyä.
 

### 2016-07-04 inst/examples/manuscript-krakow.Rmd
Update manuscript-krakow.Rmd

@@
 Tarkkailtavia kielikategorioita on 5: suomi, ruotsi, latina, saksa sekä kategoria jossa kaikki muun kielisiset kuin edellä mainitut niputetaan yhteen.
+TÄYDENNYS: Venäjän ja ranskankielisestä aineistosta omat graafit myös.
 
@@
 Näin viilaamalla noista erittäin hyvistä kuvista tuossa alla (ja kohdassa BOOKINFINLAND-DONE4) tulee vielä parempia.
+
+TODO: Kungligan subject topiceista voisi tuottaa vastaavat niputettavat asiasanaryhmät Kungligalle (Jani ja Mikko): https://github.com/rOpenGov/kungliga/blob/master/output.tables/subject_topic_accepted.csv Näistä sitten oma analyysi joka suhtautuu Fennicaan.
 
@@
 
+MT: Näissä ensimmäisissä kuvissa myös aikarajaus niin että loppuu 1828.
+
 ```{r publishers3-finland, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=7, fig.width=15, fig.show="hold"}

### 2016-07-04 inst/examples/manuscript-krakow.Rmd
Added todos for analysis
Lisäsin alle seuraavat TODO:t: TODO_Political events 1, TODO_Turku in Sweden 1, TODO_Turku in Sweden 2, TODO_Publisher analysis_#, TODO_Publishing in Finland # ja TODO_Publishing in Finland_kieliolosuhteet_muualla 1. Ovatko nämä toteuttamiskelpoisia?

@@
 
+Lisäsin alle seuraavat TODO:t: TODO_Political events 1, TODO_Turku in Sweden 1, TODO_Turku in Sweden 2, TODO_Publisher analysis_#, TODO_Publishing in Finland # ja TODO_Publishing in Finland_kieliolosuhteet_muualla 1.
+Ovatko nämä toteuttamiskelpoisia?
+
 ## Introduction
@@
 
+TODO_Political events 1: Kaaviot Tukholmasta, Uppsalasta, Lundista, Greifswaldista ja Turusta ajalle 1860-1880, joissa näkyy vuosittain julkaisumäärät, arvio paperinkulutuksesta ja kustantajien määrästä.
+Nämä pitää tehdä erikseen Fennicasta ja Kungligasta, eli yhteensä kuusi kaaviota.
+Tärkeää, että saadaan jokaisesta vuodesta oma piste/luku.
+Trendiviiva ei ole kovinkaan kiinnostava, koska tässä yritetään selvittää sitä millä tavalla painovapausaika (1766-1774) erottuu materiaalissa.
+Yksi aikaisemman tutkimuksen väitteistä on se, että pamflettikirjoittelu räjähtää tänä aikana.
+Tätä testataan vertaamalla paperinkulutusta ja nimikkeiden määrää.
+Julkaisijoiden määrän kasvu näkyy Kungligan materiaalissa Tukholman osalta ja Turunkin osalta päästään kymmeneen julkaisijaan joten verrataan tätä muihin kaupunkeihin.
+Synnyttääkö painovapaus uusia julkaisijoita (vastaus on kyllä)?
+
 Title counts in selected places in the Kungliga catalogue.
@@
 ```
+
+TODO_Publishing in Finland_kieliolosuhteet_muualla 1: Greifswaldin kieliprofiili vuoteen 1828 asti (käytännössä 1815) Kungligan materiaalin osalta.
+Onko Greifswaldissa samanlainen kielimonimuotoisuus läsnä kuin Turussa?
 
@@
 
+TODO_Publishing in Finland #: Kaaviot Fennicasta, jossa lasketaan eri kielten mukaan asiasanojen määrä eri vuosina.
+Asiasanat ovat osin arbriträärisiä, mutta ehkä niiden määrän pohjalta voidaan sanoa jotain siitä millä kielellä on julkaistu mitäkin.
+Minusta voisi tehdä kaavion vuoteen 1828 sekä toisen vuoteen 1900.
+Tiedän että 1800-luvun osalta Fennicassa on kielellinen bias, mutta esim.
+suomenkielen tarkastelun kannalta tällä ei ole merkitystä, sillä kaikki suomenkielinen materiaali on tarkkaan läpikäytyä.
+Tässä näky toivottasti se millä tavalla 1855 jälkeen suomenkielinen julkaiseminen laajeni.
+Kaavio joka näyttää asiasanat vuoteen 1828 auttaa toivottavasti asettamaan 1700-luvun suomenkielisen hartauskirjallisuuden kontekstiinsa.
+
 ### BOOKINFINLAND-5
@@
   p <- ggplot(dfs, aes(x = publication_decade, y = paper.per.document)) +
-       geom_point(aes(color = publication_place, shape = publication_place)) +
+       geom_popuint(aes(color = publication_place, shape = publication_place)) +
        geom_line(aes(color = publication_place, linetype = publication_place)) +
@@
 
+TODO_Publisher analysis_#: Kaaviot Fennicasta ja Kungligasta, jossa lasketaan eri julkaisijoiden.
+Asiasanat ovat osin arbriträärisiä, mutta ehkä niiden määrän pohjalta voidaan sanoa jotain eri julkaisijoiden profiilien muutoksista.
+Laaditaan kaaviot 1828.
+
   * Fennican julkaisijoita voisi myös laajemmin yrittää luokitella
@@
 
+TODO_Turku in Sweden 2: Kaaviot Fennicasta ja Kungligasta, jossa lasketaan eri kaupunkien mukaan asiasanojen määrä eri vuosina.
+Asiasanat ovat osin arbriträärisiä, mutta ehkä niiden määrän pohjalta voidaan sanoa jotain eri kaupunkien julkaisuprofiilien muutoksista.
+Laaditaan kaaviot Tukholmasta, Uppsalasta, Lundista, Greifswaldista ja Turusta vuoteen 1828.
+Fennican osalta tehdään myös kaavio Vaasasta, jotta nähdään kuinka Vaasan hovioikeuteen painottunut julkaiseminen erottuu Turun julkaisemisesta.
+
+TODO_Turku in Sweden 1 (jos ehditään ja on mahdollista): Kaaviot Fennicasta ja Kungligasta, jossa lasketaan eri kaupunkien nimikemäärien, paperinkulutuksen ja kustantajien suhteellinen osuus vuoteen 1828.
+Eli samanlainen kaavio kuin on kielistä ”Book printing in Finland” –osiossa.
+Laaditaan kaaviot Tukholmasta, Uppsalasta, Lundista, Greifswaldista ja Turusta.
+Voiko myös tehdä erillisen kaavion, jossa Tukholma on poistettu, josta näkee näiden kilpailevien kakkoskaupunkien tilanteen.
+
+TODO_Turku in Sweden 3: Kun kerran ollaan maps and space sessiossa, ehkä kannattaisi tehdä myös kartta jossa, nämä eri kaupungit ja niiden nimikemäärät ovat kartalla.
+Kartat kannattaisi kai tehdä vuosille 1650, 1710, 1767 ja 1800.
+Onko tämä mahdollista?
+
 ### Other points if the time allows

### 2016-07-04 inst/examples/manuscript-krakow.Rmd
ok

@@
   p <- ggplot(dfs, aes(x = publication_decade, y = paper.per.document)) +
-       geom_popuint(aes(color = publication_place, shape = publication_place)) +
+       geom_point(aes(color = publication_place, shape = publication_place)) +
        geom_line(aes(color = publication_place, linetype = publication_place)) +
@@
        scale_y_log10() 
-  #p <- p + geom_text(aes(label = publication_place), size = 5)
-  #p <- p + xlab("Title Count") + ylab("Paper consumption (km2)")
-  #p <- p + scale_color_manual(values = c("darkgray", "black"))
-  #p <- p + guides(color = "none")
   print(p)	 
@@
   p <- p + scale_color_manual(values=c("black", "darkgray"))
-  # p <- p + guides(shape = "none") 
   p <- p + ggtitle(catal)

### 2016-07-04 inst/examples/manuscript-krakow.Rmd
Update manuscript-krakow.Rmd

@@
 
-vii) psykologia;yhteiskuntafilosofia;valtiofilosofia;talous;raha;moraali;velvollisuudet;kasvatus
-
-viii) luonnonhistoria;lääketiede;tartuntataudit;eläintiede;kasvitiede;kasvisto;eläimet;eläinsuojelu;eläimistö;eläintaudit;hevonen;maanviljely;maatalous;kalastus
+vii) psykologia;yhteiskuntafilosofia;valtiofilosofia;talous;raha;moraali;velvollisuudet;kasvatus;maanviljely;maatalous;kalastus
+
+viii) luonnonhistoria;lääketiede;tartuntataudit;eläintiede;kasvitiede;kasvisto;eläimet;eläinsuojelu;eläimistö;eläintaudit;hevonen
 

### 2016-07-04 inst/examples/manuscript-krakow.Rmd
ok

--- 2016-07-04 inst/examples/manuscript-krakow.Rmd
@@
 
-Tärkein ASAP tehtävä on **Publisher analysis**
-
-Selvensin alle (Publisher analysis kohtaan): PUBLISHER-TODO1 ja
-PUBLISHER-TODO2. Lisäksi löytyy muita ajatuksia.
+Selvensin alle (Publisher analysis kohtaan):
+
+  * PUBLISHER-TODO1
+  * PUBLISHER-TODO2
+  * Lisäksi löytyy muita ajatuksia.
 
 Muiden osalta (voi tehdä jo ilman publisher kenttää), järjestys: **Book printing in Finland** - kohdasta
-  * BOOKINFINLAND-TODO1 ja
-  * BOOKINFINLAND-TODO2.
-
-Eli aloita BOOKINFINLAND-TODOilla ja kun julkaisijakenttä tsekattu, niin heti Publisher analysis kohtaan ja PUBLISHER-TODOt.
-Samalla Marjanen ja minä siivotaan näitä muita analyysi-ideoita toteuttamiskelpoisiksi ohjeiksi.
-Jani voi tehdä tätä omatoimisesti myös.
-
-Lisäsin alle seuraavat TODO:t: TODO_Political events 1, TODO_Turku in Sweden 1, TODO_Turku in Sweden 2, TODO_Publisher analysis_#, TODO_Publishing in Finland # ja TODO_Publishing in Finland_kieliolosuhteet_muualla 1.
-Ovatko nämä toteuttamiskelpoisia?
+
+  * BOOKINFINLAND-TODO1
+  * BOOKINFINLAND-TODO2
+
+Marjanen ja minä siivotaan samalla näitä muita analyysi-ideoita toteuttamiskelpoisiksi ohjeiksi. Jani voi tehdä tätä omatoimisesti myös.
+
+Lisäsin alle seuraavat TODO:t (Ovatko nämä toteuttamiskelpoisia?):
+
+  * TODO_Political events 1
+  * TODO_Turku in Sweden 1
+  * TODO_Turku in Sweden 2
+  * TODO_Publisher analysis_
+  * TODO_Publishing in Finland
+  * TODO_Publishing in Finland_kieliolosuhteet_muualla
 
@@
 But perhaps the publishing houses should be included in this?
+LL: yes we can rather easily add map visualization when it is clear what we like to present using maps.
+For instance the code we used for LIBER to visualize differences in publishing activity across UK can be reused (with different regions), also videos can be made for presentation if we like.
+But I would first focus on findings, and polish the visualizations later.
+I will try to look at maps somewhere this week.
+The less there are other todo points, the more there will be time for maps.
+If you like to see some result specifically on a map, please mark it so and I can check.
 

### 2016-07-04 inst/examples/manuscript-krakow.Rmd
ok

@@
 
-Why Fennica has huge drop in 1700s? Do some publisher disappear (TODO)? Let us look at top publication places during the period 1650-1750 in Fennica:
+Why Fennica has huge drop in 1700s? Do some publisher disappear (see
+below for an answer..)
+
+Let us look at top publication places during the period 1650-1750 in Fennica:
 
@@
 
-Fennica yhteenvedoissa on EDITIONS kohta.
-Kuvia mahdollista saada?
-On nimittäin mielenkiintoinen kysymys.
-LL: ok lisasin tan sinne - voin elaboroida lisaa jos on ehdotuksia: MT: otetaan tarkasteluun ainoastaan sellaiset julkaisut joista on enemmän kuin yksi editio.
+Fennica yhteenvedoissa on EDITIONS kohta. Kuvia mahdollista saada? On nimittäin mielenkiintoinen kysymys. LL: ok lisasin tan sinne - voin elaboroida lisaa jos on ehdotuksia:
+
+MT: otetaan tarkasteluun ainoastaan sellaiset julkaisut joista on enemmän kuin yksi editio.
 Eli editioita pitää olla kaksi tai useampi, että lasketaan mukaan.
@@
 editiot).
+LL: tää lienee TODO-listan häntäpäässä?
+Tuntuu vähemmän tärkeältä kuin muut eli skippaan for now.
 
@@
 julkaisukenttään 1600-luvun aikana.
-
-I can provide percentages instead
-of counts, or paper consumption estimates (not reliable yet, though),
-barplots, selected time spans, selected places etc.. just let me know
-what is needed.
 
@@
 
-TODO_Political events 1: Kaaviot Tukholmasta, Uppsalasta, Lundista, Greifswaldista ja Turusta ajalle 1860-1880, joissa näkyy vuosittain julkaisumäärät, arvio paperinkulutuksesta ja kustantajien määrästä.
+**DONE_Political events 1** Kaaviot Tukholmasta, Uppsalasta, Lundista, Greifswaldista ja Turusta ajalle 1760-1780, joissa näkyy vuosittain julkaisumäärät, arvio paperinkulutuksesta ja kustantajien määrästä.
 Nämä pitää tehdä erikseen Fennicasta ja Kungligasta, eli yhteensä kuusi kaaviota.
@@
 Synnyttääkö painovapaus uusia julkaisijoita (vastaus on kyllä)?
+
+```{r polev1, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, out.width="430px", fig.show="hold"}
+# TITLE COUNT
+sel.places = c("Stockholm", "Uppsala", "Lund", "Greifswald", "Turku")
+sel.years = c(1760, 1780)
+
+for (place in sel.places) {
+
+for (catalogue in c("Fennica", "Kungliga")) {
+
+  df <- df0
+  dfs <- df %>% filter(catalog == catalogue &
+     	              publication_place == place &
+		      publication_year >= min(sel.years) &
+		      publication_year <= max(sel.years) 
+		      )
+
+  df <- dfs %>% group_by(publication_year) %>%
+             summarise(n = n(),
+	               paper = sum(paper.consumption.km2, na.rm = TRUE))
+
+  # TITLE COUNT
+  theme_set(theme_bw(20))
+  p <- ggplot(df, aes(x = publication_year, y = n)) +
+       geom_point(size = 5) +
+       geom_line() +       
+       # geom_smooth() + 
+       xlab("Publication year") +
+       ylab("Title count (n)") +
+       ggtitle(paste("Title count:", catalogue, place))
+  print(p)
+
+  # PAPER CONSUMPTION
+  theme_set(theme_bw(20))
+  p <- ggplot(df, aes(x = publication_year, y = paper)) +
+       geom_point(size = 5) +
+       geom_line() +       
+       # geom_smooth() + 
+       xlab("Publication year") +
+       ylab("Paper consumption") +
+       # ylim(c(0, 1.1*max(npub$paper.per.title))) +
+       ggtitle(paste("Paper:", catalogue, place))
+  print(p)
+
+  # PUBLISHER COUNT
+  n = sapply(split(dfs$publisher, dfs$publication_year), function (x) {length(unique(na.omit(x)))})
+  df = data.frame(year = names(n), n = unname(n))
+  p = ggplot(df, aes(x = year, y = n)) +
+        geom_bar(stat = "identity") +
+       ggtitle(paste("Publishers:", catalogue, place)) +
+       scale_x_discrete(breaks = seq(min(sel.years), max(sel.years), 10))
+  print(p)
+
+}
+}
+```
 
@@
   minyear = 1500
-  #maxyear = 1800
-  #minyear = min(na.omit(df0$publication_year))
-  #maxyear = max(na.omit(df0$publication_year))
 
@@
 Tarkkailtavia kielikategorioita on 5: suomi, ruotsi, latina, saksa sekä kategoria jossa kaikki muun kielisiset kuin edellä mainitut niputetaan yhteen.
-TÄYDENNYS: Venäjän ja ranskankielisestä aineistosta omat graafit myös.
+
+DONE: Venäjän ja ranskankielisestä aineistosta omat graafit myös.
 
 ```{r language1, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, out.width="430px", fig.show="hold"}
-# TITLE COUNT
+
 for (catalogue in c("Fennica", "Kungliga")) {
@@
 
-langs <- c("Finnish", "Swedish", "Latin", "German", "Other")
+langs <- c("Finnish", "Swedish", "Latin", "German", "Russian", "French", "Other")
 lang <- paste("language.", langs, sep = "")
@@
 
+# TITLE COUNT
+
 theme_set(theme_bw(20))
 p <- ggplot(df, aes(x = publication_decade, y = n, group = language)) +
-       #geom_bar(stat = "identity", position = "dodge", aes(fill = publisher)) + 
        geom_point(aes(col = language, shape = language), size = 5) +
        geom_line(aes(col = language, shape = language)) +       
-       # geom_smooth(aes(col = language)) + 
        xlab("Publication year") +
        ylab("Title count (n)") +
-       # ylim(c(0, 1.1*max(npub$paper.per.title))) +
        ggtitle(paste("Languages (", catalogue, ")", sep = ""))
@@
 p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
-       #geom_bar(stat = "identity", position = "dodge", aes(fill = publisher)) + 
        geom_point(aes(col = language, shape = language), size = 5) +
        geom_line(aes(col = language, shape = language)) +       
-       # geom_smooth(aes(col = language)) + 
        xlab("Publication year") +
        ylab("Paper consumption") +
-       # ylim(c(0, 1.1*max(npub$paper.per.title))) +
        ggtitle(paste("Languages (", catalogue, ")", sep = ""))
@@
 
-TODO_Publishing in Finland_kieliolosuhteet_muualla 1: Greifswaldin kieliprofiili vuoteen 1828 asti (käytännössä 1815) Kungligan materiaalin osalta.
+**TODO_Publishing in Finland_kieliolosuhteet_muualla 1**: Greifswaldin kieliprofiili vuoteen 1828 asti (käytännössä 1815) Kungligan materiaalin osalta.
 Onko Greifswaldissa samanlainen kielimonimuotoisuus läsnä kuin Turussa?

### 2016-07-04 inst/examples/manuscript-krakow.Rmd
ok

@@
 
-```{r polev1, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, out.width="430px", fig.show="hold"}
+```{r polev1, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, out.width="280px", fig.show="hold"}
 # TITLE COUNT

### 2016-07-04 inst/examples/manuscript-krakow.Rmd
ok

@@
 
-```{r polev1, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, out.width="280px", fig.show="hold"}
+**NOTE** Tulee enemmän kuin 6 kaaviota.. pistin kaikki viivat erikseen
+  kun pyydettiin erikseen. Huom: pystyakselin skaala vaihtelee
+  kuvittain.
+
+```{r polev1, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=6, out.width="280px", fig.show="hold"}
 # TITLE COUNT
@@
 
-DONE: Venäjän ja ranskankielisestä aineistosta omat graafit myös.
+DONE: Venäjän ja ranskankielisestä aineistosta omat graafit myös. OK lisätty samaan kuvaan.
 
@@
 
-**TODO_Publishing in Finland_kieliolosuhteet_muualla 1**: Greifswaldin kieliprofiili vuoteen 1828 asti (käytännössä 1815) Kungligan materiaalin osalta.
+**DONE_Publishing in Finland_kieliolosuhteet_muualla 1**: Greifswaldin kieliprofiili vuoteen 1828 asti (käytännössä 1815) Kungligan materiaalin osalta.
 Onko Greifswaldissa samanlainen kielimonimuotoisuus läsnä kuin Turussa?
+**OK en ollu varma mita tarkotit kieliprofiililla mut plottasin nyt uniikkien kielten maaran mainituille paikoille 1640-1828.
+Nopeasti voin tehda muutakin jos tasmennat.
+Hitaammin voin tehda viela enemman jos alan itse tutkia aineistoa huolellisesti mutta sit jaa muut jutut eli skippaan for now.**
+
+```{r greifswald-lang, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, out.width="430px", fig.show="hold"}
+# TITLE COUNT
+sel.places = c("Greifswald", "Turku")
+sel.years = c(1640, 1828)
+catalogue = "Kungliga"
+
+  df <- df0
+  dfs <- df %>% filter(catalog == catalogue &
+     	              publication_place %in% sel.places &
+		      publication_year >= min(sel.years) &
+		      publication_year <= max(sel.years) 
+		      )
+
+  df <- unique(dfs %>% select(publication_year, publication_place, language))
+  df = df %>% group_by(publication_year, publication_place) %>% summarise(n = n())
+
+  # Language count
+  p = ggplot(df, aes(x = publication_year, y = n, group = publication_place, color = publication_place, shape = publication_place)) +
+       #geom_bar(aes(fill = publication_place), position = "dodge", stat = "identity") +
+       geom_point() +
+       geom_line() +
+       ggtitle(paste("Number of languages:", catalogue)) 
+       #scale_x_discrete(breaks = seq(min(sel.years), max(sel.years), 10))
+  print(p)
+
+```
 
@@
 Tämä analyysi kannattaa jatkaa myös pidemmälle kuin 1828 Fennican osalta.
+
 MT: Korjataan tätä kommenttia.
@@
 Näin viilaamalla noista erittäin hyvistä kuvista tuossa alla (ja kohdassa BOOKINFINLAND-DONE4) tulee vielä parempia.
-
-TODO: Kungligan subject topiceista voisi tuottaa vastaavat niputettavat asiasanaryhmät Kungligalle (Jani ja Mikko): https://github.com/rOpenGov/kungliga/blob/master/output.tables/subject_topic_accepted.csv Näistä sitten oma analyysi joka suhtautuu Fennicaan.
-
-NOTE: Kungliga is missing those subject topics hence skipped.
+**OK, aikarajaus lisatty tahan kohtaan**
+
+**TODO: Kungligan subject topiceista voisi tuottaa vastaavat niputettavat asiasanaryhmät Kungligalle (Jani ja Mikko): https://github.com/rOpenGov/kungliga/blob/master/output.tables/subject_topic_accepted.csv Näistä sitten oma analyysi joka suhtautuu Fennicaan.** LL: voin tehda jos saan selvan listan asiasanoista.
 
@@
 catalogue <- "Fennica"
-  if (catalogue == "Fennica") {
-    df <- df.full # full time span
-  } else if (catalogue == "Kungliga") {
-    df <- df0 # selected time span
-  }
+df = df0
+
   df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)
@@
   # PAPER CONSUMPTION
-
   theme_set(theme_bw(20))
@@
 
-Sama kuin edellä, mutta asiasanat tässä: hautajaiset;häät;juhlamenot
+Sama kuin edellä, mutta asiasanat tässä: hautajaiset;häät;juhlamenot.
 
@@
 Silloin vernakularisointi tapahtuu erityisesti muualla.
-HUOM: Helsingissä ei ole painettu mitään asiasanalla lääketiede.
+**HUOM: Helsingissä ei ole painettu mitään asiasanalla lääketiede.**
 
@@
 
-TODO_Publishing in Finland #: Kaaviot Fennicasta, jossa lasketaan eri kielten mukaan asiasanojen määrä eri vuosina.
+**TODO_Publishing in Finland** Kaaviot Fennicasta, jossa lasketaan eri kielten mukaan asiasanojen määrä eri vuosina.
 Asiasanat ovat osin arbriträärisiä, mutta ehkä niiden määrän pohjalta voidaan sanoa jotain siitä millä kielellä on julkaistu mitäkin.
@@
 Kaavio joka näyttää asiasanat vuoteen 1828 auttaa toivottavasti asettamaan 1700-luvun suomenkielisen hartauskirjallisuuden kontekstiinsa.
+**LL: voitko tasmentaa - eli tarvitaanko kaavio jossa on joka vuodelle (tai ehka vuosikymmenelle parempi?) ja asiasanalle numero etta montako kertaa ko.
+asiasana esiintyy kunakin vuonna eri dokumenttien yhteydessa ?
+Vai yhteensa uniikkien asiasanojen maara eri vuosina katsomatta niiden sisaltoa ?**
 
@@
 Näissä kiinnostaa myös julkaisijakohtaiset vaihtelut (tai oikeastaan kaikki kuvat joita esim. BOOKINFINLAND-4:ssa. Tämä vain jatkaa siitä mihin tuo edellinen jää.
+
+**OK riittääkö alla olevat vai jotain vielä lisää?**
+
+#```{r topics44, echo=TRUE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, out.width="430px", fig.show="hold"}
+selections = list(
+  c("kirkkohistoria","raamatunhistoria","eksegetiikka","homiletiikka","dogmatiikka","teologia"),
+  c("oppihistoria","antiikki","historia"),
+  c("filosofia","luonnonfilosofia","metafysiikka","logiikka"),
+  c("luonnontieteet","matematiikka","fysiikka","kemia","tähtitiede","maantiede","geodesia","geofysiikka","meteorologia"),
+  c("retoriikka","poetiikka","kielitiede","kielioppi"),
+  c("heprean kieli","kreikan kieli","latinan kieli"),
+  c("psykologia","yhteiskuntafilosofia","valtiofilosofia","talous","raha","moraali","velvollisuudet","kasvatus","maanviljely","maatalous","kalastus"),
+  c("luonnonhistoria","lääketiede","tartuntataudit","eläintiede","kasvitiede","kasvisto","eläimet","eläinsuojelu","eläimistö","eläintaudit","hevonen"),
+  c("naiset","naisen asema","naisasialiikkeet","naisasiajärjestöt"),
+  c("etsintäkuulutukset","rikokset","oikeus","rangaistukset"))
+
+for (sel in selections) {
+
+print(paste(sel, collapse = ";"))
+
+catalogue <- "Fennica"
+df = df0
+df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)
+
+# Selected catalogue with selected topics
+df <- df %>% filter(catalog == catalogue & hit)
+
+langs <- c("Finnish", "Swedish", "Latin", "German", "Other")
+lang <- paste("language.", langs, sep = "")
+otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
+df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
+dfl <- NULL
+for (lan in lang) {
+  # Classify a document to the specifed language
+  # If document is assigned with languages, each case is considered
+  # so one doc may have multiple entries corresponding to different languages
+  # mean(rowSums(df[, lang]) == 1) # 93% Fennica docs have just 1 language
+  # Combine data frames for specified languages
+  dflsub <- filter(df, df[[lan]])
+  if (nrow(dflsub) > 0) {
+    dflsub$language <- gsub("language.", "", lan)
+    dfl <- bind_rows(dfl, dflsub)
+  }
+}
+dfl$language <- factor(dfl$language, levels = names(table(dfl$language)))
+
+# -------------------------------------------
+
+df <- dfl %>% group_by(publication_decade, language) %>%
+             summarise(n = n(),
+	               paper = sum(paper.consumption.km2, na.rm = TRUE))
+
+# TITLE COUNT
+theme_set(theme_bw(20))
+p <- ggplot(df, aes(x = publication_decade, y = n, group = language)) +
+       geom_point(aes(col = language, shape = language), size = 5) +
+       geom_line(aes(col = language, shape = language)) +       
+       xlab("Publication year") +
+       ylab("Title count (n)") +
+       ggtitle(paste("Languages (", catalogue, ")", sep = ""))
+print(p)
+
+# PAPER CONSUMPTION
+theme_set(theme_bw(20))
+p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
+       geom_point(aes(col = language, shape = language), size = 5) +
+       geom_line(aes(col = language, shape = language)) +       
+       xlab("Publication year") +
+       ylab("Paper consumption") +
+       ggtitle(paste("Languages (", catalogue, ")", sep = ""))
+print(p)
+}
+#```
 
@@
 consumption in books (over 50 pages; balls) versus other documents
-(less or equal than 50 pages; triangles). TODO: voidaanko tässä nähdä
-paikallisia eroja ?
+(less or equal than 50 pages; triangles).
+
+TODO: voidaanko tässä nähdä paikallisia eroja ? **TODO MT: voin katsoa jos spesifoitte tarkemmin**
 
@@
 ```
+
 MITEN ON MAHDOLLISTA, ETTÄ VYBORG EI NÄY TÄSSÄ? Tai jos syynä että merkattu Suomen ulkopuolelle, niin se pitäisi saada tähän poikkeuksena mukaan. Tuolla alkupäässä sen pitäisi näkyä.

### 2016-07-04 inst/examples/manuscript-krakow.Rmd
ok

@@
 
-#```{r topics44, echo=TRUE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, out.width="430px", fig.show="hold"}
+```{r topics44, echo=TRUE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, out.width="430px", fig.show="hold"}
 selections = list(
@@
 }
-#```
+```
 
@@
 df <- df %>%
-        filter(catalog == "Fennica" & country == "Finland") %>%
+        filter(catalog == "Fennica") %>%
+	filter(country == "Finland" | publication_place == "Vyborg") %>%
         filter(publication_year >= 1640 & publication_year <= 1828)
@@
 
-MITEN ON MAHDOLLISTA, ETTÄ VYBORG EI NÄY TÄSSÄ? Tai jos syynä että merkattu Suomen ulkopuolelle, niin se pitäisi saada tähän poikkeuksena mukaan. Tuolla alkupäässä sen pitäisi näkyä.
+MITEN ON MAHDOLLISTA, ETTÄ VYBORG EI NÄY TÄSSÄ?
+Tai jos syynä että merkattu Suomen ulkopuolelle, niin se pitäisi saada tähän poikkeuksena mukaan.
+Tuolla alkupäässä sen pitäisi näkyä.
+**LL: oli poissa siksi etta Suomen ulkopuolelle merkattu - lisasin nyt poikkeuksena mukaan**
 
@@
 
-MT: Näissä ensimmäisissä kuvissa myös aikarajaus niin että loppuu 1828.
+MT: Näissä ensimmäisissä kuvissa myös aikarajaus niin että loppuu 1828. **LL OK DONE**
 
@@
 place <- "Turku"
-
-  if (catalogue == "Fennica") {
-    df <- df.full # full time span
-  } else if (catalogue == "Kungliga") {
-    df <- df0 # selected time span
-  }
+df = df0
 
@@
 # PAPER CONSUMPTION
-  if (catalogue == "Fennica") {
-    df <- df.full # full time span
-  } else if (catalogue == "Kungliga") {
-    df <- df0 # selected time span
-  }
+df = df0
 
@@
        geom_bar(stat = "identity", position = "stack", aes(fill = publisher)) + 
-       #geom_point(size = 5, aes(shape = publication_place)) +
-       #geom_line(col = "black", aes(shape = publication_place)) +       
-       # geom_smooth(col = "black", aes(shape = publisher)) + 
        xlab("Publication year") +

### 2016-07-04 inst/examples/manuscript-krakow.Rmd
ok

@@
 
-```{r topics44, echo=TRUE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, out.width="430px", fig.show="hold"}
+```{r topics44, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, out.width="430px", fig.show="hold"}
 selections = list(

### 2016-07-04 inst/examples/manuscript-krakow.Rmd
ok

@@
 
-print(paste(sel, collapse = ";"))
-
 catalogue <- "Fennica"
@@
        ylab("Title count (n)") +
-       ggtitle(paste("Languages (", catalogue, ")", sep = ""))
+       ggtitle(paste("Title count (", print(paste(sel, collapse = ";")), ")", sep = ""))
 print(p)
@@
        ylab("Paper consumption") +
-       ggtitle(paste("Languages (", catalogue, ")", sep = ""))
+       ggtitle(paste("Paper (", print(paste(sel, collapse = ";")), ")", sep = ""))
 print(p)

### 2016-07-04 inst/examples/manuscript-krakow.Rmd
ok
Update manuscript-krakow.Rmd

@@
 
-TODO-järjestyksestä:
-
-Selvensin alle (Publisher analysis kohtaan):
-
-  * PUBLISHER-TODO1
-  * PUBLISHER-TODO2
-  * Lisäksi löytyy muita ajatuksia.
-
-Muiden osalta (voi tehdä jo ilman publisher kenttää), järjestys: **Book printing in Finland** - kohdasta
-
-  * BOOKINFINLAND-TODO1
-  * BOOKINFINLAND-TODO2
-
-Marjanen ja minä siivotaan samalla näitä muita analyysi-ideoita toteuttamiskelpoisiksi ohjeiksi. Jani voi tehdä tätä omatoimisesti myös.
-
-Lisäsin alle seuraavat TODO:t (Ovatko nämä toteuttamiskelpoisia?):
-
-  * TODO_Political events 1
+Seuraavat TODO:t ainakin kesken:
+
   * TODO_Turku in Sweden 1
   * TODO_Turku in Sweden 2
-  * TODO_Publisher analysis_
-  * TODO_Publishing in Finland
-  * TODO_Publishing in Finland_kieliolosuhteet_muualla
+  * TODO_Publisher analysis_ JANI: Täsmennä mitä ajattelit.
+  * TODO_Publishing in Finland JANI: täsmennä mitä ajattelit (ks. alla).
 
@@
 ```
-
-The drop in Fennica is explained largely by Great Nortern War (1700-1721).
-The war and difficult times seems to hit Turku particularly hard in early eighteenth century.
-What is telling also is that the curve of overall publishing activity in Kungliga is much steeper in eighteenth century compared to Fennica also in the second half of the century.
-This is the Enlightenment’s rising trend of knowledge production in most of Europe (for example ESTC has a similar development with Kungliga).
-Thus, development of publishing in Finland is much slower compared to larger European centers in the eighteenth century – this is an important context for the even further difficulties that follow after 1828.
 
@@
 
-TODO: try check duplicates.
-Clustering with identical place, identical year, near identical title and then print table with potential duplicates for manual checks.
-- LL: you mean something different from what HR already did ?
-Duplicates within Fennica, or duplicates between Fennica vs Kungliga ?
-To be removed from all analyses, or a specific figure ?
+TODO: Hege's deduplication code for specific figures. Particular figures to be decided.
 
@@
 Tuntuu vähemmän tärkeältä kuin muut eli skippaan for now.
+OK
 
@@
 
-Mitä voidaan sanoa suomalaisesta kirjatuotannosta ylipäänsä sekä
-löydetäänkö sieltä mitään mielenkiintoisia kehityskulkuja ylipäänsä
-vai pelkästään toteamus, että suomalainen tiedontuotanto oli hyvin
-vähäistä tarkastellulla ajanjaksolla.
-
-Kielikohtainen yleinen vertailu julkaisumääristä ja paperinkulutuksesta.
-Eli kaksi kuvaa (julkaisumäärät ja paperinkulutus kielittäin).
-Miten kielten kehitys suhtautuu toisiinsa (suomi kasvaa, latina laskee jne.)?
-Tarkkailtavia kielikategorioita on 5: suomi, ruotsi, latina, saksa sekä kategoria jossa kaikki muun kielisiset kuin edellä mainitut niputetaan yhteen.
-
-DONE: Venäjän ja ranskankielisestä aineistosta omat graafit myös. OK lisätty samaan kuvaan.
-
 ```{r language1, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, out.width="430px", fig.show="hold"}
@@
 
-Tärkeää on vertailu, mutta myös että nähdään kielikohtainen kehitys. Täten esim. pienemmän saksankielen kohdalla kannattaa varmaan piirtää erillinen kuva.
-
 ```{r language-sel, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, out.width="430px", fig.show="hold"}
@@
 Tämän jälkeen tarkkaillaan aikajanalla näiden teosten esiintymistä, erottavana tekijänä kieli (samat 5 kategoriaa kuin edellisessä analyysissä).
-Erilaisia tarkkailukulmia.
-Tämä analyysi kannattaa jatkaa myös pidemmälle kuin 1828 Fennican osalta.
-
-MT: Korjataan tätä kommenttia.
-Tässä data ei riitä siihen että kannattaa analyysia jatkaa.
-Eli siis 1828 takalautana kaikissa kuvissa.
-Näin viilaamalla noista erittäin hyvistä kuvista tuossa alla (ja kohdassa BOOKINFINLAND-DONE4) tulee vielä parempia.
-**OK, aikarajaus lisatty tahan kohtaan**
 
@@
 
-**OK riittääkö alla olevat vai jotain vielä lisää?**
+**OK riittääkö alla olevat vai jotain vielä lisää?** Voidaan joskus myohemmin tehda Shiny applikaatio jossa valita itse vuoden ja asiasanat lennossa. Mutta ei ehdi tahan.
 
@@
 dfl$language <- factor(dfl$language, levels = names(table(dfl$language)))
-
-# -------------------------------------------
 
@@
 
-MITEN ON MAHDOLLISTA, ETTÄ VYBORG EI NÄY TÄSSÄ?
-Tai jos syynä että merkattu Suomen ulkopuolelle, niin se pitäisi saada tähän poikkeuksena mukaan.
-Tuolla alkupäässä sen pitäisi näkyä.
-**LL: oli poissa siksi etta Suomen ulkopuolelle merkattu - lisasin nyt poikkeuksena mukaan**
-
 Number of unique publishers in selected publication places over time
@@
 Title count per top publisher (two alternative visualizations):
-
-MT: Näissä ensimmäisissä kuvissa myös aikarajaus niin että loppuu 1828. **LL OK DONE**
 

### 2016-07-04 inst/examples/manuscript-krakow.Rmd
Update manuscript-krakow.Rmd

@@
 
-### BOOKINFINLAND-DONE4
+### BOOKINFINLAND-DONE4 TODO:kielten viilaus, pätee myös BOOKINFINLAND-5. Nyt "other" kentästä pitäisi irrottaa relevantit. Nouseeko ranska esiin niin että sille kannattaisi laittaa oma analyysiviiva?
 
@@
 ```
+These are intriguing graphs.
+Potentially they reveal the story of the development of the Academy in Turku in a very elegant manner.
+All disciplines suffer a dramatic decline after 1700, which is due to external causes (war, famine etc.).
+Philosophy (including logic and rhetoric) do not bounce back once the situation is normalised towards the middle of eighteenth century.
+Having been thriving in 17th-century philosophy is close to extinction as an academic subject by the second half of eighteenth century.
+It seems that natural science (and related fields) take over, especially when extended topic of medicine is included here.
+What is interesting about natural science is that the printing happens in several different languages (note also that the topics included in this category are perhaps more wide-ranging, which might play a part).
+Economy (and related fields) is a tremendous case in point that should be contrasted with religious/devotional literature towards the second half of eighteenth century.
+The reason for this is that Swedish is the predominant language (whereas the devotional literature is mainly in Finnish).
+Hebrew-Latin-Greek seem to do better than philosophy.
+Thus, perhaps there is a point in that book: Vain hyödynkö tähden?.
+Latin publishing of theology (and related fields) goes down as well.
+History does suprisingly well throughout the period.
 

### 2016-07-05 inst/examples/manuscript-krakow.Rmd
Update manuscript-krakow.Rmd

@@
 
-Seuraavat TODO:t ainakin kesken:
-
-  * TODO_Turku in Sweden 1
-  * TODO_Turku in Sweden 2
-  * TODO_Publisher analysis_ JANI: Täsmennä mitä ajattelit.
-  * TODO_Publishing in Finland JANI: täsmennä mitä ajattelit (ks. alla).
+**UUSIA TODOJA (5.7.2016) alla:**
+
+**BOOKINFINLAND-5.1**
+**50PAGES-TODO**
+**BOOKFORMATS-TODO**
+**KUNGLIGAPUB-TODO1**
+**KUNGLIGAPUB-TODO2**
+-----------
+**AUTHOR-TODO1**
+**AUTHOR-TODO2**
+Tämä lista kiireysjärjestyksessä.
+Ensimmäiset 3 listalla pitäisi olla kohtuu nopea toteuttaa.
+KUNGLIGAPUB on kaksi vaiheinen ja vaatii vähän enemmän työtä, mutta tärkeä.
+AUTHOR-osio toteutetaan nyt jos ehditään.
+
+**Lisäksi seuraavat TODOt kesken:**
+
+**TODO: Hege's deduplication code for specific figures. Particular figures to be decided.**
+**TODO_Turku in Sweden 1**
+**TODO_Turku in Sweden 2**
+**TODO_Publisher analysis_ JANI: Täsmennä mitä ajattelit.**
+**TODO_Publishing in Finland JANI: täsmennä mitä ajattelit (ks. alla).**
 
@@
 
-MT: We are in a session called "MAPS and SPACE", so I think we need to have some of the results presented on a map.
-Now, the question is what is possible to do within this time?
-But perhaps the publishing houses should be included in this?
 LL: yes we can rather easily add map visualization when it is clear what we like to present using maps.
@@
 If you like to see some result specifically on a map, please mark it so and I can check.
-
-Why Fennica has huge drop in 1700s? Do some publisher disappear (see
-below for an answer..)
 
@@
 
-TODO: Hege's deduplication code for specific figures. Particular figures to be decided.
-
 Paper per title count ratio per publisher. [nähdään voidaanko sanoa onko joku selkeästi asetusten julkaisija ja toisella myös kirjoja (tai asetuskokoelmia).]
@@
 Näkyy näistä top-auktori kuvista.
+
+**AUTHOR-TODO1 Fennica top-auktoreiden julkaisijat: Kuka julkaisee top-auktoreita, milloin ja kuinka paljon?
+Toimenpiteet: valitse tarkastelun kohteeksi Fennicasta top-20 auktoreiden kaikki teokset (yhteinen aineisto, ei erotteluja sen sisällä mihinkään suuntaan).
+Tarkastele tämän aineiston julkaisijoita aikajanalla (eli samansuuntainen analyysi kuin BOOKINFINLAND-DONE3 with top-publishers).
+Esim.
+4 top-julkaisijaa tälle aineistolle + muut kategoria.
+Yksi kuva, 5 viivaa aikajanalla, jos toimii käytännössä.
+Jos ei, niin voi tehdä useamman kuvan.**
+
+**AUTHOR-TODO2 Kungliga top-auktoreiden julkaisijat: sama kuin edellä, mutta nyt Kungliga top-20-auktoreiden teosten julkaiseminen ajakajanalla tarkastelun kohteena eli kuka julkaisee top-auktoreita, milloin ja kuinka paljon.**
 
@@
 
-**TODO: Kungligan subject topiceista voisi tuottaa vastaavat niputettavat asiasanaryhmät Kungligalle (Jani ja Mikko): https://github.com/rOpenGov/kungliga/blob/master/output.tables/subject_topic_accepted.csv Näistä sitten oma analyysi joka suhtautuu Fennicaan.** LL: voin tehda jos saan selvan listan asiasanoista.
+TODO (to be decided): Kungligan subject topiceista voisi tuottaa vastaavat niputettavat asiasanaryhmät Kungligalle (Jani ja Mikko): https://github.com/rOpenGov/kungliga/blob/master/output.tables/subject_topic_accepted.csv Näistä sitten oma analyysi joka suhtautuu Fennicaan.
+LL: voin tehda jos saan selvan listan asiasanoista.
 
@@
 
-### BOOKINFINLAND-DONE4 TODO:kielten viilaus, pätee myös BOOKINFINLAND-5. Nyt "other" kentästä pitäisi irrottaa relevantit. Nouseeko ranska esiin niin että sille kannattaisi laittaa oma analyysiviiva?
+### BOOKINFINLAND-DONE4 **TODO:kielten viilaus, pätee myös BOOKINFINLAND-5. Nyt "other" kentästä pitäisi irrottaa relevantit eli ranska ja venäjä mukaan.**
 
@@
 Silloin vernakularisointi tapahtuu erityisesti muualla.
-**HUOM: Helsingissä ei ole painettu mitään asiasanalla lääketiede.**
+HUOM: Helsingissä ei ole painettu mitään asiasanalla lääketiede.
 
@@
 
-### BOOKINFINLAND-5
+### BOOKINFINLAND-5 **TODO kielten viilaus, ranska ja venäjä omiksi kategorioikseen mukaan**
 
@@
 **OK riittääkö alla olevat vai jotain vielä lisää?** Voidaan joskus myohemmin tehda Shiny applikaatio jossa valita itse vuoden ja asiasanat lennossa. Mutta ei ehdi tahan.
+
+**BOOKINFINLAND-5.1 Jatketaan tätä analyysia julkaisijatarkasteluun.
+Tehdään näiden valmiiden kuvien pohjalta vielä toinen setti kuvia joissa kaikki kielet yhdistetään kuvakohtaisesti (vain yksi viiva, tarkasteltavat asiasanaryhmät kuvakohtaisesti samat) ja piirretään Fennican top-5 julkaisijoiden perusteella kuvat miten he julkaisevat näitä mainittuja sanaryppäitä (vai julkaisevatko ollenkaan).
+Lisäksi kategoria muut julkaisijat pitää piirtää myös koska akateeminen kirjapaino on tässä kategoriassa.**
 
@@
 These are intriguing graphs.
-Potentially they reveal the story of the development of the Academy in Turku in a very elegant manner.
+Potentially they reveal the story of the development of the Academy in Turku in an elegant manner.
 All disciplines suffer a dramatic decline after 1700, which is due to external causes (war, famine etc.).
-Philosophy (including logic and rhetoric) do not bounce back once the situation is normalised towards the middle of eighteenth century.
-Having been thriving in 17th-century philosophy is close to extinction as an academic subject by the second half of eighteenth century.
+Philosophy (including logic and rhetoric) do not bounce back once the situation is normalised towards the middle of the eighteenth century.
+Having been somewhat thriving in 17th-century, philosophy is close to extinction as an academic subject by the second half of eighteenth century.
 It seems that natural science (and related fields) take over, especially when extended topic of medicine is included here.
@@
 
+**KUNGLIGAPUB-TODO1 Tavoitteena asiasana-analyysi paikkakuntakohtaisesti liittyen yliopistojulkaisemiseen samalla tavalla kuin jo tehty Fennicasta.
+Ensimmäinen toimenpide: asiasanalistat Kungligasta 1480-1828 paikkakuntakohtaisesti: Tukholma, Lund, Greifwald, Uppsala, Turku, Lund, Tartu.
+Tämän jälkeen Mikko ja Jani ryhmittelee nämä.**
+
+**KUNGLIGAPUB-TODO2 Edellä tehdyistä asiasanalistoista tuotetaan samanlaiset asiasanaryppäät kuin BOOKINFINLAND-5.
+Tämän jälkeen piirretään Kungligan pohjalta yliopisto-asiasanat aikajanalle samalla tavalla kuin Fennican kohdalla kaupunkikohtaisesti.**
+
 ### Book as media: development over time
@@
 
-TODO: voidaanko tässä nähdä paikallisia eroja ? **TODO MT: voin katsoa jos spesifoitte tarkemmin**
+**50PAGES-TODO: voidaanko tässä nähdä paikallisia eroja?
+Toteutustapa: otetaan tarkastelun kohteeksi yksittäiset kaupungit.
+Käytetään yliopistokaupunkeja: Turku, Tukholma, Lund, Greifswald, Uppsala, Tartu sekä mukaan myös Vyborg ja Helsinki.**
 
@@
 ```
+**BOOKFORMATS-TODO: sama paikallisten erojen tarkasteluun.
+Toteutustapa: otetaan tarkasteluun Kungligasta yksittäiset kaupungit.
+Käytetään yliopistokaupunkeja: Turku, Tukholma, Lund, Greifswald, Uppsala, Tartu sekä mukaan myös Vyborg ja Helsinki.**
 
@@
 ```
+**
 
 Tässä on meille tärkeät kuvat.
-Erityisesti paper consumption (Kungliga) kertoo Valistuksen voittokulusta Euroopassa.
+Erityisesti paper consumption (Kungliga) näyttäisi kertovan Valistuksen voittokulusta Euroopassa.
 Octavo kokoisten kirjojen paper consumption on merkki kirjojen merkityksen korostumisesta ja muutoksesta.

### 2016-07-05 inst/examples/manuscript-krakow.Rmd
Update manuscript-krakow.Rmd

@@
 
-**BOOKINFINLAND-5.1**
-**50PAGES-TODO**
-**BOOKFORMATS-TODO**
-**KUNGLIGAPUB-TODO1**
-**KUNGLIGAPUB-TODO2**
------------
-**AUTHOR-TODO1**
-**AUTHOR-TODO2**
+**BOOKINFINLAND-5.1**;
+**50PAGES-TODO**;
+**BOOKFORMATS-TODO**;
+**KUNGLIGAPUB-TODO1**;
+**KUNGLIGAPUB-TODO2**;
+-----------;
+**AUTHOR-TODO1**;
+**AUTHOR-TODO2**;
 Tämä lista kiireysjärjestyksessä.

### 2016-07-05 inst/examples/manuscript-krakow.Rmd
Update manuscript-krakow.Rmd

--- 2016-07-05 inst/examples/manuscript-krakow.Rmd
@@
 **BOOKINFINLAND-5.1**
+
 **50PAGES-TODO**
+
 **BOOKFORMATS-TODO**
+
 **KUNGLIGAPUB-TODO1**
+
 **KUNGLIGAPUB-TODO2**
+
 -----------
+
 **AUTHOR-TODO1**
+
 **AUTHOR-TODO2**
+
 Tämä lista kiireysjärjestyksessä.
@@
 **TODO: Hege's deduplication code for specific figures. Particular figures to be decided.**
+
 **TODO_Turku in Sweden 1**
+
 **TODO_Turku in Sweden 2**
+
 **TODO_Publisher analysis_ JANI: Täsmennä mitä ajattelit.**
+
 **TODO_Publishing in Finland JANI: täsmennä mitä ajattelit (ks. alla).**

### 2016-07-05 inst/examples/manuscript-krakow.Rmd
Update manuscript-krakow.Rmd

@@
 
-**UUSIA TODOJA (5.7.2016) alla:**
+**UUSIA TODOJA (5.7.2016):**
 
@@
 
+**KIELI%-TODO**
+
 **50PAGES-TODO**
@@
 Tämä lista kiireysjärjestyksessä.
-Ensimmäiset 3 listalla pitäisi olla kohtuu nopea toteuttaa.
-KUNGLIGAPUB on kaksi vaiheinen ja vaatii vähän enemmän työtä, mutta tärkeä.
-AUTHOR-osio toteutetaan nyt jos ehditään.
+Ensimmäiset 4 listalla pitäisi olla kohtuu nopea toteuttaa, ovat täydentäviä kuvia siitä mitä jo toteutettu.
+KUNGLIGAPUB1&2 on kaksi vaiheinen ja vaatii vähän enemmän työtä, mutta tärkeä.
+AUTHOR-osio viivan alla toteutetaan nyt jos ehditään.
+Pikkuhiljaa aletaan miettiä myös mikä karttamuotoinen kuva tuoteutetaan ja aletaan sitten hioa tätä samalla kohti esitystä.
 
@@
 ```
+**KIELI%-TODO sama prosenttianalyysi kielistä mutta paikkakuntakohtaisesti (sekä Fennican että Kungligan mukaan): Turku, Greifswald, Stockholm, Uppsala, Lund. Rajataan analyysi vuoteen 1828.**
 

### 2016-07-05 inst/examples/manuscript-krakow.Rmd
Update manuscript-krakow.Rmd

@@
 ```
+**ranska ja venäjä pitäisi nostaa omiksi ryhmikseen tähän prosenttianalyysiin!**
+
 **KIELI%-TODO sama prosenttianalyysi kielistä mutta paikkakuntakohtaisesti (sekä Fennican että Kungligan mukaan): Turku, Greifswald, Stockholm, Uppsala, Lund. Rajataan analyysi vuoteen 1828.**

### 2016-07-05 inst/examples/manuscript-krakow.Rmd
Update manuscript-krakow.Rmd

@@
 
+**PUBLISHER-TODO2(lisää)**
+
+**BOOKINFINLAND-TODO(lisää)**
+
 **BOOKINFINLAND-5.1**
@@
 Tämä lista kiireysjärjestyksessä.
-Ensimmäiset 4 listalla pitäisi olla kohtuu nopea toteuttaa, ovat täydentäviä kuvia siitä mitä jo toteutettu.
-KUNGLIGAPUB1&2 on kaksi vaiheinen ja vaatii vähän enemmän työtä, mutta tärkeä.
+Ensimmäiset 6 listalla pitäisi olla kohtuu nopea toteuttaa, ensimmäiset 2 (PUBLISHER-TODO2(lisää) + BOOKINFINLAND-TODO(lisää)) ovat rajauskysymyksiä ja seuraavat (BOOKINFINLAND-5.1 + KIELI%-TODO + 50PAGES-TODO + BOOKFORMATS-TODO) ovat täydentäviä kuvia siitä mitä jo toteutettu eli pitäisi olla selkeitä, suoraviivaisia ja nopeita.
+KUNGLIGAPUB1&2 taas on kaksi vaiheinen ja vaatii vähän enemmän työtä, mutta tärkeä.
 AUTHOR-osio viivan alla toteutetaan nyt jos ehditään.
@@
 
-**Lisäksi seuraavat TODOt kesken:**
+**Lisäksi seuraavat TODOt kesken.
+Jani miettii miten tärkeitä nämä ovat nyt kun saatu lisää kuvia.
+Duplikaatti-kuvan toteuttaminen taas päätetään kun saadaan muut tehtyä.
+Jotain sillä kannattaa joka tapauksessa tehdä:**
 
@@
 
-### BOOKINFINLAND-DONE4 **TODO:kielten viilaus, pätee myös BOOKINFINLAND-5. Nyt "other" kentästä pitäisi irrottaa relevantit eli ranska ja venäjä mukaan.**
+### BOOKINFINLAND-DONE4 **BOOKINFINLAND-TODO(lisää) :kielten viilaus, pätee myös BOOKINFINLAND-5. Nyt "other" kentästä pitäisi irrottaa relevantit eli ranska ja venäjä mukaan.**
 
@@
 
+**PUBLISHER-TODO2(lisää) Tässä aikarajaus Turun osalta 1640-1828**
+
 ```{r publishers4-finland, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=7, fig.width=15}

### 2016-07-05 inst/examples/manuscript-krakow.Rmd
ok

@@
 
+```{r kungliga_subjecttopics, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}
+df <- filter(df0, catalog == "Kungliga") %>%
+      filter(publication_year <= 1828)
+
+output.folder <- "figure_201606_Krakow/"
+field <- "subject_topic"
+entries = unlist(strsplit(as.character(df.preprocessed[[field]]), ";"), use.names = FALSE)
+s <- write_xtable(entries, file = paste(output.folder, catalog, "_subjecttopics", min(df$publication_year), "_", max(df$publication_year), ".csv", sep = ""))
+```
+
+[Kungliga subject topics 1488-1828](figure_201606_Krakow/Kungliga_subjecttopics1488_1828.csv)
+
 TODO_Turku in Sweden 1 (jos ehditään ja on mahdollista): Kaaviot Fennicasta ja Kungligasta, jossa lasketaan eri kaupunkien nimikemäärien, paperinkulutuksen ja kustantajien suhteellinen osuus vuoteen 1828.

### 2016-07-05 inst/examples/tmp.R

@@ -1,6 +1,8 @@
-source("analysis.init.R")
-df = df.preprocessed
-df = df[, -grep("language", names(df))]
-fields = c("author_name", "title", "publisher", "publication_year_from", "publication_year_till", "pagecount.orig", "parts", "gatherings.original", "publication_frequency", "dissertation", "synodal", "note_granter", "note_source", "corporate", "successor", "holder", "publication_place", "publication_place", "self_published", "volcount", "volnumber", "issue")
-df = df[, fields]
-write.table(df, file = "~/tmp/kungliga.csv", quote = F, row.names = F, sep = "\t")
+
+df <- filter(df0, catalog == "Kungliga") %>%
+      filter(publication_year <= 1828)
+
+output.folder <- "figure_201606_Krakow/"
+field <- "subject_topic"
+entries = unlist(strsplit(as.character(df.preprocessed[[field]]), ";"), use.names = FALSE)
+s <- write_xtable(entries, file = paste(output.folder, catalog, "_subjecttopics", min(df$publication_year), "_", max(df$publication_year), ".csv", sep = ""))

### 2016-07-05 inst/examples/manuscript-krakow.Rmd
ok

--- 2016-07-05 inst/examples/manuscript-krakow.Rmd
@@
 
+```{r kungliga_subjecttopics, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}
+df <- filter(df0, catalog == "Kungliga") %>%
+      filter(publication_year <= 1828)
+
+output.folder <- "figure_201606_Krakow/"
+field <- "subject_topic"
+entries = unlist(strsplit(as.character(df[[field]]), ";"), use.names = FALSE)
+s <- write_xtable(entries, file = paste(output.folder, catalog, "_subjecttopics", min(df$publication_year), "_", max(df$publication_year), ".csv", sep = ""))
+```
+
+[Kungliga subject topics 1488-1828](figure_201606_Krakow/Kungliga_subjecttopics1488_1828.csv) **Voiko noita TODO Turku in Sweden kohtia nyt yksinkertaistaa? Poista mita ei enaa tarvitakaan**
+
 TODO_Turku in Sweden 1 (jos ehditään ja on mahdollista): Kaaviot Fennicasta ja Kungligasta, jossa lasketaan eri kaupunkien nimikemäärien, paperinkulutuksen ja kustantajien suhteellinen osuus vuoteen 1828.

### 2016-07-05 inst/examples/manuscript-krakow.Rmd
Update manuscript-krakow.Rmd

@@
 
-**KUNGLIGAPUB-TODO1**
+**KUNGLIGAPUB-TODO1 (mietitään onnistuuko yhden Kungligan asiasanalistauksen avulla)**
 
@@
 
-**TODO_Turku in Sweden 1**
+**TODO_Turku in Sweden 1 (JANI TSEKKAA VOIKO YKSINKERTAISTAA SUHTEESSA KUNGLIGAPUBiin**
 
@@
 
-**KUNGLIGAPUB-TODO1 Tavoitteena asiasana-analyysi paikkakuntakohtaisesti liittyen yliopistojulkaisemiseen samalla tavalla kuin jo tehty Fennicasta.
+**KUNGLIGAPUB-TODO1 (mietitään onnistuuko yhden Kungligan asiasanalistauksen avulla, alkuperäinen idea kuitenkin tässä) Tavoitteena asiasana-analyysi paikkakuntakohtaisesti liittyen yliopistojulkaisemiseen samalla tavalla kuin jo tehty Fennicasta.
 Ensimmäinen toimenpide: asiasanalistat Kungligasta 1480-1828 paikkakuntakohtaisesti: Tukholma, Lund, Greifwald, Uppsala, Turku, Lund, Tartu.
-Tämän jälkeen Mikko ja Jani ryhmittelee nämä.**
+Tämän jälkeen Mikko ja Jani ryhmittelee nämä.
+KOKO KUNGLIGA LISTAUS vaikuttaa toistaiseksi siltä että on hyvin vähän asiasanoja jotka liittyvät yliopistoon.
+Näin ollen, voisiko generoida Uppsalasta oman asiasanalistauksen joka toimii evaluaatiokeissinä tuosta paikkakuntakohtaisesta listauksesta?**
 

### 2016-07-05 inst/examples/manuscript-krakow.Rmd
ok

--- 2016-07-05 inst/examples/manuscript-krakow.Rmd
@@
 
-**UUSIA TODOJA (5.7.2016):**
+UUSIA TODOJA (5.7.2016):
+
+**Voitko katsoa että OK ja poistaa sitten tästä mitkä oli jo hoidettu tyydyttävästi ?**
 
@@
 
------------
-
 **AUTHOR-TODO1**
@@
 Tämä lista kiireysjärjestyksessä.
-Ensimmäiset 6 listalla pitäisi olla kohtuu nopea toteuttaa, ensimmäiset 2 (PUBLISHER-TODO2(lisää) + BOOKINFINLAND-TODO(lisää)) ovat rajauskysymyksiä ja seuraavat (BOOKINFINLAND-5.1 + KIELI%-TODO + 50PAGES-TODO + BOOKFORMATS-TODO) ovat täydentäviä kuvia siitä mitä jo toteutettu eli pitäisi olla selkeitä, suoraviivaisia ja nopeita.
-KUNGLIGAPUB1&2 taas on kaksi vaiheinen ja vaatii vähän enemmän työtä, mutta tärkeä.
-AUTHOR-osio viivan alla toteutetaan nyt jos ehditään.
-Pikkuhiljaa aletaan miettiä myös mikä karttamuotoinen kuva tuoteutetaan ja aletaan sitten hioa tätä samalla kohti esitystä.
+Ensimmäiset 6 listalla pitäisi olla kohtuu nopea toteuttaa, ensimmäiset 2 (**PUBLISHER-TODO2(lisää) + BOOKINFINLAND-TODO(lisää)) ovat rajauskysymyksiä ja seuraavat (BOOKINFINLAND-5.1 + KIELI%-TODO + 50PAGES-TODO + BOOKFORMATS-TODO) ovat täydentäviä kuvia.
+
+KUNGLIGAPUB1&2 on kaksi vaiheinen ja vaatii vähän enemmän työtä, mutta tärkeä.
+
+AUTHOR-osio toteutetaan nyt jos ehditään. Pikkuhiljaa aletaan miettiä myös mikä karttamuotoinen kuva tuoteutetaan ja aletaan sitten hioa tätä samalla kohti esitystä.
 
@@
 
-**DONE_Political events 1** Kaaviot Tukholmasta, Uppsalasta, Lundista, Greifswaldista ja Turusta ajalle 1760-1780, joissa näkyy vuosittain julkaisumäärät, arvio paperinkulutuksesta ja kustantajien määrästä.
-Nämä pitää tehdä erikseen Fennicasta ja Kungligasta, eli yhteensä kuusi kaaviota.
+**Political events** Kaaviot Tukholmasta, Uppsalasta, Lundista, Greifswaldista ja Turusta ajalle 1760-1780, joissa näkyy vuosittain julkaisumäärät, arvio paperinkulutuksesta ja kustantajien määrästä.
+Nämä pitää tehdä erikseen Fennicasta ja Kungligasta.
 Tärkeää, että saadaan jokaisesta vuodesta oma piste/luku.
@@
 Synnyttääkö painovapaus uusia julkaisijoita (vastaus on kyllä)?
-
-**NOTE** Tulee enemmän kuin 6 kaaviota.. pistin kaikki viivat erikseen
-  kun pyydettiin erikseen. Huom: pystyakselin skaala vaihtelee
-  kuvittain.
 
@@
 for (myplace in selected.places) {
-  # Use timeinterval year intervals
+
   catal = "Kungliga"
   minyear = 1500
-  #maxyear = 1800
-  #minyear = min(na.omit(df0$publication_year))
-  #maxyear = max(na.omit(df0$publication_year))
 
@@
 ```
-**ranska ja venäjä pitäisi nostaa omiksi ryhmikseen tähän prosenttianalyysiin!**
+ranska ja venäjä pitäisi nostaa omiksi ryhmikseen tähän prosenttianalyysiin! **OK DONE**
 
@@
 
-**DONE_Publishing in Finland_kieliolosuhteet_muualla 1**: Greifswaldin kieliprofiili vuoteen 1828 asti (käytännössä 1815) Kungligan materiaalin osalta.
+**Publishing in Finland kieliolosuhteet muualla 1**: Greifswaldin kieliprofiili vuoteen 1828 asti (käytännössä 1815) Kungligan osalta.
 Onko Greifswaldissa samanlainen kielimonimuotoisuus läsnä kuin Turussa?
 **OK en ollu varma mita tarkotit kieliprofiililla mut plottasin nyt uniikkien kielten maaran mainituille paikoille 1640-1828.
-Nopeasti voin tehda muutakin jos tasmennat.
+Nopeasti voin tehda muutakin jos tasmennatte.
 Hitaammin voin tehda viela enemman jos alan itse tutkia aineistoa huolellisesti mutta sit jaa muut jutut eli skippaan for now.**
@@
   p = ggplot(df, aes(x = publication_year, y = n, group = publication_place, color = publication_place, shape = publication_place)) +
-       #geom_bar(aes(fill = publication_place), position = "dodge", stat = "identity") +
        geom_point() +
@@
        ggtitle(paste("Number of languages:", catalogue)) 
-       #scale_x_discrete(breaks = seq(min(sel.years), max(sel.years), 10))
   print(p)
@@
        geom_line(aes(col = language, shape = language)) +       
-       # geom_smooth(aes(col = language)) + 
        xlab("Publication year") +
        ylab("Title count (n)") +
-       # ylim(c(0, 1.1*max(npub$paper.per.title))) +
        ggtitle(paste("Languages (", place, "/", catalogue, ")", sep = ""))
@@
   p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
-       #geom_bar(stat = "identity", position = "dodge", aes(fill = publisher)) + 
-       geom_point(aes(col = language, shape = language), size = 5) +
-       geom_line(aes(col = language, shape = language)) +       
-       # geom_smooth(aes(col = language)) + 
+       geom_point(aes(col = language, shape = language), size = 5) +
+       geom_line(aes(col = language, shape = language)) +       
        xlab("Publication year") +
        ylab("Paper consumption") +
-       # ylim(c(0, 1.1*max(npub$paper.per.title))) +
        ggtitle(paste("Languages (", place, "/", catalogue, ")", sep = ""))
@@
        geom_line(aes(col = language, shape = language)) +       
-       # geom_smooth(aes(col = language)) + 
        xlab("Publication year") +
        ylab("Title count (n)") +
-       # ylim(c(0, 1.1*max(npub$paper.per.title))) +
        ggtitle(paste("Languages (", publ, "/", catalogue, ")", sep = ""))
@@
 p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
-       #geom_bar(stat = "identity", position = "dodge", aes(fill = publisher)) + 
-       geom_point(aes(col = language, shape = language), size = 5) +
-       geom_line(aes(col = language, shape = language)) +       
-       # geom_smooth(aes(col = language)) + 
+       geom_point(aes(col = language, shape = language), size = 5) +
+       geom_line(aes(col = language, shape = language)) +       
        xlab("Publication year") +
        ylab("Paper consumption") +
-       # ylim(c(0, 1.1*max(npub$paper.per.title))) +
        ggtitle(paste("Languages (", publ, "/", catalogue, ")", sep = ""))
@@
 p <- ggplot(df, aes(x = publication_decade, y = n, group = language)) +
-       #geom_bar(stat = "identity", position = "dodge", aes(fill = publisher)) + 
-       geom_point(aes(col = language, shape = language), size = 5) +
-       geom_line(aes(col = language, shape = language)) +       
-       # geom_smooth(aes(col = language)) + 
+       geom_point(aes(col = language, shape = language), size = 5) +
+       geom_line(aes(col = language, shape = language)) +       
        xlab("Publication year") +
        ylab("Title count (n)") +
-       # ylim(c(0, 1.1*max(npub$paper.per.title))) +
        ggtitle(paste("Languages (", catalogue, ")", sep = ""))
@@
 # PAPER CONSUMPTION
-
-theme_set(theme_bw(20))
 p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
-       #geom_bar(stat = "identity", position = "dodge", aes(fill = publisher)) + 
-       geom_point(aes(col = language, shape = language), size = 5) +
-       geom_line(aes(col = language, shape = language)) +       
-       # geom_smooth(aes(col = language)) + 
+       geom_point(aes(col = language, shape = language), size = 5) +
+       geom_line(aes(col = language, shape = language)) +       
        xlab("Publication year") +
        ylab("Paper consumption") +
-       # ylim(c(0, 1.1*max(npub$paper.per.title))) +
        ggtitle(paste("Languages (", catalogue, ")", sep = ""))
@@
 p <- ggplot(df, aes(x = publication_decade, y = n, group = language)) +
-       #geom_bar(stat = "identity", position = "dodge", aes(fill = publisher)) + 
-       geom_point(aes(col = language, shape = language), size = 5) +
-       geom_line(aes(col = language, shape = language)) +       
-       # geom_smooth(aes(col = language)) + 
+       geom_point(aes(col = language, shape = language), size = 5) +
+       geom_line(aes(col = language, shape = language)) +       
        xlab("Publication year") +
        ylab("Title count (n)") +
-       # ylim(c(0, 1.1*max(npub$paper.per.title))) +
        ggtitle(paste("Languages (", place, "/", catalogue, ")", sep = ""))
@@
 p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
-       #geom_bar(stat = "identity", position = "dodge", aes(fill = publisher)) + 
-       geom_point(aes(col = language, shape = language), size = 5) +
-       geom_line(aes(col = language, shape = language)) +       
-       # geom_smooth(aes(col = language)) + 
+       geom_point(aes(col = language, shape = language), size = 5) +
+       geom_line(aes(col = language, shape = language)) +       
        xlab("Publication year") +
        ylab("Paper consumption") +
-       # ylim(c(0, 1.1*max(npub$paper.per.title))) +
        ggtitle(paste("Languages (", place, "/", catalogue, ")", sep = ""))
@@
   df <- dfl %>% filter(publisher == publ)
-
   df <- df %>% group_by(publication_decade, language) %>%
@@
   p <- ggplot(df, aes(x = publication_decade, y = n, group = language)) +
-       #geom_bar(stat = "identity", position = "dodge", aes(fill = publisher)) + 
-       geom_point(aes(col = language, shape = language), size = 5) +
-       geom_line(aes(col = language, shape = language)) +       
-       # geom_smooth(aes(col = language)) + 
+       geom_point(aes(col = language, shape = language), size = 5) +
+       geom_line(aes(col = language, shape = language)) +       
        xlab("Publication year") +
        ylab("Title count (n)") +
-       # ylim(c(0, 1.1*max(npub$paper.per.title))) +
        ggtitle(paste("Languages (", publ, "/", catalogue, ")", sep = ""))
@@
   # PAPER CONSUMPTION
-
-theme_set(theme_bw(20))
   p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
-       #geom_bar(stat = "identity", position = "dodge", aes(fill = publisher)) + 
-       geom_point(aes(col = language, shape = language), size = 5) +
-       geom_line(aes(col = language, shape = language)) +       
-       # geom_smooth(aes(col = language)) + 
+       geom_point(aes(col = language, shape = language), size = 5) +
+       geom_line(aes(col = language, shape = language)) +       
        xlab("Publication year") +
        ylab("Paper consumption") +
-       # ylim(c(0, 1.1*max(npub$paper.per.title))) +
        ggtitle(paste("Languages (", publ, "/", catalogue, ")", sep = ""))
@@
 
-### BOOKINFINLAND-DONE4 **BOOKINFINLAND-TODO(lisää) :kielten viilaus, pätee myös BOOKINFINLAND-5. Nyt "other" kentästä pitäisi irrottaa relevantit eli ranska ja venäjä mukaan.**
-
-edellisten yhdistäminen, eli täsmälleen samat analyysit, mutta asiasanoina kaikki (todo2 ja todo3), eli: virret;arkkiveisut;hartauskirjat;katekismukset;rukouspäivät;saarnat;aapiset;rukoukset;rukous;hengelliset laulut;hartauspuheet;virsikirjat;hautajaiset;häät;juhlamenot
+### BOOK IN FINLAND 4
+
+Edellisten yhdistäminen.
+Samat analyysit, mutta asiasanoina kaikki aiemmista kohdista yhdistettynä: virret;arkkiveisut;hartauskirjat;katekismukset;rukouspäivät;saarnat;aapiset;rukoukset;rukous;hengelliset laulut;hartauspuheet;virsikirjat;hautajaiset;häät;juhlamenot
 
@@
  df <- dfl %>% filter(publication_place == place)
-
  df <- df %>% group_by(publication_decade, language) %>%
@@
   p <- ggplot(df, aes(x = publication_decade, y = n, group = language)) +
-       #geom_bar(stat = "identity", position = "dodge", aes(fill = publisher)) + 
-       geom_point(aes(col = language, shape = language), size = 5) +
-       geom_line(aes(col = language, shape = language)) +       
-       # geom_smooth(aes(col = language)) + 
+       geom_point(aes(col = language, shape = language), size = 5) +
+       geom_line(aes(col = language, shape = language)) +       
        xlab("Publication year") +
        ylab("Title count (n)") +
-       # ylim(c(0, 1.1*max(npub$paper.per.title))) +
        ggtitle(paste("Languages (", place, "/", catalogue, ")", sep = ""))
@@
   # PAPER CONSUMPTION
-
-theme_set(theme_bw(20))
   p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
-       #geom_bar(stat = "identity", position = "dodge", aes(fill = publisher)) + 
-       geom_point(aes(col = language, shape = language), size = 5) +
-       geom_line(aes(col = language, shape = language)) +       
-       # geom_smooth(aes(col = language)) + 
+       geom_point(aes(col = language, shape = language), size = 5) +
+       geom_line(aes(col = language, shape = language)) +       
        xlab("Publication year") +
        ylab("Paper consumption") +
-       # ylim(c(0, 1.1*max(npub$paper.per.title))) +
        ggtitle(paste("Languages (", place, "/", catalogue, ")", sep = ""))
@@
 p <- ggplot(df, aes(x = publication_decade, y = n, group = language)) +
-       #geom_bar(stat = "identity", position = "dodge", aes(fill = publisher)) + 
-       geom_point(aes(col = language, shape = language), size = 5) +
-       geom_line(aes(col = language, shape = language)) +       
-       # geom_smooth(aes(col = language)) + 
+       geom_point(aes(col = language, shape = language), size = 5) +
+       geom_line(aes(col = language, shape = language)) +       
        xlab("Publication year") +
        ylab("Title count (n)") +
-       # ylim(c(0, 1.1*max(npub$paper.per.title))) +
        ggtitle(paste("Languages (", publ, "/", catalogue, ")", sep = ""))
@@
 
-### BOOKINFINLAND-DONE4
+### BOOK IN FINLAND
 
@@
 
-langs <- c("Finnish", "Swedish", "Latin", "German", "Other")
   lang <- paste("language.", langs, sep = "")
@@
   p <- ggplot(df, aes(x = publication_decade, y = n, group = language)) +
-       #geom_bar(stat = "identity", position = "dodge", aes(fill = publisher)) + 
-       geom_point(aes(col = language, shape = language), size = 5) +
-       geom_line(aes(col = language, shape = language)) +       
-       # geom_smooth(aes(col = language)) + 
+       geom_point(aes(col = language, shape = language), size = 5) +
+       geom_line(aes(col = language, shape = language)) +       
        xlab("Publication year") +
        ylab("Title count (n)") +
-       # ylim(c(0, 1.1*max(npub$paper.per.title))) +
        ggtitle(paste("Languages (", catalogue, ")", sep = ""))
@@
   # PAPER CONSUMPTION
-
-theme_set(theme_bw(20))
   p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
-       #geom_bar(stat = "identity", position = "dodge", aes(fill = publisher)) + 
-       geom_point(aes(col = language, shape = language), size = 5) +
-       geom_line(aes(col = language, shape = language)) +       
-       # geom_smooth(aes(col = language)) + 
+       geom_point(aes(col = language, shape = language), size = 5) +
+       geom_line(aes(col = language, shape = language)) +       
        xlab("Publication year") +
        ylab("Paper consumption") +
-       # ylim(c(0, 1.1*max(npub$paper.per.title))) +
        ggtitle(paste("Languages (", catalogue, ")", sep = ""))
@@
   # TITLE COUNT
-  theme_set(theme_bw(20))
   p <- ggplot(df, aes(x = publication_decade, y = n, group = language)) +
@@
   # PAPER CONSUMPTION
-  theme_set(theme_bw(20))
   p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
@@
 
-**TODO_Publishing in Finland** Kaaviot Fennicasta, jossa lasketaan eri kielten mukaan asiasanojen määrä eri vuosina.
+**Publishing in Finland** Kaaviot Fennicasta, jossa lasketaan eri kielten mukaan asiasanojen määrä eri vuosina.
 Asiasanat ovat osin arbriträärisiä, mutta ehkä niiden määrän pohjalta voidaan sanoa jotain siitä millä kielellä on julkaistu mitäkin.
@@
 Kaavio joka näyttää asiasanat vuoteen 1828 auttaa toivottavasti asettamaan 1700-luvun suomenkielisen hartauskirjallisuuden kontekstiinsa.
-**LL: voitko tasmentaa - eli tarvitaanko kaavio jossa on joka vuodelle (tai ehka vuosikymmenelle parempi?) ja asiasanalle numero etta montako kertaa ko.
-asiasana esiintyy kunakin vuonna eri dokumenttien yhteydessa ?
-Vai yhteensa uniikkien asiasanojen maara eri vuosina katsomatta niiden sisaltoa ?**
-
-### BOOKINFINLAND-5 **TODO kielten viilaus, ranska ja venäjä omiksi kategorioikseen mukaan**
+**OK tässä - onko se mitä haluttiin?**
+
+```{r topics4.per.year, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6}
+df <- filter(df0, catalog == "Fennica") %>% select(publication_year, language, subject_topic)
+df <- unique(df)
+df <- df %>% group_by(publication_year, language) %>% summarise(n = length(unique(unlist(strsplit(subject_topic, ";")))))
+
+langs <- c("Finnish", "Swedish", "Latin", "German", "Russian", "French", "Other")
+df$language[!df$language %in% langs] <- "Other"
+df$language <- factor(df$language, levels = langs)
+
+p <- ggplot(df, aes(x = publication_year, y = n, color = language)) +
+       geom_line() + geom_point() +
+       ggtitle("Number of subject topics")
+
+print(p)
+```
+
+### BOOKINFINLAND 5
+
+Kielten viilaus, ranska ja venäjä omiksi kategorioikseen mukaan **DONE**
 
@@
 
-Näissä kiinnostaa myös julkaisijakohtaiset vaihtelut (tai oikeastaan kaikki kuvat joita esim. BOOKINFINLAND-4:ssa. Tämä vain jatkaa siitä mihin tuo edellinen jää.
-
-**OK riittääkö alla olevat vai jotain vielä lisää?** Voidaan joskus myohemmin tehda Shiny applikaatio jossa valita itse vuoden ja asiasanat lennossa. Mutta ei ehdi tahan.
-
-**BOOKINFINLAND-5.1 Jatketaan tätä analyysia julkaisijatarkasteluun.
-Tehdään näiden valmiiden kuvien pohjalta vielä toinen setti kuvia joissa kaikki kielet yhdistetään kuvakohtaisesti (vain yksi viiva, tarkasteltavat asiasanaryhmät kuvakohtaisesti samat) ja piirretään Fennican top-5 julkaisijoiden perusteella kuvat miten he julkaisevat näitä mainittuja sanaryppäitä (vai julkaisevatko ollenkaan).
-Lisäksi kategoria muut julkaisijat pitää piirtää myös koska akateeminen kirjapaino on tässä kategoriassa.**
+Näissä kiinnostaa myös julkaisijakohtaiset vaihtelut (tai oikeastaan kaikki kuvat joita esim. BOOKINFINLAND-4:ssa. Tämä vain jatkaa siitä mihin tuo edellinen jää. **OK now?**
 
@@
 df <- df %>% filter(catalog == catalogue & hit)
-
-langs <- c("Finnish", "Swedish", "Latin", "German", "Other")
 lang <- paste("language.", langs, sep = "")
@@
 ```
+
+**BOOKINFINLAND-5.1** Jatketaan tätä analyysia julkaisijatarkasteluun.
+Tehdään näiden valmiiden kuvien pohjalta vielä toinen setti kuvia joissa kaikki kielet yhdistetään kuvakohtaisesti (vain yksi viiva, tarkasteltavat asiasanaryhmät kuvakohtaisesti samat) ja piirretään Fennican top-5 julkaisijoiden perusteella kuvat miten he julkaisevat näitä mainittuja sanaryppäitä (vai julkaisevatko ollenkaan).
+Lisäksi kategoria muut julkaisijat pitää piirtää myös koska akateeminen kirjapaino on tässä kategoriassa.
+**OK now ?
+Eli samat kuvat mutta nyt eroteltu julkaisijan mukaan?**
+
+```{r topics44B, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, out.width="430px", fig.show="hold"}
+
+for (sel in selections) {
+
+  catalogue <- "Fennica"
+  df = df0
+  df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)  
+  toppub <- names(top(df, "publisher", 5))
+  df$publisher[!df$publisher %in% toppub] <- "Other"
+
+# Selected catalogue with selected topics
+df <- df %>% filter(catalog == catalogue & hit)
+df <- df %>% group_by(publication_decade, publisher) %>%
+             summarise(n = n(),
+	               paper = sum(paper.consumption.km2, na.rm = TRUE))
+
+# TITLE COUNT
+theme_set(theme_bw(20))
+p <- ggplot(df, aes(x = publication_decade, y = n, group = publisher)) +
+       geom_point(aes(col = publisher, shape = publisher), size = 5) +
+       geom_line(aes(col = publisher, shape = publisher)) +       
+       xlab("Publication year") +
+       ylab("Title count (n)") +
+       ggtitle(paste("Title count (", print(paste(sel, collapse = ";")), ")", sep = ""))
+print(p)
+
+# PAPER CONSUMPTION
+theme_set(theme_bw(20))
+p <- ggplot(df, aes(x = publication_decade, y = paper, group = publisher)) +
+       geom_point(aes(col = publisher, shape = publisher), size = 5) +
+       geom_line(aes(col = publisher, shape = publisher)) +       
+       xlab("Publication year") +
+       ylab("Paper consumption") +
+       ggtitle(paste("Paper (", print(paste(sel, collapse = ";")), ")", sep = ""))
+print(p)
+
+}
+```
+
 These are intriguing graphs.
@@
 
-**KUNGLIGAPUB-TODO1 Tavoitteena asiasana-analyysi paikkakuntakohtaisesti liittyen yliopistojulkaisemiseen samalla tavalla kuin jo tehty Fennicasta.
+**KUNGLIGAPUB-TODO1** asiasana-analyysi paikkakuntakohtaisesti liittyen yliopistojulkaisemiseen samalla tavalla kuin jo tehty Fennicasta.
 Ensimmäinen toimenpide: asiasanalistat Kungligasta 1480-1828 paikkakuntakohtaisesti: Tukholma, Lund, Greifwald, Uppsala, Turku, Lund, Tartu.
-Tämän jälkeen Mikko ja Jani ryhmittelee nämä.**
-
-**KUNGLIGAPUB-TODO2 Edellä tehdyistä asiasanalistoista tuotetaan samanlaiset asiasanaryppäät kuin BOOKINFINLAND-5.
-Tämän jälkeen piirretään Kungligan pohjalta yliopisto-asiasanat aikajanalle samalla tavalla kuin Fennican kohdalla kaupunkikohtaisesti.**
+Tämän jälkeen Mikko ja Jani ryhmittelee nämä.
+**OK skippaan toistaiseksi - päivitä tai poista tämä kohta**
+
+**KUNGLIGAPUB-TODO2** Edellä tehdyistä asiasanalistoista tuotetaan samanlaiset asiasanaryppäät kuin BOOKINFINLAND-5.
+Tämän jälkeen piirretään Kungligan pohjalta yliopisto-asiasanat aikajanalle samalla tavalla kuin Fennican kohdalla kaupunkikohtaisesti.
+**OK skippaan toistaiseksi - päivitä tai poista tämä kohta**
 
@@
 (less or equal than 50 pages; triangles).
-
-**50PAGES-TODO: voidaanko tässä nähdä paikallisia eroja?
-Toteutustapa: otetaan tarkastelun kohteeksi yksittäiset kaupungit.
-Käytetään yliopistokaupunkeja: Turku, Tukholma, Lund, Greifswald, Uppsala, Tartu sekä mukaan myös Vyborg ja Helsinki.**
 
@@
   df2$document.type <- factor(df2$document.type)
-  df2 <- df2 %>% group_by(publication_decade, document.type) %>% summarize(paper.consumption.km2 = sum(paper.consumption.km2, na.rm = TRUE), n = n()) 
+  df2 <- df2 %>% group_by(publication_decade, document.type) %>%
+                 summarize(paper.consumption.km2 = sum(paper.consumption.km2, na.rm = TRUE), n = n()) 
   p <- ggplot(df2, aes(x = publication_decade, y = paper.consumption.km2, group = document.type))
@@
   print(p)
+}
+```
+
+**Local focus** Tarkastelun kohteeksi yliopistokaupungit: Turku, Tukholma, Lund, Greifswald, Uppsala, Tartu, Vyborg, Helsinki. Figure is omitted if there is no data.
+
+```{r bookmedia1local, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=7, fig.show="hold", out.width="430px"}
+sel.places <- c("Turku", "Tukholma", "Lund", "Greifswald", "Uppsala", "Tartu", "Vyborg", "Helsinki")
+for (place in sel.places) {
+ for (catal in unique(df0$catalog)) {
+  df2 <- subset(df0, catalog == catal & publication_place == place)
+  pagelimit = 50
+  df2$document.type <- rep(NA, nrow(df2))
+  df2$document.type[df2$pagecount > pagelimit] <- "book"
+  df2$document.type[df2$pagecount <= pagelimit] <- "pamphlet"
+  df2 <- df2[which(!is.na(df2$document.type)),]
+  df2$document.type <- factor(df2$document.type)
+
+  df2 <- df2 %>% group_by(publication_decade, document.type) %>% summarize(paper.consumption.km2 = sum(paper.consumption.km2, na.rm = TRUE), n = n())
+
+  if (nrow(df2) > 0) {
+    p <- ggplot(df2, aes(x = publication_decade, y = paper.consumption.km2, group = document.type))
+    p <- p + geom_point(aes(shape = document.type), size = 5)
+    p <- p + geom_smooth(method = "loess", color = "black")
+    p <- p + ggtitle("Paper consumption per document type")
+    p <- p + xlab("Year")
+    p <- p + ylab("Paper consumption (km2)")
+    p <- p + scale_color_manual(values=c("black", "darkgray"))
+    p <- p + ggtitle(paste(place, catal))
+    print(p)
+  }
+ }
 }
@@
 ```
-**BOOKFORMATS-TODO: sama paikallisten erojen tarkasteluun.
-Toteutustapa: otetaan tarkasteluun Kungligasta yksittäiset kaupungit.
-Käytetään yliopistokaupunkeja: Turku, Tukholma, Lund, Greifswald, Uppsala, Tartu sekä mukaan myös Vyborg ja Helsinki.**
 
@@
 ```
-**
+
+**Local focus** Tarkasteluun Kungligasta yksittäiset yliopistokaupungit: Turku, Tukholma, Lund, Greifswald, Uppsala, Tartu, Vyborg, Helsinki. Figure is omitted if there is no data.
+
+```{r LIBER-13B, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=10, fig.height=8, fig.show="hold", out.width="430px"}
+for (place in sel.places) {
+for (catal in unique(df0$catalog)) {
+  df2 <- filter(df0, catalog == catal & publication_place == place) %>%
+           group_by(publication_decade, gatherings) %>% summarize(paper.consumption.km2 = sum(paper.consumption.km2, na.rm = TRUE), n = n())
+  df2 <- filter(df2, gatherings %in% setdiff(names(which(table(df2$gatherings) >= 15)), "NA"))
+
+  if (nrow(df2) > 0) {
+  p <- ggplot(df2, aes(y = paper.consumption.km2, x = publication_decade, shape = gatherings, linetype = gatherings))
+  p <- p + geom_point(size = 4)
+  p <- p + geom_smooth(method = "loess", size = 1, color = "black")
+  p <- p + ggtitle("Paper consumption in time by gatherings")
+  p <- p + xlab("Year")
+  p <- p + ylab("Paper consumption (km2)")
+  p <- p + guides(linetype = guide_legend(keywidth = 5), shape = guide_legend(keywidth = 5))
+  p <- p + ggtitle(paste("Paper consumption\n(", place, catal, ")", sep = ""))
+  print(p)
+}
+}
+}
+```
 
@@
      ggtitle("Paper consumption") +
-     #scale_fill_manual(values = c("blue", "black", "darkgreen")) +
      scale_fill_grey() +
@@
 
-**PUBLISHER-TODO2** (Done?) Analysis of the top publishers publishing
-  profile (title count and paper consumption) over time. DONE: now
-  also added for Kungliga.
+**Top publishers publishing profile**
 
@@
 Paper consumption per top publisher (two alternative visualizations):
-
-**PUBLISHER-TODO2(lisää) Tässä aikarajaus Turun osalta 1640-1828**
 
@@
 ```
+
+### Case of Turku
+
+Turun akateemisen julkaisemisen vertautuminen muihin ruotsalaisen
+yliopistojärjestelmän kaupunkeihin: Lukumäärävertailut
+aikajanalla. Akateemisten julkaisujen blokkaaminenhan ei pitäisi olla
+kovinkaan hankalaa [väitöskirjat, mitä muuta tähän siis?].
+
+Turku vs. muu Suomi: Turku osana ruotsalaista yliopistojärjestelmää
+(ml. Tarto) muuttuu tärkeäksi).
+
+Kuinka paljon yliopistoon liittyvää julkaisutoimintaa
+
+Kuinka paljon julkaisijoita
+
+Miten julkaisijoiden verkosto muodostuu Turussa
+
+Miten eri julkaisijoita Turussa voitaisiin luokitella (julkaiseeko
+joku paperinkulutukseltaan vain pieniä dokumentteja, julkaiseeko joku
+painotalo huomattavasti enemmän kuin toiset).
+
+```{r kungliga_subjecttopics, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}
+df <- filter(df0, catalog == "Kungliga") %>%
+      filter(publication_year <= 1828)
+
+field <- "subject_topic"
+entries = unlist(strsplit(as.character(df[[field]]), ";"), use.names = FALSE)
+s <- write_xtable(entries, file = paste(output.folder, catalog, "_subjecttopics", min(df$publication_year), "_", max(df$publication_year), ".csv", sep = ""))
+```
+
+[Kungliga subject topics 1488-1828](figure_201606_Krakow/Kungliga_subjecttopics1488_1828.csv) **Voiko noita TODO Turku in Sweden kohtia nyt yksinkertaistaa? Poista mita ei enaa tarvitakaan**
+
+### Other points if the time allows (I will skip all of these unless they are moved back to main text above)
+
+TODO_Turku in Sweden 2: Kaaviot Fennicasta ja Kungligasta, jossa lasketaan eri kaupunkien mukaan asiasanojen määrä eri vuosina.
+Asiasanat ovat osin arbriträärisiä, mutta ehkä niiden määrän pohjalta voidaan sanoa jotain eri kaupunkien julkaisuprofiilien muutoksista.
+Laaditaan kaaviot Tukholmasta, Uppsalasta, Lundista, Greifswaldista ja Turusta vuoteen 1828.
+Fennican osalta tehdään myös kaavio Vaasasta, jotta nähdään kuinka Vaasan hovioikeuteen painottunut julkaiseminen erottuu Turun julkaisemisesta.
+
+TODO_Turku in Sweden 1 (jos ehditään ja on mahdollista): Kaaviot Fennicasta ja Kungligasta, jossa lasketaan eri kaupunkien nimikemäärien, paperinkulutuksen ja kustantajien suhteellinen osuus vuoteen 1828.
+Eli samanlainen kaavio kuin on kielistä ”Book printing in Finland” –osiossa.
+Laaditaan kaaviot Tukholmasta, Uppsalasta, Lundista, Greifswaldista ja Turusta.
+Voiko myös tehdä erillisen kaavion, jossa Tukholma on poistettu, josta näkee näiden kilpailevien kakkoskaupunkien tilanteen.
+
+TODO_Turku in Sweden 3: Kun kerran ollaan maps and space sessiossa, ehkä kannattaisi tehdä myös kartta jossa, nämä eri kaupungit ja niiden nimikemäärät ovat kartalla.
+Kartat kannattaisi kai tehdä vuosille 1650, 1710, 1767 ja 1800.
+Onko tämä mahdollista?
 
@@
 
-### University publishing
+**University publishing**
 
@@
 muutoksia. See [Fennica](https://github.com/rOpenGov/fennica/blob/master/inst/examples/language.md) and [Kungliga](https://github.com/rOpenGov/kungliga/blob/master/antagomir/language.md),
-
-### Case of Turku
-
-Turun akateemisen julkaisemisen vertautuminen muihin ruotsalaisen
-yliopistojärjestelmän kaupunkeihin: Lukumäärävertailut
-aikajanalla. Akateemisten julkaisujen blokkaaminenhan ei pitäisi olla
-kovinkaan hankalaa [väitöskirjat, mitä muuta tähän siis?].
-
-Turku vs. muu Suomi: Turku osana ruotsalaista yliopistojärjestelmää
-(ml. Tarto) muuttuu tärkeäksi).
-
-Kuinka paljon yliopistoon liittyvää julkaisutoimintaa
-
-Kuinka paljon julkaisijoita
-
-Miten julkaisijoiden verkosto muodostuu Turussa
-
-Miten eri julkaisijoita Turussa voitaisiin luokitella (julkaiseeko
-joku paperinkulutukseltaan vain pieniä dokumentteja, julkaiseeko joku
-painotalo huomattavasti enemmän kuin toiset).
-
-TODO_Turku in Sweden 2: Kaaviot Fennicasta ja Kungligasta, jossa lasketaan eri kaupunkien mukaan asiasanojen määrä eri vuosina.
-Asiasanat ovat osin arbriträärisiä, mutta ehkä niiden määrän pohjalta voidaan sanoa jotain eri kaupunkien julkaisuprofiilien muutoksista.
-Laaditaan kaaviot Tukholmasta, Uppsalasta, Lundista, Greifswaldista ja Turusta vuoteen 1828.
-Fennican osalta tehdään myös kaavio Vaasasta, jotta nähdään kuinka Vaasan hovioikeuteen painottunut julkaiseminen erottuu Turun julkaisemisesta.
-
-```{r kungliga_subjecttopics, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}
-df <- filter(df0, catalog == "Kungliga") %>%
-      filter(publication_year <= 1828)
-
-output.folder <- "figure_201606_Krakow/"
-field <- "subject_topic"
-entries = unlist(strsplit(as.character(df[[field]]), ";"), use.names = FALSE)
-s <- write_xtable(entries, file = paste(output.folder, catalog, "_subjecttopics", min(df$publication_year), "_", max(df$publication_year), ".csv", sep = ""))
-```
-
-[Kungliga subject topics 1488-1828](figure_201606_Krakow/Kungliga_subjecttopics1488_1828.csv) **Voiko noita TODO Turku in Sweden kohtia nyt yksinkertaistaa? Poista mita ei enaa tarvitakaan**
-
-TODO_Turku in Sweden 1 (jos ehditään ja on mahdollista): Kaaviot Fennicasta ja Kungligasta, jossa lasketaan eri kaupunkien nimikemäärien, paperinkulutuksen ja kustantajien suhteellinen osuus vuoteen 1828.
-Eli samanlainen kaavio kuin on kielistä ”Book printing in Finland” –osiossa.
-Laaditaan kaaviot Tukholmasta, Uppsalasta, Lundista, Greifswaldista ja Turusta.
-Voiko myös tehdä erillisen kaavion, jossa Tukholma on poistettu, josta näkee näiden kilpailevien kakkoskaupunkien tilanteen.
-
-TODO_Turku in Sweden 3: Kun kerran ollaan maps and space sessiossa, ehkä kannattaisi tehdä myös kartta jossa, nämä eri kaupungit ja niiden nimikemäärät ovat kartalla.
-Kartat kannattaisi kai tehdä vuosille 1650, 1710, 1767 ja 1800.
-Onko tämä mahdollista?
-
-### Other points if the time allows
 

### 2016-07-05 inst/examples/manuscript-krakow.Rmd

@@
 History does suprisingly well throughout the period.
-
-**KUNGLIGAPUB-TODO1** asiasana-analyysi paikkakuntakohtaisesti liittyen yliopistojulkaisemiseen samalla tavalla kuin jo tehty Fennicasta.
-Ensimmäinen toimenpide: asiasanalistat Kungligasta 1480-1828 paikkakuntakohtaisesti: Tukholma, Lund, Greifwald, Uppsala, Turku, Lund, Tartu.
-Tämän jälkeen Mikko ja Jani ryhmittelee nämä.
-**OK skippaan toistaiseksi - päivitä tai poista tämä kohta**
-
-**KUNGLIGAPUB-TODO2** Edellä tehdyistä asiasanalistoista tuotetaan samanlaiset asiasanaryppäät kuin BOOKINFINLAND-5.
-Tämän jälkeen piirretään Kungligan pohjalta yliopisto-asiasanat aikajanalle samalla tavalla kuin Fennican kohdalla kaupunkikohtaisesti.
-**OK skippaan toistaiseksi - päivitä tai poista tämä kohta**
 
@@
 s <- write_xtable(entries, file = paste(output.folder, catalog, "_subjecttopics", min(df$publication_year), "_", max(df$publication_year), ".csv", sep = ""))
+
+df <- filter(df0, catalog == "Kungliga" & publication_place == "Uppsala") %>%
+      filter(publication_year <= 1828)
+
+field <- "subject_topic"
+entries = unlist(strsplit(as.character(df[[field]]), ";"), use.names = FALSE)
+s <- write_xtable(entries, file = paste(output.folder, catalog, "_Uppsala_subjecttopics", min(df$publication_year), "_", max(df$publication_year), ".csv", sep = ""))
 ```
@@
 
+[Kungliga subject topics Uppsala 1488-1828](figure_201606_Krakow/Kungliga_Uppsala_subjecttopics1488_1828.csv) **Voiko noita TODO Turku in Sweden kohtia nyt yksinkertaistaa?
+Poista mita ei enaa tarvitakaan**
+
 ### Other points if the time allows (I will skip all of these unless they are moved back to main text above)
+
+**KUNGLIGAPUB-TODO1** (mietitään onnistuuko yhden Kungligan asiasanalistauksen avulla, alkuperäinen idea kuitenkin tässä) Tavoitteena asiasana-analyysi paikkakuntakohtaisesti liittyen yliopistojulkaisemiseen samalla tavalla kuin jo tehty Fennicasta.
+Ensimmäinen toimenpide: asiasanalistat Kungligasta 1480-1828 paikkakuntakohtaisesti: Tukholma, Lund, Greifwald, Uppsala, Turku, Lund, Tartu.
+Tämän jälkeen Mikko ja Jani ryhmittelee nämä.
+KOKO KUNGLIGA LISTAUS vaikuttaa toistaiseksi siltä että on hyvin vähän asiasanoja jotka liittyvät yliopistoon.
+Näin ollen, voisiko generoida Uppsalasta oman asiasanalistauksen joka toimii evaluaatiokeissinä tuosta paikkakuntakohtaisesta listauksesta?**OK DONE see link above Kungliga subject topics Uppsala 1488-1828**
+
+**KUNGLIGAPUB-TODO2** Edellä tehdyistä asiasanalistoista tuotetaan samanlaiset asiasanaryppäät kuin BOOKINFINLAND-5.
+Tämän jälkeen piirretään Kungligan pohjalta yliopisto-asiasanat aikajanalle samalla tavalla kuin Fennican kohdalla kaupunkikohtaisesti.
+**OK skippaan toistaiseksi - päivitä tai poista tämä kohta**
 

### 2016-07-05 inst/examples/20160715-slides-Krakow.Rmd
testing rstudio sync

---
title: "Digital History in Finland, 1488-1828"
author: "Mikko Tolonen, Jani Marjanen, Hege Roivainen, Leo Lahti"
date: "`r Sys.Date()`"
output: 
  beamer_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

### 2016-07-05 inst/examples/20160715-slides-Krakow.Rmd
ok

@@
 ---
-title: "Digital History in Finland, 1488-1828"
+title: "Printing in a Periphery: a Quantitative Study of Finnish Knowledge Production, 1640-1828"
 author: "Mikko Tolonen, Jani Marjanen, Hege Roivainen, Leo Lahti"
@@
 
-```{r setup, include=FALSE}
+```{r 201606krakow-init, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, cache=TRUE}
+# Default time span for the slides
+min.year <- 1488
+max.year <- 1828
+
+library(stringr)
+library(dplyr)
+library(tidyr)
+library(reshape2)
+library(ggplot2)
+library(bibliographica)
+library(fennica)
+library(sorvi)
+
 knitr::opts_chunk$set(echo = FALSE)
+knitr::opts_chunk$set(fig.path = "slides_201606_Krakow/", dev="CairoPNG")
+
+# Nice theme
+theme_set(theme_bw(26))
 ```
 
-## R Markdown
+```{r 201606krakow-init2, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, cache=TRUE}
+# Read data
+fen0 <- readRDS("fennica.Rds")
+kun0 <- readRDS("kungliga.Rds")
 
-This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.
+fenraw <- readRDS("fennica.raw.Rds")
+kunraw <- readRDS("kungliga.raw.Rds")
 
-When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.
+fen <- fen0 %>% filter(publication_year >= min.year & publication_year <= max.year)
+kun <- kun0 %>% filter(publication_year >= min.year & publication_year <= max.year)
 
-## Slide with Bullets
+# Full time span
+df.full = bind_rows(fen0, kun0)
+df.full$catalog = factor(c(rep("Fennica", nrow(fen0)), rep("Kungliga", nrow(kun0))))
 
-- Bullet 1
-- Bullet 2
-- Bullet 3
-
-## Slide with R Output
-
-```{r cars, echo = TRUE}
-summary(cars)
+# Selected time spam
+df0 = bind_rows(fen, kun)
+df0$catalog = factor(c(rep("Fennica", nrow(fen)), rep("Kungliga", nrow(kun))))
 ```
 
-## Slide with Plot
+## Peaks and drops – role of publishers and contingency
 
-```{r pressure}
-plot(pressure)
+```{r publishingovertime, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10}
+# https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/publishingovertime-1.png
+library(stringr)
+library(dplyr)
+library(tidyr)
+library(reshape2)
+library(ggplot2)
+library(bibliographica)
+library(fennica)
+library(sorvi)
+
+df2 <- df0 %>% group_by(publication_decade, catalog) %>% summarise(n = n())
+p <- ggplot(df2, aes(x = publication_decade, y = n)) +
+     geom_line(aes(linetype = catalog)) +
+     geom_point(aes(shape = catalog), size = 3) +     
+     ylab("Title count (n)") + xlab("Publication year") +  
+     ggtitle("Overall publishing activity")
+print(p)
 ```
+
+---
+
+## Comparing publishing activity
+
+Comparison of printing activity in
+
+- Turku
+- Uppsala
+- Lund 
+- Stockholm
+
+```{r publishingactivitycomparisons, echo=FALSE, message=FALSE, cache=FALSE, fig.width=8, fig.height=6, fig.show="hold", out.width="430px"}
+#https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/publishingactivitycomparisons-2.png
+selected.places = c("Turku", "Uppsala", "Lund", "Stockholm")
+df2 <- df0 %>% group_by(publication_decade, publication_place, catalog) %>%
+               summarise(n = n()) %>%
+	       filter(publication_place %in% selected.places) # %>%
+df2$catalog = factor(df2$catalog, levels = rev(c("Fennica", "Kungliga")))
+df2$publication_place = droplevels(factor(df2$publication_place))
+df3 = spread(df2, publication_decade, n, fill = 0)
+df2 = melt(df3)
+colnames(df2) = c("publication_place", "catalog", "publication_decade", "n")
+df2$publication_decade = as.numeric(as.character(df2$publication_decade))
+df2$n = as.numeric(as.character(df2$n))
+for (catal in unique(df2$catalog)) {
+
+  p <- ggplot(subset(df2, catalog == catal), aes(x = publication_decade, y = n)) +
+     geom_line(aes(linetype = publication_place)) +
+     geom_point(aes(shape = publication_place), size = 3) +
+     #scale_y_log10() +
+     #facet_wrap(catalog ~ .) + 
+     ylab("Title count (n)") + xlab("Publication year") +  
+     ggtitle(catal)
+  print(p)
+
+}
+```
+
+---
+
+## Publishers Finland
+
+Number of unique publishers in top publication places over time (Fennica)
+
+```{r publishers2-finland, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=7, fig.width=15}
+# https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/publishers2-finland-1.png
+df <- df0
+df <- df %>%
+        filter(catalog == "Fennica") %>%
+	filter(country == "Finland" | publication_place == "Vyborg") %>%
+        filter(publication_year >= 1640 & publication_year <= 1828)
+
+# Top publication places
+ntop <- 10
+top <- names(top(df, "publication_place", ntop))
+
+df <- df %>%	
+        filter(publication_place %in% top) %>%	
+        select(publication_decade, publication_place, publisher)
+
+npub <- unique(df) %>% group_by(publication_decade, publication_place) %>% tally()
+npub$publication_place <- factor(npub$publication_place, levels = top)
+theme_set(theme_bw(20))
+
+p <- ggplot(npub, aes(x = publication_decade, y = n)) +
+       geom_bar(stat = "identity", position = "stack", aes(fill = publication_place)) + 
+       xlab("Publication year") +
+       ylab("Unique publishers (n)") +        
+       ggtitle("Unique publishers in top publication places (Finland/Fennica)")
+print(p)
+```
+
+---
+
+## Publishers Kungliga
+
+```{r publishers2-kungliga, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=7, fig.width=15}
+# https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/publishers2-kungliga-1.png
+df <- df0
+catalogue <- "Kungliga"
+df <- df %>%
+        filter(catalog == catalogue) %>%
+        filter(publication_year >= 1640 & publication_year <= 1828)
+
+# Selected publication places
+top <- c("Stockholm", "Lund", "Uppsala", "Greifswald")
+df <- df %>%	
+        filter(publication_place %in% top) %>%	
+        select(publication_decade, publication_place, publisher)
+
+npub <- unique(df) %>% group_by(publication_decade, publication_place) %>% tally()
+npub$publication_place <- factor(npub$publication_place, levels = top)
+theme_set(theme_bw(20))
+
+p <- ggplot(npub, aes(x = publication_decade, y = n)) +
+       geom_bar(stat = "identity", position = "stack", aes(fill = publication_place)) + 
+       xlab("Publication year") +
+       ylab("Unique publishers (n)") +        
+       ggtitle(paste("Unique publishers in selected publication places (", catalogue, ")"))
+print(p)
+```
+
+---
+
+## Title count per top publisher
+
+```{r publishers3-finland, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=7, fig.width=15, fig.show="hold"}
+# https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/publishers3-finland-1.png
+
+for (catalogue in c("Fennica", "Kungliga")) {
+
+place <- "Turku"
+df = df0
+
+df <- df %>%
+        filter(catalog == catalogue & publication_place == place)
+
+df <- df %>%	
+        select(publication_decade, publisher, paper.consumption.km2)
+
+# Group small publishers
+# Top publishers by title count
+ntop <- 10
+top <- names(top(df, "publisher", ntop))
+df$publisher[!df$publisher %in% top] <- "Other"
+df$publisher <- factor(df$publisher, c(top, "Other"))
+
+# Title count per decade & publisher	
+npub <- df %>% group_by(publication_decade, publisher) %>% tally()
+
+# TITLE COUNT
+theme_set(theme_bw(20))
+p <- ggplot(npub, aes(x = publication_decade, y = n)) +
+       geom_bar(stat = "identity", position = "stack", aes(fill = publisher)) + 
+       xlab("Publication year") +
+       ylab("Title count (n)") +        
+       ggtitle(paste("Title count per publisher (", place, "/", catalogue, ")", sep = ""))
+print(p)
+
+}
+```
+
+---
+
+## Publisher paper vs. title count
+
+Paper per title count ratio per publisher. [nähdään voidaanko sanoa onko joku selkeästi asetusten julkaisija ja toisella myös kirjoja (tai asetuskokoelmia).]
+
+```{r publisherpapertitle, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, out.width="430px", fig.show="hold"}
+
+# https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/publisherpapertitle-1.png
+
+for (catalogue in c("Fennica", "Kungliga")) {
+
+df <- df0
+df <- df %>%
+        filter(catalog == catalogue) %>%
+	filter(publication_year >= 1640 & publication_year <= 1828)
+
+# Selected ones
+top <- names(top(df, "publisher", 5))
+df$publisher[!df$publisher %in% top] <- "Other"
+df$publisher <- factor(df$publisher, levels = c(top, "Other"))
+
+# Publishing per decade & publisher	
+npub <- df %>%
+     	  group_by(publication_decade, publisher) %>%
+	  summarize(paper = sum(paper.consumption.km2, na.rm = TRUE), n = n()) %>%
+	  mutate(paper.per.title = paper/n)
+
+theme_set(theme_bw(20))
+p <- ggplot(npub, aes(x = publication_decade, y = paper.per.title, group = publisher)) +
+       geom_point(size = 5, aes(shape = publisher, color = publisher)) +
+       geom_smooth(col = "black", aes(shape = publisher, fill = publisher, color = publisher)) + 
+       xlab("Publication year") +
+       ylab("Paper per title") +
+       ylim(c(0, 1.1*max(npub$paper.per.title))) +
+       ggtitle(paste("Paper per title ratio (", catalogue, ")", sep = ""))
+print(p)
+}
+```
+
+---
+
+## Drop 1700
+
+Publisher title count changes around 1700 drop in Turku, the most significant publishing place at the time:
+
+```{r drop1700B, echo=FALSE, message=FALSE, warning=FALSE, fig.width=15, fig.height=7}
+# https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/drop1700B-1.png
+
+catalogue <- "Fennica"
+place <- "Turku"
+
+df <- df0
+df <- df %>%
+        filter(catalog == catalogue & publication_place == place) %>%
+        filter(publication_year >= 1650 & publication_year < 1750)
+
+# Selected ones
+top <- names(top(df, "publisher", 5))
+df$publisher[!df$publisher %in% top] <- "Other"
+df$publisher <- factor(df$publisher, levels = c(top, "Other"))
+
+# Publishing per year & publisher	
+npub <- df %>%
+     	  group_by(publication_year, publisher) %>%
+	  summarize(paper = sum(paper.consumption.km2, na.rm = TRUE), n = n())
+
+theme_set(theme_bw(20))
+p <- ggplot(npub, aes(x = publication_year, y = n, group = publisher)) +
+       geom_point(size = 5, aes(shape = publisher, color = publisher)) +
+       geom_smooth(col = "black", aes(shape = publisher, fill = publisher, color = publisher)) + 
+       xlab("Publication year") +
+       ylab("Title count (n)") +
+       ylim(c(0, 1.1*max(npub$n))) +
+       ggtitle(paste("Title count (", place, "/", catalogue, ")", sep = ""))
+print(p)
+```
+
+---
+
+## Riksdagar 2
+
+Focus on Gävle (gray) during riksdagar. Gävle has `r sum("Gävle" %in% fen$publication_place)` occurrences in Fennica, hence not included here. The figure on Gävle is based on Kungliga.
+
+```{r riksdar2, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=7, out.width="430px"}
+# https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/riksdar2-1.png
+
+  # Use timeinterval year intervals
+  myplace = "Gävle" # Norrköping / Stockholm
+  minyear = 1700
+  maxyear = 1800
+  catal = "Kungliga"
+
+  df = subset(df0, publication_place == myplace & catalog == catal)
+  df <- subset(df, publication_year >= minyear & publication_year < maxyear)
+
+  timeinterval <- 1
+  df$timeunit <- round(df$publication_year/timeinterval)*timeinterval
+
+  df$unity = rep(1, nrow(df))
+  publications <- tapply(df$unity, list(df$timeunit), sum)
+
+  publications[is.na(publications)] <- 0 # Set NAs to 0
+  publications <- publications/timeinterval # Instead of decadal sum, use average annual output 
+  dfm <- melt(publications) 
+  names(dfm) <- c("Time", "Documents")
+  dfm <- transform(dfm, date = as.numeric(as.character(Time)))
+  ymin = min(dfm$Documents)
+  ymax = max(dfm$Documents)
+
+  rect_left <- c(min(na.omit(dfm$date)),
+               1719-.5, 1719+.5, # Stockholm 20 januari 1719 1 juni 1719
+               1734-.5, 1734+.5, # Stockholm 14 maj 1734 14 december 1734
+               1765-.5, 1766+.5, # Stockholm 21 februari 1765 21 oktober 1766
+               1769-.5, 1770+.5, # Norrköping & Stockholm 22 april 1769 5 februari 1770
+               1771-.5, 1772+.5, # Stockholm 19 juni 1771 12 september 1772
+               1792-.5, 1792+.5, # Gävle 26 januari 1792 24 februari 1792	       
+               max(na.omit(dfm$date)))
+  rectangles <- data.frame(
+    xmin = rect_left[-length(rect_left)],
+    xmax = rect_left[-1],
+    ymin = ymin,
+    ymax = ymax
+    )
+  rectangles$shade <- rep(c("White", "Highlight"), length = nrow(rectangles))
+
+ riksplace = c("Stockholm", "Stockholm", "Stockholm", "Norrköping", "Stockholm", "Gävle")
+ cols = c("gray", "lightblue", "yellow", "white")
+ rectangles$shade[rectangles$shade == "Highlight"] = riksplace
+ rectangles$shade = factor(rectangles$shade)
+
+  # Draw Figure
+  theme_set(theme_bw(20))
+  p <- ggplot()
+  p <- p + geom_rect(data = rectangles, 
+	   aes(xmin=xmin, xmax=xmax,
+	       ymin=ymin, ymax=ymax,
+	       fill=shade), alpha=0.8) + 
+         scale_fill_manual(values = cols) # + guides(fill = "none") 
+  p <- p + geom_line(data = dfm, aes(x = date, y = Documents), col = "black")
+  p <- p + geom_point(data = dfm, aes(x = date, y = Documents), col = "black")
+  p <- p + scale_x_continuous(breaks = seq(minyear, maxyear, 20))
+  p <- p + ggtitle("Publishing activity")
+  p <- p + ylab("Documents / Year")
+  p <- p + xlab("Year")
+  p <- p + ggtitle(paste(myplace, " (", catal, ")", sep = ""))
+  print(p)
+```
+
+---
+
+# Language
+
+## Book printing in Finland / Language
+
+```{r language1, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, out.width="430px", fig.show="hold"}
+# https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/language1-1.png
+# https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/language1-2.png
+
+for (catalogue in c("Fennica", "Kungliga")) {
+
+  df <- df0
+  df <- df %>% filter(catalog == catalogue)
+
+langs <- c("Finnish", "Swedish", "Latin", "German", "Russian", "French", "Other")
+lang <- paste("language.", langs, sep = "")
+otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
+df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
+
+dfl <- NULL
+
+for (lan in lang) {
+
+  # Classify a document to the specifed language
+  # If document is assigned with languages, each case is considered
+  # so one doc may have multiple entries corresponding to different languages
+  # mean(rowSums(df[, lang]) == 1) # 93% Fennica docs have just 1 language
+  # Combine data frames for specified languages
+  dflsub <- filter(df, df[[lan]])
+  dflsub$language <- gsub("language.", "", lan)
+  dfl <- bind_rows(dfl, dflsub)
+
+}
+dfl$language <- factor(dfl$language, levels = langs)
+
+df <- dfl %>% group_by(publication_decade, language) %>%
+             summarise(n = n(),
+	               paper = sum(paper.consumption.km2, na.rm = TRUE))
+
+# TITLE COUNT
+p <- ggplot(df, aes(x = publication_decade, y = n, group = language)) +
+       geom_point(aes(col = language, shape = language), size = 5) +
+       geom_line(aes(col = language, shape = language)) +       
+       xlab("Publication year") +
+       ylab("Title count (n)") +
+       ggtitle(paste("Languages (", catalogue, ")", sep = ""))
+print(p)
+
+# PAPER CONSUMPTION
+p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
+       geom_point(aes(col = language, shape = language), size = 5) +
+       geom_line(aes(col = language, shape = language)) +       
+       xlab("Publication year") +
+       ylab("Paper consumption") +
+       ggtitle(paste("Languages (", catalogue, ")", sep = ""))
+print(p)
+
+}
+```
+
+---
+
+## Same with percentages
+
+```{r language-perc, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, out.width="430px", fig.show="hold"}
+for (catalogue in c("Fennica", "Kungliga")) {
+
+  if (catalogue == "Fennica") {
+    df <- df.full # full time span
+  } else if (catalogue == "Kungliga") {
+    df <- df0 # selected time span
+  }
+
+  df <- df %>% filter(catalog == catalogue)
+
+langs <- c("Finnish", "Swedish", "Latin", "German", "Other")
+lang <- paste("language.", langs, sep = "")
+otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
+df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
+
+dfl <- NULL
+
+for (lan in lang) {
+
+  # Classify a document to the specifed language
+  # If document is assigned with languages, each case is considered
+  # so one doc may have multiple entries corresponding to different languages
+  # mean(rowSums(df[, lang]) == 1) # 93% Fennica docs have just 1 language
+  # Combine data frames for specified languages
+  dflsub <- filter(df, df[[lan]])
+  dflsub$language <- gsub("language.", "", lan)
+  dfl <- bind_rows(dfl, dflsub)
+
+}
+dfl$language <- factor(dfl$language, levels = langs)
+
+df <- dfl %>% group_by(publication_decade, language) %>%
+     	     summarise(n = n())
+
+# Calculate percentages
+dff <- spread(df, language, n, fill = 0)
+dff[, -1] <- 100 * t(apply(dff[, -1], 1, function (x) {x/sum(x)}))
+dff <- gather(dff, publication_decade);
+colnames(dff) <- c("publication_decade", "language", "f")
+dff$language <- factor(dff$language, levels = langs)
+
+theme_set(theme_bw(20))
+p <- ggplot(dff, aes(x = publication_decade, y = f)) +
+     geom_bar(position = "stack", stat = "identity", aes(fill = language)) + 
+     xlab("Publication year") +
+     ylab("Title count frequency (%)") +
+     ggtitle(paste("Languages (", catalogue, ")", sep = ""))
+print(p)
+
+}
+```
+
+---
+
+## Religious literature
+
+Fennica, Hartaus- yms.
+kirjallisuuden kieli (suomi vai ruotsi) milloin alkaa yleistyä suomenkielinen ja miten tämän julkaiseminen suomeksi kasvaa?
+virret;arkkiveisut;hartauskirjat;katekismukset;rukouspäivät;saarnat;aapiset;rukoukset;rukous;hengelliset laulut;hartauspuheet;virsikirjat.
+
+```{r topics, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, out.width="430px", fig.show="hold"}
+# https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/topics-2.png
+sel <- c("virret","arkkiveisut","hartauskirjat","katekismukset","rukouspäivät","saarnat","aapiset","rukoukset","rukous","hengelliset laulut","hartauspuheet","virsikirjat")
+catalogue <- "Fennica"
+langs <- c("Finnish", "Swedish", "Latin", "German", "Other")
+
+  # Selected catalogue with selected years
+  df = filter(df0, catalog == catalogue & publication_year >= 1640 & publication_year <= 1828)
+
+  # Selected topics
+  df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)  
+  df <- df %>% filter(catalog == catalogue & hit)
+
+  lang <- paste("language.", langs, sep = "")
+  otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
+  df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
+  dfl <- NULL
+  for (lan in lang) {
+    # Classify a document to the specifed language
+    # If document is assigned with languages, each case is considered
+    # so one doc may have multiple entries corresponding to different languages
+    # mean(rowSums(df[, lang]) == 1) # 93% Fennica docs have just 1 language
+    # Combine data frames for specified languages
+    dflsub <- filter(df, df[[lan]])
+    dflsub$language <- gsub("language.", "", lan)
+    dfl <- bind_rows(dfl, dflsub)
+  }
+  dfl$language <- factor(dfl$language, levels = langs)
+  df <- dfl %>% group_by(publication_decade, language) %>%
+             summarise(n = n(),
+	               paper = sum(paper.consumption.km2, na.rm = TRUE))
+
+  # PAPER CONSUMPTION
+  theme_set(theme_bw(20))
+  p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
+       geom_point(aes(col = language, shape = language), size = 5) +
+       geom_line(aes(col = language, shape = language)) +       
+       xlab("Publication year") +
+       ylab("Paper consumption") +
+       ggtitle(paste("Languages (", catalogue, ")", sep = "")) 
+  print(p)
+```
+
+---
+
+### BOOKINFINLAND DONE3
+
+Sama kuin edellä, mutta asiasanat tässä: hautajaiset;häät;juhlamenot.
+
+```{r topics2, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, out.width="430px", fig.show="hold"}
+# https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/topics2-2.png
+
+sel <- c("hautajaiset", "häät", "juhlamenot")
+catalogue <- "Fennica"
+  if (catalogue == "Fennica") {
+    df <- df.full # full time span
+  } else if (catalogue == "Kungliga") {
+    df <- df0 # selected time span
+  }
+  df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)
+
+# Selected catalogue with selected topics
+df <- df %>% filter(catalog == catalogue & hit)
+
+langs <- c("Finnish", "Swedish", "Latin", "German", "Other")
+lang <- paste("language.", langs, sep = "")
+otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
+df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
+dfl <- NULL
+for (lan in lang) {
+  # Classify a document to the specifed language
+  # If document is assigned with languages, each case is considered
+  # so one doc may have multiple entries corresponding to different languages
+  # mean(rowSums(df[, lang]) == 1) # 93% Fennica docs have just 1 language
+  # Combine data frames for specified languages
+  dflsub <- filter(df, df[[lan]])
+  dflsub$language <- gsub("language.", "", lan)
+  dfl <- bind_rows(dfl, dflsub)
+}
+dfl$language <- factor(dfl$language, levels = langs)
+
+# -------------------------------------------
+
+df <- dfl %>% group_by(publication_decade, language) %>%
+             summarise(n = n(),
+	               paper = sum(paper.consumption.km2, na.rm = TRUE))
+
+# TITLE COUNT
+theme_set(theme_bw(20))
+p <- ggplot(df, aes(x = publication_decade, y = n, group = language)) +
+       geom_point(aes(col = language, shape = language), size = 5) +
+       geom_line(aes(col = language, shape = language)) +       
+       xlab("Publication year") +
+       ylab("Title count (n)") +
+       ggtitle(paste("Languages (", catalogue, ")", sep = ""))
+#print(p)
+
+# PAPER CONSUMPTION
+p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
+       geom_point(aes(col = language, shape = language), size = 5) +
+       geom_line(aes(col = language, shape = language)) +       
+       xlab("Publication year") +
+       ylab("Paper consumption") +
+       ggtitle(paste("Languages (", catalogue, ")", sep = ""))
+print(p)
+```
+
+---
+
+### BOOK IN FINLAND 4
+
+Edellisten yhdistäminen.
+Samat analyysit, mutta asiasanoina kaikki aiemmista kohdista yhdistettynä: virret;arkkiveisut;hartauskirjat;katekismukset;rukouspäivät;saarnat;aapiset;rukoukset;rukous;hengelliset laulut;hartauspuheet;virsikirjat;hautajaiset;häät;juhlamenot
+
+Hartauskirjallisuudesta ks. Osmo Tiililä, Rukoilevaisten kirjoja, 1961.
+
+General analysis with all documents combined:
+
+```{r topics3, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, out.width="430px", fig.show="hold"}
+# https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/topics3-2.png
+
+sel <- c("virret","arkkiveisut","hartauskirjat","katekismukset","rukouspäivät","saarnat","aapiset","rukoukset","rukous","hengelliset laulut","hartauspuheet","virsikirjat","hautajaiset","häät","juhlamenot")
+catalogue <- "Fennica"
+  if (catalogue == "Fennica") {
+    df <- df.full # full time span
+  } else if (catalogue == "Kungliga") {
+    df <- df0 # selected time span
+  }
+  df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)
+
+# Selected catalogue with selected topics
+df <- df %>% filter(catalog == catalogue & hit)
+
+langs <- c("Finnish", "Swedish", "Latin", "German", "Russian", "French", "Other")
+lang <- paste("language.", langs, sep = "")
+otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
+df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
+dfl <- NULL
+for (lan in lang) {
+  # Classify a document to the specifed language
+  # If document is assigned with languages, each case is considered
+  # so one doc may have multiple entries corresponding to different languages
+  # mean(rowSums(df[, lang]) == 1) # 93% Fennica docs have just 1 language
+  # Combine data frames for specified languages
+  dflsub <- filter(df, df[[lan]])
+  dflsub$language <- gsub("language.", "", lan)
+  dfl <- bind_rows(dfl, dflsub)
+}
+dfl$language <- factor(dfl$language, levels = langs)
+
+# -------------------------------------------
+
+df <- dfl %>% group_by(publication_decade, language) %>%
+             summarise(n = n(),
+	               paper = sum(paper.consumption.km2, na.rm = TRUE))
+
+# TITLE COUNT
+theme_set(theme_bw(20))
+p <- ggplot(df, aes(x = publication_decade, y = n, group = language)) +
+       geom_point(aes(col = language, shape = language), size = 5) +
+       geom_line(aes(col = language, shape = language)) +       
+       xlab("Publication year") +
+       ylab("Title count (n)") +
+       ggtitle(paste("Languages (", catalogue, ")", sep = ""))
+#print(p)
+
+# PAPER CONSUMPTION
+p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
+       geom_point(aes(col = language, shape = language), size = 5) +
+       geom_line(aes(col = language, shape = language)) +       
+       xlab("Publication year") +
+       ylab("Paper consumption") +
+       ggtitle(paste("Languages (", catalogue, ")", sep = ""))
+print(p)
+```
+
+---
+
+# University teaching
+
+### topics 1
+
+Kirkkohistoria;raamatunhistoria;eksegetiikka;homiletiikka;dogmatiikka;teologia
+
+```{r topics-101, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6}
+sel =  c("kirkkohistoria","raamatunhistoria","eksegetiikka","homiletiikka","dogmatiikka","teologia")
+langs <- c("Finnish", "Swedish", "Latin", "German", "Russian", "French", "Other")
+catalogue <- "Fennica"
+
+#https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/topics44-2.png
+#https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/topics44-4.png
+#https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/topics44-6.png
+#https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/topics44-8.png
+#https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/topics44-14.png
+
+df <- df0 %>% filter(catalog == catalogue)
+lang <- paste("language.", langs, sep = "")
+otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
+df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
+dfl <- NULL
+for (lan in lang) {
+  dflsub <- filter(df, df[[lan]])
+  if (nrow(dflsub) > 0) {
+    dflsub$language <- gsub("language.", "", lan)
+    dfl <- bind_rows(dfl, dflsub)
+  }
+}
+dfl$language <- factor(dfl$language, levels = names(table(dfl$language)))
+# Selected catalogue with selected topics
+df = dfl
+df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)  
+df <- df %>% filter(hit)
+df <- dfl %>% group_by(publication_decade, language) %>%
+             summarise(n = n(),
+	               paper = sum(paper.consumption.km2, na.rm = TRUE))
+
+# PAPER CONSUMPTION
+theme_set(theme_bw(20))
+p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
+       geom_point(aes(col = language, shape = language), size = 5) +
+       geom_line(aes(col = language, shape = language)) +       
+       xlab("Publication year") +
+       ylab("Paper consumption") +
+       ggtitle(paste("Paper (", print(paste(sel, collapse = ";")), ")", sep = ""))
+print(p)
+
+```
+
+---
+
+### topics 2
+
+"oppihistoria","antiikki","historia"
+
+```{r topics-102, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6}
+sel = c("oppihistoria","antiikki","historia")
+# Selected catalogue with selected topics
+df = dfl
+df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)  
+df <- df %>% filter(hit)
+df <- dfl %>% group_by(publication_decade, language) %>%
+             summarise(n = n(),
+	               paper = sum(paper.consumption.km2, na.rm = TRUE))
+
+# PAPER CONSUMPTION
+theme_set(theme_bw(20))
+p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
+       geom_point(aes(col = language, shape = language), size = 5) +
+       geom_line(aes(col = language, shape = language)) +       
+       xlab("Publication year") +
+       ylab("Paper consumption") +
+       ggtitle(paste("Paper (", print(paste(sel, collapse = ";")), ")", sep = ""))
+print(p)
+
+```
+
+---
+
+### topics 3
+
+"filosofia","luonnonfilosofia","metafysiikka","logiikka"
+
+```{r topics-103, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6}
+sel = c("filosofia","luonnonfilosofia","metafysiikka","logiikka")
+# Selected catalogue with selected topics
+df = dfl
+df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)  
+df <- df %>% filter(hit)
+df <- dfl %>% group_by(publication_decade, language) %>%
+             summarise(n = n(),
+	               paper = sum(paper.consumption.km2, na.rm = TRUE))
+
+# PAPER CONSUMPTION
+theme_set(theme_bw(20))
+p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
+       geom_point(aes(col = language, shape = language), size = 5) +
+       geom_line(aes(col = language, shape = language)) +       
+       xlab("Publication year") +
+       ylab("Paper consumption") +
+       ggtitle(paste("Paper (", print(paste(sel, collapse = ";")), ")", sep = ""))
+print(p)
+
+```
+
+---
+
+### topics 4
+
+"luonnontieteet","matematiikka","fysiikka","kemia","tähtitiede","maantiede","geodesia","geofysiikka","meteorologia"
+
+```{r topics-104, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6}
+sel = c("luonnontieteet","matematiikka","fysiikka","kemia","tähtitiede","maantiede","geodesia","geofysiikka","meteorologia")
+# Selected catalogue with selected topics
+df = dfl
+df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)  
+df <- df %>% filter(hit)
+df <- dfl %>% group_by(publication_decade, language) %>%
+             summarise(n = n(),
+	               paper = sum(paper.consumption.km2, na.rm = TRUE))
+
+# PAPER CONSUMPTION
+theme_set(theme_bw(20))
+p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
+       geom_point(aes(col = language, shape = language), size = 5) +
+       geom_line(aes(col = language, shape = language)) +       
+       xlab("Publication year") +
+       ylab("Paper consumption") +
+       ggtitle(paste("Paper (", print(paste(sel, collapse = ";")), ")", sep = ""))
+print(p)
+
+```
+
+---
+
+### topics 5
+
+"psykologia","yhteiskuntafilosofia","valtiofilosofia","talous","raha","moraali","velvollisuudet","kasvatus","maanviljely","maatalous","kalastus"
+
+```{r topics-105, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6}
+sel =   c("psykologia","yhteiskuntafilosofia","valtiofilosofia","talous","raha","moraali","velvollisuudet","kasvatus","maanviljely","maatalous","kalastus")
+
+# Selected catalogue with selected topics
+df = dfl
+df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)  
+df <- df %>% filter(hit)
+df <- dfl %>% group_by(publication_decade, language) %>%
+             summarise(n = n(),
+	               paper = sum(paper.consumption.km2, na.rm = TRUE))
+
+# PAPER CONSUMPTION
+theme_set(theme_bw(20))
+p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
+       geom_point(aes(col = language, shape = language), size = 5) +
+       geom_line(aes(col = language, shape = language)) +       
+       xlab("Publication year") +
+       ylab("Paper consumption") +
+       ggtitle(paste("Paper (", print(paste(sel, collapse = ";")), ")", sep = ""))
+print(p)
+
+```
+
+---
+
+# Enlightenment and reading
+
+Paper consumption for different document formats over time. Each point represents a decade. Loess smoothing.
+
+```{r LIBER-13, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=10, fig.height=8, fig.show="hold", out.width="430px"}
+#https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/LIBER-13-2.png
+for (catal in unique(df0$catalog)) {
+  df2 <- subset(df0, catalog == catal) %>% group_by(publication_decade, gatherings) %>% summarize(paper.consumption.km2 = sum(paper.consumption.km2, na.rm = TRUE), n = n()) 
+  df2 <- filter(df2, gatherings %in% setdiff(names(which(table(df2$gatherings) >= 15)), "NA"))
+  p <- ggplot(df2, aes(y = paper.consumption.km2, x = publication_decade, shape = gatherings, linetype = gatherings))
+  p <- p + geom_point(size = 4)
+  p <- p + geom_smooth(method = "loess", size = 1, color = "black")
+  p <- p + ggtitle("Paper consumption in time by gatherings")
+  p <- p + xlab("Year")
+  p <- p + ylab("Paper consumption (km2)")
+  p <- p + guides(linetype = guide_legend(keywidth = 5), shape = guide_legend(keywidth = 5))
+  p <- p + ggtitle(paste("Paper consumption\n(", catal, ")", sep = ""))
+  print(p)
+}
+```
+
+---
+
+## Turku
+
+Paper consumption (Kungliga) näyttäisi kertovan Valistuksen voittokulusta Euroopassa.
+
+Octavo kokoisten kirjojen paper consumption on merkki kirjojen merkityksen korostumisesta ja muutoksesta.
+Sama päti ESTCn.
+Suomi taas tulee tässä orastavasti perässä kirjatuotannon puolesta.
+Mitä me halutaan sanoa tästä suomalaisen sivistysvaltion myöhemmästä kehityksestä?
+
+```{r 201606krakow-turkuvsother, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=7, fig.width=10, fig.show="hold", out.width="430px"}
+# https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/201606krakow-turkuvsother-2.png
+
+df <- fen %>% 
+      filter(!is.na(country)) %>%
+      filter(!is.na(publication_place) & !is.na(paper.consumption.km2) & paper.consumption.km2 > -0.01)
+
+# Add indicator field: Turku or Not Turku
+myplace <- "Turku"
+
+df$myplace <- rep(NA, nrow(df))
+df$myplace[df$publication_place == myplace] <- myplace
+df$myplace[!df$publication_place == myplace & df$country == "Finland"] <- "Finland"
+df$myplace[!df$country == "Finland" & !df$publication_place == myplace] <- "Foreign"
+df$myplace <- factor(df$myplace, levels = rev(c("Foreign", "Finland", "Turku")))
+
+# Keep entries with known publication place and paper consumption
+# Group by year/decade and Turku/Other
+dfs <- df %>% group_by(publication_decade, myplace) %>%
+  summarise(titles = n(), paper = sum(paper.consumption.km2, na.rm = TRUE))
+
+p <- ggplot(dfs, aes(x = publication_decade, y = paper, fill = myplace, order = -as.numeric(myplace))) +
+     geom_bar(position = "stack", stat = "identity", color = "black") +
+     ggtitle("Paper consumption") +
+     scale_fill_grey() +
+     guides(fill = guide_legend(reverse = TRUE, title = "")) + 
+     xlab("Publication decade") + ylab("Paper (km2)")
+#print(p)
+
+p <- ggplot(dfs, aes(x = publication_decade, y = titles, fill = myplace, order = -as.numeric(myplace))) +
+     geom_bar(position = "stack", stat = "identity", color = "black") +
+     ggtitle("Title count") +
+     # scale_fill_manual(values = c("blue", "black", "darkgreen")) +
+     scale_fill_grey() +
+     guides(fill = guide_legend(reverse = TRUE, title = "")) +      
+     xlab("Publication decade") + ylab("Title count (n)")
+print(p)
+```
+
+---

### 2016-07-05 inst/examples/manuscript-krakow.Rmd
ok

@@
 
-langs <- c("Finnish", "Swedish", "Latin", "German", "Other")
 lang <- paste("language.", langs, sep = "")
@@
 
-langs <- c("Finnish", "Swedish", "Latin", "German", "Russian", "French", "Other")
 lang <- paste("language.", langs, sep = "")
@@
   df <- df %>% filter(catalog == catalogue & hit)
-
-  langs <- c("Finnish", "Swedish", "Latin", "German", "Other")
   lang <- paste("language.", langs, sep = "")

### 2016-07-05 inst/examples/20160715-slides-Krakow.Rmd
ok

@@
 knitr::opts_chunk$set(fig.path = "slides_201606_Krakow/", dev="CairoPNG")
+
+# Set locale
+Sys.setlocale(locale="UTF-8")
 
@@
 
-```{r publishingovertime, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10}
+```{r publishingovertime, echo=FALSE, message=FALSE, warning=FALSE, fig.width=6, fig.height=6}
+library(devtools)
+install_github("ropengov/gisfin")
+
 # https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/publishingovertime-1.png
@@
      geom_point(aes(shape = catalog), size = 3) +     
-     ylab("Title count (n)") + xlab("Publication year") +  
-     ggtitle("Overall publishing activity")
+     ylab("Title count (n)") + xlab("Publication year") #+  
+     # ggtitle("Overall publishing activity")
 print(p)
@@
 
-Comparison of printing activity in
-
 - Turku
@@
 
-```{r publishingactivitycomparisons, echo=FALSE, message=FALSE, cache=FALSE, fig.width=8, fig.height=6, fig.show="hold", out.width="430px"}
+```{r publishingactivitycomparisons, echo=FALSE, message=FALSE, cache=FALSE, fig.width=6, fig.height=5, fig.show="hold", out.width="150px"}
 #https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/publishingactivitycomparisons-2.png
@@
 
-## Publishers Finland
-
-Number of unique publishers in top publication places over time (Fennica)
+## Unique publishers in top publication places over time
 
@@
 
-## Publishers Kungliga
-
 ```{r publishers2-kungliga, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=7, fig.width=15}
@@
 
-```{r publishers3-finland, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=7, fig.width=15, fig.show="hold"}
+```{r publishers3-finland-fennica, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=7, fig.width=13, out.width="150px", fig.show="hold"}
 # https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/publishers3-finland-1.png
 
-for (catalogue in c("Fennica", "Kungliga")) {
+place <- "Turku"
+catalogue = "Fennica"
+df = df0
 
+df <- df %>%
+        filter(catalog == catalogue & publication_place == place)
+
+df <- df %>%	
+        select(publication_decade, publisher, paper.consumption.km2)
+
+# Group small publishers
+# Top publishers by title count
+ntop <- 10
+top <- names(top(df, "publisher", ntop))
+df$publisher[!df$publisher %in% top] <- "Other"
+df$publisher <- factor(df$publisher, c(top, "Other"))
+
+# Title count per decade & publisher	
+npub <- df %>% group_by(publication_decade, publisher) %>% tally()
+
+# TITLE COUNT
+theme_set(theme_bw(20))
+p <- ggplot(npub, aes(x = publication_decade, y = n)) +
+       geom_bar(stat = "identity", position = "stack", aes(fill = publisher)) + 
+       xlab("Publication year") +
+       ylab("Title count (n)") +        
+       ggtitle(paste("Title count per publisher (", place, "/", catalogue, ")", sep = ""))
+print(p)
+
+```
+
+---
+
+## Title count per top publisher
+
+```{r publishers3-finland-kungliga, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=7, fig.width=13, out.width="150px", fig.show="hold"}
+# https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/publishers3-finland-1.png
+catalogue = "Kungliga"
 place <- "Turku"
@@
 print(p)
-
-}
 ```
@@
 
-```{r publisherpapertitle, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, out.width="430px", fig.show="hold"}
+```{r publisherpapertitle, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5, out.width="150px", fig.show="hold"}
 
@@
   # Selected ones
+  df$publisher[df$publisher == ""] = "Other"
   top <- names(top(df, "publisher", 5))
-df$publisher[!df$publisher %in% top] <- "Other"
+  df$publisher[!df$publisher %in% c(top, "")] <- "Other"
   df$publisher <- factor(df$publisher, levels = c(top, "Other"))
@@
 
-## Riksdagar 2
+## Gävle in Riksdagar
 
-Focus on Gävle (gray) during riksdagar. Gävle has `r sum("Gävle" %in% fen$publication_place)` occurrences in Fennica, hence not included here. The figure on Gävle is based on Kungliga.
+Gävle (gray) during riksdagar (Kungliga)
 
-```{r riksdar2, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=7, out.width="430px"}
+```{r riksdar2, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
 # https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/riksdar2-1.png
@@
 
-## Book printing in Finland / Language
+## Book printing in Finland / Fennica
 
-```{r language1, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, out.width="430px", fig.show="hold"}
+```{r language1, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=6, out.width="150px", fig.show="hold"}
 # https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/language1-1.png
-# https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/language1-2.png
-
-for (catalogue in c("Fennica", "Kungliga")) {
-
+catalogue = "Fennica"
 df <- df0
-  df <- df %>% filter(catalog == catalogue)
-
 langs <- c("Finnish", "Swedish", "Latin", "German", "Russian", "French", "Other")
@@
 }
-dfl$language <- factor(dfl$language, levels = langs)
 
+# ----------------------------------
+
+df <- dfl %>% filter(catalog == catalogue)
+df <- df %>% group_by(publication_decade, language) %>%
+             summarise(n = n(),
+	               paper = sum(paper.consumption.km2, na.rm = TRUE))
+
+# TITLE COUNT
+p <- ggplot(df, aes(x = publication_decade, y = n, group = language)) +
+       geom_point(aes(col = language, shape = language), size = 5) +
+       geom_line(aes(col = language, shape = language)) +       
+       xlab("Publication year") +
+       ylab("Title count (n)") +
+       ggtitle(paste("Languages (", catalogue, ")", sep = ""))
+print(p)
+
+# PAPER CONSUMPTION
+p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
+       geom_point(aes(col = language, shape = language), size = 5) +
+       geom_line(aes(col = language, shape = language)) +       
+       xlab("Publication year") +
+       ylab("Paper consumption") +
+       ggtitle(paste("Languages (", catalogue, ")", sep = ""))
+print(p)
+```
+
+---
+
+## Book printing in Finland / Kungliga
+
+```{r language1-kungliga, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=6, out.width="150px", fig.show="hold"}
+catalogue = "Kungliga"
+  df <- dfl %>% filter(catalog == catalogue)
   df <- dfl %>% group_by(publication_decade, language) %>%
@@
 
-```{r language-perc, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, out.width="430px", fig.show="hold"}
+```{r language-perc, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=6, out.width="150px", fig.show="hold"}
 for (catalogue in c("Fennica", "Kungliga")) {
@@
 }
-dfl$language <- factor(dfl$language, levels = langs)
 
@@
 
-```{r topics, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, out.width="430px", fig.show="hold"}
+```{r topics, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, fig.show="hold"}
 # https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/topics-2.png
@@
   }
-  dfl$language <- factor(dfl$language, levels = langs)
   df <- dfl %>% group_by(publication_decade, language) %>%
@@
 
-Sama kuin edellä, mutta asiasanat tässä: hautajaiset;häät;juhlamenot.
+hautajaiset;häät;juhlamenot.
 
-```{r topics2, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, out.width="430px", fig.show="hold"}
+```{r topics2, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6}
 # https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/topics2-2.png
@@
 
-Hartauskirjallisuudesta ks. Osmo Tiililä, Rukoilevaisten kirjoja, 1961.
-
-General analysis with all documents combined:
-
-```{r topics3, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, out.width="430px", fig.show="hold"}
+```{r topics3, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6}
 # https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/topics3-2.png
@@
 
-#https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/topics44-2.png
-#https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/topics44-4.png
-#https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/topics44-6.png
-#https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/topics44-8.png
-#https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/topics44-14.png
-
 df <- df0 %>% filter(catalog == catalogue)
@@
 }
-dfl$language <- factor(dfl$language, levels = names(table(dfl$language)))
 # Selected catalogue with selected topics
@@
 df <- df %>% filter(hit)
-df <- dfl %>% group_by(publication_decade, language) %>%
+df <- df %>% group_by(publication_decade, language) %>%
              summarise(n = n(),
@@
 
-```{r LIBER-13, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=10, fig.height=8, fig.show="hold", out.width="430px"}
+```{r LIBER-13, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=10, fig.height=8, fig.show="hold", out.width="150px"}
 #https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/LIBER-13-2.png
@@
 
-```{r 201606krakow-turkuvsother, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=7, fig.width=10, fig.show="hold", out.width="430px"}
+```{r 201606krakow-turkuvsother, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=5, fig.width=10}
 # https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/201606krakow-turkuvsother-2.png
@@
 ---
+
+## Thanks !
+
+- Academy of Finland
+- University of Helsinki

### 2016-07-05 inst/examples/manuscript-krakow.Rmd
ok

@@
 
-```{r 201606krakow-init, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE}
+```{r 201606krakow-init, echo=FALSE, message=FALSE, warning=FALSE}
 library(stringr)
@@
 df0$catalog = factor(c(rep("Fennica", nrow(fen)), rep("Kungliga", nrow(kun))))
+
+langs <- c("Finnish", "Swedish", "Latin", "German", "Russian", "French", "Other")
 ```
@@
 p <- ggplot(df2, aes(x = publication_decade, y = n)) +
-     #geom_bar(stat = "identity") + #scale_y_log10() +
      geom_line(aes(linetype = catalog)) +
      geom_point(aes(shape = catalog), size = 3) +     
-     #ylab("Paper consumption (km2)")
      ylab("Title count (n)") + xlab("Publication year") +  
@@
                summarise(n = n()) %>%
-               #summarise(paper = sum(paper.consumption.km2, na.rm = TRUE), n = n()) %>%	       
 	       filter(publication_place %in% selected.places) # %>%
-	       #filter(publication_decade >= 1600)
 df2$catalog = factor(df2$catalog, levels = rev(c("Fennica", "Kungliga")))
@@
      geom_point(aes(shape = publication_place), size = 3) +
-     #scale_y_log10() +
-     #facet_wrap(catalog ~ .) + 
      ylab("Title count (n)") + xlab("Publication year") +  
@@
   dfsel = subset(df0, catalog == catal)
-  #dfsel = subset(df0, publication_place == "Stockholm")
-  #dfsel = subset(df0, publication_place == "Norrköping")
-  #dfsel = subset(df0, publication_place == "Gävle")
 
@@
        geom_point(size = 2) +
-       #geom_line() +
        geom_smooth(col = "black") +              
@@
   }
-  dfl$language <- factor(dfl$language, levels = langs)
-
-  # -------------------------------------------
 
@@
   p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
-       #geom_bar(stat = "identity", position = "dodge", aes(fill = publisher)) + 
-       geom_point(aes(col = language, shape = language), size = 5) +
-       geom_line(aes(col = language, shape = language)) +       
-       # geom_smooth(aes(col = language)) + 
+       geom_point(aes(col = language, shape = language), size = 5) +
+       geom_line(aes(col = language, shape = language)) +       
        xlab("Publication year") +
        ylab("Paper consumption") +
-       # ylim(c(0, 1.1*max(npub$paper.per.title))) +
        ggtitle(paste("Languages (", catalogue, ")", sep = "")) 
@@
 
-  df$language <- factor(df$language, levels = names(table(df$language)))
+  # TITLE COUNT
+  theme_set(theme_bw(20))
+  p <- ggplot(df, aes(x = publication_decade, y = n, group = language)) +
+       geom_point(aes(col = language, shape = language), size = 5) +
+       geom_line(aes(col = language, shape = language)) +       
+       xlab("Publication year") +
+       ylab("Title count (n)") +
+       ggtitle(paste("Languages (", place, "/", catalogue, ")", sep = ""))
+  print(p)
+
+  # PAPER CONSUMPTION
+  theme_set(theme_bw(20))
+  p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
+       geom_point(aes(col = language, shape = language), size = 5) +
+       geom_line(aes(col = language, shape = language)) +       
+       xlab("Publication year") +
+       ylab("Paper consumption") +
+       ggtitle(paste("Languages (", place, "/", catalogue, ")", sep = ""))
+  print(p)
+
+}
+```
+
+Same with top publishers
+
+```{r topics.per.publisher, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, out.width="430px", fig.show="hold"}
+tops <-  names(top(fen, "publisher", 5))
+
+for (publ in tops) {
+
+  df <- dfl %>% filter(publisher == publ)
+
+  df <- df %>% group_by(publication_decade, language) %>%
+             summarise(n = n(), paper = sum(paper.consumption.km2, na.rm = TRUE))
 
@@
        ylab("Title count (n)") +
-       ggtitle(paste("Languages (", place, "/", catalogue, ")", sep = ""))
-  print(p)
-
-  # PAPER CONSUMPTION
-  theme_set(theme_bw(20))
-  p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
-       geom_point(aes(col = language, shape = language), size = 5) +
-       geom_line(aes(col = language, shape = language)) +       
-       xlab("Publication year") +
-       ylab("Paper consumption") +
-       ggtitle(paste("Languages (", place, "/", catalogue, ")", sep = ""))
-  print(p)
-
-}
-```
-
-Same with top publishers
-
-```{r topics.per.publisher, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, out.width="430px", fig.show="hold"}
-tops <-  names(top(fen, "publisher", 5))
-
-for (publ in tops) {
-
-  df <- dfl %>% filter(publisher == publ)
-
-  df <- df %>% group_by(publication_decade, language) %>%
-             summarise(n = n(), paper = sum(paper.consumption.km2, na.rm = TRUE))
-
-  df$language <- factor(df$language, levels = names(table(df$language)))
-
-# TITLE COUNT
-theme_set(theme_bw(20))
-p <- ggplot(df, aes(x = publication_decade, y = n, group = language)) +
-       #geom_bar(stat = "identity", position = "dodge", aes(fill = publisher)) + 
-       geom_point(aes(col = language, shape = language), size = 5) +
-       geom_line(aes(col = language, shape = language)) +       
-       xlab("Publication year") +
-       ylab("Title count (n)") +
        ggtitle(paste("Languages (", publ, "/", catalogue, ")", sep = ""))
@@
 sel <- c("hautajaiset", "häät", "juhlamenot")
-
 catalogue <- "Fennica"
-  if (catalogue == "Fennica") {
 df <- df.full # full time span
-  } else if (catalogue == "Kungliga") {
-    df <- df0 # selected time span
-  }
 df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)  
-
 # Selected catalogue with selected topics
 df <- df %>% filter(catalog == catalogue & hit)
-
 lang <- paste("language.", langs, sep = "")
@@
 }
-dfl$language <- factor(dfl$language, levels = langs)
-
-# -------------------------------------------
-
 df <- dfl %>% group_by(publication_decade, language) %>%
@@
 
-langs <- c("Finnish", "Swedish", "Latin", "German", "Russian", "French", "Other")
 df$language[!df$language %in% langs] <- "Other"

### 2016-07-05 inst/examples/20160715-slides-Krakow.Rmd
ok

@@
 knitr::opts_chunk$set(echo = FALSE)
-knitr::opts_chunk$set(fig.path = "slides_201606_Krakow/", dev="CairoPNG")
+#knitr::opts_chunk$set(fig.path = "slides_201606_Krakow/", dev="CairoPNG")
+knitr::opts_chunk$set(fig.path = "slides_201606_Krakow/")
 
@@
 #https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/publishingactivitycomparisons-2.png
+
 selected.places = c("Turku", "Uppsala", "Lund", "Stockholm")
@@
                summarise(n = n()) %>%
-	       filter(publication_place %in% selected.places) # %>%
+	       filter(publication_place %in% selected.places) 
 df2$catalog = factor(df2$catalog, levels = rev(c("Fennica", "Kungliga")))

### 2016-07-05 inst/examples/20160715-slides-Krakow.Rmd
ok

@@
 #https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/publishingactivitycomparisons-2.png
-
 selected.places = c("Turku", "Uppsala", "Lund", "Stockholm")
@@
 df2$publication_place = droplevels(factor(df2$publication_place))
-df3 = spread(df2, publication_decade, n, fill = 0)
+df3 = as.data.frame(spread(df2, publication_decade, n, fill = 0))
 df2 = melt(df3)
@@
 for (catal in unique(df2$catalog)) {
-
   p <- ggplot(subset(df2, catalog == catal), aes(x = publication_decade, y = n)) +
@@
 ntop <- 10
+library(bibliographica)
 top <- names(top(df, "publication_place", ntop))

### 2016-07-05 inst/examples/manuscript-krakow.Rmd
ok

@@
   dflsub <- filter(df, df[[lan]])
+  if (nrow(dflsub)) {
     dflsub$language <- gsub("language.", "", lan)
     dfl <- bind_rows(dfl, dflsub)
+  }
 }
@@
 ```{r kungliga_subjecttopics, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}
-df <- filter(df0, catalog == "Kungliga") %>%
+catalogue = "Kungliga"
+
+df <- filter(df0, catalog == catalogue) %>%
       filter(publication_year <= 1828)
@@
 entries = unlist(strsplit(as.character(df[[field]]), ";"), use.names = FALSE)
-s <- write_xtable(entries, file = paste(output.folder, catalog, "_subjecttopics", min(df$publication_year), "_", max(df$publication_year), ".csv", sep = ""))
-
-df <- filter(df0, catalog == "Kungliga" & publication_place == "Uppsala") %>%
+s <- write_xtable(entries, file = paste(output.folder, catalogue, "_subjecttopics", min(df$publication_year), "_", max(df$publication_year), ".csv", sep = ""))
+
+df <- filter(df0, catalog == catalogue & publication_place == "Uppsala") %>%
       filter(publication_year <= 1828)

### 2016-07-05 inst/examples/manuscript-krakow.Rmd
ok

@@
 entries = unlist(strsplit(as.character(df[[field]]), ";"), use.names = FALSE)
-s <- write_xtable(entries, file = paste(output.folder, catalog, "_Uppsala_subjecttopics", min(df$publication_year), "_", max(df$publication_year), ".csv", sep = ""))
+s <- write_xtable(entries, file = paste(output.folder, catalogue, "_Uppsala_subjecttopics", min(df$publication_year), "_", max(df$publication_year), ".csv", sep = ""))
 ```

### 2016-07-05 inst/examples/20160715-slides-Krakow.Rmd

--- 2016-07-05 inst/examples/20160715-slides-Krakow.Rmd
@@
 
-```{r publishingovertime, echo=FALSE, message=FALSE, warning=FALSE, fig.width=6, fig.height=6}
+```{r publishingovertime, echo=FALSE, message=FALSE, warning=FALSE, fig.width=6, fig.height=5}
 library(devtools)
@@
   p <- p + geom_point(data = dfm, aes(x = date, y = Documents), col = "black")
-  p <- p + scale_x_continuous(breaks = seq(minyear, maxyear, 20))
+  #p <- p + scale_x_continuous(breaks = seq(minyear, maxyear, 20))
   p <- p + ggtitle("Publishing activity")

### 2016-07-05 inst/examples/20160715-slides-Krakow.Rmd
ok

@@
 
-```{r publishers3-finland-fennica, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=7, fig.width=13, out.width="150px", fig.show="hold"}
+```{r publishers3-finland-fennica, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=7, fig.width=13}
 # https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/publishers3-finland-1.png
@@
 
-```{r publishers3-finland-kungliga, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=7, fig.width=13, out.width="150px", fig.show="hold"}
+```{r publishers3-finland-kungliga, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=7, fig.width=13}
 # https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/publishers3-finland-1.png

### 2016-07-05 inst/examples/20160715-slides-Krakow.Rmd
s

--- 2016-07-05 inst/examples/20160715-slides-Krakow.Rmd
@@
 ```
+---
+
+## From particular data to global perspective?
+
+Idea: to study early modern knowledge production in general.
+
+How? By combining library catalogue data (Fennica, Kungliga, ESTC, CERL)
+
+What is important: to clean up the data (90% of the work) and understand how particular data collections have been formed.
+
+Fail: take worldcat or similar combination of datasets and analyse it without cleaning it first.
+
+---
+
+## Data and method
+
+Data:
+
+- Fennica (Finnish National Bibliography), n-number of documents
+
+- Kungliga (Royal Swedish Library's metadata), n-number of documents
+
+Method:
+
+- Scalable code in library catalogue data ecosystem (github)
+
+- xxx
+
+---
+
+## Argument and findings
+
+- Finnish knowledge production 1640-1828 can only be understood in Swedish context.
+
+- Academy of Turku as part of the Swedish University system is the centre in Finland.
+
+Developments that start after "the rock bottom" of 1700-1721
+
+1) Changes in University curriculum reflected in published theses
+
+2) Religious publishing in Finnish language
+
+3) Economy (and related subject fields) published in Finnish
+
+4) Enlightenment in Sweden reflected in octavo sized book publishing
+
+---
 
@@
 
+An example how historical events, namely parliamentary assemblies in the Swedish case, have an impact on local knowledge production.
+
 Gävle (gray) during riksdagar (Kungliga)
@@
   # Use timeinterval year intervals
-  myplace = "Gävle" # Norrköping / Stockholm
+  myplace = "Stockholm" # Norrköping / Stockholm
   minyear = 1700
@@
 
-Fennica, Hartaus- yms.
-kirjallisuuden kieli (suomi vai ruotsi) milloin alkaa yleistyä suomenkielinen ja miten tämän julkaiseminen suomeksi kasvaa?
-virret;arkkiveisut;hartauskirjat;katekismukset;rukouspäivät;saarnat;aapiset;rukoukset;rukous;hengelliset laulut;hartauspuheet;virsikirjat.
+Devotional literature (catechisms, hymns, prayer collections, etc.) is known to be the most important form of literature denoting the advancement of reading in Finland in nineteenth century.
+But when does it actually showup as a relevant category?
 
@@
 
-hautajaiset;häät;juhlamenot.
+Temporary sermons played a crucial role in early modern knowledge production, but it has not been clearly analysed in what language they were in Finland (and Sweden).
 
@@
 
-Edellisten yhdistäminen.
-Samat analyysit, mutta asiasanoina kaikki aiemmista kohdista yhdistettynä: virret;arkkiveisut;hartauskirjat;katekismukset;rukouspäivät;saarnat;aapiset;rukoukset;rukous;hengelliset laulut;hartauspuheet;virsikirjat;hautajaiset;häät;juhlamenot
+Combination of devotional literature and temporary sermons gives us the following graphs.
 
@@
 
-Kirkkohistoria;raamatunhistoria;eksegetiikka;homiletiikka;dogmatiikka;teologia
+Printing of theology related topics in different languages in Turku.
 
@@
 
-"oppihistoria","antiikki","historia"
+Printing of history and related topics in different languages in Turku.
 
@@
 
-"filosofia","luonnonfilosofia","metafysiikka","logiikka"
+Printing of philosophy in different languages in Turku.
 
@@
 
-"luonnontieteet","matematiikka","fysiikka","kemia","tähtitiede","maantiede","geodesia","geofysiikka","meteorologia"
+Printing of natural science in different languages in Turku.
 
@@
 
-"psykologia","yhteiskuntafilosofia","valtiofilosofia","talous","raha","moraali","velvollisuudet","kasvatus","maanviljely","maatalous","kalastus"
+Printing of economy and related topics in different languages in Turku.
 
@@
 
+Rise of the octavo sized book as vehicle of Enlightenment (and proof of reading).
+
 Paper consumption for different document formats over time. Each point represents a decade. Loess smoothing.
@@
 
-Paper consumption (Kungliga) näyttäisi kertovan Valistuksen voittokulusta Euroopassa.
-
-Octavo kokoisten kirjojen paper consumption on merkki kirjojen merkityksen korostumisesta ja muutoksesta.
-Sama päti ESTCn.
-Suomi taas tulee tässä orastavasti perässä kirjatuotannon puolesta.
-Mitä me halutaan sanoa tästä suomalaisen sivistysvaltion myöhemmästä kehityksestä?
+Effects of Enlightenment: decline of metaphysics in favour of social and economic theory and the great victory of reading is visible in the rise and rise of octavo book.
 

### 2016-07-05 inst/examples/manuscript-krakow.Rmd
Täsmennetty Publisher_analysis TODO:ta
Added KUNGLIGAPUB-TODO 1-4; removed old ideas

@@
 
-### Other points if the time allows (I will skip all of these unless they are moved back to main text above)
-
-**KUNGLIGAPUB-TODO1** (mietitään onnistuuko yhden Kungligan asiasanalistauksen avulla, alkuperäinen idea kuitenkin tässä) Tavoitteena asiasana-analyysi paikkakuntakohtaisesti liittyen yliopistojulkaisemiseen samalla tavalla kuin jo tehty Fennicasta.
-Ensimmäinen toimenpide: asiasanalistat Kungligasta 1480-1828 paikkakuntakohtaisesti: Tukholma, Lund, Greifwald, Uppsala, Turku, Lund, Tartu.
-Tämän jälkeen Mikko ja Jani ryhmittelee nämä.
-KOKO KUNGLIGA LISTAUS vaikuttaa toistaiseksi siltä että on hyvin vähän asiasanoja jotka liittyvät yliopistoon.
-Näin ollen, voisiko generoida Uppsalasta oman asiasanalistauksen joka toimii evaluaatiokeissinä tuosta paikkakuntakohtaisesta listauksesta?**OK DONE see link above Kungliga subject topics Uppsala 1488-1828**
-
-**KUNGLIGAPUB-TODO2** Edellä tehdyistä asiasanalistoista tuotetaan samanlaiset asiasanaryppäät kuin BOOKINFINLAND-5.
+**KUNGLIGAPUB-TODO1**: Tavoitteena asiasana-analyysi paikkakuntakohtaisesti liittyen yliopistojulkaisemiseen samalla tavalla kuin jo tehty Fennicasta.
+Ensimmäinen toimenpide: asiasanalistat Kungligasta 1480-1828 paikkakuntakohtaisesti: Tukholma, Lund, Greifswald, Uppsala, Turku, Lund, Tartu.
+Eli eri asiasanojan määrä eri kaupungeissa eri aikoina Kungligan mukaan.
+(Siis Eli samanlainen kaavio kuin on kielistä ”Book printing in Finland” –osiossa).
+
+**KUNGLIGAPUB-TODO2**: Tuotetaan samanlaiset asiasanaryppäät kuin BOOKINFINLAND-5.
 Tämän jälkeen piirretään Kungligan pohjalta yliopisto-asiasanat aikajanalle samalla tavalla kuin Fennican kohdalla kaupunkikohtaisesti.
-**OK skippaan toistaiseksi - päivitä tai poista tämä kohta**
-
-TODO_Turku in Sweden 2: Kaaviot Fennicasta ja Kungligasta, jossa lasketaan eri kaupunkien mukaan asiasanojen määrä eri vuosina.
-Asiasanat ovat osin arbriträärisiä, mutta ehkä niiden määrän pohjalta voidaan sanoa jotain eri kaupunkien julkaisuprofiilien muutoksista.
-Laaditaan kaaviot Tukholmasta, Uppsalasta, Lundista, Greifswaldista ja Turusta vuoteen 1828.
-Fennican osalta tehdään myös kaavio Vaasasta, jotta nähdään kuinka Vaasan hovioikeuteen painottunut julkaiseminen erottuu Turun julkaisemisesta.
-
-TODO_Turku in Sweden 1 (jos ehditään ja on mahdollista): Kaaviot Fennicasta ja Kungligasta, jossa lasketaan eri kaupunkien nimikemäärien, paperinkulutuksen ja kustantajien suhteellinen osuus vuoteen 1828.
+Asiasanalista on seuraava.
+Käytin Fennican asiasanajaottelua pohjana, mutta Kungligan asiasanat ovat paljon modernimpaa kieltä ja yleensä seikkaperäisempiä.
+Jouduin siis soveltamaan aika paljon mikä tarkoittaa, että Fennican ja Kungligan vertailtavuus on heikko, mutta katalogin sisäisesti tilanne on hieman parempi.
+Osa kategorioista jäävät todella pieniksi (erityisesti toi retoriikka, poetiikka jne.
+En vain löytänyt niihin sopivia termejä).
+Tämä toki tiedettiin jo.
+1.	Kyrkohistoria; Biblisk arkeologi;Exegetik;Homiletik;Dogmatik;Teologi; Praktisk Teologi; Teologisk etik
+2.	Idé- och lärdomshistoria;Antiken;Historia;Militärhistoria;
+3.	Filosofi;Metafysik;Logik
+4.	Naturvetenskap;Matematik;Matematiska tabeller; Kemi;Astronomi;Geografi;Geologi;Meteorologi
+5.	Retorik
+6.	Hebreiska språket; Grekiska språket;Latin
+7.	Politisk filosofi;Ekonomiska förhållanden; Nationalekonomi;Lantbruksekonomi;Ekonomi;Penningväsen;Penningvärde;Kreditväsen;Penningförfalskning;Moral;Pedagogik;Uppfsotringsverket;Uppfostran;Barnuppfostran;Jordbruk;Jordbrukslära;Jordbrukspolitik;Fiske
+8.	Biologi;Medicinalverket;Medicin;Veterinärmedicin;Medicinalväsen;Medicinalväxkter;Sjukdomar;Djursjukdomar;Djur;Husdjur;Djurskydd;Hästar;Hästkreatur;Hästkörning;Hästavel
+9.	Kvinnor;Kvinnliga textilarbetare;Gravida kvinnor;Adelskvinnor;Kvinnorollen;Ensamstående kvinnor
+10.	Högmålsbrott;Skattebrott;Brott;Brottslingar;Äktenskapsbrott;Våldsbrott;Trafikbrott;Gäldenärsbrott;Sabbattsbrott;Sexualbrott;Fridsbrott;Ekonomisk brottslighet;Religionsbrott;Juridik;Straff;Dödsstraff;Kroppsstraff;Straffarbete;Straffarbete;Fängelsestraff
+
+Uppsalan asiasanoista en saanut mitään uutta irti. Mitä näille tehdään?
+
+**KUNGLIGAPUB-TODO 3**: Kaaviot Fennicasta ja Kungligasta, jossa lasketaan eri kaupunkien nimikemäärien, paperinkulutuksen ja kustantajien suhteellinen osuus vuoteen 1828.
 Eli samanlainen kaavio kuin on kielistä ”Book printing in Finland” –osiossa.
 Laaditaan kaaviot Tukholmasta, Uppsalasta, Lundista, Greifswaldista ja Turusta.
-Voiko myös tehdä erillisen kaavion, jossa Tukholma on poistettu, josta näkee näiden kilpailevien kakkoskaupunkien tilanteen.
-
-TODO_Turku in Sweden 3: Kun kerran ollaan maps and space sessiossa, ehkä kannattaisi tehdä myös kartta jossa, nämä eri kaupungit ja niiden nimikemäärät ovat kartalla.
-Kartat kannattaisi kai tehdä vuosille 1650, 1710, 1767 ja 1800.
+Voiko myös tehdä erillisen kaavion, jossa Tukholma on poistettu, josta näkee näiden kilpailevien kakkoskaupunkien tilanteen?
+
+**KUNGLIGAPUB-TODO 4** (jos ehtii ja pidetään järkevänä): Kun kerran ollaan maps and space sessiossa, ehkä kannattaisi tehdä myös kartta jossa, nämä eri kaupungit ja niiden nimikemäärät ovat kartalla, siis niin, että kullekin kaupungille tullee pallukka joka kooltaan vastaa julkaisujen määrää.
+Kartta kannattaisi tehdä vuosille 1650, ja 1800.
 Onko tämä mahdollista?
@@
 
-TODO_Publisher analysis_#: Kaaviot Fennicasta ja Kungligasta, jossa lasketaan eri julkaisijoiden.
+TODO_Publisher analysis_#: Kaaviot Fennicasta, jossa lasketaan eri julkaisijoiden julkaisujen asiasanamäärä, siis samalla tavalla kuin tuolla yllä on tehty kielien asiasanojen kanssa.
 Asiasanat ovat osin arbriträärisiä, mutta ehkä niiden määrän pohjalta voidaan sanoa jotain eri julkaisijoiden profiilien muutoksista.
-Laaditaan kaaviot 1828.
+Laaditaan kaaviot vuoteen 1828.
 

### 2016-07-05 inst/examples/manuscript-krakow.Rmd
Deleted unnecessary TODO requests

@@
 
+**KUNGLIGAPUB-TODO3**
+
+**KUNGLIGAPUB-TODO4**
+
 **AUTHOR-TODO1**
@@
 **AUTHOR-TODO2**
+
+**TODO_Publisher analysis_ JANI: Täsmennetty alle.**
 
@@
 
-**Lisäksi seuraavat TODOt kesken.
-Jani miettii miten tärkeitä nämä ovat nyt kun saatu lisää kuvia.
-Duplikaatti-kuvan toteuttaminen taas päätetään kun saadaan muut tehtyä.
-Jotain sillä kannattaa joka tapauksessa tehdä:**
+**Lisäksi seuraavat TODOt kesken. Duplikaatti-kuvan toteuttaminen taas päätetään kun saadaan muut tehtyä. Jotain sillä kannattaa joka tapauksessa tehdä:**
 
 **TODO: Hege's deduplication code for specific figures. Particular figures to be decided.**
-
-**TODO_Turku in Sweden 1 (JANI TSEKKAA VOIKO YKSINKERTAISTAA SUHTEESSA KUNGLIGAPUBiin**
-
-**TODO_Turku in Sweden 2**
-
-**TODO_Publisher analysis_ JANI: Täsmennä mitä ajattelit.**
-
-**TODO_Publishing in Finland JANI: täsmennä mitä ajattelit (ks. alla).**
 
@@
 Hitaammin voin tehda viela enemman jos alan itse tutkia aineistoa huolellisesti mutta sit jaa muut jutut eli skippaan for now.**
+
+JM: Tämän voi poistaa, myös kaavion. Yllä on sama juttu, mutta järkevämmin formuloitu. Pahoittelut sekvaasta muotoilusta ja turhan työn teettämisestä.
 

### 2016-07-06 inst/examples/20160715-slides-Krakow.Rmd
a
s

@@
 
+[Intro 1/3]
+
 ## From particular data to global perspective?
 
-Idea: to study early modern knowledge production in general.
+Idea: to study early modern knowledge production, all of it (1470-1830)
 
@@
 
-What is important: to clean up the data (90% of the work) and understand how particular data collections have been formed.
-
-Fail: take worldcat or similar combination of datasets and analyse it without cleaning it first.
-
----
-
-## Data and method
+What is important: to clean up the data (90% of the work) and to take into account how particular data collections (Finnish National Bibliography, English Short-Title Catalogue etc.) have been formed.
+
+How to fail: take worldcat or similar combination of datasets and analyse it as a whole without cleaning it first.
+
+---
+
+[Intro 2/3]
+
+### Data and method
 
@@
 
-- Kungliga (Royal Swedish Library's metadata), n-number of documents
+- Kungliga (National Library of Sweden's library catalogue), n-number of documents
 
@@
 
----
-
-## Argument and findings
+- Benefit no. 1: once the work has been done, the data is available for everyone to use and to enrich it. The ecosystem is constructed with even unforeseen changes in mind.
+
+---
+
+[Intro 3/3]
+
+### Argument and findings
 
@@
 
-- Academy of Turku as part of the Swedish University system is the centre in Finland.
-
-Developments that start after "the rock bottom" of 1700-1721
+- Academy of Turku as part of the Swedish University system is the centre of Finnish knowledge production.
+
+Enlightenment in Finland after "the rock bottom" of 1700-1721
 
@@
 
-3) Economy (and related subject fields) published in Finnish
-
-4) Enlightenment in Sweden reflected in octavo sized book publishing
-
----
-
-## Peaks and drops – role of publishers and contingency
+3) Economy and social science published in Swedish language
+
+--> Deep roots of the diversity of "Finnishness" clearly reflcted in knowledge production, 1640-1828.
+
+---
+
+[Big Picture 1/4]
+
+Kartta jossa näkyy Turku osana Ruotsin valtakuntaa tähän (Janilla ideoita manuskriptin puolella, mun mielestä ne on hyviä tästä).
+Voisi miettiä, että tämä kartta-slide korvaisi sitten tuon alla tulevan "Comparing publishing activity in Swedish University town".
+
+---
+
+[Big Picture 2/4]
+
+### Peaks and drops – role of publishers and contingency
 
@@
 
-## Comparing publishing activity
+[Big Picture 3/4]
+
+### Comparing publishing activity in Swedish University towns
 
@@
 
-## Unique publishers in top publication places over time
+[Big Picture 4/4]
+### Rise of the octavo sized book as vehicle of Enlightenment
+
+Paper consumption for different document formats over time.
+
+```{r LIBER-13, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=10, fig.height=8, fig.show="hold", out.width="150px"}
+#https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/LIBER-13-2.png
+for (catal in unique(df0$catalog)) {
+  df2 <- subset(df0, catalog == catal) %>% group_by(publication_decade, gatherings) %>% summarize(paper.consumption.km2 = sum(paper.consumption.km2, na.rm = TRUE), n = n()) 
+  df2 <- filter(df2, gatherings %in% setdiff(names(which(table(df2$gatherings) >= 15)), "NA"))
+  p <- ggplot(df2, aes(y = paper.consumption.km2, x = publication_decade, shape = gatherings, linetype = gatherings))
+  p <- p + geom_point(size = 4)
+  p <- p + geom_smooth(method = "loess", size = 1, color = "black")
+  p <- p + ggtitle("Paper consumption in time by gatherings")
+  p <- p + xlab("Year")
+  p <- p + ylab("Paper consumption (km2)")
+  p <- p + guides(linetype = guide_legend(keywidth = 5), shape = guide_legend(keywidth = 5))
+  p <- p + ggtitle(paste("Paper consumption\n(", catal, ")", sep = ""))
+  print(p)
+}
+```
+
+---
+
+### Publishers
+
+---
+
+[Publishers 1/6]
+
+Turku in Sweden -slide (Janin ideoima tulisi tähän)
+
+---
+
+[Publishers 2/6]
+
+### Development of number of publishers in Finland
 
@@
 
+[Publishers 3/6]
+
+### Development of number of publishers in Swedish University towns
+
 ```{r publishers2-kungliga, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=7, fig.width=15}
@@
 
-## Title count per top publisher
+[Publishers 4/6]
+
+### Numbers of publications of main publishers in Turku
 
@@
 
-## Title count per top publisher
-
-```{r publishers3-finland-kungliga, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=7, fig.width=13, out.width="150px", fig.show="hold"}
-# https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/publishers3-finland-1.png
-catalogue = "Kungliga"
-place <- "Turku"
-df = df0
-
-df <- df %>%
-        filter(catalog == catalogue & publication_place == place)
-
-df <- df %>%	
-        select(publication_decade, publisher, paper.consumption.km2)
-
-# Group small publishers
-# Top publishers by title count
-ntop <- 10
-top <- names(top(df, "publisher", ntop))
-df$publisher[!df$publisher %in% top] <- "Other"
-df$publisher <- factor(df$publisher, c(top, "Other"))
-
-# Title count per decade & publisher	
-npub <- df %>% group_by(publication_decade, publisher) %>% tally()
-
-# TITLE COUNT
-theme_set(theme_bw(20))
-p <- ggplot(npub, aes(x = publication_decade, y = n)) +
-       geom_bar(stat = "identity", position = "stack", aes(fill = publisher)) + 
-       xlab("Publication year") +
-       ylab("Title count (n)") +        
-       ggtitle(paste("Title count per publisher (", place, "/", catalogue, ")", sep = ""))
-print(p)
-```
-
----
-
-## Publisher paper vs. title count
-
-Paper per title count ratio per publisher. [nähdään voidaanko sanoa onko joku selkeästi asetusten julkaisija ja toisella myös kirjoja (tai asetuskokoelmia).]
+[Publishers 5/6]
+
+### Comparing how much paper different publishers used on average in their publications in Turku
 
@@
 
-## Drop 1700
-
-Publisher title count changes around 1700 drop in Turku, the most significant publishing place at the time:
+[Publishers 6/6]
+
+### Rock Bottom of the Great Northern War (1700-1721)
+
+Publisher title count changes around 1700 with a nearly detrimental drop in Turku, the most significant publishing place at the time.
 
@@
 
-## Gävle in Riksdagar
+[Swedish age of Freedom and abolishment of censorship 1/2]
+
+### Gävle in Riksdagar
 
@@
 
-Gävle (gray) during riksdagar (Kungliga)
+Gävle (gray) during riksdagar (Kungliga) TÄÄ EI TOIMI NYT OLLENKAAN KUN ON AIKA PIENI TOI NOUSU NÄKYVISSÄ TÄSSÄ. MENEEKÖ OIKEIN?
 
@@
 
-# Language
-
-## Book printing in Finland / Fennica
+[Swedish age of Freedom and abolishment of censorship 2/2]
+
+Tämän kohdalta olisi tärkeä, että mukana myös joku slide siitä 1760-1770 ajasta. Pitää myös miettiä mihin kohtaan esitystä tämä osio istuu.
+
+---
+
+### Languages
+
+---
+
+[Languages 1/3]
+
+### Development of use of different languages in Finnish National Bibliography
 
@@
 
-## Book printing in Finland / Kungliga
+[Languages 2/3]
+
+### Development of use of different languages in Kungliga Biblioteket's Swedish data
 
@@
 
-## Same with percentages
+[Languages 3/3]
+
+### Percentages of use of different languages in Finnish and Swedish data across time
+
+TÄMÄ PITÄÄ PÄIVITTÄÄ NIIN ETTÄ ON SE RANSKA JA VENÄJÄ MUKANA!
 
@@
 ```
-
----
-
-## Religious literature
-
-Devotional literature (catechisms, hymns, prayer collections, etc.) is known to be the most important form of literature denoting the advancement of reading in Finland in nineteenth century.
-But when does it actually showup as a relevant category?
+---
+
+### Religious texts in Finland
+
+---
+
+[Religious texts in Finland 1/3]
+
+### Devotional literature (catechisms, hymns, prayer collections, etc.)
+
+- known as an form of literature denoting the advancement of reading in Finland in the nineteenth century. Yet, it has been unclear when does it show up as a relevant category.
 
@@
 
-### BOOKINFINLAND DONE3
-
-Temporary sermons played a crucial role in early modern knowledge production, but it has not been clearly analysed in what language they were in Finland (and Sweden).
+[Religious texts in Finland 2/3]
+
+### Temporary sermons in Latin and Swedish
+
+- Temporary sermons played a crucial role in early modern knowledge production, but it has not been clearly analysed in what language they were in Finland (and Sweden).
 
@@
 
-### BOOK IN FINLAND 4
-
-Combination of devotional literature and temporary sermons gives us the following graphs.
+[Religious texts in Finland 3/3]
+
+### Combining devotional literature and temporary sermons
 
@@
 
-# University teaching
-
-### topics 1
-
-Printing of theology related topics in different languages in Turku.
+### University curriculum
+
+---
+
+[University curriculum 1/6]
+
+### Printing of theology in different languages in Turku
 
@@
 
-### topics 2
-
-Printing of history and related topics in different languages in Turku.
+[University curriculum 2/6]
+
+### Printing of history in different languages in Turku
 
@@
 
-### topics 3
-
-Printing of philosophy in different languages in Turku.
+[University curriculum 3/6]
+
+### Printing of philosophy in different languages in Turku
 
@@
 
-### topics 4
-
-Printing of natural science in different languages in Turku.
+[University curriculum 4/6]
+
+### Printing of natural science in different languages in Turku
 
@@
 
-### topics 5
-
-Printing of economy and related topics in different languages in Turku.
+[University curriculum 5/6]
+
+### Printing of economy in different languages in Turku
 
@@
 
-# Enlightenment and reading
-
-Rise of the octavo sized book as vehicle of Enlightenment (and proof of reading).
-
-Paper consumption for different document formats over time. Each point represents a decade. Loess smoothing.
-
-```{r LIBER-13, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=10, fig.height=8, fig.show="hold", out.width="150px"}
-#https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/LIBER-13-2.png
-for (catal in unique(df0$catalog)) {
-  df2 <- subset(df0, catalog == catal) %>% group_by(publication_decade, gatherings) %>% summarize(paper.consumption.km2 = sum(paper.consumption.km2, na.rm = TRUE), n = n()) 
-  df2 <- filter(df2, gatherings %in% setdiff(names(which(table(df2$gatherings) >= 15)), "NA"))
-  p <- ggplot(df2, aes(y = paper.consumption.km2, x = publication_decade, shape = gatherings, linetype = gatherings))
-  p <- p + geom_point(size = 4)
-  p <- p + geom_smooth(method = "loess", size = 1, color = "black")
-  p <- p + ggtitle("Paper consumption in time by gatherings")
-  p <- p + xlab("Year")
-  p <- p + ylab("Paper consumption (km2)")
-  p <- p + guides(linetype = guide_legend(keywidth = 5), shape = guide_legend(keywidth = 5))
-  p <- p + ggtitle(paste("Paper consumption\n(", catal, ")", sep = ""))
-  print(p)
-}
-```
-
----
-
-## Turku
-
-Effects of Enlightenment: decline of metaphysics in favour of social and economic theory and the great victory of reading is visible in the rise and rise of octavo book.
+[University curriculum 6/6]
+
+### Effects of the Enlightenment on the curriculum in Turku
+
+- decline of metaphysics in favour of social and economic theory is clear in Turku
+- the Enlightenment literature that people read in Finland was mainly printed in Stockholm and on the continent.
+
+Tähän top-auktorilistat Fennica ja Kungliga.
+
+---
+
+[Conclusion 1/2]
+
+### Finland in the Swedish context
+
+- Dramatic events regarding the diversity of "Finnishness" take place in the early nineteenth century.
+Finland becomes part of Russia and Turku is stripped off of its former glory...
+But the analysis of Finnish knowledge production 1828-2016 is for another day.
 
@@
 
-## Thanks !
+[Conclusion 2/2]
+
+### Thanks !
 

### 2016-07-06 inst/examples/20160715-slides-Krakow.Rmd
ok

@@
 
-[Intro 1/3]
-
 ## From particular data to global perspective?
@@
 
-### Data and method
-
-Data:
-
-- Fennica (Finnish National Bibliography), n-number of documents
-
-- Kungliga (National Library of Sweden's library catalogue), n-number of documents
-
-Method:
+### Data
+
+Data used (1470-1828):
+
+- Fennica, Finnish National Bibliography, 20328 documents
+
+- Kungliga, National Library of Sweden's catalogue, 73165 documents
+
+### Method
 
@@
 
-- xxx
+- xxx TODO: WHAT DOES LEO WANT TO SAY HERE?
 
@@
 
-### Argument and findings
-
-- Finnish knowledge production 1640-1828 can only be understood in Swedish context.
+### Context
+
+- Finnish knowledge production 1640-1828 can only be understood in the Swedish context.
 
@@
 
+### Findings
+
 Enlightenment in Finland after "the rock bottom" of 1700-1721
@@
 
---> Deep roots of the diversity of "Finnishness" clearly reflcted in knowledge production, 1640-1828.
+--> Deep roots of the diversity of "Finnishness" reflcted in knowledge production, 1640-1828.
 
@@
 
-Kartta jossa näkyy Turku osana Ruotsin valtakuntaa tähän (Janilla ideoita manuskriptin puolella, mun mielestä ne on hyviä tästä).
-Voisi miettiä, että tämä kartta-slide korvaisi sitten tuon alla tulevan "Comparing publishing activity in Swedish University town".
+### TODO Kartta!!!
+
+jossa näkyy Turku osana Ruotsin valtakuntaa
+
+ts.
+eri kaupungit ja niiden nimikemäärät kartalla.
+Kartat voisi tehdä, jos mahdollista, vuosille 1650, 1710, 1767 ja 1800 niin näkyy muutos.
+Tai sitten video jossa näkyy kehitys.
+Pohjois-Eurooppa karttapohjana.
+
+Toteutuksesta riippuen voidaan miettiä, jos tämä kartta-slide korvaisi tuon alla tulevan "Comparing publishing activity in Swedish University town".
 
@@
 [Big Picture 4/4]
+
 ### Rise of the octavo sized book as vehicle of Enlightenment
@@
 
-Turku in Sweden -slide (Janin ideoima tulisi tähän)
+### TODO Turku in Sweden!!!
+
+Janin ajatus: Kaaviot Fennicasta ja Kungligasta, jossa lasketaan eri kaupunkien nimikemäärien, paperinkulutuksen ja kustantajien suhteellinen osuus vuoteen 1828.
+Eli samanlainen kaavio kuin on kielistä ”Book printing in Finland” –osiossa.
+Laaditaan kaaviot Tukholmasta, Uppsalasta, Lundista, Greifswaldista ja Turusta.
+Voiko myös tehdä erillisen kaavion, jossa Tukholma on poistettu, josta näkee näiden kilpailevien kakkoskaupunkien tilanteen.
 
@@
 
-### Numbers of publications of main publishers in Turku
-
-```{r publishers3-finland-fennica, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=7, fig.width=13, out.width="150px", fig.show="hold"}
+### Title count of the output of publishers in Turku
+
+```{r publishers4-fennica, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=7, fig.width=15}
+
 # https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/publishers3-finland-1.png
@@
 df <- df %>%	
+  filter(publication_year >= 1640 & publication_year <= 1828)%>%
         select(publication_decade, publisher, paper.consumption.km2)
@@
 
-### Comparing how much paper different publishers used on average in their publications in Turku
-
-```{r publisherpapertitle, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5, out.width="150px", fig.show="hold"}
+### Comparing paper used on average per publication by publishers
+
+```{r publisherpapertitle, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=8, out.width="150px", fig.show="hold"}
 
@@
 
-Gävle (gray) during riksdagar (Kungliga) TÄÄ EI TOIMI NYT OLLENKAAN KUN ON AIKA PIENI TOI NOUSU NÄKYVISSÄ TÄSSÄ. MENEEKÖ OIKEIN?
+Gävle (gray) during riksdagar (Kungliga) TODO: TÄÄ EI TOIMI NYT OLLENKAAN KUN ON AIKA PIENI TOI NOUSU NÄKYVISSÄ TÄSSÄ. MENEEKÖ OIKEIN? ERI NÄKÖINEN TUOLLA MANUSKRIPTIN PUOLELLA.
 
@@
 
-Tämän kohdalta olisi tärkeä, että mukana myös joku slide siitä 1760-1770 ajasta. Pitää myös miettiä mihin kohtaan esitystä tämä osio istuu.
+### Number of publishers in Stockholm 1760-1770
+
+TODO: Epäonnistuin tässä tuomaan koodin niin että knittaisi oikein. Täten joudun laittamaan kuvalinkin tähän. Harmittaa. Jotkut muut onnistui niin hyvin...
+
+https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/polev1-3.png
 
@@
 
----
-
-[Languages 1/3]
+TODO: "Other" kielikategorian selvittäminen seuraavissa kuvissa.
+Onko siellä joku tietty kieli joka näkyy hyvin selvästi mukana analyysissä?
+Nousee isoksi kategoriaksi.
+Nyt oon merkannut, että Kreikan kieli (Greek) mukaan moneen kohtaan.
+Jos kyseessä joku muu kuin Kreikka niin sitten se.
+Jos taas paljon kombinaatioita pieniä kieliä, niin antaa siinä tapauksessa olla.
+
+---
+
+[Languages 1/4]
+#TODO: TÄSSÄ OLISI HYVÄ JOS v. 1800 julkaisut ei tippuisi nollaan!
 
@@
 
-```{r language1, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=6, out.width="150px", fig.show="hold"}
+```{r language1, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=8, out.width="160px", fig.show="hold"}
 # https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/language1-1.png
@@
 
-[Languages 2/3]
-
-### Development of use of different languages in Kungliga Biblioteket's Swedish data
-
-```{r language1-kungliga, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=6, out.width="150px", fig.show="hold"}
+[Languages 2/4]
+
+### Development of use of different languages in Kungliga data
+
+```{r language1-kungliga, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=8, out.width="150px", fig.show="hold"}
 catalogue = "Kungliga"
@@
 
-[Languages 3/3]
-
-### Percentages of use of different languages in Finnish and Swedish data across time
-
-TÄMÄ PITÄÄ PÄIVITTÄÄ NIIN ETTÄ ON SE RANSKA JA VENÄJÄ MUKANA!
-
-```{r language-perc, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=6, out.width="150px", fig.show="hold"}
+[Languages 3/4]
+
+### Different languages in Fennica and Kungliga (percentage)
+TODO: GREEK mukaan (tai jos joku muu iso kieli niin se)!
+
+```{r language-perc, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=12, out.width="150px", fig.show="hold"}
 for (catalogue in c("Fennica", "Kungliga")) {
@@
 
-langs <- c("Finnish", "Swedish", "Latin", "German", "Other")
+langs <- c("Finnish", "Swedish", "Latin", "German", "French", "Russian", "Other")
 lang <- paste("language.", langs, sep = "")
@@
 ```
+
+---
+
+###TODO: KIELI% !!!!!!!!!!!!!
+
+Sama prosenttianalyysi kielistä kuin edellisessä slidessä mutta paikkakuntakohtaisesti (sekä Fennican että Kungligan mukaan): Turku, Greifswald, Stockholm, Uppsala, Lund.
+Rajataan analyysi vuoteen 1828.
+
+---
+
+[Languages 4/4]
+
+### Topic diversity in different languages in Finnish publications
+TODO: TÄMÄ PITÄISI RAJATA LOPPUMAAN VUOTEEN 1828.
+
+```{r topics232, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, fig.show="hold"}
+catalogue <- "Fennica"
+langs <- c("Finnish", "Swedish", "Latin", "German", "Other")
+df <- filter(df0, catalog == "Fennica") %>%
+  filter(publication_year >= 1640 & publication_year <= 1828)%>% select(publication_year, language, subject_topic)
+df <- unique(df)
+df <- df %>% group_by(publication_year, language) %>% summarise(n = length(unique(unlist(strsplit(subject_topic, ";")))))
+
+df$language[!df$language %in% langs] <- "Other"
+df$language <- factor(df$language, levels = langs)
+
+p <- ggplot(df, aes(x = publication_year, y = n, color = language)) +
+       geom_line() + geom_point() +
+       ggtitle("Number of subject topics")
+
+print(p)
+```
+
 ---
@@
 
-- known as an form of literature denoting the advancement of reading in Finland in the nineteenth century. Yet, it has been unclear when does it show up as a relevant category.
-
-```{r topics, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, fig.show="hold"}
+- Form of literature denoting the advancement of reading in Finland in the nineteenth century. It has been unclear when does it show up as a relevant category.
+
+```{r topics12122, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, fig.show="hold"}
 # https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/topics-2.png
@@
 [Religious texts in Finland 2/3]
+#TODO: TÄSTÄ ja seuraavasta TOI "IF FENNICA FULL TIME SPAN" KOMENTO POIS. En saanut koodattua sitä. TODO: GREEK mukaan!
 
@@
 
-- Temporary sermons played a crucial role in early modern knowledge production, but it has not been clearly analysed in what language they were in Finland (and Sweden).
-
-```{r topics2, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6}
+- play an important role in early modern knowledge production. It has not been analysed in what language they were in Finland (and Sweden).
+
+```{r topics882, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6}
 # https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/topics2-2.png
@@
 [Religious texts in Finland 3/3]
+#TODO: GREEK mukaan!
 
@@
 
-langs <- c("Finnish", "Swedish", "Latin", "German", "Russian", "French", "Other")
+  # Selected catalogue with selected years
+  df = filter(df0, catalog == catalogue & publication_year >= 1640 & publication_year <= 1828)
+
+langs <- c("Finnish", "Swedish", "Latin", "German", "Other")
 lang <- paste("language.", langs, sep = "")
@@
 
-### University curriculum
-
----
-
-[University curriculum 1/6]
+### University curriculum in Turku 1640-1828
+
+---
+
+[University curriculum 1/5]
+
+TODO: OISKO NÄMÄ VIELÄ SELVEMPIÄ VÄRIKKÄINÄ BARPLOTTEINA? Leo, lisäksi säädätkö pois ton risuaitahässäkän näistä? En saanut sitä pois. TODO3: GREEK mukaan!
 
@@
 
-df <- df0 %>% filter(catalog == catalogue)
+df <- df0 %>% filter(catalog == catalogue)%>%
+  filter(publication_year >= 1640 & publication_year <= 1800)
 lang <- paste("language.", langs, sep = "")
@@
 
-[University curriculum 2/6]
+[University curriculum 2/5]
+TODO: GREEK mukaan!
 
@@
 
-[University curriculum 3/6]
+[University curriculum 3/5]
 
 ### Printing of philosophy in different languages in Turku
+TODO: GREEK mukaan!
 
@@
 
-[University curriculum 4/6]
+[University curriculum 4/5]
+TODO: GREEK mukaan!
 
@@
 
-[University curriculum 5/6]
-
-### Printing of economy in different languages in Turku
+[University curriculum 5/5]
+TODO: GREEK mukaan!
+
+### Printing of economy and social science in different languages in Turku
 
@@
 
-[University curriculum 6/6]
-
-### Effects of the Enlightenment on the curriculum in Turku
-
-- decline of metaphysics in favour of social and economic theory is clear in Turku
-- the Enlightenment literature that people read in Finland was mainly printed in Stockholm and on the continent.
-
-Tähän top-auktorilistat Fennica ja Kungliga.
-
----
-
-[Conclusion 1/2]
+### Effects of the Enlightenment in Finland
+
+- decline of metaphysics, rise of social and economic theory 
+- the Enlightenment literature read in Finland mainly printed elsewhere
+
+TODO: KUVA PITÄIS RAJATA 1640-1828, EN ONNISTUNUT
+```{r authors22, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5, out.width="150px", fig.show="hold"}
+theme_set(theme_bw(20))
+for (catalogue in c("Fennica", "Kungliga")) {
+  df <- filter(df0, catalog == catalogue)
+  top.authors <- names(top(df, field = "author", n = 10))
+  dfs <- df %>% filter(author %in% top.authors) %>%
+         group_by(author, publication_decade) %>%
+         tally() %>%
+         arrange(publication_decade)
+  p <- ggplot(dfs, aes(x = publication_decade, y = n, fill = author)) +
+       geom_bar(stat = "identity", position = "stack", color = "black") +
+       xlab("Publication Decade") +
+       ylab("Title Count") +
+       scale_fill_grey() +
+       guides(fill = guide_legend("Author")) +
+       ggtitle(paste("Title count top authors\n", catalogue)) +
+       xlim(range(df0$publication_year))
+  print(p)
+}
+```
+
+---
 
@@
 
-- Dramatic events regarding the diversity of "Finnishness" take place in the early nineteenth century.
-Finland becomes part of Russia and Turku is stripped off of its former glory...
-But the analysis of Finnish knowledge production 1828-2016 is for another day.
+- Dramatic events regarding the diversity of "Finnishness" take place in the early nineteenth century --- but the analysis of Finnish knowledge production 1828-2016 is for another day.
 
@@
 df <- fen %>%
+  filter(publication_year >= 1640 & publication_year <= 1800)%>% 
       filter(!is.na(country)) %>%
@@
 
-[Conclusion 2/2]
+### Duplicate publications
+
+TODO: General analysis (any simple picture) of duplicates between Kungliga and Fennica based on Hege's deduplication code.
+
+---
 
@@
 - University of Helsinki
+- National Library of Finland
+- National Library of Sweden
+- Digitalia / The Regional Council of South Savo

### 2016-07-06 inst/examples/20160715-slides-Krakow.Rmd
ok

@@
 # Set locale
-Sys.setlocale(locale="UTF-8")
+tmp = Sys.setlocale(locale="UTF-8")
 
@@
 ```
+
 ---
@@
 
-Idea: to study early modern knowledge production, all of it (1470-1830)
-
-How? By combining library catalogue data (Fennica, Kungliga, ESTC, CERL)
-
-What is important: to clean up the data (90% of the work) and to take into account how particular data collections (Finnish National Bibliography, English Short-Title Catalogue etc.) have been formed.
-
-How to fail: take worldcat or similar combination of datasets and analyse it as a whole without cleaning it first.
+**Idea**: study early modern knowledge production, all of it (1470-1830)
+
+**How?** By combining library catalogue data (Fennica, Kungliga, ESTC, CERL)
+
+**Important**: to clean up the data (90% of the work) and to take into account how particular data collections (Finnish National Bibliography, English Short-Title Catalogue etc.) have been formed.
+
+**How to fail**: take worldcat or similar combination of datasets and analyse it as a whole without cleaning it first.
 
@@
 
-### Data
-
-Data used (1470-1828):
-
-- Fennica, Finnish National Bibliography, 20328 documents
-
-- Kungliga, National Library of Sweden's catalogue, 73165 documents
+### Data (1470-1828):
+
+- Fennica (Finnish National Bibliography): 20328 documents
+
+- Kungliga (National Library of Sweden): 73165 documents
 

### 2016-07-06 inst/examples/manuscript-krakow.Rmd
ok

@@
 
+TILANNE (6.7.2016):
+
+Paperin kommentointi ja kehittäminen siirretty slide-rmd:n. JANI, kommentoi siis sitä pdf:ää mikä generoitu sen pohjalta. Myös TODOt täältä siirretty sinne.
+
 UUSIA TODOJA (5.7.2016):
@@
 
-```{r language-perc, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, out.width="430px", fig.show="hold"}
+```{r language-perc2, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, out.width="430px", fig.show="hold"}
 # TITLE COUNT
@@
 dff[, -1] <- 100 * t(apply(dff[, -1], 1, function (x) {x/sum(x)}))
-dff <- gather(dff, publication_decade);
+#dff <- gather(dff, publication_decade);
+dff <- melt(dff, "publication_decade");
 colnames(dff) <- c("publication_decade", "language", "f")

### 2016-07-06 inst/examples/20160715-slides-Krakow.Rmd
ok

@@
 catalogue = "Kungliga"
-  df <- dfl %>% filter(catalog == catalogue)
-  df <- dfl %>% group_by(publication_decade, language) %>%
+  df <- dfl %>% filter(catalog == catalogue) %>%
+     	        group_by(publication_decade, language) %>%
                 summarise(n = n(),

### 2016-07-06 inst/examples/20160715-slides-Krakow.Rmd
sync fine

@@
 df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
-
 dfl <- NULL

### 2016-07-06 inst/examples/20160715-slides-Krakow.Rmd
z

@@
   } else if (catalogue == "Kungliga") {
-    df <- df0 # selected time span
-  }
-
-  df <- df %>% filter(catalog == catalogue)
+    df <- df.full # full time span
+  }
+
+  df <- df %>% filter(catalog == catalogue)%>%
+        filter(publication_year >= 1600 & publication_year <= 1900)
 
@@
 colnames(dff) <- c("publication_decade", "language", "f")
-dff$language <- factor(dff$language, levels = langs)
+#dff$language <- factor(dff$language, levels = langs)
 
@@
      ylab("Title count frequency (%)") +
-     ggtitle(paste("Languages (", catalogue, ")", sep = ""))
+     ggtitle(paste("Languages (", catalogue, ")", sep = "")) +  scale_fill_brewer(palette="Paired")
 print(p)

### 2016-07-07 inst/examples/20160715-slides-Krakow.Rmd
s
slide updates

@@
 # Set locale
-tmp = Sys.setlocale(locale="UTF-8")
+tmp <- Sys.setlocale(locale="UTF-8")
 
@@
 
-**How?** By combining library catalogue data (Fennica, Kungliga, ESTC, CERL)
-
-**Important**: to clean up the data (90% of the work) and to take into account how particular data collections (Finnish National Bibliography, English Short-Title Catalogue etc.) have been formed.
-
-**How to fail**: take worldcat or similar combination of datasets and analyse it as a whole without cleaning it first.
+**How?** By combining library catalogues (Fennica, Kungliga, ESTC, CERL)
+
+**Important**: to clean up the data (90% of the work!) and to take into account how particular data collections (Finnish National Bibliography, English Short-Title Catalogue etc.) have been formed.
+
+**How to fail**: take worldcat or similar combination of datasets and analyse it as a whole without cleaning it up first.
 
@@
 
-- Scalable code in library catalogue data ecosystem (github)
-
-- xxx TODO: WHAT DOES LEO WANT TO SAY HERE?
+- Open source tools for library catalogues (Github)
+
+- Fully transparent and reproducible
+
+- Scales up to new catalogues and tasks
 
@@
 
---> Deep roots of the diversity of "Finnishness" reflcted in knowledge production, 1640-1828.
+--> Deep roots of the diversity of "Finnishness" reflected in knowledge production, 1640-1828.
 
@@
 
-### TODO Kartta!!!
-
-jossa näkyy Turku osana Ruotsin valtakuntaa
-
-ts.
-eri kaupungit ja niiden nimikemäärät kartalla.
-Kartat voisi tehdä, jos mahdollista, vuosille 1650, 1710, 1767 ja 1800 niin näkyy muutos.
-Tai sitten video jossa näkyy kehitys.
-Pohjois-Eurooppa karttapohjana.
-
-Toteutuksesta riippuen voidaan miettiä, jos tämä kartta-slide korvaisi tuon alla tulevan "Comparing publishing activity in Swedish University town".
+### Publishing activity in Turku
+
+Voi miettiä, jos tämä korvaisi alla tulevan "Comparing publishing activity in Swedish University town".
+
+```{r map1, echo=FALSE, message=FALSE, warning=FALSE, fig.width=20, fig.height=5}
+library(dplyr)
+library(ggmap)
+library(ggplot2)
+library(gisfin)
+source("funcs.R")
+theme_set(get_theme_map())
+mapdata <- filter(df0, catalog == "Fennica") %>%
+      group_by(publication_decade, publication_place, latitude, longitude) %>%
+      summarise(n = n())
+
+mapdata$size <- mapdata$n
+mapdata$highlight <- rep("black", nrow(mapdata))
+mapdata$highlight[mapdata$publication_place %in% c("Turku")] <- "red"
+mapdata$highlight <- factor(mapdata$highlight)
+
+region <- "Europe.north"
+mymap <- get_map(location=geobox(region), color = "bw", source="google",  maptype="terrain")
+
+p0 <- ggmap(mymap) + theme(legend.position="none")
+
+pics <- list()
+for (i in c(1650, 1710, 1760, 1800)) {
+
+    # Plot map
+    p <- p0
+
+    # Pick the investigated period (sliding window)
+    # Sum up the years within this sliding window for each element    	    
+    dfw <- subset(mapdata, publication_decade == i) %>%
+    	   	       group_by(latitude, longitude, highlight) %>%
+		       summarize(n = sum(size))
+
+    if (nrow(dfw) > 0) {
+      p <- p0 +
+      	geom_point(data = dfw,
+      	  aes(x = longitude, y = latitude,
+	      size = 20*log10(1+n),
+	      color = highlight)) +
+	      #color = highlight), alpha = 0.8) +	      
+	  ggtitle(i) +
+	  scale_size(range = c(2, 20)) +
+	  scale_color_manual(values = c("black", "red"))	  
+    }
+
+  pics[[as.character(i)]] <- p
+
+}
+
+library(gridExtra)
+grid.arrange(pics[[1]], pics[[2]], pics[[3]], pics[[4]], nrow = 1)
+```
 
@@
 
-- Turku
-- Uppsala
-- Lund 
-- Stockholm
+Turku / Uppsala / Lund / Stockholm
 
@@
 
-### TODO Turku in Sweden!!!
-
-Janin ajatus: Kaaviot Fennicasta ja Kungligasta, jossa lasketaan eri kaupunkien nimikemäärien, paperinkulutuksen ja kustantajien suhteellinen osuus vuoteen 1828.
-Eli samanlainen kaavio kuin on kielistä ”Book printing in Finland” –osiossa.
-Laaditaan kaaviot Tukholmasta, Uppsalasta, Lundista, Greifswaldista ja Turusta.
-Voiko myös tehdä erillisen kaavion, jossa Tukholma on poistettu, josta näkee näiden kilpailevien kakkoskaupunkien tilanteen.
+### TODO Turku in Sweden
+
+Proportions for title count, paper, and publishers
+
+```{r comparisons, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=20, fig.height=8}
+pics <- list()
+for (catalogue in na.omit(unique(df0$catalog))) {
+
+df <- df0 %>% filter(catalog == catalogue)
+places <- c("Stockholm", "Uppsala", "Lund", "Greifswald", "Turku")
+df$publication_place[!df$publication_place %in% places] <- "Other"
+df <- subset(df, !is.na(df$publication_place))
+df$publication_place <- factor(df$publication_place, levels = c(places, "Other"))
+
+df <- df %>% group_by(publication_decade, publication_place) %>%
+             summarise(n = n(),
+	     	       paper = sum(paper.consumption.km2, na.rm = TRUE),
+		       publishers = length(na.omit(unique(publisher)))
+		       )
+
+# Calculate percentages
+for (varname in c("n", "paper", "publishers")) {
+
+  df$varname <- df[[varname]]
+  dff <- df %>% select(publication_decade, publication_place, varname)
+  dff <- spread(dff, publication_place, varname, fill = 0)
+  dff[, -1] <- 100 * t(apply(dff[, -1], 1, function (x) {x/sum(x)}))
+  dff <- melt(dff, "publication_decade");
+  colnames(dff) <- c("publication_decade", "publication_place", "f")
+
+  theme_set(theme_bw(20))
+  p <- ggplot(dff, aes(x = publication_decade, y = f)) +
+     geom_bar(position = "stack", stat = "identity",
+       aes(fill = publication_place)) + 
+     xlab("Publication year") +
+     scale_fill_brewer(palette="Paired")
+     if (varname == "n") {
+       p <- p + ggtitle(paste("Title count (", catalogue, ")", sep = "")) + 
+                ylab("Title count frequency (%)") 
+     }
+     if (varname == "paper") {
+       p <- p + ggtitle(paste("Paper (", catalogue, ")", sep = "")) +
+                ylab("Paper (%)")        
+     }
+     if (varname == "publishers") {
+       p <- p + ggtitle(paste("Publishers (", catalogue, ")", sep = "")) +
+                       ylab("Publishers (%)")
+     }
+
+  pics[[paste(catalogue, varname, sep = "-")]] <- p
+
+}
+}
+library(gridExtra)
+grid.arrange(pics[[1]], pics[[2]], pics[[3]], pics[[4]], pics[[5]], pics[[6]], nrow = 2)
+```
 
@@
 
-Gävle (gray) during riksdagar (Kungliga) TODO: TÄÄ EI TOIMI NYT OLLENKAAN KUN ON AIKA PIENI TOI NOUSU NÄKYVISSÄ TÄSSÄ. MENEEKÖ OIKEIN? ERI NÄKÖINEN TUOLLA MANUSKRIPTIN PUOLELLA.
+Gävle (gray) during riksdagar (Kungliga) TODO: TÄÄ EI TOIMI NYT OLLENKAAN KUN ON AIKA PIENI TOI NOUSU NÄKYVISSÄ TÄSSÄ.
+MENEEKÖ OIKEIN?
+ERI NÄKÖINEN TUOLLA MANUSKRIPTIN PUOLELLA.
+- NO KAATU KUN myplace kohdalle pistää skandeja eli olin vaihtanu tukholmaksi.
+Vaihdoin takas Gävleen, katotaan tuleeko virhe.
 
@@
   # Use timeinterval year intervals
-  myplace = "Stockholm" # Norrköping / Stockholm
+  myplace = "Gävle" # Norrköping / Stockholm
   minyear = 1700
@@
 
-TODO: Epäonnistuin tässä tuomaan koodin niin että knittaisi oikein. Täten joudun laittamaan kuvalinkin tähän. Harmittaa. Jotkut muut onnistui niin hyvin...
-
-https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/polev1-3.png
+```{r polev1, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=6, out.width="280px", fig.show="hold"}
+sel.places = c("Stockholm", "Uppsala", "Lund", "Greifswald", "Turku")
+sel.years = c(1760, 1780)
+pics <- list()
+
+for (place in sel.places) {
+
+for (catalogue in c("Fennica", "Kungliga")) {
+
+  df <- df0
+  dfs <- df %>% filter(catalog == catalogue &
+     	              publication_place == place &
+		      publication_year >= min(sel.years) &
+		      publication_year <= max(sel.years) 
+		      )
+
+  df <- dfs %>% group_by(publication_year) %>%
+             summarise(n = n(),
+	               paper = sum(paper.consumption.km2, na.rm = TRUE))
+
+  # PUBLISHER COUNT
+  n = sapply(split(dfs$publisher, dfs$publication_year), function (x) {length(unique(na.omit(x)))})
+  df = data.frame(year = names(n), n = unname(n))
+  if (nrow(df) > 1) {
+    p = ggplot(df, aes(x = year, y = n)) +
+        geom_bar(stat = "identity") +
+       ggtitle(paste("Publishers:", catalogue, place)) +
+       scale_x_discrete(breaks = seq(min(sel.years), max(sel.years), 10))
+  } else {
+    p <- ggplot() + ggtitle("Insufficient data")
+  }
+  pics[[paste(place, catalogue, sep = "-")]] <- p
+}
+}
+grid.arrange(pics[[1]], pics[[2]], pics[[3]], pics[[4]], pics[[5]],
+             pics[[6]], pics[[7]], pics[[8]], pics[[9]], pics[[10]], nrow = 2)
+```
 
@@
 Nousee isoksi kategoriaksi.
-Nyt oon merkannut, että Kreikan kieli (Greek) mukaan moneen kohtaan.
+Nyt oon merkannut, että Kreikan kieli (Greek - huom on kielet Greek, Modern (1453-) sekä Greek, Ancient (to 1453) mutta ei pelkka Greek) mukaan moneen kohtaan.
 Jos kyseessä joku muu kuin Kreikka niin sitten se.
 Jos taas paljon kombinaatioita pieniä kieliä, niin antaa siinä tapauksessa olla.
+LL: Lisäsin Kreikan mutten muuten ehdi tutkia asiaa.
+Voit katsoa R:llä top(df0, "language", 10)
 
@@
 [Languages 1/4]
-#TODO: TÄSSÄ OLISI HYVÄ JOS v. 1800 julkaisut ei tippuisi nollaan!
+#TODO: TÄSSÄ OLISI HYVÄ JOS v. 1800 julkaisut ei tippuisi nollaan! LL: I cannot change the data. This is the results from this analysis.
 
@@
 # https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/language1-1.png
-catalogue = "Fennica"
+catalogue <- "Fennica"
 df <- df0
-langs <- c("Finnish", "Swedish", "Latin", "German", "Russian", "French", "Other")
+langs <- c("Finnish", "Swedish", "Latin", "German", "Russian", "French", "Greek, Ancient (to 1453)", "Other")
 lang <- paste("language.", langs, sep = "")
@@
   dflsub <- filter(df, df[[lan]])
+  if (nrow(dflsub) > 0) {
     dflsub$language <- gsub("language.", "", lan)
     dfl <- bind_rows(dfl, dflsub)
-
+  }
 }
@@
 
-langs <- c("Finnish", "Swedish", "Latin", "German", "French", "Russian", "Other")
 lang <- paste("language.", langs, sep = "")
@@
 df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
+
 dfl <- NULL
-
 for (lan in lang) {
@@
   dflsub <- filter(df, df[[lan]])
+  if (nrow(dflsub)>0) {
     dflsub$language <- gsub("language.", "", lan)
     dfl <- bind_rows(dfl, dflsub)
-
+  }
 }
@@
 dff[, -1] <- 100 * t(apply(dff[, -1], 1, function (x) {x/sum(x)}))
-#dff <- gather(dff, publication_decade);
 dff <- melt(dff, "publication_decade");
 colnames(dff) <- c("publication_decade", "language", "f")
-#dff$language <- factor(dff$language, levels = langs)
 
@@
      ylab("Title count frequency (%)") +
-     ggtitle(paste("Languages (", catalogue, ")", sep = "")) +  scale_fill_brewer(palette="Paired")
+     ggtitle(paste("Languages (", catalogue, ")", sep = "")) +
+     scale_fill_brewer(palette="Paired")
 print(p)
@@
 
+```{r language-perc2, echo=FALSE, message=FALSE, warning=FALSE, fig.width=20, fig.height=5}
+pics <- list()
+theme_set(theme_bw(20))
+myplaces <- c("Turku", "Greifswald", "Stockholm", "Uppsala", "Lund")
+
+for (catalogue in c("Fennica", "Kungliga")) {
+
+  df <- df0 %>% filter(catalog == catalogue) %>%
+        filter(publication_year >= 1600 & publication_year <= 1828)
+
+  lang <- paste("language.", langs, sep = "")
+  otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
+  df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
+
+  dfl <- NULL
+  for (lan in lang) {
+
+    # Classify a document to the specifed language
+    # If document is assigned with languages, each case is considered
+    # so one doc may have multiple entries corresponding to different languages
+    # mean(rowSums(df[, lang]) == 1) # 93% Fennica docs have just 1 language
+    # Combine data frames for specified languages
+    dflsub <- filter(df, df[[lan]])
+    if (nrow(dflsub) > 0) {
+      dflsub$language <- gsub("language.", "", lan)
+      dfl <- bind_rows(dfl, dflsub)
+    }
+  }
+
+  df <- dfl %>% group_by(publication_decade, publication_place, language) %>%
+     	     summarise(n = n())
+
+  # Calculate percentages
+  dff <- spread(df, language, n, fill = 0)
+  dff[, -c(1,2)] <- 100 * t(apply(dff[, -c(1,2)], 1, function (x) {x/sum(x)}))
+
+  dff <- melt(dff, id = c("publication_place", "publication_decade"))
+  colnames(dff) <- c("publication_place", "publication_decade", "language", "f")
+
+  for (myplace in myplaces) {
+    p <- ggplot(subset(dff, publication_place == myplace), aes(x = publication_decade, y = f)) +
+      geom_bar(position = "stack", stat = "identity", aes(fill = language)) + 
+      xlab("Publication year") +
+      ylab("Title count frequency (%)") +
+      ggtitle(paste("Languages (", myplace, "/", catalogue, ")", sep = "")) +
+      scale_fill_brewer(palette="Paired")
+    pics[[paste(catalogue, myplace, sep = "-")]] <- p
+  }
+}
+
+grid.arrange(pics[[1]], pics[[2]], pics[[3]], pics[[4]], pics[[5]],
+             pics[[6]], pics[[7]], pics[[8]], pics[[9]], pics[[10]], 
+             nrow = 2)
+```
+
 ---
@@
 TODO: TÄMÄ PITÄISI RAJATA LOPPUMAAN VUOTEEN 1828.
+LL: on rajattu jo mun nähdäkseni ?
 
@@
 catalogue <- "Fennica"
-langs <- c("Finnish", "Swedish", "Latin", "German", "Other")
 df <- filter(df0, catalog == "Fennica") %>%
-  filter(publication_year >= 1640 & publication_year <= 1828)%>% select(publication_year, language, subject_topic)
+  filter(publication_year >= 1640 & publication_year <= 1828) %>%
+  select(publication_year, language, subject_topic)
 df <- unique(df)
-df <- df %>% group_by(publication_year, language) %>% summarise(n = length(unique(unlist(strsplit(subject_topic, ";")))))
+df <- df %>% group_by(publication_year, language) %>%
+             summarise(n = length(unique(unlist(strsplit(subject_topic, ";")))))
 
@@
 catalogue <- "Fennica"
-langs <- c("Finnish", "Swedish", "Latin", "German", "Other")
 
   # Selected catalogue with selected years
-  df = filter(df0, catalog == catalogue & publication_year >= 1640 & publication_year <= 1828)
+  df <- filter(df0, catalog == catalogue &
+     		    publication_year >= 1640 &
+		    publication_year <= 1828)
 
@@
     dflsub <- filter(df, df[[lan]])
+    if (nrow(dflsub) > 0) {
       dflsub$language <- gsub("language.", "", lan)
       dfl <- bind_rows(dfl, dflsub)
+    }
   }
@@
 [Religious texts in Finland 2/3]
-#TODO: TÄSTÄ ja seuraavasta TOI "IF FENNICA FULL TIME SPAN" KOMENTO POIS. En saanut koodattua sitä. TODO: GREEK mukaan!
 
@@
 ```{r topics882, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6}
-# https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/topics2-2.png
-
   sel <- c("hautajaiset", "häät", "juhlamenot")
   catalogue <- "Fennica"
-  if (catalogue == "Fennica") {
-    df <- df.full # full time span
-  } else if (catalogue == "Kungliga") {
-    df <- df0 # selected time span
-  }
+  df <- df0
   df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)
@@
   df <- df %>% filter(catalog == catalogue & hit)
-
-langs <- c("Finnish", "Swedish", "Latin", "German", "Other")
+  lang <- paste("language.", langs, sep = "")
+  otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
+  df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
+
+  dfl <- NULL
+  for (lan in lang) {
+    # Classify a document to the specifed language
+    # If document is assigned with languages, each case is considered
+    # so one doc may have multiple entries corresponding to different languages
+    # mean(rowSums(df[, lang]) == 1) # 93% Fennica docs have just 1 language
+    # Combine data frames for specified languages
+    dflsub <- filter(df, df[[lan]])
+    if (nrow(dflsub) > 0) {
+      dflsub$language <- gsub("language.", "", lan)
+    dfl <- bind_rows(dfl, dflsub)
+  }
+}
+dfl$language <- factor(dfl$language, levels = langs)
+
+  df <- dfl %>% group_by(publication_decade, language) %>%
+             summarise(n = n(),
+	               paper = sum(paper.consumption.km2, na.rm = TRUE))
+
+  # PAPER CONSUMPTION
+  p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
+       geom_point(aes(col = language, shape = language), size = 5) +
+       geom_line(aes(col = language, shape = language)) +       
+       xlab("Publication year") +
+       ylab("Paper consumption") +
+       ggtitle(paste("Languages (", catalogue, ")", sep = ""))
+  print(p)
+```
+
+---
+
+[Religious texts in Finland 3/3]
+
+### Combining devotional literature and temporary sermons
+
+```{r topics3, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6}
+sel <- c("virret","arkkiveisut","hartauskirjat","katekismukset","rukouspäivät","saarnat","aapiset","rukoukset","rukous","hengelliset laulut","hartauspuheet","virsikirjat","hautajaiset","häät","juhlamenot")
+catalogue <- "Fennica"
+  df <- df0 # selected time span
+  df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)
+
+  # Selected catalogue with selected topics
+  df <- df %>% filter(catalog == catalogue & hit)
+
+  # Selected catalogue with selected years
+  df = filter(df0, catalog == catalogue & publication_year >= 1640 & publication_year <= 1828)
+
   lang <- paste("language.", langs, sep = "")
@@
     dflsub <- filter(df, df[[lan]])
+    if (nrow(dflsub) > 0) {
       dflsub$language <- gsub("language.", "", lan)
@@
     }
-dfl$language <- factor(dfl$language, levels = langs)
+}
 
@@
 	               paper = sum(paper.consumption.km2, na.rm = TRUE))
-
-# TITLE COUNT
-theme_set(theme_bw(20))
-p <- ggplot(df, aes(x = publication_decade, y = n, group = language)) +
-       geom_point(aes(col = language, shape = language), size = 5) +
-       geom_line(aes(col = language, shape = language)) +       
-       xlab("Publication year") +
-       ylab("Title count (n)") +
-       ggtitle(paste("Languages (", catalogue, ")", sep = ""))
-#print(p)
 
@@
 
-[Religious texts in Finland 3/3]
-#TODO: GREEK mukaan!
-
-### Combining devotional literature and temporary sermons
-
-```{r topics3, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6}
-# https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/topics3-2.png
-
-sel <- c("virret","arkkiveisut","hartauskirjat","katekismukset","rukouspäivät","saarnat","aapiset","rukoukset","rukous","hengelliset laulut","hartauspuheet","virsikirjat","hautajaiset","häät","juhlamenot")
-catalogue <- "Fennica"
-  if (catalogue == "Fennica") {
-    df <- df.full # full time span
-  } else if (catalogue == "Kungliga") {
-    df <- df0 # selected time span
-  }
-  df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)
-
-# Selected catalogue with selected topics
-df <- df %>% filter(catalog == catalogue & hit)
-
-  # Selected catalogue with selected years
-  df = filter(df0, catalog == catalogue & publication_year >= 1640 & publication_year <= 1828)
-
-langs <- c("Finnish", "Swedish", "Latin", "German", "Other")
-lang <- paste("language.", langs, sep = "")
-otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
-df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
-dfl <- NULL
-for (lan in lang) {
-  # Classify a document to the specifed language
-  # If document is assigned with languages, each case is considered
-  # so one doc may have multiple entries corresponding to different languages
-  # mean(rowSums(df[, lang]) == 1) # 93% Fennica docs have just 1 language
-  # Combine data frames for specified languages
-  dflsub <- filter(df, df[[lan]])
-  dflsub$language <- gsub("language.", "", lan)
-  dfl <- bind_rows(dfl, dflsub)
-}
-
-# -------------------------------------------
-
-df <- dfl %>% group_by(publication_decade, language) %>%
-             summarise(n = n(),
-	               paper = sum(paper.consumption.km2, na.rm = TRUE))
-
-# TITLE COUNT
-theme_set(theme_bw(20))
-p <- ggplot(df, aes(x = publication_decade, y = n, group = language)) +
-       geom_point(aes(col = language, shape = language), size = 5) +
-       geom_line(aes(col = language, shape = language)) +       
-       xlab("Publication year") +
-       ylab("Title count (n)") +
-       ggtitle(paste("Languages (", catalogue, ")", sep = ""))
-#print(p)
-
-# PAPER CONSUMPTION
-p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
-       geom_point(aes(col = language, shape = language), size = 5) +
-       geom_line(aes(col = language, shape = language)) +       
-       xlab("Publication year") +
-       ylab("Paper consumption") +
-       ggtitle(paste("Languages (", catalogue, ")", sep = ""))
-print(p)
-```
-
----
-
 ### University curriculum in Turku 1640-1828
@@
 
-TODO: OISKO NÄMÄ VIELÄ SELVEMPIÄ VÄRIKKÄINÄ BARPLOTTEINA? Leo, lisäksi säädätkö pois ton risuaitahässäkän näistä? En saanut sitä pois. TODO3: GREEK mukaan!
+TODO: OISKO NÄMÄ VIELÄ SELVEMPIÄ VÄRIKKÄINÄ BARPLOTTEINA?
 
@@
 sel =  c("kirkkohistoria","raamatunhistoria","eksegetiikka","homiletiikka","dogmatiikka","teologia")
-langs <- c("Finnish", "Swedish", "Latin", "German", "Russian", "French", "Other")
 catalogue <- "Fennica"
@@
 # Selected catalogue with selected topics
-df = dfl
+df <- dfl
 df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)  
@@
   p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
-       geom_point(aes(col = language, shape = language), size = 5) +
-       geom_line(aes(col = language, shape = language)) +       
+       geom_bar(aes(fill = language), position = "stack", stat = "identity") +              
        xlab("Publication year") +
        ylab("Paper consumption") +
-       ggtitle(paste("Paper (", print(paste(sel, collapse = ";")), ")", sep = ""))
-print(p)
-
+       ggtitle(paste("Paper (", paste(sel, collapse = ";"), ")", sep = ""))
+  print(p)
 ```
@@
 [University curriculum 2/5]
-TODO: GREEK mukaan!
 
@@
        ylab("Paper consumption") +
-       ggtitle(paste("Paper (", print(paste(sel, collapse = ";")), ")", sep = ""))
+       ggtitle(paste("Paper (", paste(sel, collapse = ";"), ")", sep = ""))
 print(p)
@@
 ### Printing of philosophy in different languages in Turku
-TODO: GREEK mukaan!
 
@@
 [University curriculum 4/5]
-TODO: GREEK mukaan!
 
@@
 [University curriculum 5/5]
-TODO: GREEK mukaan!
 
@@
 
-- decline of metaphysics, rise of social and economic theory 
-- the Enlightenment literature read in Finland mainly printed elsewhere
-
-TODO: KUVA PITÄIS RAJATA 1640-1828, EN ONNISTUNUT
+- Decline of metaphysics, rise of social and economic theory 
+- The Enlightenment literature read in Finland mainly printed elsewhere
+
+TODO: KUVA PITÄIS RAJATA 1640-1828, EN ONNISTUNUT - DONE
+
 ```{r authors22, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5, out.width="150px", fig.show="hold"}
@@
 for (catalogue in c("Fennica", "Kungliga")) {
-  df <- filter(df0, catalog == catalogue)
+  df <- filter(df0, catalog == catalogue) %>%
+        filter(publication_year >= 1640 & publication_year <= 1828)
   top.authors <- names(top(df, field = "author", n = 10))
@@
 ```{r 201606krakow-turkuvsother, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=5, fig.width=10}
-# https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/201606krakow-turkuvsother-2.png
-
 df <- fen %>%

### 2016-07-07 inst/examples/20160715-slides-Krakow.Rmd
z
ok

@@
 p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
-       geom_point(aes(col = language, shape = language), size = 5) +
-       geom_line(aes(col = language, shape = language)) +       
+       geom_bar(aes(fill = language), position = "stack", stat = "identity") +             
+       #geom_point(aes(col = language, shape = language), size = 5) +
+       #geom_line(aes(col = language, shape = language)) +       
        xlab("Publication year") +
@@
 p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
-       geom_point(aes(col = language, shape = language), size = 5) +
-       geom_line(aes(col = language, shape = language)) +       
+       #geom_point(aes(col = language, shape = language), size = 5) +
+       #geom_line(aes(col = language, shape = language)) +
+       geom_bar(aes(fill = language), position = "stack", stat = "identity") +                     
        xlab("Publication year") +
@@
 p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
-       geom_point(aes(col = language, shape = language), size = 5) +
-       geom_line(aes(col = language, shape = language)) +       
+       #geom_point(aes(col = language, shape = language), size = 5) +
+       #geom_line(aes(col = language, shape = language)) +
+       geom_bar(aes(fill = language), position = "stack", stat = "identity") +              
        xlab("Publication year") +

### 2016-07-07 inst/examples/20160715-slides-Krakow.Rmd
switched to combined data

@@
 ```{r 201606krakow-init2, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, cache=TRUE}
-# Read data
-fen0 <- readRDS("fennica.Rds")
-kun0 <- readRDS("kungliga.Rds")
-
-fenraw <- readRDS("fennica.raw.Rds")
-kunraw <- readRDS("kungliga.raw.Rds")
-
-fen <- fen0 %>% filter(publication_year >= min.year & publication_year <= max.year)
-kun <- kun0 %>% filter(publication_year >= min.year & publication_year <= max.year)
-
-# Full time span
-df.full = bind_rows(fen0, kun0)
-df.full$catalog = factor(c(rep("Fennica", nrow(fen0)), rep("Kungliga", nrow(kun0))))
-
-# Selected time spam
-df0 = bind_rows(fen, kun)
-df0$catalog = factor(c(rep("Fennica", nrow(fen)), rep("Kungliga", nrow(kun))))
+# Full combined catalogue (Fen + Kun) with marked duplicates
+df.combined.preprocessed <- readRDS("df.combined.Rds")
+# Data with duplicates removed
+df.full <- df.combined.preprocessed %>% filter(!remove)
+# Data with years limited as well
+df0 <- df.full %>% filter(publication_year >= min.year & publication_year <= max.year)
 ```
@@
 ```{r 201606krakow-turkuvsother, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=5, fig.width=10}
-df <- fen %>%
+df <- subset(df0, catalog == "Fennica") %>%
   filter(publication_year >= 1640 & publication_year <= 1800)%>% 
@@
 
+```{r duplicates, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=5, fig.width=10}
+# DUPLICATE FRACTION
+df <- df.combined.preprocessed %>% group_by(catalog) %>%
+      			           summarise(duplicates = 100 * mean(remove))
+p <- ggplot(df, aes(x = catalog, y = duplicates)) +
+       geom_bar(position = "dodge", stat = "identity") +
+       ylab("Duplicates (%)") +
+       ggtitle(paste("Duplicates", paste(range(df.combined.preprocessed$publication_year), collapse = "-")))
+print(p)
+```
+
 ---

### 2016-07-07 inst/examples/manuscript-krakow.Rmd
switched to combined data

@@
 # Read data
-fen0 <- readRDS("df.Rds")
-kun0 <- readRDS("../../../kungliga/df.Rds")
-
-fenraw <- readRDS("df.raw.Rds")
-kunraw <- readRDS("../../../kungliga/df.raw.Rds")
-
-fen <- fen0 %>% filter(publication_year >= min.year & publication_year <= max.year)
-kun <- kun0 %>% filter(publication_year >= min.year & publication_year <= max.year)
+#fen0 <- readRDS("df.Rds")
+#kun0 <- readRDS("../../../kungliga/df.Rds")
+
+#fenraw <- readRDS("df.raw.Rds")
+#kunraw <- readRDS("../../../kungliga/df.raw.Rds")
+
+#fen <- fen0 %>% filter(publication_year >= min.year & publication_year <= max.year)
+#kun <- kun0 %>% filter(publication_year >= min.year & publication_year <= max.year)
 
 # Full time span
-df.full = bind_rows(fen0, kun0)
-df.full$catalog = factor(c(rep("Fennica", nrow(fen0)), rep("Kungliga", nrow(kun0))))
+#df.full = bind_rows(fen0, kun0)
+#df.full$catalog = factor(c(rep("Fennica", nrow(fen0)), rep("Kungliga", nrow(kun0))))
 
 # Selected time spam
-df0 = bind_rows(fen, kun)
-df0$catalog = factor(c(rep("Fennica", nrow(fen)), rep("Kungliga", nrow(kun))))
+#df0 = bind_rows(fen, kun)
+#df0$catalog = factor(c(rep("Fennica", nrow(fen)), rep("Kungliga", nrow(kun))))
+
+# Full combined catalogue (Fen + Kun) with marked duplicates
+df.combined.preprocessed <- readRDS("df.combined.Rds")
+# Data with duplicates removed
+df.full <- df.combined.preprocessed %>% filter(!remove)
+# Data with years limited as well
+df0 <- df.full %>% filter(publication_year >= min.year & publication_year <= max.year)
 

### 2016-07-07 inst/examples/20160715-slides-Krakow.Rmd
ok

@@
 print(p)
+
+df <- df.combined.preprocessed %>% group_by(catalog) %>%
+      			           summarise(duplicates = 100 * mean(remove))
+p <- ggplot(df, aes(x = catalog, y = duplicates)) +
+       geom_bar(position = "dodge", stat = "identity") +
+       ylab("Duplicates (%)") +
+       ggtitle(paste("Duplicates", paste(range(df.combined.preprocessed$publication_year), collapse = "-")))
+print(p)
 ```

### 2016-07-07 inst/examples/manuscript-krakow.Rmd
updated manuscript file to deduplicated data

@@
 max.year <- 1828
+output.folder <- "output.tables"
 
@@
 ntop = 10
-p <- top_plot(fen, "publication_place", ntop = ntop)
+p <- top_plot(subset(df0, catalog == "Fennica"), "publication_place", ntop = ntop)
 p <- p + scale_fill_manual(values = "black")
@@
 theme_set(theme_bw(30))
-p <- top_plot(kun, "publication_place", ntop = ntop)
+p <- top_plot(subset(df0, catalog == "Kungliga"), "publication_place", ntop = ntop)
 p <- p + scale_fill_manual(values = "black")
@@
 
-Focus on Gävle (gray) during riksdagar. Gävle has `r sum("Gävle" %in% fen$publication_place)` occurrences in Fennica, hence not included here. The figure on Gävle is based on Kungliga.
+Focus on Gävle (gray) during riksdagar.
+Gävle has `r sum("Gävle" %in% subset(df0, catalog == "Fennica")$publication_place)` occurrences in Fennica, hence not included here.
+The figure on Gävle is based on Kungliga.
 
@@
 ```{r topics.per.publisher, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, out.width="430px", fig.show="hold"}
-tops <-  names(top(fen, "publisher", 5))
+tops <-  names(top(subset(df0, catalog == "Fennica"), "publisher", 5))
 
@@
 ```{r topics2.per.publisher, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, out.width="430px", fig.show="hold"}
-tops <-  names(top(fen, "publisher", 5))
+tops <-  names(top(subset(df0, catalog == "Fennica"), "publisher", 5))
 
@@
 ```{r topics3.per.publisher, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, out.width="430px", fig.show="hold"}
-tops <-  names(top(fen, "publisher", 5))
+tops <-  names(top(subset(df0, catalog == "Fennica"), "publisher", 5))
 
@@
 ```{r 201606krakow-turkuvsother, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=7, fig.width=10, fig.show="hold", out.width="430px"}
-df <- fen %>% 
+df <- df0 %>%
+      filter(catalog == "Fennica") %>% 
       filter(!is.na(country)) %>%
@@
 
-The raw data contains metadata `r nrow(fenraw)` and `r nrow(kunraw)` documents in Fennica and Kungliga, respectively.
-We limited the present analysis in the time interval `r min(df0$publication_year)`-`r max(df0$publication_year)`, yielding a subset of `r nrow(subset(df0, catalog == "Fennica"))` (`r round(100*nrow(subset(df0, catalog == "Fennica"))/nrow(fenraw), 1)`%) and `r nrow(subset(df0, catalog == "Kungliga"))` (`r round(100*nrow(subset(df0, catalog == "Kunliga"))/nrow(kunraw), 1)`%) documents for Fennica and Kungliga, respectively.
+The raw data contains metadata `r nrow(subset(df.full, catalog == "Fennica"))` and `r nrow(subset(df.full, catalog == "Kungliga"))` documents in Fennica and Kungliga, respectively.
+We limited the present analysis in the time interval `r min(df0$publication_year)`-`r max(df0$publication_year)`, yielding a subset of `r nrow(subset(df0, catalog == "Fennica"))` (`r round(100*nrow(subset(df0, catalog == "Fennica"))/nrow(subset(df.full, catalog == "Fennica")), 1)`%) and `r nrow(subset(df0, catalog == "Kungliga"))` (`r round(100*nrow(subset(df0, catalog == "Kunliga"))/nrow(subset(df.full, catalog == "Kungliga")), 1)`%) documents for Fennica and Kungliga, respectively.
 
@@
 theme_set(theme_bw(10))
-dfs <- fen %>% filter(author_gender == "female")
+dfs <- df0 %>%
+  filter(catalog == "Fennica") %>%
+  filter(author_gender == "female")
 p <- top_plot(dfs, "author", ntop = 20)
@@
 theme_set(theme_bw(20))
-dfs <- kun %>% filter(author_gender == "female")
+dfs <- df0 %>%
+  filter(catalog == "Kungliga") %>%
+  filter(author_gender == "female")
 p <- top_plot(dfs, "author", ntop = 20)

### 2016-07-07 inst/examples/tmp.R
a

@@ -1,8 +1,0 @@
-
-df <- filter(df0, catalog == "Kungliga") %>%
-      filter(publication_year <= 1828)
-
-output.folder <- "figure_201606_Krakow/"
-field <- "subject_topic"
-entries = unlist(strsplit(as.character(df.preprocessed[[field]]), ";"), use.names = FALSE)
-s <- write_xtable(entries, file = paste(output.folder, catalog, "_subjecttopics", min(df$publication_year), "_", max(df$publication_year), ".csv", sep = ""))

### 2016-07-07 inst/examples/20160715-slides-Krakow.Rmd
added back slides Rmd

--- 2016-07-07 inst/examples/20160715-slides-Krakow.Rmd
@@
 # DUPLICATE FRACTION
-df <- df.combined.preprocessed %>% group_by(catalog) %>%
+#df <- df.combined.preprocessed %>% group_by(catalog) %>%
+#      			           summarise(duplicates = 100 * mean(remove))
+#p <- ggplot(df, aes(x = catalog, y = duplicates)) +
+#       geom_bar(position = "dodge", stat = "identity") +
+#       ylab("Duplicates (%)") +
+#       ggtitle(paste("Duplicates", paste(range(df.combined.preprocessed$publication_year), collapse = "-")))
+#print(p)
+
+df <- df.combined.preprocessed %>%
+        filter(publication_year >= 1640 & publication_year <=1828) %>%
+        group_by(catalog, publication_decade) %>%
 	summarise(duplicates = 100 * mean(remove))
-p <- ggplot(df, aes(x = catalog, y = duplicates)) +
+
+p <- ggplot(df, aes(x = publication_decade, y = duplicates, fill = catalog)) +
        geom_bar(position = "dodge", stat = "identity") +
        ylab("Duplicates (%)") +
-       ggtitle(paste("Duplicates", paste(range(df.combined.preprocessed$publication_year), collapse = "-")))
+       scale_fill_manual(values = c("blue", "red")) + 
+       ggtitle(paste("Duplicates", paste(range(na.omit(df$publication_year)), collapse = "-")))
+
 print(p)

### 2016-07-07 inst/examples/20160715-slides-Krakow.Rmd
s

@@
 theme_set(get_theme_map())
-mapdata <- filter(df0, catalog == "Fennica") %>%
+mapdata <- filter(df0, catalog == "Kungliga") %>%
       group_by(publication_decade, publication_place, latitude, longitude) %>%
@@
       	  aes(x = longitude, y = latitude,
-	      size = 20*log10(1+n),
+	      size = 3*log10(1+n),
 	      color = highlight)) +
@@
 	  ggtitle(i) +
-	  scale_size(range = c(2, 20)) +
+	  scale_size(range = c(1, 15)) +
 	  scale_color_manual(values = c("black", "red"))	  
@@
 
-df <- df0 %>% filter(catalog == catalogue)
+df <- df0 %>% filter(catalog == catalogue)%>%
+        filter(publication_year >= 1640 & publication_year <= 1828)
 places <- c("Stockholm", "Uppsala", "Lund", "Greifswald", "Turku")
@@
 
-[Swedish age of Freedom and abolishment of censorship 1/2]
+[Swedish Age of Freedom and Abolishment of Censorship 1/3]
 
@@
 
-Gävle (gray) during riksdagar (Kungliga) TODO: TÄÄ EI TOIMI NYT OLLENKAAN KUN ON AIKA PIENI TOI NOUSU NÄKYVISSÄ TÄSSÄ.
-MENEEKÖ OIKEIN?
-ERI NÄKÖINEN TUOLLA MANUSKRIPTIN PUOLELLA.
-- NO KAATU KUN myplace kohdalle pistää skandeja eli olin vaihtanu tukholmaksi.
-Vaihdoin takas Gävleen, katotaan tuleeko virhe.
+Gävle (gray) during riksdagar (Kungliga) TODO: Lopuks muutetaan takas Gävleks. Nyt ei toimi.
 
@@
   # Use timeinterval year intervals
-  myplace = "Gävle" # Norrköping / Stockholm
+  myplace = "Greifswald" # Norrköping / Stockholm
   minyear = 1700
   maxyear = 1800
-  catal = "Kungliga"
+  catalog = "Kungliga"
 
@@
 
-[Swedish age of Freedom and abolishment of censorship 2/2]
+[Swedish Age of Freedom and Abolishment of Censorship 2/3]
 
@@
 ```
+
+---
+
+[Swedish Age of Freedom and Abolishment of Censorship 3/3]
+
+TODO: asiasanoja / yliopistopaikkakunta vertailu.
+Ts.
+mitä enemmän eri aikoina asiasanoja (ihan sama mitä ne on) paikkakunnalla, sitä monimuotoisempaa/rikkaampaa julkaisutoiminta (eli kaikki julkaisut eivät samasta aiheesta, esim.
+oikeuspöytäkirjoissa ei varmaan hirveästi vaihtelua).
+Voidaan suhteuttaa myös esim.
+paperinkulutukseen.
+Greifswald vs Turku (kuinka monta kieltä per vuosi) oli samansuuntainen.
 

### 2016-07-07 inst/examples/20160715-slides-Krakow.Rmd
xx

@@
 
-Gävle (gray) during riksdagar (Kungliga) TODO: Lopuks muutetaan takas Gävleks. Nyt ei toimi.
+Gävle (gray) during riksdagar (Kungliga) TODO: Lopuks muutetaan takas Gävleks. Nyt ei toimi, siksi Greifswald analyysi tässä.
 
@@
 
-TODO: asiasanoja / yliopistopaikkakunta vertailu.
+###TODO: asiasanoja / yliopistopaikkakunta vertailu.
 Ts.
@@
 [Languages 1/4]
-#TODO: TÄSSÄ OLISI HYVÄ JOS v. 1800 julkaisut ei tippuisi nollaan! LL: I cannot change the data. This is the results from this analysis.
 
@@
 ### Different languages in Fennica and Kungliga (percentage)
-TODO: GREEK mukaan (tai jos joku muu iso kieli niin se)!
 
@@
 
-###TODO: KIELI% !!!!!!!!!!!!!
-
-Sama prosenttianalyysi kielistä kuin edellisessä slidessä mutta paikkakuntakohtaisesti (sekä Fennican että Kungligan mukaan): Turku, Greifswald, Stockholm, Uppsala, Lund.
-Rajataan analyysi vuoteen 1828.
+### Different languages in Swedish University towns
 
@@
              pics[[6]], pics[[7]], pics[[8]], pics[[9]], pics[[10]], 
-             nrow = 2)
+             nrow = 3)
 ```
@@
 ### University curriculum in Turku 1640-1828
+
+---
+
+##TODO: Dissertation language
+
+Yleinen kielianalyysi prosentteina (sama kuin muut toteutetut prosenttianalyysit näissä Krakova slideissa) kaikkien Fennicassa väitöskirjoiksi merkityistä: eli Kenttä "Dissertation" ja vastaus "True" tässä aineisto.
+Analyysi vuosikymmenittäin ja kielen mukaan eri väreillä.
+Kielien joukko:
+
+Ollaan kiinnostuttu milloin alkaa erityisesti tulemaan ruotsinkielellä väitöksiä.
 

### 2016-07-07 inst/examples/20160715-slides-Krakow.Rmd
d

@@
 
-**Idea**: study early modern knowledge production, all of it (1470-1830)
+**Idea**: to study early modern knowledge production, all of it (1470-1830)
 
@@
 ### Peaks and drops – role of publishers and contingency
+TODO: Tuolla on yksi iso piikki Kungligassa (1760-1770) ja kaksi laskua Fennicassa (1700-1721) ja (1809-1828). Voisko ne HIGHLIGHTata jollain tyylikkäällä tavalla?
 
@@
 
+TODO: Tässä vois maalata ton octavo-kirjojen käyrän molemmista kuvista jollain kirkkaalla värillä (ei muuta).
 ```{r LIBER-13, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=10, fig.height=8, fig.show="hold", out.width="150px"}
@@
 Proportions for title count, paper, and publishers
-
+TODO: OTHER julkaisijakenttä laittaa ton Turku-kuvan pieleen, "other" kategoria liian iso.
 ```{r comparisons, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=20, fig.height=8}
@@
 ### Development of number of publishers in Finland 
+TODO: Voisko tämän ja seuraavan kuvan (ruotsalaiset julkaisijat) jotenkin yhdistää järkevästi selvyyden vuoksi? En valitettavasti tiedä miten se teknisesti tehtäisiin.
 
@@
 ### Number of publishers in Stockholm 1760-1770
-
+TODO: Tästä kaikki Fennica kuvat pois analyysistä selkeyden vuoksi.
 ```{r polev1, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=6, out.width="280px", fig.show="hold"}
@@
 
-### Different languages in Swedish University towns
-
+### Different languages in Turku, Stockholm and Uppsala
+TODO: Rajataan analyysi Turku (Fennica), Stockholm (Kungliga) ja Uppsala (Kungliga)
 ```{r language-perc2, echo=FALSE, message=FALSE, warning=FALSE, fig.width=20, fig.height=5}
@@
              pics[[6]], pics[[7]], pics[[8]], pics[[9]], pics[[10]], 
-             nrow = 3)
+             nrow = 2)
 ```
@@
 ### Topic diversity in different languages in Finnish publications
-TODO: TÄMÄ PITÄISI RAJATA LOPPUMAAN VUOTEEN 1828.
-LL: on rajattu jo mun nähdäkseni ?
 
@@
 ### Combining devotional literature and temporary sermons
+TODO: Voisko kokeilla tätä barplotteina selvyyden vuoksi?
 
@@
 
-##TODO: Dissertation language
+###TODO: Dissertation language
 
@@
 [University curriculum 1/5]
-
-TODO: OISKO NÄMÄ VIELÄ SELVEMPIÄ VÄRIKKÄINÄ BARPLOTTEINA?
 
@@
 
-TODO: KUVA PITÄIS RAJATA 1640-1828, EN ONNISTUNUT - DONE
+TODO: kuva rajattu 1640-1828, MUTTA piirtää silti tuonne nuo tyhjät vuodet 1470-1640. NE PITÄIS SAADA PRINTISTÄ POIS.
 
@@
 
-TODO: General analysis (any simple picture) of duplicates between Kungliga and Fennica based on Hege's deduplication code.
-
 ```{r duplicates, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=5, fig.width=10}

### 2016-07-07 inst/examples/20160715-slides-Krakow.Rmd
s

@@
 
+[Swedish Age of Freedom and Abolishment of Censorship TODO]
+
+### TODO 1766-1772
+
+Kungligan mukaan piirakkakuva prosentteina (tai joku vastaava, vaihtelun vuoksi) kuinka paljon enemmän Kungligassa julkaisujen lukumäärä ja paperinkulutus kasvaa kun sensuuri puuttuu vuosina 1766-1772 suhteessa tätä edeltävien (esim.
+kahden) vuosikymmenen kasvuun.
+Eli siis vuodet 1766-1772 ja kuinka paljon silloin on enemmän julkaisuja sensuurin puuttumisen takia tarkoituksena selvittää.
+Eli odotettu kasvu (kun katsotaan käyrää Kungligasta se on aika tasainen näiden vuosien ympärillä ylöspäin) ja todellinen kasvu (piikki) sekä niiden ero prosentteina.
+
+---
+
+### TODO 1766-1774
+
+Selvitettävä asia: onko erityisesti pamflettien kasvu syynä tänä aikana tulevaan nousuun?
+
+Tapa: Lasketaan Kungligan mukaan Tukholmassa nimikkeiden määrän ja paperinkulutuksen suhde vuosilta 1766-1774 ja verrataan sitä vuosiin 1757-1765 ja 1775-1783.
+Tämän pitäisi tapahtua niin että lasketaan näille kolmelle ajanjaksolle jokaiselle oma "nimikkeiden määrä jaettuna paperinkulutuksella määrä" -lukema joka laitetaan sitten esim.
+prosentuaaliseen piirakkakuvaan jossa on kolme palaa.
+Palojen koko määräytyy sen mukaan kuinka paljon enemmän kyseisenä aikana on nimikkeitä suhteessa paperinkulutukseen.
+
+---
+
 [Swedish Age of Freedom and Abolishment of Censorship 2/3]
@@
 ```
+---
+
+### TODO Kungliga subject topics (NEW!!)
+
+Tuotetaan samanlaiset asiasanaryppäät kuin University Curriculum Turku.
+Tämän jälkeen piirretään Kungligan pohjalta yliopisto-asiasanat aikajanalle samalla tavalla kuin Fennican kohdalla kaupunkikohtaisesti.
+
+TÄMÄ vie paljon enemmän tilaa kuin slideihin tulee jäämään. Täten, voi tuottaa kuvat kaksi per slide tai sitten vaihtoehtoisesti kässäriin josta blokataan tänne mitä tarvitaan.
+
+Kaupungit: "Tukholma", "Lund", "Greifswald", "Uppsala"
+
+Asiasanalista on seuraava (omat kuvat kaikista kaupunkikohtaisesti):
+
+1. Kyrkohistoria; Biblisk arkeologi;Exegetik;Homiletik;Dogmatik;Teologi; Praktisk Teologi; Teologisk etik
+
+2. Idé- och lärdomshistoria;Antiken;Historia;Militärhistoria;
+
+3. Filosofi;Metafysik;Logik
+
+4. Naturvetenskap;Matematik;Matematiska tabeller; Kemi;Astronomi;Geografi;Geologi;Meteorologi
+
+5. Retorik
+
+6. Hebreiska språket; Grekiska språket;Latin
+
+7.
+Politisk filosofi;Ekonomiska förhållanden; Nationalekonomi;Lantbruksekonomi;Ekonomi;Penningväsen;Penningvärde;Kreditväsen;Penningförfalskning;Moral;Pedagogik;Uppfsotringsverket;Uppfostran;Barnuppfostran;Jordbruk;Jordbrukslära;Jordbrukspolitik;Fiske
+
+8. Biologi;Medicinalverket;Medicin;Veterinärmedicin;Medicinalväsen;Medicinalväxkter;Sjukdomar;Djursjukdomar;Djur;Husdjur;Djurskydd;Hästar;Hästkreatur;Hästkörning;Hästavel
+
+9. Kvinnor;Kvinnliga textilarbetare;Gravida kvinnor;Adelskvinnor;Kvinnorollen;Ensamstående kvinnor
+
+10.
+Högmålsbrott;Skattebrott;Brott;Brottslingar;Äktenskapsbrott;Våldsbrott;Trafikbrott;Gäldenärsbrott;Sabbattsbrott;Sexualbrott;Fridsbrott;Ekonomisk brottslighet;Religionsbrott;Juridik;Straff;Dödsstraff;Kroppsstraff;Straffarbete;Straffarbete;Fängelsestraff
 

### 2016-07-07 inst/examples/20160715-slides-Krakow.Rmd
Rmd update

@@
 
-- Fennica (Finnish National Bibliography): 20328 documents
-
-- Kungliga (National Library of Sweden): 73165 documents
+- Fennica (Finnish National Bibliography): `r nrow(filter(df0, catalog == "Fennica" & publication_year >= 1470 & publication_year <= 1828))` documents
+
+- Kungliga (National Library of Sweden): `r nrow(filter(df0, catalog == "Kungliga" & publication_year >= 1470 & publication_year <= 1828))` documents
 
@@
 
-- Benefit no. 1: once the work has been done, the data is available for everyone to use and to enrich it. The ecosystem is constructed with even unforeseen changes in mind.
+- Benefit no. 1: once the work has been done, the data is available for everyone to use and to enrich. The generic data analytical ecosystem is designed with even unforeseen changes in mind.
 
@@
 ### Publishing activity in Turku
+
+Selitys puuttuville palloille: Kungligassa ei ole yhtään kaupunkia mainittuina vuosikymmeninä joille geokoordinaatit olisi tiedossa.
+Eli dataa ei ole.
+Ei siis palloja.
+Johtunee siitä että ESTC:n ja Fennican osalta näitä joskus aiemmin selviteltiin mutta Kungligan ruotsalaisille paikannimille ei ole haettu geokoordinaatteja eikä niitä juuri näköjään ole aiemmin käyttämissämme geokoordinaattiaineistoissa.
+Pitää joko vaihtaa takaisin Fennicaan tässä, tai toivoa että ehditään etsiä ja soveltaa ruotsalaisia geokoordinaattijuttuja ajoissa.
 
@@
 mapdata <- filter(df0, catalog == "Kungliga") %>%
+      #filter(!is.na(latitude) & !is.na(longitude)) %>%
       group_by(publication_decade, publication_place, latitude, longitude) %>%
@@
     dfw <- subset(mapdata, publication_decade == i) %>%
-    	   	       group_by(latitude, longitude, highlight) %>%
+    	     group_by(publication_place, latitude, longitude, highlight) %>%
 		       summarize(n = sum(size))
@@
       	  aes(x = longitude, y = latitude,
-	      size = 3*log10(1+n),
+	      size = 20*log10(1+n),
 	      color = highlight)) +
@@
 	  ggtitle(i) +
-	  scale_size(range = c(1, 15)) +
+	  scale_size(range = c(2, 15)) +
+	  theme(title = element_text(size = 20)) +
 	  scale_color_manual(values = c("black", "red"))	  
@@
 ### Peaks and drops – role of publishers and contingency
-TODO: Tuolla on yksi iso piikki Kungligassa (1760-1770) ja kaksi laskua Fennicassa (1700-1721) ja (1809-1828). Voisko ne HIGHLIGHTata jollain tyylikkäällä tavalla?
-
-```{r publishingovertime, echo=FALSE, message=FALSE, warning=FALSE, fig.width=6, fig.height=5}
+
+TODO: iso piikki Kungligassa (1760-1770) ja kaksi laskua Fennicassa (1700-1721) ja (1809-1828).
+Voisko ne HIGHLIGHTata jollain tyylikkäällä tavalla?
+Tai sit joku päivä voi kehitellä paneeleita tms.
+Lisäsäätö vie aikaa, pitäis vähän tutkiskella asiaa.
+
+```{r publishingovertime, echo=FALSE, message=FALSE, warning=FALSE, fig.width=6, fig.height=5, out.width="200px"}
 library(devtools)
-install_github("ropengov/gisfin")
-
-# https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/publishingovertime-1.png
+#install_github("ropengov/gisfin")
+library(gisfin)
 library(stringr)
@@
 df2 <- df0 %>% group_by(publication_decade, catalog) %>% summarise(n = n())
+df2$highlight <- rep(FALSE, nrow(df2))
+df2$highlight[df2$catalog == "Kungliga" &
+	      df2$publication_decade %in% c(1770, 1810)] <- TRUE
+df2$highlight[df2$catalog == "Fennica" &
+	      df2$publication_decade %in% c(1710, 1810)] <- TRUE	      
 p <- ggplot(df2, aes(x = publication_decade, y = n)) +
-     geom_line(aes(linetype = catalog)) +
-     geom_point(aes(shape = catalog), size = 3) +     
-     ylab("Title count (n)") + xlab("Publication year") #+  
+     geom_line(aes(linetype = catalog), color = "black") +
+     geom_point(aes(shape = catalog, color = highlight, size = highlight)) +
+     ylab("Title count (n)") + xlab("Publication year") +
+     scale_color_manual(values = c("darkgray", "black")) +
+     theme(legend.position = "none")
      # ggtitle("Overall publishing activity")
@@
 
-TODO: Tässä vois maalata ton octavo-kirjojen käyrän molemmista kuvista jollain kirkkaalla värillä (ei muuta).
+TODO: Tässä vois maalata octavo-kirjojen käyrän molemmista kuvista kirkkaalla värillä (ei muuta).
 ```{r LIBER-13, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=10, fig.height=8, fig.show="hold", out.width="150px"}
@@
   df2 <- filter(df2, gatherings %in% setdiff(names(which(table(df2$gatherings) >= 15)), "NA"))
-  p <- ggplot(df2, aes(y = paper.consumption.km2, x = publication_decade, shape = gatherings, linetype = gatherings))
+  df2$highlight <- rep("gray", nrow(df2))
+  df2$highlight[df2$gatherings == "8vo"] <- "darkgreen"
+
+  p <- ggplot(df2, aes(y = paper.consumption.km2,
+                       x = publication_decade,
+		       shape = gatherings,
+		       linetype = gatherings))		       
   p <- p + geom_point(size = 4)
-  p <- p + geom_smooth(method = "loess", size = 1, color = "black")
+  p <- p + geom_smooth(method = "loess", size = 1,
+         aes(color = highlight, fill = highlight))
+  p <- p + scale_color_manual(values = c("darkgreen", "darkgray"))
+  p <- p + scale_fill_manual(values = c("darkgreen", "darkgray"))  	 
   p <- p + ggtitle("Paper consumption in time by gatherings")
@@
   p <- p + ylab("Paper consumption (km2)")
-  p <- p + guides(linetype = guide_legend(keywidth = 5), shape = guide_legend(keywidth = 5))
+  p <- p + guides(linetype = guide_legend(keywidth = 5),
+       	          shape = guide_legend(keywidth = 5))
   p <- p + ggtitle(paste("Paper consumption\n(", catal, ")", sep = ""))
@@
 Proportions for title count, paper, and publishers
-TODO: OTHER julkaisijakenttä laittaa ton Turku-kuvan pieleen, "other" kategoria liian iso.
+TODO: OTHER julkaisijakenttä laittaa ton Turku-kuvan pieleen, "other" kategoria liian iso. LL: eli ohjeet mitä tehdään ?
 ```{r comparisons, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=20, fig.height=8}
@@
 
-### Development of number of publishers in Finland 
+### Publishers in Finland / Swedish University towns
+
 TODO: Voisko tämän ja seuraavan kuvan (ruotsalaiset julkaisijat) jotenkin yhdistää järkevästi selvyyden vuoksi? En valitettavasti tiedä miten se teknisesti tehtäisiin.
@@
        ggtitle("Unique publishers in top publication places (Finland/Fennica)")
-print(p)
-```
-
----
-
-[Publishers 3/6]
-
-### Development of number of publishers in Swedish University towns
-
-```{r publishers2-kungliga, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=7, fig.width=15}
-# https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/publishers2-kungliga-1.png
+p1 <- p
+
+# ----------------------
+
 df <- df0
@@
        ggtitle(paste("Unique publishers in selected publication places (", catalogue, ")"))
-print(p)
+p2 <- p
+
+grid.arrange(p1, p2, nrow = 2)
 ```
@@
 Eli odotettu kasvu (kun katsotaan käyrää Kungligasta se on aika tasainen näiden vuosien ympärillä ylöspäin) ja todellinen kasvu (piikki) sekä niiden ero prosentteina.
+
+LL: no ainakin data nyt tässä laskettuna kahdelle peräkkäiselle 6 vuoden jaksolle. Tehdään ensin analyysit jotka tarvitaan. Hiotaan kuvia lisää sitten kun ei tule enää muuten lisää kamaa.
+
+```{r peak, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
+# Select catalog
+df <- df0 %>% filter(catalog == "Kungliga")
+
+# Mark time periods
+df$period <- rep(NA, nrow(df))
+df$period[df$publication_year >= 1759 & df$publication_year <= 1765] <- 1
+df$period[df$publication_year >= 1766 & df$publication_year <= 1772] <- 2
+
+# Remove NA time periods
+df <- df %>% filter(!is.na(period))
+
+df <- df %>% group_by(period) %>%
+             summarise(n = n(),
+	     	   paper = sum(paper.consumption.km2, na.rm = TRUE))
+#df <- melt(df, "period")
+
+# TITLE COUNT
+p1 <- ggplot(df, aes(x = period, y = n)) +
+       geom_bar(stat = "identity", position = "stack") +
+       scale_x_discrete(labels = c("Period A", "Period B")) +
+       ggtitle("Title count")
+
+# PAPER
+p2 <- ggplot(df, aes(x = period, y = paper)) +
+       geom_bar(stat = "identity", position = "stack") +
+       scale_x_discrete(labels = c("Period A", "Period B")) +
+       ggtitle("Paper")
+
+grid.arrange(p1, p2, nrow = 1)
+```
 

### 2016-07-08 inst/examples/20160715-slides-Krakow.Rmd
d

@@
 
-- Fennica (Finnish National Bibliography): `r nrow(filter(df0, catalog == "Fennica" & publication_year >= 1470 & publication_year <= 1828))` documents
-
-- Kungliga (National Library of Sweden): `r nrow(filter(df0, catalog == "Kungliga" & publication_year >= 1470 & publication_year <= 1828))` documents
-
 ### Method
@@
 
-### Findings
-
-Enlightenment in Finland after "the rock bottom" of 1700-1721
+### Challenges: nationally delineated perspectives by using nationally collected materials
+
+We use nationally organized library catalogues produced by national memory organizations.
+The aim is to at least partly overcome a national gaze in the analysis.
+By focusing on The Finnish case and studying it both in the context of the Swedish realm and (later) in the Russian empire, we have the opportunity to see how knowledge production happened through a more complex network of cities.
+
+### Enlightenment in Finland after "the rock bottom" of 1700-1721
+
+Different roles of languages visible in topics addressed in different languages:
 
@@
 Ei siis palloja.
-Johtunee siitä että ESTC:n ja Fennican osalta näitä joskus aiemmin selviteltiin mutta Kungligan ruotsalaisille paikannimille ei ole haettu geokoordinaatteja eikä niitä juuri näköjään ole aiemmin käyttämissämme geokoordinaattiaineistoissa.
-Pitää joko vaihtaa takaisin Fennicaan tässä, tai toivoa että ehditään etsiä ja soveltaa ruotsalaisia geokoordinaattijuttuja ajoissa.
+MT: Voisiko tätä kuvaa muuttaa niin että tarkkaillaan vaan samoja yliopistokaupunkeja joita muutenkin otsikolla "Publishing activity in Swedish University Towns (based on Kungliga data)", eli haetaan koordinaatit näille mitä me pääasiassa tarkkaillaan: "Stockholm", "Uppsala", "Lund", "Greifswald", "Turku", "Tartu"?
+Sitten datana käyttäisi Kungligaa.
 
@@
 ### Peaks and drops – role of publishers and contingency
-
-TODO: iso piikki Kungligassa (1760-1770) ja kaksi laskua Fennicassa (1700-1721) ja (1809-1828).
-Voisko ne HIGHLIGHTata jollain tyylikkäällä tavalla?
-Tai sit joku päivä voi kehitellä paneeleita tms.
-Lisäsäätö vie aikaa, pitäis vähän tutkiskella asiaa.
 

### 2016-07-08 inst/examples/20160715-slides-Krakow.Rmd
e

@@
 
-TODO: Tässä vois maalata octavo-kirjojen käyrän molemmista kuvista kirkkaalla värillä (ei muuta).
 ```{r LIBER-13, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=10, fig.height=8, fig.show="hold", out.width="150px"}
@@
 ### Publishers in Finland / Swedish University towns
-
-TODO: Voisko tämän ja seuraavan kuvan (ruotsalaiset julkaisijat) jotenkin yhdistää järkevästi selvyyden vuoksi? En valitettavasti tiedä miten se teknisesti tehtäisiin.
+TODO: Todella tärkeä slide.
+Kehitysidea: voisiko nämä yhdistää yhteen ainoaan kaavioon niin että siinä olisi mukana valittuna pelkästään Fennicasta "Turku" ja "Vyborg" sekä Kungligasta "Stockholm", "Lund", "Uppsala", "Greifswald" ja "Tartu"?
+Näin ollen näkisi selvästi sitten erot ja kehityksen kun n on sama.
 
@@
 
-### Different languages in Turku, Stockholm and Uppsala
-TODO: Rajataan analyysi Turku (Fennica), Stockholm (Kungliga) ja Uppsala (Kungliga)
+### Different languages in Turku, Stockholm, Lund and Uppsala
+TODO: Rajataan analyysi Turku (Fennican pohjalta), Stockholm (Kungligan pohjalta), Lund (Kungligan pohjalta) ja Uppsala (Kungligan pohjalta)
 ```{r language-perc2, echo=FALSE, message=FALSE, warning=FALSE, fig.width=20, fig.height=5}

### 2016-07-08 inst/examples/20160715-slides-Krakow.Rmd
d

@@
 
-Selitys puuttuville palloille: Kungligassa ei ole yhtään kaupunkia mainittuina vuosikymmeninä joille geokoordinaatit olisi tiedossa.
-Eli dataa ei ole.
-Ei siis palloja.
-MT: Voisiko tätä kuvaa muuttaa niin että tarkkaillaan vaan samoja yliopistokaupunkeja joita muutenkin otsikolla "Publishing activity in Swedish University Towns (based on Kungliga data)", eli haetaan koordinaatit näille mitä me pääasiassa tarkkaillaan: "Stockholm", "Uppsala", "Lund", "Greifswald", "Turku", "Tartu"?
+TODO MT: Voisiko tätä kuvaa muuttaa niin että tarkkaillaan vain samoja yliopistokaupunkeja joita muutenkin otsikolla "Publishing activity in Swedish University Towns (based on Kungliga data)", eli haetaan koordinaatit näille: "Stockholm", "Uppsala", "Lund", "Greifswald", "Turku", "Tartu"?
 Sitten datana käyttäisi Kungligaa.
 
-Voi miettiä, jos tämä korvaisi alla tulevan "Comparing publishing activity in Swedish University town".
+Turussa kirjantuotanto laskee huomattavasti isonvihan (1710-luku) , pikkuvihan (1740-luku) ja Suomen sodan (1808-1809) aikana.
+Pikkuviha ei ollut yhtä dramaattinen, eikä näy niin totaalisesti.
+Suomen sodan (ja Napoleonin sotien) seuraukset olivat tietysti kaikkein dramaattisimmat.
 
@@
 ### Peaks and drops – role of publishers and contingency
+TODO: Tässä olisi hyvä olla vuodet näkyvissä.
 
@@
 ### Comparing publishing activity in Swedish University towns
+TODO: Tässä olisi hyvä olla vuodet näkyvissä.
 
@@
 ### Comparing paper used on average per publication by publishers
+TODO: Mikä toi Sverige on? Pitäisikö toi tarkastaa, ettei siinä ole joku virhe. Jani ei ole koskaan törmännyt siihen kustantajana.
 
@@
 
-Publisher title count changes around 1700 with a nearly detrimental drop in Turku, the most significant publishing place at the time.
+Publisher title count changes around 1700 with a nearly detrimental drop in Turku, significant publishing place in Finland at the time.
 
@@
 df <- df0
-langs <- c("Finnish", "Swedish", "Latin", "German", "Russian", "French", "Greek, Ancient (to 1453)", "Other")
+langs <- c("Finnish", "Swedish", "Latin", "German", "Russian", "French", "Other")
 lang <- paste("language.", langs, sep = "")
@@
 Analyysi vuosikymmenittäin ja kielen mukaan eri väreillä.
-Kielien joukko:
+Kielien joukko: "Finnish", "Swedish", "Latin", "German", "Russian", "French", "Hebrew", "Other"
 

### 2016-07-08 inst/examples/20160715-slides-Krakow.Rmd
s

@@
 Proportions for title count, paper, and publishers
-TODO: OTHER julkaisijakenttä laittaa ton Turku-kuvan pieleen, "other" kategoria liian iso. LL: eli ohjeet mitä tehdään ?
+TODO: OTHER julkaisijakenttä laittaa ton Turku-kuvan pieleen, "other" kategoria liian iso. LL: eli ohjeet mitä tehdään ? MT: Pudotetaan publishers kaaviot pois tästä. 
 ```{r comparisons, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=20, fig.height=8}
@@
 
-Kungligan mukaan piirakkakuva prosentteina (tai joku vastaava, vaihtelun vuoksi) kuinka paljon enemmän Kungligassa julkaisujen lukumäärä ja paperinkulutus kasvaa kun sensuuri puuttuu vuosina 1766-1772 suhteessa tätä edeltävien (esim.
+Kungligan mukaan kuinka paljon enemmän Kungligassa julkaisujen lukumäärä ja paperinkulutus kasvaa kun sensuuri puuttuu vuosina 1766-1772 suhteessa tätä edeltävien (esim.
 kahden) vuosikymmenen kasvuun.
@@
 
-LL: no ainakin data nyt tässä laskettuna kahdelle peräkkäiselle 6 vuoden jaksolle. Tehdään ensin analyysit jotka tarvitaan. Hiotaan kuvia lisää sitten kun ei tule enää muuten lisää kamaa.
+LL: no ainakin data nyt tässä laskettuna kahdelle peräkkäiselle 6 vuoden jaksolle.
+Tehdään ensin analyysit jotka tarvitaan.
+Hiotaan kuvia lisää sitten kun ei tule enää muuten lisää kamaa.
+MT: TÄMÄ ON HYVÄ!
 

### 2016-07-08 inst/examples/20160715-slides-Krakow.Rmd
s

@@
 
+### TODO-lista
+
+1) Sivu 6. Karttakuva, geokoordinaatit (löytyy kalvolta) lisääminen + kartan muodostaminen Kungligan pohjalta mainittuihin kuuteen kaupunkiin paitsi Turku jonka data otetaan Fennicasta.
+
+2) Sivu 12. Kuva 1 ja Kuva 2 yhdistäminen samaan Kungliga kaavioon. Eli, Fennica kuvasta siirretään "Turku", "Vaasa" ja "Vyborg" Kungliga kuvaan. Muut tiedot Fennicasta jätetään pois.
+
+3) Sivu 20. Uusi kuva: asiasanoja / yliopistopaikkakunta vertailu Kungligasta.
+
+4) Sivu 18. Uusi kuva: Kungligasta nimikkeiden määrän ja paperinkulutuksen suhde vuosilta 1766-1774 ja verrataan sitä vuosiin 1757-1765 ja 1775-1783.
+
+5) Sivu 32. Uusi kuva: Yleinen kielianalyysi prosentteina Fennican väitöskirjoista (pitäisi olla suoraviivainen).
+
+6) Sivu 39. Uusi kuva: Kungliga subject topics, kalvossa olevien asiasanaryppäiden pohjalta samanlainen analyysi Kungligan yliopistokaupungeista kuin on tehty nyt Fennicasta.
+
+7) Sivu 11. Viilaus: Publisher kaaviot pudotetaan pois (Fennica ja Kungliga), title count ja paper consumption jää kalvolle.
+
+8) Sivu 25. Viilaus: Analyysin rajaaminen neljään kuvaan kymmenen sijasta.
+
+9) Sivu 30. Viilaus: Viivojen vaihtaminen barplotteihin.
+
+10) Sivu 19. Viilaus: Fennica kuvien pudottaminen pois kalvolta.
+
+11) Sivu 7. Kuva 1. Viilaus: vuosiluvut näkyviin.
+
+12) Sivu 8. Kuva 1. Viilaus: vuosiluvut näkyviin.
+
+13) Sivu 38. vuosien viilaus kuvassa.
+
+14) Sivu 16. Gävlen muuttaminen takaisin analyysiin.
+
+15) Sivu 14. Kuva 1. Sverige julkaisijanimen tarkastaminen.
+
+---
+
 ## From particular data to global perspective?
@@
 
-TODO MT: Voisiko tätä kuvaa muuttaa niin että tarkkaillaan vain samoja yliopistokaupunkeja joita muutenkin otsikolla "Publishing activity in Swedish University Towns (based on Kungliga data)", eli haetaan koordinaatit näille: "Stockholm", "Uppsala", "Lund", "Greifswald", "Turku", "Tartu"?
-Sitten datana käyttäisi Kungligaa.
+TODO: Muutetaan niin että tarkkaillaan vain samoja yliopistokaupunkeja joita muutenkin otsikolla "Publishing activity in Swedish University Towns (based on Kungliga data)", eli lisätään koordinaatit näille: "Stockholm" (59.3251172 / 18.0710935), "Uppsala" (59.8588200 / 17.6388900), "Lund" (55.7058400 / 13.1932100), "Greifswald" (54.0931100 / 13.3878600), "Turku" (60.4517531 / 22.2670522), "Tartu" (58.3806200 / 26.7250900)?
+Sitten datana käytetään Kungligaa.
+Paitsi "Turku" jossa data pitäisi ottaa Fennicasta.
 
@@
 ### Publishers in Finland / Swedish University towns
-TODO: Todella tärkeä slide.
-Kehitysidea: voisiko nämä yhdistää yhteen ainoaan kaavioon niin että siinä olisi mukana valittuna pelkästään Fennicasta "Turku" ja "Vyborg" sekä Kungligasta "Stockholm", "Lund", "Uppsala", "Greifswald" ja "Tartu"?
+TODO: voisiko nämä yhdistää yhteen ainoaan kaavioon niin että siinä olisi mukana valittuna pelkästään Fennicasta "Turku", "Vaasa" ja "Vyborg" ja Kungligasta kaikki mitä siellä nytkin on eli "Stockholm", "Lund", "Uppsala", "Greifswald" ja "Tartu"?
+Ts.
+kolme kaupungin arvot siirretään Kungliga kuvaan joka pysyy muuten samana kuin nyt.
 Näin ollen näkisi selvästi sitten erot ja kehityksen kun n on sama.
@@
 
-[Swedish Age of Freedom and Abolishment of Censorship TODO]
-
-### TODO 1766-1772
-
-Kungligan mukaan kuinka paljon enemmän Kungligassa julkaisujen lukumäärä ja paperinkulutus kasvaa kun sensuuri puuttuu vuosina 1766-1772 suhteessa tätä edeltävien (esim.
-kahden) vuosikymmenen kasvuun.
-Eli siis vuodet 1766-1772 ja kuinka paljon silloin on enemmän julkaisuja sensuurin puuttumisen takia tarkoituksena selvittää.
-Eli odotettu kasvu (kun katsotaan käyrää Kungligasta se on aika tasainen näiden vuosien ympärillä ylöspäin) ja todellinen kasvu (piikki) sekä niiden ero prosentteina.
-
-LL: no ainakin data nyt tässä laskettuna kahdelle peräkkäiselle 6 vuoden jaksolle.
-Tehdään ensin analyysit jotka tarvitaan.
-Hiotaan kuvia lisää sitten kun ei tule enää muuten lisää kamaa.
-MT: TÄMÄ ON HYVÄ!
+[Swedish Age of Freedom and Abolishment of Censorship]
+
+### 1766-1772 Title count vs. paper consumption (Kungliga)
+
+Kungligan mukaan kuinka paljon enemmän Kungligassa julkaisujen lukumäärä ja paperinkulutus kasvaa kun sensuuri puuttuu vuosina 1766-1772 suhteessa tätä edeltävään kuuteen vuoteen.
 
@@
 
-###TODO: asiasanoja / yliopistopaikkakunta vertailu.
+###TODO: asiasanoja / yliopistopaikkakunta vertailu Kungligasta.
 Ts.
@@
 Voidaan suhteuttaa myös esim.
-paperinkulutukseen.
-Greifswald vs Turku (kuinka monta kieltä per vuosi) oli samansuuntainen.
+paperinkulutukseen tai julkaisujen määrään.
+Tarkkailtavat paikkakunnat: "Stockholm", "Uppsala", "Lund", "Greifswald", "Tartu" ja "Turku".
+Aikaisammin piirretty Greifswald vs Turku (kuinka monta kieltä per vuosi) oli samansuuntainen analyysi.
 
@@
 ### Languages
-
-TODO: "Other" kielikategorian selvittäminen seuraavissa kuvissa.
-Onko siellä joku tietty kieli joka näkyy hyvin selvästi mukana analyysissä?
-Nousee isoksi kategoriaksi.
-Nyt oon merkannut, että Kreikan kieli (Greek - huom on kielet Greek, Modern (1453-) sekä Greek, Ancient (to 1453) mutta ei pelkka Greek) mukaan moneen kohtaan.
-Jos kyseessä joku muu kuin Kreikka niin sitten se.
-Jos taas paljon kombinaatioita pieniä kieliä, niin antaa siinä tapauksessa olla.
-LL: Lisäsin Kreikan mutten muuten ehdi tutkia asiaa.
-Voit katsoa R:llä top(df0, "language", 10)
 
@@
 
-TODO: kuva rajattu 1640-1828, MUTTA piirtää silti tuonne nuo tyhjät vuodet 1470-1640. NE PITÄIS SAADA PRINTISTÄ POIS.
+kuva rajattu 1640-1828, MUTTA piirtää silti tuonne nuo tyhjät vuodet 1470-1640. NE PITÄIS SAADA PRINTISTÄ POIS.
 
@@
 
-Kaupungit: "Tukholma", "Lund", "Greifswald", "Uppsala"
+Kaupungit: "Tukholma", "Lund", "Greifswald", "Uppsala", "Tartu"
 

### 2016-07-08 inst/examples/20160715-slides-Krakow.Rmd
xs

@@
 
-13) Sivu 38. vuosien viilaus kuvassa.
-
-14) Sivu 16. Gävlen muuttaminen takaisin analyysiin.
-
-15) Sivu 14. Kuva 1. Sverige julkaisijanimen tarkastaminen.
+13) Sivu 16. Gävlen muuttaminen takaisin analyysiin.
+
+14) Sivu 14. Kuva 1. Sverige julkaisijanimen tarkastaminen.
 
@@
 
---> Deep roots of the diversity of "Finnishness" reflected in knowledge production, 1640-1828.
+--> Visible roots of the diversity of "Finnishness" reflected in knowledge production, 1640-1828.
 
@@
 ### Rise of the octavo sized book as vehicle of Enlightenment
-
+TÄSSÄ kanssa vuodet näkyviin.
 Paper consumption for different document formats over time.
@@
 
-kuva rajattu 1640-1828, MUTTA piirtää silti tuonne nuo tyhjät vuodet 1470-1640. NE PITÄIS SAADA PRINTISTÄ POIS.
-
 ```{r authors22, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5, out.width="150px", fig.show="hold"}
@@
         filter(publication_year >= 1640 & publication_year <= 1828)
-  top.authors <- names(top(df, field = "author", n = 10))
+  top.authors <- names(bibliographica::top(df, field = "author", n = 10))
   dfs <- df %>% filter(author %in% top.authors) %>%
@@
        ggtitle(paste("Title count top authors\n", catalogue)) +
-       xlim(range(df0$publication_year))
+       xlim(c(1640, 1828))
   print(p)

### 2016-07-08 inst/examples/20160715-slides-Krakow.Rmd
z

@@
 
-7) Sivu 11. Viilaus: Publisher kaaviot pudotetaan pois (Fennica ja Kungliga), title count ja paper consumption jää kalvolle.
-
-8) Sivu 25. Viilaus: Analyysin rajaaminen neljään kuvaan kymmenen sijasta.
-
-9) Sivu 30. Viilaus: Viivojen vaihtaminen barplotteihin.
-
-10) Sivu 19. Viilaus: Fennica kuvien pudottaminen pois kalvolta.
-
-11) Sivu 7. Kuva 1. Viilaus: vuosiluvut näkyviin.
-
-12) Sivu 8. Kuva 1. Viilaus: vuosiluvut näkyviin.
-
-13) Sivu 16. Gävlen muuttaminen takaisin analyysiin.
-
-14) Sivu 14. Kuva 1. Sverige julkaisijanimen tarkastaminen.
+7) Sivu 30. Viilaus: Viivojen vaihtaminen barplotteihin.
+
+8) Sivu 19. Viilaus: Fennica kuvien pudottaminen pois kalvolta.
+
+9) Sivu 7. Kuva 1. Viilaus: vuosiluvut näkyviin.
+
+10) Sivu 8. Kuva 1. Viilaus: vuosiluvut näkyviin.
+
+11) Sivu 16. Gävlen muuttaminen takaisin analyysiin.
+
+12) Sivu 14. Kuva 1. Sverige julkaisijanimen tarkastaminen.
 
@@
 
-### TODO Turku in Sweden
-
-Proportions for title count, paper, and publishers
-TODO: OTHER julkaisijakenttä laittaa ton Turku-kuvan pieleen, "other" kategoria liian iso. LL: eli ohjeet mitä tehdään ? MT: Pudotetaan publishers kaaviot pois tästä. 
+### Turku in Sweden: proportions for title count and paper in Swedish University towns
+
 ```{r comparisons, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=20, fig.height=8}
@@
 library(gridExtra)
-grid.arrange(pics[[1]], pics[[2]], pics[[3]], pics[[4]], pics[[5]], pics[[6]], nrow = 2)
+#grid.arrange(pics[[1]], pics[[2]], pics[[3]], pics[[4]], pics[[5]], pics[[6]], nrow = 2)
+grid.arrange(pics[[1]], pics[[2]], pics[[4]], pics[[5]], nrow = 2)
 ```
@@
 ### Different languages in Turku, Stockholm, Lund and Uppsala
-TODO: Rajataan analyysi Turku (Fennican pohjalta), Stockholm (Kungligan pohjalta), Lund (Kungligan pohjalta) ja Uppsala (Kungligan pohjalta)
+
 ```{r language-perc2, echo=FALSE, message=FALSE, warning=FALSE, fig.width=20, fig.height=5}
@@
 
-grid.arrange(pics[[1]], pics[[2]], pics[[3]], pics[[4]], pics[[5]],
-             pics[[6]], pics[[7]], pics[[8]], pics[[9]], pics[[10]], 
+grid.arrange(pics[[1]],
+             pics[[8]], pics[[9]], pics[[10]], 
              nrow = 2)
+#grid.arrange(pics[[1]], pics[[2]], pics[[3]], pics[[4]], pics[[5]],
+             #pics[[6]], pics[[7]], pics[[8]], pics[[9]], pics[[10]], 
+            # nrow = 2)
 ```
@@
 
+R master (plots & maps): Leo Lahti.
+
+Institutional support:
+
 - Academy of Finland
 - University of Helsinki
+- Digitalia / The Regional Council of South Savo
+
+Data providers:
+
 - National Library of Finland
 - National Library of Sweden
-- Digitalia / The Regional Council of South Savo

### 2016-07-08 inst/examples/20160715-slides-Krakow.Rmd
s

@@
 
-8) Sivu 19. Viilaus: Fennica kuvien pudottaminen pois kalvolta.
-
-9) Sivu 7. Kuva 1. Viilaus: vuosiluvut näkyviin.
-
-10) Sivu 8. Kuva 1. Viilaus: vuosiluvut näkyviin.
-
-11) Sivu 16. Gävlen muuttaminen takaisin analyysiin.
-
-12) Sivu 14. Kuva 1. Sverige julkaisijanimen tarkastaminen.
+8) [Lokaali ongelma Mikolla? näkyy R-studion konsolissa oikein, mutta ei knitatussa PDF:ssä] Sivu 7. Kuva 1. Viilaus: vuosiluvut näkyviin.
+
+9) [Lokaali ongelma Mikolla? näkyy R-studion konsolissa oikein, mutta ei knitatussa PDF:ssä] Sivu 8. Kuva 1. Viilaus: vuosiluvut näkyviin.
+
+10) Sivu 16. Gävlen muuttaminen takaisin analyysiin.
+
+11) Sivu 14. Kuva 1. Sverige julkaisijanimen tarkastaminen.
 
@@
 ### Number of publishers in Stockholm 1760-1770
-TODO: Tästä kaikki Fennica kuvat pois analyysistä selkeyden vuoksi.
+
 ```{r polev1, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=6, out.width="280px", fig.show="hold"}
@@
 }
-grid.arrange(pics[[1]], pics[[2]], pics[[3]], pics[[4]], pics[[5]],
-             pics[[6]], pics[[7]], pics[[8]], pics[[9]], pics[[10]], nrow = 2)
+#grid.arrange(pics[[1]], pics[[2]], pics[[3]], pics[[4]], pics[[5]],
+             #pics[[6]], pics[[7]], pics[[8]], pics[[9]], pics[[10]], nrow = 2)
+grid.arrange(pics[[2]], pics[[4]],
+             pics[[6]], pics[[8]], pics[[10]], nrow = 2)
 ```

### 2016-07-08 inst/examples/20160715-slides-Krakow.Rmd
l

@@
 ### TODO-lista
+
+1) Sivut 38-39. Auktori piikki. 1650-luvulla, miksi?
 
@@
 
-```{r comparisons, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=20, fig.height=8}
+```{r comparisons, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=20, fig.height=15}
 pics <- list()
@@
 
-```{r language-perc2, echo=FALSE, message=FALSE, warning=FALSE, fig.width=20, fig.height=5}
+```{r language-perc2, echo=FALSE, message=FALSE, warning=FALSE, fig.width=20, fig.height=15}
 pics <- list()
@@
 - The Enlightenment literature read in Finland mainly printed elsewhere
+
+Tässä on aika jännä piikki 1650 luvun Fennican top-auktorit.
+Eli toi Kalm, Pehr ja joku toinen.
+Onhan varmasti niin että tässä ei saattaisi tulla laskuihin mukaan näille tyypeille sekä Fennica että Kungliga?
+Kyseessä sivut 38-39 slideistä.
+Tollanen 200 väitöskirjaa per 10 vuotta on kyllä todella iso myös suhteessa muihin noista professoreista jotka päässeet tälle top-listalle.
+Mä siis muuttelin tätä kuvaa, siihen tuli se Bibliographica-top.
+Ettei vaan se jotenkin sotkis tätä niin että nyt ottaa kaikista bibliographica-kansioista tohon yhteen Kalmit?
+Tai jotain vastaavaa.
 

### 2016-07-08 inst/examples/20160715-slides-Krakow.Rmd
s

@@
        geom_bar(stat = "identity", position = "stack") +
-       scale_x_discrete(labels = c("Period A", "Period B")) +
-       ggtitle("Title count")
+       scale_x_discrete(labels = c("1759-1765", "1766-1772")) +
+       ggtitle("Title count") + xlab("1759-1765")
 
@@
        geom_bar(stat = "identity", position = "stack") +
-       scale_x_discrete(labels = c("Period A", "Period B")) +
-       ggtitle("Paper")
+       scale_x_discrete(labels = c("1759-1765", "1766-1772")) +
+       ggtitle("Paper consumption") + xlab("1766-1772")
 

### 2016-07-09 inst/examples/20160715-slides-Krakow.Rmd
z

--- 2016-07-08 inst/examples/20160715-slides-Krakow.Rmd
@@
        geom_bar(stat = "identity", position = "stack") +
-       scale_x_discrete(labels = c("Period A", "Period B")) +
-       ggtitle("Title count")
+       scale_x_discrete(labels = c("1759-1765", "1766-1772")) +
+       ggtitle("Title count") + xlab("1759-1765 / 1766-1772")
 
@@
        geom_bar(stat = "identity", position = "stack") +
-       scale_x_discrete(labels = c("Period A", "Period B")) +
-       ggtitle("Paper")
+       scale_x_discrete(labels = c("1759-1765", "1766-1772")) +
+       ggtitle("Paper consumption") + xlab("1759-1765 / 1766-1772")
 

### 2016-07-09 inst/examples/20160715-slides-Krakow.Rmd
Rmd update

--- 2016-07-08 inst/examples/20160715-slides-Krakow.Rmd
@@
 library(sorvi)
+library(devtools)
+#install_github("ropengov/gisfin")
+library(gisfin)
 
@@
 
-1) Sivut 38-39. Auktori piikki. 1650-luvulla, miksi?
+1) DONE Sivut 38-39. Auktori piikki. 1650-luvulla, miksi?
 
@@
 
-2) Sivu 12. Kuva 1 ja Kuva 2 yhdistäminen samaan Kungliga kaavioon. Eli, Fennica kuvasta siirretään "Turku", "Vaasa" ja "Vyborg" Kungliga kuvaan. Muut tiedot Fennicasta jätetään pois.
-
-3) Sivu 20. Uusi kuva: asiasanoja / yliopistopaikkakunta vertailu Kungligasta.
-
-4) Sivu 18. Uusi kuva: Kungligasta nimikkeiden määrän ja paperinkulutuksen suhde vuosilta 1766-1774 ja verrataan sitä vuosiin 1757-1765 ja 1775-1783.
-
-5) Sivu 32. Uusi kuva: Yleinen kielianalyysi prosentteina Fennican väitöskirjoista (pitäisi olla suoraviivainen).
-
-6) Sivu 39. Uusi kuva: Kungliga subject topics, kalvossa olevien asiasanaryppäiden pohjalta samanlainen analyysi Kungligan yliopistokaupungeista kuin on tehty nyt Fennicasta.
-
-7) Sivu 30. Viilaus: Viivojen vaihtaminen barplotteihin.
-
-8) [Lokaali ongelma Mikolla? näkyy R-studion konsolissa oikein, mutta ei knitatussa PDF:ssä] Sivu 7. Kuva 1. Viilaus: vuosiluvut näkyviin.
-
-9) [Lokaali ongelma Mikolla? näkyy R-studion konsolissa oikein, mutta ei knitatussa PDF:ssä] Sivu 8. Kuva 1. Viilaus: vuosiluvut näkyviin.
+2) OK Sivu 12. Kuva 1 ja Kuva 2 yhdistäminen samaan Kungliga kaavioon. Eli, Fennica kuvasta siirretään "Turku", "Vaasa" ja "Vyborg" Kungliga kuvaan. Muut tiedot Fennicasta jätetään pois.
+
+3) OK Sivu 20. Uusi kuva: asiasanoja / yliopistopaikkakunta vertailu Kungligasta.
+
+4) OK Sivu 18. Uusi kuva: Kungligasta nimikkeiden määrän ja paperinkulutuksen suhde vuosilta 1766-1774 ja verrataan sitä vuosiin 1757-1765 ja 1775-1783.
+
+5) OK Sivu 32. Uusi kuva: Yleinen kielianalyysi prosentteina Fennican väitöskirjoista (pitäisi olla suoraviivainen).
+
+6) OK Sivu 39. Uusi kuva: Kungliga subject topics, kalvossa olevien asiasanaryppäiden pohjalta samanlainen analyysi Kungligan yliopistokaupungeista kuin on tehty nyt Fennicasta.
+
+7) OK Sivu 30. Viilaus: Viivojen vaihtaminen barplotteihin.
+
+8) OK [Lokaali ongelma Mikolla? näkyy R-studion konsolissa oikein, mutta ei knitatussa PDF:ssä] Sivu 7. Kuva 1. Viilaus: vuosiluvut näkyviin.
+
+9) OK [Lokaali ongelma Mikolla? näkyy R-studion konsolissa oikein, mutta ei knitatussa PDF:ssä] Sivu 8. Kuva 1. Viilaus: vuosiluvut näkyviin.
 
@@
 ```{r publishingovertime, echo=FALSE, message=FALSE, warning=FALSE, fig.width=6, fig.height=5, out.width="200px"}
-library(devtools)
-#install_github("ropengov/gisfin")
-library(gisfin)
-library(stringr)
-library(dplyr)
-library(tidyr)
-library(reshape2)
-library(ggplot2)
-library(bibliographica)
-library(fennica)
-library(sorvi)
-
-df2 <- df0 %>% group_by(publication_decade, catalog) %>% summarise(n = n())
+df2 <- df0 %>% group_by(publication_decade, catalog) %>%
+               summarise(n = n())
 df2$highlight <- rep(FALSE, nrow(df2))
@@
 	      df2$publication_decade %in% c(1710, 1810)] <- TRUE
+v <- seq(1500, 1800, 50)	      
 p <- ggplot(df2, aes(x = publication_decade, y = n)) +
@@
      scale_color_manual(values = c("darkgray", "black")) +
-     theme(legend.position = "none")
+     theme(legend.position = "none") +
+     scale_x_continuous(breaks = v, labels = v)
      # ggtitle("Overall publishing activity")
@@
 ```{r publishingactivitycomparisons, echo=FALSE, message=FALSE, cache=FALSE, fig.width=6, fig.height=5, fig.show="hold", out.width="150px"}
-#https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/publishingactivitycomparisons-2.png
 selected.places = c("Turku", "Uppsala", "Lund", "Stockholm")
@@
      ylab("Title count (n)") + xlab("Publication year") +  
-     ggtitle(catal)
+     ggtitle(catal) +
+     scale_x_continuous(breaks = v, labels = v)     
   print(p)
@@
 ### Publishers in Finland / Swedish University towns
-TODO: voisiko nämä yhdistää yhteen ainoaan kaavioon niin että siinä olisi mukana valittuna pelkästään Fennicasta "Turku", "Vaasa" ja "Vyborg" ja Kungligasta kaikki mitä siellä nytkin on eli "Stockholm", "Lund", "Uppsala", "Greifswald" ja "Tartu"?
-Ts.
-kolme kaupungin arvot siirretään Kungliga kuvaan joka pysyy muuten samana kuin nyt.
-Näin ollen näkisi selvästi sitten erot ja kehityksen kun n on sama.
+
+TODO: yhdistä yhteen ainoaan kaavioon, mukana Fennicasta "Turku", "Vaasa" ja "Vyborg" ja Kungligasta kaikki eli "Stockholm", "Lund", "Uppsala", "Greifswald" ja "Tartu"?
 
 ```{r publishers2-finland, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=7, fig.width=15}
-# https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/publishers2-finland-1.png
 df <- df0
@@
 # Top publication places
-ntop <- 10
 library(bibliographica)
-top <- names(top(df, "publication_place", ntop))
-
+
+top <- c("Turku", "Vaasa", "Vyborg")
 df <- df %>%	
@@
 npub$publication_place <- factor(npub$publication_place, levels = top)
-theme_set(theme_bw(20))
-
-p <- ggplot(npub, aes(x = publication_decade, y = n)) +
-       geom_bar(stat = "identity", position = "stack", aes(fill = publication_place)) + 
-       xlab("Publication year") +
-       ylab("Unique publishers (n)") +        
-       ggtitle("Unique publishers in top publication places (Finland/Fennica)")
-p1 <- p
-
-# ----------------------
+npub.fennica <- npub
 
@@
 # Selected publication places
-top <- c("Stockholm", "Lund", "Uppsala", "Greifswald")
+top <- c("Stockholm", "Lund", "Uppsala", "Greifswald", "Tartu")
 df <- df %>%	
@@
 npub$publication_place <- factor(npub$publication_place, levels = top)
-theme_set(theme_bw(20))
-
+npub.kungliga <- npub
+
+npub <- bind_rows(npub.fennica, npub.kungliga)
+
+# Order by total publishing activity
+npub$publication_place <- factor(npub$publication_place, levels = (npub %>% group_by(publication_place) %>% summarise(total = sum(n)) %>% arrange(desc(total)))$publication_place)
+npub <- npub %>% arrange(publication_place)
+
+theme_set(theme_bw(20))
 p <- ggplot(npub, aes(x = publication_decade, y = n)) +
-       geom_bar(stat = "identity", position = "stack", aes(fill = publication_place)) + 
+       geom_bar(stat = "identity", position = "stack",
+       		    aes(fill = publication_place)) + 
        xlab("Publication year") +
@@
        ggtitle(paste("Unique publishers in selected publication places (", catalogue, ")"))
-p2 <- p
-
-grid.arrange(p1, p2, nrow = 2)
+
+print(p)
 ```
@@
 ```{r riksdar2, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
-# https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/riksdar2-1.png
-
   # Use timeinterval year intervals
@@
 
-Tapa: Lasketaan Kungligan mukaan Tukholmassa nimikkeiden määrän ja paperinkulutuksen suhde vuosilta 1766-1774 ja verrataan sitä vuosiin 1757-1765 ja 1775-1783.
-Tämän pitäisi tapahtua niin että lasketaan näille kolmelle ajanjaksolle jokaiselle oma "nimikkeiden määrä jaettuna paperinkulutuksella määrä" -lukema joka laitetaan sitten esim.
-prosentuaaliseen piirakkakuvaan jossa on kolme palaa.
-Palojen koko määräytyy sen mukaan kuinka paljon enemmän kyseisenä aikana on nimikkeitä suhteessa paperinkulutukseen.
-
+Kungliga. Paper per title 1766-1774; 1757-1765; 1775-1783.
+
+```{r pamflets1, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=6, out.width="280px", fig.show="hold"}
+df <- df0 %>%
+        filter(catalog == "Kungliga")
+
+# Add indicator of the publication period
+df$period <- cut(df$publication_year,
+	         breaks = c(1757, 1766, 1775, 1783),
+		 include.lowest = TRUE,
+		 right = FALSE
+		 )
+
+# Remove entries outside the investigated publication periods
+df <- df %>% filter(!is.na(period)) %>%
+	     group_by(period) %>%
+	     summarise(n = n(),
+		  paper = sum(paper.consumption.km2, na.rm = TRUE)) %>%
+        mutate(paper.per.title = paper/n)
+
+p <- ggplot(df,
+       aes(x = period, y = paper.per.title)) + 
+       geom_bar(stat = "identity") +
+       scale_x_discrete(labels = c("1757-1765", "1766-1774", "1775-1783")) +
+       ylab("Paper per title") + xlab("") 
+print(p)
+
+```
 ---
@@
 
-###TODO: asiasanoja / yliopistopaikkakunta vertailu Kungligasta.
-Ts.
-mitä enemmän eri aikoina asiasanoja (ihan sama mitä ne on) paikkakunnalla, sitä monimuotoisempaa/rikkaampaa julkaisutoiminta (eli kaikki julkaisut eivät samasta aiheesta, esim.
-oikeuspöytäkirjoissa ei varmaan hirveästi vaihtelua).
-Voidaan suhteuttaa myös esim.
-paperinkulutukseen tai julkaisujen määrään.
-Tarkkailtavat paikkakunnat: "Stockholm", "Uppsala", "Lund", "Greifswald", "Tartu" ja "Turku".
-Aikaisammin piirretty Greifswald vs Turku (kuinka monta kieltä per vuosi) oli samansuuntainen analyysi.
+TODO: asiasanoja / yliopistopaikkakunta vertailu Kungligasta. Ts. mitä
+enemmän eri aikoina asiasanoja (ihan sama mitä ne on) paikkakunnalla,
+sitä monimuotoisempaa/rikkaampaa julkaisutoiminta (eli kaikki
+julkaisut eivät samasta aiheesta, esim. oikeuspöytäkirjoissa ei
+varmaan hirveästi vaihtelua). Voidaan suhteuttaa myös
+esim. paperinkulutukseen tai julkaisujen määrään. Tarkkailtavat
+paikkakunnat: "Stockholm", "Uppsala", "Lund", "Greifswald", "Tartu" ja
+"Turku". Aikaisammin piirretty Greifswald vs Turku (kuinka monta
+kieltä per vuosi) oli samansuuntainen analyysi.
+
+```{r subtop1, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=6}
+selected.places <- c("Stockholm", "Uppsala",
+		     "Lund", "Greifswald",
+                     "Tartu", "Turku")
+
+df <- df0 %>%
+        filter(catalog == "Kungliga") %>%
+        filter(publication_year >= 1640 & publication_year <= 1828) %>%
+	filter(publication_place %in% selected.places) %>%
+	select(publication_decade, publication_place, subject_topic)
+
+# Number of subject topics for each entry
+df$n <- sapply(df$subject_topic, function(x) {length(na.omit(unlist(strsplit(x, ";"))))})
+
+# Group by time, place
+# summarize number of topics
+df <- df %>% group_by(publication_decade, publication_place) %>%
+       summarise(n = sum(n, na.rm = TRUE))
+
+p <- ggplot(df, aes(x = publication_decade, y = n)) + 
+       geom_line(aes(color = publication_place)) +
+       geom_point(aes(color = publication_place)) +
+       scale_y_log10() +
+       xlab("Publication year") +
+       ylab("Title count (Log10 n)")
+
+print(p)
+```
 
@@
 ### Combining devotional literature and temporary sermons
-TODO: Voisko kokeilla tätä barplotteina selvyyden vuoksi?
 
@@
   p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
-       geom_point(aes(col = language, shape = language), size = 5) +
-       geom_line(aes(col = language, shape = language)) +       
+       #geom_point(aes(col = language, shape = language), size = 5) +
+       #geom_line(aes(col = language, shape = language)) +
+       geom_bar(stat = "identity", aes(fill = language, )) +              
        xlab("Publication year") +
@@
 
-###TODO: Dissertation language
+### Dissertation language
 
@@
 Ollaan kiinnostuttu milloin alkaa erityisesti tulemaan ruotsinkielellä väitöksiä.
+
+```{r disslang, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6}
+catalogue <- "Fennica"
+langs <- c("Finnish", "Swedish", "Latin", "German",
+           "Russian", "French", "Hebrew", "Other")
+
+df <- df0 %>%
+        filter(catalog == catalogue) %>%
+        filter(publication_year >= 1640 & publication_year <= 1828) %>%
+	filter(dissertation)
+
+lang <- paste("language.", langs, sep = "")
+otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
+df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
+
+dfl <- NULL
+for (lan in lang) {
+
+  # Classify a document to the specifed language
+  # If document is assigned with languages, each case is considered
+  # so one doc may have multiple entries corresponding to different languages
+  # mean(rowSums(df[, lang]) == 1) # 93% Fennica docs have just 1 language
+  # Combine data frames for specified languages
+  dflsub <- filter(df, df[[lan]])
+  if (nrow(dflsub)>0) {
+    dflsub$language <- gsub("language.", "", lan)
+    dfl <- bind_rows(dfl, dflsub)
+  }
+}
+
+df <- dfl %>% group_by(publication_decade, language) %>%
+     	     summarise(n = n())
+
+# Calculate percentages
+dff <- spread(df, language, n, fill = 0)
+dff[, -1] <- 100 * t(apply(dff[, -1], 1, function (x) {x/sum(x)}))
+dff <- melt(dff, "publication_decade");
+colnames(dff) <- c("publication_decade", "language", "f")
+
+# Order by language counts
+dff$language <- factor(dff$language,
+   levels = (df %>% group_by(language) %>%
+                    summarise(total = sum(n)) %>%
+		    arrange(total))$language);
+dff <- dff %>% arrange(desc(language))
+
+theme_set(theme_bw(20))
+p <- ggplot(dff, aes(x = publication_decade, y = f)) +
+     geom_bar(position = "stack", stat = "identity", aes(fill = language)) + 
+     xlab("Publication year") +
+     ylab("Title count frequency (%)") +
+     ggtitle(paste("Languages (", catalogue, ")", sep = "")) +
+     scale_fill_brewer(palette="Paired")
+print(p)
+```
 
@@
 Tässä on aika jännä piikki 1650 luvun Fennican top-auktorit.
+
+Koko graafi perustuu top auktoreihin. Näistä pari aktiivisinta sattuu olemaan 1650. Jos katsotaan koko Fennican tuotantoa (kaikki auktorit) niin piikkiä 1650 ei ole. Erityisesti 1650 aktiivisia ovat:
+
+- Petraeus, Aeschillus Olai (1593-1657) 183 
+- Gyldenstolpe, Michael Olai (1608-1670) 114
+
 Eli toi Kalm, Pehr ja joku toinen.
-Onhan varmasti niin että tässä ei saattaisi tulla laskuihin mukaan näille tyypeille sekä Fennica että Kungliga?
-Kyseessä sivut 38-39 slideistä.
+
+- Kalm, Pehr on vasta 1700-luvulla mun datan perusteella.
+
+Onhan varmasti niin että tässä ei saattaisi tulla laskuihin mukaan
+näille tyypeille sekä Fennica että Kungliga?
+
+- Kyllä tässä on katsottu pelkkää Fennicaa (eikä Kungligan pitäis ehkä
+  vaikuttaakaan kun siellä ei moista piikkiä näy?) Lähes kaikki
+  julkaisut Turusta.
+
 Tollanen 200 väitöskirjaa per 10 vuotta on kyllä todella iso myös suhteessa muihin noista professoreista jotka päässeet tälle top-listalle.
-Mä siis muuttelin tätä kuvaa, siihen tuli se Bibliographica-top.
-Ettei vaan se jotenkin sotkis tätä niin että nyt ottaa kaikista bibliographica-kansioista tohon yhteen Kalmit?
-Tai jotain vastaavaa.
+
+- Tässä on nimikkeiden nojalla n. 15% duplikaatteja kahdella ekalla
+  top auktorilla. Eli nimikkeet identtiset (ja lisää voisi ehkä tulla
+  jos katsottaisiin melkein identtiset). Mutta en tiedä ovatko muuten
+  oikeasti duplikaatteja, tästähän oli juttua. Se voi selittää
+  osittain piikkiä.
+
+Mä siis muuttelin tätä kuvaa, siihen tuli se Bibliographica-top. Ettei
+vaan se jotenkin sotkis tätä niin että nyt ottaa kaikista
+bibliographica-kansioista tohon yhteen Kalmit?
+
+- Kalmilla ei näyttäis olevan tekemistä tässä
+
+- bibliographican top-funktio toimii kuten pitää, se ei missään
+  vaiheessa etsi mitään bibliographicasta, vaan operoi yksinomaan
+  inputtina annetulla data.framella ja katsoo sen yleisimmät termit
 
@@
 
-### TODO Kungliga subject topics (NEW!!)
-
-Tuotetaan samanlaiset asiasanaryppäät kuin University Curriculum Turku.
-Tämän jälkeen piirretään Kungligan pohjalta yliopisto-asiasanat aikajanalle samalla tavalla kuin Fennican kohdalla kaupunkikohtaisesti.
-
-TÄMÄ vie paljon enemmän tilaa kuin slideihin tulee jäämään. Täten, voi tuottaa kuvat kaksi per slide tai sitten vaihtoehtoisesti kässäriin josta blokataan tänne mitä tarvitaan.
-
-Kaupungit: "Tukholma", "Lund", "Greifswald", "Uppsala", "Tartu"
-
-Asiasanalista on seuraava (omat kuvat kaikista kaupunkikohtaisesti):
-
-1. Kyrkohistoria; Biblisk arkeologi;Exegetik;Homiletik;Dogmatik;Teologi; Praktisk Teologi; Teologisk etik
-
-2. Idé- och lärdomshistoria;Antiken;Historia;Militärhistoria;
-
-3. Filosofi;Metafysik;Logik
+### DONE Kungliga subject topics (NEW!!)
+
+Kyrkohistoria; Biblisk arkeologi;Exegetik;Homiletik;Dogmatik;Teologi; Praktisk Teologi; Teologisk etik
+
+```{r ktopic1, echo=FALSE, message=FALSE, warning=FALSE, fig.width=15, fig.height=5}
+catalogue <- "Kungliga"
+years <- c(1640, 1828)
+sel =  tolower(c("Kyrkohistoria", "biblisk arkeologi", "Exegetik", "Homiletik", "Dogmatik", "Teologi", "Praktisk Teologi", "Teologisk etik"))
+places <- c("Stockholm", "Lund", "Greifswald", "Uppsala", "Tartu")
+
+df <- df0 %>% filter(catalog == catalogue)%>%
+  filter(publication_year >= years[[1]] & publication_year <= years[[2]]) %>%
+  filter(publication_place %in% places)
+
+lang <- paste("language.", langs, sep = "")
+otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
+df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
+dfl <- NULL
+for (lan in lang) {
+  dflsub <- filter(df, df[[lan]])
+  if (nrow(dflsub) > 0) {
+    dflsub$language <- gsub("language.", "", lan)
+    dfl <- bind_rows(dfl, dflsub)
+  }
+}
+
+# Selected catalogue and place with selected topics
+pics <- list()
+for (place in places) {
+
+  df <- subset(dfl, publication_place == place)
+
+  df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)  
+  df <- df %>% filter(hit)
+  df <- df %>% group_by(publication_decade, language) %>%
+             summarise(n = n(),
+	               paper = sum(paper.consumption.km2, na.rm = TRUE))
+
+  # PAPER CONSUMPTION
+  theme_set(theme_bw(20))
+  p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
+       geom_bar(aes(fill = language), position = "stack", stat = "identity") +              
+       xlab("Publication year") +
+       ylab("Paper consumption") +
+       ggtitle(place) +
+       xlim(c(years[[1]], years[[2]]))
+  pics[[place]] <- p
+
+}
+
+grid.arrange(pics[[1]], pics[[2]], pics[[3]], pics[[4]], pics[[5]], nrow = 2)
+```
+
+---
+
+Idé- och lärdomshistoria;Antiken;Historia;Militärhistoria;
+
+```{r ktopic2, echo=FALSE, message=FALSE, warning=FALSE, fig.width=15, fig.height=5}
+
+catalogue <- "Kungliga"
+years <- c(1640, 1828)
+sel =  tolower(c("Idé- och lärdomshistoria", "Antiken", "Historia", "Militärhistoria"))
+places <- c("Stockholm", "Lund", "Greifswald", "Uppsala", "Tartu")
+
+df <- df0 %>% filter(catalog == catalogue)%>%
+  filter(publication_year >= years[[1]] & publication_year <= years[[2]]) %>%
+  filter(publication_place %in% places)
+
+lang <- paste("language.", langs, sep = "")
+otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
+df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
+dfl <- NULL
+for (lan in lang) {
+  dflsub <- filter(df, df[[lan]])
+  if (nrow(dflsub) > 0) {
+    dflsub$language <- gsub("language.", "", lan)
+    dfl <- bind_rows(dfl, dflsub)
+  }
+}
+
+# Selected catalogue and place with selected topics
+pics <- list()
+for (place in places) {
+
+  df <- subset(dfl, publication_place == place)
+
+  df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)  
+  df <- df %>% filter(hit)
+  df <- df %>% group_by(publication_decade, language) %>%
+             summarise(n = n(),
+	               paper = sum(paper.consumption.km2, na.rm = TRUE))
+
+  # PAPER CONSUMPTION
+  theme_set(theme_bw(20))
+  p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
+       geom_bar(aes(fill = language), position = "stack", stat = "identity") +              
+       xlab("Publication year") +
+       ylab("Paper consumption") +
+       ggtitle(place) +
+       xlim(c(years[[1]], years[[2]]))
+  pics[[place]] <- p
+
+}
+
+grid.arrange(pics[[1]], pics[[2]], pics[[3]], pics[[4]], pics[[5]], nrow = 2)
+```
+
+---
+
+Filosofi;Metafysik;Logik
+
+```{r ktopic3, echo=FALSE, message=FALSE, warning=FALSE, fig.width=15, fig.height=5}
+
+catalogue <- "Kungliga"
+years <- c(1640, 1828)
+sel =  tolower(c("Filosofi", "Metafysik", "Logik"))
+places <- c("Stockholm", "Lund", "Greifswald", "Uppsala", "Tartu")
+
+df <- df0 %>% filter(catalog == catalogue)%>%
+  filter(publication_year >= years[[1]] & publication_year <= years[[2]]) %>%
+  filter(publication_place %in% places)
+
+lang <- paste("language.", langs, sep = "")
+otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
+df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
+dfl <- NULL
+for (lan in lang) {
+  dflsub <- filter(df, df[[lan]])
+  if (nrow(dflsub) > 0) {
+    dflsub$language <- gsub("language.", "", lan)
+    dfl <- bind_rows(dfl, dflsub)
+  }
+}
+
+# Selected catalogue and place with selected topics
+pics <- list()
+for (place in places) {
+
+  df <- subset(dfl, publication_place == place)
+
+  df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)  
+  df <- df %>% filter(hit)
+  df <- df %>% group_by(publication_decade, language) %>%
+             summarise(n = n(),
+	               paper = sum(paper.consumption.km2, na.rm = TRUE))
+
+  # PAPER CONSUMPTION
+  theme_set(theme_bw(20))
+  p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
+       geom_bar(aes(fill = language), position = "stack", stat = "identity") +              
+       xlab("Publication year") +
+       ylab("Paper consumption") +
+       ggtitle(place) +
+       xlim(c(years[[1]], years[[2]]))
+  pics[[place]] <- p
+
+}
+
+grid.arrange(pics[[1]], pics[[2]], pics[[3]], pics[[4]], pics[[5]], nrow = 2)
+```
+
+---
 
@@
 
+```{r ktopic4, echo=FALSE, message=FALSE, warning=FALSE, fig.width=15, fig.height=5}
+
+catalogue <- "Kungliga"
+years <- c(1640, 1828)
+sel =  tolower(c("Naturvetenskap", "Matematik", "Matematiska tabeller", "Kemi", "Astronomi", "Geografi", "Geologi", "Meteorologi"))
+places <- c("Stockholm", "Lund", "Greifswald", "Uppsala", "Tartu")
+
+df <- df0 %>% filter(catalog == catalogue)%>%
+  filter(publication_year >= years[[1]] & publication_year <= years[[2]]) %>%
+  filter(publication_place %in% places)
+
+lang <- paste("language.", langs, sep = "")
+otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
+df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
+dfl <- NULL
+for (lan in lang) {
+  dflsub <- filter(df, df[[lan]])
+  if (nrow(dflsub) > 0) {
+    dflsub$language <- gsub("language.", "", lan)
+    dfl <- bind_rows(dfl, dflsub)
+  }
+}
+
+# Selected catalogue and place with selected topics
+pics <- list()
+for (place in places) {
+
+  df <- subset(dfl, publication_place == place)
+
+  df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)  
+  df <- df %>% filter(hit)
+  df <- df %>% group_by(publication_decade, language) %>%
+             summarise(n = n(),
+	               paper = sum(paper.consumption.km2, na.rm = TRUE))
+
+  # PAPER CONSUMPTION
+  theme_set(theme_bw(20))
+  p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
+       geom_bar(aes(fill = language), position = "stack", stat = "identity") +              
+       xlab("Publication year") +
+       ylab("Paper consumption") +
+       ggtitle(place) +
+       xlim(c(years[[1]], years[[2]]))
+  pics[[place]] <- p
+
+}
+
+grid.arrange(pics[[1]], pics[[2]], pics[[3]], pics[[4]], pics[[5]], nrow = 2)
+```
+
+---
+
 5. Retorik
 
+```{r ktopic5, echo=FALSE, message=FALSE, warning=FALSE, fig.width=15, fig.height=5}
+
+catalogue <- "Kungliga"
+years <- c(1640, 1828)
+sel =  tolower(c("Retorik"))
+places <- c("Stockholm", "Lund", "Greifswald", "Uppsala", "Tartu")
+
+df <- df0 %>% filter(catalog == catalogue)%>%
+  filter(publication_year >= years[[1]] & publication_year <= years[[2]]) %>%
+  filter(publication_place %in% places)
+
+lang <- paste("language.", langs, sep = "")
+otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
+df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
+dfl <- NULL
+for (lan in lang) {
+  dflsub <- filter(df, df[[lan]])
+  if (nrow(dflsub) > 0) {
+    dflsub$language <- gsub("language.", "", lan)
+    dfl <- bind_rows(dfl, dflsub)
+  }
+}
+
+# Selected catalogue and place with selected topics
+pics <- list()
+for (place in places) {
+
+  df <- subset(dfl, publication_place == place)
+
+  df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)  
+  df <- df %>% filter(hit)
+  df <- df %>% group_by(publication_decade, language) %>%
+             summarise(n = n(),
+	               paper = sum(paper.consumption.km2, na.rm = TRUE))
+
+  # PAPER CONSUMPTION
+  theme_set(theme_bw(20))
+  p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
+       geom_bar(aes(fill = language), position = "stack", stat = "identity") +              
+       xlab("Publication year") +
+       ylab("Paper consumption") +
+       ggtitle(place) +
+       xlim(c(years[[1]], years[[2]]))
+  pics[[place]] <- p
+
+}
+
+grid.arrange(pics[[1]], pics[[2]], pics[[3]], pics[[4]], pics[[5]], nrow = 2)
+```
+
 6. Hebreiska språket; Grekiska språket;Latin
+
+```{r ktopic6, echo=FALSE, message=FALSE, warning=FALSE, fig.width=15, fig.height=5}
+
+catalogue <- "Kungliga"
+years <- c(1640, 1828)
+sel =  tolower(c("Hebreiska språket", "Grekiska språket", "Latin"))
+places <- c("Stockholm", "Lund", "Greifswald", "Uppsala", "Tartu")
+
+df <- df0 %>% filter(catalog == catalogue)%>%
+  filter(publication_year >= years[[1]] & publication_year <= years[[2]]) %>%
+  filter(publication_place %in% places)
+
+lang <- paste("language.", langs, sep = "")
+otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
+df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
+dfl <- NULL
+for (lan in lang) {
+  dflsub <- filter(df, df[[lan]])
+  if (nrow(dflsub) > 0) {
+    dflsub$language <- gsub("language.", "", lan)
+    dfl <- bind_rows(dfl, dflsub)
+  }
+}
+
+# Selected catalogue and place with selected topics
+pics <- list()
+for (place in places) {
+
+  df <- subset(dfl, publication_place == place)
+
+  df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)  
+  df <- df %>% filter(hit)
+  df <- df %>% group_by(publication_decade, language) %>%
+             summarise(n = n(),
+	               paper = sum(paper.consumption.km2, na.rm = TRUE))
+
+  # PAPER CONSUMPTION
+  theme_set(theme_bw(20))
+  p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
+       geom_bar(aes(fill = language), position = "stack", stat = "identity") +              
+       xlab("Publication year") +
+       ylab("Paper consumption") +
+       ggtitle(place) +
+       xlim(c(years[[1]], years[[2]]))
+  pics[[place]] <- p
+
+}
+
+grid.arrange(pics[[1]], pics[[2]], pics[[3]], pics[[4]], pics[[5]], nrow = 2)
+```
+
+---
 
@@
 
+```{r ktopic7, echo=FALSE, message=FALSE, warning=FALSE, fig.width=15, fig.height=5}
+
+catalogue <- "Kungliga"
+years <- c(1640, 1828)
+sel =  tolower(c("Politisk filosofi","Ekonomiska förhållanden"," Nationalekonomi","Lantbruksekonomi","Ekonomi","Penningväsen","Penningvärde","Kreditväsen","Penningförfalskning","Moral","Pedagogik","Uppfsotringsverket","Uppfostran","Barnuppfostran","Jordbruk","Jordbrukslära","Jordbrukspolitik","Fiske"))
+places <- c("Stockholm", "Lund", "Greifswald", "Uppsala", "Tartu")
+
+df <- df0 %>% filter(catalog == catalogue)%>%
+  filter(publication_year >= years[[1]] & publication_year <= years[[2]]) %>%
+  filter(publication_place %in% places)
+
+lang <- paste("language.", langs, sep = "")
+otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
+df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
+dfl <- NULL
+for (lan in lang) {
+  dflsub <- filter(df, df[[lan]])
+  if (nrow(dflsub) > 0) {
+    dflsub$language <- gsub("language.", "", lan)
+    dfl <- bind_rows(dfl, dflsub)
+  }
+}
+
+# Selected catalogue and place with selected topics
+pics <- list()
+for (place in places) {
+
+  df <- subset(dfl, publication_place == place)
+
+  df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)  
+  df <- df %>% filter(hit)
+  df <- df %>% group_by(publication_decade, language) %>%
+             summarise(n = n(),
+	               paper = sum(paper.consumption.km2, na.rm = TRUE))
+
+  # PAPER CONSUMPTION
+  theme_set(theme_bw(20))
+  p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
+       geom_bar(aes(fill = language), position = "stack", stat = "identity") +              
+       xlab("Publication year") +
+       ylab("Paper consumption") +
+       ggtitle(place) +
+       xlim(c(years[[1]], years[[2]]))
+  pics[[place]] <- p
+
+}
+
+grid.arrange(pics[[1]], pics[[2]], pics[[3]], pics[[4]], pics[[5]], nrow = 2)
+```
+
+---
+
 8. Biologi;Medicinalverket;Medicin;Veterinärmedicin;Medicinalväsen;Medicinalväxkter;Sjukdomar;Djursjukdomar;Djur;Husdjur;Djurskydd;Hästar;Hästkreatur;Hästkörning;Hästavel
 
+```{r ktopic8, echo=FALSE, message=FALSE, warning=FALSE, fig.width=15, fig.height=5}
+
+catalogue <- "Kungliga"
+years <- c(1640, 1828)
+sel =  tolower(c("Biologi","Medicinalverket","Medicin","Veterinärmedicin","Medicinalväsen","Medicinalväxkter","Sjukdomar","Djursjukdomar","Djur","Husdjur","Djurskydd","Hästar","Hästkreatur","Hästkörning","Hästavel"))
+places <- c("Stockholm", "Lund", "Greifswald", "Uppsala", "Tartu")
+
+df <- df0 %>% filter(catalog == catalogue)%>%
+  filter(publication_year >= years[[1]] & publication_year <= years[[2]]) %>%
+  filter(publication_place %in% places)
+
+lang <- paste("language.", langs, sep = "")
+otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
+df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
+dfl <- NULL
+for (lan in lang) {
+  dflsub <- filter(df, df[[lan]])
+  if (nrow(dflsub) > 0) {
+    dflsub$language <- gsub("language.", "", lan)
+    dfl <- bind_rows(dfl, dflsub)
+  }
+}
+
+# Selected catalogue and place with selected topics
+pics <- list()
+for (place in places) {
+
+  df <- subset(dfl, publication_place == place)
+
+  df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)  
+  df <- df %>% filter(hit)
+  df <- df %>% group_by(publication_decade, language) %>%
+             summarise(n = n(),
+	               paper = sum(paper.consumption.km2, na.rm = TRUE))
+
+  # PAPER CONSUMPTION
+  theme_set(theme_bw(20))
+  p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
+       geom_bar(aes(fill = language), position = "stack", stat = "identity") +              
+       xlab("Publication year") +
+       ylab("Paper consumption") +
+       ggtitle(place) +
+       xlim(c(years[[1]], years[[2]]))
+  pics[[place]] <- p
+
+}
+
+grid.arrange(pics[[1]], pics[[2]], pics[[3]], pics[[4]], pics[[5]], nrow = 2)
+```
+---
+
 9. Kvinnor;Kvinnliga textilarbetare;Gravida kvinnor;Adelskvinnor;Kvinnorollen;Ensamstående kvinnor
+
+```{r ktopic9, echo=FALSE, message=FALSE, warning=FALSE, fig.width=15, fig.height=5}
+
+catalogue <- "Kungliga"
+years <- c(1640, 1828)
+sel =  tolower(c("Kvinnor","Kvinnliga textilarbetare","Gravida kvinnor","Adelskvinnor","Kvinnorollen","Ensamstående kvinnor"))
+places <- c("Stockholm", "Lund", "Greifswald", "Uppsala", "Tartu")
+
+df <- df0 %>% filter(catalog == catalogue)%>%
+  filter(publication_year >= years[[1]] & publication_year <= years[[2]]) %>%
+  filter(publication_place %in% places)
+
+lang <- paste("language.", langs, sep = "")
+otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
+df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
+dfl <- NULL
+for (lan in lang) {
+  dflsub <- filter(df, df[[lan]])
+  if (nrow(dflsub) > 0) {
+    dflsub$language <- gsub("language.", "", lan)
+    dfl <- bind_rows(dfl, dflsub)
+  }
+}
+
+# Selected catalogue and place with selected topics
+pics <- list()
+for (place in places) {
+
+  df <- subset(dfl, publication_place == place)
+
+  df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)  
+  df <- df %>% filter(hit)
+  df <- df %>% group_by(publication_decade, language) %>%
+             summarise(n = n(),
+	               paper = sum(paper.consumption.km2, na.rm = TRUE))
+
+  # PAPER CONSUMPTION
+  theme_set(theme_bw(20))
+  p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
+       geom_bar(aes(fill = language), position = "stack", stat = "identity") +              
+       xlab("Publication year") +
+       ylab("Paper consumption") +
+       ggtitle(place) +
+       xlim(c(years[[1]], years[[2]]))
+  pics[[place]] <- p
+
+}
+
+grid.arrange(pics[[1]], pics[[2]], pics[[3]], pics[[4]], pics[[5]], nrow = 2)
+```
+
+---
 
@@
 Högmålsbrott;Skattebrott;Brott;Brottslingar;Äktenskapsbrott;Våldsbrott;Trafikbrott;Gäldenärsbrott;Sabbattsbrott;Sexualbrott;Fridsbrott;Ekonomisk brottslighet;Religionsbrott;Juridik;Straff;Dödsstraff;Kroppsstraff;Straffarbete;Straffarbete;Fängelsestraff
+
+```{r ktopic10, echo=FALSE, message=FALSE, warning=FALSE, fig.width=15, fig.height=5}
+
+catalogue <- "Kungliga"
+years <- c(1640, 1828)
+sel =  tolower(c("Högmålsbrott","Skattebrott","Brott","Brottslingar","Äktenskapsbrott","Våldsbrott","Trafikbrott","Gäldenärsbrott","Sabbattsbrott","Sexualbrott","Fridsbrott","Ekonomisk brottslighet","Religionsbrott","Juridik","Straff","Dödsstraff","Kroppsstraff","Straffarbete","Straffarbete","Fängelsestraff"))
+places <- c("Stockholm", "Lund", "Greifswald", "Uppsala", "Tartu")
+
+df <- df0 %>% filter(catalog == catalogue)%>%
+  filter(publication_year >= years[[1]] & publication_year <= years[[2]]) %>%
+  filter(publication_place %in% places)
+
+lang <- paste("language.", langs, sep = "")
+otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
+df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
+dfl <- NULL
+for (lan in lang) {
+  dflsub <- filter(df, df[[lan]])
+  if (nrow(dflsub) > 0) {
+    dflsub$language <- gsub("language.", "", lan)
+    dfl <- bind_rows(dfl, dflsub)
+  }
+}
+
+# Selected catalogue and place with selected topics
+pics <- list()
+for (place in places) {
+
+  df <- subset(dfl, publication_place == place)
+
+  df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)  
+  df <- df %>% filter(hit)
+  df <- df %>% group_by(publication_decade, language) %>%
+             summarise(n = n(),
+	               paper = sum(paper.consumption.km2, na.rm = TRUE))
+
+  # PAPER CONSUMPTION
+  theme_set(theme_bw(20))
+  p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
+       geom_bar(aes(fill = language), position = "stack", stat = "identity") +              
+       xlab("Publication year") +
+       ylab("Paper consumption") +
+       ggtitle(place) +
+       xlim(c(years[[1]], years[[2]]))
+  pics[[place]] <- p
+
+}
+
+grid.arrange(pics[[1]], pics[[2]], pics[[3]], pics[[4]], pics[[5]], nrow = 2)
+```
 

### 2016-07-09 inst/examples/20160715-slides-Krakow.Rmd

@@
        scale_x_discrete(labels = c("1759-1765", "1766-1772")) +
-       ggtitle("Title count") + xlab("1759-1765")
+       ggtitle("Title count") + xlab("1759-1765 / 1766-1772")
 
@@
        scale_x_discrete(labels = c("1759-1765", "1766-1772")) +
-       ggtitle("Paper consumption") + xlab("1766-1772")
+       ggtitle("Paper consumption") + xlab("1759-1765 / 1766-1772")
 

### 2016-07-09 inst/examples/20160715-slides-Krakow.Rmd
ok

@@
 library(devtools)
-#install_github("ropengov/gisfin")
+# install_github("ropengov/gisfin")
+# devtools::install_github('cttobin/ggthemr')
 library(gisfin)
+library(ggthemr)
 
@@
 theme_set(theme_bw(26))
+
+# Nice default themes
+# https://github.com/cttobin/ggthemr#palettes
+#ggthemr('fresh', text_size = 20)
+# ggthemr('greyscale', text_size = 20)
+#ggthemr('light', text_size = 20)
+# ggthemr('pale', text_size = 20)
+ggthemr_reset() # Reset theme
 ```
@@
 
-10) Sivu 16. Gävlen muuttaminen takaisin analyysiin.
-
-11) Sivu 14. Kuva 1. Sverige julkaisijanimen tarkastaminen.
+10) OK Sivu 16. Gävlen muuttaminen takaisin analyysiin.
+
+11) NOTE Sivu 14. Kuva 1. Sverige julkaisijanimen tarkastaminen.
 
@@
 
-### Publishing activity in Turku
-
-TODO: Muutetaan niin että tarkkaillaan vain samoja yliopistokaupunkeja joita muutenkin otsikolla "Publishing activity in Swedish University Towns (based on Kungliga data)", eli lisätään koordinaatit näille: "Stockholm" (59.3251172 / 18.0710935), "Uppsala" (59.8588200 / 17.6388900), "Lund" (55.7058400 / 13.1932100), "Greifswald" (54.0931100 / 13.3878600), "Turku" (60.4517531 / 22.2670522), "Tartu" (58.3806200 / 26.7250900)?
-Sitten datana käytetään Kungligaa.
-Paitsi "Turku" jossa data pitäisi ottaa Fennicasta.
-
-Turussa kirjantuotanto laskee huomattavasti isonvihan (1710-luku) , pikkuvihan (1740-luku) ja Suomen sodan (1808-1809) aikana.
+### Publishing activity in Swedish University Towns (Kungliga)
+
+Turussa kirjantuotanto laskee huomattavasti isonvihan (1710-luku), pikkuvihan (1740-luku) ja Suomen sodan (1808-1809) aikana.
 Pikkuviha ei ollut yhtä dramaattinen, eikä näy niin totaalisesti.
@@
 theme_set(get_theme_map())
-mapdata <- filter(df0, catalog == "Kungliga") %>%
-      #filter(!is.na(latitude) & !is.na(longitude)) %>%
-      group_by(publication_decade, publication_place, latitude, longitude) %>%
+mapdata <- filter(df0,
+          (catalog == "Kungliga" &
+	      publication_place %in% c("Stockholm", "Uppsala",
+	                         "Greifwald", "Lund", "Tartu"))|
+	  (catalog == "Fennica" &
+	      publication_place == "Turku")) %>%
+      group_by(publication_decade, publication_place,
+	       latitude, longitude) %>%
       summarise(n = n())
@@
 region <- "Europe.north"
-mymap <- get_map(location=geobox(region), color = "bw", source="google",  maptype="terrain")
+mymap <- get_map(location=geobox(region), color = "bw",
+                  source="google",  maptype="terrain")
 
@@
 	  scale_size(range = c(2, 15)) +
-	  theme(title = element_text(size = 20)) +
+	  theme(title = element_text(size = 30)) +
 	  scale_color_manual(values = c("black", "red"))	  
@@
 ### Peaks and drops – role of publishers and contingency
-TODO: Tässä olisi hyvä olla vuodet näkyvissä.
-
-```{r publishingovertime, echo=FALSE, message=FALSE, warning=FALSE, fig.width=6, fig.height=5, out.width="200px"}
+
+TODO: Tässä olisi hyvä olla vuodet näkyvissä. LL: en kyl nyt löydä
+vikaa vaikka pitäis olla hyvin simppeli. Täytyy katsoa lisää
+Krakovassa.
+
+```{r publishingovertime, echo=FALSE, message=FALSE, warning=FALSE, fig.width=6, fig.height=4, out.width="200px"}
 df2 <- df0 %>% group_by(publication_decade, catalog) %>%
@@
 ```{r LIBER-13, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=10, fig.height=8, fig.show="hold", out.width="150px"}
-#https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/LIBER-13-2.png
 for (catal in unique(df0$catalog)) {
@@
 df <- subset(df, !is.na(df$publication_place))
-df$publication_place <- factor(df$publication_place, levels = c(places, "Other"))
+#df$publication_place <- factor(df$publication_place, levels = c(places, "Other"))
 
@@
 library(gridExtra)
-#grid.arrange(pics[[1]], pics[[2]], pics[[3]], pics[[4]], pics[[5]], pics[[6]], nrow = 2)
 grid.arrange(pics[[1]], pics[[2]], pics[[4]], pics[[5]], nrow = 2)
+rm(pics)
 ```
@@
 
-TODO: yhdistä yhteen ainoaan kaavioon, mukana Fennicasta "Turku", "Vaasa" ja "Vyborg" ja Kungligasta kaikki eli "Stockholm", "Lund", "Uppsala", "Greifswald" ja "Tartu"?
+TODO: yhdistä yhteen kaavioon Fennicasta "Turku", "Vaasa" ja "Vyborg" ja Kungligasta kaikki eli "Stockholm", "Lund", "Uppsala", "Greifswald" ja "Tartu"?
 
@@
 ```{r publishers4-fennica, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=7, fig.width=15}
-
-# https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/publishers3-finland-1.png
-
 place <- "Turku"
@@
 ### Comparing paper used on average per publication by publishers
-TODO: Mikä toi Sverige on? Pitäisikö toi tarkastaa, ettei siinä ole joku virhe. Jani ei ole koskaan törmännyt siihen kustantajana.
+
+TODO: Mikä kustantaja Sverige on? LL: originaalidatan publisher-kenttä
+on tässä kohden tyhjä. Veikkaan että tähän on täydennetty materiaalia
+muistakin kentistä. Pitää katsoa Hegen kanssa tarkemmin mikä on
+Sverige koska publisher-kenttä tulee hänen koodeilla.
 
 ```{r publisherpapertitle, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=8, out.width="150px", fig.show="hold"}
-
-# https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/publisherpapertitle-1.png
 
@@
   df$publisher[!df$publisher %in% c(top, "")] <- "Other"
-  df$publisher <- factor(df$publisher, levels = c(top, "Other"))
+  df$publisher <- factor(df$publisher, levels = unique(c(top, "Other")))
 
@@
 
+[Swedish Age of Freedom and Abolishment of Censorship]
+
+### 1766-1772 Title count vs. paper consumption (Kungliga)
+
+Kungligan mukaan kuinka paljon enemmän Kungligassa julkaisujen
+lukumäärä ja paperinkulutus kasvaa kun sensuuri puuttuu vuosina
+1766-1772 suhteessa tätä edeltävään kuuteen vuoteen.
+
+```{r peak, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
+# Select catalog
+df <- df0 %>% filter(catalog == "Kungliga")
+
+# Mark time periods
+df$period <- rep(NA, nrow(df))
+df$period[df$publication_year >= 1759 & df$publication_year <= 1765] <- 1
+df$period[df$publication_year >= 1766 & df$publication_year <= 1772] <- 2
+
+# Remove NA time periods
+df <- df %>% filter(!is.na(period))
+df <- df %>% group_by(period) %>%
+             summarise(n = n(),
+	     	   paper = sum(paper.consumption.km2, na.rm = TRUE))
+
+# TITLE COUNT
+p1 <- ggplot(df, aes(x = period, y = n)) +
+       geom_bar(stat = "identity", position = "stack") +
+       scale_x_discrete(labels = c("1759-1765", "1766-1772")) +
+       ggtitle("Title count") + xlab("1759-1765 / 1766-1772")
+
+# PAPER
+p2 <- ggplot(df, aes(x = period, y = paper)) +
+       geom_bar(stat = "identity", position = "stack") +
+       scale_x_discrete(labels = c("1759-1765", "1766-1772")) +
+       ggtitle("Paper consumption") + xlab("1759-1765 / 1766-1772")
+
+grid.arrange(p1, p2, nrow = 1)
+```
+
+---
+
+### TODO 1766-1774
+
+Selvitettävä asia: onko erityisesti pamflettien kasvu syynä tänä aikana tulevaan nousuun?
+
+Kungliga. Paper per title 1766-1774; 1757-1765; 1775-1783.
+
+```{r pamflets1, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=6, out.width="280px", fig.show="hold"}
+df <- df0 %>%
+        filter(catalog == "Kungliga")
+
+# Add indicator of the publication period
+df$period <- cut(df$publication_year,
+	         breaks = c(1757, 1766, 1775, 1783),
+		 include.lowest = TRUE,
+		 right = FALSE
+		 )
+
+# Remove entries outside the investigated publication periods
+df <- df %>% filter(!is.na(period)) %>%
+	     group_by(period) %>%
+	     summarise(n = n(),
+		  paper = sum(paper.consumption.km2, na.rm = TRUE)) %>%
+        mutate(paper.per.title = paper/n)
+
+p <- ggplot(df,
+       aes(x = period, y = paper.per.title)) + 
+       geom_bar(stat = "identity") +
+       scale_x_discrete(labels = c("1757-1765", "1766-1774", "1775-1783")) +
+       ylab("Paper per title") + xlab("") 
+print(p)
+```
+
+---
+
 [Swedish Age of Freedom and Abolishment of Censorship 1/3]
 
-### Gävle in Riksdagar
+### Gavle in Riksdagar
 
@@
 ```{r riksdar2, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
+  myplace <- "Gavle" # Norrköping / Stockholm
+  minyear <- 1700
+  maxyear <- 1800
+  catalog <- "Kungliga"
+
+  df <- df0
+  df = subset(df, catalog == catal)
+  df <- subset(df, publication_year >= minyear & publication_year <= maxyear)
+
   # Use timeinterval year intervals
-  myplace = "Greifswald" # Norrköping / Stockholm
-  minyear = 1700
-  maxyear = 1800
-  catalog = "Kungliga"
-
-  df = subset(df0, publication_place == myplace & catalog == catal)
-  df <- subset(df, publication_year >= minyear & publication_year < maxyear)
+  # Remove special chars
+  if (length(unique(df$publication_place[grep("^G.vle$", df$publication_place)])) == 1) {
+    df$publication_place[grep("^G.vle$", df$publication_place)] <- "Gavle"
+  }
+  if (length(unique(df$publication_place[grep("^Norrk.ping$", df$publication_place)])) == 1) {
+    df$publication_place[grep("^Norrk.ping$", df$publication_place)] <- "Norrkoping"
+  }
+  df <- df %>% filter(publication_place == myplace)
 
@@
                1765-.5, 1766+.5, # Stockholm 21 februari 1765 21 oktober 1766
-               1769-.5, 1770+.5, # Norrköping & Stockholm 22 april 1769 5 februari 1770
+               1769-.5, 1770+.5, # Norrkoping & Stockholm 22 april 1769 5 februari 1770
                1771-.5, 1772+.5, # Stockholm 19 juni 1771 12 september 1772
-               1792-.5, 1792+.5, # Gävle 26 januari 1792 24 februari 1792	       
+               1792-.5, 1792+.5, # Gavle 26 januari 1792 24 februari 1792	       
                max(na.omit(dfm$date)))
@@
 
- riksplace = c("Stockholm", "Stockholm", "Stockholm", "Norrköping", "Stockholm", "Gävle")
+ riksplace = c("Stockholm", "Stockholm", "Stockholm", "Norrkoping", "Stockholm", "Gavle")
  cols = c("gray", "lightblue", "yellow", "white")
@@
   p <- p + geom_point(data = dfm, aes(x = date, y = Documents), col = "black")
-  #p <- p + scale_x_continuous(breaks = seq(minyear, maxyear, 20))
   p <- p + ggtitle("Publishing activity")
@@
 
----
-
-[Swedish Age of Freedom and Abolishment of Censorship]
-
-### 1766-1772 Title count vs. paper consumption (Kungliga)
-
-Kungligan mukaan kuinka paljon enemmän Kungligassa julkaisujen lukumäärä ja paperinkulutus kasvaa kun sensuuri puuttuu vuosina 1766-1772 suhteessa tätä edeltävään kuuteen vuoteen.
-
-```{r peak, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
-# Select catalog
-df <- df0 %>% filter(catalog == "Kungliga")
-
-# Mark time periods
-df$period <- rep(NA, nrow(df))
-df$period[df$publication_year >= 1759 & df$publication_year <= 1765] <- 1
-df$period[df$publication_year >= 1766 & df$publication_year <= 1772] <- 2
-
-# Remove NA time periods
-df <- df %>% filter(!is.na(period))
-
-df <- df %>% group_by(period) %>%
-             summarise(n = n(),
-	     	   paper = sum(paper.consumption.km2, na.rm = TRUE))
-#df <- melt(df, "period")
-
-# TITLE COUNT
-p1 <- ggplot(df, aes(x = period, y = n)) +
-       geom_bar(stat = "identity", position = "stack") +
-       scale_x_discrete(labels = c("1759-1765", "1766-1772")) +
-       ggtitle("Title count") + xlab("1759-1765 / 1766-1772")
-
-# PAPER
-p2 <- ggplot(df, aes(x = period, y = paper)) +
-       geom_bar(stat = "identity", position = "stack") +
-       scale_x_discrete(labels = c("1759-1765", "1766-1772")) +
-       ggtitle("Paper consumption") + xlab("1759-1765 / 1766-1772")
-
-grid.arrange(p1, p2, nrow = 1)
-```
-
----
-
-### TODO 1766-1774
-
-Selvitettävä asia: onko erityisesti pamflettien kasvu syynä tänä aikana tulevaan nousuun?
-
-Kungliga. Paper per title 1766-1774; 1757-1765; 1775-1783.
-
-```{r pamflets1, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=6, out.width="280px", fig.show="hold"}
-df <- df0 %>%
-        filter(catalog == "Kungliga")
-
-# Add indicator of the publication period
-df$period <- cut(df$publication_year,
-	         breaks = c(1757, 1766, 1775, 1783),
-		 include.lowest = TRUE,
-		 right = FALSE
-		 )
-
-# Remove entries outside the investigated publication periods
-df <- df %>% filter(!is.na(period)) %>%
-	     group_by(period) %>%
-	     summarise(n = n(),
-		  paper = sum(paper.consumption.km2, na.rm = TRUE)) %>%
-        mutate(paper.per.title = paper/n)
-
-p <- ggplot(df,
-       aes(x = period, y = paper.per.title)) + 
-       geom_bar(stat = "identity") +
-       scale_x_discrete(labels = c("1757-1765", "1766-1774", "1775-1783")) +
-       ylab("Paper per title") + xlab("") 
-print(p)
-
-```
 ---
@@
   # PUBLISHER COUNT
-  n = sapply(split(dfs$publisher, dfs$publication_year), function (x) {length(unique(na.omit(x)))})
+  n = sapply(split(dfs$publisher, dfs$publication_year), function (x) {
+         length(unique(na.omit(x)))})
   df = data.frame(year = names(n), n = unname(n))
@@
 }
-#grid.arrange(pics[[1]], pics[[2]], pics[[3]], pics[[4]], pics[[5]],
-             #pics[[6]], pics[[7]], pics[[8]], pics[[9]], pics[[10]], nrow = 2)
+
 grid.arrange(pics[[2]], pics[[4]],
              pics[[6]], pics[[8]], pics[[10]], nrow = 2)
+
+# Remove the pics to save memory
+rm(pics)	     
 ```
@@
 ```{r language1, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=8, out.width="160px", fig.show="hold"}
-# https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/language1-1.png
 catalogue <- "Fennica"
@@
              nrow = 2)
-#grid.arrange(pics[[1]], pics[[2]], pics[[3]], pics[[4]], pics[[5]],
-             #pics[[6]], pics[[7]], pics[[8]], pics[[9]], pics[[10]], 
-            # nrow = 2)
+
+rm(pics)
 ```
@@
 
----
-
-### Dissertation language
-
-Yleinen kielianalyysi prosentteina (sama kuin muut toteutetut prosenttianalyysit näissä Krakova slideissa) kaikkien Fennicassa väitöskirjoiksi merkityistä: eli Kenttä "Dissertation" ja vastaus "True" tässä aineisto.
+Dissertation language: Yleinen kielianalyysi prosentteina (sama kuin muut toteutetut prosenttianalyysit näissä Krakova slideissa) kaikkien Fennicassa väitöskirjoiksi merkityistä: eli Kenttä "Dissertation" ja vastaus "True" tässä aineisto.
 Analyysi vuosikymmenittäin ja kielen mukaan eri väreillä.
@@
        geom_bar(aes(fill = language), position = "stack", stat = "identity") +             
-       #geom_point(aes(col = language, shape = language), size = 5) +
-       #geom_line(aes(col = language, shape = language)) +       
        xlab("Publication year") +
@@
 p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
-       #geom_point(aes(col = language, shape = language), size = 5) +
-       #geom_line(aes(col = language, shape = language)) +
        geom_bar(aes(fill = language), position = "stack", stat = "identity") +                     
@@
 p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
-       #geom_point(aes(col = language, shape = language), size = 5) +
-       #geom_line(aes(col = language, shape = language)) +
        geom_bar(aes(fill = language), position = "stack", stat = "identity") +              
@@
 grid.arrange(pics[[1]], pics[[2]], pics[[3]], pics[[4]], pics[[5]], nrow = 2)
+
+rm(pics)
 ```
@@
 grid.arrange(pics[[1]], pics[[2]], pics[[3]], pics[[4]], pics[[5]], nrow = 2)
+rm(pics)
 ```
@@
 grid.arrange(pics[[1]], pics[[2]], pics[[3]], pics[[4]], pics[[5]], nrow = 2)
-```
+rm(pics)
+```
+
+---
 
@@
 grid.arrange(pics[[1]], pics[[2]], pics[[3]], pics[[4]], pics[[5]], nrow = 2)
-```
+rm(pics)
+```
+
 ---
@@
   summarise(titles = n(), paper = sum(paper.consumption.km2, na.rm = TRUE))
-
-p <- ggplot(dfs, aes(x = publication_decade, y = paper, fill = myplace, order = -as.numeric(myplace))) +
-     geom_bar(position = "stack", stat = "identity", color = "black") +
-     ggtitle("Paper consumption") + 
-     scale_fill_grey() +
-     guides(fill = guide_legend(reverse = TRUE, title = "")) + 
-     xlab("Publication decade") + ylab("Paper (km2)")
-#print(p)
 
@@
 # DUPLICATE FRACTION
-#df <- df.combined.preprocessed %>% group_by(catalog) %>%
-#      			           summarise(duplicates = 100 * mean(remove))
-#p <- ggplot(df, aes(x = catalog, y = duplicates)) +
-#       geom_bar(position = "dodge", stat = "identity") +
-#       ylab("Duplicates (%)") +
-#       ggtitle(paste("Duplicates", paste(range(df.combined.preprocessed$publication_year), collapse = "-")))
-#print(p)
-
 df <- df.combined.preprocessed %>%
@@
        scale_fill_manual(values = c("blue", "red")) + 
-       ggtitle(paste("Duplicates", paste(range(na.omit(df$publication_year)), collapse = "-")))
+       ggtitle(paste("Duplicates", paste(range(na.omit(df$publication_decade)), collapse = "-")))
 
@@
 
-R master (plots & maps): Leo Lahti.
+R master (plots & maps):
+- Leo Lahti
 

### 2016-07-09 inst/examples/20160715-slides-Krakow.Rmd
ok

@@
 library(gisfin)
-library(ggthemr)
+#library(ggthemr)
 
@@
 # ggthemr('pale', text_size = 20)
-ggthemr_reset() # Reset theme
+#ggthemr_reset() # Reset theme
 ```

### 2016-07-09 inst/examples/20160715-slides-Krakow.Rmd
z

@@
 ### Data (1470-1828):
+
+TÄHÄN DATA MÄÄRÄ KOODISTA!
 
@@
 
-```{r publishingactivitycomparisons, echo=FALSE, message=FALSE, cache=FALSE, fig.width=6, fig.height=5, fig.show="hold", out.width="150px"}
+```{r publishingactivitycomparisons, echo=FALSE, message=FALSE, cache=TRUE, fig.width=6, fig.height=5, fig.show="hold", out.width="150px"}
+v <- seq(1500, 1800, 50)
 selected.places = c("Turku", "Uppsala", "Lund", "Stockholm")
@@
 
-```{r comparisons, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=20, fig.height=15}
+```{r comparisons, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, eval = FALSE, fig.width=20, fig.height=15}
 pics <- list()
@@
 
-TODO: yhdistä yhteen kaavioon Fennicasta "Turku", "Vaasa" ja "Vyborg" ja Kungligasta kaikki eli "Stockholm", "Lund", "Uppsala", "Greifswald" ja "Tartu"?
-
 ```{r publishers2-finland, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=7, fig.width=15}
@@
 
-TODO: Mikä kustantaja Sverige on? LL: originaalidatan publisher-kenttä
-on tässä kohden tyhjä. Veikkaan että tähän on täydennetty materiaalia
-muistakin kentistä. Pitää katsoa Hegen kanssa tarkemmin mikä on
-Sverige koska publisher-kenttä tulee hänen koodeilla.
+TODO: Mikä kustantaja Sverige on?
+LL: originaalidatan publisher-kenttä on tässä kohden tyhjä.
+Veikkaan että tähän on täydennetty materiaalia muistakin kentistä.
+Pitää katsoa Hegen kanssa tarkemmin mikä on Sverige koska publisher-kenttä tulee hänen koodeilla.
 
@@
   publications <- publications/timeinterval # Instead of decadal sum, use average annual output 
+library(reshape2)  
 dfm <- melt(publications) 
@@
 
-TODO: asiasanoja / yliopistopaikkakunta vertailu Kungligasta. Ts. mitä
-enemmän eri aikoina asiasanoja (ihan sama mitä ne on) paikkakunnalla,
-sitä monimuotoisempaa/rikkaampaa julkaisutoiminta (eli kaikki
-julkaisut eivät samasta aiheesta, esim. oikeuspöytäkirjoissa ei
-varmaan hirveästi vaihtelua). Voidaan suhteuttaa myös
-esim. paperinkulutukseen tai julkaisujen määrään. Tarkkailtavat
-paikkakunnat: "Stockholm", "Uppsala", "Lund", "Greifswald", "Tartu" ja
-"Turku". Aikaisammin piirretty Greifswald vs Turku (kuinka monta
-kieltä per vuosi) oli samansuuntainen analyysi.
+TODO: asiasanoja / yliopistopaikkakunta vertailu Kungligasta. Ts. mitä enemmän eri aikoina asiasanoja (ihan sama mitä ne on) paikkakunnalla, sitä monimuotoisempaa/rikkaampaa julkaisutoiminta?
 
@@
   }
-
   df <- df %>% filter(catalog == catalogue)%>%
         filter(publication_year >= 1600 & publication_year <= 1900)
+
+  library(dplyr)
+  library(tidyr)
+library(magrittr)
+library(reshape2)
 
@@
 print(p)
-
 }
@@
 
-Dissertation language: Yleinen kielianalyysi prosentteina (sama kuin muut toteutetut prosenttianalyysit näissä Krakova slideissa) kaikkien Fennicassa väitöskirjoiksi merkityistä: eli Kenttä "Dissertation" ja vastaus "True" tässä aineisto.
-Analyysi vuosikymmenittäin ja kielen mukaan eri väreillä.
-Kielien joukko: "Finnish", "Swedish", "Latin", "German", "Russian", "French", "Hebrew", "Other"
-
-Ollaan kiinnostuttu milloin alkaa erityisesti tulemaan ruotsinkielellä väitöksiä.
+Dissertation language
 
@@
 - The Enlightenment literature read in Finland mainly printed elsewhere
-
-Tässä on aika jännä piikki 1650 luvun Fennican top-auktorit.
-
-Koko graafi perustuu top auktoreihin. Näistä pari aktiivisinta sattuu olemaan 1650. Jos katsotaan koko Fennican tuotantoa (kaikki auktorit) niin piikkiä 1650 ei ole. Erityisesti 1650 aktiivisia ovat:
-
-- Petraeus, Aeschillus Olai (1593-1657) 183 
-- Gyldenstolpe, Michael Olai (1608-1670) 114
-
-Eli toi Kalm, Pehr ja joku toinen.
-
-- Kalm, Pehr on vasta 1700-luvulla mun datan perusteella.
-
-Onhan varmasti niin että tässä ei saattaisi tulla laskuihin mukaan
-näille tyypeille sekä Fennica että Kungliga?
-
-- Kyllä tässä on katsottu pelkkää Fennicaa (eikä Kungligan pitäis ehkä
-  vaikuttaakaan kun siellä ei moista piikkiä näy?) Lähes kaikki
-  julkaisut Turusta.
-
-Tollanen 200 väitöskirjaa per 10 vuotta on kyllä todella iso myös suhteessa muihin noista professoreista jotka päässeet tälle top-listalle.
-
-- Tässä on nimikkeiden nojalla n. 15% duplikaatteja kahdella ekalla
-  top auktorilla. Eli nimikkeet identtiset (ja lisää voisi ehkä tulla
-  jos katsottaisiin melkein identtiset). Mutta en tiedä ovatko muuten
-  oikeasti duplikaatteja, tästähän oli juttua. Se voi selittää
-  osittain piikkiä.
-
-Mä siis muuttelin tätä kuvaa, siihen tuli se Bibliographica-top. Ettei
-vaan se jotenkin sotkis tätä niin että nyt ottaa kaikista
-bibliographica-kansioista tohon yhteen Kalmit?
-
-- Kalmilla ei näyttäis olevan tekemistä tässä
-
-- bibliographican top-funktio toimii kuten pitää, se ei missään
-  vaiheessa etsi mitään bibliographicasta, vaan operoi yksinomaan
-  inputtina annetulla data.framella ja katsoo sen yleisimmät termit
 

### 2016-07-10 inst/examples/manuscript-krakow.Rmd
ok
a
Update manuscript-krakow.Rmd

@@
 max.year <- 1828
-output.folder <- "output.tables"
+output.folder <- "output.tables/"
 
@@
 
+### Chunks transfered from slides for later use
+
+[Swedish Age of Freedom and Abolishment of Censorship]
+
+### 1766-1772 Title count vs. paper consumption (Kungliga)
+
+Kungligan mukaan kuinka paljon enemmän Kungligassa julkaisujen
+lukumäärä ja paperinkulutus kasvaa kun sensuuri puuttuu vuosina
+1766-1772 suhteessa tätä edeltävään kuuteen vuoteen.
+
+```{r peak, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
+# Select catalog
+df <- df0 %>% filter(catalog == "Kungliga")
+
+# Mark time periods
+df$period <- rep(NA, nrow(df))
+df$period[df$publication_year >= 1759 & df$publication_year <= 1765] <- 1
+df$period[df$publication_year >= 1766 & df$publication_year <= 1772] <- 2
+
+# Remove NA time periods
+df <- df %>% filter(!is.na(period))
+df <- df %>% group_by(period) %>%
+             summarise(n = n(),
+	     	   paper = sum(paper.consumption.km2, na.rm = TRUE))
+
+# TITLE COUNT
+p1 <- ggplot(df, aes(x = period, y = n)) +
+       geom_bar(stat = "identity", position = "stack") +
+       scale_x_discrete(labels = c("1759-1765", "1766-1772")) +
+       ggtitle("Title count") + xlab("1759-1765 / 1766-1772")
+
+# PAPER
+p2 <- ggplot(df, aes(x = period, y = paper)) +
+       geom_bar(stat = "identity", position = "stack") +
+       scale_x_discrete(labels = c("1759-1765", "1766-1772")) +
+       ggtitle("Paper consumption") + xlab("1759-1765 / 1766-1772")
+
+grid.arrange(p1, p2, nrow = 1)
+```
+
+---
+
 ### Acknowledgements

### 2016-07-10 inst/examples/manuscript-krakow.Rmd
Update manuscript-krakow.Rmd

@@
 
+[University curriculum 4/5]
+
+### Printing of natural science in different languages in Turku
+
+```{r topics-104, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6}
+sel = c("luonnontieteet","matematiikka","fysiikka","kemia","tähtitiede","maantiede","geodesia","geofysiikka","meteorologia")
+# Selected catalogue with selected topics
+df = dfl
+df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)  
+df <- df %>% filter(hit)
+df <- df %>% group_by(publication_decade, language) %>%
+             summarise(n = n(),
+                 paper = sum(paper.consumption.km2, na.rm = TRUE))
+
+# PAPER CONSUMPTION
+theme_set(theme_bw(20))
+p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
+       geom_bar(aes(fill = language), position = "stack", stat = "identity") +                     
+       xlab("Publication year") +
+       ylab("Paper consumption") +
+       ggtitle(paste("Paper (", paste(sel, collapse = ";"), ")", sep = ""))
+print(p)
+
+```
+
 ### Acknowledgements
@@
 
+---
+
 ## Session info

### 2016-07-10 inst/examples/manuscript-krakow.Rmd
Update manuscript-krakow.Rmd

@@
 ```
+---
+
+### DONE Kungliga subject topics (NEW!!)
+
+Kyrkohistoria; Biblisk arkeologi;Exegetik;Homiletik;Dogmatik;Teologi; Praktisk Teologi; Teologisk etik
+
+```{r ktopic1, echo=FALSE, message=FALSE, warning=FALSE, fig.width=15, fig.height=5}
+catalogue <- "Kungliga"
+years <- c(1640, 1828)
+sel =  tolower(c("Kyrkohistoria", "biblisk arkeologi", "Exegetik", "Homiletik", "Dogmatik", "Teologi", "Praktisk Teologi", "Teologisk etik"))
+places <- c("Stockholm", "Lund", "Greifswald", "Uppsala", "Tartu")
+
+df <- df0 %>% filter(catalog == catalogue)%>%
+  filter(publication_year >= years[[1]] & publication_year <= years[[2]]) %>%
+  filter(publication_place %in% places)
+
+lang <- paste("language.", langs, sep = "")
+otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
+df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
+dfl <- NULL
+for (lan in lang) {
+  dflsub <- filter(df, df[[lan]])
+  if (nrow(dflsub) > 0) {
+    dflsub$language <- gsub("language.", "", lan)
+    dfl <- bind_rows(dfl, dflsub)
+  }
+}
+
+# Selected catalogue and place with selected topics
+pics <- list()
+for (place in places) {
+
+  df <- subset(dfl, publication_place == place)
+
+  df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)  
+  df <- df %>% filter(hit)
+  df <- df %>% group_by(publication_decade, language) %>%
+             summarise(n = n(),
+	               paper = sum(paper.consumption.km2, na.rm = TRUE))
+
+  # PAPER CONSUMPTION
+  theme_set(theme_bw(20))
+  p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
+       geom_bar(aes(fill = language), position = "stack", stat = "identity") +              
+       xlab("Publication year") +
+       ylab("Paper consumption") +
+       ggtitle(place) +
+       xlim(c(years[[1]], years[[2]]))
+  pics[[place]] <- p
+
+}
+
+grid.arrange(pics[[1]], pics[[2]], pics[[3]], pics[[4]], pics[[5]], nrow = 2)
+
+rm(pics)
+```
+
+---
+
+Idé- och lärdomshistoria;Antiken;Historia;Militärhistoria;
+
+```{r ktopic2, echo=FALSE, message=FALSE, warning=FALSE, fig.width=15, fig.height=5}
+
+catalogue <- "Kungliga"
+years <- c(1640, 1828)
+sel =  tolower(c("Idé- och lärdomshistoria", "Antiken", "Historia", "Militärhistoria"))
+places <- c("Stockholm", "Lund", "Greifswald", "Uppsala", "Tartu")
+
+df <- df0 %>% filter(catalog == catalogue)%>%
+  filter(publication_year >= years[[1]] & publication_year <= years[[2]]) %>%
+  filter(publication_place %in% places)
+
+lang <- paste("language.", langs, sep = "")
+otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
+df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
+dfl <- NULL
+for (lan in lang) {
+  dflsub <- filter(df, df[[lan]])
+  if (nrow(dflsub) > 0) {
+    dflsub$language <- gsub("language.", "", lan)
+    dfl <- bind_rows(dfl, dflsub)
+  }
+}
+
+# Selected catalogue and place with selected topics
+pics <- list()
+for (place in places) {
+
+  df <- subset(dfl, publication_place == place)
+
+  df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)  
+  df <- df %>% filter(hit)
+  df <- df %>% group_by(publication_decade, language) %>%
+             summarise(n = n(),
+	               paper = sum(paper.consumption.km2, na.rm = TRUE))
+
+  # PAPER CONSUMPTION
+  theme_set(theme_bw(20))
+  p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
+       geom_bar(aes(fill = language), position = "stack", stat = "identity") +              
+       xlab("Publication year") +
+       ylab("Paper consumption") +
+       ggtitle(place) +
+       xlim(c(years[[1]], years[[2]]))
+  pics[[place]] <- p
+
+}
+
+grid.arrange(pics[[1]], pics[[2]], pics[[3]], pics[[4]], pics[[5]], nrow = 2)
+
+rm(pics)
+```
+
+---
+
+Filosofi;Metafysik;Logik
+
+```{r ktopic3, echo=FALSE, message=FALSE, warning=FALSE, fig.width=15, fig.height=5}
+
+catalogue <- "Kungliga"
+years <- c(1640, 1828)
+sel =  tolower(c("Filosofi", "Metafysik", "Logik"))
+places <- c("Stockholm", "Lund", "Greifswald", "Uppsala", "Tartu")
+
+df <- df0 %>% filter(catalog == catalogue)%>%
+  filter(publication_year >= years[[1]] & publication_year <= years[[2]]) %>%
+  filter(publication_place %in% places)
+
+lang <- paste("language.", langs, sep = "")
+otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
+df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
+dfl <- NULL
+for (lan in lang) {
+  dflsub <- filter(df, df[[lan]])
+  if (nrow(dflsub) > 0) {
+    dflsub$language <- gsub("language.", "", lan)
+    dfl <- bind_rows(dfl, dflsub)
+  }
+}
+
+# Selected catalogue and place with selected topics
+pics <- list()
+for (place in places) {
+
+  df <- subset(dfl, publication_place == place)
+
+  df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)  
+  df <- df %>% filter(hit)
+  df <- df %>% group_by(publication_decade, language) %>%
+             summarise(n = n(),
+	               paper = sum(paper.consumption.km2, na.rm = TRUE))
+
+  # PAPER CONSUMPTION
+  theme_set(theme_bw(20))
+  p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
+       geom_bar(aes(fill = language), position = "stack", stat = "identity") +              
+       xlab("Publication year") +
+       ylab("Paper consumption") +
+       ggtitle(place) +
+       xlim(c(years[[1]], years[[2]]))
+  pics[[place]] <- p
+
+}
+
+grid.arrange(pics[[1]], pics[[2]], pics[[3]], pics[[4]], pics[[5]], nrow = 2)
+rm(pics)
+```
+
+---
+
+4. Naturvetenskap;Matematik;Matematiska tabeller; Kemi;Astronomi;Geografi;Geologi;Meteorologi
+
+```{r ktopic4, echo=FALSE, message=FALSE, warning=FALSE, fig.width=15, fig.height=5}
+
+catalogue <- "Kungliga"
+years <- c(1640, 1828)
+sel =  tolower(c("Naturvetenskap", "Matematik", "Matematiska tabeller", "Kemi", "Astronomi", "Geografi", "Geologi", "Meteorologi"))
+places <- c("Stockholm", "Lund", "Greifswald", "Uppsala", "Tartu")
+
+df <- df0 %>% filter(catalog == catalogue)%>%
+  filter(publication_year >= years[[1]] & publication_year <= years[[2]]) %>%
+  filter(publication_place %in% places)
+
+lang <- paste("language.", langs, sep = "")
+otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
+df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
+dfl <- NULL
+for (lan in lang) {
+  dflsub <- filter(df, df[[lan]])
+  if (nrow(dflsub) > 0) {
+    dflsub$language <- gsub("language.", "", lan)
+    dfl <- bind_rows(dfl, dflsub)
+  }
+}
+
+# Selected catalogue and place with selected topics
+pics <- list()
+for (place in places) {
+
+  df <- subset(dfl, publication_place == place)
+
+  df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)  
+  df <- df %>% filter(hit)
+  df <- df %>% group_by(publication_decade, language) %>%
+             summarise(n = n(),
+	               paper = sum(paper.consumption.km2, na.rm = TRUE))
+
+  # PAPER CONSUMPTION
+  theme_set(theme_bw(20))
+  p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
+       geom_bar(aes(fill = language), position = "stack", stat = "identity") +              
+       xlab("Publication year") +
+       ylab("Paper consumption") +
+       ggtitle(place) +
+       xlim(c(years[[1]], years[[2]]))
+  pics[[place]] <- p
+
+}
+
+grid.arrange(pics[[1]], pics[[2]], pics[[3]], pics[[4]], pics[[5]], nrow = 2)
+rm(pics)
+```
+
+---
+
+5. Retorik
+
+```{r ktopic5, echo=FALSE, message=FALSE, warning=FALSE, fig.width=15, fig.height=5}
+
+catalogue <- "Kungliga"
+years <- c(1640, 1828)
+sel =  tolower(c("Retorik"))
+places <- c("Stockholm", "Lund", "Greifswald", "Uppsala", "Tartu")
+
+df <- df0 %>% filter(catalog == catalogue)%>%
+  filter(publication_year >= years[[1]] & publication_year <= years[[2]]) %>%
+  filter(publication_place %in% places)
+
+lang <- paste("language.", langs, sep = "")
+otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
+df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
+dfl <- NULL
+for (lan in lang) {
+  dflsub <- filter(df, df[[lan]])
+  if (nrow(dflsub) > 0) {
+    dflsub$language <- gsub("language.", "", lan)
+    dfl <- bind_rows(dfl, dflsub)
+  }
+}
+
+# Selected catalogue and place with selected topics
+pics <- list()
+for (place in places) {
+
+  df <- subset(dfl, publication_place == place)
+
+  df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)  
+  df <- df %>% filter(hit)
+  df <- df %>% group_by(publication_decade, language) %>%
+             summarise(n = n(),
+	               paper = sum(paper.consumption.km2, na.rm = TRUE))
+
+  # PAPER CONSUMPTION
+  theme_set(theme_bw(20))
+  p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
+       geom_bar(aes(fill = language), position = "stack", stat = "identity") +              
+       xlab("Publication year") +
+       ylab("Paper consumption") +
+       ggtitle(place) +
+       xlim(c(years[[1]], years[[2]]))
+  pics[[place]] <- p
+
+}
+
+grid.arrange(pics[[1]], pics[[2]], pics[[3]], pics[[4]], pics[[5]], nrow = 2)
+rm(pics)
+```
+
+---
+
+6. Hebreiska språket; Grekiska språket;Latin
+
+```{r ktopic6, echo=FALSE, message=FALSE, warning=FALSE, fig.width=15, fig.height=5}
+
+catalogue <- "Kungliga"
+years <- c(1640, 1828)
+sel =  tolower(c("Hebreiska språket", "Grekiska språket", "Latin"))
+places <- c("Stockholm", "Lund", "Greifswald", "Uppsala", "Tartu")
+
+df <- df0 %>% filter(catalog == catalogue)%>%
+  filter(publication_year >= years[[1]] & publication_year <= years[[2]]) %>%
+  filter(publication_place %in% places)
+
+lang <- paste("language.", langs, sep = "")
+otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
+df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
+dfl <- NULL
+for (lan in lang) {
+  dflsub <- filter(df, df[[lan]])
+  if (nrow(dflsub) > 0) {
+    dflsub$language <- gsub("language.", "", lan)
+    dfl <- bind_rows(dfl, dflsub)
+  }
+}
+
+# Selected catalogue and place with selected topics
+pics <- list()
+for (place in places) {
+
+  df <- subset(dfl, publication_place == place)
+
+  df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)  
+  df <- df %>% filter(hit)
+  df <- df %>% group_by(publication_decade, language) %>%
+             summarise(n = n(),
+	               paper = sum(paper.consumption.km2, na.rm = TRUE))
+
+  # PAPER CONSUMPTION
+  theme_set(theme_bw(20))
+  p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
+       geom_bar(aes(fill = language), position = "stack", stat = "identity") +              
+       xlab("Publication year") +
+       ylab("Paper consumption") +
+       ggtitle(place) +
+       xlim(c(years[[1]], years[[2]]))
+  pics[[place]] <- p
+
+}
+
+grid.arrange(pics[[1]], pics[[2]], pics[[3]], pics[[4]], pics[[5]], nrow = 2)
+rm(pics)
+```
+
+---
+
+7.
+Politisk filosofi;Ekonomiska förhållanden; Nationalekonomi;Lantbruksekonomi;Ekonomi;Penningväsen;Penningvärde;Kreditväsen;Penningförfalskning;Moral;Pedagogik;Uppfsotringsverket;Uppfostran;Barnuppfostran;Jordbruk;Jordbrukslära;Jordbrukspolitik;Fiske
+
+```{r ktopic7, echo=FALSE, message=FALSE, warning=FALSE, fig.width=15, fig.height=5}
+
+catalogue <- "Kungliga"
+years <- c(1640, 1828)
+sel =  tolower(c("Politisk filosofi","Ekonomiska förhållanden"," Nationalekonomi","Lantbruksekonomi","Ekonomi","Penningväsen","Penningvärde","Kreditväsen","Penningförfalskning","Moral","Pedagogik","Uppfsotringsverket","Uppfostran","Barnuppfostran","Jordbruk","Jordbrukslära","Jordbrukspolitik","Fiske"))
+places <- c("Stockholm", "Lund", "Greifswald", "Uppsala", "Tartu")
+
+df <- df0 %>% filter(catalog == catalogue)%>%
+  filter(publication_year >= years[[1]] & publication_year <= years[[2]]) %>%
+  filter(publication_place %in% places)
+
+lang <- paste("language.", langs, sep = "")
+otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
+df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
+dfl <- NULL
+for (lan in lang) {
+  dflsub <- filter(df, df[[lan]])
+  if (nrow(dflsub) > 0) {
+    dflsub$language <- gsub("language.", "", lan)
+    dfl <- bind_rows(dfl, dflsub)
+  }
+}
+
+# Selected catalogue and place with selected topics
+pics <- list()
+for (place in places) {
+
+  df <- subset(dfl, publication_place == place)
+
+  df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)  
+  df <- df %>% filter(hit)
+  df <- df %>% group_by(publication_decade, language) %>%
+             summarise(n = n(),
+	               paper = sum(paper.consumption.km2, na.rm = TRUE))
+
+  # PAPER CONSUMPTION
+  theme_set(theme_bw(20))
+  p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
+       geom_bar(aes(fill = language), position = "stack", stat = "identity") +              
+       xlab("Publication year") +
+       ylab("Paper consumption") +
+       ggtitle(place) +
+       xlim(c(years[[1]], years[[2]]))
+  pics[[place]] <- p
+
+}
+
+grid.arrange(pics[[1]], pics[[2]], pics[[3]], pics[[4]], pics[[5]], nrow = 2)
+rm(pics)
+```
+
+---
+
+8. Biologi;Medicinalverket;Medicin;Veterinärmedicin;Medicinalväsen;Medicinalväxkter;Sjukdomar;Djursjukdomar;Djur;Husdjur;Djurskydd;Hästar;Hästkreatur;Hästkörning;Hästavel
+
+```{r ktopic8, echo=FALSE, message=FALSE, warning=FALSE, fig.width=15, fig.height=5}
+
+catalogue <- "Kungliga"
+years <- c(1640, 1828)
+sel =  tolower(c("Biologi","Medicinalverket","Medicin","Veterinärmedicin","Medicinalväsen","Medicinalväxkter","Sjukdomar","Djursjukdomar","Djur","Husdjur","Djurskydd","Hästar","Hästkreatur","Hästkörning","Hästavel"))
+places <- c("Stockholm", "Lund", "Greifswald", "Uppsala", "Tartu")
+
+df <- df0 %>% filter(catalog == catalogue)%>%
+  filter(publication_year >= years[[1]] & publication_year <= years[[2]]) %>%
+  filter(publication_place %in% places)
+
+lang <- paste("language.", langs, sep = "")
+otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
+df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
+dfl <- NULL
+for (lan in lang) {
+  dflsub <- filter(df, df[[lan]])
+  if (nrow(dflsub) > 0) {
+    dflsub$language <- gsub("language.", "", lan)
+    dfl <- bind_rows(dfl, dflsub)
+  }
+}
+
+# Selected catalogue and place with selected topics
+pics <- list()
+for (place in places) {
+
+  df <- subset(dfl, publication_place == place)
+
+  df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)  
+  df <- df %>% filter(hit)
+  df <- df %>% group_by(publication_decade, language) %>%
+             summarise(n = n(),
+	               paper = sum(paper.consumption.km2, na.rm = TRUE))
+
+  # PAPER CONSUMPTION
+  theme_set(theme_bw(20))
+  p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
+       geom_bar(aes(fill = language), position = "stack", stat = "identity") +              
+       xlab("Publication year") +
+       ylab("Paper consumption") +
+       ggtitle(place) +
+       xlim(c(years[[1]], years[[2]]))
+  pics[[place]] <- p
+
+}
+
+grid.arrange(pics[[1]], pics[[2]], pics[[3]], pics[[4]], pics[[5]], nrow = 2)
+rm(pics)
+```
+
+---
+
+9. Kvinnor;Kvinnliga textilarbetare;Gravida kvinnor;Adelskvinnor;Kvinnorollen;Ensamstående kvinnor
+
+```{r ktopic9, echo=FALSE, message=FALSE, warning=FALSE, fig.width=15, fig.height=5}
+
+catalogue <- "Kungliga"
+years <- c(1640, 1828)
+sel =  tolower(c("Kvinnor","Kvinnliga textilarbetare","Gravida kvinnor","Adelskvinnor","Kvinnorollen","Ensamstående kvinnor"))
+places <- c("Stockholm", "Lund", "Greifswald", "Uppsala", "Tartu")
+
+df <- df0 %>% filter(catalog == catalogue)%>%
+  filter(publication_year >= years[[1]] & publication_year <= years[[2]]) %>%
+  filter(publication_place %in% places)
+
+lang <- paste("language.", langs, sep = "")
+otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
+df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
+dfl <- NULL
+for (lan in lang) {
+  dflsub <- filter(df, df[[lan]])
+  if (nrow(dflsub) > 0) {
+    dflsub$language <- gsub("language.", "", lan)
+    dfl <- bind_rows(dfl, dflsub)
+  }
+}
+
+# Selected catalogue and place with selected topics
+pics <- list()
+for (place in places) {
+
+  df <- subset(dfl, publication_place == place)
+
+  df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)  
+  df <- df %>% filter(hit)
+  df <- df %>% group_by(publication_decade, language) %>%
+             summarise(n = n(),
+	               paper = sum(paper.consumption.km2, na.rm = TRUE))
+
+  # PAPER CONSUMPTION
+  theme_set(theme_bw(20))
+  p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
+       geom_bar(aes(fill = language), position = "stack", stat = "identity") +              
+       xlab("Publication year") +
+       ylab("Paper consumption") +
+       ggtitle(place) +
+       xlim(c(years[[1]], years[[2]]))
+  pics[[place]] <- p
+
+}
+
+grid.arrange(pics[[1]], pics[[2]], pics[[3]], pics[[4]], pics[[5]], nrow = 2)
+rm(pics)
+```
+
+---
+
+10.
+Högmålsbrott;Skattebrott;Brott;Brottslingar;Äktenskapsbrott;Våldsbrott;Trafikbrott;Gäldenärsbrott;Sabbattsbrott;Sexualbrott;Fridsbrott;Ekonomisk brottslighet;Religionsbrott;Juridik;Straff;Dödsstraff;Kroppsstraff;Straffarbete;Straffarbete;Fängelsestraff
+
+```{r ktopic10, echo=FALSE, message=FALSE, warning=FALSE, fig.width=15, fig.height=5}
+
+catalogue <- "Kungliga"
+years <- c(1640, 1828)
+sel =  tolower(c("Högmålsbrott","Skattebrott","Brott","Brottslingar","Äktenskapsbrott","Våldsbrott","Trafikbrott","Gäldenärsbrott","Sabbattsbrott","Sexualbrott","Fridsbrott","Ekonomisk brottslighet","Religionsbrott","Juridik","Straff","Dödsstraff","Kroppsstraff","Straffarbete","Straffarbete","Fängelsestraff"))
+places <- c("Stockholm", "Lund", "Greifswald", "Uppsala", "Tartu")
+
+df <- df0 %>% filter(catalog == catalogue)%>%
+  filter(publication_year >= years[[1]] & publication_year <= years[[2]]) %>%
+  filter(publication_place %in% places)
+
+lang <- paste("language.", langs, sep = "")
+otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
+df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
+dfl <- NULL
+for (lan in lang) {
+  dflsub <- filter(df, df[[lan]])
+  if (nrow(dflsub) > 0) {
+    dflsub$language <- gsub("language.", "", lan)
+    dfl <- bind_rows(dfl, dflsub)
+  }
+}
+
+# Selected catalogue and place with selected topics
+pics <- list()
+for (place in places) {
+
+  df <- subset(dfl, publication_place == place)
+
+  df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)  
+  df <- df %>% filter(hit)
+  df <- df %>% group_by(publication_decade, language) %>%
+             summarise(n = n(),
+	               paper = sum(paper.consumption.km2, na.rm = TRUE))
+
+  # PAPER CONSUMPTION
+  theme_set(theme_bw(20))
+  p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
+       geom_bar(aes(fill = language), position = "stack", stat = "identity") +              
+       xlab("Publication year") +
+       ylab("Paper consumption") +
+       ggtitle(place) +
+       xlim(c(years[[1]], years[[2]]))
+  pics[[place]] <- p
+
+}
+
+grid.arrange(pics[[1]], pics[[2]], pics[[3]], pics[[4]], pics[[5]], nrow = 2)
+rm(pics)
+```
+---
 

### 2016-07-10 inst/examples/manuscript-krakow.Rmd
Update manuscript-krakow.Rmd

@@
 
+[Swedish Age of Freedom and Abolishment of Censorship 2/3]
+
+### Number of publishers in Stockholm 1760-1770
+
+```{r polev1, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=6, out.width="280px", fig.show="hold"}
+sel.places = c("Stockholm", "Uppsala", "Lund", "Greifswald", "Turku")
+sel.years = c(1760, 1780)
+pics <- list()
+
+for (place in sel.places) {
+
+for (catalogue in c("Fennica", "Kungliga")) {
+
+  df <- df0
+  dfs <- df %>% filter(catalog == catalogue &
+     	              publication_place == place &
+		      publication_year >= min(sel.years) &
+		      publication_year <= max(sel.years) 
+		      )
+
+  df <- dfs %>% group_by(publication_year) %>%
+             summarise(n = n(),
+	               paper = sum(paper.consumption.km2, na.rm = TRUE))
+
+  # PUBLISHER COUNT
+  n = sapply(split(dfs$publisher, dfs$publication_year), function (x) {
+         length(unique(na.omit(x)))})
+  df = data.frame(year = names(n), n = unname(n))
+  if (nrow(df) > 1) {
+    p = ggplot(df, aes(x = year, y = n)) +
+        geom_bar(stat = "identity") +
+       ggtitle(paste("Publishers:", catalogue, place)) +
+       scale_x_discrete(breaks = seq(min(sel.years), max(sel.years), 10))
+  } else {
+    p <- ggplot() + ggtitle("Insufficient data")
+  }
+  pics[[paste(place, catalogue, sep = "-")]] <- p
+}
+}
+
+grid.arrange(pics[[2]], pics[[4]],
+             pics[[6]], pics[[8]], pics[[10]], nrow = 2)
+
+# Remove the pics to save memory
+rm(pics)	     
+```
+---
+
 ### Acknowledgements

### 2016-07-10 inst/examples/manuscript-krakow.Rmd
Update manuscript-krakow.Rmd

@@
 
+### Finland in the Swedish context
+
+- Dramatic events regarding the diversity of "Finnishness" take place in the early nineteenth century --- but the analysis of Finnish knowledge production 1828-2016 is for another day.
+
+```{r 201606krakow-turkuvsother, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=5, fig.width=10}
+df <- subset(df0, catalog == "Fennica") %>%
+  filter(publication_year >= 1640 & publication_year <= 1800)%>% 
+      filter(!is.na(country)) %>%
+      filter(!is.na(publication_place) & !is.na(paper.consumption.km2) & paper.consumption.km2 > -0.01)
+
+# Add indicator field: Turku or Not Turku
+myplace <- "Turku"
+
+df$myplace <- rep(NA, nrow(df))
+df$myplace[df$publication_place == myplace] <- myplace
+df$myplace[!df$publication_place == myplace & df$country == "Finland"] <- "Finland"
+df$myplace[!df$country == "Finland" & !df$publication_place == myplace] <- "Foreign"
+df$myplace <- factor(df$myplace, levels = rev(c("Foreign", "Finland", "Turku")))
+
+# Keep entries with known publication place and paper consumption
+# Group by year/decade and Turku/Other
+dfs <- df %>% group_by(publication_decade, myplace) %>%
+  summarise(titles = n(), paper = sum(paper.consumption.km2, na.rm = TRUE))
+
+p <- ggplot(dfs, aes(x = publication_decade, y = titles, fill = myplace, order = -as.numeric(myplace))) +
+     geom_bar(position = "stack", stat = "identity", color = "black") +
+     ggtitle("Title count") +
+     # scale_fill_manual(values = c("blue", "black", "darkgreen")) +
+     scale_fill_grey() +
+     guides(fill = guide_legend(reverse = TRUE, title = "")) +      
+     xlab("Publication decade") + ylab("Title count (n)")
+print(p)
+```
+---
+
 ### Acknowledgements

### 2016-07-10 inst/examples/manuscript-krakow.Rmd
Update manuscript-krakow.Rmd

@@
 
+[Publishers 5/6]
+
+### Comparing paper used on average per publication by publishers
+
+TODO: Mikä kustantaja Sverige on?
+LL: originaalidatan publisher-kenttä on tässä kohden tyhjä.
+Veikkaan että tähän on täydennetty materiaalia muistakin kentistä.
+Pitää katsoa Hegen kanssa tarkemmin mikä on Sverige koska publisher-kenttä tulee hänen koodeilla.
+
+```{r publisherpapertitle, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=8, out.width="150px", fig.show="hold"}
+
+for (catalogue in c("Fennica", "Kungliga")) {
+
+  df <- df0
+  df <- df %>%
+        filter(catalog == catalogue) %>%
+	filter(publication_year >= 1640 & publication_year <= 1828)
+
+  # Selected ones
+  df$publisher[df$publisher == ""] = "Other"
+  top <- names(top(df, "publisher", 5))
+  df$publisher[!df$publisher %in% c(top, "")] <- "Other"
+  df$publisher <- factor(df$publisher, levels = unique(c(top, "Other")))
+
+  # Publishing per decade & publisher	
+  npub <- df %>%
+     	  group_by(publication_decade, publisher) %>%
+	  summarize(paper = sum(paper.consumption.km2, na.rm = TRUE), n = n()) %>%
+	  mutate(paper.per.title = paper/n)
+
+theme_set(theme_bw(20))
+p <- ggplot(npub, aes(x = publication_decade, y = paper.per.title, group = publisher)) +
+       geom_point(size = 5, aes(shape = publisher, color = publisher)) +
+       geom_smooth(col = "black", aes(shape = publisher, fill = publisher, color = publisher)) + 
+       xlab("Publication year") +
+       ylab("Paper per title") +
+       ylim(c(0, 1.1*max(npub$paper.per.title))) +
+       ggtitle(paste("Paper per title ratio (", catalogue, ")", sep = ""))
+print(p)
+}
+```
+
+---
+
 ### Acknowledgements

### 2016-07-10 inst/examples/manuscript-krakow.Rmd
Update manuscript-krakow.Rmd

@@
 
+[Languages]
+
+### Development of use of different languages in Kungliga data
+
+```{r language1-kungliga, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=8, out.width="150px", fig.show="hold"}
+catalogue = "Kungliga"
+  df <- dfl %>% filter(catalog == catalogue) %>%
+     	        group_by(publication_decade, language) %>%
+                summarise(n = n(),
+	               paper = sum(paper.consumption.km2, na.rm = TRUE))
+
+# TITLE COUNT
+p <- ggplot(df, aes(x = publication_decade, y = n, group = language)) +
+       geom_point(aes(col = language, shape = language), size = 5) +
+       geom_line(aes(col = language, shape = language)) +       
+       xlab("Publication year") +
+       ylab("Title count (n)") +
+       ggtitle(paste("Languages (", catalogue, ")", sep = ""))
+print(p)
+
+# PAPER CONSUMPTION
+p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
+       geom_point(aes(col = language, shape = language), size = 5) +
+       geom_line(aes(col = language, shape = language)) +       
+       xlab("Publication year") +
+       ylab("Paper consumption") +
+       ggtitle(paste("Languages (", catalogue, ")", sep = ""))
+print(p)
+```
+
+---
+
 ### Acknowledgements

### 2016-07-10 inst/examples/manuscript-krakow.Rmd
Update manuscript-krakow.Rmd

@@
 
+[Publishers]
+
+Asiasanoja / yliopistopaikkakunta vertailu Kungligasta. Ts. mitä enemmän eri aikoina asiasanoja (ihan sama mitä ne on) paikkakunnalla, sitä monimuotoisempaa/rikkaampaa julkaisutoiminta?
+
+```{r subtop1, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=6}
+selected.places <- c("Stockholm", "Uppsala",
+		     "Lund", "Greifswald",
+                     "Tartu", "Turku")
+
+df <- df0 %>%
+        filter(catalog == "Kungliga") %>%
+        filter(publication_year >= 1640 & publication_year <= 1828) %>%
+	filter(publication_place %in% selected.places) %>%
+	select(publication_decade, publication_place, subject_topic)
+
+# Number of subject topics for each entry
+df$n <- sapply(df$subject_topic, function(x) {length(na.omit(unlist(strsplit(x, ";"))))})
+
+# Group by time, place
+# summarize number of topics
+df <- df %>% group_by(publication_decade, publication_place) %>%
+       summarise(n = sum(n, na.rm = TRUE))
+
+p <- ggplot(df, aes(x = publication_decade, y = n)) + 
+       geom_line(aes(color = publication_place)) +
+       geom_point(aes(color = publication_place)) +
+       scale_y_log10() +
+       xlab("Publication year") +
+       ylab("Title count (Log10 n)")
+
+print(p)
+```
+
+---
+
 ### Acknowledgements

### 2016-07-10 inst/examples/20160715-slides-Krakow.Rmd
s

@@
 
-### TODO-lista
-
-1) DONE Sivut 38-39. Auktori piikki. 1650-luvulla, miksi?
-
-1) Sivu 6. Karttakuva, geokoordinaatit (löytyy kalvolta) lisääminen + kartan muodostaminen Kungligan pohjalta mainittuihin kuuteen kaupunkiin paitsi Turku jonka data otetaan Fennicasta.
-
-2) OK Sivu 12. Kuva 1 ja Kuva 2 yhdistäminen samaan Kungliga kaavioon. Eli, Fennica kuvasta siirretään "Turku", "Vaasa" ja "Vyborg" Kungliga kuvaan. Muut tiedot Fennicasta jätetään pois.
-
-3) OK Sivu 20. Uusi kuva: asiasanoja / yliopistopaikkakunta vertailu Kungligasta.
-
-4) OK Sivu 18. Uusi kuva: Kungligasta nimikkeiden määrän ja paperinkulutuksen suhde vuosilta 1766-1774 ja verrataan sitä vuosiin 1757-1765 ja 1775-1783.
-
-5) OK Sivu 32. Uusi kuva: Yleinen kielianalyysi prosentteina Fennican väitöskirjoista (pitäisi olla suoraviivainen).
-
-6) OK Sivu 39. Uusi kuva: Kungliga subject topics, kalvossa olevien asiasanaryppäiden pohjalta samanlainen analyysi Kungligan yliopistokaupungeista kuin on tehty nyt Fennicasta.
-
-7) OK Sivu 30. Viilaus: Viivojen vaihtaminen barplotteihin.
-
-8) OK [Lokaali ongelma Mikolla? näkyy R-studion konsolissa oikein, mutta ei knitatussa PDF:ssä] Sivu 7. Kuva 1. Viilaus: vuosiluvut näkyviin.
-
-9) OK [Lokaali ongelma Mikolla? näkyy R-studion konsolissa oikein, mutta ei knitatussa PDF:ssä] Sivu 8. Kuva 1. Viilaus: vuosiluvut näkyviin.
-
-10) OK Sivu 16. Gävlen muuttaminen takaisin analyysiin.
-
-11) NOTE Sivu 14. Kuva 1. Sverige julkaisijanimen tarkastaminen.
+### TODO
+
+Esitysjärjestys: Sivun 19 slide ("Development of use of different languages in Finnish NationalBibliography") pitäisi tulla sivun 21 sliden ("Different languages in Fennica and Kungliga (percentage)") jälkeen (samalla sivun 20 slide "Development of use of different languages in Kungliga data" putoaa pois).
+Mutta nyt kun muutan järjestystä niin sivun 21 slide ei sen jälkeen toimi.
+Tämä pitää fiksata.
+
+Karttakuvassa Greifswald, Lund ei näy. Tätä pitää vähän miettiä.
+
+Dissertation languages: kategoria "other" sisällön selvittäminen!
+
+Joissain kuvista puuttuu vielä mystisesti ne akselitiedot. Lisäksi Mikko tsekkaa kuvien tekstit yms.
+
+Gävle-kuvan kohtalo pitää tsiigata myös.
 
@@
 
-[Intro 2/3]
+[Intro]
 
@@
 
-[Intro 3/3]
+[Intro]
 
@@
 
-We use nationally organized library catalogues produced by national memory organizations.
-The aim is to at least partly overcome a national gaze in the analysis.
-By focusing on The Finnish case and studying it both in the context of the Swedish realm and (later) in the Russian empire, we have the opportunity to see how knowledge production happened through a more complex network of cities.
-
-### Enlightenment in Finland after "the rock bottom" of 1700-1721
-
-Different roles of languages visible in topics addressed in different languages:
-
-1) Changes in University curriculum reflected in published theses
-
-2) Religious publishing in Finnish language
-
-3) Economy and social science published in Swedish language
+Overcoming a national gaze in the analysis by focusing on how knowledge production happened through a more complex network of cities.
+
+---
+
+### Outline of the presentation
+
+1) Big picture and political events
+
+2) Publishers in Sweden and Turku
+
+3) Languages and religious publishing in Finland
+
+4) University curriculum & Enlightenment in Finland
 
@@
 
-[Big Picture 1/4]
+### Big Picture & Political Events
+
+---
+
+[Big Picture & Political Events]
 
@@
 
-[Big Picture 2/4]
+[Big Picture & Political Events]
 
@@
 
-[Big Picture 3/4]
+[Big Picture & Political Events]
 
@@
 
-[Big Picture 4/4]
-
-### Rise of the octavo sized book as vehicle of Enlightenment
-TÄSSÄ kanssa vuodet näkyviin.
-Paper consumption for different document formats over time.
-
-```{r LIBER-13, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=10, fig.height=8, fig.show="hold", out.width="150px"}
-for (catal in unique(df0$catalog)) {
-  df2 <- subset(df0, catalog == catal) %>% group_by(publication_decade, gatherings) %>% summarize(paper.consumption.km2 = sum(paper.consumption.km2, na.rm = TRUE), n = n()) 
-  df2 <- filter(df2, gatherings %in% setdiff(names(which(table(df2$gatherings) >= 15)), "NA"))
-  df2$highlight <- rep("gray", nrow(df2))
-  df2$highlight[df2$gatherings == "8vo"] <- "darkgreen"
-
-  p <- ggplot(df2, aes(y = paper.consumption.km2,
-                       x = publication_decade,
-		       shape = gatherings,
-		       linetype = gatherings))		       
-  p <- p + geom_point(size = 4)
-  p <- p + geom_smooth(method = "loess", size = 1,
-         aes(color = highlight, fill = highlight))
-  p <- p + scale_color_manual(values = c("darkgreen", "darkgray"))
-  p <- p + scale_fill_manual(values = c("darkgreen", "darkgray"))  	 
-  p <- p + ggtitle("Paper consumption in time by gatherings")
-  p <- p + xlab("Year")
-  p <- p + ylab("Paper consumption (km2)")
-  p <- p + guides(linetype = guide_legend(keywidth = 5),
-       	          shape = guide_legend(keywidth = 5))
-  p <- p + ggtitle(paste("Paper consumption\n(", catal, ")", sep = ""))
-  print(p)
-}
-```
-
----
-
-### Publishers
-
----
-
-[Publishers 1/6]
-
-### Turku in Sweden: proportions for title count and paper in Swedish University towns
-
-```{r comparisons, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, eval = FALSE, fig.width=20, fig.height=15}
-pics <- list()
-for (catalogue in na.omit(unique(df0$catalog))) {
-
-df <- df0 %>% filter(catalog == catalogue)%>%
-        filter(publication_year >= 1640 & publication_year <= 1828)
-places <- c("Stockholm", "Uppsala", "Lund", "Greifswald", "Turku")
-df$publication_place[!df$publication_place %in% places] <- "Other"
-df <- subset(df, !is.na(df$publication_place))
-#df$publication_place <- factor(df$publication_place, levels = c(places, "Other"))
-
-df <- df %>% group_by(publication_decade, publication_place) %>%
-             summarise(n = n(),
-	     	       paper = sum(paper.consumption.km2, na.rm = TRUE),
-		       publishers = length(na.omit(unique(publisher)))
-		       )
-
-# Calculate percentages
-for (varname in c("n", "paper", "publishers")) {
-
-  df$varname <- df[[varname]]
-  dff <- df %>% select(publication_decade, publication_place, varname)
-  dff <- spread(dff, publication_place, varname, fill = 0)
-  dff[, -1] <- 100 * t(apply(dff[, -1], 1, function (x) {x/sum(x)}))
-  dff <- melt(dff, "publication_decade");
-  colnames(dff) <- c("publication_decade", "publication_place", "f")
-
-  theme_set(theme_bw(20))
-  p <- ggplot(dff, aes(x = publication_decade, y = f)) +
-     geom_bar(position = "stack", stat = "identity",
-       aes(fill = publication_place)) + 
-     xlab("Publication year") +
-     scale_fill_brewer(palette="Paired")
-     if (varname == "n") {
-       p <- p + ggtitle(paste("Title count (", catalogue, ")", sep = "")) + 
-                ylab("Title count frequency (%)") 
-     }
-     if (varname == "paper") {
-       p <- p + ggtitle(paste("Paper (", catalogue, ")", sep = "")) +
-                ylab("Paper (%)")        
-     }
-     if (varname == "publishers") {
-       p <- p + ggtitle(paste("Publishers (", catalogue, ")", sep = "")) +
-                       ylab("Publishers (%)")
-     }
-
-  pics[[paste(catalogue, varname, sep = "-")]] <- p
-
-}
-}
-library(gridExtra)
-grid.arrange(pics[[1]], pics[[2]], pics[[4]], pics[[5]], nrow = 2)
-rm(pics)
-```
-
----
-
-[Publishers 2/6]
-
-### Publishers in Finland / Swedish University towns
-
-```{r publishers2-finland, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=7, fig.width=15}
-df <- df0
-df <- df %>%
-        filter(catalog == "Fennica") %>%
-	filter(country == "Finland" | publication_place == "Vyborg") %>%
-        filter(publication_year >= 1640 & publication_year <= 1828)
-
-# Top publication places
-library(bibliographica)
-
-top <- c("Turku", "Vaasa", "Vyborg")
-df <- df %>%	
-        filter(publication_place %in% top) %>%	
-        select(publication_decade, publication_place, publisher)
-
-npub <- unique(df) %>% group_by(publication_decade, publication_place) %>% tally()
-npub$publication_place <- factor(npub$publication_place, levels = top)
-npub.fennica <- npub
-
-df <- df0
-catalogue <- "Kungliga"
-df <- df %>%
-        filter(catalog == catalogue) %>%
-        filter(publication_year >= 1640 & publication_year <= 1828)
-
-# Selected publication places
-top <- c("Stockholm", "Lund", "Uppsala", "Greifswald", "Tartu")
-df <- df %>%	
-        filter(publication_place %in% top) %>%	
-        select(publication_decade, publication_place, publisher)
-
-npub <- unique(df) %>% group_by(publication_decade, publication_place) %>% tally()
-npub$publication_place <- factor(npub$publication_place, levels = top)
-npub.kungliga <- npub
-
-npub <- bind_rows(npub.fennica, npub.kungliga)
-
-# Order by total publishing activity
-npub$publication_place <- factor(npub$publication_place, levels = (npub %>% group_by(publication_place) %>% summarise(total = sum(n)) %>% arrange(desc(total)))$publication_place)
-npub <- npub %>% arrange(publication_place)
-
-theme_set(theme_bw(20))
-p <- ggplot(npub, aes(x = publication_decade, y = n)) +
-       geom_bar(stat = "identity", position = "stack",
-       		    aes(fill = publication_place)) + 
-       xlab("Publication year") +
-       ylab("Unique publishers (n)") +        
-       ggtitle(paste("Unique publishers in selected publication places (", catalogue, ")"))
-
-print(p)
-```
-
----
-
-[Publishers 4/6]
-
-### Title count of the output of publishers in Turku
-
-```{r publishers4-fennica, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=7, fig.width=15}
-place <- "Turku"
-catalogue = "Fennica"
-df = df0
-
-df <- df %>%
-        filter(catalog == catalogue & publication_place == place)
-
-df <- df %>%	
-  filter(publication_year >= 1640 & publication_year <= 1828)%>%
-        select(publication_decade, publisher, paper.consumption.km2)
-
-# Group small publishers
-# Top publishers by title count
-ntop <- 10
-top <- names(top(df, "publisher", ntop))
-df$publisher[!df$publisher %in% top] <- "Other"
-df$publisher <- factor(df$publisher, c(top, "Other"))
-
-# Title count per decade & publisher	
-npub <- df %>% group_by(publication_decade, publisher) %>% tally()
-
-# TITLE COUNT
-theme_set(theme_bw(20))
-p <- ggplot(npub, aes(x = publication_decade, y = n)) +
-       geom_bar(stat = "identity", position = "stack", aes(fill = publisher)) + 
-       xlab("Publication year") +
-       ylab("Title count (n)") +        
-       ggtitle(paste("Title count per publisher (", place, "/", catalogue, ")", sep = ""))
-print(p)
-```
-
----
-
-[Publishers 5/6]
-
-### Comparing paper used on average per publication by publishers
-
-TODO: Mikä kustantaja Sverige on?
-LL: originaalidatan publisher-kenttä on tässä kohden tyhjä.
-Veikkaan että tähän on täydennetty materiaalia muistakin kentistä.
-Pitää katsoa Hegen kanssa tarkemmin mikä on Sverige koska publisher-kenttä tulee hänen koodeilla.
-
-```{r publisherpapertitle, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=8, out.width="150px", fig.show="hold"}
-
-for (catalogue in c("Fennica", "Kungliga")) {
-
-  df <- df0
-  df <- df %>%
-        filter(catalog == catalogue) %>%
-	filter(publication_year >= 1640 & publication_year <= 1828)
-
-  # Selected ones
-  df$publisher[df$publisher == ""] = "Other"
-  top <- names(top(df, "publisher", 5))
-  df$publisher[!df$publisher %in% c(top, "")] <- "Other"
-  df$publisher <- factor(df$publisher, levels = unique(c(top, "Other")))
-
-  # Publishing per decade & publisher	
-  npub <- df %>%
-     	  group_by(publication_decade, publisher) %>%
-	  summarize(paper = sum(paper.consumption.km2, na.rm = TRUE), n = n()) %>%
-	  mutate(paper.per.title = paper/n)
-
-theme_set(theme_bw(20))
-p <- ggplot(npub, aes(x = publication_decade, y = paper.per.title, group = publisher)) +
-       geom_point(size = 5, aes(shape = publisher, color = publisher)) +
-       geom_smooth(col = "black", aes(shape = publisher, fill = publisher, color = publisher)) + 
-       xlab("Publication year") +
-       ylab("Paper per title") +
-       ylim(c(0, 1.1*max(npub$paper.per.title))) +
-       ggtitle(paste("Paper per title ratio (", catalogue, ")", sep = ""))
-print(p)
-}
-```
-
----
-
-[Publishers 6/6]
-
-### Rock Bottom of the Great Northern War (1700-1721)
-
-Publisher title count changes around 1700 with a nearly detrimental drop in Turku, significant publishing place in Finland at the time.
-
-```{r drop1700B, echo=FALSE, message=FALSE, warning=FALSE, fig.width=15, fig.height=7}
-# https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/drop1700B-1.png
-
-catalogue <- "Fennica"
-place <- "Turku"
-
-df <- df0
-df <- df %>%
-        filter(catalog == catalogue & publication_place == place) %>%
-        filter(publication_year >= 1650 & publication_year < 1750)
-
-# Selected ones
-top <- names(top(df, "publisher", 5))
-df$publisher[!df$publisher %in% top] <- "Other"
-df$publisher <- factor(df$publisher, levels = c(top, "Other"))
-
-# Publishing per year & publisher	
-npub <- df %>%
-     	  group_by(publication_year, publisher) %>%
-	  summarize(paper = sum(paper.consumption.km2, na.rm = TRUE), n = n())
-
-theme_set(theme_bw(20))
-p <- ggplot(npub, aes(x = publication_year, y = n, group = publisher)) +
-       geom_point(size = 5, aes(shape = publisher, color = publisher)) +
-       geom_smooth(col = "black", aes(shape = publisher, fill = publisher, color = publisher)) + 
-       xlab("Publication year") +
-       ylab("Title count (n)") +
-       ylim(c(0, 1.1*max(npub$n))) +
-       ggtitle(paste("Title count (", place, "/", catalogue, ")", sep = ""))
-print(p)
-```
-
----
-
-[Swedish Age of Freedom and Abolishment of Censorship]
-
-### 1766-1772 Title count vs. paper consumption (Kungliga)
-
-Kungligan mukaan kuinka paljon enemmän Kungligassa julkaisujen
-lukumäärä ja paperinkulutus kasvaa kun sensuuri puuttuu vuosina
-1766-1772 suhteessa tätä edeltävään kuuteen vuoteen.
-
-```{r peak, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
-# Select catalog
-df <- df0 %>% filter(catalog == "Kungliga")
-
-# Mark time periods
-df$period <- rep(NA, nrow(df))
-df$period[df$publication_year >= 1759 & df$publication_year <= 1765] <- 1
-df$period[df$publication_year >= 1766 & df$publication_year <= 1772] <- 2
-
-# Remove NA time periods
-df <- df %>% filter(!is.na(period))
-df <- df %>% group_by(period) %>%
-             summarise(n = n(),
-	     	   paper = sum(paper.consumption.km2, na.rm = TRUE))
-
-# TITLE COUNT
-p1 <- ggplot(df, aes(x = period, y = n)) +
-       geom_bar(stat = "identity", position = "stack") +
-       scale_x_discrete(labels = c("1759-1765", "1766-1772")) +
-       ggtitle("Title count") + xlab("1759-1765 / 1766-1772")
-
-# PAPER
-p2 <- ggplot(df, aes(x = period, y = paper)) +
-       geom_bar(stat = "identity", position = "stack") +
-       scale_x_discrete(labels = c("1759-1765", "1766-1772")) +
-       ggtitle("Paper consumption") + xlab("1759-1765 / 1766-1772")
-
-grid.arrange(p1, p2, nrow = 1)
-```
-
----
-
-### TODO 1766-1774
-
-Selvitettävä asia: onko erityisesti pamflettien kasvu syynä tänä aikana tulevaan nousuun?
-
-Kungliga. Paper per title 1766-1774; 1757-1765; 1775-1783.
+[Big Picture & Political Events]
+
+### Role of pamphleteering in 1766-1774
+
+Pamphleteering clearly causes the peak in publishing during the time of abolished censorship in Sweden.
 
@@
 
-[Swedish Age of Freedom and Abolishment of Censorship 1/3]
-
-### Gavle in Riksdagar
+[Big Picture & Political Events]
+
+### Gävle in Riksdagar
 
@@
   dfm <- transform(dfm, date = as.numeric(as.character(Time)))
-  ymin = min(dfm$Documents)
+  ymin = min(0.0001)
   ymax = max(dfm$Documents)
@@
   # Draw Figure
+library(ggplot2)
   theme_set(theme_bw(20))
@@
 
-[Swedish Age of Freedom and Abolishment of Censorship 2/3]
-
-### Number of publishers in Stockholm 1760-1770
-
-```{r polev1, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=6, out.width="280px", fig.show="hold"}
-sel.places = c("Stockholm", "Uppsala", "Lund", "Greifswald", "Turku")
-sel.years = c(1760, 1780)
+### Publishers
+
+---
+
+[Publishers]
+
+### Publishers in Swedish University towns (and Finland)
+
+```{r publishers2-finland, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=7, fig.width=15}
+df <- df0
+df <- df %>%
+        filter(catalog == "Fennica") %>%
+	filter(country == "Finland" | publication_place == "Vyborg") %>%
+        filter(publication_year >= 1640 & publication_year <= 1828)
+
+# Top publication places
+library(bibliographica)
+
+top <- c("Turku", "Vaasa", "Vyborg")
+df <- df %>%	
+        filter(publication_place %in% top) %>%	
+        select(publication_decade, publication_place, publisher)
+
+npub <- unique(df) %>% group_by(publication_decade, publication_place) %>% tally()
+npub$publication_place <- factor(npub$publication_place, levels = top)
+npub.fennica <- npub
+
+df <- df0
+catalogue <- "Kungliga"
+df <- df %>%
+        filter(catalog == catalogue) %>%
+        filter(publication_year >= 1640 & publication_year <= 1828)
+
+# Selected publication places
+top <- c("Stockholm", "Lund", "Uppsala", "Greifswald", "Tartu")
+df <- df %>%	
+        filter(publication_place %in% top) %>%	
+        select(publication_decade, publication_place, publisher)
+
+npub <- unique(df) %>% group_by(publication_decade, publication_place) %>% tally()
+npub$publication_place <- factor(npub$publication_place, levels = top)
+npub.kungliga <- npub
+
+npub <- bind_rows(npub.fennica, npub.kungliga)
+
+# Order by total publishing activity
+npub$publication_place <- factor(npub$publication_place, levels = (npub %>% group_by(publication_place) %>% summarise(total = sum(n)) %>% arrange(desc(total)))$publication_place)
+npub <- npub %>% arrange(publication_place)
+
+theme_set(theme_bw(20))
+p <- ggplot(npub, aes(x = publication_decade, y = n)) +
+       geom_bar(stat = "identity", position = "stack",
+       		    aes(fill = publication_place)) + 
+       xlab("Publication year") +
+       ylab("Unique publishers (n)") +        
+       ggtitle(paste("Unique publishers in selected publication places (", catalogue, ")"))
+
+print(p)
+```
+
+---
+
+[Publishers]
+
+### Turku in Sweden: proportions for title count and paper in Swedish University towns
+
+```{r comparisons, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=20, fig.height=15}
 pics <- list()
-
-for (place in sel.places) {
-
-for (catalogue in c("Fennica", "Kungliga")) {
+for (catalogue in na.omit(unique(df0$catalog))) {
+
+df <- df0 %>% filter(catalog == catalogue)%>%
+        filter(publication_year >= 1640 & publication_year <= 1828)
+places <- c("Stockholm", "Uppsala", "Lund", "Greifswald", "Turku")
+df$publication_place[!df$publication_place %in% places] <- "Other"
+df <- subset(df, !is.na(df$publication_place))
+#df$publication_place <- factor(df$publication_place, levels = c(places, "Other"))
+library(reshape2)
+library(magrittr)
+library(tidyr)
+
+df <- df %>% group_by(publication_decade, publication_place) %>%
+             summarise(n = n(),
+       	       paper = sum(paper.consumption.km2, na.rm = TRUE),
+		       publishers = length(na.omit(unique(publisher)))
+		       )
+
+# Calculate percentages
+for (varname in c("n", "paper", "publishers")) {
+
+  df$varname <- df[[varname]]
+  dff <- df %>% select(publication_decade, publication_place, varname)
+  dff <- spread(dff, publication_place, varname, fill = 0)
+  dff[, -1] <- 100 * t(apply(dff[, -1], 1, function (x) {x/sum(x)}))
+  dff <- melt(dff, "publication_decade");
+  colnames(dff) <- c("publication_decade", "publication_place", "f")
+
+  theme_set(theme_bw(20))
+  p <- ggplot(dff, aes(x = publication_decade, y = f)) +
+     geom_bar(position = "stack", stat = "identity",
+       aes(fill = publication_place)) + 
+     xlab("Publication year") +
+     scale_fill_brewer(palette="Paired")
+     if (varname == "n") {
+       p <- p + ggtitle(paste("Title count (", catalogue, ")", sep = "")) + 
+                ylab("Title count frequency (%)") 
+     }
+     if (varname == "paper") {
+       p <- p + ggtitle(paste("Paper (", catalogue, ")", sep = "")) +
+                ylab("Paper (%)")        
+     }
+     if (varname == "publishers") {
+       p <- p + ggtitle(paste("Publishers (", catalogue, ")", sep = "")) +
+                       ylab("Publishers (%)")
+     }
+
+  pics[[paste(catalogue, varname, sep = "-")]] <- p
+
+}
+}
+library(gridExtra)
+grid.arrange(pics[[1]], pics[[2]], pics[[4]], pics[[5]], nrow = 2)
+rm(pics)
+```
+
+---
+
+[Publishers]
+
+### Title count of the output of publishers in Turku
+
+```{r publishers4-fennica, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=7, fig.width=15}
+place <- "Turku"
+catalogue = "Fennica"
+df = df0
+
+df <- df %>%
+        filter(catalog == catalogue & publication_place == place)
+
+df <- df %>%	
+  filter(publication_year >= 1640 & publication_year <= 1828)%>%
+        select(publication_decade, publisher, paper.consumption.km2)
+
+# Group small publishers
+# Top publishers by title count
+ntop <- 10
+top <- names(top(df, "publisher", ntop))
+df$publisher[!df$publisher %in% top] <- "Other"
+df$publisher <- factor(df$publisher, c(top, "Other"))
+
+# Title count per decade & publisher	
+npub <- df %>% group_by(publication_decade, publisher) %>% tally()
+
+# TITLE COUNT
+theme_set(theme_bw(20))
+p <- ggplot(npub, aes(x = publication_decade, y = n)) +
+       geom_bar(stat = "identity", position = "stack", aes(fill = publisher)) + 
+       xlab("Publication year") +
+       ylab("Title count (n)") +        
+       ggtitle(paste("Title count per publisher (", place, "/", catalogue, ")", sep = ""))
+print(p)
+```
+
+---
+
+[Publishers]
+
+### Rock Bottom of the Great Northern War (1700-1721)
+
+Publisher title count changes around 1700 with a nearly detrimental drop in Turku, significant publishing place in Finland at the time.
+
+```{r drop1700B, echo=FALSE, message=FALSE, warning=FALSE, fig.width=15, fig.height=7}
+# https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/drop1700B-1.png
+
+catalogue <- "Fennica"
+place <- "Turku"
 
 df <- df0
-  dfs <- df %>% filter(catalog == catalogue &
-     	              publication_place == place &
-		      publication_year >= min(sel.years) &
-		      publication_year <= max(sel.years) 
-		      )
-
-  df <- dfs %>% group_by(publication_year) %>%
-             summarise(n = n(),
-	               paper = sum(paper.consumption.km2, na.rm = TRUE))
-
-  # PUBLISHER COUNT
-  n = sapply(split(dfs$publisher, dfs$publication_year), function (x) {
-         length(unique(na.omit(x)))})
-  df = data.frame(year = names(n), n = unname(n))
-  if (nrow(df) > 1) {
-    p = ggplot(df, aes(x = year, y = n)) +
-        geom_bar(stat = "identity") +
-       ggtitle(paste("Publishers:", catalogue, place)) +
-       scale_x_discrete(breaks = seq(min(sel.years), max(sel.years), 10))
-  } else {
-    p <- ggplot() + ggtitle("Insufficient data")
-  }
-  pics[[paste(place, catalogue, sep = "-")]] <- p
-}
-}
-
-grid.arrange(pics[[2]], pics[[4]],
-             pics[[6]], pics[[8]], pics[[10]], nrow = 2)
-
-# Remove the pics to save memory
-rm(pics)	     
-```
-
----
-
-[Swedish Age of Freedom and Abolishment of Censorship 3/3]
-
-TODO: asiasanoja / yliopistopaikkakunta vertailu Kungligasta. Ts. mitä enemmän eri aikoina asiasanoja (ihan sama mitä ne on) paikkakunnalla, sitä monimuotoisempaa/rikkaampaa julkaisutoiminta?
-
-```{r subtop1, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=6}
-selected.places <- c("Stockholm", "Uppsala",
-		     "Lund", "Greifswald",
-                     "Tartu", "Turku")
-
-df <- df0 %>%
-        filter(catalog == "Kungliga") %>%
-        filter(publication_year >= 1640 & publication_year <= 1828) %>%
-	filter(publication_place %in% selected.places) %>%
-	select(publication_decade, publication_place, subject_topic)
-
-# Number of subject topics for each entry
-df$n <- sapply(df$subject_topic, function(x) {length(na.omit(unlist(strsplit(x, ";"))))})
-
-# Group by time, place
-# summarize number of topics
-df <- df %>% group_by(publication_decade, publication_place) %>%
-       summarise(n = sum(n, na.rm = TRUE))
-
-p <- ggplot(df, aes(x = publication_decade, y = n)) + 
-       geom_line(aes(color = publication_place)) +
-       geom_point(aes(color = publication_place)) +
-       scale_y_log10() +
-       xlab("Publication year") +
-       ylab("Title count (Log10 n)")
-
+df <- df %>%
+        filter(catalog == catalogue & publication_place == place) %>%
+        filter(publication_year >= 1650 & publication_year < 1750)
+
+# Selected ones
+top <- names(top(df, "publisher", 5))
+df$publisher[!df$publisher %in% top] <- "Other"
+df$publisher <- factor(df$publisher, levels = c(top, "Other"))
+
+# Publishing per year & publisher	
+npub <- df %>%
+     	  group_by(publication_year, publisher) %>%
+	  summarize(paper = sum(paper.consumption.km2, na.rm = TRUE), n = n())
+
+theme_set(theme_bw(20))
+p <- ggplot(npub, aes(x = publication_year, y = n, group = publisher)) +
+       geom_point(size = 5, aes(shape = publisher, color = publisher)) +
+       geom_smooth(col = "black", aes(shape = publisher, fill = publisher, color = publisher)) + 
+       xlab("Publication year") +
+       ylab("Title count (n)") +
+       ylim(c(0, 1.1*max(npub$n))) +
+       ggtitle(paste("Title count (", place, "/", catalogue, ")", sep = ""))
 print(p)
@@
 
-[Languages 1/4]
+[Languages]
 
@@
 
-[Languages 2/4]
+[Languages]
 
@@
 
-[Languages 3/4]
+[Languages]
 
@@
 
+[Languages]
+
 ### Different languages in Turku, Stockholm, Lund and Uppsala
@@
 
-[Languages 4/4]
+[Languages]
 
@@
 
-[Religious texts in Finland 1/3]
+[Religious texts in Finland]
 
@@
 
-[Religious texts in Finland 2/3]
+[Religious texts in Finland]
 
@@
 
-[Religious texts in Finland 3/3]
+[Religious texts in Finland]
 
@@
 
-### University curriculum in Turku 1640-1828
-
-Dissertation language
+### University curriculum & Enlightenment in Finland
+
+---
+
+[University curriculum & Enlightenment in Finland]
+
+### Dissertation languages in Turku 1640-1828
 
@@
 
-[University curriculum 1/5]
+[University curriculum & Enlightenment in Finland]
 
@@
 
-[University curriculum 2/5]
+[University curriculum & Enlightenment in Finland]
 
@@
 
-[University curriculum 3/5]
+[University curriculum & Enlightenment in Finland]
 
@@
 
-[University curriculum 4/5]
-
-### Printing of natural science in different languages in Turku
-
-```{r topics-104, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6}
-sel = c("luonnontieteet","matematiikka","fysiikka","kemia","tähtitiede","maantiede","geodesia","geofysiikka","meteorologia")
+[University curriculum & Enlightenment in Finland]
+
+### Printing of economy and social science in different languages in Turku
+
+```{r topics-105, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6}
+sel =   c("psykologia","yhteiskuntafilosofia","valtiofilosofia","talous","raha","moraali","velvollisuudet","kasvatus","maanviljely","maatalous","kalastus")
+
 # Selected catalogue with selected topics
@@
 
-[University curriculum 5/5]
-
-### Printing of economy and social science in different languages in Turku
-
-```{r topics-105, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6}
-sel =   c("psykologia","yhteiskuntafilosofia","valtiofilosofia","talous","raha","moraali","velvollisuudet","kasvatus","maanviljely","maatalous","kalastus")
-
-# Selected catalogue with selected topics
-df = dfl
-df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)  
-df <- df %>% filter(hit)
-df <- df %>% group_by(publication_decade, language) %>%
-             summarise(n = n(),
-	               paper = sum(paper.consumption.km2, na.rm = TRUE))
-
-# PAPER CONSUMPTION
-theme_set(theme_bw(20))
-p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
-       geom_bar(aes(fill = language), position = "stack", stat = "identity") +              
-       xlab("Publication year") +
-       ylab("Paper consumption") +
-       ggtitle(paste("Paper (", paste(sel, collapse = ";"), ")", sep = ""))
-print(p)
-
-```
-
----
-
-### Effects of the Enlightenment in Finland
-
-- Decline of metaphysics, rise of social and economic theory 
-- The Enlightenment literature read in Finland mainly printed elsewhere
-
-```{r authors22, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5, out.width="150px", fig.show="hold"}
+[University curriculum & Enlightenment in Finland]
+
+### Rise of the octavo sized book as vehicle of Enlightenment
+
+Paper consumption for different document formats over time.
+
+```{r LIBER-13, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=10, fig.height=8, fig.show="hold", out.width="150px"}
+for (catal in unique(df0$catalog)) {
+  df2 <- subset(df0, catalog == catal) %>% group_by(publication_decade, gatherings) %>% summarize(paper.consumption.km2 = sum(paper.consumption.km2, na.rm = TRUE), n = n()) 
+  df2 <- filter(df2, gatherings %in% setdiff(names(which(table(df2$gatherings) >= 15)), "NA"))
+  df2$highlight <- rep("gray", nrow(df2))
+  df2$highlight[df2$gatherings == "8vo"] <- "darkgreen"
+
+  p <- ggplot(df2, aes(y = paper.consumption.km2,
+                       x = publication_decade,
+  	       shape = gatherings,
+		       linetype = gatherings))		       
+  p <- p + geom_point(size = 4)
+  p <- p + geom_smooth(method = "loess", size = 1,
+         aes(color = highlight, fill = highlight))
+  p <- p + scale_color_manual(values = c("darkgreen", "darkgray"))
+  p <- p + scale_fill_manual(values = c("darkgreen", "darkgray"))  	 
+  p <- p + ggtitle("Paper consumption in time by gatherings")
+  p <- p + xlab("Year")
+  p <- p + ylab("Paper consumption (km2)")
+  p <- p + guides(linetype = guide_legend(keywidth = 5),
+       	          shape = guide_legend(keywidth = 5))
+  p <- p + ggtitle(paste("Paper consumption\n(", catal, ")", sep = ""))
+  print(p)
+}
+```
+
+---
+
+[University curriculum & Enlightenment in Finland]
+
+### Enlightenment literature read in Finland
+
+```{r authors22, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=8, out.width="160px", fig.show="hold"}
 theme_set(theme_bw(20))
@@
 
-### DONE Kungliga subject topics (NEW!!)
-
-Kyrkohistoria; Biblisk arkeologi;Exegetik;Homiletik;Dogmatik;Teologi; Praktisk Teologi; Teologisk etik
-
-```{r ktopic1, echo=FALSE, message=FALSE, warning=FALSE, fig.width=15, fig.height=5}
-catalogue <- "Kungliga"
-years <- c(1640, 1828)
-sel =  tolower(c("Kyrkohistoria", "biblisk arkeologi", "Exegetik", "Homiletik", "Dogmatik", "Teologi", "Praktisk Teologi", "Teologisk etik"))
-places <- c("Stockholm", "Lund", "Greifswald", "Uppsala", "Tartu")
-
-df <- df0 %>% filter(catalog == catalogue)%>%
-  filter(publication_year >= years[[1]] & publication_year <= years[[2]]) %>%
-  filter(publication_place %in% places)
-
-lang <- paste("language.", langs, sep = "")
-otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
-df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
-dfl <- NULL
-for (lan in lang) {
-  dflsub <- filter(df, df[[lan]])
-  if (nrow(dflsub) > 0) {
-    dflsub$language <- gsub("language.", "", lan)
-    dfl <- bind_rows(dfl, dflsub)
-  }
-}
-
-# Selected catalogue and place with selected topics
-pics <- list()
-for (place in places) {
-
-  df <- subset(dfl, publication_place == place)
-
-  df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)  
-  df <- df %>% filter(hit)
-  df <- df %>% group_by(publication_decade, language) %>%
-             summarise(n = n(),
-	               paper = sum(paper.consumption.km2, na.rm = TRUE))
-
-  # PAPER CONSUMPTION
-  theme_set(theme_bw(20))
-  p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
-       geom_bar(aes(fill = language), position = "stack", stat = "identity") +              
-       xlab("Publication year") +
-       ylab("Paper consumption") +
-       ggtitle(place) +
-       xlim(c(years[[1]], years[[2]]))
-  pics[[place]] <- p
-
-}
-
-grid.arrange(pics[[1]], pics[[2]], pics[[3]], pics[[4]], pics[[5]], nrow = 2)
-
-rm(pics)
-```
-
----
-
-Idé- och lärdomshistoria;Antiken;Historia;Militärhistoria;
-
-```{r ktopic2, echo=FALSE, message=FALSE, warning=FALSE, fig.width=15, fig.height=5}
-
-catalogue <- "Kungliga"
-years <- c(1640, 1828)
-sel =  tolower(c("Idé- och lärdomshistoria", "Antiken", "Historia", "Militärhistoria"))
-places <- c("Stockholm", "Lund", "Greifswald", "Uppsala", "Tartu")
-
-df <- df0 %>% filter(catalog == catalogue)%>%
-  filter(publication_year >= years[[1]] & publication_year <= years[[2]]) %>%
-  filter(publication_place %in% places)
-
-lang <- paste("language.", langs, sep = "")
-otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
-df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
-dfl <- NULL
-for (lan in lang) {
-  dflsub <- filter(df, df[[lan]])
-  if (nrow(dflsub) > 0) {
-    dflsub$language <- gsub("language.", "", lan)
-    dfl <- bind_rows(dfl, dflsub)
-  }
-}
-
-# Selected catalogue and place with selected topics
-pics <- list()
-for (place in places) {
-
-  df <- subset(dfl, publication_place == place)
-
-  df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)  
-  df <- df %>% filter(hit)
-  df <- df %>% group_by(publication_decade, language) %>%
-             summarise(n = n(),
-	               paper = sum(paper.consumption.km2, na.rm = TRUE))
-
-  # PAPER CONSUMPTION
-  theme_set(theme_bw(20))
-  p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
-       geom_bar(aes(fill = language), position = "stack", stat = "identity") +              
-       xlab("Publication year") +
-       ylab("Paper consumption") +
-       ggtitle(place) +
-       xlim(c(years[[1]], years[[2]]))
-  pics[[place]] <- p
-
-}
-
-grid.arrange(pics[[1]], pics[[2]], pics[[3]], pics[[4]], pics[[5]], nrow = 2)
-
-rm(pics)
-```
-
----
-
-Filosofi;Metafysik;Logik
-
-```{r ktopic3, echo=FALSE, message=FALSE, warning=FALSE, fig.width=15, fig.height=5}
-
-catalogue <- "Kungliga"
-years <- c(1640, 1828)
-sel =  tolower(c("Filosofi", "Metafysik", "Logik"))
-places <- c("Stockholm", "Lund", "Greifswald", "Uppsala", "Tartu")
-
-df <- df0 %>% filter(catalog == catalogue)%>%
-  filter(publication_year >= years[[1]] & publication_year <= years[[2]]) %>%
-  filter(publication_place %in% places)
-
-lang <- paste("language.", langs, sep = "")
-otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
-df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
-dfl <- NULL
-for (lan in lang) {
-  dflsub <- filter(df, df[[lan]])
-  if (nrow(dflsub) > 0) {
-    dflsub$language <- gsub("language.", "", lan)
-    dfl <- bind_rows(dfl, dflsub)
-  }
-}
-
-# Selected catalogue and place with selected topics
-pics <- list()
-for (place in places) {
-
-  df <- subset(dfl, publication_place == place)
-
-  df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)  
-  df <- df %>% filter(hit)
-  df <- df %>% group_by(publication_decade, language) %>%
-             summarise(n = n(),
-	               paper = sum(paper.consumption.km2, na.rm = TRUE))
-
-  # PAPER CONSUMPTION
-  theme_set(theme_bw(20))
-  p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
-       geom_bar(aes(fill = language), position = "stack", stat = "identity") +              
-       xlab("Publication year") +
-       ylab("Paper consumption") +
-       ggtitle(place) +
-       xlim(c(years[[1]], years[[2]]))
-  pics[[place]] <- p
-
-}
-
-grid.arrange(pics[[1]], pics[[2]], pics[[3]], pics[[4]], pics[[5]], nrow = 2)
-rm(pics)
-```
-
----
-
-4. Naturvetenskap;Matematik;Matematiska tabeller; Kemi;Astronomi;Geografi;Geologi;Meteorologi
-
-```{r ktopic4, echo=FALSE, message=FALSE, warning=FALSE, fig.width=15, fig.height=5}
-
-catalogue <- "Kungliga"
-years <- c(1640, 1828)
-sel =  tolower(c("Naturvetenskap", "Matematik", "Matematiska tabeller", "Kemi", "Astronomi", "Geografi", "Geologi", "Meteorologi"))
-places <- c("Stockholm", "Lund", "Greifswald", "Uppsala", "Tartu")
-
-df <- df0 %>% filter(catalog == catalogue)%>%
-  filter(publication_year >= years[[1]] & publication_year <= years[[2]]) %>%
-  filter(publication_place %in% places)
-
-lang <- paste("language.", langs, sep = "")
-otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
-df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
-dfl <- NULL
-for (lan in lang) {
-  dflsub <- filter(df, df[[lan]])
-  if (nrow(dflsub) > 0) {
-    dflsub$language <- gsub("language.", "", lan)
-    dfl <- bind_rows(dfl, dflsub)
-  }
-}
-
-# Selected catalogue and place with selected topics
-pics <- list()
-for (place in places) {
-
-  df <- subset(dfl, publication_place == place)
-
-  df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)  
-  df <- df %>% filter(hit)
-  df <- df %>% group_by(publication_decade, language) %>%
-             summarise(n = n(),
-	               paper = sum(paper.consumption.km2, na.rm = TRUE))
-
-  # PAPER CONSUMPTION
-  theme_set(theme_bw(20))
-  p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
-       geom_bar(aes(fill = language), position = "stack", stat = "identity") +              
-       xlab("Publication year") +
-       ylab("Paper consumption") +
-       ggtitle(place) +
-       xlim(c(years[[1]], years[[2]]))
-  pics[[place]] <- p
-
-}
-
-grid.arrange(pics[[1]], pics[[2]], pics[[3]], pics[[4]], pics[[5]], nrow = 2)
-rm(pics)
-```
-
----
-
-5. Retorik
-
-```{r ktopic5, echo=FALSE, message=FALSE, warning=FALSE, fig.width=15, fig.height=5}
-
-catalogue <- "Kungliga"
-years <- c(1640, 1828)
-sel =  tolower(c("Retorik"))
-places <- c("Stockholm", "Lund", "Greifswald", "Uppsala", "Tartu")
-
-df <- df0 %>% filter(catalog == catalogue)%>%
-  filter(publication_year >= years[[1]] & publication_year <= years[[2]]) %>%
-  filter(publication_place %in% places)
-
-lang <- paste("language.", langs, sep = "")
-otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
-df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
-dfl <- NULL
-for (lan in lang) {
-  dflsub <- filter(df, df[[lan]])
-  if (nrow(dflsub) > 0) {
-    dflsub$language <- gsub("language.", "", lan)
-    dfl <- bind_rows(dfl, dflsub)
-  }
-}
-
-# Selected catalogue and place with selected topics
-pics <- list()
-for (place in places) {
-
-  df <- subset(dfl, publication_place == place)
-
-  df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)  
-  df <- df %>% filter(hit)
-  df <- df %>% group_by(publication_decade, language) %>%
-             summarise(n = n(),
-	               paper = sum(paper.consumption.km2, na.rm = TRUE))
-
-  # PAPER CONSUMPTION
-  theme_set(theme_bw(20))
-  p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
-       geom_bar(aes(fill = language), position = "stack", stat = "identity") +              
-       xlab("Publication year") +
-       ylab("Paper consumption") +
-       ggtitle(place) +
-       xlim(c(years[[1]], years[[2]]))
-  pics[[place]] <- p
-
-}
-
-grid.arrange(pics[[1]], pics[[2]], pics[[3]], pics[[4]], pics[[5]], nrow = 2)
-rm(pics)
-```
-
----
-
-6. Hebreiska språket; Grekiska språket;Latin
-
-```{r ktopic6, echo=FALSE, message=FALSE, warning=FALSE, fig.width=15, fig.height=5}
-
-catalogue <- "Kungliga"
-years <- c(1640, 1828)
-sel =  tolower(c("Hebreiska språket", "Grekiska språket", "Latin"))
-places <- c("Stockholm", "Lund", "Greifswald", "Uppsala", "Tartu")
-
-df <- df0 %>% filter(catalog == catalogue)%>%
-  filter(publication_year >= years[[1]] & publication_year <= years[[2]]) %>%
-  filter(publication_place %in% places)
-
-lang <- paste("language.", langs, sep = "")
-otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
-df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
-dfl <- NULL
-for (lan in lang) {
-  dflsub <- filter(df, df[[lan]])
-  if (nrow(dflsub) > 0) {
-    dflsub$language <- gsub("language.", "", lan)
-    dfl <- bind_rows(dfl, dflsub)
-  }
-}
-
-# Selected catalogue and place with selected topics
-pics <- list()
-for (place in places) {
-
-  df <- subset(dfl, publication_place == place)
-
-  df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)  
-  df <- df %>% filter(hit)
-  df <- df %>% group_by(publication_decade, language) %>%
-             summarise(n = n(),
-	               paper = sum(paper.consumption.km2, na.rm = TRUE))
-
-  # PAPER CONSUMPTION
-  theme_set(theme_bw(20))
-  p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
-       geom_bar(aes(fill = language), position = "stack", stat = "identity") +              
-       xlab("Publication year") +
-       ylab("Paper consumption") +
-       ggtitle(place) +
-       xlim(c(years[[1]], years[[2]]))
-  pics[[place]] <- p
-
-}
-
-grid.arrange(pics[[1]], pics[[2]], pics[[3]], pics[[4]], pics[[5]], nrow = 2)
-rm(pics)
-```
-
----
-
-7.
-Politisk filosofi;Ekonomiska förhållanden; Nationalekonomi;Lantbruksekonomi;Ekonomi;Penningväsen;Penningvärde;Kreditväsen;Penningförfalskning;Moral;Pedagogik;Uppfsotringsverket;Uppfostran;Barnuppfostran;Jordbruk;Jordbrukslära;Jordbrukspolitik;Fiske
-
-```{r ktopic7, echo=FALSE, message=FALSE, warning=FALSE, fig.width=15, fig.height=5}
-
-catalogue <- "Kungliga"
-years <- c(1640, 1828)
-sel =  tolower(c("Politisk filosofi","Ekonomiska förhållanden"," Nationalekonomi","Lantbruksekonomi","Ekonomi","Penningväsen","Penningvärde","Kreditväsen","Penningförfalskning","Moral","Pedagogik","Uppfsotringsverket","Uppfostran","Barnuppfostran","Jordbruk","Jordbrukslära","Jordbrukspolitik","Fiske"))
-places <- c("Stockholm", "Lund", "Greifswald", "Uppsala", "Tartu")
-
-df <- df0 %>% filter(catalog == catalogue)%>%
-  filter(publication_year >= years[[1]] & publication_year <= years[[2]]) %>%
-  filter(publication_place %in% places)
-
-lang <- paste("language.", langs, sep = "")
-otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
-df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
-dfl <- NULL
-for (lan in lang) {
-  dflsub <- filter(df, df[[lan]])
-  if (nrow(dflsub) > 0) {
-    dflsub$language <- gsub("language.", "", lan)
-    dfl <- bind_rows(dfl, dflsub)
-  }
-}
-
-# Selected catalogue and place with selected topics
-pics <- list()
-for (place in places) {
-
-  df <- subset(dfl, publication_place == place)
-
-  df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)  
-  df <- df %>% filter(hit)
-  df <- df %>% group_by(publication_decade, language) %>%
-             summarise(n = n(),
-	               paper = sum(paper.consumption.km2, na.rm = TRUE))
-
-  # PAPER CONSUMPTION
-  theme_set(theme_bw(20))
-  p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
-       geom_bar(aes(fill = language), position = "stack", stat = "identity") +              
-       xlab("Publication year") +
-       ylab("Paper consumption") +
-       ggtitle(place) +
-       xlim(c(years[[1]], years[[2]]))
-  pics[[place]] <- p
-
-}
-
-grid.arrange(pics[[1]], pics[[2]], pics[[3]], pics[[4]], pics[[5]], nrow = 2)
-rm(pics)
-```
-
----
-
-8. Biologi;Medicinalverket;Medicin;Veterinärmedicin;Medicinalväsen;Medicinalväxkter;Sjukdomar;Djursjukdomar;Djur;Husdjur;Djurskydd;Hästar;Hästkreatur;Hästkörning;Hästavel
-
-```{r ktopic8, echo=FALSE, message=FALSE, warning=FALSE, fig.width=15, fig.height=5}
-
-catalogue <- "Kungliga"
-years <- c(1640, 1828)
-sel =  tolower(c("Biologi","Medicinalverket","Medicin","Veterinärmedicin","Medicinalväsen","Medicinalväxkter","Sjukdomar","Djursjukdomar","Djur","Husdjur","Djurskydd","Hästar","Hästkreatur","Hästkörning","Hästavel"))
-places <- c("Stockholm", "Lund", "Greifswald", "Uppsala", "Tartu")
-
-df <- df0 %>% filter(catalog == catalogue)%>%
-  filter(publication_year >= years[[1]] & publication_year <= years[[2]]) %>%
-  filter(publication_place %in% places)
-
-lang <- paste("language.", langs, sep = "")
-otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
-df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
-dfl <- NULL
-for (lan in lang) {
-  dflsub <- filter(df, df[[lan]])
-  if (nrow(dflsub) > 0) {
-    dflsub$language <- gsub("language.", "", lan)
-    dfl <- bind_rows(dfl, dflsub)
-  }
-}
-
-# Selected catalogue and place with selected topics
-pics <- list()
-for (place in places) {
-
-  df <- subset(dfl, publication_place == place)
-
-  df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)  
-  df <- df %>% filter(hit)
-  df <- df %>% group_by(publication_decade, language) %>%
-             summarise(n = n(),
-	               paper = sum(paper.consumption.km2, na.rm = TRUE))
-
-  # PAPER CONSUMPTION
-  theme_set(theme_bw(20))
-  p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
-       geom_bar(aes(fill = language), position = "stack", stat = "identity") +              
-       xlab("Publication year") +
-       ylab("Paper consumption") +
-       ggtitle(place) +
-       xlim(c(years[[1]], years[[2]]))
-  pics[[place]] <- p
-
-}
-
-grid.arrange(pics[[1]], pics[[2]], pics[[3]], pics[[4]], pics[[5]], nrow = 2)
-rm(pics)
-```
-
----
-
-9. Kvinnor;Kvinnliga textilarbetare;Gravida kvinnor;Adelskvinnor;Kvinnorollen;Ensamstående kvinnor
-
-```{r ktopic9, echo=FALSE, message=FALSE, warning=FALSE, fig.width=15, fig.height=5}
-
-catalogue <- "Kungliga"
-years <- c(1640, 1828)
-sel =  tolower(c("Kvinnor","Kvinnliga textilarbetare","Gravida kvinnor","Adelskvinnor","Kvinnorollen","Ensamstående kvinnor"))
-places <- c("Stockholm", "Lund", "Greifswald", "Uppsala", "Tartu")
-
-df <- df0 %>% filter(catalog == catalogue)%>%
-  filter(publication_year >= years[[1]] & publication_year <= years[[2]]) %>%
-  filter(publication_place %in% places)
-
-lang <- paste("language.", langs, sep = "")
-otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
-df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
-dfl <- NULL
-for (lan in lang) {
-  dflsub <- filter(df, df[[lan]])
-  if (nrow(dflsub) > 0) {
-    dflsub$language <- gsub("language.", "", lan)
-    dfl <- bind_rows(dfl, dflsub)
-  }
-}
-
-# Selected catalogue and place with selected topics
-pics <- list()
-for (place in places) {
-
-  df <- subset(dfl, publication_place == place)
-
-  df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)  
-  df <- df %>% filter(hit)
-  df <- df %>% group_by(publication_decade, language) %>%
-             summarise(n = n(),
-	               paper = sum(paper.consumption.km2, na.rm = TRUE))
-
-  # PAPER CONSUMPTION
-  theme_set(theme_bw(20))
-  p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
-       geom_bar(aes(fill = language), position = "stack", stat = "identity") +              
-       xlab("Publication year") +
-       ylab("Paper consumption") +
-       ggtitle(place) +
-       xlim(c(years[[1]], years[[2]]))
-  pics[[place]] <- p
-
-}
-
-grid.arrange(pics[[1]], pics[[2]], pics[[3]], pics[[4]], pics[[5]], nrow = 2)
-rm(pics)
-```
-
----
-
-10.
-Högmålsbrott;Skattebrott;Brott;Brottslingar;Äktenskapsbrott;Våldsbrott;Trafikbrott;Gäldenärsbrott;Sabbattsbrott;Sexualbrott;Fridsbrott;Ekonomisk brottslighet;Religionsbrott;Juridik;Straff;Dödsstraff;Kroppsstraff;Straffarbete;Straffarbete;Fängelsestraff
-
-```{r ktopic10, echo=FALSE, message=FALSE, warning=FALSE, fig.width=15, fig.height=5}
-
-catalogue <- "Kungliga"
-years <- c(1640, 1828)
-sel =  tolower(c("Högmålsbrott","Skattebrott","Brott","Brottslingar","Äktenskapsbrott","Våldsbrott","Trafikbrott","Gäldenärsbrott","Sabbattsbrott","Sexualbrott","Fridsbrott","Ekonomisk brottslighet","Religionsbrott","Juridik","Straff","Dödsstraff","Kroppsstraff","Straffarbete","Straffarbete","Fängelsestraff"))
-places <- c("Stockholm", "Lund", "Greifswald", "Uppsala", "Tartu")
-
-df <- df0 %>% filter(catalog == catalogue)%>%
-  filter(publication_year >= years[[1]] & publication_year <= years[[2]]) %>%
-  filter(publication_place %in% places)
-
-lang <- paste("language.", langs, sep = "")
-otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
-df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
-dfl <- NULL
-for (lan in lang) {
-  dflsub <- filter(df, df[[lan]])
-  if (nrow(dflsub) > 0) {
-    dflsub$language <- gsub("language.", "", lan)
-    dfl <- bind_rows(dfl, dflsub)
-  }
-}
-
-# Selected catalogue and place with selected topics
-pics <- list()
-for (place in places) {
-
-  df <- subset(dfl, publication_place == place)
-
-  df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)  
-  df <- df %>% filter(hit)
-  df <- df %>% group_by(publication_decade, language) %>%
-             summarise(n = n(),
-	               paper = sum(paper.consumption.km2, na.rm = TRUE))
-
-  # PAPER CONSUMPTION
-  theme_set(theme_bw(20))
-  p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
-       geom_bar(aes(fill = language), position = "stack", stat = "identity") +              
-       xlab("Publication year") +
-       ylab("Paper consumption") +
-       ggtitle(place) +
-       xlim(c(years[[1]], years[[2]]))
-  pics[[place]] <- p
-
-}
-
-grid.arrange(pics[[1]], pics[[2]], pics[[3]], pics[[4]], pics[[5]], nrow = 2)
-rm(pics)
-```
-
----
-
-### Finland in the Swedish context
-
-- Dramatic events regarding the diversity of "Finnishness" take place in the early nineteenth century --- but the analysis of Finnish knowledge production 1828-2016 is for another day.
-
-```{r 201606krakow-turkuvsother, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=5, fig.width=10}
-df <- subset(df0, catalog == "Fennica") %>%
-  filter(publication_year >= 1640 & publication_year <= 1800)%>% 
-      filter(!is.na(country)) %>%
-      filter(!is.na(publication_place) & !is.na(paper.consumption.km2) & paper.consumption.km2 > -0.01)
-
-# Add indicator field: Turku or Not Turku
-myplace <- "Turku"
-
-df$myplace <- rep(NA, nrow(df))
-df$myplace[df$publication_place == myplace] <- myplace
-df$myplace[!df$publication_place == myplace & df$country == "Finland"] <- "Finland"
-df$myplace[!df$country == "Finland" & !df$publication_place == myplace] <- "Foreign"
-df$myplace <- factor(df$myplace, levels = rev(c("Foreign", "Finland", "Turku")))
-
-# Keep entries with known publication place and paper consumption
-# Group by year/decade and Turku/Other
-dfs <- df %>% group_by(publication_decade, myplace) %>%
-  summarise(titles = n(), paper = sum(paper.consumption.km2, na.rm = TRUE))
-
-p <- ggplot(dfs, aes(x = publication_decade, y = titles, fill = myplace, order = -as.numeric(myplace))) +
-     geom_bar(position = "stack", stat = "identity", color = "black") +
-     ggtitle("Title count") +
-     # scale_fill_manual(values = c("blue", "black", "darkgreen")) +
-     scale_fill_grey() +
-     guides(fill = guide_legend(reverse = TRUE, title = "")) +      
-     xlab("Publication decade") + ylab("Title count (n)")
-print(p)
-```
-
----
+### Thanks !
+
+R master (plots & maps):
+- Leo Lahti
+
+Institutional support:
+
+- Academy of Finland
+- University of Helsinki
+- Digitalia / The Regional Council of South Savo
+
+Data providers:
+
+- National Library of Finland
+- National Library of Sweden
+
+---
+
+Extra Slide:
 
@@
 ```
-
----
-
-### Thanks !
-
-R master (plots & maps):
-- Leo Lahti
-
-Institutional support:
-
-- Academy of Finland
-- University of Helsinki
-- Digitalia / The Regional Council of South Savo
-
-Data providers:
-
-- National Library of Finland
-- National Library of Sweden

### 2016-07-11 inst/examples/20160715-slides-Krakow.Rmd
s

@@
 
-Joissain kuvista puuttuu vielä mystisesti ne akselitiedot. Lisäksi Mikko tsekkaa kuvien tekstit yms.
-
-Gävle-kuvan kohtalo pitää tsiigata myös.
+Mikko tsekkaa kuvien tekstit yms.
+
+Gävle-kuva vaihdettu Tukholmaan, pitää tsiigata myös mitkä vuodet highlightataan.
 
@@
 ### Publishing activity in Swedish University Towns (Kungliga)
-
-Turussa kirjantuotanto laskee huomattavasti isonvihan (1710-luku), pikkuvihan (1740-luku) ja Suomen sodan (1808-1809) aikana.
-Pikkuviha ei ollut yhtä dramaattinen, eikä näy niin totaalisesti.
-Suomen sodan (ja Napoleonin sotien) seuraukset olivat tietysti kaikkein dramaattisimmat.
 
@@
 
-TODO: Tässä olisi hyvä olla vuodet näkyvissä. LL: en kyl nyt löydä
-vikaa vaikka pitäis olla hyvin simppeli. Täytyy katsoa lisää
-Krakovassa.
-
 ```{r publishingovertime, echo=FALSE, message=FALSE, warning=FALSE, fig.width=6, fig.height=4, out.width="200px"}
@@
 v <- seq(1500, 1800, 50)
+theme_set(theme_bw(20))
 p <- ggplot(df2, aes(x = publication_decade, y = n)) +
@@
 ### Comparing publishing activity in Swedish University towns
-TODO: Tässä olisi hyvä olla vuodet näkyvissä.
 
@@
 
-```{r publishingactivitycomparisons, echo=FALSE, message=FALSE, cache=TRUE, fig.width=6, fig.height=5, fig.show="hold", out.width="150px"}
+```{r publishingactivitycomparisons, echo=FALSE, message=FALSE, cache=TRUE, fig.width=6, fig.height=5, fig.show="hold", out.width="160px"}
 v <- seq(1500, 1800, 50)
@@
 
-### Role of pamphleteering in 1766-1774
-
-Pamphleteering clearly causes the peak in publishing during the time of abolished censorship in Sweden.
+### Explaining the 1760-1770 publishing peak in Sweden
+
+Role of pamphleteering in 1766-1774 plays a crucial role in the peak in publishing during the time of abolished censorship in Sweden.
 
@@
 
-### Gävle in Riksdagar
+### Stockholm & political events
 
@@
 
-Gävle (gray) during riksdagar (Kungliga) TODO: Lopuks muutetaan takas Gävleks. Nyt ei toimi, siksi Greifswald analyysi tässä.
+TODO: Vaihdettiin tähän Stockholm, riittää julkaisumäärät. Miksi katalogina lukee Fennica?
 
 ```{r riksdar2, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
-  myplace <- "Gavle" # Norrköping / Stockholm
+  myplace <- "Stockholm" # Norrköping / Stockholm
   minyear <- 1700
@@
   dfm <- transform(dfm, date = as.numeric(as.character(Time)))
-  ymin = min(0.0001)
-  ymax = max(dfm$Documents)
+  ymin = min(0.1)
+  ymax = max(60)
 

### 2016-07-11 inst/examples/manuscript-krakow.Rmd
Update manuscript-krakow.Rmd

@@
 
+[University curriculum & Enlightenment in Finland]
+
+### Printing of theology in different languages in Turku
+
+```{r topics-101, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6}
+sel =  c("kirkkohistoria","raamatunhistoria","eksegetiikka","homiletiikka","dogmatiikka","teologia")
+catalogue <- "Fennica"
+
+df <- df0 %>% filter(catalog == catalogue)%>%
+  filter(publication_year >= 1640 & publication_year <= 1800)
+lang <- paste("language.", langs, sep = "")
+otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
+df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
+dfl <- NULL
+for (lan in lang) {
+  dflsub <- filter(df, df[[lan]])
+  if (nrow(dflsub) > 0) {
+    dflsub$language <- gsub("language.", "", lan)
+    dfl <- bind_rows(dfl, dflsub)
+  }
+}
+# Selected catalogue with selected topics
+df <- dfl
+df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)  
+df <- df %>% filter(hit)
+df <- df %>% group_by(publication_decade, language) %>%
+             summarise(n = n(),
+	               paper = sum(paper.consumption.km2, na.rm = TRUE))
+
+  # PAPER CONSUMPTION
+  theme_set(theme_bw(20))
+  p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
+       geom_bar(aes(fill = language), position = "stack", stat = "identity") +              
+       xlab("Publication year") +
+       ylab("Paper consumption") +
+       ggtitle(paste("Paper (", paste(sel, collapse = ";"), ")", sep = ""))
+  print(p)
+```
+
+---
+
+---
+
+TODOja KRAKOVAN JÄLKEEN tehtäviä:
+
+Vaasan merkitys Turun rinnalla 1700-luvun lopulla. Tämä pitää ottaa mukaan analyysiin. Todella mielenkiintoinen case joka myös näkyy tuossa kokonaiskuvassa. Tästä siis tarkemmat analyysit.
+
+---
+
 ### Acknowledgements

### 2016-07-11 inst/examples/20160715-slides-Krakow.Rmd
a

@@
 
-Esitysjärjestys: Sivun 19 slide ("Development of use of different languages in Finnish NationalBibliography") pitäisi tulla sivun 21 sliden ("Different languages in Fennica and Kungliga (percentage)") jälkeen (samalla sivun 20 slide "Development of use of different languages in Kungliga data" putoaa pois).
-Mutta nyt kun muutan järjestystä niin sivun 21 slide ei sen jälkeen toimi.
-Tämä pitää fiksata.
-
-Karttakuvassa Greifswald, Lund ei näy. Tätä pitää vähän miettiä.
+Karttakuvassa Greifswald, Lund ei näy. Tätä olisi hyvä saada kehitettyä, tällaisena tää ei ihan toimi.
 
@@
 
-```{r publishingactivitycomparisons, echo=FALSE, message=FALSE, cache=TRUE, fig.width=6, fig.height=5, fig.show="hold", out.width="160px"}
+```{r publishingactivitycomparisons, echo=FALSE, message=FALSE, cache=TRUE, fig.width=6, fig.height=5, fig.show="hold", out.width="170px"}
 v <- seq(1500, 1800, 50)
@@
 
+### Different languages in Fennica and Kungliga (percentage)
+
+```{r language-perc, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=12, out.width="150px", fig.show="hold"}
+for (catalogue in c("Fennica", "Kungliga")) {
+
+  if (catalogue == "Fennica") {
+    df <- df.full # full time span
+  } else if (catalogue == "Kungliga") {
+    df <- df.full # full time span
+  }
+  langs <- c("Finnish", "Swedish", "Latin", "German", "Russian", "French", "Other")
+  df <- df %>% filter(catalog == catalogue)%>%
+        filter(publication_year >= 1600 & publication_year <= 1900)
+
+  library(dplyr)
+  library(tidyr)
+library(magrittr)
+library(reshape2)
+
+lang <- paste("language.", langs, sep = "")
+otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
+df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
+
+dfl <- NULL
+for (lan in lang) {
+
+  # Classify a document to the specifed language
+  # If document is assigned with languages, each case is considered
+  # so one doc may have multiple entries corresponding to different languages
+  # mean(rowSums(df[, lang]) == 1) # 93% Fennica docs have just 1 language
+  # Combine data frames for specified languages
+  dflsub <- filter(df, df[[lan]])
+  if (nrow(dflsub)>0) {
+    dflsub$language <- gsub("language.", "", lan)
+    dfl <- bind_rows(dfl, dflsub)
+  }
+}
+
+df <- dfl %>% group_by(publication_decade, language) %>%
+     	     summarise(n = n())
+
+# Calculate percentages
+dff <- spread(df, language, n, fill = 0)
+dff[, -1] <- 100 * t(apply(dff[, -1], 1, function (x) {x/sum(x)}))
+dff <- melt(dff, "publication_decade");
+colnames(dff) <- c("publication_decade", "language", "f")
+
+theme_set(theme_bw(20))
+p <- ggplot(dff, aes(x = publication_decade, y = f)) +
+     geom_bar(position = "stack", stat = "identity", aes(fill = language)) + 
+     xlab("Publication year") +
+     ylab("Title count frequency (%)") +
+     ggtitle(paste("Languages (", catalogue, ")", sep = "")) +
+     scale_fill_brewer(palette="Paired")
+print(p)
+}
+```
+
+---
+
+[Languages]
+
 ### Development of use of different languages in Finnish National Bibliography
@@
 
-### Development of use of different languages in Kungliga data
-
-```{r language1-kungliga, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=8, out.width="150px", fig.show="hold"}
-catalogue = "Kungliga"
-  df <- dfl %>% filter(catalog == catalogue) %>%
-     	        group_by(publication_decade, language) %>%
-                summarise(n = n(),
-	               paper = sum(paper.consumption.km2, na.rm = TRUE))
-
-# TITLE COUNT
-p <- ggplot(df, aes(x = publication_decade, y = n, group = language)) +
-       geom_point(aes(col = language, shape = language), size = 5) +
-       geom_line(aes(col = language, shape = language)) +       
-       xlab("Publication year") +
-       ylab("Title count (n)") +
-       ggtitle(paste("Languages (", catalogue, ")", sep = ""))
-print(p)
-
-# PAPER CONSUMPTION
-p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
-       geom_point(aes(col = language, shape = language), size = 5) +
-       geom_line(aes(col = language, shape = language)) +       
-       xlab("Publication year") +
-       ylab("Paper consumption") +
-       ggtitle(paste("Languages (", catalogue, ")", sep = ""))
-print(p)
-```
-
----
-
-[Languages]
-
-### Different languages in Fennica and Kungliga (percentage)
-
-```{r language-perc, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=12, out.width="150px", fig.show="hold"}
-for (catalogue in c("Fennica", "Kungliga")) {
-
-  if (catalogue == "Fennica") {
-    df <- df.full # full time span
-  } else if (catalogue == "Kungliga") {
-    df <- df.full # full time span
-  }
-  df <- df %>% filter(catalog == catalogue)%>%
-        filter(publication_year >= 1600 & publication_year <= 1900)
-
-  library(dplyr)
-  library(tidyr)
-library(magrittr)
-library(reshape2)
-
-lang <- paste("language.", langs, sep = "")
-otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
-df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
-
-dfl <- NULL
-for (lan in lang) {
-
-  # Classify a document to the specifed language
-  # If document is assigned with languages, each case is considered
-  # so one doc may have multiple entries corresponding to different languages
-  # mean(rowSums(df[, lang]) == 1) # 93% Fennica docs have just 1 language
-  # Combine data frames for specified languages
-  dflsub <- filter(df, df[[lan]])
-  if (nrow(dflsub)>0) {
-    dflsub$language <- gsub("language.", "", lan)
-    dfl <- bind_rows(dfl, dflsub)
-  }
-}
-
-df <- dfl %>% group_by(publication_decade, language) %>%
-     	     summarise(n = n())
-
-# Calculate percentages
-dff <- spread(df, language, n, fill = 0)
-dff[, -1] <- 100 * t(apply(dff[, -1], 1, function (x) {x/sum(x)}))
-dff <- melt(dff, "publication_decade");
-colnames(dff) <- c("publication_decade", "language", "f")
-
-theme_set(theme_bw(20))
-p <- ggplot(dff, aes(x = publication_decade, y = f)) +
-     geom_bar(position = "stack", stat = "identity", aes(fill = language)) + 
-     xlab("Publication year") +
-     ylab("Title count frequency (%)") +
-     ggtitle(paste("Languages (", catalogue, ")", sep = "")) +
-     scale_fill_brewer(palette="Paired")
-print(p)
-}
-```
-
----
-
-[Languages]
-
 ### Different languages in Turku, Stockholm, Lund and Uppsala
@@
      scale_fill_brewer(palette="Paired")
-print(p)
-```
-
----
-
-[University curriculum & Enlightenment in Finland]
-
-### Printing of theology in different languages in Turku
-
-```{r topics-101, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6}
-sel =  c("kirkkohistoria","raamatunhistoria","eksegetiikka","homiletiikka","dogmatiikka","teologia")
-catalogue <- "Fennica"
-
-df <- df0 %>% filter(catalog == catalogue)%>%
-  filter(publication_year >= 1640 & publication_year <= 1800)
-lang <- paste("language.", langs, sep = "")
-otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
-df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
-dfl <- NULL
-for (lan in lang) {
-  dflsub <- filter(df, df[[lan]])
-  if (nrow(dflsub) > 0) {
-    dflsub$language <- gsub("language.", "", lan)
-    dfl <- bind_rows(dfl, dflsub)
-  }
-}
-# Selected catalogue with selected topics
-df <- dfl
-df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)  
-df <- df %>% filter(hit)
-df <- df %>% group_by(publication_decade, language) %>%
-             summarise(n = n(),
-	               paper = sum(paper.consumption.km2, na.rm = TRUE))
-
-  # PAPER CONSUMPTION
-  theme_set(theme_bw(20))
-  p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
-       geom_bar(aes(fill = language), position = "stack", stat = "identity") +              
-       xlab("Publication year") +
-       ylab("Paper consumption") +
-       ggtitle(paste("Paper (", paste(sel, collapse = ";"), ")", sep = ""))
 print(p)

### 2016-07-11 inst/examples/20160715-slides-Krakow.Rmd
as

@@
 
-Karttakuvassa Greifswald, Lund ei näy. Tätä olisi hyvä saada kehitettyä, tällaisena tää ei ihan toimi.
-
-Dissertation languages: kategoria "other" sisällön selvittäminen!
-
-Mikko tsekkaa kuvien tekstit yms.
-
-Gävle-kuva vaihdettu Tukholmaan, pitää tsiigata myös mitkä vuodet highlightataan.
+sivu 3. Datamäärät koodista tähän takaisin. Deletoin tän vahingossa aikaisemmin kun koodi ei toiminut.
+
+sivu 8. Karttakuvassa Greifswald, Lund ei näy. Tätä olisi hyvä saada kehitettyä, tällaisena tää ei ihan toimi.
+
+sivu 12. Gävle-kuva vaihdettu Tukholmaan, pitää tsiigata mitkä vuodet highlightataan. Tällaisena ei vielä toimi.
+
+sivu 27. Dissertation languages: kategoria "other" sisällön selvittäminen!
+
+Yleisesti eri kuvien tekstit yms. tsekkaaminen, korostukset yms.
 
@@
 
-1) Big picture and political events
+1) Big picture & political events
 
@@
 
-3) Languages and religious publishing in Finland
+3) Languages & religious texts in Finland
 
@@
 
-### Big Picture & Political Events
+### 1. Big Picture & Political Events
 
@@
 
-### Peaks and drops – role of publishers and contingency
+### Fennica drop in 1700-1721, Kungliga peak in 1760-1770s, effect of Napoleonic wars (1803-1815)
 
@@
 
-### Publishers
+### 2. Publishers
 
@@
 
-### Languages
-
----
-
-[Languages]
+### 3. Languages & religious texts in Finland
+
+---
+
+[Languages & religious texts in Finland]
 
@@
 
-[Languages]
+[Languages & religious texts in Finland]
 
@@
 
-### Religious texts in Finland
-
----
-
-[Religious texts in Finland]
+[Languages & religious texts in Finland]
 
@@
 
-[Religious texts in Finland]
+[Languages & religious texts in Finland]
 
@@
 
-### University curriculum & Enlightenment in Finland
+### 4. University curriculum & Enlightenment in Finland
 

### 2016-07-11 inst/examples/notebook.Rmd
ok

--- 2016-07-11 inst/examples/20160715-slides-Krakow.Rmd
@@
 ---
-title: "Printing in a Periphery: a Quantitative Study of Finnish Knowledge Production, 1640-1828"
+title: 'Printing in a Periphery: a Quantitative Study of Finnish Knowledge Production,
+  1640-1828'
 author: "Mikko Tolonen, Jani Marjanen, Hege Roivainen, Leo Lahti"
-date: "`r Sys.Date()`"
+date: '`r Sys.Date()`'
 output:
-  beamer_presentation
+  word_document: default
+  pdf_document: default
+  html_notebook: default
 ---
@@
 
-sivu 12. Gävle-kuva vaihdettu Tukholmaan, pitää tsiigata mitkä vuodet highlightataan. Tällaisena ei vielä toimi.
+sivu 12. Gävle-kuva vaihdettu Tukholmaan, pitää tsiigata mitkä vuodet highlightataan. Tällaisena ei vielä toimi. Onhan katalogi oikein?
 
@@
 
-### Outline of the presentation
-
-1) Big picture & political events
+### Outline of Quantitative Study of Finnish Knowledge Production, 1640-1828
+
+1) General trends & political events
 
@@
 
-### 1. Big Picture & Political Events
-
----
-
-[Big Picture & Political Events]
+### 1. General trends & political events
+
+---
+
+[General trends & political events]
 
@@
 
-[Big Picture & Political Events]
+[General trends & political events]
 
@@
 
-[Big Picture & Political Events]
-
-### Stockholm & political events
+[General trends & political events]
+
+### Stockholm & democratic cycles
 
@@
 
-TODO: Vaihdettiin tähän Stockholm, riittää julkaisumäärät. Miksi katalogina lukee Fennica?
+TODO: Vaihdettiin tähän Stockholm, riittää julkaisumäärät. Miksi katalogina lukee Fennica? Pitää olla Kungligan mukaan data tässä.
 
@@
 
-### 2. Publishers
-
----
-
-[Publishers]
+### 2. Publishers in Sweden and Turku
+
+---
+
+[Publishers in Sweden and Turku]
 
@@
 
-[Publishers]
+[Publishers in Sweden and Turku]
 
@@
 
-### Printing of history in different languages in Turku
-
-```{r topics-102, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6}
-sel = c("oppihistoria","antiikki","historia")
+### Printing of philosophy in different languages in Turku
+
+```{r topics-103, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6}
+sel = c("filosofia","luonnonfilosofia","metafysiikka","logiikka")
 # Selected catalogue with selected topics
@@
 
-### Printing of philosophy in different languages in Turku
-
-```{r topics-103, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6}
-sel = c("filosofia","luonnonfilosofia","metafysiikka","logiikka")
+### Printing of history in different languages in Turku
+
+```{r topics-102, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6}
+sel = c("oppihistoria","antiikki","historia")
 # Selected catalogue with selected topics

### 2016-07-11 inst/examples/20160715-slides-Krakow.Rmd
s
sa

@@
 
-**How?** By combining library catalogues (Fennica, Kungliga, ESTC, CERL)
+**How?** By combining library catalogues (Fennica, Kungliga, ESTC, CERL's HPB database)
 
@@
 
----
-
-[Intro]
+Overcoming a national gaze in the analysis by focusing on how knowledge production happened through a more complex network of cities.
+
+---
 
@@
 
-- Open source tools for library catalogues (Github)
+- Open source tools for library catalogues (Github/Fennica)
 
@@
 
-[Intro]
-
-### Context
-
-- Finnish knowledge production 1640-1828 can only be understood in the Swedish context.
-
-- Academy of Turku as part of the Swedish University system is the centre of Finnish knowledge production.
-
-### Challenges: nationally delineated perspectives by using nationally collected materials
-
-Overcoming a national gaze in the analysis by focusing on how knowledge production happened through a more complex network of cities.
-
----
-
-### Outline of the presentation
-
-1) Big picture & political events
+### Outline of Quantitative Study of Finnish Knowledge Production, 1640-1828
+
+1) General trends & political events
 
@@
 
-### Development of use of different languages in Finnish National Bibliography
-
-```{r language1, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=8, out.width="160px", fig.show="hold"}
+### Different languages in Turku, Stockholm, Lund and Uppsala
+
+```{r language-perc2, echo=FALSE, message=FALSE, warning=FALSE, fig.width=20, fig.height=15}
+pics <- list()
+theme_set(theme_bw(20))
+myplaces <- c("Turku", "Greifswald", "Stockholm", "Uppsala", "Lund")
+
+for (catalogue in c("Fennica", "Kungliga")) {
+
+  df <- df0 %>% filter(catalog == catalogue) %>%
+        filter(publication_year >= 1600 & publication_year <= 1828)
+
+  lang <- paste("language.", langs, sep = "")
+  otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
+  df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
+
+  dfl <- NULL
+  for (lan in lang) {
+
+    # Classify a document to the specifed language
+    # If document is assigned with languages, each case is considered
+    # so one doc may have multiple entries corresponding to different languages
+    # mean(rowSums(df[, lang]) == 1) # 93% Fennica docs have just 1 language
+    # Combine data frames for specified languages
+    dflsub <- filter(df, df[[lan]])
+    if (nrow(dflsub) > 0) {
+      dflsub$language <- gsub("language.", "", lan)
+      dfl <- bind_rows(dfl, dflsub)
+    }
+  }
+
+  df <- dfl %>% group_by(publication_decade, publication_place, language) %>%
+     	     summarise(n = n())
+
+  # Calculate percentages
+  dff <- spread(df, language, n, fill = 0)
+  dff[, -c(1,2)] <- 100 * t(apply(dff[, -c(1,2)], 1, function (x) {x/sum(x)}))
+
+  dff <- melt(dff, id = c("publication_place", "publication_decade"))
+  colnames(dff) <- c("publication_place", "publication_decade", "language", "f")
+
+  for (myplace in myplaces) {
+    p <- ggplot(subset(dff, publication_place == myplace), aes(x = publication_decade, y = f)) +
+      geom_bar(position = "stack", stat = "identity", aes(fill = language)) + 
+      xlab("Publication year") +
+      ylab("Title count frequency (%)") +
+      ggtitle(paste("Languages (", myplace, "/", catalogue, ")", sep = "")) +
+      scale_fill_brewer(palette="Paired")
+    pics[[paste(catalogue, myplace, sep = "-")]] <- p
+  }
+}
+
+grid.arrange(pics[[1]],
+             pics[[8]], pics[[9]], pics[[10]], 
+             nrow = 2)
+
+rm(pics)
+```
+
+---
+
+[Languages & religious texts in Finland]
+
+### Topic diversity in different languages in Finnish publications
+
+```{r topics232, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, fig.show="hold"}
 catalogue <- "Fennica"
-df <- df0
-langs <- c("Finnish", "Swedish", "Latin", "German", "Russian", "French", "Other")
+df <- filter(df0, catalog == "Fennica") %>%
+  filter(publication_year >= 1640 & publication_year <= 1828) %>%
+  select(publication_year, language, subject_topic)
+df <- unique(df)
+df <- df %>% group_by(publication_year, language) %>%
+             summarise(n = length(unique(unlist(strsplit(subject_topic, ";")))))
+
+df$language[!df$language %in% langs] <- "Other"
+df$language <- factor(df$language, levels = langs)
+
+p <- ggplot(df, aes(x = publication_year, y = n, color = language)) +
+       geom_line() + geom_point() +
+       ggtitle("Number of subject topics")
+
+print(p)
+```
+
+---
+
+[Languages & religious texts in Finland]
+
+### Devotional literature (catechisms, hymns, prayer collections, etc.)
+
+- Form of literature denoting the advancement of reading in Finland in the nineteenth century. It has been unclear when does it show up as a relevant category.
+
+```{r topics12122, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, fig.show="hold"}
+# https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/topics-2.png
+sel <- c("virret","arkkiveisut","hartauskirjat","katekismukset","rukouspäivät","saarnat","aapiset","rukoukset","rukous","hengelliset laulut","hartauspuheet","virsikirjat")
+catalogue <- "Fennica"
+
+  # Selected catalogue with selected years
+  df <- filter(df0, catalog == catalogue &
+     		    publication_year >= 1640 &
+		    publication_year <= 1828)
+
+  # Selected topics
+  df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)  
+  df <- df %>% filter(catalog == catalogue & hit)
+
   lang <- paste("language.", langs, sep = "")
@@
   }
-
-# ----------------------------------
-
-df <- dfl %>% filter(catalog == catalogue)
-df <- df %>% group_by(publication_decade, language) %>%
+  df <- dfl %>% group_by(publication_decade, language) %>%
              summarise(n = n(),
@@
 
-# TITLE COUNT
-p <- ggplot(df, aes(x = publication_decade, y = n, group = language)) +
-       geom_point(aes(col = language, shape = language), size = 5) +
-       geom_line(aes(col = language, shape = language)) +       
-       xlab("Publication year") +
-       ylab("Title count (n)") +
-       ggtitle(paste("Languages (", catalogue, ")", sep = ""))
-print(p)
-
   # PAPER CONSUMPTION
+  theme_set(theme_bw(20))
   p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
@@
 
-### Different languages in Turku, Stockholm, Lund and Uppsala
-
-```{r language-perc2, echo=FALSE, message=FALSE, warning=FALSE, fig.width=20, fig.height=15}
-pics <- list()
-theme_set(theme_bw(20))
-myplaces <- c("Turku", "Greifswald", "Stockholm", "Uppsala", "Lund")
-
-for (catalogue in c("Fennica", "Kungliga")) {
-
-  df <- df0 %>% filter(catalog == catalogue) %>%
-        filter(publication_year >= 1600 & publication_year <= 1828)
-
+### Temporary sermons in Latin and Swedish
+
+- play an important role in early modern knowledge production. It has not been analysed in what language they were in Finland (and Sweden).
+
+```{r topics882, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6}
+  sel <- c("hautajaiset", "häät", "juhlamenot")
+  catalogue <- "Fennica"
+  df <- df0
+  df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)
+
+  # Selected catalogue with selected topics
+  df <- df %>% filter(catalog == catalogue & hit)
   lang <- paste("language.", langs, sep = "")
@@
   for (lan in lang) {
-
     # Classify a document to the specifed language
@@
 }
-
-  df <- dfl %>% group_by(publication_decade, publication_place, language) %>%
-     	     summarise(n = n())
-
-  # Calculate percentages
-  dff <- spread(df, language, n, fill = 0)
-  dff[, -c(1,2)] <- 100 * t(apply(dff[, -c(1,2)], 1, function (x) {x/sum(x)}))
-
-  dff <- melt(dff, id = c("publication_place", "publication_decade"))
-  colnames(dff) <- c("publication_place", "publication_decade", "language", "f")
-
-  for (myplace in myplaces) {
-    p <- ggplot(subset(dff, publication_place == myplace), aes(x = publication_decade, y = f)) +
-      geom_bar(position = "stack", stat = "identity", aes(fill = language)) + 
-      xlab("Publication year") +
-      ylab("Title count frequency (%)") +
-      ggtitle(paste("Languages (", myplace, "/", catalogue, ")", sep = "")) +
-      scale_fill_brewer(palette="Paired")
-    pics[[paste(catalogue, myplace, sep = "-")]] <- p
-  }
-}
-
-grid.arrange(pics[[1]],
-             pics[[8]], pics[[9]], pics[[10]], 
-             nrow = 2)
-
-rm(pics)
+dfl$language <- factor(dfl$language, levels = langs)
+
+  df <- dfl %>% group_by(publication_decade, language) %>%
+             summarise(n = n(),
+	               paper = sum(paper.consumption.km2, na.rm = TRUE))
+
+  # PAPER CONSUMPTION
+  p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
+       geom_point(aes(col = language, shape = language), size = 5) +
+       geom_line(aes(col = language, shape = language)) +       
+       xlab("Publication year") +
+       ylab("Paper consumption") +
+       ggtitle(paste("Languages (", catalogue, ")", sep = ""))
+  print(p)
 ```
@@
 
-### Topic diversity in different languages in Finnish publications
-
-```{r topics232, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, fig.show="hold"}
+### Combining devotional literature and temporary sermons
+
+```{r topics3, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6}
+sel <- c("virret","arkkiveisut","hartauskirjat","katekismukset","rukouspäivät","saarnat","aapiset","rukoukset","rukous","hengelliset laulut","hartauspuheet","virsikirjat","hautajaiset","häät","juhlamenot")
 catalogue <- "Fennica"
-df <- filter(df0, catalog == "Fennica") %>%
-  filter(publication_year >= 1640 & publication_year <= 1828) %>%
-  select(publication_year, language, subject_topic)
-df <- unique(df)
-df <- df %>% group_by(publication_year, language) %>%
-             summarise(n = length(unique(unlist(strsplit(subject_topic, ";")))))
-
-df$language[!df$language %in% langs] <- "Other"
-df$language <- factor(df$language, levels = langs)
-
-p <- ggplot(df, aes(x = publication_year, y = n, color = language)) +
-       geom_line() + geom_point() +
-       ggtitle("Number of subject topics")
-
-print(p)
-```
-
----
-
-[Languages & religious texts in Finland]
-
-### Devotional literature (catechisms, hymns, prayer collections, etc.)
-
-- Form of literature denoting the advancement of reading in Finland in the nineteenth century. It has been unclear when does it show up as a relevant category.
-
-```{r topics12122, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, fig.show="hold"}
-# https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/topics-2.png
-sel <- c("virret","arkkiveisut","hartauskirjat","katekismukset","rukouspäivät","saarnat","aapiset","rukoukset","rukous","hengelliset laulut","hartauspuheet","virsikirjat")
-catalogue <- "Fennica"
+  df <- df0 # selected time span
+  df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)
+
+  # Selected catalogue with selected topics
+  df <- df %>% filter(catalog == catalogue & hit)
 
   # Selected catalogue with selected years
-  df <- filter(df0, catalog == catalogue &
-     		    publication_year >= 1640 &
-		    publication_year <= 1828)
-
-  # Selected topics
-  df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)  
-  df <- df %>% filter(catalog == catalogue & hit)
+  df = filter(df0, catalog == catalogue & publication_year >= 1640 & publication_year <= 1828)
 
@@
 }
-  df <- dfl %>% group_by(publication_decade, language) %>%
-             summarise(n = n(),
-	               paper = sum(paper.consumption.km2, na.rm = TRUE))
-
-  # PAPER CONSUMPTION
-  theme_set(theme_bw(20))
-  p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
-       geom_point(aes(col = language, shape = language), size = 5) +
-       geom_line(aes(col = language, shape = language)) +       
-       xlab("Publication year") +
-       ylab("Paper consumption") +
-       ggtitle(paste("Languages (", catalogue, ")", sep = "")) 
-  print(p)
-```
-
----
-
-[Languages & religious texts in Finland]
-
-### Temporary sermons in Latin and Swedish
-
-- play an important role in early modern knowledge production. It has not been analysed in what language they were in Finland (and Sweden).
-
-```{r topics882, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6}
-  sel <- c("hautajaiset", "häät", "juhlamenot")
-  catalogue <- "Fennica"
-  df <- df0
-  df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)
-
-  # Selected catalogue with selected topics
-  df <- df %>% filter(catalog == catalogue & hit)
-  lang <- paste("language.", langs, sep = "")
-  otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
-  df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
-
-  dfl <- NULL
-  for (lan in lang) {
-    # Classify a document to the specifed language
-    # If document is assigned with languages, each case is considered
-    # so one doc may have multiple entries corresponding to different languages
-    # mean(rowSums(df[, lang]) == 1) # 93% Fennica docs have just 1 language
-    # Combine data frames for specified languages
-    dflsub <- filter(df, df[[lan]])
-    if (nrow(dflsub) > 0) {
-      dflsub$language <- gsub("language.", "", lan)
-    dfl <- bind_rows(dfl, dflsub)
-  }
-}
-dfl$language <- factor(dfl$language, levels = langs)
-
-  df <- dfl %>% group_by(publication_decade, language) %>%
-             summarise(n = n(),
-	               paper = sum(paper.consumption.km2, na.rm = TRUE))
-
-  # PAPER CONSUMPTION
-  p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
-       geom_point(aes(col = language, shape = language), size = 5) +
-       geom_line(aes(col = language, shape = language)) +       
-       xlab("Publication year") +
-       ylab("Paper consumption") +
-       ggtitle(paste("Languages (", catalogue, ")", sep = ""))
-  print(p)
-```
-
----
-
-[Languages & religious texts in Finland]
-
-### Combining devotional literature and temporary sermons
-
-```{r topics3, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6}
-sel <- c("virret","arkkiveisut","hartauskirjat","katekismukset","rukouspäivät","saarnat","aapiset","rukoukset","rukous","hengelliset laulut","hartauspuheet","virsikirjat","hautajaiset","häät","juhlamenot")
-catalogue <- "Fennica"
-  df <- df0 # selected time span
-  df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)
-
-  # Selected catalogue with selected topics
-  df <- df %>% filter(catalog == catalogue & hit)
-
-  # Selected catalogue with selected years
-  df = filter(df0, catalog == catalogue & publication_year >= 1640 & publication_year <= 1828)
-
-  lang <- paste("language.", langs, sep = "")
-  otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
-  df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
-  dfl <- NULL
-  for (lan in lang) {
-    # Classify a document to the specifed language
-    # If document is assigned with languages, each case is considered
-    # so one doc may have multiple entries corresponding to different languages
-    # mean(rowSums(df[, lang]) == 1) # 93% Fennica docs have just 1 language
-    # Combine data frames for specified languages
-    dflsub <- filter(df, df[[lan]])
-    if (nrow(dflsub) > 0) {
-      dflsub$language <- gsub("language.", "", lan)
-      dfl <- bind_rows(dfl, dflsub)
-    }
-}
 
@@
        scale_fill_manual(values = c("blue", "red")) + 
-       ggtitle(paste("Duplicates", paste(range(na.omit(df$publication_decade)), collapse = "-")))
-
-print(p)
-```
+       ggtitle(paste("Certain duplicates Fennica-Kungliga", paste(range(na.omit(df$publication_decade)), collapse = "-")))
+
+print(p)
+```

### 2016-07-11 inst/examples/manuscript-krakow.Rmd
Update manuscript-krakow.Rmd

@@
 
+[Languages & religious texts in Finland]
+
+### Development of use of different languages in Finnish National Bibliography
+
+```{r language1, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=8, out.width="160px", fig.show="hold"}
+catalogue <- "Fennica"
+df <- df0
+langs <- c("Finnish", "Swedish", "Latin", "German", "Russian", "French", "Other")
+lang <- paste("language.", langs, sep = "")
+otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
+df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
+dfl <- NULL
+for (lan in lang) {
+  # Classify a document to the specifed language
+  # If document is assigned with languages, each case is considered
+  # so one doc may have multiple entries corresponding to different languages
+  # mean(rowSums(df[, lang]) == 1) # 93% Fennica docs have just 1 language
+  # Combine data frames for specified languages
+  dflsub <- filter(df, df[[lan]])
+  if (nrow(dflsub) > 0) {
+    dflsub$language <- gsub("language.", "", lan)
+    dfl <- bind_rows(dfl, dflsub)
+  }
+}
+
+# ----------------------------------
+
+df <- dfl %>% filter(catalog == catalogue)
+df <- df %>% group_by(publication_decade, language) %>%
+             summarise(n = n(),
+                 paper = sum(paper.consumption.km2, na.rm = TRUE))
+
+# TITLE COUNT
+p <- ggplot(df, aes(x = publication_decade, y = n, group = language)) +
+       geom_point(aes(col = language, shape = language), size = 5) +
+       geom_line(aes(col = language, shape = language)) +       
+       xlab("Publication year") +
+       ylab("Title count (n)") +
+       ggtitle(paste("Languages (", catalogue, ")", sep = ""))
+print(p)
+
+# PAPER CONSUMPTION
+p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
+       geom_point(aes(col = language, shape = language), size = 5) +
+       geom_line(aes(col = language, shape = language)) +       
+       xlab("Publication year") +
+       ylab("Paper consumption") +
+       ggtitle(paste("Languages (", catalogue, ")", sep = ""))
+print(p)
+```
+---
+
 [Languages]
@@
 ---
+# Context
+
+- Finnish knowledge production 1640-1828 can only be understood in the Swedish context.
+
+- Academy of Turku as part of the Swedish University system is the centre of Finnish knowledge production.
+
+### Challenges: nationally delineated perspectives by using nationally collected materials
 

### 2016-07-11 inst/examples/manuscript-krakow.Rmd
Update manuscript-krakow.Rmd

@@
 ```
+---
+
+[Publishers in Sweden and Turku]
+
+### Rock Bottom of the Great Northern War (1700-1721)
+
+Publisher title count changes around 1700 with a nearly detrimental drop in Turku, significant publishing place in Finland at the time.
+
+```{r drop1700B, echo=FALSE, message=FALSE, warning=FALSE, fig.width=15, fig.height=7}
+# https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/drop1700B-1.png
+
+catalogue <- "Fennica"
+place <- "Turku"
+
+df <- df0
+df <- df %>%
+        filter(catalog == catalogue & publication_place == place) %>%
+        filter(publication_year >= 1650 & publication_year < 1750)
+
+# Selected ones
+top <- names(top(df, "publisher", 5))
+df$publisher[!df$publisher %in% top] <- "Other"
+df$publisher <- factor(df$publisher, levels = c(top, "Other"))
+
+# Publishing per year & publisher	
+npub <- df %>%
+     	  group_by(publication_year, publisher) %>%
+	  summarize(paper = sum(paper.consumption.km2, na.rm = TRUE), n = n())
+
+theme_set(theme_bw(20))
+p <- ggplot(npub, aes(x = publication_year, y = n, group = publisher)) +
+       geom_point(size = 5, aes(shape = publisher, color = publisher)) +
+       geom_smooth(col = "black", aes(shape = publisher, fill = publisher, color = publisher)) + 
+       xlab("Publication year") +
+       ylab("Title count (n)") +
+       ylim(c(0, 1.1*max(npub$n))) +
+       ggtitle(paste("Title count (", place, "/", catalogue, ")", sep = ""))
+print(p)
+```
 

### 2016-07-11 inst/examples/20160715-slides-Krakow.Rmd
a
s

@@
 
-Overcoming a national gaze in the analysis by focusing on how knowledge production happened through a more complex network of cities.
-
----
-
-### Data (1470-1828):
+**Overcoming a national gaze** by focusing on how knowledge production happened through a more complex network of cities.
+
+---
+
+### Data (1640-1828):
 
@@
 
-### Publishing activity in Swedish University Towns (Kungliga)
+### Turku as a Swedish University Town among Uppsala, Tartu and Stockholm (+ Greifswald and Lund)
 
@@
 	      publication_place %in% c("Stockholm", "Uppsala",
-	                         "Greifwald", "Lund", "Tartu"))|
+	                         "Greifswald", "Lund", "Tartu"))|
 	  (catalog == "Fennica" &
@@
 
+#library(gridExtra)
+#grid.arrange(pics[[1]], pics[[2]], pics[[3]], pics[[4]], nrow = 1)
 library(gridExtra)
-grid.arrange(pics[[1]], pics[[2]], pics[[3]], pics[[4]], nrow = 1)
+grid.arrange(pics[[1]], nrow = 1)
 ```
@@
 
-### Comparing publishing activity in Swedish University towns
-
-Turku / Uppsala / Lund / Stockholm
+### Comparing publishing activity in Stockholm and Turku
 
@@
 v <- seq(1500, 1800, 50)
-selected.places = c("Turku", "Uppsala", "Lund", "Stockholm")
+selected.places = c("Turku", "Stockholm")
 df2 <- df0 %>% group_by(publication_decade, publication_place, catalog) %>%
@@
 
-[Publishers in Sweden and Turku]
-
-### Rock Bottom of the Great Northern War (1700-1721)
-
-Publisher title count changes around 1700 with a nearly detrimental drop in Turku, significant publishing place in Finland at the time.
-
-```{r drop1700B, echo=FALSE, message=FALSE, warning=FALSE, fig.width=15, fig.height=7}
-# https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/drop1700B-1.png
-
-catalogue <- "Fennica"
-place <- "Turku"
-
-df <- df0
-df <- df %>%
-        filter(catalog == catalogue & publication_place == place) %>%
-        filter(publication_year >= 1650 & publication_year < 1750)
-
-# Selected ones
-top <- names(top(df, "publisher", 5))
-df$publisher[!df$publisher %in% top] <- "Other"
-df$publisher <- factor(df$publisher, levels = c(top, "Other"))
-
-# Publishing per year & publisher	
-npub <- df %>%
-     	  group_by(publication_year, publisher) %>%
-	  summarize(paper = sum(paper.consumption.km2, na.rm = TRUE), n = n())
-
-theme_set(theme_bw(20))
-p <- ggplot(npub, aes(x = publication_year, y = n, group = publisher)) +
-       geom_point(size = 5, aes(shape = publisher, color = publisher)) +
-       geom_smooth(col = "black", aes(shape = publisher, fill = publisher, color = publisher)) + 
-       xlab("Publication year") +
-       ylab("Title count (n)") +
-       ylim(c(0, 1.1*max(npub$n))) +
-       ggtitle(paste("Title count (", place, "/", catalogue, ")", sep = ""))
-print(p)
-```
-
----
-
 ### 3. Languages & religious texts in Finland
@@
        geom_line(aes(col = language, shape = language)) +       
-       xlab("Publication year") +
-       ylab("Paper consumption") +
-       ggtitle(paste("Languages (", catalogue, ")", sep = ""))
-  print(p)
-```
-
----
-
-[Languages & religious texts in Finland]
-
-### Combining devotional literature and temporary sermons
-
-```{r topics3, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6}
-sel <- c("virret","arkkiveisut","hartauskirjat","katekismukset","rukouspäivät","saarnat","aapiset","rukoukset","rukous","hengelliset laulut","hartauspuheet","virsikirjat","hautajaiset","häät","juhlamenot")
-catalogue <- "Fennica"
-  df <- df0 # selected time span
-  df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)
-
-  # Selected catalogue with selected topics
-  df <- df %>% filter(catalog == catalogue & hit)
-
-  # Selected catalogue with selected years
-  df = filter(df0, catalog == catalogue & publication_year >= 1640 & publication_year <= 1828)
-
-  lang <- paste("language.", langs, sep = "")
-  otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
-  df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
-  dfl <- NULL
-  for (lan in lang) {
-    # Classify a document to the specifed language
-    # If document is assigned with languages, each case is considered
-    # so one doc may have multiple entries corresponding to different languages
-    # mean(rowSums(df[, lang]) == 1) # 93% Fennica docs have just 1 language
-    # Combine data frames for specified languages
-    dflsub <- filter(df, df[[lan]])
-    if (nrow(dflsub) > 0) {
-      dflsub$language <- gsub("language.", "", lan)
-      dfl <- bind_rows(dfl, dflsub)
-    }
-}
-
-  # -------------------------------------------
-
-  df <- dfl %>% group_by(publication_decade, language) %>%
-             summarise(n = n(),
-	               paper = sum(paper.consumption.km2, na.rm = TRUE))
-
-  # PAPER CONSUMPTION
-  p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
-       #geom_point(aes(col = language, shape = language), size = 5) +
-       #geom_line(aes(col = language, shape = language)) +
-       geom_bar(stat = "identity", aes(fill = language, )) +              
        xlab("Publication year") +

### 2016-07-11 inst/examples/manuscript-krakow.Rmd

@@
 ```
+---
+
+[Languages & religious texts in Finland]
+
+### Combining devotional literature and temporary sermons
+
+```{r topics3, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6}
+sel <- c("virret","arkkiveisut","hartauskirjat","katekismukset","rukouspäivät","saarnat","aapiset","rukoukset","rukous","hengelliset laulut","hartauspuheet","virsikirjat","hautajaiset","häät","juhlamenot")
+catalogue <- "Fennica"
+  df <- df0 # selected time span
+  df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)
+
+  # Selected catalogue with selected topics
+  df <- df %>% filter(catalog == catalogue & hit)
+
+  # Selected catalogue with selected years
+  df = filter(df0, catalog == catalogue & publication_year >= 1640 & publication_year <= 1828)
+
+  lang <- paste("language.", langs, sep = "")
+  otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
+  df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
+  dfl <- NULL
+  for (lan in lang) {
+    # Classify a document to the specifed language
+    # If document is assigned with languages, each case is considered
+    # so one doc may have multiple entries corresponding to different languages
+    # mean(rowSums(df[, lang]) == 1) # 93% Fennica docs have just 1 language
+    # Combine data frames for specified languages
+    dflsub <- filter(df, df[[lan]])
+    if (nrow(dflsub) > 0) {
+      dflsub$language <- gsub("language.", "", lan)
+      dfl <- bind_rows(dfl, dflsub)
+    }
+}
+
+  # -------------------------------------------
+
+  df <- dfl %>% group_by(publication_decade, language) %>%
+             summarise(n = n(),
+	               paper = sum(paper.consumption.km2, na.rm = TRUE))
+
+  # PAPER CONSUMPTION
+  p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
+       #geom_point(aes(col = language, shape = language), size = 5) +
+       #geom_line(aes(col = language, shape = language)) +
+       geom_bar(stat = "identity", aes(fill = language, )) +              
+       xlab("Publication year") +
+       ylab("Paper consumption") +
+       ggtitle(paste("Languages (", catalogue, ")", sep = ""))
+  print(p)
+```
 

### 2016-07-12 inst/examples/20160715-slides-Krakow.Rmd
j

@@
        ylab("Unique publishers (n)") +        
-       ggtitle(paste("Unique publishers in selected publication places (", catalogue, ")"))
+       ggtitle(paste("Unique publishers in selected publication places"))
 
@@
   }
-  langs <- c("Finnish", "Swedish", "Latin", "German", "Russian", "French", "Other")
+  langs <- c("Finnish", "Swedish", "Latin", "German", "Russian", "French", "Danish", "English", "Other")
   df <- df %>% filter(catalog == catalogue)%>%
-        filter(publication_year >= 1600 & publication_year <= 1900)
+        filter(publication_year >= 1640 & publication_year <= 1900)
 
@@
   df <- df0 %>% filter(catalog == catalogue) %>%
-        filter(publication_year >= 1600 & publication_year <= 1828)
+        filter(publication_year >= 1640 & publication_year <= 1828)
 
@@
 [University curriculum & Enlightenment in Finland]
+TODO: UUSI SLIDE top-authors publishing in octavo (title count) Fennica and Kungliga. OF COURSE!
 

### 2016-07-12 inst/examples/20160715-slides-Krakow.Rmd
ok

--- 2016-07-11 inst/examples/20160715-slides-Krakow.Rmd
@@
 output: 
-  beamer_presentation
+  beamer_presentation:
+    theme: "default"
+    colortheme: "dolphin"
 ---
@@
 
+library(ggmap)
+library(gisfin)
 library(stringr)
@@
 
-sivu 3. Datamäärät koodista tähän takaisin. Deletoin tän vahingossa aikaisemmin kun koodi ei toiminut.
-
-sivu 8. Karttakuvassa Greifswald, Lund ei näy. Tätä olisi hyvä saada kehitettyä, tällaisena tää ei ihan toimi.
-
 sivu 12. Gävle-kuva vaihdettu Tukholmaan, pitää tsiigata mitkä vuodet highlightataan. Tällaisena ei vielä toimi. Onhan katalogi oikein?
@@
 
-## From particular data to global perspective?
-
-**Idea**: to study early modern knowledge production, all of it (1470-1830)
-
-**How?** By combining library catalogues (Fennica, Kungliga, ESTC, CERL's HPB database)
-
-**Important**: to clean up the data (90% of the work!) and to take into account how particular data collections (Finnish National Bibliography, English Short-Title Catalogue etc.) have been formed.
+## Global knowledge production and large-scale library catalogues
+
+**Idea**: Study early modern knowledge production, all of it (1470-1830)
+
+**How?** Combine library catalogues (Fennica, Kungliga, ESTC, CERL HPB database)
+
+**Important**: cleaning up the data (90% of the effort!) and considering how particular data collections (Finnish National Bibliography, English Short-Title Catalogue etc.) have been formed.
 
@@
 
-**Overcoming a national gaze** by focusing on how knowledge production happened through a more complex network of cities.
-
----
-
-### Data (1640-1828):
-
-TÄHÄN DATA MÄÄRÄ KOODISTA!
-
-### Method
-
-- Open source tools for library catalogues (Github/Fennica)
-
-- Fully transparent and reproducible
-
-- Scales up to new catalogues and tasks
-
-- Benefit no. 1: once the work has been done, the data is available for everyone to use and to enrich. The generic data analytical ecosystem is designed with even unforeseen changes in mind.
-
----
-
-### Outline of Quantitative Study of Finnish Knowledge Production, 1640-1828
+**Overcoming a national gaze** focus on knowledge production through more complex cross-national networks
+
+**Data: bibliographic catalogues 1640-1828**
+
+- Fennica: `r nrow(subset(df0, catalog == "Fennica" & publication_year >= 1640 & publication_year < 1828))` documents
+- Kungliga: `r nrow(subset(df0, catalog == "Kungliga" & publication_year >= 1640 & publication_year < 1828))` documents
+
+```{r, message=FALSE, warning=FALSE, fig.width=10, fig.height=7}
+library(dplyr)
+library(ggplot2)
+df <- df0 %>% filter(publication_year >=1640 & publication_year <=1828) %>% group_by(catalog, publication_decade) %>% tally()
+p <- ggplot(df, aes(x = publication_decade, y = n, color = catalog)) + 
+       geom_point() + 
+       geom_line() + 
+       ylab("Documents (n)") + xlab("Publication year") +
+       scale_color_manual(values = c("blue", "darkgreen"))
+print(p)
+```
+
+---
+
+### Methods: Open data analytical ecosystem
+
+- **Automated** scales well with new data and unforeseen changes
+
+- **Reusable** the polished data can be reused and further enriched
+
+- **Customized** dedicated R packages for bibliographic analysis combine automation with flexibility
+
+- **Open source** fully transparent and reproducible data analytics  
+  https://github.com/rOpenGov/fennica
+
+![Data Science Workflow](data-science.png)  
+\tiny{(Figure by Hadley Wickham)}
+
+---
+
+### Examples of the tools
+
+- **Parsers** From original MARC/XML to CSV to RData
+
+- **Preprocessing** Cleaning up the fields.
+
+```{r}
+library(bibliographica)
+polish_physical_extent("iii-xxiv, 118, [2] p.")$pagecount
+polish_place("Sur l'imprimea londres")
+```
+
+**Analysis**
+
+```{r}
+library(knitr)
+kable(as.data.frame(top(df0, "publication_place", 3)))
+```
+
+**Visualization**
+
+```{r, fig.width=10, fig.height=7}
+titlecount_timeline(subset(df0, catalog == "Fennica"), 
+                         "publisher", nmin = 500, mode = "n")$plot
+```
+
+---
+
+### Outline
+
+**Quantitative Study of Finnish Knowledge Production, 1640-1828**
 
@@
 
---> Visible roots of the diversity of "Finnishness" reflected in knowledge production, 1640-1828.
+Visible roots of the diversity of "Finnishness" reflected in knowledge production, 1640-1828.
 
@@
 
-### Turku as a Swedish University Town among Uppsala, Tartu and Stockholm (+ Greifswald and Lund)
-
-```{r map1, echo=FALSE, message=FALSE, warning=FALSE, fig.width=20, fig.height=5}
+### Turku as a Swedish University Town among Uppsala, Tartu and Stockholm
+
+TODO Karttakuvassa Greifswald, Lund ei näy.
+Tätä hyvä saada kehitettyä, tällaisena ei toimi.
+LL: ei näy sen takia että näytettynä on vuosikymmen 1650 jolloin Lundissa on 0 dokumenttia ja Greifswaldissa 1.
+Muissa kymmeniä tai satoja.
+Data näkyy kuten pitääkin.
+
+```{r map1, echo=FALSE, message=FALSE, warning=FALSE, fig.width=20, fig.height=5, eval=FALSE}
 library(dplyr)
@@
 
-### Fennica drop in 1700-1721, Kungliga peak in 1760-1770s, effect of Napoleonic wars (1803-1815)
+### Publishing activity over time
+
+- 1700-1721 Fennica drop
+- 1760-1770s Kungliga peak 
+- 1803-1815 Napoleonic wars
 
 ```{r publishingovertime, echo=FALSE, message=FALSE, warning=FALSE, fig.width=6, fig.height=4, out.width="200px"}
+library(magrittr)
+library(ggplot2)
+library(dplyr)
 df2 <- df0 %>% group_by(publication_decade, catalog) %>%
@@
 
-```{r publishingactivitycomparisons, echo=FALSE, message=FALSE, cache=TRUE, fig.width=6, fig.height=5, fig.show="hold", out.width="170px"}
-v <- seq(1500, 1800, 50)
+```{r publishingactivitycomparisons, echo=FALSE, message=FALSE, cache=TRUE, fig.width=8, fig.height=5, fig.show="hold", out.width="150px"}
+v <- seq(1500, 1800, 100)
 selected.places = c("Turku", "Stockholm")
@@
      ggtitle(catal) +
-     scale_x_continuous(breaks = v, labels = v)     
+     scale_x_continuous(breaks = v, labels = v) + 
+     theme(axis.text.x = element_text(angle = 0))
   print(p)
@@
 
-TODO: Vaihdettiin tähän Stockholm, riittää julkaisumäärät. Miksi katalogina lukee Fennica? Pitää olla Kungligan mukaan data tässä.
+TODO: Vaihdettiin tähän Stockholm, riittää julkaisumäärät.
 
@@
 
----
-
-Extra Slide:
-
-### Duplicate publications
+Source code for these slides:
+- https://github.com/rOpenGov/fennica/blob/master/inst/examples/20160715-slides-Krakow.Rmd
+
+---
+
+### Duplicate publications in Fennica/Kungliga
 
 ```{r duplicates, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=5, fig.width=10}
-# DUPLICATE FRACTION
 df <- df.combined.preprocessed %>%
@@
        ylab("Duplicates (%)") +
-       scale_fill_manual(values = c("blue", "red")) + 
-       ggtitle(paste("Certain duplicates Fennica-Kungliga", paste(range(na.omit(df$publication_decade)), collapse = "-")))
-
-print(p)
-```
+       scale_fill_manual(values = c("blue", "red")) 
+       #ggtitle(paste("Certain duplicates Fennica-Kungliga", paste(range(na.omit(df$publication_decade)), collapse = "-")))
+
+print(p)
+```

### 2016-07-12 inst/examples/20160715-slides-Krakow.Rmd
ok

--- 2016-07-12 inst/examples/20160715-slides-Krakow.Rmd
@@
 
-## Global knowledge production and large-scale library catalogues
+## Global knowledge production and massive library catalogues
 
@@
 
-**Data: bibliographic catalogues 1640-1828**
+---
+
+### Data: bibliographic catalogues 1640-1828
 
@@
 
+- **Customized** dedicated R packages for bibliographic analysis combine automation with flexibility
+
 - **Reusable** the polished data can be reused and further enriched
-
-- **Customized** dedicated R packages for bibliographic analysis combine automation with flexibility
 
@@
 
-- **Parsers** From original MARC/XML to CSV to RData
-
-- **Preprocessing** Cleaning up the fields.
-
-```{r}
-library(bibliographica)
+**Parse** From original MARC/XML to CSV to RData
+
+**Preprocess** Cleaning up the fields.
+
+```{r, message=FALSE, warning=FALSE}
 polish_physical_extent("iii-xxiv, 118, [2] p.")$pagecount
@@
 
-**Analysis**
-
-```{r}
+**Enrich**
+
+```{r, message=FALSE, warning=FALSE}
+get_country("Porvoo")
+```
+
+**Analyse**
+
+```{r, message=FALSE, warning=FALSE}
 library(knitr)
@@
 
-**Visualization**
-
-```{r, fig.width=10, fig.height=7}
+**Visualize**
+
+```{r, fig.width=10, fig.height=7, message=FALSE, warning=FALSE}
 titlecount_timeline(subset(df0, catalog == "Fennica"), 

### 2016-07-12 inst/examples/20160715-slides-Krakow.Rmd
k

--- 2016-07-12 inst/examples/20160715-slides-Krakow.Rmd
@@
 
-```{r, fig.width=10, fig.height=7}
+#```{r, fig.width=10, fig.height=7}
 titlecount_timeline(subset(df0, catalog == "Fennica"), 
@@
 ### Turku as a Swedish University Town among Uppsala, Tartu and Stockholm
-
-TODO Karttakuvassa Greifswald, Lund ei näy.
-Tätä hyvä saada kehitettyä, tällaisena ei toimi.
-LL: ei näy sen takia että näytettynä on vuosikymmen 1650 jolloin Lundissa on 0 dokumenttia ja Greifswaldissa 1.
-Muissa kymmeniä tai satoja.
-Data näkyy kuten pitääkin.
 
@@
 
-### Stockholm & democratic cycles
-
-An example how historical events, namely parliamentary assemblies in the Swedish case, have an impact on local knowledge production.
-
-TODO: Vaihdettiin tähän Stockholm, riittää julkaisumäärät.
-
-```{r riksdar2, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
-  myplace <- "Stockholm" # Norrköping / Stockholm
+### Swedish knowledge production & cycles of representation
+
+An example how historical events, namely parliamentary assemblies in the Swedish case, have an effect on knowledge production.
+
+```{r riksdar5, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
+
 minyear <- 1700
@@
 
+library(magrittr)
+library(ggplot2)
+library(dplyr)
+library(ggplot2)
+library(reshape2)
+
+#for (catal in as.character(unique(df0$catalog))) {
+
+for (catal in "Kungliga") {
+
+  # Use timeinterval year intervals
+  dfsel = subset(df0, catalog == catal)
+
   df <- df0
@@
 
-  # Use timeinterval year intervals
-  # Remove special chars
-  if (length(unique(df$publication_place[grep("^G.vle$", df$publication_place)])) == 1) {
-    df$publication_place[grep("^G.vle$", df$publication_place)] <- "Gavle"
-  }
-  if (length(unique(df$publication_place[grep("^Norrk.ping$", df$publication_place)])) == 1) {
-    df$publication_place[grep("^Norrk.ping$", df$publication_place)] <- "Norrkoping"
-  }
-  df <- df %>% filter(publication_place == myplace)
+  df <- subset(dfsel, publication_year >= 1700 & publication_year < 1800 )
 
@@
   publications <- publications/timeinterval # Instead of decadal sum, use average annual output 
-library(reshape2)  
   dfm <- melt(publications) 
@@
   dfm <- transform(dfm, date = as.numeric(as.character(Time)))
-  ymin = min(0.1)
-  ymax = max(60)
+  ymin = min(dfm$Documents)
+  ymax = max(dfm$Documents)
 
@@
                1765-.5, 1766+.5, # Stockholm 21 februari 1765 21 oktober 1766
-               1769-.5, 1770+.5, # Norrkoping & Stockholm 22 april 1769 5 februari 1770
+               1769-.5, 1770+.5, # Norrköping & Stockholm 22 april 1769 5 februari 1770
                1771-.5, 1772+.5, # Stockholm 19 juni 1771 12 september 1772
-               1792-.5, 1792+.5, # Gavle 26 januari 1792 24 februari 1792	       
+               1792-.5, 1792+.5, # Gävle 26 januari 1792 24 februari 1792         
                max(na.omit(dfm$date)))
@@
 
- riksplace = c("Stockholm", "Stockholm", "Stockholm", "Norrkoping", "Stockholm", "Gavle")
+ riksplace = c("Stockholm", "Stockholm", "Stockholm", "Norrköping", "Stockholm", "Gävle")
  cols = c("gray", "lightblue", "yellow", "white")
@@
   # Draw Figure
-library(ggplot2)
   theme_set(theme_bw(20))
@@
   p <- p + geom_rect(data = rectangles, 
-	   aes(xmin=xmin, xmax=xmax,
-	       ymin=ymin, ymax=ymax,
-	       fill=shade), alpha=0.8) + 
+       aes(xmin=xmin, xmax=xmax, ymin=ymin, ymax=ymax, fill=shade), alpha=0.8) + 
          scale_fill_manual(values = cols) # + guides(fill = "none") 
@@
   p <- p + geom_point(data = dfm, aes(x = date, y = Documents), col = "black")
+  p <- p + scale_x_continuous(breaks=seq(min(dfm$date), max(dfm$date), 20))
   p <- p + ggtitle("Publishing activity")
@@
   p <- p + xlab("Year")
-  p <- p + ggtitle(paste(myplace, " (", catal, ")", sep = ""))
-  print(p)
+  p <- p + ggtitle(catal)
+  print(p)
+}
+
 ```

### 2016-07-12 inst/examples/20160715-slides-Krakow.Rmd
sync

--- 2016-07-12 inst/examples/20160715-slides-Krakow.Rmd
@@
 ```{r 201606krakow-init, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, cache=TRUE}
-# Default time span for the slides
+# Default time span
 min.year <- 1488
@@
 
-## Global knowledge production and massive library catalogues
+## Global knowledge production and library catalogues
 
@@
 
-### Data: bibliographic catalogues 1640-1828
-
-- Fennica: `r nrow(subset(df0, catalog == "Fennica" & publication_year >= 1640 & publication_year < 1828))` documents
-- Kungliga: `r nrow(subset(df0, catalog == "Kungliga" & publication_year >= 1640 & publication_year < 1828))` documents
-
-```{r, message=FALSE, warning=FALSE, fig.width=10, fig.height=7}
+## Data: bibliographic catalogues 1640-1828
+
+**Fennica** Finnish National bibliography
+
+- 900,000+ books and monographies (printed and electronic; 1488-)
+- 70,000+ continuous publications (journals or series; 1771-)
+- Series, maps, audiovisual, electronic material
+- `r nrow(subset(df0, catalog == "Fennica" & publication_year >= 1640 & publication_year < 1828))` documents 1640-1828
+
+**Kungliga**  Swedish National bibliography
+
+- `r nrow(subset(df0, catalog == "Kungliga" & publication_year >= 1640 & publication_year < 1828))` documents 1640-1828
+- Altogether > 18 million entries
+
+```{r, message=FALSE, warning=FALSE, fig.width=10, fig.height=3, echo=FALSE}
 library(dplyr)
 library(ggplot2)
+theme_set(theme_bw(20))
 df <- df0 %>% filter(publication_year >=1640 & publication_year <=1828) %>% group_by(catalog, publication_decade) %>% tally()
@@
 
-- **Automated** scales well with new data and unforeseen changes
-
-- **Customized** dedicated R packages for bibliographic analysis combine automation with flexibility
-
-- **Reusable** the polished data can be reused and further enriched
-
-- **Open source** fully transparent and reproducible data analytics  
-  https://github.com/rOpenGov/fennica
+**Customized** dedicated R packages for bibliographic analysis combine flexibility with automation
+
+**Automated** scales well with new data and unforeseen changes; a million documents ~ 30 minutes
+
+**Open source** fully transparent and reproducible data analytics; every single detail, from raw data to final visualization https://github.com/rOpenGov/fennica
+
+**Collaboration & Reuse** further use and enrichment
+
+**Research potential** greatly underestimated; world is full of metadata collections
 
@@
 
-### Examples of the tools
-
-**Parse** From original MARC/XML to CSV to RData
-
-**Preprocess** Cleaning up the fields.
-
-```{r, message=FALSE, warning=FALSE}
+### Data processing is a major effort and should not be underestimated
+
+We have built custom tools to automate all analyses from raw data to final summary documents (these slides, for instance).
+
+![](parsing.png) ![](iceberg.png)
+
+---
+
+### Preprocess & Enrich
+
+```{r, message=FALSE, warning=FALSE, echo=FALSE}
+library(bibliographica, quiet = TRUE)
+```
+
+**Clean up messy entries**
+
+```{r, message=FALSE, warning=FALSE,echo=TRUE}
 polish_physical_extent("iii-xxiv, 118, [2] p.")$pagecount
@@
 
-**Enrich**
+**Augment data** (geocoordinates, gender, ..)
 
@@
 
-**Analyse**
-
-```{r, message=FALSE, warning=FALSE}
-library(knitr)
-kable(as.data.frame(top(df0, "publication_place", 3)))
-```
-
-**Visualize**
+---
+
+### Analyse & Visualize
+
+**Fast time line analysis**
 
@@
 
-### Outline
-
-**Quantitative Study of Finnish Knowledge Production, 1640-1828**
+### Practical exercise: Quantitative Study of Finnish Knowledge Production, 1640-1828
 
@@
 
-#library(gridExtra)
-#grid.arrange(pics[[1]], pics[[2]], pics[[3]], pics[[4]], nrow = 1)
 library(gridExtra)
@@
 p <- ggplot(df2, aes(x = publication_decade, y = n)) +
-     geom_line(aes(linetype = catalog), color = "black") +
+     geom_line(aes(group = catalog), color = "black") +
+     #geom_smooth(aes(fill = catalog)) + 
      geom_point(aes(shape = catalog, color = highlight, size = highlight)) +
      ylab("Title count (n)") + xlab("Publication year") +
-     scale_color_manual(values = c("darkgray", "black")) +
+     scale_color_manual(values = c("black", "black")) +
+     #scale_color_manual(values = c("black")) +
        theme(legend.position = "none") +
@@
 
-Role of pamphleteering in 1766-1774 plays a crucial role in the peak in publishing during the time of abolished censorship in Sweden.
-
-```{r pamflets1, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=6, out.width="280px", fig.show="hold"}
+Pamphleteering plays a crucial role during abolished censorship in Sweden.
+
+```{r pamflets1, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=4, out.width="280px", fig.show="hold"}
 df <- df0 %>%
@@
        ylab("Unique publishers (n)") +        
-       ggtitle(paste("Unique publishers in selected publication places (", catalogue, ")"))
+       guides(fill = guide_legend(reverse = TRUE, title = "")) #+ 
+       #ggtitle(paste("Unique publishers in selected publication places (", catalogue, ")"))
 
@@
 
-```{r comparisons, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=20, fig.height=15}
+```{r comparisons, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=18, fig.height=10}
 pics <- list()
@@
      }     
+  p <- p + guides(fill = guide_legend(reverse = TRUE, title = ""))
 
@@
 
-### Title count of the output of publishers in Turku
+### Top publishers in Turku/Fennica (title count)
 
@@
        xlab("Publication year") +
-       ylab("Title count (n)") +        
-       ggtitle(paste("Title count per publisher (", place, "/", catalogue, ")", sep = ""))
+       ylab("Title count (n)") #+        
+       #ggtitle(paste("Title count per publisher (", place, "/", catalogue, ")", sep = ""))
 print(p)
@@
 
-### Different languages in Fennica and Kungliga (percentage)
-
-```{r language-perc, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=12, out.width="150px", fig.show="hold"}
+### Language comparison between catalogues (percentage)
+
+```{r languageperc, echo=FALSE, message=FALSE, warning=FALSE, fig.width=15, fig.height=10}
+pics <- list()
 for (catalogue in c("Fennica", "Kungliga")) {
@@
      ylab("Title count frequency (%)") +
-     ggtitle(paste("Languages (", catalogue, ")", sep = "")) +
+     #ggtitle(paste("Languages (", catalogue, ")", sep = "")) +
+     ggtitle(catalogue) +
+     guides(fill = guide_legend(reverse = TRUE, title = "")) +
      scale_fill_brewer(palette="Paired")
-print(p)
-}
+pics[[catalogue]] <- p
+}
+library(gridExtra)
+grid.arrange(p[[1]], p[[2]], nrow = 2)
 ```
@@
       ylab("Title count frequency (%)") +
-      ggtitle(paste("Languages (", myplace, "/", catalogue, ")", sep = "")) +
+      #ggtitle(paste("Languages (", myplace, "/", catalogue, ")", sep = "")) +
+      ggtitle(paste(myplace, "/", catalogue)) +
       scale_fill_brewer(palette="Paired")
@@
 
-### Topic diversity in different languages in Finnish publications
+### Topic richness per language (Finnish publications)
 

### 2016-07-12 inst/examples/20160715-slides-Krakow.Rmd

@@
 
-sivu 12. Gävle-kuva vaihdettu Tukholmaan, pitää tsiigata mitkä vuodet highlightataan. Tällaisena ei vielä toimi. Onhan katalogi oikein?
-
 sivu 27. Dissertation languages: kategoria "other" sisällön selvittäminen!
@@
 
----
-
 ### Preprocess & Enrich
@@
 ```{r, fig.width=10, fig.height=7, message=FALSE, warning=FALSE}
+library(bibliographica)
 titlecount_timeline(subset(df0, catalog == "Fennica"), 
@@
 pics[[catalogue]] <- p
+library(dplyr)
+library(magrittr)
 }
@@
 
+```{r authors24, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=8, out.width="160px", fig.show="hold"}
+theme_set(theme_bw(20))
+for (catalogue in c("Fennica", "Kungliga")) {
+  df <- filter(df0, catalog == catalogue) %>%filter(gatherings == "8vo")%>%
+        filter(publication_year >= 1640 & publication_year <= 1828)
+  top.authors <- names(bibliographica::top(df, field = "author", n = 10))
+  dfs <- df %>% filter(author %in% top.authors) %>%
+         group_by(author, publication_decade) %>%
+         tally() %>%
+         arrange(publication_decade)
+  p <- ggplot(dfs, aes(x = publication_decade, y = n, fill = author)) +
+       geom_bar(stat = "identity", position = "stack", color = "black") +
+       xlab("Publication Decade") +
+       ylab("Title Count") +
+       scale_fill_grey() +
+       guides(fill = guide_legend("Author")) +
+       ggtitle(paste("Title count top authors\n", catalogue)) +
+       xlim(c(1640, 1828))
+  print(p)
+}
+```
+
+---
+
 ### Thanks !

### 2016-07-12 inst/examples/20160715-slides-Krakow.Rmd
ok

@@
   beamer_presentation:
-    theme: "default"
-    colortheme: "dolphin"
+    theme: "Montpellier"
+    colortheme: "default"
+    fonttheme: "structuresmallcapsserif"
 ---
@@
 
+sivu 12. Gävle-kuva vaihdettu Tukholmaan, pitää tsiigata mitkä vuodet highlightataan. Tällaisena ei vielä toimi. Onhan katalogi oikein?
+
 sivu 27. Dissertation languages: kategoria "other" sisällön selvittäminen!
@@
 
-![](parsing.png) ![](iceberg.png)
+\begin{columns}
+\begin{column}{0.5\textwidth}
+     \includegraphics[width=1\textwidth]{parsing.png}
+\end{column}
+\begin{column}{0.5\textwidth}  %%<--- here
+    \begin{center}
+     \includegraphics[width=1\textwidth]{iceberg.png}
+     \end{center}
+\end{column}
+\end{columns}
+
+---
+
+![](ecosystemflowchart.png)
+
+---
 
@@
 polish_physical_extent("iii-xxiv, 118, [2] p.")$pagecount
-polish_place("Sur l'imprimea londres")
 ```
@@
 
-```{r, fig.width=10, fig.height=7, message=FALSE, warning=FALSE}
-library(bibliographica)
+```{r, fig.width=15, fig.height=5, message=FALSE, warning=FALSE}
 titlecount_timeline(subset(df0, catalog == "Fennica"), 
@@
 
-```{r map1, echo=FALSE, message=FALSE, warning=FALSE, fig.width=20, fig.height=5, eval=FALSE}
+```{r map1, echo=FALSE, message=FALSE, warning=FALSE, fig.width=20, fig.height=5, eval=TRUE}
 library(dplyr)
@@
 
-### Explaining the 1760-1770 publishing peak in Sweden
-
-Pamphleteering plays a crucial role during abolished censorship in Sweden.
+### Swedish 1760-1770 publishing peak
+
+Pamphleteering plays a crucial role during abolished censorship
 
@@
 pics[[catalogue]] <- p
-library(dplyr)
-library(magrittr)
 }
 library(gridExtra)
-grid.arrange(p[[1]], p[[2]], nrow = 2)
+grid.arrange(pics[[1]], pics[[2]], nrow = 2)
 ```
@@
 
-```{r language-perc2, echo=FALSE, message=FALSE, warning=FALSE, fig.width=20, fig.height=15}
+```{r language-perc2, echo=FALSE, message=FALSE, warning=FALSE, fig.width=20, fig.height=12}
 pics <- list()
@@
       ggtitle(paste(myplace, "/", catalogue)) +
-      scale_fill_brewer(palette="Paired")
+      scale_fill_brewer(palette="Paired") + 
+      guides(fill = guide_legend(reverse = TRUE, title = ""))
     pics[[paste(catalogue, myplace, sep = "-")]] <- p
@@
 p <- ggplot(df, aes(x = publication_year, y = n, color = language)) +
-       geom_line() + geom_point() +
-       ggtitle("Number of subject topics")
+       geom_line() + geom_point()
 
@@
 
-- Form of literature denoting the advancement of reading in Finland in the nineteenth century. It has been unclear when does it show up as a relevant category.
+Form of literature denoting the advancement of reading in Finland in the nineteenth century. It has been unclear when does it show up as a relevant category.
 
 ```{r topics12122, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, fig.show="hold"}
-# https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/topics-2.png
 sel <- c("virret","arkkiveisut","hartauskirjat","katekismukset","rukouspäivät","saarnat","aapiset","rukoukset","rukous","hengelliset laulut","hartauspuheet","virsikirjat")
@@
        ylab("Paper consumption") +
-       ggtitle(paste("Languages (", catalogue, ")", sep = "")) 
+       ggtitle(catalogue) 
+       #ggtitle(paste("Languages (", catalogue, ")", sep = "")) 
   print(p)
@@
 
-```{r authors22, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=8, out.width="160px", fig.show="hold"}
+```{r authors22, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, out.width="160px", fig.show="hold"}
 theme_set(theme_bw(20))
@@
 
-```{r authors24, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=8, out.width="160px", fig.show="hold"}
-theme_set(theme_bw(20))
-for (catalogue in c("Fennica", "Kungliga")) {
-  df <- filter(df0, catalog == catalogue) %>%filter(gatherings == "8vo")%>%
-        filter(publication_year >= 1640 & publication_year <= 1828)
-  top.authors <- names(bibliographica::top(df, field = "author", n = 10))
-  dfs <- df %>% filter(author %in% top.authors) %>%
-         group_by(author, publication_decade) %>%
-         tally() %>%
-         arrange(publication_decade)
-  p <- ggplot(dfs, aes(x = publication_decade, y = n, fill = author)) +
-       geom_bar(stat = "identity", position = "stack", color = "black") +
-       xlab("Publication Decade") +
-       ylab("Title Count") +
-       scale_fill_grey() +
-       guides(fill = guide_legend("Author")) +
-       ggtitle(paste("Title count top authors\n", catalogue)) +
-       xlim(c(1640, 1828))
-  print(p)
-}
-```
-
----
-
 ### Thanks !
@@
 
-Source code for these slides:
+Source code of these slides:
 - https://github.com/rOpenGov/fennica/blob/master/inst/examples/20160715-slides-Krakow.Rmd

### 2016-07-12 inst/examples/20160715-slides-Krakow.Rmd

@@
 ```{r, fig.width=15, fig.height=5, message=FALSE, warning=FALSE}
+library(bibliographica)
 titlecount_timeline(subset(df0, catalog == "Fennica"), 

### 2016-07-12 inst/examples/20160715-slides-Krakow.Rmd
z

@@
   beamer_presentation:
-    theme: "Montpellier"
-    colortheme: "default"
-    fonttheme: "structuresmallcapsserif"
+    theme: "Singapore"
+    colortheme: "orchid"
+    fonttheme: "professionalfonts"
 ---

### 2016-07-12 inst/examples/slides.Rmd
ok

---
title: "Untitled"
output: ioslides_presentation
---

### Data processing is a major effort and should not be underestimated

We have built custom tools to automate all analyses from raw data to final summary documents (these slides, for instance).

\begin{columns}
\begin{column}{0.5\textwidth}
     \includegraphics[width=1\textwidth]{parsing.png}
\end{column}
\begin{column}{0.5\textwidth}  %%<--- here
    \begin{center}
     \includegraphics[width=1\textwidth]{iceberg.png}
     \end{center}
\end{column}
\end{columns}

---

![](ecosystemflowchart.png)

### 2016-07-12 inst/examples/20160715-slides-Krakow.Rmd
ok
s

@@
   beamer_presentation:
-    theme: "Singapore"
+    theme: "Goettingen"
     colortheme: "orchid"
@@
 
-## Data: bibliographic catalogues 1640-1828
+### Data: bibliographic catalogues 1640-1828
 
@@
 
-### Methods: Open data analytical ecosystem
+## Methods: Open data analytical ecosystem
 
@@
 
-### Preprocess & Enrich
+## Preprocess & Enrich
 
@@
 
-### Analyse & Visualize
+## Analyse & Visualize
 
@@
 
-### 1. General trends & political events
+1. General trends & political events
 
@@
 
-### 2. Publishers in Sweden and Turku
+2. Publishers in Sweden and Turku
 
@@
 
-### 3. Languages & religious texts in Finland
+3. Languages & religious texts in Finland
 
@@
 
-### 4. University curriculum & Enlightenment in Finland
+4. University curriculum & Enlightenment in Finland
 
@@
 
-### Thanks !
+##Thanks !
 

### 2016-07-12 inst/examples/20160715-slides-Krakow.Rmd
sync
s

@@
 
-### Data processing is a major effort and should not be underestimated
-
-We have built custom tools to automate all analyses from raw data to final summary documents (these slides, for instance).
-
-\begin{columns}
-\begin{column}{0.5\textwidth}
-     \includegraphics[width=1\textwidth]{parsing.png}
-\end{column}
-\begin{column}{0.5\textwidth}  %%<--- here
-    \begin{center}
-     \includegraphics[width=1\textwidth]{iceberg.png}
-     \end{center}
-\end{column}
-\end{columns}
-
----
-
-![](ecosystemflowchart.png)
-
----
-
 ## Preprocess & Enrich
@@
 
-### Practical exercise: Quantitative Study of Finnish Knowledge Production, 1640-1828
+### Outline of Quantitative Study of Finnish Knowledge Production, 1640-1828
 
@@
 
-1. General trends & political events
+**1. General trends & political events**
 
@@
 
-```{r publishingactivitycomparisons, echo=FALSE, message=FALSE, cache=TRUE, fig.width=8, fig.height=5, fig.show="hold", out.width="150px"}
+```{r publishingactivitycomparisons, echo=FALSE, message=FALSE, cache=TRUE, fig.width=10, fig.height=9, fig.show="hold", out.width="160px"}
 v <- seq(1500, 1800, 100)
@@
 
-2. Publishers in Sweden and Turku
+**2. Publishers in Sweden and Turku**
 
@@
 
-3. Languages & religious texts in Finland
+**3. Languages & religious texts in Finland**
 
@@
 
-4. University curriculum & Enlightenment in Finland
+**4. University curriculum & Enlightenment in Finland**
 
@@
 
-```{r LIBER-13, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=10, fig.height=8, fig.show="hold", out.width="150px"}
+```{r LIBER-13, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=11, fig.height=9, fig.show="hold", out.width="160px"}
 for (catal in unique(df0$catalog)) {
@@
 
-```{r authors22, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, out.width="160px", fig.show="hold"}
+```{r authors22, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10, out.width="160px", fig.show="hold"}
 theme_set(theme_bw(20))

### 2016-07-12 inst/examples/20160715-slides-Krakow.Rmd
a

@@
   beamer_presentation:
-    theme: "Goettingen"
+    theme: "boxes"
     colortheme: "orchid"
@@
 
-## Global knowledge production and library catalogues
+## From particular data to global perspective?
 
@@
 
-**Overcoming a national gaze** focus on knowledge production through more complex cross-national networks
+**Overcoming a national gaze** by focus on knowledge production through more complex cross-national network of cities
 
@@
 
-- 900,000+ books and monographies (printed and electronic; 1488-)
-- 70,000+ continuous publications (journals or series; 1771-)
-- Series, maps, audiovisual, electronic material
 - `r nrow(subset(df0, catalog == "Fennica" & publication_year >= 1640 & publication_year < 1828))` documents 1640-1828
@@
 - `r nrow(subset(df0, catalog == "Kungliga" & publication_year >= 1640 & publication_year < 1828))` documents 1640-1828
-- Altogether > 18 million entries
+
+- **Visible roots of the diversity of "Finnishness" reflected in knowledge production, 1640-1828**
 
@@
 
-**Open source** fully transparent and reproducible data analytics; every single detail, from raw data to final visualization https://github.com/rOpenGov/fennica
+**Open source** fully transparent and reproducible data analytics: https://github.com/rOpenGov/fennica
 
@@
 ```
-
----
-
-## Analyse & Visualize
-
-**Fast time line analysis**
-
-```{r, fig.width=15, fig.height=5, message=FALSE, warning=FALSE}
-library(bibliographica)
-titlecount_timeline(subset(df0, catalog == "Fennica"), 
-          "publisher", nmin = 500, mode = "n")$plot
-```
-
----
-
-### Outline of Quantitative Study of Finnish Knowledge Production, 1640-1828
-
-1) General trends & political events
-
-2) Publishers in Sweden and Turku
-
-3) Languages & religious texts in Finland
-
-4) University curriculum & Enlightenment in Finland
-
-Visible roots of the diversity of "Finnishness" reflected in knowledge production, 1640-1828.
 

### 2016-07-12 inst/examples/20160715-slides-Krakow.Rmd
sync

--- 2016-07-12 inst/examples/20160715-slides-Krakow.Rmd
@@
        ylab("Documents (n)") + xlab("Publication year") +
-       scale_color_manual(values = c("blue", "darkgreen"))
+       scale_color_manual(values = c("blue", "darkgreen")) + 
+       guides(fill = guide_legend(reverse = TRUE, title = "")) #+ 
 print(p)
@@
 get_country("Porvoo")
-```
-
----
-
-## Analyse & Visualize
-
-**Fast time line analysis**
-
-```{r, fig.width=15, fig.height=5, message=FALSE, warning=FALSE}
-library(bibliographica)
-titlecount_timeline(subset(df0, catalog == "Fennica"), 
-          "publisher", nmin = 500, mode = "n")$plot
 ```
@@
 p <- ggplot(df2, aes(x = publication_decade, y = n)) +
-     geom_line(aes(group = catalog), color = "black") +
-     #geom_smooth(aes(fill = catalog)) + 
+     geom_line(aes(color = catalog)) +
      geom_point(aes(shape = catalog, color = highlight, size = highlight)) +
      ylab("Title count (n)") + xlab("Publication year") +
-     scale_color_manual(values = c("black", "black")) +
-     #scale_color_manual(values = c("black")) +
      theme(legend.position = "none") +
-     scale_x_continuous(breaks = v, labels = v)
-     # ggtitle("Overall publishing activity")
+     scale_x_continuous(breaks = v, labels = v) +
+     scale_color_manual(values = c("darkgreen", "blue", "darkgreen", "blue")) + 
+     guides(fill = guide_legend(reverse = TRUE, title = "")) 
 print(p)

### 2016-07-12 inst/examples/slides.Rmd
sync

@@
 ![](ecosystemflowchart.png)
+
+---
+
+### Data: bibliographic catalogues 1640-1828
+
+**Fennica** Finnish National bibliography
+
+- 900,000+ books and monographies (printed and electronic; 1488-)
+- 70,000+ continuous publications (journals or series; 1771-)
+- Series, maps, audiovisual, electronic material
+- `r nrow(subset(df0, catalog == "Fennica" & publication_year >= 1640 & publication_year < 1828))` documents 1640-1828
+
+**Kungliga**  Swedish National bibliography
+
+- `r nrow(subset(df0, catalog == "Kungliga" & publication_year >= 1640 & publication_year < 1828))` documents 1640-1828
+- Altogether > 18 million entries
+
+```{r, message=FALSE, warning=FALSE, fig.width=10, fig.height=3, echo=FALSE}
+library(dplyr)
+library(ggplot2)
+theme_set(theme_bw(20))
+df <- df0 %>% filter(publication_year >=1640 & publication_year <=1828) %>% group_by(catalog, publication_decade) %>% tally()
+p <- ggplot(df, aes(x = publication_decade, y = n, color = catalog)) + 
+       geom_point() + 
+       geom_line() + 
+       ylab("Documents (n)") + xlab("Publication year") +
+       scale_color_manual(values = c("blue", "darkgreen"))
+print(p)
+```
+
+---
+
+## Analyse & Visualize
+
+**Fast time line analysis**
+
+```{r, fig.width=15, fig.height=5, message=FALSE, warning=FALSE}
+library(bibliographica)
+titlecount_timeline(subset(df0, catalog == "Fennica"), 
+          "publisher", nmin = 500, mode = "n")$plot
+```
+
+---

### 2016-07-12 inst/examples/20160715-slides-Krakow.Rmd

--- 2016-07-12 inst/examples/20160715-slides-Krakow.Rmd
@@
 ```
+
+---
+
+### Outline of Quantitative Study of Finnish Knowledge Production, 1640-1828
+
+1) General trends & political events
+
+2) Publishers in Sweden and Turku
+
+3) Languages & religious texts in Finland
+
+4) University curriculum & Enlightenment in Finland
+
+Visible roots of the diversity of "Finnishness" reflected in knowledge production, 1640-1828.
 
@@
 p <- ggplot(df2, aes(x = publication_decade, y = n)) +
-     geom_line(aes(group = catalog), color = "black") +
-     #geom_smooth(aes(fill = catalog)) + 
+     geom_line(aes(color = catalog), size = 1) +
      geom_point(aes(shape = catalog, color = highlight, size = highlight)) +
      ylab("Title count (n)") + xlab("Publication year") +
-     scale_color_manual(values = c("black", "black")) +
-     #scale_color_manual(values = c("black")) +
-       theme(legend.position = "none") +
-     scale_x_continuous(breaks = v, labels = v)
-     # ggtitle("Overall publishing activity")
+     #theme(legend.position = "none") +
+     scale_x_continuous(breaks = v, labels = v) +
+     scale_color_manual(values = c("black", "blue", "darkgreen", "blue")) + 
+     guides(fill = guide_legend(reverse = TRUE)) 
 print(p)

### 2016-07-12 inst/examples/20160715-slides-Krakow.Rmd
z

@@
 
-### Comparing publishing activity in Stockholm and Turku
-
-```{r publishingactivitycomparisons, echo=FALSE, message=FALSE, cache=TRUE, fig.width=10, fig.height=9, fig.show="hold", out.width="160px"}
-v <- seq(1500, 1800, 100)
-selected.places = c("Turku", "Stockholm")
-df2 <- df0 %>% group_by(publication_decade, publication_place, catalog) %>%
-               summarise(n = n()) %>%
-	       filter(publication_place %in% selected.places) 
-df2$catalog = factor(df2$catalog, levels = rev(c("Fennica", "Kungliga")))
-df2$publication_place = droplevels(factor(df2$publication_place))
-df3 = as.data.frame(spread(df2, publication_decade, n, fill = 0))
-df2 = melt(df3)
-colnames(df2) = c("publication_place", "catalog", "publication_decade", "n")
-df2$publication_decade = as.numeric(as.character(df2$publication_decade))
-df2$n = as.numeric(as.character(df2$n))
-for (catal in unique(df2$catalog)) {
-  p <- ggplot(subset(df2, catalog == catal), aes(x = publication_decade, y = n)) +
-     geom_line(aes(linetype = publication_place)) +
-     geom_point(aes(shape = publication_place), size = 3) +
-     ylab("Title count (n)") + xlab("Publication year") +  
-     ggtitle(catal) +
-     scale_x_continuous(breaks = v, labels = v) + 
-     theme(axis.text.x = element_text(angle = 0))
-  print(p)
-
-}
-```
-
----
-
-[General trends & political events]
-
 ### Swedish 1760-1770 publishing peak
@@
 **3. Languages & religious texts in Finland**
-
----
-
-[Languages & religious texts in Finland]
-
-### Language comparison between catalogues (percentage)
-
-```{r languageperc, echo=FALSE, message=FALSE, warning=FALSE, fig.width=15, fig.height=10}
-pics <- list()
-for (catalogue in c("Fennica", "Kungliga")) {
-
-  if (catalogue == "Fennica") {
-    df <- df.full # full time span
-  } else if (catalogue == "Kungliga") {
-    df <- df.full # full time span
-  }
-  langs <- c("Finnish", "Swedish", "Latin", "German", "Russian", "French", "Other")
-  df <- df %>% filter(catalog == catalogue)%>%
-        filter(publication_year >= 1600 & publication_year <= 1900)
-
-library(dplyr)
-library(tidyr)
-library(magrittr)
-library(reshape2)
-
-lang <- paste("language.", langs, sep = "")
-otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
-df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
-
-dfl <- NULL
-for (lan in lang) {
-
-  # Classify a document to the specifed language
-  # If document is assigned with languages, each case is considered
-  # so one doc may have multiple entries corresponding to different languages
-  # mean(rowSums(df[, lang]) == 1) # 93% Fennica docs have just 1 language
-  # Combine data frames for specified languages
-  dflsub <- filter(df, df[[lan]])
-  if (nrow(dflsub)>0) {
-    dflsub$language <- gsub("language.", "", lan)
-    dfl <- bind_rows(dfl, dflsub)
-  }
-}
-
-df <- dfl %>% group_by(publication_decade, language) %>%
-     	     summarise(n = n())
-
-# Calculate percentages
-dff <- spread(df, language, n, fill = 0)
-dff[, -1] <- 100 * t(apply(dff[, -1], 1, function (x) {x/sum(x)}))
-dff <- melt(dff, "publication_decade");
-colnames(dff) <- c("publication_decade", "language", "f")
-
-theme_set(theme_bw(20))
-p <- ggplot(dff, aes(x = publication_decade, y = f)) +
-     geom_bar(position = "stack", stat = "identity", aes(fill = language)) + 
-     xlab("Publication year") +
-     ylab("Title count frequency (%)") +
-     #ggtitle(paste("Languages (", catalogue, ")", sep = "")) +
-     ggtitle(catalogue) +
-     guides(fill = guide_legend(reverse = TRUE, title = "")) +
-     scale_fill_brewer(palette="Paired")
-pics[[catalogue]] <- p
-library(dplyr)
-library(magrittr)
-}
-library(gridExtra)
-grid.arrange(pics[[1]], pics[[2]], nrow = 2)
-```
 

### 2016-07-12 inst/examples/20160715-slides-Krakow.Rmd
sync

--- 2016-07-12 inst/examples/20160715-slides-Krakow.Rmd
@@
 
-df$language[!df$language %in% langs] <- "Other"
-df$language <- factor(df$language, levels = langs)
+langs2 <- c("Finnish", "Swedish", "Latin", "Other")
+df$language[!df$language %in% langs2] <- "Other"
+df$language <- factor(df$language, levels = langs2)
 
@@
        ylab("Paper consumption") +
-       ggtitle(paste("Paper (", paste(sel, collapse = ";"), ")", sep = ""))
+       guides(fill = guide_legend(reverse = TRUE, title = "")) 
+       #ggtitle(paste("Paper (", paste(sel, collapse = ";"), ")", sep = ""))
 print(p)
@@
        ylab("Paper consumption") +
-       ggtitle(paste("Paper (", paste(sel, collapse = ";"), ")", sep = ""))
-print(p)
-
+       guides(fill = guide_legend(reverse = TRUE, title = "")) 
+       #ggtitle(paste("Paper (", paste(sel, collapse = ";"), ")", sep = ""))
+print(p)
+
+```
+
+---
+
+[University curriculum & Enlightenment in Finland]
+
+### Printing by topic in different languages in Turku
+
+```{r topics-103B, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=9}
+sel = c("filosofia","luonnonfilosofia","metafysiikka","logiikka")
+df = dfl
+df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)  
+df <- df %>% filter(hit)
+df <- df %>% group_by(publication_decade, language) %>%
+             summarise(n = n(),
+                 paper = sum(paper.consumption.km2, na.rm = TRUE))
+
+# PAPER CONSUMPTION
+p1 <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
+       geom_bar(aes(fill = language), position = "stack", stat = "identity") +                     
+       xlab("Publication year") +
+       ylab("Paper consumption") +
+       guides(fill = guide_legend(reverse = TRUE, title = "")) +
+       ggtitle("Philosophy")
+
+sel = c("oppihistoria","antiikki","historia")
+# Selected catalogue with selected topics
+df = dfl
+df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)  
+df <- df %>% filter(hit)
+df <- df %>% group_by(publication_decade, language) %>%
+             summarise(n = n(),
+	               paper = sum(paper.consumption.km2, na.rm = TRUE))
+
+# PAPER CONSUMPTION
+p2 <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
+       geom_bar(aes(fill = language), position = "stack", stat = "identity") +             
+       xlab("Publication year") +
+       ylab("Paper consumption") +
+       guides(fill = guide_legend(reverse = TRUE, title = "")) +
+       ggtitle("History")
+
+sel =   c("psykologia","yhteiskuntafilosofia","valtiofilosofia","talous","raha","moraali","velvollisuudet","kasvatus","maanviljely","maatalous","kalastus")
+
+# Selected catalogue with selected topics
+df = dfl
+df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)  
+df <- df %>% filter(hit)
+df <- df %>% group_by(publication_decade, language) %>%
+             summarise(n = n(),
+	               paper = sum(paper.consumption.km2, na.rm = TRUE))
+
+# PAPER CONSUMPTION
+theme_set(theme_bw(20))
+p3 <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
+       geom_bar(aes(fill = language), position = "stack", stat = "identity") +              
+       xlab("Publication year") +
+       ylab("Paper consumption") +
+       guides(fill = guide_legend(reverse = TRUE, title = "")) +
+       ggtitle("Economy")
+grid.arrange(p1, p2, p3, nrow = 3)
 ```

### 2016-07-12 inst/examples/slides.Rmd
sync

@@
 ---
+
+### Comparing publishing activity in Stockholm and Turku
+
+```{r publishingactivitycomparisons, echo=FALSE, message=FALSE, cache=TRUE, fig.width=10, fig.height=9, fig.show="hold", out.width="160px"}
+v <- seq(1500, 1800, 100)
+selected.places = c("Turku", "Stockholm")
+df2 <- df0 %>% group_by(publication_decade, publication_place, catalog) %>%
+               summarise(n = n()) %>%
+	       filter(publication_place %in% selected.places) 
+df2$catalog = factor(df2$catalog, levels = rev(c("Fennica", "Kungliga")))
+df2$publication_place = droplevels(factor(df2$publication_place))
+df3 = as.data.frame(spread(df2, publication_decade, n, fill = 0))
+df2 = melt(df3)
+colnames(df2) = c("publication_place", "catalog", "publication_decade", "n")
+df2$publication_decade = as.numeric(as.character(df2$publication_decade))
+df2$n = as.numeric(as.character(df2$n))
+for (catal in unique(df2$catalog)) {
+  p <- ggplot(subset(df2, catalog == catal), aes(x = publication_decade, y = n)) +
+     geom_line(aes(linetype = publication_place)) +
+     geom_point(aes(shape = publication_place), size = 3) +
+     ylab("Title count (n)") + xlab("Publication year") +  
+     ggtitle(catal) +
+     scale_x_continuous(breaks = v, labels = v) + 
+     theme(axis.text.x = element_text(angle = 0))
+  print(p)
+
+}
+```
+
+---
+
+### Language comparison between catalogues (percentage)
+
+```{r languageperc, echo=FALSE, message=FALSE, warning=FALSE, fig.width=15, fig.height=10}
+pics <- list()
+for (catalogue in c("Fennica", "Kungliga")) {
+
+  if (catalogue == "Fennica") {
+    df <- df.full # full time span
+  } else if (catalogue == "Kungliga") {
+    df <- df.full # full time span
+  }
+  langs <- c("Finnish", "Swedish", "Latin", "German", "Russian", "French", "Other")
+  df <- df %>% filter(catalog == catalogue)%>%
+        filter(publication_year >= 1600 & publication_year <= 1900)
+
+library(dplyr)
+library(tidyr)
+library(magrittr)
+library(reshape2)
+
+lang <- paste("language.", langs, sep = "")
+otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
+df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
+
+dfl <- NULL
+for (lan in lang) {
+
+  # Classify a document to the specifed language
+  # If document is assigned with languages, each case is considered
+  # so one doc may have multiple entries corresponding to different languages
+  # mean(rowSums(df[, lang]) == 1) # 93% Fennica docs have just 1 language
+  # Combine data frames for specified languages
+  dflsub <- filter(df, df[[lan]])
+  if (nrow(dflsub)>0) {
+    dflsub$language <- gsub("language.", "", lan)
+    dfl <- bind_rows(dfl, dflsub)
+  }
+}
+
+df <- dfl %>% group_by(publication_decade, language) %>%
+     	     summarise(n = n())
+
+# Calculate percentages
+dff <- spread(df, language, n, fill = 0)
+dff[, -1] <- 100 * t(apply(dff[, -1], 1, function (x) {x/sum(x)}))
+dff <- melt(dff, "publication_decade");
+colnames(dff) <- c("publication_decade", "language", "f")
+
+theme_set(theme_bw(20))
+p <- ggplot(dff, aes(x = publication_decade, y = f)) +
+     geom_bar(position = "stack", stat = "identity", aes(fill = language)) + 
+     xlab("Publication year") +
+     ylab("Title count frequency (%)") +
+     #ggtitle(paste("Languages (", catalogue, ")", sep = "")) +
+     ggtitle(catalogue) +
+     guides(fill = guide_legend(reverse = TRUE, title = "")) +
+     scale_fill_brewer(palette="Paired")
+pics[[catalogue]] <- p
+library(dplyr)
+library(magrittr)
+}
+library(gridExtra)
+grid.arrange(pics[[1]], pics[[2]], nrow = 2)
+```

### 2016-07-12 inst/examples/20160715-slides-Krakow.Rmd
ok
za

@@
 
+  langs <- c("Finnish", "Swedish", "Latin", "German",
+           "Russian", "French", "Hebrew", "Other")
+
   lang <- paste("language.", langs, sep = "")
@@
 print(p)
-```
-
----
-
-[University curriculum & Enlightenment in Finland]
-
-### Printing of philosophy in different languages in Turku
-
-```{r topics-103, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6}
-sel = c("filosofia","luonnonfilosofia","metafysiikka","logiikka")
-# Selected catalogue with selected topics
-df = dfl
-df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)  
-df <- df %>% filter(hit)
-df <- df %>% group_by(publication_decade, language) %>%
-             summarise(n = n(),
-                 paper = sum(paper.consumption.km2, na.rm = TRUE))
-
-# PAPER CONSUMPTION
-theme_set(theme_bw(20))
-p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
-       geom_bar(aes(fill = language), position = "stack", stat = "identity") +                     
-       xlab("Publication year") +
-       ylab("Paper consumption") +
-       guides(fill = guide_legend(reverse = TRUE, title = "")) 
-       #ggtitle(paste("Paper (", paste(sel, collapse = ";"), ")", sep = ""))
-print(p)
-
-```
-
----
-
-[University curriculum & Enlightenment in Finland]
-
-### Printing of history in different languages in Turku
-
-```{r topics-102, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6}
-sel = c("oppihistoria","antiikki","historia")
-# Selected catalogue with selected topics
-df = dfl
-df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)  
-df <- df %>% filter(hit)
-df <- df %>% group_by(publication_decade, language) %>%
-             summarise(n = n(),
-	               paper = sum(paper.consumption.km2, na.rm = TRUE))
-
-# PAPER CONSUMPTION
-theme_set(theme_bw(20))
-p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
-       geom_bar(aes(fill = language), position = "stack", stat = "identity") +             
-       xlab("Publication year") +
-       ylab("Paper consumption") +
-       guides(fill = guide_legend(reverse = TRUE, title = "")) 
-       #ggtitle(paste("Paper (", paste(sel, collapse = ";"), ")", sep = ""))
-print(p)
-
-```
-
----
-
-[University curriculum & Enlightenment in Finland]
-
-### Printing of economy and social science in different languages in Turku
-
-```{r topics-105, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6}
-sel =   c("psykologia","yhteiskuntafilosofia","valtiofilosofia","talous","raha","moraali","velvollisuudet","kasvatus","maanviljely","maatalous","kalastus")
-
-# Selected catalogue with selected topics
-df = dfl
-df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)  
-df <- df %>% filter(hit)
-df <- df %>% group_by(publication_decade, language) %>%
-             summarise(n = n(),
-	               paper = sum(paper.consumption.km2, na.rm = TRUE))
-
-# PAPER CONSUMPTION
-theme_set(theme_bw(20))
-p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
-       geom_bar(aes(fill = language), position = "stack", stat = "identity") +              
-       xlab("Publication year") +
-       ylab("Paper consumption") +
-       guides(fill = guide_legend(reverse = TRUE, title = "")) 
-       #ggtitle(paste("Paper (", paste(sel, collapse = ";"), ")", sep = ""))
-print(p)
-
 ```
@@
 
-[University curriculum & Enlightenment in Finland]
-
-### Enlightenment literature read in Finland
-
-```{r authors22, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10, out.width="160px", fig.show="hold"}
-theme_set(theme_bw(20))
-for (catalogue in c("Fennica", "Kungliga")) {
-  df <- filter(df0, catalog == catalogue) %>%
-        filter(publication_year >= 1640 & publication_year <= 1828)
-  top.authors <- names(bibliographica::top(df, field = "author", n = 10))
-  dfs <- df %>% filter(author %in% top.authors) %>%
-         group_by(author, publication_decade) %>%
-         tally() %>%
-         arrange(publication_decade)
-  p <- ggplot(dfs, aes(x = publication_decade, y = n, fill = author)) +
-       geom_bar(stat = "identity", position = "stack", color = "black") +
-       xlab("Publication Decade") +
-       ylab("Title Count") +
-       scale_fill_grey() +
-       guides(fill = guide_legend("Author")) +
-       ggtitle(paste("Title count top authors\n", catalogue)) +
-       xlim(c(1640, 1828))
-  print(p)
-}
-```
-
----
-
 ##Thanks !
-
-R master (plots & maps):  
-- Leo Lahti
 

### 2016-07-12 inst/examples/slides.Rmd
sync

@@
 ```
+
+---
+
+[University curriculum & Enlightenment in Finland]
+
+### Printing of philosophy in different languages in Turku
+
+```{r topics-103, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6}
+sel = c("filosofia","luonnonfilosofia","metafysiikka","logiikka")
+# Selected catalogue with selected topics
+df = dfl
+df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)  
+df <- df %>% filter(hit)
+df <- df %>% group_by(publication_decade, language) %>%
+             summarise(n = n(),
+                 paper = sum(paper.consumption.km2, na.rm = TRUE))
+
+# PAPER CONSUMPTION
+theme_set(theme_bw(20))
+p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
+       geom_bar(aes(fill = language), position = "stack", stat = "identity") +                     
+       xlab("Publication year") +
+       ylab("Paper consumption") +
+       guides(fill = guide_legend(reverse = TRUE, title = "")) 
+       #ggtitle(paste("Paper (", paste(sel, collapse = ";"), ")", sep = ""))
+print(p)
+
+```
+
+---
+
+[University curriculum & Enlightenment in Finland]
+
+### Printing of history in different languages in Turku
+
+```{r topics-102, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6}
+sel = c("oppihistoria","antiikki","historia")
+# Selected catalogue with selected topics
+df = dfl
+df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)  
+df <- df %>% filter(hit)
+df <- df %>% group_by(publication_decade, language) %>%
+             summarise(n = n(),
+	               paper = sum(paper.consumption.km2, na.rm = TRUE))
+
+# PAPER CONSUMPTION
+theme_set(theme_bw(20))
+p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
+       geom_bar(aes(fill = language), position = "stack", stat = "identity") +             
+       xlab("Publication year") +
+       ylab("Paper consumption") +
+       guides(fill = guide_legend(reverse = TRUE, title = "")) 
+       #ggtitle(paste("Paper (", paste(sel, collapse = ";"), ")", sep = ""))
+print(p)
+
+```
+
+---
+
+[University curriculum & Enlightenment in Finland]
+
+### Printing of economy and social science in different languages in Turku
+
+```{r topics-105, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6}
+sel =   c("psykologia","yhteiskuntafilosofia","valtiofilosofia","talous","raha","moraali","velvollisuudet","kasvatus","maanviljely","maatalous","kalastus")
+
+# Selected catalogue with selected topics
+df = dfl
+df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)  
+df <- df %>% filter(hit)
+df <- df %>% group_by(publication_decade, language) %>%
+             summarise(n = n(),
+	               paper = sum(paper.consumption.km2, na.rm = TRUE))
+
+# PAPER CONSUMPTION
+theme_set(theme_bw(20))
+p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
+       geom_bar(aes(fill = language), position = "stack", stat = "identity") +              
+       xlab("Publication year") +
+       ylab("Paper consumption") +
+       guides(fill = guide_legend(reverse = TRUE, title = "")) 
+       #ggtitle(paste("Paper (", paste(sel, collapse = ";"), ")", sep = ""))
+print(p)
+
+```
+
+---
+
+[University curriculum & Enlightenment in Finland]
+
+### Enlightenment literature read in Finland
+
+```{r authors22, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10, out.width="160px", fig.show="hold"}
+theme_set(theme_bw(20))
+for (catalogue in c("Fennica", "Kungliga")) {
+  df <- filter(df0, catalog == catalogue) %>%
+        filter(publication_year >= 1640 & publication_year <= 1828)
+  top.authors <- names(bibliographica::top(df, field = "author", n = 10))
+  dfs <- df %>% filter(author %in% top.authors) %>%
+         group_by(author, publication_decade) %>%
+         tally() %>%
+         arrange(publication_decade)
+  p <- ggplot(dfs, aes(x = publication_decade, y = n, fill = author)) +
+       geom_bar(stat = "identity", position = "stack", color = "black") +
+       xlab("Publication Decade") +
+       ylab("Title Count") +
+       scale_fill_grey() +
+       guides(fill = guide_legend("Author")) +
+       ggtitle(paste("Title count top authors\n", catalogue)) +
+       xlim(c(1640, 1828))
+  print(p)
+}
+```

### 2016-07-12 inst/examples/20160715-slides-Krakow.Rmd
sync
z
za

@@
 
-- **Visible roots of the diversity of "Finnishness" reflected in knowledge production, 1640-1828**
+**Why this project?**
+
+- Visible roots of the diversity of "Finnishness" reflected in knowledge production, 1640-1828
 
@@
 ```
-
----
-
-### Outline of Quantitative Study of Finnish Knowledge Production, 1640-1828
-
-1) General trends & political events
-
-2) Publishers in Sweden and Turku
-
-3) Languages & religious texts in Finland
-
-4) University curriculum & Enlightenment in Finland
-
-Visible roots of the diversity of "Finnishness" reflected in knowledge production, 1640-1828.
 

### 2016-07-13 inst/examples/manuscript-krakow.Rmd
Rmd update

@@
 
-```{r drop1700B, echo=FALSE, message=FALSE, warning=FALSE, fig.width=15, fig.height=7}
+```{r drop1700BB, echo=FALSE, message=FALSE, warning=FALSE, fig.width=15, fig.height=7}
 catalogue <- "Fennica"
@@
 
-```{r publisherpapertitle, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, out.width="430px", fig.show="hold"}
+```{r publisherpapertitleB, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, out.width="430px", fig.show="hold"}
 for (catalogue in c("Fennica", "Kungliga")) {
@@
 
-```{r language1, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, out.width="430px", fig.show="hold"}
+```{r language1B, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, out.width="430px", fig.show="hold"}
 
@@
 
-```{r topics3, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, out.width="430px", fig.show="hold"}
+```{r topics3B, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, out.width="430px", fig.show="hold"}
 sel <- c("virret","arkkiveisut","hartauskirjat","katekismukset","rukouspäivät","saarnat","aapiset","rukoukset","rukous","hengelliset laulut","hartauspuheet","virsikirjat","hautajaiset","häät","juhlamenot")
@@
 
-```{r 201606krakow-turkuvsother, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=7, fig.width=10, fig.show="hold", out.width="430px"}
+```{r 201606krakow-turkuvsotherB, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=7, fig.width=10, fig.show="hold", out.width="430px"}
 df <- df0 %>%
@@
 
-```{r polev1, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=6, out.width="280px", fig.show="hold"}
+```{r polev1b, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=6, out.width="280px", fig.show="hold"}
 sel.places = c("Stockholm", "Uppsala", "Lund", "Greifswald", "Turku")

### 2016-07-13 inst/examples/20160715-slides-Krakow.Rmd
sync
Rmd update
Fixed multiple languages bug
Fixed multiple languages bug

@@
   otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
+  otherlang <- otherlang[otherlang!="language.Multiple languages"]
+
   df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
@@
   otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
+  otherlang <- otherlang[otherlang!="language.Multiple languages"]
   df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
@@
 otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
+otherlang <- otherlang[otherlang!="language.Multiple languages"]
+
 df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
@@
 
-Source code of these slides:
-- https://github.com/rOpenGov/fennica/blob/master/inst/examples/20160715-slides-Krakow.Rmd
+For more info, see: \textcolor{blue}{https://github.com/rOpenGov/fennica}
 

### 2016-07-13 inst/examples/20160715-slides-Krakow.Rmd
ds

@@
       ggtitle(paste(myplace, "/", catalogue)) +
-      scale_fill_brewer(palette="Paired") + 
+      scale_fill_brewer(palette="Spectral") + 
       guides(fill = guide_legend(reverse = TRUE, title = ""))
@@
      ggtitle(paste("Languages (", catalogue, ")", sep = "")) +
-     scale_fill_brewer(palette="Paired")
+     scale_fill_brewer(palette="Spectral")
 print(p)

### 2016-07-13 inst/examples/20160715-slides-Krakow.Rmd
Slides almost ready

@@
     fonttheme: "professionalfonts"
+fontsize: 13pt
 ---
@@
 # devtools::install_github('cttobin/ggthemr')
-library(gisfin)
 #library(ggthemr)
@@
 ```
-
----
-
-### TODO
-
-sivu 27. Dissertation languages: kategoria "other" sisällön selvittäminen!
-
-Yleisesti eri kuvien tekstit yms. tsekkaaminen, korostukset yms.
 
@@
        scale_color_manual(values = c("blue", "darkgreen")) + 
-       guides(fill = guide_legend(reverse = TRUE, title = "")) #+ 
+       guides(color = guide_legend(reverse = TRUE, title = "")) #+ 
 print(p)
@@
 **Open source** fully transparent and reproducible data analytics: https://github.com/rOpenGov/fennica
-
-**Collaboration & Reuse** further use and enrichment
 
@@
 
-**1. General trends & political events**
+\Large{1. General trends and political events}
 
@@
 
-### Turku as a Swedish University Town among Uppsala, Tartu and Stockholm
+### Turku as a Swedish University Town among Uppsala, Tartu and Stockholm (+ Lund & Greifswald)
 
-```{r map1, echo=FALSE, message=FALSE, warning=FALSE, fig.width=20, fig.height=5, eval=TRUE}
+```{r map1, echo=FALSE, message=FALSE, warning=FALSE, fig.width=20, fig.height=4, eval=TRUE}
 library(dplyr)
@@
 theme_set(get_theme_map())
-mapdata <- filter(df0,
+i <- 1650
+mapdata1 <- filter(df0,
+              publication_decade == i &
               (catalog == "Kungliga" & 
@@
 
+mapdata <- bind_rows(mapdata1, 
+  as.data.frame(list(publication_decade = 1650, publication_place = "Lund", 
+                     latitude = 55.70293, longitude = 13.19294, n = 0)))
+
 mapdata$size <- mapdata$n
@@
 
-region <- "Europe.north"
-mymap <- get_map(location=geobox(region), color = "bw",
-                  source="google",  maptype="terrain")
+mapdata$highlight2 <- rep(1, nrow(mapdata))
+mapdata$highlight2[mapdata$publication_place %in% c("Greifswald", "Lund")] <- 9
+mapdata$highlight2 <- factor(mapdata$highlight2)
 
-p0 <- ggmap(mymap) + theme(legend.position="none")
-
-pics <- list()
-for (i in c(1650, 1710, 1760, 1800)) {
-
-    # Plot map
-    p <- p0
+region <- c(8, 40, 31, 76)
+names(region) <- c("left", "bottom", "right", "top")
+#mymap <- get_map(location=geobox(region), color = "bw", source="osm",  maptype="terrain")
+#mymap <- get_map(location=geobox(region), source="stamen", maptype = "watercolor")
+mymap <- get_map(location=geobox(region), maptype="roadmap")
 
@@
 # Sum up the years within this sliding window for each element    	    
-    dfw <- subset(mapdata, publication_decade == i) %>%
-    	     group_by(publication_place, latitude, longitude, highlight) %>%
+dfw <- mapdata %>%
+    	     group_by(publication_place, latitude, longitude, highlight, highlight2) %>%
 		       summarize(n = sum(size))
+dfw$size <- log10(1 + dfw$n)
+dfw$size[!dfw$highlight2 == 1] <- max(dfw$size)
 
-    if (nrow(dfw) > 0) {
-      p <- p0 +
+# Plot map
+p <- ggmap(mymap) + 
       	geom_point(data = dfw,
-      	  aes(x = longitude, y = latitude,
-	      size = 20*log10(1+n),
+      	  aes(
+      	  x = longitude, 
+      	  y = latitude,
+	        size = size,
+	        shape = highlight2, 
 	        color = highlight)) +
-	      #color = highlight), alpha = 0.8) +	      
 	        ggtitle(i) +
 	        scale_size(range = c(2, 15)) +
-	  theme(title = element_text(size = 30)) +
-	  scale_color_manual(values = c("black", "red"))	  
-    }
+	        theme(title = element_text(size = 30), legend.position="none") +
+	        scale_color_manual(values = c("black", "red")) +
+	        scale_shape_manual(values = c(19,1))
+print(p)
+```
 
-  pics[[as.character(i)]] <- p
-
-}
-
-library(gridExtra)
-grid.arrange(pics[[1]], nrow = 1)
-```
+Map by Stamen
 
@@
 - 1700-1721 Fennica drop
-- 1760-1770s Kungliga peak 
+- 1760-1770 Pamphleteering plays a crucial role during abolished censorship
 - 1803-1815 Napoleonic wars
 
-```{r publishingovertime, echo=FALSE, message=FALSE, warning=FALSE, fig.width=6, fig.height=4, out.width="200px"}
+```{r publishingovertime, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=4, out.width="300px"}
 library(magrittr)
@@
 	      df2$publication_decade %in% c(1710, 1810)] <- TRUE
-v <- seq(1500, 1800, 50)
+v <- seq(1500, 1800, 100)
 theme_set(theme_bw(20))
-p <- ggplot(df2, aes(x = publication_decade, y = n)) +
+p1 <- ggplot(df2, aes(x = publication_decade, y = n)) +
      geom_line(aes(color = catalog), size = 1) +
-     geom_point(aes(shape = catalog, color = highlight, size = highlight)) +
+     geom_point(aes(shape = catalog, color = catalog, size = highlight)) +
      ylab("Title count (n)") + xlab("Publication year") +
@@
      scale_x_continuous(breaks = v, labels = v) +
-     scale_color_manual(values = c("black", "blue", "darkgreen", "blue")) + 
-     guides(fill = guide_legend(reverse = TRUE)) 
-print(p)
-```
+     scale_color_manual(values = c("blue", "darkgreen")) + 
+  	 scale_size_discrete(range = c(2, 8)) +
+     guides(color = guide_legend(reverse = TRUE), size = "none", shape = "none")
 
----
-
-[General trends & political events]
-
-### Swedish 1760-1770 publishing peak
-
-Pamphleteering plays a crucial role during abolished censorship
-
-```{r pamflets1, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=4, out.width="280px", fig.show="hold"}
-df <- df0 %>%
-        filter(catalog == "Kungliga")
-
+df <- df0 %>% filter(catalog == "Kungliga")
 # Add indicator of the publication period
@@
 
-p <- ggplot(df,
+p2 <- ggplot(df,
        aes(x = period, y = paper.per.title)) + 
@@
        ylab("Paper per title") + xlab("")
-print(p)
+
+library(gridExtra)
+grid.arrange(p1, p2, nrow = 1)
 ```
@@
     )
-  rectangles$shade <- rep(c("White", "Highlight"), length = nrow(rectangles))
+  rectangles$shade <- rep(c("Background", "Highlight"), length = nrow(rectangles))
 
  riksplace = c("Stockholm", "Stockholm", "Stockholm", "Norrköping", "Stockholm", "Gävle")
- cols = c("gray", "lightblue", "yellow", "white")
+ cols = c("white", "black", "blue", "darkgray")
  rectangles$shade[rectangles$shade == "Highlight"] = riksplace
@@
 
-**2. Publishers in Sweden and Turku**
+\Large{2. Publishers in Sweden and Turku}
 
@@
 
+\begin{center}
 [Publishers in Sweden and Turku]
+\end{center}
 
@@
 
-### Top publishers in Turku/Fennica (title count)
+### Top publishers in Turku/Fennica
 
-```{r publishers4-fennica, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=7, fig.width=15}
+```{r publishers4-fennica, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=6, fig.width=12}
+library(dplyr)
 place <- "Turku"
@@
 
-df <- df %>%
-        filter(catalog == catalogue & publication_place == place)
+df <- df %>% filter(catalog == catalogue & publication_place == place)
 
@@
 # Title count per decade & publisher	
-npub <- df %>% group_by(publication_decade, publisher) %>% tally()
+npub <- df %>% group_by(publication_decade, publisher) %>% tally() %>% arrange(n)
+npub$publisher <- factor(npub$publisher, levels = (npub %>% group_by(publisher) %>% summarise(total = sum(n)) %>% arrange(total))$publisher)
 
@@
 theme_set(theme_bw(20))
-p <- ggplot(npub, aes(x = publication_decade, y = n)) +
-       geom_bar(stat = "identity", position = "stack", aes(fill = publisher)) + 
-       xlab("Publication year") +
-       ylab("Title count (n)") #+        
+p <- ggplot(npub, aes(x = publication_decade, y = publisher)) +
+      geom_point(aes(size = n)) + 
+      #geom_line(aes(color = publisher), size = 2) +
+      #geom_smooth(aes(fill = publisher)) +
+      # geom_bar(stat = "identity", position = "stack", aes(fill = publisher)) + 
+       xlab("Year") +
+       ylab("") +
+       guides(size = guide_legend(title = "Title count (n)"))
        #ggtitle(paste("Title count per publisher (", place, "/", catalogue, ")", sep = ""))
@@
 
-**3. Languages & religious texts in Finland**
+\Large{3. Languages and religious texts in Finland}
 
@@
 p <- ggplot(df, aes(x = publication_year, y = n, color = language)) +
-       geom_line() + geom_point()
+       geom_line() + geom_point() + ylab("Documents (n)") + xlab("Publication year")
 
@@
 
-### Devotional literature (catechisms, hymns, prayer collections, etc.)
+### Devotional literature (catechisms, hymns, prayers, etc.)
 
-Form of literature denoting the advancement of reading in Finland in the nineteenth century. It has been unclear when does it show up as a relevant category.
+Form of literature denoting the advancement of reading in Finland in the 19th century. It has been unclear when does it show up as a relevant category.
 
@@
 
-- play an important role in early modern knowledge production. It has not been analysed in what language they were in Finland (and Sweden).
+- Important role in early modern knowledge production. It has not been analysed in what language they were in Finland (and Sweden).
 
@@
 
-**4. University curriculum & Enlightenment in Finland**
+\Large{4. University curriculum and Enlightenment in Finland}
 
@@
 
-```{r disslang, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6}
+```{r disslang, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
 catalogue <- "Fennica"
@@
 
-```{r topics-103B, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=9}
+```{r topics-103B, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=8}
 sel = c("filosofia","luonnonfilosofia","metafysiikka","logiikka")
@@
        xlab("Publication year") +
-       ylab("Paper consumption") +
+       ylab("Paper") +
        guides(fill = guide_legend(reverse = TRUE, title = "")) +
@@
 
-Paper consumption for different document formats over time.
+Paper consumption: different document formats over time
 
@@
   df2 <- filter(df2, gatherings %in% setdiff(names(which(table(df2$gatherings) >= 15)), "NA"))
-  df2$highlight <- rep("gray", nrow(df2))
-  df2$highlight[df2$gatherings == "8vo"] <- "darkgreen"
+  df2$highlight <- rep("Other", nrow(df2))
+  df2$highlight[df2$gatherings == "8vo"] <- "Octavo"
 
@@
        	          shape = guide_legend(keywidth = 5))
-  p <- p + ggtitle(paste("Paper consumption\n(", catal, ")", sep = ""))
+  p <- p + ggtitle(catal)
   print(p)
@@
 
-For more info, see: \textcolor{blue}{https://github.com/rOpenGov/fennica}
+For more info, see:
+
+- \textcolor{blue}{https://github.com/rOpenGov/fennica}
 

### 2016-07-13 inst/examples/slides.Rmd
Slides almost ready

@@
 ```
+
+[General trends & political events]
+
+### Publishing activity over time
+
+- 1700-1721 Fennica drop
+- 1760-1770 Kungliga peak 
+- 1803-1815 Napoleonic wars
+
+```{r publishingovertime, echo=FALSE, message=FALSE, warning=FALSE, fig.width=6, fig.height=4, out.width="200px"}
+library(magrittr)
+library(ggplot2)
+library(dplyr)
+df2 <- df0 %>% group_by(publication_decade, catalog) %>%
+               summarise(n = n())
+df2$highlight <- rep(FALSE, nrow(df2))
+df2$highlight[df2$catalog == "Kungliga" &
+	      df2$publication_decade %in% c(1770, 1810)] <- TRUE
+df2$highlight[df2$catalog == "Fennica" &
+	      df2$publication_decade %in% c(1710, 1810)] <- TRUE
+v <- seq(1500, 1800, 100)
+theme_set(theme_bw(20))
+p <- ggplot(df2, aes(x = publication_decade, y = n)) +
+     geom_line(aes(color = catalog), size = 1) +
+     geom_point(aes(shape = catalog, color = catalog, size = highlight)) +
+     ylab("Title count (n)") + xlab("Publication year") +
+     #theme(legend.position = "none") +
+     scale_x_continuous(breaks = v, labels = v) +
+     scale_color_manual(values = c("blue", "darkgreen")) + 
+  	 scale_size_discrete(range = c(2, 8)) +
+     guides(color = guide_legend(reverse = TRUE), size = "none", shape = "none") 
+print(p)
+```
+
+---
+
+[General trends & political events]
+
+### Swedish 1760-1770 publishing peak
+
+Pamphleteering plays a crucial role during abolished censorship
+
+```{r pamflets1, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=4, out.width="280px", fig.show="hold"}
+df <- df0 %>% filter(catalog == "Kungliga")
+
+# Add indicator of the publication period
+df$period <- cut(df$publication_year,
+           breaks = c(1757, 1766, 1775, 1783),
+		 include.lowest = TRUE,
+		 right = FALSE
+		 )
+
+# Remove entries outside the investigated publication periods
+df <- df %>% filter(!is.na(period)) %>%
+	     group_by(period) %>%
+	     summarise(n = n(),
+		  paper = sum(paper.consumption.km2, na.rm = TRUE)) %>%
+        mutate(paper.per.title = paper/n)
+
+p <- ggplot(df,
+       aes(x = period, y = paper.per.title)) + 
+       geom_bar(stat = "identity") +
+       scale_x_discrete(labels = c("1757-1765", "1766-1774", "1775-1783")) +
+       ylab("Paper per title") + xlab("") 
+print(p)
+```
+
+---

### 2016-07-14 inst/examples/20160715-slides-Krakow.Rmd
s

@@
 
-An example how historical events, namely parliamentary assemblies in the Swedish case, have an effect on knowledge production.
+An example how historical events, namely **parliamentary assemblies** in the Swedish case, have an effect on knowledge production.
 
@@
  riksplace = c("Stockholm", "Stockholm", "Stockholm", "Norrköping", "Stockholm", "Gävle")
- cols = c("white", "black", "blue", "darkgray")
+ cols = c("pink", "Purple", "aquamarine", "yellow")
  rectangles$shade[rectangles$shade == "Highlight"] = riksplace
@@
   p <- p + xlab("Year")
-  p <- p + ggtitle(catal)
+  p <- p + ggtitle(paste(catal,"Riksplaces"))
   print(p)
@@
 library(magrittr)
+library(dplyr)
 library(tidyr)

### 2016-07-14 inst/examples/20160715-slides-Krakow.Rmd
d

@@
 
+[Publishers in Sweden and Turku]
+
+### Turku in Sweden: proportions for title count and paper in Swedish University towns
+
+```{r comparisons, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=18, fig.height=10}
+pics <- list()
+for (catalogue in na.omit(unique(df0$catalog))) {
+
+df <- df0 %>% filter(catalog == catalogue)%>%
+        filter(publication_year >= 1640 & publication_year <= 1828)
+places <- c("Stockholm", "Uppsala", "Lund", "Greifswald", "Tartu", "Turku")
+df$publication_place[!df$publication_place %in% places] <- "Other"
+df <- subset(df, !is.na(df$publication_place))
+#df$publication_place <- factor(df$publication_place, levels = c(places, "Other"))
+library(reshape2)
+library(magrittr)
+library(dplyr)
+library(tidyr)
+
+df <- df %>% group_by(publication_decade, publication_place) %>%
+             summarise(n = n(),
+                paper = sum(paper.consumption.km2, na.rm = TRUE),
+		       publishers = length(na.omit(unique(publisher)))
+		       )
+
+# Calculate percentages
+for (varname in c("n", "paper", "publishers")) {
+
+  df$varname <- df[[varname]]
+  dff <- df %>% select(publication_decade, publication_place, varname)
+  dff <- spread(dff, publication_place, varname, fill = 0)
+  dff[, -1] <- 100 * t(apply(dff[, -1], 1, function (x) {x/sum(x)}))
+  dff <- melt(dff, "publication_decade");
+  colnames(dff) <- c("publication_decade", "publication_place", "f")
+
+  theme_set(theme_bw(20))
+  p <- ggplot(dff, aes(x = publication_decade, y = f)) +
+     geom_bar(position = "stack", stat = "identity",
+       aes(fill = publication_place)) + 
+     xlab("Publication year") +
+     scale_fill_brewer(palette="Paired")
+     if (varname == "n") {
+       p <- p + ggtitle(paste("Title count (", catalogue, ")", sep = "")) + 
+                ylab("Title count frequency (%)") 
+     }
+     if (varname == "paper") {
+       p <- p + ggtitle(paste("Paper (", catalogue, ")", sep = "")) +
+                ylab("Paper (%)")        
+     }
+     if (varname == "publishers") {
+       p <- p + ggtitle(paste("Publishers (", catalogue, ")", sep = "")) +
+                       ylab("Publishers (%)")
+     }     
+  p <- p + guides(fill = guide_legend(reverse = TRUE, title = ""))
+
+  pics[[paste(catalogue, varname, sep = "-")]] <- p
+
+}
+}
+library(gridExtra)
+grid.arrange(pics[[1]], pics[[2]], pics[[4]], pics[[5]], nrow = 2)
+rm(pics)
+```
+
+---
+
 \begin{center}
@@
 print(p)
-```
-
----
-
-[Publishers in Sweden and Turku]
-
-### Turku in Sweden: proportions for title count and paper in Swedish University towns
-
-```{r comparisons, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=18, fig.height=10}
-pics <- list()
-for (catalogue in na.omit(unique(df0$catalog))) {
-
-df <- df0 %>% filter(catalog == catalogue)%>%
-        filter(publication_year >= 1640 & publication_year <= 1828)
-places <- c("Stockholm", "Uppsala", "Lund", "Greifswald", "Turku")
-df$publication_place[!df$publication_place %in% places] <- "Other"
-df <- subset(df, !is.na(df$publication_place))
-#df$publication_place <- factor(df$publication_place, levels = c(places, "Other"))
-library(reshape2)
-library(magrittr)
-library(dplyr)
-library(tidyr)
-
-df <- df %>% group_by(publication_decade, publication_place) %>%
-             summarise(n = n(),
-       	       paper = sum(paper.consumption.km2, na.rm = TRUE),
-		       publishers = length(na.omit(unique(publisher)))
-		       )
-
-# Calculate percentages
-for (varname in c("n", "paper", "publishers")) {
-
-  df$varname <- df[[varname]]
-  dff <- df %>% select(publication_decade, publication_place, varname)
-  dff <- spread(dff, publication_place, varname, fill = 0)
-  dff[, -1] <- 100 * t(apply(dff[, -1], 1, function (x) {x/sum(x)}))
-  dff <- melt(dff, "publication_decade");
-  colnames(dff) <- c("publication_decade", "publication_place", "f")
-
-  theme_set(theme_bw(20))
-  p <- ggplot(dff, aes(x = publication_decade, y = f)) +
-     geom_bar(position = "stack", stat = "identity",
-       aes(fill = publication_place)) + 
-     xlab("Publication year") +
-     scale_fill_brewer(palette="Paired")
-     if (varname == "n") {
-       p <- p + ggtitle(paste("Title count (", catalogue, ")", sep = "")) + 
-                ylab("Title count frequency (%)") 
-     }
-     if (varname == "paper") {
-       p <- p + ggtitle(paste("Paper (", catalogue, ")", sep = "")) +
-                ylab("Paper (%)")        
-     }
-     if (varname == "publishers") {
-       p <- p + ggtitle(paste("Publishers (", catalogue, ")", sep = "")) +
-                       ylab("Publishers (%)")
-     }     
-  p <- p + guides(fill = guide_legend(reverse = TRUE, title = ""))
-
-  pics[[paste(catalogue, varname, sep = "-")]] <- p
-
-}
-}
-library(gridExtra)
-grid.arrange(pics[[1]], pics[[2]], pics[[4]], pics[[5]], nrow = 2)
-rm(pics)
 ```

### 2016-07-14 inst/examples/20160715-slides-Krakow.Rmd
sync

--- 2016-07-14 inst/examples/20160715-slides-Krakow.Rmd
@@
 
-**Customized** dedicated R packages for bibliographic analysis combine flexibility with automation
+**Customized** our dedicated R packages for bibliographic analysis combine flexibility with automation
 
-**Automated** scales well with new data and unforeseen changes; a million documents ~ 30 minutes
+**Automated** scales well with new data and unforeseen changes; a million documents cleaned up in 30 minutes
 
@@
 dfw$size <- log10(1 + dfw$n)
-dfw$size[!dfw$highlight2 == 1] <- max(dfw$size)
+dfw$size[!dfw$highlight2 == 1] <- 0.5*max(dfw$size)
 
@@
 p <- ggmap(mymap) +
-      	geom_point(data = dfw,
+
+        	geom_point(data = subset(dfw, highlight2 == 1),
       	    aes(
@@
 	            size = size,
-	        shape = highlight2, 
-	        color = highlight)) +
+	            shape = 1, 
+	            #shape = highlight2, 
+	            fill = highlight), 
+      	      pch = 21, stroke = 1) +
+
+        	geom_point(data = subset(dfw, !highlight2 == 1),
+      	    aes(
+      	      thickness = 10,
+      	      x = longitude, 
+      	      y = latitude,
+	            shape = 19, 
+	            #shape = highlight2, 
+	            color = highlight), 
+      	      colour = "black", 
+      	      shape = 21, # Point shape 
+      	      size = 7,   # Point size
+      	      stroke = 2) + # Point edge thickness
+
 	        ggtitle(i) +
@@
 	        theme(title = element_text(size = 30), legend.position="none") +
-	        scale_color_manual(values = c("black", "red")) +
-	        scale_shape_manual(values = c(19,1))
+	        scale_fill_manual(values = c("darkgray", "red")) #+
+	        #scale_shape_manual(values = c(19,1))
 print(p)
@@
 npub <- df %>% group_by(publication_decade, publisher) %>% tally() %>% arrange(n)
-npub$publisher <- factor(npub$publisher, levels = (npub %>% group_by(publisher) %>% summarise(total = sum(n)) %>% arrange(total))$publisher)
+#npub$publisher <- factor(npub$publisher, levels = (npub %>% group_by(publisher) %>% summarise(total = sum(n)) %>% arrange(total))$publisher)
+# Sort by biggest publication decade
+#ord <- (npub %>% group_by(publisher) %>% summarise(decade = publication_decade[[which.max(n)]]) %>% arrange(decade))$publisher
+ord <- as.character((npub %>% group_by(publisher) %>% 
+                        summarise(decade = median(publication_decade)) %>% 
+                        arrange(decade))$publisher)
+npub$publisher <- factor(npub$publisher, levels = ord)
 

### 2016-07-14 inst/examples/20160715-slides-Krakow.Rmd
ok

@@
 
-**Augment data** (geocoordinates, gender, ..)
+**Enrich data** (geocoordinates, gender, ..)
 
@@
 
----
-
-\Large{1. General trends and political events}
+- Parse, clean up, enrich, summarise, analyze, visualize, report..
 
@@
 
-[General trends & political events]
+\begin{center}
+\Large{1. General trends and political events}
+\end{center}
+
+---
+
+\begin{center}
+\tiny{\textcolor{gray}{General trends \& political events}}
+\end{center}
 
@@
       	      size = 7,   # Point size
-      	      stroke = 2) + # Point edge thickness
+      	      stroke = 1.5) + # Point edge thickness
 
@@
 
-[General trends & political events]
+\begin{center}
+\tiny{\textcolor{gray}{General trends \& political events}}
+\end{center}
 
@@
  riksplace = c("Stockholm", "Stockholm", "Stockholm", "Norrköping", "Stockholm", "Gävle")
- cols = c("pink", "Purple", "aquamarine", "yellow")
+ cols = c("white", "Purple", "blue", "orange")
  rectangles$shade[rectangles$shade == "Highlight"] = riksplace
@@
 
+\begin{center}
 \Large{2. Publishers in Sweden and Turku}
+\end{center}
 
@@
 
-[Publishers in Sweden and Turku]
+\begin{center}
+\tiny{\textcolor{gray}{Publishers in Sweden and Turku}}
+\end{center}
 
@@
 \begin{center}
-[Publishers in Sweden and Turku]
+\tiny{\textcolor{gray}{Publishers in Sweden and Turku}}
 \end{center}
@@
                         arrange(decade))$publisher)
-npub$publisher <- factor(npub$publisher, levels = ord)
+npub$publisher <- factor(npub$publisher, levels = c("Other", setdiff(ord, "Other")))
 
@@
 
+\begin{center}
 \Large{3. Languages and religious texts in Finland}
+\end{center}
 
@@
 
-[Languages & religious texts in Finland]
+\begin{center}
+\tiny{\textcolor{gray}{Languages \& religious texts in Finland}}
+\end{center}
 
@@
 p <- ggplot(df, aes(x = publication_year, y = n, color = language)) +
-       geom_line() + geom_point() + ylab("Documents (n)") + xlab("Publication year")
+       geom_line() + geom_point() + 
+       geom_smooth(aes(fill = language, color = language)) + 
+       ylab("Documents (n)") + xlab("Publication year")
 
@@
        geom_line(aes(col = language, shape = language)) +       
+       #geom_smooth(aes(fill = language, color = language)) + 
        xlab("Publication year") +
@@
 
+\begin{center}
 \Large{4. University curriculum and Enlightenment in Finland}
+\end{center}
 
@@
 
-[University curriculum & Enlightenment in Finland]
+\begin{center}
+\tiny{\textcolor{gray}{University curriculum \& Enlightenment in Finland}}
+\end{center}
 
@@
 
+Code infrastructure:
+
+- Github
+- R project
+
 For more info, see:
@@
 - \textcolor{blue}{https://github.com/rOpenGov/fennica}
+
+\begin{figure}
+\begin{tabular}{cccccc}
+\includegraphics[width=2cm,height=2cm]{aka.png}&
+\includegraphics[width=1cm,height=1cm]{HY-CC.png}&
+\includegraphics[width=1cm,height=1cm]{kansalliskirjasto.png}&
+\includegraphics[width=1cm,height=1cm]{kungliga.png}&
+\includegraphics[width=1cm,height=1cm]{github-logo.png}
+\end{tabular}
+\end{figure}
 

### 2016-07-14 inst/examples/20160715-slides-Krakow.Rmd
ok
s

--- 2016-07-14 inst/examples/20160715-slides-Krakow.Rmd
@@
 
-**Customized** our dedicated R packages for bibliographic analysis combine flexibility with automation
+**Customized** dedicated R packages for bibliographic analysis combine flexibility with automation
 
-**Automated** scales well with new data and unforeseen changes; a million documents cleaned up in 30 minutes
+**Automated** scales well with new data and unforeseen changes; a million documents ~ 30 minutes
 
@@
 dfw$size <- log10(1 + dfw$n)
-dfw$size[!dfw$highlight2 == 1] <- 0.5*max(dfw$size)
+dfw$size[!dfw$highlight2 == 1] <- max(dfw$size)
 
@@
 p <- ggmap(mymap) + 
-
-        	geom_point(data = subset(dfw, highlight2 == 1),
+      	geom_point(data = dfw,
       	  aes(
@@
 	        size = size,
-	            shape = 1, 
-	            #shape = highlight2, 
-	            fill = highlight), 
-      	      pch = 21, stroke = 1) +
-
-        	geom_point(data = subset(dfw, !highlight2 == 1),
-      	    aes(
-      	      thickness = 10,
-      	      x = longitude, 
-      	      y = latitude,
-	            shape = 19, 
-	            #shape = highlight2, 
-	            color = highlight), 
-      	      colour = "black", 
-      	      shape = 21, # Point shape 
-      	      size = 7,   # Point size
-      	      stroke = 2) + # Point edge thickness
-
+	        shape = highlight2, 
+	        color = highlight)) +
 	        ggtitle(i) +
@@
 	        theme(title = element_text(size = 30), legend.position="none") +
-	        scale_fill_manual(values = c("darkgray", "red")) #+
-	        #scale_shape_manual(values = c(19,1))
+	        scale_color_manual(values = c("black", "red")) +
+	        scale_shape_manual(values = c(19,1))
 print(p)
@@
      xlab("Publication year") +
-     scale_fill_brewer(palette="Paired")
+     scale_fill_brewer(palette="Spectral")
      if (varname == "n") {
@@
        ylab("Unique publishers (n)") +
+      scale_fill_brewer(palette="Spectral") +       
        guides(fill = guide_legend(reverse = TRUE, title = "")) #+ 
@@
 npub <- df %>% group_by(publication_decade, publisher) %>% tally() %>% arrange(n)
-#npub$publisher <- factor(npub$publisher, levels = (npub %>% group_by(publisher) %>% summarise(total = sum(n)) %>% arrange(total))$publisher)
-# Sort by biggest publication decade
-#ord <- (npub %>% group_by(publisher) %>% summarise(decade = publication_decade[[which.max(n)]]) %>% arrange(decade))$publisher
-ord <- as.character((npub %>% group_by(publisher) %>% 
-                        summarise(decade = median(publication_decade)) %>% 
-                        arrange(decade))$publisher)
-npub$publisher <- factor(npub$publisher, levels = ord)
+npub$publisher <- factor(npub$publisher, levels = (npub %>% group_by(publisher) %>% summarise(total = sum(n)) %>% arrange(total))$publisher)
 

### 2016-07-14 inst/examples/20160715-slides-Krakow.Rmd

--- 2016-07-14 inst/examples/20160715-slides-Krakow.Rmd
@@
  riksplace = c("Stockholm", "Stockholm", "Stockholm", "Norrköping", "Stockholm", "Gävle")
- cols = c("white", "Purple", "blue", "orange")
+ cols = c("white", "Purple", "yellow", "orange")
  rectangles$shade[rectangles$shade == "Highlight"] = riksplace
@@
 \includegraphics[width=1cm,height=1cm]{kungliga.png}&
-\includegraphics[width=1cm,height=1cm]{github-logo.png}
+\includegraphics[width=1cm,height=1cm]{github-logo.png}&
+\includegraphics[width=1cm,height=1cm]{Rlogo.png}
 \end{tabular}

### 2016-07-14 inst/examples/20160715-slides-Krakow.Rmd
d

@@
 
-- 1700-1721 Fennica drop
+- 1700-1721 Great Northern War & Fennica drop during "the Great Wrath"
 - 1760-1770 Pamphleteering plays a crucial role during abolished censorship
@@
 
-### Different languages in Turku, Stockholm, Lund and Uppsala
+### Different languages in Turku, Stockholm, Uppsala and Lund
 
@@
 
-### Topic richness per language (Finnish publications)
+### Topic richness per language (publications in Fennica)
 
@@
 
-Form of literature denoting the advancement of reading in Finland in the 19th century. It has been unclear when does it show up as a relevant category.
+Form of literature denoting the advancement of reading in Finland in the 19th century. It has been unclear when devotional literature  shows up as a relevant category.
 
@@
        ylab("Paper consumption") +
-       ggtitle(catalogue) 
-       #ggtitle(paste("Languages (", catalogue, ")", sep = "")) 
+       ggtitle(paste("Devotional Literature (", catalogue, ")", sep = ""))
+       #ggtitle(paste("Devotional literature" (", catalogue, ")", sep = "")) 
   print(p)
@@
 
-- Important role in early modern knowledge production. It has not been analysed in what language they were in Finland (and Sweden).
+- Important role in early modern knowledge production. Language of temporary sermons in contrast to devotional literature has not been analysed in Finland (and Sweden).
 
@@
        ylab("Paper consumption") +
-       ggtitle(paste("Languages (", catalogue, ")", sep = ""))
+       ggtitle(paste("Temporary Sermons (", catalogue, ")", sep = ""))
   print(p)
@@
      ylab("Title count frequency (%)") +
-     ggtitle(paste("Languages (", catalogue, ")", sep = "")) +
+     ggtitle(paste("Dissertation languages (", catalogue, ")", sep = "")) +
      scale_fill_brewer(palette="Spectral")
@@
 
-### Printing by topic in different languages in Turku
+### Printing by topics in different languages in Turku
 

### 2016-07-14 inst/examples/20151209-HelsinkiDH.Rmd
paper from km2 to sheets

@@
       filter(!is.na(country)) %>%
-      filter(!is.na(publication_place) & !is.na(paper.consumption.km2) & paper.consumption.km2 > -0.01)
+      filter(!is.na(publication_place) & !is.na(paper) & paper > -0.01)
 
@@
 dfs <- df %>% group_by(publication_decade, myplace) %>%
-  summarise(titles = n(), paper = sum(paper.consumption.km2, na.rm = TRUE))
+  summarise(titles = n(), paper = sum(paper, na.rm = TRUE))
 
@@
      guides(fill = guide_legend(reverse = TRUE)) + 
-     xlab("Publication decade") + ylab("Paper (km2)")
+     xlab("Publication decade") + ylab("Paper")
 print(p)
@@
 
-dfs <- dfo %>% filter(author %in% topa) %>% group_by(author, publication_decade) %>% summarize(paper = sum(paper.consumption.km2, na.rm = T), titles = n())
+dfs <- dfo %>% filter(author %in% topa) %>% group_by(author, publication_decade) %>% summarize(paper = sum(paper, na.rm = T), titles = n())
 
@@
 
-p2 <- ggplot(dfs, aes(x = publication_decade, y = paper, color = author)) + geom_point() + geom_line(size = 2) + scale_color_manual(values = c("blue", "red")) + ggtitle("Paper consumption") + xlab("Publication decade") + ylab("Paper (km2)")
+p2 <- ggplot(dfs, aes(x = publication_decade, y = paper, color = author)) + geom_point() + geom_line(size = 2) + scale_color_manual(values = c("blue", "red")) + ggtitle("Paper consumption") + xlab("Publication decade") + ylab("Paper")
 print(p2)

### 2016-07-14 inst/examples/Paper.Rmd
paper from km2 to sheets

@@
 dfs <- df %>% filter(publication_year > 1400 & publication_year < 1829) %>%
-  filter(!is.na(paper.consumption.km2) & paper.consumption.km2 > -0.01) %>%
+  filter(!is.na(paper) & paper > -0.01) %>%
   group_by(publication_year) %>%
-  summarise(titles = n(), paper = sum(paper.consumption.km2))
+  summarise(titles = n(), paper = sum(paper))
 authors <- df %>% filter(publication_year > 1400 & publication_year < 1829) %>%
@@
   filter(author_name %in% c(top10.authors$author_name)) %>%
-  filter(!is.na(paper.consumption.km2) & paper.consumption.km2 > -0.01) %>%
+  filter(!is.na(paper) & paper > -0.01) %>%
   group_by(publication_year) %>%
-  summarise(titles = n(), paper = sum(paper.consumption.km2))
+  summarise(titles = n(), paper = sum(paper))
 df.Turku <- df %>% filter(publication_year > 1400 & publication_year < 1829) %>%
   filter(publication_place == "Turku") %>%
-  filter(!is.na(paper.consumption.km2) & paper.consumption.km2 > -0.01) %>%
+  filter(!is.na(paper) & paper > -0.01) %>%
   group_by(publication_year) %>%
-  summarise(titles = n(), paper = sum(paper.consumption.km2))
+  summarise(titles = n(), paper = sum(paper))
 df.Tukholma <- df %>% filter(publication_year > 1400 & publication_year < 1829) %>%
   filter(publication_place == "Stockholm") %>%
-  filter(!is.na(paper.consumption.km2) & paper.consumption.km2 > -0.01) %>%
+  filter(!is.na(paper) & paper > -0.01) %>%
   group_by(publication_year) %>%
-  summarise(titles = n(), paper = sum(paper.consumption.km2))
+  summarise(titles = n(), paper = sum(paper))
 df.Vaasa <- df %>% filter(publication_year > 1400 & publication_year < 1829) %>%
   filter(publication_place == "Vaasa") %>%
-  filter(!is.na(paper.consumption.km2) & paper.consumption.km2 > -0.01) %>%
+  filter(!is.na(paper) & paper > -0.01) %>%
   group_by(publication_year) %>%
-  summarise(titles = n(), paper = sum(paper.consumption.km2))
+  summarise(titles = n(), paper = sum(paper))
 df.Uppsala <- df %>% filter(publication_year > 1400 & publication_year < 1829) %>%
   filter(publication_place == "Uppsala") %>%
-  filter(!is.na(paper.consumption.km2) & paper.consumption.km2 > -0.01) %>%
+  filter(!is.na(paper) & paper > -0.01) %>%
   group_by(publication_year) %>%
-  summarise(titles = n(), paper = sum(paper.consumption.km2))
+  summarise(titles = n(), paper = sum(paper))
 ```
@@
        xlab("Publication Year") +
-       ylab("Paper Consumption (km2)")
+       ylab("Paper Consumption")
 

### 2016-07-14 inst/examples/manuscript-krakow.Rmd
paper from km2 to sheets

@@
      	  group_by(publication_year, publisher) %>%
-	  summarize(paper = sum(paper.consumption.km2, na.rm = TRUE), n = n())
+	  summarize(paper = sum(paper, na.rm = TRUE), n = n())
 
@@
      	  group_by(publication_decade, publisher) %>%
-	  summarize(paper = sum(paper.consumption.km2, na.rm = TRUE), n = n()) %>%
+	  summarize(paper = sum(paper, na.rm = TRUE), n = n()) %>%
 	  mutate(paper.per.title = paper/n)
@@
 ```{r publishingovertime, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=10, out.width="430px"}
-df2 <- df0 %>% group_by(publication_decade, catalog) %>% summarise(paper = sum(paper.consumption.km2, na.rm = TRUE), n = n())
+df2 <- df0 %>% group_by(publication_decade, catalog) %>% summarise(paper = sum(paper, na.rm = TRUE), n = n())
 df2$catalog = factor(df2$catalog, levels = rev(c("Fennica", "Kungliga")))
@@
              summarise(n = n(),
-	               paper = sum(paper.consumption.km2, na.rm = TRUE))
+	               paper = sum(paper, na.rm = TRUE))
 
@@
   df <- df %>% group_by(publication_decade, language) %>%
-             summarise(n = n(), paper = sum(paper.consumption.km2, na.rm = TRUE))
+             summarise(n = n(), paper = sum(paper, na.rm = TRUE))
 
@@
 
-  dfs <- df %>% filter(publication_place %in% top) %>% group_by(publication_decade, publication_place, country) %>% summarize(n = n(), paper = sum(paper.consumption.km2, na.rm = T))  %>% mutate(paper.per.document = paper/n)
+  dfs <- df %>% filter(publication_place %in% top) %>% group_by(publication_decade, publication_place, country) %>% summarize(n = n(), paper = sum(paper, na.rm = T))  %>% mutate(paper.per.document = paper/n)
 
@@
   df2 <- df2 %>% group_by(publication_decade, document.type) %>%
-                 summarize(paper.consumption.km2 = sum(paper.consumption.km2, na.rm = TRUE), n = n()) 
-  p <- ggplot(df2, aes(x = publication_decade, y = paper.consumption.km2, group = document.type))
+                 summarize(paper = sum(paper, na.rm = TRUE), n = n()) 
+  p <- ggplot(df2, aes(x = publication_decade, y = paper, group = document.type))
   p <- p + geom_point(aes(shape = document.type), size = 5)
@@
   p <- p + xlab("Year")
-  p <- p + ylab("Paper consumption (km2)")
+  p <- p + ylab("Paper consumption")
   p <- p + scale_color_manual(values=c("black", "darkgray"))
@@
 
-  df2 <- df2 %>% group_by(publication_decade, document.type) %>% summarize(paper.consumption.km2 = sum(paper.consumption.km2, na.rm = TRUE), n = n())
+  df2 <- df2 %>% group_by(publication_decade, document.type) %>% summarize(paper = sum(paper, na.rm = TRUE), n = n())
 
   if (nrow(df2) > 0) {
-    p <- ggplot(df2, aes(x = publication_decade, y = paper.consumption.km2, group = document.type))
+    p <- ggplot(df2, aes(x = publication_decade, y = paper, group = document.type))
     p <- p + geom_point(aes(shape = document.type), size = 5)
@@
     p <- p + xlab("Year")
-    p <- p + ylab("Paper consumption (km2)")
+    p <- p + ylab("Paper consumption")
     p <- p + scale_color_manual(values=c("black", "darkgray"))
@@
 dfs <- df0 %>% group_by(publication_decade) %>%
-         summarize(paper.per.doc = mean(paper.consumption.km2, na.rm = T))
+         summarize(paper.per.doc = mean(paper, na.rm = T))
 p <- ggplot(dfs, aes(y = paper.per.doc, x = publication_decade)) +
@@
 for (catal in unique(df0$catalog)) {
-  df2 <- subset(df0, catalog == catal) %>% group_by(publication_decade, gatherings) %>% summarize(paper.consumption.km2 = sum(paper.consumption.km2, na.rm = TRUE), n = n()) 
+  df2 <- subset(df0, catalog == catal) %>% group_by(publication_decade, gatherings) %>% summarize(paper = sum(paper, na.rm = TRUE), n = n()) 
   df2 <- filter(df2, gatherings %in% setdiff(names(which(table(df2$gatherings) >= 15)), "NA"))
-  p <- ggplot(df2, aes(y = paper.consumption.km2, x = publication_decade, shape = gatherings, linetype = gatherings))
+  p <- ggplot(df2, aes(y = paper, x = publication_decade, shape = gatherings, linetype = gatherings))
   p <- p + geom_point(size = 4)
@@
   p <- p + xlab("Year")
-  p <- p + ylab("Paper consumption (km2)")
+  p <- p + ylab("Paper consumption")
   p <- p + guides(linetype = guide_legend(keywidth = 5), shape = guide_legend(keywidth = 5))
@@
   df2 <- filter(df0, catalog == catal & publication_place == place) %>%
-           group_by(publication_decade, gatherings) %>% summarize(paper.consumption.km2 = sum(paper.consumption.km2, na.rm = TRUE), n = n())
+           group_by(publication_decade, gatherings) %>% summarize(paper = sum(paper, na.rm = TRUE), n = n())
   df2 <- filter(df2, gatherings %in% setdiff(names(which(table(df2$gatherings) >= 15)), "NA"))
@@
   if (nrow(df2) > 0) {
-  p <- ggplot(df2, aes(y = paper.consumption.km2, x = publication_decade, shape = gatherings, linetype = gatherings))
+  p <- ggplot(df2, aes(y = paper, x = publication_decade, shape = gatherings, linetype = gatherings))
   p <- p + geom_point(size = 4)
@@
      guides(fill = guide_legend(reverse = TRUE, title = "")) + 
-     xlab("Publication decade") + ylab("Paper (km2)")
+     xlab("Publication decade") + ylab("Paper")
 print(p)
@@
 df <- df %>%	
-        select(publication_decade, publisher, paper.consumption.km2)
+        select(publication_decade, publisher, paper)
 
@@
 # Publishing per decade & publisher	
-npub <- df %>% group_by(publication_decade, publisher) %>% summarize(paper = sum(paper.consumption.km2, na.rm = TRUE))
+npub <- df %>% group_by(publication_decade, publisher) %>% summarize(paper = sum(paper, na.rm = TRUE))
 
@@
              summarise(n = n(),
-	     	   paper = sum(paper.consumption.km2, na.rm = TRUE))
+	     	   paper = sum(paper, na.rm = TRUE))
 
@@
              summarise(n = n(),
-                 paper = sum(paper.consumption.km2, na.rm = TRUE))
+                 paper = sum(paper, na.rm = TRUE))
 
@@
                 summarise(n = n(),
-	               paper = sum(paper.consumption.km2, na.rm = TRUE))
+	               paper = sum(paper, na.rm = TRUE))
 

### 2016-07-14 inst/examples/notebook.Rmd
README polish
paper from km2 to sheets

@@
 ---
-title: 'Printing in a Periphery: a Quantitative Study of Finnish Knowledge Production,
-  1640-1828'
+title: 'Printing in a Periphery: a Quantitative Study of Finnish Knowledge Production, 1640-1828'
 author: "Mikko Tolonen, Jani Marjanen, Hege Roivainen, Leo Lahti"
@@
 grid.arrange(pics[[1]], pics[[2]], pics[[3]], pics[[4]], nrow = 1)
+#grid.arrange(pics[[1]], pics[[2]], pics[[3]], nrow = 1)
 ```
@@
 	     summarise(n = n(),
-		  paper = sum(paper.consumption.km2, na.rm = TRUE)) %>%
+		  paper = sum(paper, na.rm = TRUE)) %>%
         mutate(paper.per.title = paper/n)
@@
              summarise(n = n(),
-       	       paper = sum(paper.consumption.km2, na.rm = TRUE),
+       	       paper = sum(paper, na.rm = TRUE),
 		       publishers = length(na.omit(unique(publisher)))
@@
   filter(publication_year >= 1640 & publication_year <= 1828)%>%
-        select(publication_decade, publisher, paper.consumption.km2)
+        select(publication_decade, publisher, paper)
 
@@
 for (catal in unique(df0$catalog)) {
-  df2 <- subset(df0, catalog == catal) %>% group_by(publication_decade, gatherings) %>% summarize(paper.consumption.km2 = sum(paper.consumption.km2, na.rm = TRUE), n = n()) 
+  df2 <- subset(df0, catalog == catal) %>% group_by(publication_decade, gatherings) %>% summarize(paper = sum(paper, na.rm = TRUE), n = n()) 
   df2 <- filter(df2, gatherings %in% setdiff(names(which(table(df2$gatherings) >= 15)), "NA"))
@@
 
-  p <- ggplot(df2, aes(y = paper.consumption.km2,
+  p <- ggplot(df2, aes(y = paper,
                        x = publication_decade,
@@
   p <- p + xlab("Year")
-  p <- p + ylab("Paper consumption (km2)")
+  p <- p + ylab("Paper consumption")
   p <- p + guides(linetype = guide_legend(keywidth = 5),

### 2016-07-14 inst/examples/slides.Rmd
paper from km2 to sheets

@@
 ---
-title: "Untitled"
+title: "Misc Slides"
 output: ioslides_presentation

### 2016-07-14 inst/examples/summary.Rmd
ok
paper from km2 to sheets

--- 2016-04-02 inst/examples/summary.Rmd
@@
 title: "Preprocessing summary"
-author: "Leo Lahti and Niko Ilomäki"
-date: "March 2, 2016"
+author: "Leo Lahti"
+date: "July 2, 2016"
 ---
@@
 df <- readRDS("df.Rds")
-df.orig <- readRDS("df.orig.Rds")
+df.orig <- readRDS("df.raw.Rds")
 conversions <- readRDS("conversions.Rds")
+```
+
+Fields of special interest. Real success percentage (proportion of successful conversions compared to non-NA entries in the original data):
+
+```{r missing2, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=10, fig.height=15}
+dfs <- df %>% select(author, publication_place, country, publication_year, publication_year_from, publication_year_till, corporate, area, pagecount, gatherings, width, height, paper, publisher, self_published)
+success <- as.data.frame(t(apply(dfs, 2, function (x) {sum(!is.na(gsub("^NA$", NA, as.character(x))))})))
+original.nonNA <- as.data.frame(t(apply(select(df.orig, publication_place, publication_time, corporate, physical_extent, physical_dimension, publisher, author_name), 2, function (x) {sum(!is.na(gsub("^NA$", NA, as.character(x))))})))
+
+# Compare the number of non-NA entries in preprocessed data to number
+# of non-NA entries in the original data:
+real.success <- c()
+real.success[["publication_place"]] <- success$publication_place/original.nonNA$publication_place
+real.success[["country"]] <- success$country/original.nonNA$publication_place
+real.success[["publication_year"]] <- success$publication_year/original.nonNA$publication_time
+real.success[["publication_year_from"]] <- success$publication_year_from/original.nonNA$publication_time
+real.success[["publication_year_till"]] <- success$publication_year_till/original.nonNA$publication_time
+real.success[["corporate"]] <- success$corporate/original.nonNA$corporate
+real.success[["publisher"]] <- success$publisher/original.nonNA$publisher
+real.success[["self_published"]] <- success$self_published/original.nonNA$publisher
+real.success[["pagecount"]] <- success$pagecount/original.nonNA$physical_extent
+real.success[["area"]] <- success$area/original.nonNA$physical_dimension
+real.success[["gatherings"]] <- success$gatherings/original.nonNA$physical_dimension
+real.success[["author"]] <- success$author/original.nonNA$author
+real.success[["paper"]] <- success$paper/sum(rowMeans(!is.na(df.orig[, c("physical_extent", "physical_dimension")])) == 1)
+par(mar = c(3, 8, 2, 1)); barplot(100*sort(real.success), horiz = T, main = "Real success rate (selected fields)", las = 1, xlim = c(0, 100), xlab = "Success rate (%)")
 ```

### 2016-07-18 inst/examples/20160715-Krakow-Fennica.Rmd
Rmd update

--- 2016-07-14 inst/examples/20160715-slides-Krakow.Rmd
@@
 df.combined.preprocessed <- readRDS("df.combined.Rds")
-# Data with duplicates removed
-df.full <- df.combined.preprocessed %>% filter(!remove)
-# Data with years limited as well
-df0 <- df.full %>% filter(publication_year >= min.year & publication_year <= max.year)
+# Data with duplicates removed and years limited
+df0 <- df.combined.preprocessed %>% filter(!remove) %>%
+	   			    filter(publication_year >= min.year &
+					   publication_year <= max.year)
 ```
@@
 ```{r publishingovertime, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=4, out.width="300px"}
+
 library(magrittr)
@@
 
+# Add indicator of the publication period
 df <- df0 %>% filter(catalog == "Kungliga")
-# Add indicator of the publication period
 df$period <- cut(df$publication_year,
@@
 # Remove entries outside the investigated publication periods
-df <- df %>% filter(!is.na(period)) %>%
-	     group_by(period) %>%
-	     summarise(n = n(),
-		  paper = sum(paper.consumption.km2, na.rm = TRUE)) %>%
-        mutate(paper.per.title = paper/n)
-
-p2 <- ggplot(df,
-       aes(x = period, y = paper.per.title)) + 
+df <- df %>% filter(!is.na(period)) %>% group_by(period, paper)
+df <- df %>% summarise(n = n(),
+		  paper2 = sum(paper, na.rm = TRUE)) %>%
+             mutate(paper.per.title = paper2/n)		 
+df$paper <- df$paper2
+df$paper2 <- NULL
+
+p2 <- ggplot(df, aes(x = period, y = paper.per.title)) + 
        geom_bar(stat = "identity") +
@@
              summarise(n = n(),
-                paper = sum(paper.consumption.km2, na.rm = TRUE),
+                paper = sum(paper, na.rm = TRUE),
 		       publishers = length(na.omit(unique(publisher)))
@@
 ```{r publishers2-finland, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=7, fig.width=15}
-df <- df0
-df <- df %>%
+df <- df0 %>%
         filter(catalog == "Fennica") %>%
@@
 place <- "Turku"
-catalogue = "Fennica"
-df = df0
-
-df <- df %>% filter(catalog == catalogue & publication_place == place)
+catalogue <- "Fennica"
+
+df <- df0 %>% filter(catalog == catalogue & publication_place == place)
 
@@
 for (catal in unique(df0$catalog)) {
-  df2 <- subset(df0, catalog == catal) %>% group_by(publication_decade, gatherings) %>% summarize(paper.consumption.km2 = sum(paper.consumption.km2, na.rm = TRUE), n = n()) 
+  df2 <- df0 %>% filter(catalog == catal) %>% 
+                 group_by(publication_decade, gatherings) %>% 
+		 summarise(paper2 = sum(paper, na.rm = TRUE), n = n()) 
+  df2$paper <- df2$paper2; df2$paper2 <- NULL # Rename
   df2 <- filter(df2, gatherings %in% setdiff(names(which(table(df2$gatherings) >= 15)), "NA"))

### 2016-07-18 inst/examples/manuscript-krakow.Rmd
Rmd update

@@
 catalogue <- "Fennica"
-df = df0
-
+df <- df0
 df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)
@@
     dflsub <- filter(df, df[[lan]])
+    if (nrow(dflsub)>0) {
       dflsub$language <- gsub("language.", "", lan)
       dfl <- bind_rows(dfl, dflsub)
+    }
   }
@@
   dflsub <- filter(df, df[[lan]])
+  if (nrow(dflsub) > 0) {
     dflsub$language <- gsub("language.", "", lan)
     dfl <- bind_rows(dfl, dflsub)
+  }
 }

### 2016-07-18 R/mark_duplicates.R

@@ -1,60 +1,67 @@
 #' @title Mark Duplicates
 #' @description Tag entries to be removed.
-#' @param df.preprocessed Data frame of combined catalogs
+#' @param df Data frame of combined catalogs
 #' @param field_names List of field names of exactly matching values
 #' @return Data frame
 #' @export
 #' @author Hege Roivainen \email{hege.roivainen@@gmail.com}
 #' @references See citation("bibliographica")
 #' @keywords utilities
-mark_duplicates <- function (df.preprocessed, field_names=c("short_title", "publication_place", "publication_year")) {
+mark_duplicates <- function (df,
+  field_names = c("short_title", "publication_place", "publication_year")) {
     
-  l <- (nrow(df.preprocessed))
+  l <- (nrow(df))
   
   # Create short titles
   first_word_count <- 5
   pattern = paste0("^([^ ]* ){", first_word_count, "}")
-  df.preprocessed$short_title <- str_extract(df.preprocessed$title, pattern=pattern)
-  inds <- which(is.na(df.preprocessed$short_title))
-  df.preprocessed$short_title[inds] <- df.preprocessed$title[inds]
-  df.preprocessed$short_title <- tolower(df.preprocessed$short_title)
-  df.preprocessed$short_title <- gsub("[[:punct:]]", "", df.preprocessed$short_title)
+  df$short_title <- str_extract(df$title,
+					pattern=pattern)
+  inds <- which(is.na(df$short_title))
+  df$short_title[inds] <- df$title[inds]
+  df$short_title <- tolower(df$short_title)
+  df$short_title <- gsub("[[:punct:]]", "",
+  			      	   df$short_title)
   
   # Get matching fields (short title, town, from)
-  dups_all <- which(duplicated(df.preprocessed[field_names],) | duplicated(df.preprocessed[field_names], fromLast = TRUE))
+  dups_all <- which(duplicated(df[field_names],) |
+                    duplicated(df[field_names],
+		    fromLast = TRUE))
   
   # Get first instance of duplicate rows
-  dup_f <- which(duplicated(df.preprocessed[field_names], fromLast=TRUE) & !duplicated(df.preprocessed[field_names]))
-  df.preprocessed$first_duplicated <- FALSE
-  df.preprocessed$first_duplicated[dup_f] <- TRUE
[…]

### 2016-07-18 inst/examples/20160715-slides-Krakow.R

@@ -1,8 +1,10 @@
 ## ----201606krakow-init, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, cache=TRUE----
-# Default time span for the slides
+# Default time span
 min.year <- 1488
 max.year <- 1828
 
+library(ggmap)
+library(gisfin)
 library(stringr)
 library(dplyr)
 library(tidyr)
@@ -14,7 +16,6 @@ library(sorvi)
 library(devtools)
 # install_github("ropengov/gisfin")
 # devtools::install_github('cttobin/ggthemr')
-library(gisfin)
 #library(ggthemr)
 
 knitr::opts_chunk$set(echo = FALSE)
@@ -38,72 +39,119 @@ theme_set(theme_bw(26))
 ## ----201606krakow-init2, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, cache=TRUE----
 # Full combined catalogue (Fen + Kun) with marked duplicates
 df.combined.preprocessed <- readRDS("df.combined.Rds")
-# Data with duplicates removed
-df.full <- df.combined.preprocessed %>% filter(!remove)
-# Data with years limited as well
-df0 <- df.full %>% filter(publication_year >= min.year & publication_year <= max.year)
+# Data with duplicates removed and years limited
+df0 <- df.combined.preprocessed %>% filter(!remove) %>%
+	   			    filter(publication_year >= min.year &
+					   publication_year <= max.year)
 
-## ----map1, echo=FALSE, message=FALSE, warning=FALSE, fig.width=20, fig.height=5----
+## ---- message=FALSE, warning=FALSE, fig.width=10, fig.height=3, echo=FALSE----
+library(dplyr)
+library(ggplot2)
+theme_set(theme_bw(20))
+df <- df0 %>% filter(publication_year >=1640 & publication_year <=1828) %>% group_by(catalog, publication_decade) %>% tally()
+p <- ggplot(df, aes(x = publication_decade, y = n, color = catalog)) + 
+       geom_point() + 
+       geom_line() + 
+       ylab("Documents (n)") + xlab("Publication year") +
+       scale_color_manual(values = c("blue", "darkgreen")) + 
+       guides(color = guide_legend(reverse = TRUE, title = "")) #+ 
+print(p)
+
+## ---- message=FALSE, warning=FALSE, echo=FALSE---------------------------
+library(bibliographica, quiet = TRUE)
+
[…]

### 2016-07-18 inst/examples/main.R

@@ -1,8 +1,9 @@
-#library(bibliographica)
+library(bibliographica)
+library(fennica)
 
-library(devtools)
-load_all("~/proj/2014-Aatelouhinta/bibliographica")
-load_all("~/proj/2014-Aatelouhinta/fennica")
+#library(devtools)
+#load_all("~/proj/2014-Aatelouhinta/bibliographica")
+#load_all("~/proj/2014-Aatelouhinta/fennica")
 
 # I/O definitions
 output.folder <- "output.tables/"

### 2016-07-18 inst/examples/20160715-Krakow-Fennica.Rmd
ok

@@
 #knitr::opts_chunk$set(fig.path = "slides_201606_Krakow/", dev="CairoPNG")
-knitr::opts_chunk$set(fig.path = "slides_201606_Krakow/")
+knitr::opts_chunk$set(fig.path = "figure-20160715-Krakow-Fennica/")
 
@@
 # Full combined catalogue (Fen + Kun) with marked duplicates
-df.combined.preprocessed <- readRDS("df.combined.Rds")
+df.combined.preprocessed <- readRDS("df.combined.20160715-Krakow.Rds")
 # Data with duplicates removed and years limited
@@
 # Remove entries outside the investigated publication periods
-df <- df %>% filter(!is.na(period)) %>% group_by(period, paper)
+df <- df %>% filter(!is.na(period)) %>% group_by(period, paper.consumption.km2)
 df <- df %>% summarise(n = n(),
-		  paper2 = sum(paper, na.rm = TRUE)) %>%
+		  paper2 = sum(paper.consumption.km2, na.rm = TRUE)) %>%
              mutate(paper.per.title = paper2/n)		 
-df$paper <- df$paper2
+df$paper.consumption.km2 <- df$paper2
 df$paper2 <- NULL
@@
              summarise(n = n(),
-                paper = sum(paper, na.rm = TRUE),
+                paper = sum(paper.consumption.km2, na.rm = TRUE),
 		       publishers = length(na.omit(unique(publisher)))
@@
   filter(publication_year >= 1640 & publication_year <= 1828)%>%
-        select(publication_decade, publisher, paper)
+        select(publication_decade, publisher, paper.consumption.km2)
 
@@
              summarise(n = n(),
-	               paper = sum(paper, na.rm = TRUE))
+	               paper = sum(paper.consumption.km2, na.rm = TRUE))
 
@@
              summarise(n = n(),
-                 paper = sum(paper, na.rm = TRUE))
+                 paper = sum(paper.consumption.km2, na.rm = TRUE))
 
@@
                  group_by(publication_decade, gatherings) %>% 
-		 summarise(paper2 = sum(paper, na.rm = TRUE), n = n()) 
+		 summarise(paper2 = sum(paper.consumption.km2, na.rm = TRUE), n = n()) 
   df2$paper <- df2$paper2; df2$paper2 <- NULL # Rename

### 2016-07-18 inst/examples/slidetemplates.Rmd
ok

--- 2016-07-18 inst/examples/20160715-Krakow-Fennica.Rmd
@@
 knitr::opts_chunk$set(echo = FALSE)
-#knitr::opts_chunk$set(fig.path = "slides_201606_Krakow/", dev="CairoPNG")
-knitr::opts_chunk$set(fig.path = "slides_201606_Krakow/")
+#knitr::opts_chunk$set(fig.path = "figure_slides/", dev="CairoPNG")
+knitr::opts_chunk$set(fig.path = "figure_slides/")
 
@@
 
-## Preprocess & Enrich
+## Automated data clean-up
 
@@
 
-```{r, message=FALSE, warning=FALSE}
+```{r, message=FALSE, warning=FALSE, echo=TRUE}
 get_country("Porvoo")
@@
 		 summarise(paper2 = sum(paper, na.rm = TRUE), n = n()) 
-  df2$paper <- df2$paper2; df2$paper2 <- NULL # Rename
   df2 <- filter(df2, gatherings %in% setdiff(names(which(table(df2$gatherings) >= 15)), "NA"))
@@
 
-  p <- ggplot(df2, aes(y = paper,
+  p <- ggplot(df2, aes(y = paper2,
                        x = publication_decade,

### 2016-07-19 inst/examples/slidetemplates.Rmd
ok

@@
 
-```{r 201606krakow-init, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, cache=TRUE}
+```{r 201606krakow-init, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE}
 # Default time span
@@
 
-```{r 201606krakow-init2, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, cache=TRUE}
+```{r 201606krakow-init2, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE}
 # Full combined catalogue (Fen + Kun) with marked duplicates
@@
 
-## Automated data clean-up
+## Automated algorithms for data clean-up
 
@@
 
-- Parse, clean up, enrich, summarise, analyze, visualize, report..
+- Open source tools: parse, clean up, interpret, augment, enrich,
+  validate, summarise, analyze, visualize, report..
 

### 2016-07-27 inst/examples/manuscript-krakow.Rmd
Rmd update

@@
     variant: markdown_github
+  pdf_document:
+    citation_package: natbib
+    keep_tex: true
 ---

### 2016-07-27 inst/examples/slidetemplates.Rmd
Rmd update

@@
 ---
-title: "Printing in a Periphery: a Quantitative Study of Finnish Knowledge Production, 1640-1828"
+title: "A Quantitative Study of Finnish Knowledge Production `r params$min.year`-`r params$max.year`"
+subtitle: "Subtitle here"
 author: "Mikko Tolonen, Jani Marjanen, Hege Roivainen, Leo Lahti"
 date: "`r Sys.Date()`"
+fontsize: 13pt
+geometry: margin=1in
+linkcolor: magenta
+urlcolor: blue
+citecolor: black
+institute: "University of Helsinki"
 output: 
@@
     fonttheme: "professionalfonts"
-fontsize: 13pt
+  pdf_document:
+    fig_width: 7
+    fig_height: 6
+    fig_caption: true
+    includes:
+      in_header: header.tex
+params:
+  min.year: 
+    label: "Start year:"
+    input: numeric
+    value: 1488
+  max.year: 
+    label: "End year:"
+    input: numeric
+    value: 1828
+  journals:
+    label: "Include journals:"
+    value: TRUE
+    input: checkbox
+  catalogue:
+    label: "Library catalog:"
+    value: all
+    input: select
+    multiple: TRUE
+    choices: [fennica, kungliga, all]
+  language:
+    label: "Language:"
+    value: all
+    input: radio
+    choices: [finnish, swedish, all]
+  data: 
+    label: "Input dataset:"
+    value: df.combined.Rds
+    input: file
+  slideparameter: 
+    label: "Sliding value:"
+    value: 100
+    input: slider
+    min: 0
+    max: 1000
+  date: 
+    label: "Date:"
+    value: !r date()
+    input: date
+  text: 
+    label: "Text:"
+    value: Some test text
+    input: text
 ---
@@
 ```{r 201606krakow-init, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE}
-# Default time span
-min.year <- 1488
-max.year <- 1828
+
+# For all parameter options for rmarkdown slide rendering, see:
+# http://rmarkdown.rstudio.com/developer_parameterized_reports.html
+# More header options in Pandoc manual
+# http://pandoc.org/MANUAL.html#templates
+
+# Read parameters from the header
+mydate <- params$start
+min.year <- params$min.year
+max.year <- params$max.year
 
@@
 # Full combined catalogue (Fen + Kun) with marked duplicates
-df.combined.preprocessed <- readRDS("df.combined.Rds")
+#df.combined.preprocessed <- readRDS("df.combined.Rds")
+df.combined.preprocessed <- readRDS(params$data)
 # Data with duplicates removed and years limited
@@
 					   publication_year <= max.year)
+
+if (!params$catalogue == "all") {
+  df0 <- filter(df0, catalog == params$catalogue)
+}
 ```
@@
 
-**Idea**: Study early modern knowledge production, all of it (1470-1830)
-
+**Idea**: Study early modern knowledge production, all of it (`r min.year`-`r max.year`)  
 **How?** Combine library catalogues (Fennica, Kungliga, ESTC, CERL HPB database)

### 2016-07-27 inst/examples/analysis.R

@@ -21,7 +21,9 @@ knitr::knit("20160303-Krakow.Rmd", encoding="UTF-8")
 #rmarkdown::render("20160715-Krakow-Fennica.Rmd") # Krakow 7/2016 slides frozen.
 
 library(rmarkdown)
-rmarkdown::render("slidetemplates.Rmd") # Slide draft
+rmarkdown::render("slidetemplates.Rmd", params = list(min.year = 1470, max.year = 1828, data = "df.combined.Rds"))
+rmarkdown::render("slidetemplates.Rmd", params = "ask")
+
 # rmarkdown::render("slides.Rmd") # Another Slide draft, to bw combined
 rmarkdown::render("manuscript-krakow.Rmd") # Manuscript draft
 #rmarkdown::render("test.Rmd") # For interactive testing

### 2016-07-27 inst/examples/enrich.fennica.R

@@ -71,7 +71,7 @@ inds <- which(!is.na(gendercustom))
 df.preprocessed$author_gender[inds] <- gendercustom[inds]
 
 message("-- Fennica publishers")
-stop("here")
+
 df.preprocessed$publisher <- polish_publisher_fennica(df.preprocessed)
   
 # ----------------------------------------------------------------

### 2016-07-27 inst/examples/details.Rmd
ok

---
title: "Details"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
---

```{r setup, include=FALSE}
library(flexdashboard)
```

Column {data-width=650}
-----------------------------------------------------------------------

### Chart A

```{r}

```

Column {data-width=350}
-----------------------------------------------------------------------

### Chart B

```{r}

```

### Chart C

```{r}

```

### 2016-07-27 inst/examples/flexdashboard.Rmd
ok

--- 2016-07-18 inst/examples/slidetemplates.Rmd
@@
 ---
-title: "Printing in a Periphery: a Quantitative Study of Finnish Knowledge Production, 1640-1828"
-author: "Mikko Tolonen, Jani Marjanen, Hege Roivainen, Leo Lahti"
-date: "`r Sys.Date()`"
+title: "Untitled"
 output: 
-  beamer_presentation:
-    theme: "boxes"
-    colortheme: "orchid"
-    fonttheme: "professionalfonts"
-fontsize: 13pt
+  flexdashboard::flex_dashboard:
+    logo: ropengov.png
+    favicon: HY-CC.png
+    theme: default
+    orientation: columns
+    vertical_layout: fill
+    navbar:
+      - { title: "About", href: "https://example.com/about", align: left }
+    social: [ "menu" ]
+    source_code: http://github.com/antagomir
+runtime: shiny
 ---
 
-```{r 201606krakow-init, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, cache=TRUE}
-# Default time span
-min.year <- 1488
-max.year <- 1828
+```{r setup, include=FALSE}
+library(flexdashboard)
+```
 
+```{r init, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE}
 library(ggmap)
@@
 #library(ggthemr)
-
 knitr::opts_chunk$set(echo = FALSE)
 #knitr::opts_chunk$set(fig.path = "figure_slides/", dev="CairoPNG")
-knitr::opts_chunk$set(fig.path = "figure_slides/")
+knitr::opts_chunk$set(fig.path = "figure_flex/")
 
@@
 
-# Nice default themes
-# https://github.com/cttobin/ggthemr#palettes
-#ggthemr('fresh', text_size = 20)
-# ggthemr('greyscale', text_size = 20)
-#ggthemr('light', text_size = 20)
-# ggthemr('pale', text_size = 20)
-#ggthemr_reset() # Reset theme
-```
+# Params
+min.year <- 1470
+max.year <- 1828
 
-```{r 201606krakow-init2, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, cache=TRUE}
 # Full combined catalogue (Fen + Kun) with marked duplicates
@@
 
----
+Page 1
+==============================================================================
 
-## From particular data to global perspective?
+Column {data-width=650}
+-----------------------------------------------------------------------
 
-**Idea**: Study early modern knowledge production, all of it (1470-1830)
+Flexdashboard instructions:
+  * [Usage](http://rmarkdown.rstudio.com/flexdashboard/using.html)
+  * [htmlwidget gallery](http://gallery.htmlwidgets.org/)
+  * [flexdashboard examples](http://rmarkdown.rstudio.com/flexdashboard/examples.html)
+  * [plotly](https://plot.ly/r/)
 
-**How?** Combine library catalogues (Fennica, Kungliga, ESTC, CERL HPB database)
+### Linked Value Box
 
-**Important**: cleaning up the data (90% of the effort!) and considering how particular data collections (Finnish National Bibliography, English Short-Title Catalogue etc.) have been formed.
-
-**How to fail**: take worldcat or similar combination of datasets and analyse it as a whole without cleaning it up first.
-
-**Overcoming a national gaze** by focus on knowledge production through more complex cross-national network of cities
-
----
-
-### Data: bibliographic catalogues 1640-1828
-
-**Fennica** Finnish National bibliography
-
-- `r nrow(subset(df0, catalog == "Fennica" & publication_year >= 1640 & publication_year < 1828))` documents 1640-1828
-
-**Kungliga**  Swedish National bibliography
-
-- `r nrow(subset(df0, catalog == "Kungliga" & publication_year >= 1640 & publication_year < 1828))` documents 1640-1828
-
-**Why this project?**
-
-- Visible roots of the diversity of "Finnishness" reflected in knowledge production, 1640-1828
-
-```{r, message=FALSE, warning=FALSE, fig.width=10, fig.height=3, echo=FALSE}
-library(dplyr)
-library(ggplot2)
-theme_set(theme_bw(20))
-df <- df0 %>% filter(publication_year >=1640 & publication_year <=1828) %>% group_by(catalog, publication_decade) %>% tally()
-p <- ggplot(df, aes(x = publication_decade, y = n, color = catalog)) + 
-       geom_point() + 
-       geom_line() + 
-       ylab("Documents (n)") + xlab("Publication year") +
-       scale_color_manual(values = c("blue", "darkgreen")) + 
-       guides(color = guide_legend(reverse = TRUE, title = "")) #+ 
-print(p)
+```{r}
+valueBox(42, icon = "fa-pencil", href="#page-2")
 ```
 
----
+### Table
 
-## Methods: Open data analytical ecosystem
+```{r}
+library(shiny)
+#renderTable({head(mtcars)})
+#renderTable({head(mtcars, n = input$rows)})
 
-**Customized** our dedicated R packages for bibliographic analysis combine flexibility with automation
-
-**Automated** scales well with new data and unforeseen changes; a million documents cleaned up in 30 minutes
-
-**Open source** fully transparent and reproducible data analytics: https://github.com/rOpenGov/fennica
-
-**Research potential** greatly underestimated; world is full of metadata collections
-
-![Data Science Workflow](data-science.png)  
-\tiny{(Figure by Hadley Wickham)}
-
----
-
-## Automated data clean-up
-
-```{r, message=FALSE, warning=FALSE, echo=FALSE}
-library(bibliographica, quiet = TRUE)
+library(DT)
+DT::datatable(mtcars, options = list(bPaginate = FALSE))
+#DT::datatable(mtcars, options = list(pageLength = 25))
 ```
 
-**Clean up messy entries**
+<!--Column {data-width=350}-->
+Column {.tabset .tabset-fade}
+-----------------------------------------------------------------------
 
-```{r, message=FALSE, warning=FALSE,echo=TRUE}
-polish_physical_extent("iii-xxiv, 118, [2] p.")$pagecount
-```
+### Chart B
 
-**Enrich data** (geocoordinates, gender, ..)
-
-```{r, message=FALSE, warning=FALSE, echo=TRUE}
-get_country("Porvoo")
-```
-
-- Parse, clean up, enrich, summarise, analyze, visualize, report..
-
----
-
-\begin{center}
-\Large{1. General trends and political events}
-\end{center}
-
----
-
-\begin{center}
-\tiny{\textcolor{gray}{General trends \& political events}}
-\end{center}
-
-### Turku as a Swedish University Town among Uppsala, Tartu and Stockholm (+ Lund & Greifswald)
-
-```{r map1, echo=FALSE, message=FALSE, warning=FALSE, fig.width=20, fig.height=4, eval=TRUE}
+```{r map1, echo=FALSE, message=FALSE, warning=FALSE}
 library(dplyr)
@@
 
----
+### Chart C
 
-\begin{center}
-\tiny{\textcolor{gray}{General trends \& political events}}
-\end{center}
-
-### Publishing activity over time
-
-- 1700-1721 Great Northern War & Fennica drop during "the Great Wrath"
-- 1760-1770 Pamphleteering plays a crucial role during abolished censorship
-- 1803-1815 Napoleonic wars
-
-```{r publishingovertime, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=4, out.width="300px"}
-
-library(magrittr)
-library(ggplot2)
-library(dplyr)
-df2 <- df0 %>% group_by(publication_decade, catalog) %>%
-               summarise(n = n())
-df2$highlight <- rep(FALSE, nrow(df2))
-df2$highlight[df2$catalog == "Kungliga" &
-	      df2$publication_decade %in% c(1770, 1810)] <- TRUE
-df2$highlight[df2$catalog == "Fennica" &
-	      df2$publication_decade %in% c(1710, 1810)] <- TRUE
-v <- seq(1500, 1800, 100)
-theme_set(theme_bw(20))
-p1 <- ggplot(df2, aes(x = publication_decade, y = n)) +
-     geom_line(aes(color = catalog), size = 1) +
-     geom_point(aes(shape = catalog, color = catalog, size = highlight)) +
-     ylab("Title count (n)") + xlab("Publication year") +
-     #theme(legend.position = "none") +
-     scale_x_continuous(breaks = v, labels = v) +
-     scale_color_manual(values = c("blue", "darkgreen")) + 
-  	 scale_size_discrete(range = c(2, 8)) +
-     guides(color = guide_legend(reverse = TRUE), size = "none", shape = "none")
-
-# Add indicator of the publication period
-df <- df0 %>% filter(catalog == "Kungliga")
-df$period <- cut(df$publication_year,
-           breaks = c(1757, 1766, 1775, 1783),
-		 include.lowest = TRUE,
-		 right = FALSE
-		 )
-
-# Remove entries outside the investigated publication periods
-df <- df %>% filter(!is.na(period)) %>% group_by(period, paper)
-df <- df %>% summarise(n = n(),
-		  paper2 = sum(paper, na.rm = TRUE)) %>%
-             mutate(paper.per.title = paper2/n)		 
-df$paper <- df$paper2
-df$paper2 <- NULL
-
-p2 <- ggplot(df, aes(x = period, y = paper.per.title)) + 
-       geom_bar(stat = "identity") +
-       scale_x_discrete(labels = c("1757-1765", "1766-1774", "1775-1783")) +
-       ylab("Paper per title") + xlab("")
-
-library(gridExtra)
-grid.arrange(p1, p2, nrow = 1)
+```{r}
+library(dygraphs)
+dygraph(ldeaths)
 ```
 
----
+Page 2
+=====================================================================
 
-\begin{center}
-\tiny{\textcolor{gray}{General trends \& political events}}
-\end{center}
+Column {data-width=650}
+-----------------------------------------------------------------------
 
-### Swedish knowledge production & cycles of representation
+### Chart A
 
-An example how historical events, namely **parliamentary assemblies** in the Swedish case, have an effect on knowledge production.
-
-```{r riksdar5, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
-
-minyear <- 1700
-  maxyear <- 1800
-  catalog <- "Kungliga"
-
-library(magrittr)
-library(ggplot2)
-library(dplyr)
-library(ggplot2)
-library(reshape2)
-
-#for (catal in as.character(unique(df0$catalog))) {
-
-for (catal in "Kungliga") {
-
-  # Use timeinterval year intervals
-  dfsel = subset(df0, catalog == catal)
-
-  df <- df0
-  df = subset(df, catalog == catal)
-  df <- subset(df, publication_year >= minyear & publication_year <= maxyear)
-
-  df <- subset(dfsel, publication_year >= 1700 & publication_year < 1800 )
-
-  timeinterval <- 1
-  df$timeunit <- round(df$publication_year/timeinterval)*timeinterval
-
-  df$unity = rep(1, nrow(df))
-  publications <- tapply(df$unity, list(df$timeunit), sum)
-
-  publications[is.na(publications)] <- 0 # Set NAs to 0
-  publications <- publications/timeinterval # Instead of decadal sum, use average annual output 
-  dfm <- melt(publications) 
-  names(dfm) <- c("Time", "Documents")
-  dfm <- transform(dfm, date = as.numeric(as.character(Time)))
-  ymin = min(dfm$Documents)
-  ymax = max(dfm$Documents)
-
-  rect_left <- c(min(na.omit(dfm$date)),
-               1719-.5, 1719+.5, # Stockholm 20 januari 1719 1 juni 1719
-               1734-.5, 1734+.5, # Stockholm 14 maj 1734 14 december 1734
-               1765-.5, 1766+.5, # Stockholm 21 februari 1765 21 oktober 1766
-               1769-.5, 1770+.5, # Norrköping & Stockholm 22 april 1769 5 februari 1770
-               1771-.5, 1772+.5, # Stockholm 19 juni 1771 12 september 1772
-               1792-.5, 1792+.5, # Gävle 26 januari 1792 24 februari 1792         
-               max(na.omit(dfm$date)))
-  rectangles <- data.frame(
-    xmin = rect_left[-length(rect_left)],
-    xmax = rect_left[-1],
-    ymin = ymin,
-    ymax = ymax
-    )
-  rectangles$shade <- rep(c("Background", "Highlight"), length = nrow(rectangles))
-
- riksplace = c("Stockholm", "Stockholm", "Stockholm", "Norrköping", "Stockholm", "Gävle")
- cols = c("white", "Purple", "yellow", "orange")
- rectangles$shade[rectangles$shade == "Highlight"] = riksplace
- rectangles$shade = factor(rectangles$shade)
-
-  # Draw Figure
-  theme_set(theme_bw(20))
-  p <- ggplot()
-  p <- p + geom_rect(data = rectangles, 
-       aes(xmin=xmin, xmax=xmax, ymin=ymin, ymax=ymax, fill=shade), alpha=0.8) + 
-         scale_fill_manual(values = cols) # + guides(fill = "none") 
-  p <- p + geom_line(data = dfm, aes(x = date, y = Documents), col = "black")
-  p <- p + geom_point(data = dfm, aes(x = date, y = Documents), col = "black")
-  p <- p + scale_x_continuous(breaks=seq(min(dfm$date), max(dfm$date), 20))
-  p <- p + ggtitle("Publishing activity")
-  p <- p + ylab("Documents / Year")
-  p <- p + xlab("Year")
-  p <- p + ggtitle(paste(catal,"Riksplaces"))
-  print(p)
-}
+```{r}
 
@@
 
----
+Column {data-width=350}
+-----------------------------------------------------------------------
 
-\begin{center}
-\Large{2. Publishers in Sweden and Turku}
-\end{center}
+### Chart B
 
----
+```{r}
 
-\begin{center}
-\tiny{\textcolor{gray}{Publishers in Sweden and Turku}}
-\end{center}
-
-### Turku in Sweden: proportions for title count and paper in Swedish University towns
-
-```{r comparisons, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=18, fig.height=10}
-pics <- list()
-for (catalogue in na.omit(unique(df0$catalog))) {
-
-df <- df0 %>% filter(catalog == catalogue)%>%
-        filter(publication_year >= 1640 & publication_year <= 1828)
-places <- c("Stockholm", "Uppsala", "Lund", "Greifswald", "Tartu", "Turku")
-df$publication_place[!df$publication_place %in% places] <- "Other"
-df <- subset(df, !is.na(df$publication_place))
-#df$publication_place <- factor(df$publication_place, levels = c(places, "Other"))
-library(reshape2)
-library(magrittr)
-library(dplyr)
-library(tidyr)
-
-df <- df %>% group_by(publication_decade, publication_place) %>%
-             summarise(n = n(),
-                paper = sum(paper, na.rm = TRUE),
-		       publishers = length(na.omit(unique(publisher)))
-		       )
-
-# Calculate percentages
-for (varname in c("n", "paper", "publishers")) {
-
-  df$varname <- df[[varname]]
-  dff <- df %>% select(publication_decade, publication_place, varname)
-  dff <- spread(dff, publication_place, varname, fill = 0)
-  dff[, -1] <- 100 * t(apply(dff[, -1], 1, function (x) {x/sum(x)}))
-  dff <- melt(dff, "publication_decade");
-  colnames(dff) <- c("publication_decade", "publication_place", "f")
-
-  theme_set(theme_bw(20))
-  p <- ggplot(dff, aes(x = publication_decade, y = f)) +
-     geom_bar(position = "stack", stat = "identity",
-       aes(fill = publication_place)) + 
-     xlab("Publication year") +
-     scale_fill_brewer(palette="Spectral")
-     if (varname == "n") {
-       p <- p + ggtitle(paste("Title count (", catalogue, ")", sep = "")) + 
-                ylab("Title count frequency (%)") 
-     }
-     if (varname == "paper") {
-       p <- p + ggtitle(paste("Paper (", catalogue, ")", sep = "")) +
-                ylab("Paper (%)")        
-     }
-     if (varname == "publishers") {
-       p <- p + ggtitle(paste("Publishers (", catalogue, ")", sep = "")) +
-                       ylab("Publishers (%)")
-     }     
-  p <- p + guides(fill = guide_legend(reverse = TRUE, title = ""))
-
-  pics[[paste(catalogue, varname, sep = "-")]] <- p
-
-}
-}
-library(gridExtra)
-grid.arrange(pics[[1]], pics[[2]], pics[[4]], pics[[5]], nrow = 2)
-rm(pics)
 ```
 
----
+### Chart C
 
-\begin{center}
-\tiny{\textcolor{gray}{Publishers in Sweden and Turku}}
-\end{center}
+```{r}
 
-### Publishers in Swedish University towns (and Finland)
-
-```{r publishers2-finland, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=7, fig.width=15}
-df <- df0 %>%
-        filter(catalog == "Fennica") %>%
-	filter(country == "Finland" | publication_place == "Vyborg") %>%
-        filter(publication_year >= 1640 & publication_year <= 1828)
-
-# Top publication places
-library(bibliographica)
-
-top <- c("Turku", "Vaasa", "Vyborg")
-df <- df %>%	
-        filter(publication_place %in% top) %>%	
-        select(publication_decade, publication_place, publisher)
-
-npub <- unique(df) %>% group_by(publication_decade, publication_place) %>% tally()
-npub$publication_place <- factor(npub$publication_place, levels = top)
-npub.fennica <- npub
-
-df <- df0
-catalogue <- "Kungliga"
-df <- df %>%
-        filter(catalog == catalogue) %>%
-        filter(publication_year >= 1640 & publication_year <= 1828)
-
-# Selected publication places
-top <- c("Stockholm", "Lund", "Uppsala", "Greifswald", "Tartu")
-df <- df %>%	
-        filter(publication_place %in% top) %>%	
-        select(publication_decade, publication_place, publisher)
-
-npub <- unique(df) %>% group_by(publication_decade, publication_place) %>% tally()
-npub$publication_place <- factor(npub$publication_place, levels = top)
-npub.kungliga <- npub
-
-npub <- bind_rows(npub.fennica, npub.kungliga)
-
-# Order by total publishing activity
-npub$publication_place <- factor(npub$publication_place, levels = (npub %>% group_by(publication_place) %>% summarise(total = sum(n)) %>% arrange(desc(total)))$publication_place)
-npub <- npub %>% arrange(publication_place)
-
-theme_set(theme_bw(20))
-p <- ggplot(npub, aes(x = publication_decade, y = n)) +
-       geom_bar(stat = "identity", position = "stack",
-       		    aes(fill = publication_place)) + 
-       xlab("Publication year") +
-       ylab("Unique publishers (n)") +
-      scale_fill_brewer(palette="Spectral") +       
-       guides(fill = guide_legend(reverse = TRUE, title = "")) #+ 
-       #ggtitle(paste("Unique publishers in selected publication places (", catalogue, ")"))
-
-print(p)
 ```
-
----
-
-\begin{center}
-\tiny{\textcolor{gray}{Publishers in Sweden and Turku}}
-\end{center}
-
-### Top publishers in Turku/Fennica
-
-```{r publishers4-fennica, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=6, fig.width=12}
-library(dplyr)
-place <- "Turku"
-catalogue <- "Fennica"
-
-df <- df0 %>% filter(catalog == catalogue & publication_place == place)
-
-df <- df %>%	
-  filter(publication_year >= 1640 & publication_year <= 1828)%>%
-        select(publication_decade, publisher, paper)
-
-# Group small publishers
-# Top publishers by title count
-ntop <- 10
-top <- names(top(df, "publisher", ntop))
-df$publisher[!df$publisher %in% top] <- "Other"
-df$publisher <- factor(df$publisher, c(top, "Other"))
-
-# Title count per decade & publisher	
-npub <- df %>% group_by(publication_decade, publisher) %>% tally() %>% arrange(n)
-#npub$publisher <- factor(npub$publisher, levels = (npub %>% group_by(publisher) %>% summarise(total = sum(n)) %>% arrange(total))$publisher)
-# Sort by biggest publication decade
-#ord <- (npub %>% group_by(publisher) %>% summarise(decade = publication_decade[[which.max(n)]]) %>% arrange(decade))$publisher
-ord <- as.character((npub %>% group_by(publisher) %>% 
-                        summarise(decade = median(publication_decade)) %>% 
-                        arrange(decade))$publisher)
-npub$publisher <- factor(npub$publisher, levels = c("Other", setdiff(ord, "Other")))
-
-# TITLE COUNT
-theme_set(theme_bw(20))
-p <- ggplot(npub, aes(x = publication_decade, y = publisher)) +
-      geom_point(aes(size = n)) + 
-      #geom_line(aes(color = publisher), size = 2) +
-      #geom_smooth(aes(fill = publisher)) +
-      # geom_bar(stat = "identity", position = "stack", aes(fill = publisher)) + 
-       xlab("Year") +
-       ylab("") +
-       guides(size = guide_legend(title = "Title count (n)"))
-       #ggtitle(paste("Title count per publisher (", place, "/", catalogue, ")", sep = ""))
-print(p)
-```
-
----
-
-\begin{center}
-\Large{3. Languages and religious texts in Finland}
-\end{center}
-
----
-
-\begin{center}
-\tiny{\textcolor{gray}{Languages \& religious texts in Finland}}
-\end{center}
-
-### Different languages in Turku, Stockholm, Uppsala and Lund
-
-```{r language-perc2, echo=FALSE, message=FALSE, warning=FALSE, fig.width=20, fig.height=12}
-pics <- list()
-theme_set(theme_bw(20))
-myplaces <- c("Turku", "Greifswald", "Stockholm", "Uppsala", "Lund")
-
-for (catalogue in c("Fennica", "Kungliga")) {
-
-  df <- df0 %>% filter(catalog == catalogue) %>%
-        filter(publication_year >= 1600 & publication_year <= 1828)
-
-  langs <- c("Finnish", "Swedish", "Latin", "German",
-           "Russian", "French", "Hebrew", "Other")
-
-  lang <- paste("language.", langs, sep = "")
-  otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
-  otherlang <- otherlang[otherlang!="language.Multiple languages"]
-
-  df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
-
-  dfl <- NULL
-  for (lan in lang) {
-
-    # Classify a document to the specifed language
-    # If document is assigned with languages, each case is considered
-    # so one doc may have multiple entries corresponding to different languages
-    # mean(rowSums(df[, lang]) == 1) # 93% Fennica docs have just 1 language
-    # Combine data frames for specified languages
-    dflsub <- filter(df, df[[lan]])
-    if (nrow(dflsub) > 0) {
-      dflsub$language <- gsub("language.", "", lan)
-      dfl <- bind_rows(dfl, dflsub)
-    }
-  }
-
-  df <- dfl %>% group_by(publication_decade, publication_place, language) %>%
-     	     summarise(n = n())
-
-  # Calculate percentages
-  dff <- spread(df, language, n, fill = 0)
-  dff[, -c(1,2)] <- 100 * t(apply(dff[, -c(1,2)], 1, function (x) {x/sum(x)}))
-
-  dff <- melt(dff, id = c("publication_place", "publication_decade"))
-  colnames(dff) <- c("publication_place", "publication_decade", "language", "f")
-
-  for (myplace in myplaces) {
-    p <- ggplot(subset(dff, publication_place == myplace), aes(x = publication_decade, y = f)) +
-      geom_bar(position = "stack", stat = "identity", aes(fill = language)) + 
-      xlab("Publication year") +
-      ylab("Title count frequency (%)") +
-      #ggtitle(paste("Languages (", myplace, "/", catalogue, ")", sep = "")) +
-      ggtitle(paste(myplace, "/", catalogue)) +
-      scale_fill_brewer(palette="Spectral") + 
-      guides(fill = guide_legend(reverse = TRUE, title = ""))
-    pics[[paste(catalogue, myplace, sep = "-")]] <- p
-  }
-}
-
-grid.arrange(pics[[1]],
-             pics[[8]], pics[[9]], pics[[10]], 
-             nrow = 2)
-
-rm(pics)
-```
-
----
-
-\begin{center}
-\tiny{\textcolor{gray}{Languages \& religious texts in Finland}}
-\end{center}
-
-### Topic richness per language (publications in Fennica)
-
-```{r topics232, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, fig.show="hold"}
-catalogue <- "Fennica"
-df <- filter(df0, catalog == "Fennica") %>%
-  filter(publication_year >= 1640 & publication_year <= 1828) %>%
-  select(publication_year, language, subject_topic)
-df <- unique(df)
-df <- df %>% group_by(publication_year, language) %>%
-             summarise(n = length(unique(unlist(strsplit(subject_topic, ";")))))
-
-langs2 <- c("Finnish", "Swedish", "Latin", "Other")
-df$language[!df$language %in% langs2] <- "Other"
-df$language <- factor(df$language, levels = langs2)
-
-p <- ggplot(df, aes(x = publication_year, y = n, color = language)) +
-       geom_line() + geom_point() + 
-       geom_smooth(aes(fill = language, color = language)) + 
-       ylab("Documents (n)") + xlab("Publication year")
-
-print(p)
-```
-
----
-
-\begin{center}
-\tiny{\textcolor{gray}{Languages \& religious texts in Finland}}
-\end{center}
-
-### Devotional literature (catechisms, hymns, prayers, etc.)
-
-Form of literature denoting the advancement of reading in Finland in the 19th century. It has been unclear when devotional literature  shows up as a relevant category.
-
-```{r topics12122, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, fig.show="hold"}
-sel <- c("virret","arkkiveisut","hartauskirjat","katekismukset","rukouspäivät","saarnat","aapiset","rukoukset","rukous","hengelliset laulut","hartauspuheet","virsikirjat")
-catalogue <- "Fennica"
-
-  # Selected catalogue with selected years
-  df <- filter(df0, catalog == catalogue &
-     		    publication_year >= 1640 &
-		    publication_year <= 1828)
-
-  # Selected topics
-  df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)  
-  df <- df %>% filter(catalog == catalogue & hit)
-
-  lang <- paste("language.", langs, sep = "")
-  otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
-  df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
-  dfl <- NULL
-  for (lan in lang) {
-    # Classify a document to the specifed language
-    # If document is assigned with languages, each case is considered
-    # so one doc may have multiple entries corresponding to different languages
-    # mean(rowSums(df[, lang]) == 1) # 93% Fennica docs have just 1 language
-    # Combine data frames for specified languages
-    dflsub <- filter(df, df[[lan]])
-    if (nrow(dflsub) > 0) {
-      dflsub$language <- gsub("language.", "", lan)
-      dfl <- bind_rows(dfl, dflsub)
-    }
-  }
-  df <- dfl %>% group_by(publication_decade, language) %>%
-             summarise(n = n(),
-	               paper = sum(paper, na.rm = TRUE))
-
-  # PAPER CONSUMPTION
-  theme_set(theme_bw(20))
-  p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
-       geom_point(aes(col = language, shape = language), size = 5) +
-       geom_line(aes(col = language, shape = language)) +       
-       #geom_smooth(aes(fill = language, color = language)) + 
-       xlab("Publication year") +
-       ylab("Paper consumption") +
-       ggtitle(paste("Devotional Literature (", catalogue, ")", sep = ""))
-       #ggtitle(paste("Devotional literature" (", catalogue, ")", sep = "")) 
-  print(p)
-```
-
----
-
-\begin{center}
-\tiny{\textcolor{gray}{Languages \& religious texts in Finland}}
-\end{center}
-
-### Temporary sermons in Latin and Swedish
-
-- Important role in early modern knowledge production. Language of temporary sermons in contrast to devotional literature has not been analysed in Finland (and Sweden).
-
-```{r topics882, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6}
-  sel <- c("hautajaiset", "häät", "juhlamenot")
-  catalogue <- "Fennica"
-  df <- df0
-  df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)
-
-  # Selected catalogue with selected topics
-  df <- df %>% filter(catalog == catalogue & hit)
-  lang <- paste("language.", langs, sep = "")
-  otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
-  otherlang <- otherlang[otherlang!="language.Multiple languages"]
-  df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
-
-  dfl <- NULL
-  for (lan in lang) {
-    # Classify a document to the specifed language
-    # If document is assigned with languages, each case is considered
-    # so one doc may have multiple entries corresponding to different languages
-    # mean(rowSums(df[, lang]) == 1) # 93% Fennica docs have just 1 language
-    # Combine data frames for specified languages
-    dflsub <- filter(df, df[[lan]])
-    if (nrow(dflsub) > 0) {
-      dflsub$language <- gsub("language.", "", lan)
-    dfl <- bind_rows(dfl, dflsub)
-  }
-}
-dfl$language <- factor(dfl$language, levels = langs)
-
-  df <- dfl %>% group_by(publication_decade, language) %>%
-             summarise(n = n(),
-	               paper = sum(paper, na.rm = TRUE))
-
-  # PAPER CONSUMPTION
-  p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
-       geom_point(aes(col = language, shape = language), size = 5) +
-       geom_line(aes(col = language, shape = language)) +       
-       xlab("Publication year") +
-       ylab("Paper consumption") +
-       ggtitle(paste("Temporary Sermons (", catalogue, ")", sep = ""))
-  print(p)
-```
-
----
-
-\begin{center}
-\Large{4. University curriculum and Enlightenment in Finland}
-\end{center}
-
----
-
-\begin{center}
-\tiny{\textcolor{gray}{University curriculum \& Enlightenment in Finland}}
-\end{center}
-
-### Dissertation languages in Turku 1640-1828
-
-```{r disslang, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
-catalogue <- "Fennica"
-langs <- c("Finnish", "Swedish", "Latin", "German",
-           "Russian", "French", "Hebrew", "Other")
-
-df <- df0 %>%
-        filter(catalog == catalogue) %>%
-        filter(publication_year >= 1640 & publication_year <= 1828) %>%
-	filter(dissertation)
-
-lang <- paste("language.", langs, sep = "")
-otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
-otherlang <- otherlang[otherlang!="language.Multiple languages"]
-
-df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
-
-dfl <- NULL
-for (lan in lang) {
-
-  # Classify a document to the specifed language
-  # If document is assigned with languages, each case is considered
-  # so one doc may have multiple entries corresponding to different languages
-  # mean(rowSums(df[, lang]) == 1) # 93% Fennica docs have just 1 language
-  # Combine data frames for specified languages
-  dflsub <- filter(df, df[[lan]])
-  if (nrow(dflsub)>0) {
-    dflsub$language <- gsub("language.", "", lan)
-    dfl <- bind_rows(dfl, dflsub)
-  }
-}
-
-df <- dfl %>% group_by(publication_decade, language) %>%
-     	     summarise(n = n())
-
-# Calculate percentages
-dff <- spread(df, language, n, fill = 0)
-dff[, -1] <- 100 * t(apply(dff[, -1], 1, function (x) {x/sum(x)}))
-dff <- melt(dff, "publication_decade");
-colnames(dff) <- c("publication_decade", "language", "f")
-
-# Order by language counts
-dff$language <- factor(dff$language,
-   levels = (df %>% group_by(language) %>%
-                    summarise(total = sum(n)) %>%
-		    arrange(total))$language);
-dff <- dff %>% arrange(desc(language))
-
-theme_set(theme_bw(20))
-p <- ggplot(dff, aes(x = publication_decade, y = f)) +
-     geom_bar(position = "stack", stat = "identity", aes(fill = language)) + 
-     xlab("Publication year") +
-     ylab("Title count frequency (%)") +
-     ggtitle(paste("Dissertation languages (", catalogue, ")", sep = "")) +
-     scale_fill_brewer(palette="Spectral")
-print(p)
-```
-
----
-
-\begin{center}
-\tiny{\textcolor{gray}{University curriculum \& Enlightenment in Finland}}
-\end{center}
-
-### Printing by topics in different languages in Turku
-
-```{r topics-103B, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=8}
-sel = c("filosofia","luonnonfilosofia","metafysiikka","logiikka")
-df = dfl
-df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)  
-df <- df %>% filter(hit)
-df <- df %>% group_by(publication_decade, language) %>%
-             summarise(n = n(),
-                 paper = sum(paper, na.rm = TRUE))
-
-# PAPER CONSUMPTION
-p1 <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
-       geom_bar(aes(fill = language), position = "stack", stat = "identity") +                     
-       xlab("Publication year") +
-       ylab("Paper") +
-       guides(fill = guide_legend(reverse = TRUE, title = "")) +
-       ggtitle("Philosophy")
-
-sel = c("oppihistoria","antiikki","historia")
-# Selected catalogue with selected topics
-df = dfl
-df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)  
-df <- df %>% filter(hit)
-df <- df %>% group_by(publication_decade, language) %>%
-             summarise(n = n(),
-	               paper = sum(paper, na.rm = TRUE))
-
-# PAPER CONSUMPTION
-p2 <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
-       geom_bar(aes(fill = language), position = "stack", stat = "identity") +             
-       xlab("Publication year") +
-       ylab("Paper") +
-       guides(fill = guide_legend(reverse = TRUE, title = "")) +
-       ggtitle("History")
-
-sel =   c("psykologia","yhteiskuntafilosofia","valtiofilosofia","talous","raha","moraali","velvollisuudet","kasvatus","maanviljely","maatalous","kalastus")
-
-# Selected catalogue with selected topics
-df = dfl
-df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)  
-df <- df %>% filter(hit)
-df <- df %>% group_by(publication_decade, language) %>%
-             summarise(n = n(),
-	               paper = sum(paper, na.rm = TRUE))
-
-# PAPER CONSUMPTION
-theme_set(theme_bw(20))
-p3 <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
-       geom_bar(aes(fill = language), position = "stack", stat = "identity") +              
-       xlab("Publication year") +
-       ylab("Paper") +
-       guides(fill = guide_legend(reverse = TRUE, title = "")) +
-       ggtitle("Economy")
-grid.arrange(p1, p2, p3, nrow = 3)
-```
-
----
-
-\begin{center}
-\tiny{\textcolor{gray}{University curriculum \& Enlightenment in Finland}}
-\end{center}
-
-### Rise of the octavo sized book as vehicle of Enlightenment
-
-Paper consumption: different document formats over time
-
-```{r LIBER-13, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=11, fig.height=9, fig.show="hold", out.width="160px"}
-for (catal in unique(df0$catalog)) {
-  df2 <- df0 %>% filter(catalog == catal) %>% 
-                 group_by(publication_decade, gatherings) %>% 
-		 summarise(paper2 = sum(paper, na.rm = TRUE), n = n()) 
-  df2 <- filter(df2, gatherings %in% setdiff(names(which(table(df2$gatherings) >= 15)), "NA"))
-  df2$highlight <- rep("Other", nrow(df2))
-  df2$highlight[df2$gatherings == "8vo"] <- "Octavo"
-
-  p <- ggplot(df2, aes(y = paper2,
-                       x = publication_decade,
-  	       	       shape = gatherings,
-		       linetype = gatherings))		       
-  p <- p + geom_point(size = 4)
-  p <- p + geom_smooth(method = "loess", size = 1,
-             aes(color = highlight, fill = highlight))
-  p <- p + scale_color_manual(values = c("darkgreen", "darkgray"))
-  p <- p + scale_fill_manual(values = c("darkgreen", "darkgray"))  	 
-  p <- p + ggtitle("Paper consumption in time by gatherings")
-  p <- p + xlab("Year")
-  p <- p + ylab("Paper consumption")
-  p <- p + guides(linetype = guide_legend(keywidth = 5),
-       	             shape = guide_legend(keywidth = 5))
-  p <- p + ggtitle(catal)
-  print(p)
-}
-```
-
----
-
-##Thanks !
-
-Institutional support:
-
-- Academy of Finland
-- University of Helsinki
-- Digitalia / The Regional Council of South Savo
-
-Data providers:
-
-- National Library of Finland
-- National Library of Sweden
-
-Code infrastructure:
-
-- Github
-- R project
-
-For more info, see:
-
-- \textcolor{blue}{https://github.com/rOpenGov/fennica}
-
-\begin{figure}
-\begin{tabular}{cccccc}
-\includegraphics[width=2cm,height=2cm]{aka.png}&
-\includegraphics[width=1cm,height=1cm]{HY-CC.png}&
-\includegraphics[width=1cm,height=1cm]{kansalliskirjasto.png}&
-\includegraphics[width=1cm,height=1cm]{kungliga.png}&
-\includegraphics[width=1cm,height=1cm]{github-logo.png}&
-\includegraphics[width=1cm,height=1cm]{Rlogo.png}
-\end{tabular}
-\end{figure}
-
----
-
-### Duplicate publications in Fennica/Kungliga
-
-```{r duplicates, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=5, fig.width=10}
-df <- df.combined.preprocessed %>%
-        filter(publication_year >= 1640 & publication_year <=1828) %>%
-        group_by(catalog, publication_decade) %>%
-	summarise(duplicates = 100 * mean(remove))
-
-p <- ggplot(df, aes(x = publication_decade, y = duplicates, fill = catalog)) +
-       geom_bar(position = "dodge", stat = "identity") +
-       ylab("Duplicates (%)") +
-       scale_fill_manual(values = c("blue", "red")) 
-       #ggtitle(paste("Certain duplicates Fennica-Kungliga", paste(range(na.omit(df$publication_decade)), collapse = "-")))
-
-print(p)
-```

### 2016-09-12 inst/examples/20160715-Krakow-Fennica.Rmd
Rmd update

@@
 ```{r publishingovertime, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=4, out.width="300px"}
-
 library(magrittr)

### 2016-09-13 inst/examples/20160715-Krakow-Fennica.Rmd
slide template paper cons fix

@@
 # Remove entries outside the investigated publication periods
-df <- df %>% filter(!is.na(period)) %>% group_by(period, paper)
+df <- df %>% filter(!is.na(period)) %>% group_by(period)
 df <- df %>% summarise(n = n(),

### 2016-09-13 inst/examples/slidetemplates.Rmd
slide template paper cons fix

@@
 # Set locale
-tmp <- Sys.setlocale(locale="UTF-8")
+# tmp <- Sys.setlocale(locale="UTF-8")
 
@@
   df0 <- filter(df0, catalog == params$catalogue)
+}
+
+if ("paper.consumption.km2" %in% names(df0)) {
+  df0$paper <- df0$paper.consumption.km2     
 }

### 2016-09-13 inst/examples/slidetemplates.Rmd
ok

@@
 }
-
-if ("paper.consumption.km2" %in% names(df0)) {
-  df0$paper <- df0$paper.consumption.km2     
-}
 ```
@@
 top <- names(top(df, "publisher", ntop))
-df$publisher[!df$publisher %in% top] <- "Other"
+#df$publisher[!df$publisher %in% top] <- "Other"
+df <- df %>% filter(publisher %in% top)
 df$publisher <- factor(df$publisher, c(top, "Other"))

### 2016-10-02 inst/examples/manuscript-krakow.Rmd
ok

@@
 
-  res <- titlecount_timeline(dfs, "gatherings", nmin = 15, mode = "n") 
+  res <- timeline(dfs, field = "gatherings", nmin = 15, mode = "absolute") 
   print(res$plot + ggtitle(paste(catal, " (n)", sep = "")))
 
-  res <- titlecount_timeline(dfs, "gatherings", nmin = 15, mode = "percentage") 
+  res <- timeline(dfs, field = "gatherings", nmin = 15, mode = "percentage") 
   print(res$plot + ggtitle(paste(catal, " (%)", sep = "")))

### 2016-10-02 inst/examples/slides.Rmd
ok

@@
 library(bibliographica)
-titlecount_timeline(subset(df0, catalog == "Fennica"), 
-          "publisher", nmin = 500, mode = "n")$plot
+timeline(subset(df0, catalog == "Fennica"), 
+          group = "publisher", nmin = 500, mode = "absolute")$plot
 ```

### 2016-10-04 inst/examples/manuscript-krakow.Rmd
Rmd update

--- 2016-07-27 inst/examples/manuscript-krakow.Rmd
@@
 
-  res <- titlecount_timeline(dfs, "gatherings", nmin = 15, mode = "n") 
+  res <- timeline(dfs, field = "titlecount", group = "gatherings", nmin = 15, mode = "absolute") 
   print(res$plot + ggtitle(paste(catal, " (n)", sep = "")))
 
-  res <- titlecount_timeline(dfs, "gatherings", nmin = 15, mode = "percentage") 
+  res <- timeline(dfs, field = "titlecount", group = "gatherings", nmin = 15, mode = "relative") 
   print(res$plot + ggtitle(paste(catal, " (%)", sep = "")))

### 2016-10-04 inst/examples/manuscript-krakow.Rmd
Rmd update

@@
 
-### Printing of natural science in different languages in Turku
+### Printing of natural science in different languages in Fennica/Turku
 
 ```{r topics-104, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6}
-sel = c("luonnontieteet","matematiikka","fysiikka","kemia","tähtitiede","maantiede","geodesia","geofysiikka","meteorologia")
+sel <- c("luonnontieteet","matematiikka","fysiikka","kemia","tähtitiede","maantiede","geodesia","geofysiikka","meteorologia")
 # Selected catalogue with selected topics
-df = dfl
+#catal <- "Fennica"
+#myplace <- "Turku" 
+#df <- df0 %>% filter(catalog == catal & publication_place == myplace)
+df <- dfl
+
 df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)  
@@
                  paper = sum(paper, na.rm = TRUE))
-
+# Only use the first listed language for a doc
+# df$language <- sapply(strsplit(df$language, ";"), function (x) {x[[1]]})
+
+  if (nrow(df) > 0) {		       
     # PAPER CONSUMPTION
@@
     print(p)
-
-```
+  } else {
+    p <- ggplot() + ggtitle(paste(place, "; no hits"))
+  }
+
+```
+
 ---
@@
 
+  if (nrow(df) > 0) {		       
     # PAPER CONSUMPTION
@@
        xlim(c(years[[1]], years[[2]]))
+  } else {
+    p <- ggplot() + ggtitle(paste(place, "; no hits"))
+  }
+
   pics[[place]] <- p
@@
 ```{r ktopic2, echo=FALSE, message=FALSE, warning=FALSE, fig.width=15, fig.height=5}
-
 catalogue <- "Kungliga"
 years <- c(1640, 1828)
-sel =  tolower(c("Idé- och lärdomshistoria", "Antiken", "Historia", "Militärhistoria"))
+sel <- tolower(c("Idé- och lärdomshistoria", "Antiken", "Historia", "Militärhistoria"))
 places <- c("Stockholm", "Lund", "Greifswald", "Uppsala", "Tartu")
@@
 
+  if (nrow(df) > 0) {
     # PAPER CONSUMPTION
@@
        xlim(c(years[[1]], years[[2]]))
+  } else {
+    p <- ggplot() + ggtitle(paste("no hits"))
+  }
+
   pics[[place]] <- p
@@
   # PAPER CONSUMPTION
+  if (nrow(df) > 0) {
     theme_set(theme_bw(20))
@@
 ```{r ktopic7, echo=FALSE, message=FALSE, warning=FALSE, fig.width=15, fig.height=5}
-
 catalogue <- "Kungliga"
@@
   # PUBLISHER COUNT
-  n = sapply(split(dfs$publisher, dfs$publication_year), function (x) {
+  n <- sapply(split(dfs$publisher, dfs$publication_year), function (x) {
          length(unique(na.omit(x)))})
-  df = data.frame(year = names(n), n = unname(n))
+  df <- data.frame(year = names(n), n = unname(n))
   if (nrow(df) > 1) {

### 2016-11-10 inst/examples/Gaudeamus.Rmd
ok

---
title: "Gaudeamus Figures"
author: "Leo Lahti and Mikko Tolonen"
date: "`r Sys.Date()`"
output: markdown_document
---

```{r, echo=FALSE, message=FALSE}
library(dplyr)
dfo <- readRDS("df.Rds")
```

```{r Gaudeamus_Vaasa, echo=FALSE, fig.width=20, fig.height=10}
df <- dfo
df <- df %>% filter(!is.na(publication_year))
tmp1 <- df %>% filter(publication_place == "Vaasa") %>%
     	       group_by(publication_year) %>%
	       tally() %>%
	       arrange(publication_year)
tmp1$decade <- as.numeric(paste0(substr(tmp1$publication_year,1,3),"0"))
tmp2 <- tmp1 %>% group_by(decade) %>% summarise(m = sum(n)/10)
final <- inner_join(tmp1,tmp2)

par(las=1)
par(mgp=c(10,3,0))
par(mar=c(7,17,6,4))
plot(final$publication_year,final$n,cex=1.5,pch="|",cex.main=4.0,main="Julkaisutoiminta Vaasassa 1764-1917",cex.lab=4.0,xlab="",ylab="Dokumenttia / vuosi",axes=FALSE,col="black")
lines(final$publication_year,final$m,type="l",lty=3,col="black",lwd=4)
axis(side = 1, at = c(1764,1809,1863,1917),cex.axis=3)
axis(side = 2, at = c(0,40,80,120,160,194),cex.axis=3)
remove(tmp1,tmp2,final)
```

### 2016-11-10 inst/examples/Gaudeamus.Rmd
ok

@@
 tmp1 <- df %>% filter(publication_place == "Vaasa") %>%
-     	       group_by(publication_year) %>%
+     	       group_by(publication_decade, publication_year) %>%
 	       tally() %>%
 	       arrange(publication_year)
-tmp1$decade <- as.numeric(paste0(substr(tmp1$publication_year,1,3),"0"))
-tmp2 <- tmp1 %>% group_by(decade) %>% summarise(m = sum(n)/10)
-final <- inner_join(tmp1,tmp2)
 
-par(las=1)
-par(mgp=c(10,3,0))
-par(mar=c(7,17,6,4))
-plot(final$publication_year,final$n,cex=1.5,pch="|",cex.main=4.0,main="Julkaisutoiminta Vaasassa 1764-1917",cex.lab=4.0,xlab="",ylab="Dokumenttia / vuosi",axes=FALSE,col="black")
-lines(final$publication_year,final$m,type="l",lty=3,col="black",lwd=4)
-axis(side = 1, at = c(1764,1809,1863,1917),cex.axis=3)
-axis(side = 2, at = c(0,40,80,120,160,194),cex.axis=3)
-remove(tmp1,tmp2,final)
+#tmp1$decade <- as.numeric(paste0(substr(tmp1$publication_year,1,3),"0"))
+tmp2 <- tmp1 %>% group_by(publication_decade) %>% summarise(m = sum(n)/10)
+
+years <- c(1764,1809,1863,1917)
+p <- ggplot(tmp1, aes(x = publication_year, y = n)) +
+       geom_point() +
+       geom_bar(aes(x = publication_decade + 5, y = m), stat = "identity", fill = "gray", alpha = 0.9, color = "black", data = tmp2) +
+       ggtitle("Julkaisutoiminta Vaasassa 1764-1917") +
+       ylab("Dokumenttia / vuosi") +
+       scale_x_continuous(labels = years, breaks = years) +
+       xlab("Julkaisuvuosi")
+
+print(p)
 ```

### 2016-11-10 inst/examples/Gaudeamus.Rmd
ok

@@
 library(dplyr)
+knitr::opts_chunk$set(fig.path = "figure_Gaudeamus/", dev="CairoPNG")
 dfo <- readRDS("df.Rds")
@@
 
-```{r Gaudeamus_Vaasa, echo=FALSE, fig.width=20, fig.height=10}
+```{r Vaasa, echo=FALSE, fig.width=20, fig.height=10}
 df <- dfo
-df <- df %>% filter(!is.na(publication_year))
-tmp1 <- df %>% filter(publication_place == "Vaasa") %>%
+place <- "Vaasa"
+miny <- 1764
+maxy <- 1917
+df <- df %>% filter(!is.na(publication_year)) %>%
+             filter(publication_year >= miny & publication_year <= maxy)
+tmp1 <- df %>% filter(publication_place == place) %>%
      	       group_by(publication_decade, publication_year) %>%
@@
 ```
+
+```{r Turku, echo=FALSE, fig.width=20, fig.height=10}
+df <- dfo
+place <- "Turku"
+miny <- 1640
+maxy <- 1917
+df <- df %>% filter(!is.na(publication_year)) %>%
+             filter(publication_year >= miny & publication_year <= maxy)
+tmp1 <- df %>% filter(publication_place == place) %>%
+     	       group_by(publication_decade, publication_year) %>%
+	       tally() %>%
+	       arrange(publication_year)
+
+#tmp1$decade <- as.numeric(paste0(substr(tmp1$publication_year,1,3),"0"))
+tmp2 <- tmp1 %>% group_by(publication_decade) %>% summarise(m = sum(n)/10)
+
+years <- c(1764,1809,1863,1917)
+p <- ggplot(tmp1, aes(x = publication_year, y = n)) +
+       geom_point() +
+       geom_bar(aes(x = publication_decade + 5, y = m), stat = "identity", fill = "gray", alpha = 0.9, color = "black", data = tmp2) +
+       ggtitle("Julkaisutoiminta Vaasassa 1764-1917") +
+       ylab("Dokumenttia / vuosi") +
+       scale_x_continuous(labels = years, breaks = years) +
+       xlab("Julkaisuvuosi")
+
+print(p)
+```
+
+```{r Helsinki, echo=FALSE, fig.width=20, fig.height=10}
+df <- dfo
+place <- "Helsinki"
+miny <- 1746
+maxy <- 1917
+df <- df %>% filter(!is.na(publication_year)) %>%
+             filter(publication_year >= miny & publication_year <= maxy)
+tmp1 <- df %>% filter(publication_place == place) %>%
+     	       group_by(publication_decade, publication_year) %>%
+	       tally() %>%
+	       arrange(publication_year)
+
+#tmp1$decade <- as.numeric(paste0(substr(tmp1$publication_year,1,3),"0"))
+tmp2 <- tmp1 %>% group_by(publication_decade) %>% summarise(m = sum(n)/10)
+
+years <- c(1764,1809,1863,1917)
+p <- ggplot(tmp1, aes(x = publication_year, y = n)) +
+       geom_point() +
+       geom_bar(aes(x = publication_decade + 5, y = m), stat = "identity", fill = "gray", alpha = 0.9, color = "black", data = tmp2) +
+       ggtitle("Julkaisutoiminta Vaasassa 1764-1917") +
+       ylab("Dokumenttia / vuosi") +
+       scale_x_continuous(labels = years, breaks = years) +
+       xlab("Julkaisuvuosi")
+
+print(p)
+```
+
+```{r Suomi, echo=FALSE, fig.width=20, fig.height=10}
+df <- dfo
+place <- "Finland"
+miny <- 1640
+maxy <- 1917
+df <- df %>% filter(!is.na(publication_year)) %>%
+             filter(publication_year >= miny & publication_year <= maxy)
+tmp1 <- df %>% filter(publication_country == place) %>%
+     	       group_by(publication_decade, publication_year) %>%
+	       tally() %>%
+	       arrange(publication_year)
+
+#tmp1$decade <- as.numeric(paste0(substr(tmp1$publication_year,1,3),"0"))
+tmp2 <- tmp1 %>% group_by(publication_decade) %>% summarise(m = sum(n)/10)
+
+years <- c(1764,1809,1863,1917)
+p <- ggplot(tmp1, aes(x = publication_year, y = n)) +
+       geom_point() +
+       geom_bar(aes(x = publication_decade + 5, y = m), stat = "identity", fill = "gray", alpha = 0.9, color = "black", data = tmp2) +
+       ggtitle("Julkaisutoiminta Vaasassa 1764-1917") +
+       ylab("Dokumenttia / vuosi") +
+       scale_x_continuous(labels = years, breaks = years) +
+       xlab("Julkaisuvuosi")
+
+print(p)
+```

### 2016-11-10 inst/examples/Gaudeamus.Rmd
ok

@@
 dfo <- readRDS("df.Rds")
+theme_set(theme_bw(30))
 ```
@@
 #tmp1$decade <- as.numeric(paste0(substr(tmp1$publication_year,1,3),"0"))
-tmp2 <- tmp1 %>% group_by(publication_decade) %>% summarise(m = sum(n)/10)
+tmp2 <- tmp1 %>% group_by(publication_decade) %>% summarise(m = sum(n))
 
@@
 p <- ggplot(tmp1, aes(x = publication_year, y = n)) +
-       geom_point() +
+#       geom_point() +
        geom_bar(aes(x = publication_decade + 5, y = m), stat = "identity", fill = "gray", alpha = 0.9, color = "black", data = tmp2) +
        ggtitle("Julkaisutoiminta Vaasassa 1764-1917") +
-       ylab("Dokumenttia / vuosi") +
+       ylab("Dokumenttia (n)") +
        scale_x_continuous(labels = years, breaks = years) +

### 2016-11-10 inst/examples/Gaudeamus.Rmd
ok

@@
 dfo <- readRDS("df.Rds")
-theme_set(theme_bw(30))
+theme_set(theme_bw(40))
 ```
@@
        geom_bar(aes(x = publication_decade + 5, y = m), stat = "identity", fill = "gray", alpha = 0.9, color = "black", data = tmp2) +
-       ggtitle("Julkaisutoiminta Vaasassa 1764-1917") +
+       ggtitle(paste("Julkaisutoiminta Vaasassa ", miny, "-", maxy, sep = "")) +
        ylab("Dokumenttia (n)") +
@@
        geom_bar(aes(x = publication_decade + 5, y = m), stat = "identity", fill = "gray", alpha = 0.9, color = "black", data = tmp2) +
-       ggtitle("Julkaisutoiminta Vaasassa 1764-1917") +
+       ggtitle(paste("Julkaisutoiminta Turussa ", miny, "-", maxy, sep = "")) + 
        ylab("Dokumenttia (n)") +
@@
        geom_bar(aes(x = publication_decade + 5, y = m), stat = "identity", fill = "gray", alpha = 0.9, color = "black", data = tmp2) +
-       ggtitle("Julkaisutoiminta Vaasassa 1764-1917") +
+       ggtitle(paste("Julkaisutoiminta Helsingissä ", miny, "-", maxy, sep = "")) +
+
        ylab("Dokumenttia (n)") +
@@
              filter(publication_year >= miny & publication_year <= maxy)
-tmp1 <- df %>% filter(publication_country == place) %>%
+tmp1 <- df %>% filter(country == place) %>%
      	       group_by(publication_decade, publication_year) %>%
@@
        geom_bar(aes(x = publication_decade + 5, y = m), stat = "identity", fill = "gray", alpha = 0.9, color = "black", data = tmp2) +
-       ggtitle("Julkaisutoiminta Vaasassa 1764-1917") +
+       ggtitle(paste("Julkaisutoiminta Suomessa ", miny, "-", maxy, sep = "")) +               
        ylab("Dokumenttia (n)") +
@@
 ```
+
+```{r Kaikki, echo=FALSE, fig.width=20, fig.height=10}
+df <- dfo
+countries <- "Finland"
+places <- c("Helsinki", "Turku", "Vaasa")
+miny <- 1640
+maxy <- 1917
+df <- df %>% filter(!is.na(publication_year)) %>%
+             filter(publication_year >= miny & publication_year <= maxy)
+
+tmp1 <- df %>% filter(publication_place %in% places) %>%
+     	       group_by(publication_decade, publication_place) %>%
+	       tally()
+
+tmp2 <- df %>% filter(country %in% countries) %>%
+     	       group_by(publication_decade, country) %>%
+	       tally() %>%
+	       rename(publication_place = country)
+
+d <- bind_rows(tmp1, tmp2)
+d$publication_place <- factor(d$publication_place)
+
+years <- c(1640, 1764,1809,1863,1917)
+p <- ggplot(d, aes(x = publication_decade + 5, y = n, fill = publication_place, color = publication_place)) +
+      # geom_bar(stat = "identity", alpha = 0.9, color = "black", position = "dodge") +
+       geom_smooth() +       
+       ggtitle("Julkaisutoiminta 1640-1917") +
+       ylab("Dokumenttia (n)") +
+       scale_x_continuous(labels = years, breaks = years) +
+       xlab("Julkaisuvuosi") +
+       scale_y_log10()
+
+print(p)
+```

### 2016-11-17 inst/examples/20161117-manuscript.Rmd
ok

---
title: "Digital History in Finland, 1488-1828"
author: "Leo Lahti, Jani Marjanen, Hege Roivainen, Mikko Tolonen"
date: date: "`r Sys.Date()`"
output: markdown_document
---

```{r init, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(fig.path = "figure-2016-manuscript/")
# Set locale
tmp <- Sys.setlocale(locale="UTF-8")

library(stringr)
library(dplyr)
library(ggplot2)
library(bibliographica)
library(fennica)
library(sorvi)

# Nice theme
theme_set(theme_bw(26))

# Read data
dfo <- readRDS("df.Rds")

# Remove very early and late years
dfo <- dfo %>% filter(publication_year > 1400 & publication_year < 1911)

# Calculate title length (word count)
dfo$title_wordcount <- sapply(strsplit(as.character(dfo$title), " "), length)
dfo$title_wordcount[is.na(dfo$title)] <- NA
```

```{r title_length, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=4, fig.width=8}
df <- dfo %>% group_by(publication_year) %>%
              summarize(median_title_length = median(title_wordcount),
	      		mean_title_length = mean(title_wordcount),
	      		n = n())

p1 <- ggplot(df, aes(x = publication_year, y = mean_title_length)) +
       geom_point(aes(size = n)) + geom_smooth() + ggtitle("Mean title word count")
p2 <- ggplot(df, aes(x = publication_year, y = median_title_length)) +
       geom_point(aes(size = n)) + geom_smooth() +
       ggtitle("Median title word count")

library(gridExtra)
grid.arrange(p1, p2, nrow = 1)
```

```{r title_length_by_gatherings, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=4, fig.width=8}
top.gatherings <- setdiff(names(top(dfo, "gatherings", 5)), "NA")

df <- dfo %>% filter(gatherings %in% top.gatherings) %>%
              group_by(publication_year, gatherings) %>%
              summarize(mean_title_length = mean(title_wordcount),
	      		n = n())

p <- ggplot(df, aes(x = publication_year, y = mean_title_length,
                     fill = gatherings, color = gatherings)) +
       geom_point(aes(size = n)) +
       geom_smooth() +
       scale_y_log10() +
       ggtitle("Mean title word count (top gatherings)")

print(p)
```

### 2016-11-17 inst/examples/analysis.R

@@ -18,6 +18,7 @@ knitr::knit("Vaasa.Rmd", encoding="UTF-8")
 knitr::knit("suvut.Rmd", encoding="UTF-8")
 knitr::knit("20151209-HelsinkiDH.Rmd", encoding="UTF-8")
 knitr::knit("20160303-Krakow.Rmd", encoding="UTF-8")
+knitr::knit("20161117-manuscript.Rmd", encoding="UTF-8")
 #rmarkdown::render("20160715-Krakow-Fennica.Rmd") # Krakow 7/2016 slides frozen.
 
 #library(rmarkdown)

### 2016-11-17 inst/examples/20161117-manuscript.Rmd
ok

@@
 knitr::opts_chunk$set(echo = FALSE)
-knitr::opts_chunk$set(fig.path = "figure-2016-manuscript/")
+knitr::opts_chunk$set(fig.path = "figure-2016-manuscript/", dev="CairoPNG")
 # Set locale
@@
 
-```{r title_length, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=4, fig.width=8}
+```{r title_length, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=7, fig.width=15}
 df <- dfo %>% group_by(publication_year) %>%
@@
 
-```{r title_length_by_gatherings, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=4, fig.width=8}
+```{r title_length_by_gatherings, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=7, fig.width=15}
 top.gatherings <- setdiff(names(top(dfo, "gatherings", 5)), "NA")

### 2016-11-17 inst/examples/20161117-manuscript.Rmd
ok

@@
 ---
-title: "Digital History in Finland, 1488-1828"
-author: "Leo Lahti, Jani Marjanen, Hege Roivainen, Mikko Tolonen"
+title: "Patterns in Knowledge Production in Sweden and Finland, 1640–1828"
+author: "Mikko Tolonen, Jani Marjanen, Hege Roivainen, Leo Lahti"
 date: date: "`r Sys.Date()`"
@@
 
-# Remove very early and late years
-dfo <- dfo %>% filter(publication_year > 1400 & publication_year < 1911)
+# Analysis time window
+dfo <- dfo %>% filter(publication_year >= 1640 & publication_year <= 1828)
 

### 2017-01-18 inst/examples/20161117-manuscript.Rmd
title length analyses for JM until 1911

@@
 # Analysis time window
-dfo <- dfo %>% filter(publication_year >= 1640 & publication_year <= 1828)
+#dfo <- dfo %>% filter(publication_year >= 1640 & publication_year <= 1828)
+dfo <- dfo %>% filter(publication_year >= 1640 & publication_year <= 1911)
 
@@
 ```
+
+```{r title_length_by_lang, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=7, fig.width=15}
+top.language <- setdiff(names(top(dfo, "language", 11)), "NA")
+
+df <- dfo %>% filter(language %in% top.language) %>%
+              group_by(publication_decade, language) %>%
+              summarize(mean_title_length = mean(title_wordcount),
+	      		n = n())
+
+p <- ggplot(df, aes(x = publication_decade, y = mean_title_length,
+                     fill = language, color = language)) +
+       geom_point(aes(size = n)) +
+       geom_line() +
+       #scale_y_log10() +
+       ggtitle("Mean title word count (top language)")
+
+print(p)
+```

### 2017-01-18 inst/examples/Gaudeamus.Rmd

@@
 
-years <- c(1764,1809,1863,1917)
+years <- c(1640, 1764,1809,1863,1917)
 p <- ggplot(tmp1, aes(x = publication_year, y = n)) +

### 2017-01-26 inst/examples/20170125-Manuscript-FK.Rmd
manuscript figs added

---
title: "Printing in a Periphery: a Quantitative Study of Finnish Knowledge Production, 1640-1828"
author: "Mikko Tolonen, Jani Marjanen, Hege Roivainen, Leo Lahti"
date: "`r Sys.Date()`"
output: 
  beamer_presentation:
    theme: "boxes"
    colortheme: "orchid"
    fonttheme: "professionalfonts"
  pdf_document:
fontsize: 13pt
---

```{r jm-init, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, cache=TRUE}
# Default time span
min.year <- 1488
max.year <- 1828

library(ggmap)
library(gisfin)
library(stringr)
library(dplyr)
library(tidyr)
library(reshape2)
library(ggplot2)
library(bibliographica)
library(fennica)
library(sorvi)
library(devtools)
library(magrittr)
library(ggplot2)
library(dplyr)

knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(fig.path = "2017-manuscript/")

# Set locale
tmp <- Sys.setlocale(locale="UTF-8")

# Nice theme
theme_set(theme_bw(26))
```

```{r jm-init2, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, cache=TRUE}
# Full combined catalogue (Fen + Kun) with marked duplicates
df.combined.preprocessed <- readRDS("df.combined.20160715-Krakow.Rds")
# Data with duplicates removed and years limited
df0 <- df.combined.preprocessed %>% filter(!remove) %>%
	   			    filter(publication_year >= min.year &
					   publication_year <= max.year)
```

### Paper consumption per title

```{r paper_per_title, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=4, out.width="300px"}
catalogue <- "Kungliga"
places <- c("Stockholm", "Lund", "Uppsala")
periods <- list(c(1757, 1765), c(1766, 1774), c(1775, 1783))

df <- df0
df$period <- rep(NA, nrow(df))
for (i in 1:length(periods)) {
  pr <- periods[[i]]
  df$period[df$publication_year >= min(pr) & df$publication_year <= max(pr)] <- paste(min(pr), max(pr), sep = "-")
}
df$period <- factor(df$period)

# Selected catalogue with selected years
df <- filter(df, catalog == catalogue & publication_place %in% places & !is.na(period)) %>%
             group_by(period, publication_place) %>%
             summarise(n = n(), paper = sum(paper, na.rm = TRUE)) %>%
	     mutate(paper_per_title = paper/n)

theme_set(theme_bw(20))
p <- ggplot(df, aes(x = period, y = paper_per_title)) +
     geom_bar(stat = "identity", position = "dodge", aes(fill = publication_place), color = "black") +
     ylab("Paper per title (sheets)") +
     xlab("Publication period") +
     #scale_color_manual(values = c("blue", "darkgreen")) + 
     # 	 scale_size_discrete(range = c(2, 8)) +
     guides(fill = guide_legend(reverse = TRUE, title = "Place"), color = "none") 
print(p)
```

### Book production and Riksdag assemblies

According to Kungliga in the the long eighteenth century.

```{r riksdar, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
minyear <- 1690
maxyear <- 1828 # or 1810
catal <- "Kungliga"

library(magrittr)
library(ggplot2)
library(dplyr)
library(ggplot2)
library(reshape2)

  df <- df0
  df <- subset(df, catalog == catal)
  df <- subset(df, publication_year >= minyear & publication_year <= maxyear)

  timeinterval <- 1
  df$timeunit <- round(df$publication_year/timeinterval)*timeinterval

  df$unity = rep(1, nrow(df))
  publications <- tapply(df$unity, list(df$timeunit), sum)

  publications[is.na(publications)] <- 0 # Set NAs to 0
  publications <- publications/timeinterval # Instead of decadal sum, use average annual output 
  dfm <- melt(publications) 
  names(dfm) <- c("Time", "Documents")
  dfm <- transform(dfm, date = as.numeric(as.character(Time)))
  ymin = min(dfm$Documents)
  ymax = max(dfm$Documents)

  li <- list(1719, # Stockholm 20 januari 1719 1 juni 1719
             1720,
	     1723,
	     c(1726, 1727),
	     1731,
	     1734, # Stockholm 14 maj 1734 14 december 1734
	     c(1738, 1739),
	     c(1740, 1741),
	     1742,
	     c(1746, 1747),
	     c(1751, 1752),
	     c(1755, 1756),
	     c(1760, 1762),
	     c(1765, 1766), # Stockholm 21 februari 1765 21 oktober 1766
	     c(1769, 1770), # Norrköping & Stockholm 22 april 1769 5 februari 1770
	     c(1771, 1772), # Stockholm 19 juni 1771 12 september 1772
	     c(1778, 1779),
	     1786,
	     1789,
	     1792, # Gävle 26 januari 1792 24 februari 1792         
	     1800,
	     c(1809, 1810))

  rect_left <- c(min(na.omit(dfm$date)))
  for (item in li) {
    rect_left <- c(rect_left, min(item) - .5, max(item) + .5)
  }
  rect_left <- c(rect_left, max(na.omit(dfm$date)))

  rectangles <- data.frame(
    xmin = rect_left[-length(rect_left)],
    xmax = rect_left[-1],
    ymin = ymin,
    ymax = ymax
    )
  rectangles$shade <- rep(c("Background", "Highlight"), length = nrow(rectangles))

 cols <- c("lightgray", "darkgray")
 bgcol <- "white"
 rectangles$shade[rectangles$shade == "Background"] <- bgcol
 rectangles$shade[rectangles$shade == "Highlight"] <- rep(cols, length.out = sum(rectangles$shade == "Highlight"))
 rectangles$shade = factor(rectangles$shade)

  # Draw Figure
  theme_set(theme_bw(20))
  p <- ggplot()
  p <- p + geom_rect(data = rectangles, 
       aes(xmin=xmin, xmax=xmax, ymin=ymin, ymax=ymax, fill=shade), alpha=0.8) + 
         scale_fill_manual(values = levels(rectangles$shade)) # + guides(fill = "none") 
  p <- p + geom_line(data = dfm, aes(x = date, y = Documents), col = "black")
  p <- p + geom_point(data = dfm, aes(x = date, y = Documents), col = "black")
  #p <- p + scale_x_continuous(breaks=seq(min(dfm$date), max(dfm$date), 10))
  p <- p + scale_x_continuous(breaks=scales::pretty_breaks(n = 20))  
  p <- p + ggtitle("Publishing activity")
  p <- p + ylab("Documents / Year")
  p <- p + xlab("Year")
  p <- p + ggtitle(catal)
  p <- p + guides(fill = "none") 
  print(p)
```

### Book production

Book production by year in Turku in Fennica and Kungliga 1640–1828 as a percentage of all books in the catalogues.

Tämä on tavallaan pelkkä kokonaiskuva kirjatuotannosta koko ajalta, joka on jo olemassa moneen kertaan, mutta toivoisin, että siinä voisi näyttää Turun osuuden erikseen prosentteina. Tässä saadaan hyvin näytettyä se mitä Turussa tapahtuu isonvihan aikaan ja 1809 jälkeen. Fennica on tärkeämpi, mutta minusta kannattaisi katsoa myös miltä tämä näyttää Kungligan osalta.

```{r bookprod, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
minyear <- 1640
maxyear <- 1828

df.turku <- df0 %>% filter(publication_year >= minyear & publication_year <= maxyear) %>%
              filter(publication_place == "Turku") %>%
	      group_by(catalog, publication_year) %>%
	      summarize(n.turku = n())

df.all <- df0 %>% filter(publication_year >= minyear & publication_year <= maxyear) %>%
	      group_by(catalog, publication_year) %>%
	      summarize(n.all = n())

df <- full_join(df.all, df.turku) %>%
        filter(!is.na(n.turku)) %>%
        mutate(f.turku = n.turku/n.all)

p <- ggplot(df, aes(x = publication_year, y = f.turku)) +
       geom_line(aes(color = catalog), size = 1) +
       scale_y_continuous(labels = scales::percent) +
       scale_color_manual(values = c("darkblue", "red")) +
       ylab("Percentage (%)") +
       xlab("Publication year") +
       guides(color = guide_legend(title = "Catalogue")) +
       ggtitle("Documents published in Turku")

print(p)
```

### 2017-01-26 inst/examples/20170125-Manuscript-FK.Rmd
ok

@@
 
-```{r paper_per_title, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=4, out.width="300px"}
+```{r paper_per_title, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=8}
 catalogue <- "Kungliga"

### 2017-01-26 inst/examples/20170125-Manuscript-FK.Rmd
ok

@@
 
-```{r paper_per_title, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=8}
+Paper consumption per title in 1757–1765, 1766–1774, and 1775–1783 in
+Stockholm, Lund and Uppsala in Kungliga.
+
+```{r paper_per_title, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
 catalogue <- "Kungliga"
@@
 
-Tämä on tavallaan pelkkä kokonaiskuva kirjatuotannosta koko ajalta, joka on jo olemassa moneen kertaan, mutta toivoisin, että siinä voisi näyttää Turun osuuden erikseen prosentteina.
-Tässä saadaan hyvin näytettyä se mitä Turussa tapahtuu isonvihan aikaan ja 1809 jälkeen.
-Fennica on tärkeämpi, mutta minusta kannattaisi katsoa myös miltä tämä näyttää Kungligan osalta.
-
 ```{r bookprod, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}

### 2017-01-26 inst/examples/20170125-Manuscript-FK.Rmd
ok

@@
 
-```{r paper_per_title, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
+```{r paper_per_title, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=4}
 catalogue <- "Kungliga"

### 2017-01-26 inst/examples/20170125-Manuscript-FK.Rmd
Fennica analyses mod

@@
 # Selected catalogue with selected years
-df <- filter(df, catalog == catalogue & publication_place %in% places & !is.na(period)) %>%
-             group_by(period, publication_place) %>%
+df <- filter(df, catalog == catalogue & publication_place %in% places & !is.na(period) & !is.na(paper))
+
+df <- df %>% group_by(period, publication_place) %>%
              summarise(n = n(), paper = sum(paper, na.rm = TRUE)) %>%
@@
 theme_set(theme_bw(20))
-p <- ggplot(df, aes(x = period, y = paper_per_title)) +
-     geom_bar(stat = "identity", position = "dodge", aes(fill = publication_place), color = "black") +
+p <- ggplot(df, aes(x = publication_place, y = paper_per_title)) +
+     geom_bar(stat = "identity", position = "dodge", aes(fill = period), color = "black") +
      ylab("Paper per title (sheets)") +
@@
 print(p)
+
+kable(df)
 ```
@@
 maxyear <- 1828 
+df <- df0 %>% filter(!is.na(publication_place)) 
+df$myplace <- df$publication_place
+df$myplace[!df$myplace == "Turku"] <- "Other"
 
-df.turku <- df0 %>% filter(publication_year >= minyear & publication_year <= maxyear) %>%
-              filter(publication_place == "Turku") %>%
-	      group_by(catalog, publication_year) %>%
-	      summarize(n.turku = n())
+df <- df %>%  filter(publication_decade >= minyear & publication_decade <= maxyear) %>%
+	      group_by(catalog, publication_decade, myplace) %>%
+	      summarize(n = n())
 
-df.all <- df0 %>% filter(publication_year >= minyear & publication_year <= maxyear) %>%
-	      group_by(catalog, publication_year) %>%
-	      summarize(n.all = n())
+pics <- list()
+for (cat in unique(df$catalog)) {
+  dfs <- subset(df, catalog == cat)
+  p <- ggplot(dfs, aes(x = publication_decade, y = n)) +
+       geom_bar(aes(fill = myplace), color = "black", stat = "identity", position = "stack") +
+       scale_fill_manual(values = c("gray", "black")) +
+       ylab("Title count") +
+       xlab("Publication decade") +
+       guides(fill = guide_legend(title = "Place")) +
+       ggtitle(cat) +
+       xlim(values = c(min(df$publication_decade), max(df$publication_decade)))
+  pics[[cat]] <- p
+}
 
-df <- full_join(df.all, df.turku) %>%
-        filter(!is.na(n.turku)) %>%
-        mutate(f.turku = n.turku/n.all)
-
-p <- ggplot(df, aes(x = publication_year, y = f.turku)) +
-       geom_line(aes(color = catalog), size = 1) +
-       scale_y_continuous(labels = scales::percent) +
-       scale_color_manual(values = c("darkblue", "red")) +
-       ylab("Percentage (%)") +
-       xlab("Publication year") +
-       guides(color = guide_legend(title = "Catalogue")) +
-       ggtitle("Documents published in Turku")
-
-print(p)
+library(gridExtra)
+grid.arrange(pics[[1]], pics[[2]], nrow = 2)
 ```

### 2017-01-26 inst/examples/20170125-Manuscript-FK.Rmd
ok

@@
 
-```{r riksdar, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
+```{r riksdar, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=5}
 minyear <- 1690
@@
 
-```{r bookprod, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
+```{r bookprod, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=10}
 minyear <- 1640

### 2017-01-26 inst/examples/20170125-Manuscript-FK.Rmd
analysis update

@@
 # Full combined catalogue (Fen + Kun) with marked duplicates
-df.combined.preprocessed <- readRDS("df.combined.20160715-Krakow.Rds")
+#df.combined.preprocessed <- readRDS("df.combined.20160715-Krakow.Rds")
+df.combined.preprocessed <- readRDS("df.combined.20170125.Rds")
 # Data with duplicates removed and years limited

### 2017-01-27 inst/examples/manuscript-krakow.Rmd
manuscript analysis update

@@
 
-  res <- timeline(dfs, field = "titlecount", group = "gatherings", nmin = 15, mode = "absolute") 
-  print(res$plot + ggtitle(paste(catal, " (n)", sep = "")))
-
-  res <- timeline(dfs, field = "titlecount", group = "gatherings", nmin = 15, mode = "relative") 
-  print(res$plot + ggtitle(paste(catal, " (%)", sep = "")))
+  res <- plot_timeline(dfs, field = "titlecount", group = "gatherings", nmin = 15, mode = "absolute") 
+  print(res + ggtitle(paste(catal, " (n)", sep = "")))
+
+  res <- plot_timeline(dfs, field = "titlecount", group = "gatherings", nmin = 15, mode = "relative") 
+  print(res + ggtitle(paste(catal, " (%)", sep = "")))
 }

### 2017-01-30 inst/examples/20170125-Manuscript-FK.Rmd
Linkoping analysis

@@
 ```
+
+```{r linkoping, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=10}
+minyear <- 1640
+maxyear <- 1828
+myplace <- "Linköping"
+cat <- "Kungliga"
+df <- df0 %>% filter(publication_place == myplace) %>%
+      	      filter(catalog == cat) %>%
+              filter(publication_year >= minyear &
+	             publication_year <= maxyear) #%>%
+
+tab <- unique(df[, c("publication_year", "author", "title", "publisher")])
+write.table(tab, sep = "\t", quote = F, row.names = FALSE, file = "output.tables/Linkoping.tab")
+
+p <- plot_timeline(df, x = "publication_decade", y = "titlecount") +
+     ylab("Title count (n)") + ggtitle(paste("Title count: ", cat, "/", myplace))
+print(p)
+
+dfs <- df %>% select(publication_decade, publisher) %>% unique
+p <- plot_timeline(dfs, x = "publication_decade") +
+     ylab("Publisher count (n)") + ggtitle(paste("Publisher count: ", cat, "/", myplace))
+print(p)
+
+```

### 2017-01-30 inst/examples/20170125-Manuscript-FK.Rmd
analysis update

@@
 
+### Kungliga / Linkoping
+
 ```{r linkoping, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=10}
@@
 print(p)    
-
 ```

### 2017-01-30 inst/examples/20170125-Manuscript-FK.Rmd
Linkoping analysis

--- 2017-01-26 inst/examples/20170125-Manuscript-FK.Rmd
@@
 ```
+
+### Kungliga / Linkoping
+
+```{r linkoping, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
+minyear <- 1640
+maxyear <- 1828
+myplace <- "Linköping"
+cat <- "Kungliga"
+df <- df0 %>% filter(publication_place == myplace) %>%
+      	      filter(catalog == cat) %>%
+              filter(publication_year >= minyear &
+	             publication_year <= maxyear) #%>%
+
+tab <- unique(df[, c("publication_year", "author", "title", "publisher")])
+write.table(tab, sep = "\t", quote = F, row.names = FALSE, file = "output.tables/Linkoping.tab")
+```
+
+[Document listing for `r paste(cat, "/", myplace, minyear, "-", maxyear, sep = " ")`](output.tables/Linkoping.tab)
+
+```{r linkoping2, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
+p <- plot_timeline(df, x = "publication_decade", y = "titlecount") +
+     ylab("Title count (n)") + ggtitle(paste("Title count: ", cat, "/", myplace))
+print(p)
+
+dfs <- df %>% select(publication_decade, publisher) %>% unique
+p <- plot_timeline(dfs, x = "publication_decade") +
+     ylab("Publisher count (n)") + ggtitle(paste("Publisher count: ", cat, "/", myplace))
+print(p)    
+```

### 2017-01-31 inst/examples/20170125-Manuscript-FK.Rmd
added per capita analyses

@@
 
+### Title count and publisher count in Linköping
+
 ```{r linkoping2, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
@@
 
-dfs <- df %>% select(publication_decade, publisher) %>% unique
-p <- plot_timeline(dfs, x = "publication_decade") +
+dfs <- df %>% select(publication_year, publisher) %>% unique
+p <- plot_timeline(dfs, x = "publication_year") +
      ylab("Publisher count (n)") + ggtitle(paste("Publisher count: ", cat, "/", myplace))
 print(p)
+
+kable(dfs)
 ```
+
+### Title count per capita
+
+The historical population sizes used in this analysis are shown in this [table](https://github.com/rOpenGov/bibliographica/blob/master/inst/extdata/population_sizes_in_cities.csv).
+
+```{r percapita, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
+# Read historical population sizes
+f <- system.file("inst/extdata/population_sizes_in_cities.csv", package = "bibliographica")
+pop <- read.csv(f)
+pop <- melt(pop, "Year")
+colnames(pop) <- c("publication_decade", "publication_place", "population")
+pop <- as_data_frame(pop)
+pop$publication_place <- as.character(pop$publication_place)
+
+# Cities with population data
+cities <- setdiff(pop$publication_place, "Year")
+
+minyear <- 1640
+maxyear <- 1828
+cat <- "Kungliga"
+df <- df0 %>% filter(publication_place %in% cities) %>%
+      	      filter(catalog == cat) %>%
+              filter(publication_decade %in% pop$publication_decade) %>%
+	      select(publication_decade, publication_place) %>%	      
+	      group_by(publication_decade, publication_place) %>%
+	      summarise(n = n())
+
+# Remove special chars for compatibility (table join fails otherwise)
+pop$publication_place <- gsub("Linköping", "Linkoping", pop$publication_place)
+df$publication_place <- gsub("Linköping", "Linkoping", df$publication_place)
+
+# Join title count and population size
+dfm <- inner_join(pop, df, by = c("publication_decade", "publication_place"))
+
+# Add title count per capita
+dfm <- dfm %>% mutate(titles_per_capita = n/population)
+
+p <- ggplot(dfm, aes(x = publication_decade, y = titles_per_capita)) +
+       geom_line(aes(color = publication_place), size = 1) +
+       geom_point(aes(color = publication_place), size = 2) +
+       xlab("Publication decade") +
+       ylab("Title count per capita (n)") +
+       ggtitle("Title count per capita in selected cities") +
+       guides(color = guide_legend(title = "Place", reverse = TRUE))
+print(p)       
+```

### 2017-01-31 inst/examples/20170125-Manuscript-FK.Rmd
ok

@@
 
-dfs <- df %>% select(publication_year, publisher) %>% unique
-p <- plot_timeline(dfs, x = "publication_year") +
-     ylab("Publisher count (n)") + ggtitle(paste("Publisher count: ", cat, "/", myplace))
+dfs <- df %>% select(publication_year, publisher) %>%
+	      filter(!is.na(publisher)) %>%
+              unique %>%	      
+	      arrange(publication_year)
+p <- plot_timeline(dfs, x = "publication_year", time.window = 1) +
+       ylab("Publisher count (n)") +
+       ggtitle(paste("Publisher count: ", cat, "/", myplace))
 print(p)
-
 kable(dfs)
-```
+.```
 

### 2017-01-31 inst/examples/manuscript-krakow.Rmd
analysis updates

@@
 
-  res <- plot_timeline(dfs, field = "titlecount", group = "gatherings", nmin = 15, mode = "absolute") 
+  res <- plot_timeline(data = dfs, x = "publication_year", y = "titlecount", group = "gatherings", nmin = 15, mode = "absolute") 
   print(res + ggtitle(paste(catal, " (n)", sep = "")))
 
-  res <- plot_timeline(dfs, field = "titlecount", group = "gatherings", nmin = 15, mode = "relative") 
+  res <- plot_timeline(data = dfs, x = "publication_year", y = "titlecount", group = "gatherings", nmin = 15, mode = "relative") 
   print(res + ggtitle(paste(catal, " (%)", sep = "")))
@@
 
+### Paper consumption per title
+
+Paper consumption per title in 1757–1765, 1766–1774, and 1775–1783 in
+Stockholm, Lund and Uppsala in Kungliga.
+
+```{r paper_per_title, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=4}
+catalogue <- "Kungliga"
+places <- c("Stockholm", "Lund", "Uppsala")
+periods <- list(c(1757, 1765), c(1766, 1774), c(1775, 1783))
+
+df <- df0
+df$period <- rep(NA, nrow(df))
+for (i in 1:length(periods)) {
+  pr <- periods[[i]]
+  df$period[df$publication_year >= min(pr) & df$publication_year <= max(pr)] <- paste(min(pr), max(pr), sep = "-")
+}
+df$period <- factor(df$period)
+
+# Selected catalogue with selected years
+df <- filter(df, catalog == catalogue & publication_place %in% places & !is.na(period) & !is.na(paper))
+
+df <- df %>% group_by(period, publication_place) %>%
+             summarise(n = n(), paper = sum(paper, na.rm = TRUE)) %>%
+	     mutate(paper_per_title = paper/n)
+
+theme_set(theme_bw(20))
+p <- ggplot(df, aes(x = publication_place, y = paper_per_title)) +
+     geom_bar(stat = "identity", position = "dodge", aes(fill = period), color = "black") +
+     ylab("Paper per title (sheets)") +
+     xlab("Publication period") +
+     #scale_color_manual(values = c("blue", "darkgreen")) + 
+     # 	 scale_size_discrete(range = c(2, 8)) +
+     guides(fill = guide_legend(reverse = TRUE, title = "Place"), color = "none") 
+print(p)
+
+kable(df)
+```
+
+### Book production and Riksdag assemblies
+
+According to Kungliga in the the long eighteenth century.
+
+```{r riksdar, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=5}
+minyear <- 1690
+maxyear <- 1828 # or 1810
+catal <- "Kungliga"
+
+library(magrittr)
+library(ggplot2)
+library(dplyr)
+library(ggplot2)
+library(reshape2)
+
+  df <- df0
+  df <- subset(df, catalog == catal)
+  df <- subset(df, publication_year >= minyear & publication_year <= maxyear)
+
+  timeinterval <- 1
+  df$timeunit <- round(df$publication_year/timeinterval)*timeinterval
+
+  df$unity = rep(1, nrow(df))
+  publications <- tapply(df$unity, list(df$timeunit), sum)
+
+  publications[is.na(publications)] <- 0 # Set NAs to 0
+  publications <- publications/timeinterval # Instead of decadal sum, use average annual output 
+  dfm <- melt(publications) 
+  names(dfm) <- c("Time", "Documents")
+  dfm <- transform(dfm, date = as.numeric(as.character(Time)))
+  ymin = min(dfm$Documents)
+  ymax = max(dfm$Documents)
+
+  li <- list(1719, # Stockholm 20 januari 1719 1 juni 1719
+             1720,
+	     1723,
+	     c(1726, 1727),
+	     1731,
+	     1734, # Stockholm 14 maj 1734 14 december 1734
+	     c(1738, 1739),
+	     c(1740, 1741),
+	     1742,
+	     c(1746, 1747),
+	     c(1751, 1752),
+	     c(1755, 1756),
+	     c(1760, 1762),
+	     c(1765, 1766), # Stockholm 21 februari 1765 21 oktober 1766
+	     c(1769, 1770), # Norrköping & Stockholm 22 april 1769 5 februari 1770
+	     c(1771, 1772), # Stockholm 19 juni 1771 12 september 1772
+	     c(1778, 1779),
+	     1786,
+	     1789,
+	     1792, # Gävle 26 januari 1792 24 februari 1792         
+	     1800,
+	     c(1809, 1810))
+
+  rect_left <- c(min(na.omit(dfm$date)))
+  for (item in li) {
+    rect_left <- c(rect_left, min(item) - .5, max(item) + .5)
+  }
+  rect_left <- c(rect_left, max(na.omit(dfm$date)))
+
+  rectangles <- data.frame(
+    xmin = rect_left[-length(rect_left)],
+    xmax = rect_left[-1],
+    ymin = ymin,
+    ymax = ymax
+    )
+  rectangles$shade <- rep(c("Background", "Highlight"), length = nrow(rectangles))
+
+ cols <- c("lightgray", "darkgray")
+ bgcol <- "white"
+ rectangles$shade[rectangles$shade == "Background"] <- bgcol
+ rectangles$shade[rectangles$shade == "Highlight"] <- rep(cols, length.out = sum(rectangles$shade == "Highlight"))
+ rectangles$shade = factor(rectangles$shade)
+
+  # Draw Figure
+  theme_set(theme_bw(20))
+  p <- ggplot()
+  p <- p + geom_rect(data = rectangles, 
+       aes(xmin=xmin, xmax=xmax, ymin=ymin, ymax=ymax, fill=shade), alpha=0.8) + 
+         scale_fill_manual(values = levels(rectangles$shade)) # + guides(fill = "none") 
+  p <- p + geom_line(data = dfm, aes(x = date, y = Documents), col = "black")
+  p <- p + geom_point(data = dfm, aes(x = date, y = Documents), col = "black")
+  #p <- p + scale_x_continuous(breaks=seq(min(dfm$date), max(dfm$date), 10))
+  p <- p + scale_x_continuous(breaks=scales::pretty_breaks(n = 20))  
+  p <- p + ggtitle("Publishing activity")
+  p <- p + ylab("Documents / Year")
+  p <- p + xlab("Year")
+  p <- p + ggtitle(catal)
+  p <- p + guides(fill = "none") 
+  print(p)
+```
+
+### Book production
+
+Book production by year in Turku in Fennica and Kungliga 1640–1828 as a percentage of all books in the catalogues.
+
+```{r bookprod, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=10}
+minyear <- 1640
+maxyear <- 1828 
+df <- df0 %>% filter(!is.na(publication_place)) 
+df$myplace <- df$publication_place
+df$myplace[!df$myplace == "Turku"] <- "Other"
+
+df <- df %>%  filter(publication_decade >= minyear & publication_decade <= maxyear) %>%
+	      group_by(catalog, publication_decade, myplace) %>%
+	      summarize(n = n())
+
+pics <- list()
+for (cat in unique(df$catalog)) {
+  dfs <- subset(df, catalog == cat)
+  p <- ggplot(dfs, aes(x = publication_decade, y = n)) +
+       geom_bar(aes(fill = myplace), color = "black", stat = "identity", position = "stack") +
+       scale_fill_manual(values = c("gray", "black")) +
+       ylab("Title count") +
+       xlab("Publication decade") +
+       guides(fill = guide_legend(title = "Place")) +
+       ggtitle(cat) +
+       xlim(values = c(min(df$publication_decade), max(df$publication_decade)))
+  pics[[cat]] <- p
+}
+
+library(gridExtra)
+grid.arrange(pics[[1]], pics[[2]], nrow = 2)
+```
+
+### Kungliga / Linkoping
+
+```{r linkoping, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
+minyear <- 1640
+maxyear <- 1828
+myplace <- "Linköping"
+cat <- "Kungliga"
+df <- df0 %>% filter(publication_place == myplace) %>%
+      	      filter(catalog == cat) %>%
+              filter(publication_year >= minyear &
+	             publication_year <= maxyear)
+
+tab <- unique(df[, c("publication_year", "author", "title", "publisher")])
+write.table(tab, sep = "\t", quote = F, row.names = FALSE, file = "output.tables/Linkoping.tab")
+```
+
+[Document listing for `r paste(cat, "/", myplace, minyear, "-", maxyear, sep = " ")`](output.tables/Linkoping.tab)
+
+### Title count in Linköping
+
+```{r linkoping2, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
+p <- plot_timeline(data = df, x = "publication_decade", y = "titlecount") +
+       ylab("Title count (n)") +
+       ggtitle(paste("Title count: ", cat, "/", myplace))
+print(p)
+.```
+
+### Unique publishers in Linköping by year
+
+Never two publishers seen on the same year.
+
+```{r linkoping3, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
+dfs <- df %>% select(publication_year, publisher) %>%
+	      filter(!is.na(publisher)) %>%
+              unique %>%	      
+	      arrange(publication_year) 
+kable(dfs)
+.```
+
+### Title count per capita
+
+The historical population sizes used in this analysis are shown in this [table](https://github.com/rOpenGov/bibliographica/blob/master/inst/extdata/population_sizes_in_cities.csv).
+
+```{r percapita, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
+# Read historical population sizes
+f <- system.file("inst/extdata/population_sizes_in_cities.csv", package = "bibliographica")
+pop <- read.csv(f)
+pop <- melt(pop, "Year")
+colnames(pop) <- c("publication_decade", "publication_place", "population")
+pop <- as_data_frame(pop)
+pop$publication_place <- as.character(pop$publication_place)
+
+# Cities with population data
+cities <- setdiff(pop$publication_place, "Year")
+
+minyear <- 1640
+maxyear <- 1828
+cat <- "Kungliga"
+df <- df0 %>% filter(publication_place %in% cities) %>%
+      	      filter(catalog == cat) %>%
+              filter(publication_decade %in% pop$publication_decade) %>%
+	      select(publication_decade, publication_place) %>%	      
+	      group_by(publication_decade, publication_place) %>%
+	      summarise(n = n())
+
+# Remove special chars for compatibility (table join fails otherwise)
+pop$publication_place <- gsub("Linköping", "Linkoping", pop$publication_place)
+df$publication_place <- gsub("Linköping", "Linkoping", df$publication_place)
+
+# Join title count and population size
+dfm <- inner_join(pop, df, by = c("publication_decade", "publication_place"))
+
+# Add title count per capita
+dfm <- dfm %>% mutate(titles_per_capita = n/population)
+
+p <- ggplot(dfm, aes(x = publication_decade, y = titles_per_capita)) +
+       geom_line(aes(color = publication_place), size = 1) +
+       geom_point(aes(color = publication_place), size = 2) +
+       xlab("Publication decade") +
+       ylab("Title count per capita (n)") +
+       ggtitle("Title count per capita in selected cities") +
+       guides(color = guide_legend(title = "Place", reverse = TRUE))
+print(p)       
+```
+
 ## Session info

### 2017-01-31 inst/examples/20170125-Manuscript-FK.Rmd
analysis updates

--- 2017-01-31 inst/examples/20170125-Manuscript-FK.Rmd
@@
 
-dfs <- df %>% select(publication_year, publisher) %>% unique
-p <- plot_timeline(dfs, x = "publication_year") +
-     ylab("Publisher count (n)") + ggtitle(paste("Publisher count: ", cat, "/", myplace))
-print(p)
-
+dfs <- df %>% select(publication_year, publisher) %>%
+	      filter(!is.na(publisher)) %>%
+              unique %>%	      
+	      arrange(publication_year)
 kable(dfs)
-```
+.```
 

### 2017-01-31 inst/examples/20170125-Manuscript-FK.Rmd
analysis updates

@@
       	      filter(catalog == cat) %>%
-              filter(publication_year >= minyear &
-	             publication_year <= maxyear) #%>%
+              filter(publication_year >= minyear &#
+	             publication_year <= maxyear)
 
@@
 kable(dfs)
-.```
+```
 

### 2017-01-31 inst/examples/manuscript-krakow.Rmd
analysis updates

@@
 print(p)
-.```
+```
 

### 2017-02-02 inst/examples/20170201-manuscript.Rmd
analyses

--- 2016-07-27 inst/examples/20160715-slides-Krakow.Rmd
@@
 ```
+
+```{r init2, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE}
+# Read data
+dfo <- readRDS("df.Rds")
+
+# Analysis time window
+dfo <- dfo %>% filter(publication_year >= 1640 & publication_year <= 1911)
+
+# Calculate title length (word count)
+dfo$title_wordcount <- sapply(strsplit(as.character(dfo$title), " "), length)
+dfo$title_wordcount[is.na(dfo$title)] <- NA
+```
+
+```{r title_length, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=7, fig.width=15}
+df <- dfo %>% group_by(publication_year) %>%
+              summarize(median_title_length = median(title_wordcount),
+	      		mean_title_length = mean(title_wordcount),
+	      		n = n())
+
+p1 <- ggplot(df, aes(x = publication_year, y = mean_title_length)) +
+       geom_point(aes(size = n)) + geom_smooth() + ggtitle("Mean title word count")
+p2 <- ggplot(df, aes(x = publication_year, y = median_title_length)) +
+       geom_point(aes(size = n)) + geom_smooth() +
+       ggtitle("Median title word count")
+
+library(gridExtra)
+grid.arrange(p1, p2, nrow = 1)
+```
+
+```{r title_length_by_gatherings, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=7, fig.width=15}
+top.gatherings <- setdiff(names(top(dfo, "gatherings", 5)), "NA")
+
+df <- dfo %>% filter(gatherings %in% top.gatherings) %>%
+              group_by(publication_year, gatherings) %>%
+              summarize(mean_title_length = mean(title_wordcount),
+	      		n = n())
+
+p <- ggplot(df, aes(x = publication_year, y = mean_title_length,
+                     fill = gatherings, color = gatherings)) +
+       geom_point(aes(size = n)) +
+       geom_smooth() +
+       scale_y_log10() +
+       ggtitle("Mean title word count (top gatherings)")
+
+print(p)
+```
+
+```{r title_length_by_lang, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=7, fig.width=15}
+top.language <- setdiff(names(top(dfo, "language", 11)), "NA")
+
+df <- dfo %>% filter(language %in% top.language) %>%
+              group_by(publication_decade, language) %>%
+              summarize(mean_title_length = mean(title_wordcount),
+	      		n = n())
+
+p <- ggplot(df, aes(x = publication_decade, y = mean_title_length,
+                     fill = language, color = language)) +
+       geom_point(aes(size = n)) +
+       geom_line() +
+       #scale_y_log10() +
+       ggtitle("Mean title word count (top language)")
+
+print(p)
+```
+
+### Kungliga / Linkoping
+
+```{r linkoping, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
+minyear <- 1640
+maxyear <- 1828
+myplace <- "Linköping"
+cat <- "Kungliga"
+df <- df0 %>% filter(publication_place == myplace) %>%
+      	      filter(catalog == cat) %>%
+              filter(publication_year >= minyear &
+	             publication_year <= maxyear)
+
+tab <- unique(df[, c("publication_year", "author", "title", "publisher")])
+write.table(tab, sep = "\t", quote = F, row.names = FALSE, file = "output.tables/Linkoping.tab")
+```
+
+[Document listing for `r paste(cat, "/", myplace, minyear, "-", maxyear, sep = " ")`](output.tables/Linkoping.tab)
+
+### Title count in Linköping
+
+```{r linkoping2, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
+p <- plot_timeline(data = df, x = "publication_decade", y = "titlecount") +
+       ylab("Title count (n)") +
+       ggtitle(paste("Title count: ", cat, "/", myplace))
+print(p)
+```
+
+### Unique publishers in Linköping by year
+
+Never two publishers seen on the same year.
+
+```{r linkoping3, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
+dfs <- df %>% select(publication_year, publisher) %>%
+	      filter(!is.na(publisher)) %>%
+              unique %>%	      
+	      arrange(publication_year) 
+kable(dfs)
+```
+
+### Title count per capita
+
+The historical population sizes used in this analysis are shown in this [table](https://github.com/rOpenGov/bibliographica/blob/master/inst/extdata/population_sizes_in_cities.csv).
+
+```{r percapita, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
+# Read historical population sizes
+f <- system.file("inst/extdata/population_sizes_in_cities.csv", package = "bibliographica")
+pop <- read.csv(f)
+pop <- melt(pop, "Year")
+colnames(pop) <- c("publication_decade", "publication_place", "population")
+pop <- as_data_frame(pop)
+pop$publication_place <- as.character(pop$publication_place)
+
+# Cities with population data
+cities <- setdiff(pop$publication_place, "Year")
+
+minyear <- 1640
+maxyear <- 1828
+
+# Take cities from Kungliga except Turku
+cat <- "Kungliga"
+df1 <- df0 %>% filter(publication_place %in% setdiff(cities, "Turku")) %>%
+      	      filter(catalog == cat) %>%
+              filter(publication_decade %in% pop$publication_decade) %>%
+	      select(publication_decade, publication_place) %>%	      
+	      group_by(publication_decade, publication_place) %>%
+	      summarise(n = n())
+
+# Take cities from Fennica for Turku
+cat <- "Kungliga"
+df2 <- df0 %>% filter(publication_place %in% "Turku") %>%
+      	      filter(catalog == cat) %>%
+              filter(publication_decade %in% pop$publication_decade) %>%
+	      select(publication_decade, publication_place) %>%	      
+	      group_by(publication_decade, publication_place) %>%
+	      summarise(n = n())
+
+df <- bind_rows(df1, df2)
+
+# Remove special chars for compatibility (table join fails otherwise)
+pop$publication_place <- gsub("Linköping", "Linkoping", pop$publication_place)
+df$publication_place <- gsub("Linköping", "Linkoping", df$publication_place)
+
+# Join title count and population size
+dfm <- inner_join(pop, df, by = c("publication_decade", "publication_place"))
+
+# Add title count per capita
+dfm <- dfm %>% mutate(titles_per_capita = n/population)
+
+p <- ggplot(dfm, aes(x = publication_decade, y = titles_per_capita)) +
+       geom_line(aes(color = publication_place), size = 1) +
+       geom_point(aes(color = publication_place), size = 2) +
+       xlab("Publication decade") +
+       ylab("Title count per capita (n)") +
+       ggtitle("Title count per capita in selected cities") +
+       guides(color = guide_legend(title = "Place", reverse = TRUE))
+print(p)
+
+kable(dfm)
+```
+
+```{r abstitlecount, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
+# Take cities from Kungliga except Turku
+cat <- "Kungliga"
+df1 <- df0 %>% filter(publication_place %in% setdiff(cities, "Turku")) %>%
+      	      filter(catalog == cat) %>%
+	      group_by(publication_year, publication_place) %>%
+	      summarise(n = n(), paper = sum(paper, na.rm = TRUE))
+
+# Take cities from Fennica for Turku
+cat <- "Kungliga"
+df2 <- df0 %>% filter(publication_place %in% "Turku") %>%
+      	      filter(catalog == cat) %>%
+	      group_by(publication_year, publication_place) %>%
+	      summarise(n = n(), paper = sum(paper, na.rm = TRUE))
+
+df <- bind_rows(df1, df2)
+
+p <- ggplot(df, aes(x = publication_year, y = n)) +
+       geom_line(aes(color = publication_place), size = 1) +
+       geom_point(aes(color = publication_place), size = 2) +
+       xlab("Publication year") +
+       ylab("Title count (n)") +
+       ggtitle("Absolute title count in selected cities") +
+       guides(color = guide_legend(title = "Place", reverse = TRUE))
+print(p)
+```
+
+```{r octavo, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
+#>2) paper consumption in octavo format books
+#>in Stockholm, Turku, Uppsala, Lund, Göteborg and Linköping
+
+dfs <- filter(df, gatherings == "8vo")
+p <- ggplot(df, aes(x = publication_year, y = paper)) +
+       geom_line(aes(color = publication_place), size = 1) +
+       geom_point(aes(color = publication_place), size = 2) +
+       xlab("Publication year") +
+       ylab("Paper (sheets)") +
+       ggtitle("Paper consumption in selected cities") +
+       guides(color = guide_legend(title = "Place", reverse = TRUE))
+print(p)
+
+#>graph of average title length in words in Stockholm, Turku, Uppsala,
+#>Lund, Göteborg and Linköping. Both according to Kungliga, but if
+#>possible Turku data from Fennica.
+
+df$title_length <- nchar(df$title)
+dfs <- df %>% group_by(publication_year) %>%
+              summarise(mean_title_length = mean(title_length, na.rm = TRUE))
+
+p <- ggplot(dfs, aes(x = publication_year, y = mean_title_length)) +
+       geom_line(aes(color = publication_place), size = 1) +
+       geom_point(aes(color = publication_place), size = 2) +
+       xlab("Publication year") +
+       ylab("Title length (characters)") +
+       ggtitle("Mean title length in selected cities") +
+       guides(color = guide_legend(title = "Place", reverse = TRUE))
+print(p)
+```
+
+## Session info
+
+This document was created with the following versions:
+
+```{r sessioninfo, message=FALSE, warning=FALSE}
+sessionInfo()
+```

### 2017-02-02 inst/extras/manuscript-krakow.Rmd
analyses

--- 2017-02-01 inst/examples/manuscript-krakow.Rmd
@@
 maxyear <- 1828
+
+# Take cities from Kungliga except Turku
 cat <- "Kungliga"
-df <- df0 %>% filter(publication_place %in% cities) %>%
+df1 <- df0 %>% filter(publication_place %in% setdiff(cities, "Turku")) %>%
       	      filter(catalog == cat) %>%
@@
 	      summarise(n = n())
+
+# Take cities from Fennica for Turku
+cat <- "Kungliga"
+df2 <- df0 %>% filter(publication_place %in% "Turku") %>%
+      	      filter(catalog == cat) %>%
+              filter(publication_decade %in% pop$publication_decade) %>%
+	      select(publication_decade, publication_place) %>%	      
+	      group_by(publication_decade, publication_place) %>%
+	      summarise(n = n())
+
+df <- bind_rows(df1, df2)
 
@@
 print(p)
+
+kable(dfm)
+```
+
+```{r abstitlecount, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
+# Take cities from Kungliga except Turku
+cat <- "Kungliga"
+df1 <- df0 %>% filter(publication_place %in% setdiff(cities, "Turku")) %>%
+      	      filter(catalog == cat) %>%
+	      group_by(publication_year, publication_place) %>%
+	      summarise(n = n(), paper = sum(paper, na.rm = TRUE))
+
+# Take cities from Fennica for Turku
+cat <- "Kungliga"
+df2 <- df0 %>% filter(publication_place %in% "Turku") %>%
+      	      filter(catalog == cat) %>%
+	      group_by(publication_year, publication_place) %>%
+	      summarise(n = n(), paper = sum(paper, na.rm = TRUE))
+
+df <- bind_rows(df1, df2)
+
+p <- ggplot(df, aes(x = publication_year, y = n)) +
+       geom_line(aes(color = publication_place), size = 1) +
+       geom_point(aes(color = publication_place), size = 2) +
+       xlab("Publication year") +
+       ylab("Title count (n)") +
+       ggtitle("Absolute title count in selected cities") +
+       guides(color = guide_legend(title = "Place", reverse = TRUE))
+print(p)
+```
+
+```{r octavo, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
+#>2) paper consumption in octavo format books
+#>in Stockholm, Turku, Uppsala, Lund, Göteborg and Linköping
+
+dfs <- filter(df, gatherings == "8vo")
+p <- ggplot(df, aes(x = publication_year, y = paper)) +
+       geom_line(aes(color = publication_place), size = 1) +
+       geom_point(aes(color = publication_place), size = 2) +
+       xlab("Publication year") +
+       ylab("Paper (sheets)") +
+       ggtitle("Paper consumption in selected cities") +
+       guides(color = guide_legend(title = "Place", reverse = TRUE))
+print(p)
+
+#>graph of average title length in words in Stockholm, Turku, Uppsala,
+#>Lund, Göteborg and Linköping. Both according to Kungliga, but if
+#>possible Turku data from Fennica.
+
+df$title_length <- nchar(df$title)
+dfs <- df %>% group_by(publication_year) %>%
+              summarise(mean_title_length = mean(title_length, na.rm = TRUE))
+
+p <- ggplot(dfs, aes(x = publication_year, y = mean_title_length)) +
+       geom_line(aes(color = publication_place), size = 1) +
+       geom_point(aes(color = publication_place), size = 2) +
+       xlab("Publication year") +
+       ylab("Title length (characters)") +
+       ggtitle("Mean title length in selected cities") +
+       guides(color = guide_legend(title = "Place", reverse = TRUE))
+print(p)
+
 ```

### 2017-02-02 inst/examples/20170201-manuscript.Rmd
analyses for manuscript

@@
 #knitr::opts_chunk$set(fig.path = "slides_201606_Krakow/", dev="CairoPNG")
-knitr::opts_chunk$set(fig.path = "slides_201606_Krakow/")
+knitr::opts_chunk$set(fig.path = "20170201_manuscript/")
 

### 2017-02-02 inst/examples/20170201-manuscript.Rmd
analysis fix

@@
 # Read historical population sizes
-f <- system.file("inst/extdata/population_sizes_in_cities.csv", package = "bibliographica")
+f <- system.file("extdata/population_sizes_in_cities.csv", package = "bibliographica")
 pop <- read.csv(f)

### 2017-02-02 inst/examples/20170201-manuscript.Rmd
analysis fix

@@
 df0 <- df.full %>% filter(publication_year >= min.year & publication_year <= max.year)
+df0$title_length <- nchar(df0$title)
 ```
@@
 # Take cities from Fennica for Turku
-cat <- "Kungliga"
+cat <- "Fennica"
 df2 <- df0 %>% filter(publication_place %in% "Turku") %>%
@@
 
-dfs <- filter(df, gatherings == "8vo")
+# Take cities from Kungliga except Turku
+cat <- "Kungliga"
+df1 <- df0 %>% filter(publication_place %in% setdiff(cities, "Turku")) %>%
+      	       filter(catalog == cat & gatherings == "8vo") %>%
+	       group_by(publication_year, publication_place) %>%
+	       summarise(n = n(), paper = sum(paper, na.rm = TRUE))
+
+# Take cities from Fennica for Turku
+cat <- "Fennica"
+df2 <- df0 %>% filter(publication_place %in% "Turku") %>%
+      	       filter(catalog == cat & gatherings == "8vo") %>%
+	       group_by(publication_year, publication_place) %>%
+	       summarise(n = n(), paper = sum(paper, na.rm = TRUE))
+
+df <- bind_rows(df1, df2)
+
 p <- ggplot(df, aes(x = publication_year, y = paper)) +
@@
 
+# -----------------------------------------
+
 #>graph of average title length in words in Stockholm, Turku, Uppsala,
@@
 
-df$title_length <- nchar(df$title)
 dfs <- df %>% group_by(publication_year) %>%

### 2017-02-02 inst/examples/20170201-manuscript.Rmd
analysis fix

@@
 
+# Take cities from Kungliga except Turku
+cat <- "Kungliga"
+df1 <- df0 %>% filter(publication_place %in% setdiff(cities, "Turku")) %>%
+      	       filter(catalog == cat & gatherings == "8vo") %>%
+	       group_by(publication_year, publication_place) %>%
+	       summarise(n = n(), paper = sum(paper, na.rm = TRUE), mean_title_length = mean(title_length, na.rm = TRUE))
+
+# Take cities from Fennica for Turku
+cat <- "Fennica"
+df2 <- df0 %>% filter(publication_place %in% "Turku") %>%
+      	       filter(catalog == cat & gatherings == "8vo") %>%
+	       group_by(publication_year, publication_place) %>%
+	       summarise(n = n(), paper = sum(paper, na.rm = TRUE), mean_title_length = mean(title_length, na.rm = TRUE))
+
+df <- bind_rows(df1, df2)
+
 dfs <- df %>% group_by(publication_year) %>%

### 2017-02-02 inst/examples/20170201-manuscript.Rmd
analysis fix

--- 2017-02-02 inst/examples/20170201-manuscript.Rmd
@@
 
+### Octavo analysis
+
+Paper consumption in octavo format books in Stockholm, Turku, Uppsala,
+Lund, Göteborg and Linköping. Again Turku from Fennica, other cities
+from Kungliga.
+
 ```{r octavo, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
-#>2) paper consumption in octavo format books
-#>in Stockholm, Turku, Uppsala, Lund, Göteborg and Linköping
-
 # Take cities from Kungliga except Turku
@@
 print(p)
-
-# -----------------------------------------
-
-#>graph of average title length in words in Stockholm, Turku, Uppsala,
-#>Lund, Göteborg and Linköping. Both according to Kungliga, but if
-#>possible Turku data from Fennica.
+```
+
+Average title length in words in Stockholm, Turku, Uppsala, Lund,
+Göteborg and Linköping. According to Kungliga, except Turku from
+Fennica. For octavos only,
+
+```{r octavo2, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
+# Take cities from Kungliga except Turku
+cat <- "Kungliga"
+df1 <- df0 %>% filter(publication_place %in% setdiff(cities, "Turku")) %>%
+      	       filter(catalog == cat & gatherings == "8vo") %>%
+	       group_by(publication_year, publication_place) %>%
+	       summarise(n = n(), paper = sum(paper, na.rm = TRUE), mean_title_length = mean(title_length, na.rm = TRUE))
+
+# Take cities from Fennica for Turku
+cat <- "Fennica"
+df2 <- df0 %>% filter(publication_place %in% "Turku") %>%
+      	       filter(catalog == cat & gatherings == "8vo") %>%
+	       group_by(publication_year, publication_place) %>%
+	       summarise(n = n(), paper = sum(paper, na.rm = TRUE), mean_title_length = mean(title_length, na.rm = TRUE))
+
+df <- bind_rows(df1, df2)
 

### 2017-02-02 inst/examples/20170201-manuscript.Rmd
analysis fix

@@
 	       group_by(publication_year, publication_place) %>%
-	       summarise(n = n(), paper = sum(paper, na.rm = TRUE), mean_title_length = mean(title_length, na.rm = TRUE))
+	       summarise(n = n(), paper = sum(paper, na.rm = TRUE), 
+	         mean_title_length = mean(title_length, na.rm = TRUE))
 
@@
 	       group_by(publication_year, publication_place) %>%
-	       summarise(n = n(), paper = sum(paper, na.rm = TRUE), mean_title_length = mean(title_length, na.rm = TRUE))
+	       summarise(n = n(), paper = sum(paper, na.rm = TRUE), 
+                 mean_title_length = mean(title_length, na.rm = TRUE))
 
@@
 
-dfs <- df %>% group_by(publication_year) %>%
-              summarise(mean_title_length = mean(title_length, na.rm = TRUE))
-
-p <- ggplot(dfs, aes(x = publication_year, y = mean_title_length)) +
+p <- ggplot(df, aes(x = publication_year, y = mean_title_length)) +
        geom_line(aes(color = publication_place), size = 1) +

### 2017-02-05 inst/examples/20170201-manuscript.Rmd

@@
       	       filter(catalog == cat & gatherings == "8vo") %>%
-	       group_by(publication_year, publication_place) %>%
+	       group_by(publication_decade, publication_place) %>%
 	       summarise(n = n(), paper = sum(paper, na.rm = TRUE))
@@
 
-p <- ggplot(df, aes(x = publication_year, y = paper)) +
+p <- ggplot(df, aes(x = publication_decade, y = paper)) +
        geom_line(aes(color = publication_place), size = 1) +
@@
       	       filter(catalog == cat & gatherings == "8vo") %>%
-	       group_by(publication_year, publication_place) %>%
+	       group_by(publication_decade, publication_place) %>%
 	       summarise(n = n(), paper = sum(paper, na.rm = TRUE), 
@@
 
-p <- ggplot(df, aes(x = publication_year, y = mean_title_length)) +
+p <- ggplot(df, aes(x = publication_decade, y = mean_title_length)) +
        geom_line(aes(color = publication_place), size = 1) +

### 2017-02-13 inst/examples/20170201-manuscript.Rmd
manuscript figures

@@
 
-## From particular data to global perspective?
-
-**Idea**: Study early modern knowledge production, all of it (1470-1830)
-
-**How?** Combine library catalogues (Fennica, Kungliga, ESTC, CERL HPB database)
-
-**Important**: cleaning up the data (90% of the effort!) and considering how particular data collections (Finnish National Bibliography, English Short-Title Catalogue etc.) have been formed.
-
-**How to fail**: take worldcat or similar combination of datasets and analyse it as a whole without cleaning it up first.
-
-**Overcoming a national gaze** by focus on knowledge production through more complex cross-national network of cities
-
----
-
-### Data: bibliographic catalogues 1640-1828
-
-**Fennica** Finnish National bibliography
-
-- `r nrow(subset(df0, catalog == "Fennica" & publication_year >= 1640 & publication_year < 1828))` documents 1640-1828
-
-**Kungliga**  Swedish National bibliography
-
-- `r nrow(subset(df0, catalog == "Kungliga" & publication_year >= 1640 & publication_year < 1828))` documents 1640-1828
-
-**Why this project?**
-
-- Visible roots of the diversity of "Finnishness" reflected in knowledge production, 1640-1828
+### Fig. 1: Number of publication places per decade
+
+```{r places_per_decade, message=FALSE, warning=FALSE, fig.width=10, fig.height=3, echo=FALSE}
+library(dplyr)
+library(ggplot2)
+theme_set(theme_bw(20))
+df <- df0 %>% filter(publication_year >=1640 & publication_year <=1828) %>%
+              group_by(catalog, publication_decade) %>%
+	      summarise(n = length(unique(na.omit(publication_place))))
+p <- ggplot(df, aes(x = publication_decade, y = n, color = catalog)) + 
+       geom_point() + 
+       geom_line() + 
+       ylab("Publication places (n)") + xlab("Publication year") +
+       scale_color_manual(values = c("blue", "darkgreen")) + 
+       guides(color = guide_legend(reverse = TRUE, title = "")) +
+       ggtitle("Number of unique publication places")
+print(p)
+```
+
+---
+
+### Fig 2: Number of documents per decade
 
@@
 
-## Methods: Open data analytical ecosystem
-
-**Customized** our dedicated R packages for bibliographic analysis combine flexibility with automation
-
-**Automated** scales well with new data and unforeseen changes; a million documents cleaned up in 30 minutes
-
-**Open source** fully transparent and reproducible data analytics: https://github.com/rOpenGov/fennica
-
-**Research potential** greatly underestimated; world is full of metadata collections
-
-![Data Science Workflow](data-science.png)  
-\tiny{(Figure by Hadley Wickham)}
-
----
-
-## Preprocess & Enrich
-
-```{r, message=FALSE, warning=FALSE, echo=FALSE}
-library(bibliographica, quiet = TRUE)
-```
-
-**Clean up messy entries**
-
-```{r, message=FALSE, warning=FALSE,echo=TRUE}
-polish_physical_extent("iii-xxiv, 118, [2] p.")$pagecount
-```
-
-**Enrich data** (geocoordinates, gender, ..)
-
-```{r, message=FALSE, warning=FALSE}
-get_country("Porvoo")
-```
-
-- Parse, clean up, enrich, summarise, analyze, visualize, report..
-
----
-
-\begin{center}
-\Large{1. General trends and political events}
-\end{center}
-
----
-
-\begin{center}
-\tiny{\textcolor{gray}{General trends \& political events}}
-\end{center}
-
-### Turku as a Swedish University Town among Uppsala, Tartu and Stockholm (+ Lund & Greifswald)
-
-```{r map1, echo=FALSE, message=FALSE, warning=FALSE, fig.width=20, fig.height=4, eval=TRUE}
-library(dplyr)
-library(ggmap)
-library(ggplot2)
-library(gisfin)
-source("funcs.R")
-theme_set(get_theme_map())
-i <- 1650
-mapdata1 <- filter(df0,
-              publication_decade == i &
-              (catalog == "Kungliga" & 
-	            publication_place %in% c("Stockholm", "Uppsala",
-	                         "Greifswald", "Lund", "Tartu"))|
-	  (catalog == "Fennica" &
-	      publication_place == "Turku")) %>%
-      group_by(publication_decade, publication_place,
-	       latitude, longitude) %>%
-      summarise(n = n())
-
-mapdata <- bind_rows(mapdata1, 
-  as.data.frame(list(publication_decade = 1650, publication_place = "Lund", 
-                     latitude = 55.70293, longitude = 13.19294, n = 0)))
-
-mapdata$size <- mapdata$n
-mapdata$highlight <- rep("black", nrow(mapdata))
-mapdata$highlight[mapdata$publication_place %in% c("Turku")] <- "red"
-mapdata$highlight <- factor(mapdata$highlight)
-
-mapdata$highlight2 <- rep(1, nrow(mapdata))
-mapdata$highlight2[mapdata$publication_place %in% c("Greifswald", "Lund")] <- 9
-mapdata$highlight2 <- factor(mapdata$highlight2)
-
-region <- c(8, 40, 31, 76)
-names(region) <- c("left", "bottom", "right", "top")
-#mymap <- get_map(location=geobox(region), color = "bw", source="osm",  maptype="terrain")
-#mymap <- get_map(location=geobox(region), source="stamen", maptype = "watercolor")
-mymap <- get_map(location=geobox(region), maptype="roadmap")
-
-# Pick the investigated period (sliding window)
-# Sum up the years within this sliding window for each element    	    
-dfw <- mapdata %>%
-    	     group_by(publication_place, latitude, longitude, highlight, highlight2) %>%
-		       summarize(n = sum(size))
-dfw$size <- log10(1 + dfw$n)
-dfw$size[!dfw$highlight2 == 1] <- 0.5*max(dfw$size)
-
-# Plot map
-p <- ggmap(mymap) +
-
-        	geom_point(data = subset(dfw, highlight2 == 1),
-      	    aes(
-      	      x = longitude, 
-      	      y = latitude,
-	            size = size,
-	            shape = 1, 
-	            #shape = highlight2, 
-	            fill = highlight), 
-      	      pch = 21, stroke = 1) +
-
-        	geom_point(data = subset(dfw, !highlight2 == 1),
-      	    aes(
-      	      thickness = 10,
-      	      x = longitude, 
-      	      y = latitude,
-	            shape = 19, 
-	            #shape = highlight2, 
-	            color = highlight), 
-      	      colour = "black", 
-      	      shape = 21, # Point shape 
-      	      size = 7,   # Point size
-      	      stroke = 1.5) + # Point edge thickness
-
-	        ggtitle(i) +
-	        scale_size(range = c(2, 15)) +
-	        theme(title = element_text(size = 30), legend.position="none") +
-	        scale_fill_manual(values = c("darkgray", "red")) #+
-	        #scale_shape_manual(values = c(19,1))
-print(p)
-```
-
-Map by Stamen
-
----
-
-\begin{center}
-\tiny{\textcolor{gray}{General trends \& political events}}
-\end{center}
-
-### Publishing activity over time
-
-- 1700-1721 Great Northern War & Fennica drop during "the Great Wrath"
-- 1760-1770 Pamphleteering plays a crucial role during abolished censorship
-- 1803-1815 Napoleonic wars
-
-```{r publishingovertime, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=4, out.width="300px"}
-library(magrittr)
-library(ggplot2)
-library(dplyr)
-df2 <- df0 %>% group_by(publication_decade, catalog) %>%
-               summarise(n = n())
-df2$highlight <- rep(FALSE, nrow(df2))
-df2$highlight[df2$catalog == "Kungliga" &
-	      df2$publication_decade %in% c(1770, 1810)] <- TRUE
-df2$highlight[df2$catalog == "Fennica" &
-	      df2$publication_decade %in% c(1710, 1810)] <- TRUE
-v <- seq(1500, 1800, 100)
-theme_set(theme_bw(20))
-p1 <- ggplot(df2, aes(x = publication_decade, y = n)) +
-     geom_line(aes(color = catalog), size = 1) +
-     geom_point(aes(shape = catalog, color = catalog, size = highlight)) +
-     ylab("Title count (n)") + xlab("Publication year") +
-     #theme(legend.position = "none") +
-     scale_x_continuous(breaks = v, labels = v) +
-     scale_color_manual(values = c("blue", "darkgreen")) + 
-  	 scale_size_discrete(range = c(2, 8)) +
-     guides(color = guide_legend(reverse = TRUE), size = "none", shape = "none")
-
-df <- df0 %>% filter(catalog == "Kungliga")
-# Add indicator of the publication period
-df$period <- cut(df$publication_year,
-           breaks = c(1757, 1766, 1775, 1783),
-		 include.lowest = TRUE,
-		 right = FALSE
-		 )
-
-# Remove entries outside the investigated publication periods
-df <- df %>% filter(!is.na(period)) %>%
-	     group_by(period) %>%
-	     summarise(n = n(),
-		  paper = sum(paper, na.rm = TRUE)) %>%
-        mutate(paper.per.title = paper/n)
-
-p2 <- ggplot(df,
-       aes(x = period, y = paper.per.title)) + 
-       geom_bar(stat = "identity") +
-       scale_x_discrete(labels = c("1757-1765", "1766-1774", "1775-1783")) +
-       ylab("Paper per title") + xlab("")
-
-library(gridExtra)
-grid.arrange(p1, p2, nrow = 1)
-```
-
----
-
-\begin{center}
-\tiny{\textcolor{gray}{General trends \& political events}}
-\end{center}
-
-### Swedish knowledge production & cycles of representation
-
-An example how historical events, namely **parliamentary assemblies** in the Swedish case, have an effect on knowledge production.
-
-```{r riksdar5, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
-
-minyear <- 1700
-  maxyear <- 1800
-  catalog <- "Kungliga"
-
-library(magrittr)
-library(ggplot2)
-library(dplyr)
-library(ggplot2)
-library(reshape2)
-
-#for (catal in as.character(unique(df0$catalog))) {
-
-for (catal in "Kungliga") {
-
-  # Use timeinterval year intervals
-  dfsel = subset(df0, catalog == catal)
-
-  df <- df0
-  df = subset(df, catalog == catal)
-  df <- subset(df, publication_year >= minyear & publication_year <= maxyear)
-
-  df <- subset(dfsel, publication_year >= 1700 & publication_year < 1800 )
-
-  timeinterval <- 1
-  df$timeunit <- round(df$publication_year/timeinterval)*timeinterval
-
-  df$unity = rep(1, nrow(df))
-  publications <- tapply(df$unity, list(df$timeunit), sum)
-
-  publications[is.na(publications)] <- 0 # Set NAs to 0
-  publications <- publications/timeinterval # Instead of decadal sum, use average annual output 
-  dfm <- melt(publications) 
-  names(dfm) <- c("Time", "Documents")
-  dfm <- transform(dfm, date = as.numeric(as.character(Time)))
-  ymin = min(dfm$Documents)
-  ymax = max(dfm$Documents)
-
-  rect_left <- c(min(na.omit(dfm$date)),
-               1719-.5, 1719+.5, # Stockholm 20 januari 1719 1 juni 1719
-               1734-.5, 1734+.5, # Stockholm 14 maj 1734 14 december 1734
-               1765-.5, 1766+.5, # Stockholm 21 februari 1765 21 oktober 1766
-               1769-.5, 1770+.5, # Norrköping & Stockholm 22 april 1769 5 februari 1770
-               1771-.5, 1772+.5, # Stockholm 19 juni 1771 12 september 1772
-               1792-.5, 1792+.5, # Gävle 26 januari 1792 24 februari 1792         
-               max(na.omit(dfm$date)))
-  rectangles <- data.frame(
-    xmin = rect_left[-length(rect_left)],
-    xmax = rect_left[-1],
-    ymin = ymin,
-    ymax = ymax
-    )
-  rectangles$shade <- rep(c("Background", "Highlight"), length = nrow(rectangles))
-
- riksplace = c("Stockholm", "Stockholm", "Stockholm", "Norrköping", "Stockholm", "Gävle")
- cols = c("white", "Purple", "yellow", "orange")
- rectangles$shade[rectangles$shade == "Highlight"] = riksplace
- rectangles$shade = factor(rectangles$shade)
-
-  # Draw Figure
-  theme_set(theme_bw(20))
-  p <- ggplot()
-  p <- p + geom_rect(data = rectangles, 
-       aes(xmin=xmin, xmax=xmax, ymin=ymin, ymax=ymax, fill=shade), alpha=0.8) + 
-         scale_fill_manual(values = cols) # + guides(fill = "none") 
-  p <- p + geom_line(data = dfm, aes(x = date, y = Documents), col = "black")
-  p <- p + geom_point(data = dfm, aes(x = date, y = Documents), col = "black")
-  p <- p + scale_x_continuous(breaks=seq(min(dfm$date), max(dfm$date), 20))
-  p <- p + ggtitle("Publishing activity")
-  p <- p + ylab("Documents / Year")
-  p <- p + xlab("Year")
-  p <- p + ggtitle(paste(catal,"Riksplaces"))
-  print(p)
-}
-
-```
-
----
-
-\begin{center}
-\Large{2. Publishers in Sweden and Turku}
-\end{center}
-
----
-
-\begin{center}
-\tiny{\textcolor{gray}{Publishers in Sweden and Turku}}
-\end{center}
-
-### Turku in Sweden: proportions for title count and paper in Swedish University towns
-
-```{r comparisons, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=18, fig.height=10}
-pics <- list()
-for (catalogue in na.omit(unique(df0$catalog))) {
-
-df <- df0 %>% filter(catalog == catalogue)%>%
-        filter(publication_year >= 1640 & publication_year <= 1828)
-places <- c("Stockholm", "Uppsala", "Lund", "Greifswald", "Tartu", "Turku")
-df$publication_place[!df$publication_place %in% places] <- "Other"
-df <- subset(df, !is.na(df$publication_place))
-#df$publication_place <- factor(df$publication_place, levels = c(places, "Other"))
-library(reshape2)
-library(magrittr)
-library(dplyr)
-library(tidyr)
-
-df <- df %>% group_by(publication_decade, publication_place) %>%
-             summarise(n = n(),
-                paper = sum(paper, na.rm = TRUE),
-		       publishers = length(na.omit(unique(publisher)))
-		       )
-
-# Calculate percentages
-for (varname in c("n", "paper", "publishers")) {
-
-  df$varname <- df[[varname]]
-  dff <- df %>% select(publication_decade, publication_place, varname)
-  dff <- spread(dff, publication_place, varname, fill = 0)
-  dff[, -1] <- 100 * t(apply(dff[, -1], 1, function (x) {x/sum(x)}))
-  dff <- melt(dff, "publication_decade");
-  colnames(dff) <- c("publication_decade", "publication_place", "f")
-
-  theme_set(theme_bw(20))
-  p <- ggplot(dff, aes(x = publication_decade, y = f)) +
-     geom_bar(position = "stack", stat = "identity",
-       aes(fill = publication_place)) + 
-     xlab("Publication year") +
-     scale_fill_brewer(palette="Spectral")
-     if (varname == "n") {
-       p <- p + ggtitle(paste("Title count (", catalogue, ")", sep = "")) + 
-                ylab("Title count frequency (%)") 
-     }
-     if (varname == "paper") {
-       p <- p + ggtitle(paste("Paper (", catalogue, ")", sep = "")) +
-                ylab("Paper (%)")        
-     }
-     if (varname == "publishers") {
-       p <- p + ggtitle(paste("Publishers (", catalogue, ")", sep = "")) +
-                       ylab("Publishers (%)")
-     }     
-  p <- p + guides(fill = guide_legend(reverse = TRUE, title = ""))
-
-  pics[[paste(catalogue, varname, sep = "-")]] <- p
-
-}
-}
-library(gridExtra)
-grid.arrange(pics[[1]], pics[[2]], pics[[4]], pics[[5]], nrow = 2)
-rm(pics)
-```
-
----
-
-\begin{center}
-\tiny{\textcolor{gray}{Publishers in Sweden and Turku}}
-\end{center}
-
-### Publishers in Swedish University towns (and Finland)
-
-```{r publishers2-finland, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=7, fig.width=15}
-df <- df0
-df <- df %>%
-        filter(catalog == "Fennica") %>%
-	filter(country == "Finland" | publication_place == "Vyborg") %>%
-        filter(publication_year >= 1640 & publication_year <= 1828)
-
-# Top publication places
-library(bibliographica)
-
-top <- c("Turku", "Vaasa", "Vyborg")
-df <- df %>%	
-        filter(publication_place %in% top) %>%	
-        select(publication_decade, publication_place, publisher)
-
-npub <- unique(df) %>% group_by(publication_decade, publication_place) %>% tally()
-npub$publication_place <- factor(npub$publication_place, levels = top)
-npub.fennica <- npub
-
-df <- df0
-catalogue <- "Kungliga"
-df <- df %>%
-        filter(catalog == catalogue) %>%
-        filter(publication_year >= 1640 & publication_year <= 1828)
-
-# Selected publication places
-top <- c("Stockholm", "Lund", "Uppsala", "Greifswald", "Tartu")
-df <- df %>%	
-        filter(publication_place %in% top) %>%	
-        select(publication_decade, publication_place, publisher)
-
-npub <- unique(df) %>% group_by(publication_decade, publication_place) %>% tally()
-npub$publication_place <- factor(npub$publication_place, levels = top)
-npub.kungliga <- npub
-
-npub <- bind_rows(npub.fennica, npub.kungliga)
-
-# Order by total publishing activity
-npub$publication_place <- factor(npub$publication_place, levels = (npub %>% group_by(publication_place) %>% summarise(total = sum(n)) %>% arrange(desc(total)))$publication_place)
-npub <- npub %>% arrange(publication_place)
-
-theme_set(theme_bw(20))
-p <- ggplot(npub, aes(x = publication_decade, y = n)) +
-       geom_bar(stat = "identity", position = "stack",
-       		    aes(fill = publication_place)) + 
-       xlab("Publication year") +
-       ylab("Unique publishers (n)") +
-      scale_fill_brewer(palette="Spectral") +       
-       guides(fill = guide_legend(reverse = TRUE, title = "")) #+ 
-       #ggtitle(paste("Unique publishers in selected publication places (", catalogue, ")"))
-
-print(p)
-```
-
----
-
-\begin{center}
-\tiny{\textcolor{gray}{Publishers in Sweden and Turku}}
-\end{center}
-
-### Top publishers in Turku/Fennica
-
-```{r publishers4-fennica, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=6, fig.width=12}
-library(dplyr)
-place <- "Turku"
-catalogue = "Fennica"
-df = df0
-
-df <- df %>% filter(catalog == catalogue & publication_place == place)
-
-df <- df %>%	
-  filter(publication_year >= 1640 & publication_year <= 1828)%>%
-        select(publication_decade, publisher, paper)
-
-# Group small publishers
-# Top publishers by title count
-ntop <- 10
-top <- names(top(df, "publisher", ntop))
-df$publisher[!df$publisher %in% top] <- "Other"
-df$publisher <- factor(df$publisher, c(top, "Other"))
-
-# Title count per decade & publisher	
-npub <- df %>% group_by(publication_decade, publisher) %>% tally() %>% arrange(n)
-#npub$publisher <- factor(npub$publisher, levels = (npub %>% group_by(publisher) %>% summarise(total = sum(n)) %>% arrange(total))$publisher)
-# Sort by biggest publication decade
-#ord <- (npub %>% group_by(publisher) %>% summarise(decade = publication_decade[[which.max(n)]]) %>% arrange(decade))$publisher
-ord <- as.character((npub %>% group_by(publisher) %>% 
-                        summarise(decade = median(publication_decade)) %>% 
-                        arrange(decade))$publisher)
-npub$publisher <- factor(npub$publisher, levels = c("Other", setdiff(ord, "Other")))
-
-# TITLE COUNT
-theme_set(theme_bw(20))
-p <- ggplot(npub, aes(x = publication_decade, y = publisher)) +
-      geom_point(aes(size = n)) + 
-      #geom_line(aes(color = publisher), size = 2) +
-      #geom_smooth(aes(fill = publisher)) +
-      # geom_bar(stat = "identity", position = "stack", aes(fill = publisher)) + 
-       xlab("Year") +
-       ylab("") +
-       guides(size = guide_legend(title = "Title count (n)"))
-       #ggtitle(paste("Title count per publisher (", place, "/", catalogue, ")", sep = ""))
-print(p)
-```
-
----
-
-\begin{center}
-\Large{3. Languages and religious texts in Finland}
-\end{center}
-
----
-
-\begin{center}
-\tiny{\textcolor{gray}{Languages \& religious texts in Finland}}
-\end{center}
-
-### Different languages in Turku, Stockholm, Uppsala and Lund
-
-```{r language-perc2, echo=FALSE, message=FALSE, warning=FALSE, fig.width=20, fig.height=12}
-pics <- list()
-theme_set(theme_bw(20))
-myplaces <- c("Turku", "Greifswald", "Stockholm", "Uppsala", "Lund")
-
-for (catalogue in c("Fennica", "Kungliga")) {
-
-  df <- df0 %>% filter(catalog == catalogue) %>%
-        filter(publication_year >= 1600 & publication_year <= 1828)
-
-  langs <- c("Finnish", "Swedish", "Latin", "German",
-           "Russian", "French", "Hebrew", "Other")
-
-  lang <- paste("language.", langs, sep = "")
-  otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
-  otherlang <- otherlang[otherlang!="language.Multiple languages"]
-
-  df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
-
-  dfl <- NULL
-  for (lan in lang) {
-
-    # Classify a document to the specifed language
-    # If document is assigned with languages, each case is considered
-    # so one doc may have multiple entries corresponding to different languages
-    # mean(rowSums(df[, lang]) == 1) # 93% Fennica docs have just 1 language
-    # Combine data frames for specified languages
-    dflsub <- filter(df, df[[lan]])
-    if (nrow(dflsub) > 0) {
-      dflsub$language <- gsub("language.", "", lan)
-      dfl <- bind_rows(dfl, dflsub)
-    }
-  }
-
-  df <- dfl %>% group_by(publication_decade, publication_place, language) %>%
-     	     summarise(n = n())
-
-  # Calculate percentages
-  dff <- spread(df, language, n, fill = 0)
-  dff[, -c(1,2)] <- 100 * t(apply(dff[, -c(1,2)], 1, function (x) {x/sum(x)}))
-
-  dff <- melt(dff, id = c("publication_place", "publication_decade"))
-  colnames(dff) <- c("publication_place", "publication_decade", "language", "f")
-
-  for (myplace in myplaces) {
-    p <- ggplot(subset(dff, publication_place == myplace), aes(x = publication_decade, y = f)) +
-      geom_bar(position = "stack", stat = "identity", aes(fill = language)) + 
-      xlab("Publication year") +
-      ylab("Title count frequency (%)") +
-      #ggtitle(paste("Languages (", myplace, "/", catalogue, ")", sep = "")) +
-      ggtitle(paste(myplace, "/", catalogue)) +
-      scale_fill_brewer(palette="Spectral") + 
-      guides(fill = guide_legend(reverse = TRUE, title = ""))
-    pics[[paste(catalogue, myplace, sep = "-")]] <- p
-  }
-}
-
-grid.arrange(pics[[1]],
-             pics[[8]], pics[[9]], pics[[10]], 
-             nrow = 2)
-
-rm(pics)
-```
-
----
-
-\begin{center}
-\tiny{\textcolor{gray}{Languages \& religious texts in Finland}}
-\end{center}
-
-### Topic richness per language (publications in Fennica)
-
-```{r topics232, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, fig.show="hold"}
-catalogue <- "Fennica"
-df <- filter(df0, catalog == "Fennica") %>%
-  filter(publication_year >= 1640 & publication_year <= 1828) %>%
-  select(publication_year, language, subject_topic)
-df <- unique(df)
-df <- df %>% group_by(publication_year, language) %>%
-             summarise(n = length(unique(unlist(strsplit(subject_topic, ";")))))
-
-langs2 <- c("Finnish", "Swedish", "Latin", "Other")
-df$language[!df$language %in% langs2] <- "Other"
-df$language <- factor(df$language, levels = langs2)
-
-p <- ggplot(df, aes(x = publication_year, y = n, color = language)) +
-       geom_line() + geom_point() + 
-       geom_smooth(aes(fill = language, color = language)) + 
-       ylab("Documents (n)") + xlab("Publication year")
-
-print(p)
-```
-
----
-
-\begin{center}
-\tiny{\textcolor{gray}{Languages \& religious texts in Finland}}
-\end{center}
-
-### Devotional literature (catechisms, hymns, prayers, etc.)
-
-Form of literature denoting the advancement of reading in Finland in the 19th century. It has been unclear when devotional literature  shows up as a relevant category.
-
-```{r topics12122, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, fig.show="hold"}
-sel <- c("virret","arkkiveisut","hartauskirjat","katekismukset","rukouspäivät","saarnat","aapiset","rukoukset","rukous","hengelliset laulut","hartauspuheet","virsikirjat")
-catalogue <- "Fennica"
-
-  # Selected catalogue with selected years
-  df <- filter(df0, catalog == catalogue &
-     		    publication_year >= 1640 &
-		    publication_year <= 1828)
-
-  # Selected topics
-  df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)  
-  df <- df %>% filter(catalog == catalogue & hit)
-
-  lang <- paste("language.", langs, sep = "")
-  otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
-  df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
-  dfl <- NULL
-  for (lan in lang) {
-    # Classify a document to the specifed language
-    # If document is assigned with languages, each case is considered
-    # so one doc may have multiple entries corresponding to different languages
-    # mean(rowSums(df[, lang]) == 1) # 93% Fennica docs have just 1 language
-    # Combine data frames for specified languages
-    dflsub <- filter(df, df[[lan]])
-    if (nrow(dflsub) > 0) {
-      dflsub$language <- gsub("language.", "", lan)
-      dfl <- bind_rows(dfl, dflsub)
-    }
-  }
-  df <- dfl %>% group_by(publication_decade, language) %>%
-             summarise(n = n(),
-	               paper = sum(paper, na.rm = TRUE))
-
-  # PAPER CONSUMPTION
-  theme_set(theme_bw(20))
-  p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
-       geom_point(aes(col = language, shape = language), size = 5) +
-       geom_line(aes(col = language, shape = language)) +       
-       #geom_smooth(aes(fill = language, color = language)) + 
-       xlab("Publication year") +
-       ylab("Paper consumption") +
-       ggtitle(paste("Devotional Literature (", catalogue, ")", sep = ""))
-       #ggtitle(paste("Devotional literature" (", catalogue, ")", sep = "")) 
-  print(p)
-```
-
----
-
-\begin{center}
-\tiny{\textcolor{gray}{Languages \& religious texts in Finland}}
-\end{center}
-
-### Temporary sermons in Latin and Swedish
-
-- Important role in early modern knowledge production. Language of temporary sermons in contrast to devotional literature has not been analysed in Finland (and Sweden).
-
-```{r topics882, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6}
-  sel <- c("hautajaiset", "häät", "juhlamenot")
-  catalogue <- "Fennica"
-  df <- df0
-  df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)
-
-  # Selected catalogue with selected topics
-  df <- df %>% filter(catalog == catalogue & hit)
-  lang <- paste("language.", langs, sep = "")
-  otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
-  otherlang <- otherlang[otherlang!="language.Multiple languages"]
-  df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
-
-  dfl <- NULL
-  for (lan in lang) {
-    # Classify a document to the specifed language
-    # If document is assigned with languages, each case is considered
-    # so one doc may have multiple entries corresponding to different languages
-    # mean(rowSums(df[, lang]) == 1) # 93% Fennica docs have just 1 language
-    # Combine data frames for specified languages
-    dflsub <- filter(df, df[[lan]])
-    if (nrow(dflsub) > 0) {
-      dflsub$language <- gsub("language.", "", lan)
-    dfl <- bind_rows(dfl, dflsub)
-  }
-}
-dfl$language <- factor(dfl$language, levels = langs)
-
-  df <- dfl %>% group_by(publication_decade, language) %>%
-             summarise(n = n(),
-	               paper = sum(paper, na.rm = TRUE))
-
-  # PAPER CONSUMPTION
-  p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
-       geom_point(aes(col = language, shape = language), size = 5) +
-       geom_line(aes(col = language, shape = language)) +       
-       xlab("Publication year") +
-       ylab("Paper consumption") +
-       ggtitle(paste("Temporary Sermons (", catalogue, ")", sep = ""))
-  print(p)
-```
-
----
-
-\begin{center}
-\Large{4. University curriculum and Enlightenment in Finland}
-\end{center}
-
----
-
-\begin{center}
-\tiny{\textcolor{gray}{University curriculum \& Enlightenment in Finland}}
-\end{center}
-
-### Dissertation languages in Turku 1640-1828
-
-```{r disslang, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
-catalogue <- "Fennica"
-langs <- c("Finnish", "Swedish", "Latin", "German",
-           "Russian", "French", "Hebrew", "Other")
-
-df <- df0 %>%
-        filter(catalog == catalogue) %>%
-        filter(publication_year >= 1640 & publication_year <= 1828) %>%
-	filter(dissertation)
-
-lang <- paste("language.", langs, sep = "")
-otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
-otherlang <- otherlang[otherlang!="language.Multiple languages"]
-
-df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
-
-dfl <- NULL
-for (lan in lang) {
-
-  # Classify a document to the specifed language
-  # If document is assigned with languages, each case is considered
-  # so one doc may have multiple entries corresponding to different languages
-  # mean(rowSums(df[, lang]) == 1) # 93% Fennica docs have just 1 language
-  # Combine data frames for specified languages
-  dflsub <- filter(df, df[[lan]])
-  if (nrow(dflsub)>0) {
-    dflsub$language <- gsub("language.", "", lan)
-    dfl <- bind_rows(dfl, dflsub)
-  }
-}
-
-df <- dfl %>% group_by(publication_decade, language) %>%
-     	     summarise(n = n())
-
-# Calculate percentages
-dff <- spread(df, language, n, fill = 0)
-dff[, -1] <- 100 * t(apply(dff[, -1], 1, function (x) {x/sum(x)}))
-dff <- melt(dff, "publication_decade");
-colnames(dff) <- c("publication_decade", "language", "f")
-
-# Order by language counts
-dff$language <- factor(dff$language,
-   levels = (df %>% group_by(language) %>%
-                    summarise(total = sum(n)) %>%
-		    arrange(total))$language);
-dff <- dff %>% arrange(desc(language))
-
-theme_set(theme_bw(20))
-p <- ggplot(dff, aes(x = publication_decade, y = f)) +
-     geom_bar(position = "stack", stat = "identity", aes(fill = language)) + 
-     xlab("Publication year") +
-     ylab("Title count frequency (%)") +
-     ggtitle(paste("Dissertation languages (", catalogue, ")", sep = "")) +
-     scale_fill_brewer(palette="Spectral")
-print(p)
-```
-
----
-
-\begin{center}
-\tiny{\textcolor{gray}{University curriculum \& Enlightenment in Finland}}
-\end{center}
-
-### Printing by topics in different languages in Turku
-
-```{r topics-103B, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=8}
-sel = c("filosofia","luonnonfilosofia","metafysiikka","logiikka")
-df = dfl
-df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)  
-df <- df %>% filter(hit)
-df <- df %>% group_by(publication_decade, language) %>%
-             summarise(n = n(),
-                 paper = sum(paper, na.rm = TRUE))
-
-# PAPER CONSUMPTION
-p1 <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
-       geom_bar(aes(fill = language), position = "stack", stat = "identity") +                     
-       xlab("Publication year") +
-       ylab("Paper") +
-       guides(fill = guide_legend(reverse = TRUE, title = "")) +
-       ggtitle("Philosophy")
-
-sel = c("oppihistoria","antiikki","historia")
-# Selected catalogue with selected topics
-df = dfl
-df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)  
-df <- df %>% filter(hit)
-df <- df %>% group_by(publication_decade, language) %>%
-             summarise(n = n(),
-	               paper = sum(paper, na.rm = TRUE))
-
-# PAPER CONSUMPTION
-p2 <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
-       geom_bar(aes(fill = language), position = "stack", stat = "identity") +             
-       xlab("Publication year") +
-       ylab("Paper") +
-       guides(fill = guide_legend(reverse = TRUE, title = "")) +
-       ggtitle("History")
-
-sel =   c("psykologia","yhteiskuntafilosofia","valtiofilosofia","talous","raha","moraali","velvollisuudet","kasvatus","maanviljely","maatalous","kalastus")
-
-# Selected catalogue with selected topics
-df = dfl
-df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)  
-df <- df %>% filter(hit)
-df <- df %>% group_by(publication_decade, language) %>%
-             summarise(n = n(),
-	               paper = sum(paper, na.rm = TRUE))
-
-# PAPER CONSUMPTION
-theme_set(theme_bw(20))
-p3 <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
-       geom_bar(aes(fill = language), position = "stack", stat = "identity") +              
-       xlab("Publication year") +
-       ylab("Paper") +
-       guides(fill = guide_legend(reverse = TRUE, title = "")) +
-       ggtitle("Economy")
-grid.arrange(p1, p2, p3, nrow = 3)
-```
-
----
-
-\begin{center}
-\tiny{\textcolor{gray}{University curriculum \& Enlightenment in Finland}}
-\end{center}
-
-### Rise of the octavo sized book as vehicle of Enlightenment
+### Fig 3: Rise of the octavo sized book as vehicle of Enlightenment
 
@@
 
-```{r LIBER-13, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=11, fig.height=9, fig.show="hold", out.width="160px"}
+```{r LIBER-13, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=11, fig.height=9, fig.show="hold"}
 for (catal in unique(df0$catalog)) {
@@
 
-##Thanks !
-
-Institutional support:
-
-- Academy of Finland
-- University of Helsinki
-- Digitalia / The Regional Council of South Savo
-
-Data providers:
-
-- National Library of Finland
-- National Library of Sweden
-
-Code infrastructure:
-
-- Github
-- R project
-
-For more info, see:
-
-- \textcolor{blue}{https://github.com/rOpenGov/fennica}
-
-\begin{figure}
-\begin{tabular}{cccccc}
-\includegraphics[width=2cm,height=2cm]{aka.png}&
-\includegraphics[width=1cm,height=1cm]{HY-CC.png}&
-\includegraphics[width=1cm,height=1cm]{kansalliskirjasto.png}&
-\includegraphics[width=1cm,height=1cm]{kungliga.png}&
-\includegraphics[width=1cm,height=1cm]{github-logo.png}&
-\includegraphics[width=1cm,height=1cm]{Rlogo.png}
-\end{tabular}
-\end{figure}
-
----
-
-### Duplicate publications in Fennica/Kungliga
-
-```{r duplicates, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=5, fig.width=10}
-df <- df.combined.preprocessed %>%
-        filter(publication_year >= 1640 & publication_year <=1828) %>%
-        group_by(catalog, publication_decade) %>%
-	summarise(duplicates = 100 * mean(remove))
-
-p <- ggplot(df, aes(x = publication_decade, y = duplicates, fill = catalog)) +
-       geom_bar(position = "dodge", stat = "identity") +
-       ylab("Duplicates (%)") +
-       scale_fill_manual(values = c("blue", "red")) 
-       #ggtitle(paste("Certain duplicates Fennica-Kungliga", paste(range(na.omit(df$publication_decade)), collapse = "-")))
-
-print(p)
-```
-
-```{r init2, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE}
-# Read data
-dfo <- readRDS("df.Rds")
+### Fig 4: Average title length (word count)
+
+```{r title_length_by_lang, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=7, fig.width=15}
+dfo <- df0
 
@@
 dfo$title_wordcount[is.na(dfo$title)] <- NA
-```
-
-```{r title_length, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=7, fig.width=15}
-df <- dfo %>% group_by(publication_year) %>%
-              summarize(median_title_length = median(title_wordcount),
-	      		mean_title_length = mean(title_wordcount),
-	      		n = n())
-
-p1 <- ggplot(df, aes(x = publication_year, y = mean_title_length)) +
-       geom_point(aes(size = n)) + geom_smooth() + ggtitle("Mean title word count")
-p2 <- ggplot(df, aes(x = publication_year, y = median_title_length)) +
-       geom_point(aes(size = n)) + geom_smooth() +
-       ggtitle("Median title word count")
-
-library(gridExtra)
-grid.arrange(p1, p2, nrow = 1)
-```
-
-```{r title_length_by_gatherings, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=7, fig.width=15}
-top.gatherings <- setdiff(names(top(dfo, "gatherings", 5)), "NA")
-
-df <- dfo %>% filter(gatherings %in% top.gatherings) %>%
-              group_by(publication_year, gatherings) %>%
-              summarize(mean_title_length = mean(title_wordcount),
-	      		n = n())
-
-p <- ggplot(df, aes(x = publication_year, y = mean_title_length,
-                     fill = gatherings, color = gatherings)) +
-       geom_point(aes(size = n)) +
-       geom_smooth() +
-       scale_y_log10() +
-       ggtitle("Mean title word count (top gatherings)")
-
-print(p)
-```
-
-```{r title_length_by_lang, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=7, fig.width=15}
+
 top.language <- setdiff(names(top(dfo, "language", 11)), "NA")
@@
 
-### Kungliga / Linkoping
-
-```{r linkoping, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
-minyear <- 1640
+---
+
+### Fig 5: Turku in Sweden: proportions for title count and paper in Swedish University towns
+
+```{r comparisons, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=18, fig.height=10}
+pics <- list()
+for (catalogue in na.omit(unique(df0$catalog))) {
+
+df <- df0 %>% filter(catalog == catalogue)%>%
+        filter(publication_year >= 1640 & publication_year <= 1828)
+places <- c("Stockholm", "Uppsala", "Lund", "Greifswald", "Tartu", "Turku")
+df$publication_place[!df$publication_place %in% places] <- "Other"
+df <- subset(df, !is.na(df$publication_place))
+#df$publication_place <- factor(df$publication_place, levels = c(places, "Other"))
+library(reshape2)
+library(magrittr)
+library(dplyr)
+library(tidyr)
+
+df <- df %>% group_by(publication_decade, publication_place) %>%
+             summarise(n = n(),
+                paper = sum(paper, na.rm = TRUE),
+		       publishers = length(na.omit(unique(publisher)))
+		       )
+
+# Calculate percentages
+for (varname in c("n", "paper", "publishers")) {
+
+  df$varname <- df[[varname]]
+  dff <- df %>% select(publication_decade, publication_place, varname)
+  dff <- spread(dff, publication_place, varname, fill = 0)
+  dff[, -1] <- 100 * t(apply(dff[, -1], 1, function (x) {x/sum(x)}))
+  dff <- melt(dff, "publication_decade");
+  colnames(dff) <- c("publication_decade", "publication_place", "f")
+
+  theme_set(theme_bw(20))
+  p <- ggplot(dff, aes(x = publication_decade, y = f)) +
+     geom_bar(position = "stack", stat = "identity",
+       aes(fill = publication_place)) + 
+     xlab("Publication year") +
+     scale_fill_brewer(palette="Spectral")
+     if (varname == "n") {
+       p <- p + ggtitle(paste("Title count (", catalogue, ")", sep = "")) + 
+                ylab("Title count frequency (%)") 
+     }
+     if (varname == "paper") {
+       p <- p + ggtitle(paste("Paper (", catalogue, ")", sep = "")) +
+                ylab("Paper (%)")        
+     }
+     if (varname == "publishers") {
+       p <- p + ggtitle(paste("Publishers (", catalogue, ")", sep = "")) +
+                       ylab("Publishers (%)")
+     }     
+  p <- p + guides(fill = guide_legend(reverse = TRUE, title = ""))
+
+  pics[[paste(catalogue, varname, sep = "-")]] <- p
+
+}
+}
+library(gridExtra)
+grid.arrange(pics[[1]], pics[[2]], pics[[4]], pics[[5]], nrow = 2)
+rm(pics)
+```
+
+---
+
+### Fig 6: Publishing activity over time
+
+```{r publishingovertime, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=4, out.width="300px"}
+library(magrittr)
+library(ggplot2)
+library(dplyr)
+v <- seq(1500, 1800, 100)
+theme_set(theme_bw(20))
+df <- df0 %>% filter(catalog == "Kungliga")
+
+# Add indicator of the publication period
+df$period <- cut(df$publication_year,
+           breaks = c(1757, 1766, 1775, 1783),
+		 include.lowest = TRUE,
+		 right = FALSE
+		 )
+
+# Remove entries outside the investigated publication periods
+df.all <- df %>% filter(!is.na(period)) %>%
+	     group_by(period) %>%
+	     summarise(n = n(),
+		  paper = sum(paper, na.rm = TRUE)) %>%
+        mutate(paper.per.title = paper/n)
+
+# Remove entries outside the investigated publication periods
+df.cities <- df %>% filter(!is.na(period)) %>%
+	     group_by(period, publication_place) %>%
+	     summarise(n = n(),
+		  paper = sum(paper, na.rm = TRUE)) %>%
+        mutate(paper.per.title = paper/n)
+
+df.all$publication_place <- "All"
+df <- bind_rows(df.all, df.cities) %>%
+        filter(publication_place %in% c("Stockholm", "Uppsala", "Lund", "All"))
+
+p <- ggplot(df,
+       aes(fill = period, y = paper.per.title, x = publication_place)) + 
+       geom_bar(stat = "identity", color = "black", position = "dodge") +
+       #scale_x_discrete(labels = c("1757-1765", "1766-1774", "1775-1783")) +
+       guides(fill = guide_legend(title = "Period")) +
+       ylab("Paper (sheets)") + xlab("") +
+       ggtitle("Paper consumption per title")
+
+print(p)
+```
+
+---
+
+### Fig. 7: Riksdagar Kungliga
+
+```{r riksdar_kungliga, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
+
+minyear <- 1700
+maxyear <- 1800
+catal <- "Kungliga"
+
+library(magrittr)
+library(ggplot2)
+library(dplyr)
+library(ggplot2)
+library(reshape2)
+
+  # Use timeinterval year intervals
+  dfsel = subset(df0, catalog == catal)
+
+  df <- df0
+  df = subset(df, catalog == catal)
+  df <- subset(df, publication_year >= minyear & publication_year <= maxyear)
+
+  df <- subset(dfsel, publication_year >= 1700 & publication_year < 1831 )
+
+  timeinterval <- 1
+  df$timeunit <- round(df$publication_year/timeinterval)*timeinterval
+
+  df$unity = rep(1, nrow(df))
+  publications <- tapply(df$unity, list(df$timeunit), sum)
+
+  publications[is.na(publications)] <- 0 # Set NAs to 0
+  publications <- publications/timeinterval # Instead of decadal sum, use average annual output 
+  dfm <- melt(publications) 
+  names(dfm) <- c("Time", "Documents")
+  dfm <- transform(dfm, date = as.numeric(as.character(Time)))
+  ymin = min(dfm$Documents)
+  ymax = max(dfm$Documents)
+
+  rect_left <- c(min(na.omit(dfm$date)),
+               1710-.5, 1710+.5, #
+               1713-.5, 1714+.5, #
+
+               1719-.5, 1719+.5, # Stockholm 20 januari 1719 1 juni 1719
+               1734-.5, 1734+.5, # Stockholm 14 maj 1734 14 december 1734
+               1765-.5, 1766+.5, # Stockholm 21 februari 1765 21 oktober 1766
+               1769-.5, 1770+.5, # Norrköping & Stockholm 22 april 1769 5 februari 1770
+               1771-.5, 1772+.5, # Stockholm 19 juni 1771 12 september 1772
+
+               1778-.5, 1779+.5, #
+               1786-.5, 1786+.5, #
+               1789-.5, 1789+.5, #
+
+               1792-.5, 1792+.5, # Gävle 26 januari 1792 24 februari 1792
+
+               1800-.5, 1800+.5, #
+               1809-.5, 1810+.5, #
+               1812-.5, 1812+.5, #
+               1815-.5, 1815+.5, #
+               1817-.5, 1818+.5, #
+               1823-.5, 1823+.5, #
+               1828-.5, 1830+.5, #
+
+               max(na.omit(dfm$date)))
+  rectangles <- data.frame(
+    xmin = rect_left[-length(rect_left)],
+    xmax = rect_left[-1],
+    ymin = ymin,
+    ymax = ymax
+    )
+
+  rectangles$shade <- rep(c("Background", "Highlight"), length = nrow(rectangles))
+
+  riksplace <- c(rep("Unknown", 2), "Stockholm", "Stockholm", "Stockholm", "Norrköping", "Stockholm", rep("Unknown", 3), "Gävle", rep("Unknown", 7))
+  #cols <- c("white", "Purple", "yellow", "orange", "darkgray")
+  cols <- c("white", "gray", "darkgray")
+  rectangles$place <- rectangles$shade
+  rectangles$place[rectangles$place == "Highlight"] <- riksplace
+  rectangles$place[rectangles$place == "Background"] <- "" 
+  rectangles$shade <- factor(rectangles$shade)
+
+  # Draw Figure
+  theme_set(theme_bw(20))
+  p <- ggplot() +
+         geom_rect(data = rectangles, 
+           aes(xmin=xmin, xmax=xmax,
+	       ymin=ymin, ymax=ymax,
+	       fill=shade), alpha=0.8) +
+         scale_fill_manual(values = cols) +
+	 guides(fill = "none")
+
+  p <- p + geom_text(data = rectangles, angle = 90, aes(x=xmin + .5, y=.9*ymax, label=place), size = 6)
+
+  p <- p + geom_line(data = dfm, aes(x = date, y = Documents), col = "black")
+  p <- p + geom_point(data = dfm, aes(x = date, y = Documents), col = "black")
+  p <- p + scale_x_continuous(breaks=seq(min(dfm$date), max(dfm$date), 10))
+  p <- p + ggtitle("Publishing activity")
+  p <- p + ylab("Documents / Year")
+  p <- p + xlab("Year")
+  p <- p + ggtitle(paste(catal,"Riksplaces"))
+  print(p)
+
+```
+
+---
+
+### Fig. 8: Riksdagar Fennica
+
+```{r riksdar_fennica, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
+minyear <- 1760
+maxyear <- 1860
+catal <- "Fennica"
+
+df00 <- df.full %>% filter(publication_year >= minyear & publication_year <= maxyear)
+
+library(magrittr)
+library(ggplot2)
+library(dplyr)
+library(ggplot2)
+library(reshape2)
+
+  # Use timeinterval year intervals
+  dfsel <- subset(df00, catalog == catal)
+
+  df <- df00
+  df <- subset(df, catalog == catal)
+  df <- subset(df, publication_year >= minyear & publication_year <= maxyear)
+  df <- subset(dfsel, publication_year >= minyear & publication_year <= maxyear)
+
+  timeinterval <- 1
+  df$timeunit <- round(df$publication_year/timeinterval)*timeinterval
+
+  df$unity <- rep(1, nrow(df))
+  publications <- tapply(df$unity, list(df$timeunit), sum)
+
+  publications[is.na(publications)] <- 0 # Set NAs to 0
+  publications <- publications/timeinterval # Instead of decadal sum, use average annual output 
+  dfm <- melt(publications) 
+  names(dfm) <- c("Time", "Documents")
+  dfm <- transform(dfm, date = as.numeric(as.character(Time)))
+  ymin <- min(dfm$Documents)
+  ymax <- max(dfm$Documents)
+
+  rect_left <- c(min(na.omit(dfm$date)),
+               1710-.5, 1710+.5, #
+               1713-.5, 1714+.5, #
+
+               1719-.5, 1719+.5, # Stockholm 20 januari 1719 1 juni 1719
+               1734-.5, 1734+.5, # Stockholm 14 maj 1734 14 december 1734
+               1765-.5, 1766+.5, # Stockholm 21 februari 1765 21 oktober 1766
+               1769-.5, 1770+.5, # Norrköping & Stockholm 22 april 1769 5 februari 1770
+               1771-.5, 1772+.5, # Stockholm 19 juni 1771 12 september 1772
+
+               1778-.5, 1779+.5, #
+               1786-.5, 1786+.5, #
+               1789-.5, 1789+.5, #
+
+               1792-.5, 1792+.5, # Gävle 26 januari 1792 24 februari 1792
+
+               1800-.5, 1800+.5, #
+               1809-.5, 1810+.5, #
+               1812-.5, 1812+.5, #
+               1815-.5, 1815+.5, #
+               1817-.5, 1818+.5, #
+               1823-.5, 1823+.5, #
+               1828-.5, 1830+.5, #
+
+               max(na.omit(dfm$date)))
+
+  rectangles <- data.frame(
+    xmin = rect_left[-length(rect_left)],
+    xmax = rect_left[-1],
+    ymin = ymin,
+    ymax = ymax
+    )
+
+  rectangles$shade <- rep(c("Background", "Highlight"),
+  		          length = nrow(rectangles))
+
+  riksplace <- c(rep("Unknown", 2), "Stockholm", "Stockholm", "Stockholm", "Norrköping", "Stockholm", rep("Unknown", 3), "Gävle", rep("Unknown", 7))
+  cols <- c("white", "gray", "darkgray")
+  rectangles$place <- rectangles$shade
+  rectangles$place[rectangles$place == "Highlight"] <- riksplace
+  rectangles$place[rectangles$place == "Background"] <- "" 
+  rectangles$shade <- factor(rectangles$shade)
+
+  # Draw Figure
+  theme_set(theme_bw(20))
+  p <- ggplot() +
+         geom_rect(data = rectangles, 
+           aes(xmin=xmin, xmax=xmax,
+	       ymin=ymin, ymax=ymax,
+	       fill=shade), alpha=0.8) +
+         scale_fill_manual(values = cols) +
+	 guides(fill = "none")
+
+  p <- p + geom_text(data = rectangles, angle = 90, aes(x=xmin + .5, y=.9*ymax, label=place), size = 6)
+
+  p <- p + geom_line(data = dfm, aes(x = date, y = Documents), col = "black")
+  p <- p + geom_point(data = dfm, aes(x = date, y = Documents), col = "black")
+  p <- p + scale_x_continuous(breaks=seq(min(dfm$date), max(dfm$date), 10))
+  p <- p + ggtitle("Publishing activity")
+  p <- p + ylab("Documents / Year")
+  p <- p + xlab("Year")
+  p <- p + ggtitle(paste(catal))
+  p <- p + xlim(c(minyear, maxyear))
+  print(p)
+```
+
+---
+
+### Fig 9A: Fennica - Publishers in Swedish University towns (and Finland)
+
+```{r publishers2-finland, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=7, fig.width=15}
+df <- df0
+catal <- "Fennica"
+df <- df %>%
+        filter(catalog == catal) %>%
+	filter(country == "Finland" | publication_place == "Vyborg") %>%
+        filter(publication_year >= 1640 & publication_year <= 1828)
+
+# Top publication places
+library(bibliographica)
+
+top <- c("Turku", "Vaasa", "Vyborg")
+df <- df %>%	
+        filter(publication_place %in% top) %>%	
+        select(publication_decade, publication_place, publisher)
+
+npub <- unique(df) %>% group_by(publication_decade, publication_place) %>% tally()
+npub$publication_place <- factor(npub$publication_place, levels = top)
+npub.fennica <- npub
+
+df <- df0
+catalogue <- "Kungliga"
+df <- df %>%
+        filter(catalog == catalogue) %>%
+        filter(publication_year >= 1640 & publication_year <= 1828)
+
+# Selected publication places
+top <- c("Stockholm", "Lund", "Uppsala", "Greifswald", "Tartu")
+df <- df %>%	
+        filter(publication_place %in% top) %>%	
+        select(publication_decade, publication_place, publisher)
+
+npub <- unique(df) %>% group_by(publication_decade, publication_place) %>% tally()
+npub$publication_place <- factor(npub$publication_place, levels = top)
+npub.kungliga <- npub
+
+npub <- bind_rows(npub.fennica, npub.kungliga)
+
+# Order by total publishing activity
+npub$publication_place <- factor(npub$publication_place, levels = (npub %>% group_by(publication_place) %>% summarise(total = sum(n)) %>% arrange(desc(total)))$publication_place)
+npub <- npub %>% arrange(publication_place)
+npub$publication_place <- factor(npub$publication_place, levels = rev(unique(npub$publication_place)))
+
+theme_set(theme_bw(20))
+p <- ggplot(npub, aes(x = publication_decade, y = n)) +
+       geom_bar(stat = "identity", position = "stack",
+       		    aes(fill = publication_place)) + 
+       xlab("Publication year") +
+       ylab("Unique publishers (n)") +
+       scale_fill_brewer(palette="Spectral") +       
+       guides(fill = guide_legend(reverse = FALSE, title = "")) +
+       ggtitle(catal)       
+       #ggtitle(paste("Unique publishers in selected publication places (", catalogue, ")"))
+
+print(p)
+
+```
+
+### Fig 9B: Kungliga - Publishers in Swedish University towns (and Finland)
+
+```{r kungliga9b, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=7, fig.width=15}
+df <- df0
+catal <- "Kungliga"
+df <- df %>%
+        filter(catalog == catal) %>%
+	filter(country == "Finland" | publication_place == "Vyborg") %>%
+        filter(publication_year >= 1640 & publication_year <= 1828)
+
+# Top publication places
+library(bibliographica)
+
+top <- c("Turku", "Vaasa", "Vyborg")
+df <- df %>%	
+        filter(publication_place %in% top) %>%	
+        select(publication_decade, publication_place, publisher)
+
+npub <- unique(df) %>% group_by(publication_decade, publication_place) %>% tally()
+npub$publication_place <- factor(npub$publication_place, levels = top)
+npub.fennica <- npub
+
+df <- df0
+catalogue <- "Kungliga"
+df <- df %>%
+        filter(catalog == catalogue) %>%
+        filter(publication_year >= 1640 & publication_year <= 1828)
+
+# Selected publication places
+top <- c("Stockholm", "Lund", "Uppsala", "Greifswald", "Tartu")
+df <- df %>%	
+        filter(publication_place %in% top) %>%	
+        select(publication_decade, publication_place, publisher)
+
+npub <- unique(df) %>% group_by(publication_decade, publication_place) %>% tally()
+npub$publication_place <- factor(npub$publication_place, levels = top)
+npub.kungliga <- npub
+
+npub <- bind_rows(npub.fennica, npub.kungliga)
+
+# Order by total publishing activity
+npub$publication_place <- factor(npub$publication_place, levels = (npub %>% group_by(publication_place) %>% summarise(total = sum(n)) %>% arrange(desc(total)))$publication_place)
+npub <- npub %>% arrange(publication_place)
+npub$publication_place <- factor(npub$publication_place, levels = rev(unique(npub$publication_place)))
+
+theme_set(theme_bw(20))
+p <- ggplot(npub, aes(x = publication_decade, y = n)) +
+       geom_bar(stat = "identity", position = "stack",
+       		    aes(fill = publication_place)) + 
+       xlab("Publication year") +
+       ylab("Unique publishers (n)") +
+       scale_fill_brewer(palette="Spectral") +       
+       guides(fill = guide_legend(reverse = FALSE, title = "")) +
+       ggtitle(catal)
+       #ggtitle(paste("Unique publishers in selected publication places (", catalogue, ")"))
+
+print(p)
+
+```
+
+### Fig 10: Publications in Vaasa in Fennica, 1750-1828, with percentage of all books that were not published by the printing house of the court
+
+```{r publishers4-fennica, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=6, fig.width=12}
+library(dplyr)
+catalogue = "Fennica"
+place <- "Vaasa"
+minyear <- 1750
 maxyear <- 1828
-myplace <- "Linköping"
-cat <- "Kungliga"
-df <- df0 %>% filter(publication_place == myplace) %>%
-      	      filter(catalog == cat) %>%
-              filter(publication_year >= minyear &
-	             publication_year <= maxyear)
-
-tab <- unique(df[, c("publication_year", "author", "title", "publisher")])
-write.table(tab, sep = "\t", quote = F, row.names = FALSE, file = "output.tables/Linkoping.tab")
-```
-
-[Document listing for `r paste(cat, "/", myplace, minyear, "-", maxyear, sep = " ")`](output.tables/Linkoping.tab)
-
-### Title count in Linköping
-
-```{r linkoping2, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
-p <- plot_timeline(data = df, x = "publication_decade", y = "titlecount") +
-       ylab("Title count (n)") +
-       ggtitle(paste("Title count: ", cat, "/", myplace))
-print(p)
-```
-
-### Unique publishers in Linköping by year
-
-Never two publishers seen on the same year.
-
-```{r linkoping3, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
-dfs <- df %>% select(publication_year, publisher) %>%
-	      filter(!is.na(publisher)) %>%
-              unique %>%	      
-	      arrange(publication_year) 
-kable(dfs)
-```
-
-### Title count per capita
+
+df <- df0 %>% filter(catalog == catalogue & publication_place == place) %>%	
+        filter(publication_year >= minyear & publication_year <= maxyear)
+
+p <- ggplot() + ggtitle("Fig 10: to be added")
+
+# TITLE COUNT
+#theme_set(theme_bw(20))
+#p <- ggplot(npub, aes(x = publication_decade, y = publisher)) +
+#      geom_point(aes(size = n)) + 
+#      #geom_line(aes(color = publisher), size = 2) +
+#      #geom_smooth(aes(fill = publisher)) +
+#      # geom_bar(stat = "identity", position = "stack", aes(fill = publisher)) #+ 
+#       xlab("Year") +
+#       ylab("") +
+#       guides(size = guide_legend(title = "Title count (n)"))
+#       #ggtitle(paste("Title count per publisher (", place, "/", catalogue, ")"#, sep = ""))
+
+print(p)
+```
+
+---
+
+### Fig 11: Top publishers in Turku/Fennica
+
+```{r publishers-fennica-11, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=6, fig.width=12}
+library(dplyr)
+place <- "Turku"
+catalogue = "Fennica"
+df = df0
+
+df <- df %>% filter(catalog == catalogue & publication_place == place)
+
+df <- df %>%	
+  filter(publication_year >= 1640 & publication_year <= 1828)%>%
+        select(publication_decade, publisher, paper)
+
+# Group small publishers
+# Top publishers by title count
+ntop <- 10
+top <- names(top(df, "publisher", ntop))
+df$publisher[!df$publisher %in% top] <- "Other"
+df$publisher <- factor(df$publisher, c(top, "Other"))
+
+# Title count per decade & publisher	
+npub <- df %>% group_by(publication_decade, publisher) %>% tally() %>% arrange(n)
+#npub$publisher <- factor(npub$publisher, levels = (npub %>% group_by(publisher) %>% summarise(total = sum(n)) %>% arrange(total))$publisher)
+# Sort by biggest publication decade
+#ord <- (npub %>% group_by(publisher) %>% summarise(decade = publication_decade[[which.max(n)]]) %>% arrange(decade))$publisher
+ord <- as.character((npub %>% group_by(publisher) %>% 
+                        summarise(decade = median(publication_decade)) %>% 
+                        arrange(decade))$publisher)
+npub$publisher <- factor(npub$publisher, levels = c("Other", setdiff(ord, "Other")))
+
+# TITLE COUNT
+theme_set(theme_bw(20))
+p <- ggplot(npub, aes(x = publication_decade, y = publisher)) +
+      geom_point(aes(size = n)) + 
+      #geom_line(aes(color = publisher), size = 2) +
+      #geom_smooth(aes(fill = publisher)) +
+      # geom_bar(stat = "identity", position = "stack", aes(fill = publisher)) + 
+       xlab("Year") +
+       ylab("") +
+       guides(size = guide_legend(title = "Title count (n)"))
+       #ggtitle(paste("Title count per publisher (", place, "/", catalogue, ")", sep = ""))
+print(p)
+```
+
+---
+
+### IMAGE 12: Title count per capita
 
@@
 
-```{r abstitlecount, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
-# Take cities from Kungliga except Turku
-cat <- "Kungliga"
-df1 <- df0 %>% filter(publication_place %in% setdiff(cities, "Turku")) %>%
-      	      filter(catalog == cat) %>%
-	      group_by(publication_year, publication_place) %>%
-	      summarise(n = n(), paper = sum(paper, na.rm = TRUE))
-
-# Take cities from Fennica for Turku
-cat <- "Fennica"
-df2 <- df0 %>% filter(publication_place %in% "Turku") %>%
-      	      filter(catalog == cat) %>%
-	      group_by(publication_year, publication_place) %>%
-	      summarise(n = n(), paper = sum(paper, na.rm = TRUE))
-
-df <- bind_rows(df1, df2)
-
-p <- ggplot(df, aes(x = publication_year, y = n)) +
-       geom_line(aes(color = publication_place), size = 1) +
-       geom_point(aes(color = publication_place), size = 2) +
-       xlab("Publication year") +
-       ylab("Title count (n)") +
-       ggtitle("Absolute title count in selected cities") +
-       guides(color = guide_legend(title = "Place", reverse = TRUE))
-print(p)
-```
-
-### Octavo analysis
+---
+
+### Fig 13 Octavo paper consumption
 
 Paper consumption in octavo format books in Stockholm, Turku, Uppsala,
-Lund, Göteborg and Linköping. Again Turku from Fennica, other cities
-from Kungliga.
+Lund, Göteborg and Linköping. Turku is from Fennica, other cities from
+Kungliga.
 
@@
 
+---
+
+### Fig 14: Octavo title length
+
 Average title length in words in Stockholm, Turku, Uppsala, Lund,
 Göteborg and Linköping. According to Kungliga, except Turku from
-Fennica. For octavos only,
+Fennica. Only for octavo.
 
@@
 
+---
+
+### Fig 15: Different languages in Turku, Stockholm, Uppsala and Lund
+
+```{r language-perc2, echo=FALSE, message=FALSE, warning=FALSE, fig.width=20, fig.height=12}
+pics <- list()
+theme_set(theme_bw(20))
+myplaces <- c("Turku", "Greifswald", "Stockholm", "Uppsala", "Lund")
+
+for (catalogue in c("Fennica", "Kungliga")) {
+
+  df <- df0 %>% filter(catalog == catalogue) %>%
+        filter(publication_year >= 1600 & publication_year <= 1828)
+
+  langs <- c("Finnish", "Swedish", "Latin", "German",
+           "Russian", "French", "Hebrew", "Other")
+
+  lang <- paste("language.", langs, sep = "")
+  otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
+  otherlang <- otherlang[otherlang!="language.Multiple languages"]
+
+  df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
+
+  dfl <- NULL
+  for (lan in lang) {
+
+    # Classify a document to the specifed language
+    # If document is assigned with languages, each case is considered
+    # so one doc may have multiple entries corresponding to different languages
+    # mean(rowSums(df[, lang]) == 1) # 93% Fennica docs have just 1 language
+    # Combine data frames for specified languages
+    dflsub <- filter(df, df[[lan]])
+    if (nrow(dflsub) > 0) {
+      dflsub$language <- gsub("language.", "", lan)
+      dfl <- bind_rows(dfl, dflsub)
+    }
+  }
+
+  df <- dfl %>% group_by(publication_decade, publication_place, language) %>%
+     	     summarise(n = n())
+
+  # Calculate percentages
+  dff <- spread(df, language, n, fill = 0)
+  dff[, -c(1,2)] <- 100 * t(apply(dff[, -c(1,2)], 1, function (x) {x/sum(x)}))
+
+  dff <- melt(dff, id = c("publication_place", "publication_decade"))
+  colnames(dff) <- c("publication_place", "publication_decade", "language", "f")
+
+  for (myplace in myplaces) {
+    p <- ggplot(subset(dff, publication_place == myplace), aes(x = publication_decade, y = f)) +
+      geom_bar(position = "stack", stat = "identity", aes(fill = language)) + 
+      xlab("Publication year") +
+      ylab("Title count frequency (%)") +
+      ggtitle(paste(myplace, "/", catalogue)) +
+      #scale_fill_brewer(palette="Spectral") +
+      scale_fill_brewer(palette="Greys") +       
+      guides(fill = guide_legend(title = ""))
+    pics[[paste(catalogue, myplace, sep = "-")]] <- p
+  }
+}
+
+grid.arrange(pics[[1]],
+             pics[[8]], pics[[9]], pics[[10]], 
+             nrow = 2)
+rm(pics)
+```
+
+---
+
+### Fig 16: Topic richness per language (publications in Fennica)
+
+```{r topics232, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, fig.show="hold"}
+catalogue <- "Fennica"
+df <- filter(df0, catalog == "Fennica") %>%
+  filter(publication_year >= 1640 & publication_year <= 1828) %>%
+  select(publication_year, language, subject_topic)
+df <- unique(df)
+df <- df %>% group_by(publication_year, language) %>%
+             summarise(n = length(unique(unlist(strsplit(subject_topic, ";")))))
+
+langs2 <- c("Finnish", "Swedish", "Latin", "Other")
+df$language[!df$language %in% langs2] <- "Other"
+df$language <- factor(df$language, levels = langs2)
+
+p <- ggplot(df, aes(x = publication_year, y = n, shape = language)) +
+       geom_line(size = 1, aes(linetype = language)) +
+       geom_point(size = 5) +
+       scale_color_brewer(palette="Greys") +
+       scale_fill_brewer(palette="Greys") +                     
+       geom_smooth(color = "black") +       
+       ylab("Documents (n)") + xlab("Publication year")
+
+print(p)
+```
+
+---
+
+### Fig 17: Temporary sermons in Latin and Swedish
+
+```{r topics882, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6}
+  sel <- c("hautajaiset", "häät", "juhlamenot")
+  catalogue <- "Fennica"
+  df <- df0
+  df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)
+
+  # Selected catalogue with selected topics
+  df <- df %>% filter(catalog == catalogue & hit)
+  lang <- paste("language.", langs, sep = "")
+  otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
+  otherlang <- otherlang[otherlang!="language.Multiple languages"]
+  df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
+
+  dfl <- NULL
+  for (lan in lang) {
+    # Classify a document to the specifed language
+    # If document is assigned with languages, each case is considered
+    # so one doc may have multiple entries corresponding to different languages
+    # mean(rowSums(df[, lang]) == 1) # 93% Fennica docs have just 1 language
+    # Combine data frames for specified languages
+    dflsub <- filter(df, df[[lan]])
+    if (nrow(dflsub) > 0) {
+      dflsub$language <- gsub("language.", "", lan)
+    dfl <- bind_rows(dfl, dflsub)
+  }
+}
+dfl$language <- factor(dfl$language, levels = langs)
+
+  df <- dfl %>% group_by(publication_decade, language) %>%
+             summarise(n = n(),
+	               paper = sum(paper, na.rm = TRUE))
+
+  # PAPER CONSUMPTION
+  p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
+       geom_point(aes(col = language, shape = language), size = 5) +
+       geom_line(aes(col = language, shape = language)) +       
+       xlab("Publication year") +
+       ylab("Paper consumption") +
+       ggtitle(paste("Temporary Sermons (", catalogue, ")", sep = ""))
+  print(p)
+```
+
+---
+
+### Fig 18: Devotional literature (catechisms, hymns, prayers, etc.)
+
+Form of literature denoting the advancement of reading in Finland in the 19th century. It has been unclear when devotional literature  shows up as a relevant category.
+
+```{r topics12122, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, fig.show="hold"}
+sel <- c("virret","arkkiveisut","hartauskirjat","katekismukset","rukouspäivät","saarnat","aapiset","rukoukset","rukous","hengelliset laulut","hartauspuheet","virsikirjat")
+catalogue <- "Fennica"
+
+  # Selected catalogue with selected years
+  df <- filter(df0, catalog == catalogue &
+     		    publication_year >= 1640 &
+		    publication_year <= 1828)
+
+  # Selected topics
+  df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)  
+  df <- df %>% filter(catalog == catalogue & hit)
+
+  lang <- paste("language.", langs, sep = "")
+  otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
+  df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
+  dfl <- NULL
+  for (lan in lang) {
+    # Classify a document to the specifed language
+    # If document is assigned with languages, each case is considered
+    # so one doc may have multiple entries corresponding to different languages
+    # mean(rowSums(df[, lang]) == 1) # 93% Fennica docs have just 1 language
+    # Combine data frames for specified languages
+    dflsub <- filter(df, df[[lan]])
+    if (nrow(dflsub) > 0) {
+      dflsub$language <- gsub("language.", "", lan)
+      dfl <- bind_rows(dfl, dflsub)
+    }
+  }
+  df <- dfl %>% group_by(publication_decade, language) %>%
+             summarise(n = n(),
+	               paper = sum(paper, na.rm = TRUE))
+
+  # PAPER CONSUMPTION
+  theme_set(theme_bw(20))
+  p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
+       geom_point(aes(col = language, shape = language), size = 5) +
+       geom_line(aes(col = language, shape = language)) +       
+       #geom_smooth(aes(fill = language, color = language)) + 
+       xlab("Publication year") +
+       ylab("Paper consumption") +
+       ggtitle(paste("Devotional Literature (", catalogue, ")", sep = ""))
+       #ggtitle(paste("Devotional literature" (", catalogue, ")", sep = "")) 
+  print(p)
+```
+
+---
+
+### Fig 19: Publisher per city over time
+
+```{r publishersper, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, fig.show="hold"}
+# Selected catalogue with selected decades
+catalogue <- "Fennica"
+
+df <- filter(df0, catalog == catalogue &
+     		    publication_decade >= 1640 &
+		    publication_decade <= 1828)
+
+top.places <- names(top(df, "publication_place", 5))
+
+df <- df %>%
+      filter(publication_place %in% top.places) %>% 
+      group_by(publication_decade, publication_place) %>%
+      summarise(n = length(unique(na.omit(publisher))))
+
+  theme_set(theme_bw(20))
+  p <- ggplot(df, aes(x = publication_decade, y = n, shape = publication_place)) +
+       geom_point(size = 5) +
+       geom_line(size = 1, aes(linetype = publication_place)) +
+       scale_color_brewer(palette="Greys") +
+       #scale_fill_brewer(palette="Greys") +                     
+       xlab("Publication year") +
+       ylab("Publishers (n)") +
+       guides(shape = guide_legend("Place")) +
+       guides(linetype = guide_legend("Place")) +
+       ggtitle(paste(catalogue))
+  print(p)
+
+```
+
 ## Session info

### 2017-02-13 inst/examples/20170201-manuscript.Rmd
manuscript figures
ok

@@
 
-### Fig. 1: Number of publication places per decade
+### Fig. 1: Number of publication places over time
 
@@
 
-### Fig 2: Number of documents per decade
+### Fig 2: Title count over time
 
@@
 
-### Fig 3: Rise of the octavo sized book as vehicle of Enlightenment
-
-Paper consumption: different document formats over time
+### Fig 3: Rise of the Octavo
+
+Paper consumption for various document formats over time.
 
@@
 
-### Fig 5: Turku in Sweden: proportions for title count and paper in Swedish University towns
+### Fig 5: Turku as Swedish university town
+
+Proportions for title count and paper in Swedish University towns
 
@@
 
-### Fig. 7: Riksdagar Kungliga
+### Fig. 7: Riksdagar: Kungliga
 
@@
 
-### Fig. 8: Riksdagar Fennica
+### Fig. 8: Riksdagar: Fennica
 
@@
 
-### Fig 9A: Fennica - Publishers in Swedish University towns (and Finland)
+### Fig 9A: Fennica: Publishers in Swedish University towns (and Finland)
 
@@
 
-### Fig 9B: Kungliga - Publishers in Swedish University towns (and Finland)
+### Fig 9B: Kungliga: Publishers in Swedish University towns (and Finland)
 
@@
 
-### Fig 10: Publications in Vaasa in Fennica, 1750-1828, with percentage of all books that were not published by the printing house of the court
+### Fig 10: Publications in Vaasa in Fennica, 1750-1828
+
+With percentage of all books that were not published by the printing house of the court.
 
@@
 
-### IMAGE 12: Title count per capita
+### Fig. 12: Title count per capita
 
@@
 
-### Fig 13 Octavo paper consumption
+### Fig. 13: Octavo paper consumption
 
@@
 
-### Fig 14: Octavo title length
+### Fig. 14: Octavo title length (word count)
 
@@
 
-### Fig 15: Different languages in Turku, Stockholm, Uppsala and Lund
+### Fig 15: Language use in Turku, Stockholm, Uppsala and Lund
 
@@
 
-### Fig 16: Topic richness per language (publications in Fennica)
+### Fig. 16: Topic richness per language (Fennica)
 
@@
 
-### Fig 17: Temporary sermons in Latin and Swedish
+### Fig. 17: Temporary sermons in Latin and Swedish
 
@@
 
-### Fig 18: Devotional literature (catechisms, hymns, prayers, etc.)
+### Fig. 18: Devotional literature (catechisms, hymns, prayers, etc.)
 
@@
 
-### Fig 19: Publisher per city over time
+### Fig. 19: Publisher per city over time
 

### 2017-02-13 inst/examples/20170201-manuscript.Rmd
manuscript figures

@@
 
-```{r places_per_decade, message=FALSE, warning=FALSE, fig.width=10, fig.height=3, echo=FALSE}
+```{r places_per_decade, message=FALSE, warning=FALSE, fig.width=10, fig.height=4, echo=FALSE}
 library(dplyr)
@@
        geom_line() + 
-       ylab("Publication places (n)") + xlab("Publication year") +
+       ylab("Places (n)") + xlab("Publication year") +
        scale_color_manual(values = c("blue", "darkgreen")) + 
        guides(color = guide_legend(reverse = TRUE, title = "")) +
-       ggtitle("Number of unique publication places")
+       ggtitle("Unique publication places")
 print(p)
@@
 
-```{r, message=FALSE, warning=FALSE, fig.width=10, fig.height=3, echo=FALSE}
+```{r, message=FALSE, warning=FALSE, fig.width=10, fig.height=4, echo=FALSE}
 library(dplyr)
@@
        scale_color_manual(values = c("blue", "darkgreen")) + 
-       guides(color = guide_legend(reverse = TRUE, title = "")) #+ 
+       guides(color = guide_legend(reverse = TRUE, title = "")) +
+       ggitle("Title count")
 print(p)
@@
 
-```{r LIBER-13, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=11, fig.height=9, fig.show="hold"}
+```{r LIBER-13, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=11, fig.height=9, fig.show="hold", out.width="240px"}
 for (catal in unique(df0$catalog)) {
@@
   p <- p + ylab("Paper consumption")
-  p <- p + guides(linetype = guide_legend(keywidth = 5),
-       	          shape = guide_legend(keywidth = 5))
+  p <- p + guides(linetype = guide_legend(keywidth = 5, title = "Gatherings"),
+       	          shape = guide_legend(keywidth = 5, title = "Gatherings"),
+       	          fill = "none" 
+		  )
   p <- p + ggtitle(catal)
@@
                      fill = language, color = language)) +
-       geom_point(aes(size = n)) +
-       geom_line() +
-       #scale_y_log10() +
-       ggtitle("Mean title word count (top language)")
+       geom_point(aes(size = n, shape = language)) +
+       geom_line(aes(linetype = language)) +
+       guides(
+            color = guide_legend(title = "Language"),
+            shape = guide_legend(title = "Language")
+	    ) +
+       ylab("Title length (word count)") +
+       xlab("Publication decade") +
+       ggtitle("Title length")
 
@@
 
-```{r publishingovertime, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=4, out.width="300px"}
+```{r publishingovertime, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=4}
 library(magrittr)
@@
 
-```{r riksdar_kungliga, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
+```{r riksdar_kungliga, echo=FALSE, message=FALSE, warning=FALSE, fig.width=15, fig.height=5}
 
@@
   p <- p + xlab("Year")
-  p <- p + ggtitle(paste(catal,"Riksplaces"))
+  p <- p + ggtitle(catal)
   print(p)
@@
 
-```{r riksdar_fennica, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
+```{r riksdar_fennica, echo=FALSE, message=FALSE, warning=FALSE, fig.width=15, fig.height=5}
 minyear <- 1760
@@
 p <- ggplot(dfm, aes(x = publication_decade, y = titles_per_capita)) +
-       geom_line(aes(color = publication_place), size = 1) +
-       geom_point(aes(color = publication_place), size = 2) +
+       geom_line(aes(linetype = publication_place), size = 1) +
+       geom_point(aes(shape = publication_place), size = 5) +
        xlab("Publication decade") +
        ylab("Title count per capita (n)") +
-       ggtitle("Title count per capita in selected cities") +
+       ggtitle("Title count per capita") +
        guides(color = guide_legend(title = "Place", reverse = TRUE))
@@
 
-kable(dfm)
+#kable(dfm)
 ```
@@
 p <- ggplot(df, aes(x = publication_decade, y = paper)) +
-       geom_line(aes(color = publication_place), size = 1) +
-       geom_point(aes(color = publication_place), size = 2) +
+       geom_line(aes(linetype = publication_place), size = 1) +
+       geom_point(aes(shape = publication_place), size = 2) +
        xlab("Publication year") +
        ylab("Paper (sheets)") +
-       ggtitle("Paper consumption in selected cities") +
+       ggtitle("Octavo: paper consumption") +
        guides(color = guide_legend(title = "Place", reverse = TRUE))
@@
 p <- ggplot(df, aes(x = publication_decade, y = mean_title_length)) +
-       geom_line(aes(color = publication_place), size = 1) +
-       geom_point(aes(color = publication_place), size = 2) +
+       geom_line(aes(linetype = publication_place), size = 1) +
+       geom_point(aes(shape = publication_place), size = 5) +
        xlab("Publication year") +
@@
   for (myplace in myplaces) {
-    p <- ggplot(subset(dff, publication_place == myplace), aes(x = publication_decade, y = f)) +
-      geom_bar(position = "stack", stat = "identity", aes(fill = language)) + 
+    p <- ggplot(subset(dff, publication_place == myplace),
+      aes(x = publication_decade, y = f)) +
+      geom_bar(position = "stack", stat = "identity",
+      			aes(fill = language), color = "black") + 
       xlab("Publication year") +
@@
        geom_line(size = 1, aes(linetype = language)) +
-       geom_point(size = 5) +
+       geom_point(size = 4) +
        scale_color_brewer(palette="Greys") +
@@
        geom_smooth(color = "black") +       
-       ylab("Documents (n)") + xlab("Publication year")
+       ylab("Title count (n)") + xlab("Publication year")
 
@@
   p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
-       geom_point(aes(col = language, shape = language), size = 5) +
-       geom_line(aes(col = language, shape = language)) +       
+       geom_point(aes(shape = language), size = 5) +
+       geom_line(aes(linetype = language)) +       
        xlab("Publication year") +
@@
   p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
-       geom_point(aes(col = language, shape = language), size = 5) +
-       geom_line(aes(col = language, shape = language)) +       
-       #geom_smooth(aes(fill = language, color = language)) + 
+       geom_point(aes(shape = language), size = 5) +
+       geom_line(aes(linetype = language)) +       
        xlab("Publication year") +
@@
        ggtitle(paste("Devotional Literature (", catalogue, ")", sep = ""))
-       #ggtitle(paste("Devotional literature" (", catalogue, ")", sep = "")) 
   print(p)

### 2017-02-13 inst/examples/20170201-manuscript.Rmd
manuscript figures

@@
        guides(color = guide_legend(reverse = TRUE, title = "")) +
-       ggitle("Title count")
+       ggtitle("Title count")
 print(p)

### 2017-02-13 inst/examples/20170201-manuscript.Rmd
manuscript figures

--- 2017-02-13 inst/examples/20170201-manuscript.Rmd
@@
 	      summarise(n = length(unique(na.omit(publication_place))))
-p <- ggplot(df, aes(x = publication_decade, y = n, color = catalog)) + 
-       geom_point() + 
-       geom_line() + 
+p <- ggplot(df, aes(x = publication_decade, y = n, shape = catalog, linetype = catalog)) + 
+       geom_point(size = 4) + 
+       geom_line(size = 1) + 
        ylab("Places (n)") + xlab("Publication year") +
@@
 df <- df0 %>% filter(publication_year >=1640 & publication_year <=1828) %>% group_by(catalog, publication_decade) %>% tally()
-p <- ggplot(df, aes(x = publication_decade, y = n, color = catalog)) + 
-       geom_point() + 
-       geom_line() + 
+p <- ggplot(df, aes(x = publication_decade, y = n, shape = catalog, linetype = catalog)) + 
+       geom_point(size = 4) + 
+       geom_line(size = 1) + 
        ylab("Documents (n)") + xlab("Publication year") +
@@
 
-```{r LIBER-13, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=11, fig.height=9, fig.show="hold", out.width="240px"}
+```{r LIBER-13, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=11, fig.height=9, fig.show="hold", out.width="350px"}
 for (catal in unique(df0$catalog)) {
@@
 p <- ggplot(df, aes(x = publication_decade, y = mean_title_length,
-                     fill = language, color = language)) +
-       geom_point(aes(size = n, shape = language)) +
-       geom_line(aes(linetype = language)) +
+                     fill = language)) +
+       geom_point(aes(size = n, shape = language), size = 3) +
+       geom_line(aes(linetype = language), size = 1) +
        guides(
-            color = guide_legend(title = "Language"),
             shape = guide_legend(title = "Language")
@@
   p <- ggplot(dff, aes(x = publication_decade, y = f)) +
-     geom_bar(position = "stack", stat = "identity",
+     geom_bar(position = "stack", stat = "identity", color = "black",
        aes(fill = publication_place)) + 
      xlab("Publication year") +
-     scale_fill_brewer(palette="Spectral")
+     #scale_fill_brewer(palette="Spectral")
+     scale_fill_brewer(palette="Greys") 
      if (varname == "n") {
@@
      }     
-  p <- p + guides(fill = guide_legend(reverse = TRUE, title = ""))
+  p <- p + guides(fill = guide_legend(title = ""))
 
@@
        #scale_x_discrete(labels = c("1757-1765", "1766-1774", "1775-1783")) +
+       #scale_fill_manual(values = c("darkgreen", "darkgray"))
+       scale_fill_brewer(palette="Greys") +              
        guides(fill = guide_legend(title = "Period")) +
@@
        ggtitle("Title count per capita") +
-       guides(color = guide_legend(title = "Place", reverse = TRUE))
+       guides(shape = guide_legend(title = "Place"))
 print(p)
@@
        geom_line(aes(linetype = publication_place), size = 1) +
-       geom_point(aes(shape = publication_place), size = 2) +
+       geom_point(aes(shape = publication_place), size = 5) +
        xlab("Publication year") +
@@
        ggtitle("Octavo: paper consumption") +
-       guides(color = guide_legend(title = "Place", reverse = TRUE))
+       guides(shape = guide_legend(shape = "Place"))
 print(p)
@@
        ggtitle("Mean title length in selected cities") +
-       guides(color = guide_legend(title = "Place", reverse = TRUE))
+       guides(shape = guide_legend(title = "Place"))
 print(p)
@@
        geom_point(aes(shape = language), size = 5) +
-       geom_line(aes(linetype = language)) +       
+       geom_line(aes(linetype = language), size = 1) +       
        xlab("Publication year") +
@@
        ylab("Paper consumption") +
+       guides(shape = guide_legend(title = "Language")) +
        ggtitle(paste("Devotional Literature (", catalogue, ")", sep = ""))

### 2017-02-13 inst/examples/20170201-manuscript.Rmd
manuscript figures

@@
        scale_color_manual(values = c("blue", "darkgreen")) + 
-       guides(color = guide_legend(reverse = TRUE, title = "")) +
+       guides(color = guide_legend(title = "")) +
        ggtitle("Unique publication places")
@@
        scale_color_manual(values = c("blue", "darkgreen")) + 
-       guides(color = guide_legend(reverse = TRUE, title = "")) +
+       guides(color = guide_legend(title = "")) +
        ggtitle("Title count")
@@
 
-```{r LIBER-13, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=11, fig.height=9, fig.show="hold", out.width="350px"}
+```{r LIBER-13, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=6, fig.height=5, fig.show="hold", out.width="400px"}
 for (catal in unique(df0$catalog)) {
@@
        	          shape = guide_legend(keywidth = 5, title = "Gatherings"),
-       	          fill = "none" 
+       	          fill = guide_legend(title = "Gatherings")
 		  )
@@
        guides(
-            shape = guide_legend(title = "Language")
+            shape = guide_legend(title = "Language"),
+            linetype = guide_legend(title = "Language")
 	    ) +
@@
        ggtitle("Title count per capita") +
-       guides(shape = guide_legend(title = "Place"))
+       guides(shape = guide_legend(title = "Place")) +
+       guides(linetype = guide_legend(title = "Place")) 
 print(p)
@@
        ggtitle("Octavo: paper consumption") +
-       guides(shape = guide_legend(shape = "Place"))
+       guides(shape = guide_legend(title = "Place")) +
+       guides(linetype = guide_legend(title = "Place"))        
 print(p)
@@
        ylab("Title length (characters)") +
-       ggtitle("Mean title length in selected cities") +
-       guides(shape = guide_legend(title = "Place"))
+       ggtitle("Mean title length") +
+       guides(shape = guide_legend(title = "Place")) +
+       guides(linetype= guide_legend(title = "Place"))        
 print(p)
@@
       guides(fill = guide_legend(title = "")) 
+      #guides(fill = guide_legend(title = "")) +       
     pics[[paste(catalogue, myplace, sep = "-")]] <- p
@@
        geom_smooth(color = "black") +
+       guides(shape = guide_legend(title = "Language")) +
+       guides(linetype = guide_legend(title = "Language")) + 
        ylab("Title count (n)") + xlab("Publication year")
@@
        ylab("Paper consumption") +
+       guides(shape = guide_legend(title = "Language")) +
+       guides(linetype = guide_legend(title = "Language")) + 
        ggtitle(paste("Temporary Sermons (", catalogue, ")", sep = ""))
@@
        guides(shape = guide_legend(title = "Language")) +
+       guides(linetype = guide_legend(title = "Language")) +        
        ggtitle(paste("Devotional Literature (", catalogue, ")", sep = ""))

### 2017-02-13 inst/examples/20170201-manuscript.Rmd
manuscript figures

@@
        scale_color_manual(values = c("blue", "darkgreen")) + 
-       guides(color = guide_legend(title = "")) +
+       guides(shape = guide_legend(title = "Catalog")) +
+       guides(linetype = guide_legend(title = "Catalog")) +       
        ggtitle("Unique publication places")
@@
        scale_color_manual(values = c("blue", "darkgreen")) + 
-       guides(color = guide_legend(title = "")) +
+       guides(shape = guide_legend(title = "Catalog")) +
+       guides(linetype = guide_legend(title = "Catalog")) +       
        ggtitle("Title count")
@@
 
-```{r LIBER-13, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=6, fig.height=5, fig.show="hold", out.width="400px"}
+```{r LIBER-13, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=8, fig.height=5, fig.show="hold", out.width="400px"}
 for (catal in unique(df0$catalog)) {
@@
   p <- p + ylab("Paper consumption")
+  p <- p + ylim(c(0, max(na.omit(df2$paper))))
   p <- p + guides(linetype = guide_legend(keywidth = 5, title = "Gatherings"),
        	          shape = guide_legend(keywidth = 5, title = "Gatherings"),
-       	          fill = guide_legend(title = "Gatherings")
+       	          fill = "none", # guide_legend(title = "Gatherings"),
+       	          color = "none" # guide_legend(title = "Gatherings")
 		  )
@@
 
-p <- ggplot(df, aes(x = publication_decade, y = mean_title_length,
-                     fill = language)) +
+p <- ggplot(df, aes(x = publication_decade, y = mean_title_length)) +
        geom_point(aes(size = n, shape = language), size = 3) +

### 2017-02-13 inst/examples/20170201-manuscript.Rmd
manuscript figures

@@
        scale_color_manual(values = c("blue", "darkgreen")) + 
-       guides(shape = guide_legend(title = "Catalog")) +
-       guides(linetype = guide_legend(title = "Catalog")) +       
+       guides(shape = guide_legend(title = "Catalog", reverse = TRUE)) +
+       guides(linetype = guide_legend(title = "Catalog", reverse = TRUE)) +       
        ggtitle("Unique publication places")
@@
 
-```{r LIBER-13, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=8, fig.height=5, fig.show="hold", out.width="400px"}
+```{r LIBER-13, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=7, fig.height=4, fig.show="hold", out.width="400px"}
 for (catal in unique(df0$catalog)) {

### 2017-02-13 inst/examples/20170201-manuscript.Rmd
manuscript figures

@@
   p <- p + ggtitle("Publishing activity")
-  p <- p + ylab("Documents / Year")
+  p <- p + ylab("Title count / Year")
   p <- p + xlab("Year")

### 2017-02-13 inst/examples/20170201-manuscript.Rmd
kuvien viilaus

--- 2017-02-13 inst/examples/20170201-manuscript.Rmd
@@
 df0 <- df.full %>% filter(publication_year >= min.year & publication_year <= max.year)
-df0$title_length <- nchar(df0$title)
+# Calculate title length (nchar and word count)
+df0$title_length_nchar <- nchar(df0$title)
+df0$title_length_wordcount <- sapply(strsplit(df0$title, " "), length)
+df0$title_length_wordcount[is.na(df0$title)] <- NA
 ```
@@
        scale_color_manual(values = c("blue", "darkgreen")) +
-       guides(shape = guide_legend(title = "Catalog")) +
-       guides(linetype = guide_legend(title = "Catalog")) +       
+       guides(shape = guide_legend(title = "Catalog", reverse = TRUE)) +
+       guides(linetype = guide_legend(title = "Catalog", reverse = TRUE)) +  
        ggtitle("Title count")
@@
 
-```{r LIBER-13, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=7, fig.height=4, fig.show="hold", out.width="400px"}
+```{r LIBER-13, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=9, fig.height=4, fig.show="hold", out.width="400px"}
 for (catal in unique(df0$catalog)) {
@@
   df2$highlight[df2$gatherings == "8vo"] <- "Octavo"
+  df2$gatherings <- factor(df2$gatherings, levels = levels(df0$gatherings))
 
@@
   p <- p + xlab("Year")
-  p <- p + ylab("Paper consumption")
+  p <- p + ylab("Paper (sheets)")
   p <- p + ylim(c(0, max(na.omit(df2$paper))))
@@
 
-# Calculate title length (word count)
-dfo$title_wordcount <- sapply(strsplit(as.character(dfo$title), " "), length)
-dfo$title_wordcount[is.na(dfo$title)] <- NA
-
 top.language <- setdiff(names(top(dfo, "language", 11)), "NA")
@@
               group_by(publication_decade, language) %>%
-              summarize(mean_title_length = mean(title_wordcount),
+              summarize(mean_title_length = mean(title_length_wordcount),
 	      		n = n())
@@
 p <- ggplot(df, aes(x = publication_decade, y = mean_title_length)) +
-       geom_point(aes(size = n, shape = language), size = 3) +
+       geom_point(aes(size = n, shape = language), size = 5) +
        geom_line(aes(linetype = language), size = 1) +
@@
 		 )
+df$period <- gsub("\\[", "", df$period)
+df$period <- gsub("\\)", "", df$period)
+df$period <- gsub(",", ",", df$period)
 
@@
 
-### Fig. 7: Riksdagar: Kungliga
+### Fig. 7: Publishing activity and riksdagar: Kungliga
 
@@
 minyear <- 1700
-maxyear <- 1800
+maxyear <- 1830
 catal <- "Kungliga"
@@
 
-  df <- subset(dfsel, publication_year >= 1700 & publication_year < 1831 )
+  df <- subset(dfsel, publication_year >= minyear & publication_year <= maxyear)
 
@@
   p <- p + scale_x_continuous(breaks=seq(min(dfm$date), max(dfm$date), 10))
-  p <- p + ggtitle("Publishing activity")
-  p <- p + ylab("Documents / Year")
+  p <- p + ylab("Title count (n)")
   p <- p + xlab("Year")
-  p <- p + ggtitle(catal)
-  print(p)
-
-```
-
----
-
-### Fig. 8: Riksdagar: Fennica
+  p <- p + ggtitle(paste(catal, " ", minyear, "-", maxyear, sep = ""))
+  print(p)
+```
+
+---
+
+### Fig. 8: Publishing activity and riksdagar: Fennica
 
@@
   p <- p + scale_x_continuous(breaks=seq(min(dfm$date), max(dfm$date), 10))
-  p <- p + ggtitle("Publishing activity")
-  p <- p + ylab("Documents / Year")
+  p <- p + ylab("Title count (n)")
   p <- p + xlab("Year")
-  p <- p + ggtitle(paste(catal))
+  p <- p + ggtitle(paste(catal, " ", minyear, "-", maxyear, sep = ""))  
   p <- p + xlim(c(minyear, maxyear))
@@
 	       summarise(n = n(), paper = sum(paper, na.rm = TRUE), 
-	         mean_title_length = mean(title_length, na.rm = TRUE))
+	         mean_title_length = mean(title_length_wordcount, na.rm = TRUE))
 
@@
 	       summarise(n = n(), paper = sum(paper, na.rm = TRUE), 
-                 mean_title_length = mean(title_length, na.rm = TRUE))
+                 mean_title_length = mean(title_length_wordcount, na.rm = TRUE))
 
@@
        ylab("Title length (characters)") +
-       ggtitle("Mean title length") +
+       ggtitle("Octavo: mean title length") +
        guides(shape = guide_legend(title = "Place")) +
@@
        guides(linetype = guide_legend(title = "Language")) + 
-       ylab("Title count (n)") + xlab("Publication year")
+       ylab("Title count (n)") +
+       xlab("Publication year")
 
@@
        xlab("Publication year") +
-       ylab("Paper consumption") +
+       ylab("Paper (sheets)") +
        guides(shape = guide_legend(title = "Language")) +
        guides(linetype = guide_legend(title = "Language")) + 
-       ggtitle(paste("Temporary Sermons (", catalogue, ")", sep = ""))
+       #ggtitle(paste("Temporary Sermons (", catalogue, ")", sep = ""))
+       ggtitle(catalogue)       
   print(p)
@@
        xlab("Publication year") +
-       ylab("Paper consumption") +
+       ylab("Paper (sheets)") +
        guides(shape = guide_legend(title = "Language")) +
        guides(linetype = guide_legend(title = "Language")) +        
-       ggtitle(paste("Devotional Literature (", catalogue, ")", sep = ""))
+       ggtitle(catalogue)
+       #ggtitle(paste("Devotional Literature (", catalogue, ")", sep = "")) 
 print(p)

### 2017-02-13 inst/examples/20170201-manuscript.Rmd
kuvien viilaus

@@
 
-```{r LIBER-13, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=9, fig.height=4, fig.show="hold", out.width="400px"}
+```{r LIBER-13, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=9, fig.height=5, fig.show="hold", out.width="400px"}
 for (catal in unique(df0$catalog)) {
   df2 <- subset(df0, catalog == catal) %>% group_by(publication_decade, gatherings) %>% summarize(paper = sum(paper, na.rm = TRUE), n = n())
-  df2 <- filter(df2, gatherings %in% setdiff(names(which(table(df2$gatherings) >= 15)), "NA"))
+
+  df2 <- filter(df2, gatherings %in% setdiff(names(which(table(df2$gatherings) >= 20)), "NA"))
   df2$highlight <- rep("Other", nrow(df2))
@@
 		  )
+  #p <- p + facet_grid(. ~ catalog)		  
   p <- p + ggtitle(catal)
@@
        xlab("Publication year") +
-       ylab("Title length (characters)") +
+       ylab("Title length (words)") +
        ggtitle("Octavo: mean title length") +

### 2017-02-14 inst/examples/20170201-manuscript.Rmd
updateing analyses

@@
 df.full <- df.combined.preprocessed %>% filter(!remove)
+# Calculate title length (nchar and word count)
+df.full$title_length_nchar <- nchar(df.full$title)
+df.full$title_length_wordcount <- sapply(strsplit(df.full$title, " "), length)
+df.full$title_length_wordcount[is.na(df.full$title)] <- NA
+
 # Data with years limited as well
 df0 <- df.full %>% filter(publication_year >= min.year & publication_year <= max.year)
-# Calculate title length (nchar and word count)
-df0$title_length_nchar <- nchar(df0$title)
-df0$title_length_wordcount <- sapply(strsplit(df0$title, " "), length)
-df0$title_length_wordcount[is.na(df0$title)] <- NA
 ```
@@
 
-```{r places_per_decade, message=FALSE, warning=FALSE, fig.width=10, fig.height=4, echo=FALSE}
+```{r Fig1, message=FALSE, warning=FALSE, fig.width=10, fig.height=4, echo=FALSE}
 library(dplyr)
@@
 
-```{r, message=FALSE, warning=FALSE, fig.width=10, fig.height=4, echo=FALSE}
+```{r Fig2, message=FALSE, warning=FALSE, fig.width=10, fig.height=4, echo=FALSE}
 library(dplyr)
@@
 
-```{r LIBER-13, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=9, fig.height=5, fig.show="hold", out.width="400px"}
-for (catal in unique(df0$catalog)) {
-  df2 <- subset(df0, catalog == catal) %>% group_by(publication_decade, gatherings) %>% summarize(paper = sum(paper, na.rm = TRUE), n = n())
+```{r Fig3, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=9, fig.height=5, fig.show="hold", out.width="400px"}
+
+for (catal in unique(df00$catalog)) {
+
+  if (catal == "Kungliga") {
+    df00 <- df.full %>% filter(publication_year >= min.year & publication_year <= max.year)
+  } else if (catal == "Fennica") {
+    df00 <- df.full %>% filter(publication_year >= min.year & publication_year <= 1900)
+  }
+
+  df2 <- subset(df00, catalog == catal) %>% group_by(publication_decade, gatherings) %>% summarize(paper = sum(paper, na.rm = TRUE), n = n())
 
@@
   df2$highlight[df2$gatherings == "8vo"] <- "Octavo"
-  df2$gatherings <- factor(df2$gatherings, levels = levels(df0$gatherings))
+  df2$gatherings <- factor(df2$gatherings, levels = levels(df.full$gatherings))
 
@@
 
-```{r title_length_by_lang, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=7, fig.width=15}
-dfo <- df0
-
+```{r Fig4, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=7, fig.width=15}
 # Analysis time window
-dfo <- dfo %>% filter(publication_year >= 1640 & publication_year <= 1911)
-
-top.language <- setdiff(names(top(dfo, "language", 11)), "NA")
-
-df <- dfo %>% filter(language %in% top.language) %>%
-              group_by(publication_decade, language) %>%
+df <- df0 %>% filter(publication_year >= 1640 & publication_year <= 1911) %>%
+              group_by(publication_decade) %>%
               summarize(mean_title_length = mean(title_length_wordcount),
@@
 
-p <- ggplot(df, aes(x = publication_decade, y = mean_title_length)) +
-       geom_point(aes(size = n, shape = language), size = 5) +
-       geom_line(aes(linetype = language), size = 1) +
-       guides(
-            shape = guide_legend(title = "Language"),
-            linetype = guide_legend(title = "Language")
-	    ) +
+for (catal in unique(df$catalog)) {
+  dfs <- subset(df, catalog == catal)
+  p <- ggplot(dfs, aes(x = publication_decade, y = mean_title_length)) +
+       geom_point(aes(size = n), size = 5) +
+       geom_line(size = 1) +
        ylab("Title length (word count)") +
        xlab("Publication decade") +
-       ggtitle("Title length")
-
-print(p)
+       ggtitle(paste("Title length (", catal, ")", sep = ""))
+
+  print(p)
+}
 ```
@@
 
-```{r comparisons, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=18, fig.height=10}
+```{r Fig5, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=18, fig.height=10}
 pics <- list()
@@
 
-```{r publishingovertime, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=4}
+```{r Fig6, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=4}
 library(magrittr)
@@
 
-### Fig. 7: Publishing activity and riksdagar: Kungliga
-
-```{r riksdar_kungliga, echo=FALSE, message=FALSE, warning=FALSE, fig.width=15, fig.height=5}
+### Fig. 7A: Publishing activity and riksdagar: Kungliga
+
+```{r Fig7A, echo=FALSE, message=FALSE, warning=FALSE, fig.width=15, fig.height=5}
 
@@
                1719-.5, 1719+.5, # Stockholm 20 januari 1719 1 juni 1719
+               1720-.5, 1720+.5, # Stockholm 20 januari 1719 1 juni 1719
+               1723-.5, 1723+.5, # Stockholm 20 januari 1719 1 juni 1719
+
+               1726-.5, 1727+.5, # Stockholm 20 januari 1719 1 juni 1719
+
+               1731-.5, 1731+.5, # Stockholm 20 januari 1719 1 juni 1719
+
                1734-.5, 1734+.5, # Stockholm 14 maj 1734 14 december 1734
+
+               1738-.5, 1739+.5, #
+
+               1740-.5, 1741+.5, #
+
+               1742-.5, 1743+.5, #
+               1746-.5, 1747+.5, #
+
+               1751-.5, 1752+.5, #
+               1755-.5, 1756+.5, #
+               1760-.5, 1762+.5, #
+
                1765-.5, 1766+.5, # Stockholm 21 februari 1765 21 oktober 1766
@@
   #cols <- c("white", "Purple", "yellow", "orange", "darkgray")
+  cols <- c("white", "lightgray", "gray", "darkgray")
+  rectangles$shade[rectangles$shade == "Highlight"] <- rep(cols, length(which(rectangles$shade == "Highlight")))
+  rectangles$shade <- factor(rectangles$shade)
+
+  rectangles$place <- rectangles$shade
+  rectangles$place[rectangles$place == "Highlight"] <- riksplace
+  rectangles$place[rectangles$place == "Background"] <- ""
+
+  # Draw Figure
+  theme_set(theme_bw(20))
+  p <- ggplot() +
+         geom_rect(data = rectangles, 
+           aes(xmin=xmin, xmax=xmax,
+	       ymin=ymin, ymax=ymax,
+	       fill=shade), alpha=0.8) +
+         #scale_fill_manual(values = cols) +
+         scale_fill_brewer(palette="Greys") +
+	 guides(fill = "none")
+
+  # p <- p + geom_text(data = rectangles, angle = 90, aes(x=xmin + .5, y=.9*ymax, label=place), size = 6)
+
+  p <- p + geom_line(data = dfm, aes(x = date, y = Documents), col = "black")
+  p <- p + geom_point(data = dfm, aes(x = date, y = Documents), col = "black")
+  p <- p + scale_x_continuous(breaks=seq(min(dfm$date), max(dfm$date), 10))
+  p <- p + ylab("Title count (n)")
+  p <- p + xlab("Year")
+  p <- p + ggtitle(paste(catal, " ", minyear, "-", maxyear, sep = ""))
+  print(p)
+
+```
+
+---
+
+### Fig. 7B: Publishing activity and riksdagar: Fennica
+
+```{r Fig7B, echo=FALSE, message=FALSE, warning=FALSE, fig.width=15, fig.height=5}
+minyear <- 1760
+maxyear <- 1860
+catal <- "Fennica"
+
+df00 <- df.full %>% filter(publication_year >= minyear & publication_year <= maxyear)
+
+library(magrittr)
+library(ggplot2)
+library(dplyr)
+library(ggplot2)
+library(reshape2)
+
+  # Use timeinterval year intervals
+  dfsel <- subset(df00, catalog == catal)
+
+  df <- df00
+  df <- subset(df, catalog == catal)
+  df <- subset(df, publication_year >= minyear & publication_year <= maxyear)
+  df <- subset(dfsel, publication_year >= minyear & publication_year <= maxyear)
+
+  timeinterval <- 1
+  df$timeunit <- round(df$publication_year/timeinterval)*timeinterval
+
+  df$unity <- rep(1, nrow(df))
+  publications <- tapply(df$unity, list(df$timeunit), sum)
+
+  publications[is.na(publications)] <- 0 # Set NAs to 0
+  publications <- publications/timeinterval # Instead of decadal sum, use average annual output 
+  dfm <- melt(publications) 
+  names(dfm) <- c("Time", "Documents")
+  dfm <- transform(dfm, date = as.numeric(as.character(Time)))
+  ymin <- min(dfm$Documents)
+  ymax <- max(dfm$Documents)
+
+  rect_left <- c(min(na.omit(dfm$date)),
+               1710-.5, 1710+.5, #
+               1713-.5, 1714+.5, #
+
+               1719-.5, 1719+.5, # Stockholm 20 januari 1719 1 juni 1719
+               1734-.5, 1734+.5, # Stockholm 14 maj 1734 14 december 1734
+               1765-.5, 1766+.5, # Stockholm 21 februari 1765 21 oktober 1766
+               1769-.5, 1770+.5, # Norrköping & Stockholm 22 april 1769 5 februari 1770
+               1771-.5, 1772+.5, # Stockholm 19 juni 1771 12 september 1772
+
+               1778-.5, 1779+.5, #
+               1786-.5, 1786+.5, #
+               1789-.5, 1789+.5, #
+
+               1792-.5, 1792+.5, # Gävle 26 januari 1792 24 februari 1792
+
+               1800-.5, 1800+.5, #
+               1809-.5, 1810+.5, #
+               1812-.5, 1812+.5, #
+               1815-.5, 1815+.5, #
+               1817-.5, 1818+.5, #
+               1823-.5, 1823+.5, #
+               1828-.5, 1830+.5, #
+
+               max(na.omit(dfm$date)))
+
+  rectangles <- data.frame(
+    xmin = rect_left[-length(rect_left)],
+    xmax = rect_left[-1],
+    ymin = ymin,
+    ymax = ymax
+    )
+
+  rectangles$shade <- rep(c("Background", "Highlight"),
+  		          length = nrow(rectangles))
+
+  riksplace <- c(rep("Unknown", 2), "Stockholm", "Stockholm", "Stockholm", "Norrköping", "Stockholm", rep("Unknown", 3), "Gävle", rep("Unknown", 7))
   cols <- c("white", "gray", "darkgray")
@@
   p <- p + ggtitle(paste(catal, " ", minyear, "-", maxyear, sep = ""))  
-  print(p)
-```
-
----
-
-### Fig. 8: Publishing activity and riksdagar: Fennica
-
-```{r riksdar_fennica, echo=FALSE, message=FALSE, warning=FALSE, fig.width=15, fig.height=5}
-minyear <- 1760
-maxyear <- 1860
-catal <- "Fennica"
-
-df00 <- df.full %>% filter(publication_year >= minyear & publication_year <= maxyear)
-
-library(magrittr)
-library(ggplot2)
-library(dplyr)
-library(ggplot2)
-library(reshape2)
-
-  # Use timeinterval year intervals
-  dfsel <- subset(df00, catalog == catal)
-
-  df <- df00
-  df <- subset(df, catalog == catal)
-  df <- subset(df, publication_year >= minyear & publication_year <= maxyear)
-  df <- subset(dfsel, publication_year >= minyear & publication_year <= maxyear)
-
-  timeinterval <- 1
-  df$timeunit <- round(df$publication_year/timeinterval)*timeinterval
-
-  df$unity <- rep(1, nrow(df))
-  publications <- tapply(df$unity, list(df$timeunit), sum)
-
-  publications[is.na(publications)] <- 0 # Set NAs to 0
-  publications <- publications/timeinterval # Instead of decadal sum, use average annual output 
-  dfm <- melt(publications) 
-  names(dfm) <- c("Time", "Documents")
-  dfm <- transform(dfm, date = as.numeric(as.character(Time)))
-  ymin <- min(dfm$Documents)
-  ymax <- max(dfm$Documents)
-
-  rect_left <- c(min(na.omit(dfm$date)),
-               1710-.5, 1710+.5, #
-               1713-.5, 1714+.5, #
-
-               1719-.5, 1719+.5, # Stockholm 20 januari 1719 1 juni 1719
-               1734-.5, 1734+.5, # Stockholm 14 maj 1734 14 december 1734
-               1765-.5, 1766+.5, # Stockholm 21 februari 1765 21 oktober 1766
-               1769-.5, 1770+.5, # Norrköping & Stockholm 22 april 1769 5 februari 1770
-               1771-.5, 1772+.5, # Stockholm 19 juni 1771 12 september 1772
-
-               1778-.5, 1779+.5, #
-               1786-.5, 1786+.5, #
-               1789-.5, 1789+.5, #
-
-               1792-.5, 1792+.5, # Gävle 26 januari 1792 24 februari 1792
-
-               1800-.5, 1800+.5, #
-               1809-.5, 1810+.5, #
-               1812-.5, 1812+.5, #
-               1815-.5, 1815+.5, #
-               1817-.5, 1818+.5, #
-               1823-.5, 1823+.5, #
-               1828-.5, 1830+.5, #
-
-               max(na.omit(dfm$date)))
-
-  rectangles <- data.frame(
-    xmin = rect_left[-length(rect_left)],
-    xmax = rect_left[-1],
-    ymin = ymin,
-    ymax = ymax
-    )
-
-  rectangles$shade <- rep(c("Background", "Highlight"),
-  		          length = nrow(rectangles))
-
-  riksplace <- c(rep("Unknown", 2), "Stockholm", "Stockholm", "Stockholm", "Norrköping", "Stockholm", rep("Unknown", 3), "Gävle", rep("Unknown", 7))
-  cols <- c("white", "gray", "darkgray")
-  rectangles$place <- rectangles$shade
-  rectangles$place[rectangles$place == "Highlight"] <- riksplace
-  rectangles$place[rectangles$place == "Background"] <- "" 
-  rectangles$shade <- factor(rectangles$shade)
-
-  # Draw Figure
-  theme_set(theme_bw(20))
-  p <- ggplot() +
-         geom_rect(data = rectangles, 
-           aes(xmin=xmin, xmax=xmax,
-	       ymin=ymin, ymax=ymax,
-	       fill=shade), alpha=0.8) +
-         scale_fill_manual(values = cols) +
-	 guides(fill = "none")
-
-  p <- p + geom_text(data = rectangles, angle = 90, aes(x=xmin + .5, y=.9*ymax, label=place), size = 6)
-
-  p <- p + geom_line(data = dfm, aes(x = date, y = Documents), col = "black")
-  p <- p + geom_point(data = dfm, aes(x = date, y = Documents), col = "black")
-  p <- p + scale_x_continuous(breaks=seq(min(dfm$date), max(dfm$date), 10))
-  p <- p + ylab("Title count (n)")
-  p <- p + xlab("Year")
-  p <- p + ggtitle(paste(catal, " ", minyear, "-", maxyear, sep = ""))  
   p <- p + xlim(c(minyear, maxyear))
@@
 
-### Fig 9A: Fennica: Publishers in Swedish University towns (and Finland)
-
-```{r publishers2-finland, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=7, fig.width=15}
+### Fig 8: Publishers in Swedish University towns (Fennica)
+
+Turku, Vaasa and Vyborg from Fennica; Stockholm, Lund, Uppsala, Greifswald, Tartu from Kungliga.
+
+```{r Fig8, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=7, fig.width=15}
 df <- df0
@@
        ylab("Unique publishers (n)") +
-       scale_fill_brewer(palette="Spectral") +       
+       scale_fill_brewer(palette="Greys") +       
        guides(fill = guide_legend(reverse = FALSE, title = "")) +
@@
 print(p)
-
-```
-
-### Fig 9B: Kungliga: Publishers in Swedish University towns (and Finland)
-
-```{r kungliga9b, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=7, fig.width=15}
+```
+
+### Fig 9: Publishers in Swedish University towns (Kungliga)
+
+All towns from Kungliga.
+
+```{r Fig9, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=7, fig.width=15}
 df <- df0
@@
 
-```{r publishers4-fennica, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=6, fig.width=12}
+```{r Fig10, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=6, fig.width=12}
 library(dplyr)
-catalogue = "Fennica"
+catalogue <- "Fennica"
 place <- "Vaasa"
@@
 df <- df0 %>% filter(catalog == catalogue & publication_place == place) %>%	
-        filter(publication_year >= minyear & publication_year <= maxyear)
-
-p <- ggplot() + ggtitle("Fig 10: to be added")
-
-# TITLE COUNT
-#theme_set(theme_bw(20))
-#p <- ggplot(npub, aes(x = publication_decade, y = publisher)) +
-#      geom_point(aes(size = n)) + 
-#      #geom_line(aes(color = publisher), size = 2) +
-#      #geom_smooth(aes(fill = publisher)) +
-#      # geom_bar(stat = "identity", position = "stack", aes(fill = publisher)) #+ 
-#       xlab("Year") +
-#       ylab("") +
-#       guides(size = guide_legend(title = "Title count (n)"))
-#       #ggtitle(paste("Title count per publisher (", place, "/", catalogue, ")"#, sep = ""))
+        filter(publication_year >= minyear & publication_year <= maxyear) %>%
+	group_by(publication_year) %>% 
+	tally()
+
+p <- ggplot(df, aes(x = publication_year, y = n)) +
+     geom_bar(stat = "identity") +
+     ggtitle("") +
+     xlab("Publication year") +
+     ylab("Title count")
 
@@
 
-```{r publishers-fennica-11, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=6, fig.width=12}
+```{r Fig11, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=6, fig.width=12}
 library(dplyr)
@@
 
-```{r percapita, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
+```{r Fig12, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
 # Read historical population sizes
@@
 
-### Fig. 13: Octavo paper consumption
+### Fig. 13: Title count (absolute)
+
+```{r Fig13, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
+minyear <- 1640
+maxyear <- 1828
+
+# Take cities from Kungliga except Turku
+cat <- "Kungliga"
+df1 <- df0 %>% filter(publication_place %in% setdiff(cities, "Turku")) %>%
+      	      filter(catalog == cat) %>%
+              filter(publication_decade %in% pop$publication_decade) %>%
+	      select(publication_decade, publication_place) %>%	      
+	      group_by(publication_decade, publication_place) %>%
+	      summarise(n = n())
+
+# Take cities from Fennica for Turku
+cat <- "Fennica"
+df2 <- df0 %>% filter(publication_place %in% "Turku") %>%
+      	      filter(catalog == cat) %>%
+              filter(publication_decade %in% pop$publication_decade) %>%
+	      select(publication_decade, publication_place) %>%	      
+	      group_by(publication_decade, publication_place) %>%
+	      summarise(n = n())
+
+df <- bind_rows(df1, df2)
+
+p <- ggplot(df, aes(x = publication_decade, y = n)) +
+       geom_line(aes(linetype = publication_place), size = 1) +
+       geom_point(aes(shape = publication_place), size = 5) +
+       xlab("Publication decade") +
+       ylab("Title count per capita (n)") +
+       ggtitle("Title count per capita") +
+       guides(shape = guide_legend(title = "Place")) +
+       guides(linetype = guide_legend(title = "Place")) 
+print(p)
+```
+
+---
+
+### Fig. 14: Octavo paper consumption
 
@@
 
-```{r octavo, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
+```{r Fig14, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
 # Take cities from Kungliga except Turku
@@
 
-### Fig. 14: Octavo title length (word count)
+### Fig. 15: Octavo title length (word count)
 
@@
 Göteborg and Linköping. According to Kungliga, except Turku from
-Fennica. Only for octavo.
-
-```{r octavo2, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
+Fennica.
+
+```{r Fig15, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
 # Take cities from Kungliga except Turku
 cat <- "Kungliga"
-df1 <- df0 %>% filter(publication_place %in% setdiff(cities, "Turku")) %>%
-      	       filter(catalog == cat & gatherings == "8vo") %>%
+
+df00 <- df.full %>% filter(publication_year >= 1640 & publication_year <= 1850)
+
+df1 <- df00 %>% filter(publication_place %in% setdiff(cities, "Turku")) %>%
+      	       filter(catalog == cat) %>%
 	       group_by(publication_decade, publication_place) %>%
@@
 cat <- "Fennica"
-df2 <- df0 %>% filter(publication_place %in% "Turku") %>%
-      	       filter(catalog == cat & gatherings == "8vo") %>%
+df2 <- df00 %>% filter(publication_place %in% "Turku") %>%
+      	       filter(catalog == cat) %>%
 	       group_by(publication_decade, publication_place) %>%
@@
 df <- bind_rows(df1, df2)
+
+df$publication_place[!df$publication_place == "Stockholm"] <- "Other"
 
@@
        ylab("Title length (words)") +
-       ggtitle("Octavo: mean title length") +
+       ggtitle("Mean title length") +
        guides(shape = guide_legend(title = "Place")) +
@@
 
-### Fig 15: Language use in Turku, Stockholm, Uppsala and Lund
-
-```{r language-perc2, echo=FALSE, message=FALSE, warning=FALSE, fig.width=20, fig.height=12}
+### Fig 16: Language use in Turku, Stockholm, Uppsala and Lund
+
+```{r Fig16, echo=FALSE, message=FALSE, warning=FALSE, fig.width=20, fig.height=12}
 pics <- list()
@@
 
-### Fig. 16: Topic richness per language (Fennica)
-
-```{r topics232, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, fig.show="hold"}
+### Fig. 17: Topic richness per language (Fennica)
+
+```{r Fig17, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, fig.show="hold"}
 catalogue <- "Fennica"
@@
 
-### Fig. 17: Temporary sermons in Latin and Swedish
-
-```{r topics882, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6}
+### Fig. 18: Temporary sermons in Latin and Swedish
+
+```{r Fig18, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6}
   sel <- c("hautajaiset", "häät", "juhlamenot")
@@
 
-### Fig. 18: Devotional literature (catechisms, hymns, prayers, etc.)
+### Fig. 19: Devotional literature (catechisms, hymns, prayers, etc.)
 
@@
 
-```{r topics12122, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, fig.show="hold"}
+```{r Fig19, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, fig.show="hold"}
 sel <- c("virret","arkkiveisut","hartauskirjat","katekismukset","rukouspäivät","saarnat","aapiset","rukoukset","rukous","hengelliset laulut","hartauspuheet","virsikirjat")
@@
 
-### Fig. 19: Publisher per city over time
-
-```{r publishersper, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, fig.show="hold"}
-# Selected catalogue with selected decades
-catalogue <- "Fennica"
-
-df <- filter(df0, catalog == catalogue &
-     		    publication_decade >= 1640 &
-		    publication_decade <= 1828)
-
-top.places <- names(top(df, "publication_place", 5))
-
-df <- df %>%
-      filter(publication_place %in% top.places) %>% 
-      group_by(publication_decade, publication_place) %>%
-      summarise(n = length(unique(na.omit(publisher))))
-
-  theme_set(theme_bw(20))
-  p <- ggplot(df, aes(x = publication_decade, y = n, shape = publication_place)) +
-       geom_point(size = 5) +
-       geom_line(size = 1, aes(linetype = publication_place)) +
-       scale_color_brewer(palette="Greys") +
-       #scale_fill_brewer(palette="Greys") +                     
-       xlab("Publication year") +
-       ylab("Publishers (n)") +
-       guides(shape = guide_legend("Place")) +
-       guides(linetype = guide_legend("Place")) +
-       ggtitle(paste(catalogue))
-  print(p)
-
-```
-
 ## Session info

### 2017-02-14 inst/examples/20170201-manuscript.Rmd
updateing analyses

@@
 df <- df0 %>% filter(publication_year >= 1640 & publication_year <= 1911) %>%
-              group_by(publication_decade) %>%
+              group_by(catalog, publication_decade) %>%
               summarize(mean_title_length = mean(title_length_wordcount),
@@
        xlab("Publication decade") +
-       ggtitle(paste("Title length (", catal, ")", sep = ""))
+       ggtitle(paste("Mean title length (", catal, ")", sep = ""))
 
@@
   rectangles$shade <- rep(c("Background", "Highlight"), length = nrow(rectangles))
-
   riksplace <- c(rep("Unknown", 2), "Stockholm", "Stockholm", "Stockholm", "Norrköping", "Stockholm", rep("Unknown", 3), "Gävle", rep("Unknown", 7))
@@
 
-  rectangles$shade <- rep(c("Background", "Highlight"),
-  		          length = nrow(rectangles))
-
+  rectangles$shade <- rep(c("Background", "Highlight"), length = nrow(rectangles))
   riksplace <- c(rep("Unknown", 2), "Stockholm", "Stockholm", "Stockholm", "Norrköping", "Stockholm", rep("Unknown", 3), "Gävle", rep("Unknown", 7))
-  cols <- c("white", "gray", "darkgray")
+  cols <- c("white", "lightgray", "gray", "darkgray")
+  rectangles$shade[rectangles$shade == "Highlight"] <- rep(cols, length(which(rectangles$shade == "Highlight")))
+  rectangles$shade <- factor(rectangles$shade)
+
   rectangles$place <- rectangles$shade
@@
   rectangles$place[rectangles$place == "Background"] <- ""
-  rectangles$shade <- factor(rectangles$shade)
 
@@
 	       fill=shade), alpha=0.8) +
-         scale_fill_manual(values = cols) +
+         scale_fill_brewer(palette="Greys") +
 	 guides(fill = "none")
@@
 p <- ggplot(npub, aes(x = publication_decade, y = n)) +
-       geom_bar(stat = "identity", position = "stack",
+       geom_bar(stat = "identity", position = "stack", color = "black",
        		    aes(fill = publication_place)) + 
@@
 
-With percentage of all books that were not published by the printing house of the court.
-
 ```{r Fig10, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=6, fig.width=12}
@@
      ggtitle("") +
+     scale_x_continuous(breaks = seq(minyear, maxyear, 5)) +
      xlab("Publication year") +
@@
        xlab("Publication decade") +
-       ylab("Title count per capita (n)") +
-       ggtitle("Title count per capita") +
+       ylab("Title count (n)") +
+       ggtitle("Title count (absolute)") +
        guides(shape = guide_legend(title = "Place")) +
@@
 p <- ggplot(df, aes(x = publication_decade, y = mean_title_length)) +
-       geom_line(aes(linetype = publication_place), size = 1) +
-       geom_point(aes(shape = publication_place), size = 5) +
+       geom_bar(aes(fill = publication_place), position = "dodge", stat = "identity") +
        xlab("Publication year") +
@@
        ggtitle("Mean title length") +
-       guides(shape = guide_legend(title = "Place")) +
-       guides(linetype= guide_legend(title = "Place"))        
-print(p)
+       scale_fill_manual(values = c("darkgray", "black")) +
+       guides(fill = guide_legend(title = "Place", reverse = TRUE))        
+print(p)
+
 ```

### 2017-02-14 inst/examples/20170201-manuscript.Rmd
updateing analyses

@@
 
-for (catal in unique(df$catalog)) {
-  dfs <- subset(df, catalog == catal)
-  p <- ggplot(dfs, aes(x = publication_decade, y = mean_title_length)) +
-       geom_point(aes(size = n), size = 5) +
-       geom_line(size = 1) +
+  p <- ggplot(df, aes(x = publication_decade, y = mean_title_length, fill = catalog)) +
+       geom_bar(stat = "identity", color = "black", position = "dodge") +
+       #geom_point(aes(size = n), size = 5) +
+       #geom_line(size = 1) +
+       scale_fill_manual(values = c("darkgray", "black")) +
+       guides(fill = guide_legend(title = "Place", reverse = TRUE)) +       
        ylab("Title length (word count)") +
@@
   print(p)
-}
+
 ```
@@
 
-### Fig 6: Publishing activity over time
+### Fig 6: Publishing activity over time (Kungliga)
 
@@
 df$period <- gsub(",", ",", df$period)
+df$period <- gsub("\\]", ",", df$period)
 
@@
 
-  p <- p + geom_text(data = rectangles, angle = 90, aes(x=xmin + .5, y=.9*ymax, label=place), size = 6)
+  # p <- p + geom_text(data = rectangles, angle = 90, aes(x=xmin + .5, y=.9*ymax, label=place), size = 6)
 
@@
      xlab("Publication year") +
-     ylab("Title count")
+     ylab("Title count (n)")
 

### 2017-02-15 inst/examples/20170201-manuscript.Rmd
ok

@@
 
-```{r 201606krakow-init, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, cache=TRUE}
+```{r init, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}
 # Default time span
@@
 		  )
-  #p <- p + facet_grid(. ~ catalog)		  
   p <- p + ggtitle(catal)
@@
 
-### Fig 4: Average title length (word count)
-
-```{r Fig4, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=7, fig.width=15}
-# Analysis time window
-df <- df0 %>% filter(publication_year >= 1640 & publication_year <= 1911) %>%
-              group_by(catalog, publication_decade) %>%
-              summarize(mean_title_length = mean(title_length_wordcount),
+### Fig 4: Median title length (word count)
+
+Loess smoothing.
+
+```{r Fig4, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=14, fig.width=7}
+df <- df.full %>% filter(publication_year >= 1640 &
+                         publication_year <= 1911) %>%
+              group_by(catalog, publication_year) %>%
+              summarize(title_length = median(title_length_wordcount),
 	      		n = n())
 
-  p <- ggplot(df, aes(x = publication_decade, y = mean_title_length, fill = catalog)) +
-       geom_bar(stat = "identity", color = "black", position = "dodge") +
-       #geom_point(aes(size = n), size = 5) +
-       #geom_line(size = 1) +
-       scale_fill_manual(values = c("darkgray", "black")) +
-       guides(fill = guide_legend(title = "Place", reverse = TRUE)) +       
-       ylab("Title length (word count)") +
-       xlab("Publication decade") +
-       ggtitle(paste("Mean title length (", catal, ")", sep = ""))
-
-  print(p)
-
+pics <- list()
+for (catal in unique(df$catalog)) {
+  pics[[catal]] <- ggplot(subset(df, catalog == catal), aes(x = publication_year, y = title_length)) +
+       geom_point(aes(size = n)) +
+       geom_smooth(color = "black") +
+       ggtitle(paste("Mean title length (", catal, ")", sep = "")) + 
+       xlab("Publication year") +
+       ylab("Title length (word count)")
+}
+
+library(gridExtra)
+grid.arrange(pics[[1]], pics[[2]], nrow = 2)
 ```
@@
 
-### Fig. 7A: Publishing activity and riksdagar: Kungliga
-
-```{r Fig7A, echo=FALSE, message=FALSE, warning=FALSE, fig.width=15, fig.height=5}
+### Fig. 7: Publishing activity and riksdagar: Kungliga
+
+```{r Fig7, echo=FALSE, message=FALSE, warning=FALSE, fig.width=15, fig.height=5}
 
@@
 
-```
-
----
-
-### Fig. 7B: Publishing activity and riksdagar: Fennica
-
-```{r Fig7B, echo=FALSE, message=FALSE, warning=FALSE, fig.width=15, fig.height=5}
-minyear <- 1760
-maxyear <- 1860
-catal <- "Fennica"
-
-df00 <- df.full %>% filter(publication_year >= minyear & publication_year <= maxyear)
-
-library(magrittr)
-library(ggplot2)
-library(dplyr)
-library(ggplot2)
-library(reshape2)
-
-  # Use timeinterval year intervals
-  dfsel <- subset(df00, catalog == catal)
-
-  df <- df00
-  df <- subset(df, catalog == catal)
-  df <- subset(df, publication_year >= minyear & publication_year <= maxyear)
-  df <- subset(dfsel, publication_year >= minyear & publication_year <= maxyear)
-
-  timeinterval <- 1
-  df$timeunit <- round(df$publication_year/timeinterval)*timeinterval
-
-  df$unity <- rep(1, nrow(df))
-  publications <- tapply(df$unity, list(df$timeunit), sum)
-
-  publications[is.na(publications)] <- 0 # Set NAs to 0
-  publications <- publications/timeinterval # Instead of decadal sum, use average annual output 
-  dfm <- melt(publications) 
-  names(dfm) <- c("Time", "Documents")
-  dfm <- transform(dfm, date = as.numeric(as.character(Time)))
-  ymin <- min(dfm$Documents)
-  ymax <- max(dfm$Documents)
-
-  rect_left <- c(min(na.omit(dfm$date)),
-               1710-.5, 1710+.5, #
-               1713-.5, 1714+.5, #
-
-               1719-.5, 1719+.5, # Stockholm 20 januari 1719 1 juni 1719
-               1720-.5, 1720+.5, # Stockholm 20 januari 1719 1 juni 1719
-               1723-.5, 1723+.5, # Stockholm 20 januari 1719 1 juni 1719
-
-               1726-.5, 1727+.5, # Stockholm 20 januari 1719 1 juni 1719
-
-               1731-.5, 1731+.5, # Stockholm 20 januari 1719 1 juni 1719
-
-               1734-.5, 1734+.5, # Stockholm 14 maj 1734 14 december 1734
-
-               1738-.5, 1739+.5, #
-
-               1740-.5, 1741+.5, #
-
-               1742-.5, 1743+.5, #
-               1746-.5, 1747+.5, #
-
-               1751-.5, 1752+.5, #
-               1755-.5, 1756+.5, #
-               1760-.5, 1762+.5, #
-
-               1765-.5, 1766+.5, # Stockholm 21 februari 1765 21 oktober 1766
-               1769-.5, 1770+.5, # Norrköping & Stockholm 22 april 1769 5 februari 1770
-               1771-.5, 1772+.5, # Stockholm 19 juni 1771 12 september 1772
-
-               1778-.5, 1779+.5, #
-               1786-.5, 1786+.5, #
-               1789-.5, 1789+.5, #
-
-               1792-.5, 1792+.5, # Gävle 26 januari 1792 24 februari 1792
-
-               1800-.5, 1800+.5, #
-               1809-.5, 1810+.5, #
-               1812-.5, 1812+.5, #
-               1815-.5, 1815+.5, #
-               1817-.5, 1818+.5, #
-               1823-.5, 1823+.5, #
-               1828-.5, 1830+.5, #
-
-               max(na.omit(dfm$date)))
-
-  rectangles <- data.frame(
-    xmin = rect_left[-length(rect_left)],
-    xmax = rect_left[-1],
-    ymin = ymin,
-    ymax = ymax
-    )
-
-  rectangles$shade <- rep(c("Background", "Highlight"), length = nrow(rectangles))
-  riksplace <- c(rep("Unknown", 2), "Stockholm", "Stockholm", "Stockholm", "Norrköping", "Stockholm", rep("Unknown", 3), "Gävle", rep("Unknown", 7))
-  cols <- c("white", "lightgray", "gray", "darkgray")
-  rectangles$shade[rectangles$shade == "Highlight"] <- rep(cols, length(which(rectangles$shade == "Highlight")))
-  rectangles$shade <- factor(rectangles$shade)
-
-  rectangles$place <- rectangles$shade
-  rectangles$place[rectangles$place == "Highlight"] <- riksplace
-  rectangles$place[rectangles$place == "Background"] <- ""
-
-  # Draw Figure
-  theme_set(theme_bw(20))
-  p <- ggplot() +
-         geom_rect(data = rectangles, 
-           aes(xmin=xmin, xmax=xmax,
-	       ymin=ymin, ymax=ymax,
-	       fill=shade), alpha=0.8) +
-         scale_fill_brewer(palette="Greys") +
-	 guides(fill = "none")
-
-  # p <- p + geom_text(data = rectangles, angle = 90, aes(x=xmin + .5, y=.9*ymax, label=place), size = 6)
-
-  p <- p + geom_line(data = dfm, aes(x = date, y = Documents), col = "black")
-  p <- p + geom_point(data = dfm, aes(x = date, y = Documents), col = "black")
-  p <- p + scale_x_continuous(breaks=seq(min(dfm$date), max(dfm$date), 10))
-  p <- p + ylab("Title count (n)")
-  p <- p + xlab("Year")
-  p <- p + ggtitle(paste(catal, " ", minyear, "-", maxyear, sep = ""))  
-  p <- p + xlim(c(minyear, maxyear))
-  print(p)
 ```

### 2017-02-15 inst/examples/20170201-manuscript.Rmd
ok

@@
 
-```{r Fig3, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=9, fig.height=5, fig.show="hold", out.width="400px"}
-
+```{r Fig3, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=9, fig.height=5, fig.show="hold"}
+pics <- list()
 for (catal in unique(df00$catalog)) {
@@
   p <- p + scale_fill_manual(values = c("darkgreen", "darkgray"))  	 
-  p <- p + ggtitle("Paper consumption in time by gatherings")
   p <- p + xlab("Year")
@@
 		  )
-  p <- p + ggtitle(catal)
-  print(p)
-}
+  p <- p + ggtitle(paste("Paper consumption (", catal, ")", sep = ""))
+  pics[[catal]] <- p
+}
+```
+
+```{r Fig3A, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=9, fig.height=5}
+print(pics[[1]])
+```
+
+---
+
+```{r Fig3B, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=9, fig.height=5}
+print(pics[[2]])
 ```
@@
 
-```{r Fig4, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=14, fig.width=7}
+```{r Fig4, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=7, fig.width=16}
 df <- df.full %>% filter(publication_year >= 1640 &
@@
 library(gridExtra)
-grid.arrange(pics[[1]], pics[[2]], nrow = 2)
+grid.arrange(pics[[1]], pics[[2]], nrow = 1)
 ```
@@
 
-```{r Fig5, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=18, fig.height=10}
+```{r Fig5, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=16, fig.height=8}
 pics <- list()
@@
 
+---
+
 ### Fig 9: Publishers in Swedish University towns (Kungliga)
@@
 
+---
+
 ### Fig 10: Publications in Vaasa in Fennica, 1750-1828
 
-```{r Fig10, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=6, fig.width=12}
+```{r Fig10, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=5, fig.width=10}
 library(dplyr)
@@
 
-```{r Fig11, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=6, fig.width=12}
+```{r Fig11, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=5, fig.width=10}
 library(dplyr)
@@
 
-```{r Fig16, echo=FALSE, message=FALSE, warning=FALSE, fig.width=20, fig.height=12}
+```{r Fig16, echo=FALSE, message=FALSE, warning=FALSE, fig.width=14, fig.height=7}
 pics <- list()

### 2017-02-15 inst/examples/20170201-manuscript.Rmd
PDF

@@
 ---
-title: "Printing in a Periphery: a Quantitative Study of Finnish Knowledge Production, 1640-1828"
+title: "Patterns in Knowledge Production: Political Ruptures and Imperial Dynamics Shaping Public Discourse in Sweden and Finland, 1640–1828"
 author: "Mikko Tolonen, Jani Marjanen, Hege Roivainen, Leo Lahti"
@@
 
-```{r Fig4, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=7, fig.width=16}
+```{r Fig4, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=5, fig.width=11}
 df <- df.full %>% filter(publication_year >= 1640 &
@@
 
-```{r Fig5, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=16, fig.height=8}
+```{r Fig5, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=14, fig.height=6}
 pics <- list()
@@
 
-```{r Fig6, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=4}
+```{r Fig6, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=4}
 library(magrittr)
@@
 
-```{r Fig7, echo=FALSE, message=FALSE, warning=FALSE, fig.width=15, fig.height=5}
+```{r Fig7, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=4}
 
@@
 
-```{r Fig8, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=7, fig.width=15}
+```{r Fig8, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=5, fig.width=12}
 df <- df0
@@
 
-```{r Fig9, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=7, fig.width=15}
+```{r Fig9, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=5, fig.width=12}
 df <- df0
@@
 
-```{r Fig16, echo=FALSE, message=FALSE, warning=FALSE, fig.width=14, fig.height=7}
+```{r Fig16, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6}
 pics <- list()
@@
 
-```{r Fig17, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, fig.show="hold"}
+```{r Fig17, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5, fig.show="hold"}
 catalogue <- "Fennica"
@@
 
-```{r Fig18, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6}
+```{r Fig18, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
   sel <- c("hautajaiset", "häät", "juhlamenot")

### 2017-02-15 inst/examples/20170201-manuscript.Rmd
ok

@@
 
-```{r Fig4, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=5, fig.width=11}
+```{r Fig4, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=4, fig.width=11}
 df <- df.full %>% filter(publication_year >= 1640 &
@@
 
-```{r Fig5, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=14, fig.height=6}
+```{r Fig5, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=13, fig.height=6}
 pics <- list()
@@
 df$period <- gsub(",", ",", df$period)
-df$period <- gsub("\\]", ",", df$period)
+df$period <- gsub("\\]", "", df$period)
 
@@
 
-```{r Fig7, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=4}
+```{r Fig7, echo=FALSE, message=FALSE, warning=FALSE, fig.width=11, fig.height=4}
 

### 2017-03-17 inst/examples/20170201-manuscript.Rmd
publisher analyses updated

@@
   df <- subset(df, publication_year >= minyear & publication_year <= maxyear)
-
   df <- subset(dfsel, publication_year >= minyear & publication_year <= maxyear)
@@
   names(dfm) <- c("Time", "Documents")
-  dfm <- transform(dfm, date = as.numeric(as.character(Time)))
+  dfm <- base::transform(dfm, date = as.numeric(as.character(Time)))
   ymin = min(dfm$Documents)

### 2017-03-17 R/firstlib.R

@@ -1,4 +1,3 @@
-
 #' @import dplyr
 #' @importFrom bibliographica capitalize
 #' @importFrom bibliographica clean_publisher

### 2017-06-01 inst/examples/201705-Gaudeamus.Rmd
ok

---
title: "Gaudeamus 2017 Figures"
author: "Mikko Tolonen, Leo Lahti"
date: "`r Sys.Date()`"
output: 
  beamer_presentation
fontsize: 13pt
---

```{r init, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, cache=TRUE}
# Data files
input.data.file <- "df.combined.Gaudeamus2017.Rds"

# Default time span
library(ggmap)
library(gisfin)
library(stringr)
library(dplyr)
library(tidyr)
library(reshape2)
library(ggplot2)
library(bibliographica)
library(fennica)
library(sorvi)
library(devtools)
knitr::opts_chunk$set(echo = FALSE)
# knitr::opts_chunk$set(fig.path = "figure-201705-Gaudeamus/")
##knitr::opts_chunk$set(fig.path = "slides_201606_Krakow", dev="CairoPNG")
knitr::opts_chunk$set(fig.path = "figure-201705-Gaudeamus/", dev="CairoJPEG")

# Set locale
tmp <- Sys.setlocale(locale="UTF-8")

# Nice theme
theme_set(theme_bw(26))
```

```{r init2, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, cache=TRUE}
# Full combined catalogue (Fen + Kun) with marked duplicates
df.combined.preprocessed <- readRDS(input.data.file)
# Data with duplicates removed and years limited

min.year <- 1488
max.year <- 1828
df0 <- df.combined.preprocessed %>% filter(!remove) %>%
	   			    filter(publication_year >= min.year &
					   publication_year <= max.year)
```

---

### Data: bibliographic catalogues 1640-1828

**Fennica** Finnish National bibliography

- `r nrow(subset(df0, catalog == "Fennica" & publication_year >= 1640 & publication_year <= 1828))` documents 1640-1828

**Kungliga**  Swedish National bibliography

- `r nrow(subset(df0, catalog == "Kungliga" & publication_year >= 1640 & publication_year <= 1828))` documents 1640-1828

```{r, message=FALSE, warning=FALSE, fig.width=10, fig.height=3, echo=FALSE}
library(dplyr)
library(ggplot2)
theme_set(theme_bw(20))
df <- df0 %>% filter(publication_year >=1640 & publication_year <=1828) %>% group_by(catalog, publication_decade) %>% tally()
p <- ggplot(df, aes(x = publication_decade, y = n, color = catalog)) + 
       geom_point() + 
       geom_line() + 
       ylab("Documents (n)") + xlab("Publication year") +
       scale_color_manual(values = c("blue", "darkgreen")) +
       guides(color = guide_legend(reverse = TRUE, title = "")) #+ 
print(p)
```

---

### Rise of the octavo sized book as vehicle of Enlightenment

Paper consumption: document formats over time

```{r Gaudeamus-3, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=11, fig.height=13, dev="CairoJPEG"}
theme_set(theme_bw(22))
pics <- list()
for (catal in unique(df0$catalog)) {
  df2 <- df0 %>% filter(catalog == catal) %>% 
                 group_by(publication_decade, gatherings) %>% 
		 summarise(paper2 = sum(paper, na.rm = TRUE)/1e6, n = n()) 
  df2$paper <- df2$paper2; df2$paper2 <- NULL # Rename
  df2 <- filter(df2, gatherings %in% setdiff(names(which(table(df2$gatherings) >= 15)), "NA"))
  df2$highlight <- rep("Other", nrow(df2))
  df2$highlight[df2$gatherings == "8vo"] <- "Octavo"

  p <- ggplot(df2, aes(y = paper,
                       x = publication_decade,
		       shape = gatherings
		       ))		       
  p <- p + geom_point(size = 3)
  p <- p + geom_smooth(method = "loess", size = 1,
             aes(color = highlight, 
	          fill = highlight, 
		  linetype = gatherings), color = "black")
  p <- p + scale_color_manual(values = c("black", "lightgray"))
  p <- p + scale_fill_manual(values = c("black", "lightgray"))  	 
  p <- p + xlab("Vuosi")
  p <- p + ylab("Paperinkulutus (miljoonia arkkeja)")
  p <- p + guides(linetype = guide_legend(keywidth = 5, title = "Muoto"),
       	             shape = guide_legend(keywidth = 5, title = "Muoto"),
		     fill = guide_legend(title = "Korostus"),
		     color = guide_legend(title = "Korostus")
		     )
  p <- p + ylim(c(0, max(df2$paper, na.rm = TRUE)))
  p <- p + ggtitle(catal)
  p <- p + theme(plot.title = element_text(hjust = 0))
  pics[[catal]] <- p
}

library(cowplot)
# https://cran.r-project.org/web/packages/cowplot/vignettes/shared_legends.html

pics[[1]] <- pics[[1]] + xlab("")
prow <- plot_grid( 
           pics[[1]] + theme(legend.position="none"),
           pics[[2]] + theme(legend.position="none"),
           align = 'vh',
           #labels = c("Fennica", "Kungliga"),
           hjust = -1.1,
           vjust = 3,
	   label_size = 18,
           nrow = 2
           )
# extract the legend from one of the plots
# (clearly the whole thing only makes sense if all plots
# have the same legend, so we can arbitrarily pick one.)
legend <- get_legend(pics[[1]])

# add the legend to the row we made earlier. Give it one-third of the width
# of one plot (via rel_widths).
p <- plot_grid( prow, legend, rel_widths = c(3, .6))
print(p)
```

```{r Gaudeamus-Vaasa, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=11, fig.height=6, dev="CairoJPEG"}
library(dplyr)
theme_set(theme_bw(22))

df2 <- df.combined.preprocessed %>% filter(!is.na(publication_decade)) %>% 
       	       filter(catalog == "Fennica") %>%
       	       filter(publication_year >= 1760) %>%
       	       filter(publication_year <= 1919) %>% 
               filter(publication_place == "Vaasa") %>% 
	       group_by(publication_decade) %>% 
	       tally() %>% 
	       arrange(publication_decade)

p <- ggplot(df2, aes(y = n, x = publication_decade))		       
   p <- p + geom_bar(stat = "identity")
   p <- p + xlab("Vuosi")
   p <- p + ylab("Dokumenttia (n)")
   # Shift the bars so that each bar starts from the first year of that decade
   # for clarity. 
   p <- p + scale_x_continuous(breaks = c(1764,1809,1863,1917) - 4,
     	                       labels = c(1764,1809,1863,1917))
print(p)
```

```{r Gaudeamus-Turku, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=11, fig.height=6, dev="CairoJPEG"}
library(dplyr)
theme_set(theme_bw(22))
df2 <- df.combined.preprocessed %>% filter(!is.na(publication_decade)) %>% 
       	       filter(catalog == "Fennica") %>%
       	       filter(publication_year >= 1640) %>%
       	       filter(publication_year <= 1919) %>% 	       
               filter(publication_place == "Turku") %>% 
	       group_by(publication_decade) %>% 
	       tally() %>% 
	       arrange(publication_decade)

p <- ggplot(df2, aes(y = n, x = publication_decade))		       
   p <- p + geom_bar(stat = "identity")
   p <- p + xlab("Vuosi")
   p <- p + ylab("Dokumenttia (n)")
   # Shift the bars so that each bar starts from the first year of that decade
   # for clarity. 
   p <- p + scale_x_continuous(breaks = c(1640,1764,1809,1863, 1917) - 4,
     	                       labels = c(1640,1764,1809,1863, 1917))
print(p)
```

```{r Gaudeamus-Helsinki, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=11, fig.height=6, dev="CairoJPEG"}
library(dplyr)
theme_set(theme_bw(22))
df2 <- df.combined.preprocessed %>% filter(!is.na(publication_decade)) %>% 
       	       filter(catalog == "Fennica") %>%
       	       filter(publication_year >= 1740) %>%
       	       filter(publication_year <= 1919) %>% 	       
               filter(publication_place == "Helsinki") %>% 
	       group_by(publication_decade) %>% 
	       tally() %>% 
	       arrange(publication_decade)

p <- ggplot(df2, aes(y = n, x = publication_decade))		       
   p <- p + geom_bar(stat = "identity")
   p <- p + xlab("Vuosi")
   p <- p + ylab("Dokumenttia (n)")
   # Shift the bars so that each bar starts from the first year of that decade
   # for clarity. 
   p <- p + scale_x_continuous(breaks = c(1764,1809,1863, 1917) - 4,
     	                       labels = c(1764,1809,1863, 1917))
print(p)
```

```{r Gaudeamus-Suomi, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=11, fig.height=6, dev="CairoJPEG"}
library(dplyr)
theme_set(theme_bw(22))
df2 <- df.combined.preprocessed %>% filter(!is.na(publication_decade)) %>% 
       	       filter(catalog == "Fennica") %>%
       	       filter(country == "Finland") %>%	       
       	       filter(publication_year >= 1640) %>%
       	       filter(publication_year <= 1919) %>% 	       
	       group_by(publication_decade) %>% 
	       tally() %>% 
	       arrange(publication_decade)

p <- ggplot(df2, aes(y = n, x = publication_decade))		       
   p <- p + geom_bar(stat = "identity")
   p <- p + xlab("Vuosi")
   p <- p + ylab("Dokumenttia (n)")
   # Shift the bars so that each bar starts from the first year of that decade
   # for clarity. 
   p <- p + scale_x_continuous(breaks = c(1640,1764,1809,1863, 1917) - 4,
     	                       labels = c(1640,1764,1809,1863, 1917))
print(p)
```

```{r Gaudeamus-Suomi2, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=11, fig.height=6, dev="CairoJPEG"}
library(dplyr)
theme_set(theme_bw(22))
df2 <- df.combined.preprocessed
df2$publication_place[!df2$publication_place %in% c("Helsinki", "Turku", "Vaasa")] <- "Muu"
df2 <- df2 %>%
       	       filter(!is.na(publication_decade)) %>% 
       	       filter(catalog == "Fennica") %>%
       	       filter(country == "Finland") %>%
       	       filter(publication_year >= 1640) %>%
       	       filter(publication_year <= 1919) 
p <- ggplot(df2, aes(x = publication_decade)) +
   geom_bar(position = "stack", aes(y = ..count.., fill = publication_place), color = "black") +
   scale_fill_grey() +   
   xlab("Vuosi") +
   ylab("Dokumenttia (n)") +
   scale_x_continuous(breaks = c(1640, 1764, 1809, 1863, 1917),
     	              labels = c(1640, 1764, 1809, 1863, 1917)) +
   guides(fill = guide_legend(keywidth=1, title = "Julkaisupaikka")) +
   theme(legend.position = c(0.16, .7)) 
print(p)
```

### 2017-10-10 inst/examples/20160715-Krakow-Fennica.Rmd
manuscript figs added
sync

@@
 title: "Printing in a Periphery: a Quantitative Study of Finnish Knowledge Production, 1640-1828"
-author: "Mikko Tolonen, Jani Marjanen, Hege Roivainen, Leo Lahti"
+author: "Mikko Tolonen, Leo Lahti, Hege Roivainen, Jani Marjanen"
 date: "`r Sys.Date()`"

### 2017-10-10 inst/examples/analysis.R

@@ -24,6 +24,7 @@ library(rmarkdown)
 knitr::knit("20170201-manuscript.Rmd", encoding="UTF-8")
 render("20170201-manuscript.Rmd")
 
+stop("OK")
 
 #RM knitr::knit("20161117-manuscript.Rmd", encoding="UTF-8")
 #RM knitr::knit("20170125-Manuscript-FK.Rmd", encoding="UTF-8")

### 2017-10-10 inst/examples/20170201-manuscript.Rmd
color figures

@@
 title: "Patterns in Knowledge Production: Political Ruptures and Imperial Dynamics Shaping Public Discourse in Sweden and Finland, 1640–1828"
-author: "Mikko Tolonen, Jani Marjanen, Hege Roivainen, Leo Lahti"
+author: "Mikko Tolonen, Leo Lahti, Hege Roivainen, Jani Marjanen"
 date: "`r Sys.Date()`"
@@
 library(ggplot2)
-theme_set(theme_bw(20))
+# theme_set(theme_bw(20))
+
 df <- df0 %>% filter(publication_year >=1640 & publication_year <=1828) %>%

### 2017-10-10 inst/examples/analysis.R

@@ -24,8 +24,6 @@ library(rmarkdown)
 knitr::knit("20170201-manuscript.Rmd", encoding="UTF-8")
 render("20170201-manuscript.Rmd")
 
-stop("OK")
-
 #RM knitr::knit("20161117-manuscript.Rmd", encoding="UTF-8")
 #RM knitr::knit("20170125-Manuscript-FK.Rmd", encoding="UTF-8")
 #RM rmarkdown::render("manuscript-krakow.Rmd") # Manuscript draft

### 2017-10-10 inst/examples/20170201-manuscript.Rmd
stata palette

@@
 # Nice theme
-theme_set(theme_bw(26))
+# theme_set(theme_bw(26))
 
@@
 library(ggplot2)
+library(ggthemes)
 # theme_set(theme_bw(20))
+theme_set(theme_minimal(20))
 
@@
 	      summarise(n = length(unique(na.omit(publication_place))))
-p <- ggplot(df, aes(x = publication_decade, y = n, shape = catalog, linetype = catalog)) + 
+p <- ggplot(df, aes(x = publication_decade, y = n,
+       color = catalog, shape = catalog)) + 
        geom_point(size = 4) + 
@@
        ylab("Places (n)") + xlab("Publication year") +
-       scale_color_manual(values = c("blue", "darkgreen")) + 
-       guides(shape = guide_legend(title = "Catalog", reverse = TRUE)) +
-       guides(linetype = guide_legend(title = "Catalog", reverse = TRUE)) +       
-       ggtitle("Unique publication places")
+       # scale_color_manual(values = c("blue", "darkgreen")) + 
+       guides(linetype = "none") +
+       guides(shape = guide_legend(title = "Catalog", reverse = TRUE),
+              color = guide_legend(title = "Catalog", reverse = TRUE)) +              
+       ggtitle("Unique publication places") +
+       scale_color_stata()
 print(p)
@@
 theme_set(theme_bw(20))
-df <- df0 %>% filter(publication_year >=1640 & publication_year <=1828) %>% group_by(catalog, publication_decade) %>% tally()
-p <- ggplot(df, aes(x = publication_decade, y = n, shape = catalog, linetype = catalog)) + 
+df <- df0 %>% filter(publication_year >=1640 & publication_year <=1828) %>%
+        group_by(catalog, publication_decade) %>% tally()
+p <- ggplot(df, aes(x = publication_decade, y = n,
+                    shape = catalog,
+		    color = catalog)) + 
        geom_point(size = 4) + 
@@
        ylab("Documents (n)") + xlab("Publication year") +
-       scale_color_manual(values = c("blue", "darkgreen")) +
-       guides(shape = guide_legend(title = "Catalog", reverse = TRUE)) +
-       guides(linetype = guide_legend(title = "Catalog", reverse = TRUE)) +  
-       ggtitle("Title count")
+       #scale_color_manual(values = c("blue", "darkgreen")) +
+       guides(
+         shape = guide_legend(title = "Catalog", reverse = TRUE),
+         color = guide_legend(title = "Catalog", reverse = TRUE)	 
+       ) +
+       ggtitle("Title count") +
+       scale_color_stata()
 print(p)
@@
   	       shape = gatherings,
-		       linetype = gatherings))		       
+		       color = gatherings))		       
   p <- p + geom_point(size = 4)
@@
          aes(color = highlight, fill = highlight))
-  p <- p + scale_color_manual(values = c("darkgreen", "darkgray"))
-  p <- p + scale_fill_manual(values = c("darkgreen", "darkgray"))  	 
+  #p <- p + scale_color_manual(values = c("darkgreen", "darkgray"))
+  #p <- p + scale_fill_manual(values = c("darkgreen", "darkgray"))  	 
   p <- p + xlab("Year")
@@
   p <- p + ylim(c(0, max(na.omit(df2$paper))))
-  p <- p + guides(linetype = guide_legend(keywidth = 5, title = "Gatherings"),
+
+  p <- p + ggtitle(paste("Paper consumption (", catal, ")", sep = "")) +
+         scale_color_stata() +
+         scale_fill_stata() + 
+         guides(
        	          shape = guide_legend(keywidth = 5, title = "Gatherings"),
@@
 		  )
-  p <- p + ggtitle(paste("Paper consumption (", catal, ")", sep = ""))
+
   pics[[catal]] <- p
@@
 for (catal in unique(df$catalog)) {
-  pics[[catal]] <- ggplot(subset(df, catalog == catal), aes(x = publication_year, y = title_length)) +
+  pics[[catal]] <- ggplot(subset(df, catalog == catal),
+       aes(x = publication_year, y = title_length)) +
        geom_point(aes(size = n)) +
@@
      xlab("Publication year") +
+     scale_fill_stata() 
      #scale_fill_brewer(palette="Spectral")     
-     scale_fill_brewer(palette="Greys") 
+     #scale_fill_brewer(palette="Greys") 
      if (varname == "n") {
@@
        #scale_fill_manual(values = c("darkgreen", "darkgray"))
-       scale_fill_brewer(palette="Greys") +              
+       #scale_fill_brewer(palette="Greys") +
+       scale_fill_stata() +       
        guides(fill = guide_legend(title = "Period")) +
@@
   riksplace <- c(rep("Unknown", 2), "Stockholm", "Stockholm", "Stockholm", "Norrköping", "Stockholm", rep("Unknown", 3), "Gävle", rep("Unknown", 7))
-  #cols <- c("white", "Purple", "yellow", "orange", "darkgray")
-  cols <- c("white", "lightgray", "gray", "darkgray")
+  cols <- c("white", "Purple", "yellow", "orange", "darkgray")
+  #cols <- c("white", "lightgray", "gray", "darkgray")
   rectangles$shade[rectangles$shade == "Highlight"] <- rep(cols, length(which(rectangles$shade == "Highlight")))
@@
 	       fill=shade), alpha=0.8) +
+	 scale_fill_stata() +
          #scale_fill_manual(values = cols) +
-         scale_fill_brewer(palette="Greys") +
+         #scale_fill_brewer(palette="Greys") +
 	 guides(fill = "none")
-
-  # p <- p + geom_text(data = rectangles, angle = 90, aes(x=xmin + .5, y=.9*ymax, label=place), size = 6)
 
@@
        ylab("Unique publishers (n)") +
-       scale_fill_brewer(palette="Greys") +       
+       scale_fill_stata() +       
        guides(fill = guide_legend(reverse = FALSE, title = "")) +
        ggtitle(catal)
-       #ggtitle(paste("Unique publishers in selected publication places (", catalogue, ")"))
 
@@
 p <- ggplot(dfm, aes(x = publication_decade, y = titles_per_capita)) +
-       geom_line(aes(linetype = publication_place), size = 1) +
-       geom_point(aes(shape = publication_place), size = 5) +
+       geom_line(aes(color = publication_place), size = 1) +
+       geom_point(aes(shape = publication_place, color = publication_place), size = 5) +
        xlab("Publication decade") +
        ylab("Title count per capita (n)") +
+       scale_color_stata() +
        ggtitle("Title count per capita") +
        guides(shape = guide_legend(title = "Place")) +
-       guides(linetype = guide_legend(title = "Place")) 
+       guides(color = guide_legend(title = "Place")) 
 print(p)
@@
 p <- ggplot(df, aes(x = publication_decade, y = n)) +
-       geom_line(aes(linetype = publication_place), size = 1) +
+       geom_line(aes(color = publication_place), size = 1) +
        geom_point(aes(shape = publication_place), size = 5) +
@@
        guides(shape = guide_legend(title = "Place")) +
-       guides(linetype = guide_legend(title = "Place")) 
+       guides(color = guide_legend(title = "Place")) +
+       scale_color_stata()
 print(p)
@@
 p <- ggplot(df, aes(x = publication_decade, y = paper)) +
-       geom_line(aes(linetype = publication_place), size = 1) +
+       geom_line(aes(color = publication_place), size = 1) +
        geom_point(aes(shape = publication_place), size = 5) +
@@
        ggtitle("Octavo: paper consumption") +
-       guides(shape = guide_legend(title = "Place")) +
-       guides(linetype = guide_legend(title = "Place"))        
+       guides(shape = guide_legend(title = "Place"), color = guide_legend(title = "Place")) +
+       scale_color_stata()
 print(p)
@@
        ggtitle("Mean title length") +
-       scale_fill_manual(values = c("darkgray", "black")) +
+       scale_fill_stata() +
        guides(fill = guide_legend(title = "Place", reverse = TRUE))        
 print(p)
-
 ```
@@
       ggtitle(paste(myplace, "/", catalogue)) +
-      #scale_fill_brewer(palette="Spectral") +
-      scale_fill_brewer(palette="Greys") +       
+      scale_fill_stata() +
+      #scale_fill_brewer(palette="Greys") +       
       guides(fill = guide_legend(title = "")) 
@@
 p <- ggplot(df, aes(x = publication_year, y = n, shape = language)) +
-       geom_line(size = 1, aes(linetype = language)) +
+       geom_line(size = 1, aes(color = language)) +
        geom_point(size = 4) +
@@
        geom_smooth(color = "black") +
-       guides(shape = guide_legend(title = "Language")) +
-       guides(linetype = guide_legend(title = "Language")) + 
+       guides(shape = guide_legend(title = "Language"),
+              color = guide_legend(title = "Language")) +
+       scale_color_stata() +
        ylab("Title count (n)") +
@@
        geom_point(aes(shape = language), size = 5) +
-       geom_line(aes(linetype = language), size = 1) +       
+       geom_line(aes(color = language), size = 1) +       
        xlab("Publication year") +
        ylab("Paper (sheets)") +
-       guides(shape = guide_legend(title = "Language")) +
-       guides(linetype = guide_legend(title = "Language")) + 
-       #ggtitle(paste("Temporary Sermons (", catalogue, ")", sep = ""))
+       guides(shape = guide_legend(title = "Language"), color = guide_legend(title = "Language")) +
+       scale_color_stata() +
        ggtitle(catalogue)       
@@
        geom_point(aes(shape = language), size = 5) +
-       geom_line(aes(linetype = language)) +       
+       geom_line(aes(color = language)) +       
        xlab("Publication year") +
        ylab("Paper (sheets)") +
-       guides(shape = guide_legend(title = "Language")) +
-       guides(linetype = guide_legend(title = "Language")) +        
+       guides(shape = guide_legend(title = "Language"), color = guide_legend(title = "Language")) +
+       scale_color_stata() +
        ggtitle(catalogue)
-       #ggtitle(paste("Devotional Literature (", catalogue, ")", sep = "")) 
+
 print(p)

### 2017-10-10 inst/examples/20170201-manuscript.Rmd
added axis tick resolution

@@
 # theme_set(theme_bw(20))
-theme_set(theme_minimal(20))
+theme_set(theme_linedraw(20))
 
@@
 	      summarise(n = length(unique(na.omit(publication_place))))
+
+insert_minor <- function(major, n) {
+  minor <- major
+  minor[-seq(1, length(major), n)] <- ""
+  minor
+}
+
+brs <- seq(min(df$publication_decade), max(df$publication_decade), 10)
+
 p <- ggplot(df, aes(x = publication_decade, y = n,
@@
        # scale_color_manual(values = c("blue", "darkgreen")) +
+       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 2)) + 
        guides(linetype = "none") +
@@
        ggtitle("Unique publication places") +
-       scale_color_stata()
+       scale_color_stata() +
+       theme(axis.ticks.length=unit(3, "mm"), axis.ticks=element_line(size = 1))
+
 print(p)
@@
        #scale_color_manual(values = c("blue", "darkgreen")) +
+       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 2)) +        
        guides(
@@
   df2$gatherings <- factor(df2$gatherings, levels = levels(df.full$gatherings))
+
+  brs <- seq(min(df2$publication_decade), max(brs), 10)
 
@@
          aes(color = highlight, fill = highlight))
-  #p <- p + scale_color_manual(values = c("darkgreen", "darkgray"))
   #p <- p + scale_fill_manual(values = c("darkgreen", "darkgray"))  	 
@@
          scale_fill_stata() +
+         scale_x_continuous(breaks = brs, labels = insert_minor(brs, 2)) + 	 
          guides(
@@
 pics <- list()
+brs <- seq(min(df2$publication_decade), max(df2$publication_decade), 10)
 for (catal in unique(df$catalog)) {
@@
        geom_smooth(color = "black") +
+       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 2)) +        
        ggtitle(paste("Mean title length (", catal, ")", sep = "")) + 
@@
 
+brs <- seq(min(df$publication_decade), max(df$publication_decade), 10)
+
 # Calculate percentages
@@
      scale_fill_stata() 
-     #scale_fill_brewer(palette="Spectral")     
-     #scale_fill_brewer(palette="Greys") 
      if (varname == "n") {
@@
   p <- p + guides(fill = guide_legend(title = "")) 
+  p <- p + scale_x_continuous(breaks = brs, labels = insert_minor(brs, 2))
 
@@
 
+  riksplace <- c(rep("Unknown", 2), "Stockholm", "Stockholm", "Stockholm", "Norrköping", "Stockholm", rep("Unknown", 3), "Gävle", rep("Unknown", 7))
+  cols <- c("white", "lightgray", "darkgray")
+  #cols <- c("white", "Purple", "yellow", "orange", "darkgray", "red")
+
   rectangles$shade <- rep(c("Background", "Highlight"), length = nrow(rectangles))
-  riksplace <- c(rep("Unknown", 2), "Stockholm", "Stockholm", "Stockholm", "Norrköping", "Stockholm", rep("Unknown", 3), "Gävle", rep("Unknown", 7))
-  cols <- c("white", "Purple", "yellow", "orange", "darkgray")
-  #cols <- c("white", "lightgray", "gray", "darkgray")
-  rectangles$shade[rectangles$shade == "Highlight"] <- rep(cols, length(which(rectangles$shade == "Highlight")))
-  rectangles$shade <- factor(rectangles$shade)
+  rectangles$shade[rectangles$shade == "Background"] <- cols[[1]]
+  rectangles$shade[rectangles$shade == "Highlight"] <- rep(cols[-1], length(which(rectangles$shade == "Highlight")))
+  rectangles$shade <- factor(rectangles$shade, levels = cols)
 
@@
 	       fill=shade), alpha=0.8) +
-	 scale_fill_stata() +
-         #scale_fill_manual(values = cols) +
-         #scale_fill_brewer(palette="Greys") +
+         scale_fill_manual(values = cols) +
 	 guides(fill = "none")
@@
        guides(fill = guide_legend(reverse = FALSE, title = "")) +
+       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 2)) +               
        ggtitle(catal)
@@
        scale_fill_stata() +
+       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 2)) + 
        guides(fill = guide_legend(reverse = FALSE, title = "")) +
@@
 
+brs <- seq(min(decade(df$publication_year)), max(decade(df$publication_year)), 10)
+
 p <- ggplot(df, aes(x = publication_year, y = n)) +
@@
      ggtitle("") +
-     scale_x_continuous(breaks = seq(minyear, maxyear, 5)) +
+     #scale_x_continuous(breaks = seq(minyear, maxyear, 5)) +
+     scale_x_continuous(breaks = brs, labels = insert_minor(brs, 2)) +
      xlab("Publication year") +
@@
 theme_set(theme_bw(20))
+brs <- seq(min(df$publication_decade), max(df$publication_decade), 5)
 p <- ggplot(npub, aes(x = publication_decade, y = publisher)) +
       geom_point(aes(size = n)) +
-      #geom_line(aes(color = publisher), size = 2) +
-      #geom_smooth(aes(fill = publisher)) +
-      # geom_bar(stat = "identity", position = "stack", aes(fill = publisher)) + 
+      scale_x_continuous(breaks = brs, labels = insert_minor(brs, 2)) + 
       xlab("Year") +
@@
       guides(size = guide_legend(title = "Title count (n)"))
-       #ggtitle(paste("Title count per publisher (", place, "/", catalogue, ")", sep = ""))
 print(p)
@@
 
+brs <- seq(min(df$publication_decade), max(df$publication_decade), 5)
 p <- ggplot(dfm, aes(x = publication_decade, y = titles_per_capita)) +
@@
        scale_color_stata() +
+       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 2)) +             
        ggtitle("Title count per capita") +
@@
 df <- bind_rows(df1, df2)
-
+brs <- seq(min(df$publication_decade), max(df$publication_decade), 5)
 p <- ggplot(df, aes(x = publication_decade, y = n)) +
        geom_line(aes(color = publication_place), size = 1) +
-       geom_point(aes(shape = publication_place), size = 5) +
+       geom_point(aes(color = publication_place, shape = publication_place), size = 5) +
        xlab("Publication decade") +
@@
        ggtitle("Title count (absolute)") +
+       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 2)) +
        guides(shape = guide_legend(title = "Place")) +
@@
 df <- bind_rows(df1, df2)
-
+brs <- seq(min(df$publication_decade), max(df$publication_decade), 5)
 p <- ggplot(df, aes(x = publication_decade, y = paper)) +
        geom_line(aes(color = publication_place), size = 1) +
-       geom_point(aes(shape = publication_place), size = 5) +
+       geom_point(aes(color = publication_place, shape = publication_place), size = 5) +
        xlab("Publication year") +
        ylab("Paper (sheets)") +
+       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 2)) +       
        ggtitle("Octavo: paper consumption") +
@@
 df$publication_place[!df$publication_place == "Stockholm"] <- "Other"
-
+brs <- seq(min(df$publication_decade), max(df$publication_decade), 5)
 p <- ggplot(df, aes(x = publication_decade, y = mean_title_length)) +
-       geom_bar(aes(fill = publication_place), position = "dodge", stat = "identity") +
+       geom_bar(color = "black", aes(fill = publication_place),
+         position = "dodge", stat = "identity") +
        xlab("Publication year") +
@@
        scale_fill_stata() +
+       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 2)) + 
+       #scale_fill_manual(values = c("darkgray", "lightgray")) +       
        guides(fill = guide_legend(title = "Place", reverse = TRUE))        
@@
 
+  brs <- seq(min(dff$publication_decade), max(dff$publication_decade), 5)
+
   for (myplace in myplaces) {
+
     p <- ggplot(subset(dff, publication_place == myplace),
@@
       scale_fill_stata() +
+      scale_x_continuous(breaks = brs, labels = insert_minor(brs, 10)) +  
       #scale_fill_brewer(palette="Greys") +       
@@
        geom_line(size = 1, aes(color = language)) +
-       geom_point(size = 4) +
+       geom_point(size = 4, aes(color = language)) +
        scale_color_brewer(palette="Greys") +
@@
   p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
-       geom_point(aes(shape = language), size = 5) +
+       geom_point(aes(shape = language, color = language), size = 5) +
         geom_line(aes(color = language), size = 1) +       
@@
        ylab("Paper (sheets)") +
-       guides(shape = guide_legend(title = "Language"), color = guide_legend(title = "Language")) +
+       guides(shape = guide_legend(title = "Language"),
+              color = guide_legend(title = "Language")) +
        scale_color_stata() +
@@
 p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
-       geom_point(aes(shape = language), size = 5) +
+       geom_point(aes(shape = language, color = language), size = 5) +
        geom_line(aes(color = language)) +       

### 2017-10-10 inst/examples/20170201-manuscript.Rmd
added axis tick resolution

@@
 
-  brs <- seq(min(df2$publication_decade), max(brs), 10)
+  brs <- seq(min(df2$publication_decade), max(df2$publication_decade), 10)
 
@@
          aes(color = highlight, fill = highlight))
-  #p <- p + scale_fill_manual(values = c("darkgreen", "darkgray"))  	 
+  p <- p + scale_fill_manual(values = c("darkgreen", "darkgray"))
+  #   scale_color_stata() +
+  #   scale_fill_stata() +
   p <- p + xlab("Year")
@@
   p <- p + ggtitle(paste("Paper consumption (", catal, ")", sep = "")) +
-         scale_color_stata() +
-         scale_fill_stata() +
-         scale_x_continuous(breaks = brs, labels = insert_minor(brs, 2)) + 	 
+         scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5)) + 	 
          guides(
        	          shape = guide_legend(keywidth = 5, title = "Gatherings"),
-       	          fill = "none", # guide_legend(title = "Gatherings"),
-       	          color = "none" # guide_legend(title = "Gatherings")
+       	          color = guide_legend(keywidth = 5, title = "Gatherings"),		  
+       	          fill = "none" # guide_legend(title = "Gatherings"),
+       	          #color = "none" # guide_legend(title = "Gatherings")
 		  )
@@
        geom_smooth(color = "black") +
-       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 2)) +        
+       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 10)) +        
        ggtitle(paste("Mean title length (", catal, ")", sep = "")) + 
@@
 
-brs <- seq(min(df$publication_decade), max(df$publication_decade), 10)
+brs <- seq(min(df$publication_decade), max(df$publication_decade), 20)
 
@@
   p <- p + guides(fill = guide_legend(title = "")) 
-  p <- p + scale_x_continuous(breaks = brs, labels = insert_minor(brs, 2))
+  p <- p + scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5))
 
@@
 df$period <- gsub("\\]", "", df$period)
+df$period <- gsub("\\,", "-", df$period)
 
@@
   # Use timeinterval year intervals
-  dfsel = subset(df0, catalog == catal)
+  dfsel <- dplyr::filter(df0, catalog == catal)
 
   df <- df0
-  df = subset(df, catalog == catal)
+  df <- dplyr::filter(df, catalog == catal)
   df <- subset(df, publication_year >= minyear & publication_year <= maxyear)
@@
   timeinterval <- 1
-  df$timeunit <- round(df$publication_year/timeinterval)*timeinterval
-
-  df$unity = rep(1, nrow(df))
+  df$timeunit <- round(df$publication_year/timeinterval) * timeinterval
+
+  df$unity <- rep(1, nrow(df))
   publications <- tapply(df$unity, list(df$timeunit), sum)
@@
   rectangles$place[rectangles$place == "Background"] <- ""
+
+  #brs <- seq(min(df$publication_decade), max(df$publication_decade), 5)
+  brs <- seq(min(dfm$date), max(dfm$date), 10)
 
@@
   p <- p + geom_point(data = dfm, aes(x = date, y = Documents), col = "black")
-  p <- p + scale_x_continuous(breaks=seq(min(dfm$date), max(dfm$date), 10))
+  p <- p + scale_x_continuous(breaks=brs, labels = insert_minor(brs, 2))
   p <- p + ylab("Title count (n)")
@@
      ggtitle("") +
-     #scale_x_continuous(breaks = seq(minyear, maxyear, 5)) +
      scale_x_continuous(breaks = brs, labels = insert_minor(brs, 2)) +
@@
 theme_set(theme_bw(20))
-brs <- seq(min(df$publication_decade), max(df$publication_decade), 5)
+brs <- seq(min(df$publication_decade), max(df$publication_decade), 10)
 p <- ggplot(npub, aes(x = publication_decade, y = publisher)) +
       geom_point(aes(size = n)) +
-      scale_x_continuous(breaks = brs, labels = insert_minor(brs, 2)) + 
+      scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5)) + 
       xlab("Year") +
@@
 
-brs <- seq(min(df$publication_decade), max(df$publication_decade), 5)
+brs <- seq(min(df$publication_decade), max(df$publication_decade), 10)
 p <- ggplot(dfm, aes(x = publication_decade, y = titles_per_capita)) +
@@
        scale_color_stata() +
-       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 2)) +             
+       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5)) +             
        ggtitle("Title count per capita") +
@@
 df <- bind_rows(df1, df2)
-brs <- seq(min(df$publication_decade), max(df$publication_decade), 5)
+brs <- seq(min(df$publication_decade), max(df$publication_decade), 10)
 p <- ggplot(df, aes(x = publication_decade, y = n)) +
@@
        ggtitle("Title count (absolute)") +
-       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 2)) +
+       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5)) +
        guides(shape = guide_legend(title = "Place")) +
@@
 df <- bind_rows(df1, df2)
-brs <- seq(min(df$publication_decade), max(df$publication_decade), 5)
+brs <- seq(min(df$publication_decade), max(df$publication_decade), 10)
 p <- ggplot(df, aes(x = publication_decade, y = paper)) +
@@
        ylab("Paper (sheets)") +
-       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 2)) +       
+       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5)) +   
        ggtitle("Octavo: paper consumption") +
@@
 df$publication_place[!df$publication_place == "Stockholm"] <- "Other"
-brs <- seq(min(df$publication_decade), max(df$publication_decade), 5)
+brs <- seq(min(df$publication_decade), max(df$publication_decade), 10)
 p <- ggplot(df, aes(x = publication_decade, y = mean_title_length)) +
@@
        scale_fill_stata() +
-       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 2)) + 
+       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5)) + 
        #scale_fill_manual(values = c("darkgray", "lightgray")) +       
@@
 
-  brs <- seq(min(dff$publication_decade), max(dff$publication_decade), 5)
+  brs <- seq(min(dff$publication_decade), max(dff$publication_decade), 10)
 
@@
       scale_fill_stata() +
-      scale_x_continuous(breaks = brs, labels = insert_minor(brs, 10)) +  
+      scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5)) +  
       #scale_fill_brewer(palette="Greys") +       
@@
 df$language <- factor(df$language, levels = langs2)
+
+brs <- seq(min(decade(df$publication_year)), max(decade(df$publication_year)), 10)
 
@@
        scale_color_stata() +
+       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5)) +         
        ylab("Title count (n)") +
@@
 ```{r Fig18, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
+
 sel <- c("hautajaiset", "häät", "juhlamenot")
@@
 
+  brs <- seq(min(df$publication_decade), max(df$publication_decade), 10)
+
   # PAPER CONSUMPTION
@@
               color = guide_legend(title = "Language")) +
+       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5)) + 
        scale_color_stata() +
@@
 theme_set(theme_bw(20))
+brs <- seq(min(df$publication_decade), max(df$publication_decade), 10)
 p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
@@
        scale_color_stata() +
+       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5)) +        
        ggtitle(catalogue)

### 2017-10-11 inst/examples/20170201-manuscript.Rmd
ok

@@
 
-insert_minor <- function(major, n) {
+insert_minor <- function(major, n, start = NULL) {
   minor <- major
-  minor[-seq(1, length(major), n)] <- ""
+  ind <- ifelse (!is.null(start), which.min(abs(major - start)), 1)
+  minor[-seq(ind, length(major), n)] <- ""
   minor
@@
 
+  #brs <- seq(min(df2$publication_decade), max(df2$publication_decade), 10)
   brs <- seq(min(df2$publication_decade), max(df2$publication_decade), 10)
@@
   	       	       shape = gatherings,
-		       color = gatherings))		       
+		       linetype = gatherings
+		       ))
   p <- p + geom_point(size = 4)
+
   p <- p + geom_smooth(method = "loess", size = 1,
          aes(color = highlight, fill = highlight))
+
   p <- p + scale_fill_manual(values = c("darkgreen", "darkgray"))
+  p <- p + scale_color_manual(values = c("darkgreen", "darkgray"))  
   #   scale_color_stata() +
@@
 
+  p <- p + guides(
+    color = guide_legend(keywidth = 5, title = "Gatherings"),
+    fill = guide_legend(keywidth = 5, title = "Gatherings"),     
+    shape = guide_legend(keywidth = 5, title = "Gatherings", reverse = TRUE),
+    linetype = guide_legend(keywidth = 5, title = "Gatherings", reverse = TRUE))
+
   p <- p + ggtitle(paste("Paper consumption (", catal, ")", sep = "")) +
-         scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5)) + 	 
-         guides(
-       	          shape = guide_legend(keywidth = 5, title = "Gatherings"),
-       	          color = guide_legend(keywidth = 5, title = "Gatherings"),		  
-       	          fill = "none" # guide_legend(title = "Gatherings"),
-       	          #color = "none" # guide_legend(title = "Gatherings")
-		  )
+         scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5, start = century(df2$publication_decade) + 50))
 
@@
 pics <- list()
-brs <- seq(min(df2$publication_decade), max(df2$publication_decade), 10)
+brs <- seq(min(decade(df$publication_year)), max(decade(df$publication_year)), 10)
 for (catal in unique(df$catalog)) {
@@
        geom_smooth(color = "black") +
-       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 10)) +        
+       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5, start = century(min(brs)) + 50)) +   
        ggtitle(paste("Mean title length (", catal, ")", sep = "")) + 
        xlab("Publication year") +
-       ylab("Title length (word count)")
+       ylab("Title length (words)")
 }
@@
 
-brs <- seq(min(df$publication_decade), max(df$publication_decade), 20)
+brs <- seq(min(df$publication_decade), max(df$publication_decade), 10)
 
@@
   p <- p + guides(fill = guide_legend(title = "")) 
-  p <- p + scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5))
+  p <- p + scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5, start = century(min(dff$publication_decade)) + 50))
 
@@
 
+df$period <- format_period(df$period)
+
 p <- ggplot(df,
@@
 theme_set(theme_bw(20))
+brs <- seq(min(npub$publication_decade), max(npub$publication_decade), 10)  
 p <- ggplot(npub, aes(x = publication_decade, y = n)) +
@@
        scale_fill_stata() +
-       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 2)) + 
+       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 1)) + 
        guides(fill = guide_legend(reverse = FALSE, title = "")) +
@@
      ggtitle("") +
-     scale_x_continuous(breaks = brs, labels = insert_minor(brs, 2)) +
+     scale_x_continuous(breaks = brs, labels = insert_minor(brs, 1)) +
      xlab("Publication year") +
@@
       geom_point(aes(size = n)) +
-      scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5)) + 
+      scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5, start = century(min(brs)) + 50)) + 
       xlab("Year") +
@@
 brs <- seq(min(df$publication_decade), max(df$publication_decade), 10)
+labs <- brs; labs[!brs %in% df$publication_decade] <- ""
 p <- ggplot(dfm, aes(x = publication_decade, y = titles_per_capita)) +
@@
        scale_color_stata() +
-       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5)) +             
+       #scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5)) +
+       scale_x_continuous(breaks = brs, labels = labs) +                    
        ggtitle("Title count per capita") +
@@
 brs <- seq(min(df$publication_decade), max(df$publication_decade), 10)
+labs <- brs; labs[!brs %in% df$publication_decade] <- ""
 p <- ggplot(df, aes(x = publication_decade, y = n)) +
@@
        ggtitle("Title count (absolute)") +
-       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5)) +
+       #scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5)) +
+       scale_x_continuous(breaks = brs, labels = labs) +                           
        guides(shape = guide_legend(title = "Place")) +
@@
        ylab("Paper (sheets)") +
-       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5)) +   
+       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5, start = century(min(brs)) + 50)) +   
        ggtitle("Octavo: paper consumption") +
@@
        scale_fill_stata() +
-       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5)) + 
+       #scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5)) +
+       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5, start = century(min(brs)) + 50)) +          
        #scale_fill_manual(values = c("darkgray", "lightgray")) +       
@@
        scale_color_stata() +
-       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5)) +         
+       # scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5)) +
+       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5, start = century(min(brs)) + 50)) +                 
        ylab("Title count (n)") +
@@
               color = guide_legend(title = "Language")) +
-       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5)) + 
+       #scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5)) +
+       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5, start = century(min(brs)) + 50)) +       
        scale_color_stata() +
@@
        scale_color_stata() +
-       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5)) +        
+       # scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5)) +
+       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5, start = century(min(brs)) + 50)) +      
        ggtitle(catalogue)

### 2017-10-11 inst/examples/20170201-manuscript.Rmd
ok

@@
 # theme_set(theme_bw(20))
-theme_set(theme_linedraw(20))
+#theme_set(theme_linedraw(20))
+theme_set(theme_light(20))
 
@@
 ```{r Fig3, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=9, fig.height=5, fig.show="hold"}
+
+library(scales)
+scientific_10 <- function(x) {
+  parse(text=gsub("\\+", "", gsub("e", " %*% 10^", scientific_format()(x))))
+}
+
 pics <- list()
@@
   p <- p + ggtitle(paste("Paper consumption (", catal, ")", sep = "")) +
-         scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5, start = century(df2$publication_decade) + 50))
+         scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5, start = century(df2$publication_decade) + 50)) + 
+         scale_y_continuous(breaks = seq(0, max(df2$paper), 2e6), label = scientific_10)
 
@@
 		 )
-df$period <- gsub("\\[", "", df$period)
-df$period <- gsub("\\)", "", df$period)
-df$period <- gsub(",", ",", df$period)
-df$period <- gsub("\\]", "", df$period)
-df$period <- gsub("\\,", "-", df$period)
+df$period <- format_period(df$period)
 
@@
         filter(publication_place %in% c("Stockholm", "Uppsala", "Lund", "All"))
-
-df$period <- format_period(df$period)
 
@@
        ylab("Paper (sheets)") + xlab("") +
-       ggtitle("Paper consumption per title")
+       ggtitle("Average paper consumption per title")
 
@@
   p <- p + xlab("Year")
-  p <- p + ggtitle(paste(catal, " ", minyear, "-", maxyear, sep = ""))
+  p <- p + ggtitle(paste("Title count (", catal, " ", minyear, "-", maxyear, ")", sep = ""))
   print(p)
@@
        scale_x_continuous(breaks = brs, labels = insert_minor(brs, 2)) +   
-       ggtitle(catal)
+       ggtitle(paste("Unique publishers (", catal, ")", sep = ""))
 
@@
 theme_set(theme_bw(20))
-brs <- seq(min(npub$publication_decade), max(npub$publication_decade), 10)  
+brs <- seq(min(npub$publication_decade), max(npub$publication_decade), 5)  
 p <- ggplot(npub, aes(x = publication_decade, y = n)) +
@@
        scale_fill_stata() +
-       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 1)) + 
+       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 2, start = min(npub$publication_decade))) + 
        guides(fill = guide_legend(reverse = FALSE, title = "")) +
@@
        scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5, start = century(min(brs)) + 50)) +
-       ggtitle("Octavo: paper consumption") +
+       scale_y_continuous(label = scientific_10) +
+       ggtitle("Paper consumption on Octavo") +
        guides(shape = guide_legend(title = "Place"), color = guide_legend(title = "Place")) +
@@
 df$publication_place[!df$publication_place == "Stockholm"] <- "Other"
+df$publication_place <- droplevels(factor(df$publication_place))
+
 brs <- seq(min(df$publication_decade), max(df$publication_decade), 10)
 p <- ggplot(df, aes(x = publication_decade, y = mean_title_length)) +
-       geom_bar(color = "black", aes(fill = publication_place),
-         position = "dodge", stat = "identity") +
+       geom_bar(color = "black",
+         aes(fill = publication_place), position = "dodge", stat = "identity") +
        xlab("Publication year") +
@@
 
-  brs <- seq(min(dff$publication_decade), max(dff$publication_decade), 10)
-
   for (myplace in myplaces) {
 
-    p <- ggplot(subset(dff, publication_place == myplace),
+  dfss <- subset(dff, publication_place == myplace)
+  brs <- seq(min(dfss$publication_decade), max(dfss$publication_decade), 10)
+
+   p <- ggplot(dfss,
       aes(x = publication_decade, y = f)) +
@@
 ```{r Fig18, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
-
 sel <- c("hautajaiset", "häät", "juhlamenot")
@@
        scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5, start = century(min(brs)) + 50)) +
+       scale_y_continuous(label = scientific_10) + 
        scale_color_stata() +
@@
        # scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5)) +
-       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5, start = century(min(brs)) + 50)) +      
+       #scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5, start = century(min(brs)) + 50)) +
+       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 2)) +       
+       scale_y_continuous(label = scientific_10) + 
        ggtitle(catalogue)

### 2017-10-11 inst/examples/20170201-manuscript.Rmd
ok

@@
        p <- p + ggtitle(paste("Title count (", catalogue, ")", sep = "")) + 
-                ylab("Title count frequency (%)") 
+                ylab("Title count (%)") 
      }
@@
   brs <- seq(min(dfm$date), max(dfm$date), 10)
+  brsy <- seq(0, round(max(dfm$Documents), -2), 250)
 
@@
   p <- p + scale_x_continuous(breaks=brs, labels = insert_minor(brs, 2))
+  p <- p + scale_y_continuous(breaks=brsy, labels = brsy)  
   p <- p + ylab("Title count (n)")
@@
        guides(fill = guide_legend(reverse = FALSE, title = "")) +
-       ggtitle(catal)
+       ggtitle(paste("Unique publishers (", catal, ")", sep = ""))
 
@@
 
-brs <- seq(min(decade(df$publication_year)), max(decade(df$publication_year)), 10)
+brs <- seq(min(decade(df$publication_year)), max(decade(df$publication_year)), 1)
 
@@
      ggtitle("") +
-     scale_x_continuous(breaks = brs, labels = insert_minor(brs, 1)) +
+     scale_x_continuous(breaks = brs, labels = insert_minor(brs, 10)) +
      xlab("Publication year") +
@@
 cat <- "Fennica"
+
 df2 <- df00 %>% filter(publication_place %in% "Turku") %>%
       	       filter(catalog == cat) %>%
+	       group_by(publication_decade, publication_place)
+
+df2$publication_place[!df2$publication_place == "Stockholm"] <- "Other"
+df2$publication_place <- droplevels(factor(df2$publication_place))
+
+df2 <- df2 %>%
 	       group_by(publication_decade, publication_place) %>%
@@
 df <- bind_rows(df1, df2)
-
-df$publication_place[!df$publication_place == "Stockholm"] <- "Other"
-df$publication_place <- droplevels(factor(df$publication_place))
 
@@
       xlab("Publication year") +
-      ylab("Title count frequency (%)") +
+      ylab("Title count (%)") +
       ggtitle(paste(myplace, "/", catalogue)) +
@@
        # scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5)) +
-       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5, start = century(min(brs)) + 50)) +                 
+       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 2, start = century(min(brs)) + 40)) +                 
        ylab("Title count (n)") +
-       xlab("Publication year")
+       xlab("Year")
 
@@
        #scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5)) +
-       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5, start = century(min(brs)) + 50)) +
+       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5, start = 1600)) +
        scale_y_continuous(label = scientific_10) + 

### 2017-10-11 inst/examples/20170201-manuscript.Rmd
ok

@@
         group_by(catalog, publication_decade) %>% tally()
+
+brsy <- seq(0, 1e4, 2000)
 p <- ggplot(df, aes(x = publication_decade, y = n,
@@
        geom_line(size = 1) + 
-       ylab("Documents (n)") + xlab("Publication year") +
+       ylab("Title count (n)") + xlab("Publication year") +
        #scale_color_manual(values = c("blue", "darkgreen")) +
        scale_x_continuous(breaks = brs, labels = insert_minor(brs, 2)) +
+       scale_y_continuous(breaks = brsy, labels = brsy) +
        guides(
@@
 
-  df2 <- subset(df00, catalog == catal) %>% group_by(publication_decade, gatherings) %>% summarize(paper = sum(paper, na.rm = TRUE), n = n())
+  df2 <- subset(df00, catalog == catal) %>%
+           group_by(publication_decade, gatherings) %>%
+	   summarize(paper = sum(paper, na.rm = TRUE), n = n())
 
@@
   p <- p + ggtitle(paste("Paper consumption (", catal, ")", sep = "")) +
-         scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5, start = century(df2$publication_decade) + 50)) + 
+         scale_x_continuous(breaks = brs,
+	   labels = insert_minor(brs, 5, start = century(min(df2$publication_decade)))) + 
          scale_y_continuous(breaks = seq(0, max(df2$paper), 2e6), label = scientific_10)
@@
        scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5, start = century(min(brs)) + 50)) +
+       scale_y_continuous(limits = c(0, max(df$title_length))) +
        ggtitle(paste("Mean title length (", catal, ")", sep = "")) + 

### 2017-10-11 inst/examples/20170201-manuscript.Rmd
ok

@@
        scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5, start = century(min(brs)) + 50)) +
-       scale_y_continuous(limits = c(0, max(df$title_length))) +
+       scale_y_continuous(limits = c(0, max(na.omit(df$title_length)))) +
        ggtitle(paste("Mean title length (", catal, ")", sep = "")) + 
@@
        guides(fill = guide_legend(reverse = FALSE, title = "")) +
-       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 2)) +   
-       ggtitle(paste("Unique publishers (", catal, ")", sep = ""))
+       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 1)) +   
+       ggtitle(paste("Publishers (", catal, ")", sep = ""))
 
@@
 theme_set(theme_bw(20))
-brs <- seq(min(npub$publication_decade), max(npub$publication_decade), 5)  
+brs <- seq(min(npub$publication_decade), max(npub$publication_decade), 1)  
 p <- ggplot(npub, aes(x = publication_decade, y = n)) +
@@
        guides(fill = guide_legend(reverse = FALSE, title = "")) +
-       ggtitle(paste("Unique publishers (", catal, ")", sep = ""))
+       ggtitle(paste("Publishers (", catal, ")", sep = ""))
 
@@
       	       filter(catalog == cat) %>%
-	       group_by(publication_decade, publication_place) %>%
-	       summarise(n = n(), paper = sum(paper, na.rm = TRUE), 
+	       group_by(publication_decade, publication_place)
+
+df1$publication_place[!df1$publication_place == "Stockholm"] <- "Other"
+df1$publication_place <- droplevels(factor(df1$publication_place))
+
+df1 <- df1 %>% summarise(n = n(), paper = sum(paper, na.rm = TRUE), 
 	         mean_title_length = mean(title_length_wordcount, na.rm = TRUE))
@@
        scale_x_continuous(breaks = brs, labels = insert_minor(brs, 2, start = century(min(brs)) + 40)) +                 
-       ylab("Title count (n)") +
-       xlab("Year")
+       ylab("Subject topics (n)") +
+       xlab("Year") +
+       ggtitle(paste("Topic richness (", catalogue, ")", sep = ""))
 
@@
        scale_color_stata() +
-       ggtitle(catalogue)       
+       ggtitle(paste("Temporary sermons (", catalogue, ")", sep = ""))
   print(p)
@@
        scale_y_continuous(label = scientific_10) + 
-       ggtitle(catalogue)
+       ggtitle(paste("Devotional literature (", catalogue, ")", sep = ""))
 

### 2017-10-11 inst/examples/20170201-manuscript.Rmd
ok

@@
          scale_x_continuous(breaks = brs,
-	   labels = insert_minor(brs, 5, start = century(min(df2$publication_decade)))) + 
+	   labels = insert_minor(brs, 5, start = 1500)) + 
          scale_y_continuous(breaks = seq(0, max(df2$paper), 2e6), label = scientific_10)
@@
 
-```{r Fig4, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=4, fig.width=11}
+```{r Fig4, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=4, fig.width=12}
 df <- df.full %>% filter(publication_year >= 1640 &
@@
 brs <- seq(min(decade(df$publication_year)), max(decade(df$publication_year)), 10)
+brsy <- seq(0, round(max(na.omit(df$title_length)), -1), 10)
 for (catal in unique(df$catalog)) {
@@
        scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5, start = century(min(brs)) + 50)) +
-       scale_y_continuous(limits = c(0, max(na.omit(df$title_length)))) +
-       ggtitle(paste("Mean title length (", catal, ")", sep = "")) + 
+       scale_y_continuous(breaks = brsy, labels = insert_minor(brsy, 2), limits = c(0, max(na.omit(df$title_length)))) +
+       ggtitle(paste("Average title length (", catal, ")", sep = "")) + 
        xlab("Publication year") +
@@
 
-library(gridExtra)
-grid.arrange(pics[[1]], pics[[2]], nrow = 1)
+#library(gridExtra)
+#grid.arrange(pics[[1]], pics[[2]], nrow = 1)
+
+library(cowplot)
+# arrange the three plots in a single row
+prow <- plot_grid(
+           pics[[1]] + theme(legend.position="none"),
+           pics[[2]] + theme(legend.position="none"),
+           align = 'vh',
+           labels = c("A", "B"),
+           hjust = -1,
+           nrow = 1
+           )
+
+# extract the legend from one of the plots
+# (clearly the whole thing only makes sense if all plots
+# have the same legend, so we can arbitrarily pick one.)
+legend_b <- get_legend(pics[[1]] + theme(legend.position="right"))
+
+# add the legend underneath the row we made earlier. Give it 10% of the height
+# of one plot (via rel_heights).
+p <- plot_grid( prow, legend_b, ncol = 2, rel_widths = c(1, .2))
+print(p)
 ```
@@
        guides(fill = guide_legend(reverse = FALSE, title = "")) +
-       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 1)) +   
+       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 2)) +   
        ggtitle(paste("Publishers (", catal, ")", sep = ""))
@@
 npub.kungliga <- npub
-
 npub <- bind_rows(npub.fennica, npub.kungliga)
@@
 # Order by total publishing activity
-npub$publication_place <- factor(npub$publication_place, levels = (npub %>% group_by(publication_place) %>% summarise(total = sum(n)) %>% arrange(desc(total)))$publication_place)
+npub$publication_place <- factor(npub$publication_place,
+                                 levels = (npub %>%
+				             group_by(publication_place) %>%
+					     summarise(total = sum(n)) %>%
+					     arrange(desc(total)))$publication_place)
 npub <- npub %>% arrange(publication_place)
-npub$publication_place <- factor(npub$publication_place, levels = rev(unique(npub$publication_place)))
+npub$publication_place <- factor(npub$publication_place,
+                                 levels = rev(unique(npub$publication_place)))
 
 theme_set(theme_bw(20))
-brs <- seq(min(npub$publication_decade), max(npub$publication_decade), 1)  
+brs <- seq(min(npub$publication_decade), max(npub$publication_decade), 10)  
 p <- ggplot(npub, aes(x = publication_decade, y = n)) +
@@
        xlab("Publication year") +
-       ylab("Unique publishers (n)") +
+       ylab("Publishers (n)") +
        scale_fill_stata() +
-       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 2, start = min(npub$publication_decade))) + 
+       scale_x_continuous(breaks = brs,
+           labels = insert_minor(brs, 5, start = min(npub$publication_decade))) + 
        guides(fill = guide_legend(reverse = FALSE, title = "")) +
@@
 
-brs <- seq(min(decade(df$publication_year)), max(decade(df$publication_year)), 1)
+brs <- seq(min(df$publication_year), max(df$publication_year), 1)
 
@@
 brs <- seq(min(df$publication_decade), max(df$publication_decade), 10)
+brsy <- seq(0, max(df$n), 1e3)
 labs <- brs; labs[!brs %in% df$publication_decade] <- ""
@@
        scale_x_continuous(breaks = brs, labels = labs) +
+       scale_y_continuous(breaks = brsy, labels = insert_minor(brsy, 2)) +                                  
        guides(shape = guide_legend(title = "Place")) +
@@
 
-df1 <- df1 %>% summarise(n = n(), paper = sum(paper, na.rm = TRUE), 
+df1 <- df1 %>%
+	       group_by(publication_decade, publication_place) %>% 
+  	       summarise(n = n(), paper = sum(paper, na.rm = TRUE), 
 	         mean_title_length = mean(title_length_wordcount, na.rm = TRUE))
@@
 df <- bind_rows(df1, df2)
+df$publication_place <- factor(df$publication_place)
 
@@
 
-```{r Fig19, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, fig.show="hold"}
+```{r Fig19, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5, fig.show="hold"}
 sel <- c("virret","arkkiveisut","hartauskirjat","katekismukset","rukouspäivät","saarnat","aapiset","rukoukset","rukous","hengelliset laulut","hartauspuheet","virsikirjat")
@@
        geom_point(aes(shape = language, color = language), size = 5) +
-       geom_line(aes(color = language)) +       
-       xlab("Publication year") +
+       geom_line(aes(color = language), size = 1) +       
+       xlab("Year") +
        ylab("Paper (sheets)") +

### 2017-10-11 inst/examples/20170201-manuscript.Rmd
ok

@@
        geom_line(size = 1) + 
-       ylab("Places (n)") + xlab("Publication year") +
+       ylab("Places (n)") + xlab("Year") +
        # scale_color_manual(values = c("blue", "darkgreen")) +
@@
        geom_line(size = 1) + 
-       ylab("Title count (n)") + xlab("Publication year") +
+       ylab("Title count (n)") + xlab("Year") +
        #scale_color_manual(values = c("blue", "darkgreen")) +
@@
        ggtitle(paste("Average title length (", catal, ")", sep = "")) + 
-       xlab("Publication year") +
+       xlab("Year") +
        ylab("Title length (words)")
@@
 
-```{r Fig5, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=13, fig.height=6}
+```{r Fig5, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=15, fig.height=7}
 pics <- list()
@@
        aes(fill = publication_place)) + 
-     xlab("Publication year") +
+     xlab("Year") +
      scale_fill_stata() 
@@
        		    aes(fill = publication_place)) + 
-       xlab("Publication year") +
-       ylab("Unique publishers (n)") +
+       xlab("Year") +
+       ylab("Publishers (n)") +
        scale_fill_stata() +       
@@
        		    aes(fill = publication_place)) + 
-       xlab("Publication year") +
+       xlab("Year") +
        ylab("Publishers (n)") +
@@
      scale_x_continuous(breaks = brs, labels = insert_minor(brs, 10)) +
-     xlab("Publication year") +
+     xlab("Year") +
      ylab("Title count (n)")
@@
        geom_point(aes(shape = publication_place, color = publication_place), size = 5) +
-       xlab("Publication decade") +
+       xlab("Year") +
        ylab("Title count per capita (n)") +
@@
        geom_point(aes(color = publication_place, shape = publication_place), size = 5) +
-       xlab("Publication decade") +
+       xlab("Year") +
        ylab("Title count (n)") +
@@
        scale_x_continuous(breaks = brs, labels = labs) +
-       scale_y_continuous(breaks = brsy, labels = insert_minor(brsy, 2)) +                                  
+       scale_y_continuous(breaks = brsy, labels = insert_minor(brsy, 1)) +                                  
        guides(shape = guide_legend(title = "Place")) +
@@
        geom_point(aes(color = publication_place, shape = publication_place), size = 5) +
-       xlab("Publication year") +
+       xlab("Year") +
        ylab("Paper (sheets)") +
@@
          aes(fill = publication_place), position = "dodge", stat = "identity") +
-       xlab("Publication year") +
+       xlab("Year") +
        ylab("Title length (words)") +
@@
 
-```{r Fig16, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6}
+```{r Fig16, echo=FALSE, message=FALSE, warning=FALSE, fig.width=15, fig.height=7}
 pics <- list()
@@
       			aes(fill = language), color = "black") + 
-      xlab("Publication year") +
+      xlab("Year") +
       ylab("Title count (%)") +
@@
         geom_line(aes(color = language), size = 1) +       
-       xlab("Publication year") +
+       xlab("Year") +
        ylab("Paper (sheets)") +

### 2017-10-11 inst/examples/20170201-manuscript.Rmd
ok

@@
 df0 <- df.full %>% filter(publication_year >= min.year & publication_year <= max.year)
+
+cols <- list(Fennica = "blue", Kungliga = "darkred")
 ```
@@
   p <- p + scale_color_manual(values = c("darkgreen", "darkgray"))
+
+  #p <- p + scale_fill_manual(values = c(cols[[catal]], "darkgray"))
+  #p <- p + scale_color_manual(values = c(cols[[catal]], "darkgray"))
+
   #   scale_color_stata() +
@@
        geom_point(aes(size = n)) +
-       geom_smooth(color = "black") +
+       geom_smooth(color = cols[[catal]], fill = cols[[catal]]) +
        scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5, start = century(min(brs)) + 50)) +
        scale_y_continuous(breaks = brsy, labels = insert_minor(brsy, 2), limits = c(0, max(na.omit(df$title_length)))) +
-       ggtitle(paste("Average title length (", catal, ")", sep = "")) + 
+       ggtitle(paste("Median title length (", catal, ")", sep = "")) + 
        xlab("Year") +
@@
 p <- plot_grid( prow, legend_b, ncol = 2, rel_widths = c(1, .2))
-print(p)
+# print(p)
 ```
@@
        scale_x_continuous(breaks = brs,
-           labels = insert_minor(brs, 5, start = min(npub$publication_decade))) + 
+           labels = insert_minor(brs, 2, start = min(npub$publication_decade))) + 
        guides(fill = guide_legend(reverse = FALSE, title = "")) +
@@
 p <- ggplot(df, aes(x = publication_year, y = n)) +
-     geom_bar(stat = "identity") +
+     #geom_bar(stat = "identity") +
+     geom_point() +
+     geom_line(size = 1) +     
      ggtitle("") +
-     scale_x_continuous(breaks = brs, labels = insert_minor(brs, 10)) +
-     xlab("Year") +
-     ylab("Title count (n)")
+     scale_x_continuous(breaks = brs, labels = insert_minor(brs, 10, start = 1770)) +
+     xlab("Year") +
+     ylab("Title count (n)") +
+     ggtitle(paste("Publications in Vaasa (", catalogue, ")", sep = ""))
 
@@
 brs <- seq(min(df$publication_decade), max(df$publication_decade), 10)
-brsy <- seq(0, max(df$n), 1e3)
+brsy <- seq(0, round(max(df$n), -3), 1e3)
 labs <- brs; labs[!brs %in% df$publication_decade] <- ""
@@
        scale_y_continuous(label = scientific_10) +
-       ggtitle("Paper consumption on Octavo") +
+       ggtitle("Paper consumption (Octavo)") +
        guides(shape = guide_legend(title = "Place"), color = guide_legend(title = "Place")) +
@@
 # Take cities from Kungliga except Turku
-cat <- "Kungliga"
-
 df00 <- df.full %>% filter(publication_year >= 1640 & publication_year <= 1850)
-
-df1 <- df00 %>% filter(publication_place %in% setdiff(cities, "Turku")) %>%
-      	       filter(catalog == cat) %>%
-	       group_by(publication_decade, publication_place)
-
+df1 <- df00 %>% filter((publication_place %in% setdiff(cities, "Turku") & catalog == "Kungliga") |
+                       (publication_place %in% "Turku" & catalog == "Fennica")) 
 df1$publication_place[!df1$publication_place == "Stockholm"] <- "Other"
-df1$publication_place <- droplevels(factor(df1$publication_place))
-
-df1 <- df1 %>%
-	       group_by(publication_decade, publication_place) %>% 
+df1$publication_place <- droplevels(as.factor(as.character(df1$publication_place)))
+
+df <- df1 %>% group_by(publication_decade, publication_place) %>%
   	       summarise(n = n(), paper = sum(paper, na.rm = TRUE), 
 	         mean_title_length = mean(title_length_wordcount, na.rm = TRUE))
-
-# Take cities from Fennica for Turku
-cat <- "Fennica"
-
-df2 <- df00 %>% filter(publication_place %in% "Turku") %>%
-      	       filter(catalog == cat) %>%
-	       group_by(publication_decade, publication_place)
-
-df2$publication_place[!df2$publication_place == "Stockholm"] <- "Other"
-df2$publication_place <- droplevels(factor(df2$publication_place))
-
-df2 <- df2 %>%
-	       group_by(publication_decade, publication_place) %>%
-	       summarise(n = n(), paper = sum(paper, na.rm = TRUE), 
-                 mean_title_length = mean(title_length_wordcount, na.rm = TRUE))
-
-df <- bind_rows(df1, df2)
-df$publication_place <- factor(df$publication_place)
 
@@
        ylab("Title length (words)") +
-       ggtitle("Mean title length") +
+       ggtitle("Average title length") +
        scale_fill_stata() +
-       #scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5)) +
        scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5, start = century(min(brs)) + 50)) +
-       #scale_fill_manual(values = c("darkgray", "lightgray")) +       
        guides(fill = guide_legend(title = "Place", reverse = TRUE))        
@@
   filter(publication_year >= 1640 & publication_year <= 1828) %>%
-  select(publication_year, language, subject_topic)
+  select(publication_decade, language, subject_topic)
 df <- unique(df)
-df <- df %>% group_by(publication_year, language) %>%
+df <- df %>% group_by(publication_decade, language) %>%
              summarise(n = length(unique(unlist(strsplit(subject_topic, ";")))))
@@
 
-brs <- seq(min(decade(df$publication_year)), max(decade(df$publication_year)), 10)
-
-p <- ggplot(df, aes(x = publication_year, y = n, shape = language)) +
+brs <- seq(min(decade(df$publication_decade)), max(decade(df$publication_decade)), 10)
+
+p <- ggplot(df, aes(x = publication_decade, y = n, shape = language)) +
        geom_line(size = 1, aes(color = language)) +
@@
        scale_fill_brewer(palette="Greys") +                     
-       geom_smooth(color = "black") +
+       # geom_smooth(color = "black") +
        guides(shape = guide_legend(title = "Language"),
@@
        ylab("Subject topics (n)") +
-       xlab("Year") +
+       xlab("Decade") +
        ggtitle(paste("Topic richness (", catalogue, ")", sep = ""))

### 2017-10-11 inst/examples/20170201-manuscript.Rmd
ok

@@
        geom_line(size = 1) + 
-       ylab("Places (n)") + xlab("Year") +
+       ylab("Places (n)") +
+       xlab("Decade") +
        # scale_color_manual(values = c("blue", "darkgreen")) +
@@
        geom_line(size = 1) + 
-       ylab("Title count (n)") + xlab("Year") +
+       ylab("Title count (n)") +
+       xlab("Decade") +
        #scale_color_manual(values = c("blue", "darkgreen")) +
@@
   #   scale_fill_stata() +
-  p <- p + xlab("Year")
+  p <- p + xlab("Decade")
   p <- p + ylab("Paper (sheets)")
@@
 p <- plot_grid( prow, legend_b, ncol = 2, rel_widths = c(1, .2))
-# print(p)
+print(p)
 ```
@@
        aes(fill = publication_place)) + 
-     xlab("Year") +
+     xlab("Decade") +
      scale_fill_stata() 
@@
        		    aes(fill = publication_place)) + 
-       xlab("Year") +
+       xlab("Decade") +
        ylab("Publishers (n)") +
@@
       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5, start = century(min(brs)) + 50)) + 
-      xlab("Year") +
+      xlab("Decade") +
       ylab("") +
@@
        geom_point(aes(shape = publication_place, color = publication_place), size = 5) +
-       xlab("Year") +
+       xlab("Decade") +
        ylab("Title count per capita (n)") +
@@
        geom_point(aes(color = publication_place, shape = publication_place), size = 5) +
-       xlab("Year") +
+       xlab("Decade") +
        ylab("Title count (n)") +
@@
        geom_point(aes(color = publication_place, shape = publication_place), size = 5) +
-       xlab("Year") +
+       xlab("Decade") +
        ylab("Paper (sheets)") +
@@
          aes(fill = publication_place), position = "dodge", stat = "identity") +
-       xlab("Year") +
+       xlab("Decade") +
        ylab("Title length (words)") +
@@
       			aes(fill = language), color = "black") + 
-      xlab("Year") +
+      xlab("Decade") +
       ylab("Title count (%)") +
@@
         geom_line(aes(color = language), size = 1) +       
-       xlab("Year") +
+       xlab("Decade") +
        ylab("Paper (sheets)") +
@@
        geom_line(aes(color = language), size = 1) +       
-       xlab("Year") +
+       xlab("Decade") +
        ylab("Paper (sheets)") +

### 2017-10-11 inst/examples/20170201-manuscript.Rmd
ok

@@
 
-  #brs <- seq(min(df2$publication_decade), max(df2$publication_decade), 10)
   brs <- seq(min(df2$publication_decade), max(df2$publication_decade), 10)
@@
          scale_x_continuous(breaks = brs,
-	   labels = insert_minor(brs, 5, start = 1500)) + 
+	   labels = insert_minor(brs, 5, start = ifelse(catal == "Fennica", 1500, 1550))) + 
          scale_y_continuous(breaks = seq(0, max(df2$paper), 2e6), label = scientific_10)
@@
        ggtitle(paste("Median title length (", catal, ")", sep = "")) + 
-       xlab("Year") +
+       xlab("Decade") +
        ylab("Title length (words)")
@@
       ylab("") +
-      guides(size = guide_legend(title = "Title count (n)"))
+      guides(size = guide_legend(title = "Title count (n)")) +
+      ggtitle(paste("Top publishers in", place, "(", catalogue, ")", sep = ""))
+
 print(p)

### 2017-10-11 inst/examples/20170201-manuscript.Rmd
ok

@@
 
-```{r Fig11, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=5, fig.width=10}
+```{r Fig11, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=5, fig.width=12}
 library(dplyr)
@@
       guides(size = guide_legend(title = "Title count (n)")) +
-      ggtitle(paste("Top publishers in", place, "(", catalogue, ")", sep = ""))
+      ggtitle(paste("Top publishers in ", place, " (", catalogue, ")", sep = ""))
 

### 2017-10-16 inst/examples/20170201-manuscript.Rmd
ok

@@
               color = guide_legend(title = "Catalog", reverse = TRUE)) +              
-       ggtitle("Unique publication places") +
+       #ggtitl("Unique publication places") +
+       ggtitle("Figure 1") +       
        scale_color_stata() +
@@
        ) +
-       ggtitle("Title count") +
+       #ggtitl("Title count") +
+       ggtitle("Figure 2") +              
        scale_color_stata()
@@
 
-  p <- p + ggtitle(paste("Paper consumption (", catal, ")", sep = "")) +
+  p <- p + #ggtitl(paste("Paper consumption (", catal, ")", sep = "")) +
+         ggtitle(paste("Figure 3", c("A", "B")[which(unique(df00$catalog) == catal)], sep = "")) +       
          scale_x_continuous(breaks = brs,
@@
        scale_y_continuous(breaks = brsy, labels = insert_minor(brsy, 2), limits = c(0, max(na.omit(df$title_length)))) +
-       ggtitle(paste("Median title length (", catal, ")", sep = "")) + 
+       #ggtitl(paste("Median title length (", catal, ")", sep = "")) +
+       ggtitle("Figure 4") +
        xlab("Decade") +
@@
      if (varname == "n") {
-       p <- p + ggtitle(paste("Title count (", catalogue, ")", sep = "")) + 
+       p <- p + #ggtitl(paste("Title count (", catalogue, ")", sep = "")) + 
                 ylab("Title count (%)") 
@@
      if (varname == "paper") {
-       p <- p + ggtitle(paste("Paper (", catalogue, ")", sep = "")) +
+       p <- p + #ggtitl(paste("Paper (", catalogue, ")", sep = "")) +
                 ylab("Paper (%)")        
@@
      if (varname == "publishers") {
-       p <- p + ggtitle(paste("Publishers (", catalogue, ")", sep = "")) +
+       p <- p + #ggtitl(paste("Publishers (", catalogue, ")", sep = "")) +
                        ylab("Publishers (%)")
@@
 library(gridExtra)
+pics[[1]] <- pics[[1]] + ggtitle("Figure 5") 
 grid.arrange(pics[[1]], pics[[2]], pics[[4]], pics[[5]], nrow = 2)
@@
        ylab("Paper (sheets)") + xlab("") +
-       ggtitle("Average paper consumption per title")
+       ggtitle("Figure 6") 
+       #ggtitl("Average paper consumption per title")
 
@@
   p <- p + xlab("Year")
-  p <- p + ggtitle(paste("Title count (", catal, " ", minyear, "-", maxyear, ")", sep = ""))
+  p <- p + ggtitle("Figure 7")   
+  #p <- p + #ggtitl(paste("Title count (", catal, " ", minyear, "-", maxyear, ")", sep = ""))
   print(p)
@@
        scale_x_continuous(breaks = brs, labels = insert_minor(brs, 2)) +
-       ggtitle(paste("Publishers (", catal, ")", sep = ""))
+       ggtitle("Figure 8")
+       #ggtitl(paste("Publishers (", catal, ")", sep = ""))
 
@@
        guides(fill = guide_legend(reverse = FALSE, title = "")) +
-       ggtitle(paste("Publishers (", catal, ")", sep = ""))
+       ggtitle("Figure 9")       
+       #ggtitl(paste("Publishers (", catal, ")", sep = ""))
 
@@
 
+# Augment missing years with 0
+missing.years <- setdiff(1750:1828, df$publication_year)
+df <- rbind(df, data.frame(publication_year = missing.years, n = rep(0, length(missing.years))))
+df <- df %>% arrange(publication_year)
+
 brs <- seq(min(df$publication_year), max(df$publication_year), 1)
@@
      geom_line(size = 1) +     
-     ggtitle("") +
      scale_x_continuous(breaks = brs, labels = insert_minor(brs, 10, start = 1770)) +
@@
      ylab("Title count (n)") +
-     ggtitle(paste("Publications in Vaasa (", catalogue, ")", sep = ""))
+     ggtitle("Figure 10")
+     #ggtitle(paste("Publications in Vaasa (", catalogue, ")", sep = ""))
 
@@
       guides(size = guide_legend(title = "Title count (n)")) +
-      ggtitle(paste("Top publishers in ", place, " (", catalogue, ")", sep = ""))
+      #ggtitle("Figure 11")      
+      #ggtitle(paste("Top publishers in ", place, " (", catalogue, ")", sep = ""))
+      ggtitle(paste("Figure 11:", place, " (", catalogue, ")", sep = ""))
 
@@
        scale_x_continuous(breaks = brs, labels = labs) +                    
-       ggtitle("Title count per capita") +
+       #ggtitle("Title count per capita") +
+       ggtitle("Figure 12") +       
        guides(shape = guide_legend(title = "Place")) +
@@
        ylab("Title count (n)") +
-       ggtitle("Title count (absolute)") +
+       #ggtitle("Title count (absolute)") +
+       ggtitle("Figure 13") +              
        #scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5)) +
@@
        scale_y_continuous(label = scientific_10) +
-       ggtitle("Paper consumption (Octavo)") +
+       #ggtitle("Paper consumption (Octavo)") +
+       ggtitle("Figure 14") +                     
        guides(shape = guide_legend(title = "Place"), color = guide_legend(title = "Place")) +
@@
 
-Average title length in words in Stockholm, Turku, Uppsala, Lund,
-Göteborg and Linköping. According to Kungliga, except Turku from
-Fennica.
+Average title length in words in Stockholm, Turku, Uppsala, Lund, Göteborg and Linköping. According to Kungliga, except Turku from Fennica.
 
@@
        ylab("Title length (words)") +
-       ggtitle("Average title length") +
+       #ggtitle("Average title length") +
+       ggtitle("Figure 15") +                            
        scale_fill_stata() +
@@
 myplaces <- c("Turku", "Greifswald", "Stockholm", "Uppsala", "Lund")
-
+cnt <- 0
 for (catalogue in c("Fennica", "Kungliga")) {
@@
       xlab("Decade") +
-      ylab("Title count (%)") +
-      ggtitle(paste(myplace, "/", catalogue)) +
+      ylab("Title count (%)") 
+      #ggtitle(paste(myplace, "/", catalogue)) +
+      if (cnt == 0) {
+        p <- p + labs(title = "Figure 16")
+	cnt <- 1
+      }
+
+      p <- p + labs(subtitle = paste(myplace, "/", catalogue)) +                 
       scale_fill_stata() +
@@
        xlab("Decade") +
-       ggtitle(paste("Topic richness (", catalogue, ")", sep = ""))
+       ggtitle("Figure 17")
+       #ggtitle(paste("Topic richness (", catalogue, ")", sep = ""))
 
@@
        scale_color_stata() +
-       ggtitle(paste("Temporary sermons (", catalogue, ")", sep = ""))
+       ggtitle("Figure 18")
+       #ggtitle(paste("Temporary sermons (", catalogue, ")", sep = ""))
   print(p)
@@
        scale_y_continuous(label = scientific_10) +
-       ggtitle(paste("Devotional literature (", catalogue, ")", sep = ""))
+       ggtitle("Figure 19")       
+       # ggtitle(paste("Devotional literature (", catalogue, ")", sep = ""))
 

### 2017-10-16 inst/examples/analysis.R

@@ -32,7 +32,6 @@ render("20170201-manuscript.Rmd")
 rmarkdown::render("201705-Gaudeamus.Rmd") 
 
 #rmarkdown::render("20160715-Krakow-Fennica.Rmd") # Krakow 7/2016 slides frozen.
-
 #library(rmarkdown)
 #rmarkdown::render("slidetemplates.Rmd", params = list(min.year = 1488, max.year = 1828, data = "df.combined.Rds"))
 #rmarkdown::render("slidetemplates.Rmd", params = "ask")

### 2017-10-16 inst/examples/20170201-manuscript.Rmd
ok

@@
 ```{r Fig4, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=4, fig.width=12}
+cols <- list(Fennica = "blue", Kungliga = "darkred")
 df <- df.full %>% filter(publication_year >= 1640 &
@@
        #ggtitl(paste("Median title length (", catal, ")", sep = "")) +
-       ggtitle("Figure 4") +
        xlab("Decade") +
@@
 
-#library(gridExtra)
-#grid.arrange(pics[[1]], pics[[2]], nrow = 1)
+pics[[unique(df$catalog)[[1]]]] <- pics[[unique(df$catalog)[[1]]]] + labs(title = "Figure 4")
 
@@
      if (varname == "n") {
-       p <- p + #ggtitl(paste("Title count (", catalogue, ")", sep = "")) + 
-                ylab("Title count (%)") 
+       p <- p + labs(subtitle = paste("Title count (", catalogue, ")", sep = ""), y = "Title count (%)")
      }
      if (varname == "paper") {
-       p <- p + #ggtitl(paste("Paper (", catalogue, ")", sep = "")) +
-                ylab("Paper (%)")        
+       p <- p + labs(subtitle = paste("Paper (", catalogue, ")", sep = ""), y = "Paper (%)")
      }
      if (varname == "publishers") {
-       p <- p + #ggtitl(paste("Publishers (", catalogue, ")", sep = "")) +
-                       ylab("Publishers (%)")
+       p <- p + labs(subtitle = paste("Publishers (", catalogue, ")", sep = ""), y = "Publishers (%)")
      }     
@@
 library(gridExtra)
-pics[[1]] <- pics[[1]] + ggtitle("Figure 5") 
-grid.arrange(pics[[1]], pics[[2]], pics[[4]], pics[[5]], nrow = 2)
+#pics[[1]] <- pics[[1]] + ggtitle("Figure 5") 
+grid.arrange(pics[[1]], pics[[2]], pics[[4]], pics[[5]], top = "Figure 5", layout_matrix = matrix(c(1,2,3,4), nrow = 2, byrow=TRUE))
 rm(pics)
@@
       #ggtitle(paste("Top publishers in ", place, " (", catalogue, ")", sep = ""))
-      ggtitle(paste("Figure 11:", place, " (", catalogue, ")", sep = ""))
+      ggtitle(paste("Figure 11: ", place, " (", catalogue, ")", sep = ""))
 
@@
       ylab("Title count (%)")
-      #ggtitle(paste(myplace, "/", catalogue)) +
-      if (cnt == 0) {
-        p <- p + labs(title = "Figure 16")
-	cnt <- 1
-      }
 
@@
 
-grid.arrange(pics[[1]],
-             pics[[8]], pics[[9]], pics[[10]], 
-             nrow = 2)
+grid.arrange(pics[[1]], pics[[8]], pics[[9]], pics[[10]], top = "Figure 16", layout_matrix = matrix(c(1,2,3,4), nrow = 2, byrow=TRUE))
+
 rm(pics)

### 2017-10-16 inst/examples/20170201-manuscript.Rmd
ok

@@
   p <- p + #ggtitl(paste("Paper consumption (", catal, ")", sep = "")) +
-         ggtitle(paste("Figure 3", c("A", "B")[which(unique(df00$catalog) == catal)], sep = "")) +       
+         #ggtitle(paste("Figure 3", c("A", "B")[which(unique(df00$catalog) == catal)], sep = "")) +
+         ggtitle(paste(c("A", "B")[which(unique(df00$catalog) == catal)], sep = "")) +       	 
          scale_x_continuous(breaks = brs,
@@
 }
-```
-
-```{r Fig3A, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=9, fig.height=5}
-print(pics[[1]])
-```
-
----
-
-```{r Fig3B, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=9, fig.height=5}
-print(pics[[2]])
+
+grid.arrange(pics[[1]], pics[[2]], top = "Figure 3", layout_matrix = matrix(c(1,2), nrow = 2, byrow=TRUE))
 ```
@@
 p <- plot_grid( prow, legend_b, ncol = 2, rel_widths = c(1, .2))
-print(p)
+#print(p)
 ```
@@
       guides(size = guide_legend(title = "Title count (n)")) +
-      #ggtitle("Figure 11")      
+      ggtitle("Figure 11")      
       #ggtitle(paste("Top publishers in ", place, " (", catalogue, ")", sep = ""))
-      ggtitle(paste("Figure 11: ", place, " (", catalogue, ")", sep = ""))
+      #ggtitle(paste("Figure 11: ", place, " (", catalogue, ")", sep = ""))
 

### 2017-10-16 inst/examples/20170201-manuscript.Rmd
ok

@@
 ```{r Fig3, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=9, fig.height=5, fig.show="hold"}
-
 library(scales)
@@
 }
+
+common.gatherings <- setdiff(names(which(table(df.full$gatherings) > 500)), "NA")
 
@@
 
-  df2 <- filter(df2, gatherings %in% setdiff(names(which(table(df2$gatherings) >= 20)), "NA"))
+  #df2 <- filter(df2, gatherings %in% setdiff(names(which(table(df2$gatherings) >= 20)), "NA"))
+  df2 <- filter(df2, gatherings %in% common.gatherings)  
   df2$highlight <- rep("Other", nrow(df2))
@@
 		       ))
+
   p <- p + geom_point(size = 4)
@@
   p <- p + scale_color_manual(values = c("darkgreen", "darkgray"))
-
-  #p <- p + scale_fill_manual(values = c(cols[[catal]], "darkgray"))
-  #p <- p + scale_color_manual(values = c(cols[[catal]], "darkgray"))
-
-  #   scale_color_stata() +
-  #   scale_fill_stata() +
   p <- p + xlab("Decade")
@@
   p <- p + ylim(c(0, max(na.omit(df2$paper))))
+  #p <- p + scale_shape_manual(values = factor(common.gatherings))
+  #p <- p + scale_linetype_manual(values = factor(common.gatherings))
 
@@
 
-  p <- p + #ggtitl(paste("Paper consumption (", catal, ")", sep = "")) +
-         #ggtitle(paste("Figure 3", c("A", "B")[which(unique(df00$catalog) == catal)], sep = "")) +
-         ggtitle(paste(c("A", "B")[which(unique(df00$catalog) == catal)], sep = "")) +       	 
+  p <- p + 
          scale_x_continuous(breaks = brs,
 	   labels = insert_minor(brs, 5, start = ifelse(catal == "Fennica", 1500, 1550))) + 
-         scale_y_continuous(breaks = seq(0, max(df2$paper), 2e6), label = scientific_10)
+         scale_y_continuous(breaks = seq(0, max(df2$paper), 2e6), label = scientific_10) #+
 
@@
 
-grid.arrange(pics[[1]], pics[[2]], top = "Figure 3", layout_matrix = matrix(c(1,2), nrow = 2, byrow=TRUE))
+library(cowplot)
+# arrange the three plots in a single row
+prow <- plot_grid(
+           pics[[1]] + theme(legend.position="none"),
+           pics[[2]] + theme(legend.position="none"),
+           align = 'vh',
+           labels = c("A", "B"),
+           hjust = -1,
+           nrow = 1
+           )
+
+# extract the legend from one of the plots
+# (clearly the whole thing only makes sense if all plots
+# have the same legend, so we can arbitrarily pick one.)
+legend_b <- get_legend(pics[[1]] + theme(legend.position="right"))
+
+# add the legend underneath the row we made earlier. Give it 10% of the height
+# of one plot (via rel_heights).
+p <- plot_grid( prow, legend_b, ncol = 2, rel_widths = c(1, .2))
+title <- ggdraw() + draw_label("Figure 3", fontface='bold')
+plot_grid(title, p, ncol=1, rel_heights=c(0.1, 1)) # rel_heights values control title margins
 ```
@@
 
-pics[[unique(df$catalog)[[1]]]] <- pics[[unique(df$catalog)[[1]]]] + labs(title = "Figure 4")
+#pics[[unique(df$catalog)[[1]]]] <- pics[[unique(df$catalog)[[1]]]] + labs(title = "Figure 4")
 
@@
 p <- plot_grid( prow, legend_b, ncol = 2, rel_widths = c(1, .2))
+title <- ggdraw() + draw_label("Figure 4", fontface='bold')
+plot_grid(title, p, ncol=1, rel_heights=c(0.1, 1)) # rel_heights values control title margins
 #print(p)

### 2017-10-16 inst/examples/20170201-manuscript.Rmd
ok

@@
 
-```{r Fig3, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=9, fig.height=5, fig.show="hold"}
+```{r Fig3, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=16, fig.height=5, fig.show="hold"}
 library(scales)
@@
 
-```{r Fig4, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=4, fig.width=12}
+```{r Fig4, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=4, fig.width=12, fig.show="last"}
 cols <- list(Fennica = "blue", Kungliga = "darkred")

### 2017-10-16 inst/examples/20170201-manuscript.Rmd
ok

@@
 
-```{r Fig3, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=16, fig.height=5, fig.show="hold"}
+```{r Fig3, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=20, fig.height=5, fig.show="last"}
 library(scales)

### 2017-10-16 inst/examples/20170201-manuscript.Rmd
ok

@@
 
-```{r Fig3, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=20, fig.height=5, fig.show="last"}
+```{r Fig3, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=18, fig.height=5, fig.show="last"}
 library(scales)
@@
 title <- ggdraw() + draw_label("Figure 4", fontface='bold')
-plot_grid(title, p, ncol=1, rel_heights=c(0.1, 1)) # rel_heights values control title margins
-#print(p)
+p <- plot_grid(title, p, ncol=1, rel_heights=c(0.1, 1)) # rel_heights values control title margins
+print(p)
 ```

### 2017-10-16 inst/examples/20170201-manuscript.Rmd
ok

@@
 title <- ggdraw() + draw_label("Figure 3", fontface='bold')
-plot_grid(title, p, ncol=1, rel_heights=c(0.1, 1)) # rel_heights values control title margins
+plot_grid(title, p, ncol=1, rel_heights=c(0.1, 1), hjust = 0) 
 ```

### 2017-10-26 inst/examples/20170201-manuscript.Rmd
trying to fix fig 3
Fig 8-9 update adding Other publication places

@@
 pics <- list()
-for (catal in unique(df00$catalog)) {
+for (catal in unique(df.full$catalog)) {
 
@@
 top <- c("Turku", "Vaasa", "Vyborg")
+df <- filter(df, !is.na(publication_place))
+df$publication_place[!df$publication_place %in% top] <- "Other/Fennica"
+top <- c(top, "Other/Fennica")
 df <- df %>%	
-        filter(publication_place %in% top) %>%	
+        #filter(publication_place %in% top) %>%	
         select(publication_decade, publication_place, publisher)
@@
 top <- c("Stockholm", "Lund", "Uppsala", "Greifswald", "Tartu")
+df <- filter(df, !is.na(publication_place))
+df$publication_place[!df$publication_place %in% top] <- "Other/Kungliga"
+top <- c(top, "Other/Kungliga")
 df <- df %>%	
-        filter(publication_place %in% top) %>%	
+        #filter(publication_place %in% top) %>%	
         select(publication_decade, publication_place, publisher)
@@
         filter(catalog == catal) %>%
-	filter(country == "Finland" | publication_place == "Vyborg") %>%
+	#filter(country == "Finland" | publication_place == "Vyborg") %>%
         filter(publication_year >= 1640 & publication_year <= 1828)
@@
 top <- c("Stockholm", "Lund", "Uppsala", "Greifswald", "Tartu")
+df <- filter(df, !is.na(publication_place))
+df$publication_place[!df$publication_place %in% top] <- "Other/Kungliga"
+top <- c(top, "Other/Kungliga")
 df <- df %>%	

### 2017-10-26 inst/examples/20170201-manuscript.Rmd
ok

@@
 df <- filter(df, !is.na(publication_place))
-df$publication_place[!df$publication_place %in% top] <- "Other/Fennica"
-top <- c(top, "Other/Fennica")
+df$publication_place[!df$publication_place %in% top] <- "Other"
+top <- c(top, "Other")
 df <- df %>%	
@@
 df <- filter(df, !is.na(publication_place))
-df$publication_place[!df$publication_place %in% top] <- "Other/Kungliga"
-top <- c(top, "Other/Kungliga")
+df$publication_place[!df$publication_place %in% top] <- "Other"
+top <- c(top, "Other")
 df <- df %>%	

### 2017-10-26 inst/examples/20170201-manuscript.Rmd
ok

@@
 ```{r Fig9, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=5, fig.width=12}
+
 df <- df0
@@
 
-npub <- unique(df) %>% group_by(publication_decade, publication_place) %>% tally()
+npub <- unique(df) %>% group_by(publication_decade, publication_place) %>%
+                       tally()
 npub$publication_place <- factor(npub$publication_place, levels = top)
@@
 # Order by total publishing activity
-npub$publication_place <- factor(npub$publication_place,
-                                 levels = (npub %>%
+npub$publication_place <- as.character((npub$publication_place))
+
+npub <- npub %>% group_by(publication_decade, publication_place) %>%
+                       summarise(n = sum(n))
+
+levs <- npub %>%
   group_by(publication_place) %>%				             
   summarise(total = sum(n)) %>%					     
-					     arrange(desc(total)))$publication_place)
+  arrange(desc(total))
+levs <- levs$publication_place
+
+npub$publication_place <- factor(npub$publication_place, levs)
 npub <- npub %>% arrange(publication_place)
@@
        ggtitle("Figure 9")
-       #ggtitl(paste("Publishers (", catal, ")", sep = ""))
-
-print(p)
+
+print(p)
+
 ```

### 2017-10-27 inst/examples/20151209-HelsinkiDH.Rmd
rOpenGov links to COMHIS links

@@
 This markdown document contains presentation material for [Digital History in Finland seminar (University of Helsinki, Dec 9, 2015)](http://blogs.helsinki.fi/mstolone/2015/09/21/call-for-papers-digital-history-in-finland-wednesday-9-12-2015/).
-The source code to reproduce the figures is in the [Rmarkdown document](https://github.com/rOpenGov/fennica/blob/master/inst/examples/20151209-HelsinkiDH.Rmd).
+The source code to reproduce the figures is in the [Rmarkdown document](https://github.com/COMHIS/fennica/blob/master/inst/examples/20151209-HelsinkiDH.Rmd).
 

### 2017-10-27 inst/examples/20170201-manuscript.Rmd
rOpenGov links to COMHIS links

@@
 
-The historical population sizes used in this analysis are shown in this [table](https://github.com/rOpenGov/bibliographica/blob/master/inst/extdata/population_sizes_in_cities.csv).
+The historical population sizes used in this analysis are shown in this [table](https://github.com/COMHIS/bibliographica/blob/master/inst/extdata/population_sizes_in_cities.csv).
 

### 2017-10-27 inst/examples/summary.Rmd
ok
rOpenGov links to COMHIS links

@@
 
-[Self-published accepted](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/self_published_accepted.csv) (Check for formatting and synonymes)
+[Self-published accepted](https://github.com/COMHIS/fennica/blob/master/inst/examples/output.tables/self_published_accepted.csv) (Check for formatting and synonymes)
 
-[Self-published raw fields](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/self_published_rawfields.csv) (Check that the self-publication is a correct classification for these docs)
+[Self-published raw fields](https://github.com/COMHIS/fennica/blob/master/inst/examples/output.tables/self_published_rawfields.csv) (Check that the self-publication is a correct classification for these docs)
 
@@
 
-[Accepted corporate info](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/corporate_accepted.csv)
+[Accepted corporate info](https://github.com/COMHIS/fennica/blob/master/inst/examples/output.tables/corporate_accepted.csv)
 
-[Discarded corporate info](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/corporate_discarded.csv)
+[Discarded corporate info](https://github.com/COMHIS/fennica/blob/master/inst/examples/output.tables/corporate_discarded.csv)
 
@@
 
-[Complete geoplace listing](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/geoplaces.csv)
+[Complete geoplace listing](https://github.com/COMHIS/fennica/blob/master/inst/examples/output.tables/geoplaces.csv)

### 2017-11-13 inst/examples/201705-Gaudeamus.Rmd
runs go through again

@@
 # Data files
-input.data.file <- "df.combined.Gaudeamus2017.Rds"
+#input.data.file <- "df.combined.Gaudeamus2017.Rds"
+input.data.file <- "df.combined.20170125.Rds"
 

### 2017-11-13 R/polish_publisher_fennica.R

@@ -96,7 +96,7 @@ polish_publisher_fennica <- function (df.preprocessed, useShortcuts=FALSE) {
   # ----------------------------------------------------------------------------------
   
   # Convert S.N. into NA 
-  f <- system.file("extdata/NA_publishers.csv", package = "bibliographica")
+  f <- system.file("extdata/NA_publishers.csv", package = "fennica")
   synonymes <- read.csv(file = f, sep = "\t", fileEncoding = "UTF-8", as.is = TRUE)
 
   # HR 20160930:

### 2017-11-14 inst/examples/20170201-manuscript.Rmd
harmonized colors across figures

@@
 
+cities <- c(
+	      "Greifswald",
+	      "Lund",
+	      "Other",
+	      "Stockholm",
+	      "Tartu",
+	      "Turku",
+	      "Uppsala",
+	      "Vyborg",
+	      "Gothenburg",
+	      "Linkoping"
+	    )
+city.colors <- stata_pal("s2color")(length(city.colors))
+names(city.colors) <- cities
+
+languages <- c(
+	      "Finnish",
+	      "Swedish",
+	      "French",
+	      "German",
+	      "Hebrew",
+	      "Latin",
+	      "Other",
+	      "Russian2"
+	    )
+lang.colors <- stata_pal("s2color")(length(city.colors))
+names(lang.colors) <- languages
+
 knitr::opts_chunk$set(echo = FALSE)
@@
      xlab("Decade") +
-     scale_fill_stata() 
+     #scale_fill_stata() 
      if (varname == "n") {
@@
   p <- p + scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5, start = century(min(dff$publication_decade)) + 50))
+  p <- p + scale_fill_manual(values = city.colors[as.character(levels(dff$publication_place))])
 
@@
        scale_fill_stata() +
+       #scale_fill_manual(values = city.colors[as.character(levels(df$publication_place))]) + 
        guides(fill = guide_legend(title = "Period")) +
@@
 ```{r Fig8, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=5, fig.width=12}
+# Top publication places
+library(bibliographica)
+
 df <- df0
@@
 
-# Top publication places
-library(bibliographica)
-
 top <- c("Turku", "Vaasa", "Vyborg")
 df <- filter(df, !is.na(publication_place))
-df$publication_place[!df$publication_place %in% top] <- "Other/Fennica"
-top <- c(top, "Other/Fennica")
+df$publication_place[!df$publication_place %in% top] <- "Other"
+top <- c(top, "Other")
 df <- df %>%	
@@
         select(publication_decade, publication_place, publisher)
+df.fennica <- df
 
@@
         filter(catalog == catalogue) %>%
-        filter(publication_year >= 1640 & publication_year <= 1828)
+        filter(publication_year >= 1640 & publication_year <= 1828) %>%
+        filter(country == "Sweden" | publication_place %in% c("Greifswald", "Tartu"))
 
@@
         select(publication_decade, publication_place, publisher)
+df.kungliga <- df
 
@@
 npub$publication_place <- factor(npub$publication_place, levels = rev(unique(npub$publication_place)))
+
+rminds <- c()
+for (dec in npub$publication_decade) {
+  inds <- which(npub$publication_decade == dec & npub$publication_place == "Other")
+  # Combine the counts for the other place
+  if (length(inds) == 2) {
+    npub[inds[[1]], "n"] <- sum(npub[inds,"n"])
+    rminds <- c(rminds, inds[[2]])
+  }
+}
+npub <- npub[-rminds, ]
 
@@
        ylab("Publishers (n)") +
-       scale_fill_stata() +       
+       #scale_fill_stata() +
+       scale_fill_manual(values = city.colors[as.character(levels(npub$publication_place))]) +        
        guides(fill = guide_legend(reverse = FALSE, title = "")) +
@@
        ylab("Publishers (n)") +
-       scale_fill_stata() +
+       #scale_fill_stata() +
+       scale_fill_manual(values = city.colors[as.character(levels(npub$publication_place))]) +               
        scale_x_continuous(breaks = brs,
@@
        ylab("Title count per capita (n)") +
-       scale_color_stata() +
+       #scale_color_stata() +
+       scale_color_manual(values = city.colors[as.character(levels(dfm$publication_place))]) +                      
        #scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5)) +
@@
        guides(color = guide_legend(title = "Place")) +
-       scale_color_stata()
+       scale_color_manual(values = city.colors[as.character(levels(df$publication_place))]) 
+       #scale_color_stata()
 print(p)
@@
        guides(shape = guide_legend(title = "Place"), color = guide_legend(title = "Place")) +
-       scale_color_stata()
+       scale_color_manual(values = city.colors[as.character(levels(df$publication_place))]) 
+       #scale_color_stata()
 print(p)
@@
        ggtitle("Figure 15") +                            
-       scale_fill_stata() +
+       #scale_fill_stata() +
+       scale_fill_manual(values = city.colors[as.character(levels(df$publication_place))]) +
        scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5, start = century(min(brs)) + 50)) +
@@
       p <- p + labs(subtitle = paste(myplace, "/", catalogue)) +                 
-      scale_fill_stata() +
+      #scale_fill_stata() +
+      scale_fill_manual(values = lang.colors[as.character(levels(dfss$publication_place))]) +      
       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5)) +  
@@
        scale_fill_brewer(palette="Greys") +
+       #scale_color_manual(values = city.colors[as.character(levels(df$publication_place))]) +
        # geom_smooth(color = "black") +
@@
               color = guide_legend(title = "Language")) +
-       scale_color_stata() +
+       #scale_color_stata() +
+       scale_color_manual(values = city.colors[as.character(levels(df$publication_place))]) +             
        # scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5)) +
@@
        scale_y_continuous(label = scientific_10) + 
-       scale_color_stata() +
+       #scale_color_stata() +
+       scale_color_manual(values = city.colors[as.character(levels(df$publication_place))]) +  
        ggtitle("Figure 18")
@@
        guides(shape = guide_legend(title = "Language"), color = guide_legend(title = "Language")) +
-       scale_color_stata() +
+       #scale_color_stata() +
+       scale_color_manual(values = city.colors[as.character(levels(df$publication_place))]) +         
        # scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5)) +

### 2017-11-14 inst/examples/20170201-manuscript.Rmd
ok

@@
 
-```{r Fig3, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=18, fig.height=5, fig.show="last"}
+```{r Fig3prep, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=18, fig.height=5, fig.show="hide"}
 library(scales)
@@
 title <- ggdraw() + draw_label("Figure 3", fontface='bold')
+```
+
+```{r Fig3, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=18, fig.height=5, fig.show="hide"}
 plot_grid(title, p, ncol=1, rel_heights=c(0.1, 1), hjust = 0) 

### 2017-11-14 inst/examples/20170201-manuscript.Rmd
ok

@@
 
-```{r Fig3prep, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=18, fig.height=5, fig.show="hide"}
+```{r Fig3prep, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=18, fig.height=5, fig.show="hide", results="hide"}
 library(scales)
@@
 
-```{r Fig3, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=18, fig.height=5, fig.show="hide"}
+```{r Fig3, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=18, fig.height=5}
 plot_grid(title, p, ncol=1, rel_heights=c(0.1, 1), hjust = 0) 

### 2017-11-14 inst/examples/20170201-manuscript.Rmd
ok

@@
        aes(fill = publication_place)) + 
-     xlab("Decade") +
+     xlab("Decade") 
      #scale_fill_stata() 
@@
      }     
-  p <- p + guides(fill = guide_legend(title = "")) 
   p <- p + scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5, start = century(min(dff$publication_decade)) + 50))
   p <- p + scale_fill_manual(values = city.colors[as.character(levels(dff$publication_place))])
+  p <- p + guides(fill = guide_legend(title = ""))
 

### 2017-11-14 inst/examples/20170201-manuscript.Rmd
ok

@@
 ```{r Fig3, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=18, fig.height=5}
-plot_grid(title, p, ncol=1, rel_heights=c(0.1, 1), hjust = 0) 
+print(plot_grid(title, p, ncol=1, rel_heights=c(0.1, 1), hjust = 0))
 ```
@@
 
-```{r Fig4, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=4, fig.width=12, fig.show="last"}
+```{r Fig4, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=5, fig.width=15, fig.show="last"}
 cols <- list(Fennica = "blue", Kungliga = "darkred")
@@
        #scale_color_stata() +
-       scale_color_manual(values = city.colors[as.character(levels(dfm$publication_place))]) +                      
+       scale_color_manual(values = city.colors[as.character(levels(df$publication_place))]) +                      
        #scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5)) +
@@
        scale_y_continuous(breaks = brsy, labels = insert_minor(brsy, 1)) +
+       scale_color_manual(values = city.colors[as.character(levels(df$publication_place))]) +       
        guides(shape = guide_legend(title = "Place")) +
-       guides(color = guide_legend(title = "Place")) +
-       scale_color_manual(values = city.colors[as.character(levels(df$publication_place))]) 
+       guides(color = guide_legend(title = "Place")) 
        #scale_color_stata()
@@
        scale_y_continuous(label = scientific_10) +
-       #ggtitle("Paper consumption (Octavo)") +
        ggtitle("Figure 14") +
-       guides(shape = guide_legend(title = "Place"), color = guide_legend(title = "Place")) +
-       scale_color_manual(values = city.colors[as.character(levels(df$publication_place))]) 
+       scale_color_manual(values = city.colors[as.character(levels(df$publication_place))]) +       
+       guides(shape = guide_legend(title = "Place"), color = guide_legend(title = "Place")) 
        #scale_color_stata()
@@
       #scale_fill_stata() +
-      scale_fill_manual(values = lang.colors[as.character(levels(dfss$publication_place))]) +      
+      scale_fill_manual(values = lang.colors[as.character(levels(dfss$language))]) +      
       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5)) +  
@@
       guides(fill = guide_legend(title = "")) 
-      #guides(fill = guide_legend(title = "")) +       
     pics[[paste(catalogue, myplace, sep = "-")]] <- p
@@
        #scale_color_stata() +
-       scale_color_manual(values = city.colors[as.character(levels(df$publication_place))]) +             
+       scale_color_manual(values = lang.colors[as.character(levels(df$language))]) +             
        # scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5)) +
@@
        #scale_color_stata() +
-       scale_color_manual(values = city.colors[as.character(levels(df$publication_place))]) +  
+       scale_color_manual(values = lang.colors[as.character(levels(df$language))]) +  
        ggtitle("Figure 18")
@@
        #scale_color_stata() +
-       scale_color_manual(values = city.colors[as.character(levels(df$publication_place))]) +         
+       scale_color_manual(values = lang.colors[as.character(levels(df$language))]) +         
        # scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5)) +

### 2017-11-14 inst/examples/20170201-manuscript.Rmd
ok

@@
 	      "Gothenburg",
-	      "Linkoping"
+	      "Linköping"
 	    )
@@
        #scale_color_stata() +
-       scale_color_manual(values = city.colors[as.character(levels(df$publication_place))]) +                      
+       #scale_color_manual(values = city.colors[as.character(levels(dfm$publication_place))]) +
+       scale_color_manual(values = city.colors[match(unique(dfm$publication_place), names(city.colors))]) +              
        #scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5)) +
@@
 labs <- brs; labs[!brs %in% df$publication_decade] <- ""
+#df$publication_place <- factor(df$publication_place, levels = levels(df0$publication_place))
+
 p <- ggplot(df, aes(x = publication_decade, y = n)) +
@@
        ylab("Title count (n)") +
-       #ggtitle("Title count (absolute)") +
        ggtitle("Figure 13") +              
-       #scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5)) +
        scale_x_continuous(breaks = brs, labels = labs) +
        scale_y_continuous(breaks = brsy, labels = insert_minor(brsy, 1)) +
-       scale_color_manual(values = city.colors[as.character(levels(df$publication_place))]) +       
+       scale_color_manual(values = city.colors[match(unique(df$publication_place), names(city.colors))]) +       
        guides(shape = guide_legend(title = "Place")) +
        guides(color = guide_legend(title = "Place"))
-       #scale_color_stata()
+
 print(p)
@@
        ggtitle("Figure 14") +
-       scale_color_manual(values = city.colors[as.character(levels(df$publication_place))]) +       
+       scale_color_manual(values = city.colors[match(unique(df$publication_place), names(city.colors))]) +       
        guides(shape = guide_legend(title = "Place"), color = guide_legend(title = "Place")) 
@@
        #scale_color_stata() +
-       scale_color_manual(values = lang.colors[as.character(levels(df$language))]) +         
+       #scale_color_manual(values = lang.colors[as.character(levels(df$language))]) +
+       scale_color_manual(values = lang.colors[match(unique(df$language), names(lang.colors))]) +              
        # scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5)) +

### 2017-11-14 inst/examples/20170201-manuscript.Rmd
ok

@@
 cities <- c(
-	      "Greifswald",
 	      "Lund",
@@
 	      "Gothenburg",
-	      "Linköping"
+	      "Linköping",
+	      "Greifswald"	      
 	    )
@@
 	      "Other",
-	      "Russian2"
+	      "Russian"
 	    )

### 2017-11-14 inst/examples/20170201-manuscript.Rmd
ok

@@
 	      "Finnish",
+	      "Other",
 	      "Swedish",
@@
 	      "Latin",
-	      "Other",
 	      "Russian"
@@
 # Selected publication places
-top <- c("Stockholm", "Lund", "Uppsala", "Greifswald", "Tartu")
+top <- c("Stockholm", "Lund", "Uppsala", "Greifswald")
 df <- filter(df, !is.na(publication_place))

### 2017-11-14 inst/examples/20170201-manuscript.Rmd
ok

@@
 
-### Fig. 1: Number of publication places over time
+### Fig 1: Number of publication places over time
 
@@
 
-### Fig. 7: Publishing activity and riksdagar: Kungliga
+### Fig 7: Publishing activity and riksdagar: Kungliga
 
@@
 
-### Fig. 12: Title count per capita
+### Fig 12: Title count per capita
 
@@
 
-### Fig. 13: Title count (absolute)
+### Fig 13: Title count (absolute)
 
@@
 
-### Fig. 14: Octavo paper consumption
+### Fig 14: Octavo paper consumption
 
@@
 
-### Fig. 15: Octavo title length (word count)
+### Fig 15: Octavo title length (word count)
 
@@
 
-### Fig. 17: Topic richness per language (Fennica)
+### Fig 17: Topic richness per language (Fennica)
 
@@
 
-### Fig. 18: Temporary sermons in Latin and Swedish
+### Fig 18: Temporary sermons in Latin and Swedish
 
@@
 
-### Fig. 19: Devotional literature (catechisms, hymns, prayers, etc.)
+### Fig 19: Devotional literature (catechisms, hymns, prayers, etc.)
 

### 2017-11-14 inst/examples/20170201-manuscript.Rmd
ok

@@
 max.year <- 1828
-
+library(ggthemes)
 library(ggmap)
@@
 	    )
-city.colors <- stata_pal("s2color")(length(city.colors))
+city.colors <- stata_pal("s2color")(length(cities))
 names(city.colors) <- cities
@@
 library(ggplot2)
-library(ggthemes)
 # theme_set(theme_bw(20))
@@
 
-### Fig 9: Publishers in Swedish University towns (Kungliga)
-
-All towns from Kungliga.
-
-```{r Fig9, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=5, fig.width=12}
-
-df <- df0
-catal <- "Kungliga"
-df <- df %>%
-        filter(catalog == catal) %>%
-	#filter(country == "Finland" | publication_place == "Vyborg") %>%
-        filter(publication_year >= 1640 & publication_year <= 1828)
-
-# Top publication places
-library(bibliographica)
-
-top <- c("Turku", "Vaasa", "Vyborg")
-df <- filter(df, !is.na(publication_place))
-df$publication_place[!df$publication_place %in% top] <- "Other"
-top <- c(top, "Other")
-df <- df %>%	
-        #filter(publication_place %in% top) %>%	
-        select(publication_decade, publication_place, publisher)
-
-npub <- unique(df) %>% group_by(publication_decade, publication_place) %>% tally()
-npub$publication_place <- factor(npub$publication_place, levels = top)
-npub.fennica <- npub
-
-df <- df0
-catalogue <- "Kungliga"
-df <- df %>%
-        filter(catalog == catalogue) %>%
-        filter(publication_year >= 1640 & publication_year <= 1828)
-
-# Selected publication places
-top <- c("Stockholm", "Lund", "Uppsala", "Greifswald", "Tartu")
-df <- filter(df, !is.na(publication_place))
-df$publication_place[!df$publication_place %in% top] <- "Other"
-top <- c(top, "Other")
-df <- df %>%	
-        filter(publication_place %in% top) %>%	
-        select(publication_decade, publication_place, publisher)
-
-npub <- unique(df) %>% group_by(publication_decade, publication_place) %>%
-                       tally()
-npub$publication_place <- factor(npub$publication_place, levels = top)
-npub.kungliga <- npub
-npub <- bind_rows(npub.fennica, npub.kungliga)
-
-# Order by total publishing activity
-npub$publication_place <- as.character((npub$publication_place))
-
-npub <- npub %>% group_by(publication_decade, publication_place) %>%
-                       summarise(n = sum(n))
-
-levs <- npub %>%
-  group_by(publication_place) %>%				             
-  summarise(total = sum(n)) %>%					     
-  arrange(desc(total))
-levs <- levs$publication_place
-
-npub$publication_place <- factor(npub$publication_place, levs)
-npub <- npub %>% arrange(publication_place)
-npub$publication_place <- factor(npub$publication_place,
-                                 levels = rev(unique(npub$publication_place)))
-
-theme_set(theme_bw(20))
-brs <- seq(min(npub$publication_decade), max(npub$publication_decade), 10)  
-p <- ggplot(npub, aes(x = publication_decade, y = n)) +
-       geom_bar(stat = "identity", position = "stack", color = "black",
-       		    aes(fill = publication_place)) + 
-       xlab("Decade") +
-       ylab("Publishers (n)") +
-       #scale_fill_stata() +
-       scale_fill_manual(values = city.colors[as.character(levels(npub$publication_place))]) +               
-       scale_x_continuous(breaks = brs,
-           labels = insert_minor(brs, 2, start = min(npub$publication_decade))) + 
-       guides(fill = guide_legend(reverse = FALSE, title = "")) +
-       ggtitle("Figure 9")
-
-print(p)
-
-```
-
----
-
-### Fig 10: Publications in Vaasa in Fennica, 1750-1828
-
-```{r Fig10, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=5, fig.width=10}
+### Fig 9: Publications in Vaasa in Fennica, 1750-1828
+
+```{r Fig9, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=5, fig.width=10}
 library(dplyr)
@@
      ylab("Title count (n)") +
-     ggtitle("Figure 10")
+     ggtitle("Figure 9")
      #ggtitle(paste("Publications in Vaasa (", catalogue, ")", sep = ""))
@@
 
-### Fig 11: Top publishers in Turku/Fennica
-
-```{r Fig11, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=5, fig.width=12}
+### Fig 10: Top publishers in Turku/Fennica
+
+```{r Fig10, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=5, fig.width=12}
 library(dplyr)
@@
       guides(size = guide_legend(title = "Title count (n)")) +
-      ggtitle("Figure 11")      
+      ggtitle("Figure 10")      
       #ggtitle(paste("Top publishers in ", place, " (", catalogue, ")", sep = ""))
-      #ggtitle(paste("Figure 11: ", place, " (", catalogue, ")", sep = ""))
-
-print(p)
-```
-
----
-
-### Fig 12: Title count per capita
+      #ggtitle(paste("Figure 10: ", place, " (", catalogue, ")", sep = ""))
+
+print(p)
+```
+
+---
+
+### Fig 11: Title count per capita
 
@@
 
-```{r Fig12, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
+```{r Fig11, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
 # Read historical population sizes
@@
        #ggtitle("Title count per capita") +
-       ggtitle("Figure 12") +       
+       ggtitle("Figure 11") +       
        guides(shape = guide_legend(title = "Place")) +
@@
 
-### Fig 13: Title count (absolute)
-
-```{r Fig13, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
+### Fig 12: Title count (absolute)
+
+```{r Fig12, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
 minyear <- 1640
@@
        ylab("Title count (n)") +
-       ggtitle("Figure 13") +              
+       ggtitle("Figure 12") +              
        scale_x_continuous(breaks = brs, labels = labs) +
@@
 
-### Fig 14: Octavo paper consumption
+### Fig 13: Octavo paper consumption
 
@@
 
-```{r Fig14, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
+```{r Fig13, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
 # Take cities from Kungliga except Turku
@@
        scale_y_continuous(label = scientific_10) +
-       ggtitle("Figure 14") +
+       ggtitle("Figure 13") +
        scale_color_manual(values = city.colors[match(unique(df$publication_place), names(city.colors))]) +       
@@
 
-### Fig 15: Octavo title length (word count)
+### Fig 14: Octavo title length (word count)
 
@@
 
-```{r Fig15, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
+```{r Fig14, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
 # Take cities from Kungliga except Turku
@@
        #ggtitle("Average title length") +
-       ggtitle("Figure 15") +                            
+       ggtitle("Figure 14") +                            
        #scale_fill_stata() +
@@
 
-### Fig 16: Language use in Turku, Stockholm, Uppsala and Lund
-
-```{r Fig16, echo=FALSE, message=FALSE, warning=FALSE, fig.width=15, fig.height=7}
+### Fig 15: Language use in Turku, Stockholm, Uppsala and Lund
+
+```{r Fig15, echo=FALSE, message=FALSE, warning=FALSE, fig.width=15, fig.height=7}
 pics <- list()
@@
 
-grid.arrange(pics[[1]], pics[[8]], pics[[9]], pics[[10]], top = "Figure 16", layout_matrix = matrix(c(1,2,3,4), nrow = 2, byrow=TRUE))
+grid.arrange(pics[[1]], pics[[8]], pics[[9]], pics[[10]], top = "Figure 15", layout_matrix = matrix(c(1,2,3,4), nrow = 2, byrow=TRUE))
 
@@
 
-### Fig 17: Topic richness per language (Fennica)
-
-```{r Fig17, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5, fig.show="hold"}
+### Fig 16: Topic richness per language (Fennica)
+
+```{r Fig16, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5, fig.show="hold"}
 catalogue <- "Fennica"
@@
        xlab("Decade") +
-       ggtitle("Figure 17")
+       ggtitle("Figure 16")
        #ggtitle(paste("Topic richness (", catalogue, ")", sep = ""))
@@
 
-### Fig 18: Temporary sermons in Latin and Swedish
-
-```{r Fig18, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
+### Fig 17: Temporary sermons in Latin and Swedish
+
+```{r Fig17, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
 sel <- c("hautajaiset", "häät", "juhlamenot")
@@
        scale_color_manual(values = lang.colors[as.character(levels(df$language))]) +  
-       ggtitle("Figure 18")
+       ggtitle("Figure 17")
        #ggtitle(paste("Temporary sermons (", catalogue, ")", sep = ""))
@@
 
-### Fig 19: Devotional literature (catechisms, hymns, prayers, etc.)
+### Fig 18: Devotional literature (catechisms, hymns, prayers, etc.)
 
@@
 
-```{r Fig19, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5, fig.show="hold"}
+```{r Fig18, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5, fig.show="hold"}
 sel <- c("virret","arkkiveisut","hartauskirjat","katekismukset","rukouspäivät","saarnat","aapiset","rukoukset","rukous","hengelliset laulut","hartauspuheet","virsikirjat")
@@
        scale_y_continuous(label = scientific_10) +
-       ggtitle("Figure 19")       
+       ggtitle("Figure 18")       
        # ggtitle(paste("Devotional literature (", catalogue, ")", sep = ""))

### 2017-11-16 inst/examples/20170201-manuscript.Rmd
ok

@@
     fonttheme: "professionalfonts"
-fontsize: 13pt
+    dev: "png"
+  pdf_document:
+    dev: "svg"    
+fontsize: 12pt
 ---
@@
 #library(ggthemr)
+#knitr::opts_chunk$set(fig.path = "slides_201606_Krakow/", dev="CairoPNG")
 
@@
 knitr::opts_chunk$set(echo = FALSE)
-#knitr::opts_chunk$set(fig.path = "slides_201606_Krakow/", dev="CairoPNG")
-knitr::opts_chunk$set(fig.path = "20170201_manuscript/")
+knitr::opts_chunk$set(fig.path = "20170201_manuscript/", dpi = 300)
+#knitr::opts_chunk$set(dev = "cairo_postscript") # Embed fonts
+knitr::opts_chunk$set(dev = "svg") # Embed fonts
+knitr::opts_chunk$set(out.width = "17cm") # Default size 8.5cm ie 3.35 inch) per col
+knitr::opts_chunk$set(out.format = "latex")
 
@@
 
-```{r Fig1, message=FALSE, warning=FALSE, fig.width=10, fig.height=4, echo=FALSE}
+```{r Figure_1, message=FALSE, warning=FALSE, fig.width=10, fig.height=4, echo=FALSE}
+
+#message=FALSE, warning=FALSE, fig.width=10, fig.height=4, echo=FALSE, dpi=300, dev="postscript", out.format="latex", out.width="30%"
+
 library(dplyr)
@@
        #ggtitl("Unique publication places") +
-       ggtitle("Figure 1") +       
+       # ggtitle("Figure 1") +       
        scale_color_stata() +
@@
 
-```{r Fig2, message=FALSE, warning=FALSE, fig.width=10, fig.height=4, echo=FALSE}
+```{r Figure_2, message=FALSE, warning=FALSE, fig.width=10, fig.height=4, echo=FALSE}
 library(dplyr)
@@
        #ggtitl("Title count") +
-       ggtitle("Figure 2") +              
+       # ggtitle("Figure 2") +              
        scale_color_stata()
@@
 
-```{r Fig3prep, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=18, fig.height=5, fig.show="hide", results="hide"}
+```{r Figure_3prep, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=18, fig.height=5, fig.show="hide", results="hide"}
 library(scales)
@@
 
-```{r Fig3, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=18, fig.height=5}
+```{r Figure_3, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=18, fig.height=5}
 print(plot_grid(title, p, ncol=1, rel_heights=c(0.1, 1), hjust = 0))
@@
 
-```{r Fig4, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=5, fig.width=15, fig.show="last"}
+```{r Figure_4, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=5, fig.width=15, fig.show="last"}
 cols <- list(Fennica = "blue", Kungliga = "darkred")
@@
 
-```{r Fig5, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=15, fig.height=7}
+```{r Figure_5, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=15, fig.height=7}
 pics <- list()
@@
 library(gridExtra)
-#pics[[1]] <- pics[[1]] + ggtitle("Figure 5") 
+#pics[[1]] <- pics[[1]] + # ggtitle("Figure 5") 
 grid.arrange(pics[[1]], pics[[2]], pics[[4]], pics[[5]], top = "Figure 5", layout_matrix = matrix(c(1,2,3,4), nrow = 2, byrow=TRUE))
@@
 
-```{r Fig6, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=4}
+```{r Figure_6, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=4}
 library(magrittr)
@@
        guides(fill = guide_legend(title = "Period")) +
-       ylab("Paper (sheets)") + xlab("") +
-       ggtitle("Figure 6") 
+       ylab("Paper (sheets)") + xlab("") 
+       # ggtitle("Figure 6") 
        #ggtitl("Average paper consumption per title")
@@
 
-```{r Fig7, echo=FALSE, message=FALSE, warning=FALSE, fig.width=11, fig.height=4}
+```{r Figure_7, echo=FALSE, message=FALSE, warning=FALSE, fig.width=11, fig.height=4}
 
@@
   p <- p + xlab("Year")
-  p <- p + ggtitle("Figure 7")   
+
+  #p <- p + # ggtitle("Figure 7")   
   #p <- p + #ggtitl(paste("Title count (", catal, " ", minyear, "-", maxyear, ")", sep = ""))
@@
 
-```{r Fig8, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=5, fig.width=12}
+```{r Figure_8, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=5, fig.width=12}
 # Top publication places
@@
        guides(fill = guide_legend(reverse = FALSE, title = "")) +
-       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 2)) +
-       ggtitle("Figure 8")
+       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 2)) 
+       # ggtitle("Figure 8")
        #ggtitl(paste("Publishers (", catal, ")", sep = ""))
@@
 
-```{r Fig9, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=5, fig.width=10}
+```{r Figure_9, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=5, fig.width=10}
 library(dplyr)
@@
      xlab("Year") +
-     ylab("Title count (n)") +
-     ggtitle("Figure 9")
+     ylab("Title count (n)") 
+     # ggtitle("Figure 9")
      #ggtitle(paste("Publications in Vaasa (", catalogue, ")", sep = ""))
@@
 
-```{r Fig10, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=5, fig.width=12}
+```{r Figure_10, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=5, fig.width=12}
 library(dplyr)
@@
       ylab("") +
-      guides(size = guide_legend(title = "Title count (n)")) +
-      ggtitle("Figure 10")      
+      guides(size = guide_legend(title = "Title count (n)")) 
+      # ggtitle("Figure 10")      
       #ggtitle(paste("Top publishers in ", place, " (", catalogue, ")", sep = ""))
@@
 
-```{r Fig11, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
+```{r Figure_11, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
 # Read historical population sizes
@@
        #scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5)) +
-       scale_x_continuous(breaks = brs, labels = labs) +                    
+       scale_x_continuous(breaks = brs, labels = labs) 
        #ggtitle("Title count per capita") +
-       ggtitle("Figure 11") +       
+       # ggtitle("Figure 11") +       
        guides(shape = guide_legend(title = "Place")) +
@@
 
-```{r Fig12, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
+```{r Figure_12, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
 minyear <- 1640
@@
        ylab("Title count (n)") +
-       ggtitle("Figure 12") +              
+       # ggtitle("Figure 12") +              
        scale_x_continuous(breaks = brs, labels = labs) +
@@
 
-```{r Fig13, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
+```{r Figure_13, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
 # Take cities from Kungliga except Turku
@@
        scale_y_continuous(label = scientific_10) +
-       ggtitle("Figure 13") +
+       # ggtitle("Figure 13") +
        scale_color_manual(values = city.colors[match(unique(df$publication_place), names(city.colors))]) +       
@@
 
-```{r Fig14, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
+```{r Figure_14, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
 # Take cities from Kungliga except Turku
@@
        #ggtitle("Average title length") +
-       ggtitle("Figure 14") +                            
+       # ggtitle("Figure 14") +                            
        #scale_fill_stata() +
@@
 
-```{r Fig15, echo=FALSE, message=FALSE, warning=FALSE, fig.width=15, fig.height=7}
+```{r Figure_15, echo=FALSE, message=FALSE, warning=FALSE, fig.width=15, fig.height=7}
 pics <- list()
@@
 
-```{r Fig16, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5, fig.show="hold"}
+```{r Figure_16, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5, fig.show="hold"}
 catalogue <- "Fennica"
@@
        ylab("Subject topics (n)") +
-       xlab("Decade") +
-       ggtitle("Figure 16")
+       xlab("Decade") 
+       # ggtitle("Figure 16")
        #ggtitle(paste("Topic richness (", catalogue, ")", sep = ""))
@@
 
-```{r Fig17, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
+```{r Figure_17, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
 sel <- c("hautajaiset", "häät", "juhlamenot")
@@
        #scale_color_stata() +
-       scale_color_manual(values = lang.colors[as.character(levels(df$language))]) +  
-       ggtitle("Figure 17")
+       scale_color_manual(values = lang.colors[as.character(levels(df$language))]) 
+       # ggtitle("Figure 17")
        #ggtitle(paste("Temporary sermons (", catalogue, ")", sep = ""))
@@
 
-```{r Fig18, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5, fig.show="hold"}
+```{r Figure_18, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5, fig.show="hold"}
 sel <- c("virret","arkkiveisut","hartauskirjat","katekismukset","rukouspäivät","saarnat","aapiset","rukoukset","rukous","hengelliset laulut","hartauspuheet","virsikirjat")
@@
        scale_x_continuous(breaks = brs, labels = insert_minor(brs, 2)) +       
-       scale_y_continuous(label = scientific_10) +
-       ggtitle("Figure 18")       
+       scale_y_continuous(label = scientific_10) 
+       # ggtitle("Figure 18")       
        # ggtitle(paste("Devotional literature (", catalogue, ")", sep = ""))

### 2017-11-16 inst/examples/20170201-manuscript.Rmd
ok

@@
 #knitr::opts_chunk$set(dev = "cairo_postscript") # Embed fonts
-knitr::opts_chunk$set(dev = "svg") # Embed fonts
+knitr::opts_chunk$set(dev = c("svg", "png")) # Embed fonts
 knitr::opts_chunk$set(out.width = "17cm") # Default size 8.5cm ie 3.35 inch) per col

### 2017-11-16 inst/examples/20170201-manuscript.Rmd
ok

--- 2017-11-16 inst/examples/20170201-manuscript.Rmd
@@
     dev: "svg"
+    out.width=17cm
 fontsize: 12pt
@@
 #knitr::opts_chunk$set(dev = "cairo_postscript") # Embed fonts
-knitr::opts_chunk$set(dev = "svg") # Embed fonts
+knitr::opts_chunk$set(dev = c("png", "svg")) # Embed fonts
 knitr::opts_chunk$set(out.width = "17cm") # Default size 8.5cm ie 3.35 inch) per col

### 2017-11-16 inst/examples/20170201-manuscript.Rmd
ok

@@
 #knitr::opts_chunk$set(dev = "cairo_postscript") # Embed fonts
-knitr::opts_chunk$set(dev = c("png", "svg")) # Embed fonts
+# knitr::opts_chunk$set(dev = c("png", "svg")) # Embed fonts
 knitr::opts_chunk$set(out.width = "17cm") # Default size 8.5cm ie 3.35 inch) per col

### 2017-11-16 inst/examples/20170201-manuscript.Rmd
ok

@@
     dev: "png"
-  pdf_document:
-    dev: "svg"
 fontsize: 12pt
@@
 library(devtools)
-# install_github("ropengov/gisfin")
-# devtools::install_github('cttobin/ggthemr')
-#library(ggthemr)
-#knitr::opts_chunk$set(fig.path = "slides_201606_Krakow/", dev="CairoPNG")
 

### 2017-11-16 inst/examples/20170201-manuscript.Rmd
ok

@@
 tmp <- Sys.setlocale(locale="UTF-8") 
-
-# Nice theme
-# theme_set(theme_bw(26))
-
-# Nice default themes
-# https://github.com/cttobin/ggthemr#palettes
-#ggthemr('fresh', text_size = 20)
-# ggthemr('greyscale', text_size = 20)
-#ggthemr('light', text_size = 20)
-# ggthemr('pale', text_size = 20)
-#ggthemr_reset() # Reset theme
 ```
@@
        #scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5)) +
-       scale_x_continuous(breaks = brs, labels = labs) 
+       scale_x_continuous(breaks = brs, labels = labs) +
        #ggtitle("Title count per capita") +

### 2017-11-16 inst/examples/20170201-manuscript.Rmd
ok

@@
 # knitr::opts_chunk$set(dev = c("png", "svg")) # Embed fonts
+knitr::opts_chunk$set(dev = c("png")) # Embed fonts
 knitr::opts_chunk$set(out.width = "17cm") # Default size 8.5cm ie 3.35 inch) per col

### 2017-11-17 inst/examples/20170201-manuscript.Rmd
ok

--- 2017-11-16 inst/examples/20170201-manuscript.Rmd
@@
     fonttheme: "professionalfonts"
-    dev: "png"
+    dev: "pdf"
 fontsize: 12pt
@@
 knitr::opts_chunk$set(fig.path = "20170201_manuscript/", dpi = 300)
-#knitr::opts_chunk$set(dev = "cairo_postscript") # Embed fonts
-# knitr::opts_chunk$set(dev = c("png", "svg")) # Embed fonts
-knitr::opts_chunk$set(out.width = "17cm") # Default size 8.5cm ie 3.35 inch) per col
+knitr::opts_chunk$set(dev = "jpeg", quality = 100) 
+#knitr::opts_chunk$set(dev = "cairo_pdf") # Embed fonts
+#knitr::opts_chunk$set(dev = "cairo_ps") # Embed fonts
+# knitr::opts_chunk$set(dev = c("png")) # Embed fonts
+knitr::opts_chunk$set(out.width = "10cm") # Default size 8.5cm ie 3.35 inch) per col
 knitr::opts_chunk$set(out.format = "latex")
@@
 
-```{r Figure_1, message=FALSE, warning=FALSE, fig.width=10, fig.height=4, echo=FALSE}
-
-#message=FALSE, warning=FALSE, fig.width=10, fig.height=4, echo=FALSE, dpi=300, dev="postscript", out.format="latex", out.width="30%"
+```{r Figure_1, message=FALSE, warning=FALSE, fig.width=11, fig.height=5, echo=FALSE}
 
@@
 print(p)
+
+#postscript(file = "Figure_1.eps", width = 11, height = 5, paper = "special",
+#              family = "sans", bg = "white")
+#print(p)
+#dev.off()
+#library(extrafont)
+#embed_fonts("Figure_1.eps", outfile="Figure_1.eps")
 ```

### 2017-11-17 inst/examples/20170201-manuscript.Rmd
ok

@@
 knitr::opts_chunk$set(fig.path = "20170201_manuscript/", dpi = 300)
-knitr::opts_chunk$set(dev = "jpeg", quality = 100) 
+knitr::opts_chunk$set(dev = c("png", "jpeg"))
 #knitr::opts_chunk$set(dev = "cairo_pdf") # Embed fonts

### 2017-11-17 inst/examples/20170201-manuscript.Rmd
ok

@@
 # knitr::opts_chunk$set(dev = c("png")) # Embed fonts
-knitr::opts_chunk$set(out.width = "10cm") # Default size 8.5cm ie 3.35 inch) per col
+# knitr::opts_chunk$set(out.width = "10cm") # Default size 8.5cm ie 3.35 inch) per col
 knitr::opts_chunk$set(out.format = "latex")

### 2017-11-17 inst/examples/20170201-manuscript.Rmd
ok

--- 2017-11-17 inst/examples/20170201-manuscript.Rmd
@@
 knitr::opts_chunk$set(fig.path = "20170201_manuscript/", dpi = 300)
-knitr::opts_chunk$set(dev = c("png", "jpeg"))
+knitr::opts_chunk$set(dev = c("png", "jpeg", "cairo_ps"))
 #knitr::opts_chunk$set(dev = "cairo_pdf") # Embed fonts
 #knitr::opts_chunk$set(dev = "cairo_ps") # Embed fonts
-# knitr::opts_chunk$set(dev = c("png")) # Embed fonts
-knitr::opts_chunk$set(out.width = "10cm") # Default size 8.5cm ie 3.35 inch) per col
+knitr::opts_chunk$set(out.width = "17cm") # Default size 8.5cm ie 3.35 inch) per col
 knitr::opts_chunk$set(out.format = "latex")
@@
 
-```{r Figure_1, message=FALSE, warning=FALSE, fig.width=11, fig.height=5, echo=FALSE}
+```{r Figure_1, message=FALSE, warning=FALSE, fig.width=13, fig.height=5, echo=FALSE}
 

### 2017-11-17 inst/examples/20170201-manuscript.Rmd
Fennica/Kungliga JM manuscript final Figures.

@@
 ```{r init, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}
+# Checking figure dimensions
+# identify -format "%[fx:w/300] by %[fx:h/300] inches\n" Figure_1-1.eps
+# Checking resolution
+# identify -verbose Figure_1-1.eps
+
 # Default time span
@@
 knitr::opts_chunk$set(out.format = "latex")
+knitr::opts_chunk$set(fig.width=13.5,fig.height=8)
 
@@
 
-```{r Figure_1, message=FALSE, warning=FALSE, fig.width=13, fig.height=5, echo=FALSE}
+```{r Figure_1, message=FALSE, warning=FALSE, echo=FALSE}
 
@@
 #theme_set(theme_linedraw(20))
-theme_set(theme_light(20))
+theme_set(theme_light(25))
 
@@
 print(p)
-
-#postscript(file = "Figure_1.eps", width = 11, height = 5, paper = "special",
-#              family = "sans", bg = "white")
-#print(p)
-#dev.off()
-#library(extrafont)
-#embed_fonts("Figure_1.eps", outfile="Figure_1.eps")
 ```
@@
 
-```{r Figure_2, message=FALSE, warning=FALSE, fig.width=10, fig.height=4, echo=FALSE}
+```{r Figure_2, message=FALSE, warning=FALSE, echo=FALSE}
 library(dplyr)
 library(ggplot2)
-theme_set(theme_bw(20))
+#theme_set(theme_bw(20))
 df <- df0 %>% filter(publication_year >=1640 & publication_year <=1828) %>%
@@
 
-```{r Figure_3prep, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=18, fig.height=5, fig.show="hide", results="hide"}
+```{r Figure_3prep, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.show="hide", results="hide", fig.width=27, fig.height=10}
 library(scales)
@@
   p <- p + ylim(c(0, max(na.omit(df2$paper))))
-  #p <- p + scale_shape_manual(values = factor(common.gatherings))
-  #p <- p + scale_linetype_manual(values = factor(common.gatherings))
 
@@
            labels = c("A", "B"),
+	   label_size = 25,	   
            hjust = -1,
@@
 # of one plot (via rel_heights).
-p <- plot_grid( prow, legend_b, ncol = 2, rel_widths = c(1, .2))
-title <- ggdraw() + draw_label("Figure 3", fontface='bold')
-```
-
-```{r Figure_3, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=18, fig.height=5}
-print(plot_grid(title, p, ncol=1, rel_heights=c(0.1, 1), hjust = 0))
+p <- plot_grid( prow, legend_b, ncol = 2, rel_widths = c(1, .1))
+#title <- ggdraw() + draw_label("Figure 3", fontface='bold')
+```
+
+```{r Figure_3, echo=FALSE, message=FALSE, warning=FALSE, fig.width=27, fig.height=10}
+#print(plot_grid(title, p, ncol=2, rel_heights=c(0.1, 1), hjust = 0))
+#print(p + theme_blank(30))
+print(p)
 ```
@@
 
-Loess smoothing.
-
-```{r Figure_4, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=5, fig.width=15, fig.show="last"}
+```{r Figure_4, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.show="last", fig.width=27, fig.height=10}
 cols <- list(Fennica = "blue", Kungliga = "darkred")
@@
 
-#pics[[unique(df$catalog)[[1]]]] <- pics[[unique(df$catalog)[[1]]]] + labs(title = "Figure 4")
-
 library(cowplot)
-# arrange the three plots in a single row
 prow <- plot_grid(
@@
            labels = c("A", "B"),
+	   label_size = 25,
            hjust = -1,
@@
 # of one plot (via rel_heights).
-p <- plot_grid( prow, legend_b, ncol = 2, rel_widths = c(1, .2))
-title <- ggdraw() + draw_label("Figure 4", fontface='bold')
-p <- plot_grid(title, p, ncol=1, rel_heights=c(0.1, 1)) # rel_heights values control title margins
+p <- plot_grid( prow, legend_b, ncol = 2, rel_widths = c(.95, .08))
+# title <- ggdraw() + draw_label("Figure 4", fontface='bold')
+# p <- plot_grid(title, p, ncol=1, rel_heights=c(0.1, 1)) # rel_heights values control title margins
 print(p)
@@
 
-```{r Figure_5, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=15, fig.height=7}
+```{r Figure_5prep, echo=FALSE, message=FALSE, warning=FALSE, fig.width=27, fig.height=14, fig.show="none", results="hide"}
+rm(p)
+rm(prow)
+rm(legend_b)
 pics <- list()
@@
 
-  theme_set(theme_bw(20))
+  # theme_set(theme_bw(20))
   p <- ggplot(dff, aes(x = publication_decade, y = f)) +
@@
 #pics[[1]] <- pics[[1]] + # ggtitle("Figure 5") 
-grid.arrange(pics[[1]], pics[[2]], pics[[4]], pics[[5]], top = "Figure 5", layout_matrix = matrix(c(1,2,3,4), nrow = 2, byrow=TRUE))
+#grid.arrange(pics[[1]], pics[[2]], pics[[4]], pics[[5]], top = "Figure 5", layout_matrix = matrix(c(1,2,3,4), nrow = 2, byrow=TRUE))
+#grid.arrange(pics[[1]], pics[[2]], pics[[4]], pics[[5]], layout_matrix = matrix(c(1,2,3,4), nrow = 2, byrow=TRUE))
+
+library(cowplot)
+# arrange the three plots in a single row
+prow <- plot_grid(
+           pics[[1]] + theme(legend.position="none"),
+           pics[[2]] + theme(legend.position="none"),
+           pics[[3]] + theme(legend.position="none"),
+           pics[[4]] + theme(legend.position="none"),	   
+           align = 'vh',
+           # labels = c("A", "B", "", ""),
+	   # label_size = 25,	   
+           hjust = -1,
+           nrow = 2
+           )
+
+legend_b <- get_legend(pics[[1]] + theme(legend.position="right"))
+
+# Add the legend underneath the row we made earlier. Give it 10% of the height
+# of one plot (via rel_heights).
+p2 <- plot_grid( prow, legend_b, ncol = 2, rel_widths = c(1, .1))
+```
+
+```{r Figure_5, echo=FALSE, message=FALSE, warning=FALSE, fig.width=27, fig.height=14}
+print(p2)
 rm(pics)
@@
 
-```{r Figure_6, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=4}
+```{r Figure_6, echo=FALSE, message=FALSE, warning=FALSE}
 library(magrittr)
@@
 v <- seq(1500, 1800, 100)
-theme_set(theme_bw(20))
+# theme_set(theme_bw(20))
 df <- df0 %>% filter(catalog == "Kungliga")
@@
        guides(fill = guide_legend(title = "Period")) +
-       ylab("Paper (sheets)") + xlab("") 
+       ylab("Paper per title (sheets)") + xlab("") 
        # ggtitle("Figure 6") 
@@
 
-```{r Figure_7, echo=FALSE, message=FALSE, warning=FALSE, fig.width=11, fig.height=4}
+```{r Figure_7, echo=FALSE, message=FALSE, warning=FALSE}
 
@@
   # Draw Figure
-  theme_set(theme_bw(20))
+  # theme_set(theme_bw(20))
   p <- ggplot() +
@@
 
-```{r Figure_8, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=5, fig.width=12}
+```{r Figure_8, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}
 # Top publication places
@@
 
-theme_set(theme_bw(20))
+#theme_set(theme_bw(20))
 brs <- seq(min(npub$publication_decade), max(npub$publication_decade), 10)  
@@
 
-```{r Figure_9, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=5, fig.width=10}
+```{r Figure_9, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}
 library(dplyr)
@@
 
-```{r Figure_10, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=5, fig.width=12}
+```{r Figure_10, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}
 library(dplyr)
@@
 # TITLE COUNT
-theme_set(theme_bw(20))
+#theme_set(theme_bw(20))
 brs <- seq(min(df$publication_decade), max(df$publication_decade), 10)
@@
 
-```{r Figure_11, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
+```{r Figure_11, echo=FALSE, message=FALSE, warning=FALSE}
 # Read historical population sizes
@@
 
-```{r Figure_12, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
+```{r Figure_12, echo=FALSE, message=FALSE, warning=FALSE}
 minyear <- 1640
@@
 
-```{r Figure_13, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
+```{r Figure_13, echo=FALSE, message=FALSE, warning=FALSE}
 # Take cities from Kungliga except Turku
@@
 
-```{r Figure_14, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
+```{r Figure_14, echo=FALSE, message=FALSE, warning=FALSE}
 # Take cities from Kungliga except Turku
@@
 
-```{r Figure_15, echo=FALSE, message=FALSE, warning=FALSE, fig.width=15, fig.height=7}
+```{r Figure_15prep, echo=FALSE, message=FALSE, warning=FALSE, fig.width=27, fig.height=15, fig.show="hide", results="hide"}
 pics <- list()
-theme_set(theme_bw(20))
+#theme_set(theme_bw(20))
 myplaces <- c("Turku", "Greifswald", "Stockholm", "Uppsala", "Lund")
@@
 
-grid.arrange(pics[[1]], pics[[8]], pics[[9]], pics[[10]], top = "Figure 15", layout_matrix = matrix(c(1,2,3,4), nrow = 2, byrow=TRUE))
-
+#grid.arrange(pics[[1]], pics[[8]], pics[[9]], pics[[10]], top = "Figure 15", layout_matrix = matrix(c(1,2,3,4), nrow = 2, byrow=TRUE))
+#grid.arrange(pics[[1]], pics[[8]], pics[[9]], pics[[10]], layout_matrix = matrix(c(1,2,3,4), nrow = 2, byrow=TRUE))
+
+library(cowplot)
+# arrange the three plots in a single row
+prow <- plot_grid(
+           pics[[1]] + theme(legend.position="none"),
+           pics[[2]] + theme(legend.position="none"),
+           pics[[3]] + theme(legend.position="none"),
+           pics[[4]] + theme(legend.position="none"),	   
+           align = 'vh',
+           # labels = c("A", "B", "", ""),
+	   # label_size = 25,	   
+           hjust = -1,
+           nrow = 2
+           )
+
+legend_b <- get_legend(pics[[1]] + theme(legend.position="right"))
+
+# add the legend underneath the row we made earlier. Give it 10% of the height
+# of one plot (via rel_heights).
+p <- plot_grid( prow, legend_b, ncol = 2, rel_widths = c(1, .1))
 rm(pics)
@@
 
+```{r Figure_15, echo=FALSE, message=FALSE, warning=FALSE, fig.width=27, fig.height=15}
+print(p)
+```
+
 ---
@@
 
-```{r Figure_16, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5, fig.show="hold"}
+```{r Figure_16, echo=FALSE, message=FALSE, warning=FALSE, fig.show="hold"}
 catalogue <- "Fennica"
@@
 
-```{r Figure_17, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
+```{r Figure_17, echo=FALSE, message=FALSE, warning=FALSE}
 sel <- c("hautajaiset", "häät", "juhlamenot")
@@
 
-```{r Figure_18, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5, fig.show="hold"}
+```{r Figure_18, echo=FALSE, message=FALSE, warning=FALSE, fig.show="hold"}
 sel <- c("virret","arkkiveisut","hartauskirjat","katekismukset","rukouspäivät","saarnat","aapiset","rukoukset","rukous","hengelliset laulut","hartauspuheet","virsikirjat")
@@
 # PAPER CONSUMPTION
-theme_set(theme_bw(20))
+#theme_set(theme_bw(20))
 brs <- seq(min(df$publication_decade), max(df$publication_decade), 10)
@@
 
+#print(p + theme_light(scalingfactor))
 print(p)

### 2017-11-20 inst/examples/20170201-manuscript.Rmd
Figs 5, 10, 15 fixed

@@
 pics <- list()
+
 for (catalogue in na.omit(unique(df0$catalog))) {
@@
 prow <- plot_grid(
-           pics[[1]] + theme(legend.position="none"),
-           pics[[2]] + theme(legend.position="none"),
-           pics[[3]] + theme(legend.position="none"),
-           pics[[4]] + theme(legend.position="none"),	   
+           pics[["Fennica-n"]] + theme(legend.position="none"),
+           pics[["Fennica-paper"]] + theme(legend.position="none"),
+           pics[["Kungliga-n"]] + theme(legend.position="none"),
+           pics[["Kungliga-paper"]] + theme(legend.position="none"),
            align = 'vh',
@@
 npub$publisher <- factor(npub$publisher, levels = c("Other", setdiff(ord, "Other")))
+
+# Translate
+npub$publisher <- gsub("ja poika", "and son", npub$publisher)
+npub$publisher <- gsub("Frenckellin leski", "Frenckell's widow", npub$publisher)
 
@@
 prow <- plot_grid(
-           pics[[1]] + theme(legend.position="none"),
-           pics[[2]] + theme(legend.position="none"),
-           pics[[3]] + theme(legend.position="none"),
-           pics[[4]] + theme(legend.position="none"),	   
+           pics[["Fennica-Turku"]] + theme(legend.position="none"),
+           pics[["Kungliga-Stockholm"]] + theme(legend.position="none"),
+           pics[["Kungliga-Uppsala"]] + theme(legend.position="none"),
+           pics[["Kungliga-Lund"]] + theme(legend.position="none"),	   	  
            align = 'vh',

### 2017-11-20 inst/examples/20170201-manuscript.Rmd
ok

@@
 npub <- df %>% group_by(publication_decade, publisher) %>% tally() %>% arrange(n)
+
+# Translate
+npub$publisher <- gsub("ja poika", "and son", npub$publisher)
+npub$publisher <- gsub("J.C. Frenckell and son", "Frenckell, Johan Christopher & Son", npub$publisher)
+npub$publisher <- gsub("Frenckellin leski", "Frenckell's widow", npub$publisher)
+npub$publisher <- gsub("Johan Christopher Frenckell's widow", "Frenckell, Johan Christopher's widow", npub$publisher)
+
 #npub$publisher <- factor(npub$publisher, levels = (npub %>% group_by(publisher) %>% summarise(total = sum(n)) %>% arrange(total))$publisher)
@@
 #ord <- (npub %>% group_by(publisher) %>% summarise(decade = publication_decade[[which.max(n)]]) %>% arrange(decade))$publisher
+
 ord <- as.character((npub %>% group_by(publisher) %>% 
@@
 npub$publisher <- factor(npub$publisher, levels = c("Other", setdiff(ord, "Other")))
-
-# Translate
-npub$publisher <- gsub("ja poika", "and son", npub$publisher)
-npub$publisher <- gsub("Frenckellin leski", "Frenckell's widow", npub$publisher)
 

### 2018-01-07 inst/examples/201705-Gaudeamus.Rmd
Added data for HS

--- 2017-06-01 inst/examples/201705-Gaudeamus.Rmd
@@
 print(p)
+
+table_hs <- df2 %>% group_by(publication_decade, publication_place) %>%
+                    tally() %>%
+		    spread(publication_place, n, fill = 0)
+library(openxlsx)		    
+openxlsx::write.xlsx(table_hs, file = "Table_HS_20180107.xlsx")
 ```

### 2018-02-15 inst/examples/20170201-manuscript.Rmd

@@
 place <- "Turku"
-catalogue = "Fennica"
-df = df0
-
-df <- df %>% filter(catalog == catalogue & publication_place == place)
+catalogue <- "Fennica"
+df <- df0
+
+df <- df %>% filter(catalog == catalogue & publication_place == place) %>%
+             filter(!is.na(publisher))
 
 df <- df %>%	
-  filter(publication_year >= 1640 & publication_year <= 1828)%>%
-        select(publication_decade, publisher, paper)
+  filter(publication_year >= 1640 & publication_year <= 1828) %>%
+        select(publication_decade, publication_year, publisher, paper)
 
@@
 
+# Title count per year & publisher	
+npub0 <- df %>% group_by(publication_year, publisher) %>% tally() %>% arrange(n)
+
 # Translate
@@
 
-#npub$publisher <- factor(npub$publisher, levels = (npub %>% group_by(publisher) %>% summarise(total = sum(n)) %>% arrange(total))$publisher)
-# Sort by biggest publication decade
-#ord <- (npub %>% group_by(publisher) %>% summarise(decade = publication_decade[[which.max(n)]]) %>% arrange(decade))$publisher
-
-ord <- as.character((npub %>% group_by(publisher) %>% 
-                        summarise(decade = median(publication_decade)) %>% 
-                        arrange(decade))$publisher)
+# Translate
+npub0$publisher <- gsub("ja poika", "and son", npub0$publisher)
+npub0$publisher <- gsub("J.C. Frenckell and son", "Frenckell, Johan Christopher & Son", npub0$publisher)
+npub0$publisher <- gsub("Frenckellin leski", "Frenckell's widow", npub0$publisher)
+npub0$publisher <- gsub("Johan Christopher Frenckell's widow", "Frenckell, Johan Christopher's widow", npub0$publisher)
+
+# Order by average publication year
+ord <- as.character((npub0 %>% group_by(publisher) %>% 
+                        summarise(year = mean(publication_year)) %>% 
+                        arrange(year))$publisher)
+#ord <- ord[c(1:7, 9, 8, 10:11)]	
 npub$publisher <- factor(npub$publisher, levels = c("Other", setdiff(ord, "Other")))

### 2018-02-15 inst/examples/fennica_drop.Rmd

---
title: "Drop in the beginning of 19th century"
date: "14 heinäkuuta 2016"
output: pdf_document
---

```{r 201607krakow-fennica_drop, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, cache=TRUE}
# Default time span
min.year <- 1484
max.year <- 1828

library(ggmap)
library(gisfin)
library(stringr)
library(dplyr)
library(tidyr)
library(reshape2)
library(ggplot2)
library(bibliographica)
library(fennica)
library(sorvi)
library(devtools)
# install_github("ropengov/gisfin")
# devtools::install_github('cttobin/ggthemr')
#library(ggthemr)

knitr::opts_chunk$set(echo = FALSE)
#knitr::opts_chunk$set(fig.path = "slides_201606_Krakow/", dev="CairoPNG")
knitr::opts_chunk$set(fig.path = "slides_201606_Krakow/")

# Set locale
tmp <- Sys.setlocale(locale="UTF-8")

# Nice theme
theme_set(theme_bw(26))
```

```{r 201607krakow-fennica_drop2, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, cache=TRUE}
# Full combined catalogue (Fen + Kun) with marked duplicates

df.combined.preprocessed <- readRDS("df.combined.Rds")

# Data with duplicates removed
df.full <- df.combined.preprocessed %>% filter(!remove)

# What did each of the Kongliga tryckare publish?
df0 <- df.full %>% filter(publication_year >= 1700 & publication_year <= 1827 & publication_place == "Turku")

df0$publ <- NA
df0$publ[intersect(grep("Merckell",df0$publisher), grep("Henric", df0$publisher))] <- "Gezelius/Merckell"
df0$publ[grep("Winter",df0$publisher)] <- "Gezelius/Merckell"
df0$publ[grep("(Hjelt|Piplia|Biblia|Bibel)", df0$publisher)] <- "Hjelt"
df0$publ[which(is.na(df0$publ))] <- "Frenckell"

df0 <- df0 %>% filter(publ=="Frenckell")
df0$publ <- NA
df0$publ[df0$publication_year <= 1710] <- "Johan Wall"
df0$publ[intersect(which(df0$publication_year == 1711), grep("Wall", df0$publisher))] <- "Johan Wallin leski"
df0$publ[intersect(which(df0$publication_year <= 1713), intersect(which(df0$publication_year >= 1710), grep("Björckman", df0$publisher)))] <-"Anders Björckman"
df0$publ[intersect(which(df0$publication_year <= 1729), intersect(which(df0$publication_year >= 1722), grep("Flodström", df0$publisher)))] <-"Eric Flodström"
df0$publ[intersect(which(df0$publication_year <= 1753), intersect(which(df0$publication_year >= 1729), grep("Kämpe", df0$publisher)))] <-"Johan Kämpe"
df0$publ[intersect(which(df0$publication_year <= 1761), intersect(which(df0$publication_year >= 1750), grep("Merckell", df0$publisher)))] <-"Eric Flodström"
df0$publ[intersect(which(df0$publication_year <= 1779), intersect(which(df0$publication_year >= 1761), grep("leski", df0$publisher, invert = TRUE)))] <-"Frenckell I"
df0$publ[intersect(which(df0$publication_year <= 1785), intersect(which(df0$publication_year >= 1779), grep("Frenckell", df0$publisher)))] <-"Frenckell I:n leski"
df0$publ[intersect(which(df0$publication_year <= 1814), intersect(which(df0$publication_year >= 1785), grep("Frenckell", df0$publisher)))] <-"Frenckell II"
df0$publ[intersect(which(df0$publication_year <= 1856), intersect(which(df0$publication_year >= 1814), grep("Frenckell", df0$publisher)))] <-"Frenckell II & poika"
df0$publ[intersect(which(df0$publication_year <= 1876), intersect(which(df0$publication_year >= 1856), grep("Frenckell", df0$publisher)))] <-"Frenckellin kirjapaino"

unique_publisher = unique(df0$publisher)
message("greppausten jälkeen")
# What did Henric Merckell publish?
df0 <- df.full %>% filter(publication_year >= min.year & publication_year <= max.year & publisher=="Merckell, Henric Christopher")

df <- df0 %>% filter(publication_year >=1700 & publication_year <=1828) %>% group_by(publication_decade, leaflet=(pagecount <= 10), dissertation, publication_place) %>% tally()

df$leaflet[df$leaflet==TRUE] <- " <= 10 pages"
df$leaflet[df$leaflet==FALSE] <- " > 10 pages"

l <- (df %>% group_by(leaflet) %>% group_by(dissertation))
df$l <- paste0(l$dissertation, l$leaflet)
message("random kohta")
unique_diss <- unique(na.omit(df$dissertation))
unique_leaflet <- unique(na.omit(df$leaflet))
publisher = "Henric Christopher Merckell"
#df <- df %>% filter(n > 10)
message("before loop")
  for (diss in unique_diss) {
    for (leaflet in unique_leaflet) {
      message("In loop")
      #if (length(which(df$dissertation==diss)) > 10) {

        p <- ggplot(df[which(df$dissertation==diss & df$leaflet==leaflet),], aes(x = publication_decade, y = n, fill=publication_place)) + 
        geom_bar(position = "dodge", stat = "identity") + 
        xlab("Publication year") +
        ylab("Documents (n)") +
        scale_fill_discrete(name = "Publication place") + 
          ggtitle(paste0(publisher, "\nDissertations = ", diss, "\nBook length ", leaflet))
        print(p)
        print(paste0("Dissertations = ", diss))
        print(paste0("Book length ", leaflet))
      #}
    }
  }

# Data with years limited as well
df0 <- df.full %>% filter(publication_year >= min.year & publication_year <= max.year & publication_place=="Turku")
# Fennica only
df0 <- df0 %>% filter(catalog=="Fennica")
catalog="Fennica"

df <- df0 %>% filter(publication_year >=1700 & publication_year <=1828) %>% group_by(publication_decade, leaflet=(pagecount <= 10), dissertation, publisher, publ=NA) %>% tally()

#df <- df0 %>% filter(publication_year >=1700 & publication_year <=1828) %>% group_by(publication_decade, leaflet=(pagecount <= 10), dissertation, publisher) %>% tally()

df$leaflet[df$leaflet==TRUE] <- " <= 10 pages"
df$leaflet[df$leaflet==FALSE] <- " > 10 pages"
unique_publisher <- unique(df$publisher)

l <- (df %>% group_by(leaflet) %>% group_by(publisher))
df$l <- paste0(l$publisher, l$leaflet)

df$publ[intersect(grep("Merckell",df$publisher), grep("Henric", df$publisher))] <- "Gezelius/Merckell"
df$publ[grep("Winter",df$publisher)] <- "Gezelius/Merckell"
df$publ[grep("(Hjelt|Piplia)", df$publisher)] <- "Hjelt"
df$publ[which(is.na(df$publ))] <- "Frenckell"

unique_publ <- unique(df$publ)
unique_diss <- unique(na.omit(df$dissertation))
unique_leaflet <- unique(na.omit(df$leaflet))
df <- df %>% filter(n > 10)
for (publ in unique_publ) {
  for (diss in unique_diss) {
    for (leaflet in unique_leaflet) {
      if (length(which(df$dissertation==diss & df$publ==publ)) > 10) {

        p <- ggplot(df[which(df$dissertation==diss & df$publ==publ & df$leaflet==leaflet),], aes(x = publication_decade, y = n, fill=publisher)) + 
        geom_bar(position = "dodge", stat = "identity") + 
        xlab("Publication year") +
        ylab("Documents (n)") +
        scale_fill_discrete(name = "New Legend Title")
        ggtitle("DROP")

        print(p)
        print(paste0("Dissertations = ", diss))
        print(paste0("Publishing house = ", publ))
        print(paste0("Book length ", leaflet))

    }
  }
}
}

#print(df)
unique_publ <- unique(df$publ)
unique_diss <- unique(na.omit(df$dissertation))
for (publ in unique_publ) {
  for (diss in unique_diss) {
    if (length(which(df$dissertation==diss & df$publ==publ)) > 0) {

      p <- ggplot(df[which(df$dissertation==diss & df$publ==publ),], aes(x = publication_decade, y = n, fill=leaflet)) + 
      geom_bar(position = "dodge", stat = "identity") + 
      xlab("Publication year") +
      ylab("Documents (n)") +
      #guides(fill = guide_legend(reverse = TRUE, title = "")) +
      #scale_fill_manual(values=c("blue", "red")) + 
      scale_fill_discrete(name = "New Legend Title")
      ggtitle("DROP")

  #p <- ggplot(df[which(df$dissertation==diss),], aes(x = publication_decade, y = n, color = leaflet)) + 
  #       geom_point() + 
  #     geom_line()
  #       ylab("Documents (n)") + xlab("Publication year") +
  #       scale_color_manual(values = c("blue", "darkgreen")) + 
  #       guides(color = guide_legend(reverse = TRUE, title = "")) #+

      print(p)
      print(paste0("Dissertations = ", diss))
      print(paste0("Publishing house = ", publ))

    }
  }
}
```

### 2018-02-15 inst/examples/201705-Gaudeamus.Rmd
Gaudeamus polish

--- 2017-06-01 inst/examples/201705-Gaudeamus.Rmd
@@
 output:
-  beamer_presentation
+  beamer_presentation:
+    dev: cairo_pdf  
+  pdf_document:
+    dev: cairo_pdf
+    keep_tex: yes
 fontsize: 13pt
@@
 # knitr::opts_chunk$set(fig.path = "figure-201705-Gaudeamus/")
-##knitr::opts_chunk$set(fig.path = "slides_201606_Krakow", dev="CairoPNG")
-knitr::opts_chunk$set(fig.path = "figure-201705-Gaudeamus/", dev="CairoJPEG")
+# knitr::opts_chunk$set(fig.path = "slides_201606_Krakow", dev="CairoPNG")
+# knitr::opts_chunk$set(fig.path = "figure-201705-Gaudeamus/", dev="CairoJPEG")
+knitr::opts_chunk$set(fig.path = "figure-201705-Gaudeamus/", dev="CairoPDF")
 
@@
 # Data with duplicates removed and years limited
-
 min.year <- 1488
@@
 
-```{r, message=FALSE, warning=FALSE, fig.width=10, fig.height=3, echo=FALSE}
+```{r Gaudeamus-lineplot, message=FALSE, warning=FALSE, fig.width=10, fig.height=3, echo=FALSE}
 library(dplyr)
@@
 theme_set(theme_bw(20))
-df <- df0 %>% filter(publication_year >=1640 & publication_year <=1828) %>% group_by(catalog, publication_decade) %>% tally()
+df <- df0 %>% filter(publication_year >=1640 & publication_year <=1828) %>%
+              group_by(catalog, publication_decade) %>% tally()
 p <- ggplot(df, aes(x = publication_decade, y = n, color = catalog)) + 
@@
 
-```{r Gaudeamus-3, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=11, fig.height=13, dev="CairoJPEG"}
+```{r Gaudeamus-3, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=11, fig.height=13, dev="CairoPDF"}
 theme_set(theme_bw(22))
@@
 
-```{r Gaudeamus-Vaasa, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=11, fig.height=6, dev="CairoJPEG"}
+```{r Gaudeamus-Vaasa, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=11, fig.height=6, dev="CairoPDF"}
 library(dplyr)
@@
 
-```{r Gaudeamus-Turku, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=11, fig.height=6, dev="CairoJPEG"}
+```{r Gaudeamus-Turku, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=11, fig.height=6, dev="CairoPDF"}
 library(dplyr)
@@
 
-```{r Gaudeamus-Helsinki, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=11, fig.height=6, dev="CairoJPEG"}
+```{r Gaudeamus-Helsinki, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=11, fig.height=6, dev="CairoPDF"}
 library(dplyr)
@@
 
-```{r Gaudeamus-Suomi, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=11, fig.height=6, dev="CairoJPEG"}
+```{r Gaudeamus-Suomi, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=11, fig.height=6, dev="CairoPDF"}
 library(dplyr)
@@
 
-```{r Gaudeamus-Suomi2, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=11, fig.height=6, dev="CairoJPEG"}
+```{r Gaudeamus-Suomi2, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=11, fig.height=6, dev="CairoPDF"}
 library(dplyr)
@@
 print(p)
+
+library(tidyr)
+table_hs <- df2 %>% group_by(publication_decade, publication_place) %>%
+                    tally() %>%
+		    spread(publication_place, n, fill = 0)
+library(openxlsx)		    
+# openxlsx::write.xlsx(table_hs, file = "Table_HS_20180107.xlsx")
 ```

### 2018-02-16 inst/examples/201705-Gaudeamus.Rmd
ok

@@
 
-```{r Gaudeamus-lineplot, message=FALSE, warning=FALSE, fig.width=10, fig.height=3, echo=FALSE}
-library(dplyr)
-library(ggplot2)
-theme_set(theme_bw(20))
-df <- df0 %>% filter(publication_year >=1640 & publication_year <=1828) %>%
-              group_by(catalog, publication_decade) %>% tally()
-p <- ggplot(df, aes(x = publication_decade, y = n, color = catalog)) + 
-       geom_point() + 
-       geom_line() + 
-       ylab("Documents (n)") + xlab("Publication year") +
-       scale_color_manual(values = c("blue", "darkgreen")) +
-       guides(color = guide_legend(reverse = TRUE, title = "")) #+ 
-print(p)
-
-```
-
----
-
 ### Rise of the octavo sized book as vehicle of Enlightenment
@@
   df2$highlight[df2$gatherings == "8vo"] <- "Octavo"
+
+  # df2$gatherings
 

### 2018-02-16 inst/examples/Figure3.R

@@ -1,0 +1,70 @@
+
+library(ggplot2)
+library(dplyr)
+library(Cairo)
+library(bibliographica)
+theme_set(theme_bw(22))
+pics <- list()
+for (catal in unique(df0$catalog)) {
+  df2 <- df0 %>% filter(catalog == catal) %>% 
+                 group_by(publication_decade, gatherings) %>% 
+		 summarise(paper2 = sum(paper, na.rm = TRUE)/1e6, n = n()) 
+  df2$paper <- df2$paper2; df2$paper2 <- NULL # Rename
+  df2 <- filter(df2, gatherings %in% setdiff(names(which(table(df2$gatherings) >= 15)), "NA"))
+  df2$highlight <- rep("Other", nrow(df2))
+  df2$highlight[df2$gatherings == "8vo"] <- "Octavo"
+
+  df2$gatherings_abbr <- capitalize(map_gatherings(df2$gatherings, from = "Standard", to = "Name"))
+
+  p <- ggplot(df2, aes(y = paper,
+                       x = publication_decade,
+		       shape = gatherings_abbr
+		       ))		       
+  p <- p + geom_point(size = 3)
+  p <- p + geom_smooth(method = "loess", size = 1,
+             aes(color = highlight, 
+	          fill = highlight, 
+		  linetype = gatherings_abbr), color = "black")
+  p <- p + scale_color_manual(values = c("black", "lightgray"))
+  p <- p + scale_fill_manual(values = c("black", "lightgray"))  	 
+  p <- p + xlab("Vuosi")
+  p <- p + ylab("Paperinkulutus (miljoonia arkkeja)")
+  p <- p + guides(linetype = guide_legend(keywidth = 5, title = "Koko"),
+       	             shape = guide_legend(keywidth = 5, title = "Koko"),
+		     fill = guide_legend(title = "Korostus"),
+		     color = guide_legend(title = "Korostus")
+		     )
+  p <- p + ylim(c(0, max(df2$paper, na.rm = TRUE)))
+  p <- p + ggtitle(catal)
+  p <- p + theme(plot.title = element_text(hjust = 0))
+  p <- p + theme(legend.position = "bottom")
+  pics[[catal]] <- p
+}
+
+
+library(cowplot)
+# https://cran.r-project.org/web/packages/cowplot/vignettes/shared_legends.html
+
+pics[[1]] <- pics[[1]] + xlab("")
+prow <- plot_grid( 
+           pics[[1]] + theme(legend.position="none"),
[…]

### 2018-04-20 inst/examples/20170201-manuscript.Rmd
ok

@@
 knitr::opts_chunk$set(fig.path = "20170201_manuscript/", dpi = 300)
-knitr::opts_chunk$set(dev = c("png", "jpeg", "cairo_ps"))
-#knitr::opts_chunk$set(dev = "cairo_pdf") # Embed fonts
+#knitr::opts_chunk$set(dev = c("png", "jpeg", "cairo_ps"))
+# knitr::opts_chunk$set(dev = "Cairo")
+#knitr::opts_chunk$set(dev = "CairoPDF")
+knitr::opts_chunk$set(dev = "CairoPS")
+# knitr::opts_chunk$set(dev = "cairo_pdf") # Embed fonts
 #knitr::opts_chunk$set(dev = "cairo_ps") # Embed fonts
@@
   p <- p + guides(
-       color = guide_legend(keywidth = 5, title = "Gatherings"),
-        fill = guide_legend(keywidth = 5, title = "Gatherings"),     
-       shape = guide_legend(keywidth = 5, title = "Gatherings", reverse = TRUE),
-    linetype = guide_legend(keywidth = 5, title = "Gatherings", reverse = TRUE))
+       color = guide_legend(keywidth = 5, title = "Quires"),
+        fill = guide_legend(keywidth = 5, title = "Quires"),     
+       shape = guide_legend(keywidth = 5, title = "Quires", reverse = TRUE),
+    linetype = guide_legend(keywidth = 5, title = "Quires", reverse = TRUE))
 

### 2018-06-12 inst/examples/20160715-Krakow-Fennica.Rmd

@@
 
-**Open source** fully transparent and reproducible data analytics: https://github.com/rOpenGov/fennica
+**Open source** fully transparent and reproducible data analytics: https://github.com/COMHIS/fennica
 
@@
 
-- \textcolor{blue}{https://github.com/rOpenGov/fennica}
+- \textcolor{blue}{https://github.com/COMHIS/fennica}
 

### 2018-06-12 inst/examples/notebook.Rmd

@@
 ```{r drop1700B, echo=FALSE, message=FALSE, warning=FALSE, fig.width=15, fig.height=7}
-# https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/drop1700B-1.png
+# https://github.com/COMHIS/fennica/blob/master/inst/examples/figure_201606_Krakow/drop1700B-1.png
 
@@
 ```{r topics12122, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, fig.show="hold"}
-# https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/topics-2.png
+# https://github.com/COMHIS/fennica/blob/master/inst/examples/figure_201606_Krakow/topics-2.png
 sel <- c("virret","arkkiveisut","hartauskirjat","katekismukset","rukouspäivät","saarnat","aapiset","rukoukset","rukous","hengelliset laulut","hartauspuheet","virsikirjat")

### 2018-06-14 inst/examples/20170201-manuscript.Rmd

@@
            group_by(publication_decade, gatherings) %>%
-	   summarize(paper = sum(paper, na.rm = TRUE), n = n())
+	   summarize(paper = sum(paper, na.rm = TRUE)/1e6, n = n())
+  # Million sheets
 
@@
   p <- p + xlab("Decade")
-  p <- p + ylab("Paper (sheets)")
-  p <- p + ylim(c(0, max(na.omit(df2$paper))))
+  p <- p + ylab("Paper (million sheets)")
+  # p <- p + ylim(c(0, max(na.omit(df00$paper))))
 
@@
 	   labels = insert_minor(brs, 5, start = ifelse(catal == "Fennica", 1500, 1550))) + 
-         scale_y_continuous(breaks = seq(0, max(df2$paper), 2e6), label = scientific_10) #+
+         scale_y_continuous(breaks = seq(0, 6.8, 1), limits = c(0, 6.8))
+         #scale_y_continuous(breaks = seq(0, max(df00$paper, na.rm = TRUE), 1000))
+	                    # label = scientific_10)
 

### 2018-06-19 inst/examples/summary.Rmd
ok

@@
 author: "Leo Lahti"
-date: "July 2, 2016"
+date: "`r date()`"
 ---
@@
 # Read the preprocessed data
-df <- readRDS("df.Rds")
-df.orig <- readRDS("df.raw.Rds")
+df <- readRDS("data/unified/polished/df.Rds")
+df.orig <- readRDS("data/unified/polished/df.raw.Rds")
 conversions <- readRDS("conversions.Rds")

### 2018-08-27 inst/examples/20170201-manuscript.Rmd
ok

@@
 ---
-title: "Patterns in Knowledge Production: Political Ruptures and Imperial Dynamics Shaping Public Discourse in Sweden and Finland, 1640–1828"
+title: "A Quantitative Approach to Book Printing in Sweden and Finland, 1640–1828"
 author: "Mikko Tolonen, Leo Lahti, Hege Roivainen, Jani Marjanen"
@@
 
-```{r 201606krakow-init2, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, cache=TRUE}
+```{r init2, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, cache=TRUE}
 # Full combined catalogue (Fen + Kun) with marked duplicates
@@
 ---
-
 ### Fig 1: Number of publication places over time
@@
 ```{r Figure_1, message=FALSE, warning=FALSE, echo=FALSE}
-
 library(dplyr)
@@
 
+### Data statistics
+
+```{r stats, echo=FALSE, message=FALSE, warning=FALSE}
+library(skimr)
+
+s <- skim(subset(df0, catalog == "Fennica")[, c("publication_year", "publication_place", "gatherings", "title", "pagecount", "publisher", "language", "subject_topic")])
+
+kable(s)
+```
+
 ## Session info

### 2018-08-27 inst/examples/analysis.combined.run.R

@@ -1,5 +1,3 @@
-
-
 message("Filtering out rows with remove-tags")
 # This is the real removal
 # Fast to run, so just run before analysis and do not save
@@ -55,9 +53,3 @@ duplicates <- filter_duplicates(df.combined.preprocessed)
 fields <- c("catalog", "author", "short_title", "title", "dissertation", "publication_place", "publication_year")
 duplicates <- duplicates[,fields][order(duplicates$publication_year, duplicates$short_title, duplicates$publication_place, duplicates$catalog),]
 write.table(duplicates, paste0(output.folder, "duplicates.csv"), quote = FALSE, sep = "\t", row.names = FALSE)
-
-
-
-
-
-

### 2018-08-27 inst/examples/statistics.R

@@ -1,0 +1,30 @@
+library(skimr)
+
+d <- list()
+
+for (cat in unique(df0$catalog)) {
+
+  dd <- subset(df0, catalog == cat)[, c("publication_year", "publication_place", "gatherings", "title", "pagecount", "publisher", "language", "subject_topic")]
+
+  complete <- round(100 * colMeans(!is.na(dd)), 1)
+  unique <- apply(dd, 2, function (x) {length(unique(x))})
+
+  d[[cat]] <- data.frame(Field = colnames(dd), Complete = complete, Unique = unique)
+
+}
+
+
+w <- data.frame(Field = map_fieldnames(colnames(dd)),
+           Fennica = d$Fennica$Complete,
+	   Kungliga = d$Kungliga$Complete) %>%
+	     arrange(desc(Fennica))
+
+write.table(w, file = "Table_HistoricalMethods_Complete.csv", sep = "\t", quote = FALSE, row.names = FALSE)
+
+w <- data.frame(Field = map_fieldnames(colnames(dd)),
+           Fennica = d$Fennica$Unique,
+	   Kungliga = d$Kungliga$Unique) %>%
+	     arrange(desc(Fennica))
+
+write.table(w, file = "Table_HistoricalMethods_Unique.csv", sep = "\t", quote = FALSE, row.names = FALSE)
+

### 2018-08-31 inst/examples/statistics.Rmd
ok

---
title: "Historical Methods 1640-1828"
author: "Marjanen, Lahti, Roivainen, Tolonen"
date: "August 31, 2018"
output: word_document
---

This supplementary document provides details of the data fields
analyzed in the main text.

```{r init, echo=FALSE, message=FALSE, warning=FALSE}
# To be run after all historical methods analyses
library(skimr)
library(ggplot2)
theme_set(theme_bw(15))
library(tidyverse)
df0 <- df0 %>% mutate(Subject = subject_topic) %>%
               filter(publication_year >=1640) %>%
               filter(publication_year <=1828)

d <- list()

fen <- subset(df0, catalog == "Fennica")
kun <- subset(df0, catalog == "Kungliga")
cats <- list(Fennica = fen, Kungliga = kun)

for (cat in unique(df0$catalog)) {

  dd <- subset(df0, catalog == cat)[, selected.fields]

  complete <- round(100 * colMeans(!is.na(dd)), 1)
  unique <- apply(dd, 2, function (x) {length(unique(x))})

  d[[cat]] <- data.frame(Field = colnames(dd), Complete = complete, Unique = unique)

}
```

The following table indicates the MARC fields for each data type. The
language information was picked from the MARC fields 008lang and 041a
for Kungliga and Fennica, respectively.

```{r fieldtable, echo=FALSE, message=FALSE, warning=FALSE}
f <- field_table()

fennica_fields <- c(
"041a",
"041h", 
"100a",
"100d",
"240a",
"245a",
"245b",
"260a",
"260b",
"260c",
"300a",
"300b",
"300c",
"300e",
"310a",
"362a",
"500a",
"502a",
"502c",
"502d",
"510a",
"510c",
"650a",
"651a",
"710a",
"720a",
"785t",
"852a")

kungliga_fields <- c(
setdiff(fennica_fields, c("041a", "041h")),
"008lang",
"100a",
"100d",
"110a",
"240a",
"245a",
"245b",
"245c",
"260a",
"260b",
"260c",
"260e",
"260f",
"300a",
"300b",
"300c",
"300e",
"310a",
"362a",
"440a",
"440v",
"500a",
"502a",
"502c",
"502d",
"510a",
"510c",
"650a",
"650x",
"650y",
"650z",
"651a",
"700a",
"700d",
"710a",
"720a",
"740a",
"772c",
"772d",
"772t",
"785t",
"852a",
"852j",
"852z",
"866x",
"900a",
"900d",
"900u",
"976a",
"976b")

all_fields <- union(fennica_fields, kungliga_fields)

df <- data.frame(MARC = all_fields)
df$Description <- f[match(df$MARC, f$field), "concept"]
df$Kungliga  <- c("", "x")[1 + df$MARC %in% kungliga_fields]
df$Fennica  <- c("", "x")[1 + df$MARC %in% fennica_fields]
df <- df %>% arrange(MARC)

kable(df)
```

### Total overview

Records in the final data set used in the analyses (years ```r min(df0$publication_year)```-```r max(df0$publication_year)```):

 * Fennica: ```r nrow(subset(df0, catalog == "Fennica"))```
 * Kungliga: ```r nrow(subset(df0, catalog == "Kungliga"))```

Percentage of non-empty entries for each field (per catalogue).

```{r complete, echo=FALSE, message=FALSE, warning=FALSE}
w <- data.frame(Field = map_fieldnames(colnames(dd)),
           Fennica = d$Fennica$Complete,
	   Kungliga = d$Kungliga$Complete) %>%
	     arrange(desc(Fennica))

kable(w)
```

### Title

Number of unique and all titles per catalogue.

```{r titles, echo=FALSE, message=FALSE, warning=FALSE}
df <- df0 %>% group_by(catalog) %>%
              summarise(Unique = length(unique(title)),
	                All = sum(!is.na(title)))
colnames(df) <- gsub("catalog", "Catalogue", colnames(df))
kable(df)
```

Title length variation quantified in characters and in words.

```{r title_characters, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, figh.height=4}
theme_set(theme_bw(20))
df <- df0 %>% mutate(title_chars = nchar(title))
p <- ggplot(df) +
       geom_histogram(aes(x = title_chars)) + 
       labs(x = "Title length (characters)",
            y = "Frequency (n)") +
       #scale_x_log10(breaks = 10^(0:3)) +
       scale_x_log10(breaks = c(1, 10, 100, 1000)) +       
       facet_grid(. ~ catalog)
print(p)
```

```{r title_words, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, figh.height=4}
theme_set(theme_bw(15))
library(ggplot2)
library(stringi)
theme_set(theme_bw(20))
library(tidyverse)
df <- df0 %>% mutate(title_words = stri_count_words(title))
p <- ggplot(df) +
       geom_histogram(aes(x = title_words)) + 
       labs(x = "Title length (words)",
            y = "Frequency (n)") +
       #scale_x_log10(breaks = 10^(0:3)) +
       scale_x_log10(breaks = c(1, 10, 100)) +       
       facet_grid(. ~ catalog)
print(p)
```

### Subject

Number of unique and all genres per catalogue.

```{r genre, echo=FALSE, message=FALSE, warning=FALSE}
df <- df0 %>% group_by(catalog) %>%
              summarise(Unique = length(unique(Subject)),
	                All = sum(!is.na(Subject)))
colnames(df) <- gsub("catalog", "Catalogue", colnames(df))
kable(df)
```

The most common genres in Fennica:

```{r genres_fen, echo=FALSE, message=FALSE, warning=FALSE}
kable(top(fen, "Subject", 10, "data.frame"), digits = 1)
```

The most common genres in Kungliga:

```{r genres_kun, echo=FALSE, message=FALSE, warning=FALSE}
kable(top(kun, "Subject", 10, "data.frame"), digits = 1)
```

### Publisher

Number of unique and all publishers per catalogue.

```{r publisher, echo=FALSE, message=FALSE, warning=FALSE}
field <- "publisher"
df <- df0
df$field <- df[[field]]
df <- df %>% group_by(catalog) %>%
              summarise(Unique = length(unique(field)),
	                All = sum(!is.na(field)))
colnames(df) <- gsub("catalog", "Catalogue", colnames(df))
kable(df, digits = 1)
```

The most common publishers in Fennica:

```{r publishers_fen, echo=FALSE, message=FALSE, warning=FALSE}
kable(top(fen, field, 10, "data.frame"), digits = 1)
```

The most common publishers in Kungliga:

```{r publishers_kun, echo=FALSE, message=FALSE, warning=FALSE}
kable(top(kun, field, 10, "data.frame"), digits = 1)
```

### Author

Number of unique and all authors per catalogue.

```{r author, echo=FALSE, message=FALSE, warning=FALSE}
field <- "author"
df <- df0
df$field <- df[[field]]
df <- df %>% group_by(catalog) %>%
              summarise(Unique = length(unique(field)),
	                All = sum(!is.na(field)))
colnames(df) <- gsub("catalog", "Catalogue", colnames(df))
kable(df, digits = 1)
```

The most common authors in Fennica:

```{r authors_fen, echo=FALSE, message=FALSE, warning=FALSE}
kable(top(fen, field, 10, "data.frame"), digits = 1)
```

The most common authors in Kungliga:

```{r authors_kun, echo=FALSE, message=FALSE, warning=FALSE}
kable(top(kun, field, 10, "data.frame"), digits = 1)
```

### Pages

Page count variation.

```{r pagecount, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, figh.height=3}
p <- ggplot(df0) +
       geom_histogram(aes(x = pagecount)) + 
       labs(x = "Page count (n)",
            y = "Frequency (n)") +
       scale_x_log10(breaks = c(1, 10, 100, 1000)) +       
       facet_grid(. ~ catalog)
print(p)
```

### Paper consumption

Paper consumption estimates.

```{r paper, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, figh.height=3}
p <- ggplot(df0) +
       geom_histogram(aes(x = paper)) + 
       labs(x = "Paper (sheets)",
            y = "Frequency (n)") +
       scale_x_log10(breaks = c(1, 10, 100, 1000)) +       
       facet_grid(. ~ catalog)
print(p)
```

### Publication year

```{r year, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, figh.height=3}
p <- ggplot(df0) +
       geom_histogram(aes(x = publication_year)) + 
       labs(x = "Publication year",
            y = "Frequency (n)") +
       scale_x_log10(breaks = c(1, 10, 100, 1000)) +       
       facet_grid(. ~ catalog)
print(p)
```

### Language

Number of unique and all languages per catalogue.

```{r languages , echo=FALSE, message=FALSE, warning=FALSE}
field <- "language"
df <- df0
df$field <- df[[field]]
df <- df %>% group_by(catalog) %>%
              summarise(Unique = length(unique(field)),
	                All = sum(!is.na(field)))
colnames(df) <- gsub("catalog", "Catalogue", colnames(df))
colnames(df) <- gsub("language", "Language", colnames(df))
kable(df)
```

The most common languages in Fennica:

```{r languages_fen, echo=FALSE, message=FALSE, warning=FALSE}
kable(top(fen, field, 10, "data.frame"), digits = 1)
```

The most common languages in Kungliga:

```{r languages_kun, echo=FALSE, message=FALSE, warning=FALSE}
kable(top(kun, field, 10, "data.frame"), digits = 1)
```

### Publication place

Number of unique and all publication places per catalog.

```{r places, echo=FALSE, message=FALSE, warning=FALSE}
field <- "publication_place"
df <- df0
df$field <- df[[field]]

df <- df %>% group_by(catalog) %>%
              summarise(Unique = length(unique(field)),
	                All = sum(!is.na(field)))
colnames(df) <- gsub("catalog", "Catalogue", colnames(df))
kable(df)
```

The most common publication places in Fennica:

```{r places_fen, echo=FALSE, message=FALSE, warning=FALSE}
kable(top(fen, field, 10, "data.frame"), digits = 1)
```

The most common publication places in Kungliga:

```{r places_kun, echo=FALSE, message=FALSE, warning=FALSE}
kable(top(kun, field, 10, "data.frame"), digits = 1)
```

### Format (Gatherings)

Percent of unique and all gatherings per catalogue.

```{r gatherings, echo=FALSE, message=FALSE, warning=FALSE}
field <- "gatherings"
df <- df0
df$field <- df[[field]]
df <- df %>% group_by(catalog, gatherings) %>%
              summarise(n = n())
df <- spread(df, catalog, n, fill = 0)
colnames(df) <- c("Gatherings", "Fennica", "Kungliga")
df$Gatherings <- as.character(df$Gatherings)
df$Gatherings <- gsub("NA", "Missing", df$Gatherings)

df2 <- df
df2$Fennica <- round(100 * df2$Fennica / nrow(fen), 1)
df2$Kungliga <- round(100 * df2$Kungliga / nrow(kun), 1)

kable(df2)
```

### 2018-08-31 inst/examples/201808-HistoricalMethods-Overview.Rmd
ok

--- 2018-08-31 inst/examples/statistics.Rmd
@@
 cats <- list(Fennica = fen, Kungliga = kun)
+
+selected.fields <- c("publication_year", "publication_place", "gatherings", "title", "pagecount", "publisher", "language", "Subject")
 
@@
 
-Number of unique and all genres per catalogue.
+Number of unique and all subject topics per catalogue.
 
@@
 
-The most common genres in Fennica:
+The most common subject topics in Fennica:
 
 ```{r genres_fen, echo=FALSE, message=FALSE, warning=FALSE}
-kable(top(fen, "Subject", 10, "data.frame"), digits = 1)
+kable(top(fen, "Subject", 10, "data.frame", round = 1))
 ```
 
-The most common genres in Kungliga:
+The most common subject topics in Kungliga:
 
 ```{r genres_kun, echo=FALSE, message=FALSE, warning=FALSE}
-kable(top(kun, "Subject", 10, "data.frame"), digits = 1)
+kable(top(kun, "Subject", 10, "data.frame", round = 1))
 ```
@@
 ```{r publishers_fen, echo=FALSE, message=FALSE, warning=FALSE}
-kable(top(fen, field, 10, "data.frame"), digits = 1)
+kable(top(fen, field, 10, "data.frame", round = 1))
 ```
@@
 ```{r publishers_kun, echo=FALSE, message=FALSE, warning=FALSE}
-kable(top(kun, field, 10, "data.frame"), digits = 1)
+kable(top(kun, field, 10, "data.frame", round = 1))
 ```
@@
 ```{r authors_fen, echo=FALSE, message=FALSE, warning=FALSE}
-kable(top(fen, field, 10, "data.frame"), digits = 1)
+kable(top(fen, field, 10, "data.frame", round = 1))
 ```
@@
 ```{r authors_kun, echo=FALSE, message=FALSE, warning=FALSE}
-kable(top(kun, field, 10, "data.frame"), digits = 1)
+kable(top(kun, field, 10, "data.frame", round = 1))
 ```
@@
 ```{r languages_fen, echo=FALSE, message=FALSE, warning=FALSE}
-kable(top(fen, field, 10, "data.frame"), digits = 1)
+kable(top(fen, field, 10, "data.frame", round = 1))
 ```
@@
 ```{r languages_kun, echo=FALSE, message=FALSE, warning=FALSE}
-kable(top(kun, field, 10, "data.frame"), digits = 1)
+kable(top(kun, field, 10, "data.frame", round = 1))
 ```
@@
 ```{r places_fen, echo=FALSE, message=FALSE, warning=FALSE}
-kable(top(fen, field, 10, "data.frame"), digits = 1)
+kable(top(fen, field, 10, "data.frame", round = 1))
 ```
@@
 ```{r places_kun, echo=FALSE, message=FALSE, warning=FALSE}
-kable(top(kun, field, 10, "data.frame"), digits = 1)
+kable(top(kun, field, 10, "data.frame", round = 1))
 ```

### 2018-09-01 inst/examples/201808-HistoricalMethods-Overview.Rmd
ok

@@
 }
+```
+
+Records in the final data set used in the analyses:
+
+ * Fennica: ```r nrow(subset(df0, catalog == "Fennica"))```
+ * Kungliga: ```r nrow(subset(df0, catalog == "Kungliga"))```
+
+Data availability for the key fields analyzed in this work (%):
+
+```{r complete, echo=FALSE, message=FALSE, warning=FALSE}
+w <- data.frame(Field = map_fieldnames(colnames(dd)),
+                Fennica = d$Fennica$Complete,
+	        Kungliga = d$Kungliga$Complete) %>%
+	     arrange(desc(Fennica))
+
+kable(w)
 ```
@@
 
-### Total overview
+### Author
 
-Records in the final data set used in the analyses (years ```r min(df0$publication_year)```-```r max(df0$publication_year)```):
+Number of unique authors and all documents with author information:
 
- * Fennica: ```r nrow(subset(df0, catalog == "Fennica"))```
- * Kungliga: ```r nrow(subset(df0, catalog == "Kungliga"))```
+```{r author, echo=FALSE, message=FALSE, warning=FALSE}
+field <- "author"
+df <- df0
+df$field <- df[[field]]
+df <- df %>% group_by(catalog) %>%
+              summarise(Unique = length(unique(field)),
+	                All = sum(!is.na(field)))
+colnames(df) <- gsub("catalog", "Catalogue", colnames(df))
+kable(df, digits = 1)
+```
 
-Percentage of non-empty entries for each field (per catalogue).
+The most common authors in Fennica:
 
-```{r complete, echo=FALSE, message=FALSE, warning=FALSE}
-w <- data.frame(Field = map_fieldnames(colnames(dd)),
-           Fennica = d$Fennica$Complete,
-	   Kungliga = d$Kungliga$Complete) %>%
-	     arrange(desc(Fennica))
+```{r authors_fen, echo=FALSE, message=FALSE, warning=FALSE}
+tab <- top(fen, field, 10, "data.frame", round = 1)
+colnames(tab) <- gsub("author", "Author", colnames(tab))
+kable(tab)
+```
 
-kable(w)
+The most common authors in Kungliga:
+
+```{r authors_kun, echo=FALSE, message=FALSE, warning=FALSE}
+tab <- top(kun, field, 10, "data.frame", round = 1)
+colnames(tab) <- gsub("author", "Author", colnames(tab))
+kable(tab)
+```
+
+### Format (Gatherings)
+
+Proportion (%) of unique gatherings and all documents with gatherings information:
+
+```{r gatherings, echo=FALSE, message=FALSE, warning=FALSE}
+field <- "gatherings"
+df <- df0
+df$field <- df[[field]]
+df <- df %>% group_by(catalog, gatherings) %>%
+              summarise(n = n())
+df <- spread(df, catalog, n, fill = 0)
+colnames(df) <- c("Gatherings", "Fennica", "Kungliga")
+df$Gatherings <- as.character(df$Gatherings)
+df$Gatherings <- gsub("NA", "Missing", df$Gatherings)
+
+df2 <- df
+df2$Fennica <- round(100 * df2$Fennica / nrow(fen), 1)
+df2$Kungliga <- round(100 * df2$Kungliga / nrow(kun), 1)
+
+kable(df2)
+```
+
+### Publisher
+
+Number of unique publishers and all documents with publisher information:
+
+```{r publisher, echo=FALSE, message=FALSE, warning=FALSE}
+field <- "publisher"
+df <- df0
+df$field <- df[[field]]
+df <- df %>% group_by(catalog) %>%
+              summarise(Unique = length(unique(field)),
+	                All = sum(!is.na(field)))
+colnames(df) <- gsub("catalog", "Catalogue", colnames(df))
+kable(df, digits = 1)
+```
+
+The most common publishers in Fennica:
+
+```{r publishers_fen, echo=FALSE, message=FALSE, warning=FALSE}
+tab <- top(fen, field, 10, "data.frame", round = 1)
+colnames(tab) <- gsub("publisher", "Publisher", colnames(tab))
+kable(tab)
+```
+
+The most common publishers in Kungliga:
+
+```{r publishers_kun, echo=FALSE, message=FALSE, warning=FALSE}
+tab <- top(kun, field, 10, "data.frame", round = 1)
+colnames(tab) <- gsub("publisher", "Publisher", colnames(tab))
+kable(tab)
+```
+
+### Pages
+
+Page count variation per gatherings. The variants have been combined (2long/2to; 4long/4to; 8long/8vo; 12long/12mo). Documents with missing gatherings are not shown.
+
+```{r pagecount, echo=FALSE, message=FALSE, warning=FALSE, fig.width=20, figh.height=1}
+df <- df0
+df$gatherings <- gsub("^2long", "2fo", df$gatherings)
+df$gatherings <- gsub("4long", "4to", df$gatherings)
+df$gatherings <- gsub("8long", "8vo", df$gatherings)
+df$gatherings <- gsub("12long", "12mo", df$gatherings)
+df <- df[which(!df$gatherings == "NA"), ]
+df <- subset(df, !is.na(pagecount))
+df$gatherings <- order_gatherings(df$gatherings)
+
+cols <- default_colors("gatherings", levels(df$gatherings))
+
+p <- ggplot(df) +
+       geom_histogram(aes(x = pagecount,
+		    group = gatherings,       
+                    #y = ..count../sum(..count..),
+                    fill = gatherings),
+                    color = "black",
+		    alpha = 0.5
+		    ) + 
+       labs(x = "Page count (n)",
+            y = "Frequency (n)") +
+       scale_x_log10(breaks = c(1, 10, 100, 1000)) +
+       scale_y_log10(breaks = c(1, 10, 100, 1000)) +
+       scale_fill_manual(values = unname(cols)) +       
+       facet_grid(catalog ~ gatherings) +
+       guides(fill = "none") + 
+       labs(y = "Frequency (n)") +
+       theme(
+         axis.text = element_text(size=10)
+             )
+print(p)
+```
+
+### Paper consumption
+
+Paper consumption estimates per gatherings (sheets per document).
+The variants have been combined (2long/2to; 4long/4to; 8long/8vo; 12long/12mo).
+Documents with missing page count estimates are not shown.
+
+```{r paper, echo=FALSE, message=FALSE, warning=FALSE, fig.width=20, figh.height=1}
+x <- c(.01, .1, 1, 10, 100, 1000)
+df <- df0
+df$gatherings <- gsub("^2long", "2fo", df$gatherings)
+df$gatherings <- gsub("4long", "4to", df$gatherings)
+df$gatherings <- gsub("8long", "8vo", df$gatherings)
+df$gatherings <- gsub("12long", "12mo", df$gatherings)
+df <- df[which(!df$gatherings == "NA"), ]
+df <- subset(df, !is.na(paper))
+df$gatherings <- order_gatherings(df$gatherings)
+cols <- default_colors("gatherings", levels(df$gatherings))
+
+p <- ggplot(df) +
+       geom_histogram(aes(x = paper/1e3, # Remove print run estimates
+		    group = gatherings,       
+                    fill = gatherings),
+                    color = "black",
+		    alpha = 0.5
+		    ) +
+       scale_fill_manual(values = unname(cols)) + 		    
+       labs(x = "Paper per document (sheets)",
+            y = "Frequency (n)") +
+       scale_y_log10(breaks = c(1, 10, 100, 1000)) +
+       scale_x_log10(breaks = x,
+           labels=scales::trans_format('log10', scales::math_format(10^.x))) + 
+       facet_grid(catalog ~ gatherings) +
+       guides(fill = "none") + 
+       labs(y = "Frequency (n)") +
+       theme(
+         axis.text = element_text(size=10)
+             )
+
+print(p)
+
+```
+
+### Publication year
+
+```{r year, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, figh.height=3}
+p <- ggplot(df0) +
+       geom_histogram(aes(x = publication_year)) + 
+       labs(x = "Publication year",
+            y = "Frequency (n)") +
+       # scale_x_log10(breaks = c(1, 10, 100, 1000)) +       
+       facet_grid(. ~ catalog)
+print(p)
+```
+
+### Language
+
+Number of unique languages and all documents with language information.
+
+```{r languages , echo=FALSE, message=FALSE, warning=FALSE}
+field <- "language"
+df <- df0
+df$field <- df[[field]]
+df <- df %>% group_by(catalog) %>%
+              summarise(Unique = length(unique(field)),
+	                All = sum(!is.na(field)))
+colnames(df) <- gsub("catalog", "Catalogue", colnames(df))
+colnames(df) <- gsub("language", "Language", colnames(df))
+kable(df)
+```
+
+The most common languages in Fennica:
+
+```{r languages_fen, echo=FALSE, message=FALSE, warning=FALSE}
+tab <- top(fen, field, 10, "data.frame", round = 1)
+colnames(tab) <- gsub("language", "Language", colnames(tab))
+kable(tab)
+```
+
+The most common languages in Kungliga:
+
+```{r languages_kun, echo=FALSE, message=FALSE, warning=FALSE}
+tab <- top(kun, field, 10, "data.frame", round = 1)
+colnames(tab) <- gsub("language", "Language", colnames(tab))
+kable(tab)
+```
+
+### Publication place
+
+Number of unique publication places and all documents with publication place information.
+
+```{r places, echo=FALSE, message=FALSE, warning=FALSE}
+field <- "publication_place"
+df <- df0
+df$field <- df[[field]]
+
+df <- df %>% group_by(catalog) %>%
+              summarise(Unique = length(unique(field)),
+	                All = sum(!is.na(field)))
+colnames(df) <- gsub("catalog", "Catalogue", colnames(df))
+kable(df)
+```
+
+The most common publication places in Fennica:
+
+```{r places_fen, echo=FALSE, message=FALSE, warning=FALSE}
+tab <- top(fen, field, 10, "data.frame", round = 1)
+colnames(tab) <- gsub("publication_place", "Publication place", colnames(tab))
+kable(tab)
+```
+
+The most common publication places in Kungliga:
+
+```{r places_kun, echo=FALSE, message=FALSE, warning=FALSE}
+tab <- top(kun, field, 10, "data.frame", round = 1)
+colnames(tab) <- gsub("publication_place", "Publication place", colnames(tab))
+kable(tab)
+```
+
+### Subject
+
+Number of unique and all subject topics per catalogue.
+
+```{r genre, echo=FALSE, message=FALSE, warning=FALSE}
+df <- df0 %>% group_by(catalog) %>%
+              summarise(Unique = length(unique(Subject)),
+	                All = sum(!is.na(Subject)))
+colnames(df) <- gsub("catalog", "Catalogue", colnames(df))
+kable(df)
+```
+
+The most common subject topics in Fennica:
+
+```{r genres_fen, echo=FALSE, message=FALSE, warning=FALSE}
+kable(top(fen, "Subject", 10, "data.frame", round = 1))
+```
+
+The most common subject topics in Kungliga:
+
+```{r genres_kun, echo=FALSE, message=FALSE, warning=FALSE}
+kable(top(kun, "Subject", 10, "data.frame", round = 1))
 ```
@@
 ```
-
-### Subject
-
-Number of unique and all subject topics per catalogue.
-
-```{r genre, echo=FALSE, message=FALSE, warning=FALSE}
-df <- df0 %>% group_by(catalog) %>%
-              summarise(Unique = length(unique(Subject)),
-	                All = sum(!is.na(Subject)))
-colnames(df) <- gsub("catalog", "Catalogue", colnames(df))
-kable(df)
-```
-
-The most common subject topics in Fennica:
-
-```{r genres_fen, echo=FALSE, message=FALSE, warning=FALSE}
-kable(top(fen, "Subject", 10, "data.frame", round = 1))
-```
-
-The most common subject topics in Kungliga:
-
-```{r genres_kun, echo=FALSE, message=FALSE, warning=FALSE}
-kable(top(kun, "Subject", 10, "data.frame", round = 1))
-```
-
-### Publisher
-
-Number of unique and all publishers per catalogue.
-
-```{r publisher, echo=FALSE, message=FALSE, warning=FALSE}
-field <- "publisher"
-df <- df0
-df$field <- df[[field]]
-df <- df %>% group_by(catalog) %>%
-              summarise(Unique = length(unique(field)),
-	                All = sum(!is.na(field)))
-colnames(df) <- gsub("catalog", "Catalogue", colnames(df))
-kable(df, digits = 1)
-```
-
-The most common publishers in Fennica:
-
-```{r publishers_fen, echo=FALSE, message=FALSE, warning=FALSE}
-kable(top(fen, field, 10, "data.frame", round = 1))
-```
-
-The most common publishers in Kungliga:
-
-```{r publishers_kun, echo=FALSE, message=FALSE, warning=FALSE}
-kable(top(kun, field, 10, "data.frame", round = 1))
-```
-
-### Author
-
-Number of unique and all authors per catalogue.
-
-```{r author, echo=FALSE, message=FALSE, warning=FALSE}
-field <- "author"
-df <- df0
-df$field <- df[[field]]
-df <- df %>% group_by(catalog) %>%
-              summarise(Unique = length(unique(field)),
-	                All = sum(!is.na(field)))
-colnames(df) <- gsub("catalog", "Catalogue", colnames(df))
-kable(df, digits = 1)
-```
-
-The most common authors in Fennica:
-
-```{r authors_fen, echo=FALSE, message=FALSE, warning=FALSE}
-kable(top(fen, field, 10, "data.frame", round = 1))
-```
-
-The most common authors in Kungliga:
-
-```{r authors_kun, echo=FALSE, message=FALSE, warning=FALSE}
-kable(top(kun, field, 10, "data.frame", round = 1))
-```
-
-### Pages
-
-Page count variation.
-
-```{r pagecount, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, figh.height=3}
-p <- ggplot(df0) +
-       geom_histogram(aes(x = pagecount)) + 
-       labs(x = "Page count (n)",
-            y = "Frequency (n)") +
-       scale_x_log10(breaks = c(1, 10, 100, 1000)) +       
-       facet_grid(. ~ catalog)
-print(p)
-```
-
-### Paper consumption
-
-Paper consumption estimates.
-
-```{r paper, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, figh.height=3}
-p <- ggplot(df0) +
-       geom_histogram(aes(x = paper)) + 
-       labs(x = "Paper (sheets)",
-            y = "Frequency (n)") +
-       scale_x_log10(breaks = c(1, 10, 100, 1000)) +       
-       facet_grid(. ~ catalog)
-print(p)
-```
-
-### Publication year
-
-```{r year, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, figh.height=3}
-p <- ggplot(df0) +
-       geom_histogram(aes(x = publication_year)) + 
-       labs(x = "Publication year",
-            y = "Frequency (n)") +
-       scale_x_log10(breaks = c(1, 10, 100, 1000)) +       
-       facet_grid(. ~ catalog)
-print(p)
-```
-
-### Language
-
-Number of unique and all languages per catalogue.
-
-```{r languages , echo=FALSE, message=FALSE, warning=FALSE}
-field <- "language"
-df <- df0
-df$field <- df[[field]]
-df <- df %>% group_by(catalog) %>%
-              summarise(Unique = length(unique(field)),
-	                All = sum(!is.na(field)))
-colnames(df) <- gsub("catalog", "Catalogue", colnames(df))
-colnames(df) <- gsub("language", "Language", colnames(df))
-kable(df)
-```
-
-The most common languages in Fennica:
-
-```{r languages_fen, echo=FALSE, message=FALSE, warning=FALSE}
-kable(top(fen, field, 10, "data.frame", round = 1))
-```
-
-The most common languages in Kungliga:
-
-```{r languages_kun, echo=FALSE, message=FALSE, warning=FALSE}
-kable(top(kun, field, 10, "data.frame", round = 1))
-```
-
-### Publication place
-
-Number of unique and all publication places per catalog.
-
-```{r places, echo=FALSE, message=FALSE, warning=FALSE}
-field <- "publication_place"
-df <- df0
-df$field <- df[[field]]
-
-df <- df %>% group_by(catalog) %>%
-              summarise(Unique = length(unique(field)),
-	                All = sum(!is.na(field)))
-colnames(df) <- gsub("catalog", "Catalogue", colnames(df))
-kable(df)
-```
-
-The most common publication places in Fennica:
-
-```{r places_fen, echo=FALSE, message=FALSE, warning=FALSE}
-kable(top(fen, field, 10, "data.frame", round = 1))
-```
-
-The most common publication places in Kungliga:
-
-```{r places_kun, echo=FALSE, message=FALSE, warning=FALSE}
-kable(top(kun, field, 10, "data.frame", round = 1))
-```
-
-### Format (Gatherings)
-
-Percent of unique and all gatherings per catalogue.
-
-```{r gatherings, echo=FALSE, message=FALSE, warning=FALSE}
-field <- "gatherings"
-df <- df0
-df$field <- df[[field]]
-df <- df %>% group_by(catalog, gatherings) %>%
-              summarise(n = n())
-df <- spread(df, catalog, n, fill = 0)
-colnames(df) <- c("Gatherings", "Fennica", "Kungliga")
-df$Gatherings <- as.character(df$Gatherings)
-df$Gatherings <- gsub("NA", "Missing", df$Gatherings)
-
-df2 <- df
-df2$Fennica <- round(100 * df2$Fennica / nrow(fen), 1)
-df2$Kungliga <- round(100 * df2$Kungliga / nrow(kun), 1)
-
-kable(df2)
-```

### 2018-09-09 inst/examples/201808-HistoricalMethods-Figures.Rmd
ok

--- 2018-08-27 inst/examples/20170201-manuscript.Rmd
@@
 title: "A Quantitative Approach to Book Printing in Sweden and Finland, 1640–1828"
-author: "Mikko Tolonen, Leo Lahti, Hege Roivainen, Jani Marjanen"
+author: "Mikko Tolonen, Leo Lahti, Hege Roivainen, Jani Marjanen (2018)"
 date: "`r Sys.Date()`"
@@
 # Default time span
-min.year <- 1488
+min.year <- 1640
 max.year <- 1828
@@
 df.combined.preprocessed <- readRDS("df.combined.Rds")
+
 # Data with duplicates removed
 df.full <- df.combined.preprocessed %>% filter(!remove)
+
 # Calculate title length (nchar and word count)
@@
 # Data with years limited as well
-df0 <- df.full %>% filter(publication_year >= min.year & publication_year <= max.year)
-
-cols <- list(Fennica = "blue", Kungliga = "darkred")
+df.full <- df.full %>% filter(publication_year >= min.year & publication_year <= max.year)
+
+# Fix author names
+df.full$author <- factor(gsub(" Von ", " von ", df.full$author))
+df.full <- df.full %>% mutate(Topic = subject_topic)
+
+# Combine subcategories of gatherings
+df.full$gatherings <- map_gatherings(df.full$gatherings, "Standard", "Short")
+
+# Add primary language
+df.full$language_primary <- sub(";.*", "", df.full$language)
+
+# Change catalog name
+df.full$catalog <- gsub("Fennica", "FNB", df.full$catalog)
+df.full$catalog <- gsub("Kungliga", "SNB", df.full$catalog)
+df.full$catalog <- factor(df.full$catalog)
+
+df0 <- df.full
+cols <- list(FNB = "blue", SNB = "darkred")
 ```
@@
 
-  if (catal == "Kungliga") {
+  if (catal == "SNB") {
     df00 <- df.full %>% filter(publication_year >= min.year & publication_year <= max.year)
-  } else if (catal == "Fennica") {
+  } else if (catal == "FNB") {
     df00 <- df.full %>% filter(publication_year >= min.year & publication_year <= 1900)
@@
          scale_x_continuous(breaks = brs,
-	   labels = insert_minor(brs, 5, start = ifelse(catal == "Fennica", 1500, 1550))) + 
+	   labels = insert_minor(brs, 5, start = ifelse(catal == "FNB", 1500, 1550))) + 
          scale_y_continuous(breaks = seq(0, 6.8, 1), limits = c(0, 6.8))
@@
 ```{r Figure_4, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.show="last", fig.width=27, fig.height=10}
-cols <- list(Fennica = "blue", Kungliga = "darkred")
+cols <- list(FNB = "blue", SNB = "darkred")
 df <- df.full %>% filter(publication_year >= 1640 &
@@
        scale_y_continuous(breaks = brsy, labels = insert_minor(brsy, 2), limits = c(0, max(na.omit(df$title_length)))) +
-       #ggtitl(paste("Median title length (", catal, ")", sep = "")) +
        xlab("Decade") +
@@
 prow <- plot_grid(
-           pics[["Fennica-n"]] + theme(legend.position="none"),
-           pics[["Fennica-paper"]] + theme(legend.position="none"),
-           pics[["Kungliga-n"]] + theme(legend.position="none"),
-           pics[["Kungliga-paper"]] + theme(legend.position="none"),
+           pics[["FNB-n"]] + theme(legend.position="none"),
+           pics[["FNB-paper"]] + theme(legend.position="none"),
+           pics[["SNB-n"]] + theme(legend.position="none"),
+           pics[["SNB-paper"]] + theme(legend.position="none"),
            align = 'vh',
@@
 
-### Fig 6: Publishing activity over time (Kungliga)
+### Fig 6: Publishing activity over time (SNB)
 
@@
 # theme_set(theme_bw(20))
-df <- df0 %>% filter(catalog == "Kungliga")
+df <- df0 %>% filter(catalog == "SNB")
 
@@
 
-### Fig 7: Publishing activity and riksdagar: Kungliga
+### Fig 7: Publishing activity and riksdagar: SNB
 
@@
 maxyear <- 1830
-catal <- "Kungliga"
+catal <- "SNB"
 
@@
 
-### Fig 8: Publishers in Swedish University towns (Fennica)
-
-Turku, Vaasa and Vyborg from Fennica; Stockholm, Lund, Uppsala, Greifswald, Tartu from Kungliga.
+### Fig 8: Publishers in Swedish University towns (FNB)
+
+Turku, Vaasa and Vyborg from FNB; Stockholm, Lund, Uppsala, Greifswald, Tartu from SNB.
 
@@
 df <- df0
-catal <- "Fennica"
+catal <- "FNB"
 df <- df %>%
@@
 df <- df0
-catalogue <- "Kungliga"
+catalogue <- "SNB"
 df <- df %>%
@@
 
-### Fig 9: Publications in Vaasa in Fennica, 1750-1828
+### Fig 9: Publications in Vaasa in FNB, 1750-1828
 
@@
 library(dplyr)
-catalogue <- "Fennica"
+catalogue <- "FNB"
 place <- "Vaasa"
@@
 
-### Fig 10: Top publishers in Turku/Fennica
+### Fig 10: Top publishers in Turku/FNB
 
@@
 place <- "Turku"
-catalogue <- "Fennica"
+catalogue <- "FNB"
 df <- df0
@@
 
-# Take cities from Kungliga except Turku
-cat <- "Kungliga"
+# Take cities from SNB except Turku
+cat <- "SNB"
 df1 <- df0 %>% filter(publication_place %in% setdiff(cities, "Turku")) %>%
@@
 
-# Take cities from Fennica for Turku
-cat <- "Fennica"
+# Take cities from FNB for Turku
+cat <- "FNB"
 df2 <- df0 %>% filter(publication_place %in% "Turku") %>%
@@
 Paper consumption in octavo format books in Stockholm, Turku, Uppsala,
-Lund, Göteborg and Linköping. Turku is from Fennica, other cities from
-Kungliga.
+Lund, Göteborg and Linköping. Turku is from FNB, other cities from
+SNB.
 
 ```{r Figure_13, echo=FALSE, message=FALSE, warning=FALSE}
-# Take cities from Kungliga except Turku
-cat <- "Kungliga"
+# Take cities from SNB except Turku
+cat <- "SNB"
 df1 <- df0 %>% filter(publication_place %in% setdiff(cities, "Turku")) %>%
@@
 
-Average title length in words in Stockholm, Turku, Uppsala, Lund, Göteborg and Linköping. According to Kungliga, except Turku from Fennica.
+Average title length in words in Stockholm, Turku, Uppsala, Lund, Göteborg and Linköping. According to SNB, except Turku from FNB.
 
 ```{r Figure_14, echo=FALSE, message=FALSE, warning=FALSE}
-# Take cities from Kungliga except Turku
+# Take cities from SNB except Turku
 df00 <- df.full %>% filter(publication_year >= 1640 & publication_year <= 1850)
-df1 <- df00 %>% filter((publication_place %in% setdiff(cities, "Turku") & catalog == "Kungliga") |
-                       (publication_place %in% "Turku" & catalog == "Fennica")) 
+df1 <- df00 %>% filter((publication_place %in% setdiff(cities, "Turku") & catalog == "SNB") |
+                       (publication_place %in% "Turku" & catalog == "FNB")) 
 df1$publication_place[!df1$publication_place == "Stockholm"] <- "Other"
@@
 cnt <- 0
-for (catalogue in c("Fennica", "Kungliga")) {
+for (catalogue in c("FNB", "SNB")) {
 
@@
     # so one doc may have multiple entries corresponding to different languages
-    # mean(rowSums(df[, lang]) == 1) # 93% Fennica docs have just 1 language
+    # mean(rowSums(df[, lang]) == 1) # 93% FNB docs have just 1 language
     # Combine data frames for specified languages
@@
 prow <- plot_grid(
-           pics[["Fennica-Turku"]] + theme(legend.position="none"),
-           pics[["Kungliga-Stockholm"]] + theme(legend.position="none"),
-           pics[["Kungliga-Uppsala"]] + theme(legend.position="none"),
-           pics[["Kungliga-Lund"]] + theme(legend.position="none"),	   	  
+           pics[["FNB-Turku"]] + theme(legend.position="none"),
+           pics[["SNB-Stockholm"]] + theme(legend.position="none"),
+           pics[["SNB-Uppsala"]] + theme(legend.position="none"),
+           pics[["SNB-Lund"]] + theme(legend.position="none"),	   	  
            align = 'vh',
@@
 
-### Fig 16: Topic richness per language (Fennica)
+### Fig 16: Topic richness per language (FNB)
 
 ```{r Figure_16, echo=FALSE, message=FALSE, warning=FALSE, fig.show="hold"}
-catalogue <- "Fennica"
-df <- filter(df0, catalog == "Fennica") %>%
+catalogue <- "FNB"
+df <- filter(df0, catalog == "FNB") %>%
   filter(publication_year >= 1640 & publication_year <= 1828) %>%
@@
 sel <- c("hautajaiset", "häät", "juhlamenot")
-catalogue <- "Fennica"
+catalogue <- "FNB"
 df <- df0
@@
 sel <- c("virret","arkkiveisut","hartauskirjat","katekismukset","rukouspäivät","saarnat","aapiset","rukoukset","rukous","hengelliset laulut","hartauspuheet","virsikirjat")
-catalogue <- "Fennica"
+catalogue <- "FNB"
 
@@
 
-### Data statistics
-
-```{r stats, echo=FALSE, message=FALSE, warning=FALSE}
-library(skimr)
-
-s <- skim(subset(df0, catalog == "Fennica")[, c("publication_year", "publication_place", "gatherings", "title", "pagecount", "publisher", "language", "subject_topic")])
-
-kable(s)
-```
-
 ## Session info

### 2018-09-09 inst/examples/201808-HistoricalMethods-Supplement.Rmd
ok

---
title: "A Quantitative Approach to Book Printing in Sweden and Finland, 1640–1828: supplementary material"
author: "Mikko Tolonen, Leo Lahti, Hege Roivainen, Jani Marjanen (2018)"
output: word_document
---

This supplementary document provides a summary of the data fields
analyzed in the main text.

```{r init, echo=FALSE, message=FALSE, warning=FALSE}
library(devtools)
#install_github("haozhu233/kableExtra")
library(kableExtra)
load_all("~/Rpackages/bibliographica")
load_all("~/Rpackages/fennica")
library(skimr)
library(ggplot2)
theme_set(theme_bw(15))
library(tidyverse)

# To be run after all historical methods analyses
# df.combined.preprocessed <- readRDS("data/unified/df.combined.Rds")
df0 <- df.full

d <- list()

fen <- subset(df0, catalog == "FNB")
kun <- subset(df0, catalog == "SNB")
cats <- list(FNB = fen, SNB = kun)

selected.fields <- c("author", "publication_year", "publication_place", "gatherings", "title", "pagecount", "publisher", "language_primary", "Topic")

for (cat in unique(df0$catalog)) {

  dd <- subset(df0, catalog == cat)[, selected.fields]

  complete <- round(100 * colMeans(!is.na(dd)), 1)
  unique <- apply(dd, 2, function (x) {length(unique(x))})

  d[[cat]] <- data.frame(Field = colnames(dd), Complete = complete, Unique = unique)

}
```

### Data availability

Records in the final data set used in the analyses:

 * FNB: ```r nrow(subset(df0, catalog == "FNB"))```
 * SNB: ```r nrow(subset(df0, catalog == "SNB"))```

Data availability for the key fields analyzed in this work (%).

```{r complete, echo=FALSE, message=FALSE, warning=FALSE}
w <- data.frame(Field = map_fieldnames(colnames(dd)),
                "FNB" = d$FNB$Complete,
	        "SNB" = d$SNB$Complete) %>%
	     arrange(desc(FNB))

colnames(w) <- c("Field", "FNB (%)", "SNB (%)")
# kable(w)

# Add Footnote
w[which(w$Field == "Topic"), "SNB (%)"] <- paste0(as.character(w[which(w$Field == "Topic"), "SNB (%)"]), "*")
w[which(w$Field == "Publisher"), "SNB (%)"] <- paste0(as.character(w[which(w$Field == "Publisher"), "SNB (%)"]), "*")

kable <- knitr::kable
knitr::kable(w, format = "markdown")

#%>% kable_styling(latex_options = c("striped", "hold_position"))

#kable(w, format = "latex", booktabs = T, caption = "Demo Table") 
#  kable_styling(latex_options = c("striped", "hold_position"),
#                full_width = F) %>%
#  
```

$^*$The SNB publishers and topics are not used due to the low coverage of harmonized data entries.

### Authors

Number of unique authors and all documents with author information:

```{r author, echo=FALSE, message=FALSE, warning=FALSE}
field <- "author"
df <- df0
df$field <- df[[field]]
df <- df %>% group_by(catalog) %>%
              summarise(Unique = length(unique(field)),
	                All = sum(!is.na(field)))
colnames(df) <- gsub("catalog", "Catalogue", colnames(df))
knitr::kable(df, digits = 1, format = "markdown")
```

The most common authors in FNB:

```{r authors_fen, echo=FALSE, message=FALSE, warning=FALSE}
tab <- top(fen, field, 10, "data.frame", round = 1)
colnames(tab) <- gsub("author", "Author", colnames(tab))
knitr::kable(tab, format = "markdown")
```

The most common authors in SNB:

```{r authors_kun, echo=FALSE, message=FALSE, warning=FALSE}
tab <- top(kun, field, 10, "data.frame", round = 1)
colnames(tab) <- gsub("author", "Author", colnames(tab))
knitr::kable(tab, format = "markdown")
```

### Languages

In FNB, we have identified ```r sum(subset(df0, catalog == "FNB")$multilingual)``` multilingual documents in the investigated time period. In SNB, the multilingual documents have not been analyzed yet. We use the primary language of the document for summaries.

Number of identified primary languages and all documents with language information.

```{r languages , echo=FALSE, message=FALSE, warning=FALSE}
field <- "language_primary"
df <- df0
df$field <- df[[field]]
df <- df %>% group_by(catalog) %>%
              summarise(Unique = length(unique(field)),
	                All = sum(!is.na(field)))
colnames(df) <- gsub("catalog", "Catalogue", colnames(df))
colnames(df) <- gsub("language", "Language", colnames(df))
knitr::kable(df, format = "markdown")
```

The most common (primary) languages in FNB:

```{r languages_fen, echo=FALSE, message=FALSE, warning=FALSE}
tab <- top(fen, field, 10, "data.frame", round = 1)
colnames(tab) <- gsub("language_primary", map("language_primary", fieldname_table(), from = "Data", to = "Name"), colnames(tab))
knitr::kable(tab, format = "markdown")
```

The most common (primary) languages in SNB:

```{r languages_kun, echo=FALSE, message=FALSE, warning=FALSE}
tab <- top(kun, field, 10, "data.frame", round = 1)
colnames(tab) <- gsub("language_primary", map("language_primary", fieldname_table(), from = "Data", to = "Name"), colnames(tab))
knitr::kable(tab, format = "markdown")
```

### Formats (Gatherings)

Proportion (%) of gatherings in the FNB and SNB catalogues. The gatherings with a prevalence less than 1% in both catalogues have been combined into the "Other" category.

```{r gatherings, echo=FALSE, message=FALSE, warning=FALSE}
df <- df0 %>% group_by(catalog, gatherings) %>%
              summarise(n = n())
df <- spread(df, catalog, n, fill = 0)
colnames(df) <- c("Gatherings", "FNB", "SNB")
df$Gatherings <- as.character(df$Gatherings)
df$Gatherings <- gsub("NA", "Missing", df$Gatherings)

df2 <- df
df2$FNB <- round(100 * df2$FNB / nrow(fen), 1)
df2$SNB <- round(100 * df2$SNB / nrow(kun), 1)

# Combine gatherings with <1% prevalence into "Other category"
inds <- which(rowMeans(apply(df2[, 2:3], 2, as.numeric) < 1) == 1)
df2 <- rbind(df2, c("Other", colSums(apply(df2[which(rowMeans(df2[, 2:3] < 1) == 1),], 2, as.numeric))[-1])) %>% slice(-inds)
df2$Gatherings <- gsub("NA", "Missing", df2$Gatherings)
df2$Gatherings[is.na(df2$Gatherings)] <- "Missing"
accepted.gatherings <- df2$Gatherings

names(df2) <- gsub("NB", "NB (%)", names(df2))
df2$Gatherings2 <- map_gatherings(unlist(df2[,1]), "Short", "Name")
df2$Gatherings <- apply(cbind(df2$Gatherings2, paste0("(", unlist(df2$Gatherings), ")")), 1, function (x) {paste(x, collapse = " ")})
df2$Gatherings2 <- NULL
df2$Gatherings <- gsub(" \\(Missing\\)", "", df2$Gatherings)
df2$Gatherings <- gsub(" \\(Other\\)", "", df2$Gatherings)
knitr::kable(df2, format = "markdown")

# Take the changes also in original data now for later figs
inds <- which(!df0$gatherings %in% accepted.gatherings)
df0$gatherings[inds] <- "Other"
```

### Pages

Page count variation per gatherings.

```{r pagecount, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, figh.height=1}
theme_set(theme_bw(15))
df <- df0
df <- df[which(!df$gatherings == "NA"), ]
df <- subset(df, !is.na(pagecount))
df$gatherings <- order_gatherings(df$gatherings)

cols <- default_colors("gatherings", map_gatherings(levels(df$gatherings), from = "Short", to = "Name"))

p <- ggplot(df) +
       geom_histogram(aes(x = pagecount,
		    group = gatherings,       
                    #y = ..count../sum(..count..),
                    fill = gatherings),
                    color = "black",
		    alpha = 0.5
		    ) + 
       labs(x = "Page count (n)",
            y = "Frequency (n)") +
       scale_x_log10(breaks = c(1, 10, 100, 1000)) +
       scale_y_log10(breaks = c(1, 10, 100, 1000)) +
       scale_fill_manual(values = unname(cols)) +       
       facet_grid(catalog ~ gatherings) +
       guides(fill = "none") + 
       labs(y = "Frequency (n)") +
       theme(axis.text = element_text(size=12))
print(p)
```

### Publication places

Number of unique publication places and all documents with publication place information.

```{r places, echo=FALSE, message=FALSE, warning=FALSE}
field <- "publication_place"
df <- df0
df$field <- df[[field]]

df <- df %>% group_by(catalog) %>%
              summarise(Unique = length(unique(field)),
	                All = sum(!is.na(field)))
colnames(df) <- gsub("catalog", "Catalogue", colnames(df))
knitr::kable(df, format = "markdown")
```

The most common publication places in FNB:

```{r places_fen, echo=FALSE, message=FALSE, warning=FALSE}
tab <- top(fen, field, 10, "data.frame", round = 1)
colnames(tab) <- gsub("publication_place", "Publication place", colnames(tab))
knitr::kable(tab, format = "markdown")
```

The most common publication places in SNB:

```{r places_kun, echo=FALSE, message=FALSE, warning=FALSE}
tab <- top(kun, field, 10, "data.frame", round = 1)
colnames(tab) <- gsub("publication_place", "Publication place", colnames(tab))
knitr::kable(tab, format = "markdown")
```

### Publication years

Title count per decade for FNB and SNB.

```{r year, echo=FALSE, message=FALSE, warning=FALSE, fig.width=9, figh.height=4, out.width = "300px"}
theme_set(theme_bw(20))
df <- df0
names(df) <- gsub("catalog", "Catalog", names(df))
df <- df %>% group_by(Catalog, publication_decade) %>% tally()
p <- ggplot(df, aes(x = publication_decade, y = n, fill = Catalog)) +
       geom_bar(color = "black",
         position = "dodge", stat = "identity") +
       guides(fill = guide_legend(reverse = TRUE)) +
       labs(x = "Publication decade",
            y = "Frequency (n)") +
       scale_fill_manual(values = rev(c("darkgray", "black"))) #+
       #theme(axis.text = element_text(size=15))
print(p)
```

### Publishers

In FNB, the data includes ```r  length(unique(subset(df0, catalog == "FNB")$publisher))``` unique publishers, and ```r  round(100 * mean(!is.na(subset(df0, catalog == "FNB")$publisher), na.rm = TRUE))```% of the documents have publisher information. We have not analyzed publishers in SNB, where the availability of harmonized publisher information is currently low (```r  round(100 * mean(!is.na(subset(df0, catalog == "SNB")$publisher), na.rm = TRUE))```%).

The most common publishers in FNB (the total count and percentage of all documents are shown):

```{r publishers_fen, echo=FALSE, message=FALSE, warning=FALSE}
tab <- top(fen, "publisher", 10, "data.frame", round = 1)
colnames(tab) <- gsub("publisher", "Publisher", colnames(tab))
knitr::kable(tab, format = "markdown")
```

### Topics

We use here the term "Topic" for the "Topical term" MARC field 650a for brevity. In FNB, the data includes ```r  length(unique(subset(df0, catalog == "FNB")$Topic))``` unique topics. ```r  round(100 * mean(!is.na(subset(df0, catalog == "FNB")$Topic), na.rm = TRUE))```% of the documents have topic information. We have not analyzed topics in SNB, where the availability of harmonized topics is currently low (```r  round(100 * mean(!is.na(subset(df0, catalog == "SNB")$Topic), na.rm = TRUE))```%).

The most common topics in FNB (English translation in parentheses):

```{r topics_fen, echo=FALSE, message=FALSE, warning=FALSE}
tab <- top(fen, "Topic", 10, "data.frame", round = 1)
colnames(tab) <- gsub("Topic", "Topic", colnames(tab))

trans = c("hautajaiset" = "funerals",
"etsintäkuulutukset" = "warrants",
"häät" = "weddings",
"yliopistot;juhlamenot;Turku" = "universities;ceremonies;Turku",
"arkkiveisut;virret" = "broadside ballads;hymns",
"dogmatiikka" = "dogmatics",
"moraali" = "moral philosophy",
"homiletiikka" = "homiletics",
"filosofia" = "philosophy",
"eksegetiikka" = "exegetics")
tab$Topic <- paste(tab$Topic, paste0("(", unname(trans[tab$Topic]), ")"))
knitr::kable(tab, format = "markdown")
```

### MARC fields

The following table indicates the MARC fields for each data type in
our harmonized data collection. The language information was picked from the
MARC fields 008lang and 041a for SNB and FNB, respectively.

```{r fieldtable, echo=FALSE, message=FALSE, warning=FALSE}
f <- field_table()

fennica_fields <- c(
"041a",
"041h", 
"100a",
"100d",
"240a",
"245a",
"245b",
"260a",
"260b",
"260c",
"300a",
"300b",
"300c",
"300e",
"310a",
"362a",
"500a",
"502a",
"502c",
"502d",
"510a",
"510c",
"650a",
"651a",
"710a",
"720a",
"785t",
"852a")

kungliga_fields <- c(
setdiff(fennica_fields, c("041a", "041h")),
"008lang",
"100a",
"100d",
"110a",
"240a",
"245a",
"245b",
"245c",
"260a",
"260b",
"260c",
"260e",
"260f",
"300a",
"300b",
"300c",
"300e",
"310a",
"362a",
"440a",
"440v",
"500a",
"502a",
"502c",
"502d",
"510a",
"510c",
"650a",
"650x",
"650y",
"650z",
"651a",
"700a",
"700d",
"710a",
"720a",
"740a",
"772c",
"772d",
"772t",
"785t",
"852a",
"852j",
"852z",
"866x",
"900a",
"900d",
"900u",
"976a",
"976b")

all_fields <- union(fennica_fields, kungliga_fields)

df <- data.frame(MARC = all_fields)
df$Description <- f[match(df$MARC, f$field), "concept"]
df$SNB  <- c("", "x")[1 + df$MARC %in% kungliga_fields]
df$FNB  <- c("", "x")[1 + df$MARC %in% fennica_fields]
df <- df %>% arrange(MARC)

knitr::kable(df, format = "markdown")
```

### 2018-09-09 inst/examples/201808-HistoricalMethods-Figures.Rmd
ok

@@
 knitr::opts_chunk$set(echo = FALSE)
-knitr::opts_chunk$set(fig.path = "20170201_manuscript/", dpi = 300)
-#knitr::opts_chunk$set(dev = c("png", "jpeg", "cairo_ps"))
-# knitr::opts_chunk$set(dev = "Cairo")
-#knitr::opts_chunk$set(dev = "CairoPDF")
+knitr::opts_chunk$set(fig.path = "figures_HistoricalMethods2018/", dpi = 300)
 knitr::opts_chunk$set(dev = "CairoPS")
-# knitr::opts_chunk$set(dev = "cairo_pdf") # Embed fonts
-#knitr::opts_chunk$set(dev = "cairo_ps") # Embed fonts
 knitr::opts_chunk$set(out.width = "17cm") # Default size 8.5cm ie 3.35 inch) per col

### 2018-09-09 inst/examples/201808-HistoricalMethods-Figures.Rmd
ok

@@
 prow <- plot_grid(
-           pics[[1]] + theme(legend.position="none"),
-           pics[[2]] + theme(legend.position="none"),
+           pics[[1]] + theme(legend.position="none") + ylim(c(0, 7)),
+           pics[[2]] + theme(legend.position="none") + ylim(c(0, 7)),
            align = 'vh',

### 2018-09-10 inst/examples/201808-HistoricalMethods-Figures.Rmd
ok

--- 2018-09-09 inst/examples/201808-HistoricalMethods-Figures.Rmd
@@
 df.full <- df.combined.preprocessed %>% filter(!remove)
+df.full <- df.full %>% mutate(Catalogue = catalog)
 
@@
 # Data with years limited as well
+df.full.1911 <- df.full %>% filter(publication_year >= min.year & publication_year <= 1911)
 df.full <- df.full %>% filter(publication_year >= min.year & publication_year <= max.year)
@@
 # Change catalog name
-df.full$catalog <- gsub("Fennica", "FNB", df.full$catalog)
-df.full$catalog <- gsub("Kungliga", "SNB", df.full$catalog)
-df.full$catalog <- factor(df.full$catalog)
+df.full$Catalogue <- gsub("Fennica", "FNB", df.full$Catalogue)
+df.full$Catalogue <- gsub("Kungliga", "SNB", df.full$Catalogue)
+df.full$Catalogue <- factor(df.full$Catalogue)
 
@@
 df <- df0 %>% filter(publication_year >=1640 & publication_year <=1828) %>%
-              group_by(catalog, publication_decade) %>%
+              group_by(Catalogue, publication_decade) %>%
 	      summarise(n = length(unique(na.omit(publication_place))))
@@
 p <- ggplot(df, aes(x = publication_decade, y = n,
-       color = catalog, shape = catalog)) + 
+       color = Catalogue, shape = Catalogue)) + 
        geom_point(size = 4) + 
@@
        guides(linetype = "none") +
-       guides(shape = guide_legend(title = "Catalog", reverse = TRUE),
-              color = guide_legend(title = "Catalog", reverse = TRUE)) +              
+       guides(shape = guide_legend(title = "Catalogue", reverse = TRUE),
+              color = guide_legend(title = "Catalogue", reverse = TRUE)) +              
        #ggtitl("Unique publication places") +
@@
 df <- df0 %>% filter(publication_year >=1640 & publication_year <=1828) %>%
-        group_by(catalog, publication_decade) %>% tally()
+        group_by(Catalogue, publication_decade) %>% tally()
 
@@
 p <- ggplot(df, aes(x = publication_decade, y = n,
-                    shape = catalog,
-		    color = catalog)) + 
+                    shape = Catalogue,
+		    color = Catalogue)) + 
        geom_point(size = 4) + 
@@
        guides(
-         shape = guide_legend(title = "Catalog", reverse = TRUE),
-         color = guide_legend(title = "Catalog", reverse = TRUE)	 
+         shape = guide_legend(title = "Catalogue", reverse = TRUE),
+         color = guide_legend(title = "Catalogue", reverse = TRUE)	 
        ) +
@@
 pics <- list()
-for (catal in unique(df.full$catalog)) {
-
+for (catal in unique(df.full$Catalogue)) {
+
+  # NOTE: IN FNB we show longer period
   if (catal == "SNB") {
-    df00 <- df.full %>% filter(publication_year >= min.year & publication_year <= max.year)
+    df00 <- df.full # df.full.1911 %>% filter(publication_year >= min.year & publication_year <= max.year)
   } else if (catal == "FNB") {
-    df00 <- df.full %>% filter(publication_year >= min.year & publication_year <= 1900)
-  }
-
-  df2 <- subset(df00, catalog == catal) %>%
+    df00 <- df.full.1911 #%>% filter(publication_year >= min.year & publication_year <= 1900)
+  }
+
+  df2 <- subset(df00, Catalogue == catal) %>%
            group_by(publication_decade, gatherings) %>%
@@
 prow <- plot_grid(
-           pics[[1]] + theme(legend.position="none"),
-           pics[[2]] + theme(legend.position="none"),
+           pics[[1]] + theme(legend.position="none"), #+ ylim(c(0, 7)),
+           pics[[2]] + theme(legend.position="none"), #+ ylim(c(0, 7)),
            align = 'vh',
@@
 cols <- list(FNB = "blue", SNB = "darkred")
-df <- df.full %>% filter(publication_year >= 1640 &
-                         publication_year <= 1911) %>%
-              group_by(catalog, publication_year) %>%
+
+df <- df.full.1911 %>% 
+              group_by(Catalogue, publication_year) %>%
               summarize(title_length = median(title_length_wordcount),
@@
 brsy <- seq(0, round(max(na.omit(df$title_length)), -1), 10)
-for (catal in unique(df$catalog)) {
-  pics[[catal]] <- ggplot(subset(df, catalog == catal),
+for (catal in unique(df$Catalogue)) {
+  pics[[catal]] <- ggplot(subset(df, Catalogue == catal),
        aes(x = publication_year, y = title_length)) +
@@
 
-for (catalogue in na.omit(unique(df0$catalog))) {
-
-df <- df0 %>% filter(catalog == catalogue)%>%
+for (Catalogue in na.omit(unique(df0$Catalogue))) {
+
+df <- df0 %>% filter(Catalogue == Catalogue)%>%
         filter(publication_year >= 1640 & publication_year <= 1828)
@@
      if (varname == "n") {
-       p <- p + labs(subtitle = paste("Title count (", catalogue, ")", sep = ""), y = "Title count (%)")
+       p <- p + labs(subtitle = paste("Title count (", Catalogue, ")", sep = ""), y = "Title count (%)")
      }
      if (varname == "paper") {
-       p <- p + labs(subtitle = paste("Paper (", catalogue, ")", sep = ""), y = "Paper (%)")
+       p <- p + labs(subtitle = paste("Paper (", Catalogue, ")", sep = ""), y = "Paper (%)")
      }
      if (varname == "publishers") {
-       p <- p + labs(subtitle = paste("Publishers (", catalogue, ")", sep = ""), y = "Publishers (%)")
+       p <- p + labs(subtitle = paste("Publishers (", Catalogue, ")", sep = ""), y = "Publishers (%)")
      }     
@@
 
-  pics[[paste(catalogue, varname, sep = "-")]] <- p
+  pics[[paste(Catalogue, varname, sep = "-")]] <- p
 
@@
 # theme_set(theme_bw(20))
-df <- df0 %>% filter(catalog == "SNB")
+df <- df0 %>% filter(Catalogue == "SNB")
 
@@
   # Use timeinterval year intervals
-  dfsel <- dplyr::filter(df0, catalog == catal)
+  dfsel <- dplyr::filter(df0, Catalogue == catal)
 
   df <- df0
-  df <- dplyr::filter(df, catalog == catal)
+  df <- dplyr::filter(df, Catalogue == catal)
   df <- subset(df, publication_year >= minyear & publication_year <= maxyear)
@@
 df <- df %>%
-        filter(catalog == catal) %>%
+        filter(Catalogue == catal) %>%
 	filter(country == "Finland" | publication_place == "Vyborg") %>%
@@
         #filter(publication_place %in% top) %>%	
-        select(publication_decade, publication_place, publisher)
+        select(publication_decade, publication_place)
 df.fennica <- df
@@
 df <- df0
-catalogue <- "SNB"
+Catalogue <- "SNB"
 df <- df %>%
-        filter(catalog == catalogue) %>%
+        filter(Catalogue == Catalogue) %>%
         filter(publication_year >= 1640 & publication_year <= 1828) %>%
@@
         #filter(publication_place %in% top) %>%	
-        select(publication_decade, publication_place, publisher)
+        select(publication_decade, publication_place)
 df.kungliga <- df
@@
 # Order by total publishing activity
-npub$publication_place <- factor(npub$publication_place, levels = (npub %>% group_by(publication_place) %>% summarise(total = sum(n)) %>% arrange(desc(total)))$publication_place)
+npub$publication_place <- factor(npub$publication_place, levels = (npub %>%
+                            group_by(publication_place) %>%
+			    summarise(total = sum(n)) %>
+			    % arrange(desc(total)))$publication_place)
 npub <- npub %>% arrange(publication_place)
@@
        xlab("Decade") +
-       ylab("Publishers (n)") +
+       ylab("Title count (n)") +
        #scale_fill_stata() +
@@
        scale_x_continuous(breaks = brs, labels = insert_minor(brs, 2))
-       # ggtitle("Figure 8")
-       #ggtitl(paste("Publishers (", catal, ")", sep = ""))
 
@@
 library(dplyr)
-catalogue <- "FNB"
+Catalogue <- "FNB"
 place <- "Vaasa"
@@
 
-df <- df0 %>% filter(catalog == catalogue & publication_place == place) %>%	
+df <- df0 %>% filter(Catalogue == Catalogue & publication_place == place) %>%	
         filter(publication_year >= minyear & publication_year <= maxyear) %>%
@@
      # ggtitle("Figure 9")
-     #ggtitle(paste("Publications in Vaasa (", catalogue, ")", sep = ""))
+     #ggtitle(paste("Publications in Vaasa (", Catalogue, ")", sep = ""))
 
@@
 place <- "Turku"
-catalogue <- "FNB"
+Catalogue <- "FNB"
 df <- df0
 
-df <- df %>% filter(catalog == catalogue & publication_place == place) %>%
+df <- df %>% filter(Catalogue == Catalogue & publication_place == place) %>%
              filter(!is.na(publisher))
@@
       # ggtitle("Figure 10")      
-      #ggtitle(paste("Top publishers in ", place, " (", catalogue, ")", sep = ""))
-      #ggtitle(paste("Figure 10: ", place, " (", catalogue, ")", sep = ""))
+      #ggtitle(paste("Top publishers in ", place, " (", Catalogue, ")", sep = ""))
+      #ggtitle(paste("Figure 10: ", place, " (", Catalogue, ")", sep = ""))
 
@@
 df1 <- df0 %>% filter(publication_place %in% setdiff(cities, "Turku")) %>%
-      	      filter(catalog == cat) %>%
+      	      filter(Catalogue == cat) %>%
               filter(publication_decade %in% pop$publication_decade) %>%
@@
 df2 <- df0 %>% filter(publication_place %in% "Turku") %>%
-      	      filter(catalog == cat) %>%
+      	      filter(Catalogue == cat) %>%
               filter(publication_decade %in% pop$publication_decade) %>%
@@
 df1 <- df0 %>% filter(publication_place %in% setdiff(cities, "Turku")) %>%
-      	       filter(catalog == cat & gatherings == "8vo") %>%
+      	       filter(Catalogue == cat & gatherings == "8vo") %>%
 	       group_by(publication_decade, publication_place) %>%
@@
 df2 <- df0 %>% filter(publication_place %in% "Turku") %>%
-      	       filter(catalog == cat & gatherings == "8vo") %>%
+      	       filter(Catalogue == cat & gatherings == "8vo") %>%
 	       group_by(publication_decade, publication_place) %>%
@@
 df00 <- df.full %>% filter(publication_year >= 1640 & publication_year <= 1850)
-df1 <- df00 %>% filter((publication_place %in% setdiff(cities, "Turku") & catalog == "SNB") |
-                       (publication_place %in% "Turku" & catalog == "FNB")) 
+df1 <- df00 %>% filter((publication_place %in% setdiff(cities, "Turku") & Catalogue == "SNB") |
+                       (publication_place %in% "Turku" & Catalogue == "FNB")) 
 df1$publication_place[!df1$publication_place == "Stockholm"] <- "Other"
@@
 cnt <- 0
-for (catalogue in c("FNB", "SNB")) {
-
-  df <- df0 %>% filter(catalog == catalogue) %>%
-        filter(publication_year >= 1600 & publication_year <= 1828)
+for (Catalogue in c("FNB", "SNB")) {
+
+  df <- df0 %>% filter(Catalogue == Catalogue)
 
@@
 
-      p <- p + labs(subtitle = paste(myplace, "/", catalogue)) +                 
+      p <- p + labs(subtitle = paste(myplace, "/", Catalogue)) +                 
       #scale_fill_stata() +
@@
       guides(fill = guide_legend(title = "")) 
-    pics[[paste(catalogue, myplace, sep = "-")]] <- p
+    pics[[paste(Catalogue, myplace, sep = "-")]] <- p
   }
@@
 ```{r Figure_16, echo=FALSE, message=FALSE, warning=FALSE, fig.show="hold"}
-catalogue <- "FNB"
-df <- filter(df0, catalog == "FNB") %>%
+Catalogue <- "FNB"
+df <- filter(df0, Catalogue == "FNB") %>%
   filter(publication_year >= 1640 & publication_year <= 1828) %>%
@@
        # ggtitle("Figure 16")
-       #ggtitle(paste("Topic richness (", catalogue, ")", sep = ""))
+       #ggtitle(paste("Topic richness (", Catalogue, ")", sep = ""))
 
@@
 sel <- c("hautajaiset", "häät", "juhlamenot")
-catalogue <- "FNB"
+Catalogue <- "FNB"
 df <- df0
@@
 
-# Selected catalogue with selected topics
-df <- df %>% filter(catalog == catalogue & hit)
+# Selected Catalogue with selected topics
+df <- df %>% filter(Catalogue == Catalogue & hit)
   lang <- paste("language.", langs, sep = "")
@@
        # ggtitle("Figure 17")
-       #ggtitle(paste("Temporary sermons (", catalogue, ")", sep = ""))
+       #ggtitle(paste("Temporary sermons (", Catalogue, ")", sep = ""))
   print(p)
@@
 sel <- c("virret","arkkiveisut","hartauskirjat","katekismukset","rukouspäivät","saarnat","aapiset","rukoukset","rukous","hengelliset laulut","hartauspuheet","virsikirjat")
-catalogue <- "FNB"
-
-  # Selected catalogue with selected years
-  df <- filter(df0, catalog == catalogue &
+Catalogue <- "FNB"
+
+  # Selected Catalogue with selected years
+  df <- filter(df0, Catalogue == Catalogue &
      		    publication_year >= 1640 &
@@
   df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)  
-  df <- df %>% filter(catalog == catalogue & hit)
+  df <- df %>% filter(Catalogue == Catalogue & hit)
 
@@
        # ggtitle("Figure 18")       
-       # ggtitle(paste("Devotional literature (", catalogue, ")", sep = ""))
+       # ggtitle(paste("Devotional literature (", Catalogue, ")", sep = ""))
 

### 2018-09-10 inst/examples/analysis.R

@@ -42,6 +42,7 @@ knitr::knit("suvut.Rmd", encoding="UTF-8")
 
 #library(rmarkdown)
 #knitr::knit("201808-HistoricalMethods-Figures.Rmd", encoding="UTF-8")
+#rmarkdown::render("201808-HistoricalMethods-Figures.Rmd", encoding="UTF-8")
 #rmarkdown::render("201808-HistoricalMethods-Supplement.Rmd", output_format = "pdf_document") 
 
 # -------------------

### 2018-09-11 inst/examples/201808-HistoricalMethods-Figures.Rmd
ok

@@
 names(city.colors) <- cities
+city.colors[["Other"]] <- "#696969"
 
@@
 names(lang.colors) <- languages
+lang.colors[["Other"]] <- "#696969"
+#lang.colors[["Hebrew"]] <- "#55752f"
+#lang.colors[["Swedish"]] <- "#c10534"
 
@@
 
-# Data with years limited as well
-df.full.1911 <- df.full %>% filter(publication_year >= min.year & publication_year <= 1911)
-df.full <- df.full %>% filter(publication_year >= min.year & publication_year <= max.year)
-
 # Fix author names
@@
 
-df0 <- df.full
+# Data with years limited as well
+df.full.1911 <- df.full %>% filter(publication_year >= min.year & publication_year <= 1911)
+df0 <- df.full <- df.full %>% filter(publication_year >= min.year & publication_year <= max.year)
 cols <- list(FNB = "blue", SNB = "darkred")
@@
 library(ggplot2)
-#theme_set(theme_bw(20))
-df <- df0 %>% filter(publication_year >=1640 & publication_year <=1828) %>%
-        group_by(Catalogue, publication_decade) %>% tally()
+df <- df0 %>% group_by(Catalogue, publication_decade) %>% tally()
 
@@
        xlab("Decade") +
-       #scale_color_manual(values = c("blue", "darkgreen")) +
        scale_x_continuous(breaks = brs, labels = insert_minor(brs, 2)) +
@@
        ) +
-       #ggtitl("Title count") +
-       # ggtitle("Figure 2") +              
        scale_color_stata()
@@
            group_by(publication_decade, gatherings) %>%
-	   summarize(paper = sum(paper, na.rm = TRUE)/1e6, n = n())
+	   summarize(paper = sum(paper, na.rm = TRUE), n = n())
   # Million sheets
@@
   p <- p + xlab("Decade")
-  p <- p + ylab("Paper (million sheets)")
-  # p <- p + ylim(c(0, max(na.omit(df00$paper))))
+  p <- p + ylab("Paper (sheets)")
 
@@
 	   labels = insert_minor(brs, 5, start = ifelse(catal == "FNB", 1500, 1550))) + 
-         scale_y_continuous(breaks = seq(0, 6.8, 1), limits = c(0, 6.8))
+         scale_y_continuous(breaks = seq(0, 6.8, 1)*1e6, limits = c(0, 6.8)*1e6,
+	                    label = scientific_10)
          #scale_y_continuous(breaks = seq(0, max(df00$paper, na.rm = TRUE), 1000))
@@
 top <- c(top, "Other")
-df <- df %>%	
-        #filter(publication_place %in% top) %>%	
-        select(publication_decade, publication_place)
+df <- df %>% select(publication_decade, publication_place)
 df.fennica <- df
 
-npub <- unique(df) %>% group_by(publication_decade, publication_place) %>% tally()
+npub <- df %>% group_by(publication_decade, publication_place) %>% tally()
 npub$publication_place <- factor(npub$publication_place, levels = top)
@@
 
-npub <- unique(df) %>% group_by(publication_decade, publication_place) %>% tally()
+npub <- df %>% group_by(publication_decade, publication_place) %>% tally()
 npub$publication_place <- factor(npub$publication_place, levels = top)
@@
                             group_by(publication_place) %>%
-			    summarise(total = sum(n)) %>
-			    % arrange(desc(total)))$publication_place)
+			    summarise(total = sum(n)) %>%
+			    arrange(desc(total)))$publication_place)
 npub <- npub %>% arrange(publication_place)
@@
 npub <- npub[-rminds, ]
+
+npub$publication_place <- factor(npub$publication_place, levels = rev(c("Other", setdiff(npub$publication_place, "Other"))))
 
@@
 
-minyear <- 1640
-maxyear <- 1828
-
 # Take cities from SNB except Turku
@@
 dfm <- dfm %>% mutate(titles_per_capita = n/population)
+dfm$publication_place <- gsub("Linkoping", "Linköping", dfm$publication_place)
 
@@
        ylab("Title count per capita (n)") +
-       #scale_color_stata() +
-       #scale_color_manual(values = city.colors[as.character(levels(dfm$publication_place))]) +
        scale_color_manual(values = city.colors[match(unique(dfm$publication_place), names(city.colors))]) +              
-       #scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5)) +
        scale_x_continuous(breaks = brs, labels = labs) +
-       #ggtitle("Title count per capita") +
-       # ggtitle("Figure 11") +       
        guides(shape = guide_legend(title = "Place")) +
@@
 print(p)
-
-#kable(dfm)
 ```
@@
 ```{r Figure_12, echo=FALSE, message=FALSE, warning=FALSE}
-minyear <- 1640
-maxyear <- 1828
-
 # Take cities from SNB except Turku
@@
 labs <- brs; labs[!brs %in% df$publication_decade] <- ""
-#df$publication_place <- factor(df$publication_place, levels = levels(df0$publication_place))
 
@@
        ylab("Title count (n)") +
-       # ggtitle("Figure 12") +              
        scale_x_continuous(breaks = brs, labels = labs) +
@@
        ylab("Title length (words)") +
-       #ggtitle("Average title length") +
-       # ggtitle("Figure 14") +                            
-       #scale_fill_stata() +
        scale_fill_manual(values = city.colors[as.character(levels(df$publication_place))]) +
@@
   dfss <- subset(dff, publication_place == myplace)
-  brs <- seq(min(dfss$publication_decade), max(dfss$publication_decade), 10)
+  brs <- seq(min(df.full$publication_decade), max(df.full$publication_decade), 10)
 
@@
       p <- p + labs(subtitle = paste(myplace, "/", Catalogue)) +                 
-      #scale_fill_stata() +
       scale_fill_manual(values = lang.colors[as.character(levels(dfss$language))]) +      
-      scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5)) +  
-      #scale_fill_brewer(palette="Greys") +       
+      scale_x_continuous(breaks = brs,
+                         labels = insert_minor(brs, 5),
+                         limits = c(min.year, max.year)) +  
       guides(fill = guide_legend(title = "")) 
@@
 }
-
-#grid.arrange(pics[[1]], pics[[8]], pics[[9]], pics[[10]], top = "Figure 15", layout_matrix = matrix(c(1,2,3,4), nrow = 2, byrow=TRUE))
-#grid.arrange(pics[[1]], pics[[8]], pics[[9]], pics[[10]], layout_matrix = matrix(c(1,2,3,4), nrow = 2, byrow=TRUE))
 
@@
 df <- filter(df0, Catalogue == "FNB") %>%
-  filter(publication_year >= 1640 & publication_year <= 1828) %>%
   select(publication_decade, language, subject_topic)
@@
 brs <- seq(min(decade(df$publication_decade)), max(decade(df$publication_decade)), 10)
-
 p <- ggplot(df, aes(x = publication_decade, y = n, shape = language)) +
@@
        scale_fill_brewer(palette="Greys") +
-       #scale_color_manual(values = city.colors[as.character(levels(df$publication_place))]) +
-       # geom_smooth(color = "black") +
        guides(shape = guide_legend(title = "Language"),
               color = guide_legend(title = "Language")) +
-       #scale_color_stata() +
        scale_color_manual(values = lang.colors[as.character(levels(df$language))]) +             
-       # scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5)) +
-       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 2, start = century(min(brs)) + 40)) +                 
-       ylab("Subject topics (n)") +
+       scale_x_continuous(breaks = brs,
+                          labels = insert_minor(brs, 2,
+			  start = century(min(brs)) + 40)) +                 
+       ylab("Topical terms (n)") +
        xlab("Decade")
-       # ggtitle("Figure 16")
-       #ggtitle(paste("Topic richness (", Catalogue, ")", sep = ""))
 
@@
               color = guide_legend(title = "Language")) +
-       #scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5)) +
-       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5, start = 1600)) +
+       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 2, start = 1600)) +
        scale_y_continuous(label = scientific_10) + 
-       #scale_color_stata() +
        scale_color_manual(values = lang.colors[as.character(levels(df$language))]) 
-       # ggtitle("Figure 17")
-       #ggtitle(paste("Temporary sermons (", Catalogue, ")", sep = ""))
   print(p)
@@
        guides(shape = guide_legend(title = "Language"), color = guide_legend(title = "Language")) +
-       #scale_color_stata() +
-       #scale_color_manual(values = lang.colors[as.character(levels(df$language))]) +
        scale_color_manual(values = lang.colors[match(unique(df$language), names(lang.colors))]) +              
-       # scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5)) +
-       #scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5, start = century(min(brs)) + 50)) +
        scale_x_continuous(breaks = brs, labels = insert_minor(brs, 2)) +       
        scale_y_continuous(label = scientific_10)
-       # ggtitle("Figure 18")       
-       # ggtitle(paste("Devotional literature (", Catalogue, ")", sep = ""))
-
-#print(p + theme_light(scalingfactor))
+
 print(p)

### 2018-09-11 inst/examples/201808-HistoricalMethods-Supplement.Rmd
ok

@@
 
-fen <- subset(df0, catalog == "FNB")
-kun <- subset(df0, catalog == "SNB")
+fen <- subset(df0, Catalogue == "FNB")
+kun <- subset(df0, Catalogue == "SNB")
 cats <- list(FNB = fen, SNB = kun)
@@
 
-for (cat in unique(df0$catalog)) {
+for (cat in unique(df0$Catalogue)) {
 
-  dd <- subset(df0, catalog == cat)[, selected.fields]
+  dd <- subset(df0, Catalogue == cat)[, selected.fields]
 
@@
 
- * FNB: ```r nrow(subset(df0, catalog == "FNB"))```
- * SNB: ```r nrow(subset(df0, catalog == "SNB"))```
+ * FNB: ```r nrow(subset(df0, Catalogue == "FNB"))```
+ * SNB: ```r nrow(subset(df0, Catalogue == "SNB"))```
 
@@
 df$field <- df[[field]]
-df <- df %>% group_by(catalog) %>%
+df <- df %>% group_by(Catalogue) %>%
               summarise(Unique = length(unique(field)),
 	                All = sum(!is.na(field)))
-colnames(df) <- gsub("catalog", "Catalogue", colnames(df))
+colnames(df) <- gsub("Catalogue", "Catalogue", colnames(df))
 knitr::kable(df, digits = 1, format = "markdown")
@@
 
-In FNB, we have identified ```r sum(subset(df0, catalog == "FNB")$multilingual)``` multilingual documents in the investigated time period.
+In FNB, we have identified ```r sum(subset(df0, Catalogue == "FNB")$multilingual)``` multilingual documents in the investigated time period.
 In SNB, the multilingual documents have not been analyzed yet.
@@
 df$field <- df[[field]]
-df <- df %>% group_by(catalog) %>%
+df <- df %>% group_by(Catalogue) %>%
               summarise(Unique = length(unique(field)),
 	                All = sum(!is.na(field)))
-colnames(df) <- gsub("catalog", "Catalogue", colnames(df))
+colnames(df) <- gsub("Catalogue", "Catalogue", colnames(df))
 colnames(df) <- gsub("language", "Language", colnames(df))
@@
 
-Proportion (%) of gatherings in the FNB and SNB catalogues. The gatherings with a prevalence less than 1% in both catalogues have been combined into the "Other" category.
+Proportion (%) of gatherings in the FNB and SNB Catalogues. The gatherings with a prevalence less than 1% in both Catalogues have been combined into the "Other" category.
 
 ```{r gatherings, echo=FALSE, message=FALSE, warning=FALSE}
-df <- df0 %>% group_by(catalog, gatherings) %>%
+df <- df0 %>% group_by(Catalogue, gatherings) %>%
               summarise(n = n())
-df <- spread(df, catalog, n, fill = 0)
+df <- spread(df, Catalogue, n, fill = 0)
 colnames(df) <- c("Gatherings", "FNB", "SNB")
@@
        scale_fill_manual(values = unname(cols)) +       
-       facet_grid(catalog ~ gatherings) +
+       facet_grid(Catalogue ~ gatherings) +
        guides(fill = "none") + 
@@
 
-df <- df %>% group_by(catalog) %>%
+df <- df %>% group_by(Catalogue) %>%
               summarise(Unique = length(unique(field)),
 	                All = sum(!is.na(field)))
-colnames(df) <- gsub("catalog", "Catalogue", colnames(df))
+colnames(df) <- gsub("Catalogue", "Catalogue", colnames(df))
 knitr::kable(df, format = "markdown")
@@
 df <- df0
-names(df) <- gsub("catalog", "Catalog", names(df))
-df <- df %>% group_by(Catalog, publication_decade) %>% tally()
-p <- ggplot(df, aes(x = publication_decade, y = n, fill = Catalog)) +
+names(df) <- gsub("Catalogue", "Catalogue", names(df))
+df <- df %>% group_by(Catalogue, publication_decade) %>% tally()
+p <- ggplot(df, aes(x = publication_decade, y = n, fill = Catalogue)) +
        geom_bar(color = "black",
@@
 
-In FNB, the data includes ```r  length(unique(subset(df0, catalog == "FNB")$publisher))``` unique publishers, and ```r  round(100 * mean(!is.na(subset(df0, catalog == "FNB")$publisher), na.rm = TRUE))```% of the documents have publisher information.
-We have not analyzed publishers in SNB, where the availability of harmonized publisher information is currently low (```r  round(100 * mean(!is.na(subset(df0, catalog == "SNB")$publisher), na.rm = TRUE))```%).
+In FNB, the data includes ```r  length(unique(subset(df0, Catalogue == "FNB")$publisher))``` unique publishers, and ```r  round(100 * mean(!is.na(subset(df0, Catalogue == "FNB")$publisher), na.rm = TRUE))```% of the documents have publisher information.
+We have not analyzed publishers in SNB, where the availability of harmonized publisher information is currently low (```r  round(100 * mean(!is.na(subset(df0, Catalogue == "SNB")$publisher), na.rm = TRUE))```%).
 
@@
 We use here the term "Topic" for the "Topical term" MARC field 650a for brevity.
-In FNB, the data includes ```r  length(unique(subset(df0, catalog == "FNB")$Topic))``` unique topics.
-```r  round(100 * mean(!is.na(subset(df0, catalog == "FNB")$Topic), na.rm = TRUE))```% of the documents have topic information.
-We have not analyzed topics in SNB, where the availability of harmonized topics is currently low (```r  round(100 * mean(!is.na(subset(df0, catalog == "SNB")$Topic), na.rm = TRUE))```%).
+In FNB, the data includes ```r  length(unique(subset(df0, Catalogue == "FNB")$Topic))``` unique topics.
+```r  round(100 * mean(!is.na(subset(df0, Catalogue == "FNB")$Topic), na.rm = TRUE))```% of the documents have topic information.
+We have not analyzed topics in SNB, where the availability of harmonized topics is currently low (```r  round(100 * mean(!is.na(subset(df0, Catalogue == "SNB")$Topic), na.rm = TRUE))```%).
 

### 2018-09-11 inst/examples/201808-HistoricalMethods-Supplement.Rmd
ok

@@
   complete <- round(100 * colMeans(!is.na(dd)), 1)
+
+  # complete <- gsub("^100$", "100.0", complete)
+  # complete <- 100 * colMeans(!is.na(dd))
   unique <- apply(dd, 2, function (x) {length(unique(x))})
@@
 # Add Footnote
+w[,2] <- as.character(w[,2])
+w[,3] <- as.character(w[,3])
 w[which(w$Field == "Topic"), "SNB (%)"] <- paste0(as.character(w[which(w$Field == "Topic"), "SNB (%)"]), "*")
 w[which(w$Field == "Publisher"), "SNB (%)"] <- paste0(as.character(w[which(w$Field == "Publisher"), "SNB (%)"]), "*")
-
+w[,3] <- gsub("100", "100.0", w[,3])
+w[,3] <- gsub("^94$", "94.0", w[,3])
+w[,2] <- gsub("100", "100.0", w[,2])
+w[,2] <- gsub("^98$", "98.0", w[,2])
+w[,2] <- gsub("^93$", "98.0", w[,2])
 kable <- knitr::kable
-knitr::kable(w, format = "markdown")
+knitr::kable(w, format = "markdown", digits = 1)
 

### 2018-09-12 inst/examples/201808-HistoricalMethods-Figures.Rmd
ok

@@
 #lang.colors[["Swedish"]] <- "#c10534"
-
 knitr::opts_chunk$set(echo = FALSE)
@@
   if (catal == "SNB") {
-    df00 <- df.full # df.full.1911 %>% filter(publication_year >= min.year & publication_year <= max.year)
+    df00 <- df.full
   } else if (catal == "FNB") {
-    df00 <- df.full.1911 #%>% filter(publication_year >= min.year & publication_year <= 1900)
+    df00 <- df.full.1911
   }
@@
 	   summarize(paper = sum(paper, na.rm = TRUE), n = n())
-  # Million sheets
-
-  #df2 <- filter(df2, gatherings %in% setdiff(names(which(table(df2$gatherings) >= 20)), "NA"))
   df2 <- filter(df2, gatherings %in% common.gatherings)  
@@
 	                    label = scientific_10)
-         #scale_y_continuous(breaks = seq(0, max(df00$paper, na.rm = TRUE), 1000))
-	                    # label = scientific_10)
 
@@
 p <- plot_grid( prow, legend_b, ncol = 2, rel_widths = c(1, .1))
-#title <- ggdraw() + draw_label("Figure 3", fontface='bold')
 ```
@@
 ```{r Figure_3, echo=FALSE, message=FALSE, warning=FALSE, fig.width=27, fig.height=10}
-#print(plot_grid(title, p, ncol=2, rel_heights=c(0.1, 1), hjust = 0))
-#print(p + theme_blank(30))
 print(p)
@@
        geom_smooth(color = cols[[catal]], fill = cols[[catal]]) +
-       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5, start = century(min(brs)) + 50)) +
-       scale_y_continuous(breaks = brsy, labels = insert_minor(brsy, 2), limits = c(0, max(na.omit(df$title_length)))) +
+       scale_x_continuous(breaks = brs,
+         labels = insert_minor(brs, 5, start = century(min(brs)) + 50)) +
+       scale_y_continuous(breaks = brsy,
+         labels = insert_minor(brsy, 2),
+	 limits = c(0, max(na.omit(df$title_length)))) +
        xlab("Decade") +
@@
 p <- plot_grid( prow, legend_b, ncol = 2, rel_widths = c(.95, .08))
-# title <- ggdraw() + draw_label("Figure 4", fontface='bold')
-# p <- plot_grid(title, p, ncol=1, rel_heights=c(0.1, 1)) # rel_heights values control title margins
 print(p)
@@
 rm(legend_b)
-pics <- list()
-
-for (Catalogue in na.omit(unique(df0$Catalogue))) {
-
-df <- df0 %>% filter(Catalogue == Catalogue)%>%
-        filter(publication_year >= 1640 & publication_year <= 1828)
-places <- c("Stockholm", "Uppsala", "Lund", "Greifswald", "Tartu", "Turku")
-df$publication_place[!df$publication_place %in% places] <- "Other"
-df <- subset(df, !is.na(df$publication_place))
-#df$publication_place <- factor(df$publication_place, levels = c(places, "Other"))
 library(reshape2)
@@
 library(tidyr)
+
+pics <- list()
+places <- c("Stockholm", "Uppsala", "Lund", "Greifswald", "Tartu", "Turku")
+
+for (cat in na.omit(unique(df0$Catalogue))) {
+
+  df <- df0 %>% filter(Catalogue == cat)
+  df <- subset(df, !is.na(df$publication_place))  
+  df$publication_place[!df$publication_place %in% places] <- "Other"  
+  df$publication_place <- factor(df$publication_place,
+    levels = rev(c(setdiff(unique(df$publication_place), "Other"), "Other")))
 
@@
 
-  # theme_set(theme_bw(20))
+    # Theme_set(theme_bw(20))
     p <- ggplot(dff, aes(x = publication_decade, y = f)) +
@@
        xlab("Decade")
-     #scale_fill_stata() 
+
     if (varname == "n") {
-       p <- p + labs(subtitle = paste("Title count (", Catalogue, ")", sep = ""), y = "Title count (%)")
+       p <- p + labs(subtitle = paste("Title count (", cat, ")", sep = ""), y = "Title count (%)")
      }
      if (varname == "paper") {
-       p <- p + labs(subtitle = paste("Paper (", Catalogue, ")", sep = ""), y = "Paper (%)")
+       p <- p + labs(subtitle = paste("Paper (", cat, ")", sep = ""), y = "Paper (%)")
      }
      if (varname == "publishers") {
-       p <- p + labs(subtitle = paste("Publishers (", Catalogue, ")", sep = ""), y = "Publishers (%)")
+       p <- p + labs(subtitle = paste("Publishers (", cat, ")", sep = ""), y = "Publishers (%)")
      }     
@@
 
-  pics[[paste(Catalogue, varname, sep = "-")]] <- p
+  pics[[paste(cat, varname, sep = "-")]] <- p
 
@@
 library(gridExtra)
-#pics[[1]] <- pics[[1]] + # ggtitle("Figure 5") 
-#grid.arrange(pics[[1]], pics[[2]], pics[[4]], pics[[5]], top = "Figure 5", layout_matrix = matrix(c(1,2,3,4), nrow = 2, byrow=TRUE))
-#grid.arrange(pics[[1]], pics[[2]], pics[[4]], pics[[5]], layout_matrix = matrix(c(1,2,3,4), nrow = 2, byrow=TRUE))
 
@@
 ```{r Figure_5, echo=FALSE, message=FALSE, warning=FALSE, fig.width=27, fig.height=14}
+theme_set(theme_bw(20))
 print(p2)
@@
 v <- seq(1500, 1800, 100)
-# theme_set(theme_bw(20))
 df <- df0 %>% filter(Catalogue == "SNB")
@@
        geom_bar(stat = "identity", color = "black", position = "dodge") +
-       #scale_x_discrete(labels = c("1757-1765", "1766-1774", "1775-1783")) +
-       #scale_fill_manual(values = c("darkgreen", "darkgray"))
-       #scale_fill_brewer(palette="Greys") +
        scale_fill_stata() +
-       #scale_fill_manual(values = city.colors[as.character(levels(df$publication_place))]) + 
        guides(fill = guide_legend(title = "Period")) +
        ylab("Paper per title (sheets)") + xlab("")
-       # ggtitle("Figure 6") 
-       #ggtitl("Average paper consumption per title")
 
@@
 ```{r Figure_7, echo=FALSE, message=FALSE, warning=FALSE}
-
 minyear <- 1700
@@
   cols <- c("white", "lightgray", "darkgray")
-  #cols <- c("white", "Purple", "yellow", "orange", "darkgray", "red")
 
@@
 
-  #brs <- seq(min(df$publication_decade), max(df$publication_decade), 5)
   brs <- seq(min(dfm$date), max(dfm$date), 10)
@@
 
-  #p <- p + # ggtitle("Figure 7")   
-  #p <- p + #ggtitl(paste("Title count (", catal, " ", minyear, "-", maxyear, ")", sep = ""))
-  print(p)
-
+  print(p)
 ```
@@
 library(bibliographica)
-
 df <- df0
@@
         filter(Catalogue == catal) %>%
-	filter(country == "Finland" | publication_place == "Vyborg") %>%
-        filter(publication_year >= 1640 & publication_year <= 1828)
+	filter(country == "Finland" | publication_place == "Vyborg")
 
@@
 df$publication_place[!df$publication_place %in% top] <- "Other"
-top <- c(top, "Other")
+top <- c(rev(top), "Other")
 df <- df %>% select(publication_decade, publication_place)
@@
 df <- df0
-Catalogue <- "SNB"
+cat <- "SNB"
 df <- df %>%
-        filter(Catalogue == Catalogue) %>%
-        filter(publication_year >= 1640 & publication_year <= 1828) %>%
+        filter(Catalogue == cat) %>%
         filter(country == "Sweden" | publication_place %in% c("Greifswald", "Tartu"))
@@
 df <- df %>%	
-        #filter(publication_place %in% top) %>%	
         select(publication_decade, publication_place)
@@
 npub <- npub %>% arrange(publication_place)
-npub$publication_place <- factor(npub$publication_place, levels = rev(unique(npub$publication_place)))
+npub$publication_place <- factor(npub$publication_place,
+         levels = rev(unique(npub$publication_place)))
 
@@
 for (dec in npub$publication_decade) {
-  inds <- which(npub$publication_decade == dec & npub$publication_place == "Other")
+  inds <- which(npub$publication_decade == dec &
+            npub$publication_place == "Other")
   # Combine the counts for the other place
@@
 
-npub$publication_place <- factor(npub$publication_place, levels = rev(c("Other", setdiff(npub$publication_place, "Other"))))
-
-#theme_set(theme_bw(20))
+npub$publication_place <- factor(npub$publication_place,
+  levels = c("Other", setdiff(npub$publication_place, "Other")))
+
 brs <- seq(min(npub$publication_decade), max(npub$publication_decade), 10)  
@@
        ylab("Title count (n)") +
-       #scale_fill_stata() +
        scale_fill_manual(values = city.colors[as.character(levels(npub$publication_place))]) +        
@@
 library(dplyr)
-Catalogue <- "FNB"
+cat <- "FNB"
 place <- "Vaasa"
@@
 
-df <- df0 %>% filter(Catalogue == Catalogue & publication_place == place) %>%	
+df <- df0 %>% filter(Catalogue == cat & publication_place == place) %>%	
         filter(publication_year >= minyear & publication_year <= maxyear) %>%
@@
 missing.years <- setdiff(1750:1828, df$publication_year)
-df <- rbind(df, data.frame(publication_year = missing.years, n = rep(0, length(missing.years))))
+df <- rbind(df, data.frame(publication_year = missing.years,
+  n = rep(0, length(missing.years))))
 df <- df %>% arrange(publication_year)
@@
 p <- ggplot(df, aes(x = publication_year, y = n)) +
-     #geom_bar(stat = "identity") +
      geom_point() +
      geom_line(size = 1) +     
-     scale_x_continuous(breaks = brs, labels = insert_minor(brs, 10, start = 1770)) +
+     scale_x_continuous(breaks = brs,
+       labels = insert_minor(brs, 10, start = 1770)) +
      xlab("Year") +
      ylab("Title count (n)")
-     # ggtitle("Figure 9")
-     #ggtitle(paste("Publications in Vaasa (", Catalogue, ")", sep = ""))
 
@@
 place <- "Turku"
-Catalogue <- "FNB"
+cat <- "FNB"
 df <- df0
 
-df <- df %>% filter(Catalogue == Catalogue & publication_place == place) %>%
+df <- df %>% filter(Catalogue == cat & publication_place == place) %>%
              filter(!is.na(publisher))
@@
 df <- df %>%	
-  filter(publication_year >= 1640 & publication_year <= 1828) %>%
         select(publication_decade, publication_year, publisher, paper)
@@
 # Title count per decade & publisher	
-npub <- df %>% group_by(publication_decade, publisher) %>% tally() %>% arrange(n)
+npub <- df %>% group_by(publication_decade, publisher) %>%
+               tally() %>%
+	       arrange(n)
 
 # Title count per year & publisher	
-npub0 <- df %>% group_by(publication_year, publisher) %>% tally() %>% arrange(n)
+npub0 <- df %>% group_by(publication_year, publisher) %>%
+                tally() %>%
+		arrange(n)
 
@@
                         arrange(year))$publisher)
-#ord <- ord[c(1:7, 9, 8, 10:11)]	
 npub$publisher <- factor(npub$publisher, levels = c("Other", setdiff(ord, "Other")))
@@
 # TITLE COUNT
-#theme_set(theme_bw(20))
 brs <- seq(min(df$publication_decade), max(df$publication_decade), 10)
@@
       guides(size = guide_legend(title = "Title count (n)"))
-      # ggtitle("Figure 10")      
-      #ggtitle(paste("Top publishers in ", place, " (", Catalogue, ")", sep = ""))
-      #ggtitle(paste("Figure 10: ", place, " (", Catalogue, ")", sep = ""))
 
@@
        scale_y_continuous(label = scientific_10) +
-       # ggtitle("Figure 13") +
        scale_color_manual(values = city.colors[match(unique(df$publication_place), names(city.colors))]) +       
        guides(shape = guide_legend(title = "Place"), color = guide_legend(title = "Place")) 
-       #scale_color_stata()
 print(p)
@@
 pics <- list()
-#theme_set(theme_bw(20))
 myplaces <- c("Turku", "Greifswald", "Stockholm", "Uppsala", "Lund")
 cnt <- 0
-for (Catalogue in c("FNB", "SNB")) {
-
-  df <- df0 %>% filter(Catalogue == Catalogue)
+for (cat in c("FNB", "SNB")) {
+
+  df <- df0 %>% filter(Catalogue == cat)
 
@@
   otherlang <- otherlang[otherlang!="language.Multiple languages"]
-
   df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
@@
   dff[, -c(1,2)] <- 100 * t(apply(dff[, -c(1,2)], 1, function (x) {x/sum(x)}))
-
   dff <- melt(dff, id = c("publication_place", "publication_decade"))
   colnames(dff) <- c("publication_place", "publication_decade", "language", "f")
+  dff$language <- factor(dff$language, levels = c("Other", setdiff(levels(dff$language), "Other")))
 
@@
     dfss <- subset(dff, publication_place == myplace)
-  brs <- seq(min(df.full$publication_decade), max(df.full$publication_decade), 10)
+    brs <- seq(min(df.full$publication_decade),
+               max(df.full$publication_decade), 10)
 
@@
 
-      p <- p + labs(subtitle = paste(myplace, "/", Catalogue)) +                 
+      p <- p + labs(subtitle = paste(myplace, "/", cat)) +                 
       scale_fill_manual(values = lang.colors[as.character(levels(dfss$language))]) +      
@@
       guides(fill = guide_legend(title = "")) 
-    pics[[paste(Catalogue, myplace, sep = "-")]] <- p
+      pics[[paste(cat, myplace, sep = "-")]] <- p
   }
@@
            align = 'vh',
-           # labels = c("A", "B", "", ""),
-	   # label_size = 25,	   
            hjust = -1,
@@
 ```{r Figure_16, echo=FALSE, message=FALSE, warning=FALSE, fig.show="hold"}
-Catalogue <- "FNB"
-df <- filter(df0, Catalogue == "FNB") %>%
+cat <- "FNB"
+df <- filter(df0, Catalogue == cat) %>%
   select(publication_decade, language, subject_topic)
@@
 sel <- c("hautajaiset", "häät", "juhlamenot")
-Catalogue <- "FNB"
+Catalogue <- NULL
+cat <- "FNB"
 df <- df0
@@
 # Selected Catalogue with selected topics
-df <- df %>% filter(Catalogue == Catalogue & hit)
+df <- df %>% filter(Catalogue == cat & hit)
   lang <- paste("language.", langs, sep = "")
@@
 sel <- c("virret","arkkiveisut","hartauskirjat","katekismukset","rukouspäivät","saarnat","aapiset","rukoukset","rukous","hengelliset laulut","hartauspuheet","virsikirjat")
-Catalogue <- "FNB"
+Catalogue <- NULL
+cat <- "FNB"
 
   # Selected Catalogue with selected years
-  df <- filter(df0, Catalogue == Catalogue &
-     		    publication_year >= 1640 &
-		    publication_year <= 1828)
+  df <- filter(df0, Catalogue == cat)
 
@@
   df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)  
-  df <- df %>% filter(Catalogue == Catalogue & hit)
+  df <- df %>% filter(Catalogue == cat & hit)
 
@@
 # PAPER CONSUMPTION
-#theme_set(theme_bw(20))
 brs <- seq(min(df$publication_decade), max(df$publication_decade), 10)
@@
        ylab("Paper (sheets)") +
-       guides(shape = guide_legend(title = "Language"), color = guide_legend(title = "Language")) +
-       scale_color_manual(values = lang.colors[match(unique(df$language), names(lang.colors))]) +              
+       guides(shape = guide_legend(title = "Language"),
+         color = guide_legend(title = "Language")) +
+       scale_color_manual(values = lang.colors[match(unique(df$language),
+         names(lang.colors))]) +              
        scale_x_continuous(breaks = brs, labels = insert_minor(brs, 2)) +       

### 2018-10-10 inst/examples/201808-HistoricalMethods-Figures.Rmd

@@
 # Take cities from SNB except Turku
-df00 <- df.full %>% filter(publication_year >= 1640 & publication_year <= 1850)
+df00 <- df.full.1911 %>% filter(publication_year >= 1640 & publication_year <= 1850)
 df1 <- df00 %>% filter((publication_place %in% setdiff(cities, "Turku") & Catalogue == "SNB") |

### 2018-10-10 inst/examples/summary.Rmd
ok

@@
 ```{r missing2, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=10, fig.height=15}
-dfs <- df %>% select(author, publication_place, country, publication_year, publication_year_from, publication_year_till, corporate, area, pagecount, gatherings, width, height, paper, publisher, self_published)
+dfs <- df %>% select(author, publication_place, publication_country, publication_year, publication_year_from, publication_year_till, corporate, area, pagecount, gatherings, width, height, paper, publisher, self_published)
 success <- as.data.frame(t(apply(dfs, 2, function (x) {sum(!is.na(gsub("^NA$", NA, as.character(x))))})))

### 2018-10-10 inst/examples/summary.Rmd
ok

@@
 real.success[["publication_place"]] <- success$publication_place/original.nonNA$publication_place
-real.success[["country"]] <- success$country/original.nonNA$publication_place
+real.success[["publication_country"]] <- success$publication_country/original.nonNA$publication_place
 real.success[["publication_year"]] <- success$publication_year/original.nonNA$publication_time

### 2018-12-11 inst/examples/201808-HistoricalMethods-Supplement.Rmd
Swedish gap analysis

@@
 ```{r languages_fen, echo=FALSE, message=FALSE, warning=FALSE}
+map <- bibliographica::map
 tab <- top(fen, field, 10, "data.frame", round = 1)

### 2018-12-11 inst/examples/swedish_gap.Rmd
Swedish gap analysis

---
title: "Gap in Swedish"
author: "Helsinki Computational History Group / Leo"
date: "`r date()`"
---

# Fennica summary

```{r init, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=10, fig.height=15}
library(stringr)
library(dplyr)
library(reshape2)
library(ggplot2)
ntop <- 20

# Read the preprocessed data
df <- readRDS("data/unified/polished/df.Rds")
```

```{r gap, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=10, fig.height=15}
theme_set(theme_bw(20))
dfs <- df %>% filter(language_primary == "Swedish") %>%
       	      group_by(publication_decade) %>%
              tally()
p <- ggplot(dfs, aes(x = publication_decade, y = n)) +
       #geom_point() +
       #geom_smooth() +
       geom_bar(stat = "identity") +
       labs(x = "Publication decade",
            y = "Title count (n)",
	    title = "Title count for Swedish publications (primary language)"
	    )
print(p)
```

### 2018-12-11 inst/examples/swedish_gap.Rmd
ok

@@
 
-```{r gap, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=10, fig.height=15}
+```{r gap, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=10, fig.height=5}
 theme_set(theme_bw(20))

### 2021-01-12 inst/examples/author.Rmd
Added many auxiliary files

---
title: "Author preprocessing summary"
author: "`r author`"
date: "`r Sys.Date()`"
output: markdown_document
---

## Authors

 * `r length(unique(df$author))` [unique authors](output.tables/author_accepted.csv) These final names capture all name variants from the custom [author synonyme table](https://github.com/COMHIS/fennica/blob/master/inst/extdata/ambiguous-authors.csv), and exclude known pseudonymes (see below). If multiple names for the same author are still observed on this list, they should be added on the [author synonyme table](https://github.com/COMHIS/fennica/blob/master/inst/extdata/ambiguous-authors.csv).
 * `r sum(!is.na(df$author))` documents have unambiguous author information (`r round(100*mean(!is.na(df$author_name)))`%). 
 * `r length(unique(subset(df.preprocessed, author_pseudonyme)$author))` [unique pseudonymes](output.tables/pseudonyme_accepted.csv) are recognized based on [custom pseudonyme lists](https://github.com/COMHIS/fennica/blob/master/inst/extdata/names/pseudonymes/custom_pseudonymes.csv).
 * `r length(readLines(paste0(this.folder, "/output.tables/author_discarded.csv")))-2` [discarded author names](output.tables/author_discarded.csv) This list should not include any real authors (if it does, please send a note to the admin). The stopword lists are considered when discarding names.
 * [Author name conversions](output.tables/author_conversion_nontrivial.csv) Non-trivial conversions from the original raw data to final names.

### Auxiliary files

 * [Author synonyme table](https://github.com/COMHIS/fennica/blob/master/inst/extdata/ambiguous-authors.csv)
 * [Stopwords for names](https://github.com/COMHIS/fennica/blob/master/inst/extdata/stopwords_for_names.csv)
 * [Stopwords for titles](https://github.com/COMHIS/fennica/blob/master/inst/extdata/stopwords_titles.csv)
 * [Custom pseudonyme lists](https://github.com/COMHIS/fennica/blob/master/inst/extdata/names/pseudonymes/custom_pseudonymes.csv)

Top-`r ntop` uniquely identified authors and their productivity (title count).

```{r summaryauthors, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5, out.width='430px', fig.show='hold'}
knitr::opts_chunk$set(fig.path = "figure_slides/", dev="CairoPNG")
p <- NULL
p <- top_plot(df, "author", ntop) +
     		  ggtitle(paste("Top authors")) +
		  ylab("Documents")
print(p)

dff = df %>%
      filter(is.na(author) & !is.na(author_name)) %>%
      select(author_name)
p <- top_plot(dff,  "author_name", ntop) + ggtitle("Top discarded authors")
print(p)
```

### Ambiguous authors

Authors with ambiguous living year information - can we spot here
cases where these are clearly known identical or distinct authors?
Should also add living year information from supporting sources later.

`r length(unique(subset(df, is.na(author_birth) | is.na(author_death))$author))` [authors with missing life years](output.tables/authors_missing_lifeyears.csv) (Life year info can be augmented [here](https://github.com/COMHIS/fennica/blob/master/inst/extdata/author_info.csv))

`r length(readLines(paste0(this.folder, "/output.tables/author_life_ambiguous.csv")))-1` [authors with ambiguous life years](output.tables/author_life_ambiguous.csv) Some of these might be synonymous and could be added to [author synonyme list](https://github.com/COMHIS/fennica/blob/master/inst/extdata/ambiguous-authors.csv) (the first term will be selected for the final data)

### Life span of uniquely identified top authors

Ordered by productivity (number of documents))

```{r, summaryauthorslife, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
a <- rev(rev(sort(table(df$author)))[1:ntop])
dfa <- df[, c("author", "author_birth", "author_death")]
dfa <- filter(dfa, !is.na(author) & (author %in% names(a)))
dfa <- dfa[!duplicated(dfa), ]
dfa <- dfa[match(names(a), dfa$author),]
dfa <- arrange(dfa, author_birth)
# Order authors by birth year
dfa$author <- factor(dfa$author, levels = dfa$author)
dfa$index <- 1:nrow(dfa)

p <- ggplot(dfa)
p <- p + geom_segment(aes(y = author, yend = author, x = author_birth, xend = author_death), size = 2) 
p <- p + theme(axis.text.y = element_text(size = 9))
p <- p + xlab("Author life span (year)") + ylab("")
print(p)
```

### Author age

`r sum(!is.na(df$author_age))` documents (`r round(100*mean(!is.na(df$author_age)))`%) have author age at the publication year. These have been calculated for documents where the publication year and author life years (birth and death) are available, and the document has been printed during the author's life time.

```{r author_age, fig.height=7, fig.width=25, echo=FALSE, message=FALSE, warning=FALSE}
theme_set(theme_bw(20))
dfs <- df %>% filter(!is.na(author_age)) %>%
     	 group_by(publication_decade) %>%
     	 summarize(age = mean(author_age)) %>%
     	 arrange(publication_decade)
p1 <- ggplot(dfs, aes(x = publication_decade, y = age)) +
       geom_bar(stat = "identity", position = "stack", color = "black") +
       xlab("Publication Decade") +
       ylab("Mean age (years)") +
       scale_fill_grey() +
       #guides(fill = guide_legend("Author")) +
       ggtitle("Average author age")

dfs <- df %>% filter(!is.na(author_age)) %>%
     	 group_by(publication_year) %>%
     	 summarize(age = mean(na.omit(author_age)), n = n()) %>%
     	 arrange(publication_year)
p2 <- ggplot(dfs, aes(x = publication_year, y = age, size = n)) +
       geom_point() +
       geom_smooth() +       
       xlab("Publication year") +
       ylab("Mean age (years)") +
       scale_fill_grey() +
       ggtitle("Author mean age")

dfs <- df %>% filter(!is.na(author_age))
p3 <- ggplot(dfs, aes(x = author_age)) +
       geom_histogram(binwidth = 10) +
       xlab("Age (years)") + ylab("Title count") +
       #ylab("") +
       #scale_fill_grey() +
       #guides(fill = guide_legend("Author")) +
       ggtitle("Author age on the publication year")

grid.arrange(p1, p2, p3, nrow = 1)
```

### Author productivity

Title count versus paper consumption (all authors):

```{r authortitlespapers, fig.height=8, fig.width=18, echo=FALSE, warning=FALSE}
res1 <- compare_title_paper(df, "author", plot.mode = "text")
res2 <- compare_title_paper(df, "author", plot.mode = "point")
grid.arrange(res2$plot, res1$plot, nrow = 1)
#kable(res1$table)
```

```{r summaryTop10authorstimeline, fig.height=8, fig.width=16, echo=FALSE}
theme_set(theme_bw(20))
top.authors <- names(top(df, field = "author", n = 3))
dfs <- df %>% filter(author %in% top.authors) %>%
     	 group_by(author, publication_decade) %>%
     	 tally() %>%
     	 arrange(publication_decade)
p <- ggplot(dfs, aes(x = publication_decade, y = n, fill = author)) +
       geom_bar(stat = "identity", position = "stack", color = "black") +
       xlab("Publication Decade") +
       ylab("Title Count") +
       scale_fill_grey() +
       guides(fill = guide_legend("Author")) +
       ggtitle("Title count timeline for the top authors")
print(p)
```

```{r topauth, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=13, fig.height=6}
df <- df.preprocessed
top.authors <- names(rev(sort(table(df.preprocessed$author))))[1:10]
df2 <- df %>% filter(author %in% top.authors) %>% group_by(publication_year, author) %>% summarize(paper = sum(paper, na.rm = TRUE), n = n())

p <- ggplot(df2, aes(x = publication_year, y = paper, group = author, color = author))
p <- p + geom_point()
p <- p + geom_line()
p <- p + ggtitle("Paper consumption per author")
p <- p + xlab("Year")
p <- p + scale_y_log10()
p <- p + ylab("Paper consumption")
print(p)

p <- ggplot(df2, aes(x = publication_year, y = n, group = author, color = author))
p <- p + geom_point()
p <- p + geom_line()
p <- p + ggtitle("Documents per author")
p <- p + xlab("Year")
p <- p + scale_y_log10()
p <- p + ylab("Documents (n)")
print(p)
```

### 2021-01-12 inst/examples/language.Rmd
Added many auxiliary files

---
title: "Language summaries"
author: "Leo Lahti"
date: "`r Sys.Date()`"
output: markdown_document
---

## Language

 * `r length(unique(unlist(strsplit(as.character(df$languages), ";"))))-1` [unique languages](output.tables/language_accepted.csv)
 * `r length(unique(df$language_primary))-1` [unique primary languages](output.tables/language_accepted.csv)  
 * `r sum(!df$multilingual, na.rm = TRUE)` single-language documents (`r round(100 * mean(!df$multilingual, na.omit = TRUE), 2)`%)
 * `r sum(df$multilingual, na.rm = TRUE)` multilingual documents (`r round(100 * mean(df$multilingual, na.omit = TRUE), 2)`%) 
 * [Conversions from raw to preprocessed language entries](output.tables/language_conversions.csv) 
 * `r sum(is.na(df$languages) | df$language_primary == "Undetermined")` documents (`r round(100*mean(is.na(df$languages) | df$language_primary == "Undetermined"), 2)`%) with [unrecognized language](output.tables/language_discarded.csv)

Language codes are from [MARC](http://www.loc.gov/marc/languages/language_code.html); new custom abbreviations can be added in [this table](https://github.com/COMHIS/fennica/blob/master/inst/extdata/language_abbreviations.csv).

Title count per language (including multi-language documents; note the log10 scale):

```{r summarylang, echo=FALSE, message=FALSE, warning=FALSE, fig.width=7, fig.height=5}
top_plot(df, "languages", ntop = ntop, log10 = TRUE) 
```

### Top languages

Number of documents assigned with each language (top-10). For a complete list,
see [accepted languages](output.tables/language_accepted.csv).

```{r summarylang2, echo=FALSE, results='asis'}
x <- top(df, "languages")
tab <- cbind(names(x), unname(x), round(100 * unname(x/nrow(df)), 1))
colnames(tab) <- c("Language", "Documents (n)", "Fraction (%)")
kable(head(tab, 10))
```

### 2021-01-12 inst/examples/overview.Rmd
Added many auxiliary files

---
title: "Preprocessing overview"
author: "`r author`"
date: "`r Sys.Date()`"
output: markdown_document
---

# Preprocessing summary

The data spanning years `r min(na.omit(df$publication_year))`-`r max(na.omit(df$publication_year))` has been included and contains `r nrow(df.preprocessed)` documents (also other filter may apply depending on the data collection, see the source code for details.

## Specific fields

  * [Author info](author.md)
  * [Gender info](gender.md)
  * [Publisher info](publisher.md)
  * [Publication geography](publicationplace.md)
  * [Publication year info](publicationyear.md)
  * [Titles](title.md)  
  * [Page counts](pagecount.md)
  * [Physical dimension](dimension.md)    
  * [Document and subject topics](topic.md)
  * [Languages](language.md)

## Annotated documents

  * `r nrow(df.orig)` documents in the original raw data
  * `r nrow(df)` documents in the final preprocessed data (`r round(100 * nrow(df)/nrow(df.orig), 2)`%)

Fraction of documents with data:

```{r summaryannotations, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=8, fig.height=11}
availability <- field_availability(df)
print(availability$plot)
```

Same in exact numbers: documents with available/missing entries, and number of unique entries for each field. Sorted by missing data:

```{r sumtab, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE}
tab <- availability$table %<>% arrange(n)
names(tab) <- gsub("missing", "missing (%)", names(tab))
names(tab) <- gsub("available", "available (%)", names(tab))
names(tab) <- gsub("^n$", "available (n)", names(tab))
names(tab) <- gsub("unique_entries", "unique (n)", names(tab))
names(tab) <- gsub("field_name", "field name", names(tab))
kable(tab[, c(1, 3, 2, 4, 5)], digits = 1, caption = "Data availability")
rm(tab);gc()
```

## Field conversions

This documents the conversions from raw data to the final preprocessed version (accepted, discarded, conversions). Only some of the key tables are explicitly linked below. The complete list of all summary tables is [here](output.tables/).

Brief description of the fields:

 * [Description of the original MARC fields](https://github.com/COMHIS/fennica/blob/master/inst/extdata/fieldnames.csv)

 * [Description of the preprocessed fields](https://github.com/COMHIS/fennica/blob/master/inst/extdata/fieldname_table.csv)

## Histograms of all entries for numeric variables

```{r summary-histograms, echo=FALSE, message=FALSE, warning=FALSE, fig.width=5, fig.height=4, fig.show='hold', out.width="200px"}
num <- c();
for (field in names(df)) {num[[field]] <- is.numeric(df[[field]])}
numeric.fields <- setdiff(names(which(num)), c("row.index", "original_row", "unity"))
for (field in numeric.fields) {
  x <- log10(min(df[[field]], na.rm = TRUE)/2 + df[[field]])
  x <- x[!is.na(x) & !is.nan(x)]
  if (length(x) > 0) {
    hist(x, 30,
       main = paste(field, "histogram"),
       ylab = "Documents",
       xlab = paste(field, "(log10)")
       )
  }
}
```

## Histograms of the top entries for factor variables

Non-trivial factors with at least 2 levels are shown.

```{r summary-bars, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=5, fig.show='hold', out.width="430px"}
fac <- c(); for (field in names(df)) {fac[[field]] <- is.factor(df[[field]])}
factor.fields <- names(which(fac))
for (field in factor.fields) {
  n <- min(length(unique(df[[field]])), ntop)
  if (length(n) > 1) {
    p <- top_plot(df, field, n)  
    p <- p + ggtitle(paste("Top ", field))
    p <- p + scale_y_log10()
    p <- p + ylab("Documents (Log10)")
    print(p)
  }
}
```

### 2021-01-12 inst/examples/physical_dimension.Rmd
Added many auxiliary files

---
title: "Document dimension preprocessing summary"
author: "Helsinki Computational History Group (COMHIS)"
date: "`r Sys.Date()`"
output: markdown_document
---

```{r init, echo=FALSE}
ntop <- 20
#opts_chunk$set(comment=NA, fig.width=6, fig.height=6)
opts_chunk$set(fig.path = paste0(output.folder, "figure/"))
theme_set(theme_bw(20))
```

## Document size comparisons

  * Some dimension info is provided in the original raw data for altogether `r sum(!is.na(df.orig$physical_dimension))` documents (`r round(100*mean(!is.na(df.orig$physical_dimension)),1)`%) but could not be interpreted for `r sum(!is.na(df.orig$physical_dimension) & (is.na(df$gatherings)))` documents (ie. dimension info was successfully estimated for `r round(100 - 100 * sum(!is.na(df.orig$physical_dimension) & (is.na(df$gatherings)))/sum(!is.na(df.orig$physical_dimension)), 1)` % of the documents where this field was not empty).

  * Document size (area) info was obtained in the final preprocessed data for altogether `r sum(!is.na(df$area))` documents (`r round(100*mean(!is.na(df$area)))`%). For the remaining documents, critical dimension information was not available or could not be interpreted: [List of entries where document surface could not be estimated](physical_dimension_incomplete.csv)

  * Document gatherings info is originally available for `r sum(!is.na(df$gatherings.original))` documents (`r round(100*mean(!is.na(df$gatherings.original)))`%), and further estimated up to `r sum(!is.na(df$gatherings))` documents (`r round(100*mean(!is.na(df$gatherings)))`%) in the final preprocessed data.

  * Document height info is originally available for `r sum(!is.na(df$height.original))` documents (`r round(100*mean(!is.na(df$height.original)))`%), and further estimated up to `r sum(!is.na(df$height))` documents (`r round(100*mean(!is.na(df$height)))`%) in the final preprocessed data.

  * Document width info is originally available for `r sum(!is.na(df$width.original))` documents (`r round(100*mean(!is.na(df$width.original)))`%), and further estimated up to `r sum(!is.na(df$width))` documents (`r round(100*mean(!is.na(df$width)))`%) in the final preprocessed data.

These tables can be used to verify the accuracy of the conversions from the raw data to final estimates:

  * [Dimension conversions from raw data to final estimates](conversions_physical_dimension.csv)

  * [Automated tests for dimension conversions](https://github.com/COMHIS/fennica/blob/master/inst/extdata/tests_dimension_polish.csv)

The estimated dimensions are based on the following auxiliary information sheets:

  * [Document dimension abbreviations](https://github.com/COMHIS/fennica/blob/master/inst/extdata/document_size_abbreviations.csv)

  * [Standard sheet size estimates](https://github.com/COMHIS/fennica/blob/master/inst/extdata/sheetsizes.csv)

  * [Document dimension estimates](https://github.com/COMHIS/fennica/blob/master/inst/extdata/documentdimensions.csv) (used when information is partially missing)

<!--[Discarded dimension info](dimensions_discarded.csv)-->

Left: final gatherings vs. final document dimension (width x height). Right: original gatherings versus original heights where both are available. The point size indicates the number of documents for each case. The red dots indicate the estimated height that is used when only gathering information is available.

```{r summary, echo=FALSE, message=FALSE, warning=FALSE, fig.width=9, fig.height=7, fig.show="hold", out.width="420px"}
df <- df.preprocessed
dfs <- df %>% filter(!is.na(area) & !is.na(gatherings))
dfs <- dfs[, c("gatherings", "area")]
dfm <- melt(table(dfs)) # TODO switch to gather here
names(dfm) <- c("gatherings", "area", "documents")
dfm$gatherings <- factor(dfm$gatherings, levels = levels(df$gatherings))
p <- ggplot(dfm, aes(x = gatherings, y = area)) 
p <- p + scale_y_continuous(trans = "log2")
p <- p + geom_point(aes(size = documents))
p <- p + scale_size(trans="log10")
p <- p + ggtitle("Gatherings vs. area")
p <- p + xlab("Size (gatherings)")
p <- p + ylab("Size (area)")
p <- p + coord_flip()
print(p)

# Compare given dimensions to gatherings
# (not so much data with width so skip that)
df2 <- filter(df, !is.na(height) | !is.na(width))
df2 <- df2[!is.na(as.character(df2$gatherings)),]
df3 <- filter(df2, !is.na(height))
ss <- sheet_sizes()
df3$gathering.height.estimate <- ss[match(df3$gatherings, ss$gatherings),"height"]
df4 <- df3 %>% group_by(gatherings, height) %>% tally()
p <- ggplot(df4, aes(y = gatherings, x = height))
p <- p + geom_point(aes(size = n))
p <- p + geom_point(data = unique(df3), aes(y = gatherings, x = gathering.height.estimate), color = "red")
p <- p + ylab("Gatherings (original)") + xlab("Height (original)") 
p <- p + ggtitle("Gatherings vs. height")
print(p)
```

Left: Document dimension histogram (surface area);
Right: title count per gatherings.

```{r sizes, echo=FALSE, message=FALSE, warning=FALSE, fig.width=7, fig.height=5, fig.show="hold",out.width="420px"}
p <- ggplot(df, aes(x = area))
p <- p + geom_histogram() 
p <- p + xlab("Document surface area (log10)")
p <- p + ggtitle("Document dimension (surface area)")
p <- p + scale_x_log10()
print(p)

p <- ggplot(df, aes(x = gatherings)) 
p <- p + geom_bar()
n <- nchar(max(na.omit(table(df$gatherings))))
p <- p + scale_y_log10(breaks=10^(0:n))
p <- p + ggtitle("Title count")
p <- p + xlab("Size (gatherings)")
p <- p + ylab("Title count")
p <- p + coord_flip()
print(p)
```

<!--

### Gatherings timelines

```{r ndef, echo=FALSE, message=FALSE, warning=FALSE}
nmin <- 15
```

Popularity of different document sizes over time. Left: absolute title
counts. Right: relative title counts. Gatherings with less than `r
nmin` documents at every decade are excluded:

```{r compbyformat, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=7, fig.show="hold", out.width="430px"}
dfs <- df %>% filter(!is.na(gatherings))

res <- timeline(dfs, group = "gatherings", nmin = nmin, mode = "absolute") 
print(res$plot)

res <- timeline(dfs, group = "gatherings", nmin = nmin, mode = "percentage") 
print(res$plot)
```

## Average document dimensions

Here we use the original data only:

```{r avedimstime, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=7}
# only include gatherings with sufficiently many documents
nmin <- 2000
top.gatherings <- setdiff(names(which(table(df$gatherings.original) > nmin)), "NA")

df2 <- filter(df, !gatherings.original == "NA" &
                  (!is.na(height.original) | !is.na(width.original))) %>%
       filter(gatherings.original %in% top.gatherings) %>%
       select(publication_decade, gatherings.original, height.original, width.original)

df3 <- df2 %>% group_by(gatherings.original, publication_decade) %>% 
       summarize(mean.height.original = mean(height.original, na.rm = T),
    	         mean.width.original  = mean(width.original, na.rm = T),
		 n = n())

p <- ggplot()
p <- p + geom_point(data = df3, aes(x = publication_decade,
       	 		   	    y = mean.height.original,
				    size = n,
				    group = gatherings.original,
				    color = gatherings.original))
# Use mean height here to speed up
p <- p + geom_smooth(data = df3, method = "loess",
       	   aes(x = publication_decade,
	       y = mean.height.original,
	       group = gatherings.original,
	       color = gatherings.original))
p <- p + ggtitle("Height")
print(p)
```

Only the most frequently occurring gatherings are listed here:

```{r avedims, echo=FALSE, message=FALSE, warning=FALSE}
df2 <- filter(df, !is.na(gatherings.original) & (!is.na(height.original) | !is.na(width.original))) %>%
       filter(gatherings.original %in% top.gatherings) %>%
       group_by(gatherings.original) %>% 
       summarize(
    	    mean.width = mean(width.original, na.rm = T), 
	    median.width = mean(width.original, na.rm = T),        
            mean.height = mean(height.original, na.rm = T),
	    median.height = mean(height.original, na.rm = T),
	    n = n())

mean.dimensions <- as.data.frame(df2)
kable(mean.dimensions, caption = "Average document dimensions", digits = 2)
```

-->

### 2021-01-12 inst/examples/publicationyear.Rmd
Added many auxiliary files

---
title: "Publication year summaries"
author: "Leo Lahti"
date: "`r Sys.Date()`"
output: markdown_document
---

### Publication year

[Publication year conversions](output.tables/publication_year_conversion.csv)

[Publication year discarded](output.tables/publication_year_discarded.csv)

Publication year is available for `r sum(!is.na(df$publication_year))` documents (`r round(100*mean(!is.na(df$publication_year)))`%). The publication years span `r paste(range(na.omit(df$publication_year)), collapse = "-")`.

```{r summarypublicationyear, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
# Title count per decade
df <- df.preprocessed
df2 <- df %>% group_by(publication_decade) %>% filter(publication_decade < 2010) 
p <- ggplot(df2, aes(publication_decade)) +
     geom_bar() + scale_y_log10() +
     ggtitle("Title count timeline")
print(p)
```

### Publication frequency

Publication frequency information is available for `r sum(!is.na(df$publication_frequency_text))` documents (`r round(100*mean(!is.na(df$publication_frequency_text)))`%). The links are invalid if the lists are empty. The (estimated annual) frequencies are converted to plain text according to their closest match in [this table](https://github.com/COMHIS/fennica/blob/master/inst/extdata/frequency_conversions.csv).

[Publication frequency accepted](output.tables/publication_frequency_accepted.csv)

[Publication frequency conversions](output.tables/publication_frequency_conversion.csv)

[Publication frequency discarded](output.tables/publication_frequency_discarded.csv)

### Publication interval

Publication interval is available for `r sum(!is.na(df$publication_interval_from) | !is.na(df$publication_interval_till))` documents (`r round(100*mean(!is.na(df$publication_interval_from) | !is.na(df$publication_interval_till)))`%).

[Publication interval accepted](output.tables/publication_interval_accepted.csv)

[Publication interval conversions](output.tables/publication_interval_conversion_nontrivial.csv)

[Publication interval discarded](output.tables/publication_interval_discarded.csv)

### Editions

Automated detection of potential first editions (first_edition field)
identifies unique author-title pairs, and proposes the first
occcurrence (earliest publication_year) as the first edition. If there
are multiple instances from the same earliest year, they are all
marked as potential first editions. Later need to check if this
information is readily available in MARC.

There are `r nrow(unique(df[, c("title", "author")]))` unique
documents with an identical title and author and
`r nrow(df %>% group_by(title, author) %>% tally() %>% filter(n > 1))`
of those have multiple occurrences, sometimes with different publication
years.  The earliest occurrence is suggested as the first edition.

This figure shows the number of first editions per decade.

```{r firsteditions, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=6}
df <- df.preprocessed
df <- df %>% group_by(publication_decade) %>%
             summarise(total = n(), first = sum(first_edition, na.rm = TRUE))
df2 <- melt(df, id = "publication_decade")
theme_set(theme_bw(20))
p <- ggplot(df2, aes(x = publication_decade, y = value, group = variable)) +
       geom_point(aes(shape = variable), size = 5) +
       geom_line(aes(shape = variable)) +       
       geom_smooth(aes(col = variable, fill = variable)) + 
       xlab("Publication year") +
       ylab("First editions (n)") +
       #scale_y_log10() +
       ggtitle("First editions vs. total title count")
print(p)
```

### 2021-01-12 inst/examples/summary.Rmd
Added many auxiliary files

@@
 # Read the preprocessed data
-df <- readRDS("data/unified/polished/df.Rds")
-df.orig <- readRDS("data/unified/polished/df.raw.Rds")
+df <- readRDS("df.Rds")
+df.orig <- readRDS("df.raw.Rds")
 conversions <- readRDS("conversions.Rds")

### 2021-01-12 inst/examples/CCQ_2019/prepare_fnd_data_for_ccq2019.R

@@ -1,0 +1,39 @@
+library(ggplot2)
+library(tidyr)
+library(dplyr)
+library(fennica)
+library(magrittr)
+library(reshape2)
+library(gridExtra)
+library(knitr)
+
+# ---------------------------------
+
+# Set global parameters
+timespan <- c(1500, 1800)
+datafile <- "data/unified/polished/df.Rds"
+author <- "Lahti, Marjanen, Roivainen, Tolonen"
+#fields <- c("publication_year", "publication_place", "title", "language_primary", "languages", "gatherings", "pagecount", "printarea")
+fields <- c("publication_year", "publication_place", "title", "language_primary", "languages", "gatherings", "pagecount")
+
+print("Prepare the final data set")
+df0 <- readRDS(datafile)
+
+# Year limits
+df <- df0
+if (exists("timespan")) {
+  df <- filter(df,
+          publication_year >=  min(timespan) & 
+	  publication_year <= max(timespan))
+} else {
+  # Create timespan but do not filter if not given
+  timespan <- range(df$publication_year, na.rm = TRUE)
+}
+
+# Include the selected fields
+df <- df %>% select(fields) %>%
+             arrange(publication_year, publication_place, title, language_primary, gatherings, pagecount)
+
+# Store
+write.table(df, file = "data/unified/polished/FNB_20180627.csv", sep = "\t", row.names = FALSE, quote = FALSE)
+

### 2021-01-12 inst/examples/aaro.R

@@ -1,55 +1,0 @@
-# Install packages
-#install.packages("devtools")
-#install.packages("httr")
-#install.packages("gender")
-#install.packages(c("gender", "genderdata"),
-#                 repos = "http://packages.ropensci.org",
-#                 type = "source")
-
-library(devtools)
-#devtools::install_github("ropengov/bibliographica")
-#devtools::install_github("ropengov/fennica")
-#devtools::install_github("ropengov/sorvi")
-
-# Load packages
-library(bibliographica)
-library(fennica)
-library(sorvi)
-library(dplyr)
-
-# Load pre-calculated data tables
-df.preprocessed <- readRDS("df.Rds")
-load("geonames.RData")
-load("places.geonames.RData") # TODO! needs file places.geonames, repo has broken symlink
-
-# Get geocoordinates for the given publication places
-# The place names are returned in the output as this improves the scalability
-# with larger data collections
-# This is the current function, prepared with the Geonames database and
-# the British ESTC data collection. The function itself is not well-written but does the job for now.
-#geoc <- bibliographica::get_geocoordinates(df.preprocessed$publication_place, geonames, places.geonames)
-
-# These place names in Fennica are still missing geocoordinates (sorted by count)
-#places.missing.geoc <- sort(table(droplevels(df.preprocessed$publication_place[is.na(rowSums(geoc))])), decreasing = TRUE)
-#print(names(places.missing.geoc))
-
-# Can we find latitude and longitude for most of these places from public sources?
-# YES: R/city_geocoordinate.R
-
-# If geocoordinates can be found for some places, it would be useful to have a wrapper function
-# which takes the list of place names
-# as input (ie. names(places.missing.geoc)),
-# retrieves the geocoordinates from public sources,
-# and then returns a data.frame with two columns:
-# latitude and longitude, corresponding to the input places.
-# YES: R/city_geocoorinates_all.R
-
-# It is also OK to construct a custom mapping table (CSV file) between place names and geocoordinates
-# and just use that in the function but of course it would be more neat to just automate everything.
-# However, if we can't solve this otherwise, it would be already very useful to get geocoordinates for
-# the top-30 or so places by hand from Wikipedia or another source. This will make it possible to
-# visualize publication developments on the Finnish map.
-
-
-
-

### 2021-01-12 inst/examples/analysis.init.R

@@ -1,7 +1,6 @@
 library(ggplot2)
 library(tidyr)
 library(dplyr)
-library(bibliographica)
 library(fennica)
 library(magrittr)
 library(reshape2)
@@ -14,15 +13,14 @@ library(knitr)
 #timespan <- c(1400, 1920)
 #timespan <- c(1470, 1828)
 #timespan <- c(-Inf, Inf)
-datafile <- "data/unified/polished/df.Rds"
-datafile.orig <- "data/unified/polished/df.raw.Rds"
+datafile <- "df.Rds"
+datafile.orig <- "df.raw.Rds"
 ntop <- 20
 author <- "Helsinki Computational History Group (COMHIS)"
 
 # Already in main.R but it must
 # be possible to run analysis.R
 # independently, therefore redefined here.
-
 output.folder <- "output.tables/"
 
 # ---------------------------------

### 2021-01-12 inst/examples/analysis.run.R

@@ -2,7 +2,22 @@
 tmp <- generate_summary_tables(df.preprocessed, df.orig, output.folder)
 
 # Clean up - remove overlaps - is all needed
-summaries <- c("summary", "overview", "author", "publicationplace", "publisher", "documents", "size", "gender", "topic", "language", "title", "publicationyear", "pagecount", "dimension", "physical_dimension", "Paper")
+summaries <- c("summary",
+               "overview",
+	       "author",
+	       "publicationplace",
+	       # "publisher",
+	       "documents",
+	       "size",
+	       "gender",
+	       "topic",
+	       "language",
+	       "title",
+	       "publicationyear",
+	       "pagecount",
+	       "dimension",
+	       "physical_dimension",
+	       "Paper")
 
 df <- df.preprocessed
 
@@ -11,12 +26,10 @@ outputs <- c()
 
 # Generate the markdown summaries
 for (id in summaries) {
-this.folder <- getwd()
-outputs[[id]] <- knit(input = system.file(paste("extdata/", id, ".Rmd", sep = ""),
-  	       	package = "bibliographica"),
-       output = paste(id, ".md", sep = "")) # envir = globalenv()
-       gc()
-  }
+  this.folder <- getwd()
+  outputs[[id]] <- knit(input = paste(id, ".Rmd", sep = ""), 
+                        output = paste(id, ".md", sep = ""))
+}
 
 
 

### 2021-01-12 inst/examples/collijn.R

@@ -2,7 +2,7 @@ df <- readRDS("df.Rds")
 
 inds <- grep("\\.\\.\\.", df$title)
 
-library(bibliographica)
+# library(bibliographica)
 library(dplyr)
 
 # ----------------------------------

### 2021-01-12 inst/examples/enrich.fennica.R

@@ -59,7 +59,7 @@ df.preprocessed$publication_interval_till[is.na(df.preprocessed$publication_inte
 
   message("Custom gender information for Fennica")
   # For author names, use primarily the Finnish names database
-  # hence use it to replace the genders assigned earlier by bibliographica
+  # hence use it to replace the genders assigned earlier 
   library(fennica)
   firstname <- pick_firstname(df.preprocessed$author_name, format = "last, first")
 
@@ -76,6 +76,10 @@ df.preprocessed$publication_interval_till[is.na(df.preprocessed$publication_inte
   inds <- which(!is.na(gendercustom))
   df.preprocessed$author_gender[inds] <- gendercustom[inds]
 
+
+skip <- TRUE
+# FIXME add this
+if (!skip) {
 message("-- Fennica publishers")
   df.preprocessed.bu <- df.preprocessed
   df.preprocessed$publisher <- polish_publisher_fennica(df.preprocessed)
@@ -98,5 +102,7 @@ message("-- Fennica publishers")
   df.preprocessed$latitude <- geoinfo[inds, "latitude"]  
  
   # ----------------------------------------------------------------------
+
+}
 
 data.enriched.fennica <- df.preprocessed

### 2021-01-12 inst/examples/funcs.R

@@ -1,3 +1,470 @@
+#' @title Harmonize field names
+#' @description Convert field codes to names 
+#' @param x a vector of field codes
+#' @return Vector of field names
+#' @export
+#' @author Leo Lahti \email{leo.lahti@@iki.fi}
+#' @examples x2 <- harmonize_field_names("041a")
+#' @details For MARC field descriptions, see \url{https://www.loc.gov/marc/bibliographic/}.
+#' @keywords utilities
+harmonize_field_names <- function (x = NULL) {
+
+  # Get printing terms from a table
+  f <- system.file("extdata/fieldnames.csv", package = "comhis")
+  map <- read.csv(f, sep = "|")
+
+  if (!is.null(x)) {
+    ret <- map[match(x, map$field), "name"]
+  } else {
+    ret <- map
+  }
+  ret
+}
+
+
+
+
+#' @title Polish Place
+#' @description Polish place names.
+#' @param x A vector of place names
+#' @param synonymes Synonyme table for place names
+#' @param remove.unknown Logical. Remove places that are not validated (ie. listed in the synonyme table)?
+#' @param verbose verbose
+#' @param harmonize Harmonize the polished names. Logical.
+#' @return Polished vector
+#' @export
+#' @author Leo Lahti \email{leo.lahti@@iki.fi}
+#' @references See citation("bibliographica")
+#' @examples # x2 <- polish_place(c("London", "Paris"))
+#' @keywords utilities
+polish_place <- function (x, synonymes = NULL, remove.unknown = FALSE, verbose = FALSE, harmonize = TRUE) {
+
+  if (all(is.na(x))) {return(x)}
+
+  if (is.null(synonymes)) {
+    # Harmonize places with synonyme table
+    f <- system.file("extdata/PublicationPlaceSynonymes.csv", package = "bibliographica")
+    synonymes <- suppressWarnings(read_mapping(f, include.lowercase = T, self.match = T, ignore.empty = FALSE, mode = "table", trim = TRUE))
+
+    if (verbose) { message(paste("Reading special char table", f)) }
+    # Harmonize places with synonyme table
+    f <- system.file("extdata/replace_special_chars.csv",
+		package = "bibliographica")
[…]

### 2021-01-12 inst/examples/generate_summary_tables.R

@@ -477,7 +477,7 @@ generate_summary_tables <- function (df.preprocessed, df.orig, output.folder = "
   message("Undefined language")
   gc(); rm(dfs); rm(tmp) # Cleanup
   # Remove "und" from the list ("Undetermined")
-  f <- system.file("extdata/language_abbreviations.csv", package = "bibliographica")
+  f <- "language_abbreviations.csv"
   abrv <- read_mapping(f, include.lowercase = T, self.match = T, ignore.empty = FALSE, mode = "table", sep = "\t")
   # List unique languages that occur in the data
   lang <- tolower(df.orig$language)

### 2021-01-12 inst/examples/main.R

@@ -1,21 +1,8 @@
+# ----------------------------------------------------
+#            INITIALIZE AND LOAD DATA
+# ----------------------------------------------------
+
 source("init.R")
-
-# ----------------------------------------------------
-#            LOAD DATA FOR PREPROCESSING
-# ----------------------------------------------------
-
-df.orig <- read_bibliographic_metadata(fs, verbose = TRUE, sep = "|")
-# FIXME move this to preprocessing part
-# Modify the original data if needed 
-# Finnish/Swedish specific fixes 
-# In Finnish texts s. is used instead of p.
-
-update.fields <- names(df.orig) # Update all fields
-# Remove specified fields
-ignore.fields <- c("language2", "title_remainder",
-                       "physical_details", "physical_accomppanied",
-                       "note_general", "note_year", "original_row") # Fennica
-update.fields <- setdiff(update.fields, ignore.fields)
 
 # ----------------------------------------------------
 #           PREPROCESS DATA
@@ -24,7 +11,9 @@ update.fields <- setdiff(update.fields, ignore.fields)
 message("Preprocess selected original fields")
 source("polish_all.R")
 
-saveRDS(df.preprocessed, "data/unified/polished/df0.Rds", compress = TRUE)  
+# Store the processed data
+saveRDS(df.preprocessed, "df0.Rds", compress = TRUE)
+saveRDS(df.orig, "df.raw.Rds", compress = TRUE)  
 saveRDS(conversions, "conversions.Rds", compress = TRUE)
 
 # ----------------------------------------------------
@@ -60,19 +49,20 @@ data.enriched2 <- enrich_preprocessed_data(data.validated2, df.orig)
 
 print("Saving updates on preprocessed data")
 df.preprocessed <- data.enriched2
-saveRDS(df.preprocessed, "data/unified/polished/df.Rds")
-
-# Data releases
-# CCQ 2019 data release - run separately
-# source("prepare_fnd_data_for_ccq2019.R")
-
-# -----------------------------------
+saveRDS(df.preprocessed, "df.Rds")
 
 # Summary analyses
 source("analysis.init.R")
-source("analysis.run.R")
+# source("analysis.run.R")
+
+# ---------------------------------------------------
 
 # Specific analyses (to be updated)
 # source("analysis.R")  # Summary md docs
+
+# Data releases
+# CCQ 2019 data release - run separately
+# source("CCQ_2019/prepare_fnd_datax_for_ccq2019.R")
+
 
 

### 2021-01-12 inst/examples/phase3.R

@@ -1,8 +1,7 @@
 library(dplyr)
 library(tau)
 library(fennica)
-library(bibliographica)
-df <- tbl_df(data.frame(list(row.index = 1:data_size)))
+df <- tibble::as_tibble(data.frame(list(row.index = 1:data_size)))
 
 # ---------------------------------------------
 
@@ -42,14 +41,13 @@ df$publication_place <- polish_place(df.orig$publication_place, remove.unknown =
 
 source("city_examples.R", encoding = "UTF-8") # later account for multiple places
 
-
 # LL removed this and saved a copy to
 # inst/extras/country.R df <- deduce_country(df)
 # Now using tools from bibliographica.
 # I put the assigment df$country <- ... outside of the function
 # because the mapping function itself may have also other uses than
 # data.frame augmentation
-df$country <- bibliographica::get_country(df$city)$country
+df$country <- get_country(df$city)$country
 
 # Replaced fix_pubhouses with bibliographica function:
 #df <- fix_pubhouses(df.orig, df)

### 2021-01-12 inst/examples/physical_extent.R

@@ -1,5 +1,5 @@
 #df.tmp <- bibliographica::polish_physical_extent(df.orig[[field]], verbose = TRUE)
-rm.dim.file <- system.file("extdata/remove_dimension.csv", package = "bibliographica")    
+rm.dim.file <- "remove_dimension.csv"
 df.tmp <- polish_physical_extent(df.orig[[field]], verbose = TRUE, rm.dim.file = rm.dim.file)
 
 # Vol number and count fields could not be extracted from physical_extent field in Fennica - remove

### 2021-01-12 inst/examples/prepare_fnd_data_for_ccq2019.R

@@ -1,40 +1,0 @@
-library(ggplot2)
-library(tidyr)
-library(dplyr)
-library(bibliographica)
-library(fennica)
-library(magrittr)
-library(reshape2)
-library(gridExtra)
-library(knitr)
-
-# ---------------------------------
-
-# Set global parameters
-timespan <- c(1500, 1800)
-datafile <- "data/unified/polished/df.Rds"
-author <- "Lahti, Marjanen, Roivainen, Tolonen"
-#fields <- c("publication_year", "publication_place", "title", "language_primary", "languages", "gatherings", "pagecount", "printarea")
-fields <- c("publication_year", "publication_place", "title", "language_primary", "languages", "gatherings", "pagecount")
-
-print("Prepare the final data set")
-df0 <- readRDS(datafile)
-
-# Year limits
-df <- df0
-if (exists("timespan")) {
-  df <- filter(df,
-          publication_year >=  min(timespan) & 
-	  publication_year <= max(timespan))
-} else {
-  # Create timespan but do not filter if not given
-  timespan <- range(df$publication_year, na.rm = TRUE)
-}
-
-# Include the selected fields
-df <- df %>% select(fields) %>%
-             arrange(publication_year, publication_place, title, language_primary, gatherings, pagecount)
-
-# Store
-write.table(df, file = "data/unified/polished/FNB_20180627.csv", sep = "\t", row.names = FALSE, quote = FALSE)
-

### 2021-01-12 inst/examples/publication_place.R

@@ -1,4 +1,3 @@
-    # Polish the given field
-    df.tmp <- polish_field(df.orig, df.preprocessed, field, verbose = FALSE,
-                           languages = languages)
+tab <- polish_place(df.orig[[field]], remove.unknown = FALSE, verbose = verbose)
+df.tmp <- data.frame(publication_place = tab)
 

### 2021-01-12 inst/examples/summarize.R

@@ -1,4 +1,4 @@
-library(bibliographica)
+# library(bibliographica)
 library(dplyr)
 df.preprocessed <- readRDS("df.Rds")
 df.orig <- readRDS("df.raw.Rds")

### 2021-01-18 inst/examples/overview.Rmd
ok

@@
 
-# Preprocessing summary
+# Preprocessing summary: Fennica
 
-The data spanning years `r min(na.omit(df$publication_year))`-`r max(na.omit(df$publication_year))` has been included and contains `r nrow(df.preprocessed)` documents (also other filter may apply depending on the data collection, see the source code for details.
+The data spanning years `r min(na.omit(df$publication_year))`-`r max(na.omit(df$publication_year))` has been included and contains `r nrow(df.preprocessed)` documents (additional filters may apply depending on the analysis, see the source code for details).
 
@@
 ```
+
+Fields of special interest. Real success percentage (proportion of successful conversions compared to non-NA entries in the original data):
+
+```{r missing2, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=10, fig.height=15}
+select.fields <- c("author","publication_place","publication_country","publication_year",
+                     "publication_year_from","publication_year_till","corporate","area","pagecount",
+		     "gatherings","width","height","publisher","self_published")
+
+dfs <- df
+
+success <- as.data.frame(t(apply(dfs, 2, function (x) {sum(!is.na(gsub("^NA$", NA, as.character(x))))})))
+
+original.nonNA <- as.data.frame(t(apply(select(df.orig, publication_place,
+                    publication_time, corporate, physical_extent, physical_dimension, publisher, author_name),
+		      2, function (x) {sum(!is.na(gsub("^NA$", NA, as.character(x))))})))
+
+# Compare the number of non-NA entries in preprocessed data to number
+# of non-NA entries in the original data:
+real.success <- c()
+real.success[["publication_place"]] <- success$publication_place/original.nonNA$publication_place
+real.success[["publication_country"]] <- success$publication_country/original.nonNA$publication_place
+real.success[["publication_year"]] <- success$publication_year/original.nonNA$publication_time
+real.success[["publication_year_from"]] <- success$publication_year_from/original.nonNA$publication_time
+real.success[["publication_year_till"]] <- success$publication_year_till/original.nonNA$publication_time
+real.success[["corporate"]] <- success$corporate/original.nonNA$corporate
+real.success[["publisher"]] <- success$publisher/original.nonNA$publisher
+real.success[["self_published"]] <- success$self_published/original.nonNA$publisher
+real.success[["pagecount"]] <- success$pagecount/original.nonNA$physical_extent
+real.success[["area"]] <- success$area/original.nonNA$physical_dimension
+real.success[["gatherings"]] <- success$gatherings/original.nonNA$physical_dimension
+real.success[["author"]] <- success$author/original.nonNA$author
+# real.success[["paper"]] <- success$paper/sum(rowMeans(!is.na(df.orig[, c("physical_extent", "physical_dimension")])) == 1)
+real.success <- unlist(real.success)
+par(mar = c(3, 8, 2, 1)); barplot(100*sort(real.success), horiz = T, main = "Real success rate (selected fields)", las = 1, xlim = c(0, 100), xlab = "Success rate (%)")
+```

### 2021-01-18 inst/examples/publisher.Rmd
ok

---
title: "Publisher preprocessing summary"
author: "`r author`"
date: "`r Sys.Date()`"
output: markdown_document
---

### Publishers

 * `r length(unique(df$publisher))` [unique publishers](output.tables/publisher_accepted.csv)

 * `r sum(!is.na(df$publisher))` documents have unambiguous publisher information (`r round(100*mean(!is.na(df$publisher)), 1)`%). This includes documents identified as self-published; the author name is used as the publisher in those cases (if known).

 * `r length(which(df$self_published))` documents are identified as self-published (`r round(100*(length(which(df$self_published))/nrow(df)), 1)`%).

 * [Discarded publisher entries](output.tables/publisher_discarded.csv)

 * [Conversions from original to final names](output.tables/publisher_conversion_nontrivial.csv) (only non-trivial conversions shown)

The `r ntop` most common publishers are shown with the number of documents.

```{r summarypublisher2, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=9}
p <- top_plot(df, "publisher", ntop)
p <- p + ggtitle(paste("Top publishers"))
p <- p + scale_y_log10()
p <- p + ylab("Documents")
print(p)
```

### Publication timeline for top publishers

Title count

```{r top_pub_timeline, fig.height=10, fig.width=20, echo=FALSE}
# For some reason the ggplot never completes if top n > 2 ???
theme_set(theme_bw(20))
field <- "publisher"
tops <- names(top(df, field, n = 2))
dfs <- df %>% select(field, publication_decade) 
dfs$field <- as.character(dfs[[field]]); dfs[[field]] <- NULL
dfs <- dfs %>% filter(field %in% tops) %>%
               filter(!is.na(field) & !is.na(publication_decade)) %>%
	       count(field, publication_decade)
dfs$field <- as.factor(dfs$field)
p <- ggplot(dfs, aes(x = publication_decade, y = n, fill = field)) +
       geom_bar(stat = "identity", position = "stack", color = "black") +       
       labs(x = "Publication Decade", y = "Title Count",
            title = "Title count timeline for the top publishers") +
       scale_fill_grey() +
       guides(fill = guide_legend("Publisher")) 
# print(p)
```

Title count versus paper consumption (top publishers):

```{r publishertitlespapers, fig.height=8, fig.width=8, echo=FALSE, warning=FALSE}
#res <- compare_title_paper(df, "publisher", selected = tops)
tops <- names(top(df, field = "publisher", n = 10))
res <- compare_title_paper(df, "publisher")
print(res$plot)  
kable(subset(res$table, publisher %in% tops), digit = 2)
```

### Corporates

Summaries of the corporate field.

 * `r length(unique(df$corporate))` [unique corporates](output.tables/corporate_accepted.csv)

 * `r sum(!is.na(df$corporate))` documents have unambiguous corporate information (`r round(100*mean(!is.na(df$corporate)), 1)`%).

 * [Discarded corporate entries](output.tables/corporate_discarded.csv)

 * [Conversions from original to final names](output.tables/corporate_conversion_nontrivial.csv) (only non-trivial conversions shown)

The `r ntop` most common corporates are shown with the number of documents.

```{r summarycorporate2, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=9}
p <- top_plot(df, "corporate", ntop)
p <- p + ggtitle(paste("Top corporates"))
p <- p + scale_y_log10()
p <- p + ylab("Documents")
print(p)
```

## Publisher

[Self-published accepted](https://github.com/COMHIS/fennica/blob/master/inst/examples/output.tables/self_published_accepted.csv) (Check for formatting and synonymes)

[Self-published raw fields](https://github.com/COMHIS/fennica/blob/master/inst/examples/output.tables/self_published_rawfields.csv) (Check that the self-publication is a correct classification for these docs)

## Corporate info

[Accepted corporate info](https://github.com/COMHIS/fennica/blob/master/inst/examples/output.tables/corporate_accepted.csv)

[Discarded corporate info](https://github.com/COMHIS/fennica/blob/master/inst/examples/output.tables/corporate_discarded.csv)

### 2021-01-18 R/polish_publisher_fennica.R

@@ -79,7 +79,7 @@ polish_publisher_fennica <- function (df.preprocessed, useShortcuts=FALSE) {
   # HR 2017-03-21: Don't do sv_publisher -conversions in clean_publisher(),
   # as it's done in harmonize_publisher in a more controlled way
   unprocessed_pubs  <- clean_publisher(df.preprocessed$publisher[keep.inds], languages = c())
-
+save(df.preprocessed, file = "~/tmp/tmp.RData")    
   unprocessed_pubs  <- harmonize_publisher_fennica2(unprocessed_pubs, publication_year[keep.inds,], languages = languages)
   unprocessed_towns <- df.preprocessed$publication_place[keep.inds]
   unprocessed_years <- publication_year[keep.inds,]

### 2021-01-18 inst/examples/analysis.run.R

@@ -1,18 +1,31 @@
+library(stringr)
+library(dplyr)
+library(reshape2)
+library(ggplot2)
+library(comhis)
+library(fennica)
+
+ntop <- 20
+
+# Read the preprocessed data
+df <- readRDS("df.Rds")
+df.orig <- readRDS("df.raw.Rds")
+conversions <- readRDS("conversions.Rds")
+
 # Summarize the data and discarded entries
 tmp <- generate_summary_tables(df.preprocessed, df.orig, output.folder)
 
-# Clean up - remove overlaps - is all of this needed?
-summaries <- c("summary",
-               "overview",
+# Clean up - remove overlaps - is all of this needed
+summaries <- c("overview",
 	       "author",
 	       "publicationplace",
 	       "publisher",
-	       "size",
 	       "gender",
 	       "topic",
 	       "language",
 	       "title",
 	       "publicationyear",
+	       "size",	       
 	       "pagecount",
 	       "dimension",
 	       "physical_dimension",

### 2021-01-18 inst/examples/init.R

@@ -4,12 +4,11 @@ library(tm)
 library(stringr)
 
 # Install latest version from Github
-# install_github("comhis/fennica")
-devtools::load_all() # working from the clone and modifying it
+# install_github("comhis/fennica") # or devtools::load_all() if you are working from the clone and modifying it
 library(fennica) 
 
 # Install latest version from Github
-install_github("comhis/comhis")        
+# install_github("comhis/comhis")        
 library(comhis)  
 
 # Load misc functions needed for harmonization
@@ -26,7 +25,7 @@ languages <- c("finnish", "latin", "swedish")
 
 # List the preprocessed data file and read the data
 df.orig <- read_bibliographic_metadata("fennica_parsed.csv.gz", verbose = TRUE, sep = "|")
-df.orig <- sample_n(df.orig, 1000) # Try with a smaller subset first!
+# df.orig <- sample_n(df.orig, 1000) # Try with a smaller subset first!
 
 update.fields <- c(
       "original_row",

### 2021-01-18 inst/examples/publication_place.R

@@ -1,4 +1,3 @@
-library(stringr)
 tab <- polish_place(df.orig[[field]], remove.unknown = FALSE)
 df.tmp <- data.frame(publication_place = tab)
 

### 2021-01-18 inst/examples/subject_geography.Rmd
ok

--- 2021-01-12 inst/examples/summary.Rmd
@@
 ---
-title: "Preprocessing summary"
-author: "Leo Lahti"
-date: "`r date()`"
+title: "Subject geography preprocessing summary"
+author: "`r author`"
+date: "`r Sys.Date()`"
+output: markdown_document
 ---
 
-# Fennica summary
-
-```{r missing, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=10, fig.height=15}
-library(stringr)
-library(dplyr)
-library(reshape2)
-library(ggplot2)
-ntop <- 20
-
-# Read the preprocessed data
-df <- readRDS("df.Rds")
-df.orig <- readRDS("df.raw.Rds")
-conversions <- readRDS("conversions.Rds")
-```
-
-Fields of special interest. Real success percentage (proportion of successful conversions compared to non-NA entries in the original data):
-
-```{r missing2, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=10, fig.height=15}
-dfs <- df %>% select(author, publication_place, publication_country, publication_year, publication_year_from, publication_year_till, corporate, area, pagecount, gatherings, width, height, paper, publisher, self_published)
-success <- as.data.frame(t(apply(dfs, 2, function (x) {sum(!is.na(gsub("^NA$", NA, as.character(x))))})))
-original.nonNA <- as.data.frame(t(apply(select(df.orig, publication_place, publication_time, corporate, physical_extent, physical_dimension, publisher, author_name), 2, function (x) {sum(!is.na(gsub("^NA$", NA, as.character(x))))})))
-
-# Compare the number of non-NA entries in preprocessed data to number
-# of non-NA entries in the original data:
-real.success <- c()
-real.success[["publication_place"]] <- success$publication_place/original.nonNA$publication_place
-real.success[["publication_country"]] <- success$publication_country/original.nonNA$publication_place
-real.success[["publication_year"]] <- success$publication_year/original.nonNA$publication_time
-real.success[["publication_year_from"]] <- success$publication_year_from/original.nonNA$publication_time
-real.success[["publication_year_till"]] <- success$publication_year_till/original.nonNA$publication_time
-real.success[["corporate"]] <- success$corporate/original.nonNA$corporate
-real.success[["publisher"]] <- success$publisher/original.nonNA$publisher
-real.success[["self_published"]] <- success$self_published/original.nonNA$publisher
-real.success[["pagecount"]] <- success$pagecount/original.nonNA$physical_extent
-real.success[["area"]] <- success$area/original.nonNA$physical_dimension
-real.success[["gatherings"]] <- success$gatherings/original.nonNA$physical_dimension
-real.success[["author"]] <- success$author/original.nonNA$author
-real.success[["paper"]] <- success$paper/sum(rowMeans(!is.na(df.orig[, c("physical_extent", "physical_dimension")])) == 1)
-par(mar = c(3, 8, 2, 1)); barplot(100*sort(real.success), horiz = T, main = "Real success rate (selected fields)", las = 1, xlim = c(0, 100), xlab = "Success rate (%)")
-```
-
-## Publisher
-
-[Self-published accepted](https://github.com/COMHIS/fennica/blob/master/inst/examples/output.tables/self_published_accepted.csv) (Check for formatting and synonymes)
-
-[Self-published raw fields](https://github.com/COMHIS/fennica/blob/master/inst/examples/output.tables/self_published_rawfields.csv) (Check that the self-publication is a correct classification for these docs)
-
-We also have corporate info available ?
-
-[Accepted corporate info](https://github.com/COMHIS/fennica/blob/master/inst/examples/output.tables/corporate_accepted.csv)
-
-[Discarded corporate info](https://github.com/COMHIS/fennica/blob/master/inst/examples/output.tables/corporate_discarded.csv)
-
-## Subject geographical places
+### Subject geographical places
 

### 2021-01-18 inst/examples/title.Rmd
Title field polished

---
title: "Title field: summary"
author: "Leo Lahti"
date: "`r Sys.Date()`"
output: markdown_document
---

### Titles

 * `r length(unique(df$title))` [unique titles](output.tables/title_accepted.csv)
 * `r sum(!is.na(df$title))` documents (`r round(100*mean(!is.na(df$title)))`%) have a title
 * [Discarded titles](output.tables/title_discarded.csv)

Top-`r ntop` titles are shown together with the number of documents.

```{r summarytitle, echo=FALSE, message=FALSE, warning=FALSE, fig.width=16, fig.height=10}
p <- top_plot(df, "title", ntop = ntop) +
       scale_y_log10() +
       labs(y = "Entries (n)", title = Top titles)
print(p)
```

### 2021-01-18 inst/examples/analysis.run.R

@@ -1,16 +1,12 @@
-library(stringr)
-library(dplyr)
-library(reshape2)
-library(ggplot2)
-library(comhis)
-library(fennica)
-
-ntop <- 20
+print("Prepare the final data set")
 
 # Read the preprocessed data
-df <- readRDS("df.Rds")
-df.orig <- readRDS("df.raw.Rds")
+df.orig <- readRDS(datafile.orig)
+df0 <- readRDS(datafile)
 conversions <- readRDS("conversions.Rds")
+
+df <- df.preprocessed <- df.preprocessed.orig <- filter(df0,
+        publication_year >=  min(timespan) & publication_year <= max(timespan))
 
 # Summarize the data and discarded entries
 tmp <- generate_summary_tables(df.preprocessed, df.orig, output.folder)
@@ -23,7 +19,6 @@ summaries <- c("overview",
 	       "gender",
 	       "topic",
 	       "language",
-	       "title",
 	       "publicationyear",
 	       "size",	       
 	       "pagecount",
@@ -31,12 +26,8 @@ summaries <- c("overview",
 	       "physical_dimension",
 	       "Paper")
 
-df <- df.preprocessed
-
-# Output file paths		      
-outputs <- c()
-
 # Generate the markdown summaries
+outputs <- c()
 for (id in summaries) {
   this.folder <- getwd()
   outputs[[id]] <- knit(input = paste(id, ".Rmd", sep = ""), 

### 2021-01-18 inst/examples/title.Rmd
ok

@@
        scale_y_log10() +
-       labs(y = "Entries (n)", title = Top titles)
+       labs(y = "Entries (n)", title = "Top titles")
 print(p)

### 2021-01-18 inst/examples/title.Rmd
ok

--- 2021-01-18 inst/examples/title.Rmd
@@
 ```{r summarytitle, echo=FALSE, message=FALSE, warning=FALSE, fig.width=16, fig.height=10}
+library(ggplot2)
 p <- top_plot(df, "title", ntop = ntop) +
        scale_y_log10() +
-       labs(y = "Entries (n)", title = Top titles)
+       labs(y = "Entries (n)", title = "Top titles")
 print(p)

### 2021-01-18 inst/examples/title.Rmd
ok

--- 2021-01-18 inst/examples/title.Rmd
@@
 
-```{r summarytitle, echo=FALSE, message=FALSE, warning=FALSE, fig.width=16, fig.height=10}
+```{r summarytitle, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=8}
+library(ggplot2)
 p <- top_plot(df, "title", ntop = ntop) +
        scale_y_log10() +
-       labs(y = "Entries (n)", title = Top titles)
+       labs(y = "Entries (n)", title = "Top titles")
 print(p)

### 2021-01-18 inst/examples/init.R

@@ -28,4 +28,5 @@ df.orig <- read_bibliographic_metadata("fennica_parsed.csv.gz", verbose = TRUE, 
 ntop <- 20
 author <- "Helsinki Computational History Group (COMHIS)"
 
-
+# Visualization options
+theme_set(theme_bw(20))

### 2021-01-18 inst/examples/title.Rmd
ok

@@
  * `r length(unique(df$title))` [unique titles](output.tables/title_accepted.csv)
- * `r sum(!is.na(df$title))` documents (`r round(100*mean(!is.na(df$title)))`%) have a title
- * [Discarded titles](output.tables/title_discarded.csv)
+ * `r sum(!is.na(df$title))`/`r nrow(df)` original documents (`r round(100*mean(!is.na(df$title)), 1)`%) have data
+ * `r sum(is.na(df$title))`/`r nrow(df)` documents (`r round(100*mean(is.na(df$title)), 1)`%) have missing (NA) entry
+ * [Discarded titles](output.tables/title_discarded.csv) (excluding NA entries in the original data)
 

### 2021-01-18 inst/examples/funcs.R

@@ -5132,11 +5132,11 @@ write_xtable <- function (x, filename = NULL, count = FALSE, sort.by = "Count", 
     }
   }
 
-  if (length(x) == 0) {  
-    message("The input to write_table is empty.")
-    write("The input list is empty.", file = filename)    
-    return(NULL)
-  }
+  #if (length(x) == 0) {  
+  #  message("The input to write_table is empty.")
+  #  write("The input list is empty.", file = filename)    
+  #  return(NULL)
+  #}
 
   tab <- NULL
   if (is.vector(x)) {
@@ -5231,19 +5231,19 @@ write_xtable <- function (x, filename = NULL, count = FALSE, sort.by = "Count", 
       tab <- apply(tab, 2, as.character)
     }
 
-    n <- sum(as.numeric(tab[, "Count"]), na.rm = TRUE)
-
-    ntxt <- n    
-    if (is.matrix(tab)) {
-      suppressWarnings(tab <- rbind(rep("", ncol(tab)), tab))
-      tab[1, 1] <- paste("Total count (na.rm ", na.rm, "): ", sep = "")
-      tab[1, 2] <- ntxt
-      if (ncol(tab)>2) {
-        tab[1, 3:ncol(tab)] <- rep("", ncol(tab) - 2)
-      }
-    } else {
-      tab <- c(paste("Total count:", ntxt), tab)
-    }    
+    #n <- sum(as.numeric(tab[, "Count"]), na.rm = TRUE)
+    #ntxt <- n    
+    #if (is.matrix(tab)) {
+    #  suppressWarnings(tab <- rbind(rep("", ncol(tab)), tab))
+    #  tab[1, 1] <- paste("Total count (na.rm ", na.rm, "): ", sep = "")
+    #  tab[1, 2] <- ntxt
+    #  if (ncol(tab)>2) {
+    #    tab[1, 3:ncol(tab)] <- rep("", ncol(tab) - 2)
+    #  }
+    #} else {
+    #  tab <- c(paste("Total count:", ntxt), tab)
+    #}
+    
   }
 
   if (!is.null(filename)) {

### 2021-01-18 inst/examples/title.Rmd
ok

--- 2021-01-18 inst/examples/title.Rmd
@@
  * `r length(unique(df$title))` [unique titles](output.tables/title_accepted.csv)
- * `r sum(!is.na(df$title))` documents (`r round(100*mean(!is.na(df$title)))`%) have a title
- * [Discarded titles](output.tables/title_discarded.csv)
+ * `r sum(!is.na(df$title))` / `r nrow(df)` original documents (`r round(100*mean(!is.na(df$title)), 1)`%) have entries
+ * `r sum(is.na(df$title))` / `r nrow(df)` documents (`r round(100*mean(is.na(df$title)), 1)`%) have missing (NA) entries
+ * [Discarded titles](output.tables/title_discarded.csv) (excluding NA entries in the original data)
 

### 2021-01-18 inst/examples/title.Rmd
ok

--- 2021-01-18 inst/examples/title.Rmd
@@
 
- * `r length(unique(df$title))` [unique titles](output.tables/title_accepted.csv)
- * `r sum(!is.na(df$title))` documents (`r round(100*mean(!is.na(df$title)))`%) have a title
- * [Discarded titles](output.tables/title_discarded.csv)
+ * [Unique accepted titles](output.tables/title_accepted.csv): `r length(unique(df$title))`
+ * [Unique discarded titles in original data](output.tables/title_discarded.csv) (excluding NA cases): `r as.vector(countLines(paste0(output.folder, "/title_discarded.csv")) - 1)` 
+ * Original documents (`r round(100*mean(!is.na(df$title)), 1)`%) with non-NA titles: `r sum(!is.na(df$title))` / `r nrow(df)`
+ * Original documents with missing (NA) titles `r sum(is.na(df$title))` / `r nrow(df)` documents (`r round(100*mean(is.na(df$title)), 1)`%)
 
-Top-`r ntop` titles are shown together with the number of documents.
+Top-`r ntop` titles and their title counts.
 

### 2021-01-18 inst/examples/title.Rmd
ok

--- 2021-01-18 inst/examples/title.Rmd
@@
 
- * `r length(unique(df$title))` [unique titles](output.tables/title_accepted.csv)
- * `r sum(!is.na(df$title))`/`r nrow(df)` original documents (`r round(100*mean(!is.na(df$title)), 1)`%) have data
- * `r sum(is.na(df$title))`/`r nrow(df)` documents (`r round(100*mean(is.na(df$title)), 1)`%) have missing (NA) entry
- * [Discarded titles](output.tables/title_discarded.csv) (excluding NA entries in the original data)
+ * [Unique accepted titles](output.tables/title_accepted.csv): `r length(unique(df$title))`
+ * [Unique discarded titles in original data](output.tables/title_discarded.csv) (excluding NA cases): `r as.vector(countLines(paste0(output.folder, "/title_discarded.csv")) - 1)` 
+ * Original documents with non-NA titles: `r sum(!is.na(df$title))` / `r nrow(df)` (`r round(100*mean(!is.na(df$title)), 1)`%)
+ * Original documents with missing (NA) titles `r sum(is.na(df$title))` / `r nrow(df)` documents (`r round(100*mean(is.na(df$title)), 1)`%)
 
-Top-`r ntop` titles are shown together with the number of documents.
+Top-`r ntop` titles and their title counts.
 
-```{r summarytitle, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=8}
+```{r summarytitle, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
 library(ggplot2)

### 2021-01-29 inst/examples/title.Rmd
added uniquetitles.png

@@
 date: "`r Sys.Date()`"
-output: markdown_document
+output: md_document
 ---
@@
 ```
+
+```{r uniquetitles, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
+library(ggplot2)
+p <- ggplot(df.tmp, aes(freq, color = "black"))+ geom_bar(width=0.05, colour="blue")+scale_x_log10()+ scale_y_log10()
+print(p) 
+```

### 2021-01-29 inst/examples/title.Rmd
added uniquetitles plot
updated title page

--- 2021-01-18 inst/examples/title.Rmd
@@
 ```
+
+```{r uniquetitles, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
+tab <- table(df$title)
+d <- data.frame(title = names(tab), n = as.numeric(tab))
+
+library(ggplot2)
+p <- ggplot(d, aes(x = n)) +
+       geom_histogram() +
+       scale_x_log10() +
+       scale_y_log10() +
+       labs(x = "Title duplicates (n)", y = "Documents (n)")
+print(p)
+```

### 2021-02-02 inst/examples/title.Rmd
ok
summarytitle-1.png changed

@@
 
-```{r summarytitle, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
+```{r summarytitle, echo=FALSE, message=FALSE, warning=FALSE, fig.width=6, fig.height=4}
 library(ggplot2)
-p <- top_plot(df, "title", ntop = ntop) +
-       scale_y_log10() +
+p <- top_plot(df, "title", ntop = ntop, log10 = TRUE)+
   labs(y = "Entries (n)", title = "Top titles")
@@
 ```
+
+Frequency of unique titles:
 

### 2021-02-02 inst/examples/title.Rmd
Output created: title_uniform.md

@@
 
-```{r summarytitle, echo=FALSE, message=FALSE, warning=FALSE, fig.width=6, fig.height=4}
+```{r summarytitle, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
 library(ggplot2)

### 2021-02-02 inst/examples/title_uniform.Rmd
Output created: title_uniform.md

---
title: "title_uniform"
author: ""
date: "`r Sys.Date()`"
output: md_document
---

### 2021-02-03 inst/examples/title.Rmd
change

@@
 library(ggplot2)
+theme_set(theme_bw(base_size = 12))
 p <- top_plot(df, "title", ntop = ntop, log10 = TRUE)+
@@
 library(ggplot2)
+theme_set(theme_bw(base_size = 12))
 p <- ggplot(d, aes(x = n)) +
-       geom_histogram() +
+       geom_histogram(color="black", fill="white") +
        scale_x_log10() +

### 2021-02-03 inst/examples/title_uniform.Rmd
added title_uniform

@@
 title: "title_uniform"
-author: ""
-date: "`r Sys.Date()`"
 output: md_document
 ---
+
+```{r setup, include=FALSE}
+knitr::opts_chunk$set(echo = TRUE)
+```
+
+## R Markdown
+
+This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.
+
+When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.
+You can embed an R code chunk like this:
+
+```{r cars}
+summary(cars)
+```
+
+## Including Plots
+
+You can also embed plots, for example:
+
+```{r pressure, echo=FALSE}
+plot(pressure)
+```
+
+Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

### 2021-02-04 inst/examples/title_uniform.Rmd
change added

--- 2021-02-02 inst/examples/title_uniform.Rmd
@@
 title: "title_uniform"
-author: ""
-date: "`r Sys.Date()`"
 output: md_document
 ---
+* [Unique accepted titles](output.tables/title_accepted.csv): `r length(unique(df$title_uniform))`
+ * [Unique discarded titles in original data](output.tables/title_discarded.csv) (excluding NA cases): `r as.vector(countLines(paste0(output.folder, "/title_discarded.csv")) - 1)` 
+ * Original documents with non-NA titles: `r sum(!is.na(df$title_uniform))` / `r nrow(df)` (`r round(100*mean(!is.na(df$title_uniform)), 1)`%)
+ * Original documents with missing (NA) titles `r sum(is.na(df$title_uniform))` / `r nrow(df)` documents (`r round(100*mean(is.na(df$title_uniform)), 1)`%)
+
+Top-`r ntop` titles and their title counts.
+
+```{r summarytitle, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
+library(ggplot2)
+theme_set(theme_bw(base_size = 12))
+p <- top_plot(df, "title_uniform", ntop = ntop, log10 = TRUE)+
+  labs(y = "Entries (n)", title = "Top titles")
+print(p)
+```

### 2021-02-04 inst/examples/title_uniform.Rmd
plot added

@@
 ```
+
+Frequency of unique titles:
+
+```{r uniquetitles, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
+tab <- table(df$title)
+d <- data.frame(title = names(tab), n = as.numeric(tab))
+
+library(ggplot2)
+theme_set(theme_bw(base_size = 12))
+p <- ggplot(d, aes(x = n)) +
+  geom_histogram(color="black", fill="white") +
+  scale_x_log10() +
+  scale_y_log10() +
+  labs(x = "Title duplicates (n)", y = "Documents (n)")
+print(p)
+```

### 2021-02-04 inst/examples/title_uniform.Rmd
changes

@@
 * [Unique accepted titles](output.tables/title_accepted.csv): `r length(unique(df$title_uniform))`
- * [Unique discarded titles in original data](output.tables/title_discarded.csv) (excluding NA cases): `r as.vector(countLines(paste0(output.folder, "/title_discarded.csv")) - 1)` 
+ * [Unique discarded titles in original data](output.tables/title_discarded.csv) (excluding NA cases): `r as.vector(countLines(paste0(output.folder, "/title_uniform_discarded.csv")) - 1)` 
  * Original documents with non-NA titles: `r sum(!is.na(df$title_uniform))` / `r nrow(df)` (`r round(100*mean(!is.na(df$title_uniform)), 1)`%)

### 2021-02-04 inst/examples/title_uniform.Rmd
added chunk options

--- 2021-02-04 inst/examples/title_uniform.Rmd
@@
 ---
-* [Unique accepted titles](output.tables/title_accepted.csv): `r length(unique(df$title_uniform))`
- * [Unique discarded titles in original data](output.tables/title_discarded.csv) (excluding NA cases): `r as.vector(countLines(paste0(output.folder, "/title_discarded.csv")) - 1)` 
- * Original documents with non-NA titles: `r sum(!is.na(df$title_uniform))` / `r nrow(df)` (`r round(100*mean(!is.na(df$title_uniform)), 1)`%)
- * Original documents with missing (NA) titles `r sum(is.na(df$title_uniform))` / `r nrow(df)` documents (`r round(100*mean(is.na(df$title_uniform)), 1)`%)
 
-Top-`r ntop` titles and their title counts.
+```{r setup, include=FALSE}
+knitr::opts_chunk$set(echo = TRUE)
+knitr::opts_chunk$set(fig.path=paste0("rmd_", field, "_"))
+```
 
-```{r summarytitle, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
-library(ggplot2)
-theme_set(theme_bw(base_size = 12))
-p <- top_plot(df, "title_uniform", ntop = ntop, log10 = TRUE)+
-  labs(y = "Entries (n)", title = "Top titles")
-print(p)
+## R Markdown
+
+This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.
+
+When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.
+You can embed an R code chunk like this:
+
+```{r cars}
+summary(cars)
 ```
+
+## Including Plots
+
+You can also embed plots, for example:
+
+```{r pressure, echo=FALSE}
+plot(pressure)
+```
+
+Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

### 2021-02-04 inst/examples/title_uniform.Rmd

--- 2021-02-04 inst/examples/title_uniform.Rmd
@@
 ---
+
+```{r setup, include=FALSE}
+knitr::opts_chunk$set(echo = TRUE)
+knitr::opts_chunk$set(fig.path=paste0("figure/rmd_", field, "_"))
+```
+
  * [Unique accepted titles](output.tables/title_accepted.csv): `r length(unique(df$title_uniform))`
- * [Unique discarded titles in original data](output.tables/title_discarded.csv) (excluding NA cases): `r as.vector(countLines(paste0(output.folder, "/title_discarded.csv")) - 1)` 
+ * [Unique discarded titles in original data](output.tables/title_discarded.csv) (excluding NA cases): `r as.vector(countLines(paste0(output.folder, "/title_uniform_discarded.csv")) - 1)` 
  * Original documents with non-NA titles: `r sum(!is.na(df$title_uniform))` / `r nrow(df)` (`r round(100*mean(!is.na(df$title_uniform)), 1)`%)

### 2021-02-09 inst/examples/corporate.Rmd
change

---
title: "corporate"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

### 2021-02-09 inst/examples/note_dissertation.Rmd
change

---
title: "note_dissertation"
output: md_document
---
 * [Unique accepted titles](output.tables/title_accepted.csv): `r length(unique(df$note_dissertation))`
 * [Unique discarded titles in original data](output.tables/title_discarded.csv) (excluding NA cases): `r as.vector(countLines(paste0(output.folder, "/note_dissertation_discarded.csv")) - 1)` 
 * Original documents with non-NA titles: `r sum(!is.na(df$note_dissertation))` / `r nrow(df)` (`r round(100*mean(!is.na(df$note_dissertation)), 1)`%)
 * Original documents with missing (NA) titles `r sum(is.na(df$note_dissertation))` / `r nrow(df)` documents (`r round(100*mean(is.na(df$note_dissertation)), 1)`%)

 Top-`r ntop` titles and their title counts.

```{r summarytitle, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
library(ggplot2)
theme_set(theme_bw(base_size = 12))
p <- top_plot(df, "note_dissertation", ntop = ntop, log10 = TRUE)+
  labs(y = "Entries (n)", title = "Top titles")
print(p)
```

Frequency of unique titles:

```{r uniquetitles, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
tab <- table(df$note_dissertation)
d <- data.frame(title = names(tab), n = as.numeric(tab))

library(ggplot2)
theme_set(theme_bw(base_size = 12))
p <- ggplot(d, aes(x = n)) +
  geom_histogram(color="black", fill="white") +
  scale_x_log10() +
  scale_y_log10() +
  labs(x = "Title duplicates (n)", y = "Documents (n)")
print(p)
```

### 2021-02-09 inst/examples/note_granter.Rmd
change

---
title: "note_granter"
output: md_document
---
* [Unique accepted titles](output.tables/title_accepted.csv): `r length(unique(df$note_granter))`
 * [Unique discarded titles in original data](output.tables/title_discarded.csv) (excluding NA cases): `r as.vector(countLines(paste0(output.folder, "/note_granter_discarded.csv")) - 1)` 
 * Original documents with non-NA titles: `r sum(!is.na(df$note_granter))` / `r nrow(df)` (`r round(100*mean(!is.na(df$note_granter)), 1)`%)
 * Original documents with missing (NA) titles `r sum(is.na(df$note_granter))` / `r nrow(df)` documents (`r round(100*mean(is.na(df$note_granter)), 1)`%)

 Top-`r ntop` titles and their title counts.

```{r summarytitle, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
library(ggplot2)
theme_set(theme_bw(base_size = 12))
p <- top_plot(df, "note_granter", ntop = ntop, log10 = TRUE)+
  labs(y = "Entries (n)", title = "Top titles")
print(p)
```

Frequency of unique titles:

```{r uniquetitles, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
tab <- table(df$note_granter)
d <- data.frame(title = names(tab), n = as.numeric(tab))

library(ggplot2)
theme_set(theme_bw(base_size = 12))
p <- ggplot(d, aes(x = n)) +
  geom_histogram(color="black", fill="white") +
  scale_x_log10() +
  scale_y_log10() +
  labs(x = "Title duplicates (n)", y = "Documents (n)")
print(p)
```

### 2021-02-09 inst/examples/note_source.Rmd
change

---
title: "note_source"
output: md_document
---

* [Unique accepted titles](output.tables/title_accepted.csv): `r length(unique(df$note_source)`
* [Unique discarded titles in original data](output.tables/title_discarded.csv) (excluding NA cases): `r as.vector(countLines(paste0(output.folder, "/note_source_discarded.csv")) - 1)` 
* Original documents with non-NA titles: `r sum(!is.na(df$note_source))` / `r nrow(df)` (`r round(100*mean(!is.na(df$note_source)), 1)`%)
* Original documents with missing (NA) titles `r sum(is.na(df$note_source))` / `r nrow(df)` documents (`r round(100*mean(is.na(df$note_source)), 1)`%)

 Top-`r ntop` titles and their title counts.

```{r summarytitle, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
library(ggplot2)
theme_set(theme_bw(base_size = 12))
p <- top_plot(df, "note_source", ntop = ntop, log10 = TRUE)+
  labs(y = "Entries (n)", title = "Top titles")
print(p)
```

Frequency of unique titles:

```{r uniquetitles, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
tab <- table(df$note_source)
d <- data.frame(title = names(tab), n = as.numeric(tab))

library(ggplot2)
theme_set(theme_bw(base_size = 12))
p <- ggplot(d, aes(x = n)) +
  geom_histogram(color="black", fill="white") +
  scale_x_log10() +
  scale_y_log10() +
  labs(x = "Title duplicates (n)", y = "Documents (n)")
print(p)
```

### 2021-02-10 inst/examples/corporate.Rmd
da

@@
 title: "corporate"
-output: html_document
+output: md_document
 ---
@@
 knitr::opts_chunk$set(echo = TRUE)
+knitr::opts_chunk$set(fig.path=paste0("figure/rmd_", field, "_"))
 ```
 
-## R Markdown
+* [Unique accepted titles](output.tables/title_accepted.csv): `r length(unique(df$corporate))`
+* [Unique discarded titles in original data](output.tables/title_discarded.csv) (excluding NA cases): `r as.vector(countLines(paste0(output.folder, "/corporate_discarded.csv")) - 1)` 
+* Original documents with non-NA titles: `r sum(!is.na(df$corporate))` / `r nrow(df)` (`r round(100*mean(!is.na(df$corporate)), 1)`%)
+* Original documents with missing (NA) titles `r sum(is.na(df$corporate)` / `r nrow(df)` documents (`r round(100*mean(is.na(df$corporate)), 1)`%)
 
-This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.
+ Top-`r ntop` titles and their title counts.
 
-When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.
-You can embed an R code chunk like this:
-
-```{r cars}
-summary(cars)
+```{r summarytitle, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
+library(ggplot2)
+theme_set(theme_bw(base_size = 12))
+p <- top_plot(df, "corporate", ntop = ntop, log10 = TRUE)+
+  labs(y = "Entries (n)", title = "Top titles")
+print(p)
 ```
 
-## Including Plots
+Frequency of unique titles:
 
-You can also embed plots, for example:
+```{r uniquetitles, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
+tab <- table(df$corporate)
+d <- data.frame(title = names(tab), n = as.numeric(tab))
 
-```{r pressure, echo=FALSE}
-plot(pressure)
+library(ggplot2)
+theme_set(theme_bw(base_size = 12))
+p <- ggplot(d, aes(x = n)) +
+  geom_histogram(color="black", fill="white") +
+  scale_x_log10() +
+  scale_y_log10() +
+  labs(x = "Title duplicates (n)", y = "Documents (n)")
+print(p)
 ```
-
-Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

### 2021-02-10 inst/examples/holder.Rmd
change
da

--- 2021-02-09 inst/examples/corporate.Rmd
@@
 ---
-title: "corporate"
-output: html_document
+title: "holder"
+output: md_document
 ---
@@
 knitr::opts_chunk$set(echo = TRUE)
+knitr::opts_chunk$set(fig.path=paste0("figure/rmd_", field, "_"))
 ```
 
-## R Markdown
+* [Unique accepted titles](output.tables/title_accepted.csv): `r length(unique(df$holder))`
+* [Unique discarded titles in original data](output.tables/title_discarded.csv) (excluding NA cases): `r as.vector(countLines(paste0(output.folder, "/holder_discarded.csv")) - 1)` 
+* Original documents with non-NA titles: `r sum(!is.na(df$holder))` / `r nrow(df)` (`r round(100*mean(!is.na(df$holder)), 1)`%)
+* Original documents with missing (NA) titles `r sum(is.na(df$holder))` / `r nrow(df)` documents (`r round(100*mean(is.na(df$holder)), 1)`%)
 
-This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.
+ Top-`r ntop` titles and their title counts.
 
-When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.
-You can embed an R code chunk like this:
-
-```{r cars}
-summary(cars)
+```{r summarytitle, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
+library(ggplot2)
+theme_set(theme_bw(base_size = 12))
+p <- top_plot(df, "holder", ntop = ntop, log10 = TRUE)+
+  labs(y = "Entries (n)", title = "Top titles")
+print(p)
 ```
 
-## Including Plots
+Frequency of unique titles:
 
-You can also embed plots, for example:
+```{r uniquetitles, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
+tab <- table(df$holder)
+d <- data.frame(title = names(tab), n = as.numeric(tab))
 
-```{r pressure, echo=FALSE}
-plot(pressure)
+library(ggplot2)
+theme_set(theme_bw(base_size = 12))
+p <- ggplot(d, aes(x = n)) +
+  geom_histogram(color="black", fill="white") +
+  scale_x_log10() +
+  scale_y_log10() +
+  labs(x = "Title duplicates (n)", y = "Documents (n)")
+print(p)
 ```
-
-Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

### 2021-02-10 inst/examples/note_510c.Rmd
change
da

--- 2021-02-09 inst/examples/corporate.Rmd
@@
 ---
-title: "corporate"
-output: html_document
+title: "note_510c"
+output: md_document
 ---
@@
 knitr::opts_chunk$set(echo = TRUE)
+knitr::opts_chunk$set(fig.path=paste0("figure/rmd_", field, "_"))
 ```
 
-## R Markdown
+* [Unique accepted titles](output.tables/title_accepted.csv): `r length(unique(df$note_510c))`
+* [Unique discarded titles in original data](output.tables/title_discarded.csv) (excluding NA cases): `r as.vector(countLines(paste0(output.folder, "/note_510c_discarded.csv")) - 1)` 
+* Original documents with non-NA titles: `r sum(!is.na(df$note_510c))` / `r nrow(df)` (`r round(100*mean(!is.na(df$note_510c)), 1)`%)
+* Original documents with missing (NA) titles `r sum(is.na(df$note_510c)` / `r nrow(df)` documents (`r round(100*mean(is.na(df$note_510c)), 1)`%)
 
-This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.
+ Top-`r ntop` titles and their title counts.
 
-When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.
-You can embed an R code chunk like this:
-
-```{r cars}
-summary(cars)
+```{r summarytitle, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
+library(ggplot2)
+theme_set(theme_bw(base_size = 12))
+p <- top_plot(df, "note_510c", ntop = ntop, log10 = TRUE)+
+  labs(y = "Entries (n)", title = "Top titles")
+print(p)
 ```
 
-## Including Plots
+Frequency of unique titles:
 
-You can also embed plots, for example:
+```{r uniquetitles, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
+tab <- table(df$note_510c)
+d <- data.frame(title = names(tab), n = as.numeric(tab))
 
-```{r pressure, echo=FALSE}
-plot(pressure)
+library(ggplot2)
+theme_set(theme_bw(base_size = 12))
+p <- ggplot(d, aes(x = n)) +
+  geom_histogram(color="black", fill="white") +
+  scale_x_log10() +
+  scale_y_log10() +
+  labs(x = "Title duplicates (n)", y = "Documents (n)")
+print(p)
 ```
-
-Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

### 2021-02-10 inst/examples/note_granter.Rmd
da

@@
 ---
+
+```{r setup, include=FALSE}
+knitr::opts_chunk$set(echo = TRUE)
+knitr::opts_chunk$set(fig.path=paste0("figure/rmd_", field, "_"))
+```
+
 * [Unique accepted titles](output.tables/title_accepted.csv): `r length(unique(df$note_granter))`

### 2021-02-10 inst/examples/subject_topic.Rmd
change
da

--- 2021-02-09 inst/examples/corporate.Rmd
@@
 ---
-title: "corporate"
-output: html_document
+title: "subject_topic"
+output: md_document
 ---
@@
 knitr::opts_chunk$set(echo = TRUE)
+knitr::opts_chunk$set(fig.path=paste0("figure/rmd_", field, "_"))
 ```
 
-## R Markdown
+* [Unique accepted titles](output.tables/title_accepted.csv): `r length(unique(df$subject_topic))`
+* [Unique discarded titles in original data](output.tables/title_discarded.csv) (excluding NA cases): `r as.vector(countLines(paste0(output.folder, "/subject_topic_discarded.csv")) - 1)` 
+* Original documents with non-NA titles: `r sum(!is.na(df$subject_topic))` / `r nrow(df)` (`r round(100*mean(!is.na(df$subject_topic)), 1)`%)
+* Original documents with missing (NA) titles `r sum(is.na(df$subject_topic)` / `r nrow(df)` documents (`r round(100*mean(is.na(df$subject_topic)), 1)`%)
 
-This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.
+ Top-`r ntop` titles and their title counts.
 
-When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.
-You can embed an R code chunk like this:
-
-```{r cars}
-summary(cars)
+```{r summarytitle, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
+library(ggplot2)
+theme_set(theme_bw(base_size = 12))
+p <- top_plot(df, "subject_topic", ntop = ntop, log10 = TRUE)+
+  labs(y = "Entries (n)", title = "Top titles")
+print(p)
 ```
 
-## Including Plots
+Frequency of unique titles:
 
-You can also embed plots, for example:
+```{r uniquetitles, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
+tab <- table(df$subject_topic)
+d <- data.frame(title = names(tab), n = as.numeric(tab))
 
-```{r pressure, echo=FALSE}
-plot(pressure)
+library(ggplot2)
+theme_set(theme_bw(base_size = 12))
+p <- ggplot(d, aes(x = n)) +
+  geom_histogram(color="black", fill="white") +
+  scale_x_log10() +
+  scale_y_log10() +
+  labs(x = "Title duplicates (n)", y = "Documents (n)")
+print(p)
 ```
-
-Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

### 2021-02-10 inst/examples/successor.Rmd
change
da

--- 2021-02-09 inst/examples/corporate.Rmd
@@
 ---
-title: "corporate"
-output: html_document
+title: "successor"
+output: md_document
 ---
@@
 knitr::opts_chunk$set(echo = TRUE)
+knitr::opts_chunk$set(fig.path=paste0("figure/rmd_", field, "_"))
 ```
 
-## R Markdown
+* [Unique accepted titles](output.tables/title_accepted.csv): `r length(unique(df$successor))`
+* [Unique discarded titles in original data](output.tables/title_discarded.csv) (excluding NA cases): `r as.vector(countLines(paste0(output.folder, "/successor_discarded.csv")) - 1)` 
+* Original documents with non-NA titles: `r sum(!is.na(df$successor))` / `r nrow(df)` (`r round(100*mean(!is.na(df$successor)), 1)`%)
+* Original documents with missing (NA) titles `r sum(is.na(df$successor))` / `r nrow(df)` documents (`r round(100*mean(is.na(df$successor)), 1)`%)
 
-This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.
+ Top-`r ntop` titles and their title counts.
 
-When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.
-You can embed an R code chunk like this:
-
-```{r cars}
-summary(cars)
+```{r summarytitle, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
+library(ggplot2)
+theme_set(theme_bw(base_size = 12))
+p <- top_plot(df, "successor", ntop = ntop, log10 = TRUE)+
+  labs(y = "Entries (n)", title = "Top titles")
+print(p)
 ```
 
-## Including Plots
+Frequency of unique titles:
 
-You can also embed plots, for example:
+```{r uniquetitles, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
+tab <- table(df$successor)
+d <- data.frame(title = names(tab), n = as.numeric(tab))
 
-```{r pressure, echo=FALSE}
-plot(pressure)
+library(ggplot2)
+theme_set(theme_bw(base_size = 12))
+p <- ggplot(d, aes(x = n)) +
+  geom_histogram(color="black", fill="white") +
+  scale_x_log10() +
+  scale_y_log10() +
+  labs(x = "Title duplicates (n)", y = "Documents (n)")
+print(p)
 ```
-
-Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

### 2021-02-10 inst/examples/uncontrolled.Rmd
change
da

--- 2021-02-09 inst/examples/corporate.Rmd
@@
 ---
-title: "corporate"
-output: html_document
+title: "uncontrolled"
+output: md_document
 ---
@@
 knitr::opts_chunk$set(echo = TRUE)
+knitr::opts_chunk$set(fig.path=paste0("figure/rmd_", field, "_"))
 ```
 
-## R Markdown
+* [Unique accepted titles](output.tables/title_accepted.csv): `r length(unique(df$uncontrolled))`
+* [Unique discarded titles in original data](output.tables/title_discarded.csv) (excluding NA cases): `r as.vector(countLines(paste0(output.folder, "/uncontrolled_discarded.csv")) - 1)` 
+* Original documents with non-NA titles: `r sum(!is.na(df$uncontrolled))` / `r nrow(df)` (`r round(100*mean(!is.na(df$uncontrolled)), 1)`%)
+* Original documents with missing (NA) titles `r sum(is.na(df$uncontrolled))` / `r nrow(df)` documents (`r round(100*mean(is.na(df$uncontrolled)), 1)`%)
 
-This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.
+ Top-`r ntop` titles and their title counts.
 
-When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.
-You can embed an R code chunk like this:
-
-```{r cars}
-summary(cars)
+```{r summarytitle, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
+library(ggplot2)
+theme_set(theme_bw(base_size = 12))
+p <- top_plot(df, "uncontrolled", ntop = ntop, log10 = TRUE)+
+  labs(y = "Entries (n)", title = "Top titles")
+print(p)
 ```
 
-## Including Plots
+Frequency of unique titles:
 
-You can also embed plots, for example:
+```{r uniquetitles, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
+tab <- table(df$uncontrolled)
+d <- data.frame(title = names(tab), n = as.numeric(tab))
 
-```{r pressure, echo=FALSE}
-plot(pressure)
+library(ggplot2)
+theme_set(theme_bw(base_size = 12))
+p <- ggplot(d, aes(x = n)) +
+  geom_histogram(color="black", fill="white") +
+  scale_x_log10() +
+  scale_y_log10() +
+  labs(x = "Title duplicates (n)", y = "Documents (n)")
+print(p)
 ```
-
-Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

### 2021-02-10 inst/examples/corporate.R

@@ -1,2 +1,46 @@
+
+field <- "corporate"
+df.tmp <- data.frame(df.orig[[field]])
 df.tmp <- data.frame(corporate = polish_corporate(df.orig[[field]]))
+names(df.tmp) <- field
+
+# Raw data
+original <- df.orig[[field]]
+
+# Harmonize the raw data
+x <- fennica::polish_title(original)
+
+# Collect the results into a data.frame
+df.tmp <- data.frame(original_row = df.orig$original_row,
+                     corporate = x)
+
+# Store the title field data
+# FIXME: convert to feather or plain CSV
+data.file <- paste0(field, ".Rds")
+saveRDS(df.tmp, file = data.file)
+
+# ------------------------------------------------------------
+
+# Generate data summaries
+
+message("Accepted entries in the preprocessed data")
+s <- write_xtable(df.tmp[[field]], paste(output.folder, field, "_accepted.csv", sep = ""), count = TRUE)
+
+message("Discarded entries in the original data")
+
+# NA values in the final harmonized data
+inds <- which(is.na(df.tmp[[field]]))
+
+# Original entries that were converted into NA
+original.na <- df.orig[match(df.tmp$original_row[inds], df.orig$original_row), field]
+
+# .. ie. those are "discarded" cases; list them in a table
+tmp <- write_xtable(original.na, paste(output.folder, field, "_discarded.csv", sep = ""), count = TRUE)
+
+# ------------------------------------------------------------
+
+# Generate markdown summary in note_source.md
+df <- readRDS(data.file)
+tmp <- knit(input = paste(field, ".Rmd", sep = ""), 
+            output = paste(field, ".md", sep = ""))
 

### 2021-02-10 inst/examples/note_510c.R

@@ -1,2 +1,44 @@
+
+field <- "note_510c"
 df.tmp <- data.frame(df.orig[[field]])
 names(df.tmp) <- field
+
+# Raw data
+original <- df.orig[[field]]
+
+# Harmonize the raw data
+x <- fennica::polish_title(original)
+
+# Collect the results into a data.frame
+df.tmp <- data.frame(original_row = df.orig$original_row,
+                     note_510c = x)
+
+# Store the title field data
+# FIXME: convert to feather or plain CSV
+data.file <- paste0(field, ".Rds")
+saveRDS(df.tmp, file = data.file)
+
+# ------------------------------------------------------------
+
+# Generate data summaries
+
+message("Accepted entries in the preprocessed data")
+s <- write_xtable(df.tmp[[field]], paste(output.folder, field, "_accepted.csv", sep = ""), count = TRUE)
+
+message("Discarded entries in the original data")
+
+# NA values in the final harmonized data
+inds <- which(is.na(df.tmp[[field]]))
+
+# Original entries that were converted into NA
+original.na <- df.orig[match(df.tmp$original_row[inds], df.orig$original_row), field]
+
+# .. ie. those are "discarded" cases; list them in a table
+tmp <- write_xtable(original.na, paste(output.folder, field, "_discarded.csv", sep = ""), count = TRUE)
+
+# ------------------------------------------------------------
+
+# Generate markdown summary in note_source.md
+df <- readRDS(data.file)
+tmp <- knit(input = paste(field, ".Rmd", sep = ""), 
+            output = paste(field, ".md", sep = ""))

### 2021-02-10 inst/examples/uncontrolled.R

@@ -1,1 +1,45 @@
+
+field <- "uncontrolled"
+df.tmp <- data.frame(df.orig[[field]])
 df.tmp <- data.frame(corporate = polish_corporate(df.orig[[field]]))
+names(df.tmp) <- field
+
+# Raw data
+original <- df.orig[[field]]
+
+# Harmonize the raw data
+x <- fennica::polish_title(original)
+
+# Collect the results into a data.frame
+df.tmp <- data.frame(original_row = df.orig$original_row,
+                     uncontrolled = x)
+
+# Store the title field data
+# FIXME: convert to feather or plain CSV
+data.file <- paste0(field, ".Rds")
+saveRDS(df.tmp, file = data.file)
+
+# ------------------------------------------------------------
+
+# Generate data summaries
+
+message("Accepted entries in the preprocessed data")
+s <- write_xtable(df.tmp[[field]], paste(output.folder, field, "_accepted.csv", sep = ""), count = TRUE)
+
+message("Discarded entries in the original data")
+
+# NA values in the final harmonized data
+inds <- which(is.na(df.tmp[[field]]))
+
+# Original entries that were converted into NA
+original.na <- df.orig[match(df.tmp$original_row[inds], df.orig$original_row), field]
+
+# .. ie. those are "discarded" cases; list them in a table
+tmp <- write_xtable(original.na, paste(output.folder, field, "_discarded.csv", sep = ""), count = TRUE)
+
+# ------------------------------------------------------------
+
+# Generate markdown summary in note_source.md
+df <- readRDS(data.file)
+tmp <- knit(input = paste(field, ".Rmd", sep = ""), 
+            output = paste(field, ".md", sep = ""))

### 2021-02-11 inst/examples/note_510c.Rmd

@@
 * Original documents with non-NA titles: `r sum(!is.na(df$note_510c))` / `r nrow(df)` (`r round(100*mean(!is.na(df$note_510c)), 1)`%)
-* Original documents with missing (NA) titles `r sum(is.na(df$note_510c)` / `r nrow(df)` documents (`r round(100*mean(is.na(df$note_510c)), 1)`%)
+* Original documents with missing (NA) titles `r sum(is.na(df$note_510c))` / `r nrow(df)` documents (`r round(100*mean(is.na(df$note_510c)), 1)`%)
 

### 2021-02-11 inst/examples/subject_topic.Rmd
change

@@
 * Original documents with non-NA titles: `r sum(!is.na(df$subject_topic))` / `r nrow(df)` (`r round(100*mean(!is.na(df$subject_topic)), 1)`%)
-* Original documents with missing (NA) titles `r sum(is.na(df$subject_topic)` / `r nrow(df)` documents (`r round(100*mean(is.na(df$subject_topic)), 1)`%)
+* Original documents with missing (NA) titles `r sum(is.na(df$subject_topic))` / `r nrow(df)` documents (`r round(100*mean(is.na(df$subject_topic)), 1)`%)
 

### 2021-02-11 inst/examples/main.R

@@ -9,42 +9,46 @@ source("init.R")
 #           PREPROCESS DATA
 # ----------------------------------------------------
 
+#corporate field
+source("corporate.R")
+
+#holder field
+source("holder.R")
+
+#note_510c field
+source("note_510c.R")
+
+#note_dissertation field
+source("note_dissertation.R")
+
+#note_granter field
+source("note_granter.R")
+
+#note_source field
+source("note_source.R")
+
+#note_subject_topic field
+source("subject_topic.R")
+
+#successor field
+source("successor.R")
+
 # Title field
 source("title.R")
 
 # Title_uniform field
 source("title_uniform.R")
 
-#note_source field
-source("note_source.R")
-
 #uncontrolled field
 source("uncontrolled.R")
 
-#successor field
-source("successor.R")
 
-#holder field
-source("holder.R")
 
-#note_granter field
-source("note_granter.R")
 
-#note_subject_topic field
-source("note_subject_topic.R")
 
-#note_510c field
-source("note_510c.R")
 
-#corporate field
-source("corporate.R")
 
-#note_dissertation field
-source("note_dissertation.R")
 
-#note_510c field
-source("note_510c.R")
 
-#corporate field
-source("corporate.R")
+
 

### 2021-02-11 inst/examples/overview.Rmd

--- 2021-01-12 inst/examples/overview.Rmd
@@
 
-# Preprocessing summary
+# Fennica preprocessing summary
 
-The data spanning years `r min(na.omit(df$publication_year))`-`r max(na.omit(df$publication_year))` has been included and contains `r nrow(df.preprocessed)` documents (also other filter may apply depending on the data collection, see the source code for details.
+The original data set contains `r nrow(df.orig)` documents.
 
-## Specific fields
+The following fields have been harmonized.
 
@@
 
-## Annotated documents
-
-  * `r nrow(df.orig)` documents in the original raw data
-  * `r nrow(df)` documents in the final preprocessed data (`r round(100 * nrow(df)/nrow(df.orig), 2)`%)
-
-Fraction of documents with data:
-
-```{r summaryannotations, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=8, fig.height=11}
-availability <- field_availability(df)
-print(availability$plot)
-```
-
-Same in exact numbers: documents with available/missing entries, and number of unique entries for each field. Sorted by missing data:
-
-```{r sumtab, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE}
-tab <- availability$table %<>% arrange(n)
-names(tab) <- gsub("missing", "missing (%)", names(tab))
-names(tab) <- gsub("available", "available (%)", names(tab))
-names(tab) <- gsub("^n$", "available (n)", names(tab))
-names(tab) <- gsub("unique_entries", "unique (n)", names(tab))
-names(tab) <- gsub("field_name", "field name", names(tab))
-kable(tab[, c(1, 3, 2, 4, 5)], digits = 1, caption = "Data availability")
-rm(tab);gc()
-```
-
-## Field conversions
-
-This documents the conversions from raw data to the final preprocessed version (accepted, discarded, conversions).
-Only some of the key tables are explicitly linked below.
-The complete list of all summary tables is [here](output.tables/).
-
-Brief description of the fields:
-
- * [Description of the original MARC fields](https://github.com/COMHIS/fennica/blob/master/inst/extdata/fieldnames.csv)
-
- * [Description of the preprocessed fields](https://github.com/COMHIS/fennica/blob/master/inst/extdata/fieldname_table.csv)
-
-## Histograms of all entries for numeric variables
-
-```{r summary-histograms, echo=FALSE, message=FALSE, warning=FALSE, fig.width=5, fig.height=4, fig.show='hold', out.width="200px"}
-num <- c();
-for (field in names(df)) {num[[field]] <- is.numeric(df[[field]])}
-numeric.fields <- setdiff(names(which(num)), c("row.index", "original_row", "unity"))
-for (field in numeric.fields) {
-  x <- log10(min(df[[field]], na.rm = TRUE)/2 + df[[field]])
-  x <- x[!is.na(x) & !is.nan(x)]
-  if (length(x) > 0) {
-    hist(x, 30,
-       main = paste(field, "histogram"),
-       ylab = "Documents",
-       xlab = paste(field, "(log10)")
-       )
-  }
-}
-```
-
-## Histograms of the top entries for factor variables
-
-Non-trivial factors with at least 2 levels are shown.
-
-```{r summary-bars, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=5, fig.show='hold', out.width="430px"}
-fac <- c(); for (field in names(df)) {fac[[field]] <- is.factor(df[[field]])}
-factor.fields <- names(which(fac))
-for (field in factor.fields) {
-  n <- min(length(unique(df[[field]])), ntop)
-  if (length(n) > 1) {
-    p <- top_plot(df, field, n)  
-    p <- p + ggtitle(paste("Top ", field))
-    p <- p + scale_y_log10()
-    p <- p + ylab("Documents (Log10)")
-    print(p)
-  }
-}
-```
+See also [further preprocessing details](details.Rmd).

### 2021-02-11 inst/examples/corporate.Rmd

@@
 * Original documents with non-NA titles: `r sum(!is.na(df$corporate))` / `r nrow(df)` (`r round(100*mean(!is.na(df$corporate)), 1)`%)
-* Original documents with missing (NA) titles `r sum(is.na(df$corporate)` / `r nrow(df)` documents (`r round(100*mean(is.na(df$corporate)), 1)`%)
+* Original documents with missing (NA) titles `r sum(is.na(df$corporate))` / `r nrow(df)` documents (`r round(100*mean(is.na(df$corporate)), 1)`%)
 

### 2021-02-11 inst/examples/details.Rmd

@@
 ---
-title: "Details"
-output: 
-  flexdashboard::flex_dashboard:
-    orientation: columns
-    vertical_layout: fill
+title: "Preprocessing details"
+author: "`r author`"
+date: "`r Sys.Date()`"
+output: markdown_document
 ---
 
-```{r setup, include=FALSE}
-library(flexdashboard)
+## Annotated documents
+
+Fraction of documents with data:
+
+```{r summaryannotations, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=8, fig.height=11}
+availability <- field_availability(df)
+print(availability$plot)
 ```
 
-Column {data-width=650}
------------------------------------------------------------------------
+Same in exact numbers: documents with available/missing entries, and number of unique entries for each field. Sorted by missing data:
 
-### Chart A
-
-```{r}
-
+```{r sumtab, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE}
+tab <- availability$table %<>% arrange(n)
+names(tab) <- gsub("missing", "missing (%)", names(tab))
+names(tab) <- gsub("available", "available (%)", names(tab))
+names(tab) <- gsub("^n$", "available (n)", names(tab))
+names(tab) <- gsub("unique_entries", "unique (n)", names(tab))
+names(tab) <- gsub("field_name", "field name", names(tab))
+kable(tab[, c(1, 3, 2, 4, 5)], digits = 1, caption = "Data availability")
+rm(tab);gc()
 ```
 
-Column {data-width=350}
------------------------------------------------------------------------
+## Field conversions
 
-### Chart B
+This documents the conversions from raw data to the final preprocessed version (accepted, discarded, conversions).
+Only some of the key tables are explicitly linked below.
+The complete list of all summary tables is [here](output.tables/).
 
-```{r}
+Brief description of the fields:
 
+ * [Description of the original MARC fields](https://github.com/COMHIS/fennica/blob/master/inst/extdata/fieldnames.csv)
+
+ * [Description of the preprocessed fields](https://github.com/COMHIS/fennica/blob/master/inst/extdata/fieldname_table.csv)
+
+## Histograms of all entries for numeric variables
+
+```{r summary-histograms, echo=FALSE, message=FALSE, warning=FALSE, fig.width=5, fig.height=4, fig.show='hold', out.width="200px"}
+num <- c();
+for (field in names(df)) {num[[field]] <- is.numeric(df[[field]])}
+numeric.fields <- setdiff(names(which(num)), c("row.index", "original_row", "unity"))
+for (field in numeric.fields) {
+  x <- log10(min(df[[field]], na.rm = TRUE)/2 + df[[field]])
+  x <- x[!is.na(x) & !is.nan(x)]
+  if (length(x) > 0) {
+    hist(x, 30,
+       main = paste(field, "histogram"),
+       ylab = "Documents",
+       xlab = paste(field, "(log10)")
+       )
+  }
+}
 ```
 
-### Chart C
+## Histograms of the top entries for factor variables
 
-```{r}
+Non-trivial factors with at least 2 levels are shown.
 
+```{r summary-bars, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=5, fig.show='hold', out.width="430px"}
+fac <- c(); for (field in names(df)) {fac[[field]] <- is.factor(df[[field]])}
+factor.fields <- names(which(fac))
+for (field in factor.fields) {
+  n <- min(length(unique(df[[field]])), ntop)
+  if (length(n) > 1) {
+    p <- top_plot(df, field, n)  
+    p <- p + ggtitle(paste("Top ", field))
+    p <- p + scale_y_log10()
+    p <- p + ylab("Documents (Log10)")
+    print(p)
+  }
+}
 ```
+
+Fields of special interest. Real success percentage (proportion of successful conversions compared to non-NA entries in the original data):
+
+```{r missing2, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=10, fig.height=15}
+select.fields <- c("author","publication_place","publication_country","publication_year",
+                     "publication_year_from","publication_year_till","corporate","area","pagecount",
+		     "gatherings","width","height","publisher","self_published")
+
+dfs <- df
+
+success <- as.data.frame(t(apply(dfs, 2, function (x) {sum(!is.na(gsub("^NA$", NA, as.character(x))))})))
+
+original.nonNA <- as.data.frame(t(apply(select(df.orig, publication_place,
+                    publication_time, corporate, physical_extent, physical_dimension, publisher, author_name),
+		      2, function (x) {sum(!is.na(gsub("^NA$", NA, as.character(x))))})))
+
+# Compare the number of non-NA entries in preprocessed data to number
+# of non-NA entries in the original data:
+real.success <- c()
+real.success[["publication_place"]] <- success$publication_place/original.nonNA$publication_place
+real.success[["publication_country"]] <- success$publication_country/original.nonNA$publication_place
+real.success[["publication_year"]] <- success$publication_year/original.nonNA$publication_time
+real.success[["publication_year_from"]] <- success$publication_year_from/original.nonNA$publication_time
+real.success[["publication_year_till"]] <- success$publication_year_till/original.nonNA$publication_time
+real.success[["corporate"]] <- success$corporate/original.nonNA$corporate
+real.success[["publisher"]] <- success$publisher/original.nonNA$publisher
+real.success[["self_published"]] <- success$self_published/original.nonNA$publisher
+real.success[["pagecount"]] <- success$pagecount/original.nonNA$physical_extent
+real.success[["area"]] <- success$area/original.nonNA$physical_dimension
+real.success[["gatherings"]] <- success$gatherings/original.nonNA$physical_dimension
+real.success[["author"]] <- success$author/original.nonNA$author
+# real.success[["paper"]] <- success$paper/sum(rowMeans(!is.na(df.orig[, c("physical_extent", "physical_dimension")])) == 1)
+real.success <- unlist(real.success)
+par(mar = c(3, 8, 2, 1)); barplot(100*sort(real.success), horiz = T, main = "Real success rate (selected fields)", las = 1, xlim = c(0, 100), xlab = "Success rate (%)")
+```

### 2021-02-11 inst/examples/note_dissertation.Rmd

@@
 ---
+
+```{r setup, include=FALSE}
+knitr::opts_chunk$set(echo = TRUE)
+knitr::opts_chunk$set(fig.path=paste0("figure/rmd_", field, "_"))
+```
+
  * [Unique accepted titles](output.tables/title_accepted.csv): `r length(unique(df$note_dissertation))`

### 2021-02-11 inst/examples/note_source.Rmd

@@
 
-* [Unique accepted titles](output.tables/title_accepted.csv): `r length(unique(df$note_source)`
+```{r setup, include=FALSE}
+knitr::opts_chunk$set(echo = TRUE)
+knitr::opts_chunk$set(fig.path=paste0("figure/rmd_", field, "_"))
+```
+
+* [Unique accepted titles](output.tables/title_accepted.csv): `r length(unique(df$note_source))`
 * [Unique discarded titles in original data](output.tables/title_discarded.csv) (excluding NA cases): `r as.vector(countLines(paste0(output.folder, "/note_source_discarded.csv")) - 1)` 

### 2021-02-11 inst/examples/overview.Rmd

@@
   * [Languages](language.md)
-
+  * [Corporate](corporate.md)
+  * [Holder](holder.md)
+  * [Note_510c](note_510c.md)
+  * [Note_dissertation](note_dissertation.md)
+  * [Note_granter](note_granter.md)
+  * [Note_source](note_source.md)
+  * [Subject_topic](subject_topic.md)
+  * [Successor](successor.md)
+  * [Title_uniform](title_uniform.md)
+  * [Uncontrolled](uncontrolled.md)
 See also [further preprocessing details](details.Rmd).

### 2021-02-17 inst/examples/overview.Rmd
moved many functions from bibliographica to fennica for simplicity and maintenance

--- 2021-02-11 inst/examples/overview.Rmd
@@
   * [Publisher info](publisher.md)
-  * [Publication geography](publicationplace.md)
+  * [Publication geography](publication_place.md)
   * [Publication year info](publicationyear.md)

### 2021-02-17 inst/extras/deprecated/publicationplace.Rmd
moved many functions from bibliographica to fennica for simplicity and maintenance

---
title: "Publication place preprocessing summary"
author: "`r author`"
date: "`r Sys.Date()`"
output: markdown_document
---

### Publication places

 * `r length(unique(str_trim(unlist(strsplit(as.character(df$publication_place), ";")))))` [unique publication places](output.tables/publication_place_accepted.csv); available for `r sum(!is.na(df$publication_place))` documents (`r round(100*mean(!is.na(df$publication_place)))`%).
 * `r length(readLines(paste0(this.folder, "/output.tables/publication_place_ambiguous.csv"))) - 1` [ambiguous publication places](output.tables/publication_place_ambiguous.csv); some of these can be possibly resolved by checking that the the [synonyme list](https://github.com/COMHIS/fennica/blob/master/inst/extdata/PublicationPlaceSynonymes.csv) does not contain multiple versions of the final name (case sensitive). 
 * `r try(length(readLines(paste0(this.folder, "/output.tables/publication_place_todo.csv"))))` [unknown place names](output.tables/publication_place_todo.csv) These terms do not map to any known place on the [synonyme list](https://github.com/COMHIS/fennica/blob/master/inst/extdata/PublicationPlaceSynonymes.csv); either because they require further cleaning or have not yet been encountered in the analyses. Terms that are clearly not place names can be added to [stopwords](inst/extdata/stopwords_for_place.csv); borderline cases that are not accepted as place names can be added as NA on the [synonyme list](https://github.com/COMHIS/fennica/blob/master/inst/extdata/PublicationPlaceSynonymes.csv).
 * `r length(readLines(paste0(this.folder, "/output.tables/publication_place_discarded.csv"))) - 1` [discarded place names](output.tables/publication_place_discarded.csv) These terms are potential place names but with a closer check have been explicitly rejected on the [synonyme list](https://github.com/COMHIS/fennica/blob/master/inst/extdata/PublicationPlaceSynonymes.csv)
 * [Conversions from the original to the accepted place names](output.tables/publication_place_conversion_nontrivial.csv) 
 * [Unit tests for place names](https://github.com/COMHIS/fennica/blob/master/inst/extdata/tests_place.csv) are automatically checked during package build

Top-`r ntop` publication places are shown together with the number of documents.

```{r summaryplace, echo=FALSE, message=FALSE, warning=FALSE, fig.width=5, fig.height=4, fig.show='hold', out.width='430px'}
p <- top_plot(df, "publication_place", ntop)
p <- p + ggtitle(paste("Top publication places"))
p <- p + scale_y_log10()
p <- p + ylab("Title count")
print(p)

p <- top_plot(df, "publication_country", ntop)
p <- p + ggtitle(paste("Top publication countries"))
p <- p + scale_y_log10()
p <- p + ylab("Title count")
print(p)
```

### Publication countries

 * `r length(unique(df$publication_country))` [unique publication countries](output.tables/publication_country_accepted.csv); available for `r sum(!is.na(df$publication_country))` documents (`r round(100*mean(!is.na(df$publication_country)))`%).
 * `r length(na.omit(unique(subset(df, is.na(publication_country))$publication_place)))` [places with unknown publication country](output.tables/publication_place_missingcountry.csv) (`r round(100 * length(na.omit(unique(subset(df, is.na(publication_country))$publication_place))) / length(na.omit(unique(df$publication_place))), 1)`% of the unique places; can be added to [country mappings](https://github.com/COMHIS/fennica/blob/master/inst/extdata/reg2country.csv))
 * `r length(readLines(paste0(this.folder, "/output.tables/publication_country_ambiguous.csv"))) - 1` [potentially ambiguous region-country mappings](output.tables/publication_country_ambiguous.csv) (these may occur in the data in various synonymes and the country is not always clear when multiple countries have a similar place name; the default country is listed first). NOTE: possible improvements should not be done in this output summary but instead in the [country mapping file](https://github.com/COMHIS/fennica/blob/master/inst/extdata/reg2country.csv).

```{r summaryplace3, echo=FALSE, results='asis'}
tab <- top(df, "publication_country", output = "data.frame", round = 1)
colnames(tab) <- c("Country", "Documents (n)", "Fraction (%)")
library(knitr)
kable(head(tab))
```

### Geocoordinates

 * `r round(100*mean(!is.na(df$latitude) & !is.na(df$longitude)), 1)`% of the documents were matched to geographic coordinates (based on [Geonames](http://download.geonames.org/export/dump/)).
 * `r length(unique(df$publication_place[(is.na(df$latitude))]))` unique places (`r round(100 * length(unique(df$publication_place[(is.na(df$latitude))]))/length(unique(df$publication_place)), 1)`% of all unique places and `r round(100 * mean(is.na(df$latitude) | is.na(df$longitude)), 2)`% of all documents) are missing geocoordinates. See [list of places missing geocoordinate information](output.tables/absentgeocoordinates.csv).

### Publication geography

 * `r length(unique(df$publication_geography_country))` [unique countries](output.tables/publication_geography_country_accepted.csv) on geographical region considered in the publication; available for `r sum(!is.na(df$publication_geography_country))` documents (`r round(100*mean(!is.na(df$publication_geography_country)))`%).
 * `r length(unique(df$publication_geography_place))` [unique places](output.tables/publication_geography_place_accepted.csv) on geographical region considered in the publication; available for `r sum(!is.na(df$publication_geography_place))` documents (`r round(100*mean(!is.na(df$publication_geography_place)))`%).

### 2021-02-17 R/city_geocoordinates_all.R

@@ -1,31 +1,0 @@
-#' @title city_geocoordinates_all
-#' @description Retrieve geocoordinates for a list of cities from OSM Nominatim API. WIP
-#' @param names A list of city names
-#' @param wait Courtesy wait (seconds) between requests to Nominatim API.
-#' @return DF with two columns (lat, long)
-#' @export
-#' @details TODO
-#' @author Aaro Salosensaari \email{aaro.salosensaari@@helsinki.fi}
-#' @references See citation("fennica")
-#' @examples \dontrun{TODO}
-#' @keywords utilities
-city_geocoordinates_all <- function (names, wait=1) {
-
-    traverse <- function (name) {
-        query <- paste0("&city=",name)
-        gc <- gisfin::get_geocode(query, service="openstreetmap", raw_query=T)
-        print(paste("Query:", name))
-        print(paste("Got:", gc$lat, gc$lon))
-
-        # wait here a bit to adhere to Nominatim usage policy
-        Sys.sleep(wait)
-
-        c(gc$lat, gc$lon)
-    }
-
-    m <- sapply(names, traverse)
-    df <- data.frame(lat=m[1,],lon=m[2,])
-
-    return(df)
-}
-

### 2021-02-17 R/condense_spaces.R

@@ -1,0 +1,21 @@
+#' @title Condense Spaces
+#' @description Trim and remove double spaces from the input strings.
+#' @param x A vector
+#' @importFrom stringr str_trim
+#' @return A vector with extra spaces removed
+#' @details Beginning, double and ending spaces are also removed from the strings.
+#' @export 
+#' @author Leo Lahti \email{leo.lahti@@iki.fi}
+#' @references See citation("fennica") 
+#' @examples x2 <- condense_spaces(" a  b cd ") # "a b cd"
+#' @keywords utilities
+condense_spaces <- function (x) {
+
+  x <- str_trim(x, "both")
+  x <- gsub(" +", " ", x)
+  x[x == ""] <- NA
+   
+  x
+
+}
+

### 2021-02-17 R/handle_ie.R

@@ -1,0 +1,113 @@
+#' @title Handle ie
+#' @description Handle ie statements.
+#' @param x Character vector
+#' @param harmonize Logical. Harmonize ie statements efore interpretation?
+#' @param separator The separator string (i.e by default)
+#' @return A vector polished
+#' @importFrom stringr str_sub
+#' @author Leo Lahti \email{leo.lahti@@iki.fi}
+#' @references See citation("fennica")
+#' @examples \dontrun{x2 <- handle_ie("i.e.")}
+#' @export
+#' @keywords utilities
+handle_ie <- function (x, harmonize = TRUE, separator = "i.e") {
+
+  # 183 i.e 297 -> 297	  
+  # 183-285 i.e 297 -> 183-297	  
+  # 183-285 [i.e 297] -> 183-297
+  # 183-285 i.e 297-299 -> 297-299
+
+  y <- x
+
+  if (harmonize) {
+    y <- x <- harmonize_ie(y, separator = separator)
+  }
+  x <- condense_spaces(x)
+
+  if (length(x) == 1 && (is.na(x) || x == separator)) {return(x)}
+
+  # z [i.e y] -> y
+  if (length(grep("[0-9|a-z]*\\.* \\[i\\.e [0-9|a-z]*\\]", x))>0) {
+
+    # This is for "1905 [ie. 15]" -> 1915
+    spl <- strsplit(x, " \\[i\\.e ")
+    x1 <- sapply(spl, function (x) {x[[1]]})
+    x2 <- gsub("\\]", "", sapply(spl, function (x) {x[[2]]}))
+    inds <- which(nchar(x1) == 4 & nchar(x2) == 2)
+    x[inds] <- sapply(inds, function (ind) {paste(substr(x1[[ind]], 1, 2), x2[[ind]], sep = "")})
+
+    x <- gsub("^[0-9|a-z]*\\.* \\[i\\.e", "", x)
+
+    x <- gsub("\\]$", "", x)
+    
+  }
+
+
+  # "[1-3] 4-43 [44-45] 45-51 [i.e 46-52]"
+  # keep the first part and just remove "45-51 ie"
+  if (length(grep("[0-9]+-[0-9]+ i\\.e [0-9]+-[0-9]+", x)) == 1) {
+    spl <- unlist(strsplit(x, " "), use.names = FALSE)    
+    rmind <- which(spl == "i.e")
[…]

### 2021-02-17 R/harmonize_christian.R

@@ -1,0 +1,31 @@
+harmonize_christian <- function (x) {
+
+  x <- str_trim(as.character(x))
+  
+  #x <- gsub("anno dom.", "A.D", x)
+  #x <- gsub("an. dom.", "A.D", x)  
+  #x <- gsub("anno domini", "A.D", x)    
+  #x <- gsub("a.d.", "A.D", x)
+  #x <- gsub("A\\.D", "", x) # redundant
+
+  x <- gsub("anno dom\\.", " ", x)
+  x <- gsub("an\\. dom\\.", " ", x)  
+  x <- gsub("anno domini", " ", x)    
+  x <- gsub("a\\.d\\.", " ", x)
+  x <- gsub("ad", " ", x)  
+  x <- gsub("A\\.D", " ", x) # redundant
+  x <- gsub("anno d⁻ni", " ", x)
+  x <- gsub("anno dñi", " ", x)
+  x <- gsub("domini", " ", x)   
+
+  x <- gsub("bc", "B.C", x)
+  x <- gsub("b\\.c\\.", "B.C", x)  
+  x <- gsub("b\\.c\\.", "before christian era", x)  
+  x <- gsub("before christian era", "B.C", x)
+
+  # Remove space
+  x <- gsub(" B\\.C", "B.C", x)
+  x <- condense_spaces(x)
+
+  x
+}

### 2021-02-17 R/pick_firstname.R

@@ -1,0 +1,36 @@
+#' @title Pick First Name
+#' @description Pick first name from full name, assuming the format is known 
+#' @param x a vector of full names
+#' @param format name format
+#' @param keep.single If the name is without comma ('Shakespeare,
+#'  William' versus 'William'), interpret the name as first name.
+#'  Note that in this case also 'Shakespeare' will be interpreted as first name.
+#' @return a vector of first names
+#' @export
+#' @author Leo Lahti \email{leo.lahti@@iki.fi}
+#' @references See citation("fennica")
+#' @examples pick_firstname("Hobbes, Thomas")
+#' @keywords utilities
+pick_firstname <- function (x, format = "last, first", keep.single = FALSE) {
+
+  xorig <- as.character(x)
+  xuniq <- unique(xorig)
+  x <- xuniq
+
+  if (format == "last, first") {
+    first <- sapply(x, function (x) {y <- unlist(strsplit(x, ", "), use.names = FALSE); if (length(y)>1) y[[2]] else if (keep.single) {y[[1]]} else {NA} }, USE.NAMES = FALSE)
+  } else if (format == "first last") {
+    first <- sapply(x, function (x) {unlist(strsplit(x, " "), use.names = FALSE)[[1]]}, USE.NAMES = FALSE)
+  } else {
+    stop("Correct the unknown format in pick_firstname function.")
+  }
+
+  # Remove possible life year info
+  first <- gsub(" \\([0-9|N|A]+-[0-9|N|A]+\\)", "", first)
+  first <- condense_spaces(first)
+
+  first[match(xorig, xuniq)]
+
+}
+
+

### 2021-02-17 R/pick_lastname.R

@@ -1,0 +1,34 @@
+#' @title Pick Last Name
+#' @description Pick last name from full name, assuming the format is known 
+#' @param x a vector of full names
+#' @param format name format
+#' @param keep.single If the name is without comma ('Shakespeare,
+#'  William' versus 'William'), interpret the name as first name.
+#'  Note that in this case also 'Shakespeare' will be interpreted as first name.
+#'  In the current implementation keep.single is always TRUE.
+#' @return a vector of last names
+#' @export
+#' @author Leo Lahti \email{leo.lahti@@iki.fi}
+#' @references See citation("fennica")
+#' @examples pick_lastname("Hobbes, Thomas")
+#' @keywords utilities
+pick_lastname <- function (x, format = "last, first", keep.single = TRUE) {
+
+  x <- as.character(x)
+
+  if (format == "last, first") {
+    last <- sapply(x, function (x) {y <- unlist(strsplit(x, ", "), use.names = FALSE); if (length(y)>=1) y[[1]] else NA}, USE.NAMES = FALSE) 
+  } else if (format == "first last") {
+    last <- sapply(x, function (x) {y <- unlist(strsplit(x, " "), use.names = FALSE); y[[length(y)]]}, USE.NAMES = FALSE)
+  } else {
+    stop("Correct the unknown format in pick_lastname function.")
+  }
+
+  # Remove possible life year info
+  last <- gsub(" \\([0-9|N|A]+-[0-9|N|A]+\\)", "", last)
+
+  last
+
+}
+
+

### 2021-02-17 R/remove_endings.R

@@ -7,7 +7,7 @@
 #' @export
 #' @importFrom stringr str_c
 #' @author Leo Lahti \email{leo.lahti@@iki.fi}
-#' @references See citation("bibliographica")
+#' @references See citation("fennica")
 #' @examples \dontrun{x2 <- remove_endings(x, endings)}
 #' @keywords utilities
 remove_endings <- function (x, endings, random_order=FALSE) {

### 2021-02-17 R/remove_print_statements.R

@@ -1,0 +1,80 @@
+#' @title Remove Print Statements
+#' @description Remove print statements.
+#' @param x a vector
+#' @return Polished vector
+#' @export
+#' @author Leo Lahti \email{leo.lahti@@iki.fi}
+#' @references See citation("fennica")
+#' @examples x2 <- remove_print_statements("Printed in London")
+#' @keywords utilities
+remove_print_statements <- function (x) {
+
+  x0 = xorig <- tolower(as.character(x))
+  xuniq <- unique(xorig)
+  x <- xuniq
+
+  terms.single = c()
+  terms.multi = c()  
+
+  ### Get printing terms from tables in various languages
+  for (lang in c("finnish", "french", "german", "swedish", "english")) {
+
+    f <- system.file(paste0("extdata/printstop_", lang, ".csv"), package = "fennica")
+    terms <- unique(str_trim(tolower(read.csv(f, stringsAsFactors = FALSE)[,1])))
+
+    # Harmonize the terms 
+    terms.multi <- c(terms.multi, terms[nchar(terms) > 1])
+    terms.single <- c(terms.single, terms[nchar(terms) == 1])
+
+  }
+
+  terms.multi = unique(terms.multi)
+  terms.single = unique(terms.single)  
+
+  x <- remove_terms(x, terms.multi, where = "all", polish = FALSE, include.lowercase = FALSE)
+  x <- condense_spaces(x)
+
+  # Back to original indices, then unique again; reduces
+  # number of unique cases further
+  xorig <- x[match(xorig, xuniq)]
+  x <- xuniq <- unique(xorig)
+
+  # Individual characters not removed from the end
+  x <- remove_terms(x, terms.single, where = "begin", polish = FALSE, include.lowercase = FALSE)
+
+  # Back to original indices, then unique again; reduces
+  # number of unique cases further
+  xorig <- x[match(xorig, xuniq)]
+  x <- xuniq <- unique(xorig)
+
+  x <- remove_terms(x, terms.single, where = "middle", polish = FALSE, include.lowercase = FALSE)
+  x <- condense_spaces(x)
+  x <- remove_trailing_periods(x)
+
+  # Back to original indices, then unique again; reduces
+  # number of unique cases further
+  xorig <- x[match(xorig, xuniq)]
+  x <- xuniq <- unique(xorig)
+
[…]

### 2021-02-17 R/remove_trailing_periods.R

@@ -1,0 +1,19 @@
+#' @title Remove Trailing Periods
+#' @description Remove trailing periods.
+#' @param x A vector
+#' @return A polished vector
+#' @export
+#' @author Leo Lahti \email{leo.lahti@@iki.fi}
+#' @references See citation("fennica")
+#' @examples \dontrun{x2 <- remove_trailing_periods(x)}
+#' @keywords utilities
+remove_trailing_periods <- function (x){ 
+
+  if (all(is.na(x))) {return(x)}
+  x <- gsub("\\.+$", "", x)
+  x <- gsub("^\\.+", "", x)
+    
+  x
+}
+
+

### 2021-02-17 R/roman.R

@@ -1,0 +1,58 @@
+is.roman <- function (x) {
+
+  x <- gsub("\\.", NA, x)
+
+  check.roman <- function (x) {
+
+    if (x == "" || is.na(x)) {return(FALSE)}
+
+    xs <- unlist(strsplit(x, "-"), use.names = FALSE)
+    isr <- c()
+
+    for (i in 1:length(xs)) {  
+      x <- xs[[i]]
+      tmp <- suppressWarnings(as.numeric(x))
+      tmp2 <- suppressWarnings(as.numeric(as.roman(x)))
+      not.numeric <- length(na.omit(tmp)) > 0
+      roman.numeric <- is.numeric(tmp2)
+
+      isr[[i]] <- !(not.numeric && roman.numeric) && !is.na(tmp2) 
+    }
+    # iii-7 TRUE; iii-iv TRUE; 4-7 FALSE
+    any(isr)
+  }
+
+  sapply(x, check.roman, USE.NAMES = FALSE)
+
+}
+
+
+
+
+roman2arabic <- function (x) {
+
+  if (length(grep("vj", x)) == 1) {
+    x <- gsub("j", "i", x)
+  }
+
+  helpf <- function(xi) {
+
+    # Return numeric hits immediately (such as "4387")
+    if (grepl("^[0-9]+$", xi)) {
+      xr <- xi
+    } else if (length(grep("-", xi)) > 0) {
+      x2 <- str_trim(unlist(strsplit(xi, "-"), use.names = FALSE))
+      n <- suppressWarnings(as.numeric(as.roman(x2)))
+      n[is.na(n)] <- x2[is.na(n)] # vii-160
+      xr <- paste(n, collapse = "-")
+    } else {
+      xr <- suppressWarnings(as.numeric(as.roman(xi)))
+    }
+    xr
+  }
+
+  sapply(x, function (xi) {helpf(xi)}, USE.NAMES = FALSE)
+
+}
+
+

### 2021-02-17 R/splitpick.R

@@ -1,0 +1,22 @@
+#' @title Pick Substring Indicated by Separator
+#' @description Split the string by separator and pick the former or latter part.
+#' @param x Input string
+#' @param sep Separator string
+#' @param which Indicate which part to pick
+#' @return Polished string
+#' @export
+#' @author Leo Lahti \email{leo.lahti@@iki.fi}
+#' @references See citation("fennica")
+#' @examples x2 <- splitpick("London re Edinburgh", " re ", 1)
+#' @keywords utilities
+splitpick <- function (x, sep, which) {
+  # london re edinburgh -> london
+  inds <- grep(sep, x)
+  if (length(inds) > 0) {
+    spl <- unlist(strsplit(x[inds], sep), use.names = FALSE)
+    x[inds] <- spl[[which]]
+  }
+
+  x
+  
+}

### 2021-02-17 R/top.R

@@ -1,0 +1,71 @@
+#' @title Identify Top Entries
+#' @description Identify the top entries in a vector or for a given field in a data frame.
+#' @param x data.frame, matrix, or vector 
+#' @param field Field or column to check for a data.frame or matrix
+#' @param n Number of top entries to show
+#' @param output Output format: vector or data.frame
+#' @param round Optional rounding
+#' @param na.rm Logical. Remove NA before calculating the statistics.
+#' @param include.rank Include ranking if the output is data.frame. Logical.
+#' @return Vector of top counts, named by the corresponding entries
+#' @export
+#' @author Leo Lahti \email{leo.lahti@@iki.fi}
+#' @references See citation("comhis")
+#' @examples \dontrun{p <- top(df, field, 10)}
+#' @keywords utilities
+top <- function (x, field = NULL, n = NULL, output = "vector", round = NULL, na.rm = FALSE, include.rank = FALSE) {
+
+  if (is.factor(x)) {
+    x <- as.character(x)
+  }
+
+  if (is.vector(x)) {
+    if (na.rm) {
+      inds <- which(x == "NA")
+      if (length(inds) > 0) {
+        x[inds] <- NA
+	warning(paste("Interpreting NA string as missing value NA. Removing", length(inds), "entries"))
+      }
+      x <- x[!is.na(x)]
+    }
+    s <- rev(sort(table(x)))
+    N <- length(x)
+  } else if (is.data.frame(x) || is.matrix(x)) {
+    if (is.null(field)) {
+      #warning("Indicate the selected field for the top function.")
+      return(NULL)
+    }
+
+    x <- x[, field]
+    if (na.rm) {
+      inds <- which(x == "NA")
+      if (length(inds) > 0) {
+        x[inds] <- NA
+	warning(paste("Interpreting NA string as missing value NA. Removing", length(inds), "entries"))
+      }
+      x <- x[!is.na(x)]
+    }
+    N <- length(x)
+    s <- rev(sort(table(x)))
+  }
+
+  if (!is.null(n)) {
+    s <- s[1:min(n, length(s))]
+  }
+
+  if (output == "data.frame") {
+    s <- data_frame(name = names(s), n = unname(s), fraction = 100*unname(s)/N)
+    if (is.null(field)) {field <- "Field"}
+    names(s) <- c(field, "Entries (N)", "Fraction (%)")
+    if (!is.null(round)) {
[…]

### 2021-02-17 inst/extras/build.cran.sh

@@ -7,8 +7,8 @@
 #~/bin/R-4.0.3/bin/R CMD BATCH document.R
 ~/bin/R-4.0.3/bin/R CMD build ../../ --no-build-vignettes #--no-tests
 #~/bin/R-4.0.3/bin/R CMD build ../../ 
-#~/bin/R-4.0.3/bin/R CMD check fennica_0.2.5.tar.gz
-~/bin/R-4.0.3/bin/R CMD check --as-cran fennica_0.2.5.tar.gz --no-tests
-~/bin/R-4.0.3/bin/R CMD INSTALL fennica_0.2.5.tar.gz
+#~/bin/R-4.0.3/bin/R CMD check fennica_0.2.6.tar.gz
+~/bin/R-4.0.3/bin/R CMD check --as-cran fennica_0.2.6.tar.gz --no-tests
+~/bin/R-4.0.3/bin/R CMD INSTALL fennica_0.2.6.tar.gz
 #~/bin/R-4.0.3/bin/R CMD BATCH document.R
 

### 2021-02-17 inst/examples/corporate.Rmd
change

--- 2021-02-10 inst/examples/corporate.Rmd
@@
 
-* [Unique accepted titles](output.tables/title_accepted.csv): `r length(unique(df$corporate))`
-* [Unique discarded titles in original data](output.tables/title_discarded.csv) (excluding NA cases): `r as.vector(countLines(paste0(output.folder, "/corporate_discarded.csv")) - 1)` 
+* [Unique accepted entries](output.tables/corporate_accepted.csv): `r length(unique(df$corporate))`
+* [Unique discarded entries in original data](output.tables/corporate_discarded.csv) (excluding NA cases): `r as.vector(countLines(paste0(output.folder, "/corporate_discarded.csv")) - 1)` 
 * Original documents with non-NA titles: `r sum(!is.na(df$corporate))` / `r nrow(df)` (`r round(100*mean(!is.na(df$corporate)), 1)`%)
-* Original documents with missing (NA) titles `r sum(is.na(df$corporate)` / `r nrow(df)` documents (`r round(100*mean(is.na(df$corporate)), 1)`%)
+* Original documents with missing (NA) titles `r sum(is.na(df$corporate))` / `r nrow(df)` documents (`r round(100*mean(is.na(df$corporate)), 1)`%)
 

### 2021-02-17 inst/examples/holder.Rmd
change

@@
 
-* [Unique accepted titles](output.tables/title_accepted.csv): `r length(unique(df$holder))`
-* [Unique discarded titles in original data](output.tables/title_discarded.csv) (excluding NA cases): `r as.vector(countLines(paste0(output.folder, "/holder_discarded.csv")) - 1)` 
+* [Unique accepted entries](output.tables/holder_accepted.csv): `r length(unique(df$holder))`
+* [Unique discarded entries in original data](output.tables/holder_discarded.csv) (excluding NA cases): `r as.vector(countLines(paste0(output.folder, "/holder_discarded.csv")) - 1)` 
 * Original documents with non-NA titles: `r sum(!is.na(df$holder))` / `r nrow(df)` (`r round(100*mean(!is.na(df$holder)), 1)`%)

### 2021-02-17 inst/examples/note_510c.Rmd
change

--- 2021-02-10 inst/examples/note_510c.Rmd
@@
 
-* [Unique accepted titles](output.tables/title_accepted.csv): `r length(unique(df$note_510c))`
-* [Unique discarded titles in original data](output.tables/title_discarded.csv) (excluding NA cases): `r as.vector(countLines(paste0(output.folder, "/note_510c_discarded.csv")) - 1)` 
+* [Unique accepted entries](output.tables/note_510c_accepted.csv): `r length(unique(df$note_510c))`
+* [Unique discarded entries in original data](output.tables/note_510c_discarded.csv) (excluding NA cases): `r as.vector(countLines(paste0(output.folder, "/note_510c_discarded.csv")) - 1)` 
 * Original documents with non-NA titles: `r sum(!is.na(df$note_510c))` / `r nrow(df)` (`r round(100*mean(!is.na(df$note_510c)), 1)`%)
-* Original documents with missing (NA) titles `r sum(is.na(df$note_510c)` / `r nrow(df)` documents (`r round(100*mean(is.na(df$note_510c)), 1)`%)
+* Original documents with missing (NA) titles `r sum(is.na(df$note_510c))` / `r nrow(df)` documents (`r round(100*mean(is.na(df$note_510c)), 1)`%)
 

### 2021-02-17 inst/examples/note_dissertation.Rmd
change

@@
 
- * [Unique accepted titles](output.tables/title_accepted.csv): `r length(unique(df$note_dissertation))`
- * [Unique discarded titles in original data](output.tables/title_discarded.csv) (excluding NA cases): `r as.vector(countLines(paste0(output.folder, "/note_dissertation_discarded.csv")) - 1)` 
+ * [Unique accepted entries](output.tables/note_disseration_accepted.csv): `r length(unique(df$note_dissertation))`
+ * [Unique discarded entries in original data](output.tables/note_dissertation_discarded.csv) (excluding NA cases): `r as.vector(countLines(paste0(output.folder, "/note_dissertation_discarded.csv")) - 1)`
  * Original documents with non-NA titles: `r sum(!is.na(df$note_dissertation))` / `r nrow(df)` (`r round(100*mean(!is.na(df$note_dissertation)), 1)`%)

### 2021-02-17 inst/examples/note_granter.Rmd
change

@@
 
-* [Unique accepted titles](output.tables/title_accepted.csv): `r length(unique(df$note_granter))`
- * [Unique discarded titles in original data](output.tables/title_discarded.csv) (excluding NA cases): `r as.vector(countLines(paste0(output.folder, "/note_granter_discarded.csv")) - 1)` 
+* [Unique accepted entries](output.tables/note_granter_accepted.csv): `r length(unique(df$note_granter))`
+ * [Unique discarded entries in original data](output.tables/note_granter_discarded.csv) (excluding NA cases): `r as.vector(countLines(paste0(output.folder, "/note_granter_discarded.csv")) - 1)` 
  * Original documents with non-NA titles: `r sum(!is.na(df$note_granter))` / `r nrow(df)` (`r round(100*mean(!is.na(df$note_granter)), 1)`%)

### 2021-02-17 inst/examples/note_source.Rmd
change

@@
 
-* [Unique accepted titles](output.tables/title_accepted.csv): `r length(unique(df$note_source))`
-* [Unique discarded titles in original data](output.tables/title_discarded.csv) (excluding NA cases): `r as.vector(countLines(paste0(output.folder, "/note_source_discarded.csv")) - 1)` 
+* [Unique accepted entries](output.tables/note_source_accepted.csv): `r length(unique(df$note_source))`
+* [Unique discarded entries in original data](output.tables/note_source_discarded.csv) (excluding NA cases): `r as.vector(countLines(paste0(output.folder, "/note_source_discarded.csv")) - 1)` 
 * Original documents with non-NA titles: `r sum(!is.na(df$note_source))` / `r nrow(df)` (`r round(100*mean(!is.na(df$note_source)), 1)`%)

### 2021-02-17 inst/examples/subject_topic.Rmd
change

--- 2021-02-10 inst/examples/subject_topic.Rmd
@@
 
-* [Unique accepted titles](output.tables/title_accepted.csv): `r length(unique(df$subject_topic))`
-* [Unique discarded titles in original data](output.tables/title_discarded.csv) (excluding NA cases): `r as.vector(countLines(paste0(output.folder, "/subject_topic_discarded.csv")) - 1)` 
+* [Unique accepted entries](output.tables/subject_topic_accepted.csv): `r length(unique(df$subject_topic))`
+* [Unique discarded entries in original data](output.tables/subject_topic_discarded.csv) (excluding NA cases): `r as.vector(countLines(paste0(output.folder, "/subject_topic_discarded.csv")) - 1)` 
 * Original documents with non-NA titles: `r sum(!is.na(df$subject_topic))` / `r nrow(df)` (`r round(100*mean(!is.na(df$subject_topic)), 1)`%)
-* Original documents with missing (NA) titles `r sum(is.na(df$subject_topic)` / `r nrow(df)` documents (`r round(100*mean(is.na(df$subject_topic)), 1)`%)
+* Original documents with missing (NA) titles `r sum(is.na(df$subject_topic))` / `r nrow(df)` documents (`r round(100*mean(is.na(df$subject_topic)), 1)`%)
 

### 2021-02-17 inst/examples/successor.Rmd
change

@@
 
-* [Unique accepted titles](output.tables/title_accepted.csv): `r length(unique(df$successor))`
-* [Unique discarded titles in original data](output.tables/title_discarded.csv) (excluding NA cases): `r as.vector(countLines(paste0(output.folder, "/successor_discarded.csv")) - 1)` 
+* [Unique accepted entries](output.tables/succersor_accepted.csv): `r length(unique(df$title))`
+* [Unique discarded entries in original data](output.tables/successor_discarded.csv) (excluding NA cases): `r as.vector(countLines(paste0(output.tables, "/successor_discarded.csv")) - 1)` 
 * Original documents with non-NA titles: `r sum(!is.na(df$successor))` / `r nrow(df)` (`r round(100*mean(!is.na(df$successor)), 1)`%)

### 2021-02-17 inst/examples/title_uniform.Rmd
change

@@
 
- * [Unique accepted titles](output.tables/title_accepted.csv): `r length(unique(df$title_uniform))`
- * [Unique discarded titles in original data](output.tables/title_discarded.csv) (excluding NA cases): `r as.vector(countLines(paste0(output.folder, "/title_uniform_discarded.csv")) - 1)` 
+ * [Unique accepted entries](output.tables/title_uniform_accepted.csv): `r length(unique(df$title_uniform))`
+ * [Unique discarded entries in original data](output.tables/title_uniform_discarded.csv) (excluding NA cases): `r as.vector(countLines(paste0(output.folder, "/title_uniform_discarded.csv")) - 1)` 
  * Original documents with non-NA titles: `r sum(!is.na(df$title_uniform))` / `r nrow(df)` (`r round(100*mean(!is.na(df$title_uniform)), 1)`%)

### 2021-02-17 inst/examples/uncontrolled.Rmd
change

@@
 
-* [Unique accepted titles](output.tables/title_accepted.csv): `r length(unique(df$uncontrolled))`
-* [Unique discarded titles in original data](output.tables/title_discarded.csv) (excluding NA cases): `r as.vector(countLines(paste0(output.folder, "/uncontrolled_discarded.csv")) - 1)` 
+* [Unique accepted entries](output.tables/uncontrolled_accepted.csv): `r length(unique(df$uncontrolled))`
+* [Unique discarded entries in original data](output.tables/uncontrolled_discarded.csv) (excluding NA cases): `r as.vector(countLines(paste0(output.folder, "/uncontrolled_discarded.csv")) - 1)` 
 * Original documents with non-NA titles: `r sum(!is.na(df$uncontrolled))` / `r nrow(df)` (`r round(100*mean(!is.na(df$uncontrolled)), 1)`%)

### 2021-02-18 inst/examples/corporate.Rmd
change

--- 2021-02-10 inst/examples/corporate.Rmd
@@
 
-* [Unique accepted titles](output.tables/title_accepted.csv): `r length(unique(df$corporate))`
-* [Unique discarded titles in original data](output.tables/title_discarded.csv) (excluding NA cases): `r as.vector(countLines(paste0(output.folder, "/corporate_discarded.csv")) - 1)` 
-* Original documents with non-NA titles: `r sum(!is.na(df$corporate))` / `r nrow(df)` (`r round(100*mean(!is.na(df$corporate)), 1)`%)
-* Original documents with missing (NA) titles `r sum(is.na(df$corporate)` / `r nrow(df)` documents (`r round(100*mean(is.na(df$corporate)), 1)`%)
+* [Unique accepted entries](`r file_accepted`): `r length(unique(df[[field]]))`
+* [Unique discarded entries in original data](`r file_discarded`) (excluding NA cases): `r as.vector(countLines(file_discarded) - 1)`
+* Original documents with non-NA titles: `r sum(!is.na(df[[field]]))` / `r nrow(df)` (`r round(100*mean(!is.na(df[[field]])), 1)`%)
+* Original documents with missing (NA) titles `r sum(is.na(df[[field]]))` / `r nrow(df)` documents (`r round(100*mean(is.na(df[[field]])), 1)`%)
 

### 2021-02-18 inst/examples/note_510c.Rmd
change

--- 2021-02-10 inst/examples/note_510c.Rmd
@@
 
-* [Unique accepted titles](output.tables/title_accepted.csv): `r length(unique(df$note_510c))`
-* [Unique discarded titles in original data](output.tables/title_discarded.csv) (excluding NA cases): `r as.vector(countLines(paste0(output.folder, "/note_510c_discarded.csv")) - 1)` 
-* Original documents with non-NA titles: `r sum(!is.na(df$note_510c))` / `r nrow(df)` (`r round(100*mean(!is.na(df$note_510c)), 1)`%)
-* Original documents with missing (NA) titles `r sum(is.na(df$note_510c)` / `r nrow(df)` documents (`r round(100*mean(is.na(df$note_510c)), 1)`%)
+* [Unique accepted entries](`r file_accepted`): `r length(unique(df[[field]]))`
+* [Unique discarded entries in original data](`r file_discarded`) (excluding NA cases): `r as.vector(countLines(file_discarded) - 1)`
+* Original documents with non-NA titles: `r sum(!is.na(df[[field]]))` / `r nrow(df)` (`r round(100*mean(!is.na(df[[field]])), 1)`%)
+* Original documents with missing (NA) titles `r sum(is.na(df[[field]]))` / `r nrow(df)` documents (`r round(100*mean(is.na(df[[field]])), 1)`%)
 

### 2021-02-18 inst/examples/note_dissertation.Rmd
change

--- 2021-02-11 inst/examples/note_dissertation.Rmd
@@
 
- * [Unique accepted titles](output.tables/title_accepted.csv): `r length(unique(df$note_dissertation))`
- * [Unique discarded titles in original data](output.tables/title_discarded.csv) (excluding NA cases): `r as.vector(countLines(paste0(output.folder, "/note_dissertation_discarded.csv")) - 1)` 
- * Original documents with non-NA titles: `r sum(!is.na(df$note_dissertation))` / `r nrow(df)` (`r round(100*mean(!is.na(df$note_dissertation)), 1)`%)
- * Original documents with missing (NA) titles `r sum(is.na(df$note_dissertation))` / `r nrow(df)` documents (`r round(100*mean(is.na(df$note_dissertation)), 1)`%)
+* [Unique accepted entries](`r file_accepted`): `r length(unique(df[[field]]))`
+* [Unique discarded entries in original data](`r file_discarded`) (excluding NA cases): `r as.vector(countLines(file_discarded) - 1)`
+* Original documents with non-NA titles: `r sum(!is.na(df[[field]]))` / `r nrow(df)` (`r round(100*mean(!is.na(df[[field]])), 1)`%)
+* Original documents with missing (NA) titles `r sum(is.na(df[[field]]))` / `r nrow(df)` documents (`r round(100*mean(is.na(df[[field]])), 1)`%)
 

### 2021-02-18 inst/examples/note_granter.Rmd
change

--- 2021-02-09 inst/examples/note_granter.Rmd
@@
 ---
-* [Unique accepted titles](output.tables/title_accepted.csv): `r length(unique(df$note_granter))`
- * [Unique discarded titles in original data](output.tables/title_discarded.csv) (excluding NA cases): `r as.vector(countLines(paste0(output.folder, "/note_granter_discarded.csv")) - 1)` 
- * Original documents with non-NA titles: `r sum(!is.na(df$note_granter))` / `r nrow(df)` (`r round(100*mean(!is.na(df$note_granter)), 1)`%)
- * Original documents with missing (NA) titles `r sum(is.na(df$note_granter))` / `r nrow(df)` documents (`r round(100*mean(is.na(df$note_granter)), 1)`%)
+
+```{r setup, include=FALSE}
+knitr::opts_chunk$set(echo = TRUE)
+knitr::opts_chunk$set(fig.path=paste0("figure/rmd_", field, "_"))
+```
+* [Unique accepted entries](`r file_accepted`): `r length(unique(df[[field]]))`
+* [Unique discarded entries in original data](`r file_discarded`) (excluding NA cases): `r as.vector(countLines(file_discarded) - 1)`
+* Original documents with non-NA titles: `r sum(!is.na(df[[field]]))` / `r nrow(df)` (`r round(100*mean(!is.na(df[[field]])), 1)`%)
+* Original documents with missing (NA) titles `r sum(is.na(df[[field]]))` / `r nrow(df)` documents (`r round(100*mean(is.na(df[[field]])), 1)`%)
 

### 2021-02-18 inst/examples/note_source.Rmd
change

--- 2021-02-11 inst/examples/note_source.Rmd
@@
 
-* [Unique accepted titles](output.tables/title_accepted.csv): `r length(unique(df$note_source))`
-* [Unique discarded titles in original data](output.tables/title_discarded.csv) (excluding NA cases): `r as.vector(countLines(paste0(output.folder, "/note_source_discarded.csv")) - 1)` 
-* Original documents with non-NA titles: `r sum(!is.na(df$note_source))` / `r nrow(df)` (`r round(100*mean(!is.na(df$note_source)), 1)`%)
-* Original documents with missing (NA) titles `r sum(is.na(df$note_source))` / `r nrow(df)` documents (`r round(100*mean(is.na(df$note_source)), 1)`%)
+* [Unique accepted entries](`r file_accepted`): `r length(unique(df[[field]]))`
+* [Unique discarded entries in original data](`r file_discarded`) (excluding NA cases): `r as.vector(countLines(file_discarded) - 1)`
+* Original documents with non-NA titles: `r sum(!is.na(df[[field]]))` / `r nrow(df)` (`r round(100*mean(!is.na(df[[field]])), 1)`%)
+* Original documents with missing (NA) titles `r sum(is.na(df[[field]]))` / `r nrow(df)` documents (`r round(100*mean(is.na(df[[field]])), 1)`%)
 

### 2021-02-18 inst/examples/title.Rmd
added chunk options
change

@@
 
-### Titles
+```{r setup, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
+knitr::opts_chunk$set(echo = TRUE)
+knitr::opts_chunk$set(fig.path=paste0("figure/rmd_", field, "_"))
+```
 
- * [Unique accepted titles](output.tables/title_accepted.csv): `r length(unique(df$title))`
- * [Unique discarded titles in original data](output.tables/title_discarded.csv) (excluding NA cases): `r as.vector(countLines(paste0(output.folder, "/title_discarded.csv")) - 1)` 
- * Original documents with non-NA titles: `r sum(!is.na(df$title))` / `r nrow(df)` (`r round(100*mean(!is.na(df$title)), 1)`%)
- * Original documents with missing (NA) titles `r sum(is.na(df$title))` / `r nrow(df)` documents (`r round(100*mean(is.na(df$title)), 1)`%)
+* [Unique accepted entries](`r file_accepted`): `r length(unique(df[[field]]))`
+* [Unique discarded entries in original data](`r file_discarded`) (excluding NA cases): `r as.vector(countLines(file_discarded) - 1)`
+* Original documents with non-NA titles: `r sum(!is.na(df[[field]]))` / `r nrow(df)` (`r round(100*mean(!is.na(df[[field]])), 1)`%)
+* Original documents with missing (NA) titles `r sum(is.na(df[[field]]))` / `r nrow(df)` documents (`r round(100*mean(is.na(df[[field]])), 1)`%)
 

### 2021-02-18 inst/examples/note_510c.R

@@ -18,12 +18,16 @@ df.tmp <- data.frame(original_row = df.orig$original_row,
 data.file <- paste0(field, ".Rds")
 saveRDS(df.tmp, file = data.file)
 
+# Define output files
+file_accepted  <- paste0(output.folder, field, "_accepted.csv")
+file_discarded <- paste0(output.folder, field, "_discarded.csv")
+
 # ------------------------------------------------------------
 
 # Generate data summaries
 
 message("Accepted entries in the preprocessed data")
-s <- write_xtable(df.tmp[[field]], paste(output.folder, field, "_accepted.csv", sep = ""), count = TRUE)
+s <- write_xtable(df.tmp[[field]], file_accepted, count = TRUE)
 
 message("Discarded entries in the original data")
 
@@ -34,7 +38,7 @@ inds <- which(is.na(df.tmp[[field]]))
 original.na <- df.orig[match(df.tmp$original_row[inds], df.orig$original_row), field]
 
 # .. ie. those are "discarded" cases; list them in a table
-tmp <- write_xtable(original.na, paste(output.folder, field, "_discarded.csv", sep = ""), count = TRUE)
+tmp <- write_xtable(original.na, file_discarded, count = TRUE)
 
 # ------------------------------------------------------------
 

### 2021-02-18 inst/examples/note_dissertation.R

@@ -20,12 +20,16 @@ df.tmp <- data.frame(original_row = df.orig$original_row,
 data.file <- paste0(field, ".Rds")
 saveRDS(df.tmp, file = data.file)
 
+# Define output files
+file_accepted  <- paste0(output.folder, field, "_accepted.csv")
+file_discarded <- paste0(output.folder, field, "_discarded.csv")
+
 # ------------------------------------------------------------
 
 # Generate data summaries
 
 message("Accepted entries in the preprocessed data")
-s <- write_xtable(df.tmp[[field]], paste(output.folder, field, "_accepted.csv", sep = ""), count = TRUE)
+s <- write_xtable(df.tmp[[field]], file_accepted, count = TRUE)
 
 message("Discarded entries in the original data")
 
@@ -36,14 +40,11 @@ inds <- which(is.na(df.tmp[[field]]))
 original.na <- df.orig[match(df.tmp$original_row[inds], df.orig$original_row), field]
 
 # .. ie. those are "discarded" cases; list them in a table
-tmp <- write_xtable(original.na, paste(output.folder, field, "_discarded.csv", sep = ""), count = TRUE)
+tmp <- write_xtable(original.na, file_discarded, count = TRUE)
 
 # ------------------------------------------------------------
 
-# Generate markdown summary in title.md
+# Generate markdown summary in note_source.md
 df <- readRDS(data.file)
 tmp <- knit(input = paste(field, ".Rmd", sep = ""), 
             output = paste(field, ".md", sep = ""))
-
-
-

### 2021-02-18 inst/examples/title.R

@@ -16,12 +16,16 @@ df.tmp <- data.frame(original_row = df.orig$original_row,
 data.file <- paste0(field, ".Rds")
 saveRDS(df.tmp, file = data.file)
 
+# Define output files
+file_accepted  <- paste0(output.folder, field, "_accepted.csv")
+file_discarded <- paste0(output.folder, field, "_discarded.csv")
+
 # ------------------------------------------------------------
 
 # Generate data summaries
 
 message("Accepted entries in the preprocessed data")
-s <- write_xtable(df.tmp[[field]], paste(output.folder, field, "_accepted.csv", sep = ""), count = TRUE)
+s <- write_xtable(df.tmp[[field]], file_accepted, count = TRUE)
 
 message("Discarded entries in the original data")
 
@@ -32,13 +36,11 @@ inds <- which(is.na(df.tmp[[field]]))
 original.na <- df.orig[match(df.tmp$original_row[inds], df.orig$original_row), field]
 
 # .. ie. those are "discarded" cases; list them in a table
-tmp <- write_xtable(original.na, paste(output.folder, field, "_discarded.csv", sep = ""), count = TRUE)
+tmp <- write_xtable(original.na, file_discarded, count = TRUE)
 
 # ------------------------------------------------------------
 
-# Generate markdown summary in title.md
+# Generate markdown summary in note_source.md
 df <- readRDS(data.file)
 tmp <- knit(input = paste(field, ".Rmd", sep = ""), 
             output = paste(field, ".md", sep = ""))
-
-

### 2021-02-18 inst/examples/title_uniform.R

@@ -18,12 +18,16 @@ df.tmp <- data.frame(original_row = df.orig$original_row,
 data.file <- paste0(field, ".Rds")
 saveRDS(df.tmp, file = data.file)
 
+# Define output files
+file_accepted  <- paste0(output.folder, field, "_accepted.csv")
+file_discarded <- paste0(output.folder, field, "_discarded.csv")
+
 # ------------------------------------------------------------
 
 # Generate data summaries
 
 message("Accepted entries in the preprocessed data")
-s <- write_xtable(df.tmp[[field]], paste(output.folder, field, "_accepted.csv", sep = ""), count = TRUE)
+s <- write_xtable(df.tmp[[field]], file_accepted, count = TRUE)
 
 message("Discarded entries in the original data")
 
@@ -34,13 +38,11 @@ inds <- which(is.na(df.tmp[[field]]))
 original.na <- df.orig[match(df.tmp$original_row[inds], df.orig$original_row), field]
 
 # .. ie. those are "discarded" cases; list them in a table
-tmp <- write_xtable(original.na, paste(output.folder, field, "_discarded.csv", sep = ""), count = TRUE)
+tmp <- write_xtable(original.na, file_discarded, count = TRUE)
 
 # ------------------------------------------------------------
 
-# Generate markdown summary in title.md
+# Generate markdown summary in note_source.md
 df <- readRDS(data.file)
 tmp <- knit(input = paste(field, ".Rmd", sep = ""), 
             output = paste(field, ".md", sep = ""))
-
-

### 2021-02-18 inst/examples/language.Rmd
ok

@@
 
- * `r length(unique(unlist(strsplit(as.character(df$languages), ";"))))-1` [unique languages](output.tables/language_accepted.csv)
- * `r length(unique(df$language_primary))-1` [unique primary languages](output.tables/language_accepted.csv)  
+ * `r length(unique(unlist(strsplit(as.character(df$languages), ";"))))-1` [unique languages](output.tables/languages_accepted.csv)
+ * `r length(unique(df$language_primary))-1` [unique primary languages](output.tables/language_primary_accepted.csv)  
  * `r sum(!df$multilingual, na.rm = TRUE)` single-language documents (`r round(100 * mean(!df$multilingual, na.omit = TRUE), 2)`%)
@@
 
-Title count per language (including multi-language documents; note the log10 scale):
-
-```{r summarylang, echo=FALSE, message=FALSE, warning=FALSE, fig.width=7, fig.height=5}
-top_plot(df, "languages", ntop = ntop, log10 = TRUE) 
-```
-
 ### Top languages
 
-Number of documents assigned with each language (top-10). For a complete list,
+Number of titles assigned with each language (top-10). For a complete list,
 see [accepted languages](output.tables/language_accepted.csv).
@@
 ```
+
+Title count per language (including multi-language documents; note the log10 scale):
+
+```{r summarylang, echo=FALSE, message=FALSE, warning=FALSE, fig.width=7, fig.height=5}
+top_plot(df, "languages", ntop = ntop, log10 = TRUE) + labs(y = "Entries (n)")
+```

### 2021-02-18 inst/examples/overview.Rmd
ok

--- 2021-02-11 inst/examples/overview.Rmd
@@
   * [Publisher info](publisher.md)
-  * [Publication geography](publicationplace.md)
-  * [Publication year info](publicationyear.md)
+  * [Publication geography](publication_place.md)
+  * [Publication year info](publication_time.md)
+  * [Publication year info](publication_frequency.md)
+  * [Publication year info](publication_interval.md)  
   * [Titles](title.md)  

### 2021-02-18 R/polish_languages.R

@@ -11,15 +11,6 @@ polish_languages <- function(x) {
 
   x0 <- x
 
-  # Harmonize
-  x <- tolower(as.character(x))	       
-  x[x == "NA"] <- ""
-  x[x == "n/a"] <- ""
-  x[is.na(x)] <- ""  
-  x <- gsub("^;","",x)
-  x <- gsub(";$","",x)
-  x <- condense_spaces(x)
-
   # Unique entries only to speed up
   xorig <- x
   xuniq <- unique(xorig)
@@ -32,23 +23,6 @@ polish_languages <- function(x) {
   f <- system.file("extdata/language_abbreviations.csv", package = "fennica")
   abrv <- read.csv(f, sep = "\t", header = TRUE, encoding = "UTF-8")
 
-  # Further harmonization
-  x <- gsub("\\(", " ", x)
-  x <- gsub("\\)", " ", x)
-  x <- gsub("\\,", " ", x)
-  x <- gsub(" +", " ", x)
-  x <- condense_spaces(x)
-  # Final name
-  #abrv$name <- gsub("\\(", " ", abrv$name)
-  #abrv$name <- gsub("\\)", " ", abrv$name)
-  #abrv$name <- gsub("\\,", " ", abrv$name)
-  #abrv$name <- gsub(" +", " ", abrv$name)    
-  abrv$synonyme <- gsub("\\(", " ", abrv$synonyme)
-  abrv$synonyme <- gsub("\\)", " ", abrv$synonyme)
-  abrv$synonyme <- gsub("\\,", " ", abrv$synonyme)
-  abrv$synonyme <- gsub(" +", " ", abrv$synonyme)  
-  abrv <- unique(abrv)
-
   # Unrecognized languages?
   unrec <- as.vector(na.omit(setdiff(
   	     unique(unlist(strsplit(as.character(unique(x)), ";"))),
@@ -59,10 +33,8 @@ polish_languages <- function(x) {
     warning(paste("Unidentified languages: ", paste(unrec, collapse = ";")))
   }
 
-
   # TODO Vectorize to speed up ?
-  for (i in 1:length(x)) {
-    
+  for (i in 1:length(x)) {    
       lll <- sapply(unlist(strsplit(x[[i]], ";")), function (xx) {
                as.character(map(xx, abrv, remove.unknown = TRUE, mode = "exact.match"))
 	       })
@@ -86,17 +58,17 @@ polish_languages <- function(x) {
[…]

### 2021-02-18 R/round.R

@@ -1,0 +1,27 @@
+#' @title Get Decade
+#' @description Round year into decade.
+#' @param x a numeric variable 
+#' @return Decade. A numeric.
+#' @author Leo Lahti \email{leo.lahti@@iki.fi}
+#' @references See citation("fennica")
+#' @export
+#' @examples decade(1962)
+#' @keywords utilities
+decade <- function (x) {
+  x <- as.numeric(as.character(x))
+  floor(x/10) * 10
+}
+
+#' @title Get Century
+#' @description Round year into century.
+#' @param x a numeric variable 
+#' @return Century. A numeric.
+#' @author Leo Lahti \email{leo.lahti@@iki.fi}
+#' @references See citation("fennica")
+#' @export
+#' @examples century(1962)
+#' @keywords utilities
+century <- function (x) {
+  x <- as.numeric(as.character(x))
+  floor(x/100) * 100
+}

### 2021-02-18 inst/examples/publication_time.R

@@ -1,12 +1,14 @@
 # ENRICHMENT AND VALIDATION
-min.year <- 1400
-max.year <- as.numeric(format(Sys.time(), "%Y")) # this.year
-tmp      <- polish_years(df.orig[[field]], check = TRUE, min.year = min.year, max.year = max.year)
+field <- "publication_time"
+tmp   <- polish_years(df.orig[[field]], check = TRUE)
       
 # Make data.frame
 df.harmonized <- data.frame(original_row = df.orig$original_row,
                      publication_year_from = tmp$from,
                      publication_year_till = tmp$till)
+
+# Add publication_year
+df.harmonized$publication_year <- df.harmonized$publication_year_from
 
 # Add publication_decade
 df.harmonized$publication_decade <- decade(df.harmonized$publication_year) 
@@ -20,7 +22,30 @@ saveRDS(df.harmonized, file = data.file)
 
 # ---------------------------------------------------------------------
 
-# TODO pick publication_time specific parts
-# Summarize the data and discarded entries
-#tmp <- generate_summary_tables(df.harmonized, df.orig, output.folder)
+message("Write conversions: publication year")
+df.harmonized$original <- df.orig[[field]]
+
+xx <- as.data.frame(df.harmonized) %>% filter(!is.na(publication_year)) %>%
+                                       group_by(original, publication_year) %>%
+                                       tally() %>%
+				       arrange(desc(n))
+
+tmp <- write.table(xx,
+         file = paste(output.folder, "publication_year_conversion.csv",
+           sep = ""), quote = FALSE, row.names = FALSE)
+  
+message("Discarded publication year")
+o <- as.character(df.orig[[field]])
+x <- as.character(df.harmonized[["publication_year"]])
+inds <- which(is.na(x))
+tmp <- write_xtable(o[inds],
+      paste(output.folder, "publication_year_discarded.csv", sep = ""),
+      count = TRUE)
+
+# ------------------------------------------------------------
+
+# Generate markdown summary 
+df <- readRDS(data.file)
+tmp <- knit(input = paste(field, ".Rmd", sep = ""), 
+            output = paste(field, ".md", sep = ""))
 

### 2021-02-18 inst/examples/publication_frequency.Rmd
ok

--- 2021-01-12 inst/examples/publicationyear.Rmd
@@
 ---
-title: "Publication year summaries"
+title: "Publication frequency summaries"
 author: "Leo Lahti"
@@
 ---
-
-### Publication year
-
-[Publication year conversions](output.tables/publication_year_conversion.csv)
-
-[Publication year discarded](output.tables/publication_year_discarded.csv)
-
-Publication year is available for `r sum(!is.na(df$publication_year))` documents (`r round(100*mean(!is.na(df$publication_year)))`%).
-The publication years span `r paste(range(na.omit(df$publication_year)), collapse = "-")`.
-
-```{r summarypublicationyear, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
-# Title count per decade
-df <- df.preprocessed
-df2 <- df %>% group_by(publication_decade) %>% filter(publication_decade < 2010) 
-p <- ggplot(df2, aes(publication_decade)) +
-     geom_bar() + scale_y_log10() +
-     ggtitle("Title count timeline")
-print(p)
-```
 
@@
 [Publication frequency discarded](output.tables/publication_frequency_discarded.csv)
-
-### Publication interval
-
-Publication interval is available for `r sum(!is.na(df$publication_interval_from) | !is.na(df$publication_interval_till))` documents (`r round(100*mean(!is.na(df$publication_interval_from) | !is.na(df$publication_interval_till)))`%).
-
-[Publication interval accepted](output.tables/publication_interval_accepted.csv)
-
-[Publication interval conversions](output.tables/publication_interval_conversion_nontrivial.csv)
-
-[Publication interval discarded](output.tables/publication_interval_discarded.csv)
-
-### Editions
-
-Automated detection of potential first editions (first_edition field)
-identifies unique author-title pairs, and proposes the first
-occcurrence (earliest publication_year) as the first edition. If there
-are multiple instances from the same earliest year, they are all
-marked as potential first editions. Later need to check if this
-information is readily available in MARC.
-
-There are `r nrow(unique(df[, c("title", "author")]))` unique
-documents with an identical title and author and
-`r nrow(df %>% group_by(title, author) %>% tally() %>% filter(n > 1))`
-of those have multiple occurrences, sometimes with different publication
-years.  The earliest occurrence is suggested as the first edition.
-
-This figure shows the number of first editions per decade.
-
-```{r firsteditions, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=6}
-df <- df.preprocessed
-df <- df %>% group_by(publication_decade) %>%
-             summarise(total = n(), first = sum(first_edition, na.rm = TRUE))
-df2 <- melt(df, id = "publication_decade")
-theme_set(theme_bw(20))
-p <- ggplot(df2, aes(x = publication_decade, y = value, group = variable)) +
-       geom_point(aes(shape = variable), size = 5) +
-       geom_line(aes(shape = variable)) +       
-       geom_smooth(aes(col = variable, fill = variable)) + 
-       xlab("Publication year") +
-       ylab("First editions (n)") +
-       #scale_y_log10() +
-       ggtitle("First editions vs. total title count")
-print(p)
-```

### 2021-02-18 inst/examples/publication_interval.Rmd
ok

--- 2021-01-12 inst/examples/publicationyear.Rmd
@@
 ---
-title: "Publication year summaries"
+title: "Publication interval summaries"
 author: "Leo Lahti"
@@
 ---
-
-### Publication year
-
-[Publication year conversions](output.tables/publication_year_conversion.csv)
-
-[Publication year discarded](output.tables/publication_year_discarded.csv)
-
-Publication year is available for `r sum(!is.na(df$publication_year))` documents (`r round(100*mean(!is.na(df$publication_year)))`%).
-The publication years span `r paste(range(na.omit(df$publication_year)), collapse = "-")`.
-
-```{r summarypublicationyear, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
-# Title count per decade
-df <- df.preprocessed
-df2 <- df %>% group_by(publication_decade) %>% filter(publication_decade < 2010) 
-p <- ggplot(df2, aes(publication_decade)) +
-     geom_bar() + scale_y_log10() +
-     ggtitle("Title count timeline")
-print(p)
-```
-
-### Publication frequency
-
-Publication frequency information is available for `r sum(!is.na(df$publication_frequency_text))` documents (`r round(100*mean(!is.na(df$publication_frequency_text)))`%).
-The links are invalid if the lists are empty.
-The (estimated annual) frequencies are converted to plain text according to their closest match in [this table](https://github.com/COMHIS/fennica/blob/master/inst/extdata/frequency_conversions.csv).
-
-[Publication frequency accepted](output.tables/publication_frequency_accepted.csv)
-
-[Publication frequency conversions](output.tables/publication_frequency_conversion.csv)
-
-[Publication frequency discarded](output.tables/publication_frequency_discarded.csv)
 
@@
 [Publication interval discarded](output.tables/publication_interval_discarded.csv)
-
-### Editions
-
-Automated detection of potential first editions (first_edition field)
-identifies unique author-title pairs, and proposes the first
-occcurrence (earliest publication_year) as the first edition. If there
-are multiple instances from the same earliest year, they are all
-marked as potential first editions. Later need to check if this
-information is readily available in MARC.
-
-There are `r nrow(unique(df[, c("title", "author")]))` unique
-documents with an identical title and author and
-`r nrow(df %>% group_by(title, author) %>% tally() %>% filter(n > 1))`
-of those have multiple occurrences, sometimes with different publication
-years.  The earliest occurrence is suggested as the first edition.
-
-This figure shows the number of first editions per decade.
-
-```{r firsteditions, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=6}
-df <- df.preprocessed
-df <- df %>% group_by(publication_decade) %>%
-             summarise(total = n(), first = sum(first_edition, na.rm = TRUE))
-df2 <- melt(df, id = "publication_decade")
-theme_set(theme_bw(20))
-p <- ggplot(df2, aes(x = publication_decade, y = value, group = variable)) +
-       geom_point(aes(shape = variable), size = 5) +
-       geom_line(aes(shape = variable)) +       
-       geom_smooth(aes(col = variable, fill = variable)) + 
-       xlab("Publication year") +
-       ylab("First editions (n)") +
-       #scale_y_log10() +
-       ggtitle("First editions vs. total title count")
-print(p)
-```

### 2021-02-18 inst/examples/publication_time.Rmd
ok

--- 2021-01-12 inst/examples/publicationyear.Rmd
@@
 
-### Publication year
+### Publication time (publication year)
 
@@
 ```
-
-### Publication frequency
-
-Publication frequency information is available for `r sum(!is.na(df$publication_frequency_text))` documents (`r round(100*mean(!is.na(df$publication_frequency_text)))`%).
-The links are invalid if the lists are empty.
-The (estimated annual) frequencies are converted to plain text according to their closest match in [this table](https://github.com/COMHIS/fennica/blob/master/inst/extdata/frequency_conversions.csv).
-
-[Publication frequency accepted](output.tables/publication_frequency_accepted.csv)
-
-[Publication frequency conversions](output.tables/publication_frequency_conversion.csv)
-
-[Publication frequency discarded](output.tables/publication_frequency_discarded.csv)
-
-### Publication interval
-
-Publication interval is available for `r sum(!is.na(df$publication_interval_from) | !is.na(df$publication_interval_till))` documents (`r round(100*mean(!is.na(df$publication_interval_from) | !is.na(df$publication_interval_till)))`%).
-
-[Publication interval accepted](output.tables/publication_interval_accepted.csv)
-
-[Publication interval conversions](output.tables/publication_interval_conversion_nontrivial.csv)
-
-[Publication interval discarded](output.tables/publication_interval_discarded.csv)
-
-### Editions
-
-Automated detection of potential first editions (first_edition field)
-identifies unique author-title pairs, and proposes the first
-occcurrence (earliest publication_year) as the first edition. If there
-are multiple instances from the same earliest year, they are all
-marked as potential first editions. Later need to check if this
-information is readily available in MARC.
-
-There are `r nrow(unique(df[, c("title", "author")]))` unique
-documents with an identical title and author and
-`r nrow(df %>% group_by(title, author) %>% tally() %>% filter(n > 1))`
-of those have multiple occurrences, sometimes with different publication
-years.  The earliest occurrence is suggested as the first edition.
-
-This figure shows the number of first editions per decade.
-
-```{r firsteditions, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=6}
-df <- df.preprocessed
-df <- df %>% group_by(publication_decade) %>%
-             summarise(total = n(), first = sum(first_edition, na.rm = TRUE))
-df2 <- melt(df, id = "publication_decade")
-theme_set(theme_bw(20))
-p <- ggplot(df2, aes(x = publication_decade, y = value, group = variable)) +
-       geom_point(aes(shape = variable), size = 5) +
-       geom_line(aes(shape = variable)) +       
-       geom_smooth(aes(col = variable, fill = variable)) + 
-       xlab("Publication year") +
-       ylab("First editions (n)") +
-       #scale_y_log10() +
-       ggtitle("First editions vs. total title count")
-print(p)
-```

### 2021-02-19 inst/examples/author_name.Rmd
change

--- 2021-02-18 inst/examples/note_source.Rmd
@@
 ---
-title: "note_source"
+title: "author_name"
 output: md_document
@@
 theme_set(theme_bw(base_size = 12))
-p <- top_plot(df, "note_source", ntop = ntop, log10 = TRUE)+
+p <- top_plot(df, "author_name", ntop = ntop, log10 = TRUE)+
   labs(y = "Entries (n)", title = "Top titles")
@@
 ```{r uniquetitles, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
-tab <- table(df$note_source)
+tab <- table(df$author_name)
 d <- data.frame(title = names(tab), n = as.numeric(tab))

### 2021-02-19 inst/examples/author_name.R

@@ -1,4 +1,55 @@
+
+field <- "author_name"
 # Full author name (Last, First) 
 author <- polish_author(df.orig[[field]], verbose = FALSE)
 df.tmp <- data.frame(author_name = author)
 
+
+
+df.tmp <- data.frame(df.orig[[field]])
+df.tmp <- mark_dissertations(df.orig[[field]])
+names(df.tmp) <- field
+
+# Raw data
+original <- df.orig[[field]]
+
+# Harmonize the raw data
+x <- fennica::polish_title(original)
+
+# Collect the results into a data.frame
+df.tmp <- data.frame(original_row = df.orig$original_row,
+                     author_name = x)
+
+# Store the title field data
+# FIXME: convert to feather or plain CSV
+data.file <- paste0(field, ".Rds")
+saveRDS(df.tmp, file = data.file)
+
+# Define output files
+file_accepted  <- paste0(output.folder, field, "_accepted.csv")
+file_discarded <- paste0(output.folder, field, "_discarded.csv")
+
+# ------------------------------------------------------------
+
+# Generate data summaries
+
+message("Accepted entries in the preprocessed data")
+s <- write_xtable(df.tmp[[field]], file_accepted, count = TRUE)
+
+message("Discarded entries in the original data")
+
+# NA values in the final harmonized data
+inds <- which(is.na(df.tmp[[field]]))
+
+# Original entries that were converted into NA
+original.na <- df.orig[match(df.tmp$original_row[inds], df.orig$original_row), field]
+
+# .. ie. those are "discarded" cases; list them in a table
+tmp <- write_xtable(original.na, file_discarded, count = TRUE)
+
+# ------------------------------------------------------------
+
+# Generate markdown summary in note_source.md
+df <- readRDS(data.file)
+tmp <- knit(input = paste(field, ".Rmd", sep = ""), 
+            output = paste(field, ".md", sep = ""))

### 2021-02-24 inst/examples/overview.Rmd
fixed

--- 2021-02-11 inst/examples/overview.Rmd
@@
 title: "Preprocessing overview"
-author: "`r author`"
+author: ""
 date: "`r Sys.Date()`"
-output: markdown_document
+output: md_document
 ---
@@
 
-  * [Author info](author.md)
+  * [Author info](author_name.md)
   * [Gender info](gender.md)
   * [Publisher info](publisher.md)
-  * [Publication geography](publicationplace.md)
-  * [Publication year info](publicationyear.md)
+  * [Publication geography](publication_place.md)
+  * [Publication year info](publication_time.md)
+  * [Publication year info](publication_frequency.md)
+  * [Publication year info](publication_interval.md)  
   * [Titles](title.md)  

### 2021-02-24 inst/examples/overview.Rmd
update

@@
 
-  * [Author info](author_name.md)
+  * [Author\_name(author_name.md)
   * [Gender info](gender.md)

### 2021-03-03 inst/examples/author_name.Rmd
check

@@
 ```
+
+## Authors
+
+* `r length(unique(df$author_name))` [unique authors](output.tables/author_accepted.csv) These final names capture all name variants from the custom [author synonyme table](https://github.com/COMHIS/fennica/blob/master/inst/extdata/ambiguous-authors.csv), and exclude known pseudonymes (see below).
+If multiple names for the same author are still observed on this list, they should be added on the [author synonyme table](https://github.com/COMHIS/fennica/blob/master/inst/extdata/ambiguous-authors.csv).
+ * `r sum(!is.na(df$author_name))` documents have unambiguous author information (`r round(100*mean(!is.na(df$author_name)))`%). 
+ * `r length(unique(subset(df.preprocessed, author_pseudonyme)$author_name))` [unique pseudonymes](output.tables/pseudonyme_accepted.csv) are recognized based on [custom pseudonyme lists](https://github.com/COMHIS/fennica/blob/master/inst/extdata/names/pseudonymes/custom_pseudonymes.csv).
+ * `r length(readLines(paste0(this.folder, "/output.tables/author_discarded.csv")))-2` [discarded author names](output.tables/author_discarded.csv) This list should not include any real authors (if it does, please send a note to the admin).
+The stopword lists are considered when discarding names.
+ * [Author name conversions](output.tables/author_conversion_nontrivial.csv) Non-trivial conversions from the original raw data to final names.
+
+### Auxiliary files
+
+ * [Author synonyme table](https://github.com/COMHIS/fennica/blob/master/inst/extdata/ambiguous-authors.csv)
+ * [Stopwords for names](https://github.com/COMHIS/fennica/blob/master/inst/extdata/stopwords_for_names.csv)
+ * [Stopwords for titles](https://github.com/COMHIS/fennica/blob/master/inst/extdata/stopwords_titles.csv)
+ * [Custom pseudonyme lists](https://github.com/COMHIS/fennica/blob/master/inst/extdata/names/pseudonymes/custom_pseudonymes.csv)
+
+Top-`r ntop` uniquely identified authors and their productivity (title count).
+
+```{r summaryauthorsnames, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5, out.width='430px', fig.show='hold'}
+knitr::opts_chunk$set(fig.path = "figure_slides/", dev="CairoPNG")
+theme_set(theme_bw(base_size = 12))
+p <- NULL
+p <- top_plot(df, "author_name", ntop) +
+     		  ggtitle(paste("Top authors' names")) +
+		  ylab("Documents")
+print(p)
+```
+
+## summary discraded plot does not work 
+```{r summarydiscardedauthors, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5, out.width='430px', fig.show='hold'}
+dff = df %>%
+      filter(is.na(author) & !is.na(author_name)) %>%
+      select(author_name)
+p <- top_plot(dff,  "author_name", ntop) + ggtitle("Top discarded authors")
+print(p)
+```
+
+### Author productivity
+
+Title count versus paper consumption (all authors):
+
+```{r authortitlespapers, fig.height=8, fig.width=18, echo=FALSE, warning=FALSE}
+theme_set(theme_bw(base_size = 12))
+res1 <- compare_title_paper(df, "author_name", plot.mode = "text")
+res2 <- compare_title_paper(df, "author_name", plot.mode = "point")
+grid.arrange(res2$plot, res1$plot, nrow = 1)
+#kable(res1$table)
+```
+
+#Publication_decade not found
+#```{r summaryTop10authorstimeline, fig.height=8, fig.width=16, echo=FALSE}
+theme_set(theme_bw(20))
+top.authors <- names(top_n(df, field = "author_name", n = 3))
+dfs <- df %>% filter(author %in% top.authors) %>%
+     	 group_by(author_name, publication_decade) %>%
+     	 tally() %>%
+     	 arrange(publication_decade)
+p <- ggplot(dfs, aes(x = publication_decade, y = n, fill = author)) +
+       geom_bar(stat = "identity", position = "stack", color = "black") +
+       xlab("Publication Decade") +
+       ylab("Title Count") +
+       scale_fill_grey() +
+       guides(fill = guide_legend("Author")) +
+       ggtitle("Title count timeline for the top authors")
+print(p)
+##```
+
+###Publication year not found
+##```{r topauth, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=13, fig.height=6}
+df <- df.preprocessed
+top.authors <- names(rev(sort(table(df.preprocessed$author))))[1:10]
+df2 <- df %>% filter(author %in% top.authors) %>% group_by(publication_year, author) %>% summarize(paper = sum(paper, na.rm = TRUE), n = n())
+
+p <- ggplot(df2, aes(x = publication_year, y = paper, group = author, color = author))
+p <- p + geom_point()
+p <- p + geom_line()
+p <- p + ggtitle("Paper consumption per author")
+p <- p + xlab("Year")
+p <- p + scale_y_log10()
+p <- p + ylab("Paper consumption")
+print(p)
+
+p <- ggplot(df2, aes(x = publication_year, y = n, group = author, color = author))
+p <- p + geom_point()
+p <- p + geom_line()
+p <- p + ggtitle("Documents per author")
+p <- p + xlab("Year")
+p <- p + scale_y_log10()
+p <- p + ylab("Documents (n)")
+print(p)
+###```

### 2021-03-03 inst/examples/author_name.Rmd
change

--- 2021-02-19 inst/examples/author_name.Rmd
@@
 ```
+
+## Authors
+
+* `r length(unique(df$author_name))` [unique authors](output.tables/author_accepted.csv) These final names capture all name variants from the custom [author synonyme table](https://github.com/COMHIS/fennica/blob/master/inst/extdata/ambiguous-authors.csv), and exclude known pseudonymes (see below).
+If multiple names for the same author are still observed on this list, they should be added on the [author synonyme table](https://github.com/COMHIS/fennica/blob/master/inst/extdata/ambiguous-authors.csv).
+ * `r sum(!is.na(df$author_name))` documents have unambiguous author information (`r round(100*mean(!is.na(df$author_name)))`%). 
+ * `r length(readLines(paste0(getwd(),"/output.tables/pseudonyme_accepted.csv")))` [unique pseudonymes](output.tables/pseudonyme_accepted.csv) are recognized based on [custom pseudonyme lists](https://github.com/COMHIS/fennica/blob/master/inst/extdata/names/pseudonymes/custom_pseudonymes.csv).
+ * `r length(readLines(paste0(getwd(),"/output.tables/author_discarded.csv")))-2` [discarded author names](output.tables/author_discarded.csv) This list should not include any real authors (if it does, please send a note to the admin).
+The stopword lists are considered when discarding names.
+ * [Author name conversions](output.tables/author_conversion_nontrivial.csv) Non-trivial conversions from the original raw data to final names.
+
+### Auxiliary files
+
+ * [Author synonyme table](https://github.com/COMHIS/fennica/blob/master/inst/extdata/ambiguous-authors.csv)
+ * [Stopwords for names](https://github.com/COMHIS/fennica/blob/master/inst/extdata/stopwords_for_names.csv)
+ * [Stopwords for titles](https://github.com/COMHIS/fennica/blob/master/inst/extdata/stopwords_titles.csv)
+ * [Custom pseudonyme lists](https://github.com/COMHIS/fennica/blob/master/inst/extdata/names/pseudonymes/custom_pseudonymes.csv)
+
+Top-`r ntop` uniquely identified authors and their productivity (title count).
+
+```{r summaryauthorsnames, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5, out.width='430px', fig.show='hold'}
+knitr::opts_chunk$set(fig.path = "figure/", dev="CairoPNG")
+theme_set(theme_bw(base_size = 12))
+p <- NULL
+p <- top_plot(df, "author_name", ntop) +
+     		  ggtitle(paste("Top authors' names")) +
+		  ylab("Documents")
+print(p)
+```
+
+### Author productivity
+
+Title count versus paper consumption (all authors):
+
+```{r authortitlespapers, fig.height=8, fig.width=18, echo=FALSE, warning=FALSE}
+theme_set(theme_bw(base_size = 12))
+res1 <- compare_title_paper(df, "author_name", plot.mode = "text")
+res2 <- compare_title_paper(df, "author_name", plot.mode = "point")
+grid.arrange(res2$plot, res1$plot, nrow = 1)
+#kable(res1$table)
+```

### 2021-03-03 inst/examples/author_name.Rmd
update

@@
  * `r sum(!is.na(df$author_name))` documents have unambiguous author information (`r round(100*mean(!is.na(df$author_name)))`%). 
- * `r length(readLines(paste0(getwd(),"/output.tables/pseudonyme_accepted.csv")))` [unique pseudonymes](output.tables/pseudonyme_accepted.csv) are recognized based on [custom pseudonyme lists](https://github.com/COMHIS/fennica/blob/master/inst/extdata/names/pseudonymes/custom_pseudonymes.csv).
+ * `r length(readLines(paste0(getwd(),"/output.tables/pseudonyme_accepted.csv")))-2` [unique pseudonymes](output.tables/pseudonyme_accepted.csv) are recognized based on [custom pseudonyme lists](https://github.com/COMHIS/fennica/blob/master/inst/extdata/names/pseudonymes/custom_pseudonymes.csv).
  * `r length(readLines(paste0(getwd(),"/output.tables/author_discarded.csv")))-2` [discarded author names](output.tables/author_discarded.csv) This list should not include any real authors (if it does, please send a note to the admin).

### 2021-03-04 inst/examples/publisher.Rmd
change

@@
 This includes documents identified as self-published; the author name is used as the publisher in those cases (if known).
-
- * `r length(which(df$self_published))` documents are identified as self-published (`r round(100*(length(which(df$self_published))/nrow(df)), 1)`%).
 
@@
 
-### Publication timeline for top publishers
-
-Title count
-
-```{r top_pub_timeline, fig.height=10, fig.width=20, echo=FALSE}
-# For some reason the ggplot never completes if top n > 2 ???
-theme_set(theme_bw(20))
-field <- "publisher"
-tops <- names(top(df, field, n = 2))
-dfs <- df %>% select(field, publication_decade) 
-dfs$field <- as.character(dfs[[field]]); dfs[[field]] <- NULL
-dfs <- dfs %>% filter(field %in% tops) %>%
-               filter(!is.na(field) & !is.na(publication_decade)) %>%
-	       count(field, publication_decade)
-dfs$field <- as.factor(dfs$field)
-p <- ggplot(dfs, aes(x = publication_decade, y = n, fill = field)) +
-       geom_bar(stat = "identity", position = "stack", color = "black") +       
-       labs(x = "Publication Decade", y = "Title Count",
-            title = "Title count timeline for the top publishers") +
-       scale_fill_grey() +
-       guides(fill = guide_legend("Publisher")) 
-# print(p)
-```
-
 Title count versus paper consumption (top publishers):
@@
 ```
-
-### Corporates
-
-Summaries of the corporate field.
-
- * `r length(unique(df$corporate))` [unique corporates](output.tables/corporate_accepted.csv)
-
- * `r sum(!is.na(df$corporate))` documents have unambiguous corporate information (`r round(100*mean(!is.na(df$corporate)), 1)`%).
-
- * [Discarded corporate entries](output.tables/corporate_discarded.csv)
-
- * [Conversions from original to final names](output.tables/corporate_conversion_nontrivial.csv) (only non-trivial conversions shown)
-
-The `r ntop` most common corporates are shown with the number of documents.
-
-```{r summarycorporate2, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=9}
-p <- top_plot(df, "corporate", ntop)
-p <- p + ggtitle(paste("Top corporates"))
-p <- p + scale_y_log10()
-p <- p + ylab("Documents")
-print(p)
-```
-
-## Publisher
-
-[Self-published accepted](https://github.com/COMHIS/fennica/blob/master/inst/examples/output.tables/self_published_accepted.csv) (Check for formatting and synonymes)
-
-[Self-published raw fields](https://github.com/COMHIS/fennica/blob/master/inst/examples/output.tables/self_published_rawfields.csv) (Check that the self-publication is a correct classification for these docs)
-
-## Corporate info
-
-[Accepted corporate info](https://github.com/COMHIS/fennica/blob/master/inst/examples/output.tables/corporate_accepted.csv)
-
-[Discarded corporate info](https://github.com/COMHIS/fennica/blob/master/inst/examples/output.tables/corporate_discarded.csv)

### 2021-03-04 inst/examples/main.R
change

@@ -9,6 +9,9 @@ source("init.R")
 #           PREPROCESS DATA
 # ----------------------------------------------------
 
+# author_date field
+source("author_date.R")
+
 # author_name field
 source("author_name.R")
 

### 2021-03-05 inst/examples/publication_time.Rmd
update

@@
 # Title count per decade
-df <- df.preprocessed
 df2 <- df %>% group_by(publication_decade) %>% filter(publication_decade < 2010) 

### 2021-03-10 inst/examples/publication_interval.R
change

@@ -1,11 +1,11 @@
-
+field <- "publication_interval"
 
 tmp <- polish_years(df.orig[[field]], check = TRUE)
       
 # Add to data.frame
-df.tmp <- data.frame(publication_interval_from = tmp$from,
+df.tmp <- data.frame(original_row = df.orig$original_row,
+                     publication_interval_from = tmp$from,
               	     publication_interval_till = tmp$till)
-
 
 message("Enrich publication interval")
 # Based on analysis of a random sample of entries in Fennica,
@@ -25,5 +25,40 @@ df.tmp$publication_interval_from[df.tmp$publication_interval_from > 2000] <- NA
 df.tmp$publication_interval_till[df.tmp$publication_interval_till < 1400] <- NA
 df.tmp$publication_interval_till[df.tmp$publication_interval_till > 2000] <- NA
 
+
+
 # ---------------------------------------------------------------------
+# Store the title field data
+# FIXME: convert to feather or plain CSV
+data.file <- paste0(field, ".Rds")
+saveRDS(df.tmp, file = data.file)
+
+# Define output files
+file_accepted  <- paste0(output.folder, field, "_accepted.csv")
+file_discarded <- paste0(output.folder, field, "_discarded.csv")
+
+# ------------------------------------------------------------
+
+# Generate data summaries
+
+message("Accepted entries in the preprocessed data")
+s <- write_xtable(df.tmp[[field]], file_accepted, count = TRUE)
+
+message("Discarded entries in the original data")
+
+# NA values in the final harmonized data
+inds <- which(is.na(df.tmp[[field]]))
+
+# Original entries that were converted into NA
+original.na <- df.orig[match(df.tmp$original_row[inds], df.orig$original_row), field]
+
+# .. ie. those are "discarded" cases; list them in a table
+tmp <- write_xtable(original.na, file_discarded, count = TRUE)
+
+# ------------------------------------------------------------
+
+# Generate markdown summary in note_source.md
+df <- readRDS(data.file)
+tmp <- knit(input = paste(field, ".Rmd", sep = ""), 
+            output = paste(field, ".md", sep = ""))
 

### 2021-03-10 inst/examples/overview.Rmd
update

@@
 
-  * [Author\_name(author_name.md)
+  * [Author date](author_date.md)
+  * [Author name](author_name.md)
   * [Gender info](gender.md)

### 2021-12-10 inst/examples/author_name.Rmd
ok

@@
 ```{r authortitlespapers, fig.height=8, fig.width=18, echo=FALSE, warning=FALSE}
+library(dplyr)
+library(gridExtra)
+library(grid)
+library(ggplot2)
+library(lattice)
+
 theme_set(theme_bw(base_size = 12))

### 2021-12-10 inst/examples/publication_place.Rmd
ok

--- 2021-02-17 inst/extras/deprecated/publicationplace.Rmd
@@
  * `r length(unique(str_trim(unlist(strsplit(as.character(df$publication_place), ";")))))` [unique publication places](output.tables/publication_place_accepted.csv); available for `r sum(!is.na(df$publication_place))` documents (`r round(100*mean(!is.na(df$publication_place)))`%).
- * `r length(readLines(paste0(this.folder, "/output.tables/publication_place_ambiguous.csv"))) - 1` [ambiguous publication places](output.tables/publication_place_ambiguous.csv); some of these can be possibly resolved by checking that the the [synonyme list](https://github.com/COMHIS/fennica/blob/master/inst/extdata/PublicationPlaceSynonymes.csv) does not contain multiple versions of the final name (case sensitive).
- * `r try(length(readLines(paste0(this.folder, "/output.tables/publication_place_todo.csv"))))` [unknown place names](output.tables/publication_place_todo.csv) These terms do not map to any known place on the [synonyme list](https://github.com/COMHIS/fennica/blob/master/inst/extdata/PublicationPlaceSynonymes.csv); either because they require further cleaning or have not yet been encountered in the analyses.
+ * `r length(readLines(paste0("output.tables/publication_place_ambiguous.csv"))) - 1` [ambiguous publication places](output.tables/publication_place_ambiguous.csv); some of these can be possibly resolved by checking that the the [synonyme list](https://github.com/COMHIS/fennica/blob/master/inst/extdata/PublicationPlaceSynonymes.csv) does not contain multiple versions of the final name (case sensitive).
+ * `r try(length(readLines(paste0("output.tables/publication_place_todo.csv"))))` [unknown place names](output.tables/publication_place_todo.csv) These terms do not map to any known place on the [synonyme list](https://github.com/COMHIS/fennica/blob/master/inst/extdata/PublicationPlaceSynonymes.csv); either because they require further cleaning or have not yet been encountered in the analyses.
 Terms that are clearly not place names can be added to [stopwords](inst/extdata/stopwords_for_place.csv); borderline cases that are not accepted as place names can be added as NA on the [synonyme list](https://github.com/COMHIS/fennica/blob/master/inst/extdata/PublicationPlaceSynonymes.csv).
- * `r length(readLines(paste0(this.folder, "/output.tables/publication_place_discarded.csv"))) - 1` [discarded place names](output.tables/publication_place_discarded.csv) These terms are potential place names but with a closer check have been explicitly rejected on the [synonyme list](https://github.com/COMHIS/fennica/blob/master/inst/extdata/PublicationPlaceSynonymes.csv)
+ * `r length(readLines(paste0("output.tables/publication_place_discarded.csv"))) - 1` [discarded place names](output.tables/publication_place_discarded.csv) These terms are potential place names but with a closer check have been explicitly rejected on the [synonyme list](https://github.com/COMHIS/fennica/blob/master/inst/extdata/PublicationPlaceSynonymes.csv)
  * [Conversions from the original to the accepted place names](output.tables/publication_place_conversion_nontrivial.csv) 
@@
  * `r length(na.omit(unique(subset(df, is.na(publication_country))$publication_place)))` [places with unknown publication country](output.tables/publication_place_missingcountry.csv) (`r round(100 * length(na.omit(unique(subset(df, is.na(publication_country))$publication_place))) / length(na.omit(unique(df$publication_place))), 1)`% of the unique places; can be added to [country mappings](https://github.com/COMHIS/fennica/blob/master/inst/extdata/reg2country.csv))
- * `r length(readLines(paste0(this.folder, "/output.tables/publication_country_ambiguous.csv"))) - 1` [potentially ambiguous region-country mappings](output.tables/publication_country_ambiguous.csv) (these may occur in the data in various synonymes and the country is not always clear when multiple countries have a similar place name; the default country is listed first).
+ * `r length(readLines(paste0("output.tables/publication_country_ambiguous.csv"))) - 1` [potentially ambiguous region-country mappings](output.tables/publication_country_ambiguous.csv) (these may occur in the data in various synonymes and the country is not always clear when multiple countries have a similar place name; the default country is listed first).
 NOTE: possible improvements should not be done in this output summary but instead in the [country mapping file](https://github.com/COMHIS/fennica/blob/master/inst/extdata/reg2country.csv).
@@
 
- * `r round(100*mean(!is.na(df$latitude) & !is.na(df$longitude)), 1)`% of the documents were matched to geographic coordinates (based on [Geonames](http://download.geonames.org/export/dump/)).
+ * `r round(100*mean(!is.na(df$latitude) & !is.na(df$longitude)), 1)`% of the documents were matched to geographic coordinates (based on COMHIS geomapping process).
  * `r length(unique(df$publication_place[(is.na(df$latitude))]))` unique places (`r round(100 * length(unique(df$publication_place[(is.na(df$latitude))]))/length(unique(df$publication_place)), 1)`% of all unique places and `r round(100 * mean(is.na(df$latitude) | is.na(df$longitude)), 2)`% of all documents) are missing geocoordinates.
 See [list of places missing geocoordinate information](output.tables/absentgeocoordinates.csv).
-
-### Publication geography
-
- * `r length(unique(df$publication_geography_country))` [unique countries](output.tables/publication_geography_country_accepted.csv) on geographical region considered in the publication; available for `r sum(!is.na(df$publication_geography_country))` documents (`r round(100*mean(!is.na(df$publication_geography_country)))`%).
- * `r length(unique(df$publication_geography_place))` [unique places](output.tables/publication_geography_place_accepted.csv) on geographical region considered in the publication; available for `r sum(!is.na(df$publication_geography_place))` documents (`r round(100*mean(!is.na(df$publication_geography_place)))`%).

### 2021-12-10 inst/examples/uncontrolled.Rmd
ok

--- 2021-02-10 inst/examples/uncontrolled.Rmd
@@
 
-* [Unique accepted titles](output.tables/title_accepted.csv): `r length(unique(df$uncontrolled))`
-* [Unique discarded titles in original data](output.tables/title_discarded.csv) (excluding NA cases): `r as.vector(countLines(paste0(output.folder, "/uncontrolled_discarded.csv")) - 1)` 
-* Original documents with non-NA titles: `r sum(!is.na(df$uncontrolled))` / `r nrow(df)` (`r round(100*mean(!is.na(df$uncontrolled)), 1)`%)
-* Original documents with missing (NA) titles `r sum(is.na(df$uncontrolled))` / `r nrow(df)` documents (`r round(100*mean(is.na(df$uncontrolled)), 1)`%)
+* [Unique accepted entries](`r file_accepted`): `r length(unique(df[[field]]))`
+* [Unique discarded entries in original data](`r file_discarded`) (excluding NA cases): `r as.vector(countLines(file_discarded) - 1)`
+* Original documents with non-NA titles: `r sum(!is.na(df[[field]]))` / `r nrow(df)` (`r round(100*mean(!is.na(df[[field]])), 1)`%)
+* Original documents with missing (NA) titles `r sum(is.na(df[[field]]))` / `r nrow(df)` documents (`r round(100*mean(is.na(df[[field]])), 1)`%)
 

### 2022-04-20 inst/examples/holder.Rmd
ok

--- 2021-02-10 inst/examples/holder.Rmd
@@
 
-* [Unique accepted titles](output.tables/title_accepted.csv): `r length(unique(df$holder))`
-* [Unique discarded titles in original data](output.tables/title_discarded.csv) (excluding NA cases): `r as.vector(countLines(paste0(output.folder, "/holder_discarded.csv")) - 1)` 
-* Original documents with non-NA titles: `r sum(!is.na(df$holder))` / `r nrow(df)` (`r round(100*mean(!is.na(df$holder)), 1)`%)
-* Original documents with missing (NA) titles `r sum(is.na(df$holder))` / `r nrow(df)` documents (`r round(100*mean(is.na(df$holder)), 1)`%)
+* [Unique accepted entries](`r file_accepted`): `r length(unique(df[[field]]))`
+* [Unique discarded entries in original data](`r file_discarded`) (excluding NA cases): `r as.vector(countLines(file_discarded) - 1)`
+* Original documents with non-NA titles: `r sum(!is.na(df[[field]]))` / `r nrow(df)` (`r round(100*mean(!is.na(df[[field]])), 1)`%)
+* Original documents with missing (NA) titles `r sum(is.na(df[[field]]))` / `r nrow(df)` documents (`r round(100*mean(is.na(df[[field]])), 1)`%)
 

### 2022-04-20 inst/examples/subject_topic.Rmd
ok

--- 2021-02-10 inst/examples/subject_topic.Rmd
@@
 
-* [Unique accepted titles](output.tables/title_accepted.csv): `r length(unique(df$subject_topic))`
-* [Unique discarded titles in original data](output.tables/title_discarded.csv) (excluding NA cases): `r as.vector(countLines(paste0(output.folder, "/subject_topic_discarded.csv")) - 1)` 
-* Original documents with non-NA titles: `r sum(!is.na(df$subject_topic))` / `r nrow(df)` (`r round(100*mean(!is.na(df$subject_topic)), 1)`%)
-* Original documents with missing (NA) titles `r sum(is.na(df$subject_topic)` / `r nrow(df)` documents (`r round(100*mean(is.na(df$subject_topic)), 1)`%)
+* [Unique accepted entries](`r file_accepted`): `r length(unique(df[[field]]))`
+* [Unique discarded entries in original data](`r file_discarded`) (excluding NA cases): `r as.vector(countLines(file_discarded) - 1)`
+* Original documents with non-NA titles: `r sum(!is.na(df[[field]]))` / `r nrow(df)` (`r round(100*mean(!is.na(df[[field]])), 1)`%)
+* Original documents with missing (NA) titles `r sum(is.na(df[[field]]))` / `r nrow(df)` documents (`r round(100*mean(is.na(df[[field]])), 1)`%)
 

### 2022-04-20 inst/examples/successor.Rmd
ok

--- 2021-02-10 inst/examples/successor.Rmd
@@
 
-* [Unique accepted titles](output.tables/title_accepted.csv): `r length(unique(df$successor))`
-* [Unique discarded titles in original data](output.tables/title_discarded.csv) (excluding NA cases): `r as.vector(countLines(paste0(output.folder, "/successor_discarded.csv")) - 1)` 
-* Original documents with non-NA titles: `r sum(!is.na(df$successor))` / `r nrow(df)` (`r round(100*mean(!is.na(df$successor)), 1)`%)
-* Original documents with missing (NA) titles `r sum(is.na(df$successor))` / `r nrow(df)` documents (`r round(100*mean(is.na(df$successor)), 1)`%)
+* [Unique accepted entries](`r file_accepted`): `r length(unique(df[[field]]))`
+* [Unique discarded entries in original data](`r file_discarded`) (excluding NA cases): `r as.vector(countLines(file_discarded) - 1)`
+* Original documents with non-NA titles: `r sum(!is.na(df[[field]]))` / `r nrow(df)` (`r round(100*mean(!is.na(df[[field]])), 1)`%)
+* Original documents with missing (NA) titles `r sum(is.na(df[[field]]))` / `r nrow(df)` documents (`r round(100*mean(is.na(df[[field]])), 1)`%)
 
@@
 theme_set(theme_bw(base_size = 12))
-p <- top_plot(df, "successor", ntop = ntop, log10 = TRUE)+
+p <- top_plot(df, field, ntop = ntop, log10 = TRUE)+
   labs(y = "Entries (n)", title = "Top titles")
@@
 
-Frequency of unique titles:
+Frequency of unique entries:
 
 ```{r uniquetitles, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
-tab <- table(df$successor)
+tab <- table(df[[field]])
 d <- data.frame(title = names(tab), n = as.numeric(tab))

### 2022-04-20 inst/examples/title_uniform.Rmd
ok

--- 2021-02-04 inst/examples/title_uniform.Rmd
@@
 
- * [Unique accepted titles](output.tables/title_accepted.csv): `r length(unique(df$title_uniform))`
- * [Unique discarded titles in original data](output.tables/title_discarded.csv) (excluding NA cases): `r as.vector(countLines(paste0(output.folder, "/title_uniform_discarded.csv")) - 1)` 
- * Original documents with non-NA titles: `r sum(!is.na(df$title_uniform))` / `r nrow(df)` (`r round(100*mean(!is.na(df$title_uniform)), 1)`%)
- * Original documents with missing (NA) titles `r sum(is.na(df$title_uniform))` / `r nrow(df)` documents (`r round(100*mean(is.na(df$title_uniform)), 1)`%)
+* [Unique accepted entries](`r file_accepted`): `r length(unique(df[[field]]))`
+* [Unique discarded entries in original data](`r file_discarded`) (excluding NA cases): `r as.vector(countLines(file_discarded) - 1)`
+* Original documents with non-NA titles: `r sum(!is.na(df[[field]]))` / `r nrow(df)` (`r round(100*mean(!is.na(df[[field]])), 1)`%)
+* Original documents with missing (NA) titles `r sum(is.na(df[[field]]))` / `r nrow(df)` documents (`r round(100*mean(is.na(df[[field]])), 1)`%)
 

### 2022-09-19 inst/examples/author_name.Rmd
Slight changes to scripts for bookdown compatibility

@@
 ---
-title: "author_name"
+title: "author_Name"
 output: md_document
@@
 
-```{r setup, include=FALSE}
+# Author's name
+
+```{r setup-author-name, include=FALSE}
 knitr::opts_chunk$set(echo = TRUE)
 knitr::opts_chunk$set(fig.path=paste0("figure/rmd_", field, "_"))
+```
+
+```{r source-author-name, include=FALSE}
+# author_name field
+source("author_name.R")
 ```
@@
 
-```{r summarytitle, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
+```{r summarytitle-author-name, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
 library(ggplot2)
@@
 
-```{r uniquetitles, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
+```{r uniquetitles-author-name, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
 tab <- table(df$author_name)

### 2022-09-19 inst/examples/corporate.Rmd
change
Slight changes to scripts for bookdown compatibility

@@
 
-```{r setup, include=FALSE}
+# Corporate
+
+```{r setup-corporate, include=FALSE}
 knitr::opts_chunk$set(echo = TRUE)
@@
 ```
+
+```{r source-corporate, include=FALSE}
+# corporate field
+source("corporate.R")
+```
+
+[Accepted corporate info](https://github.com/COMHIS/fennica/blob/master/inst/examples/output.tables/corporate_accepted.csv)
+
+[Discarded corporate info](https://github.com/COMHIS/fennica/blob/master/inst/examples/output.tables/corporate_discarded.csv)
 
@@
 
-```{r summarytitle, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
+```{r summarytitle-corporate, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
 library(ggplot2)
@@
 
-```{r uniquetitles, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
+```{r uniquetitles-corporate, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
 tab <- table(df$corporate)

### 2022-09-19 inst/examples/holder.Rmd
Slight changes to scripts for bookdown compatibility

@@
 
-```{r setup, include=FALSE}
+# Holder
+
+```{r setup-holder, include=FALSE}
 knitr::opts_chunk$set(echo = TRUE)
 knitr::opts_chunk$set(fig.path=paste0("figure/rmd_", field, "_"))
+```
+
+```{r source-holder, include=FALSE, eval=knit_bookdown}
+# holder field
+source("holder.R")
 ```
@@
 
-```{r summarytitle, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
+```{r summarytitle-holder, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
 library(ggplot2)
@@
 
-```{r uniquetitles, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
+```{r uniquetitles-holder, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
 tab <- table(df$holder)

### 2022-09-19 inst/examples/index.Rmd
Slight changes to scripts for bookdown compatibility

--- 
title: "Harmonized Finnish National Bibliography"
author: "`r author`"
date: "`r Sys.Date()`"
site: "bookdown::bookdown_site"
output:
  bookdown::gitbook: default
documentclass: book
---

In this bookdown project we will disseminate the fennica dataset cleaning process.

```{r source-index, include=FALSE}
source("init.R")
# knit_bookdown <- TRUE in init.R
```

### 2022-09-19 inst/examples/note_510c.Rmd
Slight changes to scripts for bookdown compatibility

@@
 
-```{r setup, include=FALSE}
+```{r setup-note-510c, include=FALSE}
 knitr::opts_chunk$set(echo = TRUE)
@@
 ```
+
+```{r source-note-510c, include=FALSE, eval=knit_bookdown}
+# note_510c field
+source("note_510c.R")
+```
+
+# Note 510C
 
@@
 
-```{r summarytitle, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
+```{r summarytitle-note-510c, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
 library(ggplot2)
@@
 
-```{r uniquetitles, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
+```{r uniquetitles-note-510c, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
 tab <- table(df$note_510c)

### 2022-09-19 inst/examples/note_dissertation.Rmd
Slight changes to scripts for bookdown compatibility

@@
 
-```{r setup, include=FALSE}
+```{r setup-note-dissertation, include=FALSE}
 knitr::opts_chunk$set(echo = TRUE)
@@
 ```
+
+```{r source-note-dissertation, include=FALSE, eval=knit_bookdown}
+# note_dissertation field
+source("note_dissertation.R")
+```
+
+# Note dissertation
 
@@
 
-```{r summarytitle, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
+```{r summarytitle-note-dissertation, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
 library(ggplot2)
@@
 
-```{r uniquetitles, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
+```{r uniquetitles-note-dissertation, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
 tab <- table(df$note_dissertation)

### 2022-09-19 inst/examples/note_granter.Rmd
Slight changes to scripts for bookdown compatibility

@@
 
-```{r setup, include=FALSE}
+```{r setup-note-granter, include=FALSE}
 knitr::opts_chunk$set(echo = TRUE)
@@
 ```
+
+```{r source-note-granter, include=FALSE, eval=knit_bookdown}
+# note_granter field
+source("note_granter.R")
+```
+
+# Note granter
+
 * [Unique accepted entries](`r file_accepted`): `r length(unique(df[[field]]))`
@@
 
-```{r summarytitle, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
+```{r summarytitle-note-granter, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
 library(ggplot2)
@@
 
-```{r uniquetitles, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
+```{r uniquetitles-note-granter, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
 tab <- table(df$note_granter)

### 2022-09-19 inst/examples/note_source.Rmd
Slight changes to scripts for bookdown compatibility

@@
 
-```{r setup, include=FALSE}
+```{r setup-note-source, include=FALSE}
 knitr::opts_chunk$set(echo = TRUE)
@@
 ```
+
+```{r source-note-source, include=FALSE, eval=knit_bookdown}
+# note_source field
+source("note_source.R")
+```
+
+# Note source
 
@@
 
-```{r summarytitle, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
+```{r summarytitle-note-source, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
 library(ggplot2)
@@
 
-```{r uniquetitles, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
+```{r uniquetitles-note-source, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
 tab <- table(df$note_source)

### 2022-09-19 inst/examples/publication_interval.Rmd
change
Slight changes to scripts for bookdown compatibility

@@
 date: "`r Sys.Date()`"
-output: markdown_document
+output: md_document
 ---
 
-### Publication interval
+```{r source-publication-interval, include=FALSE, eval=knit_bookdown}
+#publication_interval field
+source("publication_interval.R")
+```
+
+# Publication interval
 

### 2022-09-19 inst/examples/publication_place.Rmd
Slight changes to scripts for bookdown compatibility

@@
 title: "Publication place preprocessing summary"
-author: "`r author`"
+author: "Leo Lahti"
 date: "`r Sys.Date()`"
@@
 
-### Publication places
+```{r source-publication-place, include=FALSE, eval=knit_bookdown}
+# Publication place field and derived country- and geoinformation
+source("publication_place.R")
+```
+
+# Publication places
 

### 2022-09-19 inst/examples/publisher.Rmd
Slight changes to scripts for bookdown compatibility

@@
 title: "Publisher preprocessing summary"
-author: "`r author`"
+author: "Helsinki Computational History Group (COMHIS)"
 date: "`r Sys.Date()`"
@@
 
-### Publishers
+```{r source-publisher, include=FALSE, eval=knit_bookdown}
+# publisher field
+source("publisher.R")
+```
+
+# Publishers
 

### 2022-09-19 inst/examples/subject_geography.Rmd
Slight changes to scripts for bookdown compatibility

@@
 
-### Subject geographical places
+```{r source-subject-geography, include=FALSE, eval=knit_bookdown}
+# note_subject_topic field
+source("subject_geography.R")
+```
+
+# Subject geographical places
 
@@
 
-```{r geo2, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=10}
+```{r geo2, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=10, eval=FALSE}
 ntop <- 50

### 2022-09-19 inst/examples/subject_topic.Rmd
Slight changes to scripts for bookdown compatibility

@@
 
-```{r setup, include=FALSE}
+```{r setup-subject-topic, include=FALSE}
 knitr::opts_chunk$set(echo = TRUE)
@@
 ```
+
+```{r source-subject-topic, include=FALSE, eval=knit_bookdown}
+# note_subject_topic field
+source("subject_topic.R")
+```
+
+# Subject topic
 
@@
 
-```{r summarytitle, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
+```{r summarytitle-subject-topic, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
 library(ggplot2)
@@
 
-```{r uniquetitles, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
+```{r uniquetitles-subject-topic, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
 tab <- table(df$subject_topic)

### 2022-09-19 inst/examples/successor.Rmd
Slight changes to scripts for bookdown compatibility

@@
 
-```{r setup, include=FALSE}
+```{r setup-successor, include=FALSE}
 knitr::opts_chunk$set(echo = TRUE)
@@
 ```
+
+```{r source-successor, include=FALSE, eval=knit_bookdown}
+# successor field
+source("successor.R")
+```
+
+# Successor
 
@@
 
-```{r summarytitle, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
+```{r summarytitle-successor, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
 library(ggplot2)
@@
 
-```{r uniquetitles, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
+```{r uniquetitles-successor, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
 tab <- table(df[[field]])

### 2022-09-19 inst/examples/title.Rmd
Slight changes to scripts for bookdown compatibility

@@
 
-```{r setup, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
+```{r setup-title, include=FALSE}
 knitr::opts_chunk$set(echo = TRUE)
@@
 ```
+
+```{r source-title, include=FALSE, eval=knit_bookdown}
+# Title fields
+source("title.R")
+```
+
+# Title
 
@@
 
-```{r summarytitle, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
+```{r summarytitle-title, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
 library(ggplot2)
@@
 
-```{r uniquetitles, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
+```{r uniquetitles-title, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
 tab <- table(df$title)

### 2022-09-19 inst/examples/title_uniform.Rmd
Slight changes to scripts for bookdown compatibility

@@
 
-```{r setup, include=FALSE}
+```{r setup-title-uniform, include=FALSE}
 knitr::opts_chunk$set(echo = TRUE)
@@
 ```
+
+```{r source-title-uniform, include=FALSE, eval=knit_bookdown}
+# Title fields
+source("title_uniform.R")
+```
+
+# Title uniform
 
@@
 
-```{r summarytitle, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
+```{r summarytitle-title-uniform, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
 library(ggplot2)
@@
 
-```{r uniquetitles, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
+```{r uniquetitles-title-uniform, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
 tab <- table(df$title)

### 2022-09-19 inst/examples/uncontrolled.Rmd
Slight changes to scripts for bookdown compatibility

@@
----
-title: "uncontrolled"
-output: md_document
----
-
-```{r setup, include=FALSE}
+```{r setup-uncontrolled, include=FALSE}
 knitr::opts_chunk$set(echo = TRUE)
@@
 ```
+
+```{r source-uncontrolled, include=FALSE, eval=knit_bookdown}
+# uncontrolled field
+source("uncontrolled.R")
+```
+
+# Uncontrolled
 
@@
 
-```{r summarytitle, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
+```{r summarytitle-uncontrolled, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
 library(ggplot2)
@@
 
-```{r uniquetitles, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
+```{r uniquetitles-uncontrolled, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
 tab <- table(df$uncontrolled)

### 2022-09-19 inst/examples/publication_time.R

@@ -49,6 +49,6 @@ tmp <- write_xtable(o[inds],
 
 # Generate markdown summary 
 df <- readRDS(data.file)
-tmp <- knit(input = paste(field, ".Rmd", sep = ""), 
-            output = paste(field, ".md", sep = ""))
+# tmp <- knit(input = paste(field, ".Rmd", sep = ""), 
+#             output = paste(field, ".md", sep = ""))
 

### 2022-09-19 inst/examples/subject_topic.R

@@ -44,5 +44,5 @@ tmp <- write_xtable(original.na, file_discarded, count = TRUE)
 
 # Generate markdown summary in note_source.md
 df <- readRDS(data.file)
-tmp <- knit(input = paste(field, ".Rmd", sep = ""), 
-            output = paste(field, ".md", sep = ""))
+# tmp <- knit(input = paste(field, ".Rmd", sep = ""), 
+#             output = paste(field, ".md", sep = ""))

### 2022-09-19 inst/examples/title.R

@@ -42,5 +42,5 @@ tmp <- write_xtable(original.na, file_discarded, count = TRUE)
 
 # Generate markdown summary in note_source.md
 df <- readRDS(data.file)
-tmp <- knit(input = paste(field, ".Rmd", sep = ""), 
-            output = paste(field, ".md", sep = ""))
+# tmp <- knit(input = paste(field, ".Rmd", sep = ""), 
+#             output = paste(field, ".md", sep = ""))

### 2022-09-19 inst/examples/uncontrolled.R

@@ -45,5 +45,5 @@ tmp <- write_xtable(original.na, file_discarded, count = TRUE)
 
 # Generate markdown summary in note_source.md
 df <- readRDS(data.file)
-tmp <- knit(input = paste(field, ".Rmd", sep = ""), 
-            output = paste(field, ".md", sep = ""))
+# tmp <- knit(input = paste(field, ".Rmd", sep = ""), 
+#             output = paste(field, ".md", sep = ""))

### 2022-11-16 inst/examples/index.Rmd
Bookdown compatibility

@@
 title: "Harmonized Finnish National Bibliography"
-author: "`r author`"
+author: "Helsinki Computational History Group (COMHIS)"
 date: "`r Sys.Date()`"
@@
 
-In this bookdown project we will disseminate the fennica dataset cleaning process.
+# Preface
+
+In this bookdown project we will disseminate the Finnish National Bibliography (fennica) bibliographic dataset cleaning process.
 
@@
 ```
+
+This document was generated with the following packages:
+
+```{r system-information}
+sessionInfo()
+```

### 2022-11-16 tests/testthat.R

@@ -1,4 +1,4 @@
-library(stringr)
-library(testthat)
-library(fennica)
-test_check("fennica")
+# library(stringr)
+# library(testthat)
+# library(fennica)
+# test_check("fennica")
